\section{chapter 277}






 sungwoo pulled out the “fire spirit stone (higher level)” from his bag.
 it was a legendary grade item he obtained after hunting the salamander.
 when he merely took it out, the inside of the helicopter got even warmer.
“hug this when you sleep.
”krrrrrrrrr-as if he understood sungwoo’s words, the baby dragon rolled his body after putting the fire spirit stone under his belly.
 then, he moved the chicken skeleton to cover his body.
“oh, i’ve come to think of that dragon’s name, sungwoo!”sungwoo asked hanho to name the baby black dragon the other day.
 hanho was writing something down in his notebook for some time last night.
 it seemed that he finally thought of one name for the dragon.
“how about dark fire?”“what?”sungwoo could not believe his eyes because the dragon’s new name was ridiculous.
“not good enough? well, i have another one because i know you are so picky.
 how about the caesar of korea? isn’t it majestic and meaningful? cai as the nickname? if you don’t like it, either, how about chaos empe…”“stop it! it’s my mistake to have asked you for it.
”come to think of it, it was a mistake for sungwoo to ask him such a favor because he was stupid enough to coin his nickname as something like the strongest holy thief asura.
“how come you coined such a name? hanho, didn’t you say you once raised a hamster before? what was his name?” jisu asked.
“it was vladimir.
 why?”“what the heck? hamster’s name was vladimir?”hanho nodded with a happy smile.

“isn’t it great? he gave birth to several babies, so i named them volkov, sergey, and anastasia.
 oh, i also raised a stag beetle, so i gave him the name musashi miyamoto, and i gave a beetle the name kumgang fire.
”it was the moment when the law that beauty was subjective was broken.
after all, jisu came up with one name.
“how about mir? in pure korean, it means yong or a sort of dragon.
 dragon is a little different from yong, but isn’t it cute and easy to call? i think it’s better than vladimir…”“sounds good.
 let me take that name.
”sungwoo immediately adopted her suggestion.
 then, hanho got upset right away.
“oh, my god! how insensitive you are! i stayed up last night, thinking about the baby dragon’s name! what’s the difference between vladimir and mir?”however, none of them accepted his claim.
meanwhile, the helicopter arrived at yeongdeungpo station.
“we’re landing soon!”yeongdeungpo station, looking down from above, was almost covered with pure white plastic.
it hadn’t snowed.
 the water vapor in the air condensed and turned to frost.
 as a result, the roofs of buildings, the exterior walls, the asphalt roads, sidewalks, and various items were all covered with ice.
“i don’t know what those siberian guys did to seoul, but if we don’t do anything, isn’t the whole korean peninsula going to turn into another siberia?”minhum nodded when hanho spoke.
“all the people here are on the verge of freezing to death, but they can’t escape to other areas.
 the siberian guys won’t let people escape without the crusader team defending them.
”if the siberian hunters decided to hunt the people, they could annihilate the fleeing liberation guild members instantly.
this was why the magic of dealing with fire or ice was the most useful, but at the same time, the most destructive because it could destroy a wide area most efficiently.

“damn it! is the ice age really coming?”hanho spoke jokingly, but it could be their real purpose.
***the russian guys noticed that sungwoo finally arrived.
 even though sungwoo and his party moved in secret, they got caught.
 and surprisingly, they made demands for negotiation.
“i think they must have a hidden purpose.
 their purpose is not the negotiation itself.
”minhum was skeptical about the value of the negotiation because they made the demands for negotiation only after slaughtering 50 people in the first place.
 after that, the crusaders team was annihilated.
“will you still go to the negotiating table?”“sure, let me go and see them.
”negotiating with them was not important to sungwoo.
 he needed to check their movements at a close distance.
“it might be a trap, so let me deploy the maximum number of our wide area surveillance team around the negotiation place.
”“okay.
 if we get a chance, we’ll be able to see whether the crusader team is still alive while they are distracted.
”“sure…”the negotiation place was yongsan station, almost halfway between yeongdeungpo station and mt.
 namsan.
 sungwoo and his party moved to yongsan station at the scheduled time.
krrrrrrr- krrrrrrrr-however, the problem was that the baby dragon, mir, did not want to separate from sungwoo.
 in the end, it was only after jisu hugged and put him to sleep that sungwoo could move.
“before he wakes up, leave quickly.
 i will be waiting nearby with him.
 if you have a problem, let me run to you right away.
”it would be most reassuring for him to have jisu nearby because she has transcendental senses, but for now, it was important for her to keep mir quiet.
‘if they discover i have a baby dragon, they might intend to aim for it by all means.
’it could be the worst scenario if sungwoo had to fight them while defending that little and fragile baby dragon.
‘man, he’s really a nuisance!’was it because he was just born? the baby dragon wouldn’t be separated from sungwoo, which was a big headache.
 so, sungwoo just hoped he could grow up quickly and be independent.
“let’s go.
”sungwoo went to the meeting place with hanho and minhum.
 it was yongsan station square.
“hi.
 come on.
”they were already waiting there.
 a woman wearing a white shapka greeted sungwoo’s party.
behind her were several big guys here and there.
 they were sipping something with a sullen expression.
 it was vodka.
‘they are siberian hunters.
’sungwoo felt at once that they were rough guys living in that cold area.
 although the temperature dropped down to minus 28 degrees celsius, some of them took off their jackets as if they were hot.
‘where is the boss?’however, sungwoo could not see the man he had seen in the memory fragments, druid, the no.
 1 in the russian server rankings.
 however, the huge brown bear he was carrying with him was lying on one side of the square.
grrrrrrrrrr-even though the bear was lying on the floor, he looked as big as a bus.
sungwoo was distracted by the huge build of that bear.
‘man, that bone looks great.
 i covet that.
’

at that moment, the woman wearing shapka waved her hand at sungwoo.
 sungwoo looked at her with a frown.
“hey, i can’t stand it anymore.
 what are you looking at so intensively when you have a beautiful lady in front of you?”at that moment, sungwoo was going to say, ‘i don’t need your bones!’, but stopped.
“are you in charge of this organization?”“no, i’m not.
”with an irritated expression, she took out a cigarette and put it in her mouth,then, she lit it and opened her mouth.
“i am tatana, head of the eastern guild of the siberian hunters guild.
 our tsar is still asleep after getting drunk.
”tsar? isn’t it a title referring to the emperor of the russian empire? since he was the no.
 1 player of the russian server, he was given such a huge nickname.
‘the chinese emperor or the japanese sword master are all addicted to empty formalities.
’by the way, how come that guy is sleeping and drunk, in this situation? sugnwoo was shocked by his arrogant and complacent attitude.
or he might have set the trap for sungwoo by tempting him to let down his guard.
 so, sungwoo was on alert all the time.
he immediately asked her because he didn’t want to drag on.
“so, what do you want at the negotiation?”“oh, you’re so impatient! i thought you might want to introduce yourself first… well, it’s simple.
”tatana took a long puff of the cigarette and opened her mouth, frowning her eyebrows.
“our client gave us 200 million gold in return for smashing your neck and the whole korean server.
 so, this is a 200 million gold fight.
 let me give you a question.
 how much do you think can stop the fight between us?”

 