\section{chapter 468}

it looked as if they were on the verge of annihilation.
 




"sungwoo?"fortunately, sungwoo arrived there on time!sungwoo's undead army immediately charged at the hell creatures and wiped them away around that area.
"are you okay?"junghoon's face was covered with blood, but it seemed that his life was not in danger.
 perhaps he healed his wounds through recovery skills.
"i am okay.
 but i don't know what happened to others.
"there were only about 30 people in this place right now.
 but there were still many others here and there in the ruins, including jisu, hanho, li wei, and chen.
"the demon king is still alive and well.
"hiding behind a pile of fallen trees, they looked at the demon king towering like a mountain in the distance.
bang! red flames scattered over the demon king's head with the sound of an explosion.
 it was dragon breath.
 suddenly, the red dragon passed over his head.
"isabella looks fine.
""you bet.
"isabella didn't seem to have taken too much damage in the chaotic situation.
 "i saw her covering her body with a thick shield the moment the lightning struck.
"a dragon like her used other skills than dragon breath or dragon fear.
 the dragon race was also a wizard who reached the climax of their power from the beginning.
thud! thud! thud!a fierce battle between the two continued.
 isabella took advantage of her aerial mobility to pressure the demon king.
"looking at their fight, it looks like isabella won't hold out for long.
 we need to prepare for our next move," sungwoo said.
 
in his eyes, isabella did not seem to be able to defeat the demon king.
the demon king was also healing his wounds in real-time while fighting against isabella.
new novel chapters are published on lightnovelworld.
c‌omgrrrr- grrrr- grrrr-hell creatures climbed up to the demon king's wounds and became entangled, then their bodies melted and began to merge with the demon king's body.
 that's how his bones and skin were restored.
"man, he has regenerated his head completely," said junghoon, pointing at the demon king's right head.
 "as long as those hell creatures are with him, the demon lord can continue to heal his wounds!"it was a pretty frustrating moment.
 even though they inflicted lots of damage on the demon king with a frontal attack, he would continue to recover unless they killed him once and for all.
at that moment a guard on the watch out shouted, "look over there! that dragon…"everyone turned their heads toward the demon king.
the demon king's arms stretched like tentacles and got entangled with isabella's wings.
 in other words, she was caught by him.
 'the fight is over.
'the moment she lost her aerial mobility, the only weapon with which she could confront the demon king, there was nothing she could do.
the demon king shot red rays towards the red dragon who got stuck and couldn't move at all.
six rays of light hit isabella's body, throwing her huge body into the sky.
shortly afterward, her huge body was flagged before being thrown into the amazon rainforest.
"oh no! i can't believe that!""how come even the dragon was defeated by the demon king?"everybody was shocked, lamenting here and there.
 sungwoo had a lot of thoughts at the moment.
 'as long as he controls his territory here, we can't counterattack him effectively.
'but the demon king could maintain his control of this area for only 20 minutes, but sungwoo's allies could be devastated during that span, too.

sungwoo thought hard about what to do, but he could not figure it out quickly.
 isabella fell helplessly.
kugugugugu-her huge body fell over the rainforest, maiming all the plants around her.
whooooooooo-she wasn't killed yet.
 but she couldn't move.
 she was hit with a whopping six beams.
the most up-to-date novels are published on lightnovelworld.
com"hey, isabella…"then someone approached her.
"how could you do this to me?"it was grace whose body was tanned by flames.
 although dragon breath brushed aside her slightly, grace was gasping for breath after she suffered irreparable burns.
trembling hard, she scanned isabella's body with hateful looks.
 "isabella, what did i do wrong? all i did was just show loyalty to a monster like you!"she was watching the battle in the distance, and when she saw isabella falling, she ran to isabella through the portal, full of revenge.
 "i'm going to take your life!"she then took out the item she had saved to get even on her.
 it was a green stone.
[item information]- name: stone of prayer- rank: myth- classification: consumption- effect: when your 'spirit affinity' has reached a certain level, you can summon the 'spirit king' of a specific element through this item.
it was an item with which she could summon the 'spirit king'.
"you took everything from me, so i will use everything available to kill you.
"if she summoned the strongest spirit king, he could kill isabella who fell after passing out.
she held the 'stone of prayer' in her left hand and stretched her right hand toward isabella's head.
"ouch!"at that moment something grabbed her ankle and lifted her, hanging her upside down.
 grace instinctively waved her hands to create a breeze.
 but a cold rope came out suddenly and bound her hands.
"argh! who the hell are you?"someone walked out from among the fallen trees.
"are you frustrated?"visit lightnov­elworld.
c‌om for a better experienceit was li wei.
 water spirits came up from the ground and strangled grace's body.
"are you so frustrated because you were defeated?""what the heck did you say?"li wei nodded, then said, "yeah, i know your feelings.
 i think you must be frustrated when you are so shabby like this.
 but…"li wei slowly raised his hand.
 the water spirit moved according to her movement, then wrapped her neck.
"cough, cough!"then the water spirit tightened its grip on her neck.
 "happily, hundreds of thousands won't feel frustrated because you are suffering now.
"this time the water spirit's pressure was becoming stronger now.
 

"i'm sorry, but you're right to feel frustrated.
"grace became so weak now that she let go of the grey stone in her hand, which fell on the ground.
 it rolled toward grace's feet.
"this one is…"li wei picked up the stone and said, "gosh, i can do something with this!"when even isabella collapsed, the demon king cast a glance on the ground.
 then he began to chase the enemy players who were almost near death.
 in other words, he got down to killing the remnants.
 "retreat!""but there are still survivors…""too late!"those players who were within the demon king's striking range hurriedly began to retreat.
 but the demon king's body, which had been stuck in the ground, began to slowly rise, then his lower body made of millions of bundles of tentacles appeared.
 they continued to grow like cell division, but when they gathered and could bear their weight to some extent, they seemed to be able to move.
sungwoo hasn't yet figured out the best solution to tackle the current difficulties.
'the demon king's going to finish it in 20 minutes.
'the demon king intended to move in person, and attack the players.
he knew that if he lost his control of this area 20 minutes later, he was going to be dealt a big blow once again by sungwoo's allies.
visit lightnovelworld.
com for the best novel reading experience'i have to hold out until the end.
"but could he hold out? as long as his ability to summon his subordinate spirits was restrained, there was almost nothing he could do.
at that moment he raised one of his hands slowly.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 