\section{chapter 167}

                             




 jisu slowly pulled her sword.
“oh, my god…”a group of human monsters was strewn here and there under her feet.
 behind her were also the corpses of human monsters piled up along the corridor.
the members of the surveillance team snuck out of the classroom at the end of the corridor.
their eyes popped out when they saw the corpses everywhere.
“so, is the fight over?”“i can’t believe this.
 how could he kill all of them in only a few minutes?”they were also the elite members of the liberation guild, but they thought it was unthinkable to survive, let alone fight the monsters, in a situation like this.
however, the power of the necromancer and his party was beyond imagination.
“it looks like we’re done killing the monsters inside the building, except for one.
”“one more? where is it?”quazzeeeeeek!at that moment, the door of a classroom broke, and a cloth monster and hanho appeared, tangled with each other.
 the cloth monster struck hanho’s neck with his fierce nails.
clang!however, his attack was blocked by hanho’s shield.
“ahhhhh! you are not done attacking me yet?”puck! puck! puck!while being dragged around, hanging on to the monster’s legs, hanho stabbed his knife into the monster’s body here and there.
since the cloth monster had a weak defense, hanho could strike him down with the dagger.
“it’s me, the strongest thief on earth! come on! no more?”catching his breath, hanho looked at jisu.
 she nodded.
since sungwoo killed the monster snipers surrounding the school building, hanho and jisu could get rid of the monsters that infiltrated into the building easily.

“man, it’s really tough to keep this shield continuously.
”he passed over the bodies that covered the floor and looked out the window.
“is he winning now?”outside the building, there was still a melee between the undead and the members of the evolution society.
 but as time passed, the situation was more favorable to the undead.
sungwoo already dealt a deadly blow to them, so the undead continued to increase in number after they were resurrected, while the members of the evolution society kept decreasing.
the enemies didn’t fire silver arrows anymore as if they could not use the arrows indefinitely.
thud! kuuuu-gung!however, the fierce fight taking place in the street beyond the shopping mall was unpredictable.
kugugugugugugugugu―another five-story building collapsed.
“the fight is almost over…”the fight between the two human monsters was devastating everything in the center of the city.
***the werebull crouched then bounced off the floor.
 it seemed like a huge rugby ball was flying.
 however, sungwoo slipped back to one side and avoided his rush.
kwaaaaakwang!the monster hit the truck with his body and blew it away.
pitter-patter, pitter-patter!it started to rain.
“hey, why are you obsessed with running away? didn’t you just show off your strength before?”the monster was already holding his head high.
 after he had injected himself with an unknown drug a little while ago, he seemed to have more than doubled his muscle strength than before.
when he was not pushed around by sungwoo anymore, he ruthlessly charged at sungwoo.
“i’m stage 4.
 it’s similar to your awakening!”the monster raised his fist and smiled at sungwoo.
the human monster had a stage instead of a level.
 the highest stage human monster sungwoo had dealt with until then was stage 2.

however, it seemed that this monster reached stage 4 by temporarily upgrading after injecting the ampoule.
 as a result, he was showing terrific strength incomparable to the second stage.
now, it was raining heavily.
 the monster once again crouched his body.
seizing the moment, sungwoo prepared the evil spirit bomb.
-‘evil spirit bomb’ is embedded in your weapon.
a black wave rose in sungwoo’s right hand.
 the moment the monster jumped off the ground, sungwoo reached out his right hand.
 the evil spirit bomb spread everywhere.
but the monster threw himself to the right with tremendous agility.
 the evil spirit bomb missed him and hit the shopping mall.
ku-o-o-o-o-gung!the first floor of the shopping mall was completely crushed, causing the whole building to collapse in a minute.
but the monster rolled over the floor, bounced his body up, and rushed at sungwoo.
so, sungwoo went onto the street and hid behind a van.
bang! thud! kuuuuuuuuuuuung!as if he was a bulldozer, the monster pushed everything standing in the way.
but the monster, who was running wildly, suddenly staggered and stopped all of a sudden.
“ugh?”-you have been poisoned.
it was only then that the monster began to consider the existence of the rain that wet his whole body and the clouds floating in the sky.
 he found the color of the clouds was a bizarre purple hue.
“what kind of trick are you trying to use again?” shouted the monster.
it seemed that the monster thought the raindrops fell suddenly because of unpredictable weather.
 since this was the first time sungwoo used this skill in this fight, the monster obviously didn’t know it was sungwoo’s new skill.
for sungwoo, waiting for the opportunity to use it instead of using it recklessly under siege was a good decision.
“cough! cough!”the monster stumbled, exposed to the deadly poison.
 although it wasn’t toxic enough to kill him, it was enough to disrupt his physical function.
“it’s over.
”to put an end to this fight, sungwoo prepared the final move, a new skill.
“twilight raid.
”[skill information]-name: twilight raid-grade: artisan-category: active-consumption: 40 mana, 20 souls*it corrupts the souls accumulated through ‘soul exploitation’ and uses that energy to move at high speed.
 inflicts powerful magic damage to the target enemy at the landing point and binds the enemy with the “ghost hand” for 10 seconds.
 (10 minutes of cooldown)-you have started twilight raid.
’soon, 20 souls came out of sungwoo’s body.
 they trembled restlessly and began to spread around sungwoo’s body.
 then, sungwoo’s body was mixed with a black wave.
sungwoo turned into a black ghost and flew at a tremendous speed toward the target.
goooooooooooo-a black shadow swallowed the werebull like a hurricane.
“argh! ahhhhhhhhhhh!”the werebull struggled in pain, but he couldn’t escape.
 his heavy body floated in the air and began to be swept away, like a stuffed toy blown away in a tornado.
gooooooooo!the black tornado passed tens of meters in seconds.
 it got out of the alley while moving freely among the vehicles.
 then, it landed on the blood-stained ground.
whooooo-when the black smoke went away, sungwoo was standing in the center.
 and it was the playground of the school.
“kueeeeeeh!”the werebull, which fell under sungwoo’s feet, could not even raise his body after suffering tremendous damage.
 but that wasn’t the end.
-you are bound by the “ghost hand.
”twenty black hands came up from the ground.
 then, they grabbed his neck and limbs and made it impossible for him to move for ten seconds.
“do you have another ampoule? hope not!”sungwoo then lifted the grim reaper, whose lock was released.
 he aimed at the monster’s neck, who was completely defenseless.


“kuuuuuuuuuuh…”the fight was over.
“flagbearer!”“even our flag bearer…”the members of the evolution society, who were engaged in fierce fighting against the undead, were also on the defensive.
 and when they witnessed the defeat of the werebull, their only hope, their morale was completely broken.
“explode this area! blow it all away…”the werebull muttered.
since their operation was unsuccessful, the enemies now desperately attempted to target the necromancer at the risk of their lives.
however, there was no chance that sungwoo would allow their attack.
he lifted the grim reaper.
wooooooooooong-at that moment, the space in front of their eyes distorted into an oval.
‘portal?’and beyond that appeared a white wolf dressed in black scaled armor.
“brother!”“oh, he’s the white flag bearer!”it was the human monster with psychometric skills.
 as soon as he appeared, he stretched his palm toward sungwoo.
‘wow!’sungwoo’s body floated in the air and was pushed back.
 he flew about 5 meters and landed on the ground.
‘damn it! why did he appear at this moment?’when sungwoo started counter-attacking the monster, there was no reinforcement unit to support the monster, so he thought that the enemy troops were all destroyed.
but he didn’t expect at all such a giant monster would appear in this crucial situation.
‘this is a big problem!’ 

 