\section{chapter 387}

chapter 387: war for war (4)when ahn asked him directly, wong took a deep breath, then responded with a smirk.





“i’m sure the emperor will crush the necromancer.
”“pardon? what the heck did you …”ahn didn’t seem to expect this kind of reply from him at all.
 startled, ahn tried to interrupt him, but wong continued, shaking his head, “i’m not finished yet.
 ladies and gentlemen on the korean server, i’m sorry to tell you this, but you can’t beat the unified chinese server.
 you were just lucky in the last war.
”“ah, wait a minute…”“so, please don’t have any vain hope.
 reporter ahn, i’ve been watching the necromancer’s fighting a lot on tv.
 but you, and the players on the korean server, haven’t seen the fighting of the emperor’s army, right?”reporter ahn was speechless, but wong continued, not caring at all, “oh my god…alright, necromancer, has he ever witnessed the emperor’s power in person? no, right?”after that, all kinds of curses and abusive words began to appear in the chat window.
wong saw them, too, but he didn’t stop.
“on the other hand, the emperor probably knows the necromancer well.
 so, he will be prepared very well.
 the emperor is not stupid.
 i think the emperor will devastate him after finding out his weakness.
”he then raised his index finger and started pointing at the camera.
“i’m sorry, but this is the reality.
 ladies and gentlemen on the korean server, you have to judge rationally.
 please wake up!”***
- ‘troop deployment (confirmed location)’ will start in the next 12 hours.
* the ‘list’ of deployed troops will not be disclosed.
the korean server and the chinese server were given 12 hours for troop deployment.
but this time there was no ‘cross-selection’ or ‘disclosure of the troops’ like before.
 as the type of war was different, its detailed rules were also different.
“alright, let’s double check the final war preparation!”for the remaining 12 hours, the world tree camp was busy preparing for the war with the chinese server.
 they checked out the items and troops, and at the same time, they hurriedly refurbished the castle wall and maintained the airships.
they moved newly made flying weapons to the castle wall and prepared the materials for an emergency repair in advance just in case the wall collapsed.
inho and minhum, who were in charge of defending the fortress, were checking the whole process.
“in the last battle, the escape routes on the wall were messed up.
 this time we need to clearly designate the escape route.
”“oh, we need to come up with a plan to quickly replenish the troops in the area where we suffered a lot of casualties last time.
 since we were running around in chaos, trying to make up for the killed soldiers, we invited a more fierce attack by the enemy.
”since they had experience defending the wall in the last battle, they knew their weakness very well, so they could make up for it one by one.
meanwhile, sungwoo and kyungsoo went up to the highest point of the castle wall and looked down on the surrounding area.

“sungwoo, we have a big problem,” said kyungsoo, pointing to the edge of the city center.
it was the endpoint of the invisible barrier formed in a hemispherical shape centered on the world tree.
“as the world tree grows, the invisible barrier has been extended too far.
 so, there is a gap of about two kilometers between the invisible barrier and the castle wall.
”with the continual growth of the world tree, the ‘shadow of the divine tree’ was strengthened, and because of that, the invisible barrier also went out too far.
“gosh, the castle wall and the invisible barrier should be in line for the best defense…”initially, the construction of the castle wall was tailored to the invisible barrier because both of them could enjoy synergy effects when they were grouped.
however, they were located far from each other, so it was certain that the invisible barrier would be broken through while the castle wall would be exposed to the enemy’s attack without the protection of the invisible barrier.
after thinking hard about the problem, sungwoo pointed to the downtown area between the invisible barriers.
 it was a place where old buildings mushroomed but turned into a wild place because it had been abandoned for a long time.
sungwoo said, “we can’t pull the invisible barrier or push out the castle wall, so we have to find a way to use the gap between the invisible barrier and the castle wall to delay the enemy’s attack.
”“um…do you mean something like a trap?’sungwoo nodded, then said, “yes, we need something like that.
 if we set a trap, the enemy won’t be able to reach the castle wall even if they break through the invisible barrier.
 then, we can defeat them with artillery attack.
”after hearing sungwoo’s explanation, kyungsoo also visualized some sort of attack in his mind.
instead of neglecting the gap between the castle wall and the invisible barrier, he could use it as something like a moat.
“well, i’ll try to come up with some feasible ideas by having our workshop work on it.
 i think we have to hurry up since we don’t have much time.
”although it was not the best idea, there was always an alternative.
kyongsoo hurriedly turned around to save even a little time.
at that moment sungwoo called him again, “ah, kyungsoo.
”then he mentioned something important.
“bury the monster corpses deep underground there, so the enemies stepping on the ground can’t notice it.
”meanwhile, the blacksmiths and architects have not been out for a second since last night when they went into the hephaestus’s forge.
clang! clang! clang! clang!hearst’s shouts were constantly bursting out along with the sound of hammers from the brazier where they were working.
“sh*t! i warned you that if you strike it disproportionately like that, it won’t have any durability after you finish it.
”that’s the way he shouted at the blacksmiths under his control.


“hey, i think i have to pound on your head first before you strike that metal!”the blacksmiths of the world tree camp were shocked by the way hearst treated them roughly.
 at the same time, they were emboldened to do better to humble his pride.
‘how come that american blacksmith appeared all of a sudden and acts like our supervisor? let me do better and knock the conceit out of him…’the blacksmiths affiliated with the world tree camp worked even harder, but hearst was harder and harder on them.
“hey, you still don’t understand what i’m talking about? you don’t get it? you are now making the worst weapon! are you going to sacrifice your fellows to the enemy with this shallow weapon? uh? it’s not me who is directing you to do this, but your captain wants me to make these weapons within 12 hours! got it?”as a matter of fact, most of them experienced this kind of harassment from their superiors when they were in the army for a couple of years.
 besides, when they worked in companies after being discharged from the army, they worked through many nights while putting up with their superiors’ abusive language.
therefore, the blacksmiths of the world tree camp had a sort of ‘korea buff’, a kind of stress immune system.
clang! clang! clang!“done! i’ve succeeded in making one finally!”although their work was pretty hard, nobody gave up because they knew it’s like giving up the war with the chinese server if they gave up now.


 