\section{chapter 239}

                             




the man nodded silently.
 feeling the tremendous grip on his neck, the man could not dare to resist.
“is this the core research facility of the evolution society?”the man nodded again without any hesitation.
 he wanted to live.
“is dr.
 yu, the head of the evolution society, staying in this facility?”he hesitated for a moment but soon nodded.
“good, i think i’ve come to the right place.
 is he in the basement?”he nodded for the last time.
 sungwoo quickly broke the man’s neck, and he immediately summoned five troll skeletons.
“pile up the corpses near the wall.
”the troll skeletons moved in unison, moving the corpses of the monsters piled up in the warehouse.
“now let them know that i am here!”this place, the corpse warehouse, was like an ammunition warehouse for him.
 looking at the wall with about 20 corpses piled up, sungwoo shouted ‘explode!’.
bang! bang! bang!one side of the wall was blown away with a thundering noise, vibration, and heat.
 sunlight poured in as the black smoke went out of the wall.
at that moment, the red headlights turned on and the siren rang.
 people yelling at each other were heard outside the building.
 the security guards began to react quickly.
“it’s an explosion! check out what’s going on!”“this is tower a! tower a! support us!”it didn’t take long for their voices to turn into screams.
“they are intruders!”“shoot! shoot them! …argh!”the security guards near the collapsed wall began to be attacked by something.
“damn it! they’re so fast!”“ahhhhhhhh!”short screams continued then their voices faded out one by one, followed by a long silence.
they were annihilated.

“i’m here!” a little later, jisu walked through the collapsed wall.
“let’s go down.
”sungwoo was already done piling up the corpses on the floor.
 he didn’t want to use the elevators or stairs.
 he planned to use a faster and more efficient method.
“explode!”as the corpses turned into flames, the whole floor sank.
 when concrete bounced and pipes buckled, there opened a passage down to the next floor.
it was a very easy intrusion method no one could block.
“cough! cough! what the heck is this?”“the ceiling has collapsed!”somebody was talking under the floor.
 players wearing white gowns appeared as if they were in the labs.
“what is going on upstairs? are there any survivors?”instead of answering, sungwoo sent down ghouls.
kueeeeeeeh! kueeeeeeeeeeeh!“shit, what the heck is this?”“ahhhhhhhhh! help me!”shortly afterward, the troll skeletons threw a bunch of corpses down the pit.
sungwoo was thinking of keeping going down if he could penetrate like this.
since this research facility was large, it was more likely that they hid important stuff on the lower floors of the facility.
meanwhile, there was lots of noise outside the building.
“encircle the holes in the wall!”“riot team on standby!”a large number of reinforcements arrived at the facility to help the remaining evolution society members and surrounded it, but sungwoo beckoned one of the troll skeletons.
“give them some gifts, so they won’t feel bored while waiting.
”then, the troll skeleton moved and threw a few orc corpses out of the holes.
“explode!”bang! bang! bang!
at the same time, the corpse explosion occurred, the riot team approaching the wall was smashed on the spot.
“argh! it’s the breath of abyss!”“gas! gas! put on the masks, everyone!”when the corpses exploded, a faint amount of breath of abyss was released, but the evolution society dealt with such things, so they had some protective measures at hand.
“let’s go down.
 we don’t have to care about them.
”sungwoo and jisu stood in front of a pit going underground.
“explode!”the floor began to collapse as an explosion occurred downstairs.
 at the same time, sungwoo and jisu leaped down, so they passed through two holes at once, broke through two floors, and landed on the second basement level.
unlike the lab on the upper floor, it was a very dark space.
“this place is…”one line message appeared before sungwoo’s eyes.
-field boss monster ‘durahan’ has appeared.
“uh?”“boss monster?”they looked around at the unexpected message.
 they didn’t expect this kind of situation at all.
a dungeon couldn’t be in a place like this.
 how could a field boss monster be inside a building?“sungwoo, look over there!”jisu noticed something.
 in the middle of the huge room, three water tanks were glowing with purple light.
the first tank contained a body with a severed head.
 it was a huge figure in iron armor.
the second tank contained the severed head.
 a faint glow spread from the eyes of the iron helmet.
 it seemed to be the owner of the body in the first tank.
the third tank contained a black horse.
 at first glance, it wasn’t ordinary.
 it was twice as big as a typical horse, and a purple flame was rising from its hooves.
also known as dullahan, he was commonly known as a headless knight riding a ghost horse.
“i think he is in custody.
”“yeah, you’re right.
”white chains were wrapped around the surface of the tank.
 it seemed to be sacred magic that could restrict traits of the undead.
as a group studying death, they hunted and studied the monsters related to the undead.
 previously, they did the same thing when they caught the raid boss monster, ghoul king, in the secret facility in beomgye station and used him as research material.
at that moment, durahan stretched out his left hand and touched the tank’s glass.
“uh?”the white chain reacted, and durahan’s body stiffened as if he were electrically shocked.
 then, he was pushed to the center of the tank.
‘it seemed like he asked me for something just a moment ago.
’although it was very brief, sungwoo felt that way.
[exclusive quest]-title: chivalry of the dead-type: rescue-goal: remove the seal of ‘durahan’-reward: ‘durahan’ loyalty*detained in a remote place, the field boss monster ‘durahan’ has sensed your immense death power, and he is asking for your help.
 if you save durahan, he will voluntarily be your subordinate spirit and pledge eternal allegiance.
*’durahan’ will not follow you unless you release his seal.
“great.
 good decision!”sungwoo felt once again the evolution society was the richest source of nutrients for the necromancer.
the three huge tanks containing durahan, and the white chains surrounding the tanks were devices made of divine magic.
-divine power denies you access.
*damage is inflicted by direct contact with the object.
the necromancer couldn’t break it because it was not made to contain the undead.
“no, i can’t cut it off.
”just in case, jisu tried breaking it, but in vain.
 she couldn’t.
according to the quest, sungwoo had to break the seal himself in order to gain durahan’s loyalty, so he needed another way to break it.
“this chain leads to the other room.
”finally, he found the clue.
 the white chains surrounding the tanks were running out of the door along the wall.


“i think there is something out there.
”“let’s go.
”sungwoo and jisu opened the door casually for the first time after entering this building.
clink―“they came out!”“fire!”pick! pick! pick!as soon as the two opened the door, a barrage of arrows with light were fired at them.
it seemed that the arrows contained lethal, sacred power.
however, as long as she was there, there was no way they could inflict any damage.
when she stepped forward and drew her sword, all the arrows flying at her bounced away.
 she could block them easily now.
“this is nonsense!”while they were stunned, they put up their shields, a total of ten.
 all of them were protected by divine power.
since this was the room where they detained durahan, it seemed that most of the people involved in this facility had jobs using divine power, such as paladin and priest, and they numbered a whopping 32.
“the intruder is the necromancer, as expected.
 prepare the cleansing spell!”“spread shield of life!”“light arrows: fully loaded!”they began to prepare all sorts of divine magic to confront the necromancer.
 as he was of the same kind as durahan, they seemed to believe that their operation would work.
but they seemed to have overlooked jisu standing next to sungwoo.
tramp– tramp–jisu pulled out her sword and walked forward.
 at that moment, the blue flame on her shoulder was absorbed by the blade.
hwaaaaaaaaah!with the blade dyed with the blue light, a powerful wave began to spread.
shortly afterward, as she wielded her sword, dozens of blue sword energy attacks spewed out.
they had no choice but to look blankly at the intense energy from her sword.
kwagagagaga!

 