\section{chapter 474}

gangsok smiled softly and said, "you might feel sorry about my resurrection, but you aren't the only one who can be resurrected.
"




sungwoo was not embarrassed because he expected it to some extent.
 instead of replying, sungwoo looked at him slowly.
'does he have a resurrection charm?'gangsok has already been resurrected several times.
 each time that happened, his appearance as the demon king became even more bizarre.
 this time it was a little different.
 he was revived in the form of a player.
 in other words, he wasn't reborn with the power of the demon king.
 he took his first steps as a resurrected man.
 then he looked down at the fragments of the demon king's heart strewn around.
"yeah, admit it.
 i made a mistake," he said, looking at sungwoo.
 "a really big mistake.
 i intended to use you to get rid of miscellaneous obstacles, but i never expected i would end up creating the biggest obstacle.
 did i tell you about this before? anyway, what i mean is…"then he snapped his fingers.
thud!at the same time, the hole in the demon king's heart behind sungwoo's back collapsed, making their surroundings wholly dark.
- caution! this space is collapsing.
 (if you do not escape, you will 'disappear' together.
)"this means that if you die now, everything will be over.
"the demon king's body began to collapse, or more precisely, condense.
 his flesh was crushed and shrunk inward.
kugugugugugugu-at the same time, his flesh began to boil and swell as if it would explode at any moment.
this was not just a simple sign of an explosion.
 the power and mana that made up this place fluctuated like crazy, causing unexpected changes.
sungwoo stared at him.
"are you trying a self-destruction attack after all failure? man, that befits your last moment as a villain," sungwoo said.
 gangsok responded with a chuckle, shaking his head, "well, if i self-destruct, you and i will die together.
"then, he put his hand on the boiling wall of the demon king's flesh.

there was no reaction.
"i am not going to die from this.
 technically, it's part of me, isn't it? by the way, did you call me a villain?"this content is taken from lightnov‌elworld.
comhe laughed cynically, then said, "do i look like a villain? no, not at all.
 i am in the same position as you.
 you know that, right?""what do you mean?""i mean we're all just horse pieces on the chessboard.
 don't you still understand it? it's just that our roles are different.
 i'm playing the role of a progressive man while you are playing the role of a wise man.
 in other words, you're conservative and stubborn.
"sungwoo nodded again, then said, "really? then let me correct my description.
 a villain typically refers to the culprit of any incident.
 you look like a pawn in that respect, aren't you?"when sungwoo pointed it out sarcastically, he sat down on the fragments of his heart.
 then he nodded, stroking his chin.
kugugugugugugu-meanwhile, the collapse of the inside accelerated.
 the walls and ceiling were getting closer.
gangsok said, "pawn? well, i understand your feelings.
 you must be upset.
 you have survived in one way or another, then ruled over others until now, right? you might think you're a really smart guy, but you can't do anything as you wish, and i understand your feelings.
"sungwoo didn't answer.
he continued, "this game will be over soon.
 do you want to ask anything? as you know, i know about this game better than you, right? for example, i know how players on a server that has faced their ending are dealt with.
"he spoke sarcastically, but sungwoo nodded as if he was waiting for it.
 "well, i want to ask you something else.
"he seemed surprised at sungwoo's calm answer.
"really? tell me about it then.
"sungwoo looked at the message that appeared in front of him.
 then he paused for a moment before opening his mouth.
"do you know what primordial death is?"
he asked with a frown, "what is it?"he made an embarrassed expression as if he didn't know at all.
 as if he already noticed it, sungwoo said with a nod, "man, you didn't know anything about gigantes or cronus, so it's no wonder you don't know about it because there is no description of its skill.
"gangsok stood up from his seat as if he was wary of sungwoo because he felt something strange.
 "well, if that's the case, let me show it to you.
"at that moment, a purple light burst from sungwoo's grasp.
visit lightnovelworld.
com for a better experiencethe beam was woven into a net and began to wrap around a certain area.
- caution! 'primordial death' has begun in the area.
* time in the 'mortal web' is passing very quickly.
gangsok shouted in surprise, "what the heck is this?"'primordial death' was 'time'.
 the death of living things, or their fundamental death, depends on time.
 time in the purple net began to pass as fast as millions of times.
not only the air, but also the demon king's body, the weapon sungwoo was holding, and even the two people standing in the net were swept away by the flow of time, making them old quickly.
 then only the mind or the thoughts of the two men remained in the present time.
sungwoo looked down at his hand.
 the color of his skin changed quickly and wrinkled.
 he was growing old and dying.
sungwoo raised his head and looked at gangsok.
 "you're crazy…"wrinkles were made on his bewildered face.
sungwoo said, "you said you weren't going to self-destruct, so i did it.
 this is real suicide destruction.
 every time he said something, his voice also changed.
 his voice became heavy, then hoarse.
 his vision became blurry.
"gee, what a lunatic way to behave!"now, the demon king's body was completely condensed, so he could not escape.
 of course, he knew how to get out, but he had no time because even he or sungwoo could hardly stand firmly.
 "man, why did you do this? suicide? you weren't that kind of heroic, were you?"sungwoo nodded as if he admitted it.
 "i'm sorry, but i'm not going to die.
"sungwoo smiled while feeling the pain of his body shrinking quickly.
 "did you think you were the only one who had that item, the resurrection charm?"he then took something out of his arms.
 it was parchment.
[item information]visit lightnovelworld.
c­om for a better experience- name: resurrection charm (location designation)- grade: special- class: consumption- effect: when you die, you are revived in the designated location (suwon).
this was an item he purchased at a secret shop at gimpo international airport a long time ago.
"it's finally over," said sungwoo.
 that was his declaration.
".
.
.
"gangsok did not refute his declaration.
 he just made a devastated expression.


"man, i've been working hard, but i didn't know i would end up ruining my life like this…"he looked up at the ceiling as if looking back on his past hardships, then slowly looked down at sungwoo.
 in the meantime, his hair started turning grey.
 he looked at sungwoo with a disappointed expression.
"necromancer.
.
.
.
"".
.
.
""they are evil.
""who?"gangsok pointed at the ceiling with trembling hands.
"i mean those who make, control, and enjoy this game, namely, the game masters.
 they are watching us here, so they will be coming here to see you soon.
""are they coming to me? why?""because you are a winner.
"victory?"then when are they going to come?"he put down his hand feebly as if he was exhausted.
visit lightnovelworld.
c­om for the best novel reading experiencethen he coughed several times, then spat out a word with difficulty.
"right now…"maybe they reached the end of the game.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 