\section{chapter 470}

when the demon king's territory collapsed, the red clouds covering the sky began to slowly disappear.
 the sunlight poured down on the battlefield after a long time, revealing a huge magic circle drawn on it.
 




it was the place where the necromancer was standing.
"ugh? what is that?" reporter ahn asked.
he was very nervous, watching the sudden change of the atmosphere of the battlefield.
 having witnessed countless battles involving the necromancer until now, reporter ahn instinctively realized that the necromancer seized the opportunity to counterattack, and started moving to hunt them.
 "ah! that magic circle is the same one when he summoned gigantes! i wonder what will come out of it this time.
"shortly afterward, skeleton soldiers began to walk out of it.
 rattle! rattle!they were the "prison unit" members, who he could not take out because he already summoned gigantes.
 they rushed out and lined up in front of the necromancer.
 they were armed with all kinds of weapons in an orderly formation.
"he has been replenished with a huge number of the undead! that's right.
 the necromancer has moved again!"the skeleton army of 550, and their 550 shadow soldiers appeared all of a sudden.
thump- thump-then gigantes walked from the left and right, casting a dark shadow, under which bone dragon, a group of bone wyverns, and a hundred or so ghosts flew and filled the space.
"the necromancer's undead army is gathering again!"but this was only the beginning.
- a certain area (10km) has been declared as a 'death place'.
gray smoke rose from the ground, slowly rising like water mist.
a thick haze was added to the place where the dead were clustered, creating a grotesque scene.
"man, something is going to happen again!"
"after all, the necromancer had a plan he had devised in advance.
"- the area (10km) will temporarily fall into the 'abyss' and 'space overlap' state.
updated from lightnovelworld.
com* the 'people of the abyss' effect is applied.
 the attack power and defense of the undead increase.
 (+10%)* random grade 'ownerless zombies' are generated randomly (maximum 5) per a certain period (1 minute).
when the gray smoke rose to his waist height, something huge began to rise from the center.
kugugugugugugu-it was a hexagonal pole massive enough to shake the earth.
"is it a building?"it was a tower.
 "what the heck is that?"a black tower formed in the smoke grew vertically and established itself as a magnificent tower behind the undead army.
 - a 'tower of death' has been created in the area.
* the effect of 'death magic' in the area will be greatly enhanced.
* the tower's automatic defense function 'turret' has been activated.
* creates 5 'skeleton mage' every minute.
as time went by, the necromancer's army was supposed to grow, which was nothing new.
 but as time went on, however, the way they increased in number took a different turn.
 thanks to various other factors than the creation of zombies in the place of death, and the creation of skeleton mages in the tower of death, the undead army could continue to grow.
 watching the overwhelming force of the undead army, reporter ahn muttered before he knew it, "man, this is the complete system of the necromancer.
.
.
"
reporter ahn felt thrilled to see them.
 "gosh, i think i mentioned it before.
 the necromancer is getting incredibly strong every moment.
 it's the same again this time.
"but it was still too early for him to be surprised.
"ugh?"he was stunned to see what happened next.
- caution! the 'sealed' has been summoned to the area.
"what else is this?"follow new episodes on the lightnovelworld.
com platform.
suddenly, another magic circle began to be drawn.
 it was twice as large as the magic circle that summoned the prisoners unit a little while ago.
"hey, look at that!"reporter ahn let out a sigh unwittingly.
"oh my god!"his assistant next to him, all the staff in the studio, and even the viewers of the entire world were amazed at what was happening there.
to summon the sealed, sungwoo needed the highest 'comprehensive grade', which was the last item that could summon the army of the apocalypse.
' when sungwoo obtained the synergy of 'death adjuster' he could summon three at the same time regardless of their grades.
so sungwoo looked at the huge magic circle.
'what's coming out this time?'just like prisoners unit and gigantes, he had no way of knowing what it was until he summoned it first.
 finally, it appeared.
black smoke rose from the magic circle.
 it wasn't just smoke.
 the smoke got entangled and began to form a certain shape.
'that smoke is the very being in question.
'sungwoo could feel that a powerful being that got out of its body was taking on some form.
 what was created looked like a giant as huge as the demon king.
 chains made of white light were fastened around his neck and arms.
'the sealed…'purple eyes slowly lit up over his head and blazed like a fire.
"the one who summoned me.
.
.
"its voice was echoing everywhere, which meant the owner of this voice was not an ordinary person.
"tell me what you want.
"actually what sungwoo wanted was simple and clear, like a genie from a lamp.
 what he wanted was simple.
 this content is taken from lightnov‌elworld.
c‌omso he immediately opened his mouth.
"kill that guy!"sungwoo pointed to the demon king.
 the demon king was on alert, watching this situation carefully.
 even though he had a monster's body, he had the reasonable instinct of a human, so he was calm.
"is that just that? all right, let me grant your wish.
"then he raised his head.
 at the same time, the white chains that bound his neck and arms were broken.
tung- tung- tung- he was set free now.
 

- unseals 'cronos' for only 100 seconds.
 (it will be resealed when time is up.
)cronus, the head of the titans in greek mythology, was the father of zeus.
and he was also one of the beings sealed in the deepest part of hell, 'tartaros'.
in other words, since he was the ancestor of the olympian gods, nobody could equal his strength.
'for only 100 seconds?'the problem was that cronos had only 100 seconds to freely use his power.
 at that moment cronos cast a glance at the demon king.
"you've turned into a strange thing, blinded by your arrogant greed, even if you are a trifling thing.
 let me help you give up your greed.
"the demon king did not answer.
instead, the demon king raised his eight arms and prepared to face the unknown being before him.
 he, too, must have been a bit embarrassed by cronos' appearance.
even though he had played this game several times in the past, he was defeated greatly because he didn't know the existence of 'gigantes.
' in other words, this mysterious being was a formidable enemy for the demon king.
 in some respects, sungwoo could be an unfamiliar enemy to him.
"this is the third time for him, but he doesn't know all of it.
"even if one has been playing games for a long time, it doesn't mean that the game player is always good at it.
visit lightnovelworld.
c­om for a better experiencetwo giants faced each other.
 for the little beings standing between them, they felt as if they were standing in a canyon between two mountain ranges.
cronos started moving first.
 he raised his right hand.
 then it turned into black smoke before being changed into the shape of a giant scythe.
it was the scythe of cronos, which castrated uranus and ushered in the age of the titans.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 