\section{chapter 157}

                             




kangsok han, no.
 1 on the korean server rankings, was in his mid-to-late thirties.
 he looked like a prince.
it may be the effect of his ‘godly stature,’ but somehow it looked like he had a halo around his head.
 sungwoo felt mystified and in awe of this strange man.
‘what the heck is a demigod? is it a job? or something else?’after introducing the two, junghoon went outside because kangsok wanted to talk with sungwoo alone.
in such a spacious vip lounge only sungwoo, kangsok, and the fairy stayed.
“coke? or soda? it’s not my home, but now i’ve rented it, so let me treat you,” said kangsok.
he opened the bar’s refrigerator.
“give me water.
 that’s enough.
”“i want soda!” shouted the fairy while chewing roll cake.
kangsok quietly took out a bottle of water and soda, then poured the soda into an espresso glass.
 then, he put a sip stick, commonly called a coffee straw, and placed it next to the roll cake.
“thanks!”“eat a little.
 don’t overeat like you did last time.
 you can’t fly!”“it’s too late!”kangsok sat face to face with sungwoo.
“the best necromancer on the korean server…”kangsok opened the water bottle and handed it to sungwoo.
 when he rose, his shirt sleeves rose and the bracelet on his wrist was revealed.
eyeball-shaped red gems glistened on a black metal chain.
 a total of five rings were worn on his hands.
 each of them was high grade.
 sungwoo realized that the equipment items he was wearing were gorgeous even though he was not armed.
“thank you for seeing me like this when you’re busy.
 i was impressed by your fighting in youido.
 nabi liked that fight very much.
 oh, her name is nabi.
”
“wow, you are the man who fought there! your battle in youido was really great! can you give me a ride on bone drake later?”sungwoo looked at the fairy flapping her small wings, nabi, then asked kangsok, “is that an item?”“what the heck? item? are you talking about me?”kangsok nodded with a smile.
“oh, that’s right.
 she’s an item.
 have you played something like tamagotchis? if you give cake and soda to her, her happiness will increase.
 you feel happy and satisfied while seeing her.
 it’s great for preventing depression.
”“hey! how can you call me an item! you shouldn’t do that.
 without me, you would have to talk to yourself all day long, right?”“that’s why i said you are good for preventing depression.
”the fairy screamed like crazy, swinging the teaspoon, but the little voice from that small figure drew their attention.
sungwoo said, “i heard that something is coming that will determine the fate of this land.
”sungwoo got down to the point right away, and kangsok nodded.
it was a very profound subject, but he looked relaxed.
 he picked up a can of soda and turned his head to look at nabi.
“yeah, i got a prophetic stone and got to see it.
 i think it was bad ending-15.
 oh, you know what a prophetic stone is, right?”sungwoo nodded.
bad ending meant the end of this land.
 the ‘korean server bad ending-2’, which junghoon had shown sungwoo, showed the scenes of the world tree raised in youido flooding and encroaching on the entire korean peninsula.
“interestingly, in some prophetic stones, reading a prophecy is also the starting point of that prophecy.
 i found that prophetic stone; then, the prophecy began to come true.
”kangsok continued, putting down the soda can, “the dungeon called hell’s gate has opened.
 it was a level of 27, and its level of difficulty came with a party play recommendation.
 appropriate level 27? honestly, i didn’t have a problem, but party play was a problem.
”then, he took out a stone of a familiar shape.
 it was a ‘prophecy’.
“seeing is believing, right?”sungwoo nodded and accepted the prophetic stone.
 as expected, the video was played.

-you contacted ‘a prophetic stone (korean server bad ending-15)’.
the world was engulfed in darkness.
 somewhere there was an eerie whispering.
 the voices of old men, women, and children were mixed, so they could not be understood.
“the door… opens.
”as soon as some words were heard, the ruined city came into view.
sungwoo didn’t know where it was.
 in the meantime, there was a giant corpse that could not be recognized.
 it looked like a large monster, but someone appeared in front of it.
“kangsok! look over there! a prophetic stone!”“yes, i saw it too.
”it was kangsok han and the fairy.
 they found something inside the monster’s body.
the moment he reached out and picked up the prophetic stone, something happened.
-‘hell’s gate (1st floor)’ opened.
the prophetic stone was split into two and flew into the sky like a firecracker.
 then, they flew in opposite directions.
sungwoo’s eyes followed the fragments of the stone.
 it flew for a long time before falling at a great distance.
 soon, a huge portal opened.
‘it is hell’s gate.
’in two distant places, the ‘hell’s gate (1st floor)’ was opened.
 something appeared inside the gate.
rattle- rattle-it was a burning armor of enormous size.
 all sorts of bizarre patterns were engraved on the dark gray plate.
thump- thump-every time the monster stepped forward, flames soared above his footsteps, and everything around him was scorched as he moved.
 his presence was slowly killing this world.
well, that wasn’t the end.
gruuuuuuuuuuu-like maggots on a corpse, black dogs whisked and rose from the ashes.
from then on, the scenes of the future continued.
 two “hell moving armors” marched in different directions, burning everything on the ground.
the black dogs woke up in the ashes, grew in number, and spread across the country.
the whole area of seoul started to boil, and the water in sokchon lake was completely dry.
the huge flames that burnt down the metropolitan area climbed mt.
 taebaek and encroached on the east coast.
that way, the entire korean server turned red.
 the sky over the korean peninsula was filled with black smoke.
-this is the future you will face if you cannot stop the “hell moving armor” from hell.
*’hell moving armor’ absorbs the energy of the earth as time goes by and emits a stronger flame.
“did you see it all?”“yep.
”“i think they are anxious to destroy the land of korea in this game.
”kangsok went on to say that he confronted a lot of powerful monsters he had never experienced before, but he said he could hunt them without difficulty.
the problem was why they recommended ‘party play’.
 as they witnessed in the video, the “hell moving armors” that appeared in two places kept reviving unless they were eliminated simultaneously within a certain amount of time.
“but i’m a solo player.
”that’s why he came to see the necromancer because he felt that the only player who could deal with the difficulty of the appropriate level 27, was the necromancer, except for himself.
 “anyway, those two are constantly going north.
 and they are getting stronger and stronger.
 in a few weeks, they will reach this place, youngdungpo, and soon destroy the entire korean peninsula.
”just to think of that possibility made sungwoo shudder.
“and if it’s not me, there’s almost no player who can hunt them.
 well, i could just leave this land, but let me help you, so let’s get rid of them before they become stronger, then let’s divide the reward in half.
”

when kangsok said that, sungwoo raised his head and saw him face to face because he was very embarrassed by his words.
‘help me? do you think you are not responsible for this?’since monsters popped up when he got the prophetic stone, it was rather difficult for sungwoo to blame him, but sungwoo thought he should feel guilty, to say the least.
then, kangsok offered to help him as if he showed sungwoo mercy.
‘this guy has not come to see me to ask me a favor.
’obviously, he came here to make the demands for troops to help him hunt by taking the crisis of youngdungpo as his leverage.
 although he looked gentlemanly, there was some brazenness behind it.
but at this moment, it wasn’t his attitude that sungwoo had to pay attention to.
“what is the reward?”kangsok put his head forward with a smile.
“legendary grade items”in sungwoo’s opinion, what he could get was important.
 and if he could get legendary grade items with certainty, his offer was worth considering.
but sungwoo asked curiously, “isn’t the reward just one?”kangsok said, smiling mischievously, “that’s right.
 one of us will have it.
 i can’t help it, but how about playing a game with me?”he reached out his hand.
at that moment, sungwoo could know that this guy was enjoying this hellish world.
“are you not confident?”sungwoo held his hands.
so, the no.
1 and no.
 2 on the korean servers agreed to have a duel.


 