\section{chapter 403}

they were terracottas who managed to infiltrate the top of the rampart.
 but they looked somewhat different from other terracottas.
 they seemed stronger, to say the least.





reporter ahn and wong in the studio also watched the scenes carefully and tilted their heads.
"those terracottas are definitely different, right?""ah, they are the heroes of the later han kingdom.
""later han kingdom?'raising his eyeglasses, wong nodded.
 he seemed satisfied because they were related to the history of china.
"that's right.
 they're from the three kingdoms chronology that everyone in the world knows.
 by looking at the weapons they are holding, i can see they are two famous generals, li bu, and guan yu.
"as wong said, the two terracottas resembled li bu and guan yu, not to mention their weapons.
they must have been high-grade items 'blue dragon sword' and 'bangchon spear.
'junghoo blocked them in a narrow passage on the top of the rampart.
 ".
.
.
"guan yu and li bu jumped off the ground without saying a word.
 jungwoo's sword began to clash with their blue dragon sword and bangchon spear.
"uh?"at that crucial moment, the screen of the official channel changed.
"oh! it's the necromancer who is gaining the upper hand now!"something important was going on, which was really significant.
that area turned into something like the sea.
 a storm swept over the waves over which the entire dark clouds descended.

kwagwagaguagua!sungwoo's undead army was swept away by the storm.
 even bone dragon couldn't break through the storm.
since they were basically made up of bones, they could not move at all when the physical pressure of the wind and the water was applied to them.
"i warned you, man!" zi xuan shouted at the necromancer.
only the place where she was standing remained calm without being affected by the storm.
a huge tornado was spinning around the area at high speed, blocking everything like a single barrier.
"you can't get over this barrier, no matter what you do! just give up and watch your troops collapse!"fully exposed to the storm, however, sungwoo shouted back with a nod, "sure, i won't break through that barrier!""what did you say?""as the saying goes, those full of vanity are so occupied with what's in front of their eyes that they don't know how to raise their heads to look at the sky.
"she frowned at his words, showing for the first time how nervous she was at the moment.
actually, she felt something was coming down over her head, which was gigantic, indeed.
"no way…"she felt something strange.
 there were no signs of somebody approaching her, or any human shadow.
it was natural that she felt so because what was falling from the far-off sky over her head was a huge shadow itself.
 it was none other than the shadow of 'bone dragon'.
koo-ooh-ooh-
along with the explosion, the black front paws of bone dragon stamped on her.
 she could not withstand his dreadful attack.
 at the next moment minsok, who was riding on the head of bone dragon, jumped down, holding the ruler's sword upside down, then stabbed her right shoulder.
puck!"argh!"then orun jumped down and stabbed her left shoulder with balmung in his right hand.
puck!the ruler's sword and balmung were the so-called dragon slayer.
 writhing in great pain, she could not even scream.
sungwoo approached her and shouted, "you boasted of your ability to discern my ability, right?"he looked up at the shadow of the bone dragon, then added, "let me tell you this.
 what you see doesn't mean you can see everything.
"by using the 'shadow corps' skill, sungwoo could resurrect all the shadows of his subordinate spirits as 'shadow soldiers'.
 in other words, sungwoo had a huge bone shadow soldier called bone dragon under his control, but he was hiding the shadow soldier in the clouds.
"rattle! my lord!"victor appeared from the shadow of bone dragon, and mir was chewing his right hand like dog gum.
 actually, he was protecting these guys from the fight, so he could use them as hidden cards at the crucial moment.
 his decision was right.
"well, now is the time when i enjoy my hobby.
""what did you say?"she looked up at him with a pale expression.
 enjoying his hobby? she wondered how he could say that in a situation like this.
sungwoo said casually, "i've been collecting bones at some point.
"then he took out the sword made of lava, leviathan.
 magma dripped from the tip of the sword, emitting intense heat.
"no! go away! no way!" she shouted.
but it was time for him to collect the bone materials again.
***no matter how high a player's level is, he doesn't have a lot of 'health.
'.
of course, the higher his stamina level, the bigger the gap between him and the ordinary man will be, but it doesn't mean that he can have the resilient health as found in a large boss monster.
 in other words, the moment even such a player was dealt a single fatal blow, he could be killed.
 that's the case with zi xuan.
"i'm not going to die from your attack!" she shouted.
but sungwoo stabbed the sword into her shoulders to inflict as much fatal damage on her as possible.
if she had been an ordinary woman, she would have died of shock or excessive bleeding, but she could survive because she was a very high-level player.
and there was a reason why sungwoo controlled her so relentlessly.
"she's basically a dragon…"the only weapon with which he could kill her was the 'dragon slayer'.
 it was the same even if she had the deity status of a dragon.
he raised the sword leviathan from which magma was falling.
"uh? hey, wait a minute…"zi xuan's eyelids trembled.
 she was showing some deep emotions on her pale face.
she was obviously stricken with fear.
sungwoo felt sorry for her, which made him hesitant a bit.
 but he had no intention of showing mercy on such persons, as always.


'if i showed mercy on her, she would take away everybody's life.
'especially after he got out of the demon's cave with great difficulty, he became more convinced that he should not show any mercy on his opponent.
 he needed a way to prevent the destruction of this world, but he didn't know it yet.
 that's why he needed to be stronger.
"next time when you have a chance, make the right choice!"as soon as he shouted at her, he stabbed her with the sword.
- you earned 23,000 gold by killing a player.
as she was breathing her last breath, something was seeping into leviathan's blade.
- 'leviathan (deactivated)' has taken new effect by meeting a 'special condition (dragon slayer)' as a result, leviathan, the weapon that burnt the world in the northern european mythology, obtained even the effect of 'dragon slayer.
'- 'synergy effect' is given thanks to your team play.
as expected, the synergy effect was different this time.
[synergy list]4) dragon crackdown team (hidden)- category: weapon synergy- condition: 4 or more 'dragon slayer' weapons- effect: additional damage when attacking dragons (+300%), all types of 'breath immunity' increase (+300%), 'dragon fear' immunity increases (+300%), additional expand gold when hunting dragons (+200%), chance of obtaining a special item increases (+100%).


 