\section{chapter 51}

                            the huge concrete structure shook with sparks with smoke soaring and large debris scattered all over the place.





hiding behind the skeletons, sungwoo waited for the impact of the explosions to stop.
khoooo….
soon the explosions stopped, and the cloudy smoke gradually began to disappear.
sungwoo furtively poked his head out over the skeletons.
“…was it too harsh?”fortunately, the building itself did not collapse.
sungwoo blasted the middle of the mart with the new skill, body explosion.
 when the dust and smoke disappeared, the wooden cage was gone entirely.
 and there was a large pit in its place.
 he slowly approached the pit.
“what the heck is this?”surprisingly, the protective shield was still intact.
 the high-level kobold wizard was standing on the collapsed floor, staggering.
 raising its head, the kobold confirmed that the protective shield was not damaged.
“kuhhhh!”the kobold smiled with relief and then began casting spells again.
 the countdown, which paused for a moment, resumed.
-there exists a strong protective shield.
it cannot be destroyed by any ordinary attack.
 destroy the ‘cores’ scattered throughout the dungeon.
 (0/3)‘okay, so the makeshift solution won’t work here.
’there was only one way now.
 sungwoo had to find the core.
although the mart was dark, spacious, and complex, he could kill the kobold if he could find his party and attack together within an hour.
he turned away from the pit, but he noticed the body of the kobold wizard.
‘perhaps?’
he nullified the summoning of the orc skeletons, and resurrected the four killed kobold wizards.
-the dead have become your subordinate under your authority.
-the dead have become your subordinate under your authority.
-the dead have become your subordinate under your authority.
-the dead have become your subordinate under your authority.
-‘synergy effect’ is triggered by team play.
[synergy list]apprentice wizard (stage 1) -category: synergy-condition: 3 or more wizards-effect: increase spell speed (+20%)aside from this synergy, the message that he really wanted came next.
-you can check the ‘memory fragments’ of the dead.
“…oh, i see.
”after seeing the memory of the dead first when he saved the branch manager, sungwoo pondered over the conditions under which it would be triggered.
 at first, he thought it was given when he resurrected a human being.
come to think of it now, even a monster like a kobold with a certain level of intelligence had the memory of the dead.
 he couldn’t figure out how smart these guys were compared to the goblins or orcs.
 given that they were using crude human language, they must be better than goblins or orcs.
 anyway, it was clear that the memory fragments selectively showed the information sungwoo wanted.
‘ugh? i can’t see well.
’however, the kobold’s intellect seemed weak because the reproduced memory was blurry.
sungwoo saw that they talked to each other, chuckled, then moved elsewhere in excitement.
 with the utmost concentration, he tried to read their travel path and background in the blurred memory.
 as a result, he discovered that they arrived at a ‘butcher shop.
’they installed something there.

‘good.
 i’ve identified one place.
’sungwoo read the memory fragments of the other three kobolds one after another.
as if it didn’t install the core, one of them paced up and down the cage, but the other two spat out the right information.
‘it’s the home appliances shop and the rooftop.
 first of all, let me move to the butcher shop.
’the butcher shop was not far.
 it was right in the corner of the first basement.
accompanied by the skeletons, he headed there.
 in addition, he took out the meat refrigerator entirely and searched the inside of the butcher shop thoroughly.
crackle, crackle.
and right found something like a crystal ball, embedded in a tree trunk that came down the wall.
‘it’s a core.
’without thinking further, sungwoo smashed the core with a sword.
-you have destroyed a dungeon core.
 (1/3)stop the kobold in time! (00:51:30)“good.
 let me move to the other two places.
”sungwoo moved toward the second floor where the home appliance store was located.
however, there were no monsters blocking him except for the five kobolds that he ran into on the escalator heading to the first floor.
at first he wondered why it was so quiet, but he now saw kobold bodies scattered all over the ground floor.
 it seemed that sungwoo’s party that was separated from him a while ago was fighting against the kobolds well.
‘jisu is a good warrior anyway.
’and when he went up one level and arrived at the home appliances store on the second floor, he finally found his party, namely hanho, jisu, and kyongsu.
“they’re coming from the left too!”“kyungsu, wizard on your right!”they were fighting against a group of kobolds approaching them back to back.
they seemed to be in a dangerous situation, but they were knocking down the monsters one by one.
 so, sungwoo decided to end their fighting a little earlier.
rattle, rattle!the skeletons charged at the kobolds.
 in particular, when the four kobold wizard skeletons exploded and sparked at the same time, the dark interior became bright momentarily.
 and under the light, bulky skeletons attacked the kobolds too.
 the skeletons that appeared suddenly killed the remaining group of kobolds immediately, while sungwoo’s party stared at them with blank expressions in the thick of fighting.
“he, sungwoo!”“welcome back!”it was their dramatic reunion after about 40 minutes.
“i’m glad you are safe.
 what a relief!”“oh, we were worried about you, sungwoo, since you disappeared after stepping on the trap…”there was a sense of relief among them.
“by the way, have you seen that message about instant death?”“oh, yes…”it seemed that the moment sungwoo stepped on the first basement floor, the message was sent to everyone.
 was the mechanism of this dungeon designed to present such a puzzling mission the moment anyone entered the boss room on the first basement level?“let’s divide us into two teams.
 hanho and jisoo, go to the consumer electronics section.
 if you look at the wall there, you will find a marble-like core.
 destroy it.
 kyongsu, please follow me.
”“yes.
”sungwoo thought that since the monsters on the second floor were killed, he and kyongsu were enough.
 the reason why he took kyungsu with him was because he did not know the specific location of the core, and he could find it more quickly with kyongsu.
 jisu and hanho went across the shelves, and sungwoo and kyongsu went up to the last floor, namely the rooftop.
“oh, they have come!”“kill them!”

there were lots of kobolds standing by on the rooftop.
 however, they were nothing more than miscellaneous monsters that only got him numerous gold.
 moreover, the rooftop was more spacious than the underground warehouse, so the bulky skeletons could freely move around, getting rid of the kobolds at once.
“uh, sungwoo? is that a core?”kyongsu approached the trunk of the tree at the corner of the rooftop, where a large marble was embedded.
 it was the core.
 sungwoo walked toward it quickly and struck the marble at once.
-you have destroyed a dungeon core.
 (3/3)stop the kobold within the set time! (00:40:11)jisu and han also succeed in finding the core.
 so, they destroyed all three cores.
-you have destroyed all dungeon cores.
 the protective shield has been removed.
“good.
 wait for me!”now, it was time for sungwoo to deal a painful blow to the cunning kobold wizard.
 the wizard would never have imagined that sungwoo and his party would destroy the cores in such a short time.
after meeting on the second floor again, sungwoo and his friends went straight down to the first basement level.
 then they approached the hollow pit in the middle of the underground shop.
“…kuuuhe?”after confirming that they were looking down, the high-level kobold wizard was full of embarrassment.
“why? can’t concentrate anymore? you have to be able to focus for 45 minutes, right?”without waiting any longer, sungwoo fired four green flames by controlling the kobold wizard skeletons.
pop! pop!however, the wizard raised its hand, forming a small shield to stop the flames.
but the shock forced the kobold to roll back and forth.
-lesser instant death spell has been blocked.


 