\section{chapter 217}






 kyongsu carefully checked the conditions of the village players and distributed the items to the right places.
he said, “we have supplied them with new equipment items.
 i’m sure they have become much stronger than before.
”they were leveling up in real-time, but the speed of their level-up was gradually slowing.
 it meant the time came for them to change the hunting ground.
“then, we are going to start attacking the second floor from now on.
 after each group makes a couple of rounds once more, all of our troops will go up to the boss room.
”when sungwoo said that, the players’ faces turned pale then hardened.
“let’s start over.
”their hellish training continued.
at that time, the “taebaek investigation team” of the wide area surveillance team of the liberation guild was searching all over mt.
 taebaek, focusing their search around mt.
 seorak.
 as they promised the necromancer, they were searching for the missing person named jisu.
at first, they planned to fly a magic drone to scan the mountains for her at a glance.
 no matter how big and wide the mountains were, they could check it out quickly by looking down from the sky,but things didn’t work out as they wished.
-‘lower magic’ is blocked by an ‘unknown power’.
they could not know the exact cause, but it was certain that something strange was happening in the deep mountains where humans had never trodden.
“we can’t help it.
 we have to bring more guys to search for her deep into the mountains.
”in the end, they had no choice but to do some legwork.
but the mountains were too wide and steep.
 besides, there were dreadful monsters under the control of the “king of the great mountain” in the deep mountains.
“ugh, shit…i now know why the struggle guild gave up and decided to join hands with other camps.
 yeah, they were not crazy guys.
 they are very rational.
”“you’re right.
 all the monsters here are very weird.
 it looks like each of them is a boss monster.
”
the struggle guild had been a powerful force, but they could not beat the king of the great mountain.
 in the end, they had to leave mt.
 taebek.
even though the wide area surveillance team’s intelligence agents, who specialized in concealment and stealth, focused only on the search for jisu while avoiding the monsters, they still faced several dangerous moments.
 for example, all five members of the “2nd search team ” were annihilated during the operation, which showed how powerful the monsters were.
these monsters were fundamentally different from the monsters of before who tried to beat back their opponents by outnumbering them.
 most of the monsters here had their skills, and some of them cast powerful magic.
also, they moved intelligently when they aimed for their prey, so once they started to chase, it was best to widen the distance between them and hide in a safe area.
if that happened, it meant their search efforts failed.
“damn it! surviving alone in a place like this? is that possible? don’t you think this is futile?”it was natural they felt skeptical about their search efforts in such a situation.
“haven’t you seen that woman fighting? she is not a human.
 who knows? she might be already controlling this area.
”“but this place is too dangerous.
 it’s not a matter of a temporary win, but she has to stay and hold out here in this place teeming with the monsters.
 she is in a different situation where we only search during the day and escape into the safe zone.
”“oh, you’re right.
”when they thought as far as that, they began to feel anxious.
“what would the necromancer say if you found her body and give it to him?”“…”“it’s scary even to hear that.
”they searched for her for long hours, but they could not find any traces.
so, the search team began to think about giving up the search effort and withdrawing.
and when they made the last search effort, one of its members shouted.

“i’ve found evidence of her! it’s her footsteps!”jisoo proved she survived on this hellish mountain.
***at the search camp installed at the osaek bus terminal in the valley of mt.
 taebek,the leader of the 1st search team reported, “we found her traces at an elevation of 980 meters on the northwest ridge.
”the head of the search team, who was only sighing while looking at the map all day long, opened his eyes wide and corrected his posture.
when he nodded, the team leader continued, “we found a large number of monster corpses, but they seemed to have clashed with an extraordinarily strong man.
 i think it’s the woman we have been searching for.
 and we have a witness who can decisively testify about her whereabouts.
”“witness?”the only thing they could get from the monsters’ corpses was sword wounds, but it was a different story if they found a witness.
 the witness might have had a conversation with jisu.
“the witnesses are an old man and his granddaughters living in the mountains.
 it looks like they were with the missing person briefly.
”“that means they are not together now, right?”“nope.
”“damn it! so? did he hear anything? huh?”when the search leader demanded, the team leader nodded.
“according to the old man, the woman must have received some kind of quest.
 and the quest seems to be related to the “king of the great mountain”, so i think she might have followed the path of the quest.
”“no way! it’s hard to believe she was chasing the monster king…”wasn’t it the quest that even the struggle guild, composed of hundreds of men, gave up? no matter how skillful she was in wielding the sword, she couldn’t deal with the monster king.
“oh, there is something i can’t understand.
”“what the heck is that?”“according to the old man’s granddaughter, the woman murmured something like, ‘the king of the great mountain had the last item of the king of shadow’, but i don’t know what she was talking about.
”the search leader frowned and said.
 “what the heck is the king of shadow? are there two kings here?”“well, i have no idea.
 there is no mention of that in our intelligence report.
 i’ve never heard it.
”the king of shadow was new to them.
“if a woman is chasing the king of the great mountain, it is unreasonable for us to search for her further.
 we are not here for a suicide mission, right?”but the search camp leader didn’t believe she went after the monster king alone.
if so, where did she go?***it is very important to prepare for a war and there are many ways of preparing for it.
generally speaking, they can beef up power through training and stockpiling like the world tree camp.
 on the other hand, they can inflict damage on the hostile forces through operation and intelligence.
 by damaging the opponent’s firepower, they can widen the power gap.
this method is quite difficult, but it is excellent in terms of cost-saving.
 that’s why this method requires those ‘agents’ who are thoroughly trained.
“can i ask you for directions?”sangnok-gu in ansan city was once a busy area, but after the world turned into a game, it was dreadful to meet somebody in this barren city, like this man in black who asked for directions.
“…”seungtae, the man who was asked for directions, was embarrassed, but he did not let down his guard.
 of course, he was not that nervous at the moment because he encountered only two people on the street.
“hey seungtae, what’s going on?”

seungtae looked back as if he was dumbfounded.
 there were three trucks pulled over on the street, and 26 were on the bus.
 they were staring at the two men sternly who blocked their way.
since they fiew a magic drone just in preparation for an unknown ambush, they judged they could win easily if an armed conflict occurred.
“well, i don’t know.
 they seem to be lost,” seungtae said.
“because we are busy, tell them to call 112.
 the police will show them the directions.
”they burst into laughter at that.
“wait a minute.
”emboldened by his colleagues’ backing, seungtae openly expressed displeasure.
“directions? which direction are you talking about?”“can i go to suwon if i walk in this direction?”“oh, my god…”seungtae slowly lifted his finger and pointed to the green sign on the roadside.
the sign showed the distances to nearby metropolitan cities such as seoul and suwon.
in other words, the man didn’t have to ask seungtae about the directions.
“…”the man’s eyes slowly followed seungtae’s fingers, and soon stopped at the sign.
however, there was no change in his facial expression.
 even his pupils didn’t move as if he didn’t know how to read.
he opened his mouth again.
“so, you mean suwon is in this direction?”

 