\section{chapter 175}

                             




“i’m going to promise you three things from now on.
 this promise applies to all players on the korean server,” sungwoo slowly said.
 “i’m going to go and search for all the guys who publicly announced that they would kill me, and kill all of them one by one.
”as soon as he said that, sungwoo pulled out something.
 it was a hand cannon.
bang!terror kim’s head was blown away with only one explosion.
 that terrifying scene was captured fully on the camera screen.
 sungwoo slowly loaded the hand cannon.
“and i’m going to create a new organization and kill everyone under the control of angels and demons.
”bang!this time, the man standing next to terror kim fell.
 soon, the players from the village began to flock behind sungwoo’s back.
 hundreds of them fully armed were captured in one camera angle.
“but if you choose a third camp with me, it will be a different story.
”the necromancer, who was the subject of criticism and the images of a prey for a very short period of time, revealed his true colors, and imprinted some strong images on the whole korean server.
 in other words, he sent a strong signal that their choice of the absolute race might be wrong.
as a matter of fact, the necromancer was known to have hurried out of youngdungpo station immediately after the absolute race set a price on his head.
 in other words, he chickened out and fled the area.
having heard that news, lots of people thought that the necromancer would collapse soon.
 no matter how strong the necromancer was, wasn’t his rival the absolute race?furthermore, the angel camp even gave lots of buffs to those who helped them.
 that’s why they were reckless enough to announce on the community bulletin that they would kill the necromancer.

however, the necromancer was alive, contrary to their expectations.
“argh! please help me!”“oh please help me! i just did what i was told to do.
”puck!that night, sungwoo sent out a broadcast featuring the slaughtering of terror kim terror and his followers.
 he massacred a whopping 25 men.
the viewers of that broadcast exceeded 150,000, and there was a big uproar on the community.
and those who mocked the necromancer a little while ago also reacted immediately.
-[live] broadcast to apologize for provoking the necromancer’s anger / we’re sorry.
 we made a mistake.
 (3,226 watching now)“sorry! sorry! necromancer! i think i was crazy all of a sudden at that moment…”the reason they reacted like that was because the necromancer, who was up and running, openly reiterated that he would get rid of all the players who were hostile to him.
and the necromancer’s announcement could never be taken lightly.
“it was really me who had them do an apology broadcast.
 i’m not trying to water down your serious message.
 i really repent what i did to you! if you are necromancer’s colleagues and watching this broadcast, please convey my sincere message to him!”there were a series of broadcasts in which the terrified players offered public apologies to the necromancer.

“ah, i am willing to choose the third camp in the future!”it looked like a ridiculous situation, but in hindsight, it showed how overwhelming the necromancer’s power was.
didn’t he wipe out all the enemies without any single failure until now? moreover, the fact that most of those who were hostile to him were killed was enough to scare the life out of them.
[432] is it only me who is deploring this ridiculous situation?-author: miss choi │ visit: 54,433*as soon as a bounty on the necromancer’s head was announced, you guys chose no.
 1 option and made all kinds of bluffing with threats to kill the necromancer, then you guys are begging for your lives and offering apologies like this? is it only me who is jeering at you?man, i see you guys have never changed when the world is such a mess like this.
 i think this world can be cleaner and safer thanks to the necromancer.
 by the way, it’s quite true as i have heard about him.
 he never compromised with the terrorists and killed them all.
 i like that![comments: 12]- sangyon lee: i am confused because i had to choose one of the three camps suddenly, but i’m more confused now because of the necromancer.
 i feel it in my bones that if he forms a third camp, he can destroy the angel and the demon camps altogether.
˪ deliveryman choi: 2222 i really didn’t want to see these conceited guys, so i feel really good that they’re gone! wow, it looks like the table is turned when the necromancer appears!˪ survivor 356: i also support the necromancers, but what if he fights against the absolute race?- spearman in changdong: i was so fascinated by the brilliant performance of the necromancer on the broadcast.
 you don’t appear on the monitor screen often.
 anyway, it was so moving to watch you live on the broadcast.
 i fully support you!- yasuo 1: tut, tut.
 we have to kill all the social media trolls!all the voices and comments criticising the necromancer on the community and the broadcasts disappeared quickly.
 almost all those who simply posted malicious comments disappeared, and even those who were seriously aiming for a bounty on his head didn’t openly reveal their intentions.
meanwhile, it was junghoon who found himself in the most difficult position.
 since he chose the angel camp, he had no other choice but to break up with sungwoo.
 but that’s not only what he wanted, but also something he didn’t expect at all.
he was sitting in the conference room with his deputy minhum.
“i don’t know if it is right to declare the creation of the new alliance without the necromancer.
”“i’m worried about it, too.
 we can’t deny the fact that the reason why the survivors relied on our youngdungpo group in anticipation of the establishment of the alliance was because we had the full backing of the necromancer.
”in fact, it was because of sungwoo’s suggestion that they started to form a huge organization called the “metropolitan players association”.
 and they could create it because sungwoo had been blocking external threats until now.
moreover, many of the players who came to youngdungpo after hearing the rumors about the establishment of the new alliance expected that they would be protected by the necromancer.
“commander, should we revise the plan?”but junghoon shook his head and said, “we have to go through some trials, but we can’t give up now.
 please hurry up to discover a new statue by expanding the surveillance team.
 if we can’t find another statue, we may be pushed aside by other groups.
”“if that’s the case, are you going to eventually be against the necromancer? as you know, he already openly threatened to kill both the angel camp and the devil camp,” minhum asked anxiously.
since the crusaders watched the necromancer fighting the formidable enemies up close, they knew better than anyone else that they could not beat the necromancer.
“no, that’s not what i mean.
”

actually junghoon was aware the crusaders were not powerful enough to confront the necromancr.
he said, “sungwoo is not a humane person, but he is a reasonable man.
 in other words, he understands my message, so if he can’t be our friend, we should not make him our enemy.
”“do you mean we should conduct diplomacy with him?”junghoon nodded.
 since sungwoo had an independent force, junghoon thought it was necessary for the two sides to conduct friendly diplomacy toward each other.
“minhum, the family members of the skeleton who is accompanying sungwoo are here.
”in fact, sungwoo once asked him to take good care of minsok’s family.
“oh, you are right!”“take care of them well and keep in touch with them.
 if they ask you to send them to suwon, you can decline their request by telling them it’s dangerous in suwon now.
”of course, junghoon wanted to use the minsok’s family as something like a bargaining chip to negotiate with sungwoo.
 in some respects, jungwoo could create a situation favorable to him.
“by the way, the angel camp will continue to issue the quest to catch the necromancer.
 if you don’t carry it out, won’t they give you a bigger penalty?”“well, let me wait and see if they can really do that.
”junghoon chose no.
 3, ‘bystander,’ in the ‘server quest.
’ as a result, he got a penalty, which decreased his stats temporarily.
although he has not suffered any big damage until now, he and the crusaders can lose lots of power if he keeps getting penalties.
‘i have to be prudent.
 i should not lose either the angel camp or the necromancer for now.
’

 