\section{chapter 343}

chapter 343: juju island and attack on demon’s cave (7)soon, two airships descended close to the summit of oreum.
 then, using the pulley devices they prepared in advance, they began to load troops and supplies on the airships.





at that moment, screams echoed from the deck of the messenger.
everyone raised their heads and looked at the place where the scream was coming from.
“argh! necromancer! please do something about this little monster!”it was li wei’s voice.
 she was holding mir, with a chicken skeleton hanging above his head.
besides, the skeleton was also on fire.
 fortunately, li wei was a ‘water spirit magician’, so she summoned a small water spirit and sprayed it on her head to stop the fire from catching on her hair.
“come up quickly!”when sungwoo boarded the airship, mir teleported from li wei’s arms into sungwoo’s shadow.
grrrrrrr- grrrrrr-sungwoo went out after putting mir to sleep inside the airship, but mir woke up and made a big fuss while sungwoo was away.
mir hugged sungwoo suddenly then he put his nose on sungwoo’s chest and started sniffing.
he pushed his nose into sungwoo’s inner pocket, and there was something unusual about his sniffing.
“what the heck are you doing?”gulp!“you swallowed it?”gulp? sungwoo hurriedly opened mir’s snout, but he already swallowed it.
 what he swallowed was the ‘fox marble’.
“why did you swallow it?” sungwoo asked, embarrassed.
- ‘black dragon (hatchling)’ has absorbed a magical object.
* time remaining until complete absorption: 03:59:59“what the heck is this?”
the dragon was really an incomprehensible creature.
in the meantime, one airship that veered from the battle at oreum flew to the southern slope of mt.
 halla to find the traces of the ‘black lion’.
by the time they crossed mt.
 halla, they witnessed an unidentified light soaring from lake baengnokdam from a very close distance, but they marched forward without caring about it.
right now, it was more important for them to find the navigator for ‘attacking the devil’s cave’ than the battle taking place right before my eyes.
“hey, please land near that building!”at the request of the white wolf, the airship lowered its altitude to prepare for landing.
 when they got close to the building, an old hut in the mountains was looming vaguely in their eyes.
wooong-the airship could not land on the ground because of the dense trees.
 when the airship lowered its altitude enough to be close to the ground, the white wolf and jisu boldly jumped off.
jisu drew the sword as soon as she landed on the ground.
“there is something over there…”she shouted because she felt an eerie feeling that somebody was in the forest.
 the white wolf also nodded as if he agreed with her judgment.
“as expected, this place is still full of monsters.
”when she slowly turned her head, some red eyes appeared in the dark forest.
but those eyes were fixed on a very high place.
 they were giants of overwhelming stature.
“damn it! are they ogres? almost seven…don’t you think we should ask the airship for cover fire?”the white wolf growled.
 no matter how high his level, an ogre was a top predator.
 in other words, they were very tough to deal with.
but jisu only shook her head slightly.
and the next moment, she took action right away.
quaddddddddddd-
as soon as she jumped off the ground, the tree tilted and those red eyes, or more precisely, the heads with red eyes fell, beheaded in an instant.
kugugugugugugugu-the upper parts of the trees were neatly cut and the sunlight beamed through the white wolf’s eyes.
 the white wolf had to think hard for a long time about what happened a moment ago.
“…”“let’s go,” jisu said, who already jumped back down on the ground after beheading them.
the white wolf turned around, hiding his surprise.
 he was shocked to realize belatedly that he once had confronted her.
they entered the old hut.
the wind blew in from the open window on the other side, howling softly.
as if no one lived there, the windows were broken and the ceiling was down.
“no one is here.
”even if she didn’t check it, she could tell with her sharp senses.
“but if there was somebody here before, at least i know something.
”the white wolf checked out various stuff, then laid his hand on the dusty oil stove.
when he closed his eyes, a blue light began to flash from his hands.
he began to read memories from the things left behind in the hut.
after spending about a minute, he slowly opened his eyes.
“that man is with the people here right now.
”he seemed to have traced the location of the man.
“pardon? are they monster worshipers if you are talking about the people?”“no, there are normal survivors other than monster worshippers.
”when she heard that, she turned, nodding at him.
 if he confirmed the position, she had no time to delay further.
 while getting out of the hut, she suddenly looked back at the white wolf.
“then maybe he is…” she barely opened her mouth as if she was hesitant.
“can you find other people later? i mean if you can do it…”the white wolf nodded silently.
 he could understand the situation she was in now.
“thank you.
 let’s get out of here quickly.
”having obtained the clue, they hurriedly boarded the airship.
***“no.
 3 airship is coming!”as soon as he heard it, sungwoo went out to the deck.
 no.
 3 airship that jisu and the white wolf boarded finally came back.
a short passage was connected between the two airships, through which the two passed and approached sungwoo.
“did you find that guy?”when sungwoo cut to the chase, the white wolf nodded right away.
“yes, he…”but he couldn’t finish his words.
“what’s wrong?”he moved his gaze over sungwoo’s shoulders, then frowned as if he was surprised.
then, he raised his index finger and pointed at it.
“he’s with that woman.
 but how come she was there?”

the man he pointed to was jimin, one of the survivors on jeju island.
 she was also embarrassed to see him here.
“so, that man is with a group of survivors on this island, but i’ve seen him in his memory.
 i think we can find his whereabouts if we ask her.
”“pardon? who are you looking for? uh!”but this time jimin looked somewhere with a surprised expression.
“oh, are you jisu?”after arriving on jeju island, it was already the second time someone recognized jisu.
jisoo also had a confused expression.
“sister!”“what a relief! you are alive!”jisu nodded.
“hey, sister? wait a minute…”“oh my god!”at that point, sungwoo and hanho realized that the two women resembled each other a lot.
hanho said, “hahaha.
 i felt she looked like jisu’s elder sister…”even if he didn’t ask them specifically, sungwoo could realize that the two of them were biological sisters.
 jisu finally met her sister who was living on jeju island.
“i thought you were dead, but i’m glad you’re alive like this!”“me, too!”but there was no such thing as an emotional family reunion.
 given that jisu didn’t miss her elder sister, and the way taesu spoke to her, sungwoo knew the two sisters had an unfortunate and complicated family history.


 