\section{chapter 151}

                             




-occupation by the allies is underway.
 (4 seconds left.
)“oh, no!”“it’s taken over!”“we are done!”-the allied forces have occupied point a.
* buffs are applied.
-allies have captured all points.
* additional buffs are applied.
[buff list of the mini game]indeed, it was an enormous buff.
 it was almost like 10 levels increased at a time.
‘mini-game? it’s far from a mini-game!’even if they competed with rival groups over the hegemony of mainland china, sungwoo was puzzled about how these guys driven out of the mainland could occupy taiwan, and now he seemed to understand.
 obviously, they must have gambled on this kind of huge buff for their successful operation.
-the mini-game ends in eight hours.
this time their gamble failed.
 to make them pay for the price, sungwoo and his forces were about to hunt the pirates for the next eight hours.
and all of those scenes were being broadcast live by the camera operator, who had been taken hostage.
meanwhile, a special squadron of pirates was dispatched to occupy point c, the relics of the dolmen.
 however, it took a considerable time for them to travel from the southern end of the island to the northern end, and shocking news came before they reached the destination.
“it doesn’t make any sense…”“how could our forces be defeated in an instant?”they came to know that not only huei, the best swordsman on china sever 2 but also gen.
 jigong was killed, and point a was conquered.
that shocking news drained them of hope and energy, but they decided to carry out their original mission, knowing that they could not escape from the island anyway.
“everyone, wake up! we must succeed! if we give up, it’s over!”“sure.
 at least in this place, there’s no such thing as the necromancer or that female swordsman.
 let’s go!”the special squadron attacking point c was not small.
 comprising more than 160, their average level was also over 9.
 they were an elite unit.
“we have no time! even at the risk of our lives, we have to mount a frontal attack!”
under the command of their leader with level 14, the special squadron pledged to fight bravely in the upcoming final battle.
 then, they followed the lights of the flag to enter the ruins.
soon, far away, the camp of the players of kyodong island, who were positioned around the flag, caught their eyes.
 they were apparently preparing for the pirates’ ambush.
 they seemed to number about 50.
“they’re less than i thought.
”“we can beat them even though they are backed up by enormous buffs.
”the special squadron lined up in front of their leader.
 he drew his sword and lifted it toward the sky.
“get ready for the battle! charge at them now!”but at that moment something happened.
“surprise attack!”something jumped from the ground behind the leader’s back.
 he was a man with lots of grass attached to his body and holding a dagger in both hands.
puck!“kuuuuuuuuh!”because it was an unexpected ambush, the leader of the special squadron could not respond.
 a sharp dagger was stuck in the back of his neck.
it was hanho who attacked him.
 he was hiding flat on the ground, with grass covering his cloak.
“why did you come here so late? i almost went crazy because of bugs crawling on my body while i was lying here!”complaining like that, hanho drew the sword from the corpse of the killed leader.
suddenly, a golden shield was wrapped around hanho.
-you have gained a ‘holy shield’ for 15 seconds with the ‘slayer of faith’ skill.
 (400/400)“captain!”“kill him!”“it’s just one guy!”they began to fiercely attack hanho after learning that their leader was killed.
however, the golden shield around hanho blocked all their attacks.
 since his skill level increased by one step, his ‘shield duration’ and ‘shield capacity’ increased considerably.
so, even though the pirates attacked him, hanho blocked their attacks effectively for several seconds.
hanho threw a dagger.
 the dagger, which flew almost in a straight line, struck over the shoulders of the tanks and into the necks of the wizard standing behind them.
-you have gained 9,000 gold by killing a player.

using the new scapegoat as fertilizer, his ‘shield of faith’ has been renewed.
 this was the advantage of this scary skill.
 if it had plenty of damage power, hanho could use it as an infinite shield even in the middle of the enemy camp.
tung! tung! tung!“damn it! i can’t break his shield!”“what kind of skill is it?”hanho moved forward boldly and threw another dagger.
“who the heck are you?”as soon as one of the pirates shouted, hanho’s dagger was stuck in his neck.
“kuuuuuuuuuh!”-you have gained 8,000 gold by killing a player.
“argh!”-you have gained 6,000 gold by killing a player.
“hey, remember me, everybody! i am from the korean server! i’m a friend of the necromancer! i’m the strongest sacred thief! my name is hanho lee!”the triumphant hanho roared sharply as if he became a street cat.
then, holding a dagger with both hands, he ran toward the enemy camp.
 he forced his way through the tanks, somehow stabbing the dagger into their necks and ribs.
puck! puck! puck!“ahhhhhhhhhh!”“push him!”since he was not wounded thanks to the shield, and his stats were greatly strengthened by the occupation buff, sungwoo could ambush them without any fear.
puck! puck!“hey, use magic!”“since he is too close to us, it will harm our allies if we use magic!”“then pull him away from us!”“he wouldn’t move at all like a tick!”while the disorganized pirates were struggling hard, there was a roaring shout from the left and right.
“charge at them!”“strike them!”the players of kyodong island, who had been nearly ambushed, started the raid finally.
“shoot everyone!”“kill all the pirates!”“kill every single bastard!”at the order of muyon, dozens of arrows and magic spells began to rain over the heads of the special squadron.
“ahhhhhhh! watch out on your left!”“too late!”while hanho was raising aggro, they mounted a huge attack on the defenseless special squadron and suffered fatal damage in an instant.
“they are collapsing!”“kill them all!”the players of kyodong island launched an attack for the final push.
 they closed in on them from all sides.
 there was deep anger on their faces when they charged.
 with anger fully charged on their weapons, they attacked the pirates mercilessly.
“kill them! kill them!”“you bastards! how dare you intrude here again?”“do you think we’re pushovers?”among kyodong players was a little kid, youngin, who was the brother of heyon’s relative.
the little boy threw a heavy shield and grabbed “gladius,” his sword, then ran toward a pirate bigger than him.
 he swung the sword violently, shouting at the top of his voice.
“argh! ahhhhhhhhhhh!”clang! clang! clang!the pirate was embarrassed by the kid’s attack and stumbled back.
“ugh! how dare a little kid attack me?”“let me kill you! come on!”although youngin was only level 3, he showed a tremendous force with the help of huge stats buffs.
 the pirate was wielding his sword unstably, then eventually allowed youngin’s attack.
puck!

gladius was stuck into his neck.
“ahhhhhhhhh….
” the pirate collapsed instantly.
-you have gained 8,000 gold by killing a player.
-you have leveled up.
 (lv.
 4)“wow! i took revenge on him for my father! revenge!”the power of the buff was so great as to allow even this kid with level 3 to charge at the enemy without any fear.
“we’ve won!”“they’re running away! don’t lose them!!”the special squadron was destroyed in an instant, and only a few remnants broke through the siege and started to flee, but they didn’t go far.
 the players on kyodong island were given movement speed buffs.
finally, their battle was over.
“dad, i took revenge for you…”youngin muttered while looking at his father’s relic, gladius.
someone came to him and said, “hey, you’re fantastic, little boy!”youngin was startled to hear that.
 it seemed like he was caught fighting secretly by somebody else because adults didn’t like young children to get involved in this kind of terrible fighting.
youngin turned to him with an anxious expression.
however, the other person’s reaction was favorable to his surprise.
“wow, you’re pretty courageous! you’re awesome!”it was hanho, the man covered with grass.
“oh, brother! strongest thief!”“did you hear what i said? yes, that’s me.
”hanho patted him on the shoulder and moved on.
but youngin shouted at him, “hey, brother! can i…”“huh?”“can i be as strong as you, brother?”“well… like me, not the necromancer?”

 