\section{chapter 289}






 watching the angel completely frozen in a blizzard, the players recalled only one name.
 the necromancer, the adversary of the absolute race, once again tarnished the lofty image of the angel.
“is it all over now?”the angel was motionless.
 the secret operation that involved the sprinkling of hundreds of tons of water over the angel to freeze her by activating the “frozen seed” was successful.
but they could not relax yet.
 many of them were watching the angel with bated breath and their eyes trembled.
“it’s not over yet.
 when the ice melts, the angel will move again.
 and maybe she will break through before that.
”they could not shake off their anxiety.
 it seemed that the overwhelming existence of the angel was frozen, but stood firmly inside the ice, and someday, she would move again and destroy the liberation guild.
they talked about the worst that could happen as if they were alarmists.
 they were not worrying unnecessarily.
 it was the expression of a natural sentiment of the weak who had to watch out for the worst crisis.
however, sungwoo was different.
“i can win.
”at the moment, when he froze that gigantic angel, sungwoo was already convinced of victory.
in fact, his strategy was close to gambling.
 and as soon as this gamble worked, he was convinced that everything would work out as expected.
to put it simply, he almost won.
‘if we mount a general offensive right now, we can kill the angel at once.
’-‘evil spirit bombing’ dwells in your weapon.
 (max)at the same time, an undead army appeared behind sungwoo and lined up.
sungwoo finished preparations for the battle and looked at the rooftop of youngdungpo station.
junghoo and minhum standing on the rooftop were looking down at sungwoo.
 since they entrusted him with everything, they were now waiting for his next order.

“have the flying weapons ready!”when he shouted, minhum came to his senses and immediately picked up the radio.
 soon, the flying weapons that had been prepared in advance began to move.
rattle! rattle!not only those owned by the liberation guild, but also fire arrow rockets that sungwoo stored in the inventory aimed at the frozen angel.
and minhum’s voice blared out from the speakers installed throughout youngdungpo station.
“sungwoo, we’ve all the flying weapons, all the shooters and all the wizards on standby right now.
 just let us know when you need to attack.
”however, sungwoo thought that something was still lacking.
 to kill the angel once and for all, he needed to mobilize all the firepower available.
sungwoo got aboard bone wyvern and soared into the sky.
“deputy! i heard there is a corpse depository!”“yes.
 we have piled up the corpses of the monsters steadily to make them available for weapon materials.
”“please take out all of them right now!”“oh, are you going to use explosions?”minhum could immediately figure out what the necromancer was going to do when he mentioned the corpses.
“yes, that’s right! we have to use all our weapons at once to blow up the angel with one stroke! didn’t we clear the quest before the frozen seed turned youngdungo station into something like an antarctic base, right?”minhum nodded and lifted the microphone.
 his voice came out of the speaker again.
“support team! take out all the corpses from warehouse b33 and move them to the front! and the entire army should concentrate their attack on the angel.
 our target is her head and chest! concentrate your attack!”when he gave a specific order for the first time, the players started moving again.

“i don’t have time to idle away like this!”“alright! let’s smash the angel!”no matter how scary the situation was, soldiers were supposed to act once they received an order.
they began to demolish the angel’s ugly ice statue standing tall in the middle of youngdungpo station.
***how much time has passed? the explosions that kept banging like a drum stopped.
 with the blizzard fading away, a huge white body, namely the angel’s body was seen resting on the ground.
-you have earned 35,455,650 gold by hunting the ‘angel judge’.
“it’s over now!”sungwoo recovered the frozen seed while looking up at the angel’s body.
 it was proved today that the absolute being that descended from the sky was by no means absolute.
‘the absolute race is also no different from a single monster.
 if so, the world eater would be like this.
’today’s battle proved lots of stuff.
 sungwoo not only confronted the external beings but also beat them.
-you have acquired the title of ‘angel killer.
’* your magic resistance increases (+5%)* your fainting immunity increases (+10%)* your electric shock immunity increases (+10%)-you have leveled up.
 (lv.
 23)and the reward for his victory was enormous too.
 it’s been a long time since he saw the level-up message.
‘is it the first time since i saw one during the devil’s gate quest?’as a matter of fact, he has been engaged in more fighting the enemy players than hunting since then.
 it’s because he could obtain more exp by hunting the monsters.
however, he put off choosing the level up card for now because his top priority was to obtain ‘deity upgrade’ above all, which he thought was so valuable.
-you have cleared the exclusive quest  with ‘additional condition (angel judgment and killing)’.
* you can choose a reward.
1) regular upgrade of deity2) right to change your jobas before, he could choose between the ‘regular upgrade of deity’ and ‘the right to change your job.
’ of course, what sungwoo needed right now was the regular upgrade of deity.
sungwoo chose no.
 1 option.
-your deity grade has been upgraded.
 (step 1 → step 2)[skill information]-name: anubis’ power (step 2)-grade: demi god-classification: passive and active-consumption: 0*for only one hour and 30 minutes per day, you can gain the power of ‘anubis’ by gaining deity.
 all stats increase by (+15).
 you can use the exclusive skills.
as a result, he could use the ‘anubis’ for another 30 minutes, and all his stats also increased significantly from 10 to 15.
‘well, i don’t have to be so impatient because of the time constraints in the future.
’

that was not all.
-additional reward is given for clearing the exclusive quest ‘satisfying additional condition’ (killing the angel judge)’.
with that message, something came off the angel’s chest.
 it was a ray of light, which flew toward sungwoo’s hand.
 a message rang right away.
[item information]-name: judge’s mark-grade: special-category: camp item-effect: a person with this mark can designate a member of the same camp as the ‘target of judge’.
 (location can be tracked, and all stats are temporarily reduced by 90%.
)-description: this is the power that you can gain through the camp’s special achievements, which will be able to play an excellent role in maintaining the camp’s discipline and security.
according to the description, if the camp grew bigger, it would require a more subdivided organization, and some members could be given special positions.
the “judge” was also seen as one of them, and this mark was an item that could be given to the leader of the legal entity who would mediate the problems arising within the camp.
‘however, it will take a lot of time for us to be as big as the absolute race, so i don’t have to appoint a judge right now.
’however, there was an unexpected achievement.
-you have met certain conditions.
* lich (the one who deals with death) + bi hyong’s fan (the one who controls ghosts) + the judge’s mark (the one who enforces the law) + the judge’s mark (one more judge’s mark is required.
)‘this is the message that rang when i got bi hyong’s fan.
’it seemed that the “judge’s mark’ met the remaining conditions.
 however, because it needed a total of 2, he was not yet given the reward.
‘so, what the heck is this?’

 