\section{chapter 285}






 it was 10 hours before the arrival of the angel.
“we’re going to start the temperature now!”but there was something more urgent than that.
“it is currently measured at negative 34 degrees centigrade near mt.
 namsan in seoul! as for the temperature of the center, we need to get close to measure it precisely!”the wide area surveillance team reported the results of the temperature they measured with specialized equipment on a helicopter flying over namsan.
 according to their report, the temperature in seoul kept falling.
sungwoo, his party, and junghoon were getting warm in a building near mt.
 namsan.
after a while, minhum came back and briefed them about the situation.
“after interrogating the russian prisoners, we found out what they planted in mt.
 namsan was the so-called ‘frozen seed’.
 it means something like a winter seed.
 it’s a strategic weapon that quickly lowers the surrounding temperature and freezes the whole area.
”“if you remove it, does the freezing function stop?”when sungwoo asked, minhum said with a nod, “yes.
 the problem is without that woman sorcerer named tatana, nobody can touch it.
 it’s so cold that you won’t be able to even touch it when it’s running unless you have enough cold resistance.
”junghoon swept his face down with his palm as if he was frustrated.
tatana was the person who used the freezing magic strong enough to freeze the entire crusader team.
 who else has that kind of cold resistance? there was none like her, as far as junghoon knew.
at that moment, sungwoo stood up and said, “i know something.
”“pardon? do you even have cold resistance?”“no, i’ve got something similar.
”
sungwoo could endure the strong cold through the “salamander’s aura”, the effect of the flame traits opposite to cold resistance.
 there would be some limitations.
 he wondered how far he could endure it, but right now, there was no other way.
“i have to finish it before the angel comes down, so let’s move right now.
”***members of the wide area surveillance team wearing specially modified cold protection equipment were climbing mt.
 namsan.
 water vapor was rising from their bodies then soon became frost and landed on their shoulders.
“haaa… haaa…”“it’s a blizzard ahead!”they wore gas masks and attached ‘burning stones’ they obtained by hunting “fire golems” inside their coats made of the leather of the “ice troll”.
 they felt hot as if there was a heater attached to their bodies.
however, even when they were thoroughly prepared for the extreme cold, they had no choice but to feel cold as they approached the top of mt.
 namsan.
“the blizzard is so severe! everybody, grab the rope and move in a single file!”“move in a single file!”after such a hard hike, they finally reached near the peak.
 when they looked up, they saw namsan tower standing in a blizzard, but thick ice was sticking to it as if the ice age had arrived.
“set up the equipment and measure the core temperature!”they installed precision temperature measurement equipment then aimed the laser at the center of the blizzard.
 a number appeared on the dashboard.
“the core temperature of the blizzard is negative 259 degrees centigrade!”“absolute zero,” commonly known as the temperature of outer space, was negative 273 degrees centigrade.
 so, the temperature at the core of the frozen seed was comparable to that of the space.

“crazy… now, we’re getting out of the blizzard! from now on, the necromancer will carry out the operation!”“get out of the blizzard!”while the crew members were retreating, a helicopter flew to the slope of namsan mountain.
 but the point was the limit where the helicopter could fly because there was a great possibility that if the helicopter flew further, it would be caught in a blizzard and crash.
a man jumped out of the hovering helicopter.
“he has arrived! necromancer!”“oh, my god! is there anything impossible for him?”the necromancer, wearing black armor with blue flames, walked uphill covered with snow.
every step he took, the snow that accumulated as high as his knees melted into a fan shape and disappeared.
cheeeeeeeeeeeeee-the operation team leader stepped forward to welcome the necromancer.
“i think the target of our temperature measurement is stuck right under the namsam tower!”since they couldn’t get into the blizzard, they had no choice but to estimate the location as accurately as possible.
“and the core temperature is negative 259 degrees centigrade, so if you breathe in, your lungs will be frozen.
 is it still okay with you?”“no problem!”“just in case, our team is on standby, but we cannot guarantee we will take any action to help you if something happens to you inside.
 sorry.
”“got it.
” sungwoo calmly nodded then walked straight to namsan tower without any particular preparation.
the operational team leader who followed him was forced to fall back at some point because he couldn’t endure the cold.
“please be careful.
”sungwoo disappeared into the blizzard without looking back.
“can he make it?”the team leader shook his head when one of his team members asked.
“i have no idea.
 if he can’t succeed, we have to pack up and flee from seoul.
”“haaa… by the way, why is that person always our last hope?”the team leader knew the right answer.
“well, it’s because he has never failed.
 and there is no other player after him because all the events and quest ended once and for all when he intervened.
”but no one could be sure what would happen to him this time.
***whooooooooooo-the blizzard was so severe that no one could see further than their noses.
 since the trail was also covered with snow, nobody could walk on the right trail.
 it was the so-called whiteout phenomenon that could be seen in a snowfield.
fortunately, sungwoo had a hidden weapon that was not affected by the laws of physics.
 it was a ‘spector’.
 he could move forward little by little by relying on its eyesight.
at last, he reached the heart of the blizzard.


goo goo goo-a huge pillar of ice towered over him.
 there was a hole in the middle of the long column, where a white ball was vibrating, floating in the air.
-‘frozen seed’ is working.
* creates an ice age in the area (seoul).
 (22:44:00)* if you want to stop it, you have to remove it from the ‘tower’.
‘ice age? man, it was terrible stuff.
’it was a weapon strong enough to blow up the entire ecosystem of a certain area as the russian players confessed after they were interrogated.
‘i can’t get closer.
’even if he was wearing hellfire armor and wearing salamander’s aura, sungwoo couldn’t overcome all the cold.
 his whole body got cold rapidly, and his fingers and toes began to hurt.
 he might already have gotten frostbite.
sungwoo summoned two “troll skeletons”.
 if he couldn’t go inside directly, there were plenty of skeletons who could do it for him.
“pick that one.
”however, right after he summoned the troll skeletons, frost began to accumulate all over their bodies.
 the blizzard penetrated their bones, making it difficult for them to move their joints.
rattle! rattle!they tried to move forward, but the moment they reached out to the pillar of the frozen seed, they were frozen completely and stopped moving.
‘any subject with a physical form can’t approach it.
’

 