\section{chapter 352}

chapter 352: jeju island and attack on demon’s cave (16)“ah…”




at that moment, jisu, who was looking at the portal, hardened her face.
 she looked as if she tried to see through to the world beyond it.
“sis, step back!” she shouted.
“huh? why?”“you will find it hard even to step back a little later.
”at the same time, a message rang.
- the middle-level boss monster ‘guardian of the gate of demon’s cave’ has appeared.
“he’s come out earlier than expected.
”“gatekeeper?”the ‘guardian of the gate of demon’s cave,’ who was the final boss on the first floor of this cave, appeared as the middle-level boss this time.
thump- thump- thump-he leisurely walked out of the portal.
krurrrrrr…the terrifying-looking giant growled, revealing his obsidian teeth.
the horns and projections growing from his back and shoulders wrapped around his body like armor, and he was holding a pole wrapped in blood in his right hand.
 even at the end of it, the upper body of a person was stuck like a decoration.
 it wriggled and moaned as if it was screaming.
“crazy…”it was a monster created by feelings of disgust and fear.
- you have been overwhelmed by the ‘alien creature.
’* all stats decrease.
 (-50%)gasp!
jimin almost sat down for a moment.
 the reduction in her ability by a whopping half came as a shock to her.
 she wasn’t the only one who experienced it.
“argh!”“i can’t move my body…”a large majority of the players on jeju island, whose level was low, flopped down.
even players of the world tree camp were complaining of similar symptoms.
 the appearance of the middle-level boss monster itself put sungwoo’s allies into disarray.
“what the hell is that monster…”gasping for breath, jimin looked at the monster.
 but, at that moment, she saw somebody walking casually around the monster.
 jisu was there!“jisu, how come you can…”unlike the other players who became enervated due to the drastic decrease in their stats, she looked pretty healthy, not affected by the stats decrease at all.
‘i can’t believe it!”rattle!at that moment, a dark red armor appeared on jiu’s body and began to wrap around it.
 at first glance, jimin knew this was an extraordinary piece of equipment.
rattle! rattle!as if the golden metal was tempered with blood, the armor glistened with cruel beauty.
the wing-shaped decorations here and there seemed to spread their brilliant wings at any moment.
- an ‘unknown energy (friendship)’ has appeared.
she had an aura beyond expression, which showed she obtained the ‘deity’ status.
watching her sister stepping forward, jimin realized something about her.
‘gosh, that’s why you have not moved until now because it’s not the right time for you to intervene…’
a ray of light came out from behind her.
 then, two blue tigers appeared on her sides.
it was the sortie of the valkyrie, who was preparing for the worst.
in hindsight, jisu was always consumed by a sense of helplessness and deprivation when she was young.
 because she was an illegitimate child, she was destined to be shunned by people, always conscious of how they looked at her.
 she exercised hard to overcome such prejudices and discrimination, but she didn’t do better than her half-sister.
‘it was so unfair.
’her sense of helplessness turned into the source of her frustration and resentment.
 she resented her mother, who fell in love with a married man, gave birth to her, gave her a weak body, and died irresponsibly.
 so, she resented her mother until she fell asleep every night.
‘if i didn’t run away, i felt like i would be trapped inside those walls and suffocate to death.
’by the time she grew to be a teenager, she gave up on fighting her inferiority complex and escaped.
 she left the house and began to live alone when she was a sophomore in high school.
‘i felt so comfortable briefly… yes, very briefly.
’even though she left the house, she couldn’t overcome her mental illness completely.
 she just forgot it while she was living as someone who was a tad better than ordinary men.
but she began to revive her forgotten symptoms on the first day this hellish game started.
 when she encountered a huge monster orc on the mountain behind the school and fell after confronting the monster, she felt a sense of helplessness and resentment, which she had forgotten until now, rising again.
‘back then, i felt something like a wall again…’but she felt something different this time.
‘after that, i started breaking the walls.
’how could she break the wall? and why didn’t she do it when she was young?“lady, it seems that there are two.
 there’s one more monster.
”the voice of the tigers brought jisu back to reality.
 she raised her head.
 a terrible monster standing before a purple portal caught her eyes.
“right! i felt it, too!”soon, another ‘guardian of the gate of demon’s cave’ came out of the portal.
krrrrrrrrrr…finally, two middle-level boss monsters appeared, which plunged sungwoo’s allies into chaos.
“no way! i can’t believe this!”“how come there are two terrible monsters here?”the players of the world tree camp were brave, but they knew that fighting the monsters with their stats reduced by half would be suicidal.
 that’s why inho, who was in charge of this operation, looked at jisu who was determined to confront them alone.
‘we can’t kill them just by attacking them.
 if we join the fight, she can’t fight as freely as she could,’ inho thought to himself.
that’s why she asked him not to help her during the fight.
 after all, she was going to confront the two monsters alone.
she grabbed the sword firmly and glared at the two monsters.
“we are the only ones who can fight with you.
”the two tigers standing to her left and right shouted, raising their hammers.
“yeah, i know.
”“we’re ready to join you!”“ready to play, it’s over.
”at that moment, a huge shadow approached them from behind.
“hey, dude! how come you don’t even say hi to your big brother?”he was the king of the great mountain.
 come to think of it, he was also in good shape.
“tut, tut.
 it’s just useless raising guys like you…”the king grumbled to ‘einherier’, the two tigers who became her subordinate spirits.
then, he turned to jisu and said, “lady, the two monsters are pretty hard to beat.
 as you know…”jisu nodded at his words.


during the battle in taiwan, the necromancer, armed with deity status and at level 21, had a hard time confronting one boss monster, but this time there were two monsters.
“you have to finish this fight as soon as possible because they use a wide range of magic…”she slowly turned her head and looked at her sister, jimin.
“they’re going to cause lots of harm everywhere…”“well, let me fight the monster on the right.
 jisu, get rid of the left monster!”“brother! you really make me…”not caring about the two tigers’ complaints, jisu moved to the left.
“got it.
 let’s take action right away!”the two tigers also moved with her.
 it was time for them to start the fight without further delay.
krrrrrrrrrrrrrr…the gatekeeper monster’s expressionless face turned towards jisu.
she didn’t feel scared at all while staring at his face.
 she was only thinking about how to fight.
‘let me attack him with the beam first.
’she already experienced it before, so she knew some of their attack patterns.
not surprisingly, when she approached him from the left, the monster on the left raised his staff with a human’s upper body.
 at the same time, something like a beam of light flashed.
bang!a red beam flew towards her, but she avoided it by jumping off the ground.
 there was a deep dent in the ground where the beam touched it.
bang!the monster tried to attack her, who was soaring into the air, but she wasn’t there.
 she was already approaching the gatekeeper monster quickly.


 