\section{chapter 292}






 the place where sungwoo arrived, guided by kyongsu, was outside suwon.
 it was an old town, but a light smoke was rising from a store building.
“uh? what’s that?” hanho opened his mouth, raising his head.
 he was watching the rooftop of a store building.
 it was something like a ship.
“isn’t it a real ship? why is it here?”there was a boat on top of a five-story store building.
 from a distance, it looked like unique architecture in a port city, but it was a real wooden sailboat.
the sailboat with holes in various places around it was inclined downward on the crushed rooftop of the building, which looked pretty dangerous because it was likely to collapse at any moment.
“this is an airship traveling in the sky, not sailing in the sea,” said kyongsu.
“is this flying?”“yes.
 i was also embarrassed to see it.
 it looks like it was hiding in a cloud, but it crashed in this place this morning with an explosion.
”when sungwoo checked it after hearing that, he noticed the ship was really different from the typical ships in the sea because it had huge engines on both sides of the hull.
“the building might collapse, so we have to approach it carefully.
”it was dangerous for them to enter the building, so they got onto the rooftop of the building through the next building.
while the players of the world tree camp were on the lookout for any suspicious movement nearby, the technicians who were looking inside the sailboat came out to the deck.
looking down at sungwoo and kyungsoo, they explained the results of their investigation.
“when we looked into the engine compartment, we found circular compartments for each engine.
 it looked like some important parts were missing.
 perhaps some items that could fly the ship were there.
”“got it.
 it seems like the intruders took the part, but they must be very valuable.
”if they were the items that could fly this huge object in the sky, they would definitely have tremendous value.
“if then, doesn’t it mean there are a few more airships like this somewhere?”sungwoo nodded at kyongsu’s reasoning.

“maybe there are players who can manufacture something like this, just like the evolution society made items in the field of biology.
”muyon, who had the job of a “high architect,” built the wall several kilometers long in only a few days.
 as a result, there must be a player who could make such a huge piece of equipment.
“america has the best technology even after its ruin? sungwoo, if you approach it, the item information appears.
”they installed a temporary foothold because the rooftop floor partially collapsed when the sailboat crashed.
 sungwoo stood on the squeaking foothold and put his hand on the bottom of the ship.
[item information]-name: dwarf class 3 airship-class: unknown-category: player’s manufacturing item-effect: high-altitude flight and large-scale defense barrier.
-description: this is , an aircraft transport plane made with dwarf technology.
 85 meters: long, maximum load capacity: 40 tons, total crew members: 55, maximum speed: 35 knots, general manager: jonathan cage, no.
 1 external affairs team leader.
 other detailed information is confidential.
*this item is valuable and property of w·p·u, so anybody who approaches without authorization can be killed without warning.
 (manufacturer’s direct description)-status: operation suspension (completely destroyed, no power source installed)after reading the message, sungwoo frowned.
“i don’t know what that means, but the message has lots of details.
”“that’s right.
 but i’m not sure if they are systematically organized…”sungwoo took a dim view of the fact that they were operating systematically because he had never seen any group with a system of their own operating like this.
of course, a well-established system would be needed someday.
 but what’s important right now was a flexible survival strategy, not the procedures and rules that delayed decision-making.
“we’ve found a total of 42 bodies inside the ship.
 we can’t figure out what happened, but i assume there was a revolt inside.
”
on one side of the rooftop, they were busy moving the corpses inside the ship.
 so, sungwoo approached them because he could get lots of information from the corpses than anything else.
“oh, my…”however, the corpses had their heads and limbs cut off altogether.
in this case, he could not confirm their memory fragments because he could not resurrect them as skeletons.
at that moment inho, who was in charge of managing the players at the accident site, approached.
“given the magnitude of the slaughter, don’t you think somebody with electric chainsaws came here from texas in america?” he said jokingly.
then, he began to explain, looking down at the corpses with a serious expression.
“i don’t know exactly why they did this terrible thing, but it looks like they slaughtered their targets brutally to make it impossible to identify who they were.
”“their identity?”“they come from very far.
 they were not definitely from the korean server.
 then, i guess there was a civil war.
”his guesswork was interesting.
 civil war beyond a simple revolt?when sungwoo nodded, he continued, “assuming the american people engaged in fighting with each other, they must have killed their opponents in a way that nobody could identify who the victims were.
”sungwoo nodded at his reasoning.
“that makes sense…” jisu cut in.
drawing her sword, she came forward and stared at the sailboat.
“sungwoo, we have to evacuate the people inside.
”sungwoo did not ask what was going on because her reaction like this meant that something dangerous was going on.
sungwoo looked at inho, who put the radio in his hand to his mouth without asking why.
“everybody, escape from the sailboat right now! get out of there right now!”in no time, the players working inside of the ship came out in droves.
only then did sungwoo look at jisu.
“jisu, what’s going on?”“it’s something small, but i can sense a lot of their movement in my ears like a bug.
”sungwoo immediately summoned two specters.
 then, he dispatched them deep inside the ship where she felt the sound of movement was coming from.
the specters penetrated the sailboat and reached the area in question in no time.
there was a black box.
 sungwoo read the information of that object through the specters.
ooooooooooooh-[item information]-name: player killer box (poisonous bug)-rating: unknown-category: player’s manufacturing item-effect: when the player approaches it within 5 meters, the box opens and 3,000 ‘poisonous bugs’ are released.
 regardless of your defense power, you will be counted as killed unconditionally when you are shot ten times.
‘this is actually a booby wrap.
’someone left behind a terrible gift, knowing that the world tree camp would search the wreckage of the ship.
‘they can kill us regardless of our defense power? man, this is the worst gift!’fortunately, the object was hidden in the deepest part of the ship.
 in order to cause great damage, they hid it there, so sungwoo’s party could find it later, not early on.
after sungwoo evacuated all the players, he dispatched the skeletons to pull out the box.


of course, he made sure no players should approach it.
“this is virtually like terrorism against us.
 if i hadn’t noticed it, many villagers could have died.
”there was deep anger on jisu’s face.
sungwoo said coldly, “let’s return the box to them because we haven’t opened it.
”“…”she was embarrassed because sungwoo clearly wanted to counterattack the enemy with terrorism.
sungwoo continued with a hardened expression, “if we don’t kill them now, somebody else could be killed.
 by the way, how can we find the enemy?”they were determined to fight, but they could not know their opponent.
 if sungwoo had watched their memory fragments, he would have solved the problem, but unfortunately, the heads of the corpses were cut off completely.
“ah!”at that moment, someone came to his mind.
sungwoo immediately looked back at kyongsu and said, “kyongsu, please contact hunter company.
 if you tell them you need to ask them a favor, they will accept it.
”the hunter company was very friendly to sungwoo because their leader was sungwoo’s hardcore fan.
 so, he would accept any request from sungwoo.
“okay.
 actually, i’ve been in contact with them.
 what do you want me to tell them?”“i need to find someone.
 oh, please tell them it’s not a human, but white werewolf.
”if the white werewolf had the ‘psychometry’ ability to read the memories of objects and connect with their minds, he would be able to read information from the beheaded corpses.
“pardon? who is that werewolf?” kyongsu asked.
he did not know the white werewolf’s capabilities because he had never seen it before.
so, sungwoo said briefly, looking up at the sailboat.
 “it is a hunting dog that will catch the intruder.
”

 