\section{chapter 371}

chapter 371: exit from demon’s cave and preparing to conquer china (3)sungwoo opened the device and very carefully grabbed the fruit.





[item information]- name: energy of the world tree- rank: myth- grade: unknown- effect: unknown- description: possesses wonderful power.
‘energy?’sungwoo has heard the word ‘energy’ several times.
 it meant something like the essence of some powerful power, such as the ‘mountain energy’ used by the king of the great mountain and the ‘world energy’ that the world eater aimed for.
the devil’s world tree perished a long time ago, but it seemed that even after it perished, the tree left a mass of intense energy.
for whatever reason, the world eater seemed to have decided to keep it because it would be helpful in the future, but when he could not achieve that purpose, he gave up enmity towards sungwoo and gave it to him.
‘maybe it will help grow the world tree in the sunwon village.
’the ‘myth quest’ leading to the new race ‘human dragon’ had been delayed for quite some time.
 sungwoo expected that it would take some time for the world tree to reach the stage of completion, but it could take several more months at the current growth rate, so the tree needed some kind of nutrients for rapid growth.
“sungwoo! look at this box!” hanho shouted.
hanho found something in the corner.
 it was a black iron box, large enough for a person to come in.
“isn’t something unusual? this must be a treasure chest if it’s left in a place like this, right?”sungwoo put his hand on the box.
- the box is protected by powerful magic.
* only ‘imprinted beings’ can access the box.
* ‘unseal’ order over grade 1 is required.

* requires the ‘unlock’ skill of the ultimate grade or higher.
it was a seal similar to the treasure house found at the end of a large-scale dungeon called ‘troll’s crypt’ that he had attacked quite a while ago.
“um, i think we need a key.
”“right.
”because it was sealed with a special magic, nobody could break it by force.
 so they needed an item like a ‘universal key’.
 that meant they could not open it now.
“just keep it for now.
’other than that, there was nothing else.
 sungwoo and hanho immediately went back the way they had come and soon arrived at the hole where the messenger was waiting.
woooooo-as if it had already finished preparing to escape early, the message was floating in the center of a huge hole, running the engine.
“sungwoo! we can leave right now.
” kyujngsoo shouted from the deck.
fortunately, there seemed to be no damage caused by the monsters.
while rushing to the messenger, sungwoo suddenly stopped walking and turned his head.
‘come to think of it, i still haven’t figured out who the hell made this huge hole.
’when he first entered here, he felt that there was something stuck inside the hollow area of the inner wall, but he didn’t check it because he had to go down in a hurry.
“sungwoo, what’s the matter with you?”sungwoo summoned a zombie monster bird.
“i have one more thing to check.
 go ahead and ask kyungsoo to wait for a moment.
”having said that, he got on the zombie monster bird and hurriedly took off.
 and he examined the hollow area in question.
“as expected…”
there was something very thin stuck in the center of it.
 sungwoo grabbed its end and pulled it out with force.
[item information]- name: ultra-heavy arrow- rank: myth- category: arrow- effect: unknown- description: very powerful.
 you can’t use it separately.
 you need a set item to use it.
“no way!”- set item (godly killer) has been completed.
sungwoo took out an ‘ultra-heavy’ bow, apparently an item to match with this, and checked the item description again.
[item information]- name: ultra-heavy bow- rank: myth- category: bow-effect: an ordinary person can never pull it.
 (conditions of use: muscle strength level 100 or higher)*when you pull the bow, an arrow is automatically generated and the skill “fall of the sun” is activated at the point of its impact.
+ fall of the sun: causes a wide range of explosion and fire magic near the point of its impact.
 you should use care when using it as it can burn the entire area.
 (cooldown: 10 days)+ godly killer: it’s activated when firing with the ultra-heavy arrow on the bow.
 neutralizes all defense effects of the target and causes huge destruction.
 (cooldown: 10 days)at the very end of the item explanation, a new skill called ‘godly killer’ became available.
‘it’s a weapon that punched a hole in the world tree in its completion stage.
’in other words, if sungwoo could pull it, he could break anything in the world.
right after acquiring the ultra-heavy arrow, sungwoo immediately got on the messenger.
“let’s go!”the messenger sailed at full speed and escaped the devil’s world tree.
- the gate of the demon’s cave will be sealed.
 (00:28:43)“can we get to the exit within the given time?”kyungsoo nodded at sungwoo’s question.
“judging by the time that took us here, we can get there safely.
 of course, on the assumption that we don’t encounter any unexpected variables.
”there was a high probability that no unexpected variables would occur because all the monsters must have disappeared when the world eater perished.
“fortunately, even the sandstorm has subsided.
 as things stand now, i don’t see anything that might interfere with us.
”while the messenger was sailing at full speed, sungwoo sat on a chair and checked the message he put off reading.
- the title of ‘professional dragon hunter’ has been improved (replaced) with ‘legendary dragon hunter’.
* increases stamina (+7)* increases muscle strength (+5)* increases fire immunity (+45%)* increases magic resistance (+15%)* increases fear resistance (+20%)his titles kept being upgraded when he hunted a number of dragon-type monsters, starting with drake.
 it was the same this time.


‘above all, it’s important that i have gained fear resistance this time.
’even though he possessed the deity status, he felt his body got stiff when the world eater used ‘dragon fear’.
 with fear resistance, sungwoo could get out of it and confront the dragon in perfect condition.
‘of course, it may not work before the real dragon.
’even though the world eater killed a dragon and got the deity status related to the dragon, the real dragon would be different.
 besides, the world eater that sungwoo faced was too sick and weak.
‘i don’t know exactly, but i must prepare with the assumption that the dragon is the worst enemy in every respect.
’then he confirmed another message.
- you have successfully cleared the exclusive quest [guardian’s duty-3].
* you can choose a reward.
.
 upgrading your regular deity.
 right to change your jobhe cleared the guardian quest by destroying the heart of the demon’s cave.
 as always, he received a reward related to the deity.
‘i don’t want the right to change my job… as for my deity, should i upgrade anubis?’based on his experience with using anubis, there was no difference between ‘regular deity’ and ‘temporary deity’ in terms of its capability.
 its function was exactly the same.
however, the temporary deity required strict ‘activation conditions’, but the regular deity was embedded in his body, so he could use it like a skill.
‘that alone is a huge advantage as in the case of anubis.
’he didn’t have to use ‘human monster ampoule’ to draw out the power of anubis after obtaining the regular deity.
 thanks to that, he could use it more efficiently and strategically.
what’s more, the decrease in his ability and fatigue, which came right after he used the regular deity almost like a penalty, also disappeared.
‘i may lose the conditions for triggering the deity in the worst case.
 it’s not bad to upgrade the temporary deity to a regular deity just in case.
’

 