\section{chapter 407}

how did hanho, who had a one-star job and had no awakening, obtain the deity status?




in fact, it was very simple.
"wow! so far i've never made any mistakes in my investment!"deity status meant bringing out the power of a god, so anybody who wanted it had to satisfy the certain 'traits' of the specific god.
and one could obtain it only when one gathered various 'conditions' related to the traits of the god like sungwoo and jisu.
 it was as difficult as solving a puzzle.
 besides, one should have a bit of good luck.
 because of that, gathering the 'conditions' was possible through a kind of 'hidden channel.
'surprisingly, that was the case with hanho.
- congratulations! you have met the conditions for obtaining the 'regular deity'.
* individual shield value exceeds 200,000 (master of defense)like this, one needed to achieve something ultimate to meet the condition for the 'regular deity.
'"by the way, when did my shield value go up so high? oh, i see! because i was holding this shield!"hanho's current shield value was 225,000, which was even higher than the 'shadow of the divine tree', the invisible barrier of the world tree camp.
a shield that was enormous enough to safely encircle a vast area was compressed around only one person, namely hanho.
 "oh my god! i really didn't know my shield value went up like this.
"even hanho himself was puzzled.
"well, no matter who said it, i think i have made a wise decision on whatever i did.
"basically, hanho liked all kinds of items, but he was also so single-minded as to choose something based on the criteria of 'cool.
' the main reason was that he tended to choose only those that looked 'cool' among the items.
 in that regard, hanho thought that his shield was pretty cool when he obtained it, so whenever he leveled up, he tried to raise the skills related to the shield.
that's how he obtained the current shield.
 [skill information]
- name: convinced executioner.
- grade: craftsmanvisit lightnovelworld.
c‌om for the best novel reading experience- category: active- consumption: 10*the moment you kill your opponent, you gain a holy shield for 120 seconds.
 additionally, you gain immunity to all curses and abnormal status.
 (+50%)+ inspiring faith: each time you kill the enemy, you gain an additional shield value (+100).
 (max 200)[skill information]- name: bloody penance- grade: skilled- classification: passive- consumption: 0*five minutes after you begin the fight, you will get 'red awakening every 10 minutes.
 (max 5).
 the effects are as follows: defense power increases (+5%), maximum mana increases (+50), shield formation increases (+1%), recovery speed increases (+1%)in addition, hanho obtained an overwhelming shield value by wearing items with numerous defensive effects, such as the bodyguard spirit, achilles' shield, and aegis.
above all, he was holding as many as five shields, so it was natural that their effects were maximized, which led him to obtain the deity status.
- you have gained the power of the northern god 'hyunmu'.
 (regular deity)* every time you exercise deity status, you will turn into a demigod.
 * all stats are greatly increased.
 (+10)
* you can use the skill .
* you can use the skill .
* you can use the skill .
'hyunmu' is described as the item with the strongest defense power and yin energy in oriental fantasy.
 in other words, hanho had to reach the ultimate level of defense power or yin energy in order to obtain the deity of hyunmu.
"wow! this is the ultimate of coolness!"hanho couldn't help but turn up one corner of his mouth.
 he was all smiles now.
 for more, visit lightnovelworld.
c‌om"hey, why don't you try to attack me again?"a while ago, the emperor, feeling the birth of hanho's deity status, mobilized all firepower to attack him, but hanho absorbed and bounced back all his attacks through 'absolute defense' skill.
 as a result, the oppressed's hands were bounced out of the rampart by a powerful beam of light, something that the emperor never expected.
 but that was just the beginning of hanho's counterattack.
- caution! 'incarnation (hyunmu)' has begun in the affected area.
when this message spread throughout the area, black and green glows began to appear behind hanho's back, then changed into something very quickly.
woo woo woo-the first thing that appeared was a huge shell, which was the size of a house.
 it was none other than a turtle.
 but what's strange about the turtle was that he didn't have one head.
tsutsutsutsu-another head emerged from his shell, which was the head of a giant snake.
 in other words, the turtle's tail was a snake.
"as expected, it's really cool!" hanho shouted in excitement.
 hyunmu was described as a mysterious creature mixed with a turtle and a snake and four long legs.
 that's why hanho liked it so much.
 hanho stepped out of the shadow of the gigantic creature and looked up at the oppressor's hands.
"man, i didn't know i would be such an eloquent speaker!"when hanho raised the five shields at once, the 'incarnation of hyunmu' appeared behind him and raised his body.
 "you can't pass here, greenhorn!"of course, hanho's words didn't look cool or important because it was clear that nobody could cross that area easily.
 but the thing was hanho was buying time while blocking the emperor's attack through the oppressor's hands.
 as a matter of fact, while hanho was dragging his feet like that, the necromancer was actively moving to deal a fatal blow to the emperor, as jisu expected.
the necromancer was planning to devastate the enemy instead of making this fight something like a battle of strength.
***sungwoo stood far away in the rear of the battlefield while controlling the undead army.
 although they pushed very hard, the emperor's terracotta army as well as the 'spear unit' of the chinese army, totaling more than 100,000, didn't collapse easily.
the source of this content is lightnov­elworld.
comsungwoo looked at li wei.
'even liwei's water spirits can't help much…'by manipulating the large pool of water on the ground, she created huge waves.
 when she first generated the waves, they were big enough to engulf everything, but when they got close to the enemy camp, they became remarkably small, so they could not deal any destructive blow to the enemy troops.
"damn it!" li wei shouted in frustration.
 although the waves were a powerful attack comparable to that of a disaster, it was hard for them to sweep away the army of players with various occupations without any additional reinforcement.
"they really can't get close to the enemy!"it was because of the magic unit of the chinese army that blocked the waves.
 they stopped the waves by casting the 'control magic' that could neutralize water spirits, or 'wind magic' or 'ice magic' that could neutralize the waves themselves.


"hold out a little longer! all you have to do is distract the emperor!" sungwoo said calmly.
in fact, sungwoo originally had no intention of defeating the emperor's huge army.
he raised his head and looked up at the sky.
 the sky here was relatively clear because zi xuan pulled down all the clouds.
'it's coming.
'something appeared in the light clouds in the sky.
 then it began to descend towards sungwoo fast.
 beeeeeee-it was the eagle's voice, namely, griffin.
"necromancer!"hyeon and griffin were coming toward him at his request.
"i've brought it!"using the radio item sungwoo had requested her to communicate with the allies at the rampart to bring a certain item urgently.
as a result, heyon, the 'griffin rider' with the best mobility, delivered the item.
sungwoo accepted the item.
 "okay, let's get started.
"for more, visit lightnovelworld.
comhe finally obtained the hidden item.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 