\section{chapter 373}

chapter 373: exit from demon’s cave and preparing to conquer china (5)she sped up with the intention of breaking through the thorns.
 she did some stunts in the air, avoiding the thorns.
 meanwhile, she did not stop herself from falling to the ground.





two whips chased her like a snake.
clang!she swung the sword to block them, passed by the commander, then moved towards the no.
 4 airship.
 he turned his head to chase her, and the two whips also turned to follow her.
she felt like she was chased by a guided missile when she noticed their tenacious chasing.
finally, her feet touched the hull of the crashed ship.
 at that moment, the roots creeping up from the ground crawled into the hull, supplying a large amount of mana into it.
‘not yet?’she raised her head.
 two whips were flying towards her head.
 they were so fast.
it seemed that they would pierce her through vertically at any moment.
wooooo-in an instant, the power of the airship was restored and a translucent wave rose around the airship, which indicated that the shield of the airship was restored.
clang-just like it experienced before, the airship’s shield could not stop the monster’s attack.
 he pierced the shield so easily as if he broke through plastic wrap with his finger.
but jisu’s body was not there.
using the ‘shadow chase’ skill, she arrived right in front of the monster in an instant.
until now, she couldn’t use it because the monster moved his arms so fast with perfect dexterity.
 but she was different now.
kheeeeeeeh?
even if he swung his long hands, the monster could no longer stop her from approaching him now.
‘i got him!’even though he could easily pierce the shield vertically, he could not swing it to the left and right.
 in other words, it was like him putting his arms in a swamp.
 although he could pull out his arms by force, he could not move his arms to the left and right.
but it wasn’t ‘checkmate’ yet.
‘i should not go inside further.
 hundreds of his mouths will throw out liquid.
’jisu already had such an attack in mind.
 soon, ‘einherjar’ warriors connected by a beam of light were summoned behind her back.
 they jumped out in front of her.
“we’re ready as you ordered!”each of them was holding one huge shield.
 because their minds were connected to her, she could give them her order even if she didn’t speak to them directly.
buhwaaaaaaaaaa!as expected, hundreds of mouths opened on his body and spat out a sticky liquid.
 jisoo hid behind the shield to avoid the acidic liquid.
“ugh! my shield is melting down!”their shields melted like cheese, but they could throw out the acid liquid for only two seconds, so einherjars endured it desperately.
jisu got hold of them tightly, and as soon as the monster stopped vomiting, she jumped towards him and swung the sword.
as soon as she wielded the sword, she stepped back quickly because if she hesitated a bit, she could be exposed to the monster’s thorn attack or acidic liquids.
‘damn it, i should have killed her early on…’at that moment, the monster twisted his body violently to avoid her attack, so she ended up cutting his right arm, not his head.

after all, he put down one of the two whips on the ground.
 she stepped back far from him and thought hard about the next move.
‘since he lost one arm, i can attack him more easily.
 but i shouldn’t get close to him right now.
 it’s dangerous for me to try the same tactics again.
’while she was pondering over how to attack him, suddenly, the air currents changed and a harsh wind began to blow.
 the cause of the gust was the gate of the demon’s cave.
“uh?”“what the heck is this?”everyone looked there.
 the airflow around the area began to change because the surface of the portal created a vortex after it was severely distorted.
jisu did not take her eyes off the commander, but she could feel something strange was happening at the gate of the demon’s cave.
suddenly, a wind mixed with sand was pouring out from the gate of the devil’s cave, giving out a strong smell of death.
‘something is trying to come out of the gate.
’was another demon coming out? she shook her head.
 there was no additional message about the wave of demons.
‘man, it’s huge.
’what is it?‘there is only one answer.
’she moved instinctively.
 she put her weight to her feet and relaxed her wrists.
 then, she lifted the tip of the sword slightly and breathed out slowly.
wheeeeeeeng-the gate of the demon’s cave twisted as if it had birthing pains, then huge white forepaws came out.
 everyone who saw the scene opened their mouths wide.
even jisu wiggled her eyebrows at the unexpected scene.
“oh, my god!”“what the heck is that?”bigger than anything she has ever seen, the big forepaws made of bones appeared, forcing the portal to expand.
 they broke through the ground, then bounced up, striking down the commander standing near the portal.
thud!the commander of the 1st army of the demon’s cave, who boasted of his overwhelming power, was attacked defenselessly by the monster’s unexpected and overwhelming attack.
kheeeeeee!crushed by the gigantic forepaws, the commander desperately twisted to escape, but to no avail.
jisu instinctively jumped off the ground.
 it was an opportunity she couldn’t miss.
 she charged at him quickly, then swung the sword at him accurately.
his head was cut in the blink of an eye.
- you have obtained 33,350,000 gold by hunting the boss monster ‘commander of the 1st army’ of the demon’s cave.
however, the acidic liquid that filled his body burst out and poured over her head.
she jumped off the ground and turned her body at the same time, so she could avoid his acidic liquid, but she was thrown almost 10 meters and rolled across the ground.
“jisu!”it was jimin, her elder sister.
 watching her fighting nervously until now, she finally came running to her.
“you’re okay, right?”

of course, she didn’t suffer any severe damage from such a shock.
 she stood up right away and nodded at her sister.
“what a relief! by the way, what’s that? is it a monster again? isn’t it over yet?”jimin couldn’t hide her embarrassment.
 she has seen countless monsters coming out of that hole until now, but she has never been as terrified as she is now.
 even the world tree players were whispering among themselves as if they were also embarrassed.
right after the gigantic forepaws came out, which crushed the boss monster at once, a huge skull appeared next.
kuuuuuuuuu-then, the entire body, which reached several hundred meters, perfectly revealed its overwhelming figure.
 at the same time, when the wings of the cloak hung over and completely obscured the sky, only two green eyes were glowing lonely in the shadow.
by then, everyone knew what it was.
“can you believe this?”“no way! is it…”it was bone dragon.
‘as expected…’it was the first time jisoo saw it, but she could feel it right away.
“sister, he’s not our enemy.
”jimin could not yet believe what she just saw.
“what? he’s not our enemy?”jisu nodded and said, “he’s our friendly reinforcement.
”

 