\section{chapter 283}






 while looking around, sungwoo found victor and over a thousand zombies.
then, he yelled at victor, “victor! revoke all summons of your subordinate spirits!”“pardon? crackle!”“recover mana from your zombies!”“understood!”victor at first looked puzzled because he didn’t understand sungwoo’s intentions but followed his order.
soon, the zombies who were excluded from victor’s “subordinate spirits” became wobbly and collapsed.
 now there were their bodies everywhere.
-‘evil spirit bombing’ dwells in your weapon.
sungwoo once again triggered the evil spirit bombing then fired them at the tsar.
but the tsar changed into a turtle shape right away, protecting his body.
 however, this time he did not easily give up the turtle shape because he was hit directly by the giant’s feet the moment he was released from it a little while ago.
sungwoo seized the moment and attacked his soft spot when he was noticeably slow.
“twilight raid.
”– ‘twilight raid’ has begun.
sungwoo turned into a black whirlwind and rushed toward him.
goooooooooooo-no matter how powerful the tsar was, he couldn’t withstand the twilight raid.
 the tsar’s body was entangled in a black tornado and swept away.
 a few seconds later, he was thrown on the ground violently.
 at the same time, the hand of the ghost came up from the ground and bound his body.
“kheeeeeee! you son of a bitch!”at that moment, there was an odor coming from the surroundings.
 it was from the ‘field of zombie corpses’ that victor created a little while ago.
looking down on him, sungwoo murmured, “keep crouching well, so you can be roasted well.
”then, he jumped off the ground and got out of the zombie corpse field.

he shouted at the same time.
“explosion!”bang! bang! bang! bang! bang!without changing the shape behind his back, he was helplessly engulfed in the explosion.
at that moment mir, who was in jisu’s arms, released mana at the same time when sungwoo did.
 it was a corpse explosion magic.
 and victor also participated in the chain explosion subtly.
“explode! crackle!”kwa-wa-wa-wa-wa-wang-over a thousand zombies exploded when sungoo, mir, and victor released mana at the same time, bursting with tremendous shock and heat.
 it was as if an oil refinery had exploded.
when one explosion stopped, two or three explosions followed in succession, shaking the whole yongsan area.
the melting heat spread into the air, quickly heating the siberian cold around yongsan.
 a magnificent haze arose at the point of the explosions.
“is it over?” hanho asked, but nobody answered because they didn’t know until they confirmed the results.
it was jisu who first noticed something unusual.
“no, it’s not over.
”soon, the smoke from the explosion disappeared, and something was moving.
“keeeeeeeeeeeeh…”it was the tsar.
‘is he still alive? how could he survive?’tsar, covered with wounds and in tatters, raised himself from the ground, his eyes full of resentment.
“necromancer….
”soon, the “demon beasts” began to gather behind him.
 they were united again and changed into a completely different shape, which was a black dog with three heads.
“i will tear you to pieces and kill you.
”
‘cerberus? is that his deity form?’when the tsar raised his head, the three heads charged at sungwoo.
 sungwoo could not escape by throwing his body.
 fortunately, he escaped it through the shadow movement at the last minute.
kwa-wa-wa-wang!the three heads hit the yongsan station building.
 as if three demolition cranes with iron beads moved at the same time, the ceiling and the outer walls of the station collapsed like shattered glass.
yongsan station was destroyed in a series of explosions.
 so much so that it was an unrecognizable shell as if somebody with three hands pulled down a handful of sandcastles.
‘this is dangerous.
’three giant heads turned and found sungwoo.
 when they revealed their teeth and released black smoke, sungwoo was reminded of a hellish world.
“necromancer… you are smart.
 i admit you’re smart, but you are finished.
 thanks to you, i’m now fully sober.
”“…”the tsar survived sungwoo’s double attacks.
 how could he deal with the tsar?‘if i allow his attack, it will kill me instantly.
’but sungwoo racked his brain to find a way to block the tsar’s attack.
‘it wasn’t that the explosion had no damage on him.
 if i can aim for another chance…’at that moment the whole world has turned white.
 both the sky and the ground were swallowed up by the light.
 all the shade disappeared and the outlines of things blurred.
 everyone had to stop moving and cover their eyes.
‘light?’there was no sign of anything.
 all they could sense was that the light reached this place.
as everything around them turned white, a flash of light came from the sky.
 then, dozens of lightning bolts poured out like a waterfall.
not only sungwoo but also the tsar stepped back, wary of that unexpected phenomenon.
tramp- tramp-amid the beam of light appeared a familiar face.
 it was a man wearing black ‘hard leather armor’ and holding a wooden hawk-carved cane.
“i came here, feeling the energy of hell.
 what the heck is this? just a pilgrim?”he was kangsok han, the no.
 1 in the korean server rankings.
he glanced up and down the tsar with an irritated expression.
“four-star cards and a hell pilgrim.
 i came down because i smelled something disgusting.
 was it you?”the fairy and butterfly flew over kangsok’s shoulders and looked around.
“gosh, it’s so boring! i’ve been looking forward to it!”the butterfly flew toward sungwoo and his party, waving at them.
“hi! it’s been a long time!”“…”“…”but no one returned the fairy’s greetings because they were in a dangerous situation.
with a sulky expression, the fairy sat down on his shoulders again.
“damn! i hate you all!”looking at the situation, the tsar looked frustrated.
“what the heck is this?”kangsok approached the tsar and said, “hey, hell pilgrim, you are now using the hellish power with the support of the angel camp, right?”“…”“don’t pretend to be innocent when you have the three dogs behind you like that.
 i came down here after gathering all the information about you.
 by the way, that’s not even a regular deity, isn’t it?”“how do you know that?”kangsok smiled at him scornfully.
 he walked slowly and closer to the tsar.
 and he boldly put his hand on the tsar’s shoulder.
the tsar’s eyebrows wriggled.
 normally, he would have raged into anger, but he was just staring at kangsok silently.


kangsok opened his mouth in no time.
“i am the one who will become the lord of hell, the devil king.
”the tsar’s eyebrows wriggled again, and sungwoo also frowned.
‘devil king?’sungwoo couldn’t understand what it meant.
however, he could understand why he was so obsessed with the place called ‘hell’ and what kind of quest he was proceeding with.
‘by the way, demon king? does it mean he has the power to control the monsters of hell?’the background of the game became more and more complicated as the days went by.
 following the “devil’s gate” dominated by world eater, “hell” seemed to be more than just a dungeon.
“got it.
 you must be no.
 1 in the korean server rankings, right? you are also that player who devastated the southern island of japan, right? yeah, i remember you.
”now, no.
 1 in the russian server rankings and no.
 1 in the korean server rankings stood face to face.
“i knew you were awesome when i watched you on tv, but when i watched you here, i now know how strong you are.
”kangsok just chuckled at his words, and said, tapping the tsar on the shoulder once more, “hey, just run away now instead of trying to show foolish pride.
”even though he was completely sober, the tsar blushed again because of anger and humiliation.
“what did you say?”he was the no.
 1 warrior in russia.
 if he turned after he was humiliated like this, he would not survive the harsh tundra fields.
he smiled faintly and manipulated the three heads of the black dog behind him.
 no matter how strong kangsok was, he was confident of killing the strongest korean player on the spot.
“your people are originally so arrogant like this…”but the tsar couldn’t finish his words because he was thrown through the air and got jammed into a rusty truck when something flashed before his eyes.
“kheeeeeeeeeeeeeek!”watching him, kangsok smiled and said, “don’t try to trick me.
 i’m smarter than you!”“hey, you are so damn slow! idiot!”

 