\section{chapter 244}

                            the door at the end of the corridor opened wide.
 three giant spears made of magic floated in the air.
 it was clear that given the white glow around its body, the undead had a deadly divine power.





“i’m sorry, but i’ve been watching you all along.
”sungwoo knew early on that such an ugly creature had been aiming at him.
ooh ooh ooh-two ghosts popped out of the wall.
 just before entering the hallway, sungwoo summoned specter to watch over the wall.
“shoot him!” the little guy shouted urgently.
sungwoo pulled the “mountain goblin’s wooden shield” from his back.
 at the same time, three spears flew toward sungwoo at a tremendous speed like missiles.
goong- goo-goong!the powerful magic was blocked by sungwoo’s shield and disappeared.
 sungwoo succeeded in using the item’s ability to disable the three magic attacks.
“damn it!”the little guy was running through the corridor.
 while he was running, he started whining like a child.
“this is magic was prepared by ten priests for 20 minutes! it should have killed you right away! how could you stop it?” he shouted.
sungwoo and minsok went down the corridor and chased him into the huge cavity.
“they are up there!”enemies appeared before they could take a closer look.
 ten priests were urgently preparing a new magic attack.
 however, there was something strange about them.
with their lower bodies cut off, only the upper bodies were hung from the ceiling on various chains and hoses.
 their faces were covered with white hoods.
“it seems that they are not moving on their own.
 they are only puppets,” minsok said.
he was right.
 it was certain that they were priests who dealt with divine magic, but they were only bodies.
 they seemed to be manipulated like machines.
with the sound of the chains winding, their bodies moved while hanging on the strings.
rattle!soon, they were placed in a formation to surround sungwoo and minsok, then they raised their hands unnaturally.
 upon closer examination, wires and hoses were connected to their brains and spines.

tung! tung! tung! tung!sungwoo fired at them with his repeating crossbow.
 in addition to the ignition function, sungwoo’s fire damage was amplified by the “salamander’s aura” effect he obtained by putting on the “hellfire armor”.
sungwoo’s arrows hit the priests and set them on fire in an instant.
 they didn’t even scream.
-you have earned 16,000 gold by killing a player.
-you have earned 14,000 gold by killing a player.
-you have earned 14,000 gold by killing a player.
according to the system message, they were normal players.
sungwoo didn’t know why, but the players were being controlled by somebody.
“how about it? do you like such players?”a voice came out from one corner.
 when sungwoo turned his head toward it, he noticed a d-shaped instrument panel and the young man sitting in front of it stood.
 he had pomade-slicked hair and was none other than doctor who sungwoo knew well.
“it has been my long dream to make the necromancer like that.
”then, another man appeared behind him.
“honestly, this kind of facility doesn’t seem bad, so why don’t you give it a thought? we’re going to cut off your lower body, so you don’t have to worry about feces and urine.
”he was also doctor, but he looked a little younger.
 almost like a high school student.
behind him was the little guy who escorted sungwoo at first.
the guy opened his mouth with a grumpy expression.
“that man is stubborn.
 no matter how hard i tried, i could not deceive him.
 he’s annoying.
”watching them one by one, sungwoo could not help but be startled.
 did the ‘creator’ make clones according to their age?“this is ridiculous.
 who else?”one more appeared immediately when sungwoo asked.

“there are more.
 glad we can meet your expectations.
”this time it was a middle-aged man, pushing a wheelchair.
sungwoo made eye contact with the man in the wheelchair, a gray-haired old man.
the old man scanned sungwoo then smiled in satisfaction.
“you have come! the specimen i have been looking forward to came here voluntarily.
”that old man was dr.
 hee-seung yu’s main body, doctor-000.
“welcome! watching you from a distance, i was looking forward to seeing you someday.
 you are the only one who will complete my research…”“i’m sorry, but i’ve come here to smash your study.
”but the old man just giggled at him.
“don’t worry about it.
 like those friends up there, i will trim your limbs and let you be held in their arms without complaining,” said the old man, smiling at sungwoo.
sungwoo snapped, frowning at him, “the young clones pretended to be gentlemen, but you’ve become an ugly old man speaking like a pervert!”“the older you get, the more you reveal your true colors!”after he said that, something began to protrude from the old man’s back.
gulp! gulp!it was a bundle of scarlet tentacles.
 sungwoo wondered if it was his weapon, but something he could never understand happened.
puck! puck! puck! puck!the old man’s tentacles shot forward and stuck in the necks of his clones.
then, they began to absorb their brain and spinal fluid, as if sipping the contents with a straw.
“huhhhhh…”as if they knew it already, the clones made no resistance.
 their eyes rolled, and their limbs trembled.
“oh, you guys have a tight kinship.
 so, is this what you mean by becoming one body?”dr.
 yu, who finished eating them all amid sungwoo’s scornful jeering, stood up from the wheelchair.
 he relaxed his neck muscles then slowly walked forward.
“it’s not just us.
 someday, everyone will become one body like this.
 that’s what i call…”having said that, he reached out his hand toward the ceiling.
“that’s what i call evolution.
”then, the sound of a switch going up was heard somewhere, and the searchlights installed on the ceiling turned on.
 the cavity, immersed in darkness, revealed its bare space.
it was as spacious as a dome stadium.
 all kinds of mechanical devices hung from the walls and ceiling, but it wasn’t just the mechanical devices that were hanging.
“oh, my god…” minsok lamented a little.
hundreds of players lined the ceiling with their lower bodies cut off.
their brains and spines were connected with wires and hoses, making it possible for dr.
 yu to remotely control them like the priests.
woooong-soon, players hanging from the ceiling with a mechanical sound were transported in a row along the rails.
 sungwoo and minsok felt like they were at a large-scale meat processing site.
dozens of cranes began to separate from the wall and descend.
the cranes also had rails, and bodies being carried from the ceiling took the rails and began to be deployed with different cranes.
from the end of the cranes, two players were stacked one after another until a total of 20 players were fixed on one crane.
as the current flowed, the players hanging on the crane took the same action at the same time, such as raising their hands or turning their heads.
in such a formation, 20 players could use the same magic at the same time with a single command.
pushee―black smoke emanated from the rear wall, a hole that looked like a vent.
pushee―the power source driving this huge machine seemed to blow gas through the vent.
 there, a noisy engine sound rang, making the cavity loud.


woong- woong- wooong-looking at the bizarre device moving smoothly, dr.
 yu expressed satisfaction.
“isn’t it cool? it’s not yet one body, but it’s controlled under one mind and has one movement.
”a bundle of thick cables came down from the center of the ceiling and wriggled like a snake and approached dr.
 yu.
subsequently, a bundle of tentacles stretched out from behind dr.
 yu’s back and began to get tangled with the bundle of cables.
the spark splattered wildly, but dr.
 yu looked fine.
“good!”dr.
 yu’s body ascended along the bundle of cables.
 he stopped in the air, in the middle of all those devices.
then, he slowly raised his hands as if he became a god looking down on the earth.
“okay, this is the early stage of evolution.
”sungwoo did not hide his disgust.
“evolution?”a huge black sickle appeared in sungwoo’s right hand.
 at the same time, black hair spread all over his body as he began to turn into a single black wolf.
“you keep talking about evolution…”and finally, a heavy black armor appeared on his body.
 blue heat spread from his body.
it was an indescribable kind of power, intertwined with the power of death and intense flames.
“you guys deserve extinction!”finally, it was time for sungwoo to end their long bad relationship.
“let me annihilate you.
”the final battle began.


 