\section{chapter 257}

                            having heard that, the king swallowed the remaining potato piece, with a smile in his eyes.





“um, don’t eat this potato.
 it’s not boiled enough.
 who boiled it?”then, he rolled up his sleeves.
 he sprang to his feet and looked down at sungwoo.
“sure, i also want to be recognized as a landlord by the strong man in this neighborhood.
 someone knows more about the north korean lich.
 i’ll take you to that person.
”“alright.
”sungwoo didn’t know that he would join hands with the monster like this, but he came to trust the king for some reason.
‘this guy is different.
 it looks like he is not a monster.
’sungwoo’s party stood up.
 it was time for them to get information about the north korean lich and respond to the new mainstream.
“come on, let’s go.
”“man, you won’t give me a break? okay, let’s go!”games always offered a sudden challenge, and sungwoo’s party knew how to face it.
no matter how fiercely the system would drive them, they would not leave the korean server ruined like the north korean server.
the king of the great mountain, opened his mouth with a serious expression, touching his chin.
“but i want to ask you one question.
”“what?”he pointed at the potato basket.

“do you know how many potatoes we should boil?”“…”sungwoo’s group went down the foot of the mountain, escorted by the king.
 they were now on their way to someone who had information about the lich of the north korean server.
“well, he is around here…” said the king, who was wearing a bamboo hat, while walking ahead with a cane.
sungwoo wasn’t sure, but it seemed that the king was wandering a bit.
“wait a minute.
 you know how to get there, right?” hanho asked as if he was frustrated.
“we’re almost there.
 don’t look so worried.
 am i not the king of this mountain?”the king then began to walk ahead.
“the guy who knows about the north korean lich in detail is a player from the north korean server?”when sungwoo asked, the king raised his hat and nodded.
“right.
 was it 7 days ago? i rescued him when the ogre brothers were about to eat him when he got lost in the mountain here.
 after that, the ogre brothers didn’t even say hello to me.
 they are so big and heavy, but very narrow-minded.
”the king of the great mountain was always talkative, so he often got off the main topic.
“so what did the north korean player do?”“oh, it looks like he briefly belonged to the organization that served lich.
 let’s hear the details directly from that guy.
 we have arrived at our destination finally.
 right there.
”when they looked at the place he was pointing at, there was a hut that was no different from the king’s hut.
“an old man and his grandchildren live there, so i had him stay there for now.
 master! come out!”
he screamed, approaching the hut.
 at that moment, somebody flung open the door, aiming at them with a crossbow.
a white-haired old man, who raised his dark eyebrows and pointed a crossbow at the king’s neck, was about to fire an arrow at him.
 then, the king took off his hat and waved his hand urgently.
“hey, it’s me? are you deaf now, old man? please pull yourself together as you live with your grandchildren!”“what the heck, you goblin! what has brought you here?”the old man lowered the crossbow and put on a pair of cracked rimless glasses.
“what? you called me a goblin? you are not recognizing that you are my people? if you refuse, let me lift the prohibition order on the ogres and the trolls who might approach you.
”“you mean goblin…”the king naturally sat down on the floor.
 then, the sound of the children in the room was heard.
“wow, goblin uncle is here!”“uncle, where are the tiger uncles?”a boy, who seemed five years old, came out of the room and clung to the king’s shoulder.
watching them interacting like that, sungwoo felt pretty strange.
‘a monster hanging out with a small child? i can’t understand…’the king grinned while stroking the child’s hair.
 the king looked like a friendly uncle who liked his cousins and nephews.
“oh, my…goblin? you guys are speaking like your grandfather.
 your tiger uncles are busy plowing a field.
 we don’t have a cow.
”soon, the children’s gaze rested on sungwoo’s party.
“uh? sis jisu is here too!”“sis jisu!”“how are you guys?”jisu also seemed to have built a close relationship with them while wandering through the mountains.
meanwhile, the old man prepared a dining table for his guests while grumbling about their sudden visit.
“why are you suddenly visiting my house whenever you can and bothering me? i’m so confused right now, so drink a glass of juice and beat it quickly.
”it was a bowl of puffed rice and orange juice.
 the old man handed them stainless steel cups one by one with his rough hands.
“wow, thanks for serving us your favorite fruit juice? it looks like you are giving us such a good treat today because of our new guests.
 i’m so moved!”“don’t talk nonsense, you goblin!”“haha! but where is mr.
 lee? i don’t see him…”the king scanned the old man, frowning at him, and asked, “you complained he was a red! did you throw him away in the mountain?”at that moment, somebody was heard approaching them from the backyard.
a bearded man walked over to them.
“oh, you are here.
 sorry.
 i didn’t know you came because i was working in the backyard.
”-his excessive local dialect has been ‘auto filtered.


“oh, he’s coming.
 that guy is our informant, sungho lee, who has come down from the north.
 he was once a vulgar man who served lich, but he has come to his senses.
 so, don’t make him your subordinate spirit.
”“you are too talkative, you goblin!” said the old man, who put on his rubber shoes, then went out to the yard.
then, the king pointed his finger at the old man’s back.
“now that we have to discuss the important matter, please excuse us, old man!”then, sungwoo sat face to face with sungho and heard from him about the situation on the north korean server.
the beginning of the north korean server was not that different from that of the south korean server.
 faced with the sudden disaster, the players awakened and made desperate efforts to survive.
however, since north korean society itself was not familiar with games and electronic systems, they expressed an unusually strong resistance to the phenomenon unfolding before their eyes.
“i think there were more human beasts than the players.
”that’s the state of the north korean server that sungho recalled.
 more people did not draw cards than those who did.
“a lot of people hesitated to choose because their seniors told them never to touch the cards that suddenly popped up.
 even the workers’ party sent a directive that they should not even touch the cards, arguing that it was a cunning trick set by the us imperialists…”according to him, those who were determined to survive drew the cards and succeeded in creating a self-governing organization.
they acted in groups, responded to the monsters, and cleared the quests, but faced a big obstacle.
“after all, the problem was the military that drew cards and restored their power.
 they ordered the players of our autonomous forces to obey and move under the party’s authority.
”however, the people who built their strength could not follow their orders obediently.
although they tried to maintain their autonomy, by all means, the problem was that many within the self-governing organization were still ideologically shaken.
“it’s funny that those who were ideologically strong tried to stigmatize others as traitors, and as a result, the self-governing group’s support was greatly reduced…”

 