\section{chapter 248}

                            dr.
 yu was still looking down on the floor.
 he looked very alert as if he discovered something underneath it.





“they will come here soon.
”“that’s why i asked you what it was.
”thud!just before sungwoo finished asking, the ground around him vibrated.
 everyone, including sungwoo, stumbled.
goo goo goo-soon, the entire cavern began to shake wildly.
 they could feel the vibration was slowly coming from a very deep place.
“sungwoo, it looks like something is coming up quite soon.
 it’s really big and very heavy.
”“i can feel it, too.
”a crack spread in the middle of the place that dr.
 yu was watching closely then it went down like a sinkhole.
 and black darkness soared from there.
ooh ooh ooh-something like a black wave scattered in all directions and spread out like a huge screen.
the middle of the wide curtain popped out as if somebody pushed his hand in from behind.
 something round appeared on top of the screen.
“is it an eye?”it was a huge eyeball.
 it slowly began to come out after pushing the darkness out of the veil.
 it was only an eyeball without any other part.
it tilted slowly from left to right and seemed to look around the entire cavern.
“what the hell…”without daring to move, sungwoo and his allies looked at it with stiff postures and got ready for another battle.
at that moment, a message appeared.
-you are overwhelmed by the ‘external existence’.
* all stats decrease.
 (-60%)this message was the same as the one that sungwoo saw when he opened the ‘demon’s door’ and witnessed the monsters creeping out of it.
‘is it related to the demon’s door?’
but at that time, sungwoo’s “deity status’ crushed the monster because his status was higher.
in other words, that eyeball was higher than sungwoo’s deity status.
“world eater!” dr.
 yu sighed and kneeled.
blood gushed from his severed arm, but he didn’t even care about it.
he was overwhelmed by the huge eyeball in front of him.
“please…”world eater looked at dr.
 yu.
 its huge pupil slowly expanded.
“oh, no!”at the same time, dr.
 yu’s body began to be crushed.
crunch- crunch-his skull was dented and his limbs were bizarrely bent.
his body began to compress in the air as if the force of gravity was working from all directions acting.
“argh! ahhhhhhhh!”it was punishment for dr.
 yu’s breach of contract.
“please! don’t! ugh!”his flesh and bones were squashed, and blood spewed out.
 but soon even that blood began to condense into a single point.
 it kept folding inward to the physically impossible point.
after all, dr.
 yu’s body turned into a small piece of flesh and fell to the floor.
that was it.
“…”looking at that brutal scene, sungwoo and his party realized they could not dare to deal with that huge eyeball.
it lifted its pupil and looked at them again.
 its iris moved to diminish its pupil.
 now, it fixated on sungwoo.
-the ‘unknown being’ is staring at you.
the eyeball made no sound, just looking at him quietly.

sungwoo couldn’t know the feeling of the ‘unknown being’ because it had no other facial parts or even the eyelids.
-you have incurred the anger of the ‘unknown being’.
it was clear that the huge eyeball hated sungwoo terribly.
the hatred of the unknown being was familiar to sungwoo because all the absolute beings in this game hated sungwoo without exception.
‘but this guy is dangerous.
 if it could use that power to kill me, just like dr.
 yu, how can i stop it?’just staring at dr.
 yu without touching a hand killed him instantly.
 sungwoo didn’t know how it was possible, so he couldn’t figure out how to stop it.
‘i just hope this guy can use it only for those who have a contract with him.
”sungwoo prepared to mobilize all the undead right away.
 he didn’t think he could beat such an overwhelming creature.
 he had to find a way to escape by mobilizing them to block its attack.
at that moment, the creature moved its pupil from sungwoo to some other place.
 it seemed as if its murderous look was being softened.
-the ‘unknown being’ has pledged that it will take your life someday.
fortunately, the unknown being seemed to think it was not the right time to attack sungwoo.
 the huge eyeball began to disappear into the black veil.
soon, even the black curtain scattered away like smoke.
 sungwoo and his party could not move for a while, standing in their place.
“what was that monster a moment ago?” asked jisu, putting the sword back in the sheath, with a relaxed expression.
“i think i’ll face that creature next time.
 i’ll ask then.
”then, he looked around.
 it seemed there was nothing threatening around.
a message about the end of this battle appeared at that moment.
-you have successfully cleared the exclusive quest ‘provide death to those who can’t die’.
* reward is given.
 (exclusive skill)* your fate has changed subtly.
finally, the quest was completed.
 and an exclusive skill was given to sungwoo.
-you have acquired the skill .
-skill grade has been improved.
 (professional → craftsman)“again?”this was the fourth time he acquired such a skill.
as a result, death response reached the level of “craftsmanship.
”[skill information]-name: death response-class: craftsman-category: active-cost: 130 mana*you can summon and control 50 masterless zombies amid the abyss.
 this object is not limited by the number of your subordinate spirits but will disappear as dust after 40 minutes.
 (cooldown: 25 minutes)as the grade changed from “specialist” to “craftsman”, the number of zombies that sungwoo could summon increased from 25 to a whopping 50.
he wasn’t sure of its full capacity because he hadn’t seen a skill above the ‘specialist’ level yet, but given the double increase, it reached the maximum level.
‘if i apply shadow corps here, i can summon 100 zombies.
’as the level of his skill increased, the size of his army was increasing exponentially.
with this trend going on, sungwoo would be able to control several thousand one day.
if so, could he put an end to the game itself, not to mention the “world eater” he encountered a little while ago?sungwoo could not answer now, but he could not stop rooting out the source of this whole game.
“by the way, the evolution society is finished, right?” asked jisu, letting out a sigh.
like she said, sungwoo ended one of the really bad entities that had been chasing them for a long time.
 but this time he encountered another bad guy, namely the world eater.
there were still so many bad guys including the world eater that he had to annihilate.
and he needed to do something now.
“it’s finished.
 but work starts now.
”“yeah, we’re done with the evolution society.
 but it’s just the start.
”“pardon? what are you talking about?”

“we have to collect all the stuff in this building.
”originally, it was natural that the winner would take the booty, but sungwoo had too much this time.
***the legacy left behind by the evolution society was enormous.
 of course, looking into their facilities,sungwoo and his party could find traces of their heinous activities.
 but except for them, all the rest could be called a great treasure.
for example, the necessities stored in a single warehouse among the huge facilities were numerous enough to help the players in the suwon village sustain for several months.
since the evolution society itself was a group that mainly focused on research and development, it seemed that it would serve as something like a tremendous source of nutrients for the village players who were rapidly developing as there were all kinds of materials and items in the area of living and production.
“i contacted them.
 hanho and inho will arrive here soon.
”sungwoo and jisu alone could not tour the entire facility, nor could they deal with the prisoners held by the evolution society.
 as a result, sungwoo needed a huge staff to take care of them.
after a while, four helicopters arrived.
 they flew from suwon.
hanho jumped first and shouted, “wow! finally, they surrendered! man, i should have shown my great skills right in front of them!”unlike hanho, who was a little excited, inho was full of anxiety.
after looking through the facility, inho sighed, “i saw the facility from the helicopter.
 it’s very large.
 i’ve brought 55 men here, but it looks like they are not enough.
 well, it will take at least a few weeks because your undead can’t continue to help us.
 of course, this is my opinion.
”this was the moment that the small number of elites was a drawback, not a plus.
 in other words, there was an absolute shortage of manpower now.
 as a result, it would be a big loss in terms of saving time.
“i’ve got an idea.
”sungwoo went to the white wolf that he had taken out of the prison.
 he was gathered with the human beasts who followed him.
as he approached, they showed fierce vigilance, but they gently stepped to the side without saying anything because they knew their survival depended on the necromancer.
“necromancer, what’s going on?”“well, i’m a guy with severe mood swings.
 i’ve one more condition for saving your lives.
”i have ups and downs, so instead of saving you, one more condition has been attached.
”“…”the white wolf hardened his face.
sungwoo said, “you guys know that when you move out of your original place, you have to clean it up, right?”so, sungwoo mobilized the human beasts for that huge job for free.


 