\section{chapter 397}

chapter 397: full control over death (6)this chapter is updated by wuxiahere.
com




immediately after defeating the chinese army’s shield unit at gwanggyo lake park, sungwoo led his troops across downtown suwon to head for the castle wall.
it would have taken them quite a while to get there by land, but they used a large number of flying undead and thousands of ghosts to transport all the undead army.
whooooo-the scenes of a herd of bone dragon and bone wyvern and thousands of ghosts flying in the sky with thousands of skeletons were so shocking.
“man, this is really terrible!”as li wei said, their overwhelming formation in the sky was so shocking.
 even sungwoo, who was aboard bone wyvern at the forefront, could not help but admire the majestic formation of the undead filling the sky.
if somebody looked up at them from the ground, they might feel it was so bizarre, majestic, surreal, and fantastic that they would think that they suddenly fell into the middle of hell.
‘yeah, i’ll never be able to form such a large army as this.
 they are my largest army ever!’in fact, he could control only up to 500 demons with the ‘power of the underworld.
’[skill information]– name: law of the underworld– grade: craftsman– category: active– cost: 100 mana*you can resurrect the soul of the dead as the subordinate spirit (ghost) by exercising the authority of the judge of the underworld.
 (up to 500)
in addition, you can ‘restrain’ and ‘control’ all the ghosts in the surrounding area.
 you can control them regardless of the ‘maximum number of subordinate spirits (ghosts)’, but you can’t resurrect them once they perish.
‘well, they’re lucky.
 wait a minute, are they unfortunate?’according to the skill description, sungwoo could make up to 500 ghosts.
however, the chinese army used the ‘ancient curse’ to create ‘wild hunt’, which generated a huge number of ghosts.
 as a result, all of them fell into sungwoo’s hands.
‘let me finish this war with them.
’determined like that, he reached the castle wall with his undead troops.
at that moment, however, the emperor appeared and used the ‘sky barracks’.
as soon as hundreds of doors opened in the air, a huge number of troops came out in droves and started to fill the sky, which was so overwhelming.
they are a terracotta army.
 how many are there?’terracotta soldiers were the same clay dolls that bombed the world tree camp after they were disguised as a team of crusaders led by junghoon.
 it was not clear to figure out how many were there, but they were at least 100,000.
 the problem was that they were still pouring out of the gates even when sungwoo’s party was monitoring them.
li wei, who was standing behind sungwoo, clicked her tongue.
“yeah, the emperor has been making a lot of them until now.
 even now he is still making them…”even though they could not be resurrected like sungwoo’s undead army, the emperor could continue to produce them.
‘then it’s a race against time.
’the question was whether he could subdue the emperor while he could continue to resurrect his undead army.
– grim reaper retention time (00:33:56)
but sungwoo didn’t have much time.
 he looked at li wei.
“how about your spirits? haven’t they recovered yet?”when he raided the shield unit of the chinese army at gwanggyo lake park, he found a prison for the spirits called ‘spirit control box’.
 sungwoo wiped them even before they could touch it, and saved li wei’s high-level spirits held inside the box.
 there were not many spirits there, but he accomplished li wei’s wishes anyway.
“well, it’s impossible to recover them perfectly because the elements of the spirits were contaminated.
 but these guys want to fight, too.
 they are now crying out loudly because they want to drown that emperor!”“okay, then let’s go.
 i don’t have much time.
”after he said that, he came out of his hiding place and revealed himself.
at the same time, the drone of the official channel flew over his head and broadcasted his appearance on the air.
finally, the two absolute powers, namely, the emperor of the chinese server and the necromancer of the korean server, stood face to face.
“man, i really wanted to see that guy’s thick face, but he’s wrapped up by something very thick!”sungwoo grumbled, looking at the emperor, who was wrapped all over his body by a blue shield.
“alright.
 let me take off all your shield, armor, and skin in 30 minutes except for your bones.
”sungwoo immediately advanced the entire army.
rattle- rattle-the undead moved forward loudly through the roads or by breaking the surrounding buildings.
the ghosts, who mixed with the undead, made their way over or through the buildings.
then, the bone dragon flew like a storm, casting a huge shadow over everything on the ground.
the emperor did not wait long either.
after confirming the appearance of the necromancer, he turned.
 at that moment golden threads spurted out of the blue shield around his body.
“if you get caught in the threads, you can be controlled by him.
 so watch out!” li wei shouted at sungwoo.
the emperor’s occupation was a kind of ‘puppeteer’.
 so, he must have the skill to manipulate something through threads.
however, something unexpected took place.
 dozens of threads swung like a whip and began to blow up all the buildings in the surrounding area.
dozens of buildings collapsed in an instant, forming a vast vacant lot.
 that alone was so powerful that it looked like large-scale destruction magic.
 but that was just one step he took for the next skill.
kugugugugugu-the wreckages of the smashed buildings began to form something as they got tangled along the golden threads.
 they looked like golems.
 building debris such as concrete and reinforcing bars was entangled into one, creating a ‘concrete giant’ that reached dozens of meters in the sky.
“crazy, he has already learned a new skill…”it seemed that the emperor could make dolls by using everything around him and manipulating them.
‘man, this guy is the worst enemy!’while sungwoo could only use corpses as material, it seemed that the emperor could use everything around him.
 in many ways, sungwoo was inferior to him in terms of a war of attrition.
thump- thump- thump-the concrete giant approached him, swinging his arms wildly.
 a few large pieces of debris that were hanging from his arm flew toward sungwoo.
 in effect, the concrete giant was a walking catapult itself.
 his punch alone would have smashed a dozen or so undead.
then, li wei reached out.
 water spirits were summoned behind her back.
 at the same time, they turned into a single vortex of water.
 then they were shot at the flying concrete fragments and started to push out the heavy fragments.


then some of sungwoo’s ghosts moved forward, pushed the wreckage, and threw them in the opposite direction.
the debris got stuck in the concrete giant’s head.
 its body shook violently, scattering debris in all directions, but it regained its balance.
 but at that moment, a larger shadow fell over his gigantic body.
 and his massive body was dragged into the air all of a sudden.
it was bone dragon.
the bone dragon soared into the sky flapping his wings while clutching the concrete giant the size of a building with its hind legs.
then the bone dragon threw that huge body into the middle of the enemies.
 it was like the collision of a meteorite.
quaguaguaguagua-countless numbers of terracotta were smashed by bone dragon’s attack.
– you have obtained 3,000 gold by killing the player’s ‘intermediate terracotta’.
– you have obtained 3,000 gold by killing the player’s ‘intermediate terracotta’.
– you have obtained 10,000 gold by killing the player’s ‘advanced terracotta’.
a whopping 52 messages rang, but the reward was not that impressive.
“alright! it’s my turn now.
 wipe them out!”as soon as li wei shouted, a large number of water spirits were summoned around her.
they got tangled up one by one and created a huge wave.
 and they jumped over sungwoo’s undead army and sprinted towards the enemy.
kwagwagagwagwa!

 