\section{chapter 294}






 parker grabbed jonathan by the shoulder, who was tied to his chair and looked into sungwoo’s eyes.
“although our diplomatic meeting with you was postponed for inevitable reasons, we really hope you can understand we want a friendly relationship with you…kheeeeeeek!”he could not use his cunning trick any longer because sungwoo threw his right hand, grabbed his neck, and lifted him off the ground.
sungwoo shouted, “why are you talking so much?”“kheeeeek! kuuuuuk!”“it looks like you are mistaken a lot, but do you think i’m here for a diplomatic dialogue with you?”“ka…heeek…”“i think you already know about me, don’t you?”sungwoo threw parker to the floor violently.
“argh…”his shoulder blades were fractured after being thrown down to the concrete.
 as if his spine was cracked, he felt a sharp pang in his lower body.
sungwoo didn’t stop there.
 he approached parker and crushed his knee with his foot.
crunchy!his knees bent like sorghum straw.
 parker couldn’t even scream because of immense pain.
he just scratched the floor so hard, groaning in extreme pain.

“as you know well, i’m just an exclusive terrorist, so i just want to cruelly slaughter those foreigners who have come to our land.
 that’s my hobby.
”having said so, sungwoo laughed heartily.
 of course, that’s what parker told jonathan just a little while ago.
as a matter of fact, sungwoo was listening to their conversation through the ghosts attached to the wall, namely the two spectors.
“isn’t this the scenario you wanted, right?” sungwoo asked.
but parker shook his head in a nerve-burning pain, shedding tears.
“don’t be ridiculous! you won’t get anything by torturing me like this.
 i’m a soldier of the united states.
”at that moment, the iron gate collapsed, which was standing intact despite the collapse of the building.
 and, a woman with a sword appeared behind it.
“i’ve killed all of them.
”she was jisu.
 she stood next to sungwoo, wiping off the blood on her sword.
 drops of blood she wiped off fell over parker’s face.
“whatever you do, it’s useless.
 i’m not going to tell you anything.
 don’t waste your time.
 you had better kill me quickly.
”even though his spine was fractured and his knees broken, parker was not ready to give up, with strong resolve on his face.
 he was a strong soldier full of patriotism.
 so, he was confident that he would not succumb to any torture.
however, sungwoo smiled at him scornfully.
“i’m sorry, but i don’t do anything like torture.
”“what did you say?”“do you think i’ve found out about this place by torturing somebody?”at that moment, parker’s face was covered with something.
 it was a mask.
 parker smelled the blood around his mouth and heard the voice of the necromancer ringing from somewhere.

“and i won’t even kill you.
 from now on, it is you guys who are going to be used in this political fight, not us.
”parker never gave in, but he couldn’t shake off the anxiety that he was captured by the wrong person.
“i won’t kill you, but you’ll be remembered as the worst soldier in your proud homeland.
”***the place where parker and his party were hiding was the basement of sanghyeon station in yongin city.
 sungwoo’s party came out of the rubble and was cleaning up at the moment.
“this is an object we have found inside.
”the search team members came out with a large case.
 sungwoo stepped back and made a skeleton open because he did not rule out the possibility that it might be a trap, like the “player killer box” found on a crashed airship in the past.
“nothing unusual is inside.
”fortunately, no accident happened.
 when sungwoo approached and checked it, there was an orange sphere inside the case.
 there were a total of 4 inside it.
“this must be the core part that was in the engine compartment, right?” asked kyongsu, who was looking at it, standing next to sungwoo.
“i think so.
”the engineers who searched the airship said they found traces of missing important parts in the engine compartment.
 and when they checked the plane, the parts that supplied the ship with power were missing.
 sungwoo felt these parts were the power source.
sungwoo put his hand on the part.
[item information]-name: airship engine core type-3 (flying seat)-class: unknown-category: player manufacturing item-effect: injecting mana reduces the weight of a certain volume by up to 98%, and the airship can soar into the air when injecting mana once more.
-description: this model is equipped with an ‘amplifier’ that amplifies the effect of weight reduction of the general flying seat by 300%.
*this item is a valuable property of the w·p·u, regarded as top-secret and needs top security management.
 those except for authorized people are strictly prohibited from controlling it.
 (manufacturer’s direct description)according to the description, when they attach this item to the engine, the weight of such a huge sailing ship will be reduced by more than 98%, making it easier to soar into the air.
of course, the airship would need other propulsion or steering gear, but just reducing its weight would make the whole process much easier.
“keep this well.
”the werewolf skeleton put the case inside the backpack.
 if sungwoo returned the skeleton to the “void haven” in this state, he would not have to worry about losing the parts.
it was obvious that the w·p·u cherished them a lot, but sungwoo had no intention of returning them once he obtained them.
meanwhile, hanho was healing the wounds of that black guy named jonathan cage by healing him.
“ah, you were a priest, right?” sungwoo asked.
“you bet.
 actually, i forgot it, but just remembered it.
”sitting on the rubble, sungwoo looked at jonathan.
 when he overheard the conversation through the spectors in the past, sungwoo knew he was friendly to the world tree camp.
“why did you come as far as here from america? don’t talk bullshit like forging a friendly relationship with us.
 just tell me the real reason.
”“…”

when sungwoo asked, jonathan was tight-lipped for some time.
but when sungwoo kept staring at him, he had no choice but to open his mouth.
“the us server is somewhat stable.
”“that’s why you guys have taken the liberty of coming to the korean server.
”jonathan raised his head and said, “but they are not in south america.
”“south america? which one is it? brazil?”“specifically, the amazon area.
”tropical rainforest, the amazon, was often called the lungs of the earth.
 what happened to it?“the amazon is so vast and rugged that the players on the brazilian server wouldn’t have been able to use it freely.
”“oh, i see…”sungwoo understood at once what he was trying to say.
 just as the king of monsters appeared in mt.
 taebaek, and the king of the monsters on the north korean server, monsters in the neglected the amazon would have gone through evolution until now.
however, those who evolved in the amazon were likely to be much more powerful than those in mt.
 taebaek or on the north korean server.
the amazon was one of the deepest and largest unknown lands in the world, so it was a space that was out of the reach of the players.
“monsters born there are threatening the north american continent.
 in the end, we believe that it will be difficult for us to stop them with our strength, so we hope we can form a global alliance to unite to confront the amazon monsters.
”“i don’t think all the guys in your group want it, right?”jonathan nodded bitterly and said, “after our group has become stable to some extent, there has broken out a power struggle and secret strife among us.
”

 