\section{chapter 188}

                             




did one minute pass? sungwoo’s undead army already slaughtered dozens of monsters.
if they kept up the attack like this, they could finish the 1st wave within 10 minutes.
’24 hours? no, as things stand now, just 30 minutes is enough.
’-grim reaper retention time (00:26:33)-werewolf retention time (00:27:01)if sungwoo didn’t succeed within that time frame, the situation might turn very unfavorable because the moment sungwoo’s anubis status was deactivated, his strength would be reduced by half.
 if that happened, sungwoo’s undead army couldn’t protect the entrance, and eventually, they would be surrounded and annihilated.
‘no matter what, i have to destroy them right now.
’-1st wave underway (17%)so, sungwoo used all his skills.
-‘evil spirit bomb’ has been embedded into your weapon.
he concentrated all his firepower ranging from corpse explosions to evil spirit bombs on the narrow portal.
“everyone, support the necromancer!”furthermore, even the taiwanese players jisu brought with her joined the attack.
 standing behind the undead army, they began to mount a ranged attack on the portal.
and all the scenes of them attacking the portal were broadcast live.
“wow! that’s the best of the necromancer!”“he never loses.
”the players of kanghwa island, who gathered together, were cheering for him.
“i told you so! that’s why we have to rely on him, no matter what.
”
heyon was excited.
 even when their doubts about the necromancer prevailed amid his controversial role with the third camp, only she made the case for their unconditional support for the necromancer.
 her decision was excellent.
not only them but also all the players on the korean server were duly expecting the necromancer to play a big role.
 at the moment, more than 100,000 viewers were watching what was happening in taiwan.
junghoon and the crusader team members were also watching the broadcast.
“how could he get stronger like that?”they just arrived at cheongnyangni station to fight the demon camp.
however, they had to fight against not only the demon camp but also sungwoo’s camp.
 aside from what was going on now, the necromancer, who could become their ultimate boss in the future, was showing his full power, so it was foolish for them to miss the scenes of his fighting.
“commander, i’m sorry to say this, but i don’t think we should confront sungwoo.
”“…”they thought they knew him well.
 they also knew his growth was amazing.
 but he always showed more than what they expected.
in short, the necromancer was unpredictable.
“what the heck is that devil’s gate? you saw him hunting the monsters so easily, right? if that’s the case, aren’t the monsters as weak as kobold?”yoon kang, who ruined the broadcast because of the necromancer, complained alone.
 he didn’t want to admit the necromancer’s extraordinary capabilities.
but he couldn’t open his mouth after watching what the necromancer did next.
a devil monster stepped forward with his companion’s body as a shield.
 then, he easily jumped over the siege of the undead army.
 he jumped a whopping 15 meters away at once.
in the process, he caused a great disaster.
 the moment he passed by, four taiwanese players fell on the ground.
kaak! kaak!wielding his long arm like a whip, he broke everything standing in the way including the concrete floor, marble stairs, iron street lights.
 so much so that those watching him thought he had a mechanical cutter on both arms.
“tankers! move to block the monster!”
although the tankers came running and lifted the shields, not only the shields but also their arms were cut instantly.
“gosh! that devil monster is too strong!”it would never be easy for anybody, even at level 35, to receive 500,000 gold to hunt that devil monster.
in that respect, sungwoo was extraordinary and very usual because he could decrease the devil monster’s stats by 30% with his overwhelming stats in his demigod form.
“everybody, move back!”jisu walked out of the terrified tankers.
 except for the necromancer, she was the only player who could face the devil monster.
at that moment, the monster swung his arm toward her.
when she avoided it, the ground on which she was standing disintegrated like a glass.
 but one of his nails touched her shoulder.
 a handful of her hair was cut immediately.
‘he’s super fast.
’jisu stepped back, embarrassed.
 the moment she let down her guard, she would be killed.
 however, if she could attack him at the right moment, she could also kill him right away.
hooooook!‘now is the time!’the moment the evil monster stretched out his left hand, she swung her sword using her sword skill.
 her target was his right arm.
 the moment she blocked his attack, she cut his right shoulder in the blink of an eye.
kaaaaaaaaah!the monster staggered with his mouth wide open.
 seizing the moment, jisu darted toward him using the “footprint tracking” skill, then beheaded him right away.
-you have leveled up.
 (lv.
 17)jisu ignored the level-up message and looked at sungwoo while catching her breath.
it was quiet in the area where sungwoo and his undead army had been attacking the portal.
-1st wave of the devil’s gate has been completed.
 the next wave begins in 20 seconds.
the first battle was over.
 there was only one devil monster that the necromancer allowed out of the portal.
 all the other devil monsters were killed as soon as they came out of the entrance of the portal.
-the 2nd wave of the devil’s gate begins.
and the necromancer’s second slaughter began, which was much faster than they expected.
-this area is protected by ‘the shade of the godly tree’.
* you are not a player who has been allowed access to this area.
the mercenaries of the hunter company faced an unknown invisible barrier as they previously heard.
 they were in the process of installing the item given by the evolutionary society.
“captain, are you sure the necromancer can’t move for 24 hours? i am monitoring the broadcast right now, but…”he has been monitoring the necromancer’s broadcast until today, so he grew more and more nervous.
“this is a unilateral fight…”the necromancer’s performance was overwhelming, to say the least.
“no matter how quickly he cleared the quest, how could he come to taiwan so quickly?” the captain replied.
“then, how could he approach the square?”none of them were sure because they never predicted the necromancer would appear in taiwan.
“damn it! let’s get out of here as soon as possible after installing it…”even the captain could not hide his anxiety.
 they knew well that the necromancer could show his extraordinary skills and come back sooner than expected.
‘it’s impossible for him to cross the sea in a few hours.
 of course, he can’t!’if there was no necromancer, they thought they could easily blow away a whole village.


***wave 2 was much more intense.
 stronger devil monsters popped out like a swarm of ants from an ant den.
 however, the necromancer’s siege was perfect.
-the 2nd wave of the devil’s gate has been completed.
 the next wave begins in 20 seconds.
but three of them escaped the siege, so the taiwanese players in the rear got into trouble.
fortunately, jisu succeeded in killing them all, but she suffered some deep wounds in several places.
“realign the players! supply recovery potions! we don’t have much time left.
”“everyone, prepare the magic!”given the level of the monsters, it was fortunate that the damages jisu and the players suffered were not that heavy.
had it not been for the necromancer, they might have been fiercely fighting the monsters in downtown taipei by now.
-grim reaper retention time (00:08:23)-werewolf retention time (00:08:51)‘i’ve got only eight minutes left.
’sungwoo had only 8 minutes.
 and it was time for the ‘devil’s gate gatekeeper’ to appear.
 in other words, sungwoo had to get rid of that monster within eight minutes.
rattle! rattle!sungwoo closed in on the siege by moving the undead army toward the portal.
 sungwoo was going to launch a total offensive without giving the monster any chance to escape right after the latter appeared.
-the ‘final wave’ of the devil’s gate has begun.
finally, the final battle has started.
‘uh?”

 