\section{chapter 211}






 uijin’s face became even paler.
 as if he was scared of the king of the great mountain or the repercussions of sending jisu off to such a remote area, he continued with trembling lips.
“well, we couldn’t confirm his existence.
 we only saw the quest message.
 we could not even confront his subordinates, so we finally decided to move to another area.
”“that’s why you guys decided to join the demon camp, right?”“yes, that’s right.
 they have grown stronger, so they are exerting influence outside the mountain area.
 i dare say that he is a monster of a different nature created by the hidden quest linkage.
”the struggle guild could be called one of the strongest forces within the korean server.
 so, if it’s true they came out of the mountains for fear of the monster and joined the demon camp to confront the necromancer, the ‘king of the great mountain” must be a very difficult monster to deal with.
‘so annoying.
 if this is a growing monster, it’s not good to let him grow like that.
’the ‘hidden quest’ came into being as the remnants of the “warlord monster” hid on mt.
 taebaek.
 as always, the ‘hidden quest’ created variables.
furthermore, if the hidden quest kept repeating itself and connected as uijin said, it was highly possible that a tremendously huge monster would be born.
‘it looks like things got worse because the struggle guild members kept challenging the hidden quest they could not clear.
’sungwoo resurrected bumyol as a skeleton to obtain additional information, but his “fragmentary memory” didn’t come about.
 it seemed that he couldn’t get any other information.
another force appeared on the battlefield where the fighting was over.
doo doo doo!four helicopters crossed over a small peak and dropped troops throughout the forest.
 they were none other than the crusaders team members of the angel camp.
soon, the crusaders, including junghoon and minhum walked out of the forest.
“hi, junghoon.
 what has brought you here?”the look on his face was not good at all because his troops failed to attack the dungeon, and what happened after that was more shocking.
“as expected, you have destroyed them all.
 we intended to fight the demon camp in this area and mount a hard attack on their main forces, but you have already…”
he paused for a moment, then continued, looking around.
“oh, there was a reinforcement army of the demon camp on standby nearby.
 probably, after the quest was over, it seemed that they were going to attack my forces and yours at the same time.
”like junghoon said, the demon camp prepared for the next battle after the quest by deploying the reinforcement unit near mt.
 pukhan as plan b.
“we noticed their trick and responded.
”their trick was caught by the wide area surveillance team, the intelligence unit of the liberation guild.
 since they had been spying on the enemies’ movement for quite a long time, they could collect information much more quickly than other camps.
based on that information, the crusaders made a surprise attack on the reinforcement unit of the demon camp.
 that’s why they could not come to the rescue of the struggle guild led by bumyol when they were in the thick of fighting the necromancer.
“most of them were firepower units made up of flame-type wizards and spirit magicians.
 it seemed that they planned to destroy a specific area entirely in contingencies.
 but they couldn’t do anything and finally surrendered when we closed in on them and pressed them hard.
 but we have come to…”jungwoo cut short his words then looked around.
 the forest was forcibly removed, and the demon camp player’s bodies were strewn everywhere.
“as it turned out, we saved them.
”what junghoon said was that they saved the reinforcement troops of the demon camp who almost made the wrong choice instead of helping the necromancer.
of course, things would have changed even if the reinforcement unit had arrived on time.
“but you could not have saved the other guys,” sungwoo said.
“pardon?” hunghoo asked.
“other guys?”“i have a suggestion for you.
 let me get rid of the annoying guys in the northern part of the metropolitan area.
 then, you guys of the liberation guild can occupy the metropolitan area easily.
”junghoon flinched for a moment at his words because he sensed that there might be a reason when the necromancer gave him such an offer.
“you’re talking about the reconstruction alliance of uijongbu, right? well, i guess you might want to ask us a favor for such an offer.
”
“yes, but it’s not that difficult.
 can you give me some information on mt.
 taebaek by mobilizing the wide area surveillance team, especially the mt.
 solak area? it seems that jisu was dropped somewhere there by the enemy’s magic, but she seems to have gotten into trouble, given that she could not contact the community yet.
”hanho had been watching the community carefully, but he lost track of her.
 something really bad could have happened to her.
having heard it, junghoon nodded slowly.
“sure, i’ll help you because this is not a strategic issue.
”junghoon was in a rivalry with sungwoo, but he didn’t have to create a hostile relationship with sungwoo.
 besides, this was part of the “friendly diplomacy” that junghoon had in mind.
“thank you.
 i believe you won’t hide any information from us.
”“of course not!”after sungwoo made the case for the necessity of an intelligence unit, junghoon trained a large number of players in the assassin occupation group, such as bandits who could not play a big role in group battles.
as a result, he was gradually improving his ability to gather information by finding out a synergy formula specialized in “exploration” and “intrusion.
”sungwoo believed the wide area surveillance team would surely be able to find the whereabouts of jisu.
“thank you.
”the two joined hands after a long time.
meanwhile, reporter ahn and other camera operators were broadcasting all these scenes live.
“do you see him now? as always, the necromancer has prevailed, but we still can’t believe his victory.
 who would have thought that this huge imoogi would appear as the necromancer’s subordinate spirit?”at that moment, a message rang.
-you have leveled up.
 (lv.
 13)-you have successfully cleared the ‘hidden quest’ .
* rewards are given.
 (exclusive skill)* additional functions will be opened.
 (viewers’ support function)since reporter ahn was broadcasting for several hours in a row, drawing 110,000 viewers on his broadcast, he was gaining a lot of exp at the moment.
viewers’ support function? it was like a jackpot to him.
 he glanced at the message and continued the broadcast with a smile.
“i can’t interview the necromancer right now, but as you can see now, he is talking with the angel camp about something…”the moment he turned, pointing behind his back, he witnessed an unexpected scene and stiffened his face.
“uh, uh….
”the necromancer was approaching him, staring at him.
“what the heck is going on…”he was at a loss what to do.
 even if he was a professional reporter, he could not stay calm when the man who survived the heinous battle was getting closer to him.
in the end, the necromancer opened his mouth first.
“can i just say one word?”“oh, yes, please! you can say as much as you want!”an exclusive interview with the necromancer, and at this very important moment at that?this was the moment for reporter ahn to develop his broadcast as the best broadcasting agency of the korean server.
the necromancer looked at the camera and opened his mouth.
“i will destroy the main base of the demon camp today.
 since they attacked me first, i have no intention of showing them any mercy.
 let me give them a warning before blowing away the whole region.
”he paused for a moment then continued in a heavy voice.


“the undead do not distinguish between people.
 they only make a distinction between living and dead.
 those who don’t want to die, run away.
 evacuate with your families.
 this is my only mercy to you.
 nobody in that area will be alive by tomorrow morning.
”having said that, he turned right away.
 reporter ahn kept opening and closing his mouth, missing the opportunity to ask additional questions.
then, he announced in an urgent tone.
“players of uijongbu! if you’ve seen this broadcast, just hurry up and run away.
 send the kids and old people to a different place! i, reporter ahn, am now delivering you an important message from the necromancer from the mt.
 pukhan battlefield!”he approached the camera and pretended to cut his neck.
“please don’t confront the necromancer!”and exactly 23 minutes after the message was announced, those in uijongbu turned on the broadcast.
since the necromancer already gave them a grave warning, the entire korean server paid attention to what kind of response they would come up with.
the man they saw for the first time appeared on the screen.
his face showed he was defeated.
“everybody, are you coming out now? ah…”then, he took out a prepared script and he started reading it.
“we surrender unconditionally.
 i would like to inform you that younghwan lee and the executives of the reconstruction alliance already left this place in fear an hour ago.
”on the screen of the broadcast was a statue covered with vinyl.
 the object was being loaded onto a truck by five men.
“although we were left behind like this, we don’t have any hostility to the necromancer, and we will be waiting for the necromancer after taking out the devil’s statue and disarming ourselves.
 so, please have mercy on us…”they issued a declaration of unconditional surrender.
finally, sungwoo obtained another statue.
the creation of the third camp was around the corner.


 