\section{chapter 198}

                             




the team leader reluctantly grabbed the cell phone.
 if he was forced to face the necromancer, he knew the necromancer would kill him, take out his brain and peek into his memory fragments.
 the necromancer was serious when he threatened him.
“damn, damn…”he started to write something and post it on the community bulletin, swearing.
[677] i’m the man who attacked the main base of the necromancer.
-author: hunter company 2 team leader │ hit: 91,143hello, i’m the leader of the 2nd team of the hunter company.
 a few hours ago we successfully carried out the mission commissioned by our client who we can not reveal.
besides, as the 2nd team leader, i am proud to reveal that we were responsible for the surprise attack against the necromancer’s main base, which i think caused a big controversy over the identity of the attackers.
although we couldn’t kill the necromancer, we inflicted a lot of damage to the facilities of the third camp and removed most of its members.
 i am sure the necromancer will not be able to function at all for the time being.
finally, the hunter company is always receiving your request to use us as your mercenaries.
 so, please feel free to contact us.
[comments: 146]as if he was responding to the hot interest among those visiting the community, the team leader who said he attacked the necromancer naturally appeared and lied.
the hunter company was actually in the process of building a systematic organization.
 based on that, they were building a kind of trust with the korean server, so they were quite famous within the community.
so, when the id of the 2nd team leader was proven true in such an atmosphere, the online community was flooded with all kinds of comments regarding the huge controversy over the veracity of the leader’s announcement.
[comments: 146]
- apple farmer: man, that was true!- kim kk: well, since the necromancer is human, he can lose sometimes.
- seo gwang-hyun: by the way, it looks like the hunter company is a bigger company than we think.
 just like any normal company, they have something like a department.
 they’re not a paper company.
such comments were persuasive enough to stop the growing controversy over their surprise attack on the necromancer, which was confirmed in the amount of the money they bet.
[fight for the control of the metropolitan area (2)-winner prediction (bet)]* when you bet, you will receive a “bet token” item.
* the winning camp receives 1% of the total bet amount’ as the prize money.
* dividends according to the dividend rate are paid when your prediction is correct (excluding 1% of the winning camp’s prize money)“gosh, as you said, the number of those who betted on us drastically went down, sungwoo.
 not all of them believed that propaganda,” said hanho.
“well, some believed it, but others didn’t.
 after all, they were reluctant to bet on both of them.
”sungwoo volunteered to be an investment with a clear risk.
 of course, some could still bet on this dangerous investment, but there were only a few who would do so.
“all we have to do is wait until the last moment and invest.
”however, the village players and kanghwa island players prepared a large amount of gold, waiting for the proper timing.
 and they were firmly convinced that they would be able to have the returns several times as much as the principal.
in no time the time for them to enter the dungeon was approaching.

“let’s leave for bukhansan as late as possible, so they will think we might not come at all.
”“okay.
 as you know, the most important person is supposed to appear last.
”***mt.
 pukhan had turned into a devil’s forest with the creation of the python cave.
its entrance was already occupied by the liberation guild of the angel camp.
 but it didn’t mean they controlled that area.
-you have entered the competition area.
*caution! pk is not possible in this area.
 when you attack your opponent, you will be declared as an ‘automatic death’.
the system didn’t seem to want them to play the game outside of the given rules.
as a result, the two camps of angels and demons gathered at a certain distance and faced each other, as if they were knights of two families who were about to engage in a full-fledged fight.
in the meantime, the crusader team, armed with full plate armor, displayed their strength.
 they were taking a break, after putting their long swords, iron maces, and shields on the weapon rack they prepared in advance.
“hey, the demon camp bastards have been staring at us for some time.
 what shall we do?”“what? are they anxious to suck our pricks?”opposite the angel camp troops were the demon camp forces who were armed with high-quality items.
 they seemed to be the elite forces of the demon camp.
therefore, it was natural that the two sides were waging a war of nerves.
“you know what? they are new guys.
 they are self-proclaimed warriors who allegedly came from kangwon province some time ago.
”“oh, you mean the struggle guild? they are only small fry who have not yet suffered a painful defeat, right?”“yeah, i guess so.
 how dare these bastards who had been stuck in a remote village suddenly appear and swagger before us? how about teaching them a lesson since there is no necromance here?”just like the angel camp, the demon camp troops were also hurling violent abuses, watching the crusader team on the opposite side.
“look at the bastards wearing armor and pretending to swagger before us.
”“don’t worry.
 they won’t even smile if we attack them in the heads right away.
 lazy and disgusting sons of a bitch!”meanwhile, the camera operator was in a position to benefit the most from this kind of situation.
“now, everyone, this is the entrance to mt.
 pukhan.
 it’s also the main place of the upcoming second battle for the control of the metropolitan area (2).
”in particular, the player with the nickname “reporter ahn” was using the two camps’ waiting area for the broadcast, fully utilizing his recently gained reputation.
“we are expecting a fierce competition among them, but we don’t know what will happen in the dungeon, what monsters and events are there.
 so, we have to wait until the camps enter the dungeon! hey, assistant! how many minutes are left before they can enter the dungeon?”reporter ahn had four assistants.
“well, one hour and ten minutes left.
”“one hour and ten minutes!”“with only one hour and ten minutes to go before they can enter, the necromancer, who was caught in a controversy regarding an ambush, has not yet appeared here.
”

then, he lowered his voice and began to question the alleged damages the necromancer had suffered.
“is it true that the necromancer suffered irreparable damage as the hunter company claimed? will we see him again?”but soon he began to speak in a cheerful voice as if to change the atmosphere.
“anyway, everything starts in just an hour.
 before they enter the dungeon, i would like to get some comments from the major players of each camp! first of all, let’s get some comments from the demon camp that have once suffered a painful defeat.
”at that moment, various broadcasts were on the air, but reporter ahn’s broadcast, which was being watched by 60,000 people, was the most popular.
 that’s why reporter ahn could have an interview with the powerful players from both camps.
the players from both sides, the angel and the demon camps, seemed very tense and nervous, but they seemed relieved that the necromancer, the most promising candidate for the championship, hadn’t appeared yet.
right at that moment, one assistant shouted at reporter ahn.
“reporter ahn, look in the sky!”a huge shadow was cast over the two camps’ waiting area.
 everyone raised their heads before they knew it.
 7“oh, my god! what the heck is that?”“ah…”“damn it.
”the angel camp and the demon camp groaned at the same time because their sense of relief and expectation were gone in an instant when they looked up at the sky.
“necromancer!”the most promising candidate for victory appeared proudly.


 