\section{chapter 200}






 eventually, the betting rate for the third camp rose to 18.
4%.
of course, some of them decided to bet after watching the necromancer appearing on mt.
 pukhan, with no damage at all.
“lol! if the necromancer wins.
 we’re going to get a huge dividend! i guess this is the joy of gambling.
 it seems like my father’s gambling habits seem to be revived in my dna!”at the last minute, those who supported the third camp, as well as sungwoo’s party, made a surprise bet.
[my bet status]-winner prediction: third camp-bet amount: 70,000,000 gold (73.
4%)-estimated dividend amount: 296,954,695*out of the total amount (404,570,430), excluding 1% of the prize, your bet rate (73.
4%) is determined as the dividend.
sungwoo invested a whopping 70 million gold, accounting for 73.
4% of the total bet on the third camp.
 as a result, if the third camp won, he would have a whopping 300 million gold, in addition to the prize money.
‘if i win, i can raise operating funds that exceed the other two camps.
’after all, they needed money to run and grow any organization.
the third camp led by sungwoo was a small number of elite forces, but because of their small size, they found it hard to collect operating funds.
if so, how could they get the money?well, the easiest way was to just take it out of the pockets of the other camps.
sungwoo chose that method.
-enter the ‘python cave’ dungeon in the fight for the control of the metropolitan area (2).
 (30 seconds remaining)a game that will provide quality manure for the growth of the third camp had just begun.
-you have entered the massive dungeon ‘python cave’.
* you cannot exit until you begin the attack.
when sungwoo and his party entered the green entrance and passed through the trees, the loose trees tightened and closed the entrance.
as a result, the cave was filled with complete darkness.

so, they turned on the lantern they had prepared in advance.
“we have been trapped.
”“hey, we’re in a dungeon.
”they couldn’t get out of the dungeon unless they went out where there was an exit.
“gosh, why are the trees so big?”the light of the lantern was intense, but since it was blocked by a huge tree trunk, it could not shed light far enough.
 the giant trees were lined on both sides endlessly.
and the plants that had been growing on the mountain before were laid by the roots of the huge trees, pushed out of the place and uprooted.
* grab the ‘giant jannabi’ with the key and move to the next chapter.
“jannabi?”“what the heck does it mean? is it a butterfly?” hanho murmured, tilting his head.
jisu immediately replied, “jannabi probably refers to a monkey.
”“really? which language is it?”“as far as i know, it’s pure korean.
”if what she said was true, it seemed that a monster similar to a monkey would appear.
“it will not be easy for us to deal with monkey monsters in this environment.
”sungwoo lifted the lantern.
 a huge tree in front of them stretched up to the very top of the dome.
 since it had thick branches all around its trunk, it was the best environment for animals that could climb trees well.
“let’s look over our heads carefully.
”argh! ahhhhhhhhh!there was a terrible scream from far away in the woods.
 it wasn’t just one man’s scream.
 painful screams came out in succession.
dozens were being slaughtered right now.
“they must be affiliated with other camps.
”
the three camps entered the dungeon through different entrances then scattered in the forest.
 they seemed to have encountered something in the woods.
***“that’s it!”“we’ve found it!”so, they confirmed the existence of “giant jannabi” earlier than the other camps.
“it’s a monkey! monkey!”it was a huge monkey.
 the beast with long arms covered in black hair was hanging from the tree, blinking his red eyes.
grrrrrrrrrrrrrrrrrrrr…“fire the arrows!”ping! ping!however, the arrows couldn’t hit the monkey at all.
 the monkey climbed the tree at a tremendous speed.
 not only was the tree tall, but it was so dark that they could not see the money well.
of course, they could not cut or burn this giant tree because it seemed to be protected by some magical power.
“damn it! how can we hunt that monkey?”the demon camp forces kept running around, raising their heads to search for the monkey.
however, there was one thing they were mistaken about.
this wasn’t just a chase game.
wooduuuuuuuuuk!“ahhhhhh!”while they were chasing the giant jannabi, screams began to come out from those in the rear.
 “what the heck? what’s going on in the back?”at that moment, a long arm came down from the tree and grabbed an archer’s neck.
 he was immediately pulled up into the air.
 since he was pulled up instantly, he could not respond at all.
wooduk! wooduk!his screaming resonated throughout the darkness.
 when sungwoo shone the flashlight on the tree, four giant jannabi were tearing the archer’s limbs.
“damn it! they are moving super fast! everyone, watch over your head!”“they are aiming for you from above!”the three-meter-tall monkey, giant jannabi, was a definite predator.
 they were preying on the innocent players who entered the forest.
the angel camp soldiers were faced with the same situation.
tung! tung! tung!they kept firing the iron maces in succession, but they could not shoot down the monkeys.
since they were well organized, they could avoid the fate of being pulled up the tree.
“those bastards are waiting for us to be scattered.
 so, if we show any loophole, they are going to come down and drag us up straight away.
”deputy commander minhum checked their movement and analyzed their attacking pattern coldly.
but junghoon opined differently.
“if that’s the case, we have no other choice but to disperse to lure them to the ground, right?”even at the sacrifice of his team members, he had to attack the monkeys quickly because his camp was competing with the other two camps.
“it’s dangerous, but it seems worth trying.
 but, the thing is how to drop them from the tree after luring them…”“…”of course, junghoon knew how to take the risk of making them crawl down the tree.
but dropping those monsters from the tree would be very tough.
they were incredibly fast and ridiculously resilient.
 the trees around were high with indefinite branches.
 the moment they felt threatened, they would climb up the tree instantly.
“not all of them have the key.
 that means we have to hunt lots of them.
 if they notice our intentions, they might not come down easily.
”it was clear the monkeys had some intelligence, so if junghoon had to turn to a decoy operation, the fight would drag on.
“oh, my god…”while agonizing over the best way, minhum let out a sigh before he knew it.
he was afraid that if he didn’t come up with any solution quickly, the other camps might get ahead of them.


“damn it.
 i just wonder how sungwoo is coping with this situation.
”he was referring to the necromancer.
 what kind of method will he resort to?a message that came up a few minutes later frustrated them a lot.
-the ‘third camp (temporary)’ has obtained the key.
“uh?”“how?”junghoon and minhum sighed at the same time.
the necromancer, who was treated as an underdog for some time, seemed to be taking the lead like before.
“if he keeps getting ahead of us…”the third camp was ahead of them to claim the huge sum of 300 million gold and five legendary items.
deep in the mountains, far away there was some dense smoke along with the sound of dripping water.
 it was the sign of the necromancer.
the next moment.
rattle! rattle!a multitude of beings began to pass by overhead.
 they were moving among the trees.
the crusader team members shone the light on them.
what was reflected in the light was something white.
“that’s…”they were the skeletons of the giant jannabi.
it was the moment when the strategy only available to the necromancer came to light.
the easiest way to overcome a difficult environment was to adapt to it.
the necromancer could make the beings living in that environment his subordinate spirits.
in short, the necromancer was an all-weather player.


 