\section{chapter 304}

"what the heck?"




"chairman love! damn it, how dare you invite the corpse army into this sacred space?""you betrayer!"with many accusing the chairman here and there, she walked forward.
 she raised her voice, looking around the members of the provisional congress.
"everyone, wake up!"".
.
.
"when she, who had been held in jail only a little while ago, shouted, they immediately went silent.
 their instant silence showed how influential she was before they rebelled.
 "right here we have jonathan cage, head of external affairs team 1, initially known as the victim of the messenger airship, and the necromancer of the korean server, who allegedly attacked the messenger airship.
 so, listen to me!"they began to whisper here and there when she said that.
 "yeah, he must be cage!""oh, my god, what the heck is this?"they could not help but be embarrassed by this absurd situation because what they believed until now was false.
raising her hand, chairman love continued, "chairman baker has long been making plans to conquer the provisional council!"in fact, all of the members knew about it to some extent, but they didn't react because they thought of it as part of a common power struggle.
 but what she said next was shocking.
"he planted his own moles in the messenger, and when he arrived on the korean server, he brutally murdered the messenger's crew, crashed the messenger, and made up the whole incident as if the necromancer was behind the slaughter! we were all deceived by him!"
love's argument was confirmed by the fact that jonathan and the necromancer were standing side by side with her.
"nonsense! i can't believe this!""really? was what we heard until now a fake?""that bastard, william baker! i knew he would commit such a heinous act!"with all of them devastated by the shocking confession, somebody balked at chairman love's testimony.
"are you kidding?""don't be fooled by what she said!""are you sure he is really jonathan cage? he must be using doppelganger's transformation magic! dominique love is being deceived by him!"there were a lot who balked at chairman love's words.
"they are admiral baker's closest allies," jonathan whispered to sungwoo from the side.
at that moment, a close aide of baker's shouted loud.
 "admiral baker is still alive!"everyone's eyes turned to him at his roaring voice.
he was wearing a suit, but he was a heavy guy like a bodybuilder.
 he wiggled his hips like a typical white man then shouted angrily.
"he will take revenge against the korean server after saving his power on the japanese server!"
as if he couldn't overcome his anger, he jumped down and stood before chairman love.
 he was trying to hit her with his black fists, but she didn't back off.
"gordon, it's just meaningless.
 again, it's a pointless sacrifice.
"but the man called gordon sneered at her words.
 "meaningless sacrifice? love, is that your election catchphrase? if you're addicted to humanitarianism, you won't be able to regain a strong america! you will only be taken hostage to such a corpse pilot!"then, he cried out as if to appeal, looking around the provisional congress.
"we are broken, but we are still america! american is a country of unprecedented freedom in history! would you lose your freedom and pride in this place at once?"jonathan sighed and whispered to sungwoo.
"he is admiral baker's right-hand man, arthur gordon.
 he is the 7th strongest in our server rankings.
 he has tremendous strength, and he has a dirty temper, so i have no idea what he will do at any time.
 so, watch out for him carefully!"sungwoo nodded.
 then, gordon stared at sungwoo.
 his eyebrows wriggled like a snake.
"jonathan, you disgusting bastard! what are you whispering to a zombie who is here to eat away our freedom? don't you have any pride as an american?"gordon screamed like an excited bulldog.
 but sungwoo scornfully chuckled.
gordon cast a sharp glance at him and said, "are you laughing at me?""hey, pride isn't absolute, but if your pride is as high as your big nose, i can break it forcibly.
"after all, sungwoo's scorn made him lose his reason.
 some black energy was coming out of his body.
 even love, who was standing in front of him, stepped aside, feeling unease.
 "hey, gordon, calm down," she shouted.
 but her appeal didn't enter his ears.
"shut up!"he jumped off the floor and charged at sungwoo.
 it seemed he could punch down sungwoo with one stroke.
jisu pulled the knife.
 jonathan, who was standing next to him, also stepped forward.
 he reached out and lifted the marble piece from the floor to attack gordon, but to no avail.
 the big guy charged at him like a beast, broke the marble at once, and swung a hammer-like fist at sungwoo's head.
but the moment they collided, something happened, but it was quiet again.
however, he still didn't seem to size up the situation.
the big guy, who was rushing toward sungwoo, slowly tilted to one side.
 and he lowered his big head to the floor and fell under the marble floor split by jonathan.
sungwoo was holding a huge black sickle in his hand.
 although he was no.
 7 in the server with weak forces, gordon could not be a match for sungwoo, no.
 2 in the korean server rankings who had survived the hellish situation until now.
with the grim reaper on his shoulder, he walked forward.
"is there anybody here who is still arrogant enough to need my control and punishment?"no one dared respond to him.
"then…"sungwoo sat in the chairman's seat of the senate.
 members of the provisional congress looked at him, with their jaws dropping.
"shall we discuss the war crimes you have committed in our land and how you can compensate properly?"

even though chairman love, who was so friendly to sungwoo, regained her power, he had no intention of going back empty-handed.
 chairman love recaptured the "washington provisional congress" in a moment.
 her strong leadership was still valid, and when she was backed up by the overwhelming force of the necromancer, no one dared to rebel against her.
 what's more, her supporters in various parts of washington were quickly taking back their control of all the areas including the military, production, and transportation, which they lost for one day.
 "it is my opinion that we should repent what we did deeply and pay compensation for the fact that we caused the war and caused pain, regardless of the damage we caused to the korean server, small or large," chairman love said.
 she was also favorable to the compensation for the war crimes demanded by sungwoo.
 she realized that no matter how many supporters she had, she learned a painful lesson for the past two days that she could fall overnight without a strong force, based on the bone-breaking experiences of the past two days.
"and i have no doubt that our exchanges this time will continue to serve as a strong bond that will keep us two servers together in the future.
"actually, she was determined that she would not spare any investment in order to secure a powerful ally called the necromancer.
'i feel like a gangster hired by a politician for money,' sungwoo thought.
 in that sense, he felt like he was the muzzle of terrorism in the united states, but it didn't matter to him.
 'as long as she pays me duly, i have no problem serving as her protective shield.
'and finally, at the end of the meeting, chairman love asked sungwoo what kind of compensation he wanted.
sungwoo hesitated for a moment, then slowly opened his mouth.
all of them looked at him, holding their breath.
"well, give me four airships!"

 