\section{chapter 174}

                             




however, the brief broadcast revealed the location of the necromancer, which made the community and private stations make a big fuss again.
“sungwoo, they’re crazy about killing you everywhere.
 as many as five private broadcasts are open with the keyword necromancer.
”most of the threads about the necromancer on the community bulletin included threats and bluffing to kill and chop up the necromancer.
 some of them even plotted to attack him by recruiting a party.
 the central figure making such a plan was affiliated with the “reconstruction alliance,” which suggested he would carry out the plan someday.
however, what attracted the most attention among the personal broadcasts was a player named “terror kim,” who swayed a large amount of power in the anseong area.
-[live] let me make a bombshell announcement.
 i’m going to blow up the necromancer with a nuclear bomb.
 (23,166 watching now)on the screen of the broadcast appeared a man with a strong build.
 his upper body was naked and covered with all kinds of tattoos.
“i am ‘terror kim’ of the siheung area! i’m currently ranked 10th at level 16.
”having said that, he bit a cigarette.
 then, he lit the cigarette and continued.
“necromancer, do you like bombs? uh? you seem to enjoy playing your corpse explosion game all the time, right?”then, he raised his left hand.
 at that moment, a round object appeared in the air.
it was a transparent ball containing a green liquid.
he picked it up and threw it at the building behind him.
bang! bang!then, an explosion broke out and the whole two-story building collapsed.
 he made a strange smile, with the dust pouring over his head.
“by the way, i’m the first person to make such a bomb.
 my job is ‘terrorist’, and i made the bomb with my weakest skill.
”he blew out cigarette smoke towards the camera.
“phew… but i have a bomb that will take me 24 hours to complete.
 i’m going to prepare it and move to suwon to hunt you, necromancer.
 the bounty on your head is mine.
”then, he pretended to cut his neck with his thumb.

“choose whether you want to run away or if you want to be killed by the bomb.
 i’ll blow up the whole area around you.
 the bounty is mine.
”having said that, he began to laugh like crazy.
 the broadcast ended with that.
 it felt like a warning of terror sungwoo had seen somewhere.
“it looks like he has thrown down a gauntlet.
 it sounds like a bluff, but what if his threat is real? how can you stop his bomb?”sungwoo was immune to the flames, but the explosion was a different story.
he could be killed if something went wrong.
and the problem was that it wasn’t just sungwoo that terror kim was aiming for.
 he could stage an indiscriminate terrorist attack and bomb the entire village.
***sungwoo was always on standby near the flower bed.
when night came, the waves of monsters quieted.
 of course, it didn’t mean they took a break because night came.
 it meant that all the monsters in the area had disappeared.
if so, it could mean that more powerful monsters were coming from a distant place.
“we have not had any crisis until now.
 we have gained a lot by hunting miscellaneous monsters around the area,” said kyongsu, briefing sungwoo about the recent developments.
sungwoo said, “but you must not let down your guard because it’s not just monsters that are trying to kill us.
”“are they players, then?”“although most of the warnings posted on the community bulletin and the broadcast are just bluffs, who knows when some of them will translate their words into action?”the reconstruction alliance members had already attacked sungwoo.
 normally, they would not have dared to do so, but after they got buffs called “judge’s protection” and all stats were raised by 5, they were more confident now.
“it’s crazy.
”“it’s annoying.
”-the sprout of the world tree is growing.
 (11%)
when he looked with the lantern, he noticed a small leaf growing.
 just catching goblins and kobolds didn’t seem to make a big difference.
“sungwoo? what happens next if you create a third camp?”sungwoo shook his head, and said, “i do not know.
”“ah…”“but i have no choice.
 i can only assume it will lead to a good ending.
”“what do you mean by a good ending?”sungwoo nodded.
 there is an ending to this game.
 he’s never seen the prophetic stone featuring angels and demons, but he thought they didn’t seem to lead to a good ending.
“wouldn’t it be a better ending for us to arrive on our own feet than to see the ending while following the unknown whims of the angels and demons?”angels and demons didn’t think of humans as partners.
 given the information that had been obtained to date, they were trying to give humans grades and punish them.
although sungwoo made the ‘third choice’ because of unexpected conditions, he would not have blindly believed angels and demons even if he had not made the choice.
“ending? if we go to the end, will we find out who created this game?” asked kyongsu.
 but their conversation ended there because of a huge explosion.
bang! bang!there was a huge explosion in a shopping mall building on the right side of the plaza.
orange flames were everywhere in the dark.
“uh? what the heck is that? damn it! launch the drone right now!”shouting like that, kyongsu went down the mountain.
starting at that explosion area, sungwoo lifted the repeating crossbow.
kugugugugugugugu―in no time, the central part of the shopping mall collapsed.
 as if somebody put his hand in the middle of a sandcastle, there was a big hole in it.
 black shadows began to appear in between the building debris.
“hahahaha! hahaha!”a shadow walking from the center with a burst of hearty laughter opened both hands.
“hahaha! did you think i would come here in 24 hours just because i gave you 24 hours of preparation? you should have prepared everything in advance! it’s too late for you to run away!”it was terrorist kim, the terrorist who gave a warning broadcast that morning.
 a camera operator was standing next to him.
 they were broadcasting everything right now.
“now, i don’t want to tell you a long story.
 see the climax! everyone, see the final moments of the necromancer!”terror kim lifted something in his right hand.
“this is a skill that can blow up an entire apartment building!”it was a cylindrical object filled with a red liquid.
 a faint light came out from his hand and flowed into the cylinder.
 in no time, the red liquid began to turn black.
– caution! a ‘dark red storm’ starts in the affected location.
“it’s over!”then, terror kim threw it at sungwoo.
 an unknown object flew in a straight line toward sungwoo.
 he already said what it was.
 it was an explosive skill that could blow up a whole apartment building.
“all will die! lie down!”but at that moment, sungwoo did not move.
 sungwoo lifted the shield he prepared under his feet.
 the cylindrical object burst and the black liquid was sprayed in all directions.
 however, the moment it touched the shield, a protective shield spread from the shield.
the black liquid evaporated.
“uh?”that was it.
 there wasn’t anything like a huge explosion or flashing light.
the terrorists lying down on the floor raised their heads.


“what the heck happened?” sungwoo said gently lowering the shield, “you said that this bomb was not an item but a skill, right?”[item information]-name: bandit’s wooden shield-class: hero-category: shield-effect: a shield that ‘disables’ 3 magic attacks is formed.
 (one-hour cooldown)it was an item sungwoo captured from the “red rider” of the evolution society.
this was the red rider’s shield that easily defended against sungwoo’s new skill, ‘evil spirit bombing’.
“now, let’s change the topic of your broadcast,” said sungwoo.
“damn it! how could you block my skill?” screamed terror kim.
then, the terrorist lifted a bomb as if he were desperately resisting.
at that moment, however, three arrows were stuck in his forearm.
“ahhhh!”he fell immediately, and sungwoo slowly approached him.
the camera operator standing next to the terrorist was completely frozen on the spot.
sungwoo grabbed the camera and made the cameraman film him.
“let me make a major announcement.
”the number of viewers started to rise dramatically.


 