\section{chapter 345}

chapter 345: jeju island and attack on demon’s cave (9)ten minutes before the gate of the demon’s cave opened, the players of the world tree camp gathered near oreum, prepared for the worst fight while sticking to their places.





“whew, demon’s cave…”“the demons are really terrible.
 are we going to be okay?”although they had never experienced the monsters firsthand, they witnessed them on broadcasts, namely the mysterious monsters that ripped apart steel shields like a piece of paper.
“everybody, to arms! concentrate all attacks on the gate of the devil’s cave!”inho’s shout resounded over oreum.
 he took command of the world tree camp players in this operation.
“our firepower is definitely huge, but we’re not sure it’s enough…”he was really frustrated because he didn’t know how powerful the monsters were.
after looking around the battlefield once, he made eye contact with jisu.
“jisu, we will stop them as much as possible with long-range firepower first.
 but when they break through us and the melee begins…”thinking of the worst, he spit out one last word with difficulty.
“i hope i’m in your good hands.
”trusting her was the only thing he could think of in that situation.
“don’t worry.
”“i will trust you.
”the monsters from the demon’s cave were so powerful that ordinary players could not even dare to confront them.
but there were some people who could confront them one-on-one.
 among them was jisu.
 she showed tremendous power by hunting several low-level monsters before she had obtained “awakening”, not to mention “deity” status.

now, she had acquired both.
‘i can hold out.
 i should hold out by all means,’ jisu murmured to herself.
there was no sungwoo here anymore.
 so, she had to take care of herself.
“it looks like you’re pretty strong.
”somebody spoke behind jisu’s back.
 it was her half-sister, jimin.
“you were blacklisted in our family, but you are treated as a hero here?”jisu made eye contact with her without saying a word.
talking to a family member was always difficult.
 she was like an uninvited guest in her family.
she was the shame of the family as her father’s illegitimate child.
 so, she was oppressed and discriminated against by other family members while growing up.
 she had a childhood that could happen to a tragic heroine.
jimin gave a bottle of water to her sister with her hand wearing iron knuckles.
“well, you are old enough not to run errands for your sister and brother.
 you have led an independent life for four years, right?”jisu took the bottle and said, “thanks.
”her stepmother gave her a hard time, but fortunately, her half-sister and half-brother didn’t harass her.
all the troubles started because of her father.
 as the eldest son of a martial arts family, her father ran a fairly venerable martial arts training center.
 and he gave his children moral education, accompanied by corporal punishment, day and night.
“i guess dad would feel pretty satisfied if he saw you now because you are doing well even after running away from home.
 well, he wouldn’t express his feelings, of course…”was it because they had to check their father’s moods all the time while growing up? her half-brother and sister didn’t try to push jisu out.

rather, they used to take good care of her just like a stray kitten that lost her mother on the road.
 of course, they cared about her out of a sense of obligation, not affection.
jisu thought to herself at that moment, ‘sometimes they took care of me so much that i felt like an uncomfortable guest.
 of course, i could endure it thanks to their care…’jisu lived like an invisible man in the house and took the martial arts training center as her refuge.
 that’s how she spent her childhood.
however, as she grew up and reached puberty, she began to feel frustrated even at the training center.
 after all, she left her house and the training center.
- caution!  has opened in the area.
* the area has been closed.
 (jeju city)at that moment, a purple portal opened because sungwoo used the scroll.
“now, it begins!”“everyone, prepare for the battle!”gugugugugugu-vibrations came out from the gate of the demon’s cave.
 it looked like something was about to pour out.
“oh, is that the gate of the demon’s cave?”tension was intense on jimin’s face.
 it was the first time she encountered such a bizarre phenomenon.
 she led more than a hundred survivors to join this fight, but she couldn’t hide her tense feelings when she faced a terrible omen.
“jisu, i know this is not the right time to talk about our family affairs, but i understand why you left home,” jimin suddenly said.
was it because she felt this would be the last chance to tell her half-sister what she had cherished for a long time?but jisu shook her head and responded, “well.
”jisu’s half-brother and sister became athletes like their father.
 jisu also tried to catch up with them, but she always lagged behind them.
in the meantime, she heard that her biological mother was too weak, compared with her stepmother who was a star gymnast in her hometown when she was young.
 so, her mother stayed in her hospital bed for the rest of her life and eventually died.
jisu murmured, ‘i was told i was born with sick genes.
’people began to whisper about her behind her back.
 they said since she was an illegitimate child, she was weak, compared with other children of the family.
when she heard that, jisu felt her house was like a prison built with walls that she could never climb.
 she felt like she would lose her dream forever if she didn’t run away.
 so, she ran away by getting around the walls.
one of those walls, her half-sister jimin, spoke again.
“jisu, i’m not sure if you know this, but athletes are trying to prove everything.
 so, they seem to forget their limits and challenge too much.
”“…”“so, now that i’m by your side, i’m afraid that i might be trying to prove something without letting you know.
 so i’m a little worried that you might be in danger… i mean, be careful.
”since jimin didn’t know about jisoo’s brilliant activities until now, she couldn’t hide her worries as her older sister.
as far as jimin knew, jisu was always a young girl who tried hard but never succeeded.
“sis?”“yeah.
”jimin looked at her.
but jisu said without looking at her, staring at the gate of the demon’s cave, “don’t die here.
 when you die, you’re one cut below me in martial arts.
”jimin smiled at her words and said, “i’m sorry, jisu, but i’m not old enough to need your care.
 you don’t know how strong i am?”

jisu slowly drew her sword.
 suddenly, her eyes were torn vertically.
 she had no intention of cracking a joke with her sister.
“sister, i’m sorry, but you could die here.
 i’m serious.
”“…”this was not a training center or a stadium.
“based on my experience, you can’t survive with your born talent in this game.
 and you can’t do something well just because you are strong.
”“really? what is it then?”at that moment, a bizarre cry came from the gate of the demon’s cave.
kheeeeeeeee!finally, the first monster stuck out his head.
 after that, dozens of heads and many more limbs popped out.
 jimin’s expression hardened even more.
- the ‘1st invasion wave’ has begun at the gate of demon’s cave (2nd floor).
looking at the message, jisu felt goosebumps.
“i don’t know that either.
 by the way…”she didn’t know the answer, but she knew the method.
“now, i am confident of fighting well.
”while she was undergoing this phenomenon, she didn’t get around the walls that she couldn’t climb like before.
 she broke through the walls several times and survived.
just like sungwoo requested on the day this phenomenon first occurred, she adapted to this hell.


 