\section{chapter 11}






 like a wolf hunting a big prey, the skeleton was ripping apart the boss monster’s flesh bit by bit.
argh!screaming insanely, the big monster wielded the club in all directions, only pointing it into the air.
swoosh! puk!“nice shot!”now hanho’s dagger landed squarely.
 when the dagger was lodged into its shoulder, its left shoulder immediately dropped.
 and it was caught off guard completely now.
‘now is the time.
 sacrifice yourself!’
grabbing the sword afresh, sungwoo ordered the skeleton in his heart.
 then the one-armed skeleton boldly charged toward the boss monster.
‘goodbye.
 thanks for your great job.
’4although the skeleton stuck it out for a long time and fought well at the decisive moment, it was time for it to sacrifice itself for victory.
ahhhhh!with a roar, the boss monster, which was physically a total wreck now, wielded the club toward the skeleton’s skull.
 it would be smashed to pieces by the club, but sungwoo and jisu would be able to seize the perfect chance to kill it.
 looking for the chance, they jumped at the same time.
but…clang!“…ugh?”
the one-armed skeleton gently hit back the boss monster’s big club just like a master of martial arts!1“ah!”it was the moment when  was activated.
 with the probability of 88%, it blocked the boss monster’s first attack! however, that was not the end of the story.
when it mounted another attack this time, the big monster staggered, losing its balance…puk!“…urgh?”the one-armed skeleton’s sword stabbed its neck deeply.
cough, cough.
and the big monster’s muscular body helplessly collapsed.
thump!1“…”sungwoo, who was about to attack with the sword, stopped with a bitter expression.
 jisu, who was on the verge of attacking from the other side, also slowed down.
“what? it’s over?”“sungwoo, that skeleton guy… what did it do before it perished?”“no idea… i once killed it with that heavy all-in-one desk.
 in my opinion, this all-in-one desk is the world’s strongest item.
”

9he had a point.
 even if its arms were cut and was kicked around several times, the skeleton survived and faced the boss monster to finally kill it.
 it was this desk, however, that sungwoo used to kill the skeleton with a single blow.
but a red light began to emit from its body for some reason.
“uh?’at a glance, sungwoo felt that the skeleton’s build had been strengthened.
 and there was a red pattern inscribed on its forehead.
“what the heck is that? why did you make a strange tattoo without my approval?”3of course, the fallen skeleton could not reply, so sungwoo opened his ‘list of subordinates’ to check the details.


 