\section{chapter 354}

chapter 354: jeju island and attack on demon’s cave (18)fortunately, the road was not rough for some distance because if there was another vertical passage, it would further delay their movement.





“man, i didn’t know i would explore trees like this.
 i feel like i’m a termite.
”the group tried to shake off their anxiety while walking down the dark tree that was tightly closed on all sides.
 although they had fought many dangerous battles, it’s the first time they explored an unknown space like this.
 if they could recall one, it was the ‘troll’s crypt’, a large-scale dungeon that was found underground in suwon.
however, compared to that dungeon in suwon, this place was so bizarre that it could not be described with words.
they felt they had walked quite a long time.
 as they moved forward, they found something strange.
 for example, there appeared an incredibly long vertical passage where the road was cut off, but there was a curve cut into the wall, so they could walk through it.
there were also stairs cut at regular intervals in the sudden uphill sections that sometimes appeared.
 obviously, someone opened this road.
“this place seems like an artificial space.
 is it possible that something like a monster lives in the world tree?” said kyungsu.
sungwo felt the same way, but he differed on one thing.
“well, it may not be a monster because monsters don’t cut stairs.
”“then who the hell made something like this?”sungwoo did not answer.
 as li wei had said before, this place seemed to have been abandoned, but sungwoo was skeptical because he didn’t find any clear clues.
‘obviously, more monsters will come out.
’at that moment, somebody was shouting at the forefront.
 it seemed like something happened.
 sungwoo and kyungsu stopped walking and waited for the advance team’s report.
one of the crew members in front turned his head and said, “this is a report from the advance party.
 they found something strange in the front.
 this is it.
”he gave kyungsu the item that he received from the advance party.
“torch?”a luminous jewel was embedded at the end of a long rod, not the typical one ignited with oil.
“according to them, this was hung on the wall.
”
kyungsoo looked at sungwoo and said, “did someone come here first?”“well, it’s possible somebody had been living here…”sungwoo now began to realize something more clearly.
‘is the demon’s cave another dungeon?’he suspected that this world was another artificial ‘dungeon’.
he took the torch item to the white wolf because he needed the latter’s psychometric skills.
“can you see the memories contained in this item?” sungwoo asked.
the white wolf nodded then grabbed the torch with both hands and closed his eyes.
after about 30 seconds passed, he opened his eyes again.
“it’s too blurry for me to see, but it definitely contains human memories.
 it seems to be a very old thing.
”as expected, there were humans here.
“so, what happened?”the white wolf frowned, trying to vividly reproduce what he saw.
“what i saw was an opaque and fragmented image.
 i don’t know for sure, but there must have been a war and a massacre here.
 someone attacked here, but somebody defended.
 that’s all i could recall.
”was there a war within the devil’s world tree? then, was the hole in the world tree also the result of this war?someone attacked the ‘devil’s world tree’ that devoured the entire korean server.
 and someone fought against them.
‘is this a war between the fallen and the guardian?’
based on the world where sungwoo was, the one defending the devil’s world tree was obviously the ‘fallen’.
 when sungwoo touched the prophecy stone ‘bad ending-2’, there was a message about what would happen when they could not stop the fallen.
logically, it would be the guardian like sungwoo who fought the demons.
‘then, what’s the end of this war?’when he concluded he could find the clue when he reached the end of this cave, there was more news from the advance team.
“they found bodies!”“dead bodies?”sungwoo and kyungsoo moved forward hurriedly.
 the further they went down, the wider the passage became.
 and there was a fixture on the wall where they could hang the torch.
soon, they reached the place where the advance team was, and hanho and li wei, who walked ahead of sungwoo, arrived first.
“sungwoo, look here!”they were looking down into a large pit.
 it was as wide as ten meters, with the middle of the pit dropping out into the bottom.
“this is a trap,” said kyungsoo.
sungwoo nodded.
 if there had been a war here and someone attacked the devil’s world tree, as confirmed through the torch memories, they were obviously the bodies of the attackers.
in other words, there was a high possibility that they were the ‘guardians’ of this world.
“sungwoo! aren’t these bodies our items?”hanho pointed down the pit.
 among the piles of the bones that had definitely turned to ashes, there were objects that still maintained their original shape.
“oh! they look great.
 can i walk down and pick them up?”“no!”li wei shouted and grabbed hanho’s shoulder.
“why?”she ripped the bark off the wall and threw it into the pit.
at that moment, the pit was filled with red flames.
“ugh!”“so hot!”except for sungwoo, all of them standing around the pit could not stand the heat and moved backward.
“there is a reason why a trap is here! we’ve got to think there must be something powerful enough to burn to death anyone who could enter this terrible place.
”sungwoo knelt and looked inside the pit because he felt there was something familiar to him.
‘that one is…’he had seen this kind of pit before.
 it was obviously the gigantic mouth that spewed out flames, which he had seen in the underground passage of the headquarters of the evolutionary society.
something like a disgusting mouth was protruding all over the pit.
 he already saw five of them from the place where he was standing.
‘this is one of the powers of the world eater.
’the moment he destroyed it back then, he saw a message that he incurred the wrath of an unknown being, the ‘world eater’.
‘after all, the heart of the demon’s cave, the devil’s world tree, and the world eater are related to each other.
’meanwhile, sungwoo checked the items scattered in the pit.
‘as lee wei said, the intruders who came all the way here must have been armed with high-quality items…’

among the piles of bones was something that caught his eye.
‘it also means that they were buried here.
’emitting such an artificial brilliance meant that it was a fairly high-grade item.
of course, since sungwoo was not an appraiser, he couldn’t tell what kind of item it was just by looking at it.
“uh?”a familiar object caught his eye.
 there was a black sickle exuding dark energy, namely, grim reaper.
“no way!”sungwoo doubted his eyes.
 the grim reaper was an item that could be obtained through a job quest only.
‘is there another grim reaper in this world? if so, can i get two?’he needed to check it first to confirm it.
 sungwoo now stood at the edge of the pit, which was pretty dangerous.
“necromancer! what are you doing now? huh?”li wei shouted as if she noticed his intentions.
sungwoo turned to her and said, “don’t worry.
 i will not die in that fire.
”“what? how do i know? didn’t you see it a little while ago?”“i’ve been there before.
”then, sungwoo jumped into the pit.


 