\section{chapter 295}






 according to jonathan, an old man named chairman love showed leadership in bringing several organizations together to create one large organization called wpu.
wpu succeeded in stabilizing the eastern part of the united states, but they were faced with the next big problem.
“the problem was that chairman love had strong leadership, but he didn’t have the overwhelming force to back up his leadership.
”it was a time when the individual’s forces could destroy a large organization.
 so, those strong men craving for power could not sit idle, doing anything to challenge his leadership.
in the end, there was a sharp, invisible conflict within the wpu.
“i think the news of the crash of the messenger and their fabricated report must have already been conveyed to the leadership of the wpu.
 even though chairman love and his aides are still in firm control, this kind of false news will have a big impact on the congress’ decision.
”“do you mean they can attack us?’“that’s exactly what admiral baker, who made up this plan, wants.
 i’m sure he has already started agitating and persuading congress.
 damn it!”when hanho was done healing him, jonathan was stabilized much more.
but his expression got harder and harder.
he suddenly stood up from his seat and said, “thank you for your help.
 however, even in this worst case, there is nothing i can do to contact the wpu leadership.
”“how about accessing the us server community using a mobile phone? can’t you get through to them?”jonathan shook his head calmly and said, “soon after they launched the raid, they collected all cell phones that could access the us server community and destroyed them.
 even if we get a new cell phone, it’s useless unless we can scan the qr code drawn on american soil.
”sungwoo instructed the search team to check if there was any cell phone on the enemy’s bodies, but no cell phone was found like jonathan said.
“parker and his subordinates also destroyed their cell phones in case of this kind of situation.
 they had been planning this for a long time, so they must have thought of almost all the potential outcomes.
”
jonathan shook his head while sweeping his face with his large hand.
he seemed to be trying to be calm, but he suddenly expressed frustration.
“can you go to america if we can get you a plane?”he shook his head at sungwoo’s suggestion.
“well, you can’t cross the pacific ocean with any ordinary plane because it can’t withstand strange magic storms and monster attacks.
 that’s why we needed the messenger.
 since it was completely destroyed, it won’t be able to function unless the wpu engineers fix it.
”having said that, he squatted down on the concrete debris.
at that moment, sungwoo said something, and he sprang to his feet.
“we’re now fixing the messenger.
”“really?”sungwoo turned his head and looked at kyongsu.
“kyongsu, how long will it take to fix the sailboat?”“ah, it won’t take that long.
 i hear that they’re going to fix it by tomorrow morning.
”however, jonathan looked surprised.
he said, “no, you can’t fix it here.
”“why?”
“because it requires a lot of magic engineering skills.
”sungwoo nodded, then turned around, spitting out, “our technical prowess is considerable!”***given that they built such a huge airship, sungwoo realized that the wpu engineers’ technology was amazing.
 however, suwon village, the hometown of the world tree camp, also had a group of engineers with considerable technical skills.
 many engineering students devoted themselves to the research and development of all kinds of weapons, based on the overflowing materials and gold with the blessings of the world tree.
“what do you think? it’s enchanted wood, but its durability is good, isn’t it? there is no regenerative power at all, so it looks like they don’t know how to mix the troll blood.
”“hey, who would think of mixing troll blood with something like brick or wood? as you know, we also didn’t know anything about it until some crazy guy painted with it, thinking it was red paint.
”rather, they were ahead of the wpu engineers in some respects.
“it looks like there was a shield, but it doesn’t seem to have been hung on the hull itself.
”“then, it looks like it’s coming out of some sort of engine inside.
 hey, team no.
 2, go in and check the internal facilities again.
 ”of course, just repairing the exterior of the airship wasn’t all they had to fix.
“it seems that they intentionally destroyed the engine and steering gear as well.
 obviously, they intended to disable the airship.
”“but we can fix these kinds of problems easily.
 they should have burned it if they wanted to disable it.
 how stupid they are!”repairing the airship messenger was not an impossible task.
 the engineers of suwon village analyzed the design of each part and succeeded in reproducing or replacing the damaged parts.
they worked on it overnight, and when the next morning came, they finished the job.
one engineer shouted, “we’re done!”they completely succeeded in repairing the airship that crashed in a strange land.
when they finally installed the four core type-3 engines, powerful energy circulated in the air intakes and began to encircle the hull.
 they were done preparing for its departure.
“15 wizards who will infuse mana are now aboard the airship.
 we have also succeeded in reducing the weight of the ship by injecting mana first.
 if we inject mana again, the airship will be able to soar into the air.
 shall we start?”when kyongsu asked, sungwoo nodded.
“alright.
 let’s have a takeoff for a test run!”“five, four…”with everyone focusing on it, kyongsu kept the countdown.
“three, two, one!”“first test, take off!”gooooooooooooooo-a giant 85-meter airship slowly floated in the air.
 its wild shadow slowly covered the spectators’ heads.
 then, it stopped about 50 meters in the air.
“it has made a successful takeoff!”“the inside of the ship is also stable, with no shaking or vibrations at all.
 we still have to do a little more testing, but we haven’t found any problems until now.
”spectators shouted for joy everywhere.
jonathan’s jaws dropped in surprise when he watched the whole process.
 he felt that the wpu engineers boasted of their superior technology in the world, but the engineers here were ahead of them.
“i just can’t believe this…” jonathan said, looking at sungwo.
 “who the hell are you?”

sungwoo replied quietly, “look, i already told you their technical prowess is considerable!”since the messenger left america to cross the pacific on a mission of staying on other continents for a considerable period, there was a variety of supplies on the ship.
“wow!”“this item is…”among them, one item caught the blacksmiths’ eyes.
“it’s big and beautiful!”“man, i’m so excited.
 i’m not dreaming, right?”it was a huge cannon with a 4 meter-long barrel.
 it was the main cannon of the messenger.
[item information]-name: supernatural storm-grade: legend-category: special quest reward-effect: when you load ‘spirit stone’ in the magazine, you can fire a ”spirit bullet.
’ (once every 2 minutes)-description: a mechanical device created by the ‘iron spirit’.
 it is compatible with the power of various spirits and can fire ‘spirit bullets’.
 the higher-level ‘spirit stone’ you load, the more powerful firepower you can release.
since the blacksmiths had been working hard on the production of flying weapons, they had no choice but to pay attention to this huge cannon.


 