\section{chapter 199}






 bone wyvern alpha male, which was once called the ruler of the sky, but now only one of the necromancer’s subordinate spirits, landed at the entrance of mt.
 pukhan.
with a gust of wind blowing, those who stood around the area stepped back.
soon a man in a dark green robe emerged from behind the huge wings of bone wyvern alpha male.
“he’s arrived! necromancer!”“what the heck? he looks alright without any wounds.
”“man, what’s going on? i’m confused!”as always, there were only three on the necromancer’s team.
 they were a great contrast with the other two camps with hundreds of troops, but their presence was impressive enough to draw attention instantly.
tramp- tramp-the necromancer’s team approached the crowds whispering after their arrival between those of the angel camp and the demon camp.
“hello, wait a minute!”reporter ahn came to him first.
 even though he was having an interview with a key player with the demon camp, he stopped it and rushed to the necromancer abruptly.
“hi, necromancer! could you please give me an interview? please!”even though there was a big controversy over his whereabouts and safety, the necromancer duly drew the attention of lots of people.
“wait a moment, necromancer! can you…”however, the necromancer passed by the reporter without saying anything.
“gosh! does he think he is a superstar? you know what? the pen is strong in this world, too!”but his camera continued to film sungwoo and his party.

the necromancer faced the youngdungpo prosecutor, namely junghoo, with the angel camp.
“it’s been a while.
”“i’m here as your enemy like this.
”junghoon seemed not to be pleased with sungwoo’s appearance.
like the rumors that spread throughout the community, it would have been a much more advantageous situation if the necromancer had not participated.
“i don’t know what’s going to happen inside the cave, but as long as we don’t interfere with each other, i don’t think we will attack each other,” said sungwoo.
he was serious.
 junghoon had been his ally for a long time.
 although they belonged to different camps, sungwoo did not want to kill junghoon and his crusaders.
‘but if i am forced to kill him, i will,’ sungwoo thought, but he earnestly hoped that wouldn’t happen.
meanwhile, those in the demon camp were upset after watching the necromancer facing junghoon.
“what are they talking about? by the way, sir, it’s not true that the necromancer was ambushed with big damages,” bumyol, the leader of the struggle guild from kangwon province, asked.
then, younghwan lee, who was sitting in a wooden chair, nodded calmly, with his fingers interlocked.
younghwan said, “i thought so.
 he used a trick.
 what a cunning guy! how come he could think of the money in this situation…”younghwan found out that the necromancer carried out an adroit operation for the betting profit.
“if so, why don’t you take that weapon out? then, i will destroy his head in the dungeon.
”bumyol was a strong-willed man who was as big as a bear.
 when younghawan nodded, the secretary standing behind him brought him a black hard case.
“there are only 4 arrows here.
 so, you have to make sure you shoot them accurately.
”inside the case were four silver arrows.
[item information]
-name: holy blood arrow-class: unknown-category: player manufacturing item-effect: strong divine power is concentrated in the arrows.
 inflicts additional damage to the undead types.
 (+2,000%), inflicts a fatal “cleanse” effect on the undead when you hit the target.
-description: this is a weapon we have made after research and improvement.
 would you believe we made it by boiling 10 priests alive? if you hit the necromancer’s heart, it will deal a fatal blow to him.
 (manufacturer’s skill)bumyol accepted the item and said to younghwan, “sir, don’t worry.
 one of my subordinates is an experienced archer.
 he has never missed.
 this guy hunted trolls in mt.
 taebaek.
”“although you have four arrows, you must aim for the decisive moment to fire the arrow, got it? if you miss the target, the necromancer will know the power of this weapon.
 so, remember that.
”“yes, sir.
 by the way, where did you get this weapon? i think this is the perfect weapon with which we can kill the necromancer.
”younghwan stared at him silently with no expression on his face, then said, “well, you don’t have to know about it.
”“hahaha! after all, you’ve got lots of secrets.
 okay, i’ll respect your secret.
”the demon camp bet everything on this battle.
 it meant that they were determined to kill anybody who stood in their way.
“by the way, i just can’t understand why the necromancer has only three including himself in this crucial fight.
 i think they have a lot of guts.
”“you should not see the necromancer as a one-man army.
 look at that sword woman over there.
”“oh, she looks pretty.
”a woman stood behind the necromancer.
 she was wearing a red sweatshirt, with two swords on her waist.
 she was now staring into the air.
“that woman is fifth in the korean server rankings.
 that’s not the level she could reach by simply being around the necromancer.
 when a few monsters in taiwan were slaughtering dozens of tankers, she hunted them all alone.
”“oh, i saw her fighting, too.
”she was a player ranked 5th in the korean server rankings with the nickname “kor-339”.
“that woman could be the variable in this fight.
 when the battle begins, you have to kill her first.
”“well, my subordinates might want to enjoy fighting her for some time, but since you gave me such a reminder, i’ll keep it in mind, sir.
”now, it was ten minutes to go before the three camps entered the dungeon.
light was shining from the three entrances.
-the entrance to the third camp (temporary) has been marked.
the three camps were expected to enter different entrances.
 so, the leftmost entrance was marked as blue for the angel camp, the middle was marked as green for the third camp, and the right one was marked as red for the demon camp.
a path opened up between the densely grown trees.
there was only darkness so they couldn’t see an inch in front of them, and fog came from everywhere.
“angel camp, fall in! stand by to enter the dungeon! the crusader team, you guys enter first!”the angelic camp, whose striking force numbered more than 500, was the first to move.
then, the demon camp also began to get busy.
“close in, mountain warriors!”“this mountain range is our battlefield! compared with the giant mt.
 taebaek, mt.
 pukhan is nothing!”the demon camp seemed to number more than 700, with the struggle guild fighters taking the lead.
compared with the two camps, the third camp led by the necromancer seemed pretty relaxed.
“how about entering the dungeon when it’s open?”“yeah.
”

“man, i feel like i want to stop by the restroom.
 i’m getting nervous for no reason.
”those who watched the necromancer’s team began to whisper among themselves.
“no matter how strong the necromancer is, don’t you think it’s too absurd that he is fighting the other two camps with only two supporters?”“i’m not sure if you can call the third camp a camp, compared to us.
 given their size, they’re only a party.
”“they look rather arrogant.
”is it because of the controversy over the necromancer’s whereabouts in the community?lots of comments began to be uploaded about reevaluating the necromancer.
but sungwoo didn’t care about it.
 the more they underestimated his power, the better it was for him because their betting had been going on until a moment ago.
-winner prediction (bet) ends.
[fight for control of the metropolitan area (2)-winner prediction (bet)]1) angel camp: 170,001,600 gold (41.
6%)2) demon camp: 163,300,400 gold (39.
9%)3) third camp: 95,355,000 gold (18.
4%)= total: 408,657,000 gold= prize money: 4,086,570 gold* when you bet, you will receive a “bet token” item.
* the winning camp receives 1% of the total bet amount’ as the prize money.
* dividends according to the dividend rate are paid when you have the winner prediction right.
 (excluding 1% of the winning camp’s prize money).


 