\section{chapter 146}

                             




“i am really proud to hear that from you, sungwoo since you are well ahead of me in everything,” said jisu.
she then rubbed the blade on the killed man’s clothes.
-allied forces occupied ‘c point’.
* buffs are applied.
* reoccupation is not possible for five minutes.
then, the message about the success of the occupation of c point appeared.
 it was where hanho and the players were headed.
“hanho also seems to have succeeded.
”“we’ve got only one place to occupy now.
”[buff list in the mini game]sungwoo earned a considerable buff effect through occupation.
 since they were familiar with the rules of the mini-game and the advantages of occupation, the enemies planned to have a fatal match in the huge ring called kanghwa island after preemptively monopolizing the buff.
however, sungwoo was not a man who would be easily drawn into that trick.
 he had enough experience dealing with a hellish game like this.
-the enemy forces occupied ‘a point’.
they also gained buff by securing one occupied area.
 now, they would try to split their troops to capture b and c points while defending the occupied area.
‘we have to move faster than our enemies.
’“jisu, we have succeeded in occupying this area, but the enemies will try to recapture it.
 i know it’s not easy, but please defend this place.
”
“are you going to go to point a?”he nodded as he walked to bone wyvern.
“let’s get rid of them in an hour,” he said.
he had only one hour during which he could summon the grim reaper and maintain the condition of lich.
 if he could not carry out his mission within that hour, he would be disadvantaged, for the number of skeletons that sungwoo can control would decrease by 50, and the infinite resurrection of his subordinate spirits would be impossible.
 of course, that depended on the assumption that the enemies would survive an hour of hell.
“let me contact muyon to send you a reinforcement army here.
 please hold out until then.
”“don’t worry.
”jisoo nodded calmly.
***point a was mt.
 mani.
 the captain of the pirates who arrived there, jahon, felt very annoyed and frustrated.
“we have already lost two places?”“sorry!”the purpose of the enemies in starting the mini-game was to quickly occupy a majority of the occupied areas, then press down on the islanders with overwhelming buffs.
 in other words, they sought to kill the necromancer, the dangerous enemy, by squeezing.
“do they know the rules of this mini-game? it’s impossible because we have earned it as a reward for the special quest.
”“general, i’ll make sure they do not leak this information through broadcast.
 i think this was not broadcasted because only we witnessed it,” said kuan, the man in sunglasses.
“of course, you should.
”at that moment, all these scenes were being broadcast live on the “china-2 server”.
 the number of viewers reached 170,000.
 the chat window was mainly full of sarcastic content about the red revolutionary army, but the viewers also had great expectations for their occupation of korea.
 they wanted the players from china to win, even though they were driven out of the mainland.

“send a commando for the occupation.
 we’ve got only one headache there, namely, the necromancer.
 we don’t know if he chose point b or c, but in the end, he’ll pay attention to only one place.
 in the meantime, we can occupy two places and push them out with the buff.
”jahon said no matter how hard the islanders resisted, his forces would win.
he thought that no matter how strong the necromancer, the no.
 2 of the korean server was, he could not control the battles that were occurring simultaneously in three places.
eventually, the necromancer would lose the buff and be killed.
 that was how this mini-game would end, jahon expected.
at that moment, somebody shouted, “it’s a raid!”“they’re striking from the north!”turmoil began at the edge of the enemy camp and spread everywhere.
“it’s a raid!”“undead appeared from the front!”jahon frowned at that.
 black smoke soared when explosions occurred among the trees in front.
 there was the noise of battle everywhere now.
“so, you guys chose this as your battlefield, not point b or c?”this was something jahon never expected because he assumed that sungwoo’s forces would defend their places because they were on the defensive.
he gave a hollow smile, then said, “this guy is really reckless.
 he should have defended his vulnerable rear area, but he recklessly moved into this place to attack us? what about the rear then?”jahon often heard about the bold actions of the necromancer.
 he also heard that the undead that the necromancer controlled were resurrected no matter how many times they were killed and that the necromancer himself carried a couple of giant undead with him.
“no matter how strong you are, do you think you can win when you lose all the buffs?”jahon admitted to the opponent’s strength, but he thought the necromancer’s attack now was stupid and reckless.
“this guy with such poor judgment is no.
 2 on the korean server rankings? the korean server is weak, as expected.
”jahon had a cigarette in his mouth, then watched the battle taking place in the woods.
but strangely enough, the turmoil got closer and closer.
“avoid!”“ahhhhhh!”now, his subordinates screamed from all sides, and a huge vibration that shook the earth also grew bigger and bigger.
 soon “giant undead” appeared on the ridge in the distance.
 they were ogre skeleton and bone drake which he had learned about after checking them out in advance.
“block them!”“use magic!”his subordinates were embarrassed, but they began to block them by using powerful firepower.
“they’re stronger than i thought…”then, troll skeletons appeared on a large scale.
 they pushed out his subordinates fiercely.
 he didn’t know there were so many huge skeletons.
“it looks like they got stronger in the meantime, but we can deal with them.
”splatter! splatter!at that moment, a giant in the form of a mud lump appeared.
 it was the golem.
dozens of zombies began to jump around it, wearing full plate armor made of bones.


kueeeeeeeeeeeeeeh!this time ghoul king jumped out of the ridge and ran downhill like crazy.
then, a huge shadow cast from the sky.
 when jahon raised his head, bone wyvern, which he had seen once, flew in with its huge wings spread out.
 there were three such monsters.
“what the hell keeps coming out like this?”jahon quit smoking.
 he got nervous all of a sudden.
“man, are they strong like this? they are far stronger than we have investigated.
”soon, there appeared lich with a huge scythe and the death knight with green eyes sparkling in the distance above the ridges.
“necromancer…”it was the moment when the necromancer’s undead collections were introduced to china via live broadcast.
originally, jahon was confident of occupying the korean server.
 he thought that his brother, gen.
 ingong, was defeated because they didn’t size up the enemy’s power accurately.
 he thought he was different from his brother.
‘intelligence is important.
’convinced of that, jahon kidnapped a korean server player and uncovered all kinds of information from him.
 the conclusions he made through the tips he thus obtained were clear.
“yes, i can win.
”that’s why he asked gen.
 chongong, the supreme leader, to dispatch him for the mission of occupying korea.
 he proudly expressed his confidence to gen chon.
“i can win if i am backed up by the fleet.
 when you occupy taiwan and head to korea leisurely, let me secure a port where you can safely land.
”jahon came to this place so confidently, but he was greatly humiliated in the first fight.
 his forces suffered big damages when they were bombed at sea.
even after such a humiliating loss, jahon was still confident because he had some crucial intelligence.


 