\section{chapter 171}

                             




sungwoo’s destruction of the statue of the absolute race caused a bigger stir than expected.
 the absolute race not only offered a bounty for sungwoo but also issued an order to kill him.
[server quest]*this quest was given to the entire server by the angel camp.
 you can choose one of the three options below:* when dealing with the target person, you receive the ‘blessings of the judge’ buff from the angel camp.
 all stats increase significantly over some time.
 (+5)* in the case of non-affiliated players, the ‘rank score’ will be taken into account when signing a contract with the angel camp.
* only those who have made the greatest contributions can receive one ‘holy gift ‘ from the angel camp.
support the 3rd camp (protect kor-157)* you will be allowed to choose a third faction.
* you will incur the wrath of the absolute race.
bystander* not applicable.
“sungwoo, these options are not good.
”hanho looked around with anxiety.
 youngdungpo was the territory of the allied forces, but the atmosphere now was much different from before because the players of the liberation guild located on the roof showed a somewhat different attitude.
‘even i will covet the bounty.
’the bounty put forward by the angel camp was 50 million gold.
 moreover, three options appeared.
 they had to choose one of them by all means.
however, depending on the choice, the results presented were so different.
 in short, the options openly encouraged them to kill the necromancer.
“what is this holy gift? besides, all stats increase by 5? isn’t it the same as the effect of increasing by 6-7 levels?”
“the rank score of the angel camp? i don’t know what it is, but i think it’s amazing…”but no one dared to come forward.
finally, junghoon walked out from them and said, “sungwoo…”there was puzzlement and anger on his face at the moment.
“i really can’t understand what you did a moment ago, and it’s unacceptable.
”sungwoo could not afford to explain it fully because of the urgency of the situation.
“i can feel something, but i can’t tell you with confidence, someday i can explain it.
”“i believe in what you feel, but this is different.
 if you make somebody we can’t deal with an enemy like this, i really can’t work with you in the future.
”“i understand.
”sungwoo could not blame junghoon, and it would not be strange at all for junghoon to criticize sungwoo in this situation.
sungwoo also felt like opposing the absolute race was like fighting against god.
furthermore, when junghoon and sungwoo put their hands on the statue at the same time, junghoon made a contract with the angel camp.
 nonetheless, sungwoo broke the statue, which was a great shock and a serious development for junghoon.
“and we may go further and have to fight you,” said junghoon.
even his reaction like this was fully understandable.
at that moment, the crusader team approached sungwoo slowly.
 it looked like they were about to pull out their swords and fire their crossbow at him.
jisu, too, spread her feet a little wider and put her hands on her sword.
it was a close call.
junghoon continued, “but let me choose option 3 for now.
 sooner or later, i will switch my decision to option 1 or 2.
 i hope i can find a reason for choosing option 2.
”when he said that, the crusaders took a step back.
 the tension eased a bit, but the atmosphere was still cool.
 what would have happened if sungwoo and his party fought the crusader team whose stats increased by 5? no matter how strong sungwoo was, he could not be sure of his victory.

“thank you for trusting me.
”“i just got a penalty from the angel camp for choosing option 3.
 anyway, i’m afraid i can’t help you any further,” said junghoon.
“sure, let me head to suwon.
”“yes, go ahead.
”for now, they had to split.
 it was natural that it was awkward for them to work together in such a situation.
 even if junghoon tolerated sungwoo, youngdungpo, where numerous player groups gathered, was never safe because some of them might rebel against junghoon.
but the situation in the suwon village would be different.
 it was something like a shelter that sungwoo built in preparation for contingencies like this.
sungwoo and his party escaped from the roof and quickly descended the stairs.
he was thinking of summoning bone wyvern after getting out of the area.
if he summoned bone wyvern on the rooftop visible from everywhere, he could be hit by an unexpected attack.
 they left the youngdungpo station building quickly.
“there are people everywhere.
 i can feel their intense gaze,” said jisu.
as she said, they could feel the hostile gaze of many people around them.
 some of them were peeking out of the alleys and windows, and others were staring at them outright.
 somebody was even fidgeting in a place invisible from others.
“well, i don’t think they will attack us.
 that guy over there seemed to have lifted his crossbow! hope he’s not firing.
”most of them were helped by sungwoo, so they even regarded him as a hero, but they were swayed by the enormous bounty put forward by the absolute race.
“they know they can’t attack us because of their vain desire.
”even if they coveted the bounty, they could not dare attack the necromancer.
nonetheless, if somebody had the guts to mount an attack out of greed, there was a possibility that the rest of them would run wildly to attack him.
 so, it was imperative for sungwoo and his party to leave as soon as possible.
“ugh!”at that moment, sungwoo felt something hot coming up from his chest.
‘oh no… what the heck?’it got hot little by little, then it was not hot.
“sungwoo, what’s the matter with you?”“nothing.
 move quickly!”sungwoo was bothered a bit by that, so he just focused on the situation he was facing now.
they slipped out of the second iron fence and out of the official territory of the liberation guild.
sungwoo summoned a bone wyvern immediately.
 but at that moment, jisu turned and looked over the iron fence.
“rotor sound…”“pardon?”“i can hear the rotor sound, but this is not a drone.
 they turned on the engine of the helicopter.
”it was a bad sign.
not surprisingly, when sungwoo got on the bone wyvern and looked down, three helicopters were rising over the malls in front of youngdungpo station.
‘reconstruction alliance….
’that place was where the military helicopters of the organization called the “reconstruction alliance” were located.
sungwoo had once encountered its members at the corridor of youngdungpo station before.
 he clearly remembered that they expressed a hostile attitude toward him at that time.
but he never expected they would openly attack him.
woooooooong!their helicopters began to speed up, and their fuselages tilted forward.
 they were faster than expected.
furthermore, an unusual wind blew from somewhere and began to crush the wings of the bone wyvern, which slowed down its flight significantly.
“there is an exorcist on the helicopter!”

the wind exorcist on board the helicopter was changing the direction of the wind.
 so, it seemed impossible for sungwoo to give them the slip.
 sungwoo had no intention of running away.
sungwoo was determined to deal with them harshly because they would cause big trouble later if he didn’t crush them now.
“hanho, you said before you liked helicopters or teleports better than bone wyvern, right?”“pardon? why are you saying that all of a sudden?”when sungwoo asked suddenly, hanho felt ominous.
at that moment, black smoke rose from both sides of the bone wyvern, and nine zombies were summoned.
 minsok and orun also appeared behind them.
“how about going there and taking them by yourself?”“i beg your pardon?“the zombie monster will get you on board.
”“man, are you crazy? sorry if i told you so!”in the meantime, the distance between the helicopters and the bone wyvern narrowed.
sungwoo could even see the pilot’s face.
 and someone in the lead helicopter stuck out his head.
ping!jisu moved in front of sungwoo and pulled out her sword.
jumping, she cut something out of the air.
puck!an incredibly fast object was split in half and its fragments were stuck in her left clavicle.
it was an arrowhead the size of a finger.
fortunately, the arrowhead slowed down when she blocked it with her sword.
 otherwise, she must have suffered a fatal injury.
“be careful, it’s a sniper’s fire!”

 