\section{chapter 440}

"i'm sorry, but i came here first, necromancer!"




what he said was true.
 he got here first, so it wasn't his fault that he hunted here first.
sungwoo replied, "i know.
 i don't want to pick a fight with you on that.
 but you don't have to throw stones at us who got here late, right?"obviously, gangsok deliberately dispatched angel champions and others to stand in the way of sungwoo's chase.
with an awkward expression, gangsok said, "um, i'm sorry for that.
 i guess i was in a hurry.
 but i didn't mean to kill you.
 please understand me.
 i thought you were strong enough to break through them and stand tall before me like this.
"he didn't mean to kill me? sungwoo could not understand what he was talking about.
'then what do you want?'sungwoo got curious again, so he asked, "that's enough.
 let's be honest.
""what do you mean?" gangsok retorted, tilting his head.
"if you're not trying to fight me, tell me what the hell you're trying to do.
" sungwoo needed to make sure he should clearly find out his motivations.
he continued, "you have declared war on all players in the world.
 i am also the target.
 so, i don't think you want to welcome me when you have already started the war, right?"gangsok nodded.
 since he was responsible for starting the disaster quest, he could not ask sungwoo to trust him.
"yeah, that's right.
"as soon as gangsok said that, isabella looked at him cynically as if she didn't like their conversation, then let out a deep sigh.
"keep it short.
 i can't stand it long.
 if i'm upset, i'll melt them all.
"red flames were flickering in her mouth.
 even though the flames were lingering inside her mouth, the temperature around their area was rising.

'it's definitely different.
'to be honest, sungwoo wasn't sure if he could withstand her breath.
 if he had to face it, the best policy would be to avoid it as much as possible.
"yeah, i'll have to explain why i'm doing this.
"gangsok was lost in thought for a moment, then opened his mouth.
"you think it would be inappropriate for me to say this, but it's all for the sake of our world.
"after all, what he wanted to say was something like a great cause, which sungwoo already expected.
 but he couldn't believe it.
 most of the plausible lies had some great cause.
 gangsok continued, "i'm going to be the world eater to save this world.
 and i hope you can help me.
"that's not what sungwoo wanted to hear from him.
"so, make it clear what you mean by saving this world.
 how can i help you when i don't know your purpose?"gangsok's left eyebrow twitched.
 obviously, his question hurt his pride.
however, sungwoo went further, asking, "so, tell me what the heck it is that only you know!"sungwoo thought that gangsok knew about this world more clearly than anybody else.
 gangsok said, "yeah, this game is a disaster for us, but it's literally a game, so it's only a plaything for somebody.
"sungwoo could understand his point up to this point.
 but what gangsok said next was incomprehensible.
 "so, in order to save this world, we have to gain favor with those who caused this situation, right? i know who they are and how to gain favor.
 do you understand?"sungwoo could not figure out what he meant by 'knowing them.
'
so he asked calmly, holding down the urge to get upset.
"how can i believe that? how did you know it, and what's the evidence?""as for me…"he paused a bit, and sighed, then he continued, nodding, "this game isn't new to me.
"everyone was surprised by his words.
"what did he say?" "isn't this game new to him?"in other words, was this game the second time for him? "my hometown was already destroyed.
 you have already seen the demon's cave, the world that met its final destruction.
 it's not just one or two.
"does it mean that he came from another world like world eater? was that the reason why he could get ahead of sungwoo from the beginning?gangsok continued, "this is something i've experienced by myself, and it's really true, but i have no idea how to prove it.
 so don't ask me anymore.
"".
.
.
""necromancer, please trust and follow me.
 i haven't been able to stop the doomed ending of this world no matter how hard i tried.
 but i think i can, this time.
 but you should be with me.
"obviously, gangsok was asking him a favor, but actually, his request was close to coercion.
 sungwoo was embarrassed.
 he wondered whether he should believe gangsok's absurd statement.
at that moment somebody shouted all of a sudden.
"he's a liar!""uh?"that voice came from the passage leading to the ground behind his back.
there were the white wolf, black lion, and about a dozen special commando members standing there.
"necromancer! don't believe what he says! as you said, we searched for the unidentified airship and read the memories of the man buried there.
""ah.
"gangsok let out a sigh, then chuckled.
 "you mean that guy with psychometric abilities?" he asked cynically.
 "he just wants to use you to satisfy his desires!" shouted the white wolf, who was walking toward sungwoo, revealing the truth.
 "and that guy plans to destroy our world!"destruction of our world? the white wolf continued, "in return for destroying our world, he got reassurance from the creator of this game that he would receive something.
"there was a brief silence.
 the flow of air slowed down, stopped as if it got sticky, then began to tremble.
".
.
.
"isabella's pupils widened and jisu's breathing stopped.
 both sides looked at each other.
sugnwoo grabbed the grim reaper and turned his head very slowly to face gangsok again.
 this time he looked different.
 "necromancer, aren't those guys from the 'evolution society' that we fought together in pyeongtaek? i hear that even when the japanese server invaded us, they were on their side," gangsok said cynically as if he couldn't believe it.
 "can you believe what these crazy people say? or do you trust me who has fought with you and helped you a lot?"

at that moment sungwoo screamed before he knew it.
 'ugh!'something felt hot inside his chest, which was the scales of the giant snake, imoogi.
'is it a warning for me?'his helper was sending out a warning to him.
 when he looked at gangsok, he felt it was hotter than before.
'this means i should not trust gangsok.
'to be honest, sungwoo could not figure out which side he should trust.
even the unidentified 'helper', who delivered messages to him, along with a system error, controlled sungwoo as he pleased, but didn't actively persuade him not to trust gangsok.
'but at least this helper has the power to affect the system.
'the fact that his helper had the power to bring the system down was the basis of his claim to bring it down.
"necromancer, let me ask you once again.
 who will you trust?"gangsok asked again, but sungwoo let out a sigh and replied, "all i believe is what i can control with my hands.
" if he didn't like the helper who delivered the message with the scales of imoogi, sungwoo could break his relationship at any time.
 in other words, he could discard the scales and receive the message indirectly.
 but what about this man?"really? are you sure?" gangsok asked in a frustrated voice.
 "then you don't trust me, right?"at that moment, a light flashed from his wand.
 a thick ray of light passed through sungwoo and hit something behind his back.
bang!

 