\section{chapter 370}

chapter 370: exit from demon’s cave and preparing to conquer china (2)however, taegam gathered the vast resources of the chinese continent to inflict fatal damage to the necromancer.





“in other words, as long as we have that divine power there, the necromancer’s undead army will lose their immortal power, and from that moment on, they will turn into meaningless creatures.
”the control manager nodded, but carefully raised a question.
“by the way, i’m asking you this because i’m not so sure.
 if the necromancer attacks us, don’t you think he will attack that weapon first?”the necromancer’s mobility and anomalous firepower always surprised everybody.
 and the head of the control room was also aware of that.
“uhhhh… if the gate is closed, it means he is protected by an unprecedentedly powerful shield.
 actually, he has withstood the large-scale attack magic that 1,000 wizards performed together.
 can you imagine? he has blocked the magic cast by 1,000 people which was powerful enough to blow up a city!”“really?”“when he notices the existence of the white light sphere, the necromancer will try his best to destroy it.
 but don’t you see him already being defeated helplessly?”then, taegam sharply turned at the window and continued, “if the korean server attacks us with the necromancer as the commander, it’s like they are donating their loot to us at the risk of their lives.
 i can guarantee it.
 so, let’s see.
”taegam laughed heartily in a happy mood.
 no matter how hard he thought about the coming war with the korean server led by the necromancer, he believed this was destined to be a battle that his troops would win 100%.
***immediately after the battle, a huge number of messages appeared before sungwoo’s eyes.
messages about his quest success, level-up, new title, and request for claiming a reward, etc.
‘i have to put off choosing it until later…’
- after 60 minutes, all the gates of demon’s cave will be closed.
he had to get out of this place right now.
 the heart of the demon’s cave was destroyed, so all the doors of the demon’s cave were to be closed, as scheduled.
“argh…”“man, my head is hurting so much.
”at the same time, those whose bodies were frozen by ‘dragon fear’ began to wake up.
after they fell into a defenseless state, sungwoo used some of the undead army to protect them in the corner of the cave, so there were no casualties among them.
“ahhhh! gee, i had a terrible experience.
 i felt like i was suffering from sleep paralysis.
”hanho was almost in tears.
 no matter how high his level was, he could not withstand ‘dragon fear’ if he didn’t have divine status.
‘if that’s the case, he’s going to be in big trouble when i fight the dragon.
’sungwoo was already worried about hanho.
 if the players without the deity status were defenseless against ‘dragon fear’, no one except jisu would be able to fight the dragon.
‘it is important for me to develop my own strength, but finding the way to overcome ‘dragon fear’ is urgent!’even though sungwoo is stronger than the whole alliance, it was going to be a big loss if the world tree camp and the american server became powerless before ‘dragon fear’, so it would be a formidable challenge to deal with the real dragon.
 sungwoo needed to gather all the power available, no matter how small it was.
“is the fight over?”
at that moment, kyungsoo came to sungwoo staggering.
 sungwoo nodded at him.
“ugh, i didn’t help you at all.
 can i go back?”“no, not yet.
 you have to check out something first.
”the world eater asked sungwoo to check out the ceiling of the ‘hall of guardians.
’‘i don’t know what he meant, but there was no hostility in his last words.
’sungwoo felt like the world eater wanted him to do something that he couldn’t.
“we don’t have time, so we have to move quickly.
 otherwise, we could be locked up in this hell forever.
”even before they came to their senses, the expedition team began to go back to the way they had come.
 they climbed up to victor’s cradle, opened the door, and headed to the halls of the guardian, but something was different in the hall of the guardians.
“uh? the lights in the capsules went out.
”as one of them said, the lights of the capsule devices lined up in the left and right corridors were all turned off.
 they could not know the exact reason, but the only thing that changed was the death of the ‘world eater’, the manager of this place.
‘is this what the world eater meant when he first said he was going to provide energy to keep the ark going?’perhaps they were the only players who survived in this ruined world.
 the world eater obviously struggled to save them.
“i just feel sad.
 those guys in the capsules are probably going to be dead, right?”although they were strangers that the expedition team had never met, they naturally felt sorry for their tragedy as the same humans.
“it is unavoidable.
 we can’t help them.
 above all, they lived by eating away at our lives.
 under the current system, we can’t coexist with them.
”at this point, sungwoo felt something ominous.
‘that means that another ordeal may be waiting for us even after this game is over.
 the world eater was also one of the puppets used by the system, after all…’sungwoo thought of the worst scenario where the end of this game was never within his reach.
 even if he saw the ending of this game, it could be used as a tool for another game when it was bound by the system.
 to put it simply, it could be used as a demon’s cave.
‘i can never make it happen.
’at that moment, one of the crew members in front shouted, “it’s right there! there is a passage near the ceiling!”a lattice was hung in the middle of the high ceiling.
 it was an opening through which they could go into the ceiling.
 sungwoo immediately summoned a bone wyvern.
“hanho, get on it!”with hanho behind him, sungwoo had the bone wyvern take off.
“we’re going to check the space over there and join you.
 so, go and prepare to escape, kyongsoo!”“okay.
”since all he had to do was check the opening, all of them didn’t have to accompany sungwoo.
 and they had to do it as soon as possible, so it was necessary for them to divide their work for efficiency.


when the bone wyvern approached the ceiling, hanho reached out and opened the door.
 sungwoo and hanho climbed into the ceiling.
 a long hallway unfolded.
“uh? isn’t this a sign of a trap that used to be here before?traces of something that melted down were evident on the left and right of the hallway.
“uh… it looks like melted jelly, but this smells disgusting.
”“does it look like jelly?”“i think the bear jelly melted.
”in sungwoo’s eyes, the torn flesh mixed with blood and pus looked like a carcass of an animal crushed by a truck.
‘this is that disgusting mouth that spewed flames.
’when the world eater’s power disappeared, all the living creatures related to him also perished.
 anyway, sungwoo and hanho went through the hallway without any hindrance and opened the huge iron door.
it was a dark room.
 but a bright light was steadily flowing out from the center of the darkness.
upon closer inspection, a single white fruit was floating in the square metal device and was emitting light.
“wow, it seems like a precious item, right?”

 