\section{chapter 356}

chapter 356: jeju island and attack on demon’s cave (20)jisu reached level 21 after killing two gatekeepers of the demon’s cave.





right after she was done with it, something landed behind her.
 it was heyon and gust.
“sister!”heyon was in charge of conveying jisu’s orders to the allied troops in the rear.
 she handed over her cell phone to jisu to tell her what was going on in the rear.
“you are now no.
 3 in the korean server rankings! congratulations!”the ranking page was displayed on her mobile phone screen.
 jimin opened her eyes wide at her words.
“third place? jisu, you are no.
 3?”although jimin already witnessed her overwhelming power, she was shocked again to find that her sister was the third-highest level among the entire korean server players.
“oh, i’ve just become the third.
”[kor server ranking (page 1)])kangsok han (lv.
 25)) kor-157 (lv.
 24)) kor-339 (lv.
 21)) youngdungpo prosecutor’s office (lv.
 20)) yoon choi (lv.
 18)finally, jisu climbed to 3rd place in the korean server rankings.
 of course, even when she was at a lower level than junghoon (kor-339), she was actually accepted as the next strongest player after kangsok han and the necromancer.
“by the way, given that sungwoo has also leveled up, it seems that he is fighting well in the demon’s cave.
”like inho said, sungwoo reached level 24.
“good for him!”they could confirm the life or death of their members by checking their server rankings like this.
 “as long as they could hold out well…”but at this point, inho couldn’t hide his worries.
 two gatekeepers of the demon’s cave came out during the second wave of monsters.
if so, how many more terrible monsters would come out in the future?
“now i’m worried about what kind of monsters will come out.
 i just wish they aren’t something bizarre,” inho said.
- the 3rd wave of monsters’ invasion’ of the gate of demon’s cave has begun.
as soon as inho finished his words, the wave started.
“they’re coming again!”since they had been overwhelmed by dire fear in the 2nd wave, the players of the world tree camp felt somewhat strange.
this time they were not as overwhelmed as they were before, but they were not in high morale, either.
“all we can do is just fight for our lives.
”“that’s a good idea.
”so they seemed rather calm this time.
kugugugugu-but it was not long before they began to feel restless again.
a horde of monsters began to pop out from the portal.
they immediately fired arrows and magic with the smoke arising.
“use all the firepower!”“don’t let them crawl out of the fire line!”the players intended to push the monsters away with the overwhelming firepower just like they did during the 1st wave.
“uh?”when they came to their senses, the demons scattered in all directions in the air.
kheeeeeee-the monsters soared into the sky with their huge wings spread out, which was quite unexpected.
“damn it! they’re in the air! shoot them down!”
blocking them in a two-dimensional space versus a three-dimensional space was quite different.
in other words, it was like the difference between blocking a stream in the ground and blocking smoke from spreading into the air.
pop! pop! pop! pop!the mighty firepower of the world tree camp, which had been concentrated on the ground, thinned out into the air helplessly.
 as a result, the accuracy of their attacks decreased, along with the drop in the damage to a single object.
 it meant that they lost the power of ‘resistance’ to push them away.
 in just ten seconds, dozens of monsters came out of the portal and scattered everywhere like birds that escaped from a cage.
“damn it, they are rushing toward us! shoot them down!”“it’s not easy to hit them!”they got out of the firing range, flew frantically over their heads, then charged at them wildly.
only then did the players realize that the monsters were trying to hunt them, not escape.
kheeeeeeeeee! kheeeeeeeeee!they got stuck to the shield of the airship and swung their gigantic claws.
 the players on the deck were terrified and tried to tear them off, but it wasn’t easy.
some of the monsters descended sharply towards the ground forces and raised their claws.
when they struck down with their sharp claws, which were several dozen centimeters long, dozens of players were ripped to pieces at once.
“deploy a large-scale shield!”fortunately, the priests were prepared for such an attack.
 they spread a shield over their heads, blocking the monsters’ first attack.
 but it was impossible for them to block the monsters forever.
crack! crack!“no way! how could such a massive shield be torn so easily?”their monstrous attack was beyond the players’ imagination.
 they deployed a large-scale shield by injecting a large amount of mana, but it seemed that the shield would not last even a few minutes.
“oh, my god! what should we do now?”“just fire anything right now!”their embarrassment made it impossible for them to rationally respond.
 although the world tree players were accustomed to big battles, they lost their fighting spirit at the monsters’ overwhelming offensive.
 as things stood now, it wouldn’t be surprising at all if they were instantly annihilated.
at that moment, somebody issued an order.
“charge towards the gate of the demon’s cave!”all of them could not believe their ears.
 how could they charge in this situation? did it mean this was their last-ditch effort?“just block the entrance to the portal, not attack them!”it was crusader commander junghoon who shouted at them.
holding the shield and sword, he ran towards the gate of the demon’s cave where the bombing was going on.
“charge!”about one hundred members of the crusader team followed him, shouting loudly.
the entire crusader team charged rather recklessly.
“uh?”kyungsoo understood their intentions at once.
 and he hurriedly issued an emergency order.
“stop shooting! concentrate the firepower on the air! stop all attacks on the ground near the gate!”he found a way to stop the enemy from spreading in the air.
‘yeah, we just need to block the portal on the ground before the monsters pop out and disperse into the sky.
’hundreds of monsters already jumped out and flew into the air, but if they blocked the monsters’ attack from the air, there was a chance that they could win.
‘although the firepower of cannons and wizards will be useless, blocking them physically will lead to fewer casualties on our side.
”so, kyungsoo immediately issued a follow-up order.
“priest troops, you must support the crusaders team! advance to the gate! don’t let them fall!”at his command, the priest troops began to advance, following the crusader team.
kyungsoo moved an airship and flew closely over the priests’ heads.
 he formed a kind of shield for them to block the attacks of the monsters as much as possible.
soon, the crusader team arrived at the gate.
 junghoon stuck the shield into the ground and raised his big bayonet.
“crusader team! get in line!”

at the same time, a white light flashed from his body.
 it seeped into the bodies of the crusaders, thickening the golden shield that had grown around their bodies.
“shield formation!”“shield formation!”they repeated his order here and there then blocked the gate of the demon’s cave in a semicircle.
at that moment, junghoon cut down a monster that was running towards him.
 even if he was not as strong as jisu, he was the fourth-strongest player on the korean server rankings.
“make sure no monsters come out of the gate!”“shoot them!”soon, the shooters of the crusader team lifted the muzzles of their cannons and fired a white beam of light.
qaaaaaaaaaaaaaaaaaaaaa!“aim for their wings!”the beam ripped the wings and skin of the monsters that came out of the portal.
kheeeeeeeeee!the monsters with torn wings could not fly properly and fell to the ground.
puck! puck! puck! puck!junghoon stabbed them hard with his sword.
 he had to hit them five or six times because of their vitality, but it was the most efficient hunting method for him.
“i got them!”“four monsters are popping out from the top right! ready to shoot!”not only junghoon but also his crusader team counterattacked the monsters quite successfully.
 the number of monsters flying out of their siege decreased significantly.
in other words, the crusaders were now blocking the total attack of the monsters that came out of the portal, which was quite tough for them.
“commander! our shield collapsed!”“khuuuuuk!”

 