\section{chapter 159}

                             




bone wyvern’s upper body was stuck in the middle of the road.
 those riding on it couldn’t keep their balance after hitting the ground.
“argh!”but there was no time for them to recover.
“they’re rushing us!” shouted jisu, staggering and standing from the pile of bones.
 she immediately took out the silver sword and watched her surroundings.
bark! bark!in no time, a herd of hell hounds poured out of the alley.
 they were black dogs with red eyes.
 instead of foam, they had red flames in their mouths, and black smoke was coming out of their nostrils.
jisoo swung her sword, stepping forward.
 with the energy of the sharp blade, she cut the lead hell hound.
kaaaaaaang!however, the sword only made a deep wound on the hell hound’s neck.
 the dog was charging at her like crazy.
tung! tung! tung! tung! tung!at that time, a barrage of arrows was fired from behind her and got stuck into the dog’s body randomly.
 the dog leaned forward and hit a burning street tree.
-you have earned 10,550 gold by hunting ‘hell hound’.
it was sungwoo’s repeating crossbow.
 although his newly added ‘ignition arrow’ was not active, its sound of firing was louder, showing it could inflict more damage than before.
 in other words, it was powerful enough to stop such a monster.
bark! bark!jisu and sungwoo killed only one dog.
 then two more dogs rushed at them from behind.
“let me take care of the dog on the left!” jisu said.
she was dealing with the dog.
 black smoke gathered on sungwoo’s right side, then death knight, minsok, appeared.
 he looked around and raised his sword.
“oh my god… i think we should be on alert all the time!”moving forward, she swung her sword at the dog’s ankles, the weakest spot.
 the hell hound’s forelimb was amputated and her body tilted to one side.
 at that moment, jisu disappeared.
puck!
jisu appeared in front of the hell hound and stabbed her sword into the dog’s neck.
“jisu, you have become much stronger.
 i have to fight harder!”minsok looked at her in admiration, then held out his left hand and unleashed the chains.
the moment the chains wrapped around the hell hound’s neck, he swung his shoulders to pull the dog’s neck, but the hell hound soared, and charged at him.
minsok cut its neck in the air.
tung! tung! tung! tung! tung!in the meantime, sungwoo fired the repeating crossbow at the hell hound running from behind.
 however, it was too much for him to deal with all the hell hounds charging from everywhere.
they closed in on him quickly.
“you have to escape quickly.
 soon, the giant will come.
”that’s why sungwoo didn’t summon more skeletons.
 there was no time for him to fight here any longer.
 the moment the fire giant came, everybody would be annihilated with the pile of burning concrete covering them.
‘i can’t waste my awakening time here.
’but sungwoo could not summon the grim reaper because the real fight would begin when he faced the “hell moving armor”.
 so, he had to save the available time of the grim reaper.
“the alley on the left is open!” jisu shouted.
firing the crossbow randomly, sungwoo nodded.
 she stepped forward and entered the alley, securing the path of retreat.
 minsok pulled hanho out of the pile of bones and held him on his shoulder.
 hanho had passed out due to the impact of the fall.
“come on, let’s go!”kuuuuuuuung-a little later, a tremendous vibration rang beyond the building on the right, and the entire sky turned orange.
 above the rooftop was the burning flames.
the ‘fire giant’ was approaching them.
 he was powerful enough to kill bone wyvern with one strike.
‘how can i kill the monster?’sungwoo would have to deal with that monster someday, but right now he needed to escape to a safe place and catch his breath.
bark! bark!
sungwoo and his party started to enter the alley on the left, holding back the herd of hell hounds.
 sungwoo turned around after firing the repeating crossbow.
thud-sungwoo summoned a “troll skeleton” to block the alley to separate the chasing hell hounds from them.
subordinate spirits like bone wyvern were difficult to obtain again, but sungwoo had to give them up at this moment and retreat.
“let’s get out of here while the skeleton is blocking them!”bark! bark!the hell hounds flocked into the narrow alley and collided with the troll skeleton.
 it seemed like the skeleton covered with bone armor could endure it for a while.
but the skeleton was engulfed in flames and crushed.
 four hell hounds opened their snouts at the same time and spewed out flames, melting the troll skeleton.
“we’re open to their attack!”the hell hound’s firepower was far more powerful than expected.
 sungwoo immediately summoned two more troll skeletons to delay their attack.
“run to the street!”they came out on the big road and started running.
“stop!” minsok shouted.
 there was a red marble floating in the air in front of them.
whoo-then, some sparks from somewhere flew around the object one by one, and the flames flowed in and condensed into one place.
 then, a huge flame tornado arose.
kugugugugugu-the fire giant fragmented himself to fly to them.
“man, that monster singled us out for attack!”minsok raised the sword and defended the forefront, but even though he was the powerful death knight, he couldn’t stop such a giant.
“we have to fight.
”it seemed that sungwoo had to change the plan to fight against the monster after escaping to a safe place first because if they were hesitant here, frightened, they might be killed even before confronting the ‘hell moving armor.
’“damn it! i have no choice but to summon the undead.
”sungwoo summoned the undead.
soon, troll skeletons and ghouls appeared and surrounded sungwoo and his party.
thump- thump-the fire giant, who regained his original figure and advanced along the boulevard.
chiiiiiiiiiwhen he moved, his feet burned the asphalt and generated toxic gas.
 then, his bulky body swayed without any certain shape and began to swallow the surrounding buildings.
“ahhhhhhhh!”“fire!”there was screaming inside a building.
“there are people inside there.
”that was an unexpected scene.
 it seemed that they were the players sungwoo and his party saw from the sky before the crash.
it seemed that they were hiding inside the building, but they were now in a dangerous situation because the fire giant came to this place to attack sungwoo’s party.
“if they are not helped, they will be burned to death.
”jisu did not hide the responsibility for that tragedy, but sungwoo and his party could not afford to save them now.
“dad! dad!”“guys, step back!”children’s screams erupted inside the building.
 sungwoo’s eyebrows wriggled.
this was something familiar to him.
a burning building, people screaming, and even him standing in front of them.
 this was something sungwoo had seen before.


the moment he hesitated to act in front of the flames and finally gave up was similar to the moment when his family died in the fire.
old memories rekindled his painful trauma.
since he was so weak-minded back then, he did not have the courage to jump into the flames to save his family, so he survived alone.
but now he was different.
“everyone, back off.
”now, he can jump into the fire to save them.
sungwoo put on the hood of the robe.
 then he held out his right hand.
there the grim reaper appeared.
-you have summoned the killing scythe, ‘grim reaper’.
-grim reaper retention time (00:59:59)“please guard behind me.
”green flames began to eat his body.
 pure white bones were revealed and his green eyes lit up.
-you have gained the power of ‘lich’.
* increases maximum subordinate spirits (+50).
* all stats increase (+10).
* you can revive and regenerate nearby destroyed undead ‘indefinitely as much as the maximum number of your subordinate spirits’.
“sungwoo, are you okay?”of course, sungwoo’s party trusted him, but the monster approaching them right now was quite different from the monsters they had seen before.
the fire giant was a whopping level 27 monster.
 so, everybody escaped without even trying to confront him.
“we have to check it out.
”jisu turned backward because a herd of hell hounds literally started pouring out from the alley on the right.
two-woong! two-woong!

 