\section{chapter 448}

it was the cliché of the hero and the demon king narrative that the world would be in danger if they couldn't defeat the demon king, but nobody knew that was actually the power of the demon king.





the world tree camp had to map out an operation urgently in an unexpected situation.
"commanders, gather around right now! we're going to have an emergency operation meeting!" sungwoo shouted.
 it was almost like sungwoo's unilateral command rather than a meeting.
he had no time to have an in-depth strategy meeting from the start.
 "the inside of the demon king's castle, that is, the labyrinth, must be a complex and rough dungeon.
 if our large army enters there, it is certain that we're going to suffer enormous sacrifices, not to mention huge difficulties.
 so, most of our troops should focus on the 'defense route'.
 got it?"sungwoo regarded the word 'labyrinth' as an important keyword in the quest message.
it would not be suitable for dispatching large-scale troops because it's difficult to get out once they went into the labyrinth.
"the forces in charge of the defense route should tightly surround the portal and build a fortress quickly.
 then pour all our firepower into it, so that not even a single outsider can enter the portal.
"according to sungwoo's direction, the commanders decided to dispatch almost all of the troops on the 'defense route' , so only their major players could enter the 'attack route'.
the best players in the world tree camp, such as sungwoo, jisu, hanho, junghoon, li wei, and other top players such as chen, kangyun, and ahnsok would enter the labyrinth to pull their weight.
 other than these top players, all of the 'special commando unit', and those in the thief and explorer occupation who could help clear traps or find the way in the labyrinth were also mobilized.
"alright! go to your assigned place right now!"so, except for about 320 attack route players, tens of thousands of defense route troops moved to the rear.
"necromancer! there is a red door over there.
 it seems to be the door of the labyrinth.
"they soon found the entrance to the labyrinth.
there was a red gate on one side of the black wall, which was the entrance to the labyrinth.
however, something unknown was making violent waves as if it was about to flow down at any moment, emitting heat like lava.

"sungwoo, can we enter it in that condition?" hanho asked.
when the attack route players gathered in front of the entrance, the gate opened with a bizarre sound.
follow current novels on lightnov­elworld.
c‌omgugugugugu-then black smoke was coming out of it.
 no one moved hastily.
who would dare go into the darkness inside the lava waterfall?"man, there is a saying that you have to go into a tiger den to catch a tiger, but i just feel creepy at that kind of tiger den.
 what's more, there is no tiger right there, right?" hanho asked in a bit of a frustrated voice.
 at that moment sungwoo stepped forward and said, "hanho, you forgot to mention one thing when you quoted that saying.
""excuse me? what did i forget? what was it?"sungwoo strode towards the door without any hesitation.
 "it's more effective to go into a tiger's den and hide when the tiger isn't there, then attack the tiger when it comes back than just waiting until the tiger comes back.
""oh, i guess you're right.
"hanho nodded as if he understood, and sungwoo walked into the red gate.
- you have entered the hidden stage 'demon king's castle (labyrinth)'.
* all players will be randomly placed in the 'gate'.
"what the heck?"at that moment sungwoo looked around.
 apparently, about three hundred people entered the labyrinth with him.
 but as soon as they entered the gate, hanho who was next to him disappeared.

grrrrrrr-only mir, who hanho was carrying in his arms, was squatting sadly on the ground.
 sungwoo turned his head and made eye contact with li wei, who was following him from behind.
 she was also very much embarrassed.
 "necromancer, our people around us have suddenly disappeared.
 you saw it, right? where have they gone?"sungwoo looked around slowly.
 right now there were only around 80 players left.
 then where did the other two hundred people suddenly disappear?"i think this labyrinth is making fun of us.
"follow new episodes on the lightnovelworld.
com platform.
as if to show its name was not useless, the labyrinth seemed to put in jeopardy those who set their feet here.
at that moment a red light began to glow in the darkness in front.
it was a flickering flame or a torch.
 the torches were lit one after another, revealing a gigantic hallway.
 the ceiling was so high and wide that it was not suitable for a human house.
 it was just the right size for a giant.
"there is a door at the end of the hallway!"as li wei said, there was a black stone gate at the end.
"there is a number written on it.
 it looks like number four.
"number 4? what does it mean?at that moment one of the special commando team approached sungwoo.
 "necromancer, we will contact another team.
"he was an operator in charge of communications, and he said that fortunately, the 'walkie-talkie item' was working normally.
crackle-after he exchanged several signs with the other party, the operator talked to somebody.
then he reported to sungwoo, "he said all of us entered the labyrinth, but it seemed that the moment we came in, they were dispersed in different directions.
 currently, there are three different places inside the labyrinth.
"they have confirmed that hanho and jeonghoon were separated from 121 players, while jisu and chen were separated from 109 players.
the problem was that isabella or the red dragon was in the place where jisu and chen were placed randomly.
 'it was good that i prepared several remote controls just in case,' sungwoo thought to himself.
 in fact, he made several remote controls for 'dragon keeper' that could control isabella and gave one of them to jisu.
'if i hadn't prepared for this kind of emergency.
.
.
'in the worst case, he could have lost jisu, not to mention isabella.
visit lightnov­elworld.
c‌om for a better experienceno matter how strong jisu was, she couldn't stop the red dragon alone.
 if she could escape from that place, she would be very lucky.
"let's move forward anyway," sungwoo said.
sungwoo's party formed a formation on the watch out for all directions, and slowly walked along the huge corridor lit by torches.
whooooooooo- whoooooooo-the torches were turned off whenever they passed by, followed by even deeper darkness behind them.
at that moment some indescribable bizarre sound was heard from somewhere.
 

"look at that.
"one of them whispered.
the gray walls on both sides were filled with engraved murals.
 it was impossible what they meant, but the scenes of bizarre monsters hunting and eating humans were everywhere.
 the most terrible and scariest thing was that the monsters' eyeballs were following them when they moved deep inside.
"is that gargoyle?"all kinds of stone statues were intertwined on the ceiling, reminiscent of stalactites in a limestone cave.
 so it could be gargoyle, a stone monster guarding this old castle, but it didn't move at all until they reached the door at the end of the hallway.
squeeeeeeeek-when sungwoo put his hand on the stone door, the door opened with a squeaking sound.
"is it an amphitheater?"its interior was in the shape of the colosseum.
 sungwoo suddenly felt ominous.
 it was not there for nothing, of course.
 "watch out when you enter!"they dispersed to the left and right before entering it, then gathered in one place in the stadium.
as soon as they entered, a faint light began to light up in the center of the stadium.
"heh heh heh!"new novel chapters are published on lightnovelworld.
c­omat that moment, an eerie sound of laughter rang out from somewhere, and the stage shone even brighter.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 