\section{chapter 284}






 in fact, kangsok didn’t move at all.
 all he did was shoot a beam of light from his cane.
“uh…”at that moment, the tsar shook his head, feeling dizzy as if the whole world was twisting.
but he still didn’t give up.
“haha…” the tsar raised himself with a feigned laugh.
 while he was at it, he was still looking for a way to kill kangsok, which showed his hunter’s instinct.
‘anyway, he is a wizard-type.
 his damage is enormous, but i can kill him with one stroke.
 let me block his attack by changing into a turtle shape and attack him.
’but before he put together his arms, another flash occurred.
his body bounced like a ball, pushed the truck, and rolled on the concrete floor randomly.
 his head broke and blood gushed.
 and his left knee was folded upside down.
the tsar’s plan failed.
“hey, you are not only incompetent but also stupid.
 if you’re so stupid, you won’t live long.
”kangsok held out his cane.
 it was the first time he moved since the battle broke.
then, a spark erupted from the tip of his cane, and hundreds of thin rays of light poured out and wrapped the tsar’s body.
the tsar’s body soared as if being attracted by a magnet.
 a terrifying electric current began to strike every corner of his body.
“ahhhhhhhhhh!”kangsok walked slowly, swinging the cane.
 when he took each step forward, it seemed to increase the intensity of the current.
“i think your game is over.
’
but at that moment, the tsar broke through the electric current, reached out his hand, and picked something from his pocket.
 it was a familiar object in sungwoo’s eyes.
‘that’s an angel’s wing piece.
’it was an item that could teleport its user to the ‘angel’s statue’ within a certain range, which sungwoo once used during the raid in taiwan.
the tsar used it to escape in an instant.
“uh?”kangsok stopped the attack and pulled the cane back.
 he frowned and stared into the air.
the tsar disappeared in an instant.
the butterfly soared and opened her eyes.
“no! did you miss him?”“i guess so.
 looks like the portal just opened.
 i never expected he could move his arm when he was shocked.
”“of course! you should have killed him quickly!”“well, he wasn’t the one who could stand in the way of my plans anyway.
”“that’s just an excuse!”the butterfly kept whining and punching and kicking his shoulders.
as if he didn’t care, kangsok turned casually and looked at sungwoo.
“necromancer, it’s been a long time! i didn’t know we would meet here like this.
”his eyes turned to jisu.
 more precisely, he was looking at mir in her arms.

“world tree, and now a dragon? you are overflowing with item blessings.
 what i’ve got is this noisy butterfly.
”“what the heck? what did you say now?”“by the way, what brought you here?” asked sungwoo.
kangsok just scratched his cheek, then said, “actually, i didn’t know you were here.
 i just have the ability to sense the power of hell.
 i came because of the quest i had been proceeding with.
”“devil king?”“ah, did you hear it?” said kangsok, smiling bitterly.
 “it’s a childish and funny name, right? just think of it as a hidden deity.
”“so, you’re chasing the gate of hell after clearing the quest and becoming the devil king?”kangsok nodded slightly and said, “that’s right.
 it’s a long quest, but now i’m starting to get sick and tired of it, so i want to stop it.
”“gosh, you’re so weak!” said the butterfly.
given the implication of ‘devil king,’ kangsok’s ambition to become the king was like proclaiming that he would become a heinous being.
 sungwoo’s name, the necromancer, was also often described as an evil being.
therefore, the most important thing was his ‘intention’.
 in other words, it was important to find out what kangsok would want to do after becoming the devil king.
“it may be a strange question, but what good is it for you when you become the devil king? aren’t hell monsters invading the earth? can you stop them?”“have you heard about the world eater?”he mentioned a familiar name.
“oh, that giant eye! that’s so disgusting!”“butterfly, just get out of here, please.
”sungwoo nodded slowly at his question.
“then i don’t need to explain it in detail.
 if we don’t do anything, our earth will be ruined by them, and if you are complacent, you are going to be ruled by the angel or demon camp.
 anyway, they are basically invaders with a different name.
 then, what should we do?”sungwoo immediately replied, “well we need to build an independent power, so we can’t rely on either camp.
”kangsok nodded with a smile and said, “yeah, i think you are doing very well in that regard.
 in my view, the one who can survive alone in the end wins.
 that’s what i’m doing now.
”he suddenly praised sungwoo, but sungwoo was confused whether he should think of kangsok as his ally.
at that moment, the butterfly flew, then put her palm on her forehead and looked somewhere.
“kangsok! again! again! look southeast!”“damn quest, it won’t give me any break! it looks like the door to hell has been opened somewhere,” he said with a sigh as if he was tired.
“i wish we could talk in a more relaxed mood later.
 but can we ever have such a chance?”“if you can survive, sure we will.
”“okay.
 please don’t die.
”having said that, kangsok disappeared to the portal opened by the butterfly.
hanho, who was watching them from behind, said with a sign, sighed “wow, what the hell has happened? i’m so confused… i only remember the buzzing noise of the butterfly.
”sungwoo agreed with that.
at that moment, minhum standing behind him said, “sungwoo, please take care of our men here.
 let me go and check whether the crusader team members are alive.
”sungwoo and his party could not afford to take a break just because the tsar was gone.
***

when the tsar fled alone, the siberian hunters surrendered without any resistance.
 no matter how tough they were, they did not try to resist to the end in a faraway country.
tatana, the annoying freezing wizard, died in battle.
 as a result, the curse that froze the entire crusader team disappeared.
the news spread through the wide area surveillance team that junghoon and the crusader team were awakened finally.
“what a relief!”but that wasn’t the end.
“by the way, our commander says he wants to talk with you urgently.
”sungwoo instinctively sensed that it might not be good news.
 about ten minutes later, a helicopter landed.
 junghoon, who was exhausted, got off the helicopter.
 he seemed as if he would collapse anytime soon, barely managing to stand, supported by minhum.
“sungwoo, you helped me like this, i’m sorry to give you more bad news…”“just tell me without any worries.
”junghoon nodded his head, then took his breath and continued, “yesterday, i broke the statue of the angel.
”it was something unexpected.
 the liberation guild has belonged to the angel camp for quite a long time.
 they were the core supporters of the angel camp on the korean server.
“we were cursed when i broke it.
”“what’s the curse?”“eleven hours from now, an angel will come to yeongdeungpo station.
 and i hear the angel will punish the whole of seoul.
 the absolute race people will come down.
”these guys who had been trying to dominate the korean server for a long time using all kinds of tactics finally decided to act on their own.
seeing junghoon’s anxious expression, sungwoo calmly nodded and said, “does the angel have any bones?”if kangsok conquered hell and tried to become the devil king, it meant he could conquer the place where the angel race lived.


 