\section{chapter 192}

                             




“oh, this crossbow is very good.
 i can fire three shots in a row with this.
”“this shield also ranks higher than what we use.
 i needed to strengthen the tanker line, so this is a good item.
”they selected decent items and handed out the items to the village security guards.
 they could now upgrade the combat power to defend the village.
“if our security guard keeps getting stronger like this, someday we can be stronger than the crusader team, right?” inho asked.
“well, i think that’s possible when i analyze it,” replied kyongsu.
of course, they were greatly elated with the recent victory.
although some intruders attacked the village while sungwoo was away, the village players not only defeated them but also captured them alive.
“by the way, how could you capture them instead of expelling them?”sungwoo could not believe that they captured the intruders alive.
“well…”inho began to explain, “in the past, sungwoo, you told us all we had to do was just believe in the invisible barrier, so we just patrolled around the barrier regularly.
”inho was in charge of the village’s security operation.
 he made eight patrol teams of 48 members and had them monitor and patrol around the invisible barrier closely.
“i think it was around 4:13 pm when we noticed the intruders breaking through the invisible barrier.
”“at that moment, one of the team leaders, kim, made a good judgment,” kyongsu added.
inho nodded, then continued, “that’s right.
 however, given their item level, kim judged them to be much stronger than us, so he did not engage in fighting them recklessly and reported to me immediately.
”if the battle broke out right after they broke the barrier, they had no choice but to risk several friendly casualties even if they could block the intruders.
furthermore, the patrol team needed to identify the intruders, but it would not be easy for them to capture the intruders in a fierce fight.
“so, we intentionally drew them into a trap.
”as soon as he received the report, inho prepared a trap.
“by mobilizing all the security guards, i had them block all the alleys around the invisible barrier with an “electric fence” where the intruders were drilling holes.

the ‘electric fence’ was an item used by the vampire lord when he detained people in a plaza at the time of the massacre.
 this item has been kept by the village players.
inho said after they blocked the intruders completely, they waited in hiding on the roof until all of the infiltrators snuck in.
“finally, they came in, and the invisible barrier was automatically restored, blocking their retreat.
 at that moment i fired the iron mace of lightning in mt.
 paldal at them… bang!’and the iron mace directly hit the infiltrators, inflicting heavy damage.
“we could kill half of them.
 besides, our snipers and wizards appeared on the rooftop when they finally had no choice but to surrender.
”inho shrugged because he felt proud of his operation.
 it was truly amazing that he used the strategy to defeat such a stronger opponent than his men without any casualties.
“great job! thank you,” sungwoo praised him, recognizing his brilliant strategy.
“well, a soldier who fails to carry out his security duty cannot be forgiven, as you agree.
”“by the way, where are the prisoners?”inho pointed to the museum building, “oh, right now, i’ve detained them in two warehouses inside the museum, but if they intrude often, i think we will have to build a separate prison.
”“okay.
 let me visit them in the evening.
”there was something he wanted to check out first before interrogating the prisoners.
he needed to check the reward of the “faction quest”.
[skill information]-name: the third camp’s vault (temporary)-grade: basic-category: active-consumption: a certain amount of gold-effect: opens the ‘inventory’, where you can store and share items in a subspace.
 if you have permission, you can use it anytime, anywhere.
 when you store one, 100,000 gold is consumed.
 (number limit: 10)* registered users with permission: 1
[item information]-name: flag of the third camp (temporary)-grade: special-category: faction item-effect: when installing a flag, buffs are given to the players of the third camp within a certain area (1km).
 (all stats +1) this buff will be strengthened or reduced according to the ‘power of the faction’.
although sungwoo had not yet formed the third camp, it seemed that both rewards were given as a ‘temporary’ grade.
‘but this is also different from a normal skill.
’the current skill focused on massive utilities and buffs.
 if they belonged to a specific camp or faction, they could receive special benefits they could not obtain as a sole player.
‘of course, this is far less than the rewards offered by the absolute race.
”the angel camp was generous enough to give those players who attacked sungwoo the buffs that significantly increased all of their stats.
 since it would take so long for sungwoo’s camp members to catch up with them, it was not easy for them to fight against the angel camp players.
‘that is why they needed to make a much more robust organization.
 instead of relying on the faction buffs, they need to form a strong organization by themselves…’of course, sungwoo had one thing he could rely on.
 he turned his head and looked at the world tree growing in the square.
-the world tree (2nd stage of growth) is growing.
 (15%)he was not sure how much benefit he would receive from the world tree when it fully grew, but it was certain that it would give him a huge advantage over other hostile forces.
***sungwoo sat face to face with the leader of the intruders.
 he introduced himself as a “team leader” of an organization called “hunter company.
”“hunter company?”“have you never heard of it? our company is pretty famous these days.
”he was overly talkative as if he was full of confidence and pride.
but sungwoo had no intention of quietly listening to his gibberish.
“really? well, this is going to be the end of your company’s heyday then.
”sungwoo’s threat was indeed dreadful because he clearly said he would end the hunter company.
 the guy’s eyes trembled.
“it was for business purposes that we attacked here.
 i don’t hold any grudge against you.
 it was my mistake, a fatal mistake.
”“but you want me to forgive you, right? well, i do hold a grudge against you, so i won’t make such a mistake.
”“…”honestly, no matter how that guy tried to make excuses, he could not justify his action.
 so, the more he talked, the more shallow his excuses were.
“what i mean is…”the team leader dropped his head as if he realized once again he was so scared of even making eye contact with the necromancer.
“well, i’m only a field commander, so i can’t tell you about this complicated… and you will soon see our negotiator coming here when our boss finds out my team members have been captured alive here.
 our company has even this kind of negotiating mechanism.
”negotiator? the necromancer scoffed at that expression.
“mechanism? so, your company is protecting employees? they are only ridiculous incompetents.
”“…”indeed, as he said, a negotiator they dispatched arrived 12 hours later.
inho’s patrol team captured two people waiting near the invisible barrier.
they were an old man and woman, who were wearing suits unsuitable for this era.
the man wearing a blue tie stepped forward and said, “necromancer, it is an honor to meet you.
 my name is ky, the 2nd negotiation team leader of hunter company.
 it seems like we have caused you a big inconvenience.
 i apologize on behalf of our company.
”as if they thought they were businessmen, they showed shameless kindness.
“is it the evolution society?” sungwoo asked blatantly.
he guessed the evolution society was responsible for this intrusion, so he wanted to put out the feeler directly.
but they said calmly, keeping a poker face, “pardon? what did you say? we are from the hunter company.
”

“no, i’m talking about the guys who hired you.
”“hahaha, necromancer, shall we talk about it later? i have a lot to tell you.
”but sungwoo shook his head coldly.
“i don’t have time.
 while you are trying to buy time like this, your leaders must rack their brains to run away.
 right?”“no, i don’t think so.
”“if they don’t, they are pretty stupid.
 how can they deal with me?”ky had no choice but to smile bitterly.
sungwoo suddenly lifted his index finger and started tapping his temple.
“let me tell you one thing.
 i can extract memories from your corpses.
 so, i’m going to kill you and find out your lair.
 let me start in 10 minutes.
”ky’s expression gradually darkened at his calm voice.
 he knew the necromancer was serious.
ky opened his dry lips.
“what do you want? we are here to negotiate with you, necromancer.
 we’re ready to pay the price for our wrong choice.
”sungwoo smiled softly and said, “as i said earlier, i can extract your memories.
 so, i don’t want to talk with you anymore.
”“…”“so, if you don’t want me to kill you, you have to do something more valuable than that, right? i mean something more valuable than what’s in your head.
”more valuable?ky glanced at the necromancer’s mouth while swallowing.
sungwoo slowly opened his mouth.
“find the main stronghold of the evolution society and let me know.
”sungwoo intended to resolve the old headache on the korean peninsula.


 