\section{chapter 246}

                            it was jisu who was walking toward them.
 she looked around once and complained to sungwoo in an annoyed voice, “i wish you had sent me a message if you were in a situation like this…”




“oh, i thought you couldn’t come in because the door was locked.
”since sungwoo was blocked by the divine magic, jisu broke it with her might as if it was not as strong as the chain that trapped durahan.
this was an unexpected situation for dr.
 yu, but he did not lose his composure.
“oh, i see another good body here.
 let me put you at the forefront of all the dolls over there!”having said that, he moved first.
 the shooter puppets on the crane in the middle pulled their bowstrings.
shish-shhhh!“attack!”while arrows were raining down on him, sungwoo lifted his bone shield and moved his army forward.
 hundreds of troops advanced.
“jisu, some of them fire silver arrows! be careful about them!”there was only one way for jisu to nullify the silver arrows.
 she had to notice them and bounce them back.
“sure, let me pay close attention!”rattle! rattle!the giant monsters charged fiercely at dr.
 yu’s army with troll skeletons as the main force.
after narrowing their distance as much as possible, the trolls began to pull their slingshots.
tu-woong! tu-woong!heavy bullets were fired at the dolls controlled by dr.
 yu, but when the priests in the back folded their hands together, all the cranes were covered with protective shields.
goong! gugooooooooong!the slingshot bullets missed the targets.

“damn it! after all, the priests are the problem!”while striking back the arrows, minsok used the new magic that he mastered.
 black arrows were fired from his shield and thrown towards the priests.
 it was an attack that would lay a powerful curse when the target was hit.
“please hit them!”however, the black arrows couldn’t even fly halfway across the distance before being blocked in the air.
“damn it!”as minsok complained, the 50 priests in the rear were too powerful.
 their average level was high.
 besides, since they, divided into several groups and took turns in casting spells one by one, sungwoo’s allies could not seize the moment to counter-attack them.
that wasn’t all.
“sungwoo! watch out for the 2 o’clock direction!”the crane in the 2 o’clock position with the wizards on it moved quickly and bounced forward.
 above the wizards’ heads, there was a “sand clock” sign.
 a whopping 20 of them were working together to prepare a massive magical attack.
two cranes made up of warriors were deployed around it, blocking the access of the bone wyverns.
 eventually, their magic was completed.
“avoid it!” jisu shouted.
quaguagua!an enormous column of fire fell and swept over the ground once.
 dozens of undead quickly turned into ashes.
the wizard crane slowly slipped back to the rear after its attack was completed.
it was as if sungwoo’s allies were dealing with a giant buddha statue with dozens of arms.
‘we have no choice but to suffer their attack as things stand now.
’because the crane was floating at a fairly high above ground, sungwoo’s troops on the ground could not cope with their attack efficiently.
even though ghouls and giant monkey skeletons climbed up the outer wall towards the crane, they fell helplessly whenever the fire magic was cast toward them.

‘we can’t even approach the crane.
’furthermore, the group of bone wyverns could not get close to the crane because of the intensive shooting of the snipers.
 sometimes some of them managed to push into them a little more, but while they were tearing off the protective shields over the crane, they were beaten and fell helplessly.
they were resurrected countless times, but they were faced with the same situation over and over again.
‘i need something a little tougher.
’sungwoo moved bone imoogi.
googoogoo!bone imoogi had better defense power than bone wyverns, so if he raised his body and hit the crane, he could break through the shield before his body was smashed.
‘when the bone imoogi attacks the crane, let me use his body as a staircase, so i can send the ground troops up the crane.
’sungwoo’s plan was feasible.
 if the shield over the crane was smashed, it would not be difficult for only a few undead to mount the crane and smash it easily.
but there was another problem.
“this time they’re attacking from the 11 o’clock position!” jisu shouted.
another wizard crane moved.
 it was large-scale freezing magic, and its target was bone imoogi.
 a blizzard was blowing toward his head.
bone imoogi got frozen immediately and stopped moving.
 subsequently, lightning magic was cast one after another, and bone imoogi, which lost its defense power, was shattered.
 its fragments rained down on the undead army, causing secondary damage.
‘this guy is ahead of me in attacking strategy.
’dr.
 yu was grasping every situation while looking down from the ceiling.
quaguaguagua!once again, massive flame magic was cast.
 as a result, more than half of the active undead were crushed.
“their firepower is too strong! we can’t approach them!”their attack was very organized and intense in terms of their firepower and defense power.
if they kept attacking sungwoo’s focus like this, one hour would quickly pass even without them counter-attacking properly.
as if he was completely confident, dr.
 yu lowered the crane to the ground, on which his warriors were hanging.
wheeeee―then, the warrior players with only upper bodies threw their spears.
 at the same time, the crane moved and swept past the undead army like a combine.
“damn it! they have to run out of mana! if we keep confronting them until they use up their mana, we can seize the moment to attack them, right?” minsok said.
when he suggested a reasonable idea, jisu found something.
“you can’t do it.
 they are supplied with mana potions through the hose!”players’ brains and spines had all sorts of wires, one of which was a rubber tube.
 whenever they ran out of mana, a mana potion was forcibly administered through the tube.
the thing was even before their mana potion ran out, sungwoo’s skill cooldown would be back.
jisu shouted, “watch out for the silver arrows!”but it was already too late.
 it was too far for her to strike them back.
even though it was a small-sized arrowhead, it split the head of a bone wyvern in half.
 his body was shattered to pieces and could never be resurrected.
without wasting silver arrows, dr.
 yu was killing sungwoo’s army one by one, aiming for the decisive chance to attack him.
 as time went on, sungwoo’s forces began to show their weakness.
‘we can’t defeat dr.
 yu’s forces with a full attack.
 let me think about some other tactics.
”sungwoo stepped back and thought about the battlefield.
 he had no chance of winning if his army attacked them recklessly as they had done until now.
‘there is a key player who has been controlling all their movement.
’their strategy relied on inducing their movement by delivering some electrical stimulus to those players, based on dr.
 yu’s instruction.
that meant there was a connection device that linked dr.
 yu and the key players.


‘if dr.
 yu is a brain surrounded by that solid divine magic, then there must be a heart, an engine that moves this weird mechanical device.
’the innermost wall came into his eyes while sungwoo was looking around carefully.
 there was something like an exhaust vent, which periodically emitted black smoke.
the engine in question was most likely there behind the wall.
‘what if i can turn off the engine?’all mechanical devices would stop automatically.
sungwoo sent his subordinate spirit specters there.
 they broke through the wall and allowed sungwoo to see beyond the wall.
‘as expected it’s the engine room.
’six mechanical devices were running in six separate rooms.
 they were the power source that moved the cranes and the players.
‘how can i break them?’the wall between the cavity and the engine room was too thick.
 even if sungwoo sent the evil spirit bomb, he could not destroy the wall.
besides, there was no light in the engine room, but there were six exhaust vents emitting black smoke.
‘but we can’t go in there.
’each of the vents was so small.
 an adult male could never pass through any of them.
 it was designed like that for safety.
“maybe a child can get through it…”while muttering like that, sungwoo looked down on the side all of a sudden.
rattle- rattle-most of sungwoo’s subordinate spirits were huge, but there was only one that was very small.
“wow! it was good i saved you for this occasion!”the time had come for the goblin skeleton of the undead army to play a decisive role.


 