\section{chapter 279}






 sungwoo twisted the trajectory of the arrows with the telekinesis of the ghosts.
 since the arrows were so fast, he could not control them as he wanted to, but he twisted them in an instant.
puck!eventually, an arrow hit a hunter’s thigh.
“ugh! damn it! i was hit! it’s so hot! argh!”his pain doubled because of the firing effect of the arrow.
 the ice wizard standing next to him quickly dropped the heat temperature by using ice magic on his thigh.
“hahaha! stupid alexey was hit by an arrow for the first time! it’s that bastard’s turn to wash the dishes tomorrow!”however, they could not afford to be complacent that long because ten arrows moved randomly and flew toward them from unexpected directions.
“argh!”“damn it! that bastard is using a weird trick again!”“watch out, shooters! there is something like a ghost!”when they were distracted by something else like this, it was natural that they could not focus on their main target.
in the meantime, the undead monsters frozen in pieces began to recombine one by one.
and that wasn’t the end.
“what the heck? what is that over there?”“watch out for the sky!”massive objects were pouring down from the air.
 at that moment, tatana raised her hand and made a giant ice umbrella.
 all of the hunters went under that protection of the umbrella.
quaguaguagua―dozens of spears were stuck into the umbrella.
 it was the attack by fire arrow rocket.
 sungwoo already installed the fire arrow rocket system on the nearby roof using the ‘inventory’ function.
“good! we blocked everything!”“tatana, you are awesome!”but their cheers didn’t last long.
bang! bang! bang!dozens of arrows exploded and shattered the ice umbrella, scattering its debris over the heads of the hunters like hail.

“ahhhhhhhh!”“damn, i’m so confused!”the hunters slowly lost their composure.
 then, they plunged into chaos.
“master! i’m here! rattle!”an unfamiliar voice was heard behind the hunters.
 standing there was skeleton lich, as expected.
 following lich were thousands of zombies.
ooh! ooh!“what the heck are all these zombies?”“crazy, what the hell are they doing here? it’s more hellish than siberia!”“wake up! if you wake up, you can survive! don’t forget we won’t die easily because we are supported by the power of the wild!”since sungwoo could not bring all the zombies near the dmz here, he canceled summoning them, then gathered all the corpses of the monsters on the korean server.
 it took him quite a bit of time to do that, but they arrived before it was too late.
“what the hell is our scout nikolai doing anyway? he didn’t even tip us off in advance!”“nikolai! respond! nikolai!”nikolai, who was in charge of spying on the enemies, had been killed already.
jisu wasn’t just taking care of mir.
 she was searching and killing spies like nikolai.
“they’re zombies! wipe them out!”“fire!”bang! bang!more than ten zombies were killed after being hit by just one cannon.
 but no matter how strong their firepower was, they could not block the massive onslaught of the incoming zombies.
“get ready for the clash!”“start a hand-to-hand fight!”eventually, both sides engaged in a scuffle.
‘alright, it’s my turn.
’relying on the specters’ eyes, sungwoo looked down on the battlefield from the air.
 and he placed his subordinate spirits in the right place on the battlefield.

he dispatched the bone salamander he had obtained from pyongyang to confront tatana, the most annoying opponent.
although the power inherent in the bone salamander came out in the form of a “fire spirit stone (higher grade)”, he was still exhaling intense heat.
“damn it! go away!”the freezing magic that tatana cast was scattered into the air in vain.
“get away!”stepping back, she kept casting the freezing spell randomly.
 of course, as the freezing magic continued to overlap, the salamander’s body began to get more and more frost, but she could not do anything else because of him for some time.
meanwhile, sungwoo assigned minsok and durahan the task of killing the brown bear who was destroying the undead army with overwhelming power.
thump- thump- thump- thump!riding on bone drake, durahan rammed into the brown bear.
 bone drake was a little bigger than the brown bear, but the brown bear was stronger than the drake.
kaaaaaaaaaaah!the brown bear grabbed bone drake’s chin with his relatively free paws and struck him to the ground.
 bone drake’s lower jaw was cracked open.
“is that all of your skill?”however, the real striker was minsok.
 he jumped off after stepping on bone drake and stabbed the ‘ruler’s sword’ into the brown bear’s neck.
puck!the sword, which became much stronger after its name was changed, tore the bear’s tough fur and inflicted a fatal injury on him.
in addition, minsok showed his talent as a “death wizard” and cast a curse that made the brown bear’s wounds fester.
doo doo doo doo-subsequently, a horde of zombies dispersed when the headless knight, durahan, charged at the brown bear along with the rough clattering of hoofs.
choo-ooh!durahan passed by the brown bear at tremendous speed, leaving a long stab on his side.
then, he then turned around, frantically moving around the brown bear, continuing to increase the cuts.
in the meantime, minsok struck him down with the sword while standing on his head.
puck! puck! puck!minsok and durahan kept attacking the brown bear ruthlessly, stabbing and cutting all over his body.
this huge bear could not endure their continued attack and slowly collapsed.
thud!-you have earned 4,500,000 gold by hunting the ancient druid’s subordinate spirit (ancient giant bear stage 11)’.
as soon as the huge bear fell, sungwoo resurrected him as a skeleton.
 with his skin and flesh removed, the giant bear as tall as a three-story building slowly raised his head.
“damn it! mr.
 big was struck!”“run away, everybody!”watching them, sujngwoo felt greatly satisfied.
‘finally, i got them.
’he obtained the huge bear’s bones.
meanwhile, hanho was also engaged in the scuffle, too, but he didn’t do anything.
 more precisely, he could not find the chance to attack because numerous zombies were confronting the 21 siberian hunters.
“aho!”he often threw daggers from behind then sat on the bench as if he was out of breath.
“hey, little boy!”someone came to see him in person.
“uh?”one hunter, who was 2 meters 10 centimeters tall, approached him through a horde of zombies, wielding a battle-ax.
“pardon?”hanho quickly stood from his seat in embarrassment.
then, he got upset after recalling he was called a little boy.
“what the heck? little boy? did you call me a little boy…”“yeah, i did.
 i can’t tell big from small as far as asians are concerned.
 anyway, adults and kids are all small, right? you are dead meat!”the moment he finished saying that, he swung at hanho’s head with a battle-ax.
but hanho lifted his dagger to block it.


clang! clang!his opponent was mighty.
 hanho barely blocked his attack by raising all four arms of asura cloak.
 he moved one of the six daggers that blocked the ax and aimed for the hunter’s neck.
 however, the hunter easily avoided it by bending back.
“oh, you know how to attack, little boy!”huffing and puffing, hanho corrected his posture.
“shut up, fatty!”“what? hahaha! little boy, you’re so cute! what’s your name? i am vladimir.
”hanho stopped at that moment then laughed.
“vladimir?”“yeah.
”“are you sure?”for some reason, hanho’s mouth twitched in spite of himself as if he was about to burst into laughter.
“yep, my name is vladimir!”“hahaha! oh, how funny!”eventually, he burst into hearty laughter.
“hahaha! vladimir! vladimir! hahaha!”vladimir frowned at his unexpected scornful laughter.
 then, he lifted the battle-ax.
“what the heck? why are you laughing at me like that, you idiot?”hanho stopped laughing, then sneered at him.
“because my hamster’s name was vladimir.
 hahaha! then, you have the same name as my hamster, right? hahaha! you are such a big guy with the same name as my hamster, right? hahaha!”vladimir’s face turned red with anger.
“what did you say? what the hell are you talking about! this crazy bastard! who is your hamster? if i smash your head, you can’t talk nonsense.
”then, he charged at hanho, pretty offended by hanho’s mention that his name was the same as his pet.
“let me smash your head!”

 