\section{chapter 454}

sungwoo narrowed the distance with gansok by using winter predator.
 then he jumped at gangsok and used twilight raid at the same time.





- 'twilight raid' begins.
wooooooooooo-sungwoo's body assimilated with the black smoke, then merged into a whirlwind to attack gangsok.
 since he was never prepared for this kind of surprise attack, gangsok could not avoid it in time.
 "kheeeeeek"sungwoo's whirlwind snatched his body from the air.
but gangsok wrapped his body with electric current, which was the skill that helped him block all the attacks by the undead and ghosts in the underworld.
'this is what i expected.
'sungwoo felt the extreme pain as if his body was being torn apart, but gangsok didn't stop there.
 - you have activated the 'boiling armor' of red dragon armor.
a tornado of red flames erupted around his body that was already covered with black smoke.
kuguuuuuuuuuuu!black smoke, blue lightning, and red flames intertwined with each other, creating a bizarre and beautiful trajectory.
 the trajectory drew a long curve and fell down the wall.
the two, entangled together, crashed into the amazon's muddy rainforest.
 electric current and fire were inflicting terrible damage and pain on each other, but they could not let go of their hands grabbing each other.
woooooooooo-the dead man's hands protruded from the ground and tried to bind gangsok's body, but the electric current filled with divine power pushed it away.
"if you want to turn into the demon king, you should see real blood.
 let me help you bleed now!" sungwoo shouted.
".
.
.
"at that moment gangsok's necklace shone.
in an instant, a huge wave broke out, bouncing off sungwoo.
 he was thrown away straight and hit the wall.

"argh…"the impact of hitting the wall shook his whole body.
 he had tinnitus in his ears, feeling dizzy.
follow new episodes on the lightnov‌elworld.
c‌om platform.
"what the heck is that?"it was an item.
 since both sides hid their valuable items from each other, the items could be the deciding factor in shaping the outcome of their fight.
"necromancer, you must have prepared a lot.
"gangsok got up from the mud.
"yeah, that's right.
"sungwoo also stood on his feet, enduring the impact.
"how dare you give me this kind of surprise party in my territory? stop it right now!" gangsok shouted.
"ah, but it's too early for you to be surprised yet.
 the party isn't over yet.
 it's only the beginning.
"at that moment, the darkness on the ground on which gangsok was standing shook.
 it was a shadowkoooooooooooo-giga's wide shadow rose from the ground.
 sungwoo even raised giga's shadow with the 'power of the shadow king'.
 the first thing that moved was a large hand.
"kheeeeeeeek!"gangsok could not avoid the hand that rose from the ground without any notice.
then sungwoo charged at gangsok who was caught in gigas's hand.
 but gangsok's necklace once again radiated light and caused a wave, which separated him from gigas' hand and escape in an instant.
 sungwoo changed direction at that moment, avoiding the wave, then threw something at the same time.

puck!a sharp weapon the size of one's palm was stuck into gangsok's shoulder.
".
.
.
"of course, it wasn't fatal.
 "that's my party present for you.
"if the sharp object was 'basilisk tooth', it would be a different story.
updated from lightnov‌elworld.
c‌om"the snake's venom hardens blood.
"gangsok pulled out basilisk's teeth from his shoulder.
 a black liquid oozed from the wounds.
 it was poison.
"alright.
 before your blood hardens, let me draw your blood quickly and draw a magic circle on the ground.
"the fight became less exciting because the demon king was now struggling to deal with sungwoo.
those who moved on by relying on their previous experiences would find themselves trapped in a new situation they had never experienced at all.
'how the hell did all this happen?'gangsok, who had already experienced this hellish game many times, was now in the same situation.
 he realized that this subtle emotion he was feeling was none other than embarrassment, which he really felt after a long time.
'he came up with a series of unexpected cards.
 this guy is totally different from other players that i have dealt with until now.
"simply put, it was a 'variable'.
variables kept coming out, finally creating a completely new situation that he could not properly deal with.
"kheeeeeeeeeeeek!"gangsok raised his head, but he could not see the sky because his place was blocked by four high walls.
 more precisely, they were not walls, but giants who were as tall as a building.
 they were two tall giants and their shadows.
gangsok didn't even know their names.
 their heads were leaning gently in the gray smoke, looking down at him.
 he felt as if he was forcibly dragged to the heavenly court of justice by the angry gods.
and the necromancer stood at the point where their heads met in the air.
 "necromancer, i honestly didn't expect that you were so strong like this.
 i admit you won me.
 this is a situation that i've never experienced while destroying multiple worlds.
 but…"even before sungwoo finished speaking, something struck gangsok's body like a lightning bolt.
puck!it pierced his chest.
"khuuuuuuuk!"it was a red spear or the red dragon spear.
 he suffered damage and pain, which was totally different from basilisk's teeth.
"breath field!"sungwoo used his skill straight away, so gangsok could not even have time to speak.
in other words, sungwoo clearly suggested that he would allow any moment when gangsok could turn the tide of the battle.
follow new episodes on the lightnovelworld.
com platform.
- caution! a 'breath field' has been formed in the area.
when one of the skills of 'dragon lord-red', breath field, was activated, the air around the window heated up and started to change into a magma zone.
 it was as if the heat penetrated into his maimed body and ate away at his whole body.
cheeeeeeeeee!his flesh burned and his bones melted.
finally, gangsok screamed in pain.
 it was a purely painful scream.
it's been a while since he screamed in pain instinctively.
when he was done screaming, something was heard in his mind.
- you are dead.
ironically, cold reason began to come back in his fragile mind.
 

'well, this isn't the first time something like this has happened.
'a single goal came to his mind, and he was not strong enough to achieve it.
'i have to blend into their society.
 if i destroy this world, they will accept me.
 yeah, they're not that different from us, so they'll want toys like me.
.
.
'light came back and his vision was back.
 a message appeared in front of him, indicating the inflection point of this scenario.
- you have been resurrected as 'demon king', nourished by your body's death.
but sungwoo dealt a fatal blow to him without giving him any moment of counterattack.
 - you earned 28,000 gold by killing a player.
"is it over?"even though he attacked the demon king, fully prepared over time, the fight was over more easily than he expected.
 'no, no.
 something is strange.
'sungwoo thought something was strange.
 he could not believe gangsok could fall so easily like this, even if his operation worked out smoothly.
as expected, the fight was not over yet.
 "no way.
 it's not over yet.
"follow new episodes on the lightnovelworld.
com platform.
well, it's not over.
"gangsok's body began to swell.
 it wasn't over yet.
"cough!" you can also read this novel on the more advanced platform lightnovelspot.
com

 