\section{chapter 459}

he opened the four muzzles and fired at once without any failure, which paulo could not avoid.
 after he was showered with the bullets, paulo fell backward.





"damn it! i just can't believe i am hit by a stupid guy like you!""ugh? you must be mistaken a lot.
 i'm smarter than you in one area.
"hanho's 3rd arm on the left and 3rd arm on the right wiggled his index finger.
"two more arms.
 but what's the use of having eight arms? you might throw eight punches, but that's it.
 that's why you can't beat me! i'm…"hanho stopped talking, then rubbed the tip of his nose with the index finger of his left third arm.
 somehow it looked like he was imitating somebody in a japanese boy's manga.
 "i'm versatile!"he was right.
after all, he was versatile in almost anything.
***"man, when can he ever die?"reporter ahn swallowed and wiped the sweat with trembling hands.
only then could he continue, "to be honest, i have no idea.
 this is already the second time he has been revived!"woooooo-four portals opened in the red sky of the demon king's castle.
- caution! a 'gate of hell' will open in the area.
- caution! a 'gate of hell' will open in the area.
- caution! a 'gate of hell' will open in the area.

- caution! a 'gate of hell' will open in the area.
red energy was flowing from there, then flowing towards the hole where the demon king was buried.
"what does the flow of energy from that portal mean? what is certain is that something bad is about to happen soon.
"actually, something was going on.
 this place, namely, the area around the demon king's castle was the territory of the demon king, so one of the demon king's inherent powers was in effect.
as if the flow of energy reached a certain critical point, an earthquake occurred, causing cracks in the earth.
reporter ahn shouted, "ahhh! it looks like something is going on underground!"at that moment the same message was displayed to all players throughout the world.
[disaster quest]- name: advent of the great demon king- type: optional- target: unknown- reward: unknown*someone made the demon king angry, so the real demon king has decided to reveal himself in this world.
 since the king can't control his anger, he will devastate the world.
 you can make a choice that will determine the fate of your life.
 if you pledge 'oath of allegiance' to the demon king, you will be able to live under his rule.
* whenever the demon king's followers (those who pledge an oath of allegiance) exceed a certain level, some of the followers' power will be absorbed by the demon king.
 (enhance his power.
)"ah…"reporter ahn let out a sigh.
 then he shook his head, looking at the brief message that followed.

- would you like to make an oath of allegiance to the demon king? (y/n)ahn said, "once again, here is a message that will divide the players and make them succumb to the creature that is driving the world to destruction.
"he clicked 'n' without any hesitation.
"now i can be sure this is too obvious.
 it would be foolish if you obeyed the demon king out of fear.
 it's like you are becoming pro-japanese just because you are scared about their guns," reporter ahn said, raising his voice.
 "folks, we are strong people who have survived this hell.
 i hope you can make the right choice.
"the players around the world have begun to make an important choice like a representative of justice.
***meanwhile, a completely different message appeared before sungwoo's eyes.
- when you meet special conditions, you can obtain the 'warrior's privilege'.
"what the heck is this?"warrior's privilege?come to think of it, the cliché of the 'demon king' was supposed to be accompanied by a partner called the 'warrior.
' in other words, a warrior was like the representative of justice as well as an adversary against the demon king's aggression.
'if that's the case, it means that i can obtain some capabilities that will help me fight the demon king.
'in fact, the warrior could function only when the demon king was active.
 so he appeared belatedly when the demon king threatened the world.
'by the way, what are these conditions?'kugugugu.
.
.
meanwhile, the ground split in half, and something slowly began to rise.
the land was split apart and shook violently.
red energy flowed out of the cleaves.
 the demon king was ready to move beneath it.
"prepare for the shock!"the players in the rear began to be busy preparing for the demon king's attack.
the airships lined up and aimed loaded cannons at the king.
"open the hypergate! soon our reinforcements will arrive! shit!"but it was difficult for the troops on the ground to even move smoothly.
the entire amazon shook violently as if it was turned upside down, and the ancient trees that had been taking root for decades were broken like canes suddenly.
"watch out!""be careful! trees are falling!"since tens of thousands of players were gathered in a dense formation, they were tangled up in great confusion while they were moving around.
fortunately, only the airships and the troops floating in the air could maintain an orderly formation, but even they were struggling because of the strong winds.
it wasn't just the red energy that was flowing out of the four portals.
 a gust of wind occurred, probably because of the huge pressure difference between the two spaces.
kugugugugugugu-"make the space between the airships as wide as possible! have hippogriffs land right now!"overwhelmed by the terrifying scene, even the hippogriffs did not dare to fly in the air.
 they were clinging to the temporary nest in the stern of the airships.
 the troops waiting on the deck also hurriedly took refuge in the airships.


"what the hell is coming out of that portal?"the world seen from the control room of the airship, which was relatively safe from the outside shock, was bizarrely twisted and distorted.
 it looked as if four holes were opened in the sky over the amazon that was waving and swaying like the ocean, and a red stream of water was overflowing from them.
"i don't know what it is, but something far worse than anything i've seen so far is about to happen.
"demon king.
 he was the ruler of hell.
 because of that, he could make everything that lived in his territory his subordinate spirits.
sungwoo looked up at the red sky.
 the four portals in the sky, and the unidentified energy flowing from them were a kind of 'essence' in which everything in hell was sublimated.
'now he is absorbing all of that essence in hell.
'that energy was flowing into the ground, which was being supplied to the body of the demon king who had been buried underground after he melted.
as if he wanted to recover after getting an iv, the demon king sucked up the essence of hell itself and tried to move again.
wooooooooooooo-but the problem was nobody could stop him.
 they had to prepare for the next fight against him.
 'alright.
 he will finally reveal himself!'the demon king was once the same human as other players, but eventually, he surrendered to the system and lost his humanity.
wooooooooooooooo-with the sky over the amazon spreading red, something began to happen.
bang!

 