\section{chapter 219}

                             




“a troll with six arms…what a unique taste! how come this guy was hiding something like this in this closet?”after sungwoo’s troops killed the boss monster, he found a treasure trove in a hidden space.
it was the size of a general auditorium, and there were a lot of various items piled up.
the most striking thing of them was a large-sized wagon located in the middle of them.
[item information]-name: singijon (fire arrow rocket)-grade: legend-category: weapon-effect: when mana is injected, it fires 40 projectiles at the same time and causes an explosion at the striking point.
 (fires once every 5 minutes)* ‘required mana’ varies depending on the user’s skill level.
“singijon…”of course, it was not the replica of the old korean-style fire arrow rocket.
 but it was made of a harder material than wood, and the design was somewhat more refined.
 and it contained magical power.
“i think we obtained something useful with the war around the corner.
”currently, the flying weapons that the world tree camp possessed were the two iron maces of lightning they captured from the evolution society and the ballista they manufactured.
they knew the strength of the flying weapons well because they had already used the weapons several times, but they were not easy to manufacture because of their huge size and weight.
“wow! 40 shots at a time and explosions at that? sungwoo, this is a jackpot!”now, they obtained a much more effective flying weapon.
 it seemed that they could use it on a large-scale battlefield.
“but, it’s quite heavy, so i think it’s difficult to carry this weapon.
”inho slightly pushed it, then shook his head.
 although it had wheels, it seemed that anybody using it would use all his might to push it uphill in a narrow crypt.

moreover, it was a problem to move it to the village.
 it would be easiest to transport it by air using the bone wyvern, but fixing it tightly, so that it wouldn’t fall was a big concern.
sungwoo came up with a different method.
“well, i’ve got something useful for things like this.
”-‘world tree camp’s vault’ has been activated.
it was the “camp skill” he received after winning the battle in taiwan.
[subspace vault (world tree camp)]* registered users with permission to use: 4-gold consumption per one: 100,000 gold-items in storage: 0to put it simply, it was an ‘inventory’.
 it was a system where all items could be stored and retrieved in a different space regardless of their size.
-would you like to keep the ‘singijon (fire arrow rocket)’ item?* basic cost (100,000 gold) + additional cost for a large item(50,000 gold) = 150,000 gold is consumed.
“keep it there.
”as soon as sungwoo said that, the huge object in front of them disappeared in an instant.
“wow!”“this is a jackpot! come to think of it, i wish we could have one each.
”“come on, let’s check other items as well.
”all sorts of items were piled up like a mountain inside the troll’s vault.
 it seemed that it would take a considerable time to check all the items.
“uh? what the heck is this? is it the staff used by the troll wizard?”
hanho, who was wandering around, found an incredibly long wooden staff.
inho, who was next to him, looked closely at it and opened his mouth.
“isn’t it like a pole?”“pole? what is that?”“you know that old korean totem pole.
 they used to hang something like a bird at the top of the pole.
”[item information]-name: lucky pole-class: hero-category: totem-effect: all productivity and production technology in the nearby area (5km) where the pole has been installed increase (+10%) also, all success chances increase.
 (+10%)“haha, our production players will be quite happy about this pole!”players in the living and production fields were growing fast every day, so the addition of this pole seemed to give them additional buffs.
after checking other items, sungwoo and his party also found several ‘rare’ grade items, so they could further upgrade their equipment level.
besides, they also found all kinds of material items and other items in large quantities, commonly referred to as ‘miscellaneous items.
’“i can’t check them one by one now, but if we examine them closely later, i think we can find lots of useful items.
”“good.
 let’s go back to our base first.
”players from the world tree camp returned to the village after collecting all the items in the dungeon.
although it was a long hard and tough day, they significantly leveled up and obtained a huge amount of gold and a lot of other items.
***the ‘lucky pole’ was installed at the entrance of the plaza where the world tree was standing.
 when it was installed upright on the ground, its effect was shown.
-the effect of the ‘lucky pole’ has been applied to the entire area.
* all productivity and production skills improve.
 (+10%)* all chances of success increase.
 (+10%)the buffs granted by the world tree were also being applied.
-‘abundance of the godly tree’ has been granted to the whole area.
* item production success rate increases.
 (+50%)* increases the probability of additional options when making items.
 (+10%)* item production cost decreases.
 (-10%)as a result, those players in the fields of daily life and production felt a marked increase in work efficiency.
“hey, i can peel off the leather easily when i just touch it with my hand! i feel like i’m opening a zipper.
”the tanners were now able to peel the leather so easily they could not complain about a pain in their wrists, and the blacksmiths’ hammering was much stronger than before.
“man, even if i put in roughly anything and boil the water, i can get the buffs.
 just amazing!”cooks could also give players the buff effect more easily and powerfully, apart from the taste of the food.
the buffs of the lucky pole affected not only the players but also the natural environment of the designated area.
“since we installed the lucky pole, the amount of medicinal herbs in mt.
 paldal seems to have increased.
”“it looks like those players working in the potion room will be busier.
 there are not many players there.
”herbs grown in paldalsan were widely used in various fields such as potions and food.
and if they mixed the medicinal herbs with ‘troll’s blood’, which was recently brought in large quantities, they could make high-grade health recovery potions.


on the other hand, they renovated a nearby shopping mall into something like a ‘hangar’.
they decided to store and manage large weapons such as the ballista and singijon.
kyongsu even planned on where to place the singijon and ballista in the upcoming war.
“as i expect the number of flying weapons in the future, i’m thinking of growing archery forces specialized in managing and operating large equipment.
”kyungsoo was in charge of managing the internal affairs of the village.
 recently, three more players joined to help him with his administrative work.
they had a separate office and were working under the name of the “ministry of general affairs.
” they were in charge of managing the gold deposited in the “vault of oath” and human resources.
“good.
 let’s rest for the next 12 hours then start the massive attack of the dungeon of the next difficulty level.
 please provide good food for the players who trained hard,” said sungwoo.
“sure.
 during the break, let me have the ‘surveillance team’ in full operation because this is the time when our security is at a low point.
”currently, the “surveillance team”, which was created temporarily, was closely monitoring the surroundings of the invisible barrier using jeongho’s new skill “eye of the air”.
with his new skill, he could monitor the invisible barrier with the naked eye like cctv.
 including jeongho, three others were scrutinizing different directions.
while the world tree camp was operating fully like this, somebody was watching their every movement from a distance.
“check the target!”one guy, who very secretly followed and watched sungwoo and the players of the world tree camp going into the dungeon and taking out all the items, stopped walking outside the invisible barrier.
“i’m sure he is our target.
 i’ve noticed a huge tree of unknown identity, a tree exuding a powerful force somewhere.
”on a rooftop where they can see the world tree, a man wearing a black mask came out from the shadow.
“and now they seem to be taking a break.
”he jumped at once to the building on the other side, then naturally disappeared into another shadow.
in an empty space, only a very small voice mumbled like the sound of the wind.
“it seems we can kill the target at the right time when he comes out of the invisible barrier.
 let me keep monitoring him until he comes out.
”

 