\section{chapter 293}






 “hey, johnny, johnny, come to your senses, man! wake up!”under the flickering lights, jonathan cage opened his eyes slowly.
 his vision was blurred.
he struggled to trace his memory.
 what happened? what happened to the airship, messenger, and the crew?“oh, johnny, how come you look so miserable as the hero of central park? you look like a doberman who has just come out of neutering surgery.
”“hey, parker…”jonathan recognized the man named parker in the blurry vision.
 he was a brown-haired, white man and first mate.
 robin parker used to be jonathan’s direct subordinate right before the airship crashed.
he gave johanhan a solemn salute.
“right, captain! haha, we have finally come to communicate with each other,” robin said.
there was a lot of ridicule in his tone.
“did you betray me? why?”jonathan was the head of the 1st external affairs team wpu as well as the captain of the messenger.
 as a level 19 rock-type wizard, he was quite a strong man.
however, he had no choice but to be helplessly exposed to the sudden attack of his betrayers.
“betrayal? well, you can talk about betrayal only on the assumption we were in the same boat, but we never shared our hearts with you from the beginning.
”chuckling at him, parker tapped jonathan on the cheek.

“so, this is an operation.
 we’ve carried it out so well that even james bond would envy us.
”having said that, parker stood, “okay, to sum up, i don’t know what chairman love is thinking about, but it seems he is trying to get along with the master of this small land, but admiral baker disagrees with him.
 he seems to be interested in decorating an oriental garden these days.
 so…”“no way! are you now aiming for the world tree?”“oh, bingo.
”the reason jonathan came here with the airship messenger was that some people disagreed he wanted to build a friendly relationship with the necromancer by contacting him.
in fact, chairman love, the head of the wpu organization, greatly appreciated the worth of the hero of this asian land.
 he repeatedly said that the necromancer did not fall under the control of the absolute race like they had and that he even confronted the absolute race, so he would be the key player in the reconstruction of the world.
however, there were also people who disagreed with the chairman within the wpu.
 they were hardliners led by admiral william baker.
“paker, is admiral baker trying to cause a useless sacrifice again this time? are you indulging in that ridiculous heroism, too?”“johnny! this is not heroism, man.
 you also saw that terrible world tree, didn’t you?”“…”“hope you don’t think the world tree is just an ordinary shade tree.
 it’s like a weapon of mass destruction buried somewhere in the desert in the middle east.
 if you squat in front of that and recite the quran, it will surely fly up, destroying washington d.
c.
 like a lego block,” parker said as if appealing to him with his arms wide open.
 “hey friend, we’ve always blocked the upcoming disasters at the risk of ourselves.
 and this is part of such efforts.
”all the players from the us military under admiral baker still believed that the u.
s.
 had to take the lead in solving all the problems.
 therefore, they regarded the alien power as a “potential threat” that would harm the us-centered world order and boldly eliminated them.
jonathan shook his head and said, “parker, that’s not true…”but parker rejected him and said, “and the crash of the messenger will be a catalyst.
”
he continued with a proud expression, “you and the messenger will be known to have been brutally slaughtered by the exclusive asian terrorist, and admiral baker will be supported by the provisional congress.
 then, the dwarfs will send us a fleet.
”jonathan shook his head again because he imagined the scene of the wpu’s dwarf fleet crossing the pacific ocean and bombing the world tree.
and that wasn’t the absolute path for peace.
“please think carefully…”“uh?”at that moment, parker’s eyes turned to the ceiling.
 he frowned and gazed at the corners of the flickering lights, where two vague objects were floating.
“what is that?”it was obviously a ghost.
 parker didn’t know why the ghost was here.
bang!suddenly, an explosion broke out above his head.
 with a roar tearing his eardrum, he squatted down helplessly.
jonathan, a rock-type wizard, cast magic on the falling concrete even though he was trapped, forming a round dome shape to protect his and parker’s heads.
 if not, both of them would have been fatally injured.
“cough! cough! what the heck is this?”parker climbed out of the dome and raised his head to check the situation.
faint light and an unidentified black smoke penetrated through the rubble.
parker instinctively covered his mouth and nose.
“damn it! check the inside!”“sailor! are you okay?”he heard his subordinates shouting at him nearby.
 fortunately, not all of them were not buried.
right at that moment, the debris blocking the concrete above their heads was lifted and light poured in.
“oh, my god…”parker doubted my eyes.
a giant hand made of bones was lifting a handful of debris.
 as if he felt like an ant in a burrowed anthill, parker crouched.
“we’ve found them!”an unfamiliar voice rang above his head, and soon someone jumped down.
he was an asian man wearing a dark green robe.
 a few more people came down after him.
even if he didn’t confirm them, parker immediately realized that they were the players of the world tree camp.
 if that was the case, it meant that the famous necromancer also came here.
“how did you know we were here?” parker asked.
but no one answered.
“uh, jonathan? you are jonathan, right?”

it was kyongsu’s voice.
 he recognized jonathan right away, the leader of the 1st external affairs team, whom he had met several times.
 given that jonathan was tied up in chains, kyongsu could grasp the situation to some extent.
“he’s that man over there!” said the white werewolf, who was standing at the back.
he lifted his long finger and pointed at parker.
“that white man took the initiative in slaughtering the sailors on the ship.
”he succeeded in reading the memories contained in the corpses and objects through his ‘psychometry’ ability and chased them in this place.
“what the heck? how could you say that so confidently?” parker asked.
parker panicked, but he did not lose his composure.
 since he served in the military as a us navy sergeant for a long time, he was sort of immune to this kind of dangerous situation.
“hey, i don’t know why you guys stormed into my place so roughly, but i thought fbi agents chased me here! as intellectuals, we can talk with each other nicely, can’t we?”parker stepped forward, pretending to be calm.
 then, he faced the necromancer, sungwoo.
“…”park said nothing.
 the situation was clearly unfavorable to him.
 he and his men were only a small number here, and this place was far from their home base.
however, he knew that if he lost a war of nerves with the enemy, his value as a prisoner of war would go down, so he didn’t try to be subservient to the necromancer.
“now, look here.
 you know this guy, jonathan cage.
 he went to meet you on our behalf, right?”shrugging proudly, parker stepped closer.
“you know what? there was a rebellion led by this guy, jonathan.
 it’s hard for me to explain this because it’s a complicated family feud, but we were interrogating him to find out what the plan was after subduing their revolt.
”

 