\section{chapter 402}

when they checked closely, they discovered that it was the hands of a puppeteer that controlled the golden threads.
 




five or six of the golden threads were shot towards the guardian statue on the wall, then tied tightly.
 then, something started happening.
light shone in the eyes of the guardian statue, and stones fell from between its joints.
the next moment the statue raised its head.
 then, it got off the pedestal and stepped his right foot over the wall.
thud-the statue began to be controlled by the emperor.
 since the guardian statue was also a kind of earthenware doll, it had no choice but to be controlled by the emperor.
 as a result, the 'existence of wonder' buff effect ended.
 on the contrary, the buffs were applied to the enemies.
this was obviously a devastating setback for the allied troops.
"no way.
.
.
i can't believe this!"the forces guarding the statue were stunned, unable to respond at all.
their embarrassment made them vulnerable to the enemy's relentless attack.
 dozens of them turned into stones.
and there was a man floating between the two golden hands controlling the statue.
 "is he the emperor?"if the guy was responsible for controlling the terracotta, he must be the emperor.
 however, when the necromancer attacked the emperor, even he turned out to be terracotta, not the real man.
so they couldn't believe what they saw.
"i hear that the emperor that sungwoo killed was fake.
 we can't believe he's the real emperor!" junghoon said.
 jisu also nodded, seeing eye to eye with him.

"whatever it is, we have to get rid of him because he is causing great harm to us!"then she drew the sword.
"let me go and kill him!"she stepped on the rampart and jumped into the air to cut off the puppeteer's rope.
***wong was all smiles as if he was satisfied with what's going on.
 as he argued, the emperor's army was overwhelming.
of course, the necromancer was also a formidable force, so the tide of the battle changed several times, but once again the emperor and the chinese army were gaining the upper hand in the fight.
 as a result, everybody watching the official channel felt that the occupation of the rampart was a matter of time.
"oh my .
.
.
it looks like the fight is finally over in the emperor's favor…"the moment wong said that while fidgeting with a ballpoint pen, reporter ahn sprang to his feet and shouted, "valkyrie has started to confront the emperor!"valkyrie climbed up the rampart and charged at the emperor.
 the emperor spun dozens of golden threads to stop her.
 it was a spectacular one-on-one clash.
reporter ahn shouted in excitement, "is he the real emperor? the necromancer ambushed him recently, but he was a fake, so this time he might be…"but wong resolutely shook her head and said, "well, i don't think so.
 didn't everyone see that the emperor's camouflage tactic worked well? at this point, there was no reason for the emperor to reveal himself at all.
 he is not stupid.
 he is playing, seeing several moves ahead.
"wong continued as if to sneer at reporter ahn, "valkyrie is wasting her breath now like the necromancer.
 maybe she has already been caught in a trap.
 i'm sorry to tell you this, but we might see valkyrie's fall here.
"valkyrie was trying hard to get closer to the emperor while avoiding the attack of the threads extending from the giant golden hands.
a breathtaking fight between them unfolded.
 if she made the slightest wrong move, she would be ripped apart immediately.
 on the other hand, the guardian statue being manipulated by the puppeteer was even more threatening than they imagined.

dozens of people turned into stones whenever the puppeteer, standing tall on the highest point of the rampart, shot a beam of petrification towards the inside of the rampart.
 "'well, we suffer too much damage each time the statue fires the beam!"in particular, since the space above the rampart was flat with no obstacles, it was impossible for the defending forces to avoid the beam, so they were exposed to it helplessly.
"i think i know how tricky that puppeteer's weapon is when we confront it like this…"at that moment, three airships sailed forward and bombarded the statue.
 since they could not recover it, they decided to destroy it.
however, the stone raised a huge shield to stop the bombardment.
fragments of stones fell from various parts of the statue due to the impact of the bombardment, but that's it.
 the statue was largely intact.
"oh my god, it really looks so sturdy that i don't know how they made it.
"hearst and his blacksmiths made it so strong that their excellence was rather a stumbling block for the allies.
"get out of the way!"then, a shout was heard from somewhere.
 those on the rampart dispersed to the left and right.
.
.
a spear flew through them like lightning and got stuck in the statue's chest.
 puck!then one of the shields that made up the scale armor fell off.
"we have to tear the item off to stop that statue!"it was crusader commander junghoon.
then, he picked up the shield and ran to the statue.
the statue turned towards him.
 'aegis' flashed.
 he could not avoid it.
at that moment, some light radiated from his hand.
 he also grew much stronger while obtaining more powerful skills than before.
 the two lights collided with each other.
paaaaaaah-then, the petrification light faded with its effect disappearing, so he could penetrate it frontally.
 it was an attack skill that nobody expected.
 it was similar to a wave that could block the wave of light.
"okay, we've got only one minute left now!"after throwing the shield, he pulled the sword from behind and grabbed it.
thud-a huge foot fell towards his head, but he rolled on the ground to avoid it, then stood up and jumped to the ground at the same time.
 then he grabbed the other party's knee with one hand and bounced back once more, reaching his waist.
 the guy shook his body violently, but he held out by holding the guy tightly.
then junghoon bounced off once more and soared into the air.
 almost immediately he swung the sword toward the chest of the statue.
clang-it seemed like a fatal blow, but it ended up taking off only one single scale of the shield that made up the statue's armor.
"alright! done!"however, if the item was an aegis, the shield that fired petrified rays, it was a different story.
as a matter of fact, junghoo succeeded in disarming the most important weapon of the statue.
he gripped the statue's shoulder and climbed to the top using its right ear as a handle, finally grabbing its helmet.


"hey, calm down now!"junghoon stood behind the head of the statue and grabbed the sword with both hands.
 then he struck it down with all his might.
with the sword stuck in its head, he activated the unique function of the crossbow.
when the arrow surfaced at the crossbow, he pulled it, and repeatedly at that.
two-woong! two-woong! two-woong!a beam of light glided through the blade and slid into its head.
 a white light emanated from its mouth and neck.
 then cracks began to spread over its huge body, then it collapsed vertically.
kugugugugu-junghoon safely landed on the pile of debris.
"alright, i can defend the rampart…"he got up, brushing off the fragments of stone on his shoulders.
 compared to the necromancer and the valkyrie, he was a faded hero, but his attack showed that he was still a very strong fighter.
rattle- rattle-at that moment two giants appeared in front of him.
 "uh?"

 