\section{chapter 410}

minsok shouted, looking back at durahan.
 "just run and give it to sungwoo!"




at his direction, durahan moved the monster horse.
 that gigantic monster jumped the floor and galloped at full speed.
- durahan uses the exclusive skill 'deadly run'.
'wandering knights' appeared on durahan's left and right.
 his furious charge broke through the heroic terracottas.
after trampling on the two terracottas guarding the front of the chest, duran put the saddle on his head and leaned down to grab the chest.
 then durahan's body was sucked into it.
"haaah!" minsok exclaimed with joy because it was a success.
"hope it's not too late,"minsok grabbed the sword tightly, then stared at hsiang yu.
"alright, let me fight it out with you from now on!"the tide of the war changed drastically in an instant.
the terracotta army, who were attacking the rampart, suddenly showed an abnormal reaction.
 they turned their heads all of a sudden, then stopped.
"uh? they seemed to have stopped attacking!"because of that, the troops on both sides also stopped the fighting because they felt something bizarre.
"what's going on?"the terracottas that charged at sungwoo's army like a swarm of crazy bugs suddenly stopped attacking like toys that ran out of batteries.
"no way…"the players put down their weapons and looked around.
 obviously, something happened.
at that moment there was a cry from somewhere.
"necromancer! he defeated the main force of the emperor!"someone who watched the scenes of the necromancer infiltrating the 'tomb of emperor quin shi' reported through the broadcast of the official channel.
"wow, as expected, the necromancer has made it!"
"yeah, i knew he would do it!"no matter how unfavorable the war situation was, they had a good reason not to give up.
they strongly believed that as long as they held out until the end, the necromancer would defeat the enemy and win the war at the end of the day.
new novel chapters are published on lightnovelworld.
c­omand their conviction in the ultimate victory of the necromancer proved right, as always.
they began to cheer for joy beyond the rampart, while the chinese army began to whisper with nervousness.
at that moment somebody shouted, "the fight is not over yet! don't let down your guard!"the terracottas that stood still on their spots began to move again.
they turned back their heads and looked up at the rampart.
 it was a bad sign.
"shit! pour shells again!"they resumed the attack against the terracottas.
 but there was one very big change.
"look over there! the terracottas in the rear are leaving somewhere!"a huge number of terracottas, which never decreased, began to divide into two groups.
one of their groups continued the offensive towards the rampart, while the other group was leaving to block the necromancer who was somewhere in the rear.
"we've got to stop them!"li wei didn't watch the broadcast, but she noticed that the necromancer aimed at the emperor's heart accurately.
"spread a barrier!"li wei built a huge water barrier to block the movement of the terracotta forces.
then, she dropped water bombs over the heads of the approaching terracottas.
"we can't let them pass here!"
meanwhile, a fierce fight was going on even on top of the rampart to stop the terracottas' retreat.
"jisu, one of the golden hands disappeared!" hanho shouted.
he got on the back of hyunmu's incarnation and jumped towards the rampart.
"i think he ran away somewhere!"having heard that, she looked at the oppressor's hand that she was fighting.
she thought of using a rather extreme method to behead that fake emperor by all means.
 however, sungwoo completely changed the war tactics.
'the situation has changed.
'if the situation changed, she would have to change the enemy target accordingly.
new novel chapters are published on lightnov­elworld.
comshe checked her senses to figure out what it was.
chijijijiji-like buddha's hands, the shining golden light was thinning out.
'it's disappearing.
 as expected, sungwoo succeeded in launching a surprise attack.
 that shows the hand is moving towards sungwoo.
'this meant that the situation was so dire that the emperor had to take back the most important weapon.
'if that's the case, i have to stop it somehow!'jisoo looked at hanho and shouted, "we have to stop that.
 help me.
"hanho opened his eyes wide at her words.
"wow, i'm surprised to hear you asking for my help! it's my first time hearing it.
 i'm so thrilled…""can't you be thrilled later?""oops! of course!"she jumped off the rampart and soared in the air again.
 she has already done it hundreds of times.
chuchuchuchuchuchu-once again the golden threads came out.
 but something green approached her from behind.
 "hey! i've got one! let me help you!" hanho shouted at her.
it was the 'incarnation of hyunmu' controlled by hanho.
that huge divine beast swung his tail, the snake's head, and struck the oppressor's hand.
tung!with the sound of heavy crashing, the oppressor's hand was twisted, which made hundreds of threads fly in the wrong direction.
 jisu threw herself through them.
'okay, i can avoid them this time!'she twisted his body extremely to avoid several threads.
'i can break through them!'finally, she got close to the oppressor's hand.
 she swung the sword that she tucked behind her.
she cut the oppressor's hand and soared into the sky.
 and the fake emperor, who sat on the back of the hands, looked down on her.
'he's the fake emperor.
 but he has a powerful weapon.
'the source of this content is lightnovelworld.
c­omshe could not let such a weapon be taken by the emperor.
 she had to destroy it here because it would help sungwoo.
she charged at the fake emperor's neck.
 the fake emperor also raised the weapon and confronted her.
clang! clang! clang!they clashed three times on the back of the oppressor's hand.
 she took a step back.
at that moment she felt the threads flying toward her from behind.
 a total of 13 threads were flying toward her, which she could not avoid.
 there was only one way she could counterattack now.
'let me launch a frontal attack!'

she threw herself toward the fake emperor, then wielded the sword very quickly.
clang! clang! clang! clang!she clashed against him five times, but the last clash made a strange noise, which was the sound of something breaking.
 the fake emperor's right wrist was torn apart, then thrown away.
but at that moment she felt something strange.
'gosh, he deceived me!'she hurriedly threw herself and escaped into the air on the right.
 but it was late.
something came out of the fake emperor's severed forearm and wrapped around her body.
 it was a trap.
- you have been bound by 'gleipnir'.
"argh!"a green string tied her body tightly.
 it was transparent and tough, like a fishing line.
she fell from the back of the oppressor's hands and twisted her body in the air.
"ugh! i can untie it!"no wonder she cried out like that because it was gleipnir.
 in the mythology of northern europe, gleipnir was the snare that tied the giant wolf fenrir, so she could not break it loose easily.
"sis jisu, don't worry!" hanho shouted.
the incarnation of hyunmu jumped, using the rampart as a stepping stone, and charged at the oppressor's hands.
"hey! i can attack you, too!"the snake's head wrapped around the thumb of the oppressor's hand.
 since it was in tatters because of many cuts, it was easy to grab it.
 then the turtle's head snapped its middle finger and hung on it tightly, then twisted it toward the ground.
bang!new novel chapters are published on lightnovelworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 