\section{chapter 213}

                             




inho came and said, “sungwoo, we have placed additional security guards in the area.
 they will immediately detect anyone approaching the invisible barrier.
 we also have warmed up the iron mace of lightning, so we can fire them as soon as we notice something strange.
”“good job!”“and the entire village is ready for the battle, fully armed.
”sungwoo nodded and went out of the building.
a huge tree was casting a shadow in the square.
-the world tree (2nd stage of growth) is growing.
 (83%)it had grown to a height of about 24 meters, about 8 stories high.
 the world tree could be easily noticed in nearby areas.
aside from the fact that it was unrealistically large for a tree, the beams of light were spreading from its roots to its lush branches.
“well, we don’t need any light at night thanks to the tree.
 the light is not that strong, but we feel it is unique because there is no light anywhere in this ruined world.
 all around the clock, it is emitting a sacred atmosphere,” said inho as if the world tree was a big headache.
“now we can’t hide it.
”“nope.
 it has become the landmark of this area, so we can’t.
”few people knew that the world tree was growing in suwon.
when terror kim attacked the village, the world tree was exposed to the broadcast briefly, but at that time, it was still small, so no one noticed the existence of a “world tree”.
‘if we can’t hide it, it’s time for us to use it.
’until now they have kept the existence of the world tree secret to preserve the young world tree.
however, now they have become strong enough to defend the world tree.
 besides, they had the “shade of the godly tree”, an invisible barrier on their own.
then, how could they make use of this overwhelming presence they could not hide anymore?‘yeah, let me make it stand out.
’-would you like to designate this place as the main base of the third camp? (y/n)sungwoo chose yes.
-enter the camp name.
* caution! you can’t change it for 30 days.

* caution! it takes a huge amount of gold for you to change it.
deciding the name of the camp was a really difficult problem.
 but sungwoo didn’t want to worry about such a headache.
 that’s why he didn’t change his nickname in the community.
in particular, coining the name of the organization, not the individual’s nickname, was inevitably tricky because it should reflect the personality and values of the group.
“…”finally, sungwoo slowly opened his mouth.
 for fear he might pronounce it wrong, he spoke clearly.
“world tree.
”devil and angel, these names were simple but very intense in terms of their images.
in other words, their names signified something very impressive.
then, which ‘keyword’ would be impressive enough to impart a strong image like the two names?currently, sungwoo has a strong brand name called ‘necromancer’, but this name would be more useful as an individual’s name, for the power that this name carried would be weakened if it were mentioned at an important moment.
that’s why sungwoo chose the name of the transcendent being, “world tree”.
-can you confirm it’s  camp? (y/n)“yes, confirm.
”– congratulations! you have created a new camp.
* your camp has been classified as a regular camp.
* new features will be opened according to the camp level.
-you have successfully cleared the camp quest !* reward is given.
 (initial operating fund)-you are granted the title of the camp founder.
* all stats increase.
 (+3)-you can add regular members to your camp.
* check the ‘camp members’ menu.
-‘world tree’ has become the symbol of your camp by satisfying the special conditions.

‘a symbol? is it the same role as the statue?’[world message]– congratulations! , the first player-led camp on the korean server, has been created.
the message about the creation of a new camp was delivered to all players within the invisible barrier.
“wow!”“finally, we are also a regular camp!”at first, they were in a tense mood because they were prepared for any contingency situation, but when the camp was established without any problems, they were soon in a festive mood.
“devil camp? angel camp? we don’t need them at all!”“they are ill-bred without any legitimacy.
 besides, we don’t know their leaders.
”“you bet.
 they are messed up.
”the villagers felt alienated and deprived when those belonging to the two camps dominated the community, so it was natural they were filled with emotion when they realized that the necromancer surpassed both camps and became the best on the korean server, and as a result, they witnessed the birth of a “regular camp.
”“well, we may soon see the return of a world where we can lead a decent living as humans if things keep improving like this.
”“yeah, it still sounds like a dream, but it’s not impossible as long as the necromancer…”“right.
 i think it’s possible.
”but all things didn’t necessarily work out well.
[angel’s camp emergency quest (world)]-title: cleansing the impure seeds-goal: disintegrate the “world tree camp” and destroy their leader “kor-157”-target: no restrictions (contact ‘angel statue’ after carrying out your goal)-reward: 150 million gold and the title ‘best of the server’ is given.
[demon camp emergency quest (world)]-title: stepping on and bursting parasite eggs-goal: offer the bodies of the “world tree” camp players to the “devil statue”-target: no restrictions (contact the ‘devil statue’ after carrying out your goal)-reward: 1 million gold per player and the biggest contributor is given the title of ‘best of the server.
’‘they must have invested a lot.
’when the third camp was created, the two absolute races were continuing to confront each other while they were on a roll without bothering other servers.
however, the third camp was born only in the “korean server”, beating the two absolute races and established itself as the best camp.
they must have felt a great sense of crisis because of the third camp, so it was natural they showed such a radical reaction.
however, the next message was even more shocking.
[world quest]-name: those who are hated by the big world-type: hunting or protecting-goal: hunt or protect the ‘world tree’ camp players.
-compensation: differential payment depending on the situation*”kor-157,” the founder of the “world tree camp,” was one of the world’s top players, who has continuously engaged in activities that enraged the two absolute races.
 so, they decided not to leave him alone.
 this event was supposed to take place on all servers throughout the world.
 you also have to choose whether you will obey the orders of the absolute race, or you will rebel against them and join the new camp.
* the current quest may change depending on its progress.
the system gave new quests because of the fierce reaction of the two camps, angel and demon.
 however, the system made the terrible decision to target the whole korean server as the ‘quest target.
’“this is crazy! sungwoo, don’t you think this is too much? how can they grant such a huge amount of gold per player? crazy bastards! ”“…”because of the shocking message that appeared before all the village players, the festive atmosphere among them was gone in an instant.
 they were so gloomy and frustrated.
“what the heck is all this…”“is this quest real?”sungwoo could not help but be embarrassed.
 besides, they put a huge bounty on his head, which was enough to attract players around the world to this quest.
‘honestly, it’s an opportunity that any big server nearby will never give up.
’

on the other hand, it was like a death sentence for the world tree camp, which was just established.
however, the villagers’ reaction was unexpected.
“what the heck? are they hunting us?”“damn it, they are talking bullshit.
”“for some reason, i think i can gain more exp and gold rings this time.
”“me, too.
 i think i have to dig more herbs from the mountain and fill the potion storehouse.
”they were not scared or overwhelmed at all.
 the players of the village, namely the players of the world tree camp, already became strong enough to confront any external players.
so much so they were full of determination to brave the crisis and turn it into their opportunity.
 their courage and guts were what sungwoo defined as the evidence of their real worth.
“hanho, and kyungsoo, inho!”“yep!”“yes, sir!”“here i am!”kyungsoo and inho approached him immediately.
“i think we have to be ready to fight in a big way this time.
”although sungwoo said it seriously, they didn’t get cold feet at all.
“sure, no problem.
”“i thought a day like this would come.
”“well, i’m always ready to play a supporting role behind you! yeah, the spirit of sacrifice!”they were already fully ready now.
“good.
 let’s get ready!”sungwoo nodded and quietly pulled out the “imoogi scales”.
-on air (!)‘they just can’t take their eyes off me…’regardless of who the “creator” that imoogi mentioned and their plan, sungwoo intended to crush them in a way they never expected.


 