\section{chapter 182}

                            “are you ready for shooting the scene on the camera? this is going to be a scene that will go down in history, so try to focus on my face.
”




kangyoon lee, a fire-type wizard with the liberation guild, was stationed near cheongnyangni station with his subordinates as the vanguard of the angel camp.
he has long been famous because of his nickname “kang yoon” in the korean community.
 he was widely known to have posted more comments than anyone else.
“hmm, how many viewers are coming in to see this scene today? around 50,000? of course, they should.
”to put it simply, kangyoon was a terrible attention seeker.
“it is one minute before the start of the broadcast.
”“okay! come on, let’s go!”it was dangerous to broadcast the fighting scenes live in a war.
 rather, it was crazy.
 it could expose the operation of the friendly forces and their military strength to the enemies.
however, there were dozens of broadcasts being aired from both camps.
 most of the broadcasts were done by volunteers from other regions for fun, but there were also broadcasts operated by the main camp because they wanted to appeal to the viewers for participation in their camps.
“captain, commander has asked us to indirectly emphasize the benefits of the angel camp.
 don’t forget!”“okay!”since the battle had not yet begun seriously, they needed to secure as many troops as possible through a publicity campaign, so kangyoon was selected as the chief charged with that mission.
 “now, at this moment, i am more important than the necromancer, so you should film my face with a sense of responsibility.
 got it?”“okay!”“you can just keep going like that.
 we’re going to focus on you.
 so, don’t worry!”no matter how spectacular the necromancer’s activities were, it was not as shocking as the fact that there broke out a war between the absolute races.
it was natural that the korean server players would immediately focus their attention on northern seoul.
 kangyoon’s broadcast stood out among them.
“broadcasting starts in five, four, three…”a few hours ago, he posted the pictures of the demon camp’s search team members being burned on the community bulletin, causing a shocking sensation.
at the same time, he jarred the nerves of the demon camp with provocative comments.
“even the noise marketing was perfect.
”
so, he laid the foundation for instigating the viewers to join the angel camp.
kangyoon and his subordinates expected that when the broadcast began, tens of thousands of people would come in to see the scenes.
‘if the fight between the angel and the demon camps is framed like this, the necromancer will be gone without any traces.
 a third camp led by the necromancer? bullshit! let me see how long he can keep it.
”thinking so, kangyoon frowned.
 he felt jealous towards the necromancer, but rationally, it was impossible for the necromancer to run on the path of success by making the absolute race his enemy, no matter how strong he was.
“now, the broadcast starts…”kangyoon smiled again in a leisurely manner.
“well, hello! this is k.
y.
, kangyoon who is your hero!”he opened the window, gesturing naturally.
 cheongnyangni station was seen from the window.
“have you seen the scenes of me pouring hellfire over the followers of the demon camp?”then, he raised his right hand and lit a small flame.
“huhhhhh! i smelled the burning of dried filefish fillets when i burned them.
 from now on, we’re going to broadcast from cheongnyangni…”however, the expressions of his subordinates monitoring the broadcast were not good.
“…”kangyoon, feeling something strange, stopped speaking and tilted his head.
then, one of his subordinates began to check his looks.
“captain?”“uh? what’s up?”“there are only 19 viewers?”“what the heck are you talking about?”that was ridiculous.
 how could it be only 19? soon, his men found out the reason.

“yes, the necromancer has also started broadcasting.
 looks like all the viewers have switched to that channel.
”when that annoying name appeared.
 kangyoon immediately frowned.
“what the heck? this is a war situation.
 why is he trying to broadcast in the middle of the battlefield when there is nothing important happening? does it make any sense?”“well…”after all, one of his subordinates accessed the necromancer’s broadcast and checked what’s going on.
“what the heck is this? uh? what is it?”“the necromancer has stormed us!”he just kept repeating something that kangyoon couldn’t understand at all.
“uh, where did he attack?”“i have no idea.
 i don’t think he has attacked our country.
 i see some chinese characters.
 no way!”“china?”once again, all their eyes turned to the necromancer on the screen.
***chiang kai-shek memorial hall in zhongzheng district, taipei, taiwan, at 3 pm.
the red revolutionary army’s rally was being held at this place created to commemorate taiwan’s first president, chiang kai-shek.
 they held it in front of the spiritual symbol of taiwan to commemorate their occupation of taiwan.
“with the conviction that we will unite as one force, faced with the current disaster, and create a new world…”while the moderator proceeded with the formal opening, the main figures of the red revolutionary army were seated at the head table on the gorgeous podium.
at the center was gen.
 chongong, the red revolutionary army’s top generals on his right, and some of the converted taiwanese players and prisoners.
“and our great cause was realized through the insight of the prophet and our king, gen.
 chongong, and under his will his two brothers, gen.
 jigon and gen.
 ingong, who didn’t hesitate to sacrifice themselves for gen.
 chongong…”and there were a huge number of players crowded in the square they were facing: pirates, friendly taiwanese players, mobilized elderly people, and prisoners.
this scene was being broadcast live to the china-2 server as well as the china-1 server and china-3 server.
after the red revolutionary army publicized this event widely, several factions on each server sent people, so they could broadcast the scene on their servers.
in other words, all the people in china were watching this scene.
“now gen.
 chongong, our eternal savior, will deliver a keynote speech.
 i hope you will greet our leader with big applause.
”when thunderous applause erupted, gen.
 chongong dressed in red silk stood up.
 he walked sternly to the podium and stood before the stand, reaching out and moving the microphone.
then, he slowly opened his mouth.
“i promise all the people who attended this event i will support you.
”applause came out again this time.
gen.
 chongong raised his hand and continued, “i stood alone on the day when we were faced with the disaster.
 and i began to hire loyal servants one by one, and today, i reclaimed taiwan which we had lost a long time ago.
 and let me declare proudly that tomorrow we will move into the korean peninsula.
”thud-at that moment, there was a thunderous roar somewhere.
 he felt a little vibration under his feet.
 however, not many people noticed it.
“i will kill the necromancer, the demon of the korean peninsula, and rescue the survivors of the korean peninsula from their miserable destiny…”ku-woooooooooo-there was a huge vibration again.
 this time, it shook the whole square where they were holding the ceremony.
“…”gen.
 chongong stopped his speech and wriggled his eyebrows.
 he felt ominous.
 there was silence in the square.
then, those who gathered in the square also began to turn their heads one by one, following gen.
 chongong.
whooooooooo-a gust of wind that came from an unknown place swept over the square.
 gen.
 chongong’s red silk robe fluttered roughly.
 the next moment there was a thunderous explosion.


bang! bang!the ceiling of the national library building beyond the square collapsed, where something was soaring.
 the cameraman moved the camera lens and filmed it.
“what the heck is that?”a monster made of huge bones spread its wings then flew into the sky of taiwan.
“is it wyvern?”it was bone wyvern alpha male.
right after that, dozens of bone wyverns poured out like a swarm of bats.
“ahhhhhh!”“what the hell are they?”the sun in the western sky was blocked by the wings of the huge veil, and a huge shadow waved over the crowds gathered in the square.
everyone in the square as well as those watching the broadcast witnessed lich, the one on the largest wyvern’s back, surrounded by green flames.
“no way! is he the necromancer?”“right? he must be that necromancer, right?”“oh, that bastard of the korean server?”as they said, he was that famous necromancer of the korean server.
he unexpectedly appeared right here at this ceremony.
“how could he come here?”he was holding a giant scythe in one hand and a white stone in the other, which was none other than the head of the angel statue.
the next moment, he smashed the statue to fragments and threw them away.


 