\section{chapter 311}

the situation was definitely unfavorable to the korean server led by the necromancer.





in particular, those with fewer troops tended to get weaker when their forces were split into several forces.
it was tough for sungwoo and his allies to fight the enemy as a whole, but if he had to fight on three different battlefields, it would be tougher.
 besides, there were other war rules that stood in the way of sungwoo's effective fighting.
-in the next 12 hours, the 'deployment of troops (cross selection)' on the battlefield will begin.
 the "list" of the deployed troops will be revealed to the opponent.
"man, under this 'cross selection' rule, you have to tell the enemy where you are moving, right, sungwoo?""i guess so.
 it's like pics & bans.
"since the list of sungwoo's troops was supposed to be open to the enemy wherever sungwoo moved, it was certain that the enemy would try to secure a means to bind him, so he could not move freely.
 in other words, the chinese server players would try to win on different battlefields while binding the necromancer in one specific battlefield.
"it's the worst of the worst.
""um…"this wasn't the kind of problem that they could solve just by putting their heads together.
 so, sungwoo wrapped up the meeting and stood up.
"over the next 12 hours, we will have to find out the movement of the enemy and think of plans for all situations.
"kyungsoo also stood up and said, "that's right.
 the liberation guild is expected to arrive within an hour, so i think we have to find the way with them.
 in the meantime, we need to keep our troops in order as much as possible and have a way to control the reinforcements coming from all over the country.
"they were not sure of how to cope with the coming war with the chinese server, but the war was fast approaching with not enough time to prepare.
***sungwoo took a moment to climb mt.
 paldal to see mir.
the baby dragon still relied on sungwoo.
 so, when he was away for a long time, mir might be doing something unpredictable and wild.
at that moment, someone approached sungwoo from behind.
"oh, necromancer!"
the man seemed to be a guard at mt.
 paldal, who was following sungwoo to climb the mountain.
"what's the matter?"there was something wrong with his eyes.
 his pupils dilated and his breathing was slow.
 obviously, he was out of his mind.
"someone over there is looking for you, necromancer.
""who is it?"instead of replying to sungwoo's question, he just smiled silently.
"uh, well…"then, he began to look for something inside his pocket.
"who is looking for me?" sungwoo demanded.
".
.
.
"at that moment, sungwoo felt something was wrong.
 he wasn't just insane.
sungwoo put his hand on the hand cannon on his waist and prepared to behead him right away.
"uh, uh, uh.
.
.
.
"the man rummaged his inner pocket for a while, then took out a round object.
"that guy asked me to give it to you.
""this is a potato?"it was a boiled potato.
"then, have a good time!"
having said that, the guard went down the hill.
sungwoo threw away the potato and went in the direction where the guard ran away.
a wooden bench was seen in a lush mountain.
 and there was someone lying with his head down on it.
"hey, i don't like this kind of play.
""why do you think this is just a simple play? don't you think it's part of their very important operation?"the king of the great mountain was looking at sungwoo while chewing boiled potatoes.
"what brought you here? sungwoo asked coldly.
he sneered at sungwoo's cold reaction and said, "gosh! what brought me here? just like you advised, i'm here to act as the real owner of this area!"the king adjusted his posture and stood with his arms folded.
"well, i think i'm a little late.
 maybe there is somebody stealing a glance at us, right?"at first glance, he seemed to ask sungwoo if there was somebody shadowing them.
'peeping at us?'however, sungwoo immediately grasped his point.
 then, he put his hand in the pocket and held the scale of the imoogi.
-off air (-)"nobody is peeping at us.
"the peeping eye, namely, the 'creator' was not looking into this area.
 he must have cast his gaze on some other exciting scenes in the world.
"are you sure?"the king's eyes twinkled strangely.
"you have to keep an eye on him, though.
 i'm going to tell you the most strange and scary story, but if you leak it, i'm in trouble.
"he threw the boiled potato in his hand behind his back.
 then, he stepped closer to sungwoo and muttered in a small voice.
"well, i've got some mysterious energy.
 last night, i couldn't sleep at all because of god's voice, so i'm afraid i'm going to say nonsense…""what did he say?"this time, sungwoo went a step closer to the king, thinking, 'god's voice?'sungwoo contacted them through imoogi, the giant snake.
 they were a being like the creator.
 so, this time it was clear that they sent a message to him through the king.
"oh my god, you are so impatient!" said the king.
"yeah, i'm in a hurry.
 so, tell me quickly!"when sungwoo demanded, the king looked up at the sky, fiddling with his chin.
"uh, well, they said if you were lucky, you could win this war.
 but you would be killed by the dragon.
"".
.
.
"was is it a prediction, not a piece of information? sungwoo was embarrassed by the king's unexpected words.
 then, the king began to giggle at him loudly.
"look, i already told you in advance that i was going to tell you a scary story.
""so? there must be a lesson in a scary story, right?"the king said with a smile, "find the little statue of general singh's belongings and the little statue inside admiral baker's flagship.
 find the two statues and take them to the world tree.
 then, guess what!"".
.
.
""guess what will come out of it?"sungwoo almost took out his new weapon, "winter predator," to shoot the king.


"are you making fun of me now?" sungwoo asked angrily.
"calm down, my friend! i saw murderous intent in your eyes.
 please calm down.
 if you lose me, my poor younger brothers will die from eating only potatoes.
"when sungwoo stared at him, he smiled awkwardly.
"um, i actually don't know.
 as you know, god only says what he wants to say, right? he always gives us a puzzle.
""really?""is there any reason for me to fool you around even if i make fun of you?"he approached and put his hand on sungwoo's shoulder.
"there is one more important thing here.
""what?""i told you you could win this war if you were lucky, aside from the dragon.
""how can i be lucky?"the king tapped him on the shoulder and said, "i'm now telling you i've come here to help you.
 and…" a blue light began to flutter behind his back.
 then, 12 portals were opened at once.
"those dependent on me in the great mountains asked to help you.
"the unexpected reinforcements, namely the monsters in the mountains poured out of the portals.
 but there were more reinforcements other than the mountain monsters.
when he had the king's army of monsters on standby at mt.
 paldal and went down the hill with the king, kyungsoo approached him and said, "we have an urgent message from taiwan.
 they said they were sending 3,000 troops to help us.
"those players that sungwoo had associations with in one way or another finally began to gather and rally around him.


 