\section{chapter 202}

                             




the camera turned at the same time as the assistant yelled.
a stunning moment broke their boredom in an instant.
the reporter, swallowing, announced the new development in an urgent tone.
“he’s intact! he’s still the same necromancer we know!”[real time chat]- kww: oh, no, please!- 28-year-old jinhyung: please, i bet 100,000 gold.
 necromancer, please, don’t!- kim jammin: damn, you guys wished the necromancer died, right? why are you making such a big fuss?- yasuo 1: what are the demon camp up to now? are they just numerically superior? aren’t they called the warriors of mt.
 taebaek? how can they be so defeated by three monkeys?- goblin hunter 123: lol.
 yeah, the necromancer is always right!- uncle yun: honestly, isn’t this what we all have expected? i think you guys got blinded by something wrong, but look! the necromancer was only weak in your delusions!the money of korean server’s gamblers was rolling into the pockets of the necromancer.
***sungwoo and his party, escorted by the key, soon arrived at the second place.
 thick vines were draped across the road like curtains, so they could not get into it, but when the key touched it, the road began to open to them.
ooooooooooh-blue light poured into it.
 sungwoo and his party squeezed through the cracks of the vines and escaped to the other side.
“oh, it’s bright here.
”they were still inside a forest with the sky blocked by the trees, but they didn’t need to walk in the dark because bright light was flowing from all over.
“moss?”minsok lifted his feet and looked down at the green moss emitting a blue glow.
“the moss is radiating light.
”as he said, moss clinging all over the forest was emitting blue light.
* the next chapter is an area covered with ‘poison fog’.
 hunt 100 ‘venom giant wasps’ in the area to obtain ‘venom immune buffs’ before moving to the next chapter.
weeeeeeeeeeing―
there was the sound of flapping wings.
 when they raised their heads, a wasp almost the size of a forearm flew through the trees.
 the stinger on its tail looked like a stake.
“man, i thought it was a drone.
”“because the wasp is so big, it’s unrealistic.
”jisu found something different while hanho and minsook were uttering admiration.
she raised her sword and pointed somewhere.
“there is a very noisy place.
 it is a hive where dozens of wasps are gathered.
”when they approached the place she pointed at, something was hanging from a thick branch at the top of the giant tree.
 it looked like a hut on top of a tree.
“it’s a honeycomb.
”there were dozens of poisonous giant wasps sticking around the hive that was about five meters wide.
weeeeeeng-the wasp was flying around it, which looked like a helicopter flying near a building.
“touching it is crazy, isn’t it?”hanho muttered, hiding behind the tree before he knew it.
in his mind, sungwoo would have destroyed it entirely.
what if he destroyed that terrible hive.
 it was not an ordinary wasp nest.
hanho didn’t want to imagine what would happen if he touched something terrible like that.
“sungwoo, please…”‘by the way, no matter how hard i think, it is inefficient to catch them one by one until we reach 100.
’so, sungwoo stepped forward and opened his mouth.
“everyone, step back!”as hanho expected, sungwoo was going to destroy the huge hive at once.
‘let me just burn it away.
’sungwoo raised the repeating crossbow.
 since it was equipped with the function of ignition, he could burn the wasp hive.
tung! tung!however, the arrows he fired could not even reach the wasp’s nest and fell away.

it looked like the hive was covered with a protective film, blocking the outsider’s attack.
“if that’s the case…”a little later twelve giant jannabi skeletons began to climb the tree.
rattle! rattle!on their backs were axes and rakes made of bones.
immediately after the five of them at the forefront reached the branch with the wasp hive, they drew their axes.
puck! puck! puck!then, they began to crush the branches ruthlessly.
 an ordinary man couldn’t cut them easily because they were thicker than the trunk of a pine tree, but the skeletons could easily cut them down with their immense strength.
weeeeeeng!the wasps sensed danger then quickly flew up and turned towards the skeletons.
then, they began to fire huge stingers at the skeletons.
tung! tung!the huge stingers stuck the skeletons, making a loud sound.
puck! puck!however, the skeletons continued to throw the axes casually.
 come to think of it, the wasps’ poison stingers did not affect their bones.
tong! tong! tong!normally, the wasps’ poison stingers would be fatal attacks, but they were no more than ordinary attacks as long as the poison didn’t work.
‘drop them!’sungwoo already prepared some methods to counter the wasps’ counterattack.
the undead standing behind the skeletons pulled out the rakes made of bones.
using the long and wide striking range of the rakes, they began to tear off the wasps’ wings.
wooooooooooooh-the wasps that lost their flight ability helplessly fell and were killed by the undead waiting on the ground.
-you have earned 25,000 gold by hunting the ‘poisonous giant wasp’.
-you have earned 25,000 gold by hunting the ‘poisonous giant wasp’.
-hunting a poisonous giant wasp (4/100)cracks began to spread in the thick branches.
the giant wasp nest, which was hanging at the end, collapsed.
the huge object shattered like a watermelon and sungwoo aimed the repeating crossbow straight at it.
tung! tung! tung! tung! tung!there was no protective shield around it now.
 a barrage of powerful arrows smashed the wasp’s nest to pieces.
that wasn’t all.
 sparks arose from the place where the arrows hit and merged into a huge flame.
-you have earned 5,000 gold by hunting the ‘poisonous giant wasp larva’.
-you have earned 5,000 gold by hunting the ‘poisonous giant wasp larva’.
-you have earned 25,000 gold by hunting the ‘poisonous giant wasp’.
-you have gained 200,000 gold by destroying the ‘poisonous giant wasp’.
-hunting a poisonous giant wasp (34/100)the whole wasp hive was burned down.
“wow, we can hunt 100 wasps easily!”hanho, hiding behind the roots of a tree and watching it, exclaimed in admiration.
sungwoo shook his head and said, “no, i’m going to hunt more than 100.
”“really? why?”“think carefully.
”“gosh, i have no idea!”they just had to hunt 100 wasps.
 why did sungwoo bother to hunt more?***“we have it finally!”“yeah, we got the key!”“everyone, move this way!”

as a result, they suffered great sacrifices, but they took such sacrifices for granted.
“uh, i see the light.
”“everyone, go in there!”they came across a mysterious place, filled with blue light.
“catch wasps?”“now, we have to catch wasps after monkeys?”“but i’m glad we’re not looking for something hidden.
”this time again, the demon camp troops began to scatter widely and search for targets.
but as time passed by, they felt something strange.
“2nd team! did you find a wasp?”“nope, we can’t!”“what about the 3rd team?”“no, we can’t either!”all the teams reported they had not seen any wasps yet.
bumbyol nervously swung his fist toward the trees.
bang!“damn, where the hell are the wasps?”no matter how thoroughly they searched, they couldn’t find even one live wasp.
they found it hard to search for the monkey with the key, but this time they found almost no wasps to hunt.
shortly afterward, they came to know the reason.
“no way! is that the wasp’s nest?”they began to discover huge wasp nests in the forest that had been turned into lumps of charcoal after being burnt.
“the necromancer destroyed them all?”“that bastard…”the most basic way to get ahead was to go faster than others, but the more certain way was to kick down the ladder, so they could not follow.


 