\section{chapter 286}






 after all, sungwoo used another hidden card.
 he unfolded bi hyong’s ghost fan and summoned a horde of ghosts.
 they lifted the bone weapons made by sungwoo with telekinetic power and flew towards the frozen seed.
-the powerful magical energy of the affected area blocks the access of the ‘spiritual being’.
the ghosts were pushed away like a piece of cloth blown by the wind.
 frozen seed wasn’t an easy target.
“man, should i go inside?’there seemed to be no other way in sungwoo’s eyes.
 he took out the “fire spirit stone (higher),” which he had placed near his heart.
 fortunately, he could prevent his blood from freezing because of this.
“okay, let me go inside.
”sungwoo grabbed the object in his right hand tightly and stepped into the blizzard.
tramp- tramp-the closer he got to the frozen seed, the more he lost his senses gradually.
 he now found it hard to bend his joints.
 every time he breathed, his heart hurt.
 the breath he exhaled became solid and scattered instantly.
 at one point, even his vision became blurry.
‘if i don’t do anything now, i will die soon.
’he couldn’t stand it even a minute.
 feeling the cold, he finally stood before the frozen seed.
-you are now being exposed to severe cold.
* all physical abilities decrease (-70%)if he felt so cold like this when he was standing around the frozen seed, it would be suicide for him to touch the frozen seed, just as standing near a wood fire was different from putting one’s hand in a wood fire.
however, if he could use the ‘fire spirit stone’, he could offset the cold and give it a shock.

sungwoo raised his hand hard with difficulty and struck the frozen seed with the fire spirit stone.
clang―the frozen seed shook roughly.
 sungwoo once again raised his hand and struck it hard.
clang―like a train running off the metals, the frozen seed, which was shaking violently, bounced out of the hole of the ice tower.
 sungwoo succeeded.
-‘frozen seed’ has stopped working.
then, the blizzard that was blowing all over the place stopped.
whoooooooo-as if the pure white curtain was cut off and fell, the white veil collapsed on the ground.
 the unobstructed scenery of the snow on mt.
 namsan unfolded before his eyes.
 it was beautiful.
-since you have survived the strong cold, your cold resistance increases.
 (+2%)sungwoo picked up a white marble that fell on the snowfield.
 it was still cold to the touch, but he could stand it.
[item information]-name: frozen seed-grade: special-category: orb-effect: grants the traits of ‘snow man’ for more than 100 days, cold resistance increases (+10%), mana consumption decreases when using freezing-type magic (-80%).
 causes ‘ice age’ in a certain area when it’s installed in a high area.

sungwoo stopped the ice age from arriving in seoul.
***even though sungwoo solved the case at the risk of his life, he had to tackle another big case right after that.
 sungwoo’s party and junghoon’s crusader team gathered at the entrance of yeongdeungpo station.
 it was time for them to stop the descent of the angel.
“the angel statue we possessed was somewhat different.
”he said that he had an angel statue of a higher grade than that of an ordinary grade.
 namely, a statue with four wings.
was it because of that? junghoon had been forced to become the vanguard of a ridiculous quest that only pursued the interests of the angel camp.
in the end, junghoon couldn’t stand it and broke the statue.
 by breaking it, he wanted to shake his hands off and get out of the camp.
“but once i belonged to the camp, it was impossible for me to withdraw from it.
”he said that the moment he struck the angel’s statue with his sword, a warning message appeared.
-you have made an indelible mistake.
 after a certain period of time, the “angel judge” will come down.
* all players who have joined the angel camp through the angel statue will be ‘punished.
’(all stats will be reduced by 90% when they face the angel judge.
)* the target of the judgment cannot leave the seoul area.
 no matter where you are hiding, the “angel judge” will go after you.
* on the day of the angel judge’s descent, if you select and offer 500 sacrifices (players) and repent your sins, you can be forgiven.
junghoon shook his head, recalling the warning message.
“sungwoo, you were right from the beginning.
 i now know playing into the hands of the absolute race had nothing to do with the happy ending… yeah, i’ve come to realize it now.
”“it’s not too late yet.
”the remaining time until the angel judge’s descent was about 7 hours.
 so, sungwoo and his allies could prepare and confront the judge.
however, like junghoon explained, the liberation guild belonging to the angel camp could not confront the judge.
 a 90% reduction in their stats meant that they could not fight at all.
“yeah, that’s right.
 but we are not going to give up either.
 if we had given up, we would have been killed much earlier.
”there was strong determination and fighting spirit on his face.
sungwoo nodded and said, “from now on we must build up our strength.
 the angel camp is not the only one targeting us.
”“devil…”“there are more terrible things…”the angel, the devil, and the world eater were all no different.
 with different names, all of them wanted to take control of this world.
 among them, “world eater” was the worst.
‘and there is another one above them, who is watching my words and action closely.
 he’s called the creator.
 even if i stop all of them, i will just play into the creator’s hand if i don’t know what he wants.
”at that moment, a message appeared before sungwoo’s eyes.
[exclusive quest]-name: guardian’s duty-2-type: goal guardian-goal: protect the angel camp’s target of judgment.
-reward: choose the ‘upgrading of your deity’ or the right to change your job

*an external being known as the absolute race, or the angel race, is supposed to come down to slaughter people on this earth.
 as the “guardian” of this earth, you have the duty to remove pressure from the external being.
 if you stop the plans of the angel race, you will be able to inflict big losses on them.
* you will fail when more than 80% of the ‘target of judgment’ dies.
* additional rewards will be provided when you kill the ‘angel judge’.
it was a quest related to the title of ‘guardian’.
 sungwoo knew it was triggered when the gate of hell and the devil’s gate were opened.
‘then, it means that the absolute race is not different from the monsters, right?’sungwoo now realized that the title “guardian” he possessed meant the person who defended this land with an independent force, not with the help of any external force.
therefore, such guardians were inevitably very few because most of those who survived the destruction succumbed to the temptation of the absolute race and relied on their power.
‘by the way, the upgrading of my deity?”of course, the reward caught his eye.
 the ‘anubis’ power’ that he currently had was described as the first stage.
 if so, did it mean that it was going to be upgraded to the second stage? then, could he make another huge development? whatever it was, sungwoo had no choice but to look forward to it.
“then, how should we prepare?” junghoon asked.
after pondering over it briefly, sungwoo opened his mouth.
“please gather as many people as possible who deal with water and fire.
”“water and fire?”“right.
 let’s splash water on the unwelcome guest!”however, what sungwoo was preparing was not just the downpour of water alone.
he felt some intense energy in his pocket.


 