\section{chapter 404}

when the dragon expedition changed to the dragon crackdown team, each function increased by 100%.
 and two features were added, which were about additional acquisitions after the dragon hunt.





'well, even though dragon hunting itself is a problem, i think i can get a great reward after hunting,' sungwoo muttered.
he already had four dragon slayer items, whose synergy effect could not be higher like when four liches were combined.
'is this strong enough for me to fight the amazon dragon?'but he was not sure yet.
 if there was only the amazon dragon out there, he could probably confront the monster, but he could not be sure because there was a player called the demon king with the monster.
'by the way, the title remains the same.
'when sungwoo hunted the world eater, his title of 'dragon hunter' was upgraded to a legendary grade, but there was no such message this time.
"is it all over now? done, right?" li wei asked, approaching him.
because of a large pool of water that zi xuan had drawn from the clouds, she used the water spirits to make a road, so she could walk toward him.
"li wei, can you control all this water here?" she looked around quickly and nodded.
"i can't control it as freely as i do with the water spirits, but i can anyway.
"sungwoo lifted his finger and pointed at the rampart where the emperor's terracottas were.
"then wipe them away!"she nodded at that, taking a deep breath.
"oh, before you attack them, come here.
"
he suddenly hit upon an idea.
 when she approached, he put his hand on her head.
"what are you doing now?"- you have appointed her as the 'secretary of the underworld king'.
with that message, purple energy emitted from his hand and entered her head.
she frowned very hard.
"uh? what the heck is this? what did you do to me?"[skill information]- name: appointing the underworld king's secretary- grade: ultimate- classification: active continuous type- consumption: 10 mana*you can appoint a player or your subordinate with intelligence as the 'underworld king's secretary' and have him perform the mission of the grim reaper.
 (up to five)the secretary can use the souls of the dead he has hunted or killed as 'ghosts'.
 (up to 20 per car).
 in addition, you can revive the dead secretary once with the power of the underworld king's authority.
 (standby for reuse: 49 days)the total number of ghosts that sungwoo could control with the 'law of the underworld', the skill of controlling ghosts, was 500.
if there were other ghosts around like now, sungwoo could control them, too, but there was little possibility that the same thing could happen to him again in the future.

'well, i should appoint the one i can trust as the underworld king's secretary.
'in other words, he had to maintain a strong secretary in order to mobilize the underworld king's maximum power.
li wei, who was still puzzled, asked, "then, you want me to be your subordinate spirit? are you serious?'did she feel ashamed of the master-servant relationship between him and her?sungwoo said, "don't give it any meaning.
 that is not important.
"but she turned, feeling embarrassed.
 even though she admitted he was much stronger than her, she still had much pride.
he looked down at zi xuan's body.
- you can read the 'memory fragments' of the dead.
as expected, he could find some clues from them.
 so he resurrected her as a skeleton and peeked into her memories.
shortly afterward, he slowly opened his eyes.
"it was a big mistake that he sent his closest aide to me as a fighter.
'she was a player who could get to the emperor most intimately.
 so he could glean lots of information from her memories.
he discovered that her deity status was 'dragon,' and that the emperor was hiding some secret weapon.
"man, was he hiding there?"he even found out where the emperor had been hiding.
"and the weapon he was hiding…"of course, sungwoo had a hidden weapon, too.
 he had not yet used one of the underworld king's skills.
"yeah, i'm waiting for a chance to wipe you out with a single strike…"***sungwoo's undead army began to attack the rear of the terracotta army.
 but the tide of the war did not change overnight.
the emperor was still reinforcing his terracotta army with more forces.
 compared with the size of his forces at the beginning of the war, they were reduced a lot, but as soon as they were reduced, more troops came in to fill the void.
"oh my god! the necromancer and his undead army have resumed fighting, but the rampart they are defending is still in jeopardy!" reporter ahn said, rubbing his sweaty hands on his pants.
the battlefield as seen from the air was so wide and complex that he could not grasp the situation of the war accurately.
with the necromancer resuming the fight, there was a big change in the status of the fighting in the rear area, but the emperor's attack against the rampart never slacked off.
 rather, the formation of the allied troops was collapsing quickly.
bang!an explosion was heard from one side of the rampart.
 a huge cannon was fired, which was an ugly weapon that was as long as 50 meters.
giant terracottas and steel golems had been installing that weapon in front of the gate of the castle for a few minutes, but the defending troops didn't know how to stop them.
 after all, they allowed for the monsters' attack.
"oh! come on, the gate of the castle is falling, and they are beginning to infiltrate! this is a very big crisis!" reporter ahn shouted desperately.
"well, it looks like the fight will be over pretty soon," wong chimed.
reporter ahn shook his hands nervously as if he was nervous, while wong nodded calmly.


as the guardian statue, which was the core weapon to defend the rampart, was neutralized, the rampart began to collapse quickly.
"besides, those giant golden hands seem pretty strange! valkyrie is desperately trying to stop them, but it looks like it's hard.
"the two golden hands that the emperor was controlling, namely, the 'oppressor's hands,' didn't simply control the statue.
"the flying weapons of the allied troops were taken over by the enemy!"the golden hands controlled the flying weapons with the threads, turned their nozzles in the opposite direction, and bombarded the village.
 what's more, they attacked the rampart directly and broke down many parts of the rampart.
jisu rushed to stop the attack, but she was busy avoiding the golden threads extending from the right golden hand.
"ah, valkyrie looks very tired now.
 can't she stop them?"standing on the rampart, she was panting for his breath with the sword stuck on the ground.
she was already drenched in sweat.
 she tried to approach the emperor by soaring into the air repeatedly, but she failed.
"well, it's no wonder she hit the wall.
 i guess she must have already given up because of her repeated failures," wong commented.
"damn it! please, shut up!" reporter ahn shouted.
"what the heck? what did you say?" wong asked in bewilderment.
at that moment reporter ahn sprang up and shouted, "oh! look at that! she is charging at him again! she hasn't given up yet, right?"contrary to wong's prediction, she did not give up.


 