\section{chapter 221}

                             




ninjas always move behind someone’s back, holding others’ lives at their mercy.
but this was their first time being stricken with fear that their lives were at the mercy of others.
‘isn’t it true that both hayabusa and his two minions were already killed? given i don’t have their synergy effect anymore, it’s true.
”the ninja leader looked at the bodies of the three men lying on the ground.
 it meant six of his ninja group were killed before they saw their assassin.
 as a result, the synergy effect of “operation ninja”, which required ten ninjas, was over.
the female warrior in red scanned the ninja slowly with the players of the world tree camp behind her.
 she seemed to have grasped all the ninja’s positions and movements.
the ninja leader went forward and stood before her.
he said, “i’ve heard that a great warrior is moving with the necromancer, but i’ve never thought you were so strong.
 my name is tomada kato.
”he formally introduced himself to her, but the woman reacted coldly.
“so what?”“what?”toma was back on alert, stepping back.
“how rude you are! don’t you have any honor as a swordsman like us?” he shouted.
“it looks like you guys are too immersed in the ninja game.
”“what the heck did you say?”“just disgusting.
”kato’s anger soared at her snubbing even when she ambushed and inflicted great damage on his ninja group.
 he gnashed his teeth and lifted the blade of his sword against her.
“it is commendable that you shadowed and ambushed us, but do you think you are confident of defeating us right now? okay, let me make you regret your decision.
”he rubbed his heel twice.
 it was an attack signal to his men standing behind him.
shhh!there was the sound of wind tearing behind his back.
 their attack began.
 kato threw the kunai dagger hidden in his left wrist at her and ran to her right.
‘if we attack her from all sides, she will clearly show her weakness!’siege of the enemy was a standard formula in any fight.
 kato was now trying to seize her from all directions.
his subordinates also ran in different directions and corrected their position, aiming for the chance to stab her in the ribs.

shhh! shhh!in the meantime, they kept throwing kunai daggers at her.
 dozens of kunai daggers rained down on the woman.
surprisingly, the woman hit back all the kunai daggers flying at her by moving her wrist a few times lightly.
‘good!’however, while the woman was absorbed in blocking their kuna daggers, kato’s subordinates already succeeded in seizing her from all directions.
“kill her!”“let me you regret coming to us!”they charged at her using their ninja skill ‘momentary hiding.
’ no matter how fast she could respond, it seemed impossible for her to handle the ninja who took turns appearing and disappearing.
“uh?”to their surprise, the woman disappeared before their eyes.
“kheeeeeh!”she jumped out behind one of the ninjas who was trying to attack her from behind.
embarrassed, the ninja swung his sword, but only after she cut his neck.
“that’s her ‘footprint tracking’ skill!”the ninjas knew what her skill was.
“that’s one of the skills our swordmaster uses…”since it was one of the skills used by their boss, the swordmaster okata akira, they realized how high her level was.
in the blink of an eye, she cut the neck of another ninja.
now, there were only seven ninjas left.
“damn it!”“block her attack!”the tide was turned instantly with the ninjas being on the defensive.
 they leaped back and widened their distance with the woman.
 their escape was instinctive, not pre-planned.
however, the woman ran like a wild beast, biting the ninjas’ necks one after another.
“argh!”
“damn it! go away!”the moment they touched her and her sword, their bodies were cut here and there even before they confronted her.
there were now five of them left.
“captain, what should i do now?” one of his subordinates asked.
 kato was as frustrated as his men, not knowing what to do.
shaking his head, kato said, “shit! we can’t block her with our level.
 it’s time our swordmaster confronted her directly.
”“really? is she so strong?”“well, maybe more than that…”kato also felt the woman’s skills so clearly, but he knew he could never catch up with her no matter how much he trained.
“so, what should we do from now on?”“all we can do is…”kato thought of fleeing from the scene, but he could dare to say it.
could he succeed in escaping? was he already in her striking range?as if she read his mind, she said slowly in a low voice, “don’t think about running away.
”it was like the sentence of death to himat that moment, the blue flame drifting over her shoulders seeped into the blade of her sword.
something like a dark blue wave began to come out of the black blade.
when she swung the blade, dozens of blue sword energy balls rotated at high speed and scattered forward.
kwaguguguguaa!as if dozens of beasts rushed at their prey at once and crushed them with their claws, she cut them with the powerful sword attack and ripped them apart.
“aaaaaaaaah!”“khuuuuuuuuul!”with just one stroke, she wiped out everyone who had been hiding between the two buildings.
the ninjas tried to hide somewhere by all means, but wherever they went, the sword energies instantly swept over them, cutting their bodies.
it was like a storm, and their fight was finally over.
only a whirlwind that arose amid their fierce fight blew into the alley.
“sis jisu? you must be jisu, right?”hanho, who was watching the scene in shock, came to his senses and approached her.
she wiped the blood off the sword and put it back into the sheath behind her.
“man, where have you been? we were so worried about you! and you came back at the perfect time like this…”“i arrived here several hours ago.
”“really?”jisu already arrived in suwon a few hours ago.
 after she sensed some ominous movement of the enemies, she decided not to reveal herself immediately.
 she was chasing after the assassins, waiting for the right time to counterattack.
her strategy was successful.
 not only did she block the assassins trying to flee after they smelled a rat, but she killed them all.
“what about sungwoo?”“oh, he will be here soon.
”about an hour later, sungwoo joined them.
***jisu explained to sungwoo what had happened to her until now.
after she fell in the middle of mt.
 taebaek because of the item ‘real landscape painting of the spirit’, she survived a bloody fight with monsters on the mountain.
the moment she defeated one of the strongest monsters, she was given a ‘hidden quest’.
[hidden quest]-title: encounter the “king of the great mountain.
”-type: finding the target-goal: reach the ‘king’s mountain cabin.
’-reward: qualified for ‘extra hidden quest’.
*the “king of the great mountains” who rules mt.
 taebaek wants to face the strong man who defeated one of his “vassals”.
 he’s not a violent monster but a rational being.
 he wants to interact with qualified players.
when you face the king of the great mountain, you will get an ‘unexpected quest’, and that quest can make a big change in your destiny.


* if you cannot clear the quest within 48 hours, the ‘hidden quest’ will be canceled.
* the king of the great mountain is going to test you.
 as you get closer to the king’s mountain cabin, you will confront more fierce monsters.
jisu continued, “after wandering the mountain for a long time, i was able to meet the boss monster called the king of the great mountain.
 well, it looked like the monster serpent imoogi…”she said she could converse with the king, but what she said next was surprising.
“king of the great mountain, he gave me a quest.
”she not only conversed with him but also received a quest from him.
 this meant that he was not just a boss monster, but also he played the role of an npc.
“which quest was it?”“he told me to find the item called ‘ginseng of the mountain spirit’ that had been stolen by the struggle guild.
 as a reward, he offered the last item of shadow king that you are trying to collect and my awakening.
”‘awakening’ was a privilege that was given to only those players with four-star jobs who cleared the ‘exclusive quest’.
 unfortunately, she could not receive the exclusive quest in the past because she chose a three-star job, ‘tiger fighter.
’however, she could finally obtain the qualifications for the quest thanks to the hidden quest.
“and the legacy of the shadow king…”sungwoo didn’t know the king would mention that name.
jisu said, “oh, the king of the great mountain asked me to choose an item for an additional reward, so i immediately took notice of that item because you needed it, sungwoo.
”the last item sungwoo had been looking for was on mt.
 taebaek.
jisu noticed and selected it as a quest reward.
“but how did you get here? it must be quite a long distance between here and mt.
 taebaek.
”“ah, i was helped by the king of the great mountain.
”the king of the great mountain gave her an item with which she could open the portal to her desired destination.
then, she predicted that sungwoo, who had defeated the struggle guild, had the ‘ginseng of the mountain spirit,’ so she opened the portal to suwon.
“given that the king has helped you so much like this, it seems he badly needs the ‘ginseng of the mountain spirit.
'”“i think so.
 we don’t know why he needs it, but that’s what we need right now.
”sungwoo nodded and pulled out the ‘ginseng of the mountain spirit’ from inside the pocket.
it was an item that he obtained from bumyol after he was killed.


 