\section{chapter 399}

something was running through the collapsed terracotta camp by passing through a storm of thick flames.





'lizard?'general lee looked at the scene, keeping his balance while grabbing the ground.
what he thought was a lizard was a huge bone.
 to be precise, it was the bone of the creature that could withstand such powerful explosions and flames, namely salamander.
on top of him was the necromancer.
"uh? come on, i can't believe it!"general lee sprang to his feet, startled.
the necromancer, who broke through the flames, swung a huge black scythe at the emperor.
the fight between both sides was going on along the road about two kilometers from the invisible barrier of the fortress' wall.
kyungsoo was worried that the wall and the barrier were separated from each other, but sungwoo thought that the gap between them could serve as a kind of "buffer zone" to prevent the enemy's main force from approaching the wall.
 'they fell into a trap.
'sungwoo instructed kyungsoo to bury the corpses of monsters and various flammable substances under the buffer zone very deeply, so the enemy would not notice it.
'well they noticed it later, but they couldn't stop the explosions.
'surprisingly, shortly after the high-pressure explosions began, the emperor noticed that something strange was happening underground.
 he succeeded in using a large terracotta to dig up the ground and pull out a few swollen corpses.
'how did he feel it?' sungwoo wondered at first.
but that was it.
 the emperor could not process all the corpses within 30 seconds.
eventually, they exploded.

the flames from the corpse's explosions absorbed all the combustible substances that had been buried there and made the explosions bigger.
 then, they popped out after breaking through the ground and devoured everything.
'now is the time.
'the overwhelming number of troops that stood between the emperor and sungwoo were temporarily neutralized.
 not all the terracotta were smashed, but since the ground shook violently, there were only a few of them standing properly.
 above all else, the emperor who was controlling them could not see clearly.
 in other words, if an unexpected situation unfolded now, he would not be able to properly respond.
'alright.
 let me behead him right now!' sungwoo muttered.
in fact, it was a huge gamble.
 since he hadn't yet sized up the emperor's ability, his jumping into the middle of the enemy camp was like a moth flying into the fire.
however, since sungwoo wanted to end the fight as soon as possible, this was a golden opportunity to get rid of the emperor.
sungwoo got on top of the 'bone salamander'.
 since the salamander was a fire spirit by birth, he could run faster in such wild flames.
gugugugugugu-even though the ground shook, flames soared, and a gust of wind blew, the bone salamander didn't care at all, smashing the terracotta strewn across the ground, and running through the rough terrain.
sungwoo also did not feel any discomfort thanks to his tremendous fire immunity.
watching the blue shield floating in the air, he pulled out the grim reaper for a powerful blow.
- 'evil spirit bombing is embedded in your weapon.
 (max)he finally got close to the emperor.
 he could not see clearly because of the emperor's blue shield, but the emperor was also staring at him.
at that moment, golden threads spewed out from within the blue shield.
as he saw it before, it was a powerful attack that destroyed all the buildings in the area.
bang!
the threads fell, causing a loud bang.
 the huge body of the bone salamander was crushed in an instant.
 but sungwoo was not there.
 using 'shadow movement', he got up under the shadow of the giant terracotta behind the emperor.
 then, he leaped and swung the grim reaper towards the emperor, unleashing 40 evil spirit bombing.
' at once.
'they hit it!'black spheres were shot in a straight line and hit the blue shield floating in the air.
gugugugugugugugu-because of the impact, the shield was twisted in the air, creating a crack in the blue shield.
then, it was thrown away like a kicked ball.
 sungwoo kicked the ground and jumped up to chase him.
a single golden thread flew towards sungwoo.
 but anticipating the attack, sungwoo twisted his body and pulled out the 'winter predator' he was carrying on his back.
 then, he fired it.
the whole golden thread froze in an instant.
 sungwoo stepped on it and took another leap forward.
soaring into the air higher than the emperor, he fell in a parabolic shape and slammed the grim reaper down through the cracks in the broken shield.
the huge black scythe struck him directly on the forehead, but something was strange.
it sounded like a thin shell splitting as if he hit a gourd.
'terracotta? no way!'this was not the emperor.
 even this was a clay doll, terracotta.
 and some unstable energy was within its body.
"shit!"sungwoo hastily turned around.
bang!the terracotta exploded right away.
 it was a pretty powerful bomb.
it was the same type of explosive terracotta that had infiltrated the world tree camp in the past.
'i was too complacent.
'sungwoo didn't expect at all that it was camouflage.
 since the emperor was thoroughly protected by a large number of troops, not just surrounded by the thick shield, he naturally thought that was the emperor.
'then where is the main body of the terracotta?'sungwoo quickly avoided the aftermath and looked around.
 however, it was close to impossible to identify the main body among the numerous terracottas.
and at that moment a gust of wind blew from somewhere and threw sungwoo into the air.
 it wasn't a mere blast.
"ugh, what the heck is…"it soared hundreds of meters into the air after causing tremendous damage as if it had been hit with a hammer.
 that wasn't the end.
woo woo woo!the air around sungwoo turned sharp like a knife and closed in on sungwoo as if to tear him apart.
 it was quite high-level magic.
'if i stay here, i will die!'each wind blew toward him sharply like a dagger.
sungwoo curled up to protect his exposed skin.
 at the same time, he prepared a skill for escaping.
- 'twilight assault' has begun.
although he recklessly plunged into the enemy camp to capture the emperor, he also thought about escaping just in case.
 'twilight assault' was the answer.
 that's why he saved it, even when he attacked the emperor.


woo woo woo!sungwoo's body was engulfed in black smoke and got out of the biting wind.
'thank god.
 without it, i would have been torn to pieces.
"while escaping from the place, sungwoo sensed the flow of mana that controlled this wind.
then, he looked toward the source of the flow.
someone between the densely standing large terracotta near the hole of the invisible barrier was reaching out to sungwoo.
 it was clear that he was controlling the wind and the clouds.
when he looked closely, the person in question was a pale-faced woman.
'it is a divine status.
'sugnwoo felt some powerful power, namely a deity in her.
'but, that's not the emperor.
'her power seemed unrelated to the terracotta.
then, she grabbed her hands and pulled something toward her.
'above my head?'a cluster of clouds gathered above sungwoo's head, then began to hang down like an anaconda.
at that moment, a huge cloud turned into water with an explosion and hurled towards sungwoo.
she seemed to be able to control water like li wei, but she didn't seem to control the water spirits.
'what is her job? how can she control the clouds and the wind?'

 