\section{chapter 360}

chapter 360: devil’s world tree and world eater (2)after checking the gate, kyungsoo shouted at sungwoo, “well, we need special conditions to enter this place! it seems difficult to open it forcibly, so i think you need to take care of it in person.
”




“please wait.
”sungwoo had to do something first.
 he stood in front of the dragon’s bones then held out his hand on its front claws.
“stand up!”it was none other than a dragon’s bones, so he had an opportunity to obtain the best subordinate spirit, but he had to meet some pre-conditions first.
- special conditions (proof of qualifications) are required for you to resurrect the deceased as your subordinate spirit.
as expected, this didn’t seem easy.
 however, a familiar word stood out in the message.
“proof of qualifications?”when it comes to the proof of qualifications related to a dragon, sungwoo had experiences with it before.
 actually, he succeeded in transforming the ‘ownerless sword’ into the ‘ruler’s sword’ after possessing it for 5,000 days and hatching mir.
so sungwoo immediately summoned minsok and received the ‘ruler’s sword’ from him.
[item information]- name: ruler’s sword- grade: mythical- category: two-handed sword- effect: with stamina (+10) you nullify your opponent’s defense effects.
 (20%)- description: this is a key to awaken a black dragon and the symbol of a leash with which you can handle the dragon.
 you are the master of this sword, so you will get a new name for it, based on your performance.
he tried again, holding the sword in one hand, but failed.
- the item in question has been already linked to another creature.

only then did sungwoo grasp the situation.
“oh, i see!”in order to control a transcendent being called a dragon, even a 5-star dragon knight needed to show proof of qualifications.
 and the key was the ‘sword of the ruler’, and each of them received the sword in person.
in other words, he needed another sword connected to this dragon.
“kyungsoo, did you happen to find a sword that has lost its owner among the items?”there was a high possibility that the dragon knight was killed somewhere here.
“huh? wait a minute.
”kyungsoo asked all the members of the expedition about it, but no one said they did.
“they said they didn’t see any such weapon among the items they obtained.
 let me take a careful look again just in case.
”the expedition searched through the inside of the cave again.
 they even looked under the dragon’s bones and rubble, deep pits, and the roots sprouting from the wall.
 but they could not find ‘the ruler’s sword’.
‘if that’s the case…’sungwoo turned his head.
 he thought there must be something behind the huge door blocked by the dragon’s bones.
‘yeah, what the dragon was trying to protect was the dragon knight.
 he wasn’t killed here.
 maybe somewhere there.
’sungwoo approached the iron gate.
 it was made of metal, but it emitted a turquoise glow as if it were made of bronze.
kyungsoo said, “i don’t know how to open this gate.
 when one of our crew touched it, he said he saw a message about some conditions to open it.
”- this is a space sealed with powerful magic.
 only those with ‘special qualifications’ can open the door.
as kyungsoo said, this was a place with restrictions on entry.

but the next moment another message rang.
- you have met the entry conditions.
 the ‘hall of the guardians’ will open.
sungwoo looked at the message for a long time.
 entry conditions? guardian? did it mean only the man with the title of guardians could meet the entry conditions?what about the ‘hall of guardians’ inside the ‘devil’s world tree’? sungwoo could not match both names at all.
finally, the iron gate opened slowly with a heavy noise.
“ready for battle!”all of the expedition members raised their weapons as soon as kyungsoo shouted.
some of them hid behind the dragon’s bones because it seemed that the door opened automatically instead of sungwoo opening it.
 in other words, they were prepared for the possible appearance of the enemy.
soon, the iron gate was fully opened.
the green-lighted interior was revealed, and the air that had been trapped for a long time came out.
 there was a faint chemical smell in the air.
sungwoo took his first step towards the door.
- you have entered the hidden stage ‘hall of the guardians’.
again, the message was related to the guardian, which frustrated sungwoo.
“let’s go in while staying alert!”the expedition team followed sungwoo into the gate.
 they didn’t forget to keep an eye on their surroundings while walking at a certain distance.
“this place is so complex, and you never know where monsters are going to pop out.
 so, stay alert.
”the inside of the gate was as wide as the cave that they just passed by, but unlike the empty cave, this place was a very complex facility.
 since there were green lights shining here and there, they could see faintly.
 something like a multi-story gallery continued to the left and right, where rectangular objects were lined up as if they were entering the library of a giant.
from a distance, it looked as if somebody inserted a thick book.
“what is that?”“it looks like an experimental tank.
”it wasn’t a book, but a rectangular tank of liquid.
 when sungwoo examined it closely, a green vine protruding from the ceiling was holding the tank tightly.
even the liquid inside the tank seemed to be supplied by the plant roots.
 overall, it resembled a laboratory capsule device.
 but what’s inside that capsule seemed very strange, though.
“sungwoo, there is a human inside the capsule.
”it was a human player.
“it’s not a monster, but a human.
 and when you see the air bubbles coming out, he is still alive.
”hundreds, perhaps thousands, of sleeping capsules filled this room.
for some reason, it appeared that all of them were preserved alive using special techniques.
“this is nonsense!” li wei murmured.
sungwoo felt the same.
 he couldn’t help but be shocked at the terrible scene.
how could they survive in a world of demons ruled by a transcendent being called the world eater? what if they were humans preserved in the hall of the guardians that only guardians could enter?‘then these guys are the guardians of this world?’at that moment, li wei approached sungwoo and said, “necromancer, what do you think of this scene…?”but there was nothing sungwoo could figure out.
 so he shook his head silently, and she let out a sigh.
she said, “didn’t i tell you this could be another world that already faced its ending? then, who are they and how come they are here?”

the people were asleep in an abandoned world.
 if they were asleep now, could they wake up again one day?‘it’s ominous.
’sungwoo felt like he was tracing a secret that he didn’t know.
 while he was lost in complicated thoughts, somebody suddenly shouted, “another door is ahead of us.
”again, a metal door appeared.
 it was a little smaller than the door they just passed through.
but this time the black lion responded.
 he frowned heavily and stared at the door.
“it’s over there.
 i can feel a strong sense of power there.
”finally, there was something over that door that sungwoo had been looking for.
he looked back at kyungsoo and said, “prepare for battle!”the expedition team checked their weapons and skills, while sungwoo opened the door after summoning minsok and durahan.
when he put his hand on it, the heavy door opened by itself.
thump!- you have entered the hidden stage ‘cradle of the victor’.
sugnwoo looked at the message carefully.
‘victor? what the hell does it mean?’incomprehensible puzzle pieces came out randomly in his mind, confusing him.
“damn it, this place is covered with roots everywhere.
”

 