\section{chapter 432}

chapter 432: the world tree camp’s advance (2)sunika couldn’t help but worry that the angel commander might be offended when he asked again.
 even though the angel didn’t have eyes, sunika raised his head to check his expressions instinctively.





koooooooooooo-at that moment some black smoke came from somewhere and landed on the angel commander’s head.
“what the heck is that?”sunika stepped back in embarrassment.
“how can’t the messenger of the gods see even an inch ahead?”when the smoke disappeared, a man in a dark green robe was standing on the angel commander’s head, and at the same time, numerous hands rose from the ground and bound him.
“argh! who the hell are you?”the angel commander asked, tightly bound by the hands.
 but the necromancer wielded the black scythe at him faster than he spoke.
puck!he was instantly beheaded.
clang-it seemed as if the black scythe hit his head and scratched the floor of the altar, but the altar was split in half because of its impact.
[how can you wound my sacred body…?]however, the angel commander was not yet dead.
 and the necromancer knew it too.
 some translucent ghosts flew in from somewhere.
puck! puck! puck! puck!they descended fanatically, then stabbed him with swords and spears.
[khuuuuuuuuuuh…]since he was a boss monster, he didn’t die easily, but he could not withstand such a massive attack by the ghosts at the same time.

“you must be the necromancer!”sunika immediately recognized him.
 needless to say, he was the necromancer, the head of the world tree camp.
but sungwoo didn’t even pay attention to him.
 he just stood on the head of the angel commander, raised his head, and looked up at the sky.
heeeeeeeeeeee!suddenly, the special commando unit appeared from somewhere and began to wipe out the angels floating in the sky.
marble fragments fell from the sky like pouring hail.
“i knew it…”watching them, sungwoo nodded.
 as soon as they appeared, they killed the boss monster.
then the angels around them started to get confused, not even responding properly.
 ‘yeah, he must be their boss…’although the angel race was designed intellectually, they seemed to operate in a system such as the ‘hive mind’, a single mind that ruled multiple entities, unlike their looks.
even though angels were still coming out of the hole in the sky, they looked flabby as if they were a swarm of worms hit by insecticide.
‘it was good that i got rid of the boss monster first.
’of course, he would have won even if he had an all-out war with them, but he could save time by getting rid of the boss monster.
sungwoo turned his head and looked at the golden knight, sunika, lying on the floor.
“are you done praying?”“…”“if not, you can stop now.
 the guy who will listen to your prayer…”he rolled the angel commander’s cut head to sunika, on which he had been stepping until then.
 sunika looked down at the terrible thing that rolled down under his feet.

“i beheaded him…”wooooooo-then a huge shadow came down with the roaring sound of engines.
 the airships began to fill the sky which was empty when the angels fell from it.
bang! bang! bang!the airships went ahead firing shells towards the blue portal, getting very close to it this time unlike before.
 soon they narrowed the distance close enough to get into the portal.
their advance looked risky but was part of the necromancer’s operation.
“from now on we’re going to close in on the angels and block their escape!”when inho issued the order, the hippogriffs of the messenger began to move briskly.
they moved back and forth between the airships, starting to tie them with long ropes.
hundreds of long ropes were tied to form a huge, tightly woven net.
“we’re done connecting a total of 155 vines of the world tree!”the material of the ropes was ‘the vines of the world tree’.
“great! block it!”when the airships ascended vertically, the wide net made of vines of the world tree covered the surface of the blue portal and blocked it.
“we’ve succeeded! they can’t come out!”even though the angels tried to come out of the portal, they could not easily cut off the tough vines of the world tree.
“push the bombs inside the portal right now!”they were going to block the holes of the sky, so they could not come out, then push the bombs inside.
 the more they fought the absolute races, the more they improved their attack strategy.
 obviously, their attack was overwhelming.
“man, how can they call themselves the messengers of gods?” sungwoo sneered at them.
 “they didn’t even know we were coming.
 after all, they were no more than typical monsters as needed in the game scenario.
”having said that, the necromancer approached sunika, then smashed the angel commander’s cut head to pieces.
watching all this terrible scene, sunika couldn’t hide his shock.
“monster?”since sunika survived and grew by relying on the power of the angel race, he just trusted their power blindly until now.
“aren’t they the subordinate spirits of the gods who had the power to end this ordeal? i think you guys made a big mistake…”but sunika could not finish his words because the necromancer was casting a murderous glance at him.
“stupid guys like you complicate matters and make things worse when i can solve them easily.
”having said that, sungwoo walked toward him with big strides.
“you know what? you can’t do such bad things only when i behead your stupid head just like these worm-like angels…”then sungwoo beheaded him right away.
 he got rid of the angel commander and the head of sunika who brainwashed the vietnamese players.
and he was almost done annihilating all the angels near the portal.
at that moment a message rang.
- congratulations! you have successfully defended the ‘mumbai battlefield (city)’ of indian server 2.
* 100 points will be awarded to those who chose to ‘fight’ in the area.
it was already the 20th message that sungwoo saw.
but this time it was rather different because there was another message.
- a ‘hidden event’ begins because you have protected a total of 20 servers.


“hidden event?”after checking the message, he raised his head and looked up at the sky.
whoooooooo-there was something strange about the blue portal in the sky.
 it began to whirl violently and throw out the wind.
‘something is going to happen.
’soon, the sky split in half around the portal.
“damn it! what the heck is that?” someone shouted.
obviously, it was terrible.
 it was as if the sea was splitting over their heads.
- you can enter the hidden stage ‘hall of angels’.
‘is this where angels live?’ sungwoo thought to himself.
that was not all.
[exclusive quest]- name: guardian’s counterattack-1- type: destroy target- goal: destroy the ‘hall of angels’- reward: upgrade to deity status.
 special awakening (dimensional predator) quest.
*as the ‘guardian’ of a world, you have finally found the passage to the world of invaders.
 if you go there and eliminate the ‘world seed’, the central axis of the world, you will be able to neutralize the world of the invaders.
 furthermore, you may get some ‘special power’.
* when the hall of angels is destroyed, all portals of the ‘angel race’ open to the world will be closed.
after all, the ‘guardian’ was the one who protected this world.
 and the last way to protect this world was to eliminate the cause of that threat, those who attacked it.


 