\section{chapter 187}

                            a total of 25 players were moving between the buildings.
 a road sign above their heads indicated they were going to suwon.





“we’re almost there! suwon palace is around the corner.
 we’ll move after a 10-minute break.
”they hid in the alley and began to rest.
 in the meantime, some of them were on sentry guard, which suggested that they were an organized group.
“captain, is it true that we have received 3.
5 million gold for this service? isn’t it the highest amount until now?”“i don’t know how much they agreed to pay us, but given the strength of our opponent, we have to receive a lot this time.
”the name of their organization was the “hunter company,” a group that those players who frequently used the korean server community would have heard of at least once because they uploaded promotional posts about their activities several times a day.
the threads they posted were as follows.
[501] if you need mercenaries, please contact us.
-write: captain yang │ hits: 1,413*we are the hunter company, a group of 122 mercenaries.
 we take care of everything when you need force.
 (monster hunting, dungeon crackdown, security, combat, etc.
)as of now, the average level of our members is 10, and in some cases, we can run a party with level 13 higher.
 (maximum two teams with ten members available.
)expenses are determined after you consult with us, but we may ask for additional charges afterward.
 we’re running our company based on trust.
 if you trust us and leave your work with us, we’ll never disappoint you.
[comment: 1]what do the players in the perished world need but avoid the most? it would be them fighting at the risk of their own lives.
 it was the hunter company that realized they could make lots of money by providing mercenary services.
 they were marketing their armed forces widely to earn a lot of gold.
 in short, they were mercenaries.
according to the terms of the contract, anybody who signed the contract was supposed to upload their review of their service on the community bulletin, so rumors about this company spread widely, attracting lots of customers.
“3.
5 million gold? well, this is pretty good, but i don’t think many would come out for this job.
 look at the 1st league guys.
 only a few of them have applied.
”this was a big job with a lot of money at stake, but the hunter company members looked nervous, even though they were professional mercenaries, their target was very unusual and extraordinary.
“damn it! how come our target is the necromancer? are we going to be okay? just watching him fighting scares me.
”the captain frowned at one of his members’ diffident attitude.
“what is the problem? we will be alright as long as we can hide our identities.
 anyway, he is destined to get stuck in taiwan for 24 hours.
 during that time we can attack his stronghold and escape.
”the leaders of the hunter company knew well that it would be crazy to attack the necromancer, but okayed the contract because their professional mercenaries would not deal with him directly.

their target was not the necromancer himself, but his stronghold and those around him.
“yes, that’s right.
 by the way, what’s this evolutionary society? who are these guys belonging to that organization? just hearing the name makes me feel they are not normal.
”“hey, stop talking bullshit! no matter what, we should not leak our client’s name to the outside.
 so, shut up!”“absolutely!’it was none other than evolution society that hired them.
 since they lost many members during the raid in pyongtaek, they were not in a position to confront the necromancer directly.
 so, they signed a contract with the hunter company, which had recently gained fame and trust, to attack the necromancer’s hometown, suwon village.
the captain of the team took out a canteen and drank water.
then, he stood up and said, “24 hours is enough for us to destroy a building housing 200 people quickly and get out safely.
 according to our client, there is a strong invisible barrier around that area, but…”the captain pulled something out of his pocket.
 it was an item given by the client called ‘evolution society’.
[item information]-name: mana reflux device-grade: player manufacturing-category: consumption-effect: you can reverse mana and destroy the spell.
-description: install this near the invisible barrier and inject mana.
 in about 10 minutes, it will make a hole in the barrier.
 good luck.
 (manufacturer’s skill)“okay, let’s move now.
 this time we’re going to tear down the stronghold of the necromancer.
 no matter how strong he is, he won’t be able to survive if his stronghold collapses.
”they were certain that the necromancer would not come back within 24 hours.
***around that time, the “devil’s gate,” which opened in front of the chiang kai-shek memorial hall in taipei, taiwan, was shaking violently as if it would burst at any moment.
gugung― gugugu―the taiwanese players who rose up to reclaim taiwan with jisu attacked the heart of the pirates and quickly arrived at the square.
 they witnessed the white demons, namely the undead army, surrounding the devil’s gate.

“well, is he the necromancer?”“terrific!”there were a total of 95 undead under the necromancer’s control.
 all of them were wearing bone armor and holding bone shields and were not normal undead.
armed with all sorts of synergies and buffs, they were truly the strongest army in existence.
[synergy list]company organization (hidden) -category: synergy of the members-condition: commander (level 3) trait + 90 or more members-effect: attack power increases (+7%), defense power increases (+7%), additional damage (+3%) when attacking a single enemy jointlyshield dustproof (2nd stage)-category: weapon synergy-condition: equip at least 60 shields-effects: shield defense increases (+10%), shield magic defense increases (+10%), shield attack increases (+30%), with shield attack, knockback rate increases (+15%), abnormal state resistance increases ( +20%)giant (step 5)-category: trait synergy-condition: 50 or more ‘giant’ traits-effect: reduces damage by small and medium opponents (-40%)ironclad knight (stage 7)-category: armor synergy-condition: install more than 70 ‘full plate armor’-effect: increases armor defense (+45%), forms a shield equivalent to 45% of defense.
based on his fighting experiences so far, sungwoo carefully selected synergies specialized in defense against multiple attacks.
but this was not all.
-you have strengthened the undead with exploited souls.
 (max)attack power increases by 50% (+5)increases defense by 50% (+5)40% increase in magic immunity (+4)moving speed increases by 40% (+4)abnormal state resistance increases by 20% (+2)he took hundreds of souls by killing the pirates and invested most of them in ‘strengthening the undead’ to achieve their maximum power.
 as a result, he enjoyed a huge increase in power.
the necromancer grew stronger with more battles.
 it was this immortal army of undead that verified sungwoo’s power.
‘the portal entrance is narrow.
 if we block this and get rid of them popping out of the portal, we can easily defeat them with an overwhelming advantage.
’after confirming the warning message on the survival, most players already started thinking of running away and hiding.
however, sungwoo’s goal was different.
 he could make the decision boldly because he was preparing to hunt, not merely survive.
-the ‘1st wave’ of the devil’s gate has begun.
it has finally begun.
gugugugugugugu!

with tremendous vibration, black hands popped out from the portal’s entrance.
kaak! kaak! kaak!the ‘low-level monsters’, one of whom sungwoo had already hunted, began to crawl out, making disgusting sounds, like a swarm of insects born in an ootheca.
-your deity status drastically reduces the stats of the ‘low-level monster’.
 (-30%)“attack!”the moment the monsters pushed their heads outside the portal, the undead blocking the entrance moved swiftly.
two-woong! two-woong!troll skeletons triggered the slingshots and human beast skeletons threw javelins at them.
 their target was a circular portal that was only 3 meters wide.
 they hit the target accurately.
-you have earned 500,000 gold by hunting ‘alien beings (lower monsters)’.
-you have exploited a soul.
 (14 items)-you have earned 500,000 gold by hunting ‘alien beings (lower monsters)’.
-you have exploited a soul.
 (15 items)-you have earned 500,000 gold by hunting ‘alien beings (lower monsters)’.
-you have exploited a soul.
 (16 items)most of the monsters that came out first could not withstand the fierce attack and bounced back into the portal.
 those who didn’t were shattered and fell to the ground.
the entrance of the portal was too narrow for them to counterattack.
 besides, sungwoo’s undead army blocking the entrance was too strong.
“explode!”bang! bang! bang!two demons succeeded in coming out from the portal for a few steps, but they were caught in the explosions and bounced in front of the undead army.
 the skeletons immediately threw long spears at the monsters.
-1st wave underway (13%)

 