\section{chapter 351}

chapter 351: jeju island and attack on demon’s cave (15)in orum on jeju island and the battlefield without the necromancer, those who were confronting the demons there didn’t feel at ease.





the absence of the necromancer meant they were without their greatest supporter, which, in turn, would lead to their inevitable defeat.
“whew…we have to hold out here for the success of our operation, right?”“yeah, but it’s not difficult.
 we did well in the battle of suwon a while ago, right?”despite the absence of the necromancer, they had no intention of backing down.
actually, they had been growing their power while they stayed with the necromancer.
they have also experienced many times how powerful they were.
 so, all they had to do was to prove it once again.
“to arms!”“let’s fight!”they shouted, raised their weapons, and glared at the huge purple portal.
when the messenger swooped in, the demons that opened the portal were swept back in, but they began to appear again.
kheeeeeeeeee-horrible demons, totally different from the beasts in this world, came out of the portal with screams this time.
- you have been overwhelmed by the intimidation of the ‘alien creatures’* all stats will drop.
 (-20%)“argh!”“man, my body seems to be stiff!”in fact, they were already told that their bodies would be stiffened in this situation.
 in other words, they were told that when the demons appeared, they would not be able to move quickly, overwhelmed by the demons.
 but when they actually experienced it, they felt they could hardly move even to the point that they could hardly breathe.
“hey, we’re still stronger than ordinary people.
 so, don’t be scared!”
“fire! don’t hesitate to fire!”they moved more heavily than before, then started firing at the gate of the demon’s cave.
shuuuuuuung!they first fired arrows.
 the archers fired precision arrows at the demons squeezing out of the entrance of the sticky portal.
kheeeeeeeeeh! kheeeeeeeeh!however, soon several of them jumped out of the portal and fell to the ground.
 from that moment on, they couldn’t block the demons with arrows alone.
“prepare the magic attack!”the demons were tremendously resilient and speedy.
 as long as they were alive, they would charge and smash the players in the blink of an eye.
so, sungwoo’s allies had to kill them before they attacked.
“1st row of the no.
 1 team, attack!”the wizards who were forming a group in the rear stepped forward.
 they moved like well-trained musketeers.
 ten of them at the first line shot their prepared fire magic.
whooooooooooo-10 magic blasts were shot at once and exploded at the portal entrance.
bang!a huge flame and heat arose at the center of oreum.
kheeeeeeeeee-but the monsters weren’t killed yet.
 even though they were hit by dozens of arrows and burned by 10 magic shots, they raised their battered bodies.
 then, they started running towards the players.
“damn it! how could they raise their bodies?”
watching them in shock, the jeju players including jimin could not help but be terrified.
“how could they survive after they were hit like that?”“then, why are we here fighting like this?”some of them began to regret taking part in this battle.
 they were obviously suffering from the nightmare of the demons’ attack on jeju island.
 their witness of the demons fighting right before their eyes made them skeptical about their fighting and get cold feet.
“next, fire blocking magic!”in contrast with the terrified jeju players, the world tree players were not embarrassed at all.
 as a matter of fact, they became stronger while confronting such evil monsters.
with the freezing magic exploding, they blocked the demons charging at them.
 those magicians specializing in freezing were placed at the frontline to block the demons from approaching.
tung- tung-immediately after the iron spears fired by ballistas stuck into their chests, the demons stopped on the spot.
“finally, one of them was killed!”the jeju players let out a sigh of relief, but it was too early for them to feel relaxed yet because they killed only one demon.
“oh my god! they’re pouring out!”the demons that were entangled in the sticky portal poured out like a bag of flour bursting out.
the resistance of the portal reached its limit.
 in the end, dozens of demons set foot on the ground.
“fire as many arrows as possible!”arrows rained down on them, large-scale magic attacks exploded in succession, and cannons surrounding the portal were fired one after another.
bang! bang!in addition to that, dozens of flying weapons that could be used for breaking down walls were mobilized to intensify all firepower on the demons.
 even huge roots soared up from the ground, entangled with each other, then turned into something like a giant serpent.
 above it stood a man in a robe.
“you damn bastards are crawling like bugs here and there!”shouting like that, the man stretched out his hand.
 one of the roots bound a monster and pressed it down.
 surprisingly, the monster died instantly.
“that man is wearing a strange korean robe and holding a smoking stick in his mouth.
 who the hell is he? is he an ascetic?”“i guess so.
 what the hell is his job?”the crusader team members fought well, too.
 they were maintaining cannons with a very long muzzle, not the giant crossbows they had been using.
“fire!”bang! bang!the object fired a white beam of light.
 when 20 of them fired it at once, three monsters melted and disappeared at once.
“man, these guys are just amazing…”jeju island players felt like they were watching a spectacular scene that they had never seen before.
 they were even stunned to see the occasional message about gold.
- you have obtained 24,550 gold by hunting ‘alien creatures (lesser monsters)’.
- you have leveled up.
 (lv.
 14)jimin doubted her eyes.
“i hit them with only two shots.
”she fired only two arrows with a crossbow to hit them.
 when they were killed, her performance was instantly calculated, giving her enormous gold and level-up.
‘if i could continue to stay with them…’jimin looked at her sister, jisu, who was standing nearby.
‘i guess she must have grown stronger fast with this strong army.
 i now understand why she showed such confidence to me…’

but jisu didn’t take any action yet.
 with the sword in her hand, she was just watching the situation on the battlefield that was unfolding rapidly.
 she seemed to be waiting for something.
‘if she used a sword in this situation, it would be crazy for her to fight the monsters at close range.
 she can’t do anything here.
’jimin still didn’t know much about jisu.
 it was natural she didn’t know because she had never asked her sister about her performance in detail.
 aside from the fact that jisu was pretty strong, jimin didn’t even know she was no.
 4 in the korean server rankings.
“stop shooting!”inho’s voice resounded through the loudspeaker.
 soon, they stopped attacking at once.
the area near the portal became silent.
kugugugugu-the dust and heat generated by the aftermath of their firing scattered in all directions, revealing the area near the portal.
“…”hundreds of corpses of monsters were scattered all over the area devastated by the bombing.
they successfully blocked the first wave of monsters.
 but there was only a heavy silence among the players.
“did we win?” jimin asked jisu,she said, shaking her head, “no, not yet.
”-you have blocked the 1st wave of the gate of the demon’s cave (2nd floor).
 after 20 seconds, the 2nd wave begins.
“only now has the fight begun.
”“really?” jimin said, raising the crossbow.
at the same time, she was puzzled.
 why wouldn’t her sister fight this time when even one more player would be a big help to sungwoo’s allies? even though she specialized in melee combat, shouldn’t jisu try to be of some help, using a ranged weapon like her?

 