\section{chapter 349}

chapter 349: jeju island and attack on demon’s cave (13)bang! bang! bang!




two cannons exploded in a row.
 a fire broke out among the monsters that covered their heads with something black.
“no way! cannons aren’t effective!”the demons did not collapse as easily as the hippogriffs that they encountered on jeju island.
although those who were hit by cannons lost their balance and fell, those around them just staggered as if they were a little shocked.
kheeeeeeeeeeee!their descending speed didn’t decrease, so they were close to sungwoo’s party within several moments.
“sungwoo! they’re coming down!”“damn it! flowing barrier!”shouting like that, li wei stretched out her hands.
 then, the small ‘water spirits’ that had been summoned behind her back jumped into the air and spread widely, covering the upper part of the airship like a dome.
kugugugugugugu-to be precise, it was a stream of water running down wildly while maintaining the shape of a dome.
“it’s a shield! all i can do is push them with this! but it can’t sustain long! damn it, i wish i had the high-grade spirits…”the airship’s own magic shield and liwei’s shield covered sungwoo’s party with two layers.
“yeah, this is not bad,” sungwoo nodded with satisfaction.
 the two layers of shields could protect them only briefly.
kheeeeeeee! kheeeeeeeee! kheeeeeeeee!a disgusting scream grew louder and louder above their heads.
 it looks as if they were about to smash a fragile airship like this to pieces.
“sungwoo, you must be calculating something, right?”while the others looked at him with fear and nervousness, sungwoo held his breath and waited for the right moment to attack them.

‘come closer.
’and when the monsters finally came within a certain striking range, a one-line message came to my mind.
- your deity status greatly decreases the stats of ‘intermediate monsters’.
 (-25%)“i knew it.
”no matter how strong they were, they could not help but feel intimidated and overwhelmed by sungwoo’s deity status just like the monsters sungwoo encountered in taiwan did.
kheeeee?not surprisingly, the monsters descending at full speed hesitated for a moment then slowed down.
 that meant that sungwoo finally seized the moment to attack them at the right time.
“now is the time to attack them! throw the hooks!”the troll skeletons threw the special hooks with all their might.
 the hook soared vertically then got sucked into the gap between the demons.
tung-tung-tong-tong-all seven hooks were caught somewhere and pulled tightly.
“release your tight grip!”as soon as sungwoo shouted, the troll skeletons let go of the hooks.
 then, the hooked monsters instinctively began to climb higher to shake off the hook.
as if a heavy anchor got loosened, the vines of the world tree were sucked up in an instant.
‘good.
 soar higher…’the hooked ones panicked and began to fly around wildly like flies sprayed with insecticides.
‘great.
’it was at this point that this bizarre weapon showed its true value.

hundreds of blades on the vine began to stir in the air according to the movement of the hooked monsters.
 those who just instinctively flew without a regular lineup could not avoid the long ‘straight line’ of the blades rushing through the air.
 besides, they found it even harder to avoid the lines because there were seven, not just one.
“what the heck are they?”“oh, my god…”it was as if 7 mowers with long “nylon cutters” were plowing through a swarm of grasshoppers.
“catch the vine again!”when the troll skeletons grabbed the vines, the ascending hooks began to pull them again.
 thanks to the magical power of the world tree vine, they could pull the monsters very easily.
this time, the vines swayed in all directions and tore everything that was caught in between.
torn flesh and severed limbs poured over the shields.
 in particular, the film of their wings was torn too easily, so those who lost their wings fell like fire moths.
kheeeeeeeeeeee-- you have obtained 850,000 gold by hunting an ‘alien creature (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien creature (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien creature (intermediate monster)’.
sungwoo obtained a whopping 850,000 gold per monster.
 this was really enormous.
along with the gold, he also obtained a huge amount of exp.
‘this is definitely the best hunting ground ever.
’depending on how it was used, the cave could become a ‘gold mine’ that would give enormous exp and gold.
but sungwoo could not yet be complacent.
“they’re charging at us from the 3 o’clock position!”even if the blade vines were powerful, it was impossible for sungwoo to completely cut off thousands of demons with them alone.
 in the end, dozens of them landed on the shields of the airship.
tung! tung! tung! tung! tung!when they raised their claws and scratched the shields, the shield that li wei created began to shake, incurring unbearable damage.
“get away!”as li wei stretched her hand upwards, the shield made of water spirits roared violently, repelling the monsters clinging to it.
“argh! shoot something!”since the monsters bouncing off from the inside passed through the shield, sungwoo lifted the winter predator and started intercepting them one by one.
clang! clang! clang!of course, it was impossible to kill them instantly, but just by freezing their wings, he could induce them to fall.
- you have obtained 850,000 gold by hunting an ‘alien creature.
’ (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien creature.
’ (intermediate monster)’.
at that moment, one water spirit broke out of the shield and fell onto the deck.
 it evaporated and perished.
“no! this is my limit!”then, two more water spirits disappeared.
 it was a bad situation.
monsters stuck their heads and arms through the gap.
 then, they began to tear off the shield of the airship itself.
shhh! shhh! shhh! shhh!hanho threw daggers towards the hole.
 in just one second, 12 sticks were stuck in the monsters’ heads.
“i got them!”

he killed the monster who was breaking through the hole, but when the hole was made in the shield, the corpses of other monsters fell onto the deck.
once opened, the hole expanded rapidly.
 and three monsters came through it.
“hey, let me stop them!”with a shield around his body, hanho attacked them.
 next to him was minsok.
since there weren’t many monsters trying to break through the shield, sungwoo’s allies could handle them.
 but if the shield was broken, there was no way for them to block the monsters.
“necromancer! well, that’s great, but we’re going to be wiped away by them!” li wei shouted to sungwoo.
but sungwoo shook his head with a calm expression.
“well, wiping them away is my specialty.
”sungwoo stretched out his left hand toward the corpse of an “intermediate monster” and his right hand toward his head.
- ‘high-pressure explosion’ has been applied to 22 corpses.
 (29 seconds before explosion)by using the corpses piled up one by one, sungwoo was thinking of killing them with one big strike.
“good! i don’t know what it is this time, but let me hold out!” said li wei.
while sungwoo, li wei, and hanho were struggling to block them, troll skeletons picked up the swollen corpses.
, 23, 22…sungwoo, counting the number in his heart, fired the winter predator.
 hanho rushed to the monster that landed on the deck and stuck 6 blades into his neck.
 he had already knocked down four monsters in hand-to-hand combat alone.
, 12, 11…li wei used the remaining water spirits to push them away, but the messenger was already surrounded by hundreds of monsters.
 it was like a bird being attacked by giant hornets.
, 6, 5·······.
” now is the time! throw them!”

 