\section{chapter 415}

this time it flew in from the inside of the rampart.
 something shrouded in black smoke appeared through the air.
 it landed on the highest point of the rampart.
 when the smoke faded, the hands of the dead came up from the ground in droves.
 somebody was standing on top of them.





he was the necromancer.
"he has come! necromancer!"cheers began to resound over the rampart where the allied soldiers were overcome with frustration.
 sungwoo went straight back to the world tree through the 'return' effect of the 'world tree (link)' skill, then moved here at high speed using 'twilight raid'.
when the necromancer appeared, the emperor ascended into the air, riding on the oppressor's hand.
 then he made eye contact with sungwoo.
even though he made a crying expression after he was beaten by the necromancer, he was now holding his head high as if nothing had happened to him.
"you defeated me by punching, but…"the emperor slowly raised his hands as if to make a majestic gesture.
"i'm going to win this war…"he was trying to downgrade the necromancer's beating him when he had no divine power as 'punching'.
 now that he regained his divine power, the emperor seemed to think he was confident of defeating the necromancer.
 but sungwoo shook his head, watching him pitifully.
"you still don't understand me?"sungwoo shouted, sneering at him.
 at that moment, green flames began to burn in his eyes.
"your fate was in my hands from the beginning…"as soon as sungwoo said that, something started.
go-oh-oh-oh-oh-
a strange wind raged in his ears.
 it was obviously the sound of the wind, but this was what could be heard in this world.
 it was like the howl of hell.
for more, visit lightnovelworld.
comthe round brilliance that floated above sungwoo's head, namely, the aura of the underworld king, began to gradually expand its scope.
 the emperor was not sure if it was becoming smaller or larger.
 those watching it could not describe it properly, nor could they understand it.
 they could vaguely feel that it was more dazzling than any light and far deeper than any darkness.
go-oh-oh-oh-oh-then thousands of ghosts that the necromancer was controlling soared into the air at once with a roaring sound.
 they filled the sky.
they shook their bodies wildly as if they were dancing to welcome something.
"what the hell are they doing?"the emperor stepped back unwittingly.
 obviously, something was happening.
 it was something very ominous, but he could not figure out what it was.
 he was scared because he didn't know it.
was the greatest fear that humans could feel the fear of the unknown?go-oh-oh-oh-oh-everyone felt an instinctive fear.
 the emperor, the chinese army, and even the players on the korean server felt a terrifying fear for unknown reasons.
at that moment the ghosts that soared into the sky began to unite into a single point.
 that point grew slowly, and at some point covered the world in an instant with heavy explosions.
 it was a hole and a very deep hole at that.
 watching it, somebody murmured, "the sky was fully opened.
"it was a passageway to another world.

"what the heck is that?"soon the reality of this nameless horror was revealed.
- caution! the 'gate of the underworld' has opened in the area.
at that moment, the color of the whole world disappeared.
follow new episodes on the lightnovelworld.
com platform.
- your name has been written in the book of life and death.
there was a space where only white and black lines existed.
- you have entered the underworld.
sungwoo and the emperor were inside the new space against their will.
 more precisely, this unknown space itself overflowed reality.
 and the only being that was dyed with the green light in that colorless space, stood tall on the rampart.
"i, too, have a territory like you.
"his voice echoed from all directions.
"welcome to my world.
"he finally exercised the last power of the underworld king, which he had saved for the safety of the future.
the disappearance of all color from the world was more terrifying than he thought.
in such a colorless world the sense of direction and space disappears, and one's vision eventually loses its function.
 one feels dizzy.
 one becomes gradually delirious and one's reason is not working.
 many on the battlefield closed their eyes.
 they had no choice but to do so because they felt like they would go crazy when they opened their eyes.
 but when they closed their eyes, their ears were extraordinarily sensitive to what they heard.
 they were struck with another fear.
 go-oh-oh-oh-oh-screams filled both ears.
 it looked as if that incomprehensible scream was scratching their brains.
 this was not a place where humans could endure.
sungwoo shouted at the emperor, "this is the last battlefield.
"since this was sungwoo's territory, the 'oppressor's glance' and the 'oppressor's hand' summoned by the emperor disappeared.
the emperor stood on the ground and looked up at the rampart.
 a green aura was shining brightly.
"how come this is your territory? how come they covered the world?"the emperor could not understand what's going on now.
 the tomb of the first qin emperor, which was the emperor's territory, and hephaestus' realm, the forge of hephaestus, existed in the form of items.
 therefore, this was a place unrelated to the real world, where they could get access only when they actually touched the aforementioned items.
the most up-to-date novels are published on lightnov­elworld.
comthen, how could the necromancer's territory encroach on reality?"do you think what you know is everything in this world? get over your vanity that you only have insight into.
"the necromancer kept criticizing that the emperor was full of vanity.
"you bastard! how can you dare criticize me, the emperor…"the emperor trembled with anger, but he could not refute the necromancer.
"emperor? are you promoting yourself as the emperor in this age? how stupid of you!"sungwoo stepped out of the rampart, but he started walking down the air as if there was a transparent staircase.
"when you don't know what this game is, and when you are dependent on this game, how can you dare to dominate this world? nobody can't do it!"

sungwoo made that comment deliberately.
'after this fight, i will come into contact with many more worlds.
 by then there will be very few groups who are going to fight me.
 so i'm going to take the initiative.
"with that in mind, sungwoo was planting a message in the minds of the world camp players as well as those around the world.
the message was that they could follow him without any worries because he had no intention of dominating the world like the emperor.
 "domination and control are different.
 i'm not going to use this situation to satisfy my self-interest like you.
 instead, i will establish a control mechanism that can solve this situation.
"sungwoo's voice resonating through the underworld was broadcast to the whole world through the camera of the official channel.
sungwoo was thinking of 'controlling' rather than 'dominating' the world.
 this was essential to make his plan come true because without control he could not establish any proper organization.
sungwoo slowly approached the emperor.
 watching him getting close to him, the emperor could not take any action.
".
.
.
"the emperor knew that in this world nobody could confront their master.
new novel chapters are published on lightnov­elworld.
comsungwoo slowly opened his mouth.
"i had the means to defeat you from the beginning.
"this time the voice didn't resonate throughout the world.
 sungwoo personally made his voice heard only by the emperor.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 