\section{chapter 154}

                             




night came.
“hi, everybody, i’m the ‘holy and strongest thief’.
 today’s brief news! would you like to listen?”“go ahead.
”hanho’s ability to analyze and organize the community bulletin items increased day by day.
it was the reason they called him a community analyst.
“this is the first brief news.
 it seems that the creation of the “metropolitan alliance” is progressing rapidly.
 hearing that news, the survivor coalitions in the metropolitan area are reportedly gathering in youngdungpo.
”although it had not been officially announced yet, the news that the formation of the metropolitan area alliance with the liberation guild as the center was spreading widely, so the news was emerging as the biggest issue in the community.
maybe the liberation guild leadership was intentionally spreading such rumors as part of “viral marketing.
”‘the players who have survived so far definitely have the ability to save their own lives.
’therefore, if they joined the alliance, they would be a great help, so the liberation guild was attracting as many players as possible and growing in size.
of course, how to unify the rough and undisciplined survivors was the next question.
it was necessary for them to find the leader for that purpose.
“now, second news.
 this is a secret message from kyungsu.
 he said that the average level of people in suwon village is close to 8.
 great! they are looking forward to achieving it tomorrow or the day after tomorrow.
 wow! they must have worked hard.
 kyungsu also boasts that he has reached level 11 today.
”kyungsu and inho in the suwon area were also doing well.
 just like they promised to sungwoo, they were raising the average level of the survivors there quickly.
“come to think of it, they are growing very fast.
 i’m only level 14, even though i fought next to you for a long time, sungwoo.
”through the mini-game, hanho increased by two levels.
 jisu also reached level 16, which ranked her 6th in the korea server rankings.
 given that yun cho, level 16, was no.
 5, she was about to jump to the top five.
“hanho, have you ever rolled on the ground?” sungwoo asked when he boasted.

“well, i performed very well when you were not with me.
 even today, i plucked grass and herbs and covered my body with them before fighting.
”“why did you pluck grass? did the strongest thief assassin weed?”hanho tapped his chest as if he was frustrated and angry.
“what i mean is i used a fantastic strategy to beat the enemy.
 do you think i’m just a community announcer? i’m the icon of children here.
 you don’t know anything about it, right?”“oh, really?”“besides, i’ve leveled up this time and learned the ‘sneaking’ skill! in other words, i’m becoming the strongest thief!”“great!”“yeah, sneaking is so important… oh, here is the third news.
 our great necromancer has achieved level 19, so he is the same rank as kangsok han, no.
 1 in the korean server…”hanho suddenly stopped talking, then looked at sungwoo with a smile.
“it seems he has achieved the same rank as han, but unfortunately, an hour ago, han reached level 20.
 our necromancer needs to be a little more diligent!”sungwoo’s eyebrows wriggled, but hanho was all smiles.
“wow, awesome! who is he? according to the community rumors, there was a man who smashed the kobold army alone, who occupied the sejong area! could he be kangsok han? i’m really curious!”having said that, hanho continued, tilting his head, “but aren’t you really curious? what the hell is he doing? sungwoo, you’re taking all the undead with you and smashing large enemies easily, but who is this guy?”sungwoo himself couldn’t figure out what kind of job kangsok had.
 he had never appeared in the community, and there was nobody who saw him.
“it seems that the warlord monsters in other regions were all destroyed.
 of course, they did it a bit later than us, but they did a great job.
”“those who could not hold out must have been killed.
”the warlord monster’s attack was fatal.
 perhaps weak players among the survivors were killed.
 only those who survived could move to the next level, which was more difficult.
 that was the game.
“damn it.
 they have no love for humanity anyway.
” hanho whispered, turning his head.
 “well, how can i expect this guy who collects dirty and smelly bones to have a love for humans? ah, except for orun.
”
then, he looked into the green eyes of the skeleton sitting next to him.
“sorry, you’re an exception, sir.
”it was minsok, the death knight.
 he gazed at hanho’s cell phone, holding his sword.
 “hanho, is there anything unusual in youngdungpo?” asked minsok.
“well, it’s safe.
 oh, i see.
 you said your family was there, right?”“yes.
 it doesn’t matter that i turned into a skeleton like this, but i didn’t know it would be really annoying not to be able to use a cell phone like a human.
”when he became a death knight, he was disqualified as a player, so he could not use the community.
“if i hear anything unusual, i’ll let you know right away.
 don’t worry.
 i am the best in this field.
”“sure.
 i hope i’m in your great hands.
”meanwhile, jisu sat on the ground and checked her three swords.
“hey, sis, i have never seen that sword!”in fact, she had another sword in addition to her two swords.
“right.
 i got it today.
”[item information]-name: genuine silver sword.
-class: hero-category: sword-effect: it can break magic.
-description: a sword forged with ‘genuine silver’, a rare magic metal.
 it is very light and hard.
 it also generates a unique wavelength in response to mana, through which it can destroy magic.
it was the loot she obtained after killing huei.
 at first glance, the shiny silver blade looked luxurious.
“wow, when can i get a weapon like that?”while cleaning the newly-obtained sword, she seemed very satisfied.
***the next day, the sky shook loudly early in the morning,dudududududududu―“what the heck is that? helicopter?”hanho woke up, rubbing his eyes.
 sungwoo and jisu were already walking outside.
a red helicopter landed on the dolmen gym square.
 it was a firefighting helicopter from youngdungpo.
minhum got off the helicopter and said, “sungwoo, i heard the news that you have defeated the pirates.
 you are awesome!”“thank you, but you must have a reason for coming here so early in the morning?”minhum nodded and said, “something unexpected happened.
”he then sighed and opened his mouth again.
“kangsok han, no.
 1 in the rankings, appeared.
”did the no.
1 guy appear? hasn’t he left no traces until now?“does you mean he has come to youngdungpo?”“yes,” he said with an embarrassed expression.
 in fact, he had to absorb those in the vicinity of youngdungpo to form a large group, but at this crucial time, kangsok appeared suddenly, who was much stronger than their current leader junghoon, the master of the liberation guild, which should be the central base of the new alliance.
 since the guy who has been unknown until now appeared, he naturally drew the attention of everyone in youngdungpo.


raising his glasses, minhum continued, “he said he wants to meet the necromancer, sungwoo.
”“me?”“that’s right.
 he said he wanted to talk with you about a very important issue that would determine the fate of the korean peninsula.
 damn it.
 he said he wouldn’t tell us.
 he said he wouldn’t tell us anything until the necromancer comes.
”sungwoo didn’t know what was going on, but obviously, kangsok was confident enough to openly alienate the largest forces on the korean peninsula, namely junghoon’s group.
“got it.
 tell him to wait.
”“pardon?”minhum looked surprised at his reply.
 tell him to wait? right now, nobody knew what the no.
 1 guy would do.
“because i have to manufacture something and enhance something, i have to stop by the forge.
”“oh, don’t you think it will make the situation worse?”obviously, there was confusion and anxiety spreading on his face.
“minhum, if you just try to accept his demands just because he is the no.
 1 guy, how do those who try to unite under the name of the alliance feel? if you want to show them you’re the central force, not him, you should show your power clearly.
”“ah, that’s right, but…”“then tell him to wait.
”“ah, got it.
”minhum was very anxious.
 he felt like it was the night before the storm.
it seemed that these two mighty guys might confront each other in this crucial situation.
‘man, we might suffer a side blow in the fight.
’compared to the two giants, the emerging alliance was a small fry.


 