\section{chapter 180}

                             




“uh… this is a secret message sent by heyon.
 according to her, the chinese community keeps talking about you.
 it looks like you are very popular in mainland china.
”the players on kanghwa island were spying on the chinese server community through the chinese players they held captive.
heyon shared the details through her secret message, all of which were ridiculous.
according to her, the pirates, aka the red revolutionary army, were advertising that they would kill the necromancer and that they already prepared a good strategy to kill him.
“they are arguing that they have had the angel statues for a long time, so they already have 3,000 players ready to work for the angel camp.
 of course, nobody knows for sure.
 anyway, they are bragging that they are going to get a lot of buffs and wipe out the necromancer and his 3rd faction.
”furthermore, they even detailed the long-term goal of occupying the korean peninsula on the chinese community.
hanho got furious after reading the message.
“damn it! why are these pirates running wild again? it looks like they have not yet come to their senses.
 should i kill them again?”“kill them?”“anyway, all the chinese people on the mainland are asking the pirates to kill you by all means! maybe, at this moment, the person who receives the most hatred in the world is you, sungwoo.
”after the scenes of their players being slaughtered by the necromancer were broadcasted to the chinese community, their hatred toward him knew no limits.
thanks to that, the red revolutionary army was enjoying great popularity among the chinese people on the mainland.
“oh, my god! i just imagined something ominous for a moment.
 will i fight those countless chinese people someday?” hanho asked.
“i think so,” sungwoo answered.
“then, should i pay homage to my ancestors first?” hanho said gloomily.

that night, heyon kept delivering news about the movement of the chinese server community.
 since the necromancer’s bounty was issued as a world quest, the chinese server was also overflowing with all kinds of issues about the necromancer all day long, so new information was constantly coming in.
on the chinese server, they were making a strong case for occupying the korean peninsula.
 moreover, the red revolutionary army offered to hold a huge rally to commemorate the conquest of taiwan and the future task of conquering korea.
 they were now actively advertising the projected rally widely.
“they’re going completely insane! it seems they still have a large force even after we devastated them.
 they are going to hold even a parade.
 just crazy bastards!”they even announced to advertise their power, they would broadcast the parade with about 100,000 attending live.
 how could they conceive such a parade in this era?“by the way, why are there so many forces around us who are trying to attack us? even the japanese server guys are looking for a chance to attack korea, aren’t they?”since the absolute race set a huge price on the necromancer’s head, plus 70 million gold as a reward, it was clear that people attempting to take the life of the necromancer of the korean server would appear everywhere.
“well, i don’t think they are all.
”“really? does it mean those guys in america and europe are also targeting you? man, do we have to confront those guys after we defeat the chinese guys?”sungwoo wasn’t sure about that, but those in regions other than china were most likely hostile to him.
“i can’t confirm it now, but i think they have already become our potential adversary.
”given the huge bounty on the necromancer’s head, those in the top rankings on other servers could not help but pay great attention to the unexpected bounty quest.
it was natural that they showed such a fervent reaction because the player from an alien server who may be their enemy in the future, the necromancer, appeared.
 they were greedy for the bounty, but they remained alert.
‘well, if i was in their shoes, even i may be curious about this guy who is confronting the absolute race…’ sungwoo thought to himself.
targeting the necromancer meant that they were targeting the korean server itself.
as a result of so many people focusing on him, a quest was also issued to sungwoo.

[faction quest]-title: operation counterattack-type: raid and propaganda-goal: broadcast scenes of great damage being done to the other camp-reward: faction skill, faction item*the established forces (absolute race) are wary of the emergence of new forces.
 they are turning to all kinds of ways to keep you in check by mocking you in a variety of ways and declaring a war even before the faction is founded.
 this will have a negative impact on you and your faction’s reputation.
 that is why you need to counterattack.
 prove your enemies are wrong.
 broadcast it, so that more people witness it through the air.
* condition: you must launch the first strike.
* if the scene of your being defeated is exposed, you will be given a penalty.
“broadcast…”in short, according to the condition, sungwoo should make sure the scenes of the third camp destroying the absolute race camp should be broadcast to everyone.
 it was a bizarre condition.
‘as expected, the system makes this game more fierce.
’sungwoo pulled out an item from his pocket.
[item information]-name: angel’s wing fragment-grade: legend-category: consumptionitem-effect: when you use it, you can move to the ‘angel statue’ within a certain range.
 (1 time) * the demon camp cannot use it.
-description: when the statue is destroyed, it is used for the final emergency escape.
this was an item sungwoo obtained after destroying a statue.
 the members of the demon camp were restricted to stop the enemy camps from using it, but sungwoo had not yet created a new camp.
 in other words, he could use the loophole of the system.
“i think i have to stop by taiwan anyway.
”he was thinking of attending the red revolutionary army’s huge rally as a surprise guest, where 100,000 people were supposed to gather.
destroying sungwoo and the third camp had been upgraded to a “world quest.
” as a result, more people would be hostile to sungwoo, but for now, there was nothing for sungwoo to prepare against their possible attack.
 of course, the best option would be for him to prepare for it slowly and thoroughly.
“sungwoo, i’ve confirmed that an invisible barrier zone around 2 kilometers has been set up,” inho said.
“is it possible to get out and come back through the invisible barrier?”inho nodded at sungwoo’s question, and replied, “yes.
 we can go back and forth freely, but considering the message ‘allowed player’ only, it seems that outsiders are not allowed to enter.
”sungwoo asked inho to check the range of influence of the “shadow of god tree,” the skill of the world tree.
when inho checked out the area by mobilizing a dozen search teams, he confirmed that the invisible barrier zone had been established.
[shadow of god tree]-shield (150,000/150,000)-access allowed: 226 people (see list)

* blocking outsiders’ accesssungwoo could also check the information about it, but he needed to double-check it.
“you should not let down your guard even if there is an invisible barrier zone because there may be items that can neutralize it.
”“got it.
 let me organize a surveillance team so that they can patrol around the barrier zone.
”now, the suwon village was not just a refuge for survivors.
 it was a place where the world tree was growing, and it would develop into the main stronghold of the third camp led by sungwoo.
therefore, sungwoo had to make sure the village had to be carefully managed in every way so that the village players could respond perfectly to external threats.
that afternoon, sungwoo summoned the village’s key personnel, including kyoungsu and inho.
“i think i have to go outside the village again.
 i don’t know how long it will take, but i’m going to ask you a favor once again.
”“sure, please.
”kyongsu and inho had successfully defended the village and strengthened the village players, so he could trust them.
but the situation changed two days ago when the value of the village increased markedly with the birth of the world tree as well as it becoming the target of an unspecified number of people.
“if you encounter a dangerous situation, please contact the community.
 i can come here right away using the skill of the world tree.
”fortunately, sungwoo got the skill of ‘return’ after eating the first fruit of the world tree and ‘linking’ with it.
 so, he could move to the world tree immediately once every 24 hours.
“please take this.
”sungwoo gave an item to inho.


 