\section{chapter 215}

                             




dr.
 yu said, “as i already told you, we have already commissioned the mercenaries of the korean server, but they failed miserably.
 so, i think our target must be preparing for our attack to some extent.
”having heard that, akira closed his eyes half-way, and said sharply, “dr.
 yu, i hope you don’t treat us as mercenaries.
 we’re swordsmen fighting for honor and loyalty, so we’re different from the tricksters who are fighting for pennies.
”“sure, i know that.
 i’m not ignoring the swordsmen of the yamato guild, but you will learn that the necromancer is a tough opponent.
”akira expressed some displeasure.
“please don’t worry.
 we have been trained to easily kill strong opponents.
 that’s the essence of ninjas.
”“yeah, i know very well about ninjas.
”“i would like to emphasize that it is not easy to create synergy by gathering 15 ninja players even within the japanese server.
”there was a powerful synergy that could be obtained only when ninjas gathered.
 and they were supposed to be dispatched to assassinate the korean server’s most powerful man, the necromancer.
“…”“alright.
 we’re going to turn the ship…”dr.
 yu stood at akira’s words.
 they were done concluding a deal.
“it was an honor to meet you.
”the moment dr.
 yu turned around, akira urgently added, “oh, dr.
 yu, we received an order from honbucho that our ninjas should not draw their swords until after we receive the item.
”“got it.
 we’ll send it to you by the end of today.
”after the conversation, dr.
 yu got out of the cabin and got on the helicopter.
 next to him, a young woman held out a pair of headphones.
 he put them on and sent a hand signal to take off.
woooooong-“dr.
 yu, who the hell is kumicho? who is that person?”agents aboard the helicopter were listening to his conversation with his japanese counterparts through wiretapping devices.
 they were on standby to rescue him in an emergency.

“well, he’s the leader of the yamato guild that has taken control of kyushu, but he’s an old man who couldn’t even awaken at level 22.
 so, he is raking in items needed for awakening.
 we had one, so we could strike a deal.
”the woman nodded, then looked in the direction of korea this time.
“will they be different this time? can ninja kill the necromancer?”“well, if they can only buy time for us, that’s fine.
 even if the yamato guild fails, we will have no problem as long as we can carry out our plan successfully…”“yeah, the necromancer is finished.
”“yep.
”not everyone on the korean server was scared of the necromancer.
 after they fully admitted his strength, they were preparing a fatal attack against him.
***in a perished world, how will the world war unfold under the rules of the system? and how should they prepare for it? the players of the world tree camp agonized over it deeply.
“well, we are numerically so small that we can hardly wage a war.
”“yeah, i guess so.
”until now, they have purposely pursued a small number of elite forces because they wanted to reduce the risk caused by unnecessary dependents and to lay a solid foundation.
 their goal was a success.
“fortunately, few people have died until now, but i can’t guarantee that in the future.
”when it comes to a full-fledged war, it’s a different story.
 if the war escalates into a multi-facet war that sungwoo alone can’t deal with, the villager players would also be involved in a bloody battle.
 in such a situation, it would be inevitable there would be casualties.
that was the real problem.
 the village’s population was only 226, so even if a small number of them were killed, it would be an irrecoverable blow to them.
“however, it is a big headache to increase the players indiscriminately,” kyongsu said.
inho nodded at him and said, “i agree.
 i think we need to establish a procedure to accept new players.
”“i am on the same page with you,” said sungwoo.

sungwoo felt that what they could do immediately was to raise the level of the existing players to the highest possible.
it would not be too late to increase the number of the players later because if they could secure a solid foundation first, the players who joined them later could grow faster than expected.
“then, let’s focus on how to draw up the best defense plan.
 first of all, i think my undead army will be able to play the role of defending the enemies’ attack at the forefront.
”at least one hour after the war, they won’t have to worry about a strong defense because large undead under sungwoo’s control would resurrect indefinitely and defend the front line.
“but the problem is we are always weak at defending against the enemies’ ranged attack.
”in particular, since the undead themselves were not intelligent, it was quite hard for them to operate the subordinate spirits of the ‘wizard’ series that required a high level of intelligence.
of course, they could use some basic attack magic like “kovolt wizard”, but that didn’t help much.
 they needed advanced magic that granted ranged magic and abnormal status.
“by the way, there are lots of archers among the villagers.
 how about forming an archer unit first?” inho suggested.
so, sungwoo released the items he obtained from the battle of mt.
 pukhan.
among them, the most useful was the “multiple arrow” item used by the “skoll unit”, the main force of the reconstruction alliance.
[item information]-name: highest-grade multiple arrow-grade: rare-category: crossbow-effect: semi-automatic device is attached to it.
 you can fire eight arrows in succession when you trigger it.
“oh, this is terrific! it certainly has better firepower than normal arrows or crossbows.
 even if the single-shot damage is weak, firing it like rain would be more effective in a large-scale battle.
”“but how about showing it to our kongdori players? even if we give them iron pipes, they can make a blue dragon sword.
”kongdori was a nickname for those players in the manufacturing sector.
 since they received the buffs of the ‘abundance of godly tree’, they have been producing quality items thanks to their upgrade skill level.
a little later, the two blacksmiths checked the item and began to exchange conversations with each other.
“how about attaching the spirit stone you got? i think it will be more powerful with the added effect.
”“no, i don’t think so.
 this item has been specialized for rapid-fire, so it would be better to maximize it.
 let’s attach a dwarf box as we have lots of them.
”“that would be better.
”then, they put one ‘highest quality multiple arrows’ on the workbench and started renovating it.
within a few minutes, they created a new item.
[item information]-name: highest-grade multiple arrow (large-capacity magazine)-grade: rare-category: crossbow-effect: a semi-automatic device is attached to it.
 also, a large-capacity magazine has been added.
 you can fire 28 rounds in a row when you trigger it.
the number of arrows that can be fired with a single load has increased significantly from 8 to 28.
 in terms of reducing the reload time, the rate of fire per minute has been significantly increased.
“but it cost 90,000 gold to renovate this one.
 i think it will take quite a bit of gold to renovate 25 of them.
”although the blacksmith expressed satisfaction, he looked somewhat worried because 90,000 gold was a lot of money.
but they could stop worrying after hearing sungwoo’s reassurances.
“don’t worry about the cost.
 i’ll support you as much as you can.
”“wow, our kondori players would welcome it with open hands!”sungwoo’s wealth kept growing.
 not only did he win 300 million gold with one bet, but everyone in the world tree camp also took a huge profit by betting.


perhaps the world tree camp was the most wealthy group on the entire korean server.
sungwoo thought of creating an elite group that could be a match for a group with enormous capital and buffs.
just like the necromancer could deal with hundreds or thousands of enemy troops, they could turn into a mighty force if each of them could deal with ten enemies.
“but just because the items are good, you won’t be strong automatically.
”“we have to hunt again to be strong, right?”items were a very important factor, but they showed different effects, depending on who used them.
currently, the players in the world tree’s camp had above-average levels and combat abilities.
 however, they had yet to reach the level of an individual who could deal with ten enemies, which was sungwoo’s goal.
“kyongsu, could you summarize a list of dungeons and give it to me?”“okay.
”then, inho began to explain, “the field is always tidy and clean, and there are simply too many dungeons.
 you can choose whatever you want.
”“are the dungeons large?”“yes.
 at the beginning of this chapter, there were about 4 in downtown suwon.
 we sometimes visited there, but we haven’t yet attacked them because they are so large.
”the large-scale dungeon was one of the main contents of this chapter.
“good.
 inho, please divide the players into a group to launch an attack on the dungeons.
 they are going to attack the dungeons with me.
”inho looked astonished.
“are you going to guide them in person?”“guide? well, i’m going with them, but i just hope they can endure the fight as best as they can.
”sungwoo’s goal was to make each of the village players strong enough to deal with ten enemies.
 so their hellish training began with the necromancer.


 