\section{chapter 296}






 “quest reward? are you sure? but this isn’t a player’s manufacturing item, isn’t it? if so, can’t we reverse engineer it?”“but the thing is somebody has made such a cannon, right? if so, why can’t we make it, too?how about disassembling it?’“are you serious? are you confident?”“i have to disagree.
 until you reach the ‘equipment design’ master grade, don’t even touch it.
”while they were in the thick of discussing how to handle it, sungwoo came into the blacksmiths’ workshop.
“ah, you are here, sungwoo.
 take a look at this.
 it is a canon called ‘supernatural storm.
’ if we have it, our defense power, as well as our ability to use flying weapons, will increase significantly.
 isn’t it cool?”the blacksmith team leader spoke excitedly, so sungwoo got also interested in the cannon because he felt the necessity of securing flying weapons such as the iron mace of lightning and fire rocket arrow after experiencing their enormous firepower.
“what kind of features does it have?”when sungwoo asked, the team leader explained each part of the cannon and opened the magazine of the cannon.
“and this is the core of this mighty cannon.
 you don’t have to load any ammunition here.
 if you insert the spirit stone here, it creates and fires the cannon with the power of the spirit.
”then, he pulled out a total of three red stones from the magazine, which were “fire spirit stone (lower grade).
”“hum…this is a spirit stone?”sungwoo took out the ‘fire spirit stone (high grade) that he obtained after hunting the salamander.
 when he compared the two spirit stones, this one was about three times bigger than the fire spirit stone.
“then, if you put this here, is this cannon going to be stronger?”
when sungwoo presented the fire spirit stone, it seemed they had some kind of perverted desire.
“wow! yeah, hand it to me right away!”“can we experiment with it?”“it only takes a moment for us to experiment with it!”they shouted at sungwoo at the same time, and he gave them the fire spirit stone (higher grade).
bang! bang! bang!soon, an intense heat soared from the thermal power experiment site outside the village with a roaring sound of explosions.
 even though it was more than 2 kilometers away from the village, they could feel the vibrations through the ground.
shortly afterward, the blacksmiths with a lot of soot on their faces rushed to sungwoo with a toothy smile.
“it’s a jackpot! with this firepower, we can even break through the shield the same size as the messenger and shoot it down with one stroke.
 what a jackpot!”“i would say it’s a really artistic explosion! we have blown away a five-story building with this.
 i wish you had seen it!”sensing that they got completely carried away with the firepower of the fire spirit stone, he just nodded at their words calmly instead of responding.
“good.
 nice job.
”since the fire spirit stone (higher grade) was an item he obtained after hunting an emperor-grade monster, even the wpu of the us server would not be able to bring firepower as massive as this.
at that moment, jonathan came to sungwoo.
“necromancer…”
although he called sungwoo, sungwoo did not look at him with a nonchalant expression.
then, jonathan made a desperate expression as if to ask him a favor.
this was not the first time he asked sungwoo a favor.
“please! please return the messenger to me!”when the messenger started functioning again thanks to the hard work of the engineers of the world tree camp, jonathan said he would go back to the us server on the messenger.
he said needed to go back as soon as possible to stop admiral baker from taking control of the congress of the wpu and stop their ambition to try and conquer the korean server.
however, sungwoo refused his request without any hesitation.
“give it back? to whom?” sungwoo replied with an annoyed expression.
jonathan cautiously expressed his opinion.
“as you have saved me, i’m sorry to tell you this, but the messenger is the property of the wpu as described in the ship’s information.
”at that point, sungwoo stared at jonathan intensely.
“property? don’t you think you use that word too easily? you can talk about your property under the common system recognized by society as a whole.
 how can you claim it as your property in this crazy world?”jonathan was embarrassed by sungwoo’s criticism.
sungwoo continued, “we found some of these enormous items which were partially destroyed, so we repaired them by ourselves, and we captured some others from the enemy.
 which part of the messenger you believe is the property of the wpu? do you think we took this ship from you?”“…”then, sungwoo took a step closer to him and said in a much softer voice, “now, let me make it clear to you.
 the wpu is not my enemy, right? they are your enemy.
”jonathan nodded and said without any hesitation, “yes, of course.
”“and the invaders we fought against yesterday didn’t represent the wpu, right?”“they are the betrayers of the wpu.
 believe me! they have never been affiliated with the wpu.
”sungwoo smiled at him.
at that moment, jonathan felt he made a mistake.
“that’s right.
 we won by fighting the invaders who were trying to occupy our land and our lives then obtained the legitimate spoils.
 that’s all.
”jonathan couldn’t respond at all when sungwoo made conclusive remarks like that.
“…”jonathan’s argument was poor.
 he just appealed to sungwoo emotionally, saying he lost the messenger unfairly, but he didn’t come up with any legitimate reason for getting the messenger back.
on the other hand, the world tree camp, like sungwoo said, beat the invaders and obtained their possessions.
 they didn’t even touch the possessions of the wpu.
“jonathan, you’re not trying to claim ownership by morality or law in a crazy world like this, right? think about it carefully.
 if you claim the messenger, your thinking is neither civilized nor wise.
 it’s anachronistic and old-fashioned.
”then sungwoo turned away coldly, “ah…”jonathan looked at him blankly, and muttered to himself, “you are right.
 but chairman love hopes that it’s possible to take back a normal world, and that’s why i came…”but it seemed too early.
 maybe it would be an eternal ideal because the world was too barbaric for them to create a human society.
“so, we need you all the more, necromancer.
”

ironically, there had to be someone who could face the barbaric world in a barbaric way in order to rebuild civilization.
but even chairman love, who jonathan trusted and followed, wasn’t a good person.
in fact, they lived in an era of uncertainty, a time when unexpected things happened when they woke up the next day.
“sungwoo! sungwoo!”there was turmoil early in the morning.
grrrrrrrrrr-when sungwoo rushed into the room at hanho’s shouting, mir, who was sleeping, tossed and turned, throwing a tantrum.
rattle!soon, the door opened and hanho came in, holding a cell phone in one hand.
startled, mir raised his head buried under the pillow.
 at the same time, mir summoned two chicken skeletons.
rattle! rattle!“ahh! what the heck is this?”sungwoo kicked a chicken skeleton running towards hanho and threw it against the wall before sitting down at the chair.
“man, they just tried to kill me, right? i’ve eaten numerous chickens until now, but i haven’t thought about getting killed by a chicken.
”“so, what’s going on?”

 