\section{chapter 445}

stunned, the two young tigers jumped out of the purple smoke and caught their breath.





"cough! i wish you had given us a reminder when we went out to bring the steamed potatoes….
""oh, i forgot because i was so absent-minded.
 ugh? by the way, where are my potatoes? i guess you guys are also out of mind right now.
"eventually, the two young tigers had no other choice but to climb back up the cave and come down with the baskets full of potatoes they had thrown at the entrance.
"by the way, what the hell have you been doing?""i'm curious, too.
 you have locked yourself into this place for several days.
"standing at a distance, they looked down into the purple smoke.
the king of the great mountains seemed to make something while wearing a gas mask as if he had become a researcher in a chemical laboratory.
"alright! i'm almost done!"having said that, the king picked up something, which was a brown jar.
"what is it?"the king shook the jar, which made the sound of water rippling inside.
 "it's alcohol.
""alcohol? are you serious? did you make all the fuss to make fermented drinks?""that's true, guys.
"then he checked the alcohol again.
"death has been permeated into the spirit of the mountain very well! this is a masterpiece!"it was a drink made with the 'crystals of mt.
 taebek' that jisu had recovered.
 the king seemed to have improved it by adding something more, such as the breath of the abyss.

"by the way, did you drink alcohol, your majesty?""huh? i don't drink this kind of alcohol.
"visit lightnovelworld.
c­om for a better experience"uh? who is drinking this?"the king placed the jar in the prepared wooden box and carefully wrapped it with a rope.
 "only those who enjoy death are qualified to drink this.
"he was done with fermenting some unidentified alcohol.
***the world camp fleet left the hall of angels and joined the allied forces waiting outside.
but they stopped the war with the absolute races because there was something more important than the war.
 "attention! as soon as the portal is opened, the special commando team will start first and open the hyper gate leading to amazon! everyone, get ready to face the tropical rainforest climate!"the frontline commanders gave resounding orders.
 they made preparations for a war on the new battlefield.
standing on the deck of the messenger, sungwoo watched them making preparations quietly.
 'yeah, you don't have to worry about the absolute races anymore.
'the angel race has already been destroyed.
 gangsok left to obtain the 'world seed' by attacking the other 'devil race'.
 it would not take long for the demon race to be extinguished.
'if he collects three world seeds, gangsok can become the world eater.
 i've got to block him from obtaining it by all means.
'fortunately, he found the way.
 the white wolf gained important information about his whereabouts by using his psychometric abilities.

'fortunately, i can find him in the demon king's castle.
 all i have to do is find a way of saving time to get there.
'with that in mind, he turned his head to the center of the deck.
"oh no! i don't want to open it!"there came out the crying of gangsok's fairy butterfly.
 the butterfly was trapped inside a cage made of magic engineering.
 "oh, really? are you serious?" hanho was standing in front of him with a mean expression.
 grabbing six things with his six arms, he swung them back and forth.
 they were all pesticides.
the latest episodes are on the lightnovelworld.
com website.
"then, would you like another taste of pesticide? or will you open the portal without any resistance?"the butterfly then covered her mouth and shook her head.
 it was really disgusting when she tried it.
 "no!"but hanho had no mercy.
 holding the entire cage with six arms, he pressed the ejection button with six indexes.
puseeeeeeeeeeeee-like a haze on a stage, pure white smoke completely covered the cage.
"ahhhhh! cough! cough!"the butterfly grabbed the cage's bars and screamed.
 she wouldn't be killed by pesticides or anything like that, but it seemed like the most painful torture for her.
"cough! cough! that's the demon king's domain! please think twice about it! you guys can never occupy that place!"as the butterfly said, the demon king's castle was the king's domain, and it was the 'world seed' of the underworld that created and maintained that space.
'if i attack the demon king's world seed, gangsok has no choice but to return in a hurry.
'in other words, sungwoo planned to attack the vacant castle to force its owner gangsok to postpone his schedule and return in a hurry.
but there was no easy way for sungwoo to cross the pacific ocean to the amazon rainforest.
 if he could mobilize all kinds of resources, he could find the way, but he had no time right now.
 at that moment, hanho told sungwoo he would open the easy passage to the amazon.
 that's why he was scuffling with the butterfly.
hanho said, "you still don't want to open the portal to the demon king? no?"the fairy's magic could open a portal to a designated location.
 so she must have preset the demon king's castle within her boundary.
pushheeeeeeeeee-"ahhhhhhh!""how about it? does it taste like lavender? are you okay now that you're used to it, right? eat it slowly! i'll give you more! i've got a few more boxes!""hey, you crazy! cough!"this content is taken from lightnovelworld.
comthe butterfly flew up to the top of the cage and tried to stick her head out, but she could not because of the invisible barrier around it.
"ugh! i can not! i won't open it!"pusheeeeeeeeeee-but after he applied the pesticide over and over again, she finally had no choice but to surrender.
"argh! let me surrender! got it!"at least this kind of attack was definitely the best torture for the fairy.
 

"let me open it! so stop it!"hanho smiled triumphantly, and said, "hehehe.
 you should have done it a little earlier! how can a butterfly like you try to make fun of me? get ready for another pesticide because you have to apologize to me more.
""no way! please get lost!"as it turned out, hanho's deep-rooted resentment against the butterfly provided a decisive chance for sungwoo's victory.
 ***it was sungwoo who first entered the portal that the butterfly opened.
after he went, the special commando team including jisu and junghoon entered.
"alright! install hypergate right away!"the portal the butterfly could open was not that big, so the airship could not pass through it.
 therefore, the special commando team was planning to enter first to open the 'hyper gate'.
"team 1, find the high ground to the best you can, then secure a space by removing the trees there.
 team 2, attack everything that's approaching there while on the lookout!"while they were installing the hypergate under junghoon's guidance, sungwoo summoned bone wyvern and got aboard it.
 'it's really vast!'the world's largest tropical rainforest, often called the lungs of the earth that could be seen only in movies, unfolded before his eyes.
visit to lightnovelworld.
com discover new novels.
'man, it's so hot here!'he just arrived at the amazon rainforest, but he felt as if his whole body was already clammy with sweat.
 he saw a black giant castle far away at the edge of the endless green sea.
'that's the demon king's castle.
' you can also read this novel on the more advanced platform lightnovelspot.
com

 