\section{chapter 391}

chapter 391: war for war (8)rattle! rattle! rattle!




the necromancer’s army appeared near gwanggyo lake park.
as the chinese side expected, they numbered only a few hundred.
on the other hand, the shield unit of the chinese army, who camped out in a dense gathering after eliminating all the ruined buildings around gwanggyo lake park, numbered as many as 30,000.
“um…”taegam, the chief of the royal secret service, who was in charge of the troops here, climbed on the back of a huge crane and looked at the necromancer’s army.
about thirty cranes followed him, with senior officials of the royal secret service riding on them.
“well, given the small number of the enemy, i don’t think it’s necessary to use our white sacred sphere…”then he turned his head and looked at the officials under his command.
“but don’t you think we have to use the white sacred sphere to break their fighting spirit?”the technical manager nodded at him constantly, then said, “of course! i think it’s going to deal a fatal blow to him!”taegam raised his hand with a hearty laugh.
“good! start attacking them!”then the technical manager pulled a flare from his pocket and fired it into the air.
tung!the flare exploded in the air, scattering red smoke.
 right after that, a horn sound was heard from the shield unit.
boooooooo-“come on, we’ll see the skeleton lord collapsing from now on!”taegam and his officials turned their heads and looked towards the shield unit.
 soon a huge shadow began to fall over the heads of the shield unit troops.
gugugugugu-
then, some sort of waves spread through the air, revealing something.
a gigantic white ball, namely the white sacred sphere, was there in a hidden state.
wheeeeeeng-it started working with a roaring noise, then a large amount of white light spread out in all directions.
- ‘divine power’ is filling the area.
the so-called ‘holy field’ was created.
 the ray of light flowed over and over, filling everything around the area, including the necromancer’s army.
“…”taegam and his officials were watching the scene while swallowing.
and the next moment they were all smiles.
“hahahaha! look at that!”“isn’t it like a sheaf of rice before a typhoon?”strange enough, there was no undead army there.
a huge white ball, namely, the white sacred sphere appeared.
“what the heck is that?”reporter ahn was bewildered, but wong smiled sneakily.
 wong didn’t even know what the giant sphere was, but he had a gut feeling that the war was unfolding as he claimed.
“uh?”a white light spread out.
 at first glance, the rolling waves with an aura of holiness didn’t look good to the necromancer.
as expected, hundreds of undead army advancing toward the chinese army’s shield unit stopped on the spot, then began to tremble wildly.
“oh my god…”
the undead army collapsed helplessly.
 even though they were not attacked at all, they literally fell to the ground.
 then there appeared one man standing among the piles of bones thus made from the undead army.
he was none other than the man in a dark green robe, namely the necromancer.
“…”as if he was also embarrassed, he looked around and looked down at the ground several times.
 somehow he looked shabby and miserable.
a heavy silence fell in ahn’s studio.
reporter ahn opened his mouth with a heavy heart.
“well, it seems that the necromancer’s undead army has been completely neutralized.
”reporter ahn touched his head with his trembling hand, gulped down a cup of water, then opened his mouth again.
“man, he is in really big trouble now! i think that sphere emitting light was responsible for the collapse of the undead army, but since the necromancer could not use them as his subordinate spirits, he can’t seem to destroy that sphere.
 i think he was completely defeated.
”on the other hand, wong made a relaxed expression as if he was satisfied with the situation.
he arrogantly leaned back on his chair and looked at reporter ahn.
“reporter ahn, do you remember what i emphasized?”ahn reporter frowned at his question but turned back after managing his expression.
“what did you emphasize? i can’t remember well…”wong raised his glasses and said, “i clearly told you that the reason why the emperor had no choice but to defeat the necromancer overwhelmingly was his defense weapon, right?”“oh, i see…”“there is a saying in chinese that if you know your enemy and yourself, you can win every battle.
 i think since the korean people have been influenced by the chinese culture, you guys also know the chinese saying.
”“…”“this is the difference between the two heroes.
 both of them were heroes who represented the same world, but in the end, this is a war that the smarter of the two can win.
 and the smart man is supposed to dominate the world.
 as you know, the undead are pretty ignorant, right?”wong giggled, then kept rambling.
 he said that everyone knew that the necromancer’s weakness was divine magic, but the problem was how to reproduce it in a perfect way, adding that it’s the power of the chinese server who found out how to do it.
“wait a minute!”at that moment, reporter ahn jumped to his feet suddenly.
 then he opened his eyes wide and pulled his neck towards the screen.
“oh! that’s valkyrie! valkyrie appeared in the air!”the screen was already showing a blue sky where only one person, jisu, was floating around.
“valkyrie! she’s the arrow unit itself! she has appeared with her teleportation skill! she appeared to help the necromancer! the battle is not over yet!”reporter ahn screamed without hiding excitement.
at that moment, a blue flame appeared on the blade of valkyrie’s sword.
 it was a technique everyone was familiar with, namely, one with tremendous destructive power.
she swung the swordkwawagagagaga!dozens of blue blades spewed out and poured violently towards the white sacred sphere.
“let me attack it now! i’m going to destroy it with just one single strike…”ahn’s expression hardened.
 a thick barrier appeared around the white sacred sphere.
the moment the valkyrie struck the sphere, it evaporated into the air so quickly.
reporter ahn stiffened his face, and those watching the scene in the chat room kept silent all of a sudden.
wong let out a sigh and said, “look! didn’t i tell you? the emperor and his deputies are thoroughly aware of how strong the necromancer and his subordinates are.
”wong picked up a bottle of water and nodded as if he knew the battle would unfold like this.
“what is the necromancer without the undead army? he’s not just a wizard.
 is he a corpse? hahaha! just a corpse? isn’t that a very fitting description of him?”at that moment ahn reached out his hand and covered wong’s mouth.


“wait! can you shut your mouth? oh, sorry, but shut your mouth for a moment.
”“what? what else is there to talk about?”wong frowned as if he was offended, but he turned his head to the screen after sensing something strange.
the necromancer was standing alone on a pile of bones on top of the collapsed undead army.
he was pulling a bow.
“what? arrow?”wong sneered at that, but he soon found out he was wrong.
the moment the necromancer pulled the string of the bow, a huge vibration occurred, then a crack appeared on the ground where he was standing.
everyone watching the scene was confused without knowing what would happen next.
when he pulled the bow, the ground collapsed.
 buildings around the area collapsed.
the chinese army’s shield unit was shaken with fear.
 there was a gust of wind, which made the drone shake violently.
 finally, an arrow was shot from the bow.
the studio was silent and people in the chat room stopped.
everyone was just watching the scene without a word.
“…”and when the dust settled, ahn looked at wong with a smile.
“wong, you reminded me of the chinese saying a little while ago, right? well, we have an interesting expression in korea, too.
”wong looked at him with an embarrassed expression.
“life is the performance, not the rehearsal, you bastard!”

 