\section{chapter 203}

                             




-the ‘poison immunity’ buffs are being applied.
* this effect disappears when you exit the dungeon.
* kill the boss monster ‘1st python’sungwoo and his party went into the cave filled with poisonous fog.
 it seemed they entered what looked like a stone mountain that stood in the center of the huge trees.
wooooooooong-an unpleasant wind was blowing from inside of the cave, and all kinds of hieroglyphs were engraved on the wall inside the cave.
 some of them shone purple, which made them feel eerie as if they had stepped into an ancient temple.
sungwoo carefully looked at the mural because he thought the hieroglyphs were not there simply as decorations.
however, only pictures of a large snake inside a huge pit appeared one after another, and sungwoo could not figure out what they were.
“man, it looks like we are in the boss monster’s room right now,” said hanho.
only the sound of water dropping rang after he said that.
they kept walking for a while in silence.
“…”sungwoo looked at jisu, who had been staring at the inside of the cave with a frown from the moment she entered the cave.
she then shook her head and said, “i can’t feel anything either.
 it’s like we are blocked by something like a transparent plate.
”“i see.
”if she couldn’t feel anything with her senses, there was nothing here or monsters that could hide in the dark, which was more likely, sungwoo thought.
the bigger problem was that he had never met monsters that could hide until now.
he had no choice but to feel wary.
“given the size of this dungeon.
 i think the monsters here must be very unusual and big.
 so, we need to be very careful,” said sungwoo.
 he was also on alert.
imoogi, or python, was described as the boss monster of this dungeon.
 it was a mythical creature going through the process of becoming a dragon.
in other words, this creature could be completely different from the monsters he had encountered so far.
they became warier and warier when they stepped further into the cave.
 although they couldn’t explain what it was, they felt like something sticky was getting stuck to their whole bodies and pressing them.
“eww… the more i go, the more stuffy it gets.
 it feels like i’m in hot water.
”
“me, too…”hanho’s expression fit where they were now.
 it seemed to be similar to a decline in their stats, but hanho and jisu seemed to feel it more violently than sungwoo who had divine status.
but they could not stop moving.
“let’s keep going anyway.
”even though sungwoo took action to stop the other two camps from following them, he was not sure when they would catch up.
anyway, they kept walking through the long entrance of the cave, finally encountering a wide space.
thud!in other words, they stepped into a great darkness.
the space was so vast they could not light the whole place with only a few lanterns.
 the light was eclipsed by the darkness and lost its power.
the high dark ceiling and the steep cliff seemed to devour sungwoo and his party like a giant monster.
“uh, uh…”stunned by that terrible sight, hanho groaned, which resonated through the vast space.
they had no choice but to stop there because they realized that this wasn’t a space they could cross recklessly.
splash! splash!it was the sound of dripping water.
the small sound couldn’t escape from being heard in this enormous space, hitting and bouncing, cracking and crushing against the walls and ceilings here and there before scattering into hundreds and thousands of strands of sounds and disappearing eerily.
woo-uh-uh-woo-woong-they could not identify the sound with human ears until it was gone.
 this was a place where sound was born and died at the same time.
“sungwoo, look at that over there…”“i can see it too.
”from the bottom of the cliff in the darkness, two huge lights slowly rose.
-the boss monster ‘1st python’ has appeared.
even before sungwoo properly confirmed its shape, a message announced its appearance.

they slowly stepped back.
“uh, that snake is…”“be quiet!”the serpent was overwhelmingly large.
 its head was almost 5 meters in diameter.
 they felt like the headlights of a large truck were slowly approaching in a tunnel where the lights were off.
at that moment, the giant snake slowly opened his mouth.
 its hard scales contracted and relaxed, making a fine sound of friction.
sungwoo made a bone shield in preparation for its attack.
“welcome, masters of this land!”they never thought the snake would say hello by opening its mouth.
“oh, you are good at speaking,” sungwoo responded.
the serpent spoke accurately enough to make itself understood.
“is that all you’re curious about when you have come as far as here?”how could this monster communicate with humans? sungwoo had seen some monsters like kobold spitting out unintelligible words, which were closer to screaming than human language.
however, this monster was distinctly different.
 it did not attack them like a vicious beast but rather seemed to seek rational dialogue with the players.
the serpent even said something pedantic like this, “if there is no language, there is no world.
 there are only two concepts in this world, namely those just screaming and those like me.
 but i am fully aware of everything as part of this world.
”even these pedantic lines were recited.
‘isn’t this monster trying to deceive me with this intelligent speech?”but sungwoo realized that the serpent could respond to what he was trying to say.
“so, are you the only ones here? i heard more around you, but they must be wandering around.
”“are you going to fight us?” sungwoo asked.
when he suddenly asked that, the serpent shook its head slightly as if to express doubts.
“did you not come here to kill me from the beginning? why are you talking as if i picked a fight with you?”“…”sungwoo couldn’t refute it because it was right.
“now that you are silent, you seem to admit what i said was right.
 then, take responsibility for your lack of prudence.
”the serpent pulled its head back and disappeared into the darkness.
it was most likely that there would ensue a fight.
“the serpent will attack us, so get ready.
”they held their bone shields one by one and lowered their posture.
 since it was dark, they didn’t know where and how the serpent would attack.
rattle! rattle!sungwoo summoned ten troll skeletons to use them as shields.
there was a huge pit in the middle of the space with a flat corridor around its edges, so there was enough space for them to move around for the fight.
“…”holding his breath, sungwoo waited for its attack.
 since he didn’t know how the serpent would attack, he just needed to look at its movement.
– caution! ‘goblin fire’ has been summoned in the area.
at that moment, four blue fireworks arose in the air in front of them.
 layers of darkness retreated, revealing the silhouette of the giant serpent hiding behind it.
it was staring at sungwoo and his party.
 in other words, it was aiming for their lives.
“run!”“argh!”they immediately threw themselves to the side.
a blue flame spun near its head and flew in a non-linear trajectory like a missile.
then, the flame penetrated the troll skeletons standing before them as a shield.
bang!the ten troll skeletons fell like bowling pins, burned in the flames and crushed.
that wasn’t all.
 the four blue flames turned and returned, sweeping through the collapsing bones once again.
“damn it…”as soon as he raised his body, sungwoo summoned the “grim reaper” he cherished and summoned the power of lich.


-you have summoned the scythe of death ‘grim reaper’.
-grim reaper retention time (00:59:58)-you have gained the power of lich.
* you have increased your subordinate spirits by 50.
* you have increased stats by 10.
* you can revive and regenerate nearby undead ‘indefinitely as many as the maximum number of your subordinate spirits’.
“man, this guy has evil power,” the serpent said, staring at sungwoo who grew tinged with green flames.
sungwoo then summoned the power of anubis.
-you have temporarily gained the power of the death god ‘anubis’.
-you have temporarily obtained the status of demigod.
-all stats are greatly increased.
 (+10)-you can use  skill.
-you can use  skill.
-you can use  skill.
noticing sungwoo’s powerful skills, the serpent continued, “in addition to wickedness, you are full of savageness.
”sungwoo has now turned into a black wolf.
– caution! the ‘fellblade’ has begun in this area.
– caution! ‘response of death’ has begun in this area.
sungwoo summoned all his might at once.
 sungwoo moved his body in the black smoke and fired his repeating crossbow.
tung! tung! tung! tung! tung!behind him, the troll skeletons raised their bodies and fired the slingshots, while human beast skeletons threw javelins.
 that wasn’t all.
 two “rock golems” popped out of the wall, even throwing huge rocks at the giant serpent.
so, dozens of projectiles were fired at him all at once.
but all of them were blocked without any exception.
“what the heck?”

 