\section{chapter 290}

chapter 290: youngdungpo station, angel's coming (6)




although sungwoo didn't meet all of the conditions, all the rewards were revealed.
but he still couldn't figure out what would come out.
death, ghost and judge? what will come out when they are combined? is it something like a deity like before?‘i don't have to make wild speculation, no matter what.
 since there will be an opportunity for me to gain the judge's mark through our camp's growth, let me wait until then.
'even if he got impatient, there would be nothing different.
 so, he had no choice but to wait for the right time while he was absorbed into what he had been doing.
meanwhile, not only sungwoo but also all the players here also received special rewards.
“wow! i'm disconnected from the angel camp! my missing stats have come back!”“i have been enervated until now, but i'm full of beans now!”the liberation guild was literally “liberated” from the angel camp.
 all kinds of penalties they received whenever they didn't carry out the camp ques while controlled by the angel camp were cancelled when they were liberated from the shackles of the angel camp.
“okay, we've regained our energies, so let's get back to work! move!”there was so much work to do after they were freed from the angel camp, and first of all, they had to dispose of that angel's huge body that crushed downtown youngdungpo.
-you can't resurrect an external being as your subordinate spirit.
unfortunately, sungwoo could not revive the angel's bones.
 it was the same situation as when he could not revive the monsters that came out of the devil's gate.
it seemed that as they were from the external world, not earth, they were subject to a completely different rules.
but it didn't mean that sungwoo failed to collect any bones at all.
[item information]-name: bones of the absolute race-grade: unknown
-category: manufacturing material-description: these are bones imbued with strong power.
 they are st.
u.
r.
dier than most metals and have a better magic response than most mediums.
as the material for item production, they could be excellent material for sugnwoo's skill.
sungwoo immediately created hundreds of weapons and armor using the angel's body.
and he made the undead army wear that equipment.
[item information]-name: angel's finger joint long spear-grade: hero-category: long spear-effect: ignores the attack target's defense (10%)-description: a weapon made of the bones of the absolute race, “angel.
”[item information]-name: angel's rib armor-grade: hero-category: full armor-effect: creates a s.
h.
i.
+eld that is equal to an increase in defense (+30%) and 20% of defense power.
-description: this is an armor made of the bones of the absolute race, “angel.
”‘it's amazing.
'sungwoo supplied the undead army with a huge number of new weapons.

it was very difficult to supply such high-quality weapons and armor in large quant.
i.
ties, but sungwoo could upgrade them on this occasion this time.
 naturally, he could increase the combat power of the undead army.
“hey, sungwoo, so you gave all your subordinate spirits a pair of clothes?” said hanho, approaching him.
 “it looks like you had some conscience since you supplied them with such weapons after working them so much.
”“so, do you want me to give you one, too?”“oh, my g.
o.
d, you mean that bone armor? no way! look at my helmet and other weapons!”hanho, wearing an asura cloak and an iron helmet, turned around to show off.
sungwoo met jisu's eyes while turning his gaze away from hanho's ugly armor.
 she was also frowning at him.
 mir was sleeping in her arms.
“mir just fell asleep.
”“yeah, he's still a baby.
”“you bet.
 it looks like he was tired after whining a lot then fell asleep after hugging the chicken skeleton.
”mir didn't let go of the chicken skeleton, the only survivor of the battle.
was it like something like mir's pet doll?meanwhile, minsok reunited with his family at youngdungpo station.
 actually, he could not afford to take care of his family because he had to move around here and there, but finally he could meet them.
“dad! mom has told me that you are saving the world with uncle necromancer!”“haha! you are a good boy who listens to your mom, right?”“absolutely! can i change like you if i am a good boy, right?”“haha …”did his children not know it yet or pretend not to know it? although his six-year-old son was all smiles on his face, his eight-year-old boy looked gloomy at the moment.
while they were taking a break after doing some restoration work at youngdungpo station, junghoon and minhum visited sungwoo's group who were preparing to go to suwon.
“i am wrong.
”jungwoo felt a sense of loss when he said that.
 he parted with sungwoo by choosing the absolute race, but he experienced a painful failure, after all.
as a result of his wrong choice, those who trusted and followed him also suffered a lot of damage.
but sungwoo shook his head and said, “we don't know the correct answer until this game is over.
”like sungwoo said, they could only know at the end of the game who was right and wrong, and if there was any clear guideline on that.
“can we finish this game?”there was some gloominess on junghoon's face.
sungwoo pondered over it for a moment, then nodded.
“i think the person who has created this game must have arranged for it to end at some point.
”“then, though i'm a bit late, can i join you until the end?”this wasn't the first time that junghoon reached out.
 however, he was different this time.
 in the past, sungwoo felt he was always wary of him, but he has completely changed now.
“sure, you can.
”sungwoo held his hand.
 of course, he would welcome junghoon and the liberation guild because even when junghoon belonged to the angel camp hostile to the world tree camp, he supported sungwoo even by violating his camp's order, and several times at that.
“then, let me go back to suwon for now….
”right at that moment, gust appeared above youngdungpo station.
“what the heck? isn't she heyon? why did she come here suddenly? did something bad happen to the village?”if she really came as hanho said, there must have been something bad in the village.
soon, gust landed on the street in front of the station.
 she jumped down and came running to sungwoo.
 she looked impatient.
“necromancer!”

“what's up?”she caught her breath first before opening her mouth.
“american players came here.
”“america?” hanho rumpled his hair as if he was startled.
“man, this time they came from america? when did our country begin to see so many tourists?”seongwoo asked calmly, “did they attack the village?”fortunately, heyon shook her head.
“no.
 they just said they wanted to meet and talk to you, necromancer.
”“i don't think that's the main reason you came here so urgently.
”she slowly nodded and said, “so i told them to wait…”she looked pretty embarra.
s.
sed.
“they were all killed by someone.
”“killed?”“yeah.
 the flying s.
h.
i.
+p they were riding on exploded, and a fight suddenly broke out.
 when our security guards approached them, the guys in black masks ran away.
 brother kyongsu told me i should report to you because he felt rather ominous.
”“wearing masks?”this was something definitely suspicious.
so far, his strategy to tackle this game has been simple and clear.
 in other words, all he had to do was to survive and become stronger after beating the enemies.
but something complicated was happening all over the world.


 