\section{chapter 280}






 vladmir threw the ax over hanho’s head.
 hanho blocked it with a dagger a little while ago, but this time, he couldn’t respond.
although hanho was wearing an iron helmet, it would be crumpled like a piece of paper and his skull would be broken by the ax.
clang―however, vlamidir’s ax stopped in the air.
 to be precise, it was blocked by a golden shield.
“uh?”“hey, your iq is the same as my hamster!”puck! puck! puck! puck! puck!while vladimir was confused for a moment, hanho stabbed his body with six daggers.
“khuuuuuuuuuuuu…”“when i put my hamster in the transparent case, he used to keep scratching it, thinking there was nothing there.
 you are exactly a giant hamster!”“shut up, you crazy bastard…kuhhhhhhh.
”vladimir fell under hanho’s feet.
“i’m… kuhhhhhhh… a warrior…”“goodbye, hamster.
”“…”the warrior who lived harshly in the siberian fields during his life ended up being treated as a hamster in his last moment.
anyway, the tide was turning in favor of sungwoo and his party.
 above all, tatana could not move freely because of bone salamader’s blocking her during the battle, which played a big role in helping sungwoo’s forces beat the siberian hunters.
“i got him finally!”however, bone salamander was frozen due to tatana’s continued freezing magic.
 she then sealed the monster with solid ice then turned her gaze away.
“now, let’s strike back!” she shouted.
at that moment, the frozen salamander’s body collapsed, and a blue fireball ran through the gap.

it was the necromancer.
huuuuuuuung!he threw the sickle at her neck, but she blocked it with the small shield, buckler, in her hand.
she suffered huge damage with buckler cut in half, but she could save her neck.
but she couldn’t block him from throwing his left punch.
“khuuuuuuuuuuuk!”his punch held tremendous power and knocked down her left cheekbone.
 her body was thrown into the air before falling down on the ice ground then sliding along it.
“gasp, gasp…”with a painful groan, she struggled to raise herself desperately.
 her cheekbone was smashed, and one of her eyes was completely closed.
“i thought i was going to kill you with one stroke, but you’re much stronger than i thought.
 it looks like you have good bones.
”looking down on her, sungwoo spoke in a relaxed voice.
 it was a completely different situation from when she started the fight.
 she could not stand her shame.
“damn it, i really can’t stand it.
 wake up the tsar!” she shouted, raising her body.
then, the hunters standing behind her looked embarrassed.
“what? are you serious? he’s going to be insanely upset!”turning to the man, she growled, “anton.
 he is going to chew up half of us who have survived.
 are you going to put up with his anger?”“no way! sure, let me wake up the tsar before it’s too late!”they hurriedly changed their strategy.
 sungwoo wondered why they were hesitant to wake up the guy called tsar, notorious for his nasty temper, in this emergency situation.
and the next moment one side of the walls of yongsan station was thrown entirely.
“uh? is he awake already?”then, four “agency giant bears,” one of which sungwoo just killed a little while ago, appeared.
 the siberian hunters began to retreat to the side.
“kuuuuh! ouch, my head…”
a huge guy appeared staggering among the four ancient giant bears.
 he was holding a bottle of vodka in his hand.
“what the heck? damn it!”he looked around, as if he still had a hangover, and looked at tatana.
“tatana, i told me not to wake me up until the sunset, right? can’t you remember it better than me who hasn’t sobered up yet?”“but if we didn’t wake you up, we’re in big danger.
 just look at my face, tsar…”“uh? your face has always been ugly.
”“you bad guy!”the tsar guy threw a bottle of vodka at tatana and stepped forward.
 and he faced sungwoo now.
 while rubbing his eyes, he seemed to have come to his senses suddenly.
“oh, are you that dog of death that the chinese guys talked about?”1he smiled brightly, spreading his arms.
 then, he shook his index finger up and down toward sungwoo.
“very nice! after treating you with formalin, let me put some nails in your joints and display you in front of my room.
 you’re going to be a perfect display!”sungwoo retorted with a scornful laugh, “oh, i’ve thought the same thing about you!”“really?”sunwgoo also scanned the tsar up and down and said, “by the way, you can’t be my match.
 can you do something like transforming yourself?”“uh? what the heck are you talking about?”at that moment, jisu shouted, “hey, sungwoo!”there was some urgency in her voice.
“i can’t find mir…”mir? when sungwoo turned around, he could not see mir in her arms.
then, mir came right under sungwoo’s feet, more precisely his shadow.
‘mir has duplicated my shadow movement?’sungwoo was stunned.
 was mir able to imitate all his skills?but that wasn’t the problem at the moment.
 sungwoo covered mir’s body with his feet.
‘if that guy notices he’s a dragon, he’s going to aim for him mercilessly.
”but mir came out of from near his feet, walked around, then stared at the giant bears in front.
“uh? what the heck is that? is it a cat or puppy?”grrrrrrrrrrrrng!then, mir started to growl at the bears, hundreds of times larger than him as if he was not scared at all.
-‘dragon fear’ has been activated.
* it stiffens the creatures of low level and intelligence.
surprisingly, his skill worked.
grrrrrrrrrrrrrrrr-the huge bears opened their mouths, along with convulsion in their huge muscles.
they were violently trembling in front of mir.
the tsar guy turned his head and looked at his subordinate spirits because he felt something strange about them.
“what’s the matter with you? did you drink my vodka when i was sleeping?”-since the target’s level and stamina are high, ‘dragon fear’ has been applied only to a certain extent.
* all bodily functions fall into a ‘rigid condition’.
 (-60%)ancient giant bears were much stronger than this little dragon.
was it because of their low level and intelligence? certainly, the baby dragon’s “dragon fear” skill was paying off.
“oh, my god…” hanho said, giggling at the spectacular scene.
“sungwoo, these guys from siberia are all like hamsters despite their huge build, aren’t they?”today, siberian hunters at yongsan station were being treated as hamsters.


yong or dragon, the legendary animal, was described as the most powerful creature in both east and west.
grrrrrr! grrrrrrrrr!sometimes it was portrayed as being comparable to god, or even accepted as god himself.
grrrrrrrrr-and the skill that the dragon can best reveal his dignity is the skill called ‘dragon fear’.
“what the heck? what’s the matter with you? were you guys hit by that little creature?”as the tsar guessed, the ancient giant bears were horrified.
dragon fear means the fear that the target feels when they see the dragon.
it is a fundamental fear that goes beyond ultra-low frequencies that can be felt by beasts such as tigers and lions.
 if a fragile creature faced it, of course, all of its muscles would be paralyzed, and in severe cases, it would die immediately.
sungwoo thought, ‘mir’s dragon fear is still weak, but it’s more than effective.
’even though he was still a hatchling, mir, who was from an absolute race, made monsters that were hundreds of times larger than him, get cold feet, and shrink.
kaaaaaaaaaaaaaaaah!as if they were ashamed to run away, the huge bears began to move their paws like pillars.
thump… thump…however, their movements were unusually sluggish.
 furthermore, their legs were clearly seen trembling violently.
 even though they overcame their mental fear, they could not help but tremble out of fear.
thud······since their muscles were judged “stiff” by the system, their “status abnormality” was bound to continue unless some appropriate measures were taken.
“why are you idiots so slow?” the tsar shouted.
as if he was pretty offended by their funny movement, he stretched his hand behind his back.
 then, tatana handed over the bottle of vodka to him.
 he drank vodka hysterically, threw the bottle, and broke it.
 then, he lifted his index finger and pointed at mir, raging into anger.
“damn it! trample that wiggling thing and kill him!”grrrrrrrrrrrrr.
as if he was surprised by his shouting, mir clung to sungwoo’s feet.
 then, he stared at the tsar, growling at him.
 his red eyes flashed once.


 