\section{chapter 155}

                             




sungwoo stood in front of the golden hammer-shaped icon.
 he was inside a cafe in downtown kanghwa island.
 as expected, there was a combination table in front of the counter.
when he approached it, a message appeared.
[item production/combination]-there are items that you can combine.
* required cost: 1,500,000 gold (not enough medium)shadow king’s robe (material) + drake’s leather (material) = ???* required cost: 2,000,000 gold (not enough medium)there were two items in total.
 it seemed that sungwoo could enhance both of them to enhance equipment items with the materials he obtained by hunting drake during the youido raid, but this time, it was more expensive because he had no medium such as the ‘elder slime core’.
sungwoo pulled out two material items.
[item information]-name: drake’s leather-class: hero-category: production material-description: this is a young black drake’s scales.
 the quality itself is not good because it has not yet fully grown, but it is still strong enough.
[item information]-name: dragon race’s heart (lower level)-grade: legend-category: production material
-description: the heart of a dragon is quite different from that of a trifling creature.
 it is an item that you should treat valuably.
“man, i can use this at last.
”it’s been a while since he obtained it, but he didn’t have time to stop by a forge.
so, he put the ‘repeating crossbow’ and the ‘dragon race’s heart (lower level)’ on the enhancement table.
-you have to pay (1,500,000) and there is a probability of damage (3%).
 do you want to proceed?“go ahead.
”-their combination is in progress.
 please step back from the table for safety.
wuuuuuuuuung!the shape of the dragon race’s heart crumbled as if it evaporated, then it began to be sucked into the repeating crossbow.
-their combination is complete.
it didn’t seem that its appearance changed, but red energy radiated from its body.
[item information]-name: repeating crossbow-flame-grade: legend-category: crossbow-effect: increases damage by itself (+20%), and a magazine connected to the armory in the subspace is loaded.
 (it can be fired without loading.
) if you inject mana, you can use the ‘fire arrow’ function for one minute.
there were many changes in item information.
 then, sungwoo pulled out a small stone.
“oh, yes, i’ve forgotten this!”it was a ‘c-grade equipment enhancement stone’.
 he chose this item as a reward at the golden dungeon, but he had no opportunity to use it because he hadn’t stopped by a forge.
sungwoo put the enhancement stone next to the repeating crossbow.
 then, a message appeared.

-you have to pay (1,000), and a probability of damage (5%).
 do you want to proceed?“go ahead.
”wuuuuuuuuuung!-its combination is complete.
[item information]-name: repeating crossbow-flame (+2)-grade: legend-category: crossbow-effect: increased agility (+3), increased damage by itself (+30%), a magazine connected to the armory in the subspace.
 (it can be fired without loading.
) if you inject mana, you can use the ‘fire arrow’ function for one minute.
“it’s okay.
”since it was a weapon with a very fast rate of fire, it would bring about a huge increase in damage.
 if sungwoo obtained the effect of a shadow alter ego, he would be able to destroy even a large number of enemies.
finally, he combined the shadow king’s robe’ and ‘drake’s leather.
’ it was a success.
[item information]-name: shadow king’s robe-dragon scale-grade: legend-category: coat-effect: magic damage reduction (-10%), flame immunity increase (+30%), self defense increase (+50%) you can hide when you are in shadow.
 (when attacking an opponent, you will appear, but you can be detected by detection skills.
)two options were added, and as expected, there was no change in design.
 however, drake’s leather was on the robe lining.
after he was done combining items, sungwoo uploaded a profile.
[player profile]-name: sungwoo yu-level: 19-job: necromancer, black wizard-ability: strength (21+9), agility (15+9), stamina (14+7)-gold reserve: 27,855,400-trait: chaos-maximum number of subordinate spirits: 17before he met with kangsok han, the no.
 1 on the korean server, sungwoo obtained maximum stats.
***doodoodoo!when the helicopter carrying sungwoo and minhum entered youngudngpo, three magical drones approached it.
 the drone filmed the inside of the helicopter to check its occupants, and it also served as an escort by monitoring the surrounding situation closely.
“wow, this is great!” hanho said with admiration.
like he said, youngdungpo, as seen from the sky, had changed a lot.
 the outer walls that collapsed after the evolution society’s terrorism had been repaired completely.
 given the translucent protective film protruding from the entrance of the building, it seemed that there were several ‘safety zones’ operating all the time.
furthermore, there were a total of 16 guard posts in all directions, and each guard post had two gunners on duty.
“you’re right.
 i feel they are full of determination not to allow any attack.
 there are multiple layers of security around the building.
”that wasn’t the end.
 there was an ‘outside fence’ outside the ‘inner fence’ surrounding youngdungpo station, so those groups who came to join the coalition were staying in the shopping district around the station.
 they also dispatched their guards on the rooftop and watched the surroundings.
minhum added, “a whopping 6,000 people came in droves in just a few days.
 in some cases, they came here in groups, but most of them came individually.
 so, when we form an alliance, many more people will come.
”there were about 30,000 survivors in youngdungpo before the attack, but junghoon said it was rather difficult for him to take care of them.
so, sungwoo could not be sure how many survivors would come when more alliances were formed after a successful negotiation.


nonetheless, it was clear why junghoon was attracting more and more people because the huge population would be a tremendous power for him when he established the foundation.
“do you see that over there?”when the helicopter’s altitude lowered, minhum pointed at the end of the road.
there were several military helicopters and dozens of blue tents around them.
“those guys over there are a big headache.
 they are called the reconstruction alliance.
“are they soldiers?”“well, not all of them.
 they are players from uijeongbu and namyangju, but i hear some of them are from the military.
 so, it seems that they have quite a bit of military equipment.
 with those weapons, they were apparently in the process of integrating the northern forces of kyonggi province.
 they are a very big force in that area, so they are not obedient,” said minhum in an annoyed voice.
he continued, “to say the least, they are disturbing our activities.
 we keep noticing they’re involved in something that really bothers us.
”he also said that they seemed to be trying to induce a war of nerves with the liberation guild for some kind of political operation, so much so that they were trying to stop the liberation guild from becoming a bigger force than they were now.
“we have noticed their spies checking our movement secretly and reporting to their bosses several times.
”“have they already started to hold you in check?”“i guess so.
 i am concerned that just like in medieval times, we might fight each other through something like political operation and veiled enmity.
”like minhum said, if the reconstruction alliance decided to maintain their power, they would not like the creation of a united alliance of the survivors, so they would likely stand in the way by pretending to join the alliance.
wuuuuuuuuuuung!soon, the helicopter landed.
 the new landing area on the boulevard had been expanded because some groups in remote places used planes.
two crusader members were on the ground to welcome them.
“welcome!”“our commander is waiting for you.
”sungwoo and minhum headed to the conference hall inside youngdungpo station.
 he said that junghoon was waiting there.
when they arrived on the second floor where the conference hall was located, there was a disturbance at the end of the hallway.


 