\section{chapter 235}






 an ‘exclusive quest’ was issued.
 after checking the message, sungwoo raised his head.
“death is not something you can control by studying it,” sungwoo said.
doctor smiled bloody and stepped aside.
chimera, a giant monster that had already been transformed, came one step forward.
thud-its size had already grown to about 30m.
 as the quest message said, it seemed that chimera was getting stronger and stronger after each kill.
“is this what you mean by being one body? all humans are being eaten by that monster?”“what a fantastic future! yes, we’re all heading towards the ultimate one.
”doctor’s voice was very polite.
he continued, “i’m sorry for coming late, but can i take the climax?”taking the climax?having heard that, sungwoo alternately looked at “doctor” and chimerathen, he giggled at them.
 he pulled an object from his pocket.
watching him, doctor scorned him.
“what is that? is it something valuable that you can take out to confront chimera?”it was a nondescript black crown with no ornaments.
“don’t be mistaken.
”[item information]-name: shadow king’s crown-class: myth-classification: hat-effect: private (qualification required)
-description: you can use ‘shadow king’s power’ only when you collect all the shadow king’s relics.
* holds shadow king’s relics (4/4)“you haven’t seen the climax yet,” said sungwoo, then he slowly put on the crown.
-your qualifications have been verified.
-‘shadow king’s power’ has been granted.
ooooooooooh-sungwoo’s shadow began to expand to an enormous size.
even without the influence of light, it grew endlessly, ignoring all the natural laws.
 and it soon reached the building behind him.
 as if it was blocking the light of a projector, the shape of a giant filled one side of the building.
sungwoo did not move.
 the shadow moved alone.
 it spread and raised both hands slowly and widely as if it were a benevolent king, looking down on everything and controlling everything.
– caution! the ‘fellblade’ begins in the affected area.
– caution! ‘death response’ begins in the affected area.
black smoke soared around sungwoo.
 among that came out dozens of undead.
 then, a black swamp unfolded, where a horde of zombies crawled out.
 after that, corpses on the battlefield were entangled, before two “flesh golems” raised themselves.
all of them stood tall around sungwoo.
 they were the total force that sungwoo could summon.
“haven’t i seen all of them in the past?” said doctor in a relaxed voice.
 he thought they could not beat chimera, but this time something new to doctor unfolded.
– caution! ‘shadow corps’ will rise in that area.
the shadows of the undead troops began to wriggle.
 they were moving even when the owner of the shadow didn’t move at all.
 and their hands, which were two-dimensional planes, popped out into the air from the bottom.
tsutsutsutsu―the shadows began to climb into the real world.
tsutsutsutsutsu―other shadows climbed up from the ground and stood among the undead.
then, the shadow slowly turned its black face and looked at doctor and chimera.
“what the heck is this…”
it was the moment when the necromancer’s forces doubled.
“this is the climax!”as always, the climax happened when he wanted it.
sungwoo received a black necklace from jisu a little while ago.
[item information]-name: shadow king’s necklace-grade: legend-category: necklace-effect: increases stamina (+6).
 you can obtain ‘visual information’ and ‘auditory information’ by controlling one shadow in your view (cooldown: 5 minutes)that was the shadow king’s last legacy.
“i’ve got all of them!”by collecting all four relics, sungwoo completed the hidden quest titled “heir to the shadow king”.
 and finally, he took possession of the “crown of the shadow king.
”-you have acquired a new skill as the ‘heir to the shadow king’.
 (power of the shadow king)[skill information]-name: shadow king’s power-grade: special-category: active-condition: shadow king’s heir + shadow king’s crownthe cooldown of all skills related to ‘shadow king’s relics’ has been drastically reduced.
 (-50%)+ shadow king’s army: you can realize all the shadows under your control as ‘shadow soldiers’ for one hour.
shadow soldiers have 50% attack power and 150% defense power, but they do not disappear until their original owner dies.
 (cooldown: 12 hours)“this is a jackpot!”as a result, sungwoo had completed a set item that could create optimal synergy with the existence of the necromancer.
but the very next moment, the subject of his experiment appeared before his eyes.
it was none other than the evolution society, a cockroach-like and deep-rooted arch-enemy of sungwoo.
but right now, doctor, who witnessed the shadow corps, couldn’t hide his anxiety even though he was wearing a gas mask.
sungwoo shouted, “you don’t think only you have been developing something new, right?”“…”chimera was a powerful creature.
 so much so that it ate tengu who had enough power to stop a huge transport plane.
 with such terrific power, doctor might have thought chimera could get rid of the necromancer who defeated them every time, but who could have expected that the necromancer also became stronger, and doubly at that in an instant?“it’s amazing to see you whenever i see you,” doctor honestly expressed his feelings, but he didn’t give up.
doctor trusted the creature he made.
 wasn’t it the fruit of the long and hard efforts of the evolutionary society?it was a vicious monster that would never bow down even when it faced the incredibly strong necromancer.
 chimera was certainly such a creature.
“well, i admit this is your climax.
”“you are trying to distract me with words.
”sungwoo did not want to continue to converse with him.
 even while he was talking bullshit, his time to maintain the shadow corps was decreasing.
 for now, sungwoo’s only enemy was time.
“i don’t know how long you spent making that shit, but i can smash it in an instant,” sungwoo quipped.
“really?”sungwoo then lifted the black sickle.
 at the same time, a huge shadow cast on the building reached out.
“alright.
 you just keep sitting there and counting the numbers.
”that was sungwoo’s attack signal.
 the death corps was ordered to charge at doctor and his forces.
goo goo goo-soon, a tremendous vibration rang out in downtown busan.
 a group of undead and shadow soldiers filling the four-lane roads began to move.
when they began to move, tangled with each other, they seemed to be moving as if they were a huge group.
 as such, they were charging at their target in an organized manner.


“you guys are so impatient!”doctor fled, whistling.
then chimera, who had been stopped, reacted.
kueeeeeeeeeeeeeeeeeeh!without hesitation, chimera began to stamp his feet.
 the moment they collided, chimera violently swung his front legs that looked like hooks.
kwaguaguaguagua!those at the forefront of sungwoo’s forces were caught in the hooks.
 they had tremendous destructive power, enough to smash a large skeleton to pieces, but that was all.
 chimera’s hooks smashed only some of the hundreds of processions, but an unstoppable storm swallowed chimera.
kueeeeeeeeeeeeeeeh!the corps of death charged at chimera like raging waves.
 like a huge ship being swept away by waves, his huge body skidded on the road helplessly.
the mixed forces of skeletons, zombies, ghouls, shadow soldiers, and all kinds of undead jumped at chimera like crazy dogs.
some of them penetrated through his feet.
 some climbed over his head.
 and others turned around and hung on his side and back.
puck! puck! puck!they punched, struck, and kicked their target with all their might.
 although their attacks were not powerful, they continued to inflict damage on chimera.
kueeeeeeeeeeeeeeh!despite their intensive attack, chimera tried moving desperately.
 he began to shake off those stuck on his body with the tremendous elasticity peculiar to the annular animal.
he then rotated his long body and swung his tail like a mace, which struck down dozens of undead, but the undead had no intention of retreating.
 they resurrected and went straight back to the battlefield.
 they looked like a herd of pit bulls charging at their target.
 they were tenacious and persistent.
rattle! rattle!they never died.
 they didn’t stop because they didn’t die.
 chimera couldn’t stop them because they didn’t stop.
thud! thud!after all, chimera found himself being pushed out until he bumped into an eight-story building.
although he suffered such an intensive attack, driven into the dead end, it was the building that began to collapse first.
since hundreds of monsters kept attacking him as one unit, there was no way for chimera to stick it out to the end.


 