\section{chapter 306}

the master of the workshop, arnold hearst's job was "elder blacksmith," a 5-star blacksmith.





he could create a group called "workshop" and raise blacksmiths by giving the blacksmith candidates an "additional job.
" so, his blacksmith team seemed to be similar to junghoon's crusader team in concept.
 "it's good that you are here! i have been bored because all my customers are gentlemen from washington dc.
"although he was a proud blacksmith, he was also a trader who wanted to make lots of money by using his skills.
 although he threatened jonathan that he would not repair the airship, he already dispatched his blacksmith team to the dock to start repairing it.
 actually, it was natural that he acted like that because without gold he could not run this huge workshop, let alone make a decent product.
"hmm.
.
.
 what is the object you want to make?""i need a safe space to take this item out.
"hearst chuckled at him and said, "hey friend, do you think there is a safer space to work than this hearst workshop? are you going to go to the arizona desert? there must be an abandoned us military laboratory somewhere there.
""well, i said that because i might interfere with your other tasks.
 since it's delicate work, won't your work be affected by even a little temperature change?"hearst took a step back and nodded, saying, "i like that comment.
 just follow me.
" he took sungwoo to an empty studio.
 given that there were scratches and scorch marks all over the place, it seemed to be a place where he conducted dangerous experiments.
"which do you want to make? cold or hot stuff? or thrilling stuff?""well, it has a cold property.
""got it.
"shortly afterward, his men brought in a bunch of unknown metal materials.
 when hearst snapped his fingers, they were automatically bent and a huge box was made.

"it just took 100,000 gold for me to make this safe box.
 i'm going to send the bill to you.
""no problem.
"it seemed that he used the 'auto-complete technology like muyon's architecture technology.
 he could activate it by consuming gold when mana was insufficient.
sungwoo went inside the "safety box" and summoned a skeleton.
rattle!the guy was carrying a backpack, but his backpack and back were completely frozen for some reason.
 so much so that there was even an icicle sprouting between his bones.
"oh, my god! it's disgusting.
"while hearst was muttering, sungwoo pulled out the "frozen seed" from his backpack.
at that moment, hearst opened his eyes wide.
 "oh, god.
.
.
.
"he observed the frozen seed with both hands between his armpits while rolling his eyes.
 in the meantime, the temperature inside the safety box dropped rapidly.
"i'm sure this is one of the most disgusting things i've ever seen.
"
he let out white breaths, opened the iron door of the safety box, and went out.
 then, he yelled at his subordinates to bring his coat and looked back at sungwoo.
 "okay, so what do you want me to make for you?"sungwoo brought out the 'repeating crossbow' and 'hand cannon'.
 they were long-range weapons that he used frequently, but recently he felt that their destructive power was not strong enough.
 "use this item to make something like a portable hand cannon like this.
 it should be small enough for me to carry.
"hearst laughed at that and said, "you must be crazy.
 are you going to make it your personal weapon? do you know what you are asking me now? it's like you are asking me to make a revolver out of plutonium.
 just ask me to make a nuclear bomb!""can't you make it?"".
.
.
""then let me pay for this box only because the korean servers also have great technicians.
"there was no longer a smile on hearst's face.
 then, he responded angrily as if his pride was offended, "hmm, nothing is impossible in the hearst workshop.
 we have a bunch of trouble makers here.
""hope i'm in your good hand.
"hearst took out a cigar and lit it.
 "another headache!"***while the hearst workshop was making the special order, sungwoo heard about the situation of the us server and the wpu's purpose at chairman love's office.
"america is a very complex land.
 if order breaks down, i think america is the perfect place to rebuild order.
"the us was divided into three servers, namely, one on the east coast, another one in the midwest area, and the third one on the west coast.
compared to the chinese server, which was also divided into three, the american population was much smaller, but the size of its land was similar to the chinese mainland, and there were lots of developed urban centers.
however, alaska was independent of the us server.
"because of its large land, america had three servers, and there are diverse races and cultures, so it was inevitable for the us server to branch out into quite a number of forces.
.
.
"sungwoo already heard that chairman love's leadership played a crucial role in merging the various servers into one, namely us server 1.
in particular, the wpu held the hegemony of the eastern coast and formed an alliance with the central part.
 they were allegedly continuing exchanges with all the servers in canada.
"and some time ago they contacted the japanese server and you, the korean server.
"the wpu was now in contact with other servers to create a "world players alliance".
however, they suffered a setback because of the necromancer.
 admiral baker's wrong calculations made things worse and ruined the wpu's plan.
"well, i can't blame any particular man.
 all of us were arrogant.
 because we endured without suffering big damage, compared with other servers, we thought our organization was far more healthy…"she grabbed the coffee cup and continued, "we were arrogant enough to use our overconfidence to persuade other servers.
 we didn't realize we were not ready yet…"even though she looked back on the wpu's mistake, she still did not give up her dream.


"but we still need a coalition…"chairman love looked straight into sungwoo's eyes.
 "i am not going to give up or wait too long.
 i don't know what will happen later if i wait too long.
 so, i hope you can help me unite the world.
"that was what sungwoo expected.
 however, he had no intention of accepting her request hastily because he was not interested in uniting the world.
"as for the necessity of creating the world players alliance, you are not trying to make it just for a great cause, right? didn't you think that you could not stop the threat from latin america with the wpu's strength?"sungwoo had already heard about this.
 as a matter of fact, there were the wpu's own needs behind chairman love's plausible excuses for creating such a world coalition.
chairman love nodded honestly and said, "that's right.
 i want to unite all the forces to cope with the threat we face or somebody's threat.
 like you said, the situation in latin america is not very good.
 after all, their problem will be our headache sooner or later.
 and if we collapse, america, canada and the rest of the world will fall one after another.
""is the culprit brazil?' she nodded, then said, "the mexican cartel is obviously a big headache.
 they are a bunch of lawless thieves who often come up to our land and roam around everywhere.
 however, they are divided into many forces, so they are not a big threat.
 as you know, however, brazil, or more precisely, those monsters growing in the amazon.
.
.
"love paused for a moment and sipped a cup of lukewarm coffee.
and she raised her head again and said, "you also have a baby dragon, right?""that's right.
"with her face grim, she said, "the fully grown dragon is there…"

 