\section{chapter 162}

                             




cheeeeeeeeeeeeeeeee-that was the sound of fire extinguishers being thrown.
 the powder of the fire extinguisher scattered in all directions, blocking oxygen.
 that alone would significantly lower the surrounding temperature.
the monster birds that successfully used the fire extinguishers quickly raised their altitudes.
at that moment, the monster raised his left hand.
a fireball, or a huge sphere of fire, spewed out of his palm, covering the sky.
hit by that fireball, two monster birds crashed.
“fire extinguisher team, go!”hanho and the players pulled the hose out of the indoor fire hydrant in the school.
after pulling out the 25-meter hose, they grabbed the tip of the hose and aimed over the fence.
“turn it on!”“turn on the water!”pooooooooooooooh!the cloth hose swelled and gushed like a water cannon.
 after soaking the body of the flesh golem, the water stream was blown out toward the hell moving armor.
however, the temperature around it was so high that most of the water evaporated before it even reached the ground.
“keep blowing the water!”“the temperature will go down!”cheeeeeeeeee!like a wet sauna, the whole area was covered with vapor.
“now, let me go and attack the monster,” said sungwoo, jumping off the roof.
minsok and orun followed him, jumping down to the ground.
“are we all done if we kill that monster?”“yes.
 do attack the monster as much as you can.
”since they were prepared thoroughly in advance, it was time for them to confront the monster directly.
-the dead will be your subordinate spirit.
-the dead will be your subordinate spirit.

-the dead will be your subordinate spirit.
three hellhounds raised themselves among the piles of corpses on the playground.
the three-meter beasts lowered their bodies, so sungwoo and his party could get on them.
“let’s get on.
”they got on the hellhound skeletons.
“let’s go!”the hellhound skeletons jumped off the ground.
 they ran at tremendous speed.
 sungwoo ran towards the hell moving armor and lifted the grim reaper.
 minsok and orun stood side by side.
and the moment they jumped over the fence, they disappeared into the black smoke that suddenly appeared.
– caution! the ‘fellblade’ begins in the affected area.
– caution! ‘death response’ begins in the affected area.
soon, three hellhound skeletons popped out of the black smoke, followed by dozens of undead headed by bone drake and ogre skeleton.
 furthermore, two bone wyverns soared into the sky.
thud! thud! thud! thud!the undead army launched a frontal assault on the single enemy: the hell moving armor.
rattle- rattle-the hell moving armor approached them loftily, holding a 5-meter-sized spear.
“fire extinguisher, ready to fire!”in the meantime, the human monster skeletons, summoned for this fight, were holding fire extinguishers.
 when sungwoo ordered, they pulled out the safety pin and lifted the nozzle at the same time.
“disperse!”shortly before they encountered the monster, sungwoo shouted.
 they scattered to the right and left, forming a circle around the monster.
the monster stopped and looked around once.
 then, he slowly raised his left hand for a fire sphere attack.
at that moment, sungwoo shouted, “release!”the human monster skeletons released the extinguishing agent all at once.
 although the shooting distance was not long, the extinguishing agent powder spread in all directions, forming a thick veil.
 by blocking oxygen, it caused the target to suffocate.
not surprisingly, the flame sphere that flew through the veil was noticeably smaller.
even the magic of hell seemed to be unable to completely ignore the laws of nature.
‘poisonous cloud!’in addition to this, dark clouds formed over the monster’s head, spraying raindrops.

cheeeeeeeeeeee! cheeeeeeeeee!the raindrops were getting stronger and heavier, and his body temperature dropped considerably.
 in other words, they could approach and attack him.
“attack!”rattle! rattle!troll skeletons with shields and maces stepped forward first.
 they were armed with synergy power that could break the plate armor.
booooooooooong!however, before they got close enough to attack the monster, he swung his huge spear violently, smashing five troll skeletons with a single stroke.
it caused tremendous damage to sungwoo.
 at the same time, huge flames broke out and engulfed the herd of ghouls.
 dozens of them collapsed at once.
‘how could they collapse like that when they were wearing bone armor and had bone shields? it’s dangerous!’but sungwoo looked for a loophole in his attack for a decisive counterattack.
clang!sungwoo struck the monster’s right shoulder and got out of the striking range of his huge spear.
the moment the monster looked back at sungwoo, minsok ran from the other side and smacked his back.
 then, orun fired the hand cannon while passing by his ribs quickly.
grrrrrrrrrrrrrr-when sungwoo’s allies attacked him intensively at the same time, the hell moving armor’s huge body began to stagger.
 in the meantime, the troll skeletons that had been cut in half were completely regenerated.
 no matter how high their damages were, they could be revived as long as they didn’t die.
 the troll skeletons advanced again.
at that moment, gray smoke erupted from his helmet like a long sigh.
 it looked like the monster was determined to fight it out.
 he grabbed the giant spear, then stuck the troll skeleton at the forefront and lifted it.
kwagagagagagaga!at that moment, a flame swirled from the spear and swallowed the troll skeleton.
 then it melted and shredded its thick bone like a mixer.
 the skeleton turned to ashes and disappeared.
‘that’s dangerous.
’troll skeletons were regenerated no matter how often they were attacked, but if they turned to ashes like that, they were unrecoverable.
‘i’ve got to make sure i do not lose these important undead.
’sungwoo stopped in the shadow and lifted his repeating crossbow.
tung! tung! tung! tung! tung!the enhanced arrows struck him in the back of the head.
 the monster turned and raised his left hand.
 six flame spheres were fired at sungwoo, but he wasn’t there.
 sungwoo had already moved to another shadow.
the monster started looking around for sungwoo.
thud! thud! thud!seizing that moment, ogre skeleton rushed and threw his punch using the lightning skill of his bracelet.
bang!blue lightning rained down on the hell moving armor with a powerful impact.
 it was powerful enough to blow up a whole building, but it only made him kneel.
but that was enough.
while he could not move for a moment, the two flesh golems charged at the monster, followed by 25 zombies.
“tie him up!”two large flesh golems, whose bodies were sufficiently wet, pressed the hell-moving armor with their huge weight.
 then, 25 zombies crawled all over his body and stuck to him like leeches.
 they pressed the monster with their overwhelming weight, so he could not move.
then the troll skeletons were in charge of attacking the monster.
 they started wielding maces through the gap between the flesh golems and zombies.
clang! clang! clang! clang!with a loud noise, the monster’s massive armor began to crack.
‘but the damage is not severe enough.
’the monster hardly showed any signs of collapsing.
 rather, the zombies who could not withstand the heat fell and were revived repeatedly.
 it looked like the monster would break free at any moment.
‘they should not let him break free.
 this fight will take longer if he does.
 we have to kill him now.
’sungwoo did not forget that this fight was a competition.
‘i have to kill him fast.
 legendary grade items are up for grabs.
’so, sungwoo decided to attack more aggressively.
he canceled the summon of the grim reaper.
then, the zombies that were dying were no longer revived.
 even the giant flesh golem made up of about a hundred corpses fell into a pile of corpses.
 the corpses piled up around the monster.
 sungwoo used them for corpse explosions.
“explode!”bang!a massive explosion soared from just one point.
 not the heat, but the shock crushed the monster’s armor.
 the outer walls of the surrounding buildings were torn off, and the windows collapsed.
 troll skeletons bounced several meters away.
kugugugugugugugu―it was a huge explosion, comparable to the thunderstorm in the eastern sky, which had been visible to everyone in the vicinity.
even though the monster came from hell, he couldn’t withstand the explosion concentrated in one place.
sungwoo killed the monster with a single stroke.


-you have earned 4,500,000 gold by hunting the quest boss monster ‘hell moving armor-2’.
-additional rewards are given for attacking below the recommended level.
 (class b exp card)-you have leveled up.
 (lv.
 20)-all stats increase because you reached level 20.
 (+2)-you have acquired the title of ‘hell repeller’.
* agility increases (+2)* curse/magic immunity increases (+10%)sungwoo received a huge reward and even a title.
‘wait a minute.
’but he suddenly felt the events were rather strange.
“are we done?” asked minsok.
that was the problem.
 this quest was not supposed to end like this.
 he heard that the quest would be completed when he was done attacking both places.
so, the game was not supposed to end the moment sungwoo killed the hell-moving armor.
at that moment, he heard the fairy nabi’s voice.
– hello! how regrettable! it was exactly 118 seconds apart!it meant that the hell-moving armor in the ansung area was killed first.
 nabi was laughing over the fairy communication network.
‘i lost.
’he lost by a hair’s breadth, but kangsok showed why he was ranked no.
 1 on the korean server.
 although sungwoo didn’t know what kind of job he had and what kind of skills he used, kangsok was a strong player.
at that moment, sungwoo suddenly felt something wriggling in his arms, so he pulled it out.
“this one?”the myth-grade item, “the seed of the world tree,” which he had obtained after killing drake and completing the “group quest,” was shining clearly.
and a surprising message appeared.
-you have satisfied the conditions for planting the seeds of the world tree by meeting certain conditions (namely, acquiring the title of “hell repeller”).
* you can grow the world tree as its ‘guardian’, and the world tree will grow under your influence.
‘i can now plant the world tree?’even though sungwoo lost, it seemed that he got a tremendous opportunity.


 