\section{chapter 232}

                             




-the japanese server has selected the 3rd option (duel)!* both sides should select their own ‘great fighter’ for this duel.
* failure to respond will result in a penalty for the server involved.
* victory will give the server involved a buff.
as soon as he chose the duel option, akira put down his name as the ‘great fighter.
’[duel]-japanese server’s great fighter: yamato’s sword-korean server’s great fighter: (undecided)“oh, this is the game in which this japanese fighter killed the hwarang guild leader, right?”jisu asked.
“yes.
”“can i have a duel with him?”she willingly volunteered to fight the japanese master swordsman akira.
 this was more suitable for jisu than sungwoo.
 in some respects, this was the perfect stage for her.
“are you sure you can fight him?”sungwoo wasn’t comfortable because he already witnessed akira’s fantastic swordsmanship.
 of course, he trusted her, but at the same time, he was not sure she could win.
while chatting with him like that, she handed something to him.
 it was a necklace with black jewels.
 and the moment sungwoo accepted it, two lines of messages appeared before his eyes.
-shadow king’s heir: collect relics (4/4)-you have cleared the hidden quest of collecting the relic, ‘successor of the shadow king’>.
* you are given a reward (crown of the shadow king)finally, sungwoo obtained all four relics.
“i think this item suits you better than anybody else.
”
“this is a really big gift for me.
 thank you.
”she nodded and put on the ghost face mask and pulled down her sword from behind her back.
“now, please put my name down as the korean server’s great fighter.
”-remaining time until the selection of great fighter (00:02:58)sungwoo had no time to check for new items and the quest message.
he just chose her as the great fighter of the korean server.
[duel]-japanese server’s great fighter: yamato’s sword-korea server’s great fighter: kor-339* both sides’ great fighters should move to the ‘designated place (marked on the map)’ in10 minutes.
* once a duel begins, other battles are prohibited.
 (in case of violation, you will be judged ‘automatic death.
’)since the distance between the two warriors was not far, they were given only 10 minutes of preparation.
***with a large army lined up in the middle of a four-lane road in downtown busan, the japanese server’s great fighter and swords master akira okata was standing arrogantly.
“…who the hell are you?” akira shouted.
a woman in a red sweatshirt appeared in front of him.
 with a bizarre-shaped mask on her face, she was holding a sword in her right hand.
“you guys are driving me nuts.
 let me repeat.
 i want to fight the necromancer rather than a small fry like you.
 isn’t he confident enough to confront me? so has he sent you a woman like you who could die instead of himself?”at that moment the korean server’s great fighter jisu pulled out her sword and threw the sheath to the side.
 then, she strode toward him without any hesitation.
she said, “no, i don’t think he has to come out to confront you.
 i think i can beat you at my level.
”“what the hell did you say?”he looked at her as if she was ridiculous.

but she approached him and said, “you still can’t see how strong i am?”“…”when the distance between the two narrowed less than ten steps, there was no more ridicule on his expression.
 his left eyebrow wriggled.
“…”when she got even closer to him, he held his breath.
 he was now getting prepared to attack her at the decisive moment while holding his breath.
“i see what level you are,” she said, narrowing the distance so he was only two steps away.
“you still can’t size me up?”when she finally stood before him, one step away from him, he stepped back, pulling his left leg first.
 he was now ready to draw his sword at any time.
hiding her mouth, she made a cynical smile right under his chin.
“don’t be scared.
 let me finish it very quickly.
”“…”-the showdown begins! (10 seconds ago)two swordsmen stood facing each other.
deep tranquility spread over the perished city.
 there were many watching them here and there among the ruins, but none opened their mouths.
the official channel’s drone camera captured the stopped screen, and even the noisy chatters on the chat window became silent.
that meant that all the watchers were already overwhelmed by the gravitas of the two famous swordsmen from the korean and japanese servers.
“…”“…”jisu lifted her sword first.
 of course, she didn’t do it to attack him.
 some unknown energy began to emanate from her body.
-you have activated ‘hunting instinct’.
* when the battle lasts for 120 seconds,’hunting start’ opens.
she used the ‘hunting instinct’, which was the ‘awakening skill’ she obtained after clearing the ‘hidden quest’ in mt.
 taebaek.
at that moment, her eyes were torn vertically, changing her like a wild beast with draconian teeth, a beast’s eyes, and murderous intentions.
-you have chosen a ‘hunting prey.
’she looked at her opponent, akira.
 then a certain message appeared before his eyes, too.
– caution! you have fallen into ‘the prey’s blackout.
’* all your senses have dulled (-50%)“what the heck is this?”was it called the ultra-low frequency of the beast? akira felt like his whole body was tingling and stiffening just like a deer facing a tiger.
and for a swordsman like akira, his body’s sense was important like the instinct of a flying bird that could read which way the wind was blowing.
 the bird would be swept by the wind if it lost that instinct.
‘she is dangerous.
’he was alert.
 and that alone could help him resist such a skill attack.
-your cool mental power has revived some senses.
* recover all senses (+30%)then, at the moment he put forward his right foot, akira found his opponent already standing right before his eyes.
he hurriedly twisted his body and instinctively swung his sword to protect his neck.
clang! clang!two sparks flew up in an instant.
 he quickly stepped back and lifted his sword.
“footprint tracing? hahaha!”akira also had the ‘footprint tracing’ skill, which enabled its holder to read the opponent’s movement in advance and appear on his or her expected path.
 and it was also a skill that he saved for the decisive moment.
but since his opponent already showed it, he had no reason to save it anymore.


“okay, let’s have a good fight then!”akira rushed at her.
 he jumped off the ground and thrust his sword.
but she stepped back right away, hit back his sword.
 then she made a big leap backward and swung her sword through the air.
the energy of her sword rained down over his head.
 he quickly bowed his head, but some of his hair was cut.
 he quickly got close to her, but the next moment both of them disappeared at the same time.
 then, the spot where they were trying to land appeared reversely.
now both were only two steps away from each other.
akira hurriedly turned and swung his sword.
clang! clang! clang!in an instant, they clashed swords four times in a fierce atmosphere, but it was akira who was more nervous now.
as she already showed during her fighting huei of the chinese server, jisu had a very good ‘muscle strength’ for a general swordsman.
 at that moment, a smile was in her eyes.
it was a low kick.
 jisu, who felt she wasn’t outpowered by him, lifted her hind leg and kicked him.
akira staggered at that moment.
 at that moment, she cut his thigh.
“well, akira is staggering!”his thigh was bleeding.
 and some little cheers erupted from the korean server.
however, akira was still calm.
 he caught his breath and quickly charged at her.
she lowered her posture, ready to counterattack.
 he swung his sword, but she responded by striking it back.
hung!akira’s sword was wriggling through the blade of her sword like a phantom and penetrating her.
right after that, the real blade of his sword broke through the phantom and stabbed toward her neck.
puck!the blade of his sword was stuck in her left shoulder.
 the cut wasn’t deep because she twisted her body in an instant, but she was bleeding, too.
“alright.
 how about my attack? was it good enough?” he scornfully shouted.


 