\section{chapter 333}

                             




sungwoo looked at junghoon with a calm expression and said, “junghoon, are you okay? looks like one of your team members got hurt.
 hanho, go and treat him.
”“ah, well, it’s not a big deal.
 i can treat him with my sacred touch.
”hanho approached the wounded team member, raising his arms high.
but junghoon stopped hanho with a naughty laugh.
“no, you don’t have to treat him.
 i’m rather embarrassed, but you don’t have to worry.
 it looks like the dragon has played with us roughly because he is still young.
 i’ve got more important business with you.
 as for the world tree over there, can i approach it for a closer look?”his tone and expression were exactly the same as junghoon’s.
 but sungwoo could not feel any strong impression that he used to find in junghoon.
 and he could confirm it when he examined junghoon up close.
although sungwoo didn’t know about it exactly, such a strong impression had something to do with the so-called “aura of a war hero,” a passive effect given to the crusader commander.
‘as expected, this guy is dangerous.
’while walking one step closer to junghoon, sungwoo put his hand on the hand cannon in his waist.
  “but there is something you don’t know very well.
 this dragon can read into your mind more accurately than humans, although he is young.
”“i don’t understand what you are talking about…”instead of replying to him, sungwoo pulled the hand cannon from his waist and raised the muzzle.
 then, he aimed at a crusader standing behind junghoon.
junghoon’s expression was distorted.
bang!
the crusader man’s head was smashed to pieces.
 the fragments of his skull scattered into the sky when it was smashed.
“sungwoo, what the hell are you doing now?”all the members of the world tree camp including hanho and kyungsoo were astonished.
“uh? what the heck is that?”however, it didn’t take long for them too to realize something bizarre before their eyes.
it wasn’t the flesh and brain of the crusader member’s head shattered by the hand cannon.
 it was something like pieces of clay or pottery.
 in other words, these guys standing before sungwoo were not humans.
-you have earned 10,000 gold by killing the player’s ‘superior terracotta’.
the message that appeared before their eyes proved that sungwoo’s judgment was correct.
 they were terracotta, or ‘earthenware dolls’.
when their identity was revealed, they stepped back, making a grotesque sound.
 then, they dispersed in all directions, doing something like acrobatics like a circus member.
“what the heck is this?”“catch them!”while the village security guards were moving around in confusion, some red lights lit up on their chests.
‘red light? it’s a bomb.
 and their target is the world tree.
’in other words, their purpose was to commit terrorism against the world tree.
 sungwoo pulled down the “winter predator” from his back and quickly raised the muzzle.
“move back, everybody!” sungwoo shouted.
then, he lowered the lever, switched it to ‘expansion mode,’ and pulled the trigger at those running away in all directions.
he fired about 50 freezing bullets toward them.
 they spread like firecrackers and formed a fan shape.

they made bizarre movements to try to penetrate the world tree by all means, but none of them could escape the striking range of the ‘winter predator.
’they all turned into ice sculptures.
“oh, my god…”“if i hadn’t stepped back, i would have turned into ice!”sungwoo got rid of them all with one single attack.
sungwoo broke one of the frozen terracotta.
 what came out of his body was a player manufacturing item in a round shape, which was obviously a type of bomb.
sungwoo turned his head and looked at kyungsoo.
“kyungsoo, contact yeongdeungpo right now and tell them that i’m in suwon right now.
 tell them i haven’t sent anybody to suwon, so they should not allow any outsiders inside the village!”if someone aimed at the world tree camp using their alliance with the korean server, there was a high possibility that they would try to get the same thing from the liberation guild in youngdungpo.
“by the way, pass this message to all belonging to the korean server!”“okay.
 i’ll do it right away.
”furthermore, they may be targeting the entire korean server right now.
“damn it! i was going to take a good rest after this battle, but who the hell is doing this? chinese server again?”“i guess so…”sungwoo and his allies were complacent.
 since the big battle was over, they thought that nothing unusual would happen until the next battle because both sides were exhausted.
however, since the chinese emperor did not participate in the battle, he was not exhausted, but he did not seem to think of waiting leisurely until the next battle.
as a matter of fact, he intended to deal a fatal blow to the korean server in a very cunning way like this.
“i’m declaring an emergency as of now! tighten the security of all areas! everybody, follow my direction!”shortly afterward, the broadcast in the village rang, announcing that an emergency was declared throughout the korean server, including the world tree camp.
“let me go and kick general xing’s ass right now!”after a brief break, sungwoo entered the war again.
 the first thing he did was to collect the relevant information.
***general xing’s body was stored in “warehouse 0,” the most secure place.
sungwoo stood in front of the warehouse.
-you can check the ‘memory fragments’ of the deceased.
when he resurrected the general’s body into a skeleton, he could see the video, as expected.
‘good.
 show me something useful.
’as always, the “memory fragments” of the enemy’s body would give him some clues.
since the general was no.
 2 in the chinese server rankings, there could find some information that sungwoo could use to ambush them.
when the video screen brightened, the first thing that caught sungwoo’s eye was a wood fire.
 this was a room with a very large furnace.
 sitting in front of the round table on one side was a man with a mustache.
 general singh was drinking tea with that man face to face.
“…”strangely, they didn’t talk to each other.
 instead, there was an awkward silence between them.
and the man with a mustache was staring at the general while sipping tea.
 even though sungwoo watched the guy through the general’s fragments of memory, he just felt that man’s glance was pretty annoying.


‘something must be wrong.
”when sungwoo noticed something strange, the man with a mustache smiled dismally.
“how are you?”“…”“i’m saying hello to you!”  yes.
 this was not from memory.
 this mustache man was talking to sungwoo in reality, not the owner of the fragments of memory.
“psychometry?”and this was a technique that put sungwoo into trouble before.
 it was obvious that this guy had the ability of ‘psychometry’ like the white wolf.
“oh, you already know this.
 this is a very rare ability that only two have in mainland china.
 you guys have it on the korean server?”“…”“oh, you don’t speak much.
 alright.
 we knew that you had the ability to read the information hidden in the corpse through the fragments of memory and that you would come to us like this.
 even our almighty emperor humbly acknowledged the possibility that he might lose, so he prepared this in advance!”this meant that the emperor did some trick on the general in advance for fear that he could be defeated in the war.
since sungwoo and his allies were stronger than any other force that they had dealt with, it seemed that the emperor moved, based on his men’s excellent intelligence network and human resources.
finally, the guy with a mustache stood up from the table, with the teacup in his hand.


 