\section{chapter 308}

its appearance wasn't much different from that of a rifle, but it had a large cylinder attached to its body.
 of course, it had the "frozen seed" in the cylinder.





overall, it was a little longer and thinner than the "dwarf repeating crossbow".
'it has proper weight and balance.
 very good,' sungwoo thought.
[item information]-name: winter predator-class: unknown-category: player manufacturing-effect: condenses powerful cold air and fires a bullet.
 it fires 50 shots per minute in the 'single-shot mode', and 50 shots per minute in the 'multiple mode'.
 (cooldown 1 minute)-description: the default mode is 'single shot'.
 pulling the lever down will switch to 'multiple mode', and raising it again will switch back to 'single shot mode'.
*its striking range is very wide, so you are strongly recommended to use it after checking its left and right.
 (manufacturer's description) "then, would you like to use it?"hearst seemed to encourage sungwoo to try using it right now.
sungwoo nodded and responded, "good.
"not surprisingly, hearst already arranged a shooting range.
"try pulling it boldly!"standing at the shooting range covered with dirt, sungwoo aimed at the dummy with "winter predator" from about 100 meters away.
 then, he pulled the trigger slowly.
shoot!there was little recoil from it.
 the icicle-like bullet flew very quickly and hit the dummy doll.
 at the same time, the entire body of the dummy doll was frozen.
'i can't fully use all of the frozen seed's energy, but even this is significant progress!''
he then kept firing it.
 he shot two bullets in succession.
 shoot! shoot!when two bullets hit the frozen dummy, the ice mass swelled up and shattered like glass.
its performance was pretty satisfactory in terms of blocking power, imposing abnormal status, and destructive power.
"isn't it fantastic? now, next!"when hearst said that, the collapsed dummy was removed, and 5 new dummies came in along the rail.
"next, try using the 'multiple mode.
' you already read my description of it, right? just operate it with the lever.
"sungwoo pulled down the lever on the left of the gun's body with the thumb of his right hand.
 then, the barrel was split into three.
 "oh, don't forget to always check your left and right if you don't want to split your friend's face into two!"wooong-soon, cold energy began to fluctuate inside the gun.
 it was as if there was a small blizzard at the end of the muzzle of the gun.
 sungwoo tightened his heels and pulled the trigger.
as expected, dozens of bullets were fired at once with tremendous recoil, hitting the targets in the front.
 although sungwoo aimed at the target, it was useless.
 kugugugugugugu―a blizzard soared from the hit target, which made everything around it frozen in an instant.
 everything was frozen in a fan shape, starting with the muzzle.
"damn it.
 though i made it, it's really terrible," hearst complained.
 -'winter predator' has been 'supercooled'.
 (you can't use it for one minute.
)the three-way barrel merged into one again, and sungwoo withdrew the gun.

"to be honest, this is a terrific weapon!"sungwoo couldn't help but admire it.
 with its terrifying firepower and precision, this weapon could be called a personal flying weapon.
hearst took out a cigar with a smile then muttered with a grumpy and stubborn expression.
"what are you talking about? it looks like you are completely hooked on this weapon.
 yeah, any weapon made in hearst is fabulous…""uh?"at that moment, hearst paused and gazed into the air, spitting out the cigar.
 then he frowned, spitting out abusive language, "damn, shit!"sungwoo was also looking at the message, namely the red exclamation mark icon.
"this is what you call the mainstream, right?""i think so.
""man, i have no idea what they are trying to do this time…"but this time it wasn't the 'mainstream'.
[world season start guide]-world season 1: the age of encounter (war and peace)*dear all players in the world! we would like to present a bigger world to all of you who have lived hard in their respective servers so far! are you a frog in a well? or are you still a butterfly that hasn't spread its wings yet? are you friendly to outsiders? or do you want to be coercive and control others? the 'world', not the 'server', will confirm your destiny! meet the 'world', interact with the 'world', share with the 'world', confront and win the 'world' from now on![guidelines (important)]we have chosen several rules for smooth exchanges between the servers.
1) each server can select a 'server master'.
* all players on the server have 'voting rights' and only one player can be elected as the 'server master'.
2)'server master' has the following privileges.
* alliance: you can establish an 'alliance relationship' with other servers.
 as the alliances increase, you will receive various 'benefits.
'* declaration of war: you can 'declare war' against other servers.
 the one who proclaims it first can take the initiative of choosing the 'battlefield' and 'type of war.
'* surrender: if you surrender to the other server, you hand over all authority.
 then, your server becomes 'colonial' and a certain amount of your gold income is automatically paid to the other server's master.
hearst said, "you're going to get busy, right?"as history proved, the opening of a new world usually meant chaos rather than peace.
***shortly after the message rang, sungwoo's party and chairman love's close aides gathered together.
"i think our contact this time seems to have had a big impact on this mainstream.
 of course, many countries around the world will be gradually opening their borders….
"quest or mainstream changes according to the players' actions and the event involved.
 in that respect, it was evident that this "world season" mainstream was also designed to deepen the conflicts among the countries according to the latest trends of the world.
less than 30 minutes after the message rang, a red line of the message appeared.
 -the 'egypt server' has declared a war on the 'sudan server'.
* this war will be broadcast live through 'official channel-1'.
this message caught everyone's eyes.
"wow, is there a war going on already?""sungwoo, then our server may be…"

when jisu asked, sungwoo nodded.
 the korean server could not help but worry about the neighboring countries' possible invasion.
 and such a concern became a reality sooner than expected.
-the 'china-1 server' has declared a war on the 'korea server'.
* this war will be broadcast live through the 'official channel-2'.
the china server started a war with the korean server as if they had been waiting for it.
as explained in the guide, they moved quickly to take the initiative.
 "crazy! how come they…""they moved so fast!"while everyone reacted violently, sungwoo was calm.
'well, this is not something i haven't expected.
'the chinese server, the emperor, originally planned to invade the korean server, but the world season triggered their action.
'the problem is why they have decided to invade right now.
'as a matter of fact, sungwoo was faced with the coming arrival of the great typhoon called the dragon, so, he was destined to face the double confrontation with the china server and the dragon of the amazon.
 "what should we do?"now, everyone was watching sungwoo.
 in particular, chairman rose's face darkened.
if sungwoo could not move because of the war with the china server, chairman love would lose her biggest ally.
'this war is inevitable.
 if so, i would rather use it as an opportunity for a leap forward.
'as a matter of fact, sungwoo was agonizing over how to stop the dragon, but he thought the china server might offer a solution.


 