\section{chapter 209}

                             




however, sungwoo did not use corpse explosions.
what the demon camp soldiers experienced was the giant jannabi skeletons sungwoo procured in the dungeon.
they fell from the back of bone wyverns and landed on the remaining trees right above their heads.
rattle- rattle-the giant jannabi skeletons were a race with highly developed upper bodies, so they could not fight well on the ground.
 that’s why sungwoo didn’t use them from the beginning.
however, these skeletons could show their strength in the forest.
wooduuuuk!“ahhhhhhh!”the giant jannabi skeletons dragged the players of the demon camp, who had been hiding among the trees after avoiding bone wyverns, into the treetops as if they were picking up fish from a farm.
 then, they broke the players’ necks and threw them away.
although they could not fight properly on the ground, these skeletons fought like commandos in the forest.
“ahhhhhhhh!”“they are too fast! we can’t respond to their attack!”they could not get out of the forest because they would be instantly exposed to the attacks of other large skeletons and bone wyverns.
the necromancer pressed the demon camp hard by dispatching the undead in the correct positions as if he had been watching them all along.
now, the demon camp soldiers were in a complete dilemma.
“where are the reinforcements? why aren’t they coming?” bumyol shouted.
according to younghwan, the chairman of the reconstruction alliance, a large number of support troops were on standby nearby.
 however, they hadn’t even appeared in such an emergency.
“we were in touch with them right before this batter, so i have no idea why they haven’t appeared.
”“damn it! have they deserted us? that cunning dotard has deceived us? our plan fell flat!”bumyol finally had to admit all his plans had failed.
he realized that the slogan of the struggle guild, “we’ll prevail after losing!”, could not work for the necromancer.
‘if we lose to him, that’s it.
 we don’t have any chance in the future.
’so, bumyol was determined to resist to the end.
“uijin, take out the wooden box.
”
“that item is…”“we have no other option now.
 so, take it out!”uijin reluctantly opened his backpack and pulled out a wooden box with an amulet.
“how about considering retreating?”“no! even if we survive here, we have nothing left.
 nothing… we can’t even go back to mt.
 taebaek.
”“why don’t we go back and challenge the monster?”“no, we can’t stop him!”bumyol broke open the amulet and opened the box.
 there was ginseng with red energy inside the box.
he reached out his thick hand and picked up the ginseng.
 after hesitating several times, he eventually put it in his mouth.
-‘mountain spirit’ is spreading throughout your body.
* all stats increase significantly.
 (+15)* gain auto-healing effect.
 (5% per second)* temporarily gain the ‘ power of the mountain god’ and greatly increase your influence on natural objects.
 (+80%)* affinity and dominance for all spirits are greatly increased.
 (+50%)– warning! your fitness level is lower than what you can take.
 the ‘mountain spirit’ effect is temporarily applied to your body, but terrible pain and penalties are inflicted after it expires.
– warning! the “mountain spirit” that has entered your body is absorbing your stats.
 if you leave it as it is for a long time, it can lead to death.
the “ginseng with the mountain god spirit” was a reward bumyol received after completing the “hidden quest” in mt.
 taebaek.
according to the item description, anybody who wanted to eat it should have a physical strength level of 80, so bumyol had to save it until he reached that level, but he could not afford to save it now.
“ahhhhh!”with his skin turning red, he screamed and vomited blood.
 it was a side effect of his accepting a force that he could not endure, but soon he raised his upper body upright.
“hahaha.
 my strength is overflowing now!”he temporarily gained tremendous strength, along with confidence.
“i can win.
”bumyol’s primary job was ‘a strong man’ and the job he chose as a link card was ‘spirit magician (soil)’.

the two professions created synergy, so he could use spirit magic with tremendous destructive power.
 now, he could double his ability by receiving the mountain spirit.
“all i have to do is ignore the undead and kill the necromancer!”he lifted the ax with his arm with protruding veins.
 then, the ax blade began to glow green.
“the power of the earth!”he lifted the ax and struck the ground with all his might.
“smash the earth!”a crack began to occur in the place where his ax touched.
right after that, the ground cracked like a spider web and waved, then rose like a wave.
bang!everything around him was swept away in the shock.
not only the players of the demon camp but also the necromancer’s undead, couldn’t stand where they were because of the tremendous vibration.
 it looked as if everything on the whole battlefield stopped all at once.
“necromancer! come out!”only bumyol standing in the middle of the battlefield shouted.
 he noticed reporter ahn’s camera far away and opened his mouth again.
“necromancer! come out! let’s have a duel! i know you are nothing because you are hiding all the time behind the skeletons!”it seemed as if he was challenging the necromancer openly for a fight.
“if you hide behind the skeletons like that, anybody can fight well.
 but you’re only a coward who doesn’t know how to fight without the skeletons.
”he kept provoking the necromancer blatantly to achieve his purpose.
 he walked toward the camera with big strides.
“all players on the korean server watching this scene! don’t you agree with me? don’t you have any doubts about the real identity of the necromancer?”did his open provocation work? indeed, the necromancer appeared.
 he walked out of the trees, putting the grim reaper at an angle on his shoulder.
“man, there was another guy who challenged me recklessly once…”but bumyol scoffed at the necromancer’s words.
“i am different.
 i survived and will survive with my strength.
 how long are you going to deceive people? can you confidently say that you are strong?”“you are gonna make me say it?”reporter ahn’s camera was filming the two players facing each other.
 though they didn’t talk at the moment, the results of their fighting would show who was superior.
***the ground was turned over, messing up everything.
 the players of the demon camp and sungwoo’s undead army got tangled here and there as if they were in a disaster area.
“cough! cough!”“ahhhh.
”hanho also got up from the messy scene.
 when he came to his senses, there were only people around him who were not damaged at all.
“uh, what the heck?”hanho had no choice but to be embarrassed.
“oh, how are you?”“what are you?”“you bastard! you must belong to the necromancer team!”it was because there weren’t not many who were on hanho’s side.
five players of the demon camp raised their weapons after surrounding hanho.
“kill him!”“wait a minute!”stepping back, hanho waved at them.
“well, let me pray once before i die!”“what did you say?”“what? prayer?”while they were embarrassed by his words, hanho put his hands together, bowing down deeply.
 he seemed to be praying, but the players of the demon camp scoffed at him.
“hahaha! what the heck are you doing?”“this idiot is a friend of the necromancer’s?”at that moment, the patterns drawn on hanho’s back and robe began to shine.
-‘asura’s arm’ has been activated.
-‘asura’s arm’ activation time: 00:09:59

hanho slowly raised his head with a broad smile on his face.
“you idiots! don’t you know why i prayed?”four arms spread behind hanho’s back.
“i was going to pray for your peaceful rest!”the four arms pulled the daggers from his waist.
as a result, a total of six arms spread like a ferris wheel.
on the one hand, it looked gorgeous as if a scarab broke out of its pupa and spread its long legs.
“yeah, this is what i want to show them!”hanho moved his arms.
 considering the fact that he usually fought with only two arms, maintaining the sacred shield of the “slayer of faith”, his power had increased dramatically since then.
“by the way, it’s high time i used my new item, the ‘ghost dagger.
'”hanho smiled as broadly as possible because he had to do it this time.
as expected, the players surrounding him were shocked at his expression.
but hanho felt satisfied with what he just did.
“damn it, what the heck is that crazy bastard doing?”“he’s disgusting! look at the number of his arms!”“oh, disgusting!”when he heard them expressing displeasure at his eerie look, hanho felt bad.
“what did you say? my looks are disgusting? i don’t think you don’t have any aesthetic sense! then, let me punish you as the strongest holy asura thief!”“bullshit!”“just kill him!”soon, a battle between them broke out.
hanho fired the “ghost blade”, the effect of the newly acquired item “ghost dagger,” killing one of them.
 at the same time, he triggered the ‘slayer of faith’ to protect himself with a golden shield.
tung! tung!what happened next was always the same.
 since they could not break the shield, hanho was like an invincible enemy to them.
“kheeeeee!”

 