\section{chapter 367}

chapter 367: devil’s world tree and world eater (9)sungwoo was quite familiar with the devil’s cave, but this was the first boss monster sungwoo had ever seen.
 the monster seemed to be one rank above the demon gatekeeper.





“man, it looks like this place is teeming with alien monsters we have never seen,” said minseok.
as minseok said, his appearance was terrible.
 hundreds of mouths protruded from all over his body, which was fully naked as if all his skin had been peeled off.
 they opened, gnashed their teeth, stuck out their tongues, and drooled as if they were different from each other.
 but there was only one eyeball wiggling in his face.
rattle-this monster was holding a whip made from a number of vertebrae weaved together in both hands.
 the whip was so long that it rested on his back and down to the ground.
rattle- rattle-every time he approached, the vertebrae whip wobbled and made a strange noise.
‘this guy is definitely different.
’when the gate of the demon’s cave was opened in taiwan, even its gatekeeper demonstrated tremendous firepower because as soon as he appeared, he quickly melted the undead army that had been blocking the portal.
‘something similar could happen again.
’the moment a large number of the undead army collapsed with one big attack, the demons would penetrate through the hole again.
if that actually happened, the tide of the battle would turn in the world eater’s favor.
in other words, sungwoo could not allow that to happen because of that monster.
‘stop that monster!’when sungwoo ordered, large skeletons such as ogre skeletons, bone drake, and the bone nine-tail fox narrowed their distance from the monster with one eyeball.

rattle- rattle-it was dangerous for sungwoo to advance them first because it was highly likely that the monster could turn to ranged attacks.
the monster raised his arm.
 upon closer inspection, he wasn’t holding a whip.
 that bundle of vertebrae was attached to his arm.
he didn’t swing the whip but shot it.
 the whip charged at them like a snake’s head.
 as soon as he shot the whip, it split into four at the same time.
clang! clang! clang! clang!a total of eight vertebrae flew quickly and precisely like the tail of a scorpion.
 the moment it hit the target, dozens of thorns came out of its tips.
 no matter how huge the skeletons were, they could not withstand the sharp attacks from all directions.
 they were smashed to pieces in seconds.
 but that wasn’t all.
 hundreds of mouths sticking out from the monster’s body began to throw out something.
gross! gross! gross!they spat out some sticky liquid-like pus over the piles of bones.
 gray smoke billowed out of it as if it was acidic.
in addition, something very sticky covered the bones like a slime, which began the process of resurrecting with the ‘effect of death’ applied, but they only began to move up and down, entangled with each other.
there was a foul stench everywhere.
 so sungwoo stepped back.
“man, you’re playing with a disgusting toy.
”when sungwoo sneered, the world eater turned his head.
 his pale face was so damaged that its blue veins were clearly visible.
 it looked like he was going to collapse at any moment.
he shouted, “if you want to survive in a hell like this, you have no choice but to become the king of hell.
 do you think i like that kind of monster?”given that he mentioned something like contamination when the hole was drilled, it seemed that he sealed the monster until now to protect the people in the capsules.

“anyway, that monster is one of the worst living creatures that the ruined world has ever produced.
 he was not made for hunting by the system.
 actually, he was intended as a hunter…”sungwoo looked at the commander of the 2nd army of the demon’s cave.
 at a glance, he was not a monster for hunting as the world eater said.
 he was the type of creature that looked like an intruder from an alien world to cause the outsiders’ fear with his terrifying appearance.
 it was clear that he was made for such effects from the beginning.
sungwoo nodded and said, “yeah, he’s definitely a terrible guy.
 i’m just dumbfounded by his ugly and bizarre appearance.
”then, he looked at the world eater again.
sungwoo added, “but i have a more terrifying monster than that guy.
”the world eater sneered at him, but he looked exhausted.
he said, “are you kidding? i don’t think you have any other toys that can be useful to you.
”having said that, he looked around sungwoo’s undead army.
 obviously, the main forces of the undead army were already knocked down.
the world eater opened his mouth again.
“well, the tide of the battle is in my favor now.
 necromancer, you did great, but that’s your limit.
”but sungwoo shook his head and said, “nope, i just made a new friend.
”gugugugugugugugugugu-“by the way, you know him very well, too.
”at that moment, something began to vibrate from sungwoo’s back.
 the world eater’s eyebrows twitched at that unusual omen.
sungwoo continued, “please don’t have a tearful reunion.
”shortly afterward, the entire back wall and ceiling were torn off, making a big hole.
kwawagagaga!but the hole was different from the one in the front that world eater had drilled.
as if the separated liquids were roughly mixed when the middle wall of a huge tank was removed, the two huge spaces were forcibly merged, creating an unrealistic convection phenomenon.
in no time, a gust of wind blew and shook everything.
 a thicker shadow was placed heavily over the darkness that originally existed.
 then, gray smoke rose over the shadow.
finally, a gigantic shield of wings hung over everything.
woooooooooo-as the wind twisted through the air and resounded with a majestic roar, two green eye beams appeared between its wings.
it was none other than bone dragon.
the gigantic monster filled half of this space.
 the monster of the world eater’s looked like a butterfly passing under a huge eagle.
“those bones…”the world eater couldn’t hide his shock.
 sungwoo was holding the world eater’s sword in his hands.
[item information]

- name: balmung (ruler’s sword)- rank: myth- category: two-handed sword- effect: all stats increase (+6).
 it ignores some of the attack target’s defense effects.
 (30%), the ‘dragon slayer’ effect is applied, so additional damage is given when attacking dragons.
- description: it’s a key to awaken the black dragon and a symbol of a leash that can handle the dragon.
 it was given a ‘new name’, based on the previous owner’s activities.
balmung, the sword of sigurd or siegfried, the hero of germanic mythology, was a legendary sword, which was also called under different names such as notung and gram.
‘is this what happens when i obtain the ruler’s sword?’when 5 minutes of sealing passed, sungwoo obtained the sword, and as a result, he gained control over the creature connected to this sword, namely, the bone dragon.
- by proving your qualifications, a ‘great creature’ becomes your subordinate.
and that great creature just appeared here.
“alright, let me show you that terrifying creature.
”as soon as sungwoo said that, the dragon’s front paws popped out of the gray smoke.
 then, they fell towards the commander of the 2nd army of the demon’s cave.
bang!since the creature was several hundred meters, even his front claws alone were over 10 meters in diameter.
 the commander was crushed in an instant without even resisting.
 then, he made a bizarre noise, like a bug trampled under a huge boot.


 