\section{chapter 142}






 dozens of ships were floating around a huge container ship five kilometers south of udo island in the yellow sea.
when viewed from a distance, the fleet looked like an aircraft carrier fleet, but the ships surrounding the container ship were just old fishing boats.
a private broadcast on the china-2 server was being broadcast live on the deck of the container ship.
 even though they began to broadcast it five minutes ago, the viewers watching already reached 100,000.
 there were still lots of people who survived in the vast land of china.
“welcome to our broadcast! you’ve been waiting for this for a long time!”shortly after they were done preparing broadcasting, a man wearing sunglasses jumped into the studio and started to narrate like a professional emcee.
“hello everyone! we are gen.
 jigong’s fleet of the red revolutionary army!”he spread his hands with the vast ocean behind him.
“we are still in the middle of the ocean today, but don’t feel too safe! even under our feet, namely in the deep sea, there are horrible monsters overcrowded there.
 hahaha! so, where shall we go from here after getting out of this hellish sea?”he spread his palms over the sight of the sea.
 the cameraman zoomed in.
 at first glance, an island seemed to be visible over the horizon.
“we are going to korea, the brother country of our great china in the old days! hurray!”he wildly cheered as he pleased then took off his sunglasses and checked the chat room window.
 most of the content was comments like “runaway” or “coward.
”since they were pushed out because of the fierce infighting within the china-2 server, it was impossible for them to expect a normal response from the viewers watching the scene now.
however, the man in sunglasses casually chose the chat to his liking, and replied.
“did you ask us why we’re going there? are you asking because you really don’t know? you know that our troops are taking over almost all of taiwan, right? we are doing something that even mao zedong couldn’t do.
 and our gen.
 chongong finds his second cause in conquering korea.
 i think we’re going to broadcast from seoul next time.
 hahaha!”he laughed loudly then suddenly lowered his voice and forced an eerie atmosphere.
“but there is one terrible villain in korea called the necromancer.
 and after driving out our advance party recently, he warned that he would not let us occupy korean, no matter how large an army we have.
 but…”he clenched both fists and continued, “we won’t be defeated twice because our large fleet is moving there to smash them! look at our fleet!”
the moment he extended his arms, the camera turned 360 degrees and captured everything around him.
there were dozens of fishing boats floating around, including the container ship, and the pirates who were aboard the boats shouted all at once.
“wuhhhhhhhhhhhh!”“hurray!”“long live gen.
 chongong!”shortly afterwards, the man in sunglasses reappeared, somewhat excited.
he shouted, pointing at the camera.
“hey, are you watching us? leeway, you awful spiritist! don’t hold your head high because you have taken over server 2! we will take over the korean peninsula then move to manchuria! manchria! if you’re confident, smash server 1 and confront us in manchuria!”he took off his sunglasses with his eyes glaring sharply.
“from now on, we are going to broadcast the process of occupying the korean peninsula after killing the necromancer! our proud people! please keep watching our brilliant performance!”the broadcast was scheduled to end with his shouting like that, but this was just a trailer.
they were going to prove the mighty presence of the red revolutionary army that had been pushed out of the chinese server by broadcasting live the whole process of crushing the korean server, starting with the air raid on kanghwa island.
“uh, uh! what the heck is that?”but there was something like a broadcast accident at that moment.
“i saw its huge wings!”“wait a minute! isn’t it a monster bird raised by our gen.
 ingong?”something was flying in from the eastern sky.
 everyone turned to the sky.
 even the cameraman was zooming it in.
 black birds appeared from the clouds.

“yeah, they are monster birds!”“but our gen.
 ingong was killed in action on korean soil, right?”all of them had an ominous feeling.
“then, what’s that big stuff behind them?”“man, it’s huge! almost the size of a bus, isn’t it? no way!”three huge monsters appeared behind the nine monster birds.
“are they wyverns?”their ominous premonition became reality.
something began to fall from the air.
 they were the corpses of orcs and goblins.
“what the hell…”then, there arose flames along with roaring explosions.
 the boats shook and pirates screamed everywhere.
 the fishing boats were engulfed in explosions, and debris was scattered in all directions.
 then, the boats were lifted before being sucked into the deep sea.
the chat window was now dominated by the viewers’ question marksthe broadcast ended urgently.
it was the first time that the korean server was introduced in china.
no one in the red revolutionary army expected this kind of accident.
 little did they think they would be hit by a preemptive attack on the vast sea, and by huge explosions at that.
“everybody, escape! the boat is sinking!”“jump into the sea!!”bang! bang! kuggugugugugugugugu…little did they imagine “corpse bombs” would rain down on them from the sky.
 since they were not ready for this kind of attack, they could not make an emergency exit, let alone respond.
many of the pirates wandered around on the decks before being buried at the bottom of the sea with their boats.
only one of them responded properly.
 the commander of this fleet, jahon lee, also known as gen.
 jigong aimed a huge hand cannon toward the sky.
bang! bang!the hand cannon was fired at the monster birds in the sky.
 two of them flying relatively low were shattered and scattered over the sea.
then, a freezing magic was activated around it, and three monster birds flying higher in the sky were swept away by a blizzard.
 with their wings quickly frozen, they could not keep their balance.
it was a skill that he activated by mixing ‘ice wizard’, which he chose as his occupation card right after picking ‘canon shooter,’ so he could put spell magic in the canon’s bullet.
“wow! we can count on gen.
 jigong!”“yes, we can win!” all the pirates cheered.
however, their sigh of relief did not last long.
“uh? look over there! the killed monser birds are being resurrected!”“what the heck? i saw them smashed to pieces!”the fragments of the monster birds that had been struck by the hand cannon were engulfed in green light in the air, then restored to their original figures.
 then, they glide past the fleet.
“no.
 1 is ready!”“up to no.
 8, all ready! now is the time to defend against them! form a shield!”-a ‘linked large shield’ will be deployed in the area.


gen.
 jigong mobilized all the wizards to deploy a vast shield around the fleet, so he could prevent the subsequent damages in advance.
 they would have been annihilated without his timely help.
“they are going back!”“thank god! what a relief!”“what the hell was going on?”however, they already suffered huge damages.
 seven fishing boats sank, and there were 49 casualties.
however, they had no time to check out the damages.
 they were in a situation in which the monsters in the sea could rush after smelling blood, so they had to get out of the place as soon as possible.
“man, we have suffered too much during that short span.
”jahon climbed to the deck of the container ship and looked around the fleet.
in an instant, seven ships disappeared.
 originally, he had 21 boats, so one third of them were gone.
“so, what was it exactly?” jahon asked.
the man in sunglasses lowered his head and said feebly, “since they attacked us so suddenly, i couldn’t accurately identify them…”“but i think you can still figure them out, can’t you?”jahon didn’t have a violent temper, but he was not generous to anybody who was out of his favor.
“well, given that he could handle the killed monster bird of gen.
 ingong, he used corpses as bombs and mounted a hostile attack against us, i could recall only one guy associated with that attack.
”hearing that, jahon frowned and slowly opened his mouth.
“…necromancer.
”“yes.
 i’m sure he’s responsible for this attack.
”

 