\section{chapter 240}

                             




when she swung her sword only once, the entire room was crushed.
 the sharp and quick sword energy attacks ripped through the ceiling, floor, and wall, leaving behind cracks and dents everywhere.
in particular, those who were hit directly by the sword energy suffered terrible damage.
“ahhhhhhhhhhhh! my arms!”“help me!”“damn it! keep the ranks!”about a third of them were killed on the spot.
 it was as if the space itself was slaughtered.
this was a skill called ‘blade storm’, in which powerful energy got immersed in a knife before being scattered.
 so, the more it was used in a narrow space, the more its destructive power would be doubled like a shotgun.
“she’s coming! stop her!”“hey, keep the ranks! organize the ranks!”jisu jumped through their broken shields.
whenever she swung the sword, their shields were crushed and their metal armor was cut like a tofu.
sungwoo lifted the repeating crossbow while she threw herself into the middle of the enemy camp and broke their formation.
 since they were distracted by her in front, they could not defend sungwoo’s attack on their left and right.
tung! tung! tung! tung!sungwoo fired the arrows at their sides endlessly.
 when jisu was helped by these strong reinforcements, they could no longer withstand their combined attack.
after all, the 32 special forces formed to defeat the field boss monster ‘durahan’ were wiped out in just a few minutes.
“whew! let’s go again.
”after getting rid of the obstructors, sunwoo and jisu moved along the white chains that emanated from the tank.
“that’s it.
”as expected, a white chain was connected to a device at the end.
it was a rectangular electronic device.
 there were three chains plugged in like outlets.
and a white crystal was spinning in the small groove of the electronic device.

when sungwoo approached the device, a message about it appeared.
[item information]-name: holy power unit (h2)-class: unknown-category: player manufacturing-effect: those in the clergy profession can charge it by injecting mana.
 ( wizard-type can’t) when fully charged, it generates ‘purification energy’ for 90 minutes.
-description: needs to be fully charged every 1 hour.
 please manage it 24 hours well because of the shift work.
 you should never get distracted! never! never! (manufacturer’s skill)jisu said, “if i break this, i think we can unseal the tank.
”sungwoo nodded, and lifted the grim reaper.
 then he struck down the tank with it.
cling!the crystal was shattered to pieces at once.
then, as if the electric current was cut off, the white light flowing in along the chain began to fade.
 the supply of “purification energy” mentioned in the item description was cut off.
“let’s go again.
”sungwoo and jisu returned to the room where durahan was.
“the chain has gotten loose.
”like she said, the white chain wrapped around the tank let down loosely.
sungwoo boldly approached the water tank.
 even though he got closer than before, there was no warning message stating that “the divine power is denying your access”.
‘good.
’sungwoo lifted the grim reaper.
 then he forcefully struck down the tank containing the body of durahan.
 a hole was made in the tank, and an opaque liquid began to flow out.
soon the crack spread out to the front, then the tank was broken as if exploded.
at the same time, the giant knight who was immersed in the liquid moved slowly.

rattle―as he took his first step out of the tank, the liquid that accumulated in the armor flowed down.
the knight turned to sungwoo.
 even without a head, he was a giant much taller than sungwoo.
rattle- rattle-since he wore a gray armor covering his entire body, he looked much heavier.
even though he stood still, a purple smoke rose above his shoulders, suggesting that he had an extraordinary power.
he now stood tall before sungwoo.
 since he didn’t have a head, it was not clear whether he was looking at sungwoo now.
“sungwoo?”at that moment jisu placed her hand on the hilt while staying on alert against durahan.
her sharp senses told her that this neckless knight had something like murderous intentions.
it was an ominous omen that she felt when her opponent was about to attack.
actually he was raising her right hand and pulling down the bayonet he was holding around.
he dragged a huge steel bayonet on the marble floor, making a sharp friction.
the next moment, he lifted up the heavy bayonet, and grabbed it with both hands and struck him.
the second and third tanks collapsed one after another.
“…”a head and a black horse bounced out of the tanks.
 durahan picked up his head, which dropped to the floor, with his left hand, and then stuck the bayonet in his right hand to the floor.
then he knelt in front of sungwoo.
-field boss monster ‘durahan’ pledges loyalty to you.
* this monster has become your subordinate spirit.
-you have successfully attacked the exclusive quest ‘chival of the dead’.
* rewards are given.
 (special subordinate spirit)what jiu felt from durahan was his attack instinct.
 but his target was not sungwoo.
at that moment somebody made some noise from the hold of the ceiling through which sungwoo and jisu came down.
“i think it’s down there!”several flashlight lights flashed out of the hole and shook back and forth.
 however, because the room was so spacious, it seemed that they didn’t yet find sungwoo and jisu.
“there are no holes on the second basement floor!”“okay, it seems they are on the second basement level.
 striker team, get ready to attack them! go down and chase the intruders.
”it seemed that the security forces of the evolution society were chasing sungwoo and jisu.
 soon, those guards with crossbows jumped down to the second basement floor.
sungwoo looked at durahan and said, “now, show me your loyalty.
”durahan raised his huge body.
 holding his head in his left hand, he rode a huge black horse.
 then he pulled up the bayonet stuck on the floor.
when this big giant climbed on the monster black horse twice as large as a normal horse, he was literally overwhelming.
-‘synergy effect’ is given by team play.
[synergy list]-category: personal synergy-condition: a moving creature without a head-effect: increases the probability of critical strike avoidance (+100%), complete immunity to instant death, increase immunity to shock (+50%), complete immunity to faint, complete immunity to mental-type cursesthe synergy content was so extreme that sungwoo recalled a one-armed warrior.
 could he freely move even in all kinds of critical conditions because he had no head?the next moment the monster horse kicked off the ground.
 the giant knight bounced into the darkness.
 it was such a fierce charge that could be described as lightning speed.
whenever the black monster hit the ground, purple flames erupted from its hooves.
 that light reached the enemy in the blink of an eye.
“uh?”“something is coming toward us!”

the guards who came down from the hole noticed that something was approaching them, and very fast at that.
 they bent down and lit lanterns at the purple flames.
“what the heck! that is …”“dura…”but it’s too late.
 durahan passed by them, leaving behind a destructive and cruel scene as if a huge truck swept through the sidewalk.
six guards were struck by the horse and crushed in its hoofs.
 four were beheaded by durahan.
 with a single stroke duran killed half of the security guards.
“damn it! what the hell…”“durahan has been freed! he’s coming back! get prepared!”the death rider durahan who briefly disappeared into the darkness turned the reins toward them.
 purple flames circling in the dark began to sweep over the guards.
although they were hit by durahan, they had no time to prepare for his second attack because he was too fast.
besides, his attack was different this time.
-durahan uses his exclusive skill ‘death run’.
a purple horse-drawn knight squad appeared on his sides.
 it was a total of eight ghost knights in translucent form.
“uh? what the heck?”“everybody, avoid them!”the ghost knight squad maintained their ranks with durahan as the center, and lowered the lance.
 the entire building of the evolution society shook heavily as if a tram pushed in.
what came next was what was expected.
 all the security guards were smashed by the squad without any exception.
 they were shredded, bounced off, and trampled.
 it was literally annihilation.
“…”durahan slowly slowed down, leaving behind the enemies’ bodies.
 suddenly, his ghost knight squad on both sides disappeared.
 and there wasn’t even a scream left on the road he passed bypurrrrrrrrrrrr―the monster horse was still blowing out a thick breeze.
“great…” sungwoo muttered in satisfaction.
he was even thrilled with expectation that he might find some kind of gift waiting for him if he went down deeper.


 