\section{chapter 185}

                            riding on the back of bone wyvern hundreds of meters in the air, hanho was looking down at sungwoo fighting on the ground.
 two men were riding together behind him.
 they were camera operators he brought with him for broadcasting.





and the broadcast they were broadcasting live broke the record by drawing the highest number of viewers ever on the korean server.
[live] necromancer cracking down on the pirates’ lair in taiwan (183,224 people watching)“wow! he’s crazy!”hanho, who was left behind to protect the cameramen, was now serving as a commentator about sungwoo’s fighting.
“can you see him wiping out the pirates as if he was sweeping away pests?”when he looked down at sungwoo’s fighting, hanho could not find a better expression than “wipe them out” because of the overwhelming massacre.
kuguuuuuuuung―after sungwoo’s bone wyvern alpha male landed in the middle of the square, black smoke spread and engulfed the whole area.
“black smoke is always bad news for the enemies!”as soon as hanho said that, dozens of skeletons poured out of it, pushing the pirates fiercely.
 the scenes of the pirates collapsing like grass on a summer day were vividly captured by the camera lens from hundreds of meters in the air.
bang! bang! bang!the explosions of corpses among them, the pouring of concrete debris over their heads, and the large skeletons hitting them like rhinoceros showed it was not necessary to show the viewers that the necromancer dominated the battlefield.
hanho kept commentating in excitement, “the poisonous raindrops are falling over the heads of thousands of players! ah, pirates! as if they didn’t expect it at all, they are helplessly exposed to it! they can’t endure long like that!”as the last poisonous clouds were formed to pour out raindrops, the pirate camp began to collapse rapidly.
 sungwoo’s aoe curse was enough to completely break their will to fight.
“can you believe that only one man, the necromancer, is defeating them now?”hanho’s propaganda broadcast was successful.
 the necromancer, who was alienated by the war event between the absolute races, succeeded in pulling out the angel and demon camps’ broadcasts and drawing the attention of all the viewers at the moment.
[real time chat]- tank assistant manager kim: yes! this is war! now, if you watch the fight between the angel and demon camps, you will feel like it’s like a child’s play.

- joonwo park 33: wonderful! this is the power of korea!- glasses warrior: good! kill all the chinese pirates!- kor-11334: he is korean.
 he is fucking strong!- healing sister: good riddance! the pirates have been destroyed! i was really sad to see people killed by the pirates, and i’m so happy now.
moreover, the quest would not end with sungwoo’s conquest of taiwan.
 battles were happening simultaneously in other places.
hanho raised his head and looked around downtown taipei.
kuuuuuuung- kugugugugung-explosions and smoke occurred even in the place that was out of the necromancer’s striking range.
 so, hanho raised his finger to tell the cameramen to turn the camera lens there.
he couldn’t confirm who was fighting, but he could see clearly that the battle was taking place there too.
“now, finally the taiwanese players, who were dominated by the pirates, begin to fight back!”the uprising of the taiwanese players was also based on a prepared scenario.
“while the necromancer was striking the center of the enemy camp, the taiwanese players are waging a guerrilla war against the pirates!”[real time chat]- kang ss: wow, we can’t predict the necromancer’s strategy at all!- joonwoo park 33: yeah, this is korea’s smart power!- korean dog: wow! was the necromancer helping free taiwan?- kim seung-yong: the necromancer and his party are appearing anywhere where they are needed!“uh? yeah, you guys are right! we contacted the taiwanese players in advance to help them fight back! isn’t it great?”of course, it was a lie.
 shortly after arriving in the basement of the national library where the angel statue was located, sungwoo and his party accidentally encountered the taiwanese players who had been detained in prison.

they said they were a resistance force against the red revolutionary army, but they were caught preparing for a guerrilla operation in time for the pirates’ massive rally.
“we have taken all the taiwanese players out of jail and helped them take back their weapons.
 that’s how we’re helping them now!”after the core members of the taiwanese players engaged in the guerrilla operation had been detained by the pirates, their operation almost fell flat, but the players of the korean server dramatically appeared before them.
 it was a miracle for them.
sungwoo sent jisu to help the taiwanese players with their operation, and they succeeded in rising up against the pirates, at last.
while sungwoo was striking at the heart of the enemy camp, the taiwanese players were closing in on the pirates from the outskirts.
“it seems like we have completely upset their applecart! hahaha!”with the appearance of the necromancer, the fate of the taiwanese, chinese, and korean servers began to change drastically.
***sungwoo was facing gen.
 chongong.
“…”he could behead gen.
 chongong at any moment, but he thought the general might have a hidden weapon, given that he was still standing upright.
at that moment, shouts came from everywhere.
“uh! are they our reinforcements?”the camera operators on the chinese server turned camera angles with a ray of hope.
but the shouting was not familiar to them.
 the shouting didn’t come from the pirates.
as expected, a couple of top officers came running from behind gen chongong and said, “general! even taiwanese players have rebelled against us!”“we have to get off of this island right now! let me take care of the resistance fighters, so please protect yourself!”gen.
 chongong’s rally was also being broadcast live on the taiwanese server to subjugate the taiwanese players.
 however, with the scenes of sungwoo attacking them out of the blue, the taiwanese players began to rise up against gen.
 chongong and his players.
“no, we canstart over once we kill the necromancer!” shouted gen.
 chongong.
he still didn’t give up as if he had something to rely on.
then he took something out of his pocket and lifted it, which was familiar even to sungwoo.
“devil’s gate?”“oh, you also know this.
 then, you must know this is going to be the last moment of your life, right?”it was the dungeon scroll “devil’s gate” at the recommended level 35, which sungwoo also possessed.
 he heard that the pirates used it as a kind of strategic weapon because the monsters there were so strong.
realizing that he couldn’t beat the necromancer, gen.
 chongong intended to devastate this area.
 he tore the scroll without any hesitation.
at that moment, a warning message appeared before their eyes.
– caution!  has opened in the affected area.
* the area has been closed.
 (taipei city)‘blockade? that’s why they use it as a strategic weapon.
’as soon as the door of the devil’s gate was opened, sungwoo couldn’t escape from the area.
 the door of the devil’s gate was maintained for 24 hours immediately after the scroll was used.
 it meant that sungwoo had to survive by fighting against the monsters coming out of the dungeon for one day.
“hhhhhhhhhhhhh! you’re all done!”in the meantime, gen.
 chongong pulled out another item.
 it was a necklace made of the skull of a mouse.
 given that it was covered in a blue aura, it seemed to contain some magical power.
“now, only i am no longer the target of the monsters.
 necromancer! you will be killed after you are ripped apart by the crazy monsters!”sungwoo tried to approach him, but at that moment, a purple portal opened between the two.
whooooooooo-the portal sucked in the air around the area and gradually swelled.
 sungwoo, who was standing right in front of it, had to bend his legs and lower himself not to be dragged by the wind.


googoogooo-the space inside the portal rotated counterclockwise and tangled back and forth.
 just looking at the place made sungwoo feel as if he lost a sense of space.
and a black hand popped out of it suddenly.
“what the heck is that?”“something ominous?”the camera operators filming the scene felt anxious even though they were inside the wizard’s shield.
-the strange energies of the two worlds are colliding with each other.
* the existence of both worlds adversely affects each other.
something strange was happening.
then, the long forearms and thorny shoulders squeezed out, and a head with no eyes or nose, only nasty teeth, popped out.
grrrrrrrrrrrrrrrrrrrrr…the monster revealed his gums and dropped his sticky saliva.
“damn it! i can’t move my legs!”most of the players felt that their bodies got stiff just by looking at the monster.
 just like a predator facing a greater beast, they felt something like an ultra-low frequency was penetrating their bodies-you are overwhelmed by the ‘alien being.
’* all your stats decrease.
 (-20%)they were stricken by an unfamiliar fear, which made their muscles tight.
tramp, tramp!

 