\section{chapter 328}






 general xing turned his head to look for the epicenter of the unbelievable freezing magic.
“what the heck is that? no way!”and he realized it wasn’t just the freezing magic.
he saw bone wyvern floating in the air, and the necromancer standing behind it.
 he was holding a uniquely shaped rifle.
 and a peculiar wave was emanating from the object.
as a sorcerer himself, general singh was able to sense the power.
 it was definitely ‘frozen seed’.
“nonsense! this can’t happen!”general xing was aware of the existence of the ‘frozen seed’ for a long time.
 it was found after some sort of “hidden quest” in siberia took place.
the royal bodyguards of the emperor attempted to airlift the ‘frozen seed’ to neutralize the server- 2’s sorcerer, but they failed because they lost the ‘frozen seed’ in transit.
after that, however, the siberian hunters recovered the item, but the general knew that they were robbed of the frozen seed by the necromancer in the battle in seoul.
“but how is he controlling the frozen seeds?”the problem was that the necromancer was controlling that formidable item like a personal weapon as if it was a rifle.
general xing was also familiar with the destructive power of the frozen seed, which was widely known to be out of human control.
 it was to be used in a fixed position, so it was inevitable for its user to suffer damage, too.
moreover, when the frozen seed was planted, a warning message appeared.
 so, all they had to do was to avoid the place as soon as they planted it.
 so, the general didn’t worry about it too much.
“how can he use it freely like a rifle? what kind of skill is that?”general xing stepped back.
“i’ve lost.
 i can’t win this battle.
”he stretched out his hand to withdraw the high-grade water spirits that were drying up gradually.
then, he moved them under his own feet, climbed on top of them, and held his position as if riding the waves.
 then, he soared in the air with the waves and began to leave the battlefield at terrific speed.
‘alright.
 let me find a way to survive first then gather the remaining troops and the reinforcements from seoul…’
puck!however, he could not carry out his next plan.
“argh!”he lost his balance because something got stuck in his ankle.
 he rolled under the waves and fell to the asphalt at the edges of the battlefield.
“ahhhhhhhhh!”while groaning, he looked down at his ankles.
 he saw a dagger stuck in it.
 and he felt his body gradually becoming paralyzed.
“shit! he even used paralysis magic…”at that moment, someone was walking towards him.
as if doing some sort of ceremony, that man was approaching him with a weird dance, dressed in a bizarre style.
“nice shot! i’ve got him!”he wore a gigantic iron helmet that had nothing to do with any cosmetic effects, with six arms.
 and a sacred halo that didn’t fit him was all over his body.
“nihao! mama hoo! ni huga zenguo cha ma?”he even used strange language, which created a fear of a different nature that the general had never experienced.
“what?”the stranger approached the general and smiled at him, shrugging.
“well, actually, i don’t know what i am talking about.
 i picked up some chinese words while sleeping during the chinese lesson in high school.
 but i tried to look friendly to you, so please understand me.
”“you’re crazy!”scared, general xing tried to get up, but he couldn’t because his lower body was paralyzed.
“what the heck are you talking about? who the hell are you!”
the stranger smiled at him then spat out something terrible.
“don’t you recognize me at first glance?”general xing shook his head because he couldn’t tell.
 the stranger scratched his nose with his third arm on the left then laughed.
as if he understood, the stranger said, “i’m an assassin!”“assassin?’“i don’t think you can believe me, but my specialty is assassination.
”“go away, you crazy bastard! i am a general! let me die with honor!”“uh, don’t worry about that.
 not long ago, i let vladimir perish with great honor.
”“who the hell are you talking about? who is vladimir?”as if lost in reminiscing, the stranger said, “well, it’s a hamster!”after all, the general was killed without any honor.
***when the general’s water spirits were neutralized, the korean server launched an offensive attack.
the crusader team, who were devoted to the defense of the holes of the castle wall, charged at the enemy, and the world tree camp players, who had been inevitably holed up inside the invisible barriers to get out of the striking range of the enemy, also resumed fierce attacks.
“the tide of the battle has turned! let’s destroy them!”the chinese army already suffered enormous casualties and lost their commander, so they could no longer resist.
 after all, they began to disperse without any central figure leading them.
“they are running away!”“we’ve won!”shortly after the necromancer appeared, the allies seized the opportunity to win the battle in suwon.
“damn it! it’s not over yet! we have to finish the battle quickly and join our allies in seoul! chase the remnant chinese soldiers and kill them all!”although they virtually won, they were impatient because the allies were left alone, isolated in the seoul battlefield.
‘if they are still holding out in seoul, it is a miracle…’since sungwoo was not yet briefed about the status of the allies’ fight in seoul, he had no choice but to worry.
***shortly afterward, a “reunion portal” opened on one side of the battlefield in seoul, the final battlefield-the ‘victor (korea server)’ of the suwon and busan battlefields has joined the battlefield.
* the ‘battlefield victory buff (phase 2)’ has been issued to the korean server.
 (temporarily increase all stats +15)a number of troops, including sungwoo, came out of the portal.
“what the heck is that?”when they came out, they immediately found a huge number of corpses on the streets of seoul, about 400 people when counted.
 all of them were chinese soldiers with all their heads cut.
‘they were beheaded with one stroke…’ sungwoo murmured.
the bodies were all lying in the same direction, and the bloodstains were also drawn in the same trajectory.
‘who could do this?’as far as sungwoo knew, no one could do this.
“oh my …what happened?”although sungwoo heard what happened here through the broadcast, what he actually saw here could not be more bizarre.
“hey!”at that moment, someone shouted at sungwoo.
 when he turned my head, someone was sitting on the railing on the roof of a building.
“yeah, we’re here!”

he was the king of the great mountain.
 dressed in a blood-stained white robe, he was biting a pipe in his mouth.
“you are late! too late!”he was smiling at sungwoo in a relaxed mood although he seemed exhausted.
“you failed to come here at the decisive moment unlike me when i did in pyongyang.
 necromancer, you are not that cool this time.
”giggling at him, he lifted the pipe and pointed it somewhere.
“this time she is really cool!”sungwoo turned his head to the place the king was pointing at.
at the end of the 8-lane street where the enemies’ bodies were strewn was an unusually large heap of bodies, for the strong army under general xing, who believed he would join them, were slaughtered.
then, there were three shadows standing there.
-you are facing the deity.
‘deity?’sungwoo was confused by an unexpected message.
“no way…”the one with the deity status was wearing dark red armor.
 the black wings carved all over her body were impressive.
 and all those wing patterns were covered with sticky blood.
“uh? jisu? she is jisu, right?”like hanho said, she was jisu.
 and the two tigers who were thought to have been killed were standing next to her.
 but their bodies were somewhere opaque.
 a ray of light was connected to her body.
‘are they her subordinate spirits?’the two tigers looked like her subordinate spirits.
“it looks like you guys have a deep relationship with death,” said the king, puffing off smoke.
it was the birth of “valkyrie,” the messenger of death, referring to jisu, and “einherier,” the warrior who went through death.


 