\section{chapter 195}






 “oh, i got it!” hanho clapped his hands as if he remembered something.
 “because i kept watching the liberation guild broadcast.
”“why? what happened?”if jisu was like a senor, in reality, hanho was always gathering new information as a virtual sensor.
“there was fierce fighting in various places in the north of seoul, but now it seems that there has emerged a winner.
”the “fight for control of the metropolitan area (1)” event that took place a few days ago was still going on.
 several battles were fought, leaving hundreds of victims.
 now, the angel camp was emerging as the winner of the battle.
“a few hours ago, the deputy commander announced it in the broadcast briefly.
 the broadcast ended a moment ago, but given his words that the end of the fight was near, it seems the angel camp guys are now advancing to their opponent’s last stronghold in mt.
 pukhan, i think.
”when they occupied a total of three bases, they would receive tremendous buffs marked by an increase in attack and defense by 30% for seven days.
although the expected buffs did not have a big impact from an individual perspective, they would bring about an overwhelming gap in the strength of their forces in large-scale battles.
in other words, if they won this battle, they would have an opportunity to completely eradicate the opponent’s camp.
‘that’s why both camps have no choice but to make an all-out effort to defeat each other.
 i remember hearing at first that the reconstruction alliance was winning the battle at first…’the power of the reconstruction alliance was stronger than expected.
 with the so-called ‘skoll troops’ as their main force, they pushed the advance team of the angel camp to the brink of annihilation.
‘but that was their last push.
’according to hanho’s explanation, the tide was turned when the crusader team taking side with the angel camp appeared after that.
“man, i have to admit the crusader team’s defense was the best.
 i guess there were as many as 75 guys armed with full plate armor.
 they put on shields and all kinds of buffs before aggressively pushing forward.
 they didn’t budge at all even though arrows rained down on them endlessly.
”the reconstruction alliance fighters couldn’t defeat the crusader team wearing hard armor and shields despite their overwhelming firepower.
“the youngdungpo prosecutor stuck a flag on the ground to use an aoe buff, while the priests in the rear continued to heal each of the crusader team members fighting the reconstruction alliance guys.
 in my opinion, junghoon’s troops were well organized.
”
fighting against the reconstruction alliance’s tremendous firepower from the front, the crusaders rushed through the railroads of kwangwoon university.
 then, they swept awaythe skoll troops immediately, the pride of the reconstruction alliance.
 the scenes of the crusaders crushing the skoll troops were broadcast live to 110,000 people.
“to be honest, their fight scenes were cool.
”the viewers who were not impressed with other fighting scenes could not help but feel thrilled at the crusaders’ fantastic performance.
“yeah, the crusaders have always been strong.
”sungwoo thought the world of them.
 they weren’t on the same battlefield where the necromancer fought, so their fighting was given more prominence.
 nonetheless, the crusaders, composed of a total of 75 players, had tremendous power.
on this occasion, they once again verified their power to the entire korean server.
but sungwoo felt something different after the two camps’ fierce fight.
‘as i expected, the two camps are not my rival.
’in other words, the angel camp and the demon camp on the korean server were not powerful enough to be a big threat to sungwoo.
‘as long as there are no other variables, i can destroy them.
 let me dominate the korean server while growing the world tree.
’suddenly, sungwoo was setting up a new goal, a clear and bold goal that was markedly different from the previous one.
‘if i keep trying like this, i’ll be able to find out the cause of this phenomenon and the solution to it faster.
”as always, it took power to find out the truth.
***exactly 14 hours later, the official statement of the liberation guild appeared in the community.

[544] liberation guild’s official statement about the fight for the control of the metropolitan area.
-author: youngdungpo prosecutor │ hit: 45,542if you are a member of a specific camp, you may have already heard the news through the system, but i would like to inform you that the angel camp, where our liberation guild is the key player, has won the ‘fight for the control of the metropolitan area (1)’.
however, we seek peace and harmony, and we do not want to conquer by force.
we want to announce to the demonic camp that if you are willing to give up a meaningless fight, please make a declaration of surrender through an official announcement, then follow the liberation guild’s demands.
 we will give you a grace period of 24 hours, starting now.
[comments: 101]“wow, they ended the fight in only one day.
 aren’t they going to use the momentum to form the coalition of survivor groups?”in the end, junghoon’s angel camp won.
 he proved that he could accomplish the mission without relying on the necromancer’s power.
 as a result, he would take control of the metropolitan area.
 in other words, he was one step closer to the creation of the coalition that he had been longing for.
but there were always variables in the system.
“well, i don’t think this is the end of the battle for the control of the metropolitan area.
”“really? why?”“there was a number at the end of the quest’s name.
”like sungwoo said, ‘the fight for the control of the metropolitan area (1)” was the name of the quest.
 tin other words, the number suggested there could be a follow-up quest.
as soon as sungwoo said that, a variable appeared.
“uh, what the heck is this? man, are you a shaman, sungwoo?”a quest appeared.
“oh my god…if this is the case, it means we have to fight…”[war quest]-title: battle for the control of the metropolitan area (2)-key players: angel camp (korea server), devil camp (korea server), third camp (temporary)-reward: 5 legendary item boxes-condition: attack the large-scale dungeon “python’s cave” on mt.
 pukhan before other camps.
* you can enter it after a certain time.
 (35:59:59)* different entrances to the cave are provided for each camp.
– an opportunity to participate will also be given to the third camp currently under construction.
would you like to participate in the ‘war’? (y/n)and this time, the third camp affiliated with sungwoo was also included in the variable.
“war?”“are we finally participating in the war, too?”finally, the three-way war among the three camps began.
***chi-chi-chi!

a great nature scene unfolded on the noisy screen.
“hello everyone? today, something shocking happened on mt.
 pukhan, so i turned it on live broadcast like this.
”a player with the nickname “reporter ahn” turned on a personal broadcast.
 he became famous because he continued to tenaciously cover and broadcast live the fighting scenes of the ‘fight for the control of the metropolitan area (1).
’in particular, after he gained a considerable exp thanks to the 80,000 people who watched the battle at kwangwoon university, he volunteered as a war correspondent for the angel camp.
“can you see it?”his camera was now capturing the hillsides of mt.
 pukhan where the day was breaking.
but there was something very strange about mt.
 pukhan.
“i think that’s the second place where the fight for the control of the metropolitan area was supposed to take place….
”wooooooh-black trees shot up from the center of the mountain.
“man, they are huge!”they quickly spread all over mt.
 pukhan like fungi.
 they formed a tremendous force by pushing out the trees that had been taking roots on the korean peninsula for a long time.
furthermore, the black branches of the trees stretched up like tentacles, intertwined with each other, and began to form a huge roof covering the entire mountain.
while constantly wriggling, the huge roof made those watching squeamish as if the whole mountain was alive.
“it seems as if the entire mt.
 pukhan has been covered with a huge dome.
 isn’t it impossible for sunlight to permeate into it even during the day? it’s a devil’s forest!”that wasn’t the end.


 