\section{chapter 359}

chapter 359: devil’s world tree and world eater (1)at that moment, li wei came over and said, “this is steel golem.
 he’s one of the high-rank golems.
 as far as i know, a golem master of the mongolian server who could handle all kinds of golems handled steel golems.
”




according to her explanation, a guy with a 5-star job among those dealing with golems was killed here.
‘necromancer and then golem master? is this the place where the last battle of this server took place?’the devil’s world tree that engulfed the korean server was supposed to be the ending of this server, but there must have been some who survived the battle.
 did they resist here for the last time?’grrrrrr- grrrrrrr-“huh? what’s the matter?”at that moment mir, who was in sungwoo’s arms, suddenly began to whimper.
 he stuck out his snout and sniffed.
 he even wriggled his wings as if to fly towards a certain place.
“look at this! over here!”suddenly, somebody shouted from that place.
 he found something unusual.
“have you found something over there?”grrrrrrrr-did mir detect it first? sungwoo walked over there.
 then, mir jumped out of his arms.
“mir!”mir ran into the darkness, and sungwoo followed him.
 soon, a white rock appeared.
grrrrrrr-mir was groaning sadly before it.
‘it’s not a rock.
’when sungwoo got a little closer, there were cracks at regular intervals on the surface of what he thought was a rock.

‘bone joints…’it was a huge claw, which looked like it was grabbing something.
 there were five skeletons in the claws.
 it was the trace of the claws that killed five players at a time.
“sungwoo, i wonder if this is…”kyungsoo approached him, and sungwoo slowly lifted the lantern.
 right next to the claws, a huge leg bone stood tall like stone pillars.
 it was so high that sungwoo and kyungsoo had no choice but to raise their heads.
beyond it was an arched sternum reminiscent of ancient architecture.
 and when they lifted their heads a little more, the head and skull leaned against the inner wall were finally revealed.
a wind from somewhere moved through the bones, making a melancholy sound.
the owner of the overwhelming claws that spread on the cliff lay right here.
“this is a dragon…”they were definitely a dragon’s bones.
it was the bones of the dragon that stood in the way of sungwoo’s party.
“it appears to be at least 150 meters from head to tail.
”it was so huge that the expedition team’s small lantern could not light up the dragon entirely.
‘i expected it, but i’m really surprised to confirm it.
 is he a boss monster? if not…’there could be a number of cases about the identity of these bones, but it was most likely to be the family of the ‘dragon knight’.
most of all, mir’s reaction was very unusual.
 for some reason, he couldn’t stay still after finding the dragon’s bones.
grrrrrrrrrrr- grrrrrrrrrr-he was restless as if he met his kindred.
 it was clear that he felt that these bones were those of a dragon and one deeply related to him at that.

“sungwoo, this is an adult dragon’s body, right?”“yes, that’s right.
”“but it’s dead, right? somebody killed this guy.
”that was an important fact.
 this dragon was obviously hunted by somebody.
“we have to fight dragons someday, right?”as hanho said, sungwoo had to stop the dragon after he finished the war with the chinese emperor.
 in that respect, his visit to this place provided him with a good opportunity to get information about how to kill a dragon.
“kyungsoo, we have to search the entire place.
 be careful because we might run into a dangerous situation.
”“sure.
 i’ll also collect all the dropped items.
”the expedition team began to examine the whole cavity around the dragon.
 a few minutes later, they found the first clue.
“it’s something that we found near its wing bones.
”what kyungsoo brought was a very thick rope that could be used to tie a huge ship to the dock.
[item information]- name: magical hook- grade: unknown- category: player manufacturing- effect: unknown- description: it is made of a material with special power, but it lost its original function because the source of its power has disappeared.
‘this is an item made using the stems of the world tree.
’sungwoo recognized it right away.
 just as sungwoo made a huge hook by using the skill of bone weapon manufacturing based on the stem of the world tree recently, this item was also made in a similar way.
‘they tied this dragon’s wings with this.
’as expected, their first job of hunting the dragon was to tie his wings and drag him down to the ground.
 of course, the battle area was a rather narrow cavity, so it would be relatively easy to read their memories.
“but this is difficult to use in an open space like the sky.
”sungwoo thought that this dragon must have been driven into the worst situation where he had to fight here, and the traces of his claws on the cliff clearly showed he was desperately struggling not to fall off the cliff.
at that moment, the white wolf approached and put his hand on the dragon.
 he began to read the memories of the dragon.
 it was obvious that this kind of important creature had important information, so sungwoo waited until the white wolf finished reading the dragon’s memories.
“well…”soon, he opened his eyes and said, “this monster desperately tried to survive.
 he didn’t move at all even after he fell with his wings tied.
 even though he was attacked unilaterally, it seemed as if he was trying to protect something.
”“protect something?”if the dragon tried to protect something, he seemed to be on the defending side.
“look over here! there is something else!”someone discovered another hint.
 it was right below the dragon’s chest.
sungwoo went under its huge bone.
“there is a sword stuck in the bottom here.
”like the crew member said, a sword was stuck on the bottom right below the dragon’s breastbone.
at first glance, it looked like an antique item.
 in particular, the golden handle and guard stood out.
 sungwoo put his hand on the handle of the sword.


[item information]- name: ascalon- grade: mythical- category: sword- effect: increases all stats (+5), increases magic immunity (+10%).
 ‘dragon slayer’ effect is applied, so additional damage is applied when you attacking a dragon.
 (+300%)- description: it was originally a sword with a different name, but by inflicting a fatal blow on the heart of a dragon, it earned the name of the dragon’s natural enemy.
“dragon slayer?”sungwoo figured out the situation now.
 this sword was stabbed into the dragon’s heart and killed him.
it had been stuck in the dragon’s chest for such a long time, but it looked like it fell off his scales and got stuck in the ground.
‘i’ve obtained a dagger, which i never expected.
’tie his wings then deal a fatal blow to his heart?obviously, the opponent killed the dragon in a simple and sure way.
but the problem was how to stab the sword into the dragon’s heart because it was unreasonable to expect an intelligent creature like a dragon to allow his opponent to attack his heart.
“that’s the price he had to pay for holding out to protect something.
 but he was dealt a fatal blow, after all.
”like the white wolf said, it was almost impossible for the dragon to protect something unless he crouched in one place on its own.
“sungwoo, there is a huge door over here!”and what the dragon was trying to protect was revealed.
 a huge iron gate was found on the wall behind the dragon’s bones.
 it looked like a nuclear bomb shelter.
“did the dragon try to block it?”“well, what i saw in his memories was vague, but i think you’re right,” said the white wolf.


 