\section{chapter 165}

                             




members of the evolution society were on alert after getting out of the black smoke.
 they were already aware that the necromancer sprayed gas that caused abnormal conditions.
however, an unexpected scene unfolded.
“what the heck is that…”“human monster?”as the smoke slowly faded away, there stood a creature among the white demons, exuding strange energy.
 it was a black wolf wearing a dark green robe, bone armor, and a huge black scythe.
-your body function is weakened due to unknown energy.
* all stats decrease.
 (-2)“a drop in stats?”“what’s going on here?”they weren’t entitled to detect the “godly stature” of the creature.
 a phenomenon that they couldn’t understand was happening right before their eyes.
however, they instantly knew that their death was nearing.
“shoot!”as soon as someone shouted, they fired dozens of arrows and magic at the black wolf.
however, werebear skeletons bounced forward and blocked all the arrows with their bodies.
 the next moment the upper and lower bodies of those human monsters at the forefront were cut in half.
 the black wolf’s giant scythe cut through their torsos.
“damn it! when did he attack us?”the black wolf, which was in the lobby of the building until a few moments ago, was now right in front of them.
“block him!”the human monsters hurriedly took out melee weapons to respond, but the black wolf was overwhelmingly fast.
boowoong!wielding the huge scythe freely, the black wolf slaughtered the human monsters and zombie monsters who were blocking the entrance.
 it was as if a grinder passed by them.
‘i feel completely different from before.
’the black wolf, sungwoo, was feeling an overwhelming power throughout his body.
[player profile]
-name: sungwoo yu-level: 20-job: anubis’ incarnation (demi-god)-ability: strength (23+29), agility (19+26), stamina (16+27)-reserve gold: 36,455,405-trait: chaoshis growth this time was fundamentally different from before.
 he had empowered himself by strengthening subordinate spirits with his skills until now, but this time his physical ability has grown explosively.
all stats ranging from lich buffs to anubis buffs increased by 20 points each.
‘i’m no longer in a human body.
’sungwoo moved slowly.
 he felt much lighter, and at the same time, he felt much harder.
even with the same stats, a human monster’s body structure was much tougher and more resilient than the actual human body.
 so, it’s moved more efficiently.
-you exploit the soul.
 (cumulative: 11)and at the scene of the slaughter, a black light came up and was sucked into sungwoo’s body.
it was the “soul exploitation” skill.
-you have strengthened the undead with exploited souls (10).
 (1 stack)* remaining soul: 1furthermore, it wasn’t just sungwoo alone who became stronger.
 as his modifier of “the god of death” suggested, sungwoo could strengthen his subordinate spirits by exploiting the soul of his prey.
 even his senses transcended human abilities.
 sungwoo sensed an arrow flying from a long distance and leaped back.
 five arrows hit and stuck in the place where he was just standing.
“catch him!”somewhere, a loud voice rang out.
 behind the shield line in front of the school was a gray bull.
it was a werebull.
 it seemed that he was the commander of this operation.
kuuuuuuuuuuuuuuuuuuueeh!when the werebull ordered, many zombie monsters rushed at sungwoo.
 they stretched their cloth-made arms and swung their arms from a distance.
‘if i fight against them, i may be exposed to sniping.
’
still, they were in an advantageous situation.
 if sungwoo got entangled with their cloth arms, he could be killed by their intensive attack.
rattle! rattle!sungwoo moved the undead to collide with the cloth monsters.
 then, he turned around and ran to the snipers who were besieging the school building.
“shit! ahhhhhhh!”-you earned 21,000 gold by hunting ‘tier 2 wererat.
’.
-you have exploited a soul.
 (cumulative: 2)sungwoo jumped off the ground with tremendous strength and speed.
 they didn’t even dare think of getting away from him.
sungwoo ran along the outer wall of the school and slaughtered the snipers dispatched at regular intervals there.
 although they surrounded the entire building, he could easily destroy them one by one because they deserted their positions and ran away.
-you have exploited a soul.
 (cumulative: 8)after exploiting some souls, sungwoo turned back.
a melee was unfolding in the middle of the school.
 however, sungwoo’s undead were being pushed back by the enemies.
although the undead could be resurrected indefinitely, the offensive of the cloth monsters was tough.
 besides, since the enemy wizards poured out all kinds of aoe magic skills from behind the shield ranks, the undead were smashed immediately after being resurrected.
“okay, push them like this! prepare the ‘silver arrow of the saint’!”“prepare the silver arrow!”they took out a new weapon.
 it seemed that they were thoroughly prepared to hunt the necromancer.
 soon, the ranks of the shields split, and a weretiger walked out among them.
the monster notched a 3-meter longbow.
peeeeeeeeeeeng!the moment he fired the arrow, the skeletons standing in the line of fire collapsed at once.
-your family will return to eternal death by ‘sacred power’.
-your family will return to eternal death by ‘sacred power’.
-your family will return to eternal death by ‘sacred power’.
only one arrow penetrated the three werewolf skeletons.
 and the skeletons that were destroyed by the attack could not stand up again.
“great! we can destroy them!”“we can hunt them!”there was a cheer from their camp here and there.
 one thing they feared most about the necromancer was his ability to resurrect the undead no matter how often they killed them.
so, they thought that if they could incapacitate the necromancer’s skills like that, they could deal with him confidently.
however, sungwoo had a new weapon, too.
[skill information]-name: demonic bombing-grade: artisan-category: active-cost: 20 mana‘okay, let me corrupt the souls i accumulated through ‘soul exploitation’ and explode them with a powerful curse.
 (cooldown 30 seconds)* available souls: 8sungwoo used the new skill ‘evil spirit bombing’.
-‘evil spirit bombing’ is embedded in your weapon.
the black energy was condensed along the blade of the grim reaper, then sungwoo swung it toward the ranks of shields.
boowoong!black souls shot out like missiles and poured over their heads.
ku-o-o-o-o-gung!the souls expanded, causing a massive explosion.
 although there were no soaring flames or no major impact, powerful energy crushed the whole area with a black wave spreading.
as if tremendous gravity was working on it, their flesh was torn apart, and their shields were crushed.
“ahhhhhh!”“help me!”moreover, the attack didn’t cause just physical damages.
 when the black wave touched them, their souls were also damaged.
 there occurred even “immediate death” according to certain conditions.
-this is not an attack you can withstand.


those who witnessed the message helplessly collapsed without even screaming.
“what the heck is this…”although the wizards cast spells on the shields, they were useless.
 their tight formation that looked unbreakable collapsed at once.
-you have exploited a soul.
 (24 items)sungwoo instantly killed 24 monsters with 8 souls.
 be it a sorcerer and a tanker, they could never survive once they were caught in the explosion of death.
and that wasn’t the end of the explosion.
“explode!”bang! bang! bang! bang!the corpse explosions ensued, swallowing up those who survived the first attack.
 moreover, since sungwoo’s skill level had risen to the ‘skilled’ level, a small amount of the ‘breath of abyss’ was released along with the explosion.
-you have exploited a soul.
 (34 items)pusheeeeeeee―“cough! cough!”“wear a gas mask!”the corpse explosions, coupled with the evil spirit bombing, and the breath of the abyss, destroyed the shield ranks in an instant.
-‘evil spirit bombing’ is embedded in your weapon.
after the 30 second cooldown, sungwoo once again prepared the skill.
 then, he threw it toward the collapsed ranks.
 this time, he fired 10 souls.
ku-o-o-o-o-o-gung!-you have exploited a soul.
 (55 items)it was a perfect finish.
 there were no more ranks in the place devastated by the bombing.
sungwoo enhanced the undead using 30 souls.
-you have enhanced the undead with exploited souls.
 (4 stacks)the fight wasn’t over yet.
 it was true that sungwoo inflicted huge damage, but the enemies’ power was still threatening.
“move!”

 