\section{chapter 258}

                            “they were just stupid.
”




so, while they, divided into two groups, were locked in a fierce fight in the city, the monsters gained strength in the remote areas where they weren’t noticed.
the neglected ‘raid boss monster’ became a ‘warlord monster’, and when he was left alone, he grew to be the ‘king of monsters.
’“to put it simply, there are lots of guys like me in the north, right?” the king of the great mountain said, pointing to his chest.
sungho said with a nod, “you bet.
”“that’s the worst situation,” said sungwoo.
the king tilted his head at sungwoo’s words.
“uh? are you serious? i hope i heard you wrong…” said the king.
“yes, i am.
 please continue, sungho.
”” anyway, neither the self-governing forces nor the military could stop the monster army.
”because the two forces were eager to destroy each other, they could not beef up their strength enough to beat the monsters.
at the end, when the two forces disintegrated, a “bad ending” message appeared on the entire north korean server.
after that, the mainstream or quests were not issued, and the ‘player guidebook’ app did not work.
 all functions such as community and broadcasting stations were shut down.
“so our land has turned into a hell dominated by monsters.
 and one of those rulers is that lich.
 currently, he is the ruler of kaesung, the southern part of north korea.
”“just one?”“yes, there is only one lich.
 but there are several thousand under his authority who don’t die.
”“several thousand…”
even sungwoo, who obtained the deity status, couldn’t control several thousands of undead.
 it was not likely that the north korean lich had a higher grade than sungwoo.
 probably he might enjoy the privilege of being called the king of monsters.
“you said there were players worshipping lich, right?”“yes.
 those who have nowhere to go have started serving monsters.
 in particular, lich actively accepted wizard-type players and trained them as ‘death priests’.
”just as jisu made the first awakening with the help of the king of the great mountain, the players of the ruined north korean server also served the king of monsters while trying to “change their occupations.
”maybe his ability to control several thousands of lich had something to do with his ability to make the players his subordinate spirits.
“where is it?” sungwoo asked directly.
then, sungho’s face hardened a bit.
 since he escaped from that place at the risk of his life, he had very bad memories of that place.
“it’s a place called temple, but the people there are so cruel and heinous.
 there are dozens of death priests gathered there.
 it’s a terrible place.
 you can confront them, but i hope you won’t go there.
”sungwoo smiled at him faintly.
“it sounds like a pretty good place to me.
”sungho made an awkward expression as if he could not understand.
the place called “temple” was among the mountains in the southern part of kaesong city.
two pyramids made of gray stones stood facing each other on top of a desolate ridge that had been stripped of grass and trees due to reckless development.
 hundreds of crows flew around the ugly edifice that looked like the architecture of an ancient civilization.
in the center of the basement of the pyramid was a huge altar.
with twelve torches swaying to light up the darkness, 20 death priests were seated around the altar.
they were sitting with their legs crossed and controlling a horde of zombies across the distance.
 their mission was to increase the number of zombies by attacking groups of survivors and monsters around them.

then, a problem arose.
“chief priest, we have lost contact with the zombie group in the southeast.
 i think they were attacked by somebody.
”at that report, the chief priest shook his hand, as if it was not a big deal.
“send a crow to check.
”it was often the case that a group of weak zombies was annihilated by monsters on the field.
 his briefing continued.
“well, our communication line with another group of zombies has been cut off! there seems to be something happening in that area.
”“it’s annoying.
 forward soldier crow, do you see anything unusual happening there?”“not yet, sir.
 let me have him fly further!”a little later the source of the turmoil was revealed.
“someone showed up about 8 kilometers away from us.
 they seem to be coming to the temple.
 perhaps they are the killer who got rid of our zombie hordes.
”“how many are they?”“just one.
”only one? the chief priest scoffed at that.
“just one? it looks like he got lost.
 send a squad of zombies and make him a zombie, too.
”one unit was composed of 300 zombies.
 if they closed in on him from all directions, he would not be able to confront them no matter how high of a level he was.
after issuing such an order, the chief priest stopped thinking about it.
 instead, he infused power into a crow in the northern mountains and supervised his subordinates making corpse golems.
however, he was bothered constantly.
“chief priest, you should take a look at this.
”“what is it?” he asked annoyingly.
the priest hesitantly put down a black crystal ball in front of him.
“the zombies dispatched to kill the intruder are weird.
 they won’t follow our directions!”the chief priest laid his hand on the crystal ball.
 then, he was connected with the eyes of a crow.
soon, he could see 300 zombies gathered somewhere.
“who the hell is that guy?”a player was walking leisurely among the zombie troops.
 when he stepped forward, the zombies got out of his way.
like parting in the red sea, the terrible bodies moved to either side of him easily.
“why aren’t they attacking him?”“we issued an order to them, but they won’t follow it!”“chief priest! the intruder has broken through the 8-km boundary and is now approaching the 4-km boundary!”the situation was unfolding unpredictably.
“what kind of player is he?”“i don’t know! when he gets close to us, you won’t need to possess the crow any longer.
 i think we can get more information about him when he gets closer to us!”

“that’s enough.
 it looks like he has a strange item, but when he comes within the 4-km boundary, explode the corpses and rip him apart.
 how dare he try to come here?”the temple’s security was very tight.
 its surrounding area was defended by numerous zombies.
 even if the intruder broke through them, he had to face an ‘explosion zone’ where the corpses had been buried underground.
“if that guy recklessly sets foot in our territory, he is going to be killed by the hellish flames.
 no matter how strong of a tank he is, he can’t walk into our territory without being killed.
”kung- kuwoong-at that moment, there was an explosion outside the 4-km boundary, which caused stone fragments to fall from the ceiling.
 a corpse explosion occurred at the chief priest’s order.
“did you kill him?”“oh no! the explosion occurred before he stepped on it.
”what the heck was this?“what? who executed my order too soon?”“…”since corpses were not ordinary gunpowder, corpses would never explode unless someone cast the ‘corpse explosion’ spell.
 the chief priest concluded that it was the mistake of his subordinates.
“damn idiots! you should have waited a little longer! who the hell did it?”“…”no one admitted to the mistake.
 the chief priest wanted to find out the culprit and punish him severely, but his priority at the moment was to kill the intruder approaching him first.
the chief priest stood up with his hands folded behind his back.
then, he looked nervously at the crystal ball.
“the intruder will come into the temple.
 he’s not lost.
 he was planning to come here from the beginning.
 if he enters the temple, spray poison gas and kill him.
”

 