\section{chapter 212}

                             




the necromancer entered the northern building of uijongbu city, the home of the demon camp without any bloody fighting.
as mentioned in the demon camp’s broadcast, the chairman and other executives of the reconstruction alliance had already fled the city.
 they quickly escaped after realizing they had no more power to maintain their forces after they were completely defeated in the battle in mt.
 pukhan.
thud-when sungwoo’s bone wyvern landed on the edge of the square of the government building called “kyonggi peace plaza,” a man in a suit walked out.
 he was the man who appeared on the air.
“welcome! i would like to welcome you to this place.
”he couldn’t hide his nervousness when he encountered the necromancer because he was stricken with fear that if he rubbed the necromancer wrong, his forces could be annihilated.
“i am minchol lee, and i used to run a shelter in the uijongbu area.
 well, please understand that after the reconstruction alliance came here from the northern area, we were dominated by them against our will, and we were forced to join their operation.
”minchol, who appeared to be the leader of those who were left behind, made clear that his forces were no longer aligned with the reconstruction alliance.
 minchol tried to avoid his responsibility by insisting that they were forcibly controlled by the demon camp.
however, no matter his excuses, sungwoo didn’t care.
 he fixed his eyes only on the “devil statue” in the middle of the square.
it was a sacrifice they dedicated to the necromancer.
‘this is the third and last statue.
’without replying to minchol, sungwoo walked to the center of the square.
“he is the necromancer…”“gosh, will he kill us?”the players of the demon camp stood some distance away from the statue.
 they looked like the people of a country that lost a war.
sungwoo, who was like the leader of the victor country, stood in front of the “devil’s statue”, an important symbol of the demon camp.
 they watched him.
it was a black stone statue with horns with its wings half spread to cover its chest.
‘that looks ugly.
’
the statue held a long spear upside down with its right hand.
 it was in dynamic motion as if it would hit sungwoo.
it was holding a glass of fire in its left hand, from which something was flowing.
 as a result, a dark flame was rising from beneath its feet.
‘the angel statue was holding a sword and a crown, right? what does it mean?’the stone statues seemed to imply something that each camp signified.
“whatever it is, they won’t make it happen.
”sungwoo then looked around.
“…”the players of the demon camp were looking at sungwoo with vigilant eyes.
 of course, most of them were full of awe and fear.
come to think of it, it could not be ruled out that they lured sungwoo into this place to snipe him.
 besides, this was an open place, so it was more dangerous to sungwoo.
to make matters worse, it was not easy for sungwoo to detect their movement because jisu was not around him at the moment.
 that’s why he had to defend himself as best as he could.
oooooooh-long before sungwoo landed in the square, he was monitoring every nook and corner of the area carefully by flying “spector” in the air.
 two ghosts wandered around the office building, creating an eerie atmosphere.
in addition, sungwoo dispatched zombie birds in various places on the rooftop.
 he was even ready to escape using ‘shadow teleport’ by creating a shadow in an emergency.
‘okay, no problem.
’after checking everything, sungwoo stretched out his right hand into the air, where the black grim reaper bloomed.
the devil statue split diagonally and collapsed in an instant.
-the demon camp has increased the bounty on your head.
*demon camp’s bounty: 50,000,000 gold
“ah, my level…”“mine went down, too.
”at the same time, sighs came out here and there.
 since they failed to protect the statue, they were given a strong penalty.
 they paid dearly for the price of their wrong choice of the demon camp.
however, the destruction of the statue gave sungwoo a tremendous benefit.
-third option: destroy the statutes of the absolute race (3/3)-you have successfully attacked the hidden quest .
* you are given a reward.
 (opportunity to establish the third camp)finally, sungwoo had cleared the ‘hidden quest’ for the formation of his camp.
[camp quest]-title: great moment, the founding of a camp-type: decision-goal: selection of the main base of the camp-reward: initial operating fund (30,000,000 gold)*you have passed the test to become the founder of a new camp.
 and finally, you are qualified to create a regular camp.
 the first task of creating your camp is to designate your ‘main base.
’ for the endless development of the camp, you should select a safe and excellent area and lay the foundation for the long-term project of your camp.
* you must designate your main base within 72 hours.
* once you designate it as your main base, you can’t arbitrarily change it.
now, sungwoo was given the final choice to create a camp.
 he had to decide on a place to use as the main base for the camp.
‘well, i’ve already decided on that.
’he was thinking of the place where the world tree was growing.
meanwhile, he found an item that emitted black light among the fragments of the fallen statue.
[item information]-name: devil’s horn shard-grade: legend-category: disposal item-effect: when using it, you can move to the ‘devil statue’ within a certain range.
 (1 time) * angel camp and the third camp cannot use it.
-description: if the statue is destroyed, it is used as a final emergency escape.
it was an item with the same function as the angel’s wing sungwoo had used previously.
 however, the ‘third camp’ was also included in the list of use restrictions.
when sungwoo attacked the pirates in taiwan, he used the angel’s wing shard to ambush them.
at the time, he used the loopholes of the system that those players who did not belong to any camp had no restrictions, but it seemed that they were judged as members of an official camp.
when sungwoo turned, minchol approached him and said, “necromancer, can you do me a favor?”“yes, go ahead.
”hesitating a bit, minchol pointed to the players who came out to the square.
“we were penalized for donating the devil statue to you.
 we were given the curses of leveling down and expelled from the demon camp.
”sungwoo could easily guess what he wanted to say next.
minchol continued, “well, could you accept us as the leader of the third camp? we were forcibly subjugated to the demon camp, so…”whoo- boom!

bone wyvern alpha male landed behind sungwoo.
 stunned, minchol stepped back.
“i’m sorry, but this is not the right time to accept you.
 and…”having said that, sungwoo got on the bone wyvern.
“we don’t force players to join us nor do we accept them easily.
 so, prove you are worthy enough to join us.
”proving what? minchol felt like he was freaking out, but since he was here as the representative of many players in his group, minchol had to find a way to prove their worth.
“well, how can we prove our worth?”“make me come here and ask for your help.
”minchol’s jaws dropped at that.
 how could he make the necromancer come to him for help? how could he do that?after saying terrible things like that, sungwoo got on the bone wyvern quickly and soared into the air.
 it was time for him to return to suwon.
without shutting his mouth, minchol was looking to the place where the necromancer disappeared.
in the meantime, sungwoo and hanho did not proceed with the formation of the third camp immediately when they arrived in suwon.
based on his experience, sungwoo knew he was faced with an unexpected crisis right after clearing a quest that would bring about a big change.
 that’s what happened when he planted the world tree recently.
 who would have expected that a bunch of wyverns would storm his area in droves?that’s why he had the villagers check their security and prepare for the unexpected situation.
 in other words, they were fully prepared for war.
meanwhile, he told hanho to watch the community bulletin closely because any movement by a hostile force could be exposed to the community.
 above all, he needed to find out jisu’s whereabouts, who went missing several days ago.
however, hanho shook his head shortly after checking the community bulletin carefully.
“i can’t find any posts uploaded by jisu.
 i’m worried something bad happened to her.
 sungwoo, is she okay?”“yeah, she will be fine.
”as far as he knew, she was not the type of woman who could be easily defeated by the enemy.
 after gaining overwhelming sensory abilities, she was accumulating extraordinary foresight.
 besides, junghoon promised to find her whereabouts, so sungwoo believed they could find her sooner or later.


 