\section{chapter 251}

                            “well, we are so short-handed right now.
 moreover, half of our staff went down to daejon…”




the problem was the shortage of men.
“don’t worry.
”since sungwoo was also aware of the problem, he took some measures in advance.
“i have contacted a reliable reinforcement force.
 please be ready to send all the helicopters to near lake sihwa one hour later.
”“paron? lake sihwa?”“players from kanghwa island will join us here.
 they will take boats to lake sihwa, and after that, we will meet them.
”on kanghwa island, there was a group of 256 players led by muyon.
since they were helped by sungwoo, they have consistently supported the necromancer.
 they finally decided to join the players in the suwon village.
“wow! that’s great.
 if they arrive, they will be of great help.
”when he heard such good news from sungwoo, kyongsu’s expression turned bright.
 he had been suffering the shortages of men, but he could feel relaxed now.
he continued, “our villagers will welcome the kanghwa island players without any reservation because we often inquired after each other in the community.
”although the players from the two areas had never met before, they already formed a sense of comradeship because they rallied around the necromancer as the members of the third camp.
therefore, the players of kanghwa island were reliable enough to make them not worry about the problems they encountered when they were accepting new members.
“good.
 please provide the living space for the players of kanghwa island.
”“we have already set up lodgings nearby.
 we can accept at least one thousand more.
”as expected, kyongsu already planned things like that to develop the suwon village further.
“okay, kyongsu.
 i trust you.
”“oh, by the way, the world tree has borne fruit.
 are you going to check it right now?”“yeah.
 please tell me the location.
”sungwoo followed kyongsu to approach the world tree.

the closer he approached, the higher he had to raise his head.
 in the past, it was surprisingly high, but this time he was almost overwhelmed by its growth.
“well, it’s pretty difficult to approach that monster tree.
”the square, which had been flat, was rugged with roots rising from the ground, so they could not head to the world tree right away.
some roots protruded up from the ground, almost blocking the way like a fence.
so, the two had to go around the place to reach the trunk of the world tree.
“whew! we’re finally here.
 if you look up there, there are three fruits.
”as soon as kyongsu said that, a message appeared before sungwoo’s eyes.
-‘owner of the world tree’ can select one of the following tribe traits.
 depending on the propensity of the owner, the ‘detailed traits’ of each tribe may change.
* you can select by checking the fruit.
‘fruit?’when they approached the world tree, a new message appeared, but it seemed that the new fruits were related to the selection of the tribe.
‘then, the fact that the fourth option has not been found yet means that no fruit has been born yet.
’sungwoo thought this could be a surprisingly easy puzzle.
“kyungsoo, are there only three fruits?”“probably.
 after checking that the tree bore fruits, i also checked all the branches for any other fruit, but i found none.
”“well, let’s double-check just in case.
 we don’t need many people.
 can you bring some here?”“okay.
”in the meantime, seongwoo flew near the fruits on a zombie bird.
 all three fruits were hung near the thick branches right above the stem, so he could easily confirm them.
sungwoo reached out for the platinum-colored fruit among them.
 since he had no intention of picking it, he just put his fingers lightly on the surface.
[item information]-name: second fruit of the world tree (fruit of the fairy)
-grade: myth-category: consumption-effect: unknown-description: a fruit containing the mysterious power of the world tree.
 when you eat it, you will undergo a special change.
 (however, you will not be able to eat other fruits.
)there was no specific information about the fruit, but by looking at its name, sungwoo realized this fruit was the key to choosing a tribe.
the remaining green and brown fruits were also the fruits of tree spirits and giants, respectively.
‘the problem is the fourth fruit that has not yet been discovered.
’ten players were mobilized to find the fourth fruit.
 they wore safety gear and climbed up the world tree.
“be careful, everyone! if you fall, you will die immediately!”“if i die, bury me under the world tree!”the leaves were so lush they couldn’t find the fruit with the naked eye.
 going directly through the branches was the best way to search for the fourth fruit, but they could not find the fourth fruit anywhere.
“we can’t find it! we have even crawled through the branches and checked them all, but there is nothing like a fruit anywhere.
 hey! did you find anything there?”“nope! could it be that the birds picked it?”“uh? the fruit of the world tree? is it possible our security is so loose?”“no way!”in the end, the ten players who came out to search for the fruit had to go back empty-handed.
***sungwoo was lost in thought, sitting alone on one of the roots where he could look up the world tree.
‘i have to find it by all means.
’he had no intention of choosing the option within the given conditions without finding the fourth fruit.
 since he always made an unusual choice, he could achieve faster growth than others.
the third camp, namely, the world tree camp, was also born through such a choice.
 again, he needed to select something outside the given options.
‘the message that it was not found yet clearly means that the tree has borne the fruit.
 but we can’t find it anywhere…’how long did he ponder over it? he suddenly looked at the roots rising above the surface of the square.
“wait a minute…”he then stood up from his seat and looked at the roots near him.
then, he muttered, “well, there is no law that the tree bears fruit only on its branches, right?”the existence of the “world tree” was beyond human understanding.
so, he thought it might be too narrow-minded to believe that the fruits would be born only on the branches of the world tree.
he immediately summoned two specters.
“examine everything under the roots.
”two specters crept into the ground.
 sungwoo shared their view with him.
the underground was already ravaged by the roots of the world tree.
 its strong and thick vitality pushed out the hard stratum and underground facilities and occupied a huge area underground.
when they went underground to some extent, there was a series of spaces between the roots through which people could come and go.
 it looked like a passage made intentionally.
 with a little renovation, it could serve as an underground space.
and a spacious room emerged at the center of the space, namely at the point where the thick roots united.
‘i’ve found it.
’there was a round object hanging right there.
 as sungwoo expected, the fourth fruit was growing from the root underground.
sungwoo confirmed the information of the fruit through specter.
[item information]-name: the second fruit of the world tree (unknown fruit)-grade: myth-category: consumption

-effect: unknown-description: it is still not fully ripe.
 it’s somewhere empty and unstable.
 if this fruit grows like this, it will be a worthless one.
 however, it is possible to determine the future of the fruit by “imprinting” a “special power” into it.
 depending on the magnitude of the force, the effect of the fruit will also vary.
since it was hidden, the fruit was a completely different item from the other three.
looking at the description, sungwoo could not use it right away.
although he succeeded in finding the fourth fruit, that was not all.
 he had to solve additional puzzles.
‘imprinting? does it mean that this fruit doesn’t belong to any specific tribe, so i can choose one?’it was a kind of “blank check” in that respect.
“in that case, it is important what value to enter on this blank paper.
 if this is the case, another quest?”a message rang as soon as he said that.
-you have satisfied the conditions for progressing the ‘myth quest’ by meeting certain conditions (possession of an ‘unidentified egg’).
[myth quest]-name: origin of the race (dragon race)-type: unknown-goal: find ‘the clue to evolution’-reward: evolve into a new race* you have obtained two “absolute seeds.
” one is the growing and powerful race itself, and the other is the vessel of life that can contain transcendental power.
if the two seeds are fused under destiny conditions, you will create a new myth.
* when an unknown egg ‘hatches’ and the world tree reaches the ‘completed’ stage, the ‘evolution clue’ will be revealed.
 (if either seed is damaged, you will fail.
)“dragon race?”it was more terrific than he imagined.


 