\section{chapter 148}

                             




“what the heck are you doing? are you going to show the scenes of our players being slaughtered to the chinese server?”“pardon?”kuan looked around.
 obviously, the worst situation was still unfolding, and 120,000 viewers watching it were also pouring out messages of regret and condemnation.
“ah!”their purpose was to not only win the battle but also to show off and promote the glorious scenes of winning to the chinese server.
 but this kind of scene wasn’t good.
“turn the camera from it! to no.
 2! turn it back when the tide is in our favor after showing the scene of our divers landing on the island and killing them brilliantly! just show the good scenes!”“ah! yes!”kuan hurriedly turned on his phone, then set the relay camera from channel 1 to channel 2.
soon, the broadcast screen was changed to the camera set up in a different area.
then, all sorts of protest messages popped up in the chat room, causing an uproar.
 it was natural that they vehemently protested because the scenes of fierce fighting on the battlefield until a moment ago were suddenly replaced with the scene of a quiet forest.
 10,000 viewers disappeared in an instant.
the atmosphere changed so radically the viewers got so confused.
 with the chirping of birds everywhere, masked people were moving secretly through the bushes.
“this is camera 2, and we’re now ambushing point b.
 it’s very, very quiet here.
”the camera operator at point b whispered.
 hiding on the slope of the mountain, he directed the camera lens somewhere, where there was a lawn plaza with a blue flag.
“can you see it? that’s point b.
 we don’t know what’s going on behind us, but we’re going to take over this place soon.
 it’s our first step to victory.
”the camera zoomed in.
 someone was standing behind a tree beyond the flag emanating the blue light.

it was a woman in a red sweatshirt.
 she seemed to be hiding, but the divers were highly trained, they could easily find out where she was.
“can you believe that only one woman is defending point b? those koreans left to attack our main forces,” the camera operator said, laughing slyly.
“our operation is to use commandos to occupy the rear, so it seems that we have succeeded in making a surprise attack.
”the camera lens caught the face of a woman looking around here and there.
 she seemed anxious.
“even that woman mistakenly thinks that she has hidden completely.
 as you see, very unfortunately, they don’t seem to understand the rules of the mini-game.
”the camera operator giggled again.
then, those expressing complaints in the chat room agreed with the camera operator, then began to say koreans were stupid, for most of the chinese viewers also wanted to see their players would win.
and it seemed that the situation here was getting better for them unlike a little while ago because it seemed they tried to pull out the enemy’s main forces, infiltrate the major stronghold of the enemy’s rear, which seemed very strategic in the eyes of the chinese viewers.
“huhhhhhh… hello, everyone, this is the power and wisdom of the mainland.
 our red revolutionary army is glorifying the name of the mainland to the world.
 trust us!”the viewers of the chinese server fell into a thrilling situation that showed a dramatic turnaround in the tide of the battle.
as they intended, a series of messages supporting the “red revolutionary army” began to come up one by one.
 this was the effect of their propaganda.
“now, everyone, take a good look.
 do you know who will be coming out next? the best warriors of china’s 2 servers, huei and the terrifying divers, are approaching stealthily.
”as soon as the name of a celebrity appeared, the viewers in the chat room started to get emotional and passionate.
as a popular celebrity on the chinese server, he was often called the most powerful warrior on the mainland, so much so that even if the red revolutionary army got blamed, he was excluded as a subject of criticism.
“they are almost there.
 can you see them? yeah, our hero huei! now, it’s time…”but even before the camera operator was done talking, something happened.
 the camera, directed toward that place, was illuminating that place where the divers were approaching.

“uh?”a woman in red clothes was drawing her sword.
 her face, neck, and blade were stained with blood, and several long cuts were left on the tree she was leaning against.
“…”there were several corpses underneath the tree.
“uh, so…”the woman in red was looking straight at the camera now.
 her eyes were rather empty, not just murderous and threatening.
100,000 chinese server players who were watching the broadcast made eye contact with her.
“damn it! we’re done….
”it was the moment when jahon’s ambitious plan to occupy points b and c fell flat and was being broadcast live to the chinese viewers.
***a few minutes ago.
huei, the man who stuck the flag of the mini-game on kanghwa island, was currently ranked 22nd with level 15 in the “china 2 server” rankings, and he was called the best warrior in china, but he was hesitating to take action now.
even though his main base was being attacked, he didn’t take any action, while hiding in the bushes.
 then, his men began to egg on him to take action urgently.
“captain! we shouldn’t delay any longer.
 if we don’t do anything…”“right.
 why are you dragging your feet like this because of that woman?”“no, she is different,” huei said, frowning and expressing deep frustration.
“pardon?”“that woman is different.
”his subordinates tilted their heads and asked, “what do you mean?”“i’m not sure, captain.
”huei moved his head to point to the corpses lying around the flag.
“can you see the bodies of the no.
 2 commando team?”“yes, i can see them.
”they were 12 corpses and 12 axes, which belonged to the no.
 2 team.
“they all had the same scars.
 this means that they were killed by the same person using the same weapon.
”“really?”“did the woman kill them alone?”huey nodded, then said, “she slaughtered the 12 men on the no.
 2 commando team from the elite unit.
 the two guys were killed by her with a single stroke, and the three men closest to the flag fell almost simultaneously.
 and those bodies strewn here and there were…”“they were killed while running away…”“right.
 that’s the evidence that they were killed while they were retreating in a hurry, frightened and scared.
 even the last two guys have cut scars on the back of their necks.
”the no.
 2 commando team was the unit that served as the advance party in the fleet led by gen.
 jigong.
 in other words, they were the first to land and attack at the forefront, so they were more brave and agile than anybody else.
 how could they be killed while running away?

“it’s ridiculous.
 that girl over there, who openly revealed herself like that, had such a high level as to kill them all?huei nodded, then continued, “fortunately, she hasn’t found us yet.
 even if she is a master swordsman, we can kill her if she lets down her guard.
 so, approach her carefully and kill her at once.
”the best assassins moved to kill the woman.
***sungwoo left the important base, point b, with jisu and left.
she stood leaning behind a large tree, where she could monitor the flag at point b.
she blocked the enemy’s first attempt to occupy the island, but they would never give up.
so, she was fully prepared for the upcoming fight.
 but she was the only person who would protect this place.
standing in the woods, she kept all her senses open, monitoring every movement around her.
and soon she sensed something strange.
‘someone is coming.
 they are hiding their movement.
’their movement was unusual because of their restrained footsteps and the sound of breathing.
 she instantly knew that somebody was approaching her stealthily.
‘lots of them are coming.
 six? no, eight.
’those who approached point b obviously had a professional occupation, specializing in surprise attacks and assassination.
 as long as they had similar traits, it was not easy for her to deal with them all at once.
that’s why she decided to expose her position easily.
 in short, it was sort of a deceptive operation.


 