\section{chapter 149}

                            as expected, the enemies rushed at her as if they looked down on her when she exposed her location so easily.





there were a total of three who charged at her.
clang!jisu hit the sword of the first of them.
 his sword bounced off and cut the tree where she stood leaning.
 seizing the moment, she swung her sword at his neck.
 but the man leaned back and avoided her sword, then threw himself into the woods.
‘he is fast.
’but the other two were not as agile as the man who disappeared into the woods.
they saw her wielding her sword, but they didn’t predict the energy of the sword emanating from its blade.
 the two heads were severed at the same time, falling at her feet.
right after that, she turned her head and looked somewhere among the trees on the hillside.
someone was hiding there, aiming something towards her.
 it was a camera.
‘camera? are they broadcasting this fight?’it was the moment that her face was broadcast live to the “china 2 server”.
frowning, she pulled out her legs.
 it wasn’t just the camera that was aiming at her.
the enemy numbered eight, but two of them were killed.
 the rest of them, positioned all over the forest, were closing in on her gradually.
‘arrow?’they fired two arrows at her, aiming at her eyes, but she wasn’t there when they looked at the place where she had been standing.
“damn it! how come…”she was now blocking the only man who escaped her sword.
 she caught up with him by using the ‘footstep tracking’ skill, but the man charged at her.

the two swords clang against each other.
clang! clang! clang! clang! clang!their swords collided five times in an instant.
 they couldn’t cut each other, but the man couldn’t withstand her power and stepped back.
 then he began to get out of the woods and jumped into the lawn park.
‘he is different.
’that man was clearly different from the opponents she had dealt with until now.
 he was obviously a master swordsman.
 she rotated her wrist to loosen her muscles.
 then, she went out to the lawn park to chase that man.
“wow, she is so strong! it’s more fun than i thought.
”actually, he was waiting for her there.
 he was apparently embarrassed, but at the same time, he felt the strong urge to beat her this time.
 it seemed as if he was enjoying the fight.
“how could she deal with me who chose “barbarian” as the second occupation card? even without the occupation buff, her muscle strength should be 27 and 30 if she wanted to deal with me.
 she must have invested in stats instead of drawing skills from the level-up card.
 what a freak!”he analyzed her now, and his analysis was somewhat correct.
 he fought against her again to find out her stats.
 obviously, he was a high-level master swordsman.
at that moment, something was moving.
 jisu and the man felt it at the same time.
“no!” the man screamed, but jisu moved faster than his screaming.
her sword cut through the air, and someone’s head flew through the air a few meters away.
it was a surprise attack, but the body fell some distance away from her.
 he didn’t even dare to get close to her.
“what a stupid guy! i didn’t teach you like that… by the way, you are quite extraordinary.
 i guess your agility is around 21?” asked the man.
“…”“what’s your name?”“…”
“i’m huei from a chinese server.
 to put it precisely, server 2.
 i’m called the best swordsman on the mainland.
 are you the strongest on the korean server?”jisu had no intention of responding to him, but he kept talking.
“you are a woman of few words.
 you must have noticed that the camera is filming this place, right?”huei lifted the sword and pointed at the camera.
“i’m sorry to meet you like this.
 i can’t play with you for long because i have to occupy point b quickly, but it won’t take long for me to kill somebody, of course.
”“… but in fact, it doesn’t take long for a person to lose their breath.
”smiling eerily, he pointed the sword at her.
“i have fought master swordsmen in china in a fair manner and beat them all.
 so my name is known to everyone on the mainland.
 now, let me have my men step back, so let’s fight in a fair manner.
 i will bury your body honorably.
”the camera put the two in one frame.
 the camera operator relaying that scene couldn’t hide his excitement while broadcasting it live.
“can you see them, every one! huei is trying to cut someone with all his might.
 the best swordsman in mainland china! huei’s duel begins again in this remote place!”the news spread to the chinese community that the duel between huei, the famous man on the chinese server and an unidentified korean warrior, would begin.
because of that, the number of viewers on the broadcast began to increase explosively as if to show huei’s name had such a strong appeal.
huei looked at her with a determined expression.
‘let me cut that woman here and create a sensation on the whole server.
 then, we can glorify our name and gen.
 chongong will be happy about it.
”their purpose was the same.
 in other words, they wanted to restore the reputation of the red revolutionary army, and make foreign servers such as taiwan and korea the scapegoats for him.
if huei beats the korean swordsman in his event, it will bring about positive publicity.
 even this kind of fight was also intended as propaganda.
“whuuuuu…”huei let out a rough breath, firmly grasping the hilt.
 then, certain energy began to dwell in his body and the sword.
-‘savage rage’ is activated.
* increases muscle strength for 1 minute for 3 or more consecutive attacks (+5)-‘violent vanguard’ is activated.
* attack speed increases for 5 minutes (+25%)he was now ready to do his best.
the swordsmen of the two servers, korea and china, faced each other.
 as he said, his men hiding in the woods didn’t take any action.
 it may be huei’s greed, but he wanted to make a dramatic propaganda effect by killing her one-on-one.
after a short pause, huei first moved.
 he slammed the ground.
 in an instant, the distance between them narrowed.
 he struck at the woman’s head.
clang!the two swords clashed.
 the air around them was twisted because it was surrounded by the buff.
 this time he was not pushed by her.
 he swung his sword again with confidence.
clang! clang!when they clashed for the second time, she took a side step.
 turning to the side, she was about to get out of his striking range.
clang! clang! clang!after colliding twice, their swords overlapped briefly.
 the moment the metal was crushed and sparks scattered, she moved once more.
 as expected, she took the side step to the left, then got out of his range, making a half-circle.
“you can’t get out of here!”huei took a step back not to give her any chance of attacking.
 he could respond to her with this little movement, and he had to.


at that moment, jisu’s movement changed exquisitely.
 she lowered her posture and moved in the opposite direction.
 huei’s eyes followed her movement, but it was so exquisite and accurate.
 he clearly noticed it, but before he knew it, she cut him in his ribs.
“kuuuuuuuuh!”with blood gushing from his ribs, he staggered.
“damn it! how could you…” he moaned.
she took off the blood from the blade and opened her mouth with a calm expression.
“aren’t you going to ask for your men’s help before it’s too late?”those were her first words.
 a broadcast accident occurred again.
***“hold out! hold out!”“block that golem!”on the other hand, the battlefield where the pirates’ main unit and the necromancer were fighting was very tough and scary.
 the necromancer’s forces kept resurrecting no matter how many times they were killed, and the giant slingshots the troll skeletons fired were comparable to catapults.
 they killed the tankers on impact.
bang! bang! bang!the damages caused by the continuing corpse explosions were huge, and a couple of undead swordsmen that penetrated the rear did not show any sign of falling.
“i know how you got involved in heinous actions! let me kill you all!”rattle!they were minsok, whose eyes were radiating green light, and orun.
the two defended each other’s back in the heart of the enemy camp, smashing the wizards and easily knocking out the tankers.
 

 