\section{chapter 364}

chapter 364: devil’s world tree and world eater (6)sungwoo quickly read and reread the message that appeared before his eyes.





‘i was so powerful even when i reached the ultimate stage.
’after he enhanced his skills to the ‘ultimate’ stage through the synergy of [harmony of death (hidden)], he could confirm how strong the ‘bone weapon manufacturing’ skill or ‘corpse explosion’ skill could be.
‘then, it’s a super stage now?’in sungwoo’s eyes, the super stage of skills was not something that he could reach through a typical method.
 it seemed to be a ‘hidden element’ that was available only when he met a hidden condition such as ‘divinity’ such as anubis or king of underworld.
so even the skill information about it was brilliant.
[skill information]- name: the power of the 4 knights of apocalypse- grade: super- type: passive- consumption: -*as long as the ‘apocalypse’ synergy persists, the following ‘additional effects’ are issued for 60 minutes.
.
 power of war: summons the ‘apocalypse army’ sealed in the abyss and acquires ‘command power’.
.
 power of famine: creates a ‘death land’ connected to the abyss within a certain area (10km).
.
 power of plague: the effect of area damage magic and curse magic increases significantly.
 (+400%).
 power of death: you gain strength from the death around you.
 (all skill effects +1% per death)
‘all skills related to death are strengthened at once?’the four knights of the apocalypse meant one of the apocalypse scenarios in the bible.
since they personified all the elements that could lead to the end of mankind, it seemed safe to say that it was the ‘highest stage’ of the power of death.
meanwhile, the world eater stopped attacking and looked around.
 realizing that sungwoo’s power changed significantly, he began to examine the current situation carefully.
“two scythes of the grim reaper? then…”as the world eater was the final winner of this world, he could size up the flow of the game.
 it was a kind of insight.
 he soon noticed a change in sungwoo.
“you’ve got four lich.
”however, he had no choice but to shake his head as if to deny his own calculation.
“nonsense! this synergy can’t exist!”as he said, it was obviously strange for four lich to exist in one place because such a possibility was almost remote.
at that moment, sungwoo shouted at the world eater who had already seen the end of this game once, “well, i guess you don’t know this game very well yet? what you have seen isn’t all you know.
”however, the existence of such a super-strong synergy was possible, given the repetition of variables in a very long journey.
 in other words, hidden elements were repeatedly combined to create a powerful synergy that the world eaters wanted to deny.
“you didn’t play this game for a day or two, so i think you must know it.
”this time victor and minseok stood next to sungwoo.
 mir came out from somewhere.
they were the four lich that the world eater was witnessing right before his eyes.

“don’t you know this game and this level are not all there is?”but the world eater remained calm.
 he frowned as if he was a little embarrassed, but that’s all.
he shook his head and said, “necromancer, if you think you have become stronger because of that synergy effect, you’re mistaken.
 you can’t beat me.
”the guy moved again.
 he raised the tip of his sword and stepped forward.
 however, sungwoo did not dodge like before and stretched out his hand.
then, he used a new skill.
‘summon the apocalypse army!’- you have summoned the ‘apocalypse army’ sealed in the abyss through the ‘power of the 4 knights of the apocalypse’.
‘umm.
 let me see what comes out.
’it was the first time sungwoo summoned them, so he didn’t know how the situation would change.
kugugugugugu!the first sign was a huge vibration.
 the ground shook, which was quite understandable.
since the world eater didn’t know what was going to happen, he couldn’t charge at sungwoo recklessly.
 he slowly floated into the air.
 then, some purple light began to rise from below.
 everyone’s eyes turned to the ground.
the source of the light was a magic circle.
 a huge magic circle with all kinds of bizarre shapes covered the entire cradle of the victor, namely, the world eater.
‘it’s bigger than any magic circle i’ve ever seen,’ sungwoo thought to himself.
at first glance, it seemed that something terrible was about to happen.
 in no time, an option came to sungwoo’s mind.
- select the target (corps) for you to summon.
.
 prisoners unit (summoning possible).
 gigantes (summoning impossible: below overall level).
 sealed person (summing impossible: below overall level)but right now he could make only one choice.
 was it because the skill grade of the four lich that generated synergy was generally low?so sungwoo had no choice but to choose the no.
 1 option, namely, the prisoner unit.
 then, the light emitted by the magic circle started to get stronger.
the ground began to twist violently.
“it’s falling!” minseok shouted.
was it because of the energy emitted by the magic circle? the ground was starting to crumble.
sungwoo immediately moved the ‘zombie hippogriff’ to take care of the players whose movement became stiff due to the dragon fear.
right after that, he hurriedly tried to hug mir, but mir spread his wings and flew over sungwoo.
‘what? can he fly?’believe it or not, mir had been growing before sungwoo noticed it.
kugugugu-soon, the whole ground crumbled underground.
 sungwoo barely had a zombie monster grab his shoulders.
 everything in the halls of guardians fell tens of meters underground.
 altar, capsules, bundles of tangled roots, and undead army soldiers were smashed here and there.


sugnwoo safely landed on the ground and looked at the new battlefield.
 thanks to the purple magic circle floating above his head, he could watch it more clearly.
‘it’s much wider.
’this place seemed to be a space under the roots of the world tree, which was three or four times larger than the victor’s cradle.
it was better for sungwoo because if the ‘apocalypse army’ was added to the hundreds of undead army under his control, they could get tangled with each other and make it harder to move forward.
 so it was a timely changeover of the battlefield.
sungwoo raised his head.
 floating in the air, the world eater was glaring at the purple magic circle.
- you have summoned the ‘apocalypse army (prison troops)’ from the abyss.
soon, the magic circle began to rotate slowly.
 sungwoo’s summoning began.
woowoowoo-then, something started pouring down near the center of the magic circle like a waterfall, as if a huge floodgate was opened.
kwagagaga-a huge number of skeletons came out.
 the ‘apocalypse army’, summoned from the abyss, appeared on the new battlefield in a terrifying manner.
kwajik! kwajik!they were smashed to the ground like skeletons.
 another group of skeletons collapsed on top of them.
 they kept being stacked on top of them repeatedly.
the shattered bone fragments and all kinds of weapons were mixed here and there, creating a bizarre scene.
but the real spectacle began only now.
 the shattered bones found their place on their own and began to reassemble.
rattle! rattle! rattle!

 