\section{chapter 177}

                             




a large tv was installed on one side of the watchtower, and a scene of a magic drone in action was displayed on the screen.
“you can look here.
 it’s about five kilometers away.
”what the wizard pointed at was above an apartment complex between a clear sky and thick clouds.
“…”something was flying from there.
“what is that?”it looked like a huge flying monster with long veiled wings.
“they’re wyverns!”someone muttered.
 as he said, the flock of wyverns filled the sky.
“sungwoo? can we confront them? i know you killed several of them before.
 but it looks like there are too many wyverns.
”like kyongsu just said, sungwoo confronted only three wyverns in the past.
 it was also a very tough job for him at that time.
 if he had not driven them away, he would have plunged into a dangerous situation.
however, sungwoo seemed to have full confidence this time.
 at that moment, kyongsu felt it might be his illusion that he sensed something like expectations in sungwoo’s face.
“you are right, kyongsu.
 it was a close call at the time.
”“then, how are you going to deal with them this time?”“but the situation is different now.
”sungwoo pulled out a human beast ampoule.
perhaps he could dominate the sky of the korean server.
wyverns are powerful monsters comparable to the raid boss monsters.
“they’ve arrived!”
their appearance alone was enough to terrorize the opponents, but there was a real reason why people feared wyvern.
 it was because dozens of such terrible monsters flew in groups for hunting.
 as a result, they didn’t end up hunting their prey simply.
 once they attacked any group, the attacked group could not avoid extinction.
“well, how many wyverns are there this time?”they were a disaster far beyond fear.
the wyvern group was called the ruler of the korean server, and such a title has never changed since the opening of the korean server.
only once the necromancers left a blot on their notoriety, but there was no doubt that even the necromancer was only the wyverns’ helpless prey.
krrrrrrrrrrrrrrrrrrr―such dreadful monsters appeared above the village of suwon.
“why are they circling in the sky like that? i just feel dizzy,” hanho said.
like he said, they didn’t rush to target their prey.
 no, they didn’t.
they became impatient to attack their prey at the bloody smell and the smell of human flesh coming up from the ground, but they wouldn’t dare fly down until the boss wyvern issued an order.
“because there is a more terrible monster reigning over those terrible monsters.
”his name was wyvern alpha male.
it was the boss monster that led the strongest monster group on the korean peninsula.
it is twice as large as a typical wyvern.
 even though he has the title of “boss” among wyverns, nobody has ever witnessed him directly attack his target.
 in other words, it is a monster never known clearly to the outside world.
‘wyvern alpha male doesn’t come down even after the other wyverns begin hunting their prey.
’just like he did at the battle at kimpo airport, he was always flying at the highest altitude even when other wyverns were attacking their prey.
 since the other wyverns brought prey to him, the boss monster only focused on commanding other wyverns and monitoring the situation.
‘so, i have to make him fly down, then never fly again.
 that’s my goal,’ sungwoo thought to himself.
like he did at the kimpo battle, the boss monster would fly down and launch an attack when the other wyverns under his command were put in a dangerous situation.
 but when the situation became more urgent and dangerous, he would choose to retreat, but sungwoo had no intention of expelling them or letting the boss monster withdraw them.
‘i must catch all of them and kill them this time.
’
sungwoo wanted to make all of them fodder for the world tree.
 he decided to do his best for the growth of the world tree.
“we’re all set,” said kyongsu, approaching sungwoo.
this time, all the players in the village were supposed to be mobilized.
 the players crouched on the rooftop, alleys, or under trees and waited for the wyverns to approach.
“…”soon, long and dark shadows began to come down, a sign that the wyverns’ wings came down closer.
 it also meant the boss monster had issued an order.
woooooooooooooong!their fluttering wings turned into strong winds and swept overhead.
 their attack began.
their target was the world tree growing in the square of the village in suwon, but sungwoo was standing in the middle of it.
watching him, the village players were in a tense mood.
“whew…”“everybody, stay calm! we have to wait.
”the wyverns began to move, but it was clear that they were not yet given a clear order.
sungwoo was standing under the world tree without moving at all while raising his head toward the wyverns.
five wyverns lifted their claws over his head.
 in a few seconds, the world tree would be uprooted and sungwoo would be torn apart if he didn’t do anything.
at that moment, however, sungwoo raised his right hand.
 kyongsu and inho straightened up as soon as they noticed it.
“fire iron mace!”“lift the curtain!”he issued the order according to the prepared operation.
clang! clang!the next moment, two flickering spheres fired up from somewhere on mt.
 paldal.
 they were the iron maces of the lightning god sungwoo captured from the evolution society.
 he had built battlements somewhere on mt.
 paldal early on.
bang!the formidable bullet soared in the air before nose-diving and colliding head-on with the wyvern.
keeeeeeeeck!the two wyverns at the forefront stopped fluttering their wings, then rose upside down as if to bounce off.
 then, they immediately fell free from the sky.
“they were killed on the spot!”two wyverns died instantly.
 indeed, it was a huge blow for the wyvern group.
 the ballista used by red orcs also inflicted fatal damage on the wyverns, but could not kill them immediately.
kaaaaaaaaak!however, only two of them were killed.
 the three wyverns in the rear row did not stop and continuously descended toward the world tree.
 the world tree was so attractive and lured them in.
“now is the time to attack!”at that moment, players lying face down near the world tree took off the blue curtains installed behind the world tree.
rattle!there were ogre skeleton and four troll skeletons gathered inside.
 they were hiding there, covered with plastic curtains.
ogre skeleton moved first.
 he stretched out his right arm and used the skills built into his bracelet.
dark blue lightning was shot into the sky.
 three wyverns were pushed back, electrified by the current.
 that wasn’t the end.
 the troll skeletons standing behind him pulled huge slingshots.
tu-woong! tu-woong!this time the village players poured out from around the world tree.
 they were waiting for the perfect time to attack, lying down in the parked buses and under a pile of dirt.
this was the perfect moment for their attack.
“use magic!”

“target their eyes and heads!”the players launched all sorts of attacks on the wyverns that were flying around in great confusion.
 their cooling skill hit their wings and hindered their flight, and the flames soared and burned their corneas.
 then, dozens of arrows were struck in their relatively thin stomachs.
tung! tung! tung! tung!sungwoo also fired a series of arrows.
 wyverns couldn’t fly again after being hit by all sorts of magical attacks.
-you have earned 694,031 gold by hunting wyvern.
-you have earned 665,444 gold by hunting wyvern.
-you have earned 614,511 gold by hunting wyvern.
-you have exploited their souls.
 (cumulative: 38)“we have hunted them!!”“more wyverns are coming behind you! hide, everyone!”while the players were realigning their formation, sungwoo picked up the grim reaper he had been put down on the ground and removed his hood.
 then, a black wolf’s face was revealed.
-grim reaper retention time (00:48:44)-werewolf retention time (00:49:02)when his anubis status was canceled, the cumulative souls disappeared, so sungwoo obtained the power of demigod early to hunt the monsters around.
 that’s how he exploited their souls.
“isn’t it time for the wyvern alpha male to come down now?”sungwoo raised his head and caught a huge shadow hidden in the light of the sun.
he felt the wyvern alpha male’s altitude was lower than before.
 the wyverns flying around him dispersed from side to side.
as expected, the boss monster was coming down.
“yeah, come on!”

 