\section{chapter 145}

                             




the occupied area nearby was ‘c’ marked with a green light.
 it was located to the northwest of kanghwa dolmen gymnasium.
“hanho, take the players on standby with you and move to the yellow beam right now.
 take over the area there,” sungwoo said.
“okay.
”the c area was the place that they could occupy first, and at the same time, it was the farthest from the pirate fleet now landing on the southern coast of kanghwa island.
 therefore, it would be relatively safe and serve as the last fortress for sungwoo’s forces.
“heyon, you monitor the situation in the sky and inform the people below by radio.
 if you find the enemy’s magic drone, destroy it.
”“yep!”she nodded, then ran toward gust.
 the players of kyodong island also prepared for the battle systematically.
 since they have been waiting for this moment, vowing to take revenge, they were full of determination rather than embarrassment.
“jisu, let’s go to the blue light,” sungwoo said.
the next closest place was the blue light, occupied area b.
 jisu and sungwoo got on bone wyvern, which soared into the sky instantly.
as the altitude increased, the location of the two beams of light in the south became clearer.
the blue light area was located in the middle of kanghwa island.
 and the last occupied place, the red light, seemed to be located at a mountain peak in the southernmost part of the island.
at that moment, some noise came out of the radio.
 sungwoo put the radio to his ear.
-they are landing on dongmak beach right now!it was muyon’s voice.
 he seemed to be on the southern beach checking the movement of the enemies.
 dongmak beach was near the red-lit occupied area a.
“got it.
 don’t approach them.
 just go to the area with the green light.
 since the enemies are also running a drone, you will be spotted if you get near them.
”– yes, i understand!sungwoo already reached the blue-lit area near occupied area b.
 it was inside a small theme park with a lawn square and a maze.
“look at that flag!”like jisu said, a flag was firing up a light.
 that seemed to be the object of the occupied territory.
“let’s go right away!”sungwoo had the wyvern land near the flag, and he ran towards the flag.
the alphabet ‘b’ was spinning around on the plain-looking flag.
 sungwoo approached it boldly and grabbed the flagpole.

-occupation starting now.
 (cancellation is not possible.
)“what the heck?”his hand got glued to the flagpole like a magnet.
 he couldn’t take his hand off from it no matter how hard he pulled it.
-occupation underway (100 seconds left.
)* you cannot take offensive actions during occupation.
* all the subjects of summons are incapacitated.
this was a very unfriendly game because sungwoo was never informed of such important information in advance.
“jisu, please watch your surroundings.
 we cannot move during the occupation.
”“yeah.
”she pulled out her sword and looked around.
 it was a lawn square, but because it was not maintained for a long time, it was lush with weeds.
 so, there were plenty of places for her to hide.
-occupation underway.
 (91 seconds left.
)a countdown message was displayed above the flag.
-occupation underway.
 (90 seconds left.
)however, jisu wasn’t distracted while watching out the surroundings carefully by using all her senses.
there was nothing she could feel right now, but there was a high possibility that the pirates divided their troops sporadically to try to occupy the island.
as expected, jisu sensed something unusual.
“sungwoo, i hear something coming this way.
”a little farther away, a magic circle began to be drawn in the air.
 it was quite large, estimated to be 7 meters in diameter.
when the magic circle was completed, the portal opened and armed men poured out in droves.
 there were a total of 12 pirates.
-occupation underway (84 seconds left)“ugh! damn it.
 what a rough ride for an expensive order!”“damn, i guess the wizards are giving us trouble on purpose.
”
they stood up, groaning, then noticed sungwoo and jisu.
“what the heck?”“huh? stand up quickly! they got here first!”“really? already?”it seemed that the pirates also did not know that sungwoo responded to their landing so quickly.
 they guessed that when faced with a mini-game for the first time, it usually took time for people to figure out the situation, so the koreans in kanghwa island would face the same situation.
“but there are only two out there, right?”“yeah, one of them can’t move because occupation is underway at the moment.
”they watched the countdown that appeared above the flag.
-occupation underway (71 seconds left.
)“one minute is enough.
”“of course.
 kill them!”the twelve pirates pulled out their weapons and rushed at sungwoo and jisu.
 they were holding axes.
 as a result,  was getting synergy, so sungwoo could get a buff to increase attack power and attack speed for 20 seconds from the start of the battle.
“hey, just 20 seconds is enough to kill them!”but jisu stepped back, grabbing her sword.
 her gaze was still fixed on the front.
 she was not in a hurry while checking the remaining time until the occupation.
’63 seconds left.
’she was now guessing exactly how much time was left.
“just one girl is out there!”“just cut her arms because we want to play with her after occupation.
”at that moment, they threw an ax toward her.
 she bowed down to avoid the ax.
the next moment she threw herself to the left without raising her body.
puck!the ax was stuck where she was standing.
 the ax that flew behind her came back like a boomerang.
 it was her skill.
“don’t do tricks!”jisu raised her body and her sword.
 the pirates, who already approached her, swung axes at her shoulder.
clang!two weapons clashed.
 at first glance, she seemed to be unable to withstand their axes, but she invested a lot in her muscle strength.
“argh!”one of the pirates staggered for a moment.
 the next moment her blade cut past his neck.
the head of the man standing behind him was cut off.
two of them fell to her sword.
-you have earned 9,000 gold by killing a player.
-you have earned 10,000 gold by killing a player.
the level of those enemies could be checked by the amount of gold.
 although it was above average, they were far behind jisu at level 15.
they flinched and stepped back.
“damn it! we’ll be dealing with her, so other guys go and attack the occupying man!”-occupation underway.
 (53 seconds left.
)they rushed towards sungwoo, who was defenseless at the moment.
 no matter how high sungwoo’s level was, he could not deal with ten enemies at the same time while protecting somebody else.
“kill the guy occupying now!”three pirates aimed at sungwoo and one of them at the forefront threw an ax at him.
at that moment, jisu moved.
 the moment she took one step, her feet jumped several meters ahead as if the ground was folded.
 she was right there in front of them.
“uh?”she landed in the space between sungwoo and the pirates.
jisu swung her sword to block the flying ax.
“damn it! where did she come from so suddenly?”

‘tracing footstep’ was jisu’s newest skill.
 after grasping the opponent’s movement with a transcendental sense, she could reach their target in an instant by using that skill.
she jumped off the ground.
 her blade moved three times before the pirates, who were charging at sungwoo, even got into fighting position.
 red droplets splattered in all directions.
 jisu passed by them and ran straight to the pirates in the rear.
“uh?”the pirates hurriedly lifted their weapons and changed their posture.
 behind the woman in the red gym suit running like a wild beast, they saw three colleagues falling after they were cut by her sword.
 the moment they turned to her, something passed by their necks.
“damn it!”“gather together!”with only 45 seconds left, six were killed.
 now the pirates were getting confused about the countdown on the flag.
 they didn’t know what that meant.
“ahhhhhh!”while they were stricken with fear, the woman dressed in red moved without hesitation.
just like a maniac who enjoys slaughter, she swung her sword.
she was standing right in front of them when they recklessly tried to catch up with her.
whenever they moved recklessly, they had their necks cut before they knew it.
-occupation underway (10 seconds left.
)when 10 seconds were left, jisu stopped moving.
“i’m done.
”she rubbed her face to wipe off the blood.
 during the occupation, she not only protected sungwoo but also annihilated the pirates.
-friendly forces occupied ‘b point’.
* buffs are applied.
* reoccupation is not possible for 5 minutes.
[buff list of the mini game]“well, if i couldn’t move, i was thinking of cutting off my arm and getting out…man, i think i was wrong,” sungwoo said to jisu.
honestly, he was deeply touched by her brilliant fighting.


 