\section{chapter 329}






 the three battles between the chinese server and the korean server came to an end as the final battle in seoul was won by jisu, or valkyrie.
in no time a message announcing the end of the war appeared before everyone through the official channel screen.
“it’s all over,” said reporter ahn with a sigh of relief.
every battle in busan, suwon, and seoul was fierce.
 so, broadcasting the fierce battles in three places made him exhausted as if he was fighting on the battleground.
his assistant who was next to him shouted for joy belatedly, clenching his fists as if he could feel relaxed after a long time.
“wow! finally, our korean server has won!”reporter ahn nodded but added something as if he wanted to correct his assistant’s comment a bit.
“yes, our server has won.
 more precisely, maybe the necromancer has proved it again.
 in other words, our server can’t exist without him!”his assistant clapped his hands, nodding at him.
“ah! certainly, we have to say that the necromancer has turned the tide of the war decisively not only at the just-ended battle with the chinese server but also at the recent war between the korean server and the japanese server, right?”“you bet.
 of course, this time, the swordsman named jisu played a huge role.
 she held out with an extremely small number of allies on the seoul battlefield until the necromancer arrived, and actually, it was no exaggeration to say she deserved the credit for ending the final phase of the seoul battle.
”his assistant kept nodding at reporter ahn’s commentary.

she was really cool.
 in some respects, her fighting was horrible, but at the same time beautiful.
 depending on who saw it, her beheading the chinese troops might look cruel.
 i don’t know what kind of skill it was, but she beheaded several hundreds of them all at once.
 to be honest, i’ve become this lady, or valkyrie’s, fan today.
”“me, too.
 hmm, anyway….
”reporter ahn adjusted his posture and stared at her camera.
 although the war was over, tens of thousands of viewers were still watching the broadcast.
 it was time for him to give a closing comment.
“well, it is not the end yet.
 from now on, there is something we need to pay attention to.
 it’s also very important.
”“what is that?”reporter ahn paused for a moment, then said, “this war will not end at this point.
”although his speculation often proved wrong, he spoke confidently because he had some conviction this time.
“really? do you think we’re going to go through another big event?”“think about it.
 since we were attacked like this, isn’t it time for us to counterattack?”“can you elaborate?”“if you look at korean history, our people mostly ended up defending our country when they were attacked by foreign powers.
 but the necromancer won’t walk the same path.
 he will definitely take revenge on the intruders in a big way.
”his assistant swallowed, then asked, “well, do you mean it’s time for our korean server to attack the chinese server?”
“that’s right.
 and our korean server will be at the crossroads, depending on when the necromancer will attack china.
”the korean server has already come under the shadow of the world tree camp and united as one.
 so, every matter of the korean server was supposed to be influenced by what kind of choice the necromancer would make.
“and i am totally convinced that the necromancer will prevail this time, too.
”and most of the time reporter ahn trusted the necromancer’s choice.
***the leadership of the wpu watched the war between the chinese server and the korean server from the beginning.
 although they could not directly help the korean server because they could not afford to, the world tree camp was the most important ally of the wpu.
however, the more they knew about that ally, the more they couldn’t understand.
“hey johnny, did i see something wrong?” chairman love asked.
jonathan, who was sitting next to her, said with a blank expression, “chairman, that’s what i want to ask you.
”chairman love swept her face with his hand, then said, “to be honest, i don’t know what i’ve seen.
 was war like that by nature? am i mistaken about the concept of war?”“no.
 what we have just seen was obviously different from other kinds of war.
 i would say it’s something like an epic tale on the literature of medieval knights.
”how could the fate of war be decided by a couple of men? this was totally unrealistic.
however, such a situation happened many times on the korean server.
 the big explosion in busan, the fall of a building in suwon, and the massacre in seoul.
 all of them were just unbelievable.
“he told me before he left that he would come back with more power to stop the dragon on the occasion of this war.
 what he said was right!”there was amazement as well as hope in her eyes.
“if the necromancer’s ambition is true, this is only the beginning.
 i don’t think he will be satisfied with what he has achieved this time.
”“you are right.
 he will definitely attack the chinese server.
 and what he’s going to do is not start a war with them…”chairman love turned her head and looked out the window.
 the worst creature was breathing somewhere in the sky in the south.
“he’s going to prepare for the end of the world.
”how to stop the dragon? finally, the secret way to stop the dragon, which she could not find no matter how hard she thought about it, began to come to light.
“maybe he can really kill the dragon and save us.
”***the battlefield in seoul was quiet after the battle was over.
“well, there are so many things to do in the aftermath of this fierce battle where we risked our lives,” kyungsoo lamented.


even though they won the war, they could not have a comfortable break.
they could not put off cleaning up the mess and checking the situation.
looking at the chart showing the status of the post-war situation, he sighed.
“busan has been devastated, but we have 4000 chinese prisoners of war, including 1000 from suwon and 3000 from seoul.
 man, they are more troublesome than the damages to our forces.
”the war was fierce, so the allied forces killed a huge number of enemies.
 however, at the last minute when the enemy lost the will to fight, they kept surrendering.
 the allied forces could not kill them.
so, minhum came up with a typical method to deal with the prisoners.
“i think we should empty the coal mine in mt.
 pukhan.
 it looks like we need to release the guys from the evolution society that we have detained there.
”they were so-called “unpaid coal mine slaves.
” the coal mine was the right place to accept those who committed war crimes.
“ah, you mentioned that mt.
 pukhan had mining terrain, right? how many can you accept in that place?”“well, they have only dug three tunnels, so we can make only 1,000 people work per day.
 however, i have heard there are several mine terrains in gangwon province where the struggle guild main base used to be.
”“well, then, i have to ask the king of the great mountain about it.
 let me tell sungwoo about it first.
 we need to find a place for them to work endlessly.
”“yes.
 at least they have to work if they want to get meals.
 these days food is so precious…”

 