\section{chapter 466}

those that could fly among the hell creatures attached to his body soared in the air, then charged at sungwoo, raising their claws.





woooooooo-at that moment, ghosts rose from behind sungwoo's back and got entangled with the hell creatures.
 sungwoo summoned one zombie hippogriff and rode on it.
'i've got to disable the rest of his other arms.
'sungwoo raised the grim reaper.
 then he launched the evil spirit bombing that he had prepared in advance, targeting his shoulders.
there was an explosion right above his shoulders, and the hell creatures attached to his body fell.
meanwhile, other players also began to charge at the demon king.
jisu narrowed the distance in an instant, then adroitly deflected the incoming red light.
 only she could dodge such an attack.
 'it's watching me!'the third eyeball in the middle of his head was chasing her.
 since the demon king had as many as 12 eyeballs, he was monitoring everybody in all directions carefully.
'he's coming!'shortly afterward the hell creatures attached to his body rose and rushed at her.
 at that moment blue flames lit behind her back.
 as many as 20 blue flames arose.
the summoned einherjars wielded weapons while dispersing in all directions as if they had been waiting for this moment.
 they shredded the hell creatures ruthlessly like the blade of a mixer.
 their flesh was scattered everywhere.
his eyes followed her even in that situation.
 but they lost her at some point.
even the demon king could not chase her movements perfectly.
she hid after getting as close as to the red beams emitted by the demon king.
tack-in an instant, her feet touched the center of the demon king's head.
 and 20 einherjars summoned behind her back raised their weapons.
puck! puck! puck! puck! puck!einherjars' 21 blades started chopping the demon king's center head.
his eyeballs were maimed, and his head was raised, so the power of the eight beams from it was neutralized.
 now the demon king was exposed to more danger.
 
"now is the time! charge!" shouted junghoon riding on the hippogriff, moving forward.
hundreds of hippogryphs and the special commando unit members sped up after him.
"you can fight him freely.
 but when you avoid his attack, disperse quickly!"the hippogriffs spread their wings and scattered, dodging the incoming beams.
"oh, no!"bang!of course, not all of them could avoid the beam attack.
"hey, watch out!"bang!even though they got rid of eight beams, dozens of hippogriffs and special commando unit members disappeared without any traces.
 nonetheless, most of them could get close to the demon king's head.
 then they shot the cannons and fire magic they had prepared in advance.
bang! bang! bang! bang!the cannons and fire magic hit the target accurately.
'alright.
 their attack is paying off!"sungwoo moved gigas closer to him, then placed his hand on the superheavy bow that was hanging around his waist.
'should i shoot it now?'but he immediately withdrew his hand from it because three eyeballs on his left head were chasing him.
 'not yet.
 he is still targeting me keenly.
'even in such a complicated situation, the demon king was operating three eyeballs.
he was aware that sungwoo had the most powerful card.
'i have to wait until i can seize the better moment to attack him.
'he had to divert the demon king's eyes elsewhere first before he could properly pull the tough string of the superheavy bow.
at that moment, two of the three eyeballs monitoring sungwoo soared upward.
 they looked at something else.
'it's isabella.
'
the red dragon, who had been waiting for the right time, began to fall.
 suddenly, the demon king felt a strong heat over his head.
"watch out, everybody!"dragon breath was let out directly toward the demon king's head.
isabella's one single dragon breath hit his right head.
 his flesh melted and the bones were crushed.
 sungwoo's allies joined the fight right away.
 "start bombing!" junghoon shouted.
 sungwoo turned his head.
 hundreds of shells passed over his head.
bang! bang! bang!all of those shells hit the demon king's body, causing huge flames.
 his huge body finally started to lean back.
goooooooo-while sungwoo's party was drawing the demon king's attention, the fleet boldly approached him close enough to fire cannons, then started bombing.
after that, some players approached him closely, then worked together to cast large-scale magic.
bang! bang!'now is the time!'his head as well as all his eyes were engulfed in red flames and black smoke.
sungwoo hastily took out the superheavy arrow.
at that moment a message rang.
 - warning! the calamity 'harmageddon of evil' of the demon king's territory (demon king's castle) has begun.
'what the heck is this?'sungwoo looked around, putting the superheavy arrow on the bow.
 the calamity of the demon king's territory must be the hidden card that the king had saved until now.
"sungwoo, watch out over your head!"as soon as jisu warned, he hurriedly stepped back and raised his head.
he saw the red clouds filling the sky over the demon king's castle.
 but each of those red clouds was emitting light together.
'is it lightning?'the red clouds that contained the light trembled anxiously as if they were going to throw it out.
soon red lightning bolts poured down like rain all over the place.
 the fleet behind him was swept away by it.
 he saw dozens of airships collapsing.
'what the heck is this…'sungwoo hurriedly moved bone dragon over my head, but it couldn't be faster than the light.
everything was turned upside down.
***everything under the red clouds was swept away by the red lightning and collapsed.
 thousands of people died instantly.
 few players stood intact.
 "come on, move!""help me here!"those players outside the red clouds hurriedly approached and rescued the survivors.
kheeeeeeeeeeh!but there was a big problem.
 the hell creatures began to approach them.
"damn it!"their solid ranks quickly collapsed.
 since there were fallen players all over the place, they couldn't attack the hell creatures properly.
"run away!"at that moment, the hell creatures were cut in half by somebody.
it was jisu.
 "come on, run away!" she shouted.
 only she could notice and respond to the ominous movement of clouds and avoided it.
 she spread einherjars to stop the hell creatures, then turned her head somewhere.


her eyes rested on the bone dragon.
"oh, mir?"minsok, victor, and mir were aboard bone dragon, but bone dragon seemed to have crashed after being struck by lightning.
fortunately, mir's cries were heard.
 he was moaning under the pile of bones of bone dragon.
 jisu hurriedly approached him and took him out.
"ugh?"she found something brightly shining next to mir.
 it was the grim reaper that minsok was holding, or more precisely, the grim reaper from another world that he had obtained from the demon's cave.
 "yeah, i think i know it.
"this obviously pointed to the message that she should pick it up.
 "the wine the king of the great mountains gave me, and the shaman's power of connecting death and life…"she approached it, then lifted the death scythe that only lich could handle.
- you have reached the 'lich' status by satisfying special conditions.
she already experienced the 'witness to death', which was the condition for holding the scythe of death.
 so she was fully qualified for it.
but that wasn't the end.
- you can temporarily gain the power of 'baridegi'.
it was a new divine power.
 - caution! since you have not leveled up enough to accommodate both divine powers.
 you have to give up one of them.
* you must be at least 'level 25' to have multiple divine powers.
 "uh?" her level was 24.
***meanwhile, sungwoo got up in the hallway of the labyrinth.
 when the ground sank by the red lightning, he fell into the depths of the labyrinth.
another message rang before his eyes.
- you are given a 'synergy effect' due to team play.


 