\section{chapter 238}






 the day was breaking.
 the red dot on the map, namely the headquarters of the evolution society, was pointing to a mountain in daejeon.
sungwoo and jisu were making their way through the woods.
 since it was impossible for them to walk into the main gate, they had no choice but to pass through the woods.
“this way, sungwoo.
”even if they had a map, it would be very difficult for them to get the right directions in the mountain without any equipment, but jisu, who spent a few days in mt.
 taebaek, was very helpful to sungwoo.
“well, i think even an existing trail might have been blocked in this deep mountain because it had never been maintained at all,” she said.
“i see why they concealed their main base here.
”they were already approaching the red dot marked on the map, so the two moved a little more secretly.
but when they arrived at the expected point, sungwoo felt something was wrong.
there was nothing there.
“···”it was just an endless forest.
 sungwoo once again checked the map, but this place was right.
 “this the place…”“be quiet! get down!”at that moment, jisu pulled him into the bush.
“…”her eyes were rolling fast.
 however, sungwoo saw nothing.
“do you see anything?”“no, i can’t see it either.
 but i can feel something…”she did not see it with her eyes but with a different sense.
 she began to move forward carefully, and sungwoo followed her.

-you have entered the ‘curtain of virtual image’.
* a substance that was not visible from the outside has been revealed.
the moment they took a step, what they saw changed in an instant.
“this is …”the dense trees disappeared, and a building and iron fence appeared in its place.
jisu opened her mouth, looking back and front.
“there was something like a cover-up device here.
”using a certain item, somebody was hiding the entire huge facility from outsiders’ view.
without a map, no one would ever think of going into this remote mountain, so it was safe to say they were not caught coming here.
“it’s huge…”“i think a military base used to be here.
”the headquarters of the evolution society was a facility built by remodeling a military base.
 accordingly, it was a fairly large area.
given that a large number of trucks were moving inside the barbed wires, it seemed that there were many soldiers based here.
 there was very tight security, with watchtowers installed all over the place, and their security guards were a mix of human monsters and players.
“let’s check out a little more by walking along the fence.
”sungwoo was not hasty.
 he needed to check out their power as much as possible for a fatal attack.
 then, they discovered some human monsters were wearing metal collars on their necks while working inside the iron fence.
 other human monsters were monitoring them.
‘was there an internal struggle?’at first glance, sungwoo could realize that not all human monsters here were of the same rank.
 it meant that there were rulers and ruled among them.
a cruel research facility peculiar to the evolution society appeared far inside the fence.
“that’s what we saw last time in pyeongtaek.
”
there were a lot of familiar research subjects piled up at the place she pointed.
 they were combat weapons with human heads, bodies made of cloth, and animal limbs.
at first glance, they numbered several hundred.
 it wasn’t clear whether they were functioning or being scrapped, but their experiments required a huge number of sacrifices.
‘there are so many parts and human bodies piled up there…’jisu said, raising her finger, “look at that.
”all kinds of bodies were piled up in one pit.
 it was the source of the bad smell that had been filling the air.
water tanks that had been disposed of were strewn everywhere.
 inside them were floating the heads of humans and human monsters.
“they are crazy…”although this was a tough world where one’s life was regarded as valuable, sungwoo felt he had to stop their experiments.
 if they were left neglected, they would try to experiment with the entire korean peninsula.
“let’s get started.
”now was the time for sungwoo to root out the evolution society.
“i think it would be better to detonate bombs inside than to hit them from the outside.
 what do you think, jisu?”sungwoo’s firepower was overwhelming, but it had the fatal weakness of only one hour of retention.
 if he began to attack from the outside to get into their core facility, they were more likely to hold out inside the facility.
 in that case, they would try to counterattack after holding out for an hour behind the solid walls while blocking the undead army.
‘that’s why i can kill these guys more certainly when i attack them from the deepest part of their facility.
’jisu also agreed with him, and they soon found a place that seemed to be a key facility.
“yeah, that’s their core facility.
”it was a cylindrical building with no windows, but it looked like a nuclear reactor containment building from a distance.
“how can we get in there?”as she said, it didn’t seem easy to get inside the building.
 except for the vents, there were no holes for them to squeeze in, and there were a large number of security guards around it.
moreover, several snipers were dispatched on the rooftop, on the lookout for the surrounding areas.
so, if sungwoo and jisu approached it carelessly, they would give the security guards enough time to respond, which would mean they would have to fight their way into the building with difficulty.
“i’ve got an idea,” sungwoo said.
 “only i can use it, so let me get in first and make an opening.
”“sure.
”sungwoo immediately started the operation.
-you have summoned ‘specter’.
two ghosts appeared behind sungwoo.
 they passed freely through obstacles and slowly approached the core facility.
 they were able to hide in objects such as trees and rocks, so they avoided the eyes of the security guards.
“damn it, why do i suddenly have caught a chill.
”“me, too…”if sungwoo summoned specters, his target fell to the curse of ‘fear’ and ‘movement speed reduction.
’ even though they didn’t see the specters yet, they had goosebumps just by being around specters.
 it was a typical phenomenon they experienced when they got a cold and creepy feeling with the ghosts around.
‘go into the building.
’two specters succeeded in accessing the core facility, then squeezed themselves into the solid concrete exterior walls.
 it was a completely enclosed building without a single window, but specters were ghosts.
 so, they overcame such physical limits and succeeded in infiltrating into the building.
sungwoo shared the specters’ senses, so he could overhear those inside the core facility talking with each other.
“i heard ‘no.
 1’ failed again this time?”“so, did you trigger the highest alert? but if that guy was no.
 1, he must have taken chimera with him, right? but that monster was killed? are you sure?”while he was overhearing their conversation like that, a pretty neat facility came into his eyes.
 soon, the owners of the voices came back through the hallway.
 they were players in white gowns.
“well, i’m not sure, but that’s what i heard.
 none of the commandos no.
 1 took with him this time came out alive.
”“crazy, who the hell is this necromancer? as you know, we ground so many human monsters to make chimera.
 yeah, that’s why the heads of human monsters are hostile to us.
”“ah, that white rider, werewolf, was put into jail for opposing dr.
 yu.
 it looks like dr.
 yu is trying to get rid of the beasts.
”

“i like that.
 i was sick and tired of mingling with the smelly things.
”sungwoo searched inside the facility to find a shadowy place, but it was so bright and well-organized inside it was not easy for him to find it.
after passing through several walls, the specters arrived in a room full of corpses.
‘what the heck is this again?’it seemed to be a kind of warehouse where their research materials were stored, but like a butcher shop, the bodies of orcs and ogres were hanging from the ceiling.
 their drooping bodies formed shadows.
‘i’ve found them.
’sungwoo stopped sharing the specters’ vision and looked at jisu.
“i think i can do it.
 just wait a bit.
”“yeah.
”sungwoo once again shared the specters’ vision then teleported to the shadow inside the building using the function of the ‘shadow king’s bracelet’.
the next moment, his body arose in the shadows.
 it was a facility boasting of the highest security, but sungwoo could easily infiltrate using the ‘specters’ and ‘shadow movement’ skills.
‘these guys are using these bodies to extract the breath of abyss.
 man, what a huge amount!’sungwoo was stunned to find the numerous corpses piled up in the vast warehouse.
what he saw at first glance seemed at least 300.
rattle-at that moment, the door of the warehouse was opened.
 sungwoo naturally stepped into the shadow.
a man in a sanitary suit came in with a handcart and started hauling a goblin corpse into the cart.
 the next moment, a hand protruding from the shadow grabbed his neck.
“kheeeee!”“shut up.
 just answer my questions.
”

 