\section{chapter 255}

                            while walking uphill, escorted by jisu, they were fascinated by the mountain scenery.





with white frost piling up, a light fog peeled away little by little as they moved forward.
mountain peaks stretched to the left and right of the winding valley, and scattered clouds were hanging like curtains right under them.
ooh ooh oohas the mountain breeze pulled the edge of the clouds vigorously and pulled the curtain off, a dark stone mountain gradually emerged.
 it was as if the head of a giant was looking down at sungwoo’s party.
“well, don’t you think a mountain god is living somewhere here?”as the mountain terrains changed steeply, they began to look downward.
then, the tough roots of centuries-old pine trees continued to spread like a river stream, and white rocks stuck through the greenery were connected like stairs.
red flowers of unknown names were also blooming in clusters between the rocks.
“it certainly didn’t seem like this from the beginning.
 it’s rather alien.
”“you bet.
 this is the kind of place my father likes very much,” said hanho.
all the mountains also had some sort of mysterious appearance, but now this particular appearance of mt.
 seorak seemed to have been modified by the system in one way or another as if its intrinsic characteristics were intended to stand out.
“if we go a little further, we will reach the king’s dwelling,” jisu said.
the king’s dwelling was hidden deep in mt.
 seorak.
 of course, it was far off the mountain trail, and there wasn’t even a decent path leading to his place.
so, they got out of the valley and climbed through the pine trees.
 it was a steep climb, but the rocks and tree roots acted as stairs, so they could easily climb.
“it’s right there.
”jisu lifted her index finger and pointed somewhere.
“what?”
hanho showed an absurd expression at that, so did sungwoo.
there was a hut with a shingle roof in the middle of the mountain.
“is that where the king lives?”“yes.
 it doesn’t fit his image as the great king, right?”“nope, not at all.
”wasn’t he the “king of the great mountain” who unified the whole gangwon province and drove out the powerful players’ groups? how could he live in such a shabby hut?“it feels like a grandfather wearing hemp cloth is going to come out…”as hanho said, it was a bit big, but just an old hut where a natural man could live.
and the more they approached the hut, the more embarrassed they were.
“did i look forward to it too much? i didn’t expect anything like a luxurious house, but this is…”the area around the hut was flat with a potato field.
 farm tools such as plows and sickles were strewn around it, and a handcart was overturned on one side.
the three people in the middle of the field stood out.
 two of them were enormously large.
“why are weretigers there?”human beasts in the form of a tiger, wearing cotton jackets with pickaxes in their hands, were standing there.
 however, they were different from typical weretigers.
 they were huge enough to be five meters in height.
 sungwoo’s party would look like cats if they stood before the weretigers.
one of them found sungwoo’s party and said, “uh? brother! lady jisu is here!”“really?”then, the man who was hopping on the field sprang to his feet.

“lady jisu?”he was a handsome black-haired man.
 he stepped out of the shadows of the two monsters and smiled at them.
 then, he opened both hands to welcome them.
at that moment, a message appeared before sungwoo’s eyes.
-the field boss monster ‘king of the great mountain’ has appeared.
“ah! you are finally here! come on.
 welcome, welcome!”the king of the great mountain was digging up potatoes? he had a hoe in his right hand and potatoes he just dug in his left hand.
sungwoo and hanho looked at each other, expressing absurd expressions as if they could not believe it.
“the boss monster is digging up potatoes?”“yes! next to the potato field is a radish and cabbage field.
 his majesty seems to work like that for food.
”however, the king of the great mountain approached them casually and smiled friendly.
“oh, my god… i was digging potatoes to eat today.
 i look like crap as you see…”the king handed over the hoe and potato to the giant tigers next to him, then rubbed his hands against his pants.
 his white cotton pants were stained with dirt.
“how should i treat precious guests like you? i’m sorry, but i didn’t cook rice because the cauldron was smashed.
 i ordered my youngest boy to cook rice, but he broke the lid of the pot in half.
”while saying so, the king pointed to the tiger, five meters tall, standing behind him.
then, the youngest tiger smiled, embarrassed.
“well, the pot broke when i gently tapped it…”“hey, dude! didn’t i tell you to control your strength well? some time ago you kicked while sleeping and broke the wall! tut, tut!”as anger spread over the king’s face, the youngest tiger quickly bowed down.
“i’m so sorry!”because he was so big, just bending his waist was powerful enough to cause wind.
“you have committed a crime grave enough to have your next three generations punished! escort them inside politely!”“understood.
 please come this way!”sungwoo’s party stepped into the king’s shabby palace.
the king of the great mountain, his two minions, and sungwoo’s party sat face to face at the wooden table.
it was an ordinary table that could be found in a country house, but it was large enough for giant tigers to sit before it.
“cough! cough!”hanho coughed because the king of the great mountain and two tigers were puffing out smoke from a short pipe.
“ah, don’t you guys smoke cigarettes? i’ve got some more.
 are you interested?”“…”the king was sitting roughly at the table after draping a loose overcoat over his stained clothes.
there was nothing like a king’s aura about him.
a little later one of his minions brought steamed potatoes in a basket, but no one ate.
“these are newly harvested potatoes.
 why aren’t you trying them? they are not growing in this season, but i’ve raised them with magic.
 i owe it to all the grace of our forefathers.
”the two minions bowed, chiming in with him.


“absolutely!”however, there was silence for a while after that.
“hum…”there was an uncomfortable atmosphere among them.
 more precisely, the king and sungwoo felt uncomfortable toward each other because the way sungwoo looked at him was not kind.
 there was apparent distrust in his eyes.
“hmm…”while the king was puffing out smoke, checking sungwoo’s moods, sungwoo opened his mouth first.
“are you guys monsters?”that’s the reason why sungwoo was wary of them.
 even though they helped jisu, there was no change in the fact that they were monsters.
 and all the monsters he encountered so far existed to kill humans.
 it has not yet been proven that there may be exceptions.
“monster…”the king pouted and spewed smoke over his head.
then, he slowly opened his mouth.
“you will have no other choice but to think so,” said the king, apparently rejecting sungwoo’s negative perceptions of the monsters.
“you are denying that? you are a field boss monster.
”“well, i would not deny that, but i just want to reject it.
 we were born as monsters and came to this point based on our lack of free will.
 only now we can think straight…”sungwoo thought, ‘these guys don’t want to be called a monster? they are different from other monsters.
’the king said that they were not weretigers, but a race called “tigers.
”in the beginning, they were different monsters, but they evolved repeatedly to obtain their present form.
the king continued, “after waging a lot of bloody struggles, our race has come to occupy mt.
 taebaek.
 struggle guild in chuncheon attacked us several times for some reason, but we defeated them all.
”

 