\section{chapter 309}

the china server could make sungwoo's allies grow tremendously or give them a tremendous item, or something else.
 




sungwoo stood up and said, "chairman love, i think i have to go back first.
"chairman love nodded with an anxious face.
 "i was so stressed when i thought about how to align with you to stop the dragon, but i'm so shocked to know you are waging a war soon.
 i just want to keep my fingers crossed that the korean server will win the war…'"well, if we receive more items and resources from the chinese server, we may find a way to confront the dragon.
""yeah, that would be the best option…"chairman love stood up with a long sigh.
"i want to help you as an ally, but please understand that our situation is not good.
 besides, we have to watch out for our surrounding servers, so we cannot send you troops.
""of course, i understand.
"in fact, it was only natural that sungwoo had no choice but to understand chairman love's miserable situation at the moment because it was none other than sungwoo who dealt a fatal blow to the wpu forces.
 however, given the financial situation of the wpu and the competence of the hearst workshop, it was clear that they would be able to restore their damages.
"i'll get back to you.
""yes, please.
" 
-the 'return portal' to the 'world tree' has opened.
sungwoo immediately opened the portal.
 then, sungwoo's party returned to the korean server with two airships.
***when sungwoo returned to the world tree from the us server, the world tree camp was busier than ever.
"oh, welcome back!"with kyungsoo greeting sungwoo's party, seven airships that were successfully repaired were seen floating in the sky.
gooooooooooo-a total of nine airships including the two that sungwoo brought from the us server would make a formidable fleet larger than admiral baker's fleet.
 under the magnificent ceiling covered by the world tree, nine airships were floating like a mobile.
 suwon's sky was completely obscured by their shadows.
doodoodoodoo!helicopters moved between the ground and the airships, carrying the crews and supplies.
in addition, there was a line of trucks on the road, which were endlessly transporting various weapons toward the castle wall.
when the hangar doors opened, dozens of flying weapons that blacksmiths made so far began to operate.

"as we have practiced so far, everyone should be positioned in their own place.
"then inho approached sungwoo and said, "except for the flight crew, all 105 fighters, divided into several teams, are in an emergency standby right now.
"a well-armed force lined up behind his back.
 they were obviously done preparing for the upcoming fight.
"now that you have joined us, sungwoo, i think the world tree camp has mobilized the biggest force ever.
"as a matter of fact, the world tree camp has been preparing for this moment for a long time.
"our preparations are over.
 what can we do now?"sungwoo opened his mouth while looking around.
"send a message to the server giants of korea.
"the korean server giants, such as the liberation guild, the hwarang guild, the uijeongbu emergency council, and the hunter company, were already preparing to participate in the war.
they had promised to fight with the necromancer even when the monsters came down from the north korean server.
 in fact, they were following sungwoo.
sungwoo sent a message to them.
"we won't end up just defending in this war, so tell them to prepare an overseas expedition before gathering in one place.
"right now, the korean server was fully determined to wage war after they got sungwoo's urgent message about the general mobilization.
"the hwarang guild and hunter company have responded to our message favorably.
 they say they are already on standby!"just like the koreans used to do all the time, they began to unite and prepare to fight when they were faced with the outsiders' threat while overriding their conflicting interests.
"the liberation guild and their subsidiary forces in the metropolitan area are also gathering in yeongdeungpo!""we have got a message from the uijeongbu emergency council.
 they have been engaged in exchanges with one heart society in paju, but both of them signaled they would join in our fight.
 they say they have a total force of 550.
"every server in the local areas sent the world tree camp a message about their participation, so a "communication center" was urgently established under the "department of general affairs" to handle the messages coming in from all the servers.
 they maintained multiple cell phones to monitor the movements of the communities and broadcast stations while collecting and reporting all information.
"apart from the big server groups, small and medium-sized organizations across the country have been in contact with us, offering to support our efforts in the upcoming war against the chinese server.
""there are quite a few people who want to offer gold and items as well as troops.
"those who were content with surviving on their own offered to join the coalition, but those who were afraid to do so offered support in other ways.
"wow, it looks like our people were upset because of the china server's declaration of war.
 all of a sudden, they are coming together and offering to help us!" hanho shouted.
 like hanho said, the angry players on the korean server were full of determination to fight against the chinese server's declaration of war.
and, of course, the central figure of the korean server who would unite all these groups under his command was the necromancer.
 

such a fact could be easily found out when people accessed the community bulletins.
[1,541] why are we looking for the necromancer in this situation?-author: patriotic fighter │ hit: 27,456why are we korean server players thinking of the necromancer when the chinese server bastards declared a war against the korean server? the answer is simple.
 it's because our great necromancer pulled out all the tongues of all the foreign server players who were trying to swallow up the korean peninsula.
 can he do the same thing this time? absolutely! i totally agree.
 necromancer, please do whatever you want.
 if you are pushed back by the chinese players while fighting them, let me donate my bones to you! hey, guys, let's advance to china on this occasion![comments: 55]- bowman a: i'm going to join them and fight right away.
 if i die in a fight, please use my bones, too!jinah kim: i'm going to join, too.
 use my bones too! ˪ mincheol kim our family members have had strong builds from generation to generation.
 so, use our bones, too!˪ park dragon: if i die, use me as a corpse explosion.
 ˪ sokcho survivor: he has protected us several times.
 i would like to donate my corpse, too! please use my body!˪ cheer for you! young guys in korea! you are the future of this land.
 we seniors want to take a rest.
 so, be prepared to go and fight.
 don't forget your fighting spirit!their outpouring of support for the necromancer was fully reflected in the "server master" elections in less than three hours of the elections.
- congratulations! 'kor-157' was elected as the 1st 'server master' of the korean server.
 from now on, you can select various policies on behalf of the server.
fortunately, sungwoo was elected the server master with a whopping 78.
4 votes to represent the korean server.


 