\section{chapter 452}

the sky over the amazon rainforest or the 'green hell' was being covered with red flames and black smoke.





"they're coming back! stand ready to fire!"as soon as the quest started, a portal to the world tree camp opened, and the demon king's army advanced towards it.
"first row, lift your shields!""wizard squad! prepare your defense magic!"but lots of players who were assigned to the 'defense route' were stopping the monsters from coming by blocking the entrance of the portal.
 "ready! fire magic at the same time as the fleet begins firing!""if you run out of mana, use the supplied mana potion!"the number of players that the world tree camp gathered while occupying many servers around the world was huge, indeed.
 no wonder over 100,000 players who survived the long hell gathered.
"fire!"backed up by huge supplies, an unprecedentedly huge army was defending against the demon king's attack.
 no matter how strong they were, the demon king's army could not break through their blockade.
 bang! bang! bang!they were done making three waves of fierce attacks, and the dead bodies of all kinds of monsters that turned charcoal were strewn everywhere in the amazonian rainforest.
 kheeeeeeeeeeeh!but the enemies did not stop.
 they crawled out from all over the black giant castle, trampling on the corpses of their own fellows, then marched forward fiercely.
"they're coming back! stand ready!""uh?"
at that moment, however, everything went into a lull in an instant.
whooooo-follow new episodes on the lightnovelworld.
com platform.
it was as if god was looking down at this fighting, then pressed the pause button for the whole world.
 more precisely, since the demon king's army stopped advancing, the players of the world tree camp also stopped resisting.
"what the heck is this?""they have stopped!"soon they knew why the enemy stopped advancing.
 "captain! look at the sky in the northwestern area!"something was floating between the red clouds in the sky over the demon king's castle.
 when inho checked it with a telescope item, there were four people.
standing tall in the sky, they were looking down this way.
"the demon king has arrived.
 damn it!"finally, the demon king and his minions returned to the amazon.
those assigned to the defense route were faced with the worst possible situation where they confronted the demon king without sungwoo's presence.
"send a radio to our people in the attack route right now and tell them that the demon king has appeared!" inho said, turning to look at the crew in charge of firearms.
 "in case the demon king is targeting our fleet, have some cannons ready to fire! they will try to confront us cunningly, so deploy the snipers on the deck!""understood!"
inho remembered the time when he lost two airships in an instant in the 'hall of angels'.
'no matter how hard we tried, we could not defend against them without sungwoo's help.
'one of the airships was crushed by the enemy's lightning attack, and the other melted with their single strike.
 the destruction of the two airships was the most terrifying scene for their crew.
 'as a matter of fact, the enemy's lighting was not a difficult skill.
 in other words, he could keep using it.
 if that's the case, it's a matter of time we're going to be annihilated.
'based on the enemy's power, there was a high possibility that as many as 13 airships now defending the sky would not withstand their attack for long.
 at that moment hearst entered the control room and said, "captain, is the demon king here?"new novel chapters are published on lightnovelworld.
com"that's right.
"hearst nodded his head with a grim expression, touching his beard.
"what do you think? do you think they will attack us?"it was the observation officer who answered the question instead.
"the demon king is coming this way!"inho quickly turned his head and picked up the telescope, but hearst snorted at his reply.
 "really? looks like they're trying to clean the yard first, not the house.
 alright.
 let me open the 'gift' i prepared for them.
""master hearst, i wish you all the best.
 we can't stop them with only cannons.
""even if you don't wish me luck, i can make it work, so don't worry and take care of the control tower!"hearst hurried out to the deck.
 then he made a call to somebody with a radio item.
"ah, this is master hearst.
 get everything ready.
 it's time to run the machine.
"cheeeeeeeee-then some mechanical devices installed on all the airships started working.
"okay, that's fine.
 bring it on!"hearst took out the sunglasses he prepared beforehand and put on a cigar in his mouth.
whoooooooo-suddenly, a hot wind containing moisture blew in.
 the air current changed.
 a tornado was generated by the demon king nearby.
 and then a blue flash of light started flashing over his head.
then the flash of light became dozens of strands, spewing out to sungwoo's allies.
 for more, visit lightnovelworld.
comcountless lightning bolts fell on the airship at the forefront of the world tree fleet.
the airship shook violently up and down, left and right, but it was not crushed like it was when hit in the hall of angels.
an electric current flowed through the coil connected to the airship and ran down to the lower deck of the airship, to which something was connected.
 it was a very long cable.
cheeeeeeeeeee-a huge amount of electric current came down the cable.
 all cables were connected to 'mana batteries' installed on the ground.


"success! a lot of mana is being supplied! full charge!" shouted the blacksmith who was overseeing the mana battery.
 the gauge on the instrument panel he was looking at quickly filled up.
 at that moment hearst on the deck lifted the radio and shouted.
"supply that mana to all locations immediately and use all weapons!"the weapons that were receiving electricity and mana from the ground battery center and airships through the cables opened fire.
 like machine gun firing, iron balls were fired by the power of the electric current, and magic shells were also activated by the power of mana.
"wow!"that wasn't all.
 they instantly created a huge dome-shaped shield on the ground.
of course, it was turned off again sometime later, but the process of the enemy's attack being transformed into the shield of sungwoo's allies was a huge turnaround in the fighting.
 furthermore, if that's the case, it meant that the demon king's lightning attack was nipped in the bud.
"hahaha!"watching the fighting scenes, hearst made a hearty laugh.
 "do you think we're going to suffer the same damage again? if you don't review your mistake and fix it, you are not a real engineer!"hearst already saw the airships were savagely crushed by the enemy's attack, so he double-checked the problems and fixed them.
 that's why he hastily built a system that absorbed the enemy's powerful electric current attack, then utilized its energy reversely.
of course, if the demon king intended to attack the fleet, by all means, he would launch a variety of attacks other than lightning magic.
 sungwoo's allies would not be able to withstand such an attack for long.
however, the world tree fleet overcame the risk of sinking without even counterattacking at all.
the source of this content is lightnov­elworld.
c‌om"alright.
 let me bring it on.
 i'll blow their heads off!" hearst shouted.
if they could hold out a little longer, soon the necromancer in the demon king's castle would arrive in time to confront him.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 