\section{chapter 274}






 the newborn dragon rolled on the ground with his subordinate spirit, the chicken skeleton, for several minutes.
as if he suddenly realized that he was hungry, the baby dragon put his snout into the baby foodhe had just refused only a little while ago and started to eat it quickly.
“what the heck! he’s eating it very well!”in the meantime, he resurrected any food with bones as a skeleton.
 did he do it instinctively?by the time he finished the first meal in his life, chicken skeletons, crucian carp skeletons, etc.
 gathered around him.
rattle- rattle-they were awkwardly dancing together, which seemed to reflect the unknown spirit world of the baby dragon.
“what the heck are they? is it something like witchcraft?”“i guess so.
 very strange.
”a dancing chicken skeleton? it was bizarre just like sungwoo’s undead army but in a different sense.
krrrrrrrrrrrr-after he finished eating, the baby dragon stretched comfortably then started to hop to sungwoo.
he waddled to sungwoo as if he could not yet walk straight.
 then, he raised his head and looked at sungwoo’s face.
 his bright yellow eyes slowly blinked.
“why? what do you want?” sungwoo asked.
he seemed to want something.
krrrrrrrrrng- krrrrrrrrrrng-but when sungwoo didn’t respond, the baby dragon cried out sadly, it rubbed his head against sungwoo’s ankle.
“oh, he is now recognizing his owner.
 but why is he crying?”“he seems to want you to hug him.
”
since sungwoo earned the ‘credentials’ by satisfying the 5,000 days, he naturally formed a master-servant relationship with the baby dragon even without building close ties with the baby dragon.
so, when sungwoo touched him, his profile appeared.
[creature profile]– name: –-race: black dragon-grade: hatchling (level 1)-owner: sungwoo yu (kor-157)-condition: very healthyas the black scales suggested, he was a “black dragon.
” in general fantasy, a dragon’s available abilities were different depending on the color of their bodies, but this black dragon used sungwoo’s skills by duplicating them.
‘man, he bothers me.
’sungwoo looked down at the black dragon rather bitterly.
crouching next to sungwoo’s left foot, he yawned.
‘i’ve got to treat him like raising a baby.
’sungwoo thought getting a dragon would boost his power tremendously.
 and it seemed to be true to some extent because as soon as he was born, the baby dragon made a chicken and a crucian carp his subordinate spirits.
however, sungwoo never expected that this naughty baby monster would follow him wherever he went.
“by the way, have you thought about naming him, sungwoo?” hanho asked.
“not really.
”“man, don’t you think you are too careless? a cute monster looking like you is acting charming like that.
 how come you have never thought of getting him a name while you were meeting the credentials for 5,000 days?”“then would you like to give him a name?”a hidden quest was given to hanho.
the boy dragon fell asleep under sungwoo’s feet, so sungwoo placed him in the cradle covered with the branches of the world tree.

“he’s a really lovely guy,” said heyon.
she gently rubbed the forehead of the little monster sleeping on the cradle with her index finger.
“well, gust was really cute when he was a baby like him, but he grew up fast.
”“really? i hope this guy can grow up quickly.
”“but when he grows up fully, he’s going to give you another headache.
”when sungwoo made a puzzled expression, she continued, “if gust grew up, he would fight on my behalf but that made me worried sometimes.
 i feel secure because of him, but at the same time, i’m always nervous.
”as someone who controlled the undead, sungwoo could not understand her feelings.
“i’m always worried gust might be hurt, so please take good care of the dragon.
 he’s going to be your special family member.
”even after she returned, sungwoo was sitting beside the baby dragon.
of course, he did not feel the same way as heyon.
 he just hoped that the baby dragon could grow up fast and play his role.
since he was still a baby, he slept for quite some time.
 he woke up almost after 13 hours then began to bite the chicken skeleton again.
rattle! rattle!while watching the scene of him torturing the chicken skeleton, sungwoo felt the chicken skeleton was struggling in pain.
 if the skeleton could speak, he might as well shout, ‘just kill me!’its wing bones were filled with holes because the baby dragon kept chewing them, but the skeleton was still in good shape, compared to the crucian skeleton.
 the crucian carp skeleton was already been cut into thirds, buried in one corner of the nest.
kreee-at that moment, he became interested in something else.
 seizing that moment, the chicken skeleton escaped from his tight grip and fled to the corner of the nest.
kree- kreeeeeee-“what’s the matter?’his pupils were enlarged.
 his gaze turned to the small window.
“window?”a mountain was seen outside the window.
 it seemed that the birds flying on the tree caught his attention, but he wasn’t just interested.
-‘dragon fear’ has been triggered.
* it stiffens creatures of low level and low intelligence.
at that moment, the sparrows hanging from the tree fell all of a sudden.
then, he tilted his head, not knowing what he just did.
 but sungwoo was satisfied after watching the baby dragon’s remarkable performance.
“man, he’s useful.
”on the first day of his birth, the baby dragon continued to show off his amazing skills.
***“the prisoner we brought from pyongyang died.
”“died?”minsok knocked him on the head hard enough to make him pass out but not die.
he detained the prisoner for interrogation after sungwoo took care of the baby dragon but something unexpected like this happened.
“i think he committed suicide.
 i’m not sure, but it looks like he ingested a poison hidden in his body.
 it seems that he took the extreme action to stop any intelligence leakage just like the spies from last time.
”but it wasn’t a total failure.
sungwoo went to the jail, escorted by kyongsu.
 jisu and hanho were already there.
“he looks chinese when i checked his belongings.
”“let me take a look.
”sungwoo confirmed the prisoner’s body, and he infused mana into the cold body.
‘get up.
’-you can check the ‘memory fragments’ of the dead.
as expected, fragments of his memory appeared.
‘obviously, this guy had some important information.
’

soon, the video played.
whoooooooooooooo-it was the middle of a barren snowy field.
‘where is it? to say the least, this place is not on the korean server.
’three men, including the owner of the memory fragments, were walking through the snow.
soon, they entered the coniferous forest.
 it wasn’t a mountain but a forest on the plains.
“man, i never thought i would come to the middle of siberia that i used to hear about.
 damn it! what the heck are they doing here?”sungwoo found out the location of this place after checking out the man’s complaint.
it was siberia.
the owner of the memory fragments replied, “they are hunters.
”“you mean hunting? what are they hunting?”“just anything.
”there was a sense of awe in his answer.
at that moment, sungwoo realized that the most important element in his memory fragments was the ‘hunters.
’“by the way, is the emperor going beyond the continent and trying to embrace these tribes in the periphery?”“no, the emperor has no time to care about them.
 he’s on the verge of unifying the whole continent by taking over server 2…”emperor? sungwoo now discovered who they belonged to.
 these were the subordinates of the man who claimed to be the emperor of china-1 server.
the owner of the memory fragments pulled a thermos from his waist.
 after quenching his thirst for a moment, he continued, “we have launched this operation at gen.
 singh’s order.
 the general instructed us to mobilize the barbarian tribes here to subdue the korean server.
”“i see.
 he wants to use the enemies to kill our enemies, right?”“yes, that’s why we want to go down to north korea and negotiate with the monster king who occupied it, as well as the hunters on the russian server.
 instead of fighting the korean server by ourselves, we can mobilize them to smash the korean server.
”

 