\section{chapter 276}






 the next morning, an unwelcome visitor visited the world tree camp.
“pardon? who has visited here?”while preparing breakfast after washing his face, kyongsu sprang to his feet.
he heard that someone appeared at the invisible border and wanted to meet the necromancer.
upon hearing it, he declared an emergency and summoned all of the troops.
“are you sure the visitors are foreigners?”the chief of the 1st guard team nodded at his question.
“yes.
 they are a black man and a white woman.
 they said they came from the american server.
”“america….
”“i’m going to have the ‘iron mace of lightning’ ready for firing in case of contingencies.
 like you instructed, our ‘watch squad’ is closely monitoring the area around the invisible border.
”“got it!”kyongsu greeted the guests outside the invisible border with a large number of guards on standby.
 the guests were only two.
 like the chief guard said, there was one black man and a white woman.
“i hear you are from the american server, right?”“that’s right.
”when he asked, the tall black man nodded.
 wearing a black suit, he looked like a wizard because he held a long wand in one hand.

the white woman standing next to him also wore a1 suit and had a shield and sword on her back.
“more precisely, we’re from the american-1 server.
 it covers the eastern area.
”there seemed to be no hostility in their attitude.
 however, not knowing what kind of intention they had, kyongsu was still on alert.
‘american server? if so, it means that they have crossed the pacific ocean to come here.
 how and why?’neighboring countries like china and japan could mount an attack against korea, but it would not be easy for the american server to attack korea.
even if they could, why would they bother to come all the way here by taking such an enormous risk?‘they must be very busy establishing their own power and constructing their community within their own server.
 nonetheless, they must have some reason if they have come here from such a faraway place…’as a result, kyongsu mobilized a surveillance team to thoroughly monitor the whole area around the village.
the black man continued, “we landed on a nearby shore three days ago.
 we have already known about the amazing performance of the world tree camp through the ‘world message’ and ‘the official channel’ broadcasts, so we have come here to meet you and talk with you about lots of things.
”the black man handed a cane to the white woman standing next to him and took a wallet out of his pocket.
 he took out a business card from the wallet.
“i’m jonathan cage, head of the 1st foreign affairs team, belonging to the w·p·u, the strongest force of the american-1 server.
”his organization was called washington players union and jonathan cage’s title were printed on the business card.
kyongsu couldn’t hide his embarrassed expression because he didn’t even think he would exchange business cards with somebody in this situation.
“oh, i am the general affairs manager of the world tree camp.
”“nice to meet you.
”
kyongsu held his huge hand.
 jonathan made a nice smile then cut to the chase.
“can i meet necromancer by any chance?”as expected, the purpose of their visit was to meet the necromancer.
“i’m sorry, but i can’t let you meet him now.
”“is he not here?”kyongsu shook his head and said, “he’s taking care of some important work inside.
 it looks like it will take some time.
 can you wait until then? i’m sorry, but i don’t think i can escort you inside the invisible border because of security concerns.
”in fact, the necromancer was not in the village at the moment.
 but he could not reveal it to these outside visitors.
‘if these guys have come here for the purpose of aggression, they would not miss this moment when sungwoo is not here.
’jonathan made eye contact with the white woman.
 the two nodded together as if they agreed on something.
“okay.
 if so, we will be waiting for him nearby.
 can i send you contact once every 12 hours?”“sure.
 by the way, what business has brought you here? let me tip the necromancer off in advance.
”jonathan’s answer was a bigger problem than he thought.
“we would like to discuss with him about the need for an international unity organization to achieve reunification and peace in the ruined world.
 so, we would like to invite the hero of the korean server with the greatest reputation in the world.
 we would like to discuss it with him.
”“i see.
 i understand your point.
 let me convey your message.
”international unity organization? if so, is it like the united nations before the world was ruined?‘well, it’s not easy to build such an organization.
’kyongsu was skeptical about such a grand scheme.
 as long as the system exists, how could it be possible? the system always wants a rough story.
 therefore, it will nip the foundation stone for peace in the bud.
he also wondered if w·p·u, the strongest force of the american server, was really moving for peace.
 he could not take the black man’s words at face value.
 rather it was most likely lip service.
‘it is still too early for them to cry out for peace.
’peace is the ideal they can think of when they have no problems at all.
 otherwise, it is just politics or business.
‘these guys are either predators or businessmen.
 they are being drawn to the world tree.
’***at that moment, sungwoo was on a helicopter heading for seoul.
 early this morning, he accepted the liberation guild’s request for help.
“they appeared around 8 pm yesterday.
”minhum continued to brief sungwoo inside the helicopter.
 he gave sungwoo an overall briefing, but he kept emphasizing some important points again.
“after a group of white players who appeared to be the slavic tribe unilaterally slaughtered 50 guards at the northern border post in eunpyeong-gu, they brazenly demanded negotiation with us.
”“negotiation?”“well, they were saying negotiation, but it’s clear they wanted to subdue us.
 but our commander did not accept their request, and in the end….
”minhum bit his lower lip and continued, “i heard that after he dispatched me to you, the crusader team led by him got frozen near seoul station after confronting them directly.
 i guess they were hit by massive freezing magic.
”“if they got frozen like that, are they alive or dead right now?”sungwoo couldn’t be sure of their death just because they were frozen because there were a lot of freezing-type skills that gave only ‘status abnormality’ to the target without damaging them.
“i don’t know yet.
 that’s why i’m so crazy.
 so, i contacted you right away to go there as soon as possible.
 i’m really sorry.
”

then, minhum added, holding back his frustration, “anyway, right after that, they planted in mt.
 namsan, but the temperature around seoul has dropped significantly since then.
”“temperature? is a certain area getting colder?”“yes.
 the wide-area surveillance team couldn’t even confirm what it was.
 according to them, mt.
 namsan has completely changed like everest, so none of them can approach it.
”“got it.
”after hearing the briefing, sungwoo got a sense of who the unknown attackers were.
‘the russian hunters are here.
”the siberian hunter or the no.
 1 in the russian server came to the korean peninsula, instigated by the china-1 server.
“uh, it’s really cold suddenly, isn’t it?”like hanho said, the temperature began to drop considerably after the siberian hunter entered the sky over seoul.
“did you turn off the heater? it’s freezing!”the korean peninsula was also entering midwinter, but it was a much stronger cold wave.
“when we measured the temperature near mt.
 namsan, it dropped down to -25 degrees celsius and is still going down.
 we don’t know how much it will go down.
”“oh, my god! 25 degrees below zero? this is crazy.
 it’s like siberia, isn’t it? ooops, my feet are getting cold…”“when you arrive at yeongdeungpo station, they will give you thick winter clothes and hot packs.
”groaning- groaning-at that moment, the black dragon next to sungwoo whined.
 even though he was sleeping on sungwoo’s lap while hugging the chicken skeleton, he began to feel cold.


 