\section{chapter 179}






 10 seconds was a long time.
 in particular, it was enough time for sungwoo to subdue an opponent who could not move at all.
kaaaaaak! kaaaaakaa-wyvern alpha male was a huge creature, so sungwoo couldn’t end his life within ten seconds.
 in that respect, jisu played a big role.
she knew how to collapse the huge body.
 in other words, she knew exactly how to kill this monster, especially which muscles and tendons she had to cut to destroy him.
it was her insight.
 as a physical education major, she has cut countless monsters until now in the battles.
 using her rich fighting experiences and insight, she could make an unusual judgment in killing the boss monster.
puck!the blade of her sword pierced his thick scales and got stuck into his tough flesh to cut his tendons.
“done! now, he can’t fly or walk,” jisu said.
so, he was still breathing after 10 seconds passed, but he couldn’t fly anymore.
10 seconds gave sungwoo’s party another golden chance for attack.
 minsok ended his windpipe by swinging the ‘ownerless sword’ in his hand.
-you have earned 4,324,500 gold by hunting the boss monster ‘wyvern alpha male’.
-special rewards will be given by hunting the boss monster.
 (secret store coupon)-you have acquired the title ‘conqueror of sky’.
* increased agility level (+2)* increased stamina (+2)* increased physical defense (+10%)
* increased wind resistance (+20%)the players obtained a considerable amount of gold even though it was sungwoo and jisu who hunted wyvern alpha male.
 given the amount of gold, this fight was more difficult than the hell moving armor.
sungwoo obtained a ‘secret store coupon’, so he thought he had to set a date for shopping for items in the future.
-time remaining until you are qualified: 2,733 dayssungwoo reduced the time by 700 days by hunting wyvern alpha male, which meant if he could hunt four more monsters like it, he could finally fulfill the requirements for the qualifications.
that’s not the only reward sungwoo received.
‘something inside me is getting hot again.
’he felt that ‘hot’ feeling was rather familiar.
 so, he pulled something out of pocket.
 it was a card.
woooooooong-the “b-class exp card” he obtained after hunting the hell-moving armor was glowing green.
‘it’s a level-up card.
’as he used it once before, the card reminded sungwoo when he could level up by using it.
-you have reached the level of exp with which you can level up.
 would you like to use a coupon?of course, sungwoo used the coupon.
-you have leveled up.
 (lv.
 21)he chose the ‘skill’ item on the level-up card, and the maximum number of his subordinate spirits also increased by 3.
however, he didn’t feel like it was a huge gain like before.
 since he could regenerate the undead after obtaining the grim reaper, he didn’t feel any regret about the small increase in number this time.
 of course, if he could deal with more undead, he would gain more power, so he was satisfied with the small increase in his subordinate spirits.

“it looks like the dogfighting in the sky is almost at an end,” said jisu, wiping her sword.
since they killed wyvern alpha male, it was a matter of time before they got rid of the other wyverns under him.
 even if they were numerically superior to bone wyverns, they could not beat the undead because they kept reviving even after being killed.
thus, the sky of the korean server was completely conquered by sungwoo.
***it wasn’t just sungwoo that was growing.
since sungwoo hunted a lot of mighty monsters, the world tree was supplied with excellent quality nutrients.
wooooooooong! wooooooooooong!the world tree shined, then started to grow in an instant.
 it grew as high as a three-story building at once.
-the world tree has reached the “2nd stage of growth”.
-your stats have increased as you are “linked” to the world tree.
* increased muscle strength (+1)the village players also couldn’t shut their mouths, watching the dramatic scene.
 since the world tree was growing so fast, their eyes could hardly catch up with its growth.
“oh, my god!”“growing as high as that at once?”“who knows if it can reach the clouds soon?”it wasn’t just the size of the tree that changed.
 the rays of light spreading from the roots to the leaves turned a little cloudy.
it was hard to notice it without a closer look, but it seemed to suggest some kind of change.
-the world tree is forming some ‘propensity’ thanks to your influence.
“propensity?”sungwoo was not sure whether it would be positive for the world tree to be affected by the necromancer, but he could not stop it anyway.
-the world tree gains a new power.
 * the miracle of the god tree forms a powerful ‘invisible world’ in the whole area.
 this can act as a strong shield and deter unwanted people from entering.
-the world tree gains a new power.
 * whenever “the one who is blessed by the world tree” takes another life, their souls are bound by the world tree.
as the world tree entered the “second stage of growth,” it began to have special powers like this.
 first of all, it had a defensive ability called , which was fortunate for sungwoo.
although the world tree was always defended by sungwoo and others, it was open to an unexpected outside attack anytime.
sungwoo thought, ‘if terror kim had thrown a bomb in a surprise attack, the world tree might have been blown away.
’what would happen if he fired a flying weapon such as the ‘iron mace of lightning’ from a distance? sungwoo had been nervous because there was no way he could prevent an outsider’s attack that would devastate the whole area.
however, with the  in hand, he could prevent not only powerful attacks from a distance but also the enemy’s secret infiltration.
 only now could he feel relaxed.
‘by the way, who the hell is ?’sungwoo could not figure out the use for .
to make the best-educated guess he could, he felt that he might save the “soul” consumed in using his skills when he obtained the power of “anubis.
”‘then, i can use anubis with maximum efficiency.
’generally speaking, when he deactivates the condition of anubis, the remaining souls are not saved anywhere.
 that’s why he had to save souls in advance before hunting the wyverns.


otherwise, he could not avoid the lack of firepower at the beginning of the battle, so he had to waste considerable time to accumulate as many souls as he needed.
however, if he could be supplied with the necessary souls without going through that process, it would be the best option for him.
‘well, the world tree can consume even souls? man, i’m getting a bit nervous.
’it seemed that the world tree was getting more and more estranged from its classic image as something called the tree of life.
“anyway, the world tree is growing very strong.
”but there wasn’t only good news for sungwoo.
-the angel camp has increased the bounty on your head.
* angel camp’s bounty: 70,000,000 gold-demon camp has increased the bounty on your head upwards.
* demon camp’s bounty: 25,000,000 gold-as your influence grows, the bounty quest is upgraded from ‘server quest’ to ‘world quest’.
 from now on, players around the world will be targeting your life.
“what the heck is this?” sungwoo asked, embarrassed.
“sungwoo, you are now known around the world!”it was the moment when the name of the korean server, necromancer, and the existence of the third camp became known on the world stage.
since there were no signs of a solution in the korean server, it seemed that the absolute race came up with a bigger alternative.
 in other words, they decided to throw the necromancer on the world stage.
“but if you are the target of world players, i guess the chinese server will be crazy about killing you.
”like hanho said, the “china-2 server” players, who had been defeated by the necromancer, would welcome this quest with open hands because they knew they would gain an enormous reward by killing the necromancer, their cherished enemy.


 