\section{chapter 315}

sungwoo deployed the troops as they agreed at the meeting in advance.
 he had to deploy the troops first because once they did, the chinese server would respond anyway, no matter which strategy he used.





so, he decided to choose an extreme option.
 "are you sure you're going to be okay when you go there alone? don't you need someone to assist you?" junghoon asked anxiously, but sungwoo shook his head.
"i should have nobody around me if i want to carry out my plan.
"sungwoo planned to have nobody help him.
 at that moment, minhum shouted, "the chinese server has started deploying their troops!"sungwoo and junghoon turned their heads at minhum.
a screen was pulled down on one side of the conference room.
 the official channel was broadcasting the situation of the war.
soon, the enemies began to be summoned near suwon, which made the situation pretty grim for sungwoo and his allies.
"damn, those bastards were seen roaming around on seoul streets in droves, but there are much more here!" "uh, they are a huge force.
 they have dozens of flying weapons, and general xing led them in person! besides, there's also admiral baker's fleet out there," kyungsoo said.
inho added, "it's clear they are determined to break the invisible barriers and castle walls.
 but while we're holding out here, i think sungwoo and his undead army will appear like a miracle at the crucial moment, right?"inho cracked a joke like that, but he hardened his face.
it was certain that there would be a large-scale war beyond imagination, and that the suwon village that the world tree camp put a lot of effort into building until now was in danger.
 so, they had no choice but to be worried deep down.
and now they had only one option left.
-5th choice (korean server)actually, there was no other choice here because the choices of the other two battlefields were already made.
 -battlefield: busansungwoo clicked on busan and put only one name, namely his name, in the list of troops.
 
then, he held mir in his arms.
a portal will open soon and take sungwoo to busan.
"sungwoo, do you have anything to say before you leave for busan? i think this is a crucial moment for you…" junghoon asked right before the portal opened.
 of course, sungwoo's response to his question would carry a lot of significance.
 as the spiritual leader of the korean server, he could deliver a speech that would satisfy the morale of many leaders gathered here, or he could leave his last will since he might not see them again.
 it was up to sungwoo which way he would choose.
however, sungwoo had never thought about his will.
"i'm going to take over beijing soon.
 then, we're going to fight on one battlefield.
 see you then.
"as soon as he said that, a blue light shrouded him.
-troop deployment has begun.
 "uhm, i've already arrived.
"the next moment, sungwoo was standing somewhere in downtown busan.
-the list of troop deployment has been sent to your opponent.
'will they be scared to see the list with only one man or will they like it?'when he raised his head, the drone of the official channel was filming sungwoo.
 in other words, this scene was being broadcast all over the world right now.
looking at the man standing alone on this huge battlefield, how would the players in the world feel?'most likely they are sneering at me.
'even if he showed his fantastic performance in the fight several times, the general public was supposed to have a negative perception of somebody's abnormal behavior.
 it was natural that sungwoo's victory was being denied by them at this moment.

-sixth choice (chinese server)-battlefield: busantheir final troop deployment began.
 they would pull out a card to capture sungwoo as they intended.
 -the opponent's list has been transmitted to you.
soon, numerous nicknames began to appear before his eyes.
 there were a total of 1,101.
however, it was impossible for him to size up the exact strength of the enemies, even though he could figure out the total number of their troops.
 sungwoo opened his mobile phone and turned on the official channel.
 the broadcast screen was projecting the troops of the chinese server somewhere in busan.
'what a nice selection!'they were a mix of people to capture the necromancer, such as snipers, assassins, freeze-type wizards, priests, paladins, etc.
 they were obviously elite soldiers to confront sungwoo's legion of death.
'as expected, i noticed this guy here.
'the siberian demon druid, the russian tsar, was standing at the front of the enemy camp.
while looking at the drone, he pretended to draw his neck, muttering something.
it seemed that he was saying he would catch the necromancer and chew him alive.
 and his eyes were burning with anger.
-the war begins 12 hours from now.
* caution! pk is not possible during this time.
 when you attack the opponent, you are announced 'automatically dead.
' their troop deployment was over, but the war didn't start right away.
 they were given a waiting time of 12 hours.
 it was enough for them to prepare and brush up on their strategy.
sungwoo was also preparing for the best possible operation.
he left the street and entered a building.
 and he sat down on the sofa.
"summon!"when he muttered like that, a skeleton began to form in the air.
"crackle! master? are you at it again?"victor was quick to notice his master's feelings, so he quickly grasped the situation.
 this was an absolutely bad situation for him.
"this time, please finish it quickly.
 perfect!"having said that, victor disappeared like smoke.
"summon!.
"and he appeared again.
"crackle!"sungwoo was going to keep summoning victor until he acquired the skill he wanted.
***eleven hours and 59 minutes have passed since their troop deployment was completed.
the official channel's broadcast screen alternately illuminated seoul, suwon, and busan.
 however, with only one minute to go before the war, it was showing only busan.
the system also knew it was the most important battlefield.
".
.
.
"there was lonely silence in reporter ahn's studio.
 it was definitely different than usual.
 since the fate of the korean server was at stake, he could not afford to create a lively and interesting atmosphere, no matter how good he was at it.
gulp! gulp!

reporter ahn hurriedly swallowed water.
 still, his mouth was dry.
 finally, he opened his mouth with difficulty.
"now, we have only one minute left.
 exactly one minute later the necromancer is going to fight 1,1101 fighters of the chinese server in busan.
""these 1,101 players are not ordinary warriors.
 it seems that the chinese server has selected the elites very carefully, right?"reporter ahn nodded, with his face blushing in excitement.
"of course.
 as i said earlier, you can only regard them as a special force mobilized to capture the necromancer.
""special forces to capture the necromancer?""yes, that's correct.
 priests, freeze-type wizards, and so on, who have succeeded in driving the necromancer into a corner even a little bit have gathered.
 in particular, those snipers will persistently aim at the necromancer's heart, so they can make it hard for him to move comfortably…"at that moment, some letters appeared over the sky of busan.
reporter ahn stopped talking and looked at the screen.
-the war has begun!"alright, the war has just begun!""whew! finally, we're seeing the start of the war!" "i wonder what kind of strategy the necromancer is going to use…""uh.
.
.
?"as soon as the war started, reporter ahn could not finish his words.
it's because the first scene being shown through the official channel was so intense.
kugugugugugu―

 