\section{chapter 456}

more precisely, the light was strange.
 she couldn't figure out where the light came from, but there were as many as four shadows of hers in all directions.





at that moment some unpleasant voice was heard.
"alright.
 you know what that means, right? it means you're going to be torn apart!"suddenly jisu found someone standing in front of her.
"and you know what? my side still feels hurt! shit!"it was the assassin fuming in a huff, namely vivona who controlled the shadows.
"you bitch! i'm going to kill you!"the four shadows that fell under vivona's feet began to rotate slowly.
in the meantime sungwoo had the undead army positioned in front of him, then stepped back.
at that moment a red lightning bolt fell over the spot where he had just stood before, causing sinkage here and there on the ground.
'this guy is different.
'obviously gangsok was the real demon king who was different from the typical demon king that sung had seen before.
 'he's definitely different.
 he is different from when he first transformed himself in the underworld.
'back then the demon king collapsed the underworld, but gave up confronting sungwoo's army head-on and backed off.
 but he was different this time.
 since the modifier 'real' was added to his title, the demon king was pushing away sungwoo's army in a head-on confrontation even though the latter was backed up by gigantes.
bang! a red lightning bolt exploded on the head of a gigas, shaking his gigantic body slowly.
 it was as if a building was collapsing.
then, a bunch of red lightning flashed from the 'red sphere' floating over his shoulder, sweeping over the fortress wall.
 at that moment dozens of skeletons that were shooting arrows and flying weapons were crushed at once and turned into a handful of bone powder.

'that sphere is a completely different power.
 what is gangsok's divine power other than the demon king?'there were few gods who dealt with lightning.
 zeus? thor? or somebody else?'it doesn't matter right now.
'even if sungwoo knew gangsok's divine power, it was useless if he didn't know its related skill in detail.
'now, what i can do at this point is try to aim for his soft spot and deal a fatal blow with a killer weapon.
'he might have had to use the hidden weapon 'super heavy arrow' that he had saved until now.
but he was allowed to use it only once, so he had to be careful because he should fire it only when he was sure of killing the opponent with a single strike.
'if that's not the case, i should consider using primordial death, but that's really my last resort.
'[skill information]- name: summon grim reaper (time domination)- grade: 1st awakening- category: active- consumption: 0you can summon the grim reaper, the scythe of the reaper, for only 3 hours a day.
 you will temporarily become 'lich'.
+ realm of the dead: while gaining the lich's power, the maximum number of your subordinate spirits is increased by (+50) and all stats are increased by (+10).
 the skill effect increases by (+20%) every 1 hour due to the effect of 'mastery of endurance'.
in addition, you can revive and regenerate those undead destroyed nearby indefinitely as many as the maximum number of your subordinate spirits.
 + primordial death: the moment the summon time of the item expires, you can bring out 'primordial death' for 1 minute.
 no one knows what will happen.

sungwoo was not sure what kind of power it was.
 how was it possible that nobody knew what would happen?'i don't know the exact reason, but if i look at the description, it's clear that they are hiding something intentionally.
'sungwoo felt somehow uneasy because he knew once he used this fatal skill, he had no other means to turn to.
at that moment there was a red spark about ten meters away, then the demon king jumped out of the air, using a short-distance jump skill.
"are you going to keep running away?" shouted the demon king, chagrin at sungwoo.
but sungwoo teleported behind gigas using shadow movement, but the demon king continued to chase him.
 cheeeeeee-whenever the red current flowed through his body, the demon king moved almost at the speed of sound.
 sungwoo found it impossible to overtake him.
 'if he keeps chasing me like this, he will eventually catch up with me.
'at that moment there was an explosion on the left, namely at the demon king's castle.
 and a pillar of flames burst out from the castle wall, separating the two.
the pillar of flames spewed up for a while, heating the air around it.
"is it breath?"it must be a dragon's breath that had such a powerful destructive power, which was logically isabella's breath.
shortly afterward, the castle walls exploded and a red-haired woman walked out.
as expected, she was red dragon isabella.
'damn it.
 things got messed up even worse.
'sungwoo was embarrassed because she didn't have the 'dragon keeper' around her neck.
'what happened to jisu? she would not have taken any action if she had noticed it.
'he began to feel unease now, while the demon king felt more relaxed.
"isabella, you're safe!"the demon king welcomed isabella as casually as he had left her behind.
"well, i'm just as…""what about grace?"isabella shrugged her shoulders, suggesting she didn't know about what happened to grace.
 gangsok also nodded without caring about her.
"well, it doesn't matter.
 i'm fine as long as you're with me.
 we are going to kill him quickly and go find the third world seed.
 our plan was messed up, but the outcome would be the same.
"having said that, he turned to the necromancer.
it was clear that even if the dragon and the necromancer resisted desperately, they could not block his attack.
but isabella did not move from the spot where she was now.
then she said something unexpected, "gangsok, i'm hearing a certain voice in my head.
"he asked, "what are you talking about?"isabella looked down at her floor in confusion.
"a voice is telling me to follow you, and kill all those players.
""that's good.
 that's the answer.
 that's what the gods who rule this world want.
"having said so, gangsok moved on.


"necromancer, this is the third world i have to face, and this is my last one.
 thanks for your job!"in the meantime, isabella's body was dyed red and swelled up enormously.
she was freed from polymorph and returned to her original shape, namely a giant red dragon.
the scene of the red dragon projecting her magnificent posture behind the demon king with red horns was enough to demotivate everybody.
 but some shrieking voice from somewhere disturbed the atmosphere.
"demon king!"it was grace's voice.
 the demon king turned his head as if he could not believe it.
 "is it you, grace?"some form of creature, which was unrecognizable because it melted down, was standing between the cracks in the wall that isabella had broken down.
 it was a woman.
  she was barely breathing with herself wrapped with some kind of protective magic.
"please be careful.
.
.
isabella has attacked me.
.
.
"as soon as he heard it, the demon king turned his head.
but at that moment the red pillar of flames engulfed him.
the red dragon started moving in the opposite direction.


 