\section{chapter 189}

                             




suddenly, sungwoo felt some unknown anxiety.
 something that could not be explained by human senses was flowing from the inside of the portal.
 it was something like a small particle.
‘this is dangerous.
 it will kill me!’as soon as he thought about it, he threw himself out of the place instinctively.
 at that moment, a red ray of light poured out of the portal.
bang!the red ray of light wiped out the place where sungwoo was standing and broke down one side of their siege.
although they were given all kinds of defense buffs, sungwoo’s undead skeletons were shattered and scattered in all directions.
“damn it.
”since sungwoo was in a werewolf’s body, he could detect the strange atmosphere.
normally, he would have been wiped out by that light without even feeling it.
in the meantime, the monster in question appeared out of the portal.
he was the boss monster, ‘the gatekeeper of the devil’s gate.
’the monster was about 10 meters tall, with no eyes and nose as expected.
 his mouth was decorated with savage teeth as if they were attached with obsidian.
 there were horns and bumps all over his body, which wrapped him like armor.
the most bizarre thing about the monster was the cane he was holding in his right hand.
 it was a long, veined pole witha studded woman’s torso at the end.
krrrrrrrrrrr…-you are overwhelmed by the overwhelming presence of an alien being.
* all stats decrease.
 (-50%)not only did sungwoo’s demigod status fail to activate, but also normal players saw half of their stats decreasing.
“argh!!”“oh, no! i can hardly breathe…”not only did their stats drop, but they couldn’t move because they got frozen on the spot.
 aside from confronting the monster, they could not even face the monster properly because of the big difference in level.
‘this is a dangerous situation.
’even sungwoo felt anxious.
 no matter how strong his opponent was, sungwoo could find his soft spot while attacking him, and that’s the way he killed the boss monsters until now.
 so, he thought this monster was not an exception.

but his biggest problem was time.
-grim reaper retention time (00:07:20)-werewolf retention time (00:07:48)the monster lifted the staff.
 at that moment, a red light flashed and a beam of enormous size came out.
bang!sungwoo’s undead army, who never seemed to collapse, fell like a toy block.
thud! thud! thud!of course, sungwoo could not allow his attack to continue.
 the ogre skeleton jumped out of the collapsing undead skeletons, stretching out his right arm using his blitz skill.
however, the monster formed a shield just by lifting the cane.
 although he hit the shield with his blitz skill, his attack didn’t inflict any fatal damage on the monster, who was only pushed back one step.
rattle! rattle!then, ogre skeleton charged at the monster, punching his fists at his head.
 since ogre skeleton had a fighting trait, he could make the fight favorable to him on the battlefield.
to support ogre skeleton, bone drake also came running at the monster to push him down with tremendous force.
at that moment, however, the monster’s horns and protrusions arose like springs.
 they moved autonomously like the tentacles of a jellyfish and began to tear apart everything around him.
as a result, ogre skeleton and bone drake were shattered into hundreds of pieces and scattered.
 it was like he put them in a blender.
“what happened a moment ago?”“this is unbelievable!”the monster destroying them was so shocking to those watching the scenes.
“this can’t happen! i’ve never seen this kind of annihilation before…”hanho, who was guarding the camera, uttered in confusion.
 the two large skeletons, the strongest weapons sungwoo possessed, were smashed without leaving behind any traces.
of course, they would be revived anyway, but hanho also knew that sungwoo’s condition in lich would end soon.
“as things stand now…”[real time chat]- 4th hand: what the heck happened a moment ago?
- jack kim: the necromancer’s army has been instantly annihilated.
- incheon mango: is this the end of the necromancer?- yasuo 1: lol, finally they are going to be done.
- gwangmyeong brown bear: how can you hunt that devil monster? it looks like it’s impossible.
- wando youth: please run away.
 i don’t want to see the necromancer being killed.
 we have no hope in this game if this man is killed.
numerous viewers watching their fight were astonished because the monster easily pushed out the necromancer, who fought with an overwhelming force until a moment ago.
tramp- tramp-after neutralizing all the nearby undead, the monster started approaching the necromancer.
 however, the necromancer was still standing in his place, not trying to move at all.
could it be that he got frozen? was that why he couldn’t run away?“sungwoo? why are you standing there?”“why is he standing so silently?”everyone was watching him, holding their breath.
 if he didn’t take any action, the scene of the monster ripping apart the necromancer would be broadcasted live.
“sungwoo?” jisu lifted the sword.
 even right now she could charge at the monster and attack him, using her “footprint tracking” skill.
 but she couldn’t easily try it.
 could she avoid the monster’s numerous horns and protrusions?at that moment, some incomprehensible phenomenon occurred.
“uh? what the heck is the monster doing?”the monster passed by the necromancer as if he didn’t see anything.
tramp- tramp-while watching it, hanho saw a strange object on sungwoo’s neck.
“ah, isn’t it a necklace?”the unidentified item erased the necromancer from the monster’s target listwhen the monster passed by, the necromancer gently lifted a giant scythe from his behind.
-‘evil spirit bombing’ has been embedded in your weapon.
 (max)sungwoo used 50 souls to prepare for a massive ‘evil spirit bombing.
’it was a destructive force that could crumple a truck using just one soul.
what if sungwoo prepared 50?‘i don’t have to drag it on.
 let me kill him with one single bombing.
’then, he turned his head to the gatekeeper of the devil’s gate and slowly pulled out his necklace with his left hand.
krrrrrrrrrrrrrrr-the monster suddenly stopped because he felt something strange behind him.
 then, he turned.
 sungwoo swung the grim reaper and fired the “evil spirit bombing’ at him.
kaah!the monster lifted his cane, but it was too late.
 black spheres were approaching his body.
goong-go-go-go-go-goong!fifty spheres exploded, and black waves spread.
 this unknown energy crushed everything it touched.
 great pressure pressed down on the monster, so much so that even space looked like it was bending.
even the ground could not withstand its impact.
 as if a meteorite fell on the ground, the surrounding ground sank, sucking the monster into the pit.
krrrrrrrrrrrrrrrrrr-the monster fell to his knees.
 he was still breathing, but he was on the cusp of dying.
 this was the last chance for sungwoo to attack him.
sungwoo immediately prepared the next attack.
-‘twilight raid’ has begun.
wooooooooooooooooo!sungwoo’s body assimilated 20 souls.
 then, he flew to the monster.
 a black tornado struck and crushed the monster, inflicting enormous magic damage.
and the moment the tornado disappeared, the “ghosts’ hands” came up from the ground and tightly tied his body.
“now is the time!”as soon as sungwoo shouted, dozens of undead skeletons threw themselves into the pit just like they did in a horror movie,rattle! rattle!sungwoo launched a total attack on the defenseless monster.
 he mobilized all damage skills featuring slamming and biting.
sungwoo shot his hand cannon and swung the grim reaper.


at the last moment, minsok stabbed the sword into the monster’s chest.
puck!-you have earned 7,800,000 gold by hunting the boss monster ‘devil’s gate gatekeeper’.
-you have leveled up.
 (lv.
 22)-time remaining until credentials: 1,932 days-you have acquired the title of ‘devil’s gate hunter’.
* muscle strength increases (+3)* agility increases (+3)* curse immunity increases (+10%)“whew!”“he was a really dangerous guy.
”the fact that he leveled up to 22 from level 21 right after he killed the devil’s gate gatekeeper showed how dangerous the monster was.
-choose a level up card.
‘summon specter? it’s a new skill.
’sungwoo chose no.
 5.
-you have acquired the skill .
[skill information]-name: summon specter-grade: basic-category: active-cost: 70 mana*you summon two “specters”, a ghost with no shape.
 specter’s characteristics are as follows:(1) no damage from physical attacks.
 (2) can move through obstacles and provide visibility.
 (3) inflicts “fear” and “moving speed reduction” curses to low-level opponents.
‘great! my force has been strengthened.
’

 