\section{chapter 334}

"hey, necromancer, think about it carefully.
 your race cannot avoid the emperor's sword.
 the troops we sent to your land are only a small fraction of our emperor's vast army.
"




then, he started lecturing sungwoo.
"king of a small country! know your place, give up now and kneel before our emperor.
 ask for his mercy.
 since he is benevolent, he will make you his servant.
"sungwoo felt he heard this kind of lecture several times.
 so, he wrapped his head with both hands, giggling at him.
"mercy? man, one thing is certain.
 in other words, when the world perishes, the fanatics seem to be everywhere.
 they are searching for something to worship regardless of their nationality or culture, right?""what? fanatic? do we look like fanatics in your eyes? our great empire.
.
.
""ah, are you a little different from other races? there was something for you guys to worship before this world was ruined, right?"the man didn't respond to sungwoo's questions emotionally.
 he stood in front of the window with his hands folded behind his back.
 "just keep babbling as much as you want! there is nothing that our emperor can bestow upon you, except for mercy in return for you behind his servant or death if you don't…"the video was forcibly ended right after he said that.
 obviously, sungwoo was kicked out of his memory.
new novel chapters are published on lightnovelpub[.
]com "sungwoo, did you see something unusual in the video?"sungwoo shook his head at hanho's question.
"no? why?""well, they have someone with psychometric abilities, so i was blocked from retracing their memories.
""what the heck? then, we can't find out anything?"sungwoo went straight out of the warehouse.
 he needed to find some other way.
"yeah, i need the wolf's help once again.
"the white wolf sungwoo had in mind once helped him.
 since he belonged to the korean server, sungwoo expected he would step forward once again for the fate of the korean server.
so, sungwoo summoned him once again.

follow current novels on lightnovelpub[.
]com***the world tree camp, or the entire korean server, got busy again.
 after a short break, they started preparing for a bigger fight.
sungwoo analyzed the enemy's power by disassembling the frozen "terracotta".
after they began to lose vitality from the moment they stopped working, they were now back to porcelain dolls, their original shape.
'they are very powerful.
 at least they have a four-star, maybe five-star occupation.
 is it the emperor's ability?all the five-star jobs that sungwoo encountered until now were occupied by the leaders of their occupations.
 given the size of the chinese server, there could be several five-star people under the emperor.
at that moment, someone approached him from behind.
 he was kyungsoo.
"sungwoo, someone has just come here to see you.
""oh, is he white wolf?"for more, visit lightnovelpub[.
]com"no, he is not.
 some woman…" kyungsoo said with a tense expression.
 since the fighting took place within the village because of checkpoint failures, he was pretty nervous at the moment.
 "she is looking for sungwoo, namely, the necromancer.
 but i didn't allow her to come inside the village because of what happened just a little while ago…" he said, swallowing.
 "she says her name is li wei.
 in other words, the no.
 2 sorcerer on the chinese 2nd server.
.
.
"li wei? sungwoo immediately headed to the castle wall.
 the woman who confronted the chinese emperor came here?'i can't believe it.
'he thought he should not take her words at face value.
 for now, there was a high possibility that it was the emperor's trick.
sungwoo climbed the castle wall and looked outside the invisible barrier.
 in the middle of the road full of traces of fighting, a woman was standing tall alone.
 
"did you say you are li wei?"visit lightnovelpub[.
]com for a better experience"yes, i am li wei!"she was a younger woman than he thought.
 she was standing at a distance, so he couldn't figure out her exact shape, but her outfit in a padded jumper with some cotton sticking out made her look shabby, suggesting that she was far from commanding the chinese server.
"how can i trust you? and why are you here?"when he asked, she rubbed her head with an irritated expression.
"damn it! i didn't want to come either.
 how can i prove to you who i am when i have never met you before?"she then murmured something, then looked up at sungwoo again.
"hey, necromancer! is somebody watching us now?"at that moment, sungwoo instinctively put his hand in the pocket and grabbed the "imoogi scale".
-off-air (-)updated from lightnovelpub[.
]com'i wonder if that woman asked this.
'although he could not figure out her intentions, he had the hunch that she must have asked it.
"nobody…" he answered.
 so, why did that woman ask the same kind of question as to the king of the great mountain?she satisfied his curiosity right away.
"oh? that's good to know.
 the guy who sent me here told me i should watch out for that guy's eyes…""who sent you here?"she smiled, folding her arms.
"hey! you are a great hero with god's blessings! i'm that damn god's messenger!"new novel chapters are published on lightnovelpub[.
]comthere were a lot of beings who could be called damn gods, but there were few gods who watched them.
 soon, she took something out of the pocket and lifted it over her head.
it was a very small black statue.
"look! you are looking for this, right?"it was obviously something like a "sign of blessings," that small statue sungwoo obtained from admiral baker.
 sungwoo took a deep breath and grabbed the railing of the wall.
 then, he saw her smiling.
'the second stone statue is within my reach!'it seemed that the unidentified helper, namely the king of the great mountain, began to actively help sungwoo.
 of course, it meant that the future sungwoo was faced with would be very tough.
the unidentified helper clearly told sungwoo that his purpose was to 'collapse the system.
' in that respect, he chose sungwoo as the main engine for his secret operation.
this content is taken from lightnovelpub[.
]com'that means that he has considered a variety of players different than me.
'in other words, it was highly likely that the players were also helping sungwoo under the unidentified help's influence.
'come to think of it, as part of this operation that the king induced jisu's awakening and obtaining deity status.
'and this woman, li wei, must be one of the hidden cards that the unidentified helper could use.
 "uh? why are you staring at me like that?" li wei said, sipping hot coffee.
 "it looks like you are frowning at me because you feel bad.
 are you going to kick me out of this place?"it was true that sungwoo didn't like the way she behaved.
 sitting face to face with sungwoo, she placed a "devil's statue (a sign of blessing)" on the desk, covering that object with her left arm.


she must have brought it here to give to sungwoo, but it was clear she would not hand it over to him easily.
sungwoo responded, "yeah, you could be kicked out.
""man, this is a heartless world everywhere.
"for more, visit lightnovelpub[.
]com"so, what do you want?"".
.
.
"when he asked, she tried to be indifferent.
 sungwoo demanded, "chinese server? do you want me to destroy the emperor and bring back your lost power?"when he asked her directly, she suddenly raised her head then shook it.
"that land is not mine.
 it should be returned to everyone.
 and i was not the owner of server 2; i was only no.
 1 in the server rankings.
 but…"at that moment she was full of suppressed anger.
"my spirits are being held by them right now.
 i want to get them back.
""your spirits?"the source of this content is lightnovelpub[.
]com he recalled the 'spirit control box' that general xing used.
 he knew that the general detained and used the spirits, so it was clear that they were li wei's spirits.
"are those spirits in beijing now?""right.
 they are probably bound by magic.
"sungwoo nodded, and said, "i'm going to attack the chinese server soon.
 i'll give you a chance to save the spirits then.
 if i take you to beijing, you can do it on your own, right?""good.
 please do that for me.
"

 