\section{chapter 22}






 the short and intense battle was finally over.
“whew!”letting out a hot breath, sungwoo sat down on the stairs.
 as if it were the reward for that intense battle, a welcome message appeared before his eyes.
-a ‘roulette ticket’ has been issued for killing 100 monsters.
* as the 21st achiever in history, you have been upgraded to the “unlimited” level.
 (100 people only)7‘it’s a bonus limited to 100 people, which i received when i killed 20 monsters.
’this time he examined the bonus a little more carefully.
‘the 21st achiever in history? is this the record as of now, by the world standard?’‘if that’s the case, it means there are 20 more people in the world that have slaughtered as many monsters as i did.
 did they also pick a good job at first? are there any cards with 5 stars or more? how good is a necromancer among them?’5woowoong!right at that moment, a school bus passed by on the school road at a huge speed.
 at first, he thought hanho and jisu were on it, but that bus was standing far away in its original parking spot.
“huh? what the heck is that?”was anybody trying to escape now? there were still a lot of survivors hiding inside the school.
 however, since the seal on the gate had not been broken yet, it would be impossible to try to escape now.
sungwoo continued to look at the status of the speeding bus.
 the bus succeeded in forcibly pushing out the cars that blocked the entrance, but it could never pass through the gate blocked by the purple chain icon.
 however, when the people on the bus got off, somebody’s familiar outfit caught his eye.
“···ah? is it that damn bastard?”he was none other than daesung park, the president of the student council.
it seemed that he planned to escape from behind sungwoo’s back and run away by driving a bus.
“i told him not to do it multiple times.
 how could he ignore my warning?”2stupidly enough, daesung seemed not to have taken sungwoo’s warning seriously that he could not get out of the gate unless they killed the boss monster first.
and he had to pay for his recklessness dearly.
 it just so happened that the gym was located near the gate, and the orcs in the gym began to approach the bus.

what happened after that was beyond sungwoo’s control.
 although daesung resisted by wielding the bayonet, he could not confront a dozen orcs.
“tut, tut…”but the orcs caught him alive instead of killing him.
“ahhhhhh!”a scream rang from far away.
 orcs were breaking his arms.
 after crippling his arms and legs, they grabbed his head and dragged him to the gym.
“jisu was right.
 he’s more worthless than a skull.
”2sungwoo clicked his tongue.
***sungwoo now launched the attack on the gym.
 this time, he was not alone.
 hanho, jisu and kyongsu’s party, as well as some of sungwoo’s followers, joined him.
“we will fight too!”“at least i won’t disturb you.
”1“i can protect myself!”in total, 21 people came to support sungwoo, but he was not happy because he keenly felt like it was much more comfortable to fight alone.
1“all i want you to do is not stand in the way of skeletons’ movement.
”however, this time, he thought that he needed someone vigilant in the back because he had to enter the boss monster’s room where anything could happen.
since it was not an open space, he needed to defend as much as possible to get into the enemy’s den.
so, sungwoo and the others headed for the gym to kill the last boss monster in the school.
screech—the door made of soundproof material was opened.
on both sides of the entrance, there was a rag-like leather insignia hanging on a movable basketball hoop stand with a tusk-covered oak pattern.
 then, a stage with a bizarrely decorated facade caught his eye.

“the interior here really sucks!”ropes were tied at regular intervals to the stage ceiling and the light frames.
 with the necks of the bodies tied around it, the ropes swung back and forth.
1directly beneath ropes, in the midst of the pattern drawn with blood, a red-haired orc was sitting cross-legged.
‘what the heck is it doing? meditating?’at that moment, people began to be dragged out from behind the stage.
“ahhhh! help me!”they were a group of people including daesung.
 both of his arms were hanging loose, completely broken.
sungwoo and his party approached without any interruption and stopped about twenty steps away from the stage.
“jisu, please mind your surroundings.
”at his reminder, she carefully looked around.
 since both sides were in the stands, sungwoo didn’t know where and when the orcs would launch an ambush.
 however, he could not find any special movement on their part yet.
“i don’t see them there…”“right.
 it’s completely empty.
”it was too strange.
 all he could see was about twenty orcs.
‘no way…are they going to take them hostage as their last resort?”it seemed that those stupid orcs would try it, but he could not think of any other thing at the moment.
“ugh!”as he walked one step closer, the orcs knelt on the hostages.
 then they picked up their axes from behind.
sungwoo stopped again.
“ahhhhhh! help! please save us!”the hostages shouted in panic.
 jinsok was crying with his head down.
sungwoo sighed, looking at him.
“come on, sungwoo!”daesung called him, his voice trembling with urgency.
“please save us! sungwoo, can you do it? yeah? please!”sungwoo looked at him and the boss orc alternately.
 the boss orc was murmuring something while sitting cross-legged, with black smoke rising from his hands.
at a glance, its action was suspicious.
“come on, sungwoo!”“shut up!” shouted sungwoo.
daesung stiffened, with his mouth open wide.
“you’re so stupid, but the biggest problem is that you are greedy about your title without knowing that you’re stupid.
 you’ve put other people at risk like this.
”“…”“you messed up everything by doing whatever you wanted, and you got what you wanted, right?”“what the heck…”“i’m sorry, but you can’t do it anymore here.
 well, i don’t have to say sorry.
”coldly and realistically, sungwoo now started to attack the orcs, followed by the skeletons.
at that moment, daesung’s head was cut by the orc’s axe and rolled down.
 sungwoo did not feel guilty because he brought it on himself.
“geh?”3but right after that, the orcs put the axes on their necks and cut them.
what? were they suddenly committing suicide? red blood gushed from their necks, and their heavy bodies collapsed all of a sudden.
2“ugh? what the heck are they doing?”“oh my…”

and finally, the boss orc, sitting cross-legged, opened its eyes.
 its yellow pupils faced sungwoo.
-strengthened boss monster ‘lesser black conjuror orc chief’ has appeared.
1at that moment, black smoke came out of its body.
 without any time to escape, unknown smoke quickly filled the gym.
“ugh! cough! cough!”“argh! what the heck is this? it’s strange!”“i suddenly feel so weak… ugh.
”and people who inhaled the smoke began to fall one by one.
 the only thing that was visible in their blurry sight was a warning message.
-you are sliding into a state of ‘confusion’ by the breath of the abyss.
-you are sliding into a state of ‘powerlessness’ by the breath of the abyss.
-you are sliding into a state of ‘stiffness’ by the breath of the abyss.
-your mana is constantly burning.
“argh….
” hanho opened his bag and hurriedly took out a potion.
 it was a ‘c-class antidote,’ an item from the potions package.
 to the best of his memory of the item description, the potions could rescue him from this kind of ‘abnormal condition.
’gulp- gulp-“kuuuuh…”hanho felt the symptoms of paralysis quickly disappearing.
 he hurriedly took out another bottle to give to sungwoo.
“sungwoo! where are you? take this quickly…ugh?”he finally found sungwoo, but he felt something strange.
“take care of jisu, please.
”“uh, what about you?”not affected at all by the smoke, sungwoo was walking forward with a pleasant smile on his face.
1“what the heck…”

 