\section{chapter 228}

                             




[official channel: live] ‘worldwide’ live broadcast of the war between the korean server and the japanese server (14,115,135 watching)over 14 million players were watching the fighting scenes around the world.
since they watched it on the third-party server, the war between the korean and japanese servers, which took place all of a sudden, was nothing but one of the few interesting sources of entertainment in this boring and painful world.
they randomly posted joking chats even when a terrible war game was going on in real-time, and bet on which side would win.
was the system conscious of such a reaction? the system opened up a mini-game to the viewers.
[victory prediction]it wasn’t a bet.
 the system announced it would give a special prize by drawing to those players who answered the correct answer, the result of this game was too obvious.
[victory prediction]naturally, the japan server won overwhelming votes.
 japan has always appeared strong in the minds of people around the world.
 compared to the korean server, it was natural they thought that the japanese server had a great chance of winning.
furthermore, the influence of the japanese subculture was enormous beyond imagination.
elements of traditional japanese culture such as ninjas, samurai, and shoguns were promoted through japanese animation and fixated as something like a fantasy in the minds of westerners.
however, since such creatures were fighting in the real world, the so-called japanese addicts could not help but have a crush on them.
in particular, they got carried away with akira, yamato’s sword’s brilliant activities in the one-on-one duel, as he showed samurai in the best light like a being from fantasy.
[real time chat]- j.
j.
p (usa-1): oh god! can anyone explain what i have seen now? i can’t believe i have seen a samurai in action! thanks, jpn players!- 7ate9 (usa-2): yeah, chop them all! i know that’s your race’s national specialty, isn’t it?- amigo41 (bra): the country of martial arts is different.
 one day we will confront you guys, but i can’t guarantee who’s going to win.
 you guys are great.
- te creo (cub): awesome.
 that’s all i can say.

- きんほし(jpn): wwww it’s beyond my expectations.
- davehhh (nzl): i support you.
 keep going!in other words, the chat window was overflowing with comments extolling the performance of the japanese server, while the players of the korean server kept silent until the necromancer and his allies appeared.
the moment when the japanese troops who broke through the main gate were destroyed by dozens of explosive arrows, the huge wings of the bone wyvern alpha male spread over the building, and the person in question, called kor-157, appeared, the world’s perception of the korean server began to change.
since the japanese server players intruded, determined to wage a war with the korean server, they were thoroughly prepared.
‘we should not make light of them.
 although they didn’t go through a major war, they kept hunting monsters,’ sungwoo thought.
they were armed with excellent items.
 they also learned how to receive effective synergy through appropriate party combinations.
 in other words, they were not weak.
‘it seems they have done some background investigation about me because their main target is me.
’they targeted the korean server to fight kor-157, the necromancer.
 therefore, they investigated the tactics used by the necromancer and prepared for them accordingly.
– caution! a ‘poisonous cloud’ is formed in the affected area.
for example, when the “poisonous cloud” that crippled many chinese troops during the battle in taiwan appeared in the sky, forward soldiers on the tall buildings began to shout.
“rain warning!”“rain warning!”“everyone put on a raincoat right now! the dark clouds formed over his head can sprinkle poisonous rain over us!”warning voices echoed from all sides.
 then, all japanese players started putting on thick vinyl hoods.
 although they were not a perfect shield, they were the maximum defense available for now.
“if you notice a body, clear it right away! otherwise, it will explode!”they were also conscious of the corpse explosion, so whenever they found corpses, they picked the corpses right away and threw them far away.
“watch out for the sky!”
“air response!”they also prepared a response system to cope with the necromancer’s main attack, ‘aerial dominance’, and practiced it.
“as soon as the bone wyvern comes down, spread the protective shield right away and focus the freezing magic on both wings of the bone wyvern!”by simply blocking the movement of the wings, they could minimize the threat of the bone wyvern because if the monster could not control his direction and balance, he could not mount a proper attack.
their systematic training in preparation for the necromancer’s attack was obvious to everybody.
“gather together! we are going to move as a group systematically!”it was a tactic that belied common sense that they decided to move along the uphill slope of the two-lane road as a single group.
“if there is a big impact, never scatter!”given all the players who were destroyed by the necromancers so far, lots of them were killed because they gathered in one place.
however, these japanese players made even larger formations.
 standing shoulder-to-shoulder, they were blocking aoe attacks with their shields and magic.
however, sungwoo was not agitated by them at all.
‘i think they have been preparing a lot, but all they can do is delay my attack for a few more minutes.
’no matter how well prepared they were, the necromancer could freely attack them for one hour while his lich and anubis status were activated.
rattle! rattle!if the huge skeletons kept resurrecting despite their killings, it would be impossible for even the toughest tankers to stop them forever.
tung! tung!the troll skeletons swung blunt weapons made of bones.
 those who received their attack could not keep their balances.
“you can’t stop me anymore.
”eventually, the japanese players would show their weakness because they could not be resurrected like the trolls.
“clear the bodies quickly! hurry up!”the gap in their strength was widening as time went on.
“fill the gap!”they had only one hour.
 during this one hour of fighting, the japanese players had no choice but to suffer unilateral damage, which was a tough choice for them.
so, they chose the next best option: assassinating the necromancer.
until now, no one has succeeded in assassinating him, but they wanted to avoid the hellish fighting with him for a full hour.
“be careful on your side!”moreover, the necromancer didn’t attack only from the sky and front.
“something is climbing the wall!”“what are those terrible things?”at that moment, hundreds of japanese players were climbing a two-lane uphill road with buildings on both sides.
 this was the best fighting stage for the undead, which were optimized for the three-dimensional movement, such as ‘ghouls’ and ‘giant jannabi skeletons.
’“drop them!”“be careful, you might be dragged… ahhh!”that was just the beginning of the attack of the undead.
goo-gung! goo goo goo!the noise of something scratching the ground began to get closer and closer to the japanese players like an earthquake.
 it was heard from over the building on the right.
“no way!”

“this is that monster! giant snake imoogi!”since they shared the relevant information early on, the japanese players instantly realized what they would encounter from the strong vibration.
“but that imoogi can hardly move around here because of all the buildings here.
”“yeah, that imoogi made a mistake!”it was impossible for bone imoogi, a super-large monster dozens of meters long, to move around downtown, but the monster snake appeared at last.
gugugugugugu!“the snake came out!”“avoid the snake!”its giant head popped out of the alley on the right, cut off the middle of the japanese players’ formation; then, he put his head back into the alley across the street.
the giant snake moved with tremendous speed and weight, like a subway running out of one tunnel and entering another.
“just stay still until the giant snake passes by! he can’t even turn his body!”bone imoogi was powerful enough to push a forest away by swinging his long body, but it was a different matter if the giant snake could destroy a concrete building six stories tall.
“if the snake attacks us from the front, we can use the massive freezing magic at the same time.
”in other words, they already set up a plan to counterattack the giant snake, but what happened was not what they expected at all.
bone imoogi didn’t keep passing.
 he blocked the middle of the japanese players’ formation as they labored up the hill and stopped before them.
“he stopped!”“what the heck? is he dead?”of course, bone imoogi wasn’t because sungwoo was controlling all his subordinate spirits including the giant snake.
‘now is the golden time to attack them!’

 