\section{chapter 275}






 sungwoo now grasped the whole picture of their operation.
‘i predicted that someday the chinese server would put more pressure on the korean server…’however, he did not know that they wanted to put pressure on by mobilizing other forces.
 in other words, they began a sort of diplomatic war with the korean server.
whooooooooo!at that moment, a blizzard began to hit suddenly.
“ugh!”“what the heck…”it was a huge gust.
 they had no choice but to bend down.
 a biting wind penetrated their clothes.
 there occurred a whiteout condition in an instant.
 they lost the sense of direction and perspective because everything surrounding them turned white.
“oh my god! i can’t walk!”“don’t move! if you move carelessly, you’ll get lost!”they did not move and looked ahead, covering their faces.
at that moment, huge shadows began to appear one by one beyond the white veil.
 the shadows swelled up at a tremendous rate.
 something was coming to them from afar.
“what the heck is that?”“…”then, the blizzard scattered everywhere in an instant as if nothing happened.
 and the identity of the shadow stood tall in front of their eyes.
“a bear?”they were brown bears.
 huge bears were standing tall like totem poles on the siberian field.
 the blizzard stopped because the bears blocked the path of the wind.
‘they are not werebears.
 are they the tiger race?’they were too tall for the bear race in sungwoo’s eyes.
 when they raised their upper bodies, they seemed to be as tall as a three-story apartment.
 it was natural that the blizzard stopped blowing when the five giant bears stood before them.

and a giant man wearing a white fur hat appeared among them.
 his face was covered with grotesque tattoos.
“captain? that person is…”“that person is the siberian demon, druid, the no.
 1 in the russian server rankings.
”the owner of the memory fragments made eye contact with the man.
he made a frown, which suggested he was not pleased.
“you guys smell so terrible,” druid said.
“pardon? what did you say…”the owner of the memory fragments felt insulted but bravely approached him.
“we have come here to ask you a favor.
”then, he explained to druid the purpose of his visit.
then, druid smiled.
 the flush of his cheek meant he was drunk.
“i know.
 just tell me the amount of compensation and your goal.
 then get lost! you smell bad!”“…”the video ended at that point.
“is it over?” asked hanho, popping up suddenly.
 “oh, it’s over.
 some guys are planning to attack us again this time, right?”sungwoo nodded.
“damn it! who are they this time?”“they are familiar to us.
”“pardon? who is it?”
china, japan, and even russia, the countries that aimed to occupy korea from ancient times were planning to overtake it again.
 in some respects, this was something familiar to the korean server.
***in the meantime, the sudden end of the mainstream was as shocking as its sudden start.
the forces who tried to unite around the necromancer had no choice but to disperse in frustration.
 they realized once again how pale they looked, compared with the necromancer.
in that respect, the new mainstream was an event that confirmed the possibility that the korean servers could be integrated into one, and who could be the central player of the integrated servers without any doubt.
however, the liberation guild was suffering from the aftereffects of the mainstream.
“damn it!” junghoon yelled.
he struck the desk and stared straight ahead because of the message that appeared before his eyes.
-the faction quest (special) has failed.
“hey, give me a break!”as someone who had a four-winged angel statue, he was given a faction quest related to the just-ended mainstream when it was initially issued as follows.
[faction quest (special)]-title: don’t repeat the mistake.
-type: assassination-goal: assassinate kor-157-reward: rank score*the perished world is expected to reach the korean server.
 and “kor-157,” the arrogant evil being, will appear in the chaos.
 at the decisive moment, betray kor-157 and get him killed by the monster army.
 this is an order.
* if you fail to carry out this order, your ‘rank score’ will go down.
 (if accumulated, you may be excluded from the benefits of various factions.
) in addition, the ‘all stats drop’ penalty is given to all the members of your faction (-1)a similar faction quest was issued during the korean and japanese war, but junghoon ignored the message and helped sungwoo because he was convinced that was the right thing to do.
however, the angel camp did not leave junghoon alone or give up on him.
 rather, they issued a more compelling faction quest, pressuring him and the liberation guild all the more.
‘wrong.
 i am wrong.
’junghoon chose the angel camp because of their good image, but the price he paid for it was too harsh.
-a penalty is given to all members of your camp because of the failure of ‘faction quest (special)’.
* all stats decrease.
 (-1)it was a punishment for junghoon disobeying the order.
“i can’t do it anymore! if you’re going to keep punishing us, just break the contract! leave us alone!”staring at the angel statue, he yelled at the top of his voice.
he always kept calm until now, but obviously, he could not stand it anymore.
but the angel camp replied with another command.
-high-ranking players (players) of the angel camp will be dispatched.
 kill ‘kor-157’ by obeying them.
* this is the last warning.
 if you fail to carry out this order, you will be “judged” accordingly.
junghoon sat down in the chair with a deep sigh.
at that moment, somebody knocked on the door.
 minhum, his deputy, came in.
“deputy, what’s up?” junghoon asked.
whenever he came like this, he usually brought bad news.
as expected, minhum said in a nervous voice, with anxiety on his face, “someone visited the northern border.
 they are from a foreign server.
 they look like slavs.
”are they from the russian server if they are slavic?junghoon was not sure, but they were obviously the ‘high-ranking players’ specified in the angel camp’s order.
“they have said they are from the angel camp.
 they are asking me to bring the commander of our camp, saying they are the owner of the six-winged statue.
”

that was exactly what junghoo expected, but minhum didn’t finish yet.
 he hardened his face.
“by the way, when our guards tried to inspect them, one of them caused a blizzard, which blew up the entire northern border where 50 guards were stationed.
 according to our guards, they just blew it away by casting one spell.
”junghoon raised his head, astonished.
“is that possible?”“i don’t know, but…”blowing 50 guards away with one magic spell? even the korean server could not do it.
“they are very powerful.
 i think we have to deal with him diplomatically, not by force.
 i think you had better go out and talk with them.
”junghoon let out a sigh.
“man, if we don’t unite, we’re destined to be devoured by the foreign servers.
”“…”then.
 he stood up from his seat.
“please go and see sungwoo.
”“pardon? what are you talking about?”junghoon approached the white armor hanging on the wall.
 and he looked down at the sword placed under it.
“in order to deal with the bluffing guys diplomatically, we have to be as strong as them.
”as a matter of fact, the korean peninsula had been attacked by foreign countries several times historically.
fortunately, there was one strong sword in the korean peninsula that could block them.
‘ i definitely need your help, necromancer.
’the necromancer was a lethal weapon or the best bargaining chip with which junghoon could also stab the foreign players even if he got stabbed.


 