\section{chapter 9}






 now sungwoo wanted to kill the boss monster even more.
‘why do we have to go through this damned thing?’sungwoo had been obsessed with adapting himself to the imminent situation and seeking survival, but sungwoo began questioning everything for the first time.
“sungwoo, is it really okay for us to go to the rooftop?”even before sungwoo replied, the skeletons went up the stairs.
 the door of the top floor soon appeared.
 then sungwoo flung it open.
1***sungwoo had never climbed to the rooftop of the humanities and social sciences building before.
 the last time he went there was when he practiced dancing because he could not find a proper place for practicing before the freshman talent show.
4“damn it…”right now, this place has become a sort of ‘dungeon’ for the goblins.
 the goblins were in the thick of making a tent by using all kinds of clothes they removed from the bodies of the students with the lockers and all kinds of objects they took from the hallway as a wall.
squeak!
piling up thick textbooks here and there, they were making a fire in the plastic trash bin after ripping the books apart.
“oops… he’s my classmate…”at one end of the rooftop they were busy taking the clothes off the bodies.
 one goblin was drawing a strange pattern on a dead female student’s white shirt with a red marker.
4“what the fuck…” jisu cursed in a low voice.
the three including sungwoo stood frozen at the entrance of the rooftop.
no matter how well they adapted to this crazy situation by now, they could not insensitively turn a blind eye to what was going on right before their eyes.
“…”sungwoo felt scared all of a sudden.
 why did he dare to come up to this place? on the other hand, he felt other feelings surging deep within his heart.
 at first, he could keep calm because he thought he was facing an uncontrollable phenomenon.
 but what was happening on the rooftop made him upset.
 why should he or they have to go through this? however, the more he thought about it, the more cool-headed he became.
 after all, he knew he was weak compared to them.
“…phew!”they were killed because they were weak, so sungwoo, hanho, and jisu needed to be strong.
“let’s go!”right at that moment, the goblin tearing a pair of blue jeans with a dagger turned its head toward them.
4
squeak, squeak!when the goblin screeched, all the goblins gathered on the rooftop flocked to it.
squeak, squeak, squeak!there were about 20 of them in total.
they blocked the three and expressed joy, showing their sick smiles.
 perhaps they seemed to think they outnumbered sungwoo and the other two.
“sungwoo, how about escaping this time…”but even before hanho finished his words, the skeletons rushed forward.
1‘put up a strong resistance.
’1reflecting sungwoo’s intuition, the four skeletons stood shoulder to shoulder, blocking the entrance to the rooftop.
at the same time, sungwoo lifted his left hand.
 then the red bracelet’s ‘madness of the wilderness’ on his wrist responded immediately.
woowoong—the hollow eyes of the skeletons sparkled brightly, and their hands were empowered with energy spirits.
 right at that moment, the goblins charged toward the skeletons like a herd of angry wild dogs.
but the skeletons, standing firmly at the entrance, resisted their attack.
 while blocking their attack with their left forearms, the skeletons inflicted deep stabs with their daggers.
‘their attack speed is obviously very fast.
’puk! puk! puk! puk! puk!when the goblins mounted an attack, the skeletons fought back with double the force.
 even the force on the tips of the blades was clearly visible in sungho’s eyes, which helped them pierce through not only the goblins’ swords but also their knucklebones carrying the swords.
 and that led to their instant deaths.
the first four goblins fighting at the forefront fell down in three seconds.
“just think of these skeletons as our shield!”shouting like that, sungwoo heaved his spear over the skulls of the skeletons.
the skeletons, which were 120 cm tall, served as a sort of barricade.
 thanks to them, sungwoo and the other two could freely attack the goblins safely and unilaterally outside their attack range.
jisu, who was tall, reached out and wielded her saber over the skeletons.
 but hanho, who was holding a dagger, was standing in the back blankly.
“damn it! i thought i chose the good stuff, but these are swarming with maggots!”hanho picked up two daggers just in case, but they were useless.


“oh my!”in an act of desperation, hanho threw one of the daggers at the goblins.
puk!“ugh?”it directly hit a goblin’s forehead standing in the rear.
 it fell to the ground immediately.
1“oh, i hit him! didn’t i do well?”5during his middle school days, the so-called ‘chopstick-throwing game’ was popular among students.
 their target was the outer wall of the school, but they were caught by the principal and given harsh discipline.
 ever since then, they no longer played the game.
 looking back, it was the only moment hanho emerged as the strongest winner in the game.
3now that he gained confidence, hanho drew another dagger and threw it quickly at the goblins.
 this time, he accurately hit the forehead of a goblin standing at a distance.
 for him, it was a very easy two kills.
1“i’ve found my talent!”2when the three fiercely attacked with the skeletons standing at the forefront, the goblins were visibly hesitant as if their fighting spirit had been broken.
squeak…squeak…

 