\section{chapter 270}






 while the king of the great mountain confronted the world eater, the undead army under sungwoo’s control arrived.
 sungwoo immediately pitted them against the demons in a frontal counterattack.
-you have earned 500,000 gold by hunting ‘external beings (lower monsters)’.
-you have earned 500,000 gold by hunting ‘external beings (lower monsters)’.
‘i have to block the entrance before more demons pop out.
 if demon gatekeepers appear in droves, i really can’t hunt them within the remaining time.
’‘waves’ existed in the demons’ den, where as the level of the wave went up, more powerful monsters appeared.
 in particular, the gatekeeper of the demons’ den that usually came out last was overwhelming.
of course, sungwoo was much stronger than he was during the battle in taiwan, but if dozens of terrible demons like the gatekeeper came crawling out, he would hardly win the fight.
 in the meantime, another reinforcement force arrived.
“sungwoo! we’re here, too!”as sungwoo turned his head, hanho, jisu, and two tigers came running out of an alley.
“what the heck is that strange helmet?”“strange? you don’t know anything about this helmet style!”hanho then shouted, tapping his heavy iron helmet.
“isn’t the helmet the symbol of a warrior?”“why do you think you are a warrior? aren’t you a thief?”they could not afford to argue because of the impending situation.
“hanho, don’t get too close to the demons.
 just kill them from the rear!”“do not worry! i have this helmet!”
“don’t talk nonsense! let me deal with them in front!” jisu shouted.
since she had the experience of hunting monsters during the battle in taiwan, she could confront them without any difficulty.
so, she could easily smash one or two demons.
 even if three demons charged at her at the same time, she could strike them down immediately.
two demons were immediately beheaded when she swung her sword.
surprisingly, hanho was bravely fighting.
“hahaha! come on! bring it on!”jisu thought it would be tough for him to deal with the demons, even though he was armed with the helmet, but he also had no problem confronting the charging demons.
puck! puck! puck! puck! puck! puck! puck!with an incredibly thick shield around his body, hanho was throwing six daggers at them randomly.
 they couldn’t confront him, no matter how powerful and swift they came.
kuck! kuck! kuck!the demons’ bellies were so ripped apart as to look like a beehive.
the first demon collapsed at hanho’s feet.
“oh, fifty thousand gold? what a jackpot!”while looking at the demon’s body, hanho roared arrogantly like a street cat who won the territorial battle.
“hahaha! look! i’m the holy asura rogue who can even be a tank! bring it on!”in the meantime, the two tigers under the king of the great mountain also brilliantly fought the demons.
 since they were the king’s close bodyguards, they were far stronger than ordinary monsters like the demons.
bang!
both of them were holding giant hammers, and whenever they swung the hammers, the heads of the demons were shattered to pieces.
even while they were busy smashing the demons, they struggled to make sure they kept the potato bags safely.
“hey, protect the potato bag! brother will be mad if you lose it!”“i know that, man! i am caring about it, too!”in addition, “root bundles” arising from all directions wriggled like snakes and fell on top of the demons.
bang!whenever the roots fell on them, they crushed dozens of demons at once, as if catching a swarm of insects.
“come on, make the opening to the gate!”the king of the great mountain swung the bundle of roots to clean the area around the demons’ gate.
 when they finally made the opening, they rushed toward the gate.
“we have no chance of winning this fight if we just hold out! we have to shut the gate!”shouting like that, the king threw something at the portal.
shhhhhhhhhh!it was a thin branch, which hit the center of the purple portal.
 then, the portal began to crumble like thin plastic and lose shape.
-‘the power of the world’ has forcibly closed the gate of the ‘demons’ den.
’then, it condensed into a single point and disappeared.
 it collapsed the portal.
“come on, take this!”the king handed over some of the branches to sungwoo.
“these branches are full of the spirit of the mountain! if someone with the title of ‘guardian’ uses these branches, he can shut the cracks in the world! to put it simply, the strong power of this world blocks the influence of the outside world!”“tell me who the hell you are!” sungwoo said, curious about the king.
he knew the king was an unusual monster, but he never expected the king could not only expel the world eater but knew how to shut down the gate of the demons’ den.
the king looked quite different from the monster who received the title of “king”, as well as the salamander, who was called the “emperor”.
“wouldn’t it be okay for us to sit down and talk after shutting the gates of our neighborhood?”the king was right.
nodding at him, sungwoo turned to the gate of the demons’ den.
“talk to you later,” said sungwoo.
“no problem!”it didn’t take long to close all the gates of the demons’ den.
all they had to do was to break through the demons’ attack and throw a tree branch into the gate of the demons’ den.
the city of pyongyang was quiet again.
“thank you all.
 didn’t you feel it was like a scene in an epic where everybody fought hard in perfect harmony?” the king said.
sitting on a large piece of concrete rubble, he began to peel the boiled potatoes.
“good.
 this time it’s boiled very well.
 this slightly burnt part is particularly delicious.
”he took a big bite of potato and looked at sungwoo.


“can i ask my question now?”“did you know the situation was going to be like this?”he nodded, chewing the potato.
“i knew it to some extent.
 after i received the title of the king of the great mountain some time ago, i discovered through the spirit of the mountain that there was a creature gnawing on this land.
”“are you talking about the world eater?”the king nodded and said, “yes, their purpose is to take all the lives on this land.
 how crazy they are! they should have stayed put and lived on potatoes quietly.
 why are they making such a fuss and sucking up others’ souls?”“…”“anyway, i knew that you were hated by the world eater, so i was on alert, closely checking if this monster would stick its ugly head out in the mainstream this time.
 well, i should say his eyeball, not his head.
”“what is the identity of that monster?”when sungwoo asked, the king scratched his cheek and opened his mouth after hesitating a bit.
“uh, um, if i describe him roughly, i would say he is the god of another world.
”“god? is he the god of the demons’ den? he opened the gate of the demons’ den freely.
”the king shrugged and said, “well, i don’t know where he is from, but i’m sure that he controls the demons’ den.
”earth wasn’t the only setting in this game.
 not only the “demons’ den,” dominated by the world eater but also the “hell,” which seemed to be related to kangsok han, were two of the settings.
and all of them were anxious to kill each other for no reason.
“anyway, to put it simply, one world is trying to devour another world.
 i would call it bad luck arranged by the system.
 however, since the system also wants a game that can pit the players of a certain level against each other, it has set up a certain rule that can serve as reins on them.
”“reins? then, did you expel the world eater under the rule?”

 