\section{chapter 298}






 at jinhae port in changwon city.
this was the place where a group of survivors belonging to the ‘hwarang guild’ lived until this morning.
 during the korean and japanese war, they didn’t suffer any direct damage from the japanese troops that landed on the korean server, so they were thriving on a solid foundation.
“man, this place turned into ashes.
”when they looked down from the wpu airship in the air, jinhae port was completely ruined.
since seven airships fired all sorts of magic shells like rain, it was natural that the port was devastated.
“what a spectacle!”two men were standing on the deck of vanguard, no.
 4 warship of the baker fleet.
 leaning against the railing, they watched the ruined port city.
“you bet! it’s so spectacular that nothing has survived.
”“hey, isn’t it your first time to see something like this?”“i experienced it in philadelphia.
”“oh, philadelphia…”the two men chuckled at the same time.
“our admiral hoped this kind of spectacle could be broadcast on the korean server to break their spirits, right? other than that, it’s just unbelievable for us to pour out shells here instead of on the monsters.
”“you’re right.
 admiral baker, you know, looks like a performance artist.
 don’t you think this kind of performance is also sort of a strategy?”“philadelphia?”they laughed again.
 it seemed that they had some special memories in philadelphia.

“yeah, that’s why we devastated philadelphia because chairman love accused him of causing an unnecessary sacrifice.
 what did he say? didn’t he say that it was because of the indiscriminate bombing that the philadelphia alliance surrendered early? he even said admiral baker traded shells for the lives of soldiers.
”“did admiral baker major in psychology?”“he’s an old man who was mistaken that he could get the psychological analysis of his men.
 but look what happened? since the world has changed like this, doesn’t it seem that everybody tends to believe him?”“right.
 i hear that the sailors on the ship call him odin with two eyes open.
 i knew that someday he would beat chairman love and become the top leader, but i never expected the day would come so early when he took control like this.
”as their conversation suggested, the provisional congress already fell into the hands of admiral baker.
“the crash of the messenger and the slaughter of the crew on the airship made a big impact.
 everyone knew that the necromancer was a crazy wizard who controlled corpses, but who knew he was a barbarian psychopath who we could not even talk with?”“well, that’s what the lawmakers who supported chairman love didn’t know.
 that’s why they supported admiral baker without knowing the exact situation.
 as a matter of fact, they gave up the hope that chairman love’s troops were a reinforcement who would alleviate their anxiety about the monsters coming from amazon.
”as expected, the wrong news seemed to have changed the atmosphere of the provisional congress.
sipping tea, they clicked their tongues.
“oh, by the way, i hear that there are about 6 hours left until they are done installing the hyper gate.
 i wonder if we can take a break until then.
”“well, if you listen to the guys on the ship, they might attack busan, too…”at that moment, a shadow quickly passed over the deck.
 the two raised their heads at the same time.
“uh?”“did you see that a moment ago?”seeing a shadow wasn’t common.
 unless it was a cloud, nothing could pass over their heads, and the clouds would not pass so quickly.
“look over there!”
when they looked at the far end of the horizon, something with wings disappeared through the clouds at a tremendous speed.
but even before they thought about the identity of the unidentified flying object, they were distracted by another object.
thud!suddenly, a square box fell on the deck.
– caution! the ‘player killer box’ opens!“oh, my god! this one is…”they immediately noticed what it was.
 it was a surprise box containing hundreds of “extremely poisonous worms,” which was called a “player killer box” (extremely poisonous insects), an inhumane killing weapon that the provisional congress banned them from using.
but such an object fell right under their feet, which was something very ominous.
“damn it!”“we’re finished!”wheeeeeeeeeeeeeing!the next moment, the four corners of the box opened with a mechanical sound, and a swarm of black smoke-like insects began to pour out.
 they began to squeeze through the cracks in the airship.
 the two could not stop the killer insects.
soon, the airship shook violently as if it had had a seizure.
***sungwoo was watching the whole scene of the player killer box opening from a distance through the specter.
“hmm…the box has completely swallowed up a sailing boat.
”the ‘player killer box (venomous insects)’ could not be stopped once it was opened, and it could be opened only when the player approached it.
after sungwoo discovered the object, he had the undead hold it so as to stop it from working, which was kept by them until now.
however, sungwoo now counterattcked them with the killer box.
‘an eye for an eye, and a tooth for a tooth.
 i have no reason to fight them moderately.
’they lost a whole airship and many crew members because of sungwoo’s unexpected attack.
soon, the other airships began to evade.
 they ran away from the airship full of killer bugs as if they fled from those struck by a plague.
“great! we’ve secured one more airship!”however, it seemed that they didn’t want to give up the airship easily, so they fled from the airship far away with small flying objects being separated from the fleet.
 they looked like an emergency boat, but fire-type wizards wearing protective clothing were aboard the flying objects.
 were they assigned to taking care of the killer bug box?“well, they can’t easily throw away the ship they like so much, right?”however, after a while, they turned the course again, helplessly returning to the fleet in despair.
soon, they began to shout in embarrassment here and there.
“it’s an enemy fleet! the enemy fleet has appeared!”sungwoo also turned his head.
 black figures were approaching from the inland sky.
 they were none other than dozens of bone wyverns and the messenger.
a large-scale air battle between sungwoo’s allies and admiral baker’s fleet began on the sea off changwon.
***“everybody, get ready for the battle! a fleet of the world tree camp has appeared from the north! everybody, get back to your position!”

when the broadcast rang with the siren, the wpu fleet began to be busy.
 the sailors on the ship conveyed orders and the engine room continued to run the ship at high speed.
as if they were familiar with this kind of operation, all the airships moved in unison.
the six airships fired huge cannons and formed an artillery line.
“align the entire muzzles and stand by!”the players on the ‘gun deck’ were taking their breath, pointing their guns to the enemy fleet.
their subordinates stared at the enemy with telescopes in silence.
“what the heck? wyvern? that’s a wyvern made of bones, right? are they flying here to attack us?”one of the subordinate shooters sneered at the wyverns and handed the telescope to the chief shooter.
 the chief shooter’s reaction was also no different.
“insane guys, they are coming for suicide!”they lost one airship, but they were still elated with high moralemost of the soldiers of the baker fleet were former soldiers, obeying the admiral’s absolute orders, and winning victory after victory.
 and they were virtually responsible for the creation of the wpu, the core group of the eastern united states.
“man, how come they dare to attack us like that? are they crazy? don’t those barbarians have no sense of art at all?”they mocked the approaching wyverns and sungwoo’s troops.
“hahaha! it looks like we have to smash them to pieces.
”just a few hours ago they devastated jinhae port beyond recognition, so they were confident of turning a dozen winged bones into ashes at once.
“everybody, shut up! we have an order!”

 