\section{chapter 265}

                            the necromancer jumped off the floor, swinging his scythe.





fifty spheres hit the rooftop of ryugyong hotel.
goo-ko-ko-ko-ko-ko-gung-“what the heck…”the black spheres swelled, creating an unknown wave pressing down the hotel.
 enormous energy and tremendous pressure struck down the hotel.
its steel frames, which had been deformed due to the heat, were bent randomly.
kugugugugugu―the huge skyscraper, where the monster’s emperor was asleep, collapsed.
ryugyong hotel collapsed like a sandcastle.
“unbelievable! this can’t happen! your majesty! what a disaster!”the emperor’s aide, lizardman, cried out loud.
 when the massive building collapsed, his bedroom was crushed.
kugugugugugu-the heat that filled the interior of ryugyong hotel got mixed with dust, creating a tremendous wind pressure as if a volcano erupted.
the lizardman tried to approach the emperor, but he could not because of the enormous wind pressure blowing like a desert sandstorm.
“cough! cough!”such a terrible situation continued for several minutes.
whoooo-a little later the dust settled, and they began to see the devastated ruins of the disaster more clearly.
 the symbol of pyongyang was smashed in an instant, showing the open sky after a long time.
and a man exhaling blue heat stood tall beneath a huge gray mountain made of concrete fragments.

“that guy is the necromancer!”the players of the china-1 server recognized the necromancer.
 the necromancer, who was reportedly retreating after advancing north, appeared right here in the center of pyongyang.
as if he was not just content with appearing here, he smashed the whole building of ryugyong hotel instantly.
“how could he appear here?”“it doesn’t matter.
 even if we don’t ask the emperor, it looks like he is going to fight it out with the necromancer.
 so, let’s get out of this place.
”the players on the chinese server hurriedly stepped back.
 since they came here as envoys, they didn’t have to fight a direct battle with the necromancer.
they just wanted the monsters in pyongyang to get rid of the necromancer.
***sungwoo, who was standing on the rubble of ryugyong hotel, was feeling some sort of energy coming up under his feet.
‘yeah, this guy is still alive.
’wearing hellfire armor, sungwoo felt it was like a stream of air, but given the nearby steel frame burning red, the heat was intense.
“other than me, nobody can stand this heat,” said sungwoo.
“yeah, i feel like my feet are melting,” said minsok, next to him, complaining about his pain.
“they will come in droves to protect the emperor.
 so, stop them.
”victor was dealing with the enemy’s main force to divert their attention, but there were still quite a few defending troops to protect the emperor in pyongyang.
“can you deal with him alone?” asked minsok.
sungwoo nodded at him and said, “i can deal with him because his biggest weapon can’t work any longer.
”the main weapon of salamander, this giant lizard called the spirit of fire, was flames.
 however, his flame attack would not work against sungwoo.

“alright.
 don’t worry about me.
”having said that, minsok pulled out a great sword he had lost.
 maybe he would be able to completely prove his credentials today.
“as expected, those guys are rushing to us in droves.
”when minsok turned his head to one place, a large number of monsters were flocking along the empty streets of pyongyang.
‘they are different from typical monsters.
’although their main force was not here in pyongyang, these pyongyang defenders were pretty strong.
 among them was ‘drake.
’ if they breathed out flames, dozens of zombies would melt away at once.
‘but i can’t afford to pay attention to them.
’kugugugugugugugu―a tremendous vibration was already coming up from under his feet.
at last, the emperor came to his senses.
“well, it looks like we’re going to collect lots of good bone material today, given their great builds.
 let me go ahead first,” said minsok, moving first.
purrrrrrrrrrr―then, durahan followed him, and the undead army rose themselves behind the rubble.
and their shadows fell on the ground.
 they would not allow the enemies to approach sungwoo and his allies here for at least an hour.
sungwoo turned his gaze and looked down at his feet.
bang! bang! bang!there were still occasional explosions here and there.
 somebody was coming up while throwing aside the debris.
quaguaguagua!a beam of flames broke through the debris and soared into the sky.
a long tunnel was opened from the basement when this stranger pushed out a massive chunk of concrete.
“which crazy bastard dared to come to my…?”a man walked out from there, shouting at sungwoo at the top of his voice.
“how did he ruin my palace like this…?”his whole body was flaming hot.
 he looked like iron that was just out of the furnace.
he had long hair that dropped to his waist, and with his red eyes torn vertically, he was staring at sungwoo ferociously.
“you must be responsible for messing up my place…”sungwoo could feel intense anger in his eyes, but he just shrugged.
“well, i thought you might feel hot inside, so i wanted to let some fresh air in your place, but things worked out like this before i knew it.
”“i won’t ask who you are.
 i’m going to burn you to ashes and put them under my bed.
”-the field boss monster “salamander” has appeared.
he was none other than salamander, the emperor in pyongyang.
 he was once affiliated with the drake race, but after gaining extraordinary strength, he seemed to maintain his human form like the king of the great mountain.
“it’s nice to see you reticent.
 the king in my neighborhood is so talkative that he can be a headache sometimes.
”then, sungwoo approached salamander.
 whenever he exhaled, heat flowed out of his mouth.
“haaaaa… if that’s your will, you’ll regret it from the moment you get burned.
”two flames, one red and the other blue, faced each other.
the mainstream was expected to end early, depending on the outcome of their fight here.


***meanwhile, jisu and hanho stood in front of a cave, escorted by the king of the great mountain.
“this is the place i mentioned.
”“what is this?” asked hanho.
the king of the great mountain scratched his chin and said, “well, what should i say? should i say it’s like the veins of this mountain range? it is a place where the spirits of the mountains gather, and through this place, you can go anywhere from here to mt.
 paekdu ridges in an instant.
”mt.
 paekdu ridges referred to the mountain ridges ranging from mt.
 paekdu in the north to mt.
 jiri in the south.
“so, if i go through here, you mean i can teleport somewhere on the north korean server and support sungwoo, right?” hanho asked.
“yes, that’s right.
”after he said that, the king walked ahead and went into the cave.
 the two tigers also followed him into the cave, carrying boiled potatoes on their backs.
however, hanho looked around the dark cave first and smacked his lips bitterly.
“well, sis’ jisu.
 isn’t it a tiger’s den? are we going to get kidnapped and eaten by them?”“no idea.
 why are you worried about being eaten by the tigers who can’t boil potatoes properly?”“you never know.
 they might be pretending to deceive us.
 who knows they suddenly reveal their true colors and… man… let’s go together!”so jisu and hanho also went into the cave.
the inside of the cave was cold.
 and it was filled with deep darkness.
 it seemed like they couldn’t take even one step further.
at that moment, the king lifted his index finger, and a small flame rose, which lit up brightly.
“let me take out one, too,” said jisu.
in no time, a blue flame rose from her shoulder.


 