\section{chapter 256}

                            the king was exceptionally strong among the tigers.
 as time passed, he became stronger, eventually gaining tremendous abilities.
 that’s how he received the title of “king of the great mountain.
” he said he could disguise himself as a human thanks to his abilities.





he said, “it might sound obvious, but like you, we are also governed by what you call the system.
”it was the first time that a monster mentioned the system since the giant snake imoogi.
“do you see the system window too?” sungwoo asked.
but the king shook his head, biting the cigarette pipe.
“no.
 we feel something like a god’s voice.
 should i call it what you call a quest? the system constantly forces me to have a sense of purpose, such as searching somewhere or attacking somebody.
 anyway…”he took the pipe off from his mouth and said, “it is bugging me.
 i wish it could be gone forever!”he expressed his dissatisfaction with the system vehemently.
 by expressing disbelief in the system, was he claiming that his race was different from ordinary monsters?he soon corrected his posture, sat with legs crossed, and put the pipe on his lap.
“okay, but that’s not important, right? i didn’t want to complain like this when i asked to meet you.
”finally, he seemed to cut to the chase.
“north korea?”“yeah, some damn guys in my neighborhood are sticking their heads out beyond my walls.
 don’t you think we have to think hard about it as someone living in the same territory?”“so, what’s going on on the north korean server?”when sungwoo asked, the king scratched his chin and continued.
“well, they have been sick for a long time.
 i guess the players didn’t respond properly.
 eventually, their server was destroyed.
”
it was shocking news.
“ruin?”“it’s over.
 their land is no longer owned by the players.
”what he meant by ‘over’ was the ‘end’ of the north korean server.
it seemed that the north korean server had reached the “bad ending.
”sungwoo knew that the apocalypse could happen more easily than expected because he had already witnessed various bad endings through the prophetic stone.
“the aftermath of that ruined land is gradually spreading.
 it started affecting this land some time ago.
 and the first effect was the appearance of a bunch of undead.
 so, i need you.
 when it comes to the dead, you are more expert than anyone else, right?”“is someone leading the undead now?”the man who controlled the undead was more important than the undead group.
when asked that question, the king looked straight into his eyes and replied briefly, “lich.
”“i expected him, too.
”sungwoo thought that if this was a guy who could control the undead like his army, he was most likely to have the same abilities as himself.
 and his guess was right.
“is he a player?”“no.
 he’s a monster like me.
”the guy was not in the same occupation group as the necromancer.
 maybe he was a monster born under certain conditions, just like the king of the great mountain who survived and became a mighty monster.
“but why are you trying to stop it?”
sungwoo was curious about the king’s intentions.
 monsters’ intentions were usually contrary to the players’.
 nonetheless, the king was reaching out to a player.
“uh? did you ask me why?”“if the north korean server’s lich is like you, aren’t you closer to him than a player?”the king laughed as if his question was absurd.
“well, i live on this land, too, right? some crazy guys are coming in hordes and trying to pillage our village.
 we should stop them, of course.
”was that the only reason? how could a monster like him ask the necromancer, a player, a favor for the stability of their living conditions?‘well, there is no reason that the king could not ask me a favor if he takes off the sunglasses called a monster… but i need to be more suspicious about his motivations.
’sungwoo was not sure what kind of trouble he would get into if he just trusted the king innocently.
but the king glanced at sungwoo, then grinned at him as if he understood something.
“honestly, i understand your position.
 it’s only natural that you can’t easily accept me when you sit and talk with a monster about our future, a being you had to kill blindly in the past.
 but…”he paused and looked at the two weretigers behind him.
“hey, guys, we just want to live happily, right?”they kept nodding.
 there was some unknown resentment in their eyes.
“of course!” one of them said.
“i don’t want to fight,” the other said.
the king replied, “um.
 but it doesn’t fit you to say that because you look like a monster.
”when he said that, the two tigers snorted as if they were dumbfounded.
“pardon? how come you are taking issue with our appearances?”“you look the same as us…”“stop it! you are so rude!”the king giggled at them, then picked up a potato from the basket.
 there was still steam rising from it.
“are we so different from other monsters? well, even if this was intended by the creator who made me, and even if he brainwashed me by whispering in my ears…” he said, taking a bite of the potato.
 “i just want to live a comfortable life while planting some potatoes and obtaining a stronger pot.
.
”what he said rang true.
at that moment, sungwoo thought, ‘is this guy like an npc?’come to think about it, npcs, one of the important elements of the game, had not appeared.
maybe the king of the great mountain could also serve as an npc.
only then did sungwoo feel relaxed and nod at him.
“good.
 if you give me more information about lich, let me take a look and deal with him.
”leaving the issue in north korea neglected would become a much bigger problem later.
 so, sungwoo needed to deal with it before things got out of control.
right at that moment, something started suddenly.
-(!)

there appeared a red exclamation mark before his eyes, which was not new to him.
“this?”“everyone can see this? yeah, that’s it!”jisu and hanho responded right away.
[mainstream start guide]* everybody, among the many servers in the world, only the korean server is continuing to move on in an extraordinary manner.
 for the first time they created the “third camp,” and the “world tree”, a transcendental being, is growing.
originally ‘chapter 4’ intended to cover the two absolute camps, angels and demons, but as the power of the two camps is not as strong as the korean server, it is inevitable that we have to issue a new mainstream.
 please prove in the hellish world that the extraordinary achievement of the korean server, which has made us issue another mainstream, has not been made by any ‘particular man,’[caution (important)]sungwoo, hanho, and jisu frowned, looking at the message.
“something bad happened?”while chewing the potato, the king of the great mountain looked at sungwoo and his friends with serious expressions.
 he looked quite interested.
sungwoo faced him and said, “you said you wanted to protect your house, right? this whole land, right?”“yeah.
 absolutely.
”“well, i can’t yet recognize you as my neighbor, so take this opportunity to play a landlord.
 it looks like the system doesn’t want to leave us alone.
 you will help us defend the korean server.
”having heard that, the king swallowed the remaining potato piece, with a smile in his eyes.
“um, don’t eat this potato.
 it’s not boiled enough.
 who boiled it?”then, he rolled up his sleeves.
 he sprang to his feet and looked down at sungwoo.


 