\section{chapter 143}






 jahon found it out after capturing and interrogating a player on the korean server.
he discovered that on the korean server, a hero named “necromancer” was showing an overwhelming performance, and he destroyed gen.
 ingong’s advance party.
“we were defeated twice already, and by the same guy at that.
 we’re not on good ground now.
 gen.
 chongon will be very mad about us.
”“…”“huei, kuan.
”the man in sunglasses and the long-haired man standing behind him lowered their heads when he called their names.
“yes!”“yes, general!”jahon sighed, full of discontent, then opened his mouth.
“our purpose is to take over that korean land first, but we need to spread glorious rumors about us in order to return to the chinese mainland in the future.
 you may be wondering why we need that, but don’t forget that gen.
 chongong has a bigger vision than we do.
”“of course, i understand his vision.
”“i am trying to understand his big vision.
”“by the way, you already broadcasted the scene of us being attacked, right? man, we became the subject of their ridicule.
 leeway, that spiritist bitch posted something on the bulletin board during that short moment, making fun of our gen.
 chongong…”jahon turned and grabbed the two men by the shoulders.

“we disgraced our general against our will.
 then, what should we do now? how can we recover our general’s reputation that we have disgraced?”“we need to create a scene of us defeating them.
 we have to show that we were attacked because we had bad luck,” said the long-haired man.
jahon nodded and said, “huei, that’s the right answer.
 we have to behead the necromancer and broadcast again in front of him.
 you see what i mean? what i mean is we have to get rid of the necromancer before gen.
 chongong comes back from occupying taiwan.
”“of course, i will!”“i will keep it in mind.
”jahon opened his mouth for the last time.
“prepare a mini game.
 infiltrate kanghwa island, register a mini game, and kill the necromancer.
 huei, can you sneak onto the island?”the long-haired man called huei nodded.
 and behind him those wearing long cloaks lined up.
 black driving suits were seen inside their long cloaks.
“that’s an easy job.
 even if he can watch us from the sky, he can see through the bottom of the sea.
”jaheon smiled for the first time and said, “good.
 activate a mini-game on kanghwa island, so that he can never run away.
 this is going to be a fatal battle.
 film all the scenes of us attacking him and show it to leeway and her players on the mainland.
”jahon turned and held the railing.
“he has only 50 undead at most? let me smash them to pieces, so they can never be resurrected.
”***when sungwoo bombed the pirates, he had a magic drone accompany him.
 as a result, the players on kyodong island could also watch the bombing from the sea.
terrible flying beasts moved in tandem, dropping the corpses into the correct position.

and at the right time, the corpses exploded, smashing the old ships and burying them under the sea.
 the pirates were also a huge group with discipline and a system in place, so they responded quickly and unfolded a large protective shield, but they already suffered considerable damage.
it was a perfect surprise attack.
“wow, necromancer! it’s quite true as i have heard that.
”“you bet!”“he smashed such a large number of boats in just a few minutes!”players, including muyon, could not help but admire the necromancer’s bold and brilliant performance during such a short time.
they were helplessly defeated even though hundreds of them risked their lives to defend against the pirates, but the necromancer already drove them out twice.
 in other words, the necromancer has saved their lives twice.
“if we follow this man, we will be able to win.
”“i want to take revenge after winning.
”“me, too.
 i feel like i want to kill them all and have a party over their bodies all the year round.
 son of a bitch!”the players who suffered painful damages caused by the pirates gnashed their teeth.
they were determined to stay on the island until the end, seeking revenge against the chinese pirates with the overwhelming hero called the necromancer.
a little later the necromancer and heyon, who successfully completed the first-strike operation, returned to the island.
 the leaders of the island, including muyon, came out hurriedly and greeted them.
“thank you.
 you were so amazing.
”“it was really awesome.
”however, sungwoo didn’t show off because he knew it was a one-sided victory, but it wasn’t a perfect victory.
‘the pirates are a bigger group than we think.
’during the first attack, sungwoo destroyed nearly 1,000 pirates.
 considering that the number of allies was only 814 during the final battle against the red orcs, it was a huge number.
however, the chinese pirates who came for the second invasion seemed to be twice that number.
 they mobilized a huge container ship for the players.
‘they are estimated at least 3,000.
’if so, what is the number of their main forces now attacking taiwan?after all, those from the chinese mainland did something big.
 since the start of the game, there were so many players killed in action that it was impossible to count their exact number, but as many as players also survived.
“although we mounted a massive attack against the chinese pirates, they are still up and running.
 they can lead a much larger army to attack us, or they can try to land with the current forces.
 besides, they might prepare defense against our air bombing.
”muyon said, nodding at his remarks, “i think we have to prepare for that in a hurry.
 while you were attacking them, we were done preparing to move to kanghwa island.
 minguk, have you filled up the trucks with gas?”“yes, brother.
 i packed everything and loaded the trucks.
 we can start right away.
”they were moving systematically, as if on cue.
 it was clear that they decided to fight the pirates.
sungwoo nodded, then said, “then, let’s go right away.
 i have to stop by the smithy you mentioned before.
”as soon as sungwoo said that, muyon turned and shouted, “start right away!”“start!”

“everyone, get in the truck!”players started to exit kanghwa island through kyodong avenue.
 just in case there would occur an contingency situation, heyon’s griffin and sungwoo’s flying undead flew around in the sky and escorted them.
there were a total of 258 survivors in the kyodong island group, but not everyone could fight.
according to muyeon, there were only about 100 people who could fight because a significant number of them were slaughtered during the chinese pirates’ first invasion.
‘anyway, i didn’t need a large number of combat troops.
’sungwoo was thinking of mobilizing the players of kyodong island for coastal surveillance.
 he could fight the pirates alone, but surveillance inevitably required a lot of manpower.
shortly after they safely passed kyodong ave, sungwoo stopped their trucks near the marine corps’ post and gathered the group’s players, including muyon in one place.
“just like we inflicted a huge damage to the chinese pirates, we could also suffer damages from their ambush.
 so, you have to closely monitor all coastlines.
”“as for surveillance, the coast of kanghwa island is wider than expected, but we are short-staffed right now.
 so, we have to think about how to make use of our personnel effectively.
”“brother, even if some of our survivors can’t fight, they can do surveillance, so why don’t we assign as many people as possible to the surveillance job?” minkuk said.
muyon agreed with him and said, “as he said, i’ll deploy all the personnel and all the equipment for surveillance.
 everyone is dreaming of taking revenge on the chinese pirates, so they will do their best.
”“yes, please.
 the pirates may dispatch a small number of people and attempt to monitor or ambush us.
 it would be impossible to block them completely, but at least you need to discover their invasion before their fleet approaches us.
”muyon immediately formed a group to patrol the coastal roads and moved them.
 he also took turns flying two magical drones.
 in fact, it was surprising that there were two high-end drones in this small group.
 it seemed that someone was lucky.
the rest of the players set up a camp in a place called the “kanghwa dolmen gymnasium.
”it was a new building with a fairly large stadium inside, so it was a suitable temporary residence for a large number of people.


 