\section{chapter 305}

it was natural that most of them hardened their expressions because they thought his demands were rather excessive.





"what did you say? four airships?"he asked for four airships, the core forces of the wpu.
naturally, many of the congressmen voiced their dissent.
"currently, there are only 5 airships that we can operate! even if we can repair the damaged ships today, we have less than ten airships.
.
.
""we can't give him the airships under any circumstances! without airships, you can't defeat the monsters and cartels coming up from mexico! we can't even organize a single fleet!"sungwoo was aware that the players of the wpu were very weak.
 so, if they lost the airship fleet, it was like them losing all their defense power.
 besides, seven of all the airships that wpu once owned already fell into the hands of the world tree camp.
it was only natural that the members of the provisional congress got so upset because they lost not only the three airships of the baker fleet including the messenger and the three airships of the washington fleet that were taken today.
"chairman, this is by no means a healthy alliance! our people won't accept it!""well, this is not an alliance relationship, but business, isn't it? i am already worried about how much more they will ask for in the future!" lots of congressmen here and there strongly argued that they should not hand over four airships to sungwoo, citing the specific logical reasons, but sungwoo just sat silent calmly.
'of course, my demand for four airships is excessive.
 but i should ask for more in order to get what i want.
'actually, that was the basics of any negotiation.
after that, they continued to debate about the pros and cons of handing over the four airships for more than an hour, and finally, sungwoo agreed to receive two small-sized airships and 200 million gold while pretending to make concessions to them.

if he had offered to receive only two airships from the beginning, he would have only been able to get only one.
'what a decent profit for my short trip to america!'recently, sungwoo spent lots of gold, but he didn't make as much revenue as he expected, so it seemed that he didn't have to worry about financial difficulties for some time.
when the meeting was over, the lawmakers were exhausted; they felt unhappy but at the same time relaxed at the final deal.
"oh, by the way…"at that moment, sungwoo opened his mouth.
the lawmakers hardened their faces again because they feared he might ask for something else, so they were pretty wary of him.
"i would like to stop by the dwarf workshop as a guest, and vip at that.
"his business trip in america was not over yet.
 he needed to check out something more.
***the "hearst workshop", which built airships and all sorts of high-end equipment, stood tall behind the capital.
 it was a rectangular gray building, so it made the capital building look rather drab behind it.
'it looks like a military factory is located behind the white house.
'by judging its location, sungwoo realized that the wpu regarded the hearst workshop as extremely important.

"wow, i feel like i'm looking at some ancient architecture.
 does the pyramid look like this?"when sungwoo looked at it from a distance, it looked just like a bulky gray mass, but when he approached it, he felt differently.
all kinds of patterns carved on the outer wall lit up one after another, flickering like a space station.
 it was a mysterious and gloomy, punk-like building.
"what the heck is that light?" hanho asked.
jonathan turned to hanho's question, and said, "the building itself contains blessing magic.
 that's why it triggers blessings as needed from time to time.
"obviously, it was not as good as the blessings of the world tree that gave blessings to the players' living and manufacturing capabilities, but they made and used the blessings of their own.
'in that respect, their manufacturing field is definitely ahead of ours.
'it was true that the blacksmiths of the world tree camp quickly reproduced the design of the airship when they repaired it, but the hearst workshop technicians were well ahead of them.
the interior of the workshop was no different from a typical factory.
 under the high ceiling, conveyor belt-like workbenches continued endlessly, and unknown equipment was hung from the frames attached to the wall.
clang! clang!various noises rang when sungwoo stepped further inside, creating a rough harmony.
 he felt like it was an orchestra playing bizarre songs with the metal and mechanical echoes resonating everywhere.
 and the leader of the workshop standing on the iron tower came into his view.
"hey, bastard! i clearly told you i would strike your head with the hammer if you open your mouth or turn your head when quenching, right?"an old latino man lifted a hammer over his head, spitting out abusive language.
conscious of his intense gaze, the blacksmiths in the workshop had no choice but to concentrate on their work.
"henry! you stupid bastard! whatever you do, i can see you clearly! you still don't know? huh? how dumb! is it because your brain is made of insulators and the neural circuits are not working?"the tower with an open slope, where he was yelling at the blacksmiths, was a structure that could monitor and supervise the entire factory like panopticon.
"at a first glance, that old man looks very stubborn.
""yeah, he has a nasty temper.
"when jonathan waved his hand toward the tower, the old man turned his head to him.
he wriggled his tough eyebrows and muttered something, which were apparently four letter words.
"how come you guys are here as a group without prior permission? i'm going to throw you all into the furnace if you don't…"when jonathan and his party went up to the tower, the old man sat down on an old iron chair and lit a cigar.
"oh my.
.
.
master hearst, have you not heard of the battle of the potomac river?""what is that?""well, there was a battle in washington dc.
 at the end of the day, chairman love took back her power.
 there was such a big commotion because of that.
 how come you are talking about decorum in this situation?"having heard that, master hearst, the master of this workshop, sneered at him.


"i don't care! as you know, this hearst workshop wasn't attacked at all.
 uh?"he began to throw a tantrum while tapping his shoulder with the emerald-colored hammer in his right hand.
"how could they destroyed all the airships that we had built by devoting ourselves for several months? is that true? our airships were broken easily like a startrek toy.
"".
.
.
""get lost! you guys, don't expect anything from us for the time being! it will be extremely for you wpu guys to see me rolling up my sleeves again for you! i won't do it again for you.
 never!"the old man acted as though he was not subordinate to the wpu.
 obviously, he was a man of great pride.
surprised by the old man's stubbornness, jonathan made an embarrassed expression.
so, sungwoo broke the ice by saying, "master hearst, i am not a wpu man.
 i've come here from outside the server.
 i would like to ask you to make some items.
"hearst changed his expression considerably to hear it.
"oh, you are the guy who smashed all the airships i made, right? let me see.
.
.
the winner and the loser are here at the same time? then…" he puffed out cigarette smoke for long, then said, "is this man rich?""yeah, very rich.
"he turned off the cigar in an ashtray, then stood up after dusting his hand off.
"okay, let's go to the counseling room.
"after all, it was money that could break his stubbornness.


 