\section{chapter 375}

chapter 375: exit from demon’s cavil and preparing to conquer china (7)the necromancer declared war on the chinese server and tested all players around the world.





a little later the gate of the demon’s cave was finally closed.
 it was the moment when the connection between the two worlds was completely cut off.
“alright, everybody, let’s get ready to go back!”led by kyungsoo, they began the post-war recovery work.
“a total of 98 people died.
 most of them were killed when the airship no.
 4 crashed.
”many players died during their attack on the demon’s cave, but considering the size of the enemy, the damage was not that big.
 for example, not a single member of the messenger crew who was out on the expedition was killed.
 the operation was a complete success.
“let’s prepare to tow the partially destroyed airship no.
 4 and move the supplies inside the ship to airship no.
 5.
”they loaded all supplies and troops onto the airship, while some of them began preparations to open the ‘hyper gate’ leading to suwon village.
“uh? necromancer?”at that moment, li wei visited sungwoo.
“to be honest, i was so impressed with your performance inside the demon’s cave.
 i never expected i would play second fiddle to you like this…”she continued with a rather awkward expression, “as i said before, i’ve come to you to find my subordinate spirits, but let me help you without any conditions.
”sungwoo nodded at her.
 given her power, she was welcome to join his forces.
 she once fought the monsters with sungwoo, so she was also reliable.

“oh, there are still lots of guys on chinese server 2 who are following me.
 if there is a war, they will come to help us.
”as she was once the head of the chinese server 2, it meant that if she joined sungwoo’s forces, she would add her chinese forces to sungwoo’s allies.
she said there were as many as one thousand who would help her at her order.
but li wei was not the only one who joined the world tree camp on this occasion.
“necromancer, we will continue to help you.
”the white wolf and the black lion, who were standing behind her, approached him.
“we’re not going to come to you when you need us, but we’re going to be with you all the time and use all our strength.
”“that’s right.
 we have committed lots of sins against you, so we’re going to pay back our indebtedness to you gradually in the future.
”the fact that they would also join sungwoo’s forces meant the addition of hundreds of human monsters to them.
 but this was not the end.
the players on jeju island also did not intend to break with the saviors of the necromancer and world tree camp players.
“hey, can you take us, too?”“please.
 please take care of us and our families…”
some of the players in jeju island that jimin had brought with her wanted to escape from this unstable land and join the world tree camp.
 but kyungsoo declined their request.
“i’m sorry, but we can’t afford to accept any more people right now because we’re preparing for another war soon.
 if you are in hardship, we can support you with the necessities of life.
 and…”kyungsoo then glanced at sungwoo who was talking with li wei, then said firmly, “we are not a charity and relief organization.
 once you have become capable enough to defend yourselves, you have to prove your worth to us.
 in other words, you have to be able to help someone, not a burden.
 when the time comes when you can, we would rather suggest to you that we work and fight together.
”the players in jeju island seemed a bit embarrassed but then silently nodded.
they survived in this hellish place of jeju island, which was blocked everywhere.
 although they were not as strong as the world tree camp players, they became stronger than before.
“i know what you mean.
 we will try to be mutually helpful someday.
”kyungsoo decided to provide them with an emergency contact number and give them a considerable amount of supplies.
as a matter of fact, sungwoo’s party captured a large amount of the materials collected by the ‘nine-tailed fox’ worshipers, so they would be able to grow rapidly for a while based on these supplies.
in the meantime, jimin was looking at her younger sister jisu with an awkward expression, who now felt different from before, then barely opened her mouth.
“jisu, our family members are alive in the safety area of aewol.
 how about coming back?”even though jisu had been voluntarily separated from her family for a long time, it didn’t mean she had no affection for them.
 jimin was really worried about her.
but jisu shook her head without any hesitation.
“i have no intention of going back to them yet.
 and it’s not yet the right time to go back.
”jimin nodded as if she expected her sister would answer like that.
“yeah, i feel that you are an essential member of sungwoo’s forces for the next war.
 so i can’t tell you to avoid this fight.
”jimin smiled faintly and nodded.
she continued, “our family members, especially dad, will think the world of you.
 you may find me flattering you, but you have become a hero!”“…”“so i am more concerned.
 please don’t die.
 you should come back and show off to our family members, right?’she then tried to say a little more, but sungwoo announced something through the loudspeaker from behind jisu.
“the hypergate is open! we’re leaving soon!”jisu lightly nodded and turned around.
 finally, it was time for her to return to the world tree camp***the world tree fleet returned to the sunwon village.
 the players did maintenance work on the fleet.
 sungwoo sorted out the items he collected from the demon’s cave.


the outcomes of sungwoo and his allies’ attack on the demon’s cave were remarkable.
 since they had picked up a lot of high-level equipment from the other world, it seemed like they obtained more rewards than before.
“sungwoo, there is a message for you from america.
”at that moment, kyungsoo came and told him that he had a message from the wpu of the american server.
“they said they also watched the broadcast.
 and they conveyed lots of news that they could not deliver to us until now.
’as a different server, the wpu was in america across the pacific ocean, but they were able to communicate with each other in real-time.
 the airships that they once owned were equipped with remote telecommunication devices, so they communicated through them.
“it looks like they are not onlookers.
 according to them, they have agreed to form a strategic alliance for peace with not only three american servers but the canadian server and alaskan server.
 all of them expressed their support for us at the world tree camp.
”as expected, chairman love’s leadership was remarkable.
 even though the whole world was engulfed in war, she bound the two americas in peace.
of course, she could do it because they felt friendly toward each other even before the game started.
but the problem was that they could not even communicate with the mexican server, though.
“by the way, we have some bad news.
 the attacks by the cartel coming from the mexican server are still going on, but there is some ominous sign in their activities.
”

 