\section{chapter 168}

                             




sungwoo could not continue the fight any longer.
-grim reaper retention time (00:3:30)-werewolf retention time (00:4:46)‘i’ve got only three minutes left.
 should i leave this place for the remaining time?’then, the white wolf’s body looked somewhat strange.
“kuuuuuuuh….
”the only thing the monster did after appearing was push sungwoo aside, but he grabbed his chest and kneeled.
 he seemed to be in a very bad physical condition.
“sungwoo, what happened?”“we have to run away right now.
”“pardon? what the hell is going on?”another situation happened before hanho heard from sungwoo about what had happened.
pajeeeeek! pajeeeeeeee!blue lightning fell from the sky.
 it was not just a single flash, but dozens of lightning bolts rained down like a waterfall.
‘is it lightning?’intense light obscured everyone’s vision.
 sungwoo had no choice but to turn his head and close his eyes.
“argh! what the heck is this all of a sudden?”“did anything explode?”the intense ray of light stopped, and everybody could see again gradually.
chee- cheeeee-and there appeared something where the lightning fell.
 a man wearing black leather armor and holding a huge wooden cane was standing there.
-your body function is weakened due to an unknown spirit.
 (as the two spirits collide, you are affected by a stronger wave.
)
* all stats decrease.
 (-5)“necromancer, why is it so hard for me to come and see you? you’re the best star on the korean server, as expected.
”kangsok han, the no.
 1, appeared.
 and beneath his feet was a red bear’s head.
“you bet! hey, why are you making such a big fuss from a distance? we killed this werebull running wildly with a crazy scream!”at that moment, the fairy soared from his shoulder and looked around.
“man, that is a red tongue, sungwoo!”the werebull’s eyes were pointing at the bear’s head under kangsok’s feet.
given the reaction, it looked like the cut head was one of the beheaded ‘four human beasts’.
“hurry up! shoot your lightning mace!”at that moment, a huge object began to move on the street facing the school.
 it looked like a cannon, but sungwoo noticed it was a dreadful flying weapon that the monsters had been hiding until now.
wuuuuuuuuuuuh-its huge muzzle rotated and aimed at them.
 a considerable amount of current flew through the long barrel and sparks splattered in all directions.
 the current concentrated into one sphere.
 it was the moment when a bullet with destructive power enough to blow up a building was being created.
at that moment, the light flashed.
 the bullet flew at a speed that human eyes couldn’t follow.
 its target was kangsok.
“…”but kangsok didn’t move.
 all he did was gently lift his cane.
the electric sphere stopped in the air.
“what the heck is that?“i can’t believe it!”kangsok swung his cane.
 the electric sphere began to rotate at high speed to the right, then in the next moment, it reversed.
bang!the flying weapon was hit by the bullet it shot, thrown back, and rolled across the street before hitting a building.
in no time, kangsok struck the ground with his cane.

with just one flash, a ray of lightning fell from the sky.
bang!its target was the white wolf.
 the monster hastily lifted his cane and created a protective shield over his head.
quan-ang! cheeeeeee-kangsok’s lightning and the white wolf’s shield collided.
 a tremendous amount of energy was scattered in all directions, creating a colorful spectrum.
“argh!”the white wolf staggered, as if it suffered huge damage, although he blocked the lightning.
“who the hell are you…?”“i’m no.
 1 in the korean server ranking.
”“you must be kangsok han!”“you’re right.
 so, i think you and i are going to see some failure today.
”the white wolf turned to sungwoo, frowning.
“and the necromancer.
”although the monster had seen him in his memory, it was his first time encountering the necromancer like this.
there was murderous energy in his eyes.
 he suffered lots of damage due to the necromancer’s attack several times.
 that’s why he mobilized a formidable force to kill the necromancer, but he was again defeated.
“let’s go.
 let me look forward to fighting you next time.
”mumbling like that, the monster lifted his cane.
 then, a portal opened behind him.
it was clear that the werebull and the white wolf were trying to escape through the portal.
however, sungwoo did not intend to let them flee like that.
sungwoo signaled to minsok with a glance.
the moment the two disappeared into the portal, minsok immediately threw a black chain and wound around the ankles of the werebull.
 when minsok pulled it hard, the monster’s exhausted body was dragged out.
“oh, no!”the white wolf reached out but it was late.
 he was already sucked inside the portal.
 in no time, the portal was closed.
“krrrrrrrrrrrrr….
”the werebull blankly looked into the air where the portal existed.
then a black wolf holding a huge scythe appeared in front of him.
***with the retention time of the werewolf was over, sungwoo’s demigod status was canceled.
-strong power has escaped from your body and all stats decrease for 24 hours.
 (-10)and a penalty was given for his gaining such tremendous power for some time.
“ugh…”in addition to a sharp decrease in stats, sungwoo felt tremendous fatigue.
 he felt like he was going to collapse into sleep.
but he couldn’t.
 an unexpected visitor, kangsok, approached him.
“you were hiding something terrific,” he said.
kangsok was also a demigod.
 and unlike sungwoo, the power he gained was not temporary.
“well, i just stopped by here to say hello to you, but some monsters greeted me instead.
”“you came here to say hello to me?” asked sungwoo, casting a suspicious glance.
kangsok chuckled and said, “i’m serious.
 as far as i know, this is not the only hell gate.
 so, i hope you and i can keep cooperating.
 man, i now know why you are so famous.
 terrific.
 i was amazed you killed the monster only two minutes slower than me… yeah, by a hair’s breadth.
”“…”“of course, i enjoy playing alone, but this game often compels me to socialize with somebody else,” kangsok said, passing by him.
then, he whistled while looking at the playground.
“given the choice, isn’t it good if you have a friend who can keep up with you? right?”“what is a demigod?” sungwoo asked directly what he was curious about.


“huh? you just played that role in person, didn’t you?”“then, is this your job?”kangsok shook his head, and said, “demigod is not a job.
 it’s a power you can obtain by satisfying special conditions.
 i also obtained it by meeting such conditions.
 you seem to have obtained it temporarily, but i don’t know how to get full strength.
 you have to know it yourself.
”he smiled faintly.
 it seemed he didn’t want to talk about it in detail.
 he said he wanted to keep up cooperation with sungwoo, but it was clear that he regarded sungwoo as his rival.
“well, see you next time.
”“goodbye! see you soon!” said the fairy, nabi, flying in the air.
at that moment, his body disappeared into the beam of light.
 it was his teleport skill.
‘did he really come here to help me, or did he come to confirm that i also got the demigod status?’sungwoo was not sure of that.
then, another visitor arrived.
doo doo doo!three helicopters flew in from the northern sky.
 the crusader team arrived a bit later than kangsok.
“we’re landing! we’re landing!!”they deployed magic drones in all directions to monitor the whole area, while its crews landed at wide intervals to keep vigilant of their surroundings.
soon, a helicopter landed, where junghoon, fully armed, appeared.
while looking around, he looked somewhat embarrassed because he never expected that the fight would be over even before he arrived, no matter how strong the necromancer was.
“we are very late.
 sorry, we couldn’t help.
”“well, the surveillance team’s intelligence was of great help.
 thanks to the helicopter, i can get a ride.
 i’m a bit tired now.
”sungwoo couldn’t hide the fatigue after he escaped from the demigod condition.
but there was one incident after another.
“i’ve got more news for you.
 ‘angel’s stone statue’ was unearthed in seoul.
”the traces of the absolute race finally appeared.


 