\section{chapter 310}

sungwoo's election as the representative of the korean server was a very significant event.





it was also a moment when the leader was elected in a very fair manner, with all the survivors in korea participating in the election.
 maybe sungwoo's selection was natural because he was the one and only man who proved his ability to protect the korean server several times.
"wow! congratulations!""you have a lot on your shoulder now.
 congratulations anyway.
"everyone congratulated him, but sungwoo was not that happy.
 first of all, he didn't want that position.
 in some respects, he took over because of necessity.
 so, he was supposed to feel a sense of responsibility rather than glory.
immediately after he was elected the server master, the messages he received stressed his responsibility.
-you have taken the initiative because your opponent (chinese server) has declared war.
* your opponent is currently choosing the method of war (battlefield, war type).
 once they have made the selection, the war begins 24 hours later.
* as the server master you can choose to 'surrender' (caution! in this case, your server becomes the opponent's colony.
) 'method of war?'as was the case with the korean and japanese war before, the upcoming war between the korean server and the chinese server was not a usual war.
there were set rules, and they should fight according to the established rules.
 this kind of war method was really annoying and troublesome.

'because i don't know which method they are going to choose, i can't make any decisions right away.
 what's more, do they decide on the battlefield, too?'there was one addition added when they waged the korean-japanese war, which was that the one who took the initiative would decide on the 'type' of the war, but also its 'battlefield.
''if so, there might be a possibility that we could be dragged to mainland china for this war.
'if the china server wanted a war that was extremely favorable to them, they could drag the korean server led by the necromance into their backyard.
in that case, the korean server players would not have to worry a lot about the destruction of the korean server's infrastructure by the chinese server, but if they were annihilated by the chinese server in their backyard, their infrastructure would be totally handed over to the enemy server.
'everything is uncertain now.
 it is necessary to find out the movement of the enemy a little more to grasp the exact situation.
 i need more information.
'sungwoo summoned his staff and ordered them to collect as much information as possible about the chinese server.
"it is also important to mobilize a lot of troops, but it's more important to gather information on how the enemy will move.
 please collect as much information about the enemy as you can.
""sure.
 in fact, we are working closely with the hunter company to receive all the relevant information in real-time.
"the hunter company had been actively collecting all kinds of information due to the nature of its business so far, including information about overseas servers.
as part of their efforts, the hunter company dispatched informants not only to korea but also to china and japan.
 as a result, the informants were playing a crucial role in this important situation.
 "sungwoo! this is an intelligence report from the liberation guild.
 damn it, there are 5,000 troops being mobilized on the outskirts of beijing!"
in addition, the liberation guild was also busy collecting intelligence on their own, led by their wide area surveillance team.
"i don't know how many of them will gather because they keep gathering, but given that they are gathering at full speed, they are going to decide on the type of war and the battlefield.
"when sungwoo put together all the pieces of intelligence from all the servers, he began to grasp the situation to some extent.
 first of all, the size of the chinese server troops was significant.
"another piece of intelligence from beijing just got in.
 our informant found out there was an additional force near beijing, so currently, there are a total of 9,000 troops.
 more will likely join them.
"a whopping 9,000 troops, but it was just the tip of the iceberg.
"we have information the hunter company has obtained from the okinawa server! the "kyushu unified army" who previously survived during the kyushu battle became pirates later.
 according to the intelligence, they were taken over by the chinese server! they are estimated to be about 1,000!""according to our mole, admiral baker's fleet was observed in the west sea.
 it is believed that they contacted a chinese container ship two hours ago.
"kyoungsu let out a sigh after receiving a series of intelligence reports about the enemy's movement.
 the chinese server was reaching out not only to japan but also to the united states.
 when sungwoo heard all the reports, he recalled somebody's face suddenly and said, "come to think of it, the hunters from siberia survived and escaped.
 maybe they will also get involved in this war.
"if they intervened in the war, sungwoo's allies would have to fight against the coalition forces of america, china, russia, and japan.
in particular, the addition of tsar, the russian monster, would be a huge headache for sungwoo.
"oh, my god.
.
.
 we have so many enemies," kyungsoo lamented.
 but sungwoo responded calmly to his worries.
"it's a chance for us to wipe out all of them on this occasion.
""yeah, i think so.
 do you think we can beat them all?"sungwoo nodded silently.
"we have to not only wipe them out once and for all.
 otherwise, we're eventually going to be killed by the dragon.
"they were now in a ridiculous situation.
 but they had no choice but to regard this upcoming war as training to stop a bigger catastrophe, for their victory without growth will only be a mere extension of their lives.
and finally, the signal of the war rang.
-your opponent has chosen the method of war (type, battlefield).
***shortly after the message about the war method rang, the staff of the world tree camp gathered in the conference room.
"um.
.
.
 what does this mean?"kyungsoo scratched his chin while looking at the message in the air.
[war method (important)]

-battlefield: suwon, seoul, busan-type: split and merge1) the battlefield is divided into 3 locations (suwon, seoul, and busan), and the battles take place at the same time in all places.
2) whenever you win on a battlefield, 'strong buffs' are given to the entire server.
3) a 'portal' opens for you to move to another battlefield once you win in one battlefield.
 the type of war that they chose after careful consideration was pretty unusual.
 they were supposed to wage the war in three places at the same time, but the war was supposed to be getting endlessly favorable to the one who won first.
"why did they choose such a war type? they must have a wicked reason, right?"when kyungsoo asked, inho replied, "well, this is obvious.
 they intend to separate the necromancer from the rest of the troops.
 they are going to fight against and beat us in each battlefield, then they merge at the end of the day to beat the necromancer, backed up by strong buffs.
"jisu nodded and said, "it seems that they can unconditionally beat other korean server troops that don't include the necromancer.
""how arrogant they are! but the problem is we don't have any good options right now.
 as you know, sungwoo can't fight in three different battlefields.
"

 