\section{chapter 369}

chapter 369: exit from demon’s cave and preparing to conquer china (1)the world eater was the heart of the demon’s cave.
 therefore, the world eater’s death directly led to the collapse of the demon’s cave, and its gate, which had been opened in the chinese server, beijing, also began to close slowly.





“uh? what the heck is this?”the agents guarding the gate of the demon’s cave immediately noticed something abnormal in the gate.
“hey, look here! the portal is contracting.
”the door of the demon’s cave, which had been always open in preparation for the attack on the korean server, started to shrink with a different noise than before.
“i wonder if the portal is closing.
”“what? it shouldn’t be, right?”this abnormal phenomenon was immediately reported to the capital strategic control department, which oversaw the defense and administration of beijing.
“what are you talking about? stop that bullsh*t!”it was only natural that the head of the capital strategic control department, who was in charge of management, distorted his face because something went wrong with their best strategic weapon.
then, an additional report came in.
“control manager! a report from building 3 was just in.
 two of the gates have been completely closed and the rest are likely to be closed soon!”the control manager jumped up from his seat.
“i’m asking you again! why are they being shut down? don’t you know that this is a very serious matter? the emperor ordered us to keep the gates open all the time!”
“yeah, we all know that.
 we have been in charge of the security of the building, so we don’t know about the technical issues…”in fact, since the head of the control department was also the head of this organization, he knew that it was impossible to determine why the gate of the demon’s cave was closed.
“damn it! i guess only his majesty, the emperor, knows what the problem is.
 report it to taegam, the chief of the royal security service, right now!”only the ‘emperor’ could contact the demon’s cave.
 if there had been a problem with the gate of the demon’s cave, the emperor must have already noticed it.
“sh*t! what the hell is going on inside that horrible hole?”when the head of the control department was at a loss what to do, taegam, the royal security chief, visited him unexpectedly.
 startled by his unexpected visit, the control manager sprang to his feet.
“uh? ah! taegam, you came to see me in person!”taegam was a short, middle-aged man.
 he looked around the control manager’s office once, then returned his greetings belatedly.
“control manager, thanks for your work late into the night.
”the control manager bent over and trembled before him.
“i should have reported to you first, but i was so busy checking the situation.
”taegam, the chief of the royal security service for the emperor, was recognized as the emperor’s right-hand man after general singh was killed.
‘why is this guy here all of a sudden? i might be killed if i make a mistake.
’
even when gen.
 singh was still alive, taegam served as the emperor’s eyes and ears as his closest vassal.
 because of that, the players in the chinese empire believed that taegam was the emperor’s representative.
“anyway, his majesty has ordered me to check the situation in person.
 but don’t worry because i’m not here for that reason.
”“oh, yes! i will serve you tea right away.
”the control manager checked taegam’s expression because he thought that if the emperor was upset about this incident and wanted to hold him accountable for it, he could notice some kind of emotions in taegam’s expression.
“taegam, then the emperor has already grasped the situation, right?”“exactly.
 it seems that he lost contact with the other world, but he was agonizing over the cause of the incident.
”fortunately, there seemed to be some other reason for the closure of the gate.
the control manager felt relieved but raised his eyes as if he was quite surprised.
“then, what should we do in the future? it was the most important strategic weapon with which we could defend against the barbarians’ coming invasion.
”at that moment, taegam placed his hand on the head of the control manager.
the control manager was startled, but taegam tapped him on the shoulder as if to soothe him.
“don’t worry, control manager.
 the gate of the demon’s cave was one of the nine gates, so the other gates are all safe.
 we will be able to subdue the enemy with our own strength.
”“i feel relieved to hear that.
 but do you really think we have no problem?”when he asked repeatedly, taegam tightened his grip on the control manager’s shoulder.
obviously, he was upset.
“don’t you know that the royal security service is collecting and digesting almost all the important intelligence? since we have grasped all the details about the necromancer’s power, i can say this to you confidently like this.
”“ah! absolutely! sorry, i’m so dumb!”the royal security service was none other than the security forces directly responsible to the emperor.
 taegam seemed to feel more secure and relaxed than usual.
“hmm, you must have heard that when we were planning to conquer korea, we thought hard about everything with the possibility of general singh’s defeat in mind.
 of course, we thought the chances of his defeat were very slim, and i never expected he would be devastated like that…”as taegam said, when general singh led a large expedition to conquer the korean server and the entire chinese server was drunk with the prospects of the general’s early victory, the royal security service was preparing for the next war without slacking off.
“anyway, regardless of the general’s defeat, we consider it to be an important achievement that we have clearly understood and analyzed all the strength of the korean server through that battle.
”taegam took his hand off the control manager’s shoulder, then put his hand on the back, and headed to the window.
this was a penthouse in a high-rise building in the middle of beijing, so he could see the panoramic view of downtown at a glance.
“i hear that the undead soldiers under the necromancer are an immortal army that will be hard for us to deal with, but they are only two hundred or so, right? even if they keep growing, i guess they won’t be over several dozen…”taegam stood in front of the window, where his smile was reflected.
“with that kind of firepower, he can never occupy beijing.
 and…”

he raised his index finger and pointed it somewhere out the window.
 the control manager raised his eyes and looked at that.
“since we have that thing over there, we can definitely win.
”a huge circular object floated in the place that taegam pointed at.
when he looked into it squarely, a message appeared before his eyes.
- ‘divine power’ is filling the area.
the huge circular object was emitting white light like an artificial sun.
it was the size of a huge amphitheater, but it was also an item.
in other words, it was an extra-large item that created and released a ‘holy field’ in the affected area by producing and releasing the so-called ‘white light sphere’.
it was an object that had been floating in the sky for a few days.
 it was the first time even the head of the control department saw it glowing like that.
after the gate of the demon’s cave was closed, it seemed to have started operating in preparation for the necromancer’s surprise attack.
“it will fill the whole city of beijing with holiness.
”of course, all of those who dealt with the necromancer were aware of the fact that divine power was fatal to him.
 however, priests were rarer than expected, so it was impossible for priests to keep using the holy magic that was strong enough to exterminate the necromancer’s undead army.
 however, taegam gathered the vast resources of the chinese continent to inflict fatal damage to the necromancer.
“in other words, as long as we have that divine power there, the necromancer’s undead army will lose their immortal power, and from that moment on, they will turn into meaningless creatures.
”

 