\section{chapter 350}

chapter 350: jeju island and attack on demon’s cave (14)this chapter is updated by wuxiahere.
com




five seconds before the explosion, the moment the troll skeletons threw their fully swollen corpses over their heads, sungwoo said quietly, “manufacture bone weapons.
”then, a dozen corpses of monsters and some troll skeletons stuck on the shield were dismantled before being reassembled together.
 and a huge ‘cover’ was made, completely covering the messenger.
“everybody, duck!”right after sungwoo shouted, a huge flame exploded above the messenger.
a tremendous amount of heat rose from the curved cover, then soared in one direction, namely towards the hordes of monsters.
bang! bang!everyone on the deck fell apart.
 the explosion was obviously destructive enough to crush everything in the area, but the messenger survived because the bone cover mitigated the impact.
 the messenger bounced a few dozen meters before it re-balanced.
then, lots of messages began to appear one after another before sungwoo’s eyes.
– you have obtained 850,000 gold by hunting an ‘alien creature’ (intermediate monster)’.
– you have obtained 850,000 gold by hunting an ‘alien creature’ (intermediate monster)’.
– you have obtained 850,000 gold by hunting an ‘alien creature’ (intermediate monster)’.
– you have obtained 850,000 gold by hunting an ‘alien creature’ (intermediate monster)’.
– you have obtained 850,000 gold by hunting an ‘alien creature’ (intermediate monster)’.
an endless stream of messages that announced sungwoo’s successful hunting rang.
– you have leveled up.
 (lv.
 24)finally, his level went up by one level.
an overwhelming explosion exploded under the shadow of the world tree.
bang!it was probably the most powerful explosion in the vicinity of the world tree since there was a hole in the world tree.

sungwoo murmured, ‘i’ve hunted only 90.
’obviously, the explosion melted lots of demons, but they were too small.
fortunately, the intense heat of the explosion pushed the hordes of monsters far away.
the messenger came out through the black smoke when the monsters were pushed away then sailed at full speed.
 the only way they could retreat was to break through the hole in the middle of the world tree and enter it.
 however, the predators of the demon’s cave did not give up easily, perhaps because they discovered prey after a long time.
“they are sticking around us again!”one of the crew shouted, opening the window of the control room.
sungwoo was also watching their movements carefully.
“sail at full speed! never stop!”“okay!”sungwoo, li wei, and hanho ran to the stern deck.
“oh my god… there are so many of them out there!”surprised by the explosion, the monsters who scattered came to their senses and united again, but they were already right behind sungwoo’s allies only dozens of meters away.
they looked like a wave in a storm about to rush towards the stern of the messenger at any moment and swallow the ship in one bite.
“is there another way to push them back?”sungwoo lifted the grim reaper without even having time to answer li wei’s question.
 ihe had to do something.
– ‘evil spirit bombing’ is embedded in your weapon.
 (max)among the skills that sungwoo could use, ‘evil spirit bombing’ was by far the best in terms of single skill damage.
however, the damage range was not as wide as that of the ‘corpse explosion’, so it was not suitable for confronting a large number of enemies.
‘i can’t afford to argue over which is better now.
’
so, sungwoo swung the grim reaper widely and scattered the ‘evil spirit bombing’ as widely as possible.
gugugugugugugugu-sungwoo succeeded in hitting the monsters at the forefront, dropping about 20 of them.
but he didn’t stop there.
“explode!”he triggered ‘corpse explosion’ on the 20 monsters that were killed a little while ago.
bang! bang! bang! bang! bang!with the explosions spreading over hundreds of meters across the sky, they staggered.
however, compared to the high-pressure explosion, which required 30 seconds to expand, this explosion did not do much damage.
‘but i bought some time anyway.
’what he needed to do right now was to stop them from approaching, not to kill them.
in that respect, that was a success.
 as if they were shocked by the previous gigantic explosion, they instinctively twisted their bodies at the relatively small explosion, which delayed their pursuit of sungwoo’s party.
“sungwoo! they’re finally arriving here!” hanho shouted.
finally, there was a dark shadow over their heads.
 with the world tree behind him, sungwoo raised his head.
 it was like a steep cliff.
 it stretched endlessly up to the clouds, giving him the illusion that it was about to touch the bridge of his nose due to the distortion of his vision.
bang!the messenger squeezed into the hole of the world tree violently.
kwagagagaga-it landed roughly because of its acceleration, but sungwoo jumped to the ground before the airship stopped.
 the ground was rough and wet.
sungwoo immediately ran towards the hole.
kheeeeeeeeeeee!a black shadow fell over the hole.
 it looked like it was going to squeeze into it at any moment.
but sungwoo stretched out his hands towards it.
“manufacture bone weapon!”fortunately, when he summoned victor, he used the skill ‘manufacture bone weapon’ at the same time.
 using that, he started making a bone sculpture to fill the entrance.
 he needed a stronger shield than the one he had previously covered the messenger ship.
the troll skeletons behind him were disassembled on the deck of the messenger, then passed over sungwoo’s head and began to merge into one near the hole.
they were firmly stuck on the shells of the world tree and intertwined, forming a gigantic ‘bone gate’ that could close the hole completely.
‘but this is not enough.
’sungwoo immediately took out ‘winter predator’, changed it to ‘expansion mode’, and sprayed it over the bone door.
fifty bullets were stuck to the bone door, forming a thick layer of ice in an instant.
it was like pouring concrete onto a steel frame.
 it was simple, but harder than most concrete walls because it contained magic.
“everybody, get off quickly!”“we have no time! move quickly!”soon, the crew started jumping off the messenger.
 some of them ran towards the bone door.
“use any skill that can block the entrance!”freeze-type and rock-type wizards rushed in and began to empower the entrance sungwoo blocked.
 li wei also summoned a water spirit and placed a layer of shield over it.
while the crew took additional measures, sungwoo visited the black lion.
“what about the heart of the demon’s cave and its location?”the black lion lowered his head and looked down at the ground.
“it’s right down here.
 but i can’t find the passage to the bottom.
 i’ve only found its location.
”

sungwoo nodded.
 he had no choice but to find it himself.
if there was no way down, it would be a disaster, but there was no other way than to come in here anyway.
thud! thud! thud!the sound of the monsters knocking on the door and scratching outside echoed through the hole.
 the crew hurriedly dispersed and searched the inside of the hole without feeling anxious.
at that moment, somebody shouted.
“i’ve found it! there is a passage downstairs!”it didn’t take them long to find the passage.
“but it’s too deep and dark.
”when they checked it by sending a spark of magic down there, it was a vertical passage of about 20 meters.
“we need equipment to get down.
 we can install it in 3 minutes.
”the technicians started installing the device for rappelling, and sungwoo looked around.
‘by the way, what the hell made a hole in the world tree?’no matter how hard he thought about it, he had no idea what could possibly create such a huge cavernous hole.
at that moment, he noticed a hollow place on the inner wall of the hole, which was about 100 meters above it.
 given the circumstantial evidence here, it seemed that something pierced the surface of the world tree and made this hole before bumping into it.
‘something flashed a moment ago?’he wasn’t sure, but something seemed to reflect the light of a flashlight from the center of the hollow.
 but he had no time to check it.
“we’re ready to go down!”bang!“the entrance may be broken open soon!”before this hole could turn into a mixer barrel and grind the entire crew of the messenger, they had to go further down.


 