\section{chapter 339}

chapter 339: jeju island and attack on demon’s cave (3)someone who recognized jisu appeared among the fanatics.





“hey, i’m taesoo kang.
 i would feel sad if you pretend not to recognize me when we’re from the same high school.
”jisoo reluctantly nodded.
 it seemed that they met a man here, who didn’t have a good relationship with jisu.
“oh, hi!”“hey, you are much prettier than before!”“…”“are you here to see your family?”jisu gently raised her head when taesu mentioned her family.
“not really.
 by the way, are they still alive?”taesu smiled vacantly.
 there was contempt in his lonely eyes.
“ah, well, i’m sorry to tell you this, but in this sanctuary, no one without faith can survive.
”“then, are they all dead?”“um, well, i set fire to your gym.
”having said that, he giggled heartily.
 his fellows also giggled like him.
obviously, they were insane.
“…”there was no big change in jisu’s expression.
but taesu continued, “your family really sucks! you know what? the children of your family harassed many students because they had strong builds.
 i really wanted to kill you for a long time.
 by the way, you also hated your family, right? you were born of a different mother, right?”“oh, what the heck is that? are you sure?”
“man, this is the worst family!”“well, her family was notorious among many students.
 her father used to run a martial arts center in front of the school, but he womanized from time to time…”sungwoo could not stand hearing it any longer, so he cut off taesu right away.
“i’m not going to talk with you any longer.
 step aside or be killed.
 choose one.
”although sungwoo warned them strongly, there was only anger and contempt on their faces.
it was not certain whether they didn’t know what’s going on in the outside world or whether they really didn’t know sungwoo’s party at all.
“okay, then you die.
”sungwoo didn’t want to persuade them anymore.
 so, he pulled out his hand cannon, and at the same time, those on the deck raised their weapons.
heeeeeeeeeeeee!at that moment, hippogriff light burst out and wrapped their bodies.
 it was a white shield.
‘um, they had something to rely on.
’at first, sungwoo felt it strange that they landed on the airship obediently, and he now knew they were confident of escaping from the airship easily.
sungwoo pulled down the ‘winter predator’ tied to his back.
 then, he aimed his gun at the flying hippogriff.
 he was going to aim for the moment when the shield was taken off.
but someone was faster than sungwoo.
 someone jumped out from behind him.
 she was jisu.
“let me do it!”she sprinted across the deck in an instant, then jumped after stepping on the front of the airship.
 she threw her body out of the airship towards the wide sky.
all of a sudden, her body was equipped with dark red full-body armor.
 it was the power of valkyrie.
heeeeeeeeeeeeeeee!
however, the speed of hippogriff’s flying was extraordinary.
 when he spurted up the deck like a horse and spread his wings like an eagle, he jumped dozens of meters at once.
 it seemed impossible for anybody to catch up with him until jisu disappeared in the sky.
huuuuuuuuuung-her body appeared in the distant sky right before the ranks of hippogriff.
 it looked like she teleported there, but she didn’t.
 nor was it the ‘shadow tracking’ skill that sungwoo used to know.
then, everything between those two points lost their heads.
 regardless of humans or animals, they lost their strength and fell to the ground helplessly.
“oh, my god!”“what happened a moment ago?”she didn’t teleport.
 her body itself was shot like a flash of light then penetrated the enemy.
during that short moment, her sword drew a huge trajectory, and a long line of blood stretched out into the blue sky along the trajectory.
‘she is fighting better than i think.
 her lethal power has reached its peak.
’sungwoo heard that she beheaded hundreds of enemies on the seoul battlefield.
 this was the power of the ‘valkyrie’ that even sungwoo had never seen directly.
tung-jisoo flew like a flash of light again and landed on the airship.
 and she threw someone onto the deck.
 he was taesu“ugh! who the hell are you?”while slaughtering the enemies in the air at once, she accurately picked and captured only taesu.
“it’s been a long time since we met, so wouldn’t it be a pity for us to break up like this?”at that moment, sirens began to ring on the ground.
“you have earned the wrath of god! you’re going to be donated as sacrifices without any exception! hahaha.
”taesu giggled at her, crouching.
“it looks like there were troops on the ground watching us.
 well, of course, it’s no wonder.
”soon, more hippogriffs were flying into the sky.
inho said, lamenting over that scene, “oh my…it looks like they don’t know which way the wind is blowing now.
 how can i treat these psychopaths?”sungwoo looked down at the lake in mt.
 halla.
there was one sure medicine for these types of patients.
“you have to show that there is no god.
”in other words, he was going to kill the god.
the ignorance of a group sometimes turned into their courage.
 but it is very likely that such a phenomenon ended up being the beginning of a miserable history.
“well, they could be considered a considerable air force, but…”as inho said, hundreds of hippogriffs flew up from jeju island.
obviously, they were part of their air force which was so huge that sungwoo could not ignore it.
“however, they won’t beat us.
”it was because of their recklessness that they attacked sungwoo and his allies just because they didn’t know the level of the necromancer and the world tree camp.
the world tree fleet, which defeated wpu’s baker fleet and washington fleet and absorbed their power, was clearly the strongest force in the world.
sungwoo mobilized only three airships for this operation, but they were more than enough.
“cannons in all airships are ready to fire!”“fire!”at inho’s command, the cannons mounted on the three airships turned their heads.


then, they shot cannons at the hippogriffs flying like a swarm of bees, which were powerful enough to shake off their illusions at once.
bang! bang! bang! bang! bang!hippogriff units dispersed widely in the sky, but the far-reaching explosions engulfed them right away.
just like the wasps falling after they were sprayed with pesticides, the hippogriffs lost their balance and fell to the ground helplessly.
“they are hit on the mark! we shot lots of them down!”still, they didn’t back down.
 rather, they sped up and charged at sungwoo’s army.
“oh my…how reckless they are! it looks like they think they can beat us at close range.
 they might have thought of landing on the airships to fight us empty-handed.
”sungwoo stood up and said, “then, let me confront them.
”if the enemies landed on the airship for hand-to-hand fighting, the battle would be really troublesome because it would result in harming sungwoo’s forces.
 the best way to stop them was for sungwoo to confront them alone.
sungwoo came out on the deck.
- caution! the ‘fellblade’ has begun in the affected area!kugugugugu-as if a dark cloud was gathering, black smoke burst out of the three airships.
and huge creatures came out from them and spread their wings.
 they were too huge to compare with hippogriffs in size.
they were the core forces of the world tree fleet, the bone wyverns.
“hunt them!” sungwoo shouted.


 