\section{chapter 426}

until now the world tree camp became strong by defeating the strong enemy.
 and they seemed to have reached a certain threshold.
 obviously, they have grown by leaps and bounds over the past few days, with plenty of supplies and gold, as well as the world's best players.





in other words, they achieved something like the 'quantum jump.
'.
"the hypergate is open now!"finally, the hypergate was opened.
"enter!"an unprecedentedly powerful large army, namely, the main force of the world tree camp, left the main camp and went to the battlefield.
meanwhile, the liberation guild occupied jongro early on to prepare for a defensive battle.
"we have finished inspecting all facilities.
 everything is normal.
"minhum was briefed about the situation inside the building.
 although junghoon was not present at the scene, he made sure they should finish all preparations under his command.
they installed flying weapons on the roof of the building and aimed at the portals.
 they also set up trenches on the ground and air defense shelters in the basement.
s "i didn't expect we would confront the angel race.
.
.
i wonder if we have been prepared well enough to fight them.
"minhum was still worried.
 even though the necromancer always won, his opponent this time was the mighty absolute race.
of course, the necromancer fought against the 'angel judge' in the past, his fight was not a type of war.
"deputy commander, i've something to report to you.
 we have found a group of troll looters in the subway passage and got rid of them all.
"
"great.
 collect their bodies well.
 obviously, somebody will need them.
 he might want them as soon as he arrives here.
"new novel chapters are published on lightnovelworld.
comof course, there was only one person who needed them, namely, the necromancer.
minhum got up after receiving that report last.
 he knew that the world tree camp would arrive here at any time.
wooooowooong-at that moment, the window trembled and a rumbling sound echoed from the hypergate installed on the building in the distance.
 soon the airships started to come out in a row.
"they're finally here.
"a huge airship fleet jumped over the space at once, revealing their majestic appearances.
they were the product of high-level magic engineering that only the blacksmiths of the hearst workshop could make.
"was the world tree fleet so big from the beginning?"although the number of airships was down significantly when the wpu airships left, the composition of the fleet became much more diverse.
 helicopters lined up alongside the airships, followed by squadrons of hundreds of hippogriffs.
"man, they look like a carrier strike group.
"as they said, it really reminded them of a huge carrier strike group.
with the airships serving as an aircraft carrier or the main ship, the helicopters flew around it like frigates.
 and the hippogriff squadrons overlapped on the deck of the airship, then soared again, like a carrier plane.
 there were more than a hundred "magic drones" for reconnaissance that were in operation right now, which were the eyes of the fleet.

even that wasn't all.
 if necromancer's aerial undead troops and valkyrie's einherjars were summoned, they would form a much more powerful fleet.
"how could they form such a striker group in such a short time?"obviously, minhum was there during the latest war, but sungwoo's forces were not that big back then.
"oh, i forgot it again.
 these guys are growing so fast and so tremendously!"the latest episodes are on the lightnovelworld.
com website.
those belonging to the world tree camp were now sharing the same feelings that only a few prominent players like sungwoo and jisu could feel.
***after the main forces of the world tree camp joined, they convened a commanders' meeting right away.
 they set up a meeting place in the lobby of the building.
kyungsoo stepped forward and gave a briefing.
"if we win the battlefield here in seoul, we will be given three places we can move to.
 currently, we assume they are the taiwan server, the chinese server-2, and the japanese server.
"if sungwoo won this place, he could join the three battlefields closest to the korean server while they were in the middle of the fighting.
"we're going to defend the enemies' invasion of jongro here as quickly as possible, then divide our forces into two units, so that they can move to the taiwan server and chinese server-2 respectively, and join our allies there.
"sungwoo and jisu decided to lead the two units respectively.
in fact, dividing the forces could be a risky option.
 but in order to prevent the enemies from annihilating the allies by any chance, they had to make such an inevitable choice.
"and once again let me repeat this.
 after blocking the enemy's invasion as quickly as possible, our entire forces have to gather in one battlefield to make use of our superior firepower…"when kyungsoo operated the remote control, a map was displayed on a 70-inch large monitor on one side of the conference room.
and the operation route was marked with a red dotted line on the map.
 it was a route that went through china to southeast asia, india, the middle east, europe, and australia.
"well, our overall goal is to get as many 'defense success points' as possible through this route.
"fighting in as many battlefields as possible to break the stage was sungwoo's strategy to dominate the 'fight ranking.
'"umm…"however, most of the commanders seemed to be unable to understand it.
visit lightnovelworld.
com for a better experienceat that moment, minhum raised his hand and said, "you just keep repeating that we have to "neutralize the enemy as quickly as possible", but how can we do that when we don't know how the enemy troops are composed? i think it's the most important thing to find out the information about the enemy.
"as a matter of fact, minhum's argument made sense.
 neutralizing the enemy? it's easier said than done.
but sungwoo answered that question quickly.
"well, the answer is our overwhelming firepower.
""firepower? is that all?"sungwoo replied with a nod, "yes.
 we're going to use all of the firepower and wipe out everything that comes down from the sky in an instant.
"

sungwoo was making a loud boast.
 but they could not help but question how come he was so sure.
but as he already knew the answer very well, he continued, "since the last war, our combat capabilities, especially our firepower, have improved drastically.
 i've seen it all up close and can guarantee it with confidence.
 our firepower is more than enough.
"it was the continuous production and supply of powerful weapons that made sungwoo's forces beef up their firepower gradually.
 and what made that possible was, after all, money.
"we will be able to win this war more easily than you think.
"as the man with the enormous resources of money, he was full of confidence.
s ***ten minutes before the start of the enemy's invasion, the 'official channel' was opened without exception.
 but this time, the channels numbered as many as several hundred.
 all the servers around the world were ready to broadcast the upcoming war.
among them, the channel on the korean server drew the most viewers with the audience rating reaching a whopping 68%.
why was it so high? the reason was simple.
 it was because the viewers already knew that the fate of this war would depend on the victory or defeat of the world tree camp.
the most up-to-date novels are published on lightnovelworld.
com"hello! this is reporter ahn.
 it's only been a few days since the last war ended, but i'm back again to do a live broadcast of the upcoming large war.
 this is indeed a continuation of hell.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 