\section{chapter 220}

                             




after they had 12 hours of break time, they resumed the tough training.
“this time the large-scale dungeon is on the ‘a university campus’.
 you will see fanatics appearing there.
 i think the boss monster is a kind of corrupt spirit.
”“i think we have to practice not only blocking their physical attacks but also their magic or curse attacks.
”“then, let me dispatch an advance party there to check out the situation right away.
”the world tree camp decided to dispatch an advance party before formally attacking the dungeon.
 the advance party consisted of hanho, inho, and 25 players from group 2.
“although the dungeon is located in a nearby place, it’s still outside the invisible barrier, so you should be very careful in carrying out your mission,” said sungwoo.
“yep! don’t worry.
 i will pray for them right away if something happens.
”when hanho said that proudly, kyongsu made a puzzled expression.
“prayer?”“hahaha, yeah i know something.
”“okay, let’s go anyway.
”the advance team was supposed to start first, thoroughly check the area around the dungeon entrance, and set up a guard post.
if they were ambushed while attacking the dungeon, they would be defenseless without getting any support from outsiders, so they wanted to prepare for such a possibility in advance.
“i am going to load the material in a truck and move there.
 you have to finish setting up the guard post within 4 hours,” sungwoo said.
the advance party decided to move along the road that they had opened in advance.
 it would be more convenient to use a helicopter or bone wyvern, but they wanted to secure another route in advance because it’s dangerous to use only one road.
“come on, let’s start again!”***“they are moving now.
 this time they are moving through the road.
 given their movement, they are moving in the east.
 unit 3, check the target!”the masked men in black clothes were positioned everywhere around the invisible barrier of the world tree camp.
 they were monitoring the movement of sungwoo and his party as well as the village players because they were not sure when and where they went out of the invisible barrier.
soon, sungwoo’s party began to gather along the road their truck traveled.
 they spread widely in all directions, then began to merge into a single line.
these masked men waited like shadows, then moved like the wind.
 they crisscrossed the buildings to catch up with the truck running on the road in no time.

“stop!”when the truck slowed down, these guys stopped, too.
“stand by!”they lay in wait after moving to their assigned positions.
at that moment, one masked man in the rear looked back, startled.
“uh?”“what’s up?”“didn’t you notice somebody moving around us?”“somebody?”when he said that, his colleague touched the “kunai sword” hidden under his wrist with his index finger.
 as a fellow ninja, he knew his intuition was trustworthy.
 but he didn’t find anything unusual.
“i don’t know.
 are you sure? it could be a wild animal, not a human.
”“oh, maybe.
 but it was certainly not a wild animal.
”this guy could tell the movement of a wild animal from that of a human.
with an anxious look, he looked around.
“hey, don’t worry.
 hayabusa is going to take care of it.
 he is protecting us at a certain distance.
”“i know.
”“if he doesn’t say anything to us, we are safe.
 who can dare to shadow us?”“yeah, you’re right.
”they knew how to move like a professional assassin without leaving any traces of their footsteps or their movement.
they reveal themselves only when they cut the neck of their prey, and they are only reflected in the pupils of the dying prey.
‘am i too nervous? there is no way anyone can follow us because we don’t leave behind any traces.
 and we’ve never been shadowed.
’
however, he began to reveal his anxiety finally.
“hey, have you contacted hayabusa?”the leader of the ninjas approached them and asked.
“pardon? what do you mean?”“there was no response from him a couple of minutes ago.
”“no way…”like his name, meaning ‘falcon’ suggested, hayabusa was like a surveillance satellite for ninjas.
he was supposed to monitor and warn everyone, but they lost track of him at this important moment.
they didn’t panic because they knew there were always variables in the field, disrupting their plans anytime.
 like a professional, they managed to switch to a different strategy calmly when that happened.
“hey, you guys move to area f and check the location of hayabusa.
 even if something happened to him, you should not engage in fighting with the enemy.
”the two masked men nodded and disappeared into the building across the street.
“then, are you going to carry out the operation?”“of course.
 we are going to kill the enemy advance party first, then cut the necromancer’s neck in the ambush.
 we can kill him at one stroke no matter how strong he is.
”their first target, the advance party of the world tree camp, suddenly stopped near the campus of a university.
 although they were on alert, monitoring their surroundings closely, they could not confirm the location of the ninja group.
“you’re right.
 we have never failed to kill anybody at a single stroke until now.
”[synergy list]-category: job synergy-condition: 10 or more ninja jobs-effect: all defense and resistance become 0, but at the same time nullifies all the defense and resistance power of the target.
 also, the damage of the ‘first attack’ is greatly increased.
 (+500%)ninja kills their opponents with one single stroke.
 that’s why they were training so hard to deal one fatal blow to their opponents.
there were many strong players in the japanese server, especially in the kyushu region.
at first, the “yamato guild” was a group that was not so strong.
however, they changed their images after their ninja group led by the swordmaster okata akira killed the strong players of other guilds overnight.
 they could establish themselves as the foremost guild by repeating tremendous growth without any hindrance.
“there can be no failure in this small land.
”and they are now expanding their power to the korean server, the hottest issue in the world these days.
“okay, our operation has begun!”when the leader shouted, the ninjas laid their hands on the back of their swords and scattered in all directions.
there were a total of 27 ninjas.
 they already located their prey.
 according to their enemies’ movement, they kept changing their movement, too.
 they approached naturally and secretly.
as the distance between them narrowed to a minimum and their breathing and walking stopped, they put their right hands on the back of the swords like a butterfly.
 then, like a falcon, they hid in the shadows of a mountain and spread their legs in the air while gliding down.
they expected they would finish killing their targets in just a few seconds.
finally, they began to see blood gushing from somebody.
“uh?”blood was gushing not from their prey.
 the upper body of the ninja at the forefront was cut in half and fell on the concrete floor.
 the other half, namely his lower body, was thrown off and hung on a branch in the distance.
‘what the heck is this?’they never expected this kind of situation.
 the ninjas stopped for a moment.
but their leader thought, ‘we can’t retreat like this.
 let’s break through!’if they gave up because they were caught, they would not be able to take the next step.
the leader blew a whistle like the chirping of a bird.
 the eleven ninjas bent themselves sharply then jumped off the ground.
 then, they drew the swords at the same time and charged at their opponents at a terrific speed.
 they were going to attack their target from the front.
“uh? what is this?”“we have been ambushed!”only then did the players of the world tree camp notice the appearance of the assassins.
but it was already too late.
 it looked like they would be killed immediately by the ninjas.


after killing the players, they were determined to search for the unknown attacker hiding somewhere.
“uh?”at that moment, the ninja leader felt something creepy, but he instinctively threw himself, forgetting his target.
a roar of air exploding narrowly passed over his head.
“khhhhk!”he rolled over the concrete floor, then lowered his posture with a sword in his right hand and a dagger in his left hand.
 cold sweat fell from his nose.
the bursts of sound came from the place where the roaring passed by.
 the exterior walls of the building cracked, the streetlights were torn and sparks splattered.
“khhhhhhhhe!”“kuhhhhhhhhh…”the three ninjas hiding in the building were crushed by the falling debris.
“crazy!”the remaining seven seemed to have instinctively fled, but the leader could no longer give any orders.
 his operation didn’t work out as planned.
he didn’t know what would happen next.
tramp- tramp-somebody was walking from the alley.
 he moved deliberately.
 he didn’t hide even though he could.
finally, that ghostly swordsman appeared.
“as expected…”the ninja leader had once seen her through the korean server.
a long-haired woman wearing a red sweatsuit, and ‘ghost face armor’ in the shape of a goblin’s teeth.
 her expressionless eyes seemed arrogant rather than murderous.
she slowly walked out, drawing one of her two swords from her back, and stood in front of the ninjas.
 an unidentified blue flame was floating above her right shoulder, creating an unrealistic threat.
“hey, sis jisu?”hanho among the advance party recognized her first.


 