\section{chapter 344}

chapter 344: jeju island and attack on demon’s cave (8)“then what about the other family members?”




“well, i think you can guess what might have happened.
 as you know, our family members are very strong, so they are doing well in this crazy world.
 only our younger brother, jiyun, had one of his fingers cut, but he is okay.
”jisu just nodded, but she didn’t continue to talk with her sister in this situation.
 there was already an awkward atmosphere between them.
at that moment, sungwoo interrupted them.
“i’m sorry to interrupt you, but now i have to stop your conversation.
 is black lion with you now?”jimin nodded and said, “oh, i know who he is.
 you have been looking for him, right?”***there were only 38 hours left until the war.
 although the monster worshipers stood in their way, everything proceeded swiftly after they got disillusioned from the monsters.
sungwoo met the ‘black lion’ who was with a group of survivors on jeju island, so sungwoo explained the situation and asked for his help.
 the black lion was quite hospitable.
“yeah, it’s clear from what i heard that i must do something.
”he was clutching a black spear with his overgrown mane tied in a ponytail.
 with his shoulders drooping, he looked like an old lion banished from the pack.
“we’ve never met with each other before, but i already know i’m wrong.
”he regretted that he had joined hands with the evolution society.
“well, i know i can’t be forgiven for making the selfish decision to work with the evolution society, but i hope i can be of help to you, so i can repay what i owe to you in a small way…”having heard him, sungwoo nodded and stood up from the seat.

since the black lion agreed to help him, sungwoo could not delay any longer.
“then, can you detect anything you want to detect anytime, anywhere?”he shook his head.
“my power is not absolute, but i can detect some objects that exert a large influence on any specific area.
 for example, i felt the advent of the world tree early on.
 however, if that object has the power that sustains a world, i think i can detect and find it from afar.
”his comment was a positive sign.
sungwoo looked back at inho and said, “then let’s open the gate of the demon’s cave right away.
 we have no time to delay.
”“got it.
 i’ve already prepared for it.
”sungwoo was going to launch an attack on the demon’s cave here on jeju island.
since it was high ground and had no obstacles, not to mention the major facilities of the allies, this place was perfect for sungwoo’s attack on the terrible thing called the ‘gate of the devil’s cave.
’“if you open the gate, a huge number of monsters will pour out regardless of whether we go inside.
 we need someone to stop them.
”the devil’s cave had a two-way gate.
 sungwoo was going to jump in as soon as the door opened, but it was certain that the devils would pop out in droves right after he went in.
if somebody didn’t stop them, not only would jeju island turn into hell, but also it would block the easiest way for him to escape.
“i installed the hypergate two hours ago.
 i’m going to use that to call more reinforcements in suwon.
 the manager of the general affairs team told me he already took the follow-up measures.
”according to him, kyongsoo was supposed to lead the main force of the world tree camp here.
 but they were not enough to block the demons.

sungwoo said, “we can’t solve the problem by simply blocking the demons.
 as we have already experienced several times, we will see an endless number of demons, and the gatekeeper of the demon’s cave will finally come out.
”sungwoo looked at jisu and said, “i need you here, jisu.
”“is it okay for me not to go with you?”at first, she asked him if she could go with sungwoo, but she now asked if he could make it without her.
 she was sungwoo’s essential helper.
“of course, i need you with me, but i think you are needed more here.
 please protect the people outside the cave this time.
”“got it.
”sungwoo came out on the deck.
 the messenger ship, which sungwoo would use to enter the gate of the devil’s cave, was floating above the center of oreum, and the other two airships lined up to surround the top of oreum.
and the flying weapons were fixed on the deck of the airship and aimed upward.
“the hypergate is now being connected!”soon, the hypergate that kyungsoo installed in advance began to emit a blue light.
 the passage to the suwon village was finally opened.
“the world tree fleet is here!”the main battleships of the world tree fleet came out one after another through the huge portal.
 the survivors on jeju island could not keep their mouths shut, watching the magnificent airships of the world tree fleet.
woooooooooooo-a considerable number of troops were on the deck of each airship, with all of them armed with high-quality weapons.
after they were done with the battle with the chinese server, they picked up the best of the items they collected.
 and they even brought a large number of supplies for the advance team that had no choice but to leave in a hurry.
doo doo doo-right after the world tree fleet came, five helicopters followed.
 they were junghoon and the crusader team.
 since sungwoo’s operation was very important, they came out to support him.
“each ship will move to the designated location.
”a total of 9 airships filling the sky over oreum began to unload the troops to the ground.
“the gate of the demon’s cave will open in the middle! form the ranks to surround it!”“everyone, move quickly! we do not have time!”junghoon’s crusader team was not the last to help sungwoo and his allies.
jimin also appeared with about 100 players.
she approached inho and said, “we will help you, too.
 our troops are nothing, compared with your excellent forces, but we will do anything to help you.
”“by the way, i would like to remind you this is a very dangerous operation.
”inho made an embarrassed expression, but jimin did not give up.
“this is an operation that also protects our village.
 so, we can help.
”“good, but you may regret your decision later.
”

while all of them were busy preparing for the upcoming fight, sungwoo stood in the middle of oreum.
“we’re all set!”after kyungsoo said that, sungwoo pulled out the black scroll.
- would you like to open the ‘gate of demon’s cavel (2nd floor)’?he looked around once before opening the scroll.
 everybody was ready for battle in their places.
‘all the troops i could mobilize are now gathered here, but i can’t be here.
’sungwoo was going to attack the gate of the devil’s cave from inside and outside.
 so, he could not join his allies in and outside the cave at the same time, just like he could not help them during the recent ‘simultaneous war’ in seoul, suwon and busan.
in other words, even if sungwoo’s operation succeeded, he could lose all of them here.
‘but i must carry out this operation!”sungwoo made eye contact with jisu.
 she silently nodded, and sungwoo broke the scroll.
- caution! the  has opened in the area.
* the affected area has been cordoned off.
 (jeju city)sungwoo’s attack on the devil’s cave has begun.


 