\section{chapter 147}






 “don’t worry, general.
 although i was ambushed while i was complacent, they can not confront our large army.
 i’ll do my best.
”so, right after his forces were bombed, he confidently told the messenger from gen.
 chongong about his strategy.
he also tried not to let his guard down.
 his use of the mini-game strategy to isolate kanghwa island was based on his decision to choose the best battlefield in case of contingencies and dispatch as many of his forces there as possible.
but now, all his strategies fell flat.
“what the heck is going on now?”when did his plan go wrong?“obviously, he was not as strong as this.
 i heard he had only three giant skeletons.
 i checked everything including the related threads and photos posted on their community bulletin…”but the intelligence they got was when they confronted trolls on sunyu island.
 since then, the necromancer’s whereabouts were never directly exposed to the community, so there was no way for jahon to find out more about him.
but how much could he change during that short period? so, jahon thought he didn’t need to care at all, but when he faced the necromancer right now, he was completely shocked.
“general! we’re being pushed everywhere!”“ahhhhhh! help me!”“watch out! zombies are coming from the right!”the enemies’ attack was more than jahon imagined.
the necromancer’s strength had grown explosively.
 besides, since he received buff by occupying b and c points, each of the undead had become incredibly powerful.
“it’s ridiculous… how can they become so strong during that short period? how?”rattle! rattle!the bizarre undead got closer and closer.
 the biggest headache among them was the golem.
“man, that monster is similar to what the spiritistic woman controlled…”
splatter– splatter–there were a total of two golems.
 they reached about 10 meters tall, but their soft body, whose material looked like mud, defended against most attacks well.
 no matter how hard they were hit, the mud of their body was dented deeply with no fatal damage.
“use magic!”“no, it’s useless! that’s a golem!”golems even had a passive that offset 80% of magic damage thanks to the traits of the golem race.
 they were a very annoying being with a slow but absolute defense power.
“hey, watch the sky!”“lower your head!”soon, bone wyvern and the monster birds flew overhead, dropping corpses.
bang! bang! bang!then, a huge explosion occurred, evaporating the entire slope of the mountain.
hundreds of troops were engulfed in the explosion.
 furthermore, a landslide occurred, hitting the tankers.
“argh…”jahon began to moan with a sigh.
 their attack was not over yet.
thud! thud! thud! thud!after the explosions occurred, bone drake ran downhill like crazy and pushed everybody.
“what the hell is that?”“isn’t he a boss monster level?”a monster of that size was too big for the tankers in front to stop, so they made way for bone drake.
“damn it! freeze his legs!”
the wizards decided it was impossible to kill bone drake.
 as a last resort, they cast freezing magic on his legs.
 at that moment, ice sprouted between the bones of his legs and joints, slowing his movement.
“good job!”it seemed that they succeeded in stopping that huge monster.
“come on, little kid, let’s go!”but at that moment, something jumped down from bone drake’s back.
 it was the death knight and a goblin skeleton.
“what the heck is that? argh!”“kueeeeeh!”“call the tankers!”the two swordsmen ran around and started to slaughter the wizards without the tankers’ protection.
“protect the wizards!”eventually, the tankers who were in front of them quickly moved to the rear.
at that moment, lich appeared in the shadow of a tree.
 then, he fired crossbows from the side of the tankers.
pick! pick! pick! pick! pick!the tankers with their shields down were hit by the arrows that rained down on them.
 no matter how strong they were, the tankers could not endure the powerful firepower.
“that guy is the necromancer! catch him!”“this fighting will be over if we can kill him!”when they found the necromancer, their eyes turned.
 they felt all they had to do was kill him without having to deal with the undead.
 they knew this would be an easy game as long as they killed him.
but the necromancer disappeared into the shadows.
“what the heck? i can not see him!”“uh? where is he?”the next moment, he reappeared in the shadows 10 meters away.
 this time he was behind the tanks.
“uh?”“uh, when did he go there?”the necromancer then swung his right hand violently.
 a huge scythe swept the area, causing a gust.
 at the same time, four severed heads soared into the sky.
then, the necromancer raised his left hand.
 again, he had a crossbow.
 as he pulled the trigger and fired it, six wizards behind him fell.
watching them, jahon loaded his hand cannon.
 as if he took the situation seriously, his expression was violently distorted but he regained his reason immediately.
“hold out! hold out! our terrific divers moved to capture the other two areas!”this wasn’t a fight that could be decided in one battle.
 under the rules of the mini-game, they could get an overwhelming buff only when they captured a, b, and c.
‘right here the fate of the fight is decided.
’so, jahon was not discouraged, and he tried to analyze the situation shrewdly.
“surely, there is a limit to his deceptive skills.
”in his mind, the necromancer’s skill would have a time limit, and that’s why he was attacking so fiercely without taking a break.
“kuan, avoid colliding with him as much as possible and retreat little by little while keeping him at bay.
 if this fight is dragged out, we can fight in a more favorable situation.
”“yes, sir! i will deliver your message to our troops right away.
”soon, kuan took off his sunglasses, took a deep breath, and put both hands in front of his mouth.
 then, he shouted at the top of his voice, “stop the enemy and move back little by little!”a tremendous voice resonated through the battlefield.
 then, field commanders from all over the battlefield began to repeat kuan’s message and conveyed it so everybody could hear it.
jahon drew two hand cannons.
 then, he walked forward and aimed at the undead.


pop! pop!the two troll skeletons, who were advancing two hundred meters away, immediately collapsed.
they were supposed to be resurrected, but they didn’t.
 soon, they were broken and hardened on the spot.
jahon quietly smiled.
 “it works.
”the skeleton fragments were frozen by the “freezing bullets” fired by jahon, so they could not be reunited for resurrection.
 it was a pretty encouraging scene for him.
the necromancer’s undead were dominating the battlefield, but they numbered less than 100, in jahon’s eyes.
 so, he thought that he could inflict huge damage by incapacitating some of them.
 in other words, binding the undead from being resurrected could be an effective means to attack the necromancer who didn’t know death.
he aimed at the golem that got close to him.
“blizzard sosa!”kwa-wa-wa-wang!his hand cannon fired white bullets.
 just like the name of the skill, ‘blizzard sosa’, dozens of bullets were fired at the golems.
then, the golems’ bodies got cold and soon froze hard.
 they got frozen quickly because their bodies were made of mud.
taking off his sunglasses, kuan ran in front of them and shouted at the top of his voice.
“freeze! freeze the skeletons, so their bones can’t be reunited!”then, the golems’ frozen bodies were shattered and scattered.
jahon felt his forces were at a disadvantage, but he clearly saw the possibility of victory.
“good.
 while we are holding out like this, our terrific divers can occupy points b and c, then we can push them out.
”the buff that he could obtain by occupying all three places was so powerful.
 and as long as his forces kept the necromancer at bay here.
 it was a matter of time for them to capture b and c.
“kuan! kuan!” jahon called for him hastily.
“yes! general!”

 