\section{chapter 327}






 he used a skill that allowed him to shoot randomly without reloading bullets for a certain amount of time.
 it was as though admiral baker’s body became a machine-gun battery.
kheeeek! kheeeeeeek!showered with the bullets the admiral fired in succession, the ghouls couldn’t approach him.
the fragmented bodies of ghouls bounced off in all directions, and the instrument panel of the control room was smashed to pieces.
“disgusting bastards!”admiral baker, whose face always stayed expressionless, finally began to show emotions.
he was upset.
“get out of my place right now!”ghouls aimed at the admiral using their characteristic anomalous mobility, but he didn’t allow them to approach him.
 he looked like a human turret himself.
rattle!at that moment the admiral made the mistake of missing a very small undead who secretly approached him, with his head down.
it was a goblin skeleton.
“what the heck is this?”the goblin was lying on his face, five or six steps away from the admiral, holding a long sword.
bang!admiral baker hurriedly moved the rifle behind his back to fire at the goblin, but he cleverly threw his body to escape the bullet.

“damn it!”the little monster suddenly got close to the admiral.
 he tilted the muzzle to aim at the ghoul’s head.
 he could not aim at the ghoul accurately because he could not put the rifle on his shoulder right.
 so, the admiral hurriedly stepped back and pulled out a “hand cannon” from his waist, and pulled the trigger.
bang!he hit the ghoul, but the bullet smashed only a few of his ribs.
crackle!the ghoul stopped for a moment, then approached him right away.
“get out of here!”admiral baker threw away a hand cannon that needed to be loaded, then pulled out a self-defense knife.
 he thought of widening the gap with the little monster to aim at him accurately, then shot it.
“what?”but right before colliding with the admiral, the goblin skeleton abandoned the sword, and pulled out a ‘hand cannon’.
admiral baker stared blankly at the muzzle.
 the hand cannon was aimed at his head!“uh?”he was now put on the defensive by the cunning monster.
bang!the shotgun blew off admiral baker’s head.
 with his head smashed to pieces, the admiral collapsed from the seat where he was sitting loftily until a little while ago.
“…”the control room became quiet in an instant.
 all the crew members of the flagship, including the admiral, were annihilated.
 and somebody walked on the deck, breaking the silence.

“finished already?’he was sungwoo.
 he ordered the ghouls to search inside the messy control room.
 he also made sure that the ghouls should double-check the body of admiral baker, who lost his head.
as a result, he could collect an unusual object in the admiral’s pocket.
“angel?”it was an angel doll the size of a palm.
-you have acquired the enemy camp’s item ‘angel’s statue (sign of blessing)’.
* this is a special reward given only to the high-ranking people belonging to the angel camp.
 if you go to the ‘symbol (world tree)’ of your camp, you can exchange it for a ‘camp item.
’at that moment, sungwoo thought, ‘this is the statue that the king of the great mountain has mentioned.
’actually, that’s the message that the king sent to sungwoo through somebody helping him.
according to the message, if sungwoo could get a total of two statue-like objects and take them to the world tree, he would get something very important.
“alright, i’ve obtained one!”perhaps the other one would be in gen.
 xing’s hands.
“let me go to suwon and finish the battle there.
”***although the tide of the war was turned in favor of the enemy, general xing didn’t give up yet.
in his judgment, he could reverse the situation again.
1‘if we keep the status quo and wait for the arrival of our reinforcements in seoul, we can get victory buffs and counterattack.
’the latest news he heard from his men in seoul was that his forces there were about to annihilate the remnants of the korean server.
 after that, he had no chance to get updated about the latest status of the battle in seoul because of the necromancer’s air raid, but he had no doubt that the reinforcements from seoul would soon arrive in suwon because his forces virtually won overwhelmingly there.
‘we should hold out until they arrive here.
 we can win if we hold out.
’he opened the rest of the ‘spirit control’ boxes, and controlled a total of four ‘high-grade water spirits.
’ they intertwined over the sky of the battlefield and shook like raging waves.
 when the general lifted his head, he felt like he was standing in the middle of a storm in the ocean.
kheeeeeeeeeh!“yes, be angrier.
 turn your anger to my enemies!”the power that surpassed a natural disaster was in the general’s hands.
 he reached out his hand.
 then, a huge wave swept over bone imoogi that was racing toward him like a heavy train.
the train could not beat the waves.
 bone imoogi lost his balance and began to step back.
 suddenly, the giant snake looked helpless like a snake trapped in a ditch on a rainy day.
general xing clenched his hand, stretching out his hand toward bone imoogi.
 then the waves soared and rotated, gradually turning into a huge whirlpool.
“oh my god! what the heck is that?”“man, this war is crazy!”the players on the battlefield were forced to turn their heads for a while even during the fierce battle.
kheeeeeeeeeeeh!besides, the waves were not just a simple whirlpool.
 while rotating, the water spirits’ arms extended outward long, revealing their sharp claws.
then, they ground everything caught in it like a rotating saw blade.
 concrete buildings on both sides of the road were no exception.
“avoid them! if you get closer, you will get sucked inside!”aside from the building that the necromancer brought here, this huge whirlpool was getting rid of everything that stood in its way.
so, bone imoogi could not maintain his shape inside the whirlpool no matter how strong he was.


the scene of the giant snake monster dozens of meters tall being smashed to pieces was spectacular.
 without the fall of the building, it would have been the best scene of this battle.
“yeah, this is the power of the continent.
”although the general was always prudent, he got carried away with his power this time.
always a prudent general singh, but this time he was intoxicated by his strength.
“yeah, except for the emperor who controls the river, nothing can go against the power of mother nature.
”water has always been an object of fear to humans.
 throughout human history, everybody tried to control water in one way or another, but the moment they lost control of it, everything was swept away.
water is unpredictable and destructive, above all.
 what if somebody can control that terrifying creature easily?“i’m sure it’s going to be the best weapon.
”general xing became convinced that he could reverse the situation using water spirits.
 he thought he could hold out in the current situation.
at that moment when he was stepping forward confidently, a red warning sign stopped him out of nowhere.
-the ‘spirit (high-grade water spirits)’ under your control becomes incapacitated due to a fatal problem.
“what?”panicked, the general lifted his head toward the massive whirlpool, and witnessed something unbelievable.
“what the heck is that?”that huge whirlpool was freezing very quickly.
 the dynamic waves stopped moving firmly, and the huge water droplets swelled, then became a huge ice barrier like an antarctic ice wall.
“no way! this can’t happen! how can you freeze the high-grade water spirits?’the spirit was different from normal water.
 since it had strong mana, the water spirit could not be frozen by default even if it was attacked by freezing magic.


 