\section{chapter 340}

chapter 340: jeju island and attack on demon’s cave (4)this chapter is updated by wuxiahere.
com




if an airship was like a warship sailing through the sky, the ‘bone wyvern’ was closer to a real air force fighter or bomber.
 they were optimal for intercepting hippogriffs that flocked like bees because they could maneuver quickly in the air based on independent movement.
when the bone wyverns and the zombie monsters raised their claws while descending sharply, the hippogriff units, who did not back down despite the airships’ bombardment, began to scatter in all directions.
 it was like a swarm of crows, a natural enemy, appearing in front of the swarm of wasps.
 they hurriedly turned away after learning that they could not beat the bone wyverns, no matter what.
“uh? they are retreating!”“hahaha.
 yeah, they have realized it only now!”the deck soldiers who were on alert in preparation for close combat cheered all at once.
on the other hand, the guys on the deck became busier.
“drop the altitude, so we can provide artillery support to the bone wyverns! we don’t have time, so we’re going to wipe them away with a single attack!”inho gave orders to three airships.
 he knew he didn’t have the time to attack.
‘we’ve got to wipe them away as soon as possible.
’sungwoo’s bone wyvern group descended sharply and chased the enemy.
however, the relatively small hippogriffs were faster than bone wyverns, so it was almost impossible for sungwoo to catch up with them.
tung! tung! tung!however, by triggering the ‘fixed turrets’ mounted on the back of bone wyverns, sungwoo succeeded in hitting the back of hippogriffs that were 100 meters away.
queek! queek!sungwoo succeeded in hunting a total of 10 hippogriffs, but the hippogriffs that were killed after falling to the ground opened their eyes again.
 this time their eyes were a little different.
– the dead become your subordinate spirit under your authority.

it was the moment when a new type of monster was added to sungwoo’s air force.
 they were ‘zombie hippogriffs.
’kaaaaaaaaaaaah!these zombie hippogriffs spread their torn wings and claws, smashing the living hippogriffs.
they were engaged in a fierce dogfight in the air, and soon, the number of zombie hippogriffs increased to 11.
suddenly, sungwoo’s bone wyverns approached the ground.
“crackle! master! i see the enemy’s turrets on the ground!”victor, who was behind sungwoo, shouted.
 in fact, sungwoo already confirmed it.
there were lots of enemy fortresses on the ground and everywhere in jeju cities, and rocket-type ballistas were installed on each rooftop.
 the enemy obviously installed them to defend against sungwoo’s attack from the sea and the air.
however, at that moment there were huge explosions on the ground.
kugugugugugugugu-three blocks of downtown jeju were damaged beyond recognition in an instant.
“… crackle!”victor turned his head, clenching his teeth.
 the airships that lowered their altitude were firing cannons at the enemy targets.
 obviously, the world tree fleet could not be blocked by something like ballistas.
 the airship’s cannons blew away the whole terrain where ballistas were installed.
watching the terrible scenes, inho clenched his fists.
 it was a really devastating fire.
“okay, speed up like the necromancer, everybody!”two airships followed sungwoo to continue to attack the enemy.
 but the other ship raised its attitude towards the center of jeju island, namely mt.
 halla.
aboard the airship were the search team carrying the white wolf and jisu.
 because there was no time, sungwoo divided the mission into two.

‘clear all the obstacles before searching for the black lion.
’backed by the airship’s covering fire, sungwoo tenaciously chased the fleeing hippogriffs.
 they passed through downtown jeju and flew north toward mt.
 halla national park.
as soon as ‘oreum’, a monolithic volcanic topography unique to jeju island, appeared, they started to lower their altitude towards it then a translucent purple dome covered the entire oreum.
‘invisible barrier?’sungwoo had no choice but to stop in front of it.
 it looked like it was their main base.
although it was not as difficult as the ‘shadow of the divine tree’ protecting the world tree camp, it would take a considerable amount of time to break it.
‘if this is their main camp, there will be a large number of troops inside.
’sungwoo looked inside the invisible barrier while hovering until the other airship arrived.
all kinds of buildings, including castle walls and watchtowers, were built on the small volcanic terrain.
soon, the airship approached and sungwoo landed on the deck of the messenger.
right after that, the side window of the control room opened and inho stuck his head out.
“sungwoo, what are you going to do now?”sungwoo pointed to the upper part of the invisible barrier covering oreum.
“please focus on bombarding the upper floor over there, so i can hit them from the air.
”“okay!”at that moment, hanho poked his head out the window and held out his cell phone as if he had something to say.
“sungwoo! it’s kind of weird here! i can’t connect to the community.
 it looks like they messed with it!”when hanho said that, sungwoo also took out his cell phone and tried to connect to the community.
 then he got a message that he couldn’t connect.
– you are unable to connect to the korean server community.
* the connection is being interrupted.
 please remove the item that is causing the access problem in the area and try again.
‘this is the way they have been controlling the whole island!’in fact, it was impossible for the enemy leadership to control the whole island by simply criticizing the cell phone as the devil’s plaything for there would clearly be somebody who would resist such fanatic behavior and ask for outside help using their hidden cell phones.
‘however, it seems that they can block access to the community itself with a certain item.
’by blocking the community using items and controlling the access to the island using the hippogriff troops, they were making jeju island a completely isolated world.
‘but let me end their fanatic operation today.
’shortly afterward, sungwoo’s allies bombed the invisible barrier.
bang! bang!the airship fired cannons.
 just like the baker fleet attacked the suwon village during sungwoo’s war with the chinese server, the airship concentrated the bombardment on one part of the invisible barrier.
soon, the bombed area began to crack and crumble like plastic film.
 compared to the shade of the divine tree, their defense was weak.
at the end of the second shelling, a huge hole could be seen through the giant smoke.
sungwoo raised his hand and signaled them to stop the bombing.
“let’s get into that area right now!”then, he led a group of bone wyverns and penetrated the enemy’s main base.


tuuuuuung! tuuuuuuuuung!ballistas installed in oreum fired huge iron bars, but they could not stop the invasion of dozens of bone wyverns.
 after taking control of the sky within the invisible barrier, the undead corps riding on bone wyverns’ back jumped down to the ground.
 they looked like airborne rangers landing on the ground for a massive attack.
rattle! rattle!the inside of oreum was much like a barren mountain because all the trees had been cut down, but the undead corps were crushed while landing on it.
 but they were soon reassembled and stood up.
“they’re the devil! the devil has entered!”“kill the devil!”soon, worshipers who had been hiding in dugouts all over oreum appeared.
about 500 people stood up all of a sudden.
 did they gather suddenly because of the sudden fighting?“drink the tears of god, everyone!”“let’s drink!”“let’s fight!”they screamed and began to drink an unknown potion.
“argh! ahhhhhhhhh!”“fight!”then, they began to roar like a beast.
‘is that what makes them mad?’

 