\section{chapter 416}

it was at gwanggyo lake park that sungwoo felt instinctively that he would win.
 thanks to the 'wild hunt' caused by the ancient curse, thousands of ghosts were born, who, in turn, became sungwoo's subordinate spirits by his skill, the 'law of the underworld.
' that alone was a huge power boost, but there was something else that really mattered.





'the more ghosts are, the more powerful the underworld king's last skill is.
'[skill information]- name: opening the gate of the underworld - grade: ultimate- category: active- consumption: at least 500 souls and ghosts*by consuming souls and ghosts, you can open the 'gate of the underworld'.
 (retention time: 1 minute per 100 animals) if you enter the gate of the underworld, you get the 'master of the world' effect.
 as long as the gate is open, with your skill, you will maintain the 'underworld king's power.
'+ logging on the book of life and death: you can 'force' your opponent to enter the underworld by writing his name in the book of life and death.
 (1 for every 5 souls and ghosts consumed to open the gate of the underworld)+ punishment of evil deeds: by consuming all the souls and ghosts under your control, you can impose 'punishment' in the underworld.
 the more the souls and ghosts, the greater damage you will cause to a larger area.
'this is an overwhelming effect, but it requires a lot of investment.
 so, i have to save this until the last moment.
"the underworld king's last skill, 'opening the gate of the underworld', had a greater effect when sungwoo had more ghosts under his control.
 he consumed 1,000 ghosts at a time, so he logged the names of a total of 200 enemies in the book of life and death to force them to enter the underworld.
 in other words, there were only 200 enemies in the underworld right now.
others witnessed the sky opening a hold and the "gate of the underworld" opening, but they didn't enter the underworld.
 so, in their eyes, the necromancer, the emperor, and some key chinese military officers suddenly disappeared.
"it's time to kill them all.
"sungwoo stretched out his hand towards the sky.
 the procession of ghosts filling the sky came to a standstill while flowing like a wave as soon as he gestured at them.
at that moment the emperor lowered his head deeply.

"hey, hey, necromancer.
.
.
"the most up-to-date novels are published on lightnovelworld.
comhe raised his head again.
 this time he looked cowardly.
 "i know it's late, but can we still talk? as for the control organization that you mentioned.
.
.
i think you need my help.
 i can give you much more benefits than tens of thousands of miscellaneous soldiers under your control.
 so i hope you can think about my offer wisely…"it was like a declaration of surrender.
"talk?"but sungwoo rejected his offer firmly.
"i'm sorry, but i don't want to deal with a living idiot like you.
 call me again after you die.
"as soon as he said that, sungwoo soared into the air vertically.
"wait a moment!"now his body reached the top of the underworld.
 then his voice resounded throughout the world once again.
"punishment of evil deeds!"the final judgment was meted out to the emperor.
 - 'punishment of evil deeds' has begun in your 'territory' (underworld)'.
punishment of evil deeds was the 'final weapon' with which sungwoo could mount a strong attack by consuming all the ghosts within the underworld.

"wipe them out.
"the ghosts that filled the sky of the underworld in pure white lowered their heads and looked down at the ground.
 their translucent bodies burned white, then began to evaporate into smoke.
 it was a harbinger of a terrible nightmare.
soon they began to move.
 thousands of spiritual beings dangling with their black tails began their final fall to the ground, racing towards their target.
go-oh-oh-oh-oh-updated from lightnovelworld.
comit poured down brilliantly like a meteor shower.
 when viewed from afar, it was such a beautiful and wonderful scene that nobody could describe.
 the blue milky way was melting like watercolor paints above the white world.
but the real situation was different.
the chinese army soldiers were screaming, looking up at the sky.
 but they could not be heard because their voice was buried in their screaming.
 they soon started running away.
 they scattered in all directions and ran away like crazy.
but they could not hide anywhere.
 go-oh-oh-oh-oh-soon, the ghosts rained down on the ground.
 they fell like a heavy storm.
 they tore everything that touched their bodies, including flesh, intestines, bones, and even souls.
they disassembled everything and scattered them everywhere.
at that moment the ghosts got stuck to their corpses, burned them, and eventually perished together.
***everything was over.
 the chinese server's invasion, the war, and their bad ties with the korean server that have been going on for a long time came to an end.
- [official channel: live] world season 9 (18,496,415 people)the whole world was watching the whole process of the fighting between the necromancer and the emperor.
"·…"immediately after the war ended, ahn's studio was silent for a while.
come to think of it, there were many moments when they had to shut up because of too many unexpected turns of events.
for more, visit lightnovelworld.
c‌om"ah…"reporter ahn came to his senses and looked at the camera, then he opened his mouth in a calm voice.
 "when this game started, i was once lost in thoughts about something.
 and now i've come to think about it again after a long time.
"he then reached out and pointed at the camera.
"i think you have also thought about it at least once.
 'is this a dream? yeah, it's a dream, this can't be true.
 but let me ask you this.
 are we really dreaming now?"with sunken eyes, he then looked at wong and asked, "mr.
 wong, do you still want this to be just a dream?"".
.
.
"

wong could not say anything.
 he hardened his expression.
 on the other hand, reporter ahn turned up one corner of his mouth and admired, covering his head with both hands.
"oh my god! did you see that terrific scene unfolding in the underworld? i just can't believe how the necromancer showed such an astounding performance every moment? i just can't believe it.
 oh my god, mr.
 wong, can you tell us how you felt?"".
.
.
""mr.
 wong, you have argued throughout the war that the chinese server and the emperor would win, but you were completely wrong! why do you think you were wrong?"reporter ahn tenaciously asked wong.
 finally, wong calmly nodded and said, "maybe i was.
.
.
yes, i was wrong.
 just like the necromancer pointed it out to the emperor, i was blinded by my own vanity.
"his ears turned red as if he was so ashamed about his wrong prediction.
 he continued, "have i been accustomed to the wrong thinking for a long time? it seems that i did not know how to recognize the world beyond the world that i used to know.
 i'm really sorry because i was too emotional throughout the broadcasts.
"after he said that, wong lowered his head.
 this content is taken from lightnov‌elworld.
comreporter ahn tapped him on the shoulder and said, "what you admitted is good.
 it is desirable.
 it seems that the necromancer made lots of people reflect on themselves.
"having said so, reporter ahn looked directly at the camera.
soon the camera took a close-up of his face.
 it was time for him to make a closing comment.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 