\section{chapter 161}

                             




the fire giant was the middle boss of the ‘hell’s gate’ quest.
 nevertheless, he was more threatening than most of the powerful boss monsters.
‘man, if something went awry, i would have ended up being killed without seeing the boss monster’s face.
’fortunately, sungwoo succeeded in hunting the fire giant using his plan.
 otherwise, he would not have beaten the monster with overwhelming power.
sungwoo realized the recommended level was not for nothing.
sungwoo looked down at the red marble he held in his hand.
[item information]-name: fire spirit-class: hero-category: production material-description: it contains a powerful fire force that does not exist in the real world.
 if the conditions are met, you may control it through mana.
based on his experiences in material combination, sungwoo thought it might be good material, but that was not the end.
chiiiiiiiiiii-a certain pattern began to be engraved on the back of his hand holding the core.
it was a symbol of an unknown shape.
-you have been ‘imprinted’ by the curse of hell.
 the demons of this earth will chase you.
* this curse is canceled when you succeed in hunting the boss monster (hell moving armor).
by dealing with the middle boss, the fire giant, it became inevitable for sungwoo to face an all-out battle with the hell moving armor.
‘i didn’t plan to avoid you anyway.
’in some respects, it might be a favorable fight for sungwoo because if the hell moving armor came to his place, it could create a pretty good situation for the fight.
‘in that case, i can fight in a more favorable situation.
’the battlefield was very important.
 just as a small area is advantageous when dealing with a large enemy, it was an important factor in determining victory or defeat.
in that respect, this kind of downtown was unfavorable to sungwoo.
 it was complicated, and there were too many things to burn everywhere.
sungwoo looked back at his party.
“sungwoo, you saw this message a moment ago, right?”“is that boss monster finally coming to us now?”others were now in the same situation as him.
so, sungwoo nodded and said, “let’s make a trap.
”
he was thinking of providing another hell for those monsters who came from hell.
it would be a decisive attack that would elevate sungwoo to the no.
 1 position, replacing kangsok han.
***the place sungwoo chose was the playground of a local middle school.
 there was nothing to burn there, so it would be the best battlefield for him.
he met some unexpected helpers.
 they were the players he met when confronting the fire giant.
“i have collected all the fire extinguishers in the school!”“i have brought the fire extinguishers from the vehicles.
”“i’ve obtained 11 fire extinguishers for throwing purposes.
”they said they were a group of survivors from the pyongtaek area, but they were in the middle of evacuating to the north as the hell gate opened.
however, they seemed to have judged that they had higher chances of surviving when they acted together with sungwoo than going to the north recklessly to avoid the hellhounds.
“you can stack the fire extinguishers on one side over there.
”sungwoo collected as many fire extinguishers as possible.
 the monsters could burn the surroundings by simply being there.
 so, he needed to secure enough equipment to put out the fire before confronting such a tough enemy.
“i buried them well.
”“good.
”they also dug around the playground and buried the corpses.
‘i’m going to kill them with the corpse explosion.
’sungwoo was thinking of luring them there.
“sungwoo, we’re all done.
 let’s get into the building slowly…”at that moment, a blue light flashed in the eastern sky.
“uh? lightning? wasn’t it just lightning?”hanho also witnessed the ray of light.
 even though it was broad daylight, he could see the trajectory clearly.
 the eyes of those working nearby turned to it.
“did you see it?”“lightning on such a sunny day?”kuuuuuuggung! kuuuuuuugung!then, another light flashed.
 it was a vivid ray of light falling from the sky to the ground, then another ray, and another…“uh?”“what the heck is that?”
kuuuuuuugung! kuuuuuugung!then, dozens of flashes simultaneously and randomly hit the ground.
“oh, my god!”the area hit by that lightning would obviously have been devastated.
‘no way!’obviously, the monsters were coming from the direction of ansung.
 it was another ‘hell moving armor,’ but kangsok was supposed to get rid of that monster.
at that moment, jisu shouted from the rooftop, “they are coming!”they could not afford to watch the lightning leisurely because gray smoke began to pour over the school fence.
“everyone, get inside the building!”“move! move!”after finishing the work, the players began to evacuate quickly into the building.
“uh! it’s hot!”the sound of the monsters stomping on the ground was heard from all sides, and the hot air pushed inside.
 it was a hellish heatwave‘it is definitely different.
 it’s much hotter.
’the fire giant also heated the air in the affected area, but the heat was not as intense as this.
after evacuating everyone into the school, sungwoo stood in the middle of the playground.
soon, the barking of dogs was heard from outside the school, across the road, and from across the building.
bark! bark! bark!they were the hellhounds.
 they appeared with the sound of a strong force shaking the ground just like charging knights.
 then, they gently crossed the three-meter-high fence and ran to the playground.
krrrrrrrrrrrrrr―sungwoo summoned 10 troll skeletons and had them surround his body.
 then, he armed them with the bone armor and bone shields.
‘i have to hold out here until they come fully inside.
’now, the hellhounds entered the playground one after another.
bark! bark!they circled the troll skeletons and filled their mouths with flames as if they were releasing the flames.
 even if the skeletons were armed with shields and armor, they could not endure that intense hellfire for long.
‘come inside a little more.
’another herd of hellhounds entered after breaking open the school gate.
 so far, a total of fourteen hellhounds came in, but that was not enough.
 after that, several hellhounds destroyed the iron fence to break in.
 now, a total of nineteen hellhounds.
 they were still far less than what sungwoo aimed for.
 he could see lots more coming toward him from a distance.
krrrrrrrrrrrrrrrrrrrrr-like hyenas surrounding a water buffalo, they slowly began to approach the playground, tilting their heads.
and the one that approached sungwoo opened his mouth.
 flames were coming out of his throat.
 sungwoo took out the repeating crossbow and fired through the bones of the troll skeletons.
tung! tung! tung! tung!arrows were stuck in his tongue and nose, as well as his left eye.
 at that moment, six hellhounds released flames at once.
fuhuuuuuuuuuuuuuuua!a tremendous heat filled the playground and burned all the oxygen in the area.
“argh!”the bones of the troll skeletons were heated and turned orange.
 sungwoo felt like he was being fried in the oven.
‘come on!’now, the hellhounds increased to twenty-nine.
the bone shields cracked and turned into ashes.
a tremendous amount of heat entered through the bones of the troll skeletons.
thirty-four then forty-one hellhounds came.
 they kept increasing.
sungwoo couldn’t hold out any more.
‘i’ve got to escape!’at that moment, black wings soared behind him.
 it was a zombie monster bird.
 that bird grabbed sungwoo’s shoulders with its feet and spread its wings.
 then, it soared vertically into the sky.
“explosion!”as soon as he escaped from the playground, he ignited the explosives he planted.
bang! bang! bang!the entire playground vibrated, flipped, and bounced.
 coarse sand splattered in all directions, breaking the school windows.
 red flames soared and swallowed the hellhounds, whose bodies were smashed by the tremendous impact.
-you have earned 15,000 gold by hunting the ‘hellhound’.
-you have earned 15,000 gold by hunting the ‘hellhound’.
-you have earned 15,000 gold by hunting the ‘hellhound’.
-you have earned 15,000 gold by hunting the ‘hellhound’.
a huge number of messages appeared.
 sungwoo flew to the rooftop of the school and landed there.
 the playground was devastated as if it had been hit by a missile.
“whew! nice…”

he killed almost 50 hellhounds in an instant.
 he minimized the risk factor by killing them, so he could focus on his last target.
at that moment, a nearby shopping mall collapsed due to the explosions.
a huge shadow wriggled among the fragments behind a hazy dust curtain,-boss monster “hell moving armor” has appeared.
finally, he appeared.
rattle ― rattle ―he was wearing huge armor, with a five-meter-long “spear” behind his waist.
like a heated whetstone, he vibrated the air around him.
every time he moved a step closer, all the weeds and street trees were engulfed in flames.
so, it was almost impossible for sungwoo to approach the monster.
“good.
 let me carry out the second operation.
”-you have summoned ‘golem (flesh)’.
-you have summoned golem (flesh)’.
sungwoo used the golem summoning skill.
 his target was all the kinds of corpses strewn all over the playground.
 they spontaneously rose as if being drawn by a magnet, then began to merge randomly like a giant clay doll.
 then, a 10-meter ‘flesh golem’ was born.
rattle ― rattle ―the terrible monsters made of corpses went ahead, and the troll skeletons that had been killed with explosions were reborn.
 they moved forward along with the golem, carrying bone shields and “maces” made of bones.
-synergy effect is given by team play.
[synergy list]armor breaker (stage 1)-class: weapon synergy-condition: equip at least 10 blunt weapons-effect: causes faint with a certain probability (6%), additional damage to medium and large monsters (+ 15%), additional damage to plate armor (+ 10%)sungwoo even prepared synergy for such big armor because the best way to break through the plate armor was, after all, hitting it with a heavy object.
“then, start!”nine monster birds flew from the rooftop.
 they were holding something in both feet, then dropped them towards the hell moving armor all at once.
puck! puck! puck! puck!

 