\section{chapter 388}

chapter 388: war for war (5)‘i would have done it without the help of a five-star blacksmith or even without hephaestus’s forge.
 so it’s much easier now.
 i can do it.
’




so the blacksmiths of the world tree camp were gradually getting better.
even hearst began to change his attitude.
“well, even though you guys are stupid, you’re quite skilled.
 you guys are now making what i want.
 hum…i think i can take you to my workshop later.
”“hey, who promised that? are you crazy?”“what?’hearst had no choice but to admit they improved a lot.
“damn bastards, you should have done it like this from the beginning! why did you let me curse you then?”anyway, they put their hearts and souls in it for several hours, continuing to work until only two hours were left before the start of the war.
“whew! we’re done! bring your boss, necromancer, here!”finally, arnold hearst lit a cigar for a break.
“sh*t! this is the first time in my life that i’ve experienced a crunch mode like this,” he said.
with hearst smoking a cigarette, exhausted blacksmiths and architects lined up behind him.
“thanks for your great job, everyone,” sungwoo said.
even though he comforted them with kind words, they just nodded weakly.
 it seemed that they needed sleep right away rather than his praise and comfort.
right next to them was something huge, covered with a blue tarp.
 it was at least 20 meters in size.
 was it the final results of their all-night work?“what is that?”sungwoo asked.
hearst dropped the cigarette on the floor, which he smoked almost by half.

“don’t you know what it is? this is an impenetrable flying weapon commissioned by our great guest, in other words, the final outcome of your grand delusion.
 man, you have fueled your delusion, and it’s me who has put it into reality…”when hearst beckoned, a couple of blacksmiths ran toward it and began to remove the tarp.
“oh my god, i think i’ve put your great delusion into reality.
”flutter—when the fabric surrounding the object was removed, a huge face hidden inside was revealed.
it was a stone statue.
 it looked like a giant statue of ancient rome, wearing unusual armor and holding a huge shield.
“this is a ‘totem’.
 oh, you know that a totem is an installation-type buff item, right?”when sungwoo examined the statue from top to bottom, an unusual message was displayed.
- you have witnessed the aura of a masterpiece.
 ‘blessing of fantasy’ is granted for 30 minutes.
* increases health and mana recovery speed (+20%)* all stats increase (+1)“masterpiece? it’s the first time i’ve seen a message like this,” sungwoo said.
sungwoo came closer to check the detailed information and put his hand on the knee of the statue.
[item information]- name: guardian’s statue- grade: unknown- category: player manufacturing
- effect: a number of items are connected to the ‘large totem’ to create a synergistic effect.
 just by being present, this item grants the effect of ‘awesome presence’ to allies within a nearby area (1km).
 the effect is as follows.
.
 all stats increase.
 (+10).
 physical defense and magic resistance increase.
 (+100%).
 ‘sacred shield’ is granted and strengthened.
 (+200%)*in addition, an ‘auto turret’ function is given, which fires a ‘petrification beam’ at the enemy every minute.
- description: i don’t know.
 i’m not strong enough to use it.
 (manufacturer’s own description)‘wow, this is really great.
 if this is really a petrification beam, it’s a weaponized effect of the aegis.
’as sungwoo nodded, hearst, standing behind him, began explaining the features of this new product like a door-to-door salesman.
“based on the ‘magic statue’ made by the architects here by kneading all kinds of magical materials, our blacksmiths put on extra-large armor, shields, helmets, spears.
”“then, that armor and weapon are…”sungwoo once again checked the unusual armor.
 it looked like it was designed in a mosaic style, but upon closer inspection, it was the shields of different shapes and colors.
‘aegis’ and ‘achilles’ shield’ and shields of legendary and hero grades were woven together to form a scale-like armor.
“i tried several things to bring out the effect you wanted, and this combination seems to work best.
”when more than a hundred items were attached to the large totem, an unprecedentedly powerful ‘flying weapon’ was born.
“master hearst, this is perfect!”sungwoo held out his hands to hearst, who held them, snorting at him.
“well, that’s too obvious!”an item like this would help the ‘shield unit’ led by hanho a lot.
soon, the troop deployment would begin.
***sungwoo’s choice of suwon as the battlefield was something that the chinese server had never expected.
 they also expected that sungwoo would choose the battlefield somewhere in china, if it was not beijing, so they searched for a possible place and prepared well in advance.
of course, they didn’t go through a big confusion because of that.
“well, their strategy is too obvious!”“and it’s an easy strategy, too.
”the royal secret service officials sitting around the red round table spoke confidently.
as if they were pretty confident, the chinese server was already prepared for the coming war with the korean server led by the necromancer.
taegam, the chief of the royal secret service who was sitting on the largest of the chairs at the round table, raised his hand, nodding at them.
“then, our troops are fully ready, right?”one of the officials jumped up from his seat and said, bowing to him, “we’re all ready, sir.
 we have total control of 100,000 troops.
 it is an unprecedentedly large army.
”if it was china before its fall, the number of 100,000 would be ridiculous, but it was a staggering thing to mobilize 100,000 troops now.
“okay, are you ready to ship the white sacred sphere?”the white sacred sphere was a huge totem that emitted a ‘holy field’, which formed a key force of the chinese server that could neutralize the necromancer.
“of course, we have it ready, too.
 since it’s equipped with an output device based on the wind spirit, it can move at high-speed.
”taegam stroked his beard with a satisfied expression.


“good.
 everything is working out as i want.
”then he stood up, and paced back and forth, walking around the round table with his hands behind his back.
“i met his majesty the emperor late last night.
 he asked me again about the probability of our white sacred sphere being destroyed by the necromancer…”then taegam stopped behind somebody and put a hand on his shoulder.
“hey, technical manager, i reported to the emperor we had no problem, but it bothers me because he asked me twice.
 do you think my answer was correct?”then the technical manager stood up and said, bowing to him, “of course! you saw that, right? the holy shield has been overlapped with the white sacred sphere.
 even if the necromancer uses the terrible explosion he had used in busan, it would have little effect on our white sacred sphere.
”it was the result of their experiments that even the ultimate corpse explosion, which completely destroyed downtown busan, could not penetrate the barrier of the white scared sphere.
in other words, the powerful device was the outcome of all the magical engineering of the chinese server.
“besides, the outer shield of the sphere is a metal smelted by the power of ‘kuyaja.
’ even if the shield is broken, it can give us some time for emergency exit.
 of course, they will never be able to break the shield.
”“alright, alright.
 we’ve spent a huge amount of money on it.
 so, it should work perfectly!”when taegam giggled happily, the technical manager also began to chime in and laugh.
“don’t worry, taegam! the necromancer will lose all his subordinate spirits and die in shame without even resisting!”by doing numerous experiments, they repeatedly verified that the white sacred sphere offset the magic of death.
“let me emphasize again that this is an indestructible object!”.
as far as they knew, nobody could destroy it.


 