\section{chapter 163}

master of the world tree? given the gravitas of this particular word, sungwoo realized that he had a tremendous opportunity.





shortly afterward, a quest message appeared before his eyes.
[exclusive quest]-title: guardian of death-type: keeping the goal-goal: grow the 'world tree' on this land.
-reward: exclusive skill and title of 'master of the world tree'*you have stopped an external evil invading this land.
 so, you were allowed to qualify as the "guardian.
" death is never evil.
 death is also part of this world and is the balance of this world.
 if you accept your destiny and grow a world tree that holds a mysterious power on this earth, you will be able to gain enormous power and keep the world afloat.
* if the target (world tree) is destroyed, it will cause irreparable disaster.
* your choices affect your 'destiny'.
 sungwoo's memories of the world tree were bad because of the 'bad ending-2.
' the sight of it growing in youido and spreading across the korean peninsula came to his mind.
 and that was the future that would arise when an unidentified tribe called "the fallen" owned the world tree, so their opposite seemed to be the "guardian".
and now, the title was given to sungwoo.
 'this is an opportunity only given to me.
'it was an opportunity that others could not dare to access, which even kangsok, ranked no.
 1, could not get.
 it was given only to the man who must hunt the devil from the hell gate and obtain the title of "hell repeller" after first obtaining the seeds of the world tree through the 'youido raid group quest.
' sungwoo was the only one who went through this process.
"you don't have to be impatient.
"sungwoo put the seeds of the world tree in his inner pocket.
 he could not plant the seeds of the world tree right away.
 for now, keeping these seeds safe was his top priority.
meanwhile, the legendary item, the reward for clearing the quest, was given to kangsok, as promised.
 of course, it didn't mean that sungwoo got nothing.
[item information]-name: hellfire armor-grade: special-category: reversion item
-effect: you can use 'hellfire armor'.
 (defense +50% magic immunity +30% fire immunity +100%, fire damage +20%)-description: when you wear it, its size is automatically adjusted to your body.
 since it is bound to its user, it is irreversible once you wear it.
 the 'hell moving armor' was nothing but an item.
 and sungwoo achieved level 20.
 since it was a quest with its recommended level very high, its resulting exp was tremendous.
-choose your level up card.
1) stats (random)2) skill (random)3) items (random)4) other (random)5) corpse explosion (confirmed)the fifth item caught sungwoo's eye first.
 'finally, i can upgrade the corpse explosion.
'since he used his corpse explosion skill very usefully, he now could enhance it further.
-your skill grade has been improved.
 (basic → skilled)[skill information]-name: corpse explosion-grade: skilled-category: active-consumption: 5 mana*you cause an explosion using a corpse.
 additional damage (+30%).
 it releases a small amount of 'breath of abyss' containing the power of death after the explosion.
for sungwoo, this item no.
 5 could not be better because it caused additional damage and released the abyssal breath, and the consumption of mana decreased.
he didn't know exactly how much the 'small amount' of the breath of abyss, but obviously, it not only caused the explosion damage but also much greater damage than that.
 
'great! i've gained a lot today, too!'after canceling the summons of all his subordinate spirits, sungwoo returned to the school with his party.
 there, he encountered an unexpected situation.
"sungwoo! we're in big trouble!" someone was there.
 somebody new to sungwoo appeared among the pyongtaek players behind hanho who looked embarrassed.
"necromancer, we belong to the wide area surveillance team.
"it was an organization that sungwoo knew well.
 it was an intelligence unit belonging to the liberation guild, which was created at sungwoo's advice.
 as far as he knew, they were scattered everywhere to collect information.
"what business brought you here?""you must evacuate somewhere immediately.
""escape?""we were monitoring this area, and about 15 minutes ago, we saw a large crowd moving here from the songtan area.
 considering the human monsters in the crowd, they are likely the evolution society guys.
"evolutionary society? were they aiming for sungwoo?'sure, it's highly likely they are targeting me.
'they must have been hiding in the shadows, keeping an eye on sungwoo while looking for a chance to get rid of him.
and they must have judged that this was the best opportunity to attack him because he was finishing the battle in a place far away from youngdungpo.
"we have also received a report from youngdungpo.
 soon, the commander and his crusader team will come here to fight them.
 i know we don't have to worry about you, but you need to be careful because the enemies are huge in number.
"the wide area surveillance team has been founded only recently, but they were functioning well because they collected the information and took the necessary step for the crusader team to come here even before sungwoo noticed it.
at that moment, there was a big explosion somewhere.
 bang! bang!"what the heck is this?" a member of the surveillance team stuck his head out of the window.
kugugugugugugugugu-a seven-story building near the school was in flames.
 given that the building debris rained over the ground, it seemed as if the whole upper floor had been blown away.
"that building is…""well, it's a building where b3 and b4 are hiding! they've been caught!"it seemed that someone from the surveillance team on standby had been attacked.
in other words, it meant that the evolution society guys already arrived.
"we're already under siege," jisu said, frowning.
 her senses were enough to detect the surroundings of the school, but the evolution society members already entered the streets.
"there are a lot of them.
"a surveillance team member nodded.
"we have seen about 300.
"the size of the incoming guys of the evolution society didn't matter.
 the thing was who comprised them? sungwoo stuck his head out of the window.
 at that moment, white light burst out between the alleys.
the light beam flew vertically and struck near the rooftop of the school.
bang! kuggugugugugugu.
.
.
the whole school was shaken.
 it was a weapon powerful enough to blow away the upper floors of the building.
 this kind of destructive power was comparable to the concrete fireball thrown by the fire giant.
 "what the heck are they trying to do?""have you already attacked us?"they didn't know exactly what that light beam was, but they knew it had tremendous destructive power.
"are they now warning us not to escape by flying?"if the enemies had a lot of such weapons, sungwoo could not even summon bone wyvern and escape into the air.
 the attack a little while ago was a clear warning that such an escape was impossible.
 'they must have been constantly monitoring my power, so they must have prepared thoroughly before coming here.
'clang! at that moment, a window broke and a player fell, grabbing his neck.
 "argh!.
.
.
"

a small arrow was stuck in his neck.
 the players in the school watched him, then lowered themselves, startled by the shocking attack.
"that's a sniper's attack!""everybody, escape inside the building!""get away from the window!"the enemies dispatched the snipers after surrounding the building using the terrific weapons.
 so, it would be very difficult for sungwoo and his party could get out of this place.
but that wasn't the end.
"they are now approaching us from the front!" jisu said, checking their movement.
after making a bone shield, sungwoo covered himself and approached the window.
tramp, tramp, tramp-as she said, a group of enemies was approaching from everywhere.
 they approached very carefully with a wide "kite shield" forming a defensive line.
 there were as many as 20 such formations.
 furthermore, several wizards were in the process of casting defensive spells behind them.
 like a commando of counter-terrorism suppression, they made a formation that sungwoo and his allies could not easily break through.
 "attack! attack!"when they approached close enough, the human monsters behind the shields charged.
 they ran at full speed, hanging on the exterior wall of the building, and broke through the windows.
clang! clang! "uh?""they are already into the building!"the players were stricken with fear at the sound of the windows being broken.
 sungwoo and the surveillance team members were ready for their attack, but the enemies' attack was like a bolt from the blue sky to the players in pyongtaek.
 "who the heck are these bastards?""what should we do now?""shut up! protect the children! get ready for battle!"the leader of the pyongtaek group approached sungwoo and said, "what should we do now?"they only relied on sungwoo now.
 but sungwoo couldn't come up with a definite answer.


 