\section{chapter 386}

chapter 386: war for war (3)sungwoo nodded and stood from his seat, and he rolled up the blinds.
 when the sun was beaming through the window, he could see the wall in the distance.





“to tell you the truth, i and jisu, in other words, the necromancer and valkyrie, won’t lose to the enemy.
”he was full of confidence when he said that.
 and no one could object to it because the two had never lost until now.
sungwoo continued, “we have unbreakable spears and arrows.
 if that’s the case, the enemy will try to attack our shield.
”having said that, he looked at junghoon.
“but i can’t guarantee that our shields will never be broken through by the enemy.
 can you?”junghoon silently nodded.
 of course, it’s true that the crusader team had an overwhelming defensive ability, but they exposed their limits during the recent battle at the demon’s cave.
in other words, they were not invincible shields.
while no one could answer, sungwoo raised his index finger and pointed out the window, namely at the towering wall far away from their place.
“therefore, the fortress walls and the invisible barriers of our main camp will be of great help to our shield unit.
”then, minhum raised his hand again.
“well, but during the last war, the invisible barriers and walls were broken through helplessly, right? of course, i admit that since the world tree has grown a little bit, our shield has become thicker than before, but that alone is…”in fact, they believed in the power of the invisible barriers during the first war, but they were easily broken through by the bombardment of the airships.
“oh, then, is there any other way?”when asked if there was another way, sungwoo confidently nodded.
“i don’t know it, but there are talented people who can find the way.
”after the commander’s meeting was over, sungwoo summoned hearst, the blacksmiths, and muyon for a meeting.

“welcome, my talented guys!”these were the people who would find a way to block the enemy’s attack.
“huh? talented people? what the hell are you talking about all of a sudden?”hearst kept grunting as if he was upset about being called out while they were working.
after sungwoo let him run the hephaestus’s forge, hearst was so happy that he could never stop working.
 he worked energetically like a child who was given a new game console.
“master hearst, you made a cannon out of the ‘frozen seed’ that i had in the past, right?”“oh, you mean the ‘winter predator’? sure, i did.
 are you still using it now? isn’t it broken yet?”sungwoo tilted his head and pointed to the ‘winter predator’ placed against one wall.
“yep, i’m using it very well.
 so i hope that you can use a myth-grade weapon to make a special item for me.
”“hmm, what do you want this time?”hearst took out a cigar as if it was a nuisance.
so sungwoo took out the items he had prepared in advance one after another.
he took out two, which were shields.
 he obtained them from the safe in hephaestus’s forge.
“both shields are myth-grade items.
”hearst took the shields and began to examine them one by one.
[item information]
- name: aegis- rank: myth- category: shield- effect: stamina increases (+15), physical defense increases (+150%), magic resistance increases (+150%), immunity to all curses increases (+60%), immunity to all abnormal status increases (+60%).
 as soon as the battle begins, the ‘god’s shield’ effect is activated, forming a large-scale shield.
 when you supply mana, the ‘medusa’s head’ effect is activated, giving ‘petrified’ status to the enemy within a certain distance (50m).
“man, isn’t this the shield of zeus and athens, also known as aegis?”then, he checked the second shield.
[item information]- name: achilles’ shield- rank: myth- category: shield- effect: stamina increases (+10), physical defense increases (+100%), magic resistance increases (+100%), immunity to all curses increases (+50%), immunity to all abnormal status increases (+50%).
 when you supply mana, the ‘sacred shield’ is activated.
 also, targets within the shield are immune to all abnormal status effects.
this was the ‘achilles’ shield’ sungwoo gave to hanho.
 he said he would wear it briefly before returning it, but he was unhappy about it for some reason.
“where did you get this kind of item? well, what can i make with these items? should i make snow sleds for a couple?” hearst asked, hiding his excitement.
sungwoo turned his head to muyon.
 muyoun looked perplexed as if he didn’t know why he was here.
“oh, let me introduce you to each other.
”when sungwoo introduced them, muyon, the 4-star architect, and hearst, the 5-star blacksmith, formally shook hands.
“from now on, both of you will be making items together.
”the two middle-aged men frowned at his words at the same time.
“do you want me to team up with an architect? what do you want me to make?”sungwoo said with a smile, “well, a castle wall.
”hearst spat out the cigar in his mouth.
“what? what did you say? wall?”muyon also tilted his head with a puzzled expression.
“did you say i should make a castle wall with a blacksmith?”sungwoo nodded lightly, then said, “i’m not talking about a typical wall, but one that will never break down under an enemy’s attack.
 what i mean is you should make a huge ‘defensive weapon’ that will lead us to victory in the upcoming war.
 we’ve got only 24 hours left.
”this time sungwoo had no intention of leaving the talented men neglected just like he did after he hired hearst.
“well, the fate of our lives depends on you.
 so i hope you can take a sense of responsibility for our lives.
”the two middle-aged men were speechless for a while.
***meanwhile, reporter ahn’s studio, which had prepared the broadcast early on, already started broadcasting the situation.
“hello, everyone! this is reporter ahn with reporter ahn’s apocalypse news! from now on we’re broadcasting the ‘eve of the war’! welcome, viewers!”the broadcasting by reporter ahn’s studio was much more advanced than before.


the screen for the broadcast of the official channel behind reporter ahn’s back was much larger, and it was equipped with a microphone and reflector.
“alright.
 i’m going to broadcast the vivid scenes of the war this time, too! so, please stay tuned on our broadcast!”since the viewers enjoyed reporter ahn’s dynamic commentary during the recent war, more viewers turned to his channel this time, drawing as many as 40,000 viewers.
- [live] reporter ahn’s live broadcast of the korean server’s 2nd war with the chinese server.
 (46,464 viewers)“today, i have a special guest with me in this studio! she once confronted the so-called ‘emperor’ who unified the chinese server!”reporter ahn created a special segment like this to enhance the quality of his broadcast.
“i’m glad to have you, mr.
 wong, the 17th strongest player in the chinese server 3!”as soon as he announced, wong came out to the studio.
“hello.
 i’m wong from chinese server 3.
 thank you for inviting me here.
”after he introduced himself briefly, reporter ahn began the question and answer session with him.
“alright, let me ask you from now on.
 mr.
 wong, you were from the chinese server 3.
 you said you once confronted the emperor’s army, right?”the guy named wong nodded with a heavy expression.
“yes, that’s right.
 it was really terrible.
 it’s a miracle that i survived the fight.
”the chinese server 3 was known to have been occupied by the chinese server 1, namely, the emperor, a long time ago.
“if that’s the case, i think you know better than anybody else about the emperor’s power.
 of course, since you fought him a long time ago, his power back then must be different from his most recent power.
 what is your assessment of the upcoming war?”

 