\section{chapter 355}

chapter 355: jeju island and attack on demon’s cave (19)sungwoo jumped into the pit.
 it was about 10 meters deep, but he landed easily.





the pile of bone ashes rustled unpleasantly when he tread on them.
 he didn’t hate the bones because he thought the owner of these bones might have been the ‘guardian’ of this world.
‘the ‘fallen’ won this battle by killing the guardian.
 i might face the same fate.
’sungwoo raised his head and looked at the wall half-hidden in the darkness.
 he noticed terrible lips hanging there.
 there were a total of five lips, but only three of them were making strange gurgling sounds, while the other two were pouting their lips and chewing something.
sungwoo stared at the two.
‘they’re coming out.
’at the next moment, the chewing lips widened roundly and spat something out.
 it was a huge amount of flames.
kwagwagagaga!a pillar of flames swirled and filled the pit.
 sungwoo lowered his head and raised his arms to cover his face.
 the scorching heat engulfed his entire body.
 that was it.
 his overwhelming resistance to fire protected his body.
soon, the pillar of flames was gone.
 now, all five mouths were smacking something.
it seemed that they were collecting flames in their mouths, but it would take a long time for them to spew flames again.
“oh, my god! you are intact!” li wei shouted from above the pit.
“how could you do so many miraculous things?” she asked in amazement.
she felt frustrated as if she was deprived of everything.
 as no.
 1 in the chinese server rankings, she was once strong enough to confront the emperor, but she felt there was clearly a wall that she could not overcome like the necromancer while she was fighting with him.
sungwoo removed the pile of bones and looked down at the black sickle hidden inside.
‘this is the grim reaper for sure.
’he then compared it with the grim reaper he possessed, but the two items looked exactly the same as if they were from a factory.
‘as expected, the necromancer of this world died here.
’
sungwoo slowly reached out towards it.
‘there is only one grim reaper in the world.
 can i use it after obtaining it informally like this?’he was concerned about it, but there was nothing to lose if he tried using it.
woooooooo-but when he put his hand closer to it, the object trembled and sent out a warning message.
- caution! in order to possess this item, you need a special condition called ‘death witness.
’naturally, he had already satisfied the condition for the ‘death witness’, which was the requirement for his first awakening, when he was engulfed in drake’s flames.
so, he grabbed the handle of the object without hesitation.
- caution! since you have a ‘conflicting item (grim reaper)’, you cannot get any additional effects.
* please remove the item and touch it again.
he could obtain it from a different world, but it was impossible for one person to own two grim reapers.
‘then, if i give it to my subordinate spirit, can i create another lich?’sungwoo tried a different method.
 he summoned ‘werewolf skeleton’ to have him hold the grim reaper.
- caution! your ‘target (werewolf skeleton)’ has not reached the level at which he can handle ‘the item (the grim reaper)’.
as expected, it was impossible to apply it to another creature because this item was used to bring about the awakening of those in one specific occupation.
‘by the way, what level does he need to reach to use it?’come to think of it, there was a message that when he used the skill ‘’, it could not have a great effect on the ‘target with low intellect.
’
sungwoo needed a creature with high intellect.
‘should i give it to victor?’victor had already reached the level of lich, but since he was a boss monster, not a player, he already began to feel limits to his growth.
still, if sungwoo gave him the grim reaper, he might not be able to use the ‘realm of the death’, an indefinite resurrection magic.
 two realms of death? it would be spectacular even to think of it.
‘well, who else but victor?’there were various additional factors sungwoo had in mind, but he didn’t have enough time to test each of them right now.
so, he returned the werewolf skeleton holding grim reaper to the ‘haven of void.
’“sungwoo! check that item in front of you!”hanho couldn’t jump into the pit, but he was sticking his neck into the pit.
 his saliva was about to drip.
“okay.
 wait a minute.
”sungwoo found an old book near the place where he found the grim reaper.
[item information]- name: demon magic manual (munich handbook)- rank: legend- type: orb- effect: significantly enhances the ‘undead summon effect’ among the ‘death-type magic’ of its holder.
 (however, a person without any death-type magic may receive a ‘curse of death’ if he opened it carelessly.
)it also seemed to be an item possessed by the necromancer in this world.
‘i feel like i’m inheriting the legacy of my ancestors.
’the moment sungwoo touched the item, the bookcase began to unfold by itself.
- the maximum number of your subordinate spirits increased (+15).
just possessing it increased the maximum number of his subordinates by 15.
 it was a huge increase, but that wasn’t the end.
- you have realized the knowledge of death.
then, purple energy burst out from between the pages and was absorbed by sungwoo’s body.
- when you use , you can summon an additional ‘masterless zombie’ (+10).
- when you use , you can additionally appoint a ‘skeleton mage’ (+5).
sungwoo checked the message over and over again.
‘what a jackpot!’if he applied the ‘shadow army’ here, it would increase the number of the undead troops by a whopping 50, which would increase the power of the undead army drastically.
sungwoo then discovered a ring.
[item information]- name: fatal dexterity- rank: legend- category: ring- effect: increases one-handed weapon attack power (+20%), increases fatal dagger strike chance (+50%).
 when you inject mana, your ‘master’s hand’ is activated to increase your hand movement rapidly for 1 minute.
 (+300%)

it was something sungwoo didn’t have to think hard about who needed it.
 he threw the ring at hanho.
“wow! legendary grade! thank you, sungwoo! you are the only one who cares about me! i think if i can give it to my father, he is going to be a great gambler!”in addition, sungwoo found a few hero-grade items, but there were no more useful items for him.
 so, he raked up all of them and distributed them to the crew members.
‘if the guardians had not attacked the demon world tree, they would not have been wiped out here.
 some of them moved on alive.
 then, there will be more items further out there.
’this was an opportunity for sungwoo to get items in bulk.
 he couldn’t lose the items because they were a very effective addition to their strength.
at that moment, one of the crew members in the rear came running to him.
“general manager! we have an emergency message from the airship!”“pardon? did something unusual happen to those who stayed behind?”sungwoo also listened to their conversation.
“no, that’s not true.
 the demons came in, but they suddenly flew away again.
 however, they confirmed that the demons got back into the portal.
”portal?“what the heck? portal? sungwoo, what do you think?”“well, i hope jisu can fight well.
”sungwoo used manufacture bone weapon skill and made a bridge through which he could cross the pit.
“let’s go back.
”there was only one way for them to help jisu and her party.
 it was for them to carry out their mission here and go back safely.


 