\section{chapter 390}

chapter 390: war for war (7)the ‘shield unit’ was busy repeating the complicated war preparation process, but the ‘arrow unit’ and the ‘spear unit’ were quiet.





no wonder they were quiet because the spear unit had only sungwoo and li wei, while the arrow unit had only one fighter, jisu.
of course, they could summon a large number of ‘subordinate spirits’ under their control, so not a small number of troops were assigned to the two units.
sungwoo, hanho, and jisu stood on the wall and looked around silently.
since the fight would largely depend on the judgment of sungwoo and jisu, they needed to think hard about their strategy before the war started.
“ah, jisu!”at that moment sungwoo asked, looking at her as if something came to his mind suddenly.
“the emperor has a job that controls lots of subordinate spirits like me.
 even though they won’t come out right away, they’re the key part of the chinese military.
”jisu quietly nodded.
sungwoo continued, “in other words, if we defeat the emperor, we can neutralize the entire chinese troops.
”assassination was one method the enemy used countless times to defeat the necromancer.
in other words, the emperor would probably use the same method.
“this fight won’t be easy, but i hope you can find the right chance to attack him while my troops clash with the emperor’s troops.
 even if you can’t kill him, the emperor’s troops will be in great chaos if you manage to wound him severely.
”“sure, let me try.
”“but don’t overwork yourself.
”it was important for them to fight well rather than fighting under a special operation.

“li wei, you need to find the high-level spirit.
 that’s why i have assigned you to my unit.
 if you find the spirit’s whereabouts, just let me know quickly.
 l will do my best to rescue you as much as possible.
”li wei nodded with a stiff expression.
 if things worked out well, she could put an end to her ill-fated relationship with the spirit that continued from the early days of the game.
“i’ve owed a lot to you until now, so let me show my real capabilities when you find the spirits.
”***when their war preparation time was almost over, ahn’s studio was still broadcasting the situation for as long as 19 hours.
“the chinese army is numerically incredible.
 they are so huge.
 it looks like there are more chinese troops than the viewers of my channel.
 oh, that’s not true? hahaha, thanks so much for visiting my channel!”as wong of the chinese server rambled in the last broadcast, ahn’s commentary made a big hit as if he was engaged in noise marketing.
back then, the contents of his broadcast got noticed by numerous people while spreading through the community, and as a result, the number of viewers visiting his channel increased exponentially.
“okay, the war will start soon.
 of course, i hope our korean server can win, but i think we have to look at the war rationally.
”reporter ahn swallowed, then took his eyes off from the screen and looked somewhere.
at the same time, he was checking the number of those watching his channel now.
“oh, that’s why i’ve invited that man in question here.
 i know i’m biased toward the korean server, so for balance, i have someone who thinks he is intelligent.
 mr.
 wong, welcome!”as soon as ahn introduced him.
 won appeared in the studio again.
this time, he appeared in a suit, wearing glasses, while holding a notebook in one hand.
“everyone, please calm down!”
[live chat]- i want to live: ???????- the end of my life as bar exam student: man, why is he coming back again?- righteous ansan fighter: can they defeat the chinese army?- minhyung lee( 33): no way, you shouldn’t have him as the guest!- hyunju kang: taiwan’s number one!! free tibet!!!!- ulsan kangjun: thanks for the show!- 67-year-old hyunjung park: reporter ahn, are your parents chinese-korean?there was anger among the viewers in the chat room, but what was certain was that ahn’s broadcast was an unprecedented hit.
‘yeah, something sensational is appealing to the viewers.
 i’m going to draw more viewers if i keep making my channel controversial.
 this is a great opportunity to broaden my channel viewership!’reporter ahn was receiving a ‘dedicated quest’ as a camera operator.
 so, the number of viewers was a huge driving force for the growth of his channel.
 that’s why he could not resist making won an issue.
not surprisingly, the chat room was overflowing with their criticism of wong, but the number of viewers continued to increase.
“okay, i will start broadcasting the commentary until the war is over!”reporter ahn continued the broadcast without caring about the hostile reaction of his viewers to wong at all.
***- the war has begun!finally, the war began.
“move according to our operation plan!”as if the machine was working, the shield unit moved exactly as thoroughly trained by junghoon.
“if you guys have a formation problem, just report to me immediately! you have to fix it in 10 minutes!”at that moment, a great gust of wind blew past, casting a shadow over their heads.
woo woo woo-junghoon’s forces were a combined fleet.
 a whopping 32 combined fleets soared into the air near the castle wall.
“they are so amazing!”when that scene was broadcast on the air, the players around the world could not hide their admiration.
 no other server than the korean server would be able to send such a large fleet.
 as a matter of fact, they had never seen that even before the world was ruined.
at that moment junghoon shouted, “the world is watching us! today, we’re going to promote our power to the world!”in the meantime, the spear unit of the chinese army left gwanggyo lake park early and marched toward the headquarters of the world tree camp.
clang- clang- clang- clang-from the moment they arrived in suwon, they saw a huge world tree.
 they were already inside its huge shadow.
“i just don’t know if that tree is beautiful or terrible.
”

the magical figure of the world tree made them feel uneasy.
 they felt like they set foot in a place they should not have come.
“don’t raise your head or don’t look at the tree.
 just moving forward! after all, this is the tree we have to cut down!”the spear unit was over 60,000, accounting for as many as 60% of the total chinese army.
as the footsteps of these 60,000 troops shook the city center, their morale and courage were soaring high.
what’s more, the sheer number of the troops was not all there was.
 they were hiding numerous weapons to destroy the castle wall.
“general! i can see the castle!”suddenly their target came into their view.
“watch out carefully! always mind your surroundings! the enemy’s spear and arrow units might ambush us! just suspect everything! they are using crazy methods to attack us.
”the general knew from their previous fighting experiences that the necromancer used all kinds of bizarre attacks such as causing corpse explosions or dropping buildings from the sky.
so this time they were more prudent.
 to counter the enemy’s trap or surprise attack, they ordered a scouting unit composed of players with -ray vision to search the surrounding area thoroughly.
“general! we have just received a report.
 they say that a necromancer has appeared near our shield unit!”the general smiled at that because he was becoming more convinced of victory.
“hum…did the necromancer offer to serve as their shield? then, he would not be able to avoid the fate of being a dayfly caught in a spider’s web.
”the shield unit already set up a perfect plan to catch the necromancer.


 