\section{chapter 427}

reporter ahn and his assistant continued the pirate broadcast.
 they had a timer on the desk set to alarm at the start of the enemy's invasion and continued the preview broadcast.





based on their research, they explained what strategy the world tree camp would use, or whether they could win, and how strong the major servers abroad were.
ding dong! ding dong!at that moment an alarm sounded from the timer.
"uh!"startled all of a sudden, reporter ahn reached out in surprise and turned off the alarm, while his assistant operated the remote control.
 then, the official channel appeared on the screen behind them.
"wow, the war has started!"the sky over jongro was shown on the screen.
 the blue portal opened in the sky, and the number written around it formed 0, then began to flash red.
something was about to begin.
".
.
.
"s reporter ahn and his assistant refrained from speaking and waited for something to start.
"um…"but nothing happened for several minutes.
 reporter ahn finally opened his mouth again.
"um, it's getting a bit late.
 alright, the world's attention was focused on the korean server, so let's watch how they can live up to our expectations.
.
.
uh? what?"but he was distracted immediately by another channel.
 it was a channel that relayed the italian server, rome.
"uh! we just got the news that the enemy's first invasion has just started with the italian server!"actually, there was no response from the enemy's invasion, but finally, they started invading the italian server.
"yes, i confirmed that they started the invasion.
 since the absolute faction has a different command system for each server, will the prepared guys come down first?"reporter ahn hastily moved the pirate relay screen to the italian server channel.

"oh my god!"rome appeared on the channel screen right away.
 it was a city with a long history and rich cultural heritage, with its center full of white marble buildings.
for more, visit lightnov­elworld.
combang! bang! bang!but explosions were taking place over the sky of rome.
 they looked like massive fire magic.
 and large-scale defense shields were deployed throughout the city.
 and a long pillar was connecting the hole in the sky and the ground.
how come there was a pillar all of a sudden?everyone watching it through the broadcast was puzzled.
 however, the unidentified pillar was strange.
kaaaaaaaaaaaaah!the pillar was wriggling violently while screaming horribly.
every time it screamed, a huge amount of white powder was scattered everywhere.
it was not a pillar.
"no, that's nonsense! can you see that?"it was not a pillar, but angels.
 winged angels crawled out of the hole of the sky, coming down to the ground, entangled with one another.
 they came out randomly without any particular pattern or order as if they were putting a large amount of something into a narrow hole.
kaaaaaaaaaaaaaah!while letting out a grotesque scream, they sometimes spread their wings, which looked like dust falling from a gigantic column when seen from a distance.
those angels who could not spread their wings because they were located in the center of the pillar fell to the ground, then crawled out from among the 'heaps of angels' and flew again.
they launched an ineffective offensive, but they could not be stopped.
like swarms of hell locusts sweeping through the wilderness, they flew everywhere.
"look, rome has already begun to collapse!"
indeed, the sky and earth of rome were torn apart by the wings of the bizarre angels.
"what? is that true? ah! according to the information we've just received, it's only been four minutes since their invasion started! how come they are being invaded helplessly like this?"anyone could predict that a multitude of creatures would come out of the hole in the sky.
and anyone could plan to form a great coalition to stop them, and most of them would have actually prepared it on their own.
 but it was difficult for them to do it right.
"their firepower is so insufficient.
 thousands of magic fires were shot from all sides, but even one-tenth of them seemed to have missed the target.
"even though thousands of players formed a defensive formation, they collapsed by the hordes of angels at once.
visit lightnovelworld.
com for the best novel reading experience"the italian server is finished.
"again, things didn't go as planned.
***"the invasion has already started on the italian server.
"while standing on the roof of the building, sungwoo heard the official channel broadcast that hanho was watching.
 there was only the sound of something breaking and screaming.
'if the invasion comes too late, we'll have more losses.
'sungwoo was more worried about the relatively late start of the invasion than the upcoming battle itself.
 the start of the invasion was slightly different for each server.
 it was because of the separate command system, as reporter ahn speculated.
as they were intelligent guys, they launched the invasion when they were ready after planning their strategy.
'then can we launch a preemptive strike?'there were several ways to stop their invasion.
 and the preemptive strike was one of them.
since everything was still uncertain, sungwoo couldn't try such an extreme method recklessly.
"oh my god! rome is being completely destroyed!"hanho shouted as if he was stunned, but sungwoo silently looked at the sky.
at that moment some cold energy began to emit from the hole in the sky.
'they're coming.
'sungwoo turned his head and looked at jisu standing on the railing of the opposite building.
 she, too, was looking at him and nodded.
"what a relief!""pardon? what the heck are you talking about? you are relieved that rome is being destroyed now?""no, we are not too late.
""what? i don't understand…"at that moment sungwoo stepped on the railing on the roof of the building and threw himself.
 the moment he disappeared under the building, a gust of wind blew, and 'bone dragon' soared.
"get ready! it's time for a fanfare of welcome!"visit lightnovelworld.
c‌om for the best novel reading experiencesungwoo got on the giant monster's back and soared into the blue hole in the sky.
"clear for action!"soon, the commanders gave orders after noticing that the battle was imminent, and the players who were scattered throughout the building, on the ground, and underground, jongro got ready to fight.
woo woo woo-then, the airships that had been hidden among the buildings began to appear by raising their altitude.
"focus all the fire on the hole!"they already warmed up the cannons for fire.
"let's give them a hard lesson!"

- caution! the advent of the 'angel army' has begun in the area.
with that brief message, the hole expanded several times in an instant.
 then it wriggled as if to throw out something.
kaaaaaaaaaaaaaah!a terrible scream that could not be believed to be the angel's voice came out first.
with sweat on their hands, everybody looked at them.
 it was such a cliffhanger.
"oh my.
.
.
there are so many angels!"at first, they thought only a huge cylinder was coming down.
 tens of thousands of angels squeezed through the narrow hole and came out, entangled together.
 then they dispersed in all directions, spreading their wings.
they had white and soft wings, white and soft bodies, and brilliant blonde hair, but their faces were torn vertically with only one long mouth that was watering thick saliva.
kaaaaaaaaaaaaaaah!faced with such an overwhelming enemy, the necromancer who was in control of the allied forces, issued a short order.
s "concentrate fire!"at his order, the players pulled the triggers at the targets that they aimed in advance.
bang!follow new episodes on the lightnovelworld.
c‌om platform.
welcome fanfare? maybe that was the right word to describe their attack.
 it was more like a firecracker than bombing.
 fireworks that filled the sky.
.
.
bang! bang! bang! you can also read this novel on the more advanced platform lightnovelspot.
com

 