\section{chapter 347}

chapter 347: jeju island and attack on demon’s cave (11)she said that the demon’s cave looked so much like earth.





sungwoo wondered what she meant by that, but he had to take care of something more important than solving the riddle now.
 the black lion finally sensed something.
he said, “i can feel it.
 i can feel a huge beating sound coming up from the underground.
 periodic vibrations are spreading throughout this world.
”“where is it coming from?”the black lion raised his left hand and pointed somewhere.
“it’s coming from the west.
”given that it was a periodic beating sound, it was obviously coming from the demon’s cave.
so, sungwoo felt he could find some clues if he moved there.
“if we climb higher, i think we can get out of the sandstorm.
 what a relief!”like kyungsoo said, they could escape from the thick sandstorm by raising the altitude of the messenger airship higher than the building.
“now, we’re going to fly westward at full speed!”at kyungsoo’s order, the messenger sped up.
 even at high altitudes, they could not see clearly enough, but they could move forward without any obstacles after a long time.
“we’re out of the sandstorm, but we have to be vigilant because we don’t know what’s going to happen!”they entered the demon’s cave, but there was no collision yet, which was good for them.
 but they could not get rid of their anxiety because the demons didn’t yet appear.
sungwoo stood in front of the window and looked down at the ground.

‘why did they make this place the same shape as the earth?’ sungwoo wondered.
looking down from above, he noticed that the sandstorm wasn’t all over the place.
 some areas were fully revealed after the sandstorm swept over them, but they really looked terrible.
the han river was filled with sand, dried up, and some parts of seoul disappeared in huge pits.
 given their location, they looked like the bangbae-dong areas.
as if there had been a huge explosion there, everything around the holes was ashes.
it was when they moved a little further west they saw more of it.
“we’ve detected something huge in the west!”what surprised them most appeared in the west where they were headed.
 a huge shadow had been laid behind the sandstorm for a long time, but it was not clearly visible because of the dust layer.
“oh my… that is huge!”when they approached it a little closer, they found that it was so huge that they couldn’t compare it with a typical building.
 it looked as if it was hanging from the sky over seoul, and its top pointed into the sky over the clouds.
“sungwoo, that’s yeouido over there, right? and that is the world tree, i think.
”like hanho said, there was a huge world tree in yeouido.
 however, it was so huge that it could not be compared with the world tree of suwon village.
‘it this the world tree at the stage of completion? no way!’sungwoo couldn’t say anything at the spectacular presence of the world tree.
“hey, why is the world tree here?”
“what the hell is going on?”all of them were stunned.
 the world tree that grew so tall in yeouido and its huge roots that rose from its base wrapped the entire city like hair.
 the epicenter of the destruction of this world seemed to be right there.
“then, where are we now?”“well, this place is…”“uh? can you find out something?”sungwoo seemed to know something.
 this kind of situation was rather familiar to him.
“this is the bad ending.
”this was a scene from ‘bad ending-2’, a prophetic stone that junghoon had shown him a long time ago.
 they were now in there.
the messenger made its way west along the dried han river then navigated into the shadow of the world tree.
when sungwoo raised his head and looked up at the sky, the branches of the world tree kept protruding out and bending back into the dark clouds that filled the sky, creating a bizarre scene.
“it’s like dozens of dragons were flying, entangled with each other,” said hanho.
on the one hand, it looked so unrealistic that they felt like they were looking at the tangled pipes and wiring inside a torn ceiling.
‘this is the stage where the world tree has grown completely.
”watching the world tree in yeouido at close range, sungwoo became more convinced that it was the ‘devil’s world tree’.
‘it is just the same as i saw in the prophetic stone.
 the difference is that it’s dead now.
’he could feel no power in the devil’s world tree.
 for such a powerful being, it should have emitted something extraordinary, but it didn’t.
as for sungwoo’s world tree, it was radiating a blue light day and night.
 besides, it even emitted intense mana that even low-level players could feel.
“do you feel anything extraordinary about that world tree?” sungwoo asked the black lion, just in case.
 he was so good at detecting something with his senses that he could detect the birth of the world tree through his special ability.
“well, as far as i know, this world tree was dead a long time ago.
”sungwoo nodded at his analysis.
 although it was obviously overwhelmingly large, its branches that reached beyond the clouds were bare, without a single leaf.
 and there were piles of huge leaves that had not yet rotted along the tributary of the han river surrounding yeouido,“however, i can feel the intense power underground, namely under the world tree.
 that is the source of the periodic vibrations that we first sensed.
”the black lion once again sensed the exact position of the world tree.
 there was a reason why the world tree stood there.
“then, is that related to the heart of demon’s cave?”“i guess so, given its location.
”but there was no way for them to get under that huge tree.
“should we leave the messenger to get down there?”like kyungsoo suggested, it seemed that they had no choice but to find some gaps between the roots.
but this wasn’t a good way.
 it would take quite some time for them to wander through the maze between the roots under that huge tree.
“well, let’s check it out a little bit more,” sungwoo replied.


when sungwoo said that, the messenger slowed down and began to slowly check the yeouido region around the world tree.
they had to take extreme caution because some buildings stood precariously, leaning between the roots, although most of the buildings collapsed.
“uh! look over there! there is a huge hole in the middle of the world tree.
”soon, one of the crew members discovered a crucial hint.
 after checking it using the telescope item, kyungsu handed it to sungwoo.
“even from a distance, it is clearly a huge hole.
 it’s kind of like a knot on an old tree, and maybe the messenger can land on it safely.
”sungwoo checked the hole with the telescope.
“it looks like something pierced through it.
”there was no possibility that such a hole was created naturally.
 above all, the rim of the hole was crumpled inward.
 it was a sign that the deformation was caused by a strong external force.
“really? what could have pierced that? that monster ate the entire korean server, right?”“we’ll have to go there and check it out.
”the messenger turned and headed towards the hole.
 however, not all the questions were solved easily.
gugugugugugugu-an unknown roar sounded from somewhere.
 it was a wave of air that seemed to cause something to move in unison as if a huge piece of cloth was swaying in the wind.


 