\section{chapter 222}

                             




[item information]-name: ginseng of the mountain spirit-grade: legend-category: consumption-effect: by accepting the ‘mountain spirit’, you can get a tremendous increase in stats.
 also, the ‘affinity and dominance’ for nature and spirits increases significantly, and you can sometimes get the’ power of the mountain god’ (deity status).
* caution! to fully absorb it, you need a ‘stamina level’ of at least 80.
 (recommended: 100)* caution! if you already have a different ‘deity’ status, they can clash against each other and have adverse effects.
-description: this is the ‘spirit’ formed after an unqualified person forcibly took the ‘ginseng of the mountain spirit’, so it has become much stronger because it was taken by an arrogant person.
sungwoo said, “i think what i have is probably that item, the ‘ginseng of mountain spirit.
'”it was an item with which sungwoo could get deity status, but he could not use it, not to mention any colleague who could meet the requirement for its use.
so, he gave it to jisu because he trusted her so much.
‘for me, the legacy of the shadow king is far more valuable than this,’ he thought to himself.
if he could get the shadow king’s legacy, the last item, he would be able to get stronger.
 no matter how much he would spend, he wanted to have this item by all means.
“oh, i think you’re right.
 thanks, i’ll bring you the last legacy of the shadow king by all means.
”jisu accepted the ‘ginseng of the mountain spirit’ then took out a scroll, which seemed to be an item that could take her back to mt.
 taebaek.
“i think i have to go back now.
”he felt a bit uncomfortable about her going back to the deep mountains, but he had no choice but to trust her and wait“be careful.
 don’t believe him unconditionally.
 even if he is good to you, he’s nothing but a monster!”“i’ll keep it in mind.
”jisu soon opened the portal using the scroll.
 she walked into it.
 shortly afterward, the portal was closed and she disappeared again.
“uh? where is sis jisu? she is not parting with us to be independent, right?”“just think she is on a business trip.
”“are you sure? let me ask you just in case.
 please don’t send me on a business trip.
”right after that, sungwoo resurrected the bodies of the ninjas into skeletons.

-you can check the ‘memory fragments’ of the deceased.
“sure, show me who sent them.
”although sungwoo was preparing for an attack from an overseas server, he never thought that an assassination team would be dispatched so quickly like this.
 although he was very much embarrassed, he felt strongly inclined to fight and beat them.
‘let me find out the guys who were responsible for sending the ninjas and get even with them so they can’t challenge us again’sungwoo was determined to make the instigators pay the painful price.
soon, the scenes were shown through the fragments of the memory.
 they were the memories of the ninja.
 the place was the lobby of a shopping mall in korea.
 dozens of ninjas caught sungwoo’s eyes.
 they numbered more than twice the ninjas jisu killed.
‘it means there are more ninjas somewhere right now.
’the owner of the whole plan raised the map of the korean peninsula.
 his finger pointed to what seemed to be the location they were then suwon.
“no.
 1 unit keeps moving eastward to suwon.
 no.
 2 unit, you guys follow this highway to cheonan and complete your mission.
”it seemed that they were talking a few days before the attack.
“the “hunter company” building in cheonan station.
 you want us to destroy that building then join our forces in suwon.
 is that our plan a?”“right.
 we have no specific goal.
 just destroy it, so much so that they can not rebuild it.
 that’s our client’s request.
”sungwoo smelled a rat at that point.
‘client? is the client aiming at me and the hunter company at the same time?’he recalled only one name at that moment.
***on the rooftop of a hotel building at cheonan station, ninjas dressed in black quickly landed there.
 they climbed up the outer wall of the building and penetrated the rooftop.
puck!“kheeeeeeek!”they easily assassinated the guards on the rooftop and gathered at the entrance of the staircases leading to the building.
“we’ve removed them all.
”there was no fuss while they killed five security guards.
 those in the building were unaware that somebody from outside had infiltrated the building.
“good.
 according to the information i obtained from torturing a man captured on the ground, their leaders are now in a penthouse.
 if we storm there and kill them all, they will collapse quickly.
”after he was done briefing, the leader of the no.
 2 unit put on a mask.
 then, he pointed his finger at the floor.
“now, go through the ventilation and kill those in the upper corridor first.
 go!”
the ninjas moved in unison and carried out the planned operation.
 the synergy of  added deadly power to their movements.
like painless, deadly poison spreading through veins, the ninjas slowly began to occupy the building.
then, shortly afterward, the door of the penthouse opened, and seven ninjas entered.
“uh?”“who the hell are you?”the president of hunter company and his executives who were meeting in the office of the penthouse opened their eyes wide.
“how are you?”“who the hell are you?”the hunter company leaders were stunned by their unexpected visit and overwhelmed.
wasn’t this a penthouse on the top floor of the hotel? in other words, there was watertight security around the penthouse with multiple layers of security guards guarding the place.
but the ninjas infiltrated without being caught, which meant they could not handle these infiltrators.
“stop, everybody!”the president stopped the executives from trying to take out their weapons and stood up.
he sighed, putting his hand in his pocket.
“okay.
 you guys are the ninjas belonging to the yamato guild who had secret meetings with the evolution society, right?”“oh, you have been digging up the information about our client.
 it looks like you guys are not dumb,” one of the ninjas said.
the ninja then lowered his mask and sat down on the sofa.
 he seemed relaxed.
the president sitting on the opposite side faced the ninja, then said, “of course.
 that client was once our client.
 they gathered information about you through us.
”“really? but i don’t think you should act arrogantly like that.
 you dumb bastard, knowing nothing!”at that moment, the ninjas moved and cut the necks of two of the four executives.
they put the blade against the president’s neck.
 he glared at them, swallowing nervously.
“hey, don’t try to put on airs.
 we are not negotiators.
 we only move to kill people.
”“…”“the stupid korean server, and the necromancer, the symbol of your server, will soon die.
”at that point, the president of the hunter company smiled before he knew it.
“hahaha!”“are you laughing now?”“did you say that you would kill the necromancer? no way! i don’t think so.
”the president was in awe the moment the “world quest” appeared because he believed he was the only one who would solve the fundamental problem of this game.
 therefore, he had a vague belief that the necromancer would never die.
the ninja smiled scornfully then responded.
“did you say you didn’t believe what i said? that’s your problem!”the ninja pushed his head down and tightened his hold on the handle of the sword.
 blood was coming from the president’s neck.
the ninja continued, “from the very distant past, you’ve been swimming in a well, trying to keep your pride without knowing anything.
”he struck the table with his fist.
 the center of the wooden table was hollowed out as if it had been hit with a hammer.
“…”“but in the end, the moment you’re placed in the wild like this, your bare face is revealed.
 you inferior people!”the ninja stood up and started spinning the sword.
“so, now it’s time to kill …”but at that moment, the ninja raised his head suddenly.
“boss!”“somebody is coming to us!”all the ninjas felt something strange, so they looked out of the window, stunned.
at that moment, something wriggling on the wall caught their eyes.
it looked like a ghost, but passed through the wall and disappeared.
thud! thud!the next moment the sound of bursting rang from the hotel’s ceiling, along with tremendous vibrations.
 soon, cracks like spider webs spread and stone dust poured out, causing the whole ceiling to be lifted.
“what the heck is going on?”wind blew in along with the debris from the ceiling.
 the ninjas frowned as the sunlight fell on them directly.
 the president of the hunter company found something between them.
“oh, my god! no way…”

dozens of bone wyverns were raising their wicked claws and scraping a pile of concrete like tofu.
“necromancer?”“no way, he can’t be here!”when the ninja denied it in an embarrassed voice, the president scored at him.
“hahaha, did you deny what i said?”“you bastard, how dare you speak out against me?”the ninja tried to swing his sword, but the necromancer, a man wearing a dark green robe, landed on a wooden table in the middle of the penthouse.
startled, the ninjas stepped back.
 they threatened to charge at him, but they didn’t dare to.
-your body functions are weakened due to unknown energy.
* all stats decrease.
 (-4)when they encountered a message they couldn’t understand, they had no choice but to feel fear beyond embarrassment.
“what the heck is this?”“why are our stats going down?”“how could they break through the roof and come in?”the necromancer, standing in the middle of them, slowly looked around.
he soon fixed his eyes on the president of the hunter company.
“are you taking care of my request well?”“well…”sungwoo continued, stroking the wounds on his neck with his hand.
“let me ask you for some more.
”“you mean an additional quest?”“bring me the information about the japanese server.
”“if you mean the japanese server…”the necromancer looked at the face of the ninja leader and slowly opened his mouth.
“i think the japanese server is going to be my next hunting ground.
”

 