\section{chapter 172}

                             




jisu adjusted her combating posture quickly then swung her sword twice, cutting two arrows in the air.
they were enforced arrows.
 small arrows were added to the barrel before firing.
 they were much faster and more powerful than normal arrows, but that wasn’t the end.
“it seems that the arrows are flying fast because of the accompanying wind.
”there was a reason why they were pursuing the bone wyvern.
 since they had a couple of wind exorcists, they could freely control the air fight in their favor.
sungwoo couldn’t send the zombies because the enemies were dominating the flow of air.
peeeeng!this time two enforced arrows were fired from both sides at the same time.
jisu held her breath, ready to beat them back.
“uh? what the heck is that?”just like a fish going up a river, the flying arrows were changing their direction by drawing a curve up and down as well as left and right, controlled by the wind exorcists.
since jisu could not predict which way the arrows would fly, she could not strike them back.
the wind exorcists intended to change the direction of the wind exactly at the moment jisu swung her sword.
however, jisu moved faster and threw the spirit of her sword by using her swordsmanship skill, intercepting the arrows before the wind exorcists could change their direction.
“phew…”jisu was ahead of the enemies in predicting each other’s coming attack.
shortly afterward, the bone wyvern flew among the apartments, lowering its altitude rapidly.
 the helicopters followed the bone wyvern.
 it was as if the fighters engaged in dogfighting were sliding into a canyon.
doo doo doo!a black shadow quickly fell from one side of an apartment and collided with the helicopter in the rear.

bang! kugugugugugugu―the helicopter lost its balance at the impact, then nosedived after scratching the outer wall of an apartment roughly.
 there was the sound of a big explosion.
bang!the object that collided with the helicopter was ghoul king.
the giant monster jumped from the roof of the apartment and struck the helicopter’s tail.
“nice! it was a good operation!”sungwoo summoned ghoul king on the roof of the apartment then had the bone wyvern flow low to lure the helicopter into the trap.
ghoul king climbed up the outer wall of the apartment like a spider and began to hunt for the tails of the other two helicopters.
 naturally, the enemies had no choice but to focus on the rear for fear of ghoul king’s ambush from behind.
“jisu! hanho! now is the time to take them!”“pardon? what do you mean?”“when they are focused on the tails of the helicopters, you have to take over the helicopters! have them get off the helicopters except for the pilots!”“i’m ready!” jisu loosened her shoulder.
“what? what are you ready for? are you guys crazy?”at that moment, nine monster birds grabbed jisu, hanho, minsok, and orun by the shoulders.
 then, they flew straight towards the two helicopters.
“hey! you crazy monster birds!” the enemies hurriedly aimed at the monster birds, but the five birds blocked their attack while orun and minsok rushed into the helicopters first.
of course, jisu and hanho were dispatched last for safety reasons.
 to take over the helicopters, somebody was needed to threaten the pilots.
***one bone wyvern and two helicopters landed at hwaseong square in suwon.

hanho walked out with a sullen expression and opened his mouth.
“sungwoo, i sincerely and seriously picked no.
 1 from that server quest.
 i was embarrassed this time.
”“well, i was trying to get you a helicopter that you like.
”kyongsu and inho approached sungwoo and his party.
lots of villagers were on standby, fully armed, behind them.
“welcome back.
”“as you can see, no one has chosen no.
 1.
”the villagers greeted sungwoo gladly, although he had a huge bounty on his head.
 it was natural they welcomed him back.
 they survived because of his help from the beginning of the game, and they have been relying on him for survival since then.
“i thought you would be okay, but i’m really glad you are okay.
 we have tightened the security just in case.
”“thank you.
 you did very well, as i requested.
 you did a great job!”kyongsu upgraded the villagers’ average level to 8, but kyongsu and inho seemed to be more concerned about what was happening right now than their level upgrade.
“by the way, there is a big uproar on the community bulletin now! there are so many social media whores who say they will kill you.
”“even some extreme guys are attracting argos by turning on the broadcast.
 i’ve never seen so many broadcasts turned on at the same time like this.
 they called you a hero, but now they are hell-bent on killing you!”like they complained, the korean server’s community and private broadcasts were overflowing with those who said they would kill sungwoo by choosing no.
 1 on the server quest.
“you don’t have to worry about it,” said sungwoo.
he thought their behavior was extremely normal.
 as soon as a person who has been enjoying great popularity became a problem, a large number of unspecified people would attack him in the real world.
 that was happening to him now.
sungwoo easily saw this phenomenon on the internet before its demise.
 therefore, it was not correct to think that the korean server turned against him by judging the current community atmosphere alone.
“the moment they notice the turn of events, they will be quiet again.
”sungwoo was confident that he could change the situation soon.
“ugh!”at that moment, sungwoo felt a hot pain again.
 it was caused by something deep inside his pocket, a small object hidden there.
“what’s the matter with you?”he pulled it out of his inner pocket.
the small object emitted a brilliant light.
“oh!”“what is that? is it a seed?”“i don’t know about it, but it seems like a great thing.
”the seed of the world tree was once again shining.
-by achieving certain conditions (the third choice), you have obtained qualifications to become the ‘founding father’ of the new camp.
* if you plant the seed of the world tree now, it will grow as a “god tree” that will bless your camp.
* to achieve this, you must complete the quest ‘the third choice’ and succeed in ‘creating a faction’.
“god tree?”now, the seed was in the safest place, and it was the perfect time to plant it.
***where should he plant the seed of the world tree, a huge tree with magical power?since it was hard to move once he planted it, he had to be very careful.


‘previously i would have considered planting it in other areas outside of suwon village…’it was dangerous for him to go far because he didn’t know when and where the players could ambush him.
‘in the current situation, there is no other place than one near the village.
’considering that he had to protect it until it grew, sungwoo thought the more closely he planted it near the village, the better.
‘didn’t i get the warning that if the world tree was destroyed, it would cause disaster? i need a place that is easiest to defend with all our strength rather than hide it.
’so, he decided to plant it in the square in front of hwaseong palace, right in front of the city art museum, the main building of the village.
sungwoo used a large skeleton to create a ‘flower bed’ on one side of the square.
he scraped off the sidewalk blocks and marble from the ground and dug and carried the soil from mt.
 paldal, located next to the village.
 since he didn’t know how big the world tree would grow, he had to prepare enough soil for its roots to grow.
rattle! rattle!the undead skeletons could work tirelessly, and when the players in the village helped, a small hill was created in a day.
“leave some flat ground inside the square.
 it should be used as a helicopter landing area,” sungwoo said.
when the world tree grew large, it might not be possible for aircraft to take off around it, but for now, he needed space for a helicopter or bone wyvern to fly.
“before planting the tree, we will tighten the security around this area.
 as a matter of fact, we were expanding the watchtower to the surrounding area,” said kyongsu.
inho added, nodding at him, “we are checking the safety of shopping malls and installing facilities on the rooftop.
 i think it’s good to make this neighborhood like a castle by blocking the alleys.
”sungwoo agreed with that idea.
“it seems like a good idea.
 i would also like you to find a place where you can install the flying weapon, ‘iron mace of lightning god,’ that i sent here recently.
”“how about installing one of the two flying weapons on the top of mt.
 paldal? i think we can get something like camouflage material from a nearby military base.
”“sounds like a plan.
”

 