\section{chapter 353}

chapter 353: jeju island and attack on demon’s cave (17)this chapter is updated by wuxiahere.
com




as soon as they appeared, they scattered to the left and right.
 jisu jumped straight ahead to attack the monster on the left from three directions.
at that moment, the horns and bumps that were enveloping the monster’s head began to open.
 she had seen such an attack before.
the monster’s horns and projections moved in different directions as if they were tentacles.
 and they jumped up in an instant and pierced into jisu like an awl from all directions.
although she barely escaped their attack by moving left and right, the two tigers bounced off, hit by the attack.
“khuuuuuuul!”“damn it! how come their attack is so powerful?”since they once destroyed sungwoo’s undead army, their attack was very destructive.
but jisu felt something else.
‘well, i can cut them…’she instinctively felt that the monster’s powerful horns and protrusions belonged to his body, after all.
 so she thought if she could cut them, she could rip the monster apart.
the monster attacked jisu with horns again, but she stopped on the steps to avoid his attacks, and at the same time, struck his horns with her sword.
his two horns were cut off at once and scattered in the air.
then, the monster started to step back.
 was he surprised by her unexpected counterattack?it was natural that the monster was embarrassed because he was hit hard even though he attacked her first.
‘yeah, i’m stronger than i thought,’ jisu muttered.
she realized that she could win this fight more easily than she thought.
 in fact, she grew so fast and strong by going through ‘awakening’ and obtaining ‘deity’ status that she didn’t realize it.

she took a deep breath, then stopped on the spot.
the monster gatekeeper held out his staff this time.
 it was a light attack.
bang!jisoo jumped to the side to dodge the attack.
“by the way, can you use only two skills? not any more?”jisu adjusted her posture then started walking slowly towards the monster.
 she was now ten steps away from him.
 the monster once again attacked her with his horns and projections.
this time she did not avoid his attack.
 instead, her sword was embedded with dark sword energy.
 then, she breathed out, then swung the sword with all her might at the flying horns and projections of the monster.
clang! clang!dozens of blue blades spewed out and collided with the monster’s horns and projections.
at first, the rotating speed of the blue blades clashing with his horns seemed to slow down for a moment, but the horns and projections were all split apart and scattered in all directions.
jisu crushed them with one single strike.
she sneered, “now you’ve got only one skill, right?”she smiled unwittingly because she was sure she could win the fight.
“it looks like this game seems to be pretty easy now.
”***the two monsters everyone feared were killed.
 they collapsed too easily at valkyrie’s sword attack.
 those who watched their fight could not believe their eyes.

-the ‘wave 2 stage’ of the gate of demon’s cave has been completed.
 after 20 seconds, the next wave begins.
“jisu, you have really changed a lot…”jimin couldn’t hide her surprise at her sister’s astonishing fight.
 no wonder her existing perception of jisu changed completely.
“i really didn’t know you changed so much.
 i think you are very different from the old you that i used to know.
 seriously.
”jisu nodded at her sister’s words because it’s true.
 of course, she hadn’t changed much for the last five years since she left the house.
 she definitely changed a lot only after the game began.
“when i was at the training center, i probably didn’t know how to win.
 back then i…”why couldn’t she overcome the wall? now she seemed to know why.
“i think i was just trying to survive.
 my approach was wrong.
”she tried hard to get the attention of her family members while trying not to be forgotten in the family.
 rather than trying to bring about personal achievements, she just fought hard to grab others’ attention.
 that was the problem for her.
if she fought for her safety rather than her achievement, she could exert superhuman power for a moment, but she couldn’t do it for long.
 she needed a more determined motivation to grow steadily.
‘this game is the same.
’if she participated in the game just to survive, she could end up being a mere survivor, but she couldn’t become a special hero.
‘in that respect, sungwoo was different from the beginning.
’sungwoo, the necromancer, fought to survive, but he sought greater power to survive tomorrow.
 and his approach was the answer.
“the way of winning? didn’t dad teach you? where did you learn that?”when jimin asked, jisu looked at the portal and said, “well, i learned it from the person who always won.
”she had sungwoo in mind, of course.
***“we need some people who can defend the airship.
”after they removed the heart of the gate of demon’s cave, several people had to stay behind in order to prepare for an emergency escape.
 in the end, six of the crew members volunteered to stay on the airship.
“the demons will soon enter this hole.
 if you hide and keep silent, you won’t be able to attract the attention of the monsters.
 good luck!” kyungsoo said with a bitter expression.
although he said in a calm voice, he could not guarantee their survival.
“do not worry.
”“we will make sure to survive and prepare for your escape.
”the players of the world tree camp were not afraid to make sacrifices because they knew they could survive and grow until now because lots of people were united behind the necromancer.
“aren’t we always winning, right?”“sure.
 we’re going to win this time, too.
”they had a strong sense of pride as well as a sense of solidarity.
 their strong sense of solidarity made them never hesitate to make sacrifices for their organization.
“we’re going to descend right now! everyone, come over here!”in fact, their entering the devil’s world tree didn’t guarantee them survival and success.
those who entered here as well as those who fought outside came here, determined to fight until they died.
 if either of them failed, it meant their annihilation.
‘that’s why they should succeed by all means…’

when kyungsu approached the vertical passage of the world tree, all of them had already gathered.
“only one person can go down at a time.
”they looked down the hole.
 they had to enter the veins of the devil’s world tree.
“let’s send the skeletons first.
”sungwoo summoned four ‘werewolf skeletons’ and sent them down to secure safety then had the crew members go down one after another.
he hugged mir and rode the rappel last.
 it took him less than 5 seconds to get to the bottom.
“this place is bigger than i thought.
”kyungsoo, who went down first, handed sungwoo a flashlight.
 “well, i don’t think the winged monsters will enter this place.
”the interior of the hole looked like a crypt.
 there was a gentle downhill wide enough for three people to pass, and the foul smell of mold filled the passage.
 so much so that they felt a headache because of the smell.
“man, isn’t this the smell of dying trees?” kyungsu asked.
like he said, this space itself was decaying.
 sungwoo couldn’t believe this was once the inside of the world tree full of vigor and vitality.
 death did not leave anything magical behind.
“i will send the advance party first, then,” said kyungsu.
for the safety of the expedition, three thief-type players set off as the advance team.
they would first check the route first and report back if they noticed any danger.
“alright.
 let’s start now.
”the main team, including sungwoo, started with some distance from the advance party.
“this is not an ordinary cave, but the inside of a tree, so we can’t predict what kind of terrain is waiting for us.
 i just hope we won’t encounter a cliff.
”

 