\section{chapter 460}

the cracks in the amazon widened with a roaring sound, then a huge hand rose between the cracks and touched the ground.





at that point, a giant in red came out of the cracks.
kugugugugugugugugu-it looked as if a huge mountain was rising.
 then, when he began to show up finally, he looked like a baby devil that ripped off its mother's belly.
"he has come out!""prepare the shield!"he was huge for a baby monster.
'man, he's at least 1km.
'when sungwoo looked at him, he felt like he was looking at a huge mountain peak.
he was at least twice as large as gigantes.
 he even had three heads, twelve eyes, and eight arms, so he could monitor everything in all directions.
of course, he had blind spots on his super large body.
but that wasn't the end.
"uh? po, portal! it moves!"the four portals that were open in the sky slid down through the air like magnets attached to an iron plate and started to stick to the body of the demon king.
 his flesh melted and the portal settled in it.
 it was a strange mix.
and hell creatures, large and small, started crawling out of it.
- the world boss monster 'demon king (complete body)' has appeared.
the true form of the demon king was hell itself, with the portal hanging on his body.
- guide! the voting for the 'oath of allegiance' to the demon king has been completed.
along with the appearance of the demon king, voting for the 'disaster quest' that came up a little while ago was also completed.

'the message clearly said that the power of the demon king depends on the voting rate.
 if that's the case, he can be stronger than now…'[vote results]- oath of allegiance: 8.
8%- refusal of request: 91.
2%* fails to meet the minimum condition (10%).
 no effect is given to the target (demon king).
only 8.
8% of players pledged allegiance to the demon king.
"what the heck!"sungwoo smiled at the results, then looked up at the demon king without realizing it.
"hey, think about it.
 who is going to vote for you when you're in such disgusting shape?'according to the results, it suggested that the remaining 91.
2% supported demon king's rival, sungwoo.
gangsok made a mistake.
 he had never thought that the voting results would be like this.
'but if the demon king didn't receive the expected power, was there anybody else who got the power instead?' sungwoo thought.
at that moment some white light began to flow from sungwoo's body as if his guess was right.
 and at the same time, a congratulatory message appeared before everyone's eyes.
- congrats on overcoming fear and uniting the world! more than half voted against the demon king, so there emerges the 'expected warrior.
'the expected hero referred to the demon king's only rival, namely sungwoo.
'is this the condition for being qualified as the expected warrior?'- by satisfying special conditions, you are given the hidden skill 'warrior's privilege'* this privilege is effective as long as the 'demon king (complete body)' is alive in the world.

[skill information]- name: warrior's privilege- grade: privilege- class: passive and active-consumption: nonethe warrior's stats increase (+20), and his damage by the demon king and his subordinate spirits is reduced by 'half'.
+ colleague selection: the warrior can choose 'colleagues' to confront the demon king.
 (four in total) all his colleagues' stats increase (+15), and their damage by the demon king and his subordinate spirits is reduced by half.
+ warrior's alliance: all stats of the warrior's allies' in the vicinity (within 1km) increase greatly.
 (+8)+ appearance of holy sword: one single wield contains the aura of the 'holy sword'.
 it deals additional damage to the demon king only.
 (+2,000%)"colleague selection?"the warrior was supposed to have colleagues to defeat the demon king.
but all his colleagues who could beef up his power were inside the castle of the demon king.
sungwoo turned his head and looked at the demon king's castle.
'they're still inside the castle!'none of them came out yet.
***"oh, dear.
.
.
"jisu took a deep breath in a mysterious shadow created with the mix of the two elements, darkness, and light.
'i don't know which one is real.
'vivona had as many as eight shadows, but only one of them was real.
since they kept spinning like propellers before suddenly attacking her, she could not figure out which one was real.
wooooooo-moreover, since the shadows didn't make any sound, she could not detect them with her senses alone.
in the meantime, she managed to dodge vivona's attacks dozens of times until now.
'i'm at a disadvantage now.
'blood trickled down her fingers and fell to the top of her toes.
she already had her shoulder and back cut.
 even though the cuts were not deep, she could have her head cut anytime when she let down her guard.
``it's more difficult for me to break through this obstacle because i can't summon einherjar.
'this was vivona's territory.
 since she could not open a different space, she could not summon einherjar.
 she had to overcome this obstacle by herself.
sheeeeeeeeeeek!at that moment she heard the wind cracking behind my back.
 it was vivona's attack.
since his shadow claws attacked her in a curved line, she could not avoid it by simply moving.
"khuuuuuuuuk!"she jumped forward and twisted her body in the air.
but she failed.
 something sharp brushed past her right neck.
"argh!"

his neck felt hot.
 there was a big cut on it.
 it was a pretty dangerous blow.
without caring about the pain at all, she got prepared for his next attack.
but she could not hold out like this forever.
'if i can't block him, i'm going to die at the end of the day.
'she already bled too much.
 every time she moved, the wounds opened and blood gushed out.
 but she could not get the priest's help, nor did she have time to use the healing potions.
"tut, tut.
 what a pity! you're going to die anyway.
 are you going to die like minced meat?" vivona sneered at her.
 he could not control a cynical laugh.
"whew…"but jisu was not shaken by his provocative words.
 even though she was in a bad situation, she was calm and relaxed because she had gone through this kind of fighting many times.
'let me think it over.
 there is definitely a way for me to get out of here.
'even if she died here, she was determined not to let him leave without suffering any damage because he would be a huge obstacle to sungwoo's allies.
so she made the final judgment.
'yeah, even if i was wounded seriously enough to die here, i should kill him, too.
'in other words, she adopted a strategy of 'kill me, i'll kill you.
'if she could not win the fight here and join sungwoo's allies, she thought it would be better to die here with vivona, one of the important forces of the enemy.
'alright.
 let me use that card!' even though it's an extreme card, she had saved it until now.
in particular, this was a hidden weapon with which she could kill the opponent with a single strike in a one-on-one match that involved the fight between players using swords.
she jumped off the ground.
"oh, great! which part of your body do you want me to rip apart this time?" vivona shouted, opening his eyes wide and smiling broadly.
 "can i rip your stomach and let your intestines hang loosely?" then he licked his tongue.
"alright! that sounds good!"

 