\section{chapter 253}

                            the blessing buffs improved when the world tree entered the ‘1st stage of maturity.
’




-‘abundance of godly tree (second stage)’ is given to the whole area.
* item creation success rate increases.
 (+60%)* increases the probability of additional options when making items.
 (+20%)* item production cost is reduced.
 (+30%)* increases the probability of finding rare materials nearby.
 (+10%)as a result, the two blacksmiths’ desire for production was soaring high.
 they took great delight in working because every time they attempted to make items, they succeeded, which, in turn, gave them great options.
“bachelors!”mihee, hanho’s mother, came in between the two blacksmiths.
“if you have any remaining bones, don’t take them all.
 hand them over to me.
 i’ll make delicious beef bone soup for you.
”as a chef, she developed a variety of menus to take care of not only the health of the players but also give various buff effects.
“oh, my god! ogre bone soup? i don’t want it.
 to be honest, it’s so terrible.
”“why not? it’s so savory.
 because of the strength buffs, i feel stronger when i hammer the bones.
 you still don’t know how to enjoy the soup.
”“really? just go ahead and take my bone soup, too!”the players showed their preferences for monster ingredients.
“uh? how come you can complain about the food? you should count your blessings and stop complaining! you know what? what you ate last night was red oak head meat soup.
 didn’t you put rice in it and ate it as if it was the most delicious thing?”“what did you say? oh, my…”“oops! i feel like vomiting…”meanwhile, kanghwa island players, who were assigned tasks, were busy getting accustomed to their new work.
there appeared some with extraordinary skills among them, contributing to the rapid development of the village.
 muyon, the leader of the kanghwa island players, was one of them.

“necromancer, i think my job can help fortify our village.
”“what kind of job is it?”“it’s high-architect.
 it’s a four-star job in the field of architecture.
”an architect was a builder.
 however, the prefix ‘high’ was important because even if they were in the same field, the higher their grade, the more powerful skills they could gain.
if he had a four-star architecture job, he would certainly bring about significant change in the surroundings of the village.
“well, can you build something like a fortress?”“yes.
 but until now, i have hardly ever used it because it requires a lot of gold.
”having said that, muyon handed him a piece of paper.
“after i came to this village, i designed it quickly last night.
 would you like to take a look at it?”sungwoo took the paper.
-you have just contacted the ‘blueprint (a draft for the castle wall)’.
then, as if he touched the prophetic stone, something like a video appeared before his eyes.
-you’re now watching a bird’s-eye view of the ‘castle wall blueprint’.
the scenery of the suwon village centered around the world tree came into his view.
 a high wall surrounded the world tree and the village.
it was a bird’s-eye view, as described, and showed the building to be completed.
however, this was not just an image.
 sungwoo could look into any part of the building he wanted and get detailed information about it.
[class b castle wall (detailed information)]-height: 15m-width: 3m-material: general rock, magic mineral, etc.

-effect: magic shield (5,000), shooter attack power increase (+10%)-cost: 30,000 gold per 3m² (excluding material cost)when compared visually, it looked much taller and more solid than the nearby suwon-hwasung castle wall, not to mention its functionality in the actual war situation.
furthermore, there were even “magic turrets” placed everywhere.
[b-class magic turret (details)]-height: 17m-width: 4m-material: mana stone, magic ore, fire core, etc.
-effect: magic shield (6,000), mage-type attack power increase (20%), self-attack ability (4-fire flame turret)-cost: 250,000 gold per 1 housewhen sungwoo approached the area, the scenes of its use began to play automatically.
ghaaaaaaaaa!a group of 20 orcs began to approach the castle wall.
 then, the muzzles on the turrets tilted and aimed at them.
goo-woong!they fired four flame spheres with an explosion, striking them.
bang!they were killed on the spot.
 with a heavy explosion, heat expanded and covered the surroundings.
 twenty orcs were barbecued at once.
 the asphalt floor they had stood on boiled, giving off intense heat.
‘if they can make something like this, it would be a jackpot for us!’they looked like weapons that could fire pretty powerful flames and freezing magic.
the village players had been preparing for the defense of the castle, but all they could do was block the holes between the buildings using the invisible barrier as the castle wall because they had no players with architect capabilities.
in this situation, if muyon could build a castle wall with all kinds of buffs, it would be a real jackpot for the villagers.
“it’s the best.
 i think you will need it.
 let’s go ahead.
”“well, we have secured the construction material pretty much, but the estimated budget is 150 million gold.
 we need at least such a huge amount of gold to use the automatic construction command instead of manually stacking the bricks…”“do not worry.
 i have enough money.
”currently, he had 599,884,855 gold.
 after winning the metropolitan war, he raked in a huge amount of gold through the betting pool, and he also garnered much more gold by winning a series of battles.
moreover, the amount of gold stored in the “vault of oaths” exceeded 100 million gold.
he couldn’t immediately calculate the total of the world tree camp’s assets with the addition of the war booty that would soon be delivered, so he could easily invest 150 million gold.
“alright.
 let me go over the details a little more and get back to you.
”“okay.
 if there are more options you can add, don’t worry and just add them.
 oh, you had better consult with kyongsu, not me, about this matter.
’“sure, will do.
”kyongsu was well versed in the exact situation of the village.
 since sungwoo had several reliable men in the village including kyongsu, all he had to do was review and approve their projects.
when they were in the thick of discussing the village matters, an unexpected helicopter appeared over the village.
doo doo doo!“huh? are there supplies they are supposed to deliver at this time?”“no.
 they are supposed to arrive in 2 hours.
”“then what is that helicopter?”the mysterious helicopter landed at the makeshift field.
 jisu exited it.
“sungwoo!”as soon as she got off, she called him.
 she should have been at the evolution society headquarters in daejon now, so something urgent must have happened if she appeared unexpectedly like this.


“jisu, what happened?”sungwoo came running to her, but he was rather dumbfounded to hear what she said.
“the king of the great mountain is looking for you, sungwoo!”“pardon?”the king of the great mountain was the king of the monsters that ruled mt.
 taebaek as well as the master of a powerful force that drove away the struggle guild.
 he was also responsible for giving jisu the awakening quest.
how could he look for sungwoo? was there a reason for it? he had nothing to do with sungwoo.
“i had a way to get in touch with me, but he just got in touch with me.
 he said he wanted to ask you a favor, something very urgent.
”“what do you mean by something urgent? it has to be very urgent if you also know about it.
”jisu nodded, catching her breath, and said, “sungwoo, do you remember the prophetic stone you saw? i mean the first prophetic stone i got from the soldiers.
”to the best of his memory, the first prophetic stone foretold the so-called “season 2 of hell’s coming”.
 and it was also an object that gave sungwoo a chance to awaken.
“of course, i know.
 it was about the birth of lich on the first day of the new year and covering the korean peninsula with an army of undead.
 but i’ve already become lich, so it won’t happen.
”“well, that has already happened.
”“really?”sungwoo could not help but be dumbfounded.
“it looks like it occurred because of some hidden element.
 that is…”she paused for a moment then opened her mouth again.
“i think it happened on the north korean server, and it looks like they’re coming south.
”“you mean lich has appeared on the north korean server?”“it’s not clear yet, but i think so.
”jisu didn’t know what happened, but she thought she knew why the king of the great mountain needed the necromancer.


 