\section{chapter 412}

this space was definitely the emperor's territory.
 however, thanks to the power of 'red dragon,' it was changing into a space that was somewhat advantageous for sungwoo.
 




kaaaaah!when the dragon soldiers were exposed to the heat of the 'breath field', their bodies made of flames began to grow rapidly.
- all 'dragon soldiers' within the 'breath field' have been strengthened with 'the heat of the cradle.
'as a result, they exuded steam-like snorts from their huge bodies like bulls.
then they started scratching the ground as if they wanted to charge at the terracottas.
"sweep them away!"when sungwoo ordered, ten dragon soldiers sprinted off the ground and charged.
 they looked like well-trained hunting dogs.
crash! crash! crash!they rushed to the terracottas right away and smashed them to pieces, which looked as if a 16-pound bowling ball was hitting a strike.
"now, let's have a one-on-one match between us," said sungwoo.
he was confident of defeating the emperor in a one-on-one fight.
sungwoo didn't know what kind of trial and error or growth the emperor went through while taking over the chinese server, but given his abilities, it was obvious that he controlled his subordinate spirits while hiding in a safe place.
'probably i am superior to him physically in a situation where my and his subordinate spirits have been neutralized.
"sungwoo walked down the hallway of seething flames on the broken stone fragments and stepped on the first step.
 at that moment something began to appear over the oppressor's hand behind the emperor's back.
 those were huge eyes.
 two eyes slowly opened, with golden pupils appearing.
- caution! 'oppressor's gaze' has been activated in the area.
sungwoo stopped walking up the stairs at that message.
'he used the most important hidden card.
 this is also his divine skill.
'
sungwoo and the emperor were engaged in a fierce fight like this with each of them revealing their skills one by one to gain the upper hand in the fight.
if the world eater's eyeballs were bizarre and terrifying because they were extremely realistic, there was something like an indescribable wonder as seen in an old picture in these eyes.
at that moment, those eyes glowed golden.
follow current novels on lightnov­elworld.
com- you have been exposed to 'oppressor's gaze'.
 all your bodily functions have been weakened.
 * caution! when you're exposed to this state for a long time, you will be vulnerable to the 'mind control' of the oppressor.
 "kheeeeeeeeek!"when they were exposed to the light, the dragon soldiers running wildly stopped right away.
 even sungwoo found it hard to move around.
"come on, necromancer, do you have any other skill you want to use?"the eyes of the oppressor shone again as if they gave out a spotlight.
"argh!"suddenly sungwoo had a bloody nose and heard tinnitus in his ears.
 he felt dizzy and at the same time, he felt like he was throwing up.
after all, he knelt on the third staircase.
"hmm, let me…"at that moment the emperor stood from his throne.
 he raised his hands and rolled up his sleeves.
"i have told you repeatedly that this is my territory.
"then he came down from the podium and stepped on the highest stairway.

"in other words, everything is centered around me here.
 you can't beat me here under any circumstances!"soon the golden threads stretched out from the oppressor's hand and wrapped around sungwoo's neck.
"cough, cough!"then the oppressor's hand lifted him and dragged him right in front of the emperor.
 the scenes of him being dragged before the emperor were broadcast on the air.
conscious of the drone in the air filming the scenes, the emperor dragged sungwoo closer to him.
 since he knew the importance of 'propaganda', he intended to make his victory more dramatic.
but sungwoo seemed relaxed with a burst of cynical laughter.
 "are you laughing at me?"updated from lightnovelworld.
comsungwoo was laughing at him.
 at that very moment, flames erupted from sungwoo's body.
kugugugugugugugu!- the 'boiling armor' of red dragon armor has been activated.
this was also one of the dragon item set effects, which was a skill that formed a tornado of flames around its wearer's body.
 flames rotated and soared along with the armor, and the golden threads wrapped around sungwoo's neck began to burn inside.
 as soon as sungwoo was released from the threads, he reached out and grabbed the emperor's collar, and pulled him closer.
"vanity, yeah, your unique vanity is the problem!"but the old emperor turned up one corner of his mouth.
 even though he suffered some damage from the flames, he was enduring it well as if he was immune to them to some extent.
 he was even trying to recover composure.
"oh, is this your hidden weapon?"but sungwoo shook his head and said, "no, it's not, unfortunately.
"when he heard that, the emperor looked over sungwoo's shoulder.
"ah, then are you referring to that knight hiding behind you?"far away in the dark a monster was snorting wildly.
 it was the headless knight, durahan.
"oh, you noticed it, too," sungwoo shouted.
the emperor shook his head with a sigh and said, "boy, you still don't understand.
 this is my territory.
 you can't pull the wool over my eyes.
 got it? can't you still admit it?"at that moment, durahan started running towards the stairs.
 the emperor shook his head, saying, "tut, tut.
 how stupid!"the 'oppressor's hand' spewed the threads.
bang! bang! bang! bang!durahan drove the horse in a zigzag, but he could not avoid the threads completely.
eventually, one of the threads struck the body of the monster horse hard.
 durahan lost his balance and fell over.
 but at that moment, durahan grabbed something that was on the saddle of the horse and threw it at sungwoo.
tung!sungwoo received the flying object, a huge iron box, with one hand.
 the latest episodes are on the lightnovelworld.
com website.
then he spat out one word.
"enter it!"the emperor's eyes were opened wide.
"gee, what the heck are you doing?"

at that moment, the two disappeared.
 after a brief silence, the drone of the official channel that was filming this scene from the air also disappeared somewhere.
- you have entered 'the forge of hephaestus'.
it was another area.
"what is this?"while trying to stay calm with great difficulty, the emperor looked around.
 sungwoo let go of his hand grabbing the emperor's collar while opening both arms.
his blazing armor was seen first, then a brazier burning hot behind his back caught the emperor's eye.
"come on, we can't use our divine power here.
 so this is a perfectly fair arena for us.
"the emperor glared at sungwoo and said, "did you try to drag me here from the beginning?"sungwoo nodded.
 then he stuck the grim reaper into the ground and untied and put down the winter predator, too.
 "i'm sorry to say this, but i shook the game you have been playing until now.
 we're going to compete under a new rule.
 if you want to get out of here, you have to put your hand on that anvil over there and say 'exit'.
"the emperor's eyebrows twitched.
 he tried to use his divine power, but he couldn't anymore.
 sungwoo slowly approached him.
 then he placed his hand on his shoulder and grinned, then punched him very quickly with his left hand.
"argh!"the emperor's nose and front teeth were smashed completely at sungwoo's preemptive punch.
"ahhhhhhhh, you bastard….
"after giving him a hard punch, sungwoo turned around and looked at the drone camera of the official channel floating in the air.
"from now on the type of our fight has changed.
 it's not a war, but a martial art.
"the real hidden card sungwoo had kept to himself until now changed the rule of the game completely.
for more, visit lightnovelworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 