\section{chapter 385}

chapter 385: war for war (2)obviously, there was an unexpected development, but the situation was quite simple in his opinion.





he explained, “anyway, once we defeat the chinese server, we are supposed to face the amazon dragon, right? so, the only difference is the level of difficulty we have to face has gone up a bit.
”he then looked at jonathan with a calm expression.
“jonathan, please contact chairman love again and ask her to come up with an evacuation plan.
 and ask her to keep the hypergate open all the time, so she can escape to the korean server at any time.
 she can’t stop them even if she orders the withdrawal of the wpu fleet now.
”“i agree with you, sungwoo.
 chairman love decided it was right for us to focus on the war against the chinese server for now.
”at first, the enemy of the wpu fleet was the dragon and the demon king, so they could not stop the dragon and demon king even if she summoned all the vessels of the wpu.
chairman love knew how to look at the situation in the big picture.
 she knew it was best to wait for the necromancer to return to america.
“great.
 i hope you can collect as much information about the situation on amazon as possible, so i can refer to it someday when i return.
”“sure, i’ll convey your message to her.
”sungwoo looked around the commanders and continued, “let me stress this once again.
 what matters is the upcoming war with the chinese server.
 the best answer at this point is that we have to be stronger after winning the war and respond to the disaster coming from the amazon.
 we will prevail.
”when sungwoo spoke confidently, other commanders also seemed to feel relaxed.
they had a firm conviction that the necromancer would keep his promise because he always won.
sungwoo looked back at inho and said, “then, let’s start the meeting again.
 we need to find the easiest way to destroy the chinese server and absorb their power.
”
when this war was over, sungwoo and the world tree camp would grow again.
after a short meeting, they finally decided on the ‘type of war.
’“i hope that you can double-check the rule of the type of war we have decided and understand it well enough to memorize them.
”kyungsoo printed out the a4 papers that described the rule of the event and started handing them out to the commanders one by one.
“of course, you need to make sure you and your players understand the rules fully.
”sungwoo also received the paper and examined its contents again.
- item name: spear, shield, and arrow.
 each camp divides its troops as shown below to form a total of three ‘units’ and fight on ‘one battlefield’.
* spear unit: select less than 70% of all troops.
 can move freely to any location on the battlefield.
 30% increase in attack power* shield unit: select less than 70% of all troops.
 can’t move 10 minutes after the start of battle (fixed position).
 10% increase in defense.
* arrow unit: select less than 10% of all troops.
 can move freely to any location on the battlefield.
 can teleport to an ally location every 5 minutes[ol start=”2-]
when each unit suffers 70% or more damage, they will fall into the ‘state of inability to fight’ and the ‘victory buff’ is given to the opponent.
“alright.
 let me summarize it to you again.
”while everyone was reading the paper, inho started briefing them again.
although they decided on the rule through a lengthy meeting, it was necessary for them to double-check, thoroughly understand it and discuss the details of the rule.
“the reason we chose this type of war is simple.
 we have a strong army and, above all, two mighty divine status players, namely the necromancer and the valkyrie.
 if you divide them well according to this rule, you can win with minimal damage.
”what inho was thinking of right now was to form one spear unit with sungwoo as the leader, ‘arrow unit’ led by jisu, and ‘shield unit’ led by hanho and the crusader team.
the undead corps controlled by sungwoo would be able to dominate the battlefield as the ‘spear’ that would never break at the enemy’s attack.
jisu and her einherjar subordinates were small in number, but they had overwhelming mobility.
 if they used the skill called ‘teleportation’, they would be able to use a threatening tactic like an ‘arrow’ that flew from the bow instantly.
hanho and the crusader team would perform the role of a ‘shield’ more effectively than anyone else because all of them were armed with shields over their bodies.
inho continued, “since all of you have great abilities that fit each unit, i think we can make the upcoming war favorable to us.
”however, there was one thing that they hadn’t yet decided.
chen, who was present as the commander of the taiwan server, raised his hand and asked,“i think we have decided on a good type of war after a lengthy meeting, but where is the battlefield? i think it must be a pretty important issue.
”it was sungwoo who answered that question.
“ah, let me decide on the battlefield.
 so please follow my decision.
”he declared he was going to decide by himself, but no one objected.
necromancer’s status and their trust already made them silently follow whatever he decided.
then, sungwoo said in a soft tone,”the battlefield is right here, namely, suwon.
”everyone raised their heads at his announcement.
“really?”“wait a minute!”at least for this moment, everybody here could not hide their embarrassment as if they could not understand sungwoo’s decision.
of course, it was natural that they felt so.
 to put it bluntly, what sungwoo just said was that he intended to bring in the chinese troops and fight against them right here in their backyard.
 why did he have to make such a decision?“sungwoo, it’s going to be a big war that will devastate the whole area.
 are you serious about fighting the chinese here in the main base of the korean server?”

“we’re going to sustain great damage.
 even during our first war with japan, we suffered too much damage.
 i think we’re going to experience the same thing.
”as a matter of fact, the korean server suffered huge damage during the first war.
half of the city walls in suwon collapsed, and seoul also suffered massive ruins.
 but it was busan that suffered the most damage.
“our hwarang guild lost half of the infrastructure we had built up until then.
 of course, i know it was a very valuable victory, but it’s really painful to go through that suffering again.
”“that’s right.
 if we can avoid beijing, where they have been fully prepared, it’s not going to be a disadvantage to us if we fight them in china.
”but sungwoo shook his head and said, “i am not trying to avoid our disadvantage but my purpose in choosing suwon is to pursue our extreme advantage.
”he then crossed his arms and looked around the commanders.
“you have to keep it in mind.
 we have no future unless we completely defeat the chinese server in this war.
”even if they manage to defeat the chinese server in one way or another, can they really fight the dragon and the demon king?in order to prepare for the greater war with the dragon, sungwoo had to minimize the damage while pursuing the maximum advantage.
“to bring about a perfect victory, this battlefield here or our home base will be a huge help to us.
”then minhum raised his hand and asked, “then tell me what kind of advantage we can expect if we fight in suwon?”

 