\section{chapter 428}

the moment hundreds of firecrackers exploded all at once and covered the sky, billions of fragments exploded, ripping apart the bodies of the angels that covered the sky.





all at once, thousands of them disappeared in the blink of an eye.
the bodies of the dead angels were crushed to dust as hard as a piece of marble.
 the sky was covered with a veil of pale gray dust.
"fire again!"bang!the new weapon that wiped out the angel army at once, namely, the new cannon, was 'bug hunter' newly developed by the hearst workshop to deal with a large number of enemies.
a whopping 5,500 special bullets were contained in a single warhead, so the moment it exploded, it scattered in all directions, sweeping away everything in the area.
 in other words, it was an item that caused the so-called 'steel rain'.
the blacksmiths of the hearst workshop made those 5,500 'special bullets' by grinding the branches of the world tree, which had the effect of '40% defense neutralization' by going through the 'enchant' process such as refining the leaves of the world tree in boiled water.
that was why the angels' shields melted like cheese, and their hard bodies were easily pierced and ground like tofu.
how could they launch such a ruthless attack? of course, it was money, which was the source of funds for the production of new weapons at the hearst workshop.
s "keep firing!"bang! bang! bang! bang!eight and twelve cannons were fired from each airship and skyscraper respectively in a row.
"don't stop firing!"bang! bang! bang!there was another explosion, and all of a sudden, the huge cylinder disappeared, leaving only a flat circle.
 as soon as the angels squeezed out of the narrow hole, they were caught up in the continuing explosions.
no matter how they tried, they couldn't escape the firing range.
"what? already finished?"
"what the heck? isn't it too easy?"many players around the world were astonished to see the scene.
 and naturally, they had doubts.
 how could they do that? how could they keep firing without the required cooldown? how could they get mana?this content is taken from lightnovelworld.
c­omit was common sense that a large amount of mana was needed to operate magic engineering.
no matter how many wizards were mobilized, they could not keep fighting without being supplied with mana.
"canon 3, replace the battery!"the secret of all this was the 'mana battery' they had brought from the chinese server.
 and since they acquired the mana battery technology of the 'kuyaja facility,' they could keep improving it, and they finally miniaturized and loaded lots of it on the airships.
that wasn't all.
 the 'special shell' of 'bug hunter' was a real bullet, so they needed to keep supplying shells.
"come on, let's move to ship 12! deliver shells!"using their main ship messenger as a supply warehouse, the hippogriff squadron was busy transporting the shells to another airship.
but something unusual was happening right now.
 shell boxes kept being delivered from the messenger endlessly.
"damn, they're using up the shells so fast! bring more shells from the forge!"thanks to the 'forge of hephaestus' inside the messenger, they could keep supplying the shells to airships.
dozens of workers entered the subspace and came out carrying boxes of shells.
"oh my god! every time i go in, i'm scared about the blacksmiths because they are hurling all kinds of curses at me…"the reason why they could supply the shells indefinitely was that they could immediately deliver the shells the blacksmiths produced in real-time without the restrictions of physical distance and space.
 as such, the magical engineering of the korean server, the american server, and the chinese server harmonized together to generate an unbelievable tactical system with infinite power, infinite supply, and infinite firepower.
"alright! everything is going well as we planned!"sungwoo looked down at his watch while flying under the splendid flames.

he had only two seconds left now.
"now it's time…"beep- beep- beep-the alarm on his watch rang.
"it's time for me to get ready for something big.
"as he boasted, he didn't yet fully show the so-called 'firepower' he mentioned.
new novel chapters are published on lightnovelworld.
comhe turned off the alarm on his watch.
 the alarm was set for a total of 29 minutes.
then, when he clicked the button one more time, the alarm timer was set anew.
- 00:00:59'one minute left.
'originally it was set at 30 minutes.
at that moment he heard the sound of something pulling tight from below.
 it was the rooftop of a building.
 there was a huge y-shaped machine installed there.
 at first glance, it looked like a giant slingshot.
'this is a mechanical catapult made by weaving ogre tendons with the vines of the world tree.
 it can throw any heavy object several kilometers away.
'the sound of cogwheels rolling was heard soon, and the thick string connected behind it began to have a huge tension.
sungwoo looked at the clock.
- 00:00:37then he turned his head back and looked at the rooftop.
"now is the time! fire!"as soon as he issued the order, ten catapults stopped running.
 at the next moment, the ropes that had been pulled were loosened and the fasteners holding the bows were removed.
tung! tung! tung! tung!the tight bows bounced off, ejecting something.
whoopoooooo-it was an extremely heavy object, which was the corpses of a troll and an ogre that swelled up like a rubber balloon.
 they were no ordinary corpses.
 it was a bomb of immense power that contained the ultimate corpse explosion 'twilight flooding' that required a 30-minute 'softening' process.
like he did during the battle in busan, sungwoo repeatedly summoned victor to set his corpse explosion skill to 'ultimate', then waited for the right timing to throw them at the enemies on time.
'now about 20 seconds left.
.
.
'the heavy bodies soared into the air and flew toward the hole in the sky in a beautiful curve.
bang! bang!you can find the rest of this content on the lightnovelworld.
com platform.
after they collided with the angels crawling out of the portal, they succeeded to hit the target.
"explosion!"but there was no sound of an explosion.
beep- beep- beep-only the watch showed that the explosion time passed by one minute.
actually, it was no wonder they heard no sound because the explosions occurred in an alien space near the hole.
 it was normal for those on the ground not to hear or see the explosions.
soon sungwoo saw a series of messages on the results of the successful explosions.


- you have obtained 1 point by killing a normal angel.
- you have obtained 1 point by killing a normal angel.
- you have obtained 10 points by killing an executor angel.
- you have obtained 1 point by killing a normal angel.
- you have obtained 1 point by killing a normal angel.
"okay, great!"messages like that rang endlessly.
 at a close guess, more than a few thousand rang.
- you have obtained 1 point by killing a normal angel.
s - you have obtained 1 point by killing a normal angel.
- you have obtained 1 point by killing a normal angel.
when he confirmed all the messages were about the same thing, he had no choice but to stop receiving the message.
since the angel army was squeezing out of that narrow hole, there must have been a huge number of them inside the portal.
 perhaps more than those who already came out of the hole.
the huge explosions took place while they were fiercely competing to come out of the hole, so it was no wonder there must have been enormous damage among them.
 to put it simply, it was like pushing a bomb into the anthill.
updated from lightnovelworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 