\section{chapter 178}






 meanwhile, sungwoo calculated the number of souls he exploited.
 he had 38 so far.
 those were enough for now.
kaaaaaak! kaaaaaaak! kaaaaaaak!sungwoo realized that the first five wyverns that came down were sort of an advance party to size up his forces on the ground.
 when wyvern alpha male descended, more than twenty wyverns followed him.
 like a flock of crows, they nose-dived toward the prey on the ground all at once.
 some of them aimed at the iron maces of the lightning god hidden on mt.
 paldal.
clang! clang!the reloaded iron maces of the lightning god fired another giant bullet.
 two wyverns fell helplessly from the sky.
bang!however, the wyvern herd didn’t retreat.
 once they landed on the mountain, they began to push their way through the forest by breaking trees with their huge legs.
 they found the battlements installed with the iron maces of lightning.
“damn it, i got caught!”the moment one wyvern was about to crush the iron mace, a long arm was stretched out from the trees and grabbed the wyvern’s ankle.
kuuuuuuuuuuuh!it was ghoul king.
 sungwoo had arranged for ghoul king to hide behind the battlement just in case of the wyverns’ attack.
ghoul king grabbed the wyvern’s legs with both hands and stuck him to the ground.
 then, the monster climbed on top of the wyvern and bit through his neck ruthlessly.
kueeeeeh! kueeeeeeeeeeh!after that, dozens of ghouls charged at the other wyverns and climbed on their backs.
 huge stones were being thrown at them from the trees all at once by the troll skeletons.
sungwoo shouted, “everyone, move among the trees! if you are among the trees, they won’t be able to attack you!”the wyverns who attacked the battlements could not help but be beaten unilaterally by the undead moving through the trees.
 the wyverns couldn’t counter-attack the undead efficiently unless they made mt.
 paldal forest-barren.
but what mattered was not the battlement.
 it was a place around the world tree where the wyverns concentrated their attack.
the moment sungwoo showed any weakness in the security around the world tree, the wyverns could uproot the world tree.
kaaaaaaaaak! kaaaaaaaak!the players defending the world tree looked up at the sky and were stunned at the overwhelming number of wyverns.

“man, there are too many…”“we have to defend this tree, no matter what.
 as long as the necromancer doesn’t retreat, he will find the way to defeat them.
”– caution! the ‘fellblade’ begins in the affected area.
– caution! ‘death response’ begins in the affected area.
sungwoo mobilized all his subordinate spirits to fill the area around the world tree.
 as a result, troll skeletons held up bone shields and thoroughly defended the world tree.
 the players hid under the world tree and prepared magic and arrows.
sungwoo couldn’t use the “poisonous cloud” because of the players, but he was thinking of refraining from using the skill because of its bad effect on the world tree anyway.
“get ready to spell all the magic!”“load arrows!”sungwoo prepared the most powerful skills for the moment when the wyverns approached the world tree.
– ‘evil spirit bomb’ dwells in your weapon.
sungwoo exploited four souls to fire the evil spirit bomb.
 the black spheres soared before falling and exploding right above the heads of the wyverns.
kugugugugung-the black wave from the bombs crushed their heads.
 when the three wyverns stumbled, the players cast all kinds of magic on them.
sungwoo’s defense strategy was simple.
 he would seek to defeat the wyverns one by one with a concentrated attack.
-you have earned 566,454 gold by hunting the wyverns.
and this defense strategy was the right way to deal with wyverns because of their characteristics.
 the reason why wyverns were so strong was that they were flying monsters, and they moved in groups before attacking their prey.
“wonderful! our strategy works!”“the wyvern on the left is staggering! fire intensively!”compared to large monsters such as ogre or drake, the wyverns’ defense was not very good.
 three of them were quickly thrown onto the ground.
however, sungwoo was focusing on something elsewhere: the approach of wyvern alpha male.
 he would be different from other wyverns.

wyvern alpha male stretched his wings then raised his neck.
 the moment he opened his mouth, other wyverns nearby flew away from him.
 they knew something dangerous was going to happen soon.
“everybody, be careful!” sungwoo shouted.
sungwoo lifted his bone shield, and wyvern alpha male spewed something out.
poohahahahaha!it was a green liquid.
 the substance spilled over the troll skeletons.
 then, toxic smoke rose above them, melting their bone shields instantly.
“ah, it’s an acid attack!”“everyone, get away from the attacked skeletons!”the reason why the acid attack was so dreadful was that the acid solution would remain unless it was neutralized.
 as a result, even if the skeletons kept regenerating, they melted as long as there was acid around them.
 the skeletons were now unable to move or attack, but sungwoo could not do anything about them.
“it was time to replace them anyway.
”sungwoo lifted the grim reaper.
 at that moment, the troll skeletons showered with acid collapsed, and other subordinates filled their void.
they were the wyverns killed on the ground.
 they raised themselves, revealing their strong bones instead of scales and flesh.
“well, they must be on our side, right?”“crazy…”in an instant, twelve wyverns were standing in the place of the melted troll skeletons.
 nine monster birds also appeared behind them.
sungwoo stretched out the grim reaper toward the sky.
 bone wyverns started fluttering their wings at once.
 a great gust blew away everything on the ground.
“we’re going to have a dogfight now.
”the wyverns led by the alpha male and sungwoo’s wyverns clashed in the air.
they got entangled just tens of meters in the air in a fierce dogfight.
thud! kugugugugugugugu―the fight shook the whole area.
 they knocked the other wyverns down to the ground, and some of them bounced back, thrown into a building.
 then, they kept soaring and falling.
meanwhile, the zombie birds flew between the giant wyverns at high speed, sticking to their heads and pecking their eyes.
the players were dumbfounded by the wyverns’ fierce fighting, but they saw something like humans riding on wyverns’ back.
 they were minsok and orun.
the iron maces’ attacks from the battlements on mt.
 paldal were still fatal to the wyverns.
 although the enemy wyverns and friendly bone wyverns were hit by the iron maces, bone wyverns kept reviving.
-you have earned 750,004 gold by hunting wyvern.
-you have earned 744,454 gold by hunting wyvern.
sungwoo now began to feel that he could win the fight.
kaaaaaaaaah!then, wyvern alpha male, faced with the crisis, was ready to soar into the sky again.
just like he did at the fight at kimpo international airport, the monster boldly turned and flew away when he was met with an insurmountable situation.
but this time sungwoo had no intention of letting him fly away again.
“follow him!”sungwoo jumped on the back of bone wyvern and chased the monster closely.
wyvern alpha male finally turned completely, and the other wyverns also began to prepare for the escape.
“twilight raid!”-‘twilight raid’ begins.
sungwoo collected all the souls for this attack.
 soon, 20 souls came out of sungwoo’s body and colored his body like paint.
sunngwoo became a black ghost.
 he felt his body was lighter than air and floating.
 however, there was a strong power in it.
 he felt confident that he could squeeze anything.
‘i can crush wyvern alpha male.
’sungwoo then flew towards the boss monster.
guwoooooooo!

a black tornado hit his back.
kaaaaaaaaah!the boss monster resisted but could not withstand sungwoo’s massive attack.
 sungwoo’s magical power smashed his body.
 no matter how strongly the boss monster fluttered his wings, he could not help but nose-dive back to the ground.
kaaaaaaak! kaaaaaaaaak!the boss monster was swallowed by the black tornado.
 with his wings bent in a v-shape, he fell hundreds of meters down, straight toward the ground.
 he fell in an instant.
kuuuuuuuuuuuuuug! kugugugugugugugu―his heavy body fell on the asphalt road with a huge impact.
since he was the boss monster, however, he was different from ordinary wyverns.
 he wasn’t weak enough to suffer fatal injuries just by falling.
kaaaaaaaaaaah!however, sungwoo’s ‘twilight raid’ was not a simple skill aimed at shooting down the opponent.
twenty “dead hands” emerged from the ground and held wyvern alpha male’s body tightly.
 they grabbed not only his wings but also his chin, neck, and legs tightly.
kaaaaaaak! kaaaaaaaaaak!because of this unexpected attack, the boss monster could not move for 10 seconds.
at last, sungwoo appeared in front of him, holding a giant scythe.
behind him appeared jisu and minsok followed by orun.
“it’s your first time looking up at somebody, right?” sungwoo said.
he struck its head with the grim reaper.
ten seconds was longer than expected.
it was the moment when the korean server and the ruler of the sky changed hands.
-the world tree (growth stage 1) is growing.
 (99%)

 