\section{chapter 323}






 as a matter of fact, his ankle was broken.
 he just stood frozen on the spot.
“oh, my god! i shouldn’t stay here like this, but i can’t move.
 what should i do?”hanho was embarrassed.
 he wanted to fight by all means, but he could not walk at all.
even the high-ranking priests weren’t around.
 hanho himself was a priest, but he was not strong enough to set his broken ankle right away.
“oh, no…i should get up.
”he raised his head and looked at the third hole.
 taking just one step was so painful.
 how could he move his aching body over there and fight?at that moment, somebody called him.
“brother! toughest thief brother!”“ugh?”he was that little boy youngin, hanho’s only fan.
 classified as a non-combat player, he saw hanho while carrying brick materials to the second hole.
“brother? are you okay? you are not okay, right?”his eyes were trembling.
 despite his young age and low level, he was full of excitement and curiosity, but he was terrified right now because he had never been exposed to this kind of war.
“are we losing now? are we losing this time? like when we were beaten by the pirates…”did he recall the trauma of the pirates’ slaughter of his father? it was true that they were now on the defensive because of the enemy’s strong attack.

tears welled in hanho’s eyes because of tremendous pain, but he smiled at youngjin to show he was okay, but at that moment, he had a nosebleed showing that he was hurt.
“hey, don’t be scared and fight confidently! you said you want to become stronger like me, right?’at that moment, hanho remembered what youngin had told him on ganghwa island.
although he felt ashamed to hear that, hanho felt most proud about it in his life.
 in fact, he fought more fiercely after that.
“hey, next time you may have to stand in front of that hole.
 so, stay awake!”“are you sure? me next time?”“why? can’t you do it?”“…”at this moment, youngin couldn’t answer confidently, but hanho nodded because he could understand that young boy.
“well, this battle really sucks! but you can’t run away from it just because you can’t fight.
”then hanho turned his head again and walked toward the third hole with a limp.
he said, “man, since i’ve met the wrong guy, i’m playing the role of a hero where no credit is due…”he took out a bottle of health recovery potion from his waist, drank it, and moved to the hole of the castle wall.
 he kept complaining while walking, “shit! it would have been better for me to throw daggers from behind somebody!”the hole got even bigger because of the bombing.
 since the bombing affected not only hanho’s allies but also the enemy, there was a brief lull in the fighting at the third hole.

however, the second batch of the enemy’s troops was already advancing toward them.
 but the allies could not even regroup and prepare for their attack.
“what are you doing? back to your position!”“we should block the hole!”those who witnessed their fellow soldiers being killed by the bombing could not dare to go back to defend the hole.
 only one, namely, minsok, was standing before the broken hole.
bounced away by the bombing, there were cracks in his skull and armor, and his shield was cut in half.
“hanho, you are definitely different from an ordinary thief,” he said.
hanho stood next to minsuk with a smile.
“well, i told you about it repeatedly in the past.
 you are the second who has finally recognized me.
”“what? only two? i can’t believe it.
 have you hidden your abilities on purpose?”he said, shrugging, “well, i like to move around quietly like you, dark knight.
 by the way, the enemies must feel very upset because they failed to kill us, right? i guess it’s time for somebody to appear to rescue us…”at that moment, he looked up at the sky.
“well, it looks like he is coming late today.
 but if he really comes late, we might be in big trouble…”***general xing became impatient.
 the resistance of the korean server was more persistent than he expected.
 in fact, it was natural for him to expect the fight would drag on like this.
 he also felt their resistance was understandable.
 however, he became impatient because the necromancer won the battle in busan too soon.
‘we have to make a breakthrough.
 admiral baker used even the hidden skill exclusive to him but failed.
 the two guys are the problem.
’only two people were changing the tide of the war strangely by blocking the key points.
‘let me directly take action!’general xing eventually stood up.
 he expected his troops could break through the holes of the castle wall quickly, but they couldn’t.
 so, he could not afford to command without fighting himself.
“deputy, open the spirit control box!”when he shouted, his deputy standing behind him raised his head.
“general! are you going to fight in person? currently, we have only four high-grade boxes controlling the spirit.
”“yeah, i was thinking of saving them until the last moment, but we have no time.
 open two of them right away!”two trucks appeared at his order.
 there were white wooden boxes in the cargo compartment on the truck, which had not only all sorts of amulets attached to them, but also a chain icon meaning ‘seal magic’ around the boxes.
“hey! handle it carefully! if the high-grade box is opened, we are going to be annihilated!”the words ‘water’ and ‘high-grade’ were engraved on the boxes in calligraphy.
general xing approached the frontline, followed by the two trucks carrying the boxes.
 senior sorcerers were deployed around him to spread protective shields.
 since their defense was so tight, anyone could guess that the commander-in-chief of the chinese army appeared.
“open the boxes!”the wizards who were on standby at the general’s command used the ‘unseal magic’ on the boxes.
 and each time the magic box was unsealed one by one, the boxes shook violently as if to explode anytime.
gugugugugugugu—something inside the boxes was expressing pain and anger.


clang!soon, the boxes broke and something flowed out of them.
 it was just transparent water.
there was nothing more than that.
 the wizards who unsealed the boxes were also embarrassed by something unexpected.
“uh? is that all?”but the next moment the water that came out from the boxes with a scream began to soar in the air.
 it was split into dozens of strands, then changed into the shape of a human face.
 it was full of pain.
“that is…”“they are the high-grade water spirit!”only then did the wizards notice what was coming out from the boxes.
 it wasn’t water.
 it was a spirit.
“the high-grade water spirit that we captured after defeating the wizard leeway of the chinese 2nd server? man, who would have expected he would appear here?”as a matter of fact, leeway was the colleague of the spirits who dominated the “china-2 server” until recently.
 it was widely known to the public that the spirit was intelligent and kind to humans.
 there were even rumors that he splashed around with kids.
 but the spirit as known to the public was gone.
 instead, there was a vicious beast tied to a purple chain.
kheeeeeeeeeeeh!“let me give you an order now.
 destroy the enemy according to my orders!”when general xing beckoned, the purple chain darkened.
 then, like a dog being dragged by a leash, the chain was moving freely as the general directed it with his hand.
“water spirit, don’t resist! if you resist, it will bring about your end! your fate is in my hands!”

 