\section{chapter 297}






 after checking mir’s condition, hanho approached sungwoo.
while groaning a bit, mir buried his head again under the pillow.
“oh my…some airships appeared on the south coast.
 after he checked the airships, jonathan said they seemed to be the wpu fleet.
”“they came here already? wpf fleet?”the situation was more dangerous and urgent than he thought.
 this time jonathan came to sungwoo and explained in more detail.
“the airships appeared briefly on the korean server’s broadcast, and i’m sure they are wpu fleet.
 while i was here, admiral baker took control of the provisional council and obtained the right to wage a war.
”frustration spread over his face.
 admiral baker’s forces were operating in a far more organized manner than he thought.
 even if sungwoo had returned the messenger to him, he would not have stopped them from dispatching the naval fleet here.
“but how come they have arrived so early like this? they can’t cross the pacific ocean overnight, right?”it has been less than three days since the news about the crash of the messenger in korea was delivered to the us server.
 while it was possible for them to control the temporary congress during that time, they could not reach the korean server during that time span.
“is this an item?”obviously, they didn’t cross the pacific ocean to come here.
“i guess so.
 i think they have used something called a ‘server jumper’.
”according to jonathan, there was a special weapon called the “server jumper” among the items developed by the dwarves.

it was literally something that could move at once, as if jumping between the servers, but to put it simply, it was better than the “hyper gate” used by the kyushu union army in japan previously.
in order to open the ‘hyper gate’, they had to install it first by penetrating their arrival point in advance.
 however, jonathan said that the portal would open as soon as they put the mark on the map without going through such a cumbersome process.
“it’s a top-notch security item even within the wpu, too, and judging that they used it, it would be reasonable to think admiral baker’s forces have taken full control of all power beyond the provisional congress.
 they have been preparing carefully for a long time.
”while saying so, jonathan looked at sungwoo.
though sungwoo looked calm, it seemed that he made up his mind about something.
he slowly opened his mouth, “whatever it is, the wpu is our enemy.
”jonathan sighed at his words and said, “anyway, all this happened because we couldn’t stop it.
 so, please beat them, so they will come back to their senses once again.
”please overcome it.
 so that i can get their act together.
”sungwoo stood up from the chair and said, “i can beat them, but i can’t guarantee they will go back safely.
”***the world tree camp held a strategy meeting.
 each team leader gathered in the conference room.
“this is a videotape of the broadcast that was aired three hours ago.
 the place is changwon.
”when kyungsoo said that, a video appeared on the screen.
thump- thump-
the video was filmed inside a building with a clear view of the south coast amid a roaring sound.
huge objects floated at regular intervals between the sea and the blue sky.
 they were not something like an island.
 they were airships.
“what you see on the screen are seven airships right now.
”what came next was the scenes of the airships bombing a group of survivors on the southern coast.
 all sorts of flying weapons on the seven airships fired cannons, and the buildings along the coast collapsed like sandcastles.
 it was an indiscriminate bombing.
in the meantime, there were lots of players inside the building.
because the airship launched a surprise attack, the players had no time to evacuate.
their screams rang endlessly.
“…”when the video was over, kyungsoo first opened his mouth.
“well, watching the video, we can find out that admiral baker’s purpose is not simply to hit us, the world tree camp, but to take control of the whole korean server.
”inho replied, nodding at his words, “they know that if they can beat the world tree camp, the entire korean server falls into their hands.
”then, each team leader began to give their opinions.
“by the way, i just wonder why they attacked the southern area first before coming directly to suwon.
”“they are now holding their heads high because of their victory in the south.
 doesn’t it mean that they think they can win without launching a surprise attack?”“good for them.
 if they have decided to move up from the south, we have plenty of time to prepare for the onslaught.
 we have completed the new wall, and produced lots of flying weapons, too.
 so, by the time they reach here, we will be able to attack them.
 i think we can make seven more airships on this occasion.
”at that moment, jonathan, who was watching the meeting from the back, interrupted.
“hey, i’m sorry, but they are not all the wpu fleet.
 they must be the advance party.
”having said that, jonathan looked at sungwoo, who, in turn, nodded at him, so he could explain in more detail.
“the purpose of the advance team is to lay the groundwork for their main unit to land.
the item called ‘server jumper’ that i mentioned earlier is highly effective, but it would not have been able to move the entire fleet.
 but if the advance party brought a few “hyper gates” here, they could open more portals .
”when jonathan finished talking, inho wrapped his head with his hands.
“man, that’s why they landed on the southern coast, not suwon… damn it!”his frustration represented the feelings of everyone sitting here.
 their heads were spinning like a top at the moment.
 after all, hyper gates was the problem!by now, the advance party must be busy installing hyper gates to have more troops land here, and their fleets would multiply in a few hours.
“once again, i would like to emphasize that admiral baker’s army is quite strong.
 they can smash an army of 20,000 iron orcs into ashes in just a few minutes….
”jonathan sighed, recalling his old memories.
“i still can’t forget that terrible thing.
 winning the battle unilaterally is their specialty.
”with his fingers interlocked, sungwoo looked at him.


the moment jonathan met sungwoo’s eyes, he could guess how sungwoo was trying to respond.
 he recalled what sungwoo told him in a confident voice only recently.
sungwoo slowly opened his mouth.
“as i told you before, our strength is also huge.
”then sungwoo stood up and said, “it will take time for the enemy to install the ‘hyper gates’ for large-scale space movement.
 but they won’t have little time to do so.
”sungwoo turned his head to jisu.
“jisu, did you hear anything from the king of the great mountain?”jisu nodded.
 as a matter of fact, she sent a message to the king at his request.
“he decided to give you a stone for space movement.
 instead, he forced us to buy 1000 sacks of potatoes they grew by themselves, saying we could trade them for other food.
”it seemed that the king and his men were finally sick and tired of potatoes.
anyway, sungwoo succeeded in getting a space movement stone from the king.
“this space movement stone does not require installation but allows a small number of people to move freely within the same server.
 although only a few of us can go, we can go straight to changwon where the enemy fleet has landed.
”kyungsoo laughed at his words and responded, “well, our small elite force is far from small.
”everybody in the conference room except for jonathan looked relaxed.
but jonathan still had a hard time understanding this atmosphere.


 