\section{chapter 435}

sungwoo immediately recognized that this monster was like a creature similar to the 'angel judge' who descended in yeongdeungpo in the past.





then, one more giant appeared behind his back.
 a total of two giants stood before him.
even here?'did the angels who came here ahead of us got into that building? and the guys here witnessed them?'it seemed that sungwoo and the world tree fleet had to pick up the pieces that they who got here earlier than sungwoo's parties left.
after all, the guys who were ahead of them poked at the hive, it seemed that the damage was actually being covered by the sungwoo and the world tree fleet.

"damn it, they are the same monsters that we saw before…""man, not one, but two terrible monster angels…"advertisements    many of the crew of the world tree fleet were from the liberation guild, so they had seen the descent of the angel in yeongdeungpo.
 bad memories came back to their minds.
 at that time they hunted that huge angel and it was hard.
 after freezing the giant angel with 'frozen seed', they knocked him down by launching a frontal attack.
but this time such an attack would not be effective.
"times have changed a lot.
"sungwoo looked directly at the two large creatures and pulled out something.
"i've got a very good means to get rid of bulky idiots like you.
"
it was none other than the super heavy bow.
sungwoo stood up from behind the bone dragon.
 then he pulled his right foot back and adjusted his posture.
"whew…"he took a deep breath and lifted the bow.
 the world tree fleet noticed what sungwoo was trying to do, and started to retreat early because their airships could be damaged by a huge explosion.
sungwoo put his finger on the silver arrow.
- you can pull the super heavy bow.
sungwoo had once experienced its tight tension, unbearable pressure, and explosive thrust.
 this time pulled the arrow slowly while enduring the enormous tension of the super heavy bow.
as expected, the surrounding air began to whirl with a gust of wind blowing.
whoooooooo-then he released the bow.
tuuuuuuuuung-the air around the area whirled violently, creating a roaring sound.
 even the bone dragon spread its wings to fly backward because of the impact.
the intangible arrow that sungwoo shot flew fiercely towards the first angel.


the two angels raised their huge hands.
then, their protective barrier was spread out layer by layer.
 it looked as if the barrier was made of dozens of layers.
tung! tung! tung! tung!the intangible arrow broke through the barrier like glass, but it slowed down a little each time it pierced the barrier.
'they're tough.
'the intangible arrow, whose destructive power was weakened after breaking through several layers of barrier, only crushed the angel's right hand before stopping in the air.


 