\section{chapter 382}

chapter 382: hephaestus’ forge (6)while arnold hirst started his own research at the hephaestus’s forge, sungwoo came out to the world tree.
 he took out the ‘spirit of the world tree’ from his pocket.





‘this will definitely have a big impact on the world tree.
’he originally wanted to do it earlier but put it off because he discovered the hephaestus’s forge.
[item information]- name: spirit of the world tree- grade: myth- category: unknown- effect: unknown- description: contains wonderful power.
sungwoo grabbed it then approached the world tree.
 then, the current information on the world tree appeared before his eyes.
- the world tree (maturity stage 2) is growing.
 (11%)although he didn’t pay attention to it for a while, the world tree had already grown from ‘maturity stage 1’ to ‘maturity stage 2’.
because of that, sungwoo, who stayed linked to the world tree, could also get a small increase in his stats, but he didn’t pay much attention to it because his agility increased only by 1.
‘but if the world tree grows beyond the maturity stage and reaches the next stage, it will definitely have a huge effect.
’
the world tree has always offered him wonderful benefits.
 it was thanks to the benefits of the world tree that the world tree camp was so prosperous.
it was important to obtain a lot of materials from outside, but it was all thanks to the players in the fields of life and manufacturing that sungwoo’s allies could use them with the highest efficiency, and it was the world tree that served as the driving force of their growth‘yeah, what mattered at first was each individual’s power, but in the long run, technology really matters the most.
”sungwoo could not achieve victory without the players’ technology to repair captured airships, develop various flying weapons, and build castle walls.
most rpg games tended to show a similar pattern.
 at first, those players who leveled up through more hunting would get ahead of others, but after time passed, a huge guild with an ‘infrastructure’ that could affect the overall game would prevail.
‘let me make that infrastructure stronger today.
’when sungwoo approached a little closer, a message appeared.
- you currently have an item that can become the ‘nutrient’ of the world tree (maturity stage 2).
 do you want to use it? (y/n)of course, he chose y.
wooooooo-the ‘spirit of the world tree’ he was holding in his left hand suddenly made a strange sound and floated into the air.
then, it expanded to a huge size, split into several branches, and began to be absorbed into the trunk of the world tree.
kugugugugugu-
then, the ground twisted as if an earthquake just occurred.
 sungwoo barely grabbed a root and balanced himself.
“ugh, i’m afraid it’s going to make all the surrounding buildings collapse.
’in no time, the world tree was enveloped in pure white light and began to grow at an unrealistic rate.
 it soared up several dozen meters at once, and the branches that stretched all over the sky seemed to have spread into the sky as high as several kilometers.
with such explosive growth, the surrounding buildings shook violently like ships on the waves because the roots dug into the ground like loachs, but fortunately, they didn’t collapse.
‘well, i can’t even use the museum building anymore.
’the building of the city art museum, which the world tree camp used as the headquarters from the beginning, did not escape damage.
 it tilted heavily to one side.
- the world tree has reached ‘maturity (stage 3)’.
given the important achievement of the ‘spirit of the world tree,’ he did not have to care about the building’s damage.
soon, light escaped from the world tree that expanded several times bigger than before, showing its outline more clearly.
the world tree was now thicker than most buildings and soared higher than any skyscraper.
 its branches stretched out in all directions, passed over the castle walls, and cast a magnificent shade over a vast area.
 a cool breeze was blowing through them.
- since you are ‘linked’ to the world tree, your stats increase by a certain amount.
* your stamina increases (+1)- the world tree (maturity stage 3) is growing.
 (55%)not only did the world tree grow by one more stage, but it also jumped to a whopping 55 percent of maturity 2 stage at once.
‘perhaps the next step is the final stage of its maturity.
’soon, the world tree would reach the stage of full maturity.
 then, sungwoo would be able to get the ‘clues to evolution’ to become the ‘dragon race.
’***the allies of the world tree camp began to arrive one by one for the final decisive battle against the chinese server.
“i’m going to run a ‘temporary control center’ for the allied forces.
 so, i have deployed 30 additional administrative personnel to the center,” kyungsoo said to sungwoo.
kyungsoo and the general affairs team had a control plan in place to prepare for this situation.
“this time, i announced to them in advance that they should contact us before coming here, so there will be no confusion like before.
”the first among the allied groups to join the world tree camp was the liberation guild.
 after landing at the airfield of the world tree camp, the players aboard the eight helicopters were undergoing their id verification process.
based in seoul, the liberation guild had been growing tremendously without any damage for a long time, so they continued to expand rapidly.
“sungwoo, this is the list of allied troops that have arrived.
 let me organize them in this way.
”kyungsoo compiled the list of the war veterans of the liberation guild and gave it to sungwoo.
 in fact, kyungsoo gave it to him out of formality because he was responsible for organizing and controlling the allied troops as their general manager.
“by the way, the crusader team is also terrific.
 many of its team members were killed during the battle of the demon’s cave on jeju island, but it seems that they selected a lot of temporary personnel.


as kyungsoo said, the crusaders numbered 350 people, so it was truly amazing to see them lining up on one side of the wide airfield.
rattle- rattle-all of them were equipped with heavy full plate armor, while they were carrying all kinds of heavy equipment and huge shields.
it looked like they were the heavily armored infantrymen of the future, something that could only be seen in a science-fiction movie, rather than medieval knights.
however, their expressions belied their impressive posturing on the airfield because they were amazed by what they witnessed in the world tree camp.
“wow!”“look at them!”with their jaws dropping, most of them were admiring the airships as well as the tall world tree just like children who visited an amusement park.
“how did they get all those airships? we don’t have one yet.
 man, our large transport plane looks pretty shabby compared with the airships.
”“when did the world tree grow so tall? it looks like it’s going to cover the whole world.
 it’s really so unrealistic.
 to be honest, i’m a little scared.
”it was natural that they felt so.
 even though the liberation guild kept growing tremendously, they could not be compared to the main players of the world tree camp.
“man, we have been gradually increasing our troops, but it feels like they are becoming so strong all of a sudden as if they used a cheat kit.
”“you bet…”

 