\section{chapter 170}

                             




sungwoo and his party were waiting for the statue on the rooftop of youngdungpo station with the crusader team.
“eagle-3 is approaching youngdungpo to deliver the parcel.
 one minute before its arrival.
”“all drones, stay on alert! snipers, go back to your positions!”the transport of the angel’s stone statue was completed under strict security.
 except for the crusader tam, the wide area surveillance team, and sungwoo, few players knew about the statue.
minhum explained this security measure.
“since the mainstream just started, most of the leading groups will try to get this statue first.
 they won’t dare to attack us, but right now i think it’s necessary to keep it secret.
”at this point, sungwoo could confirm that junghoon was trusting him because he didn’t keep such important information from him.
‘junghoon puts the interests of establishing the coalition before his interests.
’to him, the biggest support for the establishment of the coalition was the necromancer.
 therefore, sungwoo realized junghoon was trying to make him his surefire ally.
doo doo doo!soon, the sound of the helicopter rotor was heard from the northern sky, and a helicopter appeared carrying a container wrapped in a green tent.
“good! slowly descend!”kuuuuuuuuuuuuung―then, as soon as they carefully put it down on the rooftop of youngdungpo station, agents approached from all sides, unwrapped the tight strings, and removed the tent.
 they broke the chain that sealed the entrance.
the door opened, and a faint white figure was seen inside the container in the dark.
“let’s go.
”sungwoo and junghoon went inside first.
-you are facing the trace of the absolute race, “angel’s stone statue”.
the pure white stone statue began to glow.
“it’s just like an angel.
”as junghoon said, it was a stone statue of a female angel with pure white wings, without any special features.
her smooth body in a long cloth garment was revealed with a sword in her right hand and a crown in her left hand.

“the sword and the crown…”usually, the objects on a statue symbolized something.
sungwoo could not infer the meaning of the two items immediately.
-put your hand on the statue.
the same message came to mind in front of sungwoo and junghoon.
and they put their hands on it at the same time.
[angel’s camp: contract]2)’faction quest’ is given.
a defense increase (+10%).
 buff is given.
you can get a large amount of extra gold by killing a player in the devil’s camp.
junghoon frowned after confirming the message.
“it seems they are trying to divide the players and pit them against each other.
 well, they used to in the past, but now they are openly forming factions.
”“i think so.
”as predicted, they were supposed to be divided into two camps for this fight.
-would you like to choose the angel faction? (y/n)* after selecting a camp, you cannot “withdraw” for a certain period.
 (7 days)* if you leave the faction in the future, a ‘penalty’ may be given for angering the angel.
junghoon agonized over the message for a moment because he had to choose between the two factions.
but he wondered if it was right to choose the angel faction.
 he hesitated because he couldn’t make a definite judgment, for what’s certain for now was that he obtained the statue of the angel first.
“…”on the other hand, a completely different message appeared before sungwoo’s eyes.
-you cannot select the angel faction.

* you have a dirty item now.
 (crystal of chaos) destroy the item, remove the trait of ‘chaos’ from it, and contact it again.
‘the trait of chaos?’[item information]-name: crystal of chaos.
-grade: legend-category: orb-effect: gives its owner the trait of ‘chaos.
’ increases mana (+500), recovers mana (+250%), steals mana and health at the same time (3%)it was an item that sungwoo obtained by combining the tears of the sea spirit and the bloodstone of the demon.
 this item gave him a new trait that was neither demon, nor an angel, but ‘chaos’.
‘do i have to give it up?”it was a very valuable item for that.
 by combining two legendary grade items, he was given a ridiculous option.
 it has been an important force to him like a fountain that never dried up.
‘do i have to give up on this because of the angel faction that i don’t know anything about? no way!’seongwoo removed his hand from the statue.
 at that moment, the message about the selection of a faction disappeared, and the eyes of the angel statue seemed to stare at him.
and a new message appeared.
[hidden quest]-title: third choice-type: remove of target-goal: destroy the statue of the absolute race (0/3)-reward: establish a third faction.
*who is the one who is trampling this land? you must think about who is the real enemy before making the choice.
what is certain is that at least the ‘absolute race’ is not on your side.
 their purpose is not to pursue humanity’s prosperity.
 rather, they want to achieve their ambitions by thoroughly destroying human beings.
you, who can escape from the beasts of the absolute race by possessing the trait of ‘chaos’! you will have to stand on your own feet if you want to preserve your race and win the fight.
* when you accept the quest, you will anger the absolute race.
‘hidden quest? third faction?’as expected, there was a variable in this mainstream.
 the ‘chaos trait’ sungwoo had obtained a long time ago presented a new path.
-would you like to accept the hidden quest ‘the third choice’? (y/n)this was a huge danger and opportunity.
 so far he has never declined a path with both sides like this.
 so, sungwoo immediately clicked y.
 and his choice was like him crossing a river of no return.
-you brought out the anger of the absolute race.
-all players in the absolute race faction are given a ‘wanted order’.
 (target: kor-157)* angel’s faction bounty: 20,000,000 gold* devil’s faction bounty: 15,000,000 gold“sungwoo, what the hell is this?” asked junghoon, distorting his face.
“now, they are asking me to kill you.
”junghoon had already chosen the angel faction.
looking at junghoon quietly, sungwoo slowly opened his mouth.
“our situation is getting complicated.
”“what the hell is this about?”junghoon made a tough expression.
 he grew alert, though he didn’t know the exact situation.
“please tell me.
 you know i can’t ignore this kind of system message.
 what you mean by ‘a complicated situation’…”“then, let me do it simply.
”as soon as sungwoo said that, the grim reaper appeared in his right hand.
 he swung the grim reaper without any hesitation.
“what the heck are you doing now?”at that moment, the angel’s statue was split in half and a light came out.
-third option: destroy the statue of the absolute race (1/3)“what have you done now?”“this is the third choice.
”

“pardon?”“come to think of it, the way to control this game is always in the third choice.
 junghoon what would be our ending after we have been played around by an unidentified being, be it an angel or a demon? can we have a happy ending?”not a linear way, but a hidden way, that is, the third way has always been the right answer of attack.
 however, it also caused greater resistance.
-angel faction registers the sacrifice of your life as a ‘ faction quest’.
 in the future, all angel players will be obligated to hunt you.
-angel faction increases the bounty for you.
*angel faction’s bounty: 50,000,000 gold“what the hell did you do now…?” junghoon still couldn’t hide his embarrassment because he was given a faction quest to kill sungwoo.
however, sungwoo calmly looked at the angel’s statue and found something sparkling in the fragments.
[item information]-name: angel’s wing sculpture-grade: legend-category: disposable item-effect: when you use it, you can move to ‘angel’s ‘ within a certain range.
 (1 time)* the demon faction can’t use this.
-description: when the statue is destroyed, it is used for the final emergency exit.
“man, i can move to another statue?”maybe there was a function embedded in this sculpture, so he could move from one statue to another.
 if the rivalry between factions intensified, it was possible that they would try to destroy each other’s statues.
“by the way, where is the other statue?”sungwoo once heard there was only one place.
 sungwoo remembered the time when he read the memory fragments of gen.
 jigong.
“taiwan!”there was angel’s statue in the place where the red revolutionary army, namely the pirates existed.
in other words, it was possible that sungwoo could get rid of the second statue and the pirates at once.


 