\section{chapter 338}

chapter 338: jeju island and attack on demon’s cave (2)the world tree camp was in the process of learning navigation skills after founding an airforce using the captured airships.





the airship needed huge manpower befitting its size, so inho selected some reliable men among the outside players who participated in the recent war.
sungwoo planned to mobilize three airships and 65 crew members for this operation.
“we don’t have time.
 let’s start right now.
”the airship of the world tree camp accelerated south.
***jeju island was the largest island and sightseeing place in korea, but sungwoo had never heard of it after the world became a game.
 this was true not only of the world tree camp but also of all the large groups within the entire korean server.
unless it was a place that affected their lives, they didn’t have any reason to pay attention to the island.
“well, we have little information about jeju island.
”when the world tree airship was flying over the south sea, inho gathered as much information about jeju as possible and briefed sungwoo about it.
“so, it’s a bit strange, but if you look at the local community bulletin, there is almost nobody who mentioned jeju island.
”“then, there are few survivors there? or is it governed by monsters like north korea or amazon?”“no, it’s not.
 according to the information provided by the hunter company, there is definitely an organized survivor group there.
 but there is a problem.
”“what is it?”“it is said that an extremist group that worships monsters dominates most of jeju island.
 my guess is that they are controlling jeju island.
 they are even blocking people from posting articles about jeju island on the community bulletin.
”
sungwoo also had a hunch that something troublesome was going to happen.
“sungwoo, we have to consider that they might interfere with us.
 i don’t think this extremist group that worships monsters will be able to make good judgment.
”sungwoo nodded.
 if they have been controlling jeju island with an iron curtain to the outside world, they have no choice but to react sensitively to the approach of outside forces.
“if we come to encounter them, we’re going to tell them that we’ll leave as soon as we’re done, but if they stand in our way, we’re going to get rid of them.
 yeah, i’m serious.
”for now, he couldn’t afford to act prudently and cautiously.
 if anybody stood in his way, sungwoo had no choice but to get rid of them without any hesitation.
suddenly, part of jeju island began to appear beyond the horizon.
 they had a clear view of the island because it was a clear day.
“oh, that’s mt.
 halla! oh, come to think of it, isn’t it your hometown, sis jisu?”“yeah, that’s right.
”replying to hanho’s question, jisu looked out the window.
“wow, you are going back home after a long time, right? i guess you might feel strange.
”“well, i don’t miss this place that much.
”she always refrained from talking about her family and hometown.
 sungwoo didn’t ask her, assuming she might have a troublesome relationship with her family.
“hahaha, it’s my first time visiting jeju island.
 i wish i had come here for sightseeing in peaceful times…”even though hanho was far from quick-witted, he didn’t ask her anymore, feeling she was uncomfortable with his questions.

it was about the time when jeju island was more visible in their eyes outside the window.
“something is approaching us from jeju island!”as soon as the observation officer reported, there were disturbances within the airship.
“there are about 20 unidentified aircrafts approaching us in a wide circle!”“to arms, everybody!”when inho shouted, the players on the deck and turrets here and there began to move in a hurry.
soon, all the guns were directed at the enemy.
 since they had already fought once, they got used to it.
“uh? what the heck is that?”they looked like a mix of an eagle and a horse, namely hippogriff.
 they were flying in the air with tremendous speed and began to encircle the world tree fleet.
“shall we attack them?”the weapons control crew asked, and inho looked at sungwoo.
but sungwoo shook his head and said, “wait a minute.
”“uh? their leader is pointing down with his finger.
 he seems to signal for us to land now.
”but sungwoo shook his head again and said, “we don’t have to land.
 tell them to lower their altitude and come down to our deck while in hovering mode.
”since the world tree camp had nothing to fear, sungwoo had no intention of obeying their demands.
 sungwoo’s order was delivered to the deck officers and the deck master of the messenger sent a signal to the hippogriff unit to land.
sungwoo looked up at the sky through the window of the control room.
 they circled over the messenger for some time, as if displeased with sungwoo’s demand for landing.
“they’re coming down!”soon, a few hippogriffs changed direction and started descending towards the deck of the messenger.
“some of them have landed on deck.
”armed with weapons, sungwoo went out to the deck.
 he was just thinking of suggesting something to them.
“everyone, step back!”when the deckmen dispersed to the left and right, five giant beasts landed on one corner of the deck.
 they folded their gigantic wings, letting out air.
“they are 10, all told.
”in the meantime, players armed with crossbows and spears walked out to the deck.
‘these guys are out of their minds.
’the moment sungwoo looked at their faces, he immediately felt something strange about them.
 all of them had blown pupils.
a guy who seemed to be their leader stood before sungwoo.
“you have now crossed our sanctuary.
 i warn you to turn and go back with this stupid stuff before it’s too late.
”

“sanctuary?”“starting from here, this place is the realm of the god who sleeps in the lake paekrokdam of the sacred mt.
 halla.
”inho sneered at his words as if he was expecting the man’s reply.
 without a doubt, they were monster worshipers who allegedly occupied jeju island.
“we don’t care.
 we’re not here to do any harm to you.
 just let us go without standing in our way, then we’ll leave as soon as we finish our job here,” said sungwoo firmly.
it was like the ultimatum he planned in advance, but the opponent’s expression became even harder.
“damn it, it seems you don’t understand what i said.
 i told you this is the place where we worship our god.
 do you think this is like a tollgate where you can pass freely?”this time inho stepped forward and said, “hey, you guys don’t know who we are? have you never watched us on your cell phones or the community broadcast?”“we threw away such demonic stuff a long time ago.
 whoever you are, you better get out of here right now.
 you look like you are possessed by the devil…”when he gave an absurd reply, inho burst out laughing.
“hahaha… that’s why i didn’t see it.
 i now know why.
”inho came to learn why there was no mention of jeju island on the community bulletin at some point.
‘man, this guy must be out of his mind and possessed by something.
 does he have the same brainwashing power as gen.
 chongong of the red revolution army?’even if the world collapsed and people found it hard to stay sane, he wasn’t supposed to talk bullsh*t if he was really from a civilized world.
at that moment, somebody asked, “are you jisu?”“…”“you are jisu, right? do you remember me?”

 