\section{chapter 302}

east potomac park in washington d.
c.
 was once an ordinary civic park with public swimming pools and jogging trails, but it has now been transformed into a "dock" where airships take off and land.
 huge steel structures covered the top of the park, and airships were landing on it.





-after landing, the entire fleet should maintain a "2nd-degree combat readiness".
the broadcast rang throughout dock 3 facing the potomac river.
 the broadcast was being replayed from all the airships.
-let me repeat.
 after landing, the entire fleet should maintain a "2nd-degree combat readiness" and wait for the order from the control tower.
"understood! how many times did i hear it? i think i've heard it most often this year.
"quartermasters on no.
 3 airship lincoln of the washington fleet were on standby in boredom for almost five hours.
 they were waiting for the sortie for as many as 4 hours, but since their sortie was canceled 30 minutes ago, they have been on standby without knowing what happened.
"hey david, do you know why they repeat the same thing on the air?"quartermaster david shook his head at the boatswain's question.
 lower-level crew members of the washington fleet were not told why their naval operation was suspended temporarily.
but even during the short time all sorts of rumors circulated among the crew on the ship, but most of them were unbelievable.
"according to the rumors, there was a problem in the admiral's fleet.
 based on what he heard from those on the ship, walter said that the admiral's fleet seemed to have sunk.
" david whispered as if telling a secret that he shouldn't tell.
 then, the boatswain said cynically, "it's all speculation.
 admiral baker was defeated? is it possible he got defeated by the korean server less than half a day after he led his fleet to fight the korean server?"the boatswain tapped david on the shoulder and said, "hey, admiral baker's fleet suffered only one casualty when they fought a band of philadelphia thieves, and it was admiral baker who killed the wounded man in person, right? how could he be defeated less than half a day? no way, i can't believe it!""i don't believe it either.
 wouldn't it be more reliable to say that he was buried in the sea by incurring god's anger because of its nasty temper?"'"oh, that makes sense.
 if admiral baker was like that, he would probably conquer atlantis and come back alive.
"
the two giggled, cracking a joke about the fate of the admiral.
"so, what's your speculation about his fate?"the boatswain shrugged his shoulders and looked toward the hyper gate.
woooooooong- woooooooong-three hyper gates were operating above the "arland d.
 williams jr memorial bridge" across the potomac river.
 according to the original plan, the washington fleet should have passed through those gates 30 minutes ago and reached the korean server.
"well, as for the reason why the control tower keeps repeating the same thing, i think i can interpret it as something like 'we just don't know what happened!' nobody on the baker fleet has reported to us properly.
""pardon? what's the problem?"the chief laughed as he looked at the hyper gate.
"well, the war is already over," he said confidently.
 "already?""hey, don't you know the power of admiral baker! do you think you can compare him with that asian kid who gained some fame because of sheer luck?""well, but i just wonder how the war is over in less than a day…""to put it simply, the war ended in the blink of an eye, just like a modernized infantry struck down a primitive man.
 and the admiral discovered a rare treasure guarded by primitive men there, so he didn't report back to us because he wanted to have it alone.
"it seemed that the boatswain was speculating wildly without any ground.
 
"are you sure?""you bet.
 you can count on me.
 just wait and see.
"it was well known that the boatswain was an ardent supporter of admiral baker, but after admiral baker took over the provisional council, he did not hesitate to praise him blatantly.
oohoohoooh-"uh?"at that moment, the hyper gate began to shake.
 with the gate in operation, something was about to come out.
 an airship that was hovering nearby on a guard mission, quickly rose its altitude to escape from there.
 "look over there, boatswain! the hyper gate is working! did somebody open the door on the other side?""oh, what the heck is that? is admiral baker pulling out the giant world tree and bringing it over here?"however, the moment the gate was completely opened, they saw something completely different from what they had been expecting.
unidentified things sprang out en masse and were stuck into the hull of the airship flying near the hyper gate.
"what the heck is that?"it was like an iron post with green vines hanging at the end, which were now stretching out to the hyper gate.
the next moment, the vines were pulled tight.
somebody beyond the hyper gate was pulling the vines with tremendous force.
the airship tilted toward the gate.
"no! we're being dragged!""cut the rope right now!"if this continued, the airship would be sucked into the hyper gate.
 the airship retreated at full speed, but to no avail.
"damn it! failed! hold it tight!"eventually, the airship was sucked into the hyper gate without even trying to resist.
 in other words, it was forcibly taken to the korean server.
 all this happened in an instant as if a fly was sucked into the chameleon's mouth.
but how good would it have been to them if that was the end?immediately after the airship disappeared, it was not the glorious return of admiral baker's fleet that appeared through the three hyper gates.
"oh, my god!""oh, god.
"dozens of "bone wyverns" poured out over the potomac river, holding all sorts of bodies and bones in their feet.
"oh, my…"the proud expression on the boatswain's face disappeared, which then turned gloomy.


-prepare for battle, entire fleet! ready for the battle! make a sortie right now! fly! damn it!an emergency combat order was issued with the siren, but all the airships were anchored at the dock, except for the warship airship that had just been dragged into the hyper gate.
so, it took more time for them to take off.
but the monsters who took control of the sky over washington dc did not wait.
 corpses fell on the dock and the airships then quickly swelled up.
a huge explosion rang throughout washington dc.
meanwhile, a major battle was underway in changwon beyond the hyper gate.
"they are coming!"inho and the players of the world tree camp were prepared for the battle, gazing at the vines pulled tightly from the hyper gate.
 they felt as if something huge was caught on a fishing rod they threw into a small lake.
"as soon as they come out, you must climb up and take over the airships! no.
 2 team, take care of the superstructure of the airship.
 no.
 1 team, take over the deck!"but sungwoo had no choice but to worry right before the operation, for he knew that the object that would protrude from the end of the vines was a huge airship with dozens of enemies on board.
"man, this world tree must be a scam! how come we can steal such a warship entirely like this?"this kind of tremendous operation was possible thanks to the special item "world tree vine" that fell from the world tree.


 