\section{chapter 164}






 now, the enemies’ strategy was somewhat clear.
 by confining sungwoo inside the building, they sought to make it impossible for sungwoo to summon his main weapon, the large undead.
but it didn’t mean that they incapacitated sungwoo completely.
“protect the families inside the classroom as much as possible.
 i will block them from approaching here.
”that’s what sungwoo could tell them at this point, but the situation got worse and worse.
wuuuuuuuuuuung!one ton trucks lined up in front of the school and stopped near the basketball court.
then, the human monsters on standby ran and opened the luggage compartments.
grrrrrrrrrrrrrrrrrrrrrrrrrrrrrrrr-bizarre creatures began to move from them.
 they were monsters with a human head, a human body in tatters, and beast limbs.
‘they are not normal monsters.
’they were the final results of the unethical experiments by the evolution society.
those bizarre monsters jumped out of the trucks and started running towards the school.
there was no more time for sungwoo and his party to watch the monsters running toward them.
“hanho, jisu, stay here.
 let me close the hallway.
”sungwoo told jisu and hanho to stay in the classroom and help the players because fighting entangled in a narrow corridor could interfere with each other’s fighting style.
-you have summoned the killer scythe, ‘grim reaper’.
-grim reaper retention time (00:21:11)‘the remaining time is only 21 minutes.
’the current situation was the worst.
 cooldown or waiting time was required for sungwoo’s use of his skills, such as summoning golems and response to death.
 as a result, sungwoo’s strength was reduced by more than half.
‘well, i just hope the crusaders can arrive within 21 minutes and make a path to retreat…’sungwoo took minsok and orun out of the classroom and into the hallway.

“they’re right there!”three werewolves appeared at the end of the hallway.
 they ran down the hall with swords and axes.
 sungwoo immediately raised his repeating crossbow.
tung! tung! tung! tung!since the corridor was narrow, the monsters had no time to avoid the arrows, but the monsters lifted something round.
 then, a translucent shield was formed around them.
‘protective shield?’in other words, the enemies were thoroughly prepared.
 they prepared not only such a small protective shield but also held gas masks.
 they were armed with that weapon after finding out that the black smoke emitted by sungwoo had a curse effect.
they were thoroughly prepared to kill this big guy called necromancer.
“surround them!”somebody’s voice was heard from behind.
 they had already snuck into the building, closing in on sungwoo and his party from all sides.
“let me defend in the rear,” minsok said.
“yes, please.
”sungwoo left minsok and ornn behind and confronted the human monsters charging from the front.
the hallway was so narrow that sungwoo couldn’t use the grim reaper properly.
he grabbed the handle of the grim reaper as wide as possible and struck the translucent shield the werewolf was pushing against him.
the shield blocked the arrows, but not the grim reaper’s powerful impact.
 the shield shattered.
“let me kill you!”at that moment, another human monster stabbed his sword toward the back of sungwoo’s neck, but he stepped back and swung the grim reaper at the monster.
kuaaaaaaaaaaaaaaaah!the monster’s whole arm was cut off.
 another monster jumped over his colleague’s shoulder and swung his ax at a tremendous speed, but sungwoo was faster.
-you have earned 25,000 gold by hunting ‘stage 2 werewolf’.
sungwoo lifted the grim reaper and cut the monster in half.
 his stats were overwhelming.
 in particular, since all his stats increased by 10 when he was in lich status, the monsters could not confront him properly in terms of strength and agility no matter how strong the human monsters were.
tung! tung! tung! tung!
when the human monsters showed soft spots, sungwoo immediately lifted his repeating crossbow and fired arrows.
 this time they couldn’t stop the arrows.
 three werewolves fell on the floor.
minsok and orun also killed two human monsters.
“they’re on the first floor! they are all gathered on the first floor!”but the zombie monsters kept coming inside the school building.
 they popped up from both ends of the corridor, broke the windows, entered the classroom, and went back into the corridor.
 their footsteps were even heard on the second floor.
and outside the window, the monster snipers were approaching.
 in this situation, just holding out where they were was not the best option.
 if they got stuck in one place, they would be showered with the monsters’ arrows and magic.
“they’re coming in!”“block them!”and the monsters began to infiltrate into the classroom where the players were holding out.
ahhhhhhhhhhhhhhhhh!”all sorts of screams and frictions were heard inside.
 although jisu was the best melee attacker, she could not protect other people at the moment.
‘we can’t stop them like this anymore.
’ sungwoo thought.
 ‘we need another strategy.
’he thought hard about the best possible tactic to stop them.
 he thought of all the possible options.
 he had to be aggressive from now on.
at that moment, he hit upon one idea.
“minsok, hold out here.
”“okay.
”-the dead will be your subordinate spirit under your authority.
-the dead will be your subordinate spirit under your authority.
sungwoo had minsok defend the entrance to the classroom, then resurrected the two werewolves.
 then, he headed toward the end of the corridor.
 soon, the zombie monsters were breaking into the corridor after passing by the lobby.
guuuuuuuuuuuuuh!they came running, screaming in pain.
 their movements were very deformed, their bodies twisting with every step.
sungwoo had the werewolf skeletons collide with them head-on.
quazzzzzzzzik!at that moment, the zombie monster stretched his left arm and penetrated the skull of one werewolf skeleton.
 not caring about it, sungwoo pushed in, taking out the hand cannon from his waist.
bang!the hand cannon’s destructive power was also extraordinary.
 the heads of two zombie monsters were smashed entirely, and the other two monsters behind them were also pushed back.
-you have earned 100 gold by hunting the ‘experiment no.
-022’.
-you have earned 100 gold by hunting the ‘ experiment no.
-022’.
only 100 gold?sungwoo was dumbfounded by that small reward, but he couldn’t afford to care about it now.
he swung the grim reaper sideways without worrying about it being stuck on the wall.
soon, the grim reaper cut the heads of the two zombie monsters then scraped the left side of the wall and destroyed it.
 the next moment, a gust swept the hallway.
 the grim reaper kicked the body of the crumbling monster.
 the body of the beheaded monster was thrown into the air.
“explode!”bang!the zombie monsters coming into the hallway were thrown out in flames.
 sungwoo lifted the repeating crossbow and fired arrows towards the monsters who lost their balance.
tung! tung! tung! tung! tung! tung!with the ignition arrow function on, the zombie monsters were engulfed in flames.
sungwoo pushed ahead and arrived at a relatively large area: the lobby.
at the same time, he used his prime skill.
– caution! the ‘fellblade’ begins in the affected area.
black smoke rose, filling the lobby in an instant.
 then, it stretched out into the hallway and soared out of the window.
“he used the gas weapon!”“wear a gas mask!”with the voices of the human monsters ringing everywhere, sungwoo pulled out two items in the black smoke.
 they were ‘human monster ampoule (werewolf)’ and ‘devil’s door scroll’.


‘let me camouflage myself as a human monster and go behind them, then use the devil’s door scroll.
’the devil’s door scroll, which he captured in the pirate ship, was a dungeon with a recommended level of 35.
 considering that the recommended level of the ‘hell’s gate’ was 27, this was an extremely difficult level.
 that’s why the pirates used this item as a “strategic weapon” to destroy a certain area.
‘i was thinking of saving it, but this is not the time to save it.
’sungwoo intended to drop a “nuclear bomb” on these monsters.
he prepared the item that the pirates had made by themselves, namely ‘human monster ampoule (werewolf)’.
 when he uses this item, he will turn into a werewolf and would remain in that condition for 20 minutes.
sungwoo inserted a syringe containing the ampoule into his thigh.
“kuuuuk!”he felt a tingling pain on his thigh, then his pelvis, and finally his spine.
 his body swelled and his hair began to grow thicker.
 his skull was transformed, causing extreme pain in his face.
 now, he felt his senses were expanding.
-you have temporarily become a ‘werewolf’ due to the item effect.
but that wasn’t the end.
-special conditions have been satisfied.
* lich (death controller) + human monster (werewolf)the unexpected combination was completed when his lich condition was mixed with the human monster process.
-temporarily you have gained the power of the death god ‘anubis’.
-temporarily you have become a demigod.
-all stats are greatly increased.
 (+10)-you can use the skill .
-you can use the skill .
-you can use the skill .
variables always existed in this kind of game.
when the black smoke slowly faded away, a black wolf with a huge black scythe rose.
a purple wave spread around him.


 