\section{chapter 66}

                            the boss monster ripped open the door of the hangar, revealing its heavy body.





gruuuuu….
-the local boss monster ‘giant troll’ has appeared.
sungwoo could not think of any other expression to describe him as a giant.
“what a crazy giant…”the dark green monster dressed in brown leather stood tall, facing sungwoo and his party.
his skin was covered with thick projections and looked tough at a glance.
 he wore an accessory made of skeletons and bloody flesh around his thick neck.
he was holding a giant stick in his right hand, which he seemed to have made by pulling up an entire tree.
“dang it! i can’t believe it.
 i thought there would be only fighters in such a hanger.
 who would have thought a huge beat with two feet would come out from such a place?”“the monster is completely different from the typical monster we have dealt with until now.
”hanho and jisu did not hide their embarrassment, and sgt.
 kim’s squad members were also scared.
 even sungwoo could not help but grow tense.
‘man, he’s twice as big as the largest skeleton, the werebear skeleton.
 given it’s a boss monster, he is probably incomparable to the previous monsters…’after obtaining 4 werebear skeletons, sungwoo planned to outpower the boss monster, but he felt he had to give it up quickly.
thump- thump-the boss monster started to approach them.
“how about it, sungwoo? can you figure out his strength? it’s not too late.
 you can return the sgt.
 100,000 gold even now,” said kang, chuckling at sungwoo, but sungwoo attacked without an answer.
– caution! ‘death response’ begins in that area.
first, sungwoo summoned zombies in front of the giant troll.
 squishy mud appeared on the surface of the asphalt road on the runway, and zombies began to crawl out of it.

wuuuuuuh!ten zombies ran wildly towards the giant troll, but they looked like small tolls before the giant standing five meters tall.
the giant troll didn’t even swing the stick, as if the zombies were ridiculous, then began to kill them by trampling with his feet as if they were worms.
thump! thump!sungwoo was actually looking for that very moment.
“explosion.
”pop!a corpse exploded right under the giant troll’s feet, but it was different.
 the explosion, which always showed tremendous effects before, made him only stumble a bit.
‘this monster is not just big.
 his defense power is enormous.
 moreover, it has good resilience, so the sustained damage caused by my curse is not going to work.
’in some respects, sungwoo was lucky so far.
 whenever he encountered slimes, vampires, wizards, and other enemies, he could easily defeat them with his skills, but he couldn’t always be lucky.
‘he’s like my natural enemy.
’in fact, it was clear that the boss monster was so mighty that even sungwoo’s main skills could not function properly.
“oh my… you can’t even use your lethal skills?” sgt.
 kang asked sarcastically.
with his arms folded, he was now watching sungwoo casually.
 it looked like he would even eat popcorn cheerfully, watching sungwoo struggling.
“sgt.
 first class kang, you said you served in a special force, so let me ask you something.
 how would you deal with such a giant monster?”sgt.
 kang scratched his cheek with an air of conceit.
“heavens! you are asking for my advice! it looks like you have spaced out because of that monster.
 i’m sorry, but actually i don’t know how to respond because i was transferred out of the special forces because i couldn’t adapt myself there.
 but what i learned there was just do as you were instructed, such as shooting, exploding and beating.
 that’s it.
”“well, it looks like a movie screenwriter is one cut above a special forces man like you.
”
“pardon?”“have you ever watched a movie called star wars or district 13?”sgt.
 kang apparently looked embarrassed, unable to figure out what sungwoo was trying to point out.
“well, i suddenly wondered if i could make such a movie scene come true here.
 well, i can find out if i implement my plan now.
”sungwoo summoned one of the skeletons then began to take something out of his bag.
it was a bunch of colorful ropes.
 it was a very tough mountain rope called ‘climbing rope.
’“yeah, that’s why you have to keep everything at hand.
 it was good for me to stop by the mountaineering supply store next to the bicycle supply store.
 hanho, jisu, please help me.
”“oh, yes.
”“what are you going to do?”sungwoo tied the climbing rope to the spine of the werebear skeleton.
 then, he tied the other end to the spine of the other werebear skeleton.
 they were now connected as a pair.
thump- thump-meanwhile, the giant troll was approaching sungwoo.
 with a smile on his face, the giant troll approached at a very relaxed pace.
while watching the giant monster and sungwoo working on an unknown task alternately, sgt.
 kang gradually hardened his expression.
“hey, that monster is getting closer to you now.
 what are you doing, sungwoo?”“according to the manual, this has great ‘tensile strength’, so much so that it can withstand 2 tons of force.
 of course that monster might be stronger than that, so let me stack several like this…”sungwoo tied several climbing ropes to the back of the four werebear skeletons.
at a glance, it seemed he wrapped them with more than 10 strands of ropes.
“i don’t know if it’s enough, but let’s go.
”as soon as sungwoo ordered, they began the unknown operation.
rattle! rattle!the four wearbears with the ropes on their back rushed forward.
 whenever they moved, the ropes fluttered like a wave, and the bundle of rope rolled up on the floor began to disappear quickly.
wuuuuuuh!the giant troll also cried out, sensing the impending fight.
 since his shouting was so loud, even his skull was seen rattling even from a distance.
“ugh! that damned voice is really terrifying!”at that moment, the four werebear skeletons were split on both sides.
 just before they came close to the giant troll, two of them ran to the left and the other two to the right.
the giant troll also stopped suddenly when they dispersed before his eyes.
but the dull-headed boss monster could not figure out why.
rattle! rattle!the four werebear skeletons began to circle around the giant troll.
whenever they circled the giant, the climbing ropes slowly began to bind his legs.
at first, the monster didn’t bother much, but the long rope was shortened at a much faster rate than he thought, then coiled around his legs in an instant.
guhaaaaah!the power squeezing his legs was tremendous.
 eventually, the tough climbing rope completely encircled him from his ankles to the pelvis, which made it impossible for him to move at all.
 he staggered for a moment, then fell to the side with a thump.
“rush and attack him!”at that very moment, all the skeletons moved at sungwoo’s order.
 they were charging at the huge chunk of unprotected meat at a tremendous speed.


“huh, huh huh…”watching the incredible spectacle unfolding before his eyes, sgt.
 kang was still sarcastically chuckling.
 although he was quite impressed with sungwoo’s extraordinary attack skills, he was troubled by other worries.
‘man, i was going to attack this guy when he was weakened while confronting the giant troll.
 damn it, i can’t carry out my plan in this situation.
’at that moment, sungwoo pushed his back, shouting, “come on, go and get him! you said you were quite good at beating somebody at the special forces.
 i think you can catch the boss monster more easily than i think.
”sgt.
 kang could not think straight.
 he had to find another chance to kill sungwoo.
in fact, sgt.
 kang has seen this kind of scene in a movie.
to the best of his memory, two protagonists in the movie tied a huge insurmountable enemy with a rope, then struck his head with bricks, but this time the enemy facing sgt.
 first class kang was different.
wuuuuhh!the giant troll kept shouting.
could he beat the five-meter long giant? no, it would be impossible.
since such a huge monster was moving very slowly, they could not deal with him with a traditional attack.
the giant troll seemed to be much stronger than sgt.
 kang thought.
“damn it.
 we don’t have any time to delay the attack.
”sungwoo also heard the terrible sound of the rope being split.
 obviously, the ten climbing ropes that could withstand two tons of force gradually became loose.
the splitting noise of the ropes sounded like the countdown of a bomb explosion in sungwoo’s ears.
there was not much time.
 after all, the zombies and werebear skeletons rushed toward the boss monster and tore apart his skin with their nails and claws.
kuuuuh!swinging his hands wildly, the giant troll defended himself and counterattacked them.
 however, his counterattack was not intimidating because he, who fell to the ground, could not twist his body due to the ropes.


 