\section{chapter 447}

'i'm glad she has surrendered to me without any resistance.
 it looks like she was very upset with gangsok han.
'




at the moment isabella was bravely attacking the demon king's castle, which was once her home.
 of course, this was possible because of the 'dragon keeper' placed around her neck.
'well, the collar that hearst made for her has nicely paid off.
 this is terrific!"if she would not follow sungwoo's instructions and tried to escape, he would immediately activate the remote control and shackle her neck with the 'dragon slayer.
' moreover, jisu, who was riding on isabella's back, was keeping a close watch on her.
how long have they attacked the castle?"the shield has been broken!"part of the shield that covered the demon castle melted and a huge hole was created.
 sungwoo immediately entered the crack.
 - you have started occupying the 'labyrinth (demon king's castle).
'"come on, guys.
 tear down this vacant castle until its owner returns! destroy it all!"since sungwoo's allies were determined to destroy it, its owner, the demon king, would have no choice but to return.
 in the meantime, reporter ahn's studio was shrouded in shock.
"no way! this is nonsense! we never knew he was the demon king!"the guy who had always been shrouded in a veil, namely, the guy who was so reluctant to reveal himself to the outside that he was forgotten for a long time, emerged as the 'demon king' at the end of the day.
as a matter of fact, only a few people including sungwoo and the leadership of the world tree camp knew the demon king's identity, so it was no wonder that reporter ahn was shocked.
 he seemed to have exchanged a few words with the necromancer.
then he resumed broadcasting.
 "they have begun to fight! i don't know exactly what the stakes are, but it seems that the two are hostile to each other!"but the fighting was not likely to end anytime soon.
 
the demon king pushed the necromancer hard, then retreated.
ahn didn't know until then that the fight was only a prelude.
you can find the rest of this content on the lightnov‌elworld.
com platform.
the second round of the war began quickly.
 the necromancer tried to change the battlefield, and the battlefield was none other than the amazon rainforest.
"ah, the necromancers and the entire forces of the world tree camp made a very bold move.
 they have advanced into the amazon!""wow, great! this means that his fight with the demon king is not over yet! isn't it a signal to him that he should come back as soon as possible?"meanwhile, another message was in while ahn was busy broadcasting.
 "ah! breaking news is just in!"since he mobilized all his staff to monitor almost all broadcasts, they could get the latest information on what's happening on all the servers.
"someone has said that he is going to spread a message to the whole world through the official channel broadcast! that man is …"then the screen behind his back changed.
 "ah! he's coming out now!"he was none other than gangsok.
 he was standing in front of the camera with the collapsed building in the background.
"this is gangsok han, ranked no.
 1 on the korean server.
 i've just fought against the necromancer, and i've identified myself as the demon king!"it was the first time he used the broadcast while conscious of broadcasting since the destruction of kyushu during the korean-japanese war.
he opened his mouth very slowly, introducing himself with a serious voice.

"i'm no.
 1 on the korean server and the owner of this castle in the amazon.
 let me send a warning message to all players in the world, especially those in the world tree camp players in the amazon.
"there was anger in his voice and expression.
he continued, "i will now return to the demon king's castle in the amazon and slaughter all the players there who oppose me.
 i will kill all of them without any exception.
"this was clearly a declaration that he would no longer retreat.
 there was silence in the studio.
"but there is only one way for you to survive.
"everyone had to focus on his message.
 reporter ahn and his assistant held their breath.
new novel chapters are published on lightnov­elworld.
com"follow me and kill the necromancer.
 then follow me forever.
"after he said that, gangsok disappeared from the camera angle.
".
.
.
"it was a very brief statement with lots of ramifications.
 "ah, his message sounds like he wants to take revenge on the world tree camp that attacked the demon king and provoked the players all over the world to follow him at the same time," ahn's assistant said.
 "in other words, he said he was going to give us a chance to serve the demon king, right? great! i think this is the moment when a new force emerges.
"once again, a power game that could shake the world began.
 right after sungwoo defeated the emperor of the chinese server, the demon king of the amazon appeared this time.
reporter ahn said, "alas, things are getting complicated again.
 demon king? he must be the player who has gone crazy enough to trigger a 'disaster quest'.
 but i still believe in the necromancer.
 i think he is the solution to our problem.
"he continued frankly, "according to sources all over the world, indiscriminate slaughter took place on every server the demon king attacked.
""massacre? there's no reason for him to kill the players who don't support the absolute races, right?""i guess so.
 i think what he wants from the beginning is unilateral oppression and domination rather than integration or control of us, players.
"reporter ahn then quoted the necromancer's statement that he did not want to rule the world.
 of course, he wanted to emphasize that the necromancer was different from the emperor of the chinese server and the demon king.
"ladies and gentlemen, the world will surely become one.
 i think we all know to some extent who we should give our power to.
"then reporter ahn looked straight at the camera and continued, "dear viewers, once again i support the necromancer.
 because of that, i'm going to broadcast in favor of him from now on.
"***the demon king's castle was the demon king's 'territory' as well as his 'large-scale dungeon'.
 because of that, as soon as sungwoo entered it, a very unusual 'hidden quest' was issued at the same time.
[hidden quest]- title: subjugation of the demon king- type: dungeon attackvisit to lightnovelworld.
com discover new novels.
- goal: occupy the demon king's castle- reward: unknown[information (important)]0) in order to attack the demon king's castle, you need to attack its labyrinth.
1) the subjugation team is moving, divided into those in charge of an 'attack route' and those in charge of a 'defense route'.


2) attack route: enter the 'labyrinth' and conquer the 'deep facility' there.
3) defense route: a portal to the corresponding camp (suwon) opens.
 blocks the demon king's army advancing there.
4) whenever the team in charge of the attack route fails to capture the 'gateway' in the labyrinth or gives up, the attack against those in charge of the defense route becomes stronger.
"uh?"the world tree camp had to stop advancing after confirming the quest message.
 "damn it! what kind of quest is this?"at that moment a report came in from the rear.
"a huge, mysterious portal has appeared near the camp!"they really saw a huge portal opened between the rainforests of the amazon.
"sungwoo, is that a portal leading to the world tree camp, isn't it? if that's the case, we can advance there, but can't retreat.
"sungwoo nodded at junghoon's words.
 if the quest was controlled by the system, they could not escape freely.
 "well, it seems like the system wants to fight it out with the demon king.
"in other words, if they lost, there was nowhere they could go back.
 so they had to bet everything on this fight.
 "damn it, this guy is called the demon king, so he seems determined to show his last tragic moment like the end-stage boss in fantasy.
"the source of this content is lightnov­elworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 