\section{chapter 259}

                            the chief priest stood up with his hands folded behind his back.





then, he looked nervously at the crystal ball.
“the intruder will come into the temple.
 he’s not lost.
 he was planning to come here from the beginning.
 if he enters the temple, spray poison gas and kill him.
”the temple was guarded with multiple layers of security.
 although part of its security was destroyed by the priest’s simple mistake, the security around the temple was still very tight.
as soon as the intruder entered the entrance, the door would close and powerful poison gas would fill the area.
“good.
 come on in!”the chief priest confirmed through the crystal ball that the intruder was entering the temple.
at that moment, he ordered his subordinate to pull the prepared lever.
clatter!the entrance closed by itself, and black smoke filled the hallway.
 even if a priest possessed a lot of recovery magic, he could not survive in this situation.
“yeah, you are going to wriggle in agony and die.
”“uh?”however, a shocking scene appeared in the crystal ball.
 the intruder was leisurely walking through the poison gas without any damage.
“no way! what the hell is happening now?”rather, the poison gas only added grandeur to his footsteps, like the fog arising on a stage.
the chief priest became nervous.
“this is our last resort! free all the zombie dogs!”clatter!another lever was pulled.
 it was the last lever.
 the iron bars at the end of the temple hallway opened, and dozens of zombie dogs furiously ran along the temple hallway.

but the next scene was even more amazing.
“oh, my god… what the hell are they doing now…?”the zombie dogs running at the intruder folded their ears and wagged their tails gently as if they were welcoming their master home.
“our defensive line has collapsed! he is now coming down to the basement!”only then did the chief priest recognize the seriousness of the situation.
“this is not the player we can handle…”then, the chief priest looked at the center of the altar with a desperate expression.
there was a coffin covered with red silk.
“wake him up.
”priests here and there swallowed and grew tense.
“are you sure? should we awaken death?”“chief priest, if we wake him up, death will fall upon us too.
”the chief priest was determined.
“wake him up.
 we have no other way right now.
”eventually, the ceremony to awaken the owner of the coffin began.
 all 20 death priests folded their hands together and cast the same summoning magic.
ooh ooh ooh-the purple magic gathered at the center of the altar.
 then, the red silk slowly lifted.
kieeeeeeeeeee-the sound of the coffin opening filled the air.
 a gloomy wind blew from somewhere and extinguished the surrounding torches at once.

“…”with only the purple magic emitting a gloomy light, black smoke sprang up inside the coffin.
“how dare you guys wake me up! crackle!”a hysterical voice came out.
 in particular, the sound of the teeth bumping together was loud like castanets.
 the chief priest ran and laid face down in front of the coffin.
“prophet of death! i apologize!”“crackle! what’s going on? crackle! if it’s nothing special, i’ll make all of you parts of the flesh golem.
”thud! ku-woong!at that moment, a loud roaring sounded, replacing the chief priest’s reply.
“…”“finally, the intruder has entered our temple!”the lich’s eyes sparkled in the black smoke.
 there was deep resentment in his eyes.
kugugugu―at that moment, a stone gate, which had been locked tightly, shattered.
while the death priests looked astonished, an unidentified intruder walked in leisurely.
he was a man wearing a dark green robe.
“you bastard, how dare you intrude upon our temple?” the chief priest yelled at him.
the death priests stood up and retreated to both sides.
 since they realized they could not confront him, they stepped back.
thus, lich and the intruder were facing each other.
“oh, prophet of death! punish that ignorant stranger and give him a terrible death!”“please!”the black smoke cleared, revealing lich’s glowing purple eyes.
 a bizarre skeleton with the great nickname of the prophet of death looked at the strange intruder.
crackle! crackle! crackle! crackle! crackle!he was trembling violently, bumping his teeth.
meanwhile, other players on the korean server also showed various reactions in response to the new mainstream.
“can you see it? that’s the north korean server.
”reporter ahn’s broadcast attracted many viewers.
 while covering the major events of the korean server, he captured important moments on the camera, which established his broadcast as the main broadcasting station of the korean server.
his broadcast had become a media company with 11 employees.
“the ‘reporter ahn’s apocalyptic news’ team is here on the scene before anyone else!”although they could not cover the “korean-japanese war” that took place in busan, they hurried to the place near the dmz in paju and flew a drone camera as soon as the mainstream began.
weeeeeeeeeeing―four drone cameras exited the south korean server and entered the border of the north korean server.
the broadcast screens changed in real-time with the angles of the cameras.
 thanks to the state-of-the-art item called ‘multi controller’, they could send out multiple broadcasts at the same time.
“uh?”at that time, something was caught on camera.
 reporter ahn immediately added his narration.
“ah! they’re zombies! let me turn over to no.
 2 camera for a close-up.
”when reporter ahn beckoned, an employee manipulated the controller.
 then, more specific things were broadcast on the screen.
when the camera captured the scenes of the territory of the north korean server beyond the dmz, a large number of zombies were shown crowding in one place.


“oh, my god….
”thousands of zombies were standing along the deserted ridges.
“there are so many zombies! thousands of zombies are lining up, looking south! it seems like they are rushing to the south!”even though they were just gathered without taking any action, their presence posed a considerable threat.
“is that the start of disaster coming from the north korean server? let’s go up a little further north!”reporter ahn’s drone flew the farthest distance it could while remaining under their control.
“oh my! that stuff is…”what came out on the screen was also shocking.
 hundreds of troll troops were checking their armament, and hordes of orcs and goblins were gathered behind them.
the reason such a scene was so shocking was that the three races were uniting to prepare for war, something that could not be seen on the south korean server.
at that moment, there was white noise on the screen, which meant that the drone reached the limit of its control range.
“this is all we can show you for now, but it looks like a big war is about to break out.
 i feel something like the harbinger of war.
”some unknown smoke was rising from all over the land of north korea.
 it was like the smoke of people cooking rice.
 if that was true, it meant that a huge army was now moving to the south.
“then, how should we respond to them in the future?”-id ‘steel shield’ gave donations! (1000 gold)as a leading camera operator, he was now receiving financial support from the watchers of his broadcast.
“thank you for your support! even if the korean server collapses, we will capture all the scenes even in hell to the end!”thanks to his broadcast, some of the reality of death coming down from the north korean server was revealed to a very small extent.
but its impact was so huge.


 