\section{chapter 348}

chapter 348: jeju island and attack on demon’s cave (12)dozens of shadows then passed over the deck.
 everyone in the control room raised their heads immediately.





“what the heck is that?”“bats?”bat? it might look like bats when seen from a distance.
 if something hanging from the ceiling fell backward inside a cave, they naturally thought it was a bat, something very familiar.
however, if the ceiling on which they were hanging was a branch of the world tree that reached even the clouds, it was a different story.
soon, huge creatures with wings began to descend from the air thousands of meters above the ground like swarms of bees.
gugugugugugu-the sound of their fluttering wings was roaring like thunder.
“they are attacking us! everybody, to arms!”as soon as kyungsoo shouted, the messenger instantly got into action mode.
the crew was busy tapping the bulletin board to send messages.
“the outer shield has been activated!”“all turrets loaded!”“we’re going into evasion mode at full speed.
”sungwoo shook his head, watching the endless stream of creatures coming out from the branches in the clouds.
 he thought they were too many and they came out too fast.
“we must go at full speed towards the hole in the world tree!”sungwoo got up from his seat and opened the door leading to the hallway.
“kyungsoo, please take out the item, vine of the world tree right away.
 and don’t go outside!”in a situation where monsters like that were coming out in hordes, no one but sungwoo could stand on the deck.

“no, i will go with you, too.
”li wei followed him, followed by hanho slowly.
“well, even though i lost all the high-grade spirits, i can still fight well as the no.
1 in the chinese server rankings,” li wei said.
“sungwoo, i’ve got six arms,” said hanho.
sungwoo looked at the two faces in turn and nodded.
“i’m not going to stop you, but don’t die in vain.
”li wei raised her chin and challenged his remarks.
“like i said a few times, what i’m good at is putting myself at risk of dying.
 that means i’m really good at not dying,” she said.
although she was defeated by the emperor, it was true that she was a great fighter, given that she escaped from him after surviving.
 even after escaping through the demon’s cave, she again infiltrated beijing and stole the ‘devil’s stone statue (a token of blessing)’ from general xing’s residence.
so the three of them went out the door of the control room.
“li wei, do you know what they are?” asked sungwoo, as he headed towards the deck.
but she thought hard about it, then shook her head.
“well, i didn’t see any winged demons in the demon’s cave i entered.
 the door of the cave i opened was on the second floor.
 maybe they came from a different place?”the first and second floors of demon’s cave were different? there was no ground to believe so, but sungwoo seemed to think so.
 however, according to li wei’s reasoning, this was not the only place ruined like this.
“well, we should make sure this place we’re in should not end up being the nth floor.
”clicking his tongue, sungwoo murmured.
“uh? nth floor?”“it seems to me that this place was abandoned after one game was over.
 who knows this place could end up being like this?” said sungwoo.

but li wei was embarrassed at his words.
she said, “what? crazy, so what should we do to stop this place from being ruined?”it was a fundamental question.
 sungwoo thought for a moment but shook his head.
“i don’t know.
 all games are destined to be scrapped, no matter what its ending is.
”hanho added, “i guess so.
 the game is over forever if the person who originally enjoys it gets tired of it.
”however, somebody who did not enjoy the game and felt even displeased was helping sungwoo now.
‘i have no choice but to believe her words that she wants this game to collapse.
’the three came out onto the deck.
“they are getting close to us.
”their approach was faster than expected.
 and it looked like they numbered around one thousand.
it reminded him of the appearance of a huge swarm of locusts among the 10 plagues of egypt in the book of exodus.
“well, it’s embarrassing for us to give up now, right?”as things stood now, the messenger would be swept away by those monsters even before reaching the hole of the world tree.
“so, necromancer, what are you going to do? they are so gigantic! they’re going to rip this ship apart like piranhas eating pig carcasses.
”they were about 5 meters from head to tail, which were similar to the “lower monster” he had seen before, but their hind legs were sharp like birds of prey.
 if caught by them, everything would be smashed to pieces.
- caution! the ‘fellblade’ has begun in the region!so, sungwoo summoned the undead troops on the deck first.
 he chose large ones like ‘troll skeleton’ not to be dragged by the claws of the monsters.
“crackle! master?”“uh? where am i now?”among the undead army were victor and minsok.
 they opened their mouths wide after looking at the sky.
“crackle! crackle! man, i’m destined to open my eyes in a situation like this.
”“well, i’m used to it now, but…”at that moment, kyungsoo and some crew members came out with something, which sungwoo asked for.
“sungwoo, this is the vine of the world tree item.
”“okay.
”“whew…i wish you good luck.
”they put the item down and hurried back.
[item information]- name: world tree vine- grade: mythical- class: special equipment- effect: if you tie one side of the vine somewhere and the other end to an object, you can pull it with a strong force.
since he used it to tow the washington fleet through the hypergate during the american air raid, the item could exert tremendous power.
“manufacture bone weapons!”after sungwoo canceled the summoning of several troll skeletons, he created a new weapon by combining their bones and vines of the world tree.
rattle-

it had a hook at the end of the vine, which was bent deeply so that it would not come off easily if caught somewhere.
 in addition to the hook, there were hundreds of sharp straight blades along the long vine.
 overall, it looked like an incredibly long fishbone.
“what is that?”li wei, who was summoning the water spirit, looked at the object and tilted her head.
“it’s something that will gather exp and gold.
”“really?”the troll skeletons picked up the monstrous weapons.
 there were a total of seven, which was as long as a whopping 100 meters, so it seemed very heavy.
“that 100-meter hook with hundreds of knife blades?”li wei asked as if she had no idea what the hell that weapon was for.
 however, sungwoo believed in the monstrous power of this new item.
‘maybe exp is pouring over my head,’ sungwoo thought to himself.
the original reason why he came into this cave was that he sought to level up.
he needed to reach level 25 to secure the status of king of hell.
‘so even at this moment, i should take advantage of it somehow.
’bang!at that moment, the first cannons were fired.
 sungwoo’s allies fired first toward the demons to keep them at bay.
bang! bang! bang!however, the allies could not fully use their firepower because most of the cannons installed on the airship were designed to attack the targets on the ground, so they could not aim at the demons in the sky properly.


 