\section{chapter 401}

sungwoo took out a sword from the inventory of the world tree camp.





"it was like you showing a rabbit in front of a hunter.
""what?"a person who claimed to be a dragon appeared in front of the dragon slayer.
that woman seemed to know what sungwoo's deity status was, but she didn't seem to know which items he had.
"if you think it's advantageous for you to find out the information about your opponent.
.
.
.
"sungwoo moved his subordinate spirits and had all of them take out the weapons of 'dragon slayer.
'"you should have valued your information, but your ill-advised vanity devoured your reason.
"she wouldn't have even imagined there was a weapon like 'dragon slayer' since the amazon's dragon was still serving as the strongest boss monster.
- 'synergy effect' is given due to team play.
 4) dragon expedition (hidden)- category: weapon synergy- condition: 3 or more 'dragon slayer' weapons- effect: additional damage when attacking dragon-type targets (+200%), all types of 'breath immunity' increase (+200%), 'dragon peer' immunity increases only for the owner (+200%)"by the way, i've come to obtain the nutrients for my dragon slayer without fighting hard.
"by killing her, sungwoo would soon possess four dragon slayers.
if she had a dragon-related deity, it meant that she had the traits of a dragon.
therefore, sungwoo's 'dragon slayer' item and 'dragon expedition' synergy were certain to inflict fatal damage to her.
"what? rabbit?"but zi xuan sneered at him, which was her first reaction to him.

"alright.
 then, let me make you realize quickly that i didn't attack you out of my vanity…"after she said that, she raised her arms.
woo woo woo-then, the storm that shook the area stopped at once.
 there was silence as if the flow of air stopped.
 the next moment, she slowly lowered her hand.
 as a result, the dark clouds floating in the sky slowly moved.
woo woo woo-as if a curtain fell, dark clouds fell behind her.
 it looked like gray paint was flowing.
that huge mass of water vapor turned into a waterfall.
 the waterfall began to fall from the sky.
kugugugugu-watching it in shock, li wei stepped back from her.
"necromancer, i'm sorry, but i can't do anything.
 my spirits, whom i have saved with great difficulty, will be tied to that bitch again.
"nodding at her, he stepped forward to zi xuan.
 "step back.
"the waterfall falling from the sky became a huge wave and swept over his head and back right away.
 kwagwagaguagua!the waves overturned everything on the ground, rushed, and attacked the undead army.
 the next moment, it turned into a whirlwind and soared in the air.
 "do you think you can break through this? your army can't touch this tornado at all!"a tornado dozens of meters long swirled violently around her body.
 
there was no gap at all.
 so nobody could dare to break through it.
"yeah, just spinning like that.
 by the way, this isn't the end of your attack, right?" sungwoo sneered at her sarcastically, who seemed pretty relaxed.
 "well, i guess this is the perfect skill that can buy you more time.
 don't you think so?"she didn't show any change in her expression at his provocative remarks, but she began to move her fingertips very roughly.
 she waved the waves toward him by swinging her hands.
 she then tore off some of the tornado protecting her body and rushed it more violently than before.
'now is the time!'at that moment, sungwoo gave some instructions to somebody far away.
***meanwhile, while zi xuan was blocking the necromancer, the emperor's terracotta army charged towards the castle wall.
"uh? more of them are coming!""no way! there are too many of them charging at us!"the size of the enemies that they observed at the fortress wall was so huge that they lost their fighting spirit.
 jisu sat down on the wall and looked at the battlefield.
 she beheaded several hundred horsemen of the keshik cavalry and confronted the spear unit of the chinese army, which made it possible for her to keep them at bay for now.
kugugugugu-however, an army of over a hundred thousand terracotta dolls came out from both sides of the spear unit, then came running fiercely toward the fortress wall.
it was as if a large amount of earth and mud was swept away by a landslide.
 it seemed that the eroded soil would crush the wall and shake the roots of the world tree.
"if they break through the wall, they will run over us!"junghoon nodded at jisu's assessment.
 "i think so.
"the terracotta were charging frantically with their heads back and swinging their limbs in a bizarre way.
"shoot! shoot!"inho shouted from the deck of the messenger.
 it was necessary for them to mobilize all firepower to stop their overwhelming offensive.
 soon, dozens of airships opened fire at once.
kwa-wa-wa-wa-wa-gwang-like the so-called carpet bombing, a vast area was devastated by the fire.
but the enemy troops were little affected.
 "enemy troops.
.
.
.
"hundreds of thousands of terracotta were not strong simply because of their numerical superiority.
 they had some strange power beyond common sense.
"oh, my god! they are intact!"the moment the shells fell, they scattered all over the place like insects with developed senses.
then, they got tangled with each other naturally as if they were one body, minimizing damage from shelling.
qguaguagua-also, when the shells exploded, spreading debris and flames, the terracotta near the shells exploded themselves, forming veils of dirt.
 since many of these veils overlapped, the radius of the explosions was drastically narrowed.
"they're coming back!"thump- thump-they were not just terracotta in human form.
 giant terracottas, who were dozens of meters tall, moved forward with heavy strides.
two-woong! two-woong!along with steel golems, they used powerful flying weapons like personal firearms, which caused considerable damage to the castle wall and the airships, no matter how strong they were.
"our shield has started to be broken!""retreat, entire fleet! get ready for the next attack!"

after pouring out all their firepower, the combined fleet had no choice but to retreat deep inside the wall until they loaded cannons.
but the problem was the enemy made full use of the loophole of the allied forces' attack.
"they are climbing the wall!""shit! push them off the wall!"they finally reached the wall.
 then, like a swarm of zombies, they started stepping on each other's bodies as stairs to climb the wall.
rattle- rattle- rattle-they were climbing at a ferocious speed.
 "how come they are climbing the wall?"some of their hands and feet made of earthenware started to melt and became sticky mud, then stuck to the wall.
 when their fingers and toes melted away, the others climbed up and detonated bombs inside their bodies.
 five or six people nearby were killed at once.
"pour all the firepower!"a beam of petrification was fired automatically, turning hundreds of terracotta crawling up the walls into stones.
 but it ended up being disadvantageous to the allies.
 the stones became the stairways through which they could climb more easily.
"shit! destroy them!"at that moment, a very bright light burst out of the air in the middle of the battle.
 everyone had to close their eyes.
"what the heck is that?"suddenly, two giant hands appeared before them.
 the hands were golden as bright as the hands of buddha, and they were large enough to cover the sky.
 at first, it was so beautiful that they thought it was a huge butterfly.
the man was turning his palms toward the ground, whose knuckles were shooting out translucent golden threads.
 "ah…"

 