\section{chapter 424}

griffin quickly raised his altitude before descending again while leading the herd, followed by 213 hippogriffs in close formation, although they struggled to catch up with griffin.





"never let your guard down because they might attack you from all directions!" jisu shouted.
she was among the ranks of the riders.
 even though she didn't ride hippogriff, she could move much faster.
"watch out over your head when you fly low!"meanwhile, junghoon, who left the command of his troops in seoul to his deputy minhum, was participating in the special commando operation.
while heyon led the flight and jisu was in charge of the lookout for suspicious outsiders, junghoon was responsible for the attack and defense.
"magicians, get ready for defensive magic all the time!"since he led the 'crusaders team' for a long time, he knew the importance of their positions better than anyone else.
"deploy the shield right now!"as soon as junhoon shouted, the wizard players at the center of the ranks used a large-scale shield skill.
 then various lights came out from all over the place and got tangled together, generating a spherical shield.
"close formation!"when he issued the next order, the hippogriffs began to close the gap among them and make their formation narrower and denser.
 thanks to such a movement, the entire army could go inside the shield without anybody dropping out.
but it was not good to have the air task force gathered in one place.
 they needed a momentary defense and a faster escape at the same time.
"prepare for the escape in wide formation! escape now!"as soon as he ordered, the entire army dispersed and glided in all directions.
it seemed that they were engaged in a drill where they avoided the enemy attack, then regrouped into a single formation.
"wow, they get used to it so quickly, right? man, i really don't want to ride a flying thing without any canopy…"grrrrr! grrrrr!
at that moment, mir, who was sitting next to sungwoo, whined and suddenly started flapping his wings.
"what are you doing now?" sungwoo asked.
this content is taken from lightnovelworld.
c‌omas soon as he crossed a certain point, mir began to grow rapidly.
 he has grown as big as an adult doberman, so it was hard for sungwoo to carry him in his arms.
 he would get into big trouble if mir caused any problem.
"sungwoo, he seems to fly," said hanho.
as he said, mir seemed excited to see the group of hippogriffs in the sky and fly like them.
"no, you shouldn't fly.
 they are not playing now.
 if you intervene now, you will disturb their training.
"sungwoo gently pressed down mir's head to calm him down.
mir rested his chin on his front foot as if he was disappointed.
beep!at that moment griffin who was flying at the front broke out of the ranks and came down to the ground.
 at the same time, all 213 hippogriffs also began to land on their respective positions on the airships.
"necromancer!"sungwoo was apparently taking a short break when heyon noticed him and landed on the runway.
"look! i have obtained a new skill!"she bragged like a kid who won an award at school.
 contrary to her worries at first, she was now in a cheerful mood.
 she looked rather lively than she usually was.
she seemed very proud that she was able to contribute greatly to the world water camp by doing what she does best.
"new skill?"
"yes! to be precise, i got it through griffin.
 it's called 'flying leader'! i obtained it while continuing to fly in formation!"she then explained that she could have a number of hippogriffs follow griffin instinctively.
griffin instinctively made griffin and typhoon follow.
because of that, her endurance, flying capability, target-hitting ability, and her command delivery dramatically improved.
"to my surprise, hippogriffs followed griffin so well that he gained more confidence!"since the creature called 'hippogriff' was the product of a 'griffin' crossed with a 'horse', he seemed to instinctively follow griffin, a higher species.
updated from lightnov‌elworld.
c‌omsungwoo said with a nod, "that's great.
 as expected, you are doing fine!"when he praised her, she couldn't hide her shyness as if she was choked with emotions, with her ears blushing.
"ah, thanks!"she had been trying to be recognized by him for a long time, so she was really touched by his praise.
"we've got only a few hours left before the start of the war.
 we're into the war then!"although sungwoo said it bluntly, she was even more motivated by his words.
"alright! i will work harder! then let me go back to work!"she again got aboard griffin, and soared into the sky.
'everything is going much better than i thought.
'since the special commando unit consisted of the highly skilled elites, they quickly adapted to the tough aerial maneuvering drills.
'if they keep training and practicing like this, they are definitely going to be helpful when they hunt the dragon.
'at that moment someone visited sungwoo.
"hi, necromancer!"he was from the hearst workshop.
"you need to go to the hearst workshop to check something urgently!"so sungwoo rushed to the forge of hephaestus in search of hearst.
clang! clang! clang!amid the scorching heat, dozens of blacksmiths were busy working in front of the furnace and the anvil.
hearst walked out among them.
"oh, i called you because i've got good news for you.
"for more, visit lightnovelworld.
comthen he turned his head somewhere.
 when sungwoo turned his eyes there, he saw an open safe on the wall on his left.
"i opened another safe, and found something good.
"the vault where the players of the destroyed world kept their items could be opened once every 24 hours, but since hearst opened it forcibly, he applied the skill, 'robber's trial'.
each time he did so, one 'gold guard' appeared, but he could easily destroy them since he had a bunch of flying weapons in the forge of hephaestus as soon as they appeared.
"by the way, i developed the technology to bring the gold guard back to life.
 next time i break open the warehouse, i think i can save three of them, so we can catch them more easily.
"sungwoo was surprised to know that hearst could resurrect the gold guards and control them.
 that was clear evidence that their magic engineering technology was advancing day by day.


as was the case with science, someday they would be more useful than the players' power.
"got it.
 by the way, what are the items that you found from that warehouse?"when sungwoo asked, hearst pulled something out of his pocket and threw it.
it was a green stone.
"it's an enhancement stone.
 i want to enhance one of your items.
 what do you think?"sungwoo immediately confirmed the information of the item.
[item information]- name: help of time- grade: unknown- category: myth- description: it contains an incomprehensible formula of time.
 you don't know how to use it.
"well, the description is rather vague, but this type of thing can give items special traits or enhance the effects that are hard to attain.
"sungwoo said with a nod, "i know what it is.
"in the past, when he hunted 'fire giant' in pyeongtaek, he applied the orb of 'fire spirit' to the repeating crossbow to obtain a 'fire' effect.
 after that, he obtained 'fire spirit stone (high)' by hunting 'salamander'.
new novel chapters are published on lightnovelworld.
com'at that time both of them gave me effects related to fire.
 but it's time.
.
.
' you can also read this novel on the more advanced platform lightnovelspot.
com

 