\section{chapter 325}






 the king reached out to the corridor where there was a big fuss.
 when he did so, the remaining roots moved like curtains and blocked the hallway.
“jisu, the roots are going to disappear soon, then the enemy will try to destroy the whole building again.
 what are you going to do? it doesn’t matter whether you go out or stay inside because you will be killed anyway.
”“no way, i can’t let myself be killed without doing anything.
”she raised herself with difficulty.
 although she stumbled, she had no intention of being killed as an onlooker.
“i thought you would fight to the end,” he said.
the roots that were blocking the wall and windows disappeared, and light came in instead.
 then, the enemy made more disturbances than before.
 it was the sound of their flying weapons rolling on the floor.
thud! thud!as if they noticed that the roots were disappearing, they began bombing again.
goong-gugugugu!the building began to collapse, hit by only two cannons fired by the enemy.
“they began to bomb us already? ah! because the roots that were supporting the building disappeared, the building can not stand! we have to get out of here now!”the king moved the remaining roots and wrapped them around her body because they would be killed under the collapsing building.
the moment they got out of the building, an explosion suddenly broke out, throwing each of them in different directions.
“we’ve hit them!”the wizards who were waiting outside the building shot fire magic.
“argh!”jisu rolled on the ground miserably.
 normally, she would have minimized the impact of her fall and recovered her balance, but she could not do it right now.
her body stopped rolling after her waist bumped against a fire hydrant.
 she raised her upper body using the sword like a staff, but she could not give strength to her legs.

she slowly lifted her head.
 her vision was blurry because her face was stained with blood.
 she found herself surrounded by hundreds of enemies in no time.
“…”surrounding her from all directions, they approached her slowly.
even though they must have heard a lot about her reputation as a formidable fighter, she now looked like a dying fox, so they courageously approached her.
“oh, this bitch can’t even move right now.
 kill her right now!”but jisu shut her teeth tightly, sneering at them.
 then, she raised her body with all her might.
 there was already a pool of blood under her feet.
she raised the ghost mast that stretched to her neck and put it on.
“sure, this is a good opportunity for you guys to kill me.
 kill me if you can!”at that moment, they threw knives, spears, axes, daggers and arrows at her with a shout.
clang! clang!she struck down two arrows, but she couldn’t stop one of the daggers from getting stuck in her back.
‘let me kill as many of them as possible.
’she didn’t stop their attack.
 she didn’t care about getting wounded because she needed to move efficiently to kill more of them.
 so, she moved solely to destroy the approaching enemy.
clang! clang!she deflected three blades at the same time, but she staggered.
 she was so wounded that she could not withstand such a little attack.
but that was the same with her opponents, who lost balance from her attack.
she stabbed the sword into the staggering enemies.
“kheeeeeeek!”
she stabbed their hearts with the sword.
-you have obtained 12,000 gold by killing a player.
as soon as she took the sword out of the enemy’s heart, she swung it at the men behind her hack.
 two of them fell, grabbing their necks.
-you have obtained 14,000 gold by killing a player.
-you have obtained 14,000 gold by killing a player.
at that moment, a couple of daggers were stuck into her shoulder and thigh.
 her left arm drooped with its tendon broken.
 then, the enemies began to close in on her again.
“kill her!”however, she was still holding her sword.
 as long as she was holding it, she could kill one more enemy.
 she swung the sword at the enemy charging at her from the left.
“uh?’but there was no sword in her hand, or more precisely her right hand was missing.
“ahhhh…”when she turned her eyes, her severed right arm was soaring into the air, then fell on the pool of blood on the ground.
“great.
 but you are finished now,” said the masked man who cut her arm.
she nodded at him.
 he was right.
 her end was nearing.
but she lowered her head.
 the masked man approached her.
 he grabbed the sword with both hands.
 she felt the blade falling over her head.
right before his sword touched her neck, she twisted her body and stuck to him.
then, she pulled out the dagger from her left shoulder and cut his neck by turning her body quickly.
“kheeeeek!”although her left cheek was torn apart, she succeeded in killing him.
“kill me if you can…”although she was completely defeated, she was not yet ready to be killed obediently.
“you tough bitch! you are really…”now, they began to admire her resistance.
 since they were used to training while serving their swordmaster, they had no choice but to feel in awe of her toughness in such a perilous situation.
but that was it.
puck! puck! puck!three arrows were stuck in her chest.
she felt that something indescribable was flowing out of her body in addition to the gushing of all the blood from it.
‘is it my soul?’she felt the world became dark.
“…”then it became bright again.
-you have entered an ‘unknown place’.
‘what the heck? it’s so noisy here.
’and it became very noisy.
 loud laughter and shouting came from everywhere, which included the sound of somebody singing and others fighting.
 she felt like she was thrown into the middle of a party.
what the heck is this place?jisu looked around, but she could see nothing.
 all she could guess from her blurry eyes was that a lot of people gathered in a huge hut were eating and chatting.
‘be quiet!’

at that moment, they became silent when someone shouted.
 he was the man who sat at the highest palace of the hut.
 according to her senses, they didn’t really exist.
 they were something like an event scene to convey a message.
‘your new fate has arrived here.
 after a very intense fight, you have faced a miserable death.
 you have killed so many before you were killed.
 so…’obviously.
 that message referred to jisu.
so, she wondered if this absurd scene was her delusion of the dying process or did it mean some kind of change by the system? of course, she hoped for the latter.
at that moment the man sitting on the high place said, “you are fully qualified.
 you are qualified enough to go back to the earth to kill more bad guys.
 any objections?’nobody responded.
 she pricked her eyes at that.
 back to the earth?‘then, let me entrust that role to her.
’having heard that, she thought to herself, ‘if so, send me back to the earth!’there were too many bad guys she had not killed yet.
***the building that fell from the sky struck down admiral baker’s fleet floating in the air.
“no way! how could it…”there was no way for them to avoid such a devastating attack.
 their two airships were still smashed to pieces.
 only admiral baker’s flagship barely avoided it using the special engine attached to the ship.
bang!after destroying the two airships, the building fell over the place where the chinese army had been camping out.
 it was also a place where dozens of flying weapons were stationed.
 all of them disappeared under the building.
“ahhhhh…”but it was just the beginning of a more intensive attack.
the building that was stuck upside-down slowly began to tilt to the side.
“argh! it’s coming our way!”

 