\section{chapter 307}

chairman love called the worst monster crouching in amazon a dragon, and a fully grown dragon at that, unlike the baby dragon, mir.





"did anybody actually see the dragon?"she nodded at sungwoo's question.
she continued, "what's really fortunate is that the terrible monster doesn't seem to be coming out of amazon for a while.
.
.
"she sipped the coffee and opened her mouth again.
"in fact, until recently brazil has been the territory of a strong player guild.
 in particular, there were quite a few survivors living in the southern cities, and some guilds were powerful enough to have 10 players over level 20.
""wait a minute! 10 people at level 20?"sungwoo shook his head because he could not believe it.
"10 people? are you sure?"sungwoo, ranked second in the korean server rankings, was at level 23.
 and junghoon, no.
 3 in the korean server rankings, reached level 20 only recently, and jisu, ranked fourth, was still at level 19.
 how could one guild have 10 high-level players? sungwoo could not understand easily.
 when sungwoo could not hide his puzzled expression, chairman love added, "i understand your feelings.
 we were also shocked when we found out the level and strength of the brazilian server.
"since the wpu members led by chairman love were particularly low level on average, they must have been greatly shocked.
 "well, come to think of it, it was only natural that they were so strong because they could only survive by stopping the monsters endlessly popping out of the huge dungeon called the amazon.
""yeah, it looks like they lived in an environment in which their level was supposed to go up each day.
 i can understand to some extent," said sungwoo.
come to think of it, they had no choice but to be strong in order to survive in the amazon.
 
the eastern part of the united states was a good environment for survival, but it created an environment for the wpu players to become weak, compared with the brazil server players.
"but even the brazil server players were eventually annihilated by the amazon.
 that happened only a week ago.
"the powerful brazilian players did not exist anymore.
 the strongest warriors raised in the worst environment were eventually annihilated without being able to overcome it.
 and the name of that 'environment' was dragon.
 "fortunately, the delegation we sent to rio de janeiro came back alive, and we could hear from them in detail about the terrible catastrophe that happened to them.
 yeah, it's so terrible that we could find no hope…"according to the delegation to the brazilian server, they witnessed the warriors who confronted the amazon collapsing.
 about 10 days ago, rio de janeiro's "barreira guild'' was sick and tired of stopping the monsters popping out endlessly.
 eventually, they decided to root out the source of the problem and organized the 'amazon expedition'.
13 guilds were united to form an expedition of 2,800 players.
 they mobilized 35 helicopters and 400 heavy equipment trucks to carry out the largest operation on which the fate of brazil depended.
"but that operation was a mistake.
 they touched the disaster that had been sleeping in the amazon at that time.
""they incurred dragon's anger, right?"chairman love nodded then she shook her head.
"not really.
 we could not call it dragon's typical anger.
 how can we define it simply as dragon's anger that resulted in the disappearance of brazil and south america as a whole? every city, every survivor, everything turned into ashes because of dragon's attack.
 we watched the flames soaring over the southern skies, and we hoped that the flames would not come over to our side without even thinking of reaching out for help.
"not just one server, but all the servers in south america disappeared overnight because of just one creature.
"i would call it punishment…"chairman love frowned then she came back to the real world as if she was an old woman telling an old legend.

"and i hear that a certain quest was given to those who witnessed the horrible scenes.
 that's the key, and we should be prepared for that!"she then explained that an unfamiliar message of "disaster quest" appeared before the wpu members who witnessed the dragon.
the detailed information was like this.
[disaster quest]-name: worst creature-type: 'kill' or 'escape'-goal: unknown-reward: unknown*you have witnessed the disaster that burnt the earth.
 its name is 'dragon'.
having destroyed all the living creatures in south america, dragon returned to his nest and fell into a "dormant" state.
 however, after 48 days he will start doing activities again.
 and the dragon's next target is your hometown, north america.
you have two choices, namely, fight recklessly or flee wisely.
* after destroying north america, the dragon is going to go into a "dormant" state again.
 and when he resumes his activity, he will move to a new area.
 (expected area: east asia)"this is the hidden quest that the brazilian server woke up.
"".
.
.
"dragon was not confined to the amazon.
 this unprecedented disaster was expected to reach asia through north america within 100 days.
'man, i can't stand as an onlooker if this is true.
'sungwoo began to take the situation very seriously.
 he realized that the catastrophe he was looking at from a distance was a fireball running over his feet.
"you saw this message seven days ago first, then it means there are still 41 days left…"41 days was not short.
 chairman love gazed at sungwoo, interlocking her fingers.
"then, do you think you can build up strong forces to stop him during that period?"sungwoo shook his head.
"i do not know.
 even if i don't know exactly how strong the dragon is, i wonder if our forces can be strong enough to stop him…""you are honest.
""i have no choice but to try.
 even if i still can't stop him, i have no choice but to give up america and prepare again until he moves over to asia.
"that sounded terrible to chairman love, but it must have been a realistic plan b for sungwoo.
 chairman love said with a sigh, "oh, god…i really wish that would not happen.
 for the next 40 days, we should use all the resources before that monster strikes us.
"".
.
.
""well, that's why we thought of forming an international coalition, but if you can think of a better idea, i would like to fully support you.
"

"okay, let me think about it.
"sungwoo was now slowly preparing for a fight with the unprecedented monster in the near future.
***when half a day passed, sungwoo was contacted by the hearst workshop.
 they finally finished manufacturing the item sungwoo commissioned.
 sungwoo headed to the hearst workshop.
 when he opened the door, hearst, with a cigar in his mouth, stared at him.
"damn it! this was so annoying a task! i think all the blood flowing in my body has become a shake.
"even though he said so, hearst was obviously proud that he succeeded in making the item as sungwoo wished.
 he put his feet on an iron box on the floor.
 "after making it, i thought this was a perfect item for baskin robbins, but unfortunately, baskin robbins is ruined!""then let me open something similar to that.
"hearst pushed the box to sungwoo with his foot.
 sungwoo also lifted his foot and took the box.
 when he opened the box, there was a white rifle in it.
"what do you think? isn't it cool?"

 