\section{chapter 243}

                            sungwoo passed through a horizontal passage with minsok.





“necromancer, i can see the end of the road over there.
”“it’s shorter than i thought.
”the horizontal passage had elevations, but it was generally straight.
 so, it didn’t take long for them to reach the end.
the end of the passage led to a huge cavity.
 the stairs on the 8th basement level were quite high, and this cavity was also over 20 meters from the floor to the ceiling.
sungwoo stood tall in the great darkness and lifted the lantern.
“that thing is…”he found something strange.
 there was a rather bizarre thing stuck to the wall facing the passage.
chomp! chomp! chomp!it was a human’s mouth.
 a huge mouth, about 10 meters wide, protruded from one wall.
chomp! chomp! chomp! chomp! chomp!his pale lips were dry with stiff, dead skin, and each time the mouth opened, saliva dripped through the yellow teeth.
 from time to time, its black tongue was seen wriggling.
it murmured all the time as if it were chewing on something, but a loud disgusting noise echoed loudly as if to match its huge size.
“what the hell is this?” minsok also couldn’t hide his displeasure.
“it seems like it’s spitting out fire.
”“fire?”sungwoo noticed that his mouth was the origin of a huge column of fire sweeping the horizontal passage because the nearby floor was unusually charcoaled.
“how about tearing that mouth off?”“i hate to go close to it, but let me do it.
”
sungwoo summoned his subordinate spirits to attack the mouth.
 he was worried that it would breathe out flames, but it made little resistance as if it was not ready yet.
it just flapped its lips and screamed a disgusting sound, then quickly stuck out its tongue and stopped moving.
-by removing the ‘unknown existence’, you have incurred the anger of the ‘unknown existence’.
‘what the heck is this?’incurring his anger? what does it mean? unknown existence?it was never a good sign that the system was hiding something.
‘is it the thing that dr.
 yu is serving? the white wolf has warned me about it.
’this seemed to have something to do with the “existence” that the white wolf said he didn’t know about in detail, but sungwoo could not figure out anything right now.
 to get the clue, he had no other choice but to go deeper.
“there is a door over here!”minseok found a large door on one side of the cavity.
 it was a sealed door made of stainless steel, and the light was leaking out through a small gap.
 it seemed that a little normal space was about to appear.
sungwoo did not approach it directly but sent a werewolf skeleton to open the door.
but when he reached out and tried to grab the doorknob, the door opened by itself.
then, a little boy came out of the door.
“nice to meet you.
 welcome to the ‘abnormal response center’, a special organization under the ministry of public administration and security of the republic of korea.
”he, who was combing his hair straight, was wearing a bow tie on his tuxedo.
unsuitable for this place, he had an aura like the son of a nobleman.
“who are you?” sungwoo asked.
“i will escort you, necromancer,” he said in a gentle tone that wasn’t appropriate for his age.
 however, sungwoo raised the repeating crossbow.
 he had no reason to refrain from firing an arrow just because the other party was a child.

“escort me? don’t you think you are playing a dirty trick on me so blatantly?”“yes.
 because you are so powerful, they sent me to try to persuade you,” he said with a smile.
only then was sungwoo convinced that he was not a child.
he only looked like a child.
‘if that’s the case, this guy must be…’sungwoo realized that he was doctor, obviously one of the clones in this core facility.
at first glance, he looked like the previous clone a lot.
that meant sungwoo had finally reached the heart of the core facility where dr.
 yu was located.
so, sungwoo was sharply alert.
‘i should not be outwitted by this guy.
’sungwoo has always won the fight against this man, but he has always come up with an unexpected card.
 so, sungwoo knew if he let down his guard carelessly, he could fall into a trap set by this guy.
so, sungwoo secretly summoned “spector”.
“did you say it was the government?”“that’s right.
”sungwoo showed a willingness to talk with him a little more.
 then, he smiled brightly.
“do you want to say you are the government?”“i belonged to the government.
 i was a member of the abnormal response center, also known as ‘s·p·r·c’, one of the research institutes under the ministry of public administration and security.
”the guy opened the door, and he beckoned to sungwoo and minsok to come politely.
so, they entered the door and stepped into a white corridor.
“the government was predicting this situation on its own.
 they found out that some external forces were trying to engage and control the earth.
”that was pretty surprising.
 did they also know in advance that the world was turning into a game?“but the government didn’t help you at all, right? after this incident, the government disappeared without a trace.
 they just collapsed even without withstanding the first half of this game,” sungwoo said.
“that’s right.
 only the working-level researchers of s·p·r·c believed that and gave a warning, but the high-ranking government ministries with money and authority didn’t want to believe such a warning.
 the world turning into a game? which politician would trust the findings of such a study?”thump- thump-the three walked along a white corridor lit by led lights.
 they saw a white door at the end.
“on the day the game started, dr.
 hee-seung yu, the head of the center, and the researchers under him responded.
 at the same time the game started, they selected 4,000 survivors and evacuated them to this facility, and by creating an independent system, they started preparing for the future.
”hee-seung yu was the real name of “dr.
 yu,” the head of the evolution society.
 this meant he already knew the world was going to change like this even before the game started.
“what do you mean you prepared something?”“well, instead of rebuilding a lost republic of korea by an incompetent government, we were planning and implementing a plan to satisfy the ultimate purpose of this incident.
”sungwoo knew what the plan was.
 he recalled what he heard when he first met doctor in a secret facility underneath beomgye station.
“ultimate purpose? is it the new race, or the transcendence that you are talking about?”the boy smiled brightly when sungwoo asked as if they were talking about his favorite manga plot.
 nodding at sungwoo, he took delight in his reply.
“that’s right! dr.
 yu, just like others, drew two cards according to the system.
 the first card was “mad scientist.
” the second card was “the archbishop.
” as a result, the two cards in pursuit of the truth created synergy, and as such he got closer to the ‘correct answer’ before anyone else.
”“correct answer?”“in dr.
 yu’s eyes, this game is sort of a test.
 it’s a test that a certain being has given to judge the worth of humans.
”the guy got more excited and started talking more.


“so, we studied how to pass the test.
 haha! i mean the way to break away from the classic form of humanity and move on to becoming a bigger being! that’s why we were studying ‘death’, the biggest challenge that humans could not solve.
 necromancer, you can be of great help in that research.
 would you like to talk with us in more detail? maybe you might understand us…”“you’re wrong.
”sungwoo threw cold water over his offer.
 at that moment his face hardened.
“pardon?”then, the guy stopped suddenly in the middle of the hallway.
sungwoo looked down at him and chuckled.
“well, that transcendental being may be looking down on us, but this is not a test for us.
”sungwoo fiddled with the scales of the imoogi in his pocket.
-off air (-)did something more important than sungwoo happen? the unidentified gaze was not directed at sungwoo at the moment.
so, sungwoo slowly opened his mouth more comfortably.
“this is nothing other than their entertainment.
”sungwoo shot back at him more harshly, who could not even respond.
“and you guys are playing a stupid, fanatical villain with vain thoughts!”the guy made a long face but responded cynically.
“oh, how rude of you to express your intent so clearly that you won’t agree with our cause!”“really? well, i’m going to be ruder in the future.
 i won’t forgive you guys then.
”“sure…” then the guy stepped aside and raised his right hand and waved it lightly.
“goodbye!”

 