\section{chapter 381}

chapter 381: hephaestus’ forge (5)sungwoo had no idea why he used such an expression, but hearst was smiling at him.





it seemed that hearst looked pretty proud to have a huge number of airships behind their back that would make the players of the world tree camp open their eyes wide in pleasant surprise.
“thanks to your investment, we doubled it!”“of course, you should!”hearst opened his hands, then continued, “well, last time you were crazy about collecting my items at the workshop as if you raked in shopping items on black friday, so i’ve prepared some more this time.
 how about my present?”the us server has been peaceful for a while, so hearst’s workplace seemed pretty busy producing new powerful weapons and other items by mobilizing a huge number of craftsmen.
the huge fleet could not be seen at a glance, and sungwoo turned his head all the way to see all of the airships.
 there were as many as 30 airships that could be mobilized for war.
and when they integrated as part of sungwoo’s one team, a message appeared.
- ‘synergy effect’ is given due to your team play.
[synergy list][ol start=”3-]invincible fleet- category: vehicle synergy- condition: 30 or more large airships- effect: increases fleet flight speed (+30%), increases flight acceleration (+10%), strengthens airship shield (+30%), opens a ‘jump gate’ that allows only the flagship to move a certain distance (100km).
 (cooldown: 24 hours)since the airship was also a kind of item, synergy was activated as it increased in number.
 the fleet power of the world tree camp increased drastically.

moments later, jonathan and hearst descended to the ground.
“did you see that synergy? i didn’t expect that kind of stuff would come out.
”it seemed that hearst didn’t expect such a synergy at all.
 he giggled with a conceited expression, then said, “you probably won’t be able to pay off your indebtedness to me for the rest of your life.
”of course, he was kidding, but sungwoo shook his head because he didn’t accept hearst’s joke.
sungwoo said, “well, you’ll have to take back what you just said to me.
”when sungwoo spoke confidently, hearst’s eyebrows twitched because he annoyed the stubborn old man.
“uh? what did you say?”“well, i’ve got something that would make you have no choice but to thank me.
”like he said, sungwoo had something in his hands that would put this stubborn dotard’s nose out of joint.
sungwoo asked, “do you know the power of hephaestus by any chance?”hearst’s eyebrows twitched as soon as he heard the word ‘hephaestus,’ and his eyes lit up with embarrassment.
after all, it’s impossible that this five-star blacksmith hadn’t heard of the name hephaestus.
and, perhaps, he might have already come close to hephaestus’s ‘divine power.
’ since he was a blacksmith better than anyone else, it was natural that heart obtained such capabilities by now.
 he nodded slowly.
sungwoo said, “then, follow me.
”“sure.
”
sungwoo didn’t know why arnold hearst, who was more stubborn than anybody else, came here, but sungwoo didn’t want to waste such a talented blacksmith as heart who came here voluntarily.
 mobilizing all the available talented people for national development was the driving force of the korean-style rapid growth, after all.
hearst frowned, standing before the old box.
 then he turned his head to sungwoo.
“what is this?”“just open it.
”he scratched his chin with a questionable expression.
“i hope you are not trying to make fun of this old man who has come from a distance, right? then, i won’t be able to forgive you even if our background is different.
”he couldn’t hide his surprise when sungwoo uttered the name hephaestus.
however, he seemed to have doubts when he found the plain old box contrary to what he expected after he was startled by sungwoo’s mention of hephaestus.
“master hearst, isn’t technology inside the box, not its appearance, the most important?”“yeah, that’s right.
”as if he understood sungwoo’s remarks, he slowly reached out with a more generous expression and placed his palms on the box.
the next moment, he opened his eyes wide and he began to look around.
“uh? this one…”the forge of hephaestus appeared after it overlapped with a forge in the real world.
“if you choose y, you can enter the space completely,” sungwoo said.
as soon as he heard it, hearst stretched out his finger in the air, and his body disappeared.
 he entered into the sub-space.
 sungwoo also followed him into the forge of hephaestus.
whoooooooooooo-when sungwoo arrived in the hallway, hearst was already in front of a huge brazier at the end of the hallway, with his hand on the anvil.
“oh, i can’t believe this…”he couldn’t help but admire, then he was pressing here and there while gazing into the air.
“oh my god! i just can’t believe how this is so easy!”although it was invisible to sungwoo, quite a lot of messages were coming out.
sungwoo stood next to hearst and placed his hand on the anvil.
- if you use ‘hephaestus’s anvil’, your ‘success chance’ and ‘additional effect chance’ are greatly increased.
 also, its base durability increases by 300%.
but what sungwoo got was this very short message.
“it looks like you saw something different from me right?”hearst kept nodding, but he didn’t pay any attention to him.
“really? well, i think that’s natural.
 when i touch any anvil, i see something completely different from what other players see.
 that is one of the traits of my job.
”those in the blacksmith profession seemed to have a unique option in the general blacksmith’s anvil.
 since hearst was a five-star blacksmith, he would be able to manipulate many more various functions.
“by the way, it’s more like a shock to me as if i was shocked at the arrival of windows 95 that replaced an old 8-bit computer.
”

hearst was so excited that he could not breathe properly.
“there is a separate manual for making legendary-grade equipment, plus all kinds of special effects.
 oh my god, i can make all kinds of producing mediums that i had to obtain by hunting until now! this alone will increase my productivity several times, or more precisely, tens of times.
”hearst admired it over and over then began to manufacture something sungwoo could not see at all.
 it was like a scientist facing the ultra-high technology of an alien civilization.
several minutes passed.
 after checking all the features of his new production once, hearst finally turned his head and looked at sungwoo.
“well, like you said, i can’t help but confess to you.
 to be honest…” then, hearst held out his hand to sungwoo and said, “thank you.
”nodding at him, sungwoo grabbed his hand.
hearst continued, “yeah, i admit that this is the reward for which i won’t regret giving you several airships.
 and the effect of the increased productivity of the world tree is enormous, and if i really study here, i might complete my divine capabilities.
”“divine capabilities? what is it?”hearst said, shrugging, “i don’t know yet.
 i guess one of the blacksmith’s gods will appear, but i don’t know right now.
 besides, it will depend on what you complete out of many conditions…”he took a cigar out of his pocket, then put it back in after hesitating a bit.
it seemed to him that this space felt so special as to make him stop lighting a cigar.
“um, i would like to ask you a favor.
 can i bring some of the staff from my workshop and study with them here? of course, we will hand over all the items we make to you.
”how could sungwoo decline such an offer even when he didn’t yet offer to hire hearst’s staff?sungwoo immediately held out his hands to welcome his offer, and hearst quickly grabbed his hands.
“sure, if you can do it, i welcome it!”“man, you never miss a great opportunity that comes along!”a good facility was supposed to draw lots of talented men.


 