\section{chapter 467}

jisu was not interested in her level.





'i didn't think of it as important because i felt one's level or ranking was just a number.
.
.
'one's ranking, or more precisely, one's level could be a measure of one's strength, but it was not an absolute standard to measure one's strength.
the only thing that mattered was one's survival and victory, so one's level was just a reward that came with it in her opinion.
 so she thought she didn't have to chase monsters desperately to level up.
but she had never thought that her current level, just one level short of level 25, the condition for having multiple divine powers, stood in her way.
 'i need that level right now.
'she needed to use two divine powers right now.
 to do that, she had to reach level 25 right away.
khhhhhhhhhhhe!while she was agonizing over it, the hell creatures charged at her from all directions.
but she kept beheading them.
 she wished they could turn into her exp, but she shook her head because they were not enough to make her level up.
 'gosh, i won't be able to reach level 25 if i keep killing these low-grade monsters!'she had no time.
 she needed to find a way to level up quickly.
 she turned her head and looked around.
then, as soon as she saw the multitude of players in the back, she suddenly thought of one thing.
 'alright, i've found it!'she immediately went to see kyungsoo.
"kyungsoo!"he was absorbed into controlling the troops in the rear, but he turned his head, watching her approach her.
 he realized that she had some important business when she came to him.
"i know you are quite busy, but just do me a favor.
"
"sure, please.
 i'll do it for you!"he was doing his best to assist in the allies' combat.
 it was his job to help those fighting at the frontline to win.
"please get me some exp cards.
 i need several, not just one.
"the exp card was an item that raised one's exp, which nobody could obtain in a normal way.
 but she thought that somebody among these hundreds of thousands of players gathered here, or some elite players around the world here must have the item.
"exp cards?""is it difficult for you to get them?"he has been mulling over for a long time how to control a large number of players, so he created a 'general control room' for that purpose.
 he could keep complete control of them through this mechanism.
 so it would not be easy for him to find exp cards by checking every one of them.
"no problem! i can find them for you quickly.
"it was a matter of time.
***- you receive a 'synergy effect' due to your team play.
sungwoo was puzzled by that message that appeared before his eyes.
 'what happened all of a sudden?'even though he didn't do anything, he got one synergy effect all of a sudden.
 [synergy list]information: death adjusters (hidden)- category: job synergy- condition: 5 or more users of 'lich' level death magic
- effect: you can upgrade to the exclusive skill 'ultimate' (1 random type), and obtain the special skill 'power of the four knights of apocalypse (enhanced)'.
'five lich people?'it meant the birth of the fifth lich.
as a result, the synergy of 'apocalypse appearance' was changed to 'death adjusters', and the 'power of the four knights of apocalypse' skill seemed to have been upgraded.
[skill information]- name: power of the four knights of apocalypse (enhanced)- grade: transcendence- classification: passive- consumption : -as long as the 'death adjusters' synergy lasts, the following 'additional effects' are given for 70 minutes.
1) power of war (enhancement): you can summon the 'apocalypse army' sealed in the abyss and acquire 'command power'.
+ depending on your enhanced capabilities, you can summon all armies at the same time without any restrictions.
2) power of famine (reinforcement): you create a 'death land' connected to the abyss within a certain area (10km).
+ you summon the 'tower of death' at the center of death land, depending on your enhanced abilities.
3) power of plague (enhance): the effect of area damage magic and curse magic increase significantly.
 (+400%)+ depending on your enhanced ability, 'death bugs' will come from the enemy's corpses and attack the enemy.
 (10 per each corpse)4) power of death (enhanced): you gain strength from the corpses around you.
 (all skill effects +1% per death)+ depending on your enhanced capabilities, your subordinate spirits per death increase by 1.
an additional effect was added to sungwoo's existing skills.
 however, this was not just added but seemed to have been enhanced by a double.
'i have no idea what happened…'since he couldn't figure out what's going on outside, he could not know the reason.
but he stopped thinking about it, and hurriedly crawled out of the pit.
"kheeeeeeek.
.
.
necromancer!"at that moment somebody called him.
 next to one hippogriff that was torn apart was a member of the special commando unit, gasping for breath.
"almost all of us were annihilated by the demon king…"he died as soon as he said that.
 there were bodies strewn all around him.
they were hippogriffs and the members of the special commando unit.
 since they were floating in the sky, they could not take any action to protect themselves, so they were fully exposed to the red lightning generated by the demon king.
 sungwoo looked around.
the damage caused by the demon king's aoe skill 'evil harmagedon' was more serious than expected.
 thousands of lightning bolts from the red clouds devastated almost everything on the ground.
'nearly everything was destroyed by the demon king's single attack.
'eleven airships were destroyed after crashing, and nearly all hippogriffs were smashed by lightning.
 their feathers and blood were scattered everywhere.
 and the vast space here was reduced to ashes.
 the ground was overturned, and trees were broken, then entangled with each other to create a bizarre maze everywhere.
 kheeeeeeeeee-the hell creatures were crawling from the maze and hunting the survivors.
"argh! help!"screams were heard from all directions.
 

but this was the beginning of the problem.
 one's suffering typically doesn't start when one is in trouble, but after one's trouble is over.
 and that's the case with sungwoo's allies.
 - the 'demon king's territory' was created in the aftermath of 'harmagedon of evil'.
* the area destroyed by the 'harmagedon of evil' becomes the demon king's territory for 20 minutes.
 of course, that was bad news.
the harmagedon of evil had the effect of not only destroying the whole area but also making the whole area into the demon king's territory.
 "this is going to be a big problem…"sungwoo used his summoning skill just in case.
- this space is a 'divine territory' governed by a 'specific divine power'.
 you can't use any other divine power here.
as expected, he could not use his skills that dealt with space, such as summoning his subordinate spirits.
this was a complete disappointment for him.
 even though he obtained the hidden skill 'death adjuster', he couldn't use it because this place was the demon king's territory.
'let me move anyway.
'he was not completely defenseless because he could handle the subordinate spirits he had already summoned.
 he resurrected the undead army.
 the bones that had been scattered around stood up again.
rattle! rattle! rattle!he led about a hundred of them to get rid of the hell creatures and rescued the few remaining survivors as much as possible.
 when he advanced for about ten minutes, he could see junghoon in the distance.
"hold out until the rescue team arrives! fire!"he was fighting hard with the special commando unit of about 20 men.
but most of them seemed severely wounded.
 to make matters worse, they were in a dangerous situation where they were surrounded by the hell creatures that kept coming from the ruins on the ground.
rattle! rattle!

 