\section{chapter 173}

                             




kyongsu and inho were carrying out the necessary job with a sense of responsibility.
 while sungwoo was away, they were taking care of the survival groups in suwon and playing a new leadership role.
“captain, i don’t think there are any new monsters nearby.
”also, the former biker gang members such as taesung and yujin regularly patrolled the village and its surrounding area.
“well, there are still goblins hiding in the mall and kobolds crawling out of the basement, but it seems that direwolf is almost gone…”while managing stores in suwon station, they kept acquiring various items, among which were two magic drones, an important surveillance tool, and seven radio items.
they cleared the vehicles left unattended on the roads.
finally, they made sure all the players should sign a “vault of oath” to raise funds to run the facilities.
[item information]-name: vault of oath-grade: special-category: finance-effect: some of the gold earned by the ‘contracted players’ is automatically deposited.
-description: you can ‘register a contract’ by placing your palm on the safe.
 the vault owner can set a ‘collection rate’, and the amount of gold earned by the contractor is automatically deposited into the vault.
* collection rate: 10%* registered contractors: 226 people* current gold: 1,655,048“it looks like their living environment is getting better, although we can’t enjoy it because we keep moving around outside suwon all the time,” said hanho, looking around the village.
now, the suwon village was no longer a temporary shelter, but it was growing as a large community towards their common fate.

sungwoo stood at the center of the huge flower bed.
the time had come for him to plant the seed of the world tree.
 the villagers lined up around him and watched.
sungwoo pulled out the seed of the world tree.
 that small object shone so brightly that it was difficult to describe.
 then, a little sigh came out of the villagers.
“that’s the world tree?”“wow, i feel it’s different from typical seeds.
”sungwoo put the seed in a small hole and carefully covered the soil.
soon, golden light started to soar into the sky, and sungwoo slowly stepped back.
-you have planted the seed of the world tree (shindansu).
-a spiritual being begins to take root in this land.
[hidden quest]-title: for the spiritual tree-type: protection of goal-goal: protect the world tree until it grows to a certain size.
-reward: first fruit, permanent buffs*it is a world tree, a transcendental being, but its sprouts are still helpless.
 that is why the monsters who have sensed the existence of the world tree will come to this place in droves to covet its spirituality and nobility.
 defend the tree by all means until it grows enough to protect itself.
* the world tree can take monsters as its nutrients.
 the more monsters you defeat, the faster the world tree grows.
* if the target (world tree) is destroyed, it causes irreparable disaster.
as expected, nothing was easy.
 the world tree was not just something that sungwoo could raise by simply planting it in a sunny place and giving it water.

-this quest applies to party players in the same way.
 (total 226 people)“so, we also should protect the world tree?”“what the heck? does it mean that the monsters are rushing toward us now?”and everyone who witnessed this scene, and the players in the village, were also given the same quest.
 it meant that the level of the difficulty of this quest was very high.
‘something changed a moment ago.
’sungwoo looked around, standing on the flower bed.
 although he was not sure, the atmosphere in the area was very serious.
he felt as if some terrible energy was coming to this place.
 his foresight was almost right.
“look over there!”on the rooftop watchtower on a nearby shopping mall, the security guards began to move busily.
 it was an ominous sign.
 and one of them shouted to the square.
“monsters are popping up from the 3 o’clock position!”the security guards on the lookout tower on the other side also seemed to catch some unusual movement.
“the kobolds are crawling out of the sewer on the road!”“a lot of them, not just one or two!”an unexpected defense game began.
“everyone, move!”the players of the village achieved level 8 on average, so they already had significant combat experiences.
 the days when they were so incompetent they had to rely on sungwoo for survival were gone a long time ago.
“snipers, go to your assigned watchtower!”when inho shouted, those carrying long-range weapons moved quickly.
as if they had lots of practice for contingencies like this, they scattered in an organized way and went up to the roof of the building.
“tanks! bring the barricades!”the buses parked at the back of the square moved, and their appearance was unusual.
on one side, thick sheets of steel were welded to the buses to defend against outside attacks, while the other side was completely open.
“it’s called a castle wall car.
 when we line up the buses, we can defend a large area,” kyongsu explained.
as the rebuilt buses lined up with the sides attached with iron plates facing toward the enemy, they became like a castle wall.
“spearmen and shooters, get on the buses!”they could freely respond to the enemy’s assault by coming and going freely through the opposite side of the open holes of the buses.
 they could also climb onto the ceiling of the bus by using the ladders.
 they produced various weapons for defensive purposes like this.
“what a great strategy! whose idea was this?” asked hanho in admiration.
“there are many talents in the village.
 as you know, we have been forbidden to go outside for a while after the youngdungpo terror.
 so, while we were confined here, we devised lots of stuff to defend against attackers.
”thanks to such thorough preparation, the monsters could not attack the players directly, let alone approach the sprout of the world tree.
“goblins are coming! sweep them away with aoe magic!”“kobolds have appeared in the 1 o’clock position!”the monsters around the village had been completely swept away a long time ago.
at best, only some goblins and kobolds were hiding in the underground, so even if they were rushing toward them, there was no way their defensive line could fall.
sungwoo summoned 27 undead to help the village players, but that’s all.
 since the players were strong enough, sungwoo didn’t have to mobilize any more of his forces, but a problem was growing elsewhere.
“wow, can you see him in the picture? the necromancer is right here! when he first met the youngdungpo prosecutor, this was the place in the picture where the two shook hands.
”three players hiding in an alley were filming something somewhere.
 numerous monsters were rushing toward where their cameras were directed.
 of course, it was the suwon village.


“suddenly, the monsters just rushed in, and a battle broke out! what the hell is going on?”they were conducting a personal broadcast titled “chasing the necromancer.
”“i don’t know, but it seems like the necromancer is hunting without stopping.
 gosh, that’s why he is confronting the absolute race.
 honestly, i admit he is cool.
”“i admit, too.
 but i also admit i chose the no.
 1 option of killing the necromancer because i didn’t know.
”at first, there were only about a hundred viewers, but soon after the news about the necromancer was captured on the screen, a significant number of viewers began to watch the broadcast.
then, the hosts got excited and started to raise their voices.
“after the absolute race put up a huge bounty for the necromancer, those who said they would hunt the necromancer mushroomed everywhere throughout the server, right?”“yes.
 let me tell you something.
 the necromancer is right here.
 why don’t you come and challenge him?”they went up to the roof of a building and captured more details of the necromancer and the suwon village on the screen.
“look over there! he is the necromancer!”shouting like that, they captured and zoomed in on a certain place where the necromancer was standing on a heap of earth.
“pardon? why are you guys urging me to fight him like this? i didn’t say i’d kill the necromancer.
”“right! we have just found the place where the necromancer disappeared.
 it’s up to you, self-proclaimed necromancer slayers, what to do with him.
”a little later three ghouls under the control of the necromancer appeared on the roof.
right after that, the broadcast was suddenly stopped.
“uh? what the heck is that!”“they’ve come!”“sorry, we have just…”

 