\section{chapter 313}

"when i try to behead that guy, he is definitely going to resist violently.
 so, if the priests pray for me at that moment, i think i can get stronger," said the russian tsar.





"ah, really?""yeah.
 so, if you can, send me open-minded young female priests.
"general xing put a grape into his mouth and looked into the air.
 he was lost in thought.
".
.
.
well, that sounds like a simple but very good idea.
""you agree, right?"general xing was also aware of the fight between boris and the necromancer in seoul.
at that time, boris attacked the necromancer in a simple and ignorant way.
'according to the informant, it was a neck-and-neck fight…'if the guy ranked no.
 1 on the korean server had not appeared, the necromancer might not have won.
 then, what if boris was buffed with the priest's blessings?'if he could penetrate the wolf pack's attack and grab the wolf's head like a brown bear, that would be the most certain way to kill him.
'general xing thought that with the priests' blessings, the strong russian tsar would be much stronger.
 he would be able to break through the winds of the enemy's army and curse to get rid of the necromancer.
"alright, boris, kill the necromancer! we're going to get rid of the rest of the korean server players.
"general xing stood up.
 then, miyamoto raised his left hand and opened his mouth.
"what about your emperor? doesn't he go to war?"general xing said with a hearty laugh, "haha, the chinese army is strong.
 this war will be easier than you think.
 it is not for our emperor to participate in this minor war in person.
"
there was confidence overflowing on the general's face.
***14 hours before the start of the war, a huge number of players gathered at the entrance to the suwon village, the home of the world tree camp.
"oh, my god! what is that?"the guards on the castle wall could not help but be embarrassed when they looked down at the huge army in the village.
 "all of them are our allies, right?""i guess so.
 well, i'm still confused because our troops are small all the time.
"before the world was ruined, they could easily find such a huge army, but it was the first time such a huge army gathered since the world tree camp was founded.
"man, i've never seen so many people making such a big noise like this before.
""yeah, humans are noisy animals.
"not only were the players from all over the korean servers, but also 3,000 reinforcements from the taiwanese server joined together, so over 9,000 troops gathered in one place.
because of that, it was inevitable that they made so much noise, even though they were asked to keep quiet.
"let's fight! we are ready to fight!""bring it on, chinese bastards!""why are they not letting us in?"in fact, the place where they gathered was like a noisy market.

since they were not allowed to enter the village, they camped in front of the invisible barriers and castle walls.
 when seen from a distance, it looked like they were engaged in a fight involving flying weapons.
faced with such a huge army from all over the place, kyungsoo and the "general affairs team," who was in charge of controlling the situation, were really frustrated.
 "gosh, it looks like they number over 10,000.
 but there are more coming in from everywhere.
""what's more, they have brought in dozens of tons of war supplies.
 i can't check them out one by one.
"kyungsoo handled the matter calmly amid such confusion.
"this war won't take long, so we don't need war supplies.
 so, you don't have to bring their war supplies into the village.
 just stack them in a nearby building without checking.
"the general affairs team checked all personal belongings because they could not rule out the possibility that spies were among the unidentified volunteers.
"you have to verify your identity!""please take out your cell phone!"since what they said was automatically translated into their vernacular language, it was difficult to identify foreigners through conversation.
 so, checking that their smartphones connected to the korean server was the surest way.
"i'm sorry, but if you don't have a mobile phone, you can't be here because we can't verify your affiliation with the korean server.
 you have to follow our guides to go to other locations!"since this was a big task that the world tree camp could not handle alone, the admin office of the liberation guild took over.
 meanwhile, the leaders of each group gathered to hold a strategy meeting inside the castle.
"they are much more than any other army gathered on the korean server so far, but i'm worried about how to manage them.
 if a problem arises, they are going to turn into a bunch of sheep," junghoon said.
 then sungwoo said, "yes, that's correct.
 and not all of them can fight.
 you have to thoroughly classify them according to their fighting abilities during the remaining time, so you can send those who are not competent to the rear.
"although these volunteers' action was commendable, sungwoo felt he needed to judge their abilities coldly.
"inexperienced fighters could lose not only their lives but also cause great damage to our operation.
""then, we'll have to add checkpoints to classify them.
 let me tell them to check incoming volunteers according to their level, skills, and equipment.
"a large number of small and medium-sized survivors came to the village, but still, the big forces were usually strong players from big groups because they were verified and elite troops.
 leaders of each force then briefed sungwoo about the status of their forces.
 inho collected all the information about them and created a 'military status board'.
"now, this is the statistics of the military forces that we can trust and use in reality, except for the independents and unidentified persons.
 the liberation guild has 1,441 troops, uijeongbu and paju allied forces have 753, hunter company has 211, hwarang guild has 1,266, southern union has 401, but the taiwanese server…"surprisingly, it was the players of the taiwan server who led the most troops.
"the taiwanese server has 3,021.
"everyone's eyes turned to chen, the "server master" of the taiwanese server.
 he nodded with a cool expression.
 he looked much more confident than when sungwoo first met him at the pirates' dungeon many years ago.
"i may look arrogant, but we have come here to pay back our debt to you.
"when sungwoo defeated the "red revolutionary army '' in taiwan and freed the taiwan server, chen said that he would contact sungwoo someday with the promise that he would make his forces strong enough to satisfy sungwoo.
 finally, chen kept his promise.
"necromancer freed our server.
 since then, we have been able to unite firmly as one.
"there was no division among them because they were once ruled by the red revolutionary army.
 the taiwanese server united into a single powerful organization and developed rapidly, shaking off the shock of their colonization.
 "well, we're not yet strong, but i'm glad we can be helpful to the necromancer and the korean server.
"sungwoo nodded and chen smiled proudly.
 

taiwan was also an unexpected hope for sungwoo.
 "alright.
 let's discuss the important issue again.
 we've got less than 12 hours now.
"they contemplated the most efficient way to divide the troops into three, based on the status of the overall forces.
"because the suwon area has the invisible barrier and castle wall, can our forces hold out for a long time even if we don't dispatch a large number of troops? how about joining them after we win on other battlefields first?""hmm, the enemy might aim at that.
 since this is the most important place, we have to think about the possibility of deploying a large number of troops to prepare for their attack.
 even if other places are occupied by the enemy, and if we lose even suwon…""by the way, would it be better to divide the world tree fleet? or should we concentrate them in one place? i don't know what to do because i don't know how the enemy will attack us.
"no matter how hard they racked their brains to solve the problem, they could not.
 but the moment they had only 12 hours, 00 minutes, and 00 seconds left until the war, a message rang.
 -soon, 'battlefield placement (cross selection)' starts.
"man, it's already begun…"-first choice (korean server) "yes.
 now we don't have any more time to think about it.
 whatever it is, we have to use our first option.
"a map of the korean peninsula emerged in front of sungwoo.
 three dots flashed on the map.
seoul, suwon, busansungwoo stretched his finger toward the map.
the opening of the war game has begun.


 