\section{chapter 205}

                            then, the serpent raised itself and began to crush everything around it.





bang! bang!jisu and hanho were very nervous at that terrific scene.
“what the heck is this? do we have to fight again?”“no, stay still.
”the serpent was manipulating the traces of the battle to deceive the eyes of the returning “creator”, for it should not be caught stopping the fight while their surveillance was cut off.
“sungwoo, can you explain what the heck this is? when did you become friends with such reptiles? you guys even know each other’s names, too.
 tell me!”although they witnessed the same situation, jisu and hanho did not seem to understand it easily.
 the hint that the giant serpent gave him was so abstract that even he could not figure out exactly what was going on right now.
‘what’s certain at this point is that we need to avoid the eyes of this guy called ‘creator’ who will be back soon.
’while the serpent devastated everything around them, sungwoo looked at jisu and hanho.
“listen to me carefully.
 i don’t have time to explain to you right now.
 when the recovery work in front of you is complete, you have to pretend to fight the serpent again.
”“what are you talking about?”“listen to me.
 i think i can explain to you later, though i’m not that certain.
”jisu nodded at sungwoo’s remarks.
 hanho, too, scratching his head as if he was frustrated, immediately sent a signal that he understood.
as expected, the two were blindly following sungwoo, no matter what.
the serpent continued, “okay, now is the beginning.
 sungwoo yu, kill me and survive to the end.
 bring this system down and take back your world.
”-the system is under emergency recovery.
 (99%)at that moment, sungwoo jumped off the ground.
 the serpent also moved the goblin flame to pursue sungwoo.
 they engaged in real fighting without any hesitation.
in order not to invite any suspicion from the ‘creator,’ the serpent was attacking sungwoo ruthlessly.
‘if i’m hit by that attack, i’ll be killed!’sungwoo ran towards the cliff then threw himself.
the moment he fell, a bone wyvern soared from the bottom of the cliff.
 sungwoo flew up while hanging on the bone wyvern, but the serpent stretched out its head to attack him.
kaaaaaaaaaaah!‘this guy deliberately stretched back.
’
it was an obvious signal that sungwoo should attack its soft spot, namely the wall behind.
sungwoo was already ready for that attack.
while the serpent moved slightly forward, two zombie birds glided in the dark and quickly entered the space behind its back.
puck! puck! puck!then, they began to dig up into the wall with their claws that the serpent had already scraped once.
 the serpent crushed the two zombie birds with its head and dropped them.
“alright.
 that’s your soft spot, right?”sungwoo noticed it before this fight, but he pretended to have noticed it only now because he was aware the ‘creator’ was watching him somewhere.
sungwoo swung the grim reaper, loaded with the evil spirit bomb.
 four black spheres were fired in a straight line at its head.
goong-go-go-goong!a magic circle with a five-bang color pattern floated above its head and blocked the evil spirit bomb without any difficulty.
‘after all, it’s useless to attack the serpent.
’but it was sungwoo’s tactic to block the vision of the serpent.
sungwoo dispatched the bone wyvern to collide with it head-on.
bang!however, just before the collision, two goblin flames flew in and smashed the wyvern’s head to pieces.
 with the bone wyvern’s smashed bones falling, sungwoo was floating in the air.
however, even that was nothing but trickery.
rattle- rattle-suddenly, orun was hanging on the wall with his knife stuck into it.
 a very suspicious triangle was drawn on the wall he was clinging to, which the giant serpent tried to protect.
orun instantly lifted his hand, biting the hilt, and drew a hand cannon with his right hand.
 he pulled the trigger.
bang!since the crack had already occurred in the wall, orun could destroy the outer wall with a single shot.
“that’s it!”a small cavern was inside the wall.
 there was a gold rope made of twisted threads, along with an ocher pot inside the cavern.
that was the serpent’s greatest weakness.

“break it!”at that moment, the serpent pretended to move its body in a hurry.
 however, it was too late.
orun already hit his head against the pot.
 the jar was shattered in an instant as if it had no protective shield.
-‘the precious jar’ of the 1st python has been destroyed.
* the python has lost all magical powers.
kaaaaaaah!along with that message, the blue energy began to escape from the serpent’s body.
 the goblin flames munching through the vast space disappeared from the air.
kaaaaaaaah!the serpent roared in anger, wiggling its body.
 and it was a sign that the tide was turned.
“if you can’t use magic, you are nothing but a giant snake, right?”the giant serpent, which could not use magic, had the same strength as drake.
in other words, it was not sungwoo’s difficult opponent anymore.
based on his promise to the serpent, sungwoo intensified the attack to kill it.
now, all ranged attacks by the undead troops paid off, breaking its scales.
kaaaaaaaaaaah!the serpent twisted its body and swung its head as if resisting to the end, but it already knew its final moment from the beginning.
eventually, minsok, who got on top of its head, stuck his great sword into its forehead.
-you have earned 11,550,000 gold by hunting the boss monster ‘1st python’.
-time remaining until full credentials: 1,030 days-the title of ‘amateur dragon hunter’ has been upgraded (replaced) to ‘professional dragon hunter’.
* increases stamina (+6)* increases muscle strength (+3)* increases fire immunity (+40%)* increases magic resistance (+10%)the serpent’s head slowly tilted toward sungwoo.
 the light of both eyes, which was burning intensely, also gradually faded.
 with that look, it seemed to be asking sungwoo for something.
‘what the hell is the truth of this game…?’following the serpent’s advice, sungwoo began to look for the inverted scales on his body.
he found it on the back of his neck.
sungwoo naturally scraped it so that his action did not look strange.
[item information]-name: null-grade: null-category: null-effect: null‘what the heck is this?’no information was displayed.
 ‘null’ meant there was nothing.
but at that moment, a message rang.
-on air (!)on air, now broadcasting?the scales of the serpent issued such a message.
sungwoo now realized that the ‘creator’ that the serpent referred to was now watching this place.
‘if so, is this message invisible to the creator?’he didn’t know how it was possible to avoid the eyes of the being in charge of the system, but the being must have such a function.
‘i have no idea what’s going on now…’the creator and the other one like the creator but with different ideas: who the hell are they?and why are they playing this game?there were so many things sungwoo couldn’t know yet.


since the creator said that he would return to him someday, sungwoo would have no choice but to wait.
-in the war quest , the ‘third camp (temporary)’ has won!* rewards are given to its leader.
 (5 legendary grade item boxes)-prize money is given to the winning camp.
 (third camp)* 1% of total bet amount: 4,086,570 gold-winner prediction dividends are paid.
* third camp dividend: 296,954,695 (73.
4%)sungwoo received a whopping 300 million gold at once.
after the quest completion message and the reward message came out, light began to pour from the sky as the cave vibrated.
gung-gu gu gu-“uh, look over there! the ceiling is being opened!”mt.
 pukhan, which had been covered with caves and trees, was recovering its original shape.
“hahaha! now, shall we look at the other guys? now, it’s clear which camp is winning.
 are there any fools who are still trying to choose between the angel camp and the demon camp?”as expected, hanho, who got a windfall, shouted proudly.
it was the moment when the third camp took all the profits and proved that they were the strongest group of the korean server.
but sungwoo didn’t let down his guard.
‘are these guys in trouble really going to give up?’the war quest was over.
 if so, the “pk prohibited area” on mt.
 pukhan would also have been lifted, logically speaking.
‘i don’t think so.
’maybe, the other camps wouldn’t give up easily because they must have realized that if they left the third camp as it was now, they could not suppress the third camp’s growth.
it was highly likely that their enemies would grab the necromancer’s pants and bite his neck.
‘if that’s the case, let me get rid of them.
’to overthrow the system, sungwoo needed to reach the level at which he could control the world they created.
‘the first target is the korean server.
’

 