\section{chapter 181}

                             




[item information]-name: vault of oath-grade: special-category: finance-effect: some of the gold earned by the ‘contracted player’ is automatically deposited.
-description: you can ‘sign a contract’ by placing your palm on the safe.
 the vault owner can set a ‘collection rate’, and the amount of gold earned by the contractor is automatically deposited into the vault.
* collection rate: 10%* registered contractors: 226 people* current gold: 5,155,048“this is the safe that you contracted last time, right?” inho asked.
“yes, that’s right.
 since you have signed the contract, 10% of the gold earned so far has been accumulated.
 you can use it to fund the village’s operation,” said sungwoo.
since sungwoo has been hunting the monsters aiming for the world tree, a huge amount of gold has been accumulated in the safe.
sungwoo had the intention of using the gold he earned for personal purposes, namely something like a protection fee.
 however, it was right for him to invest it in the village right now.
“okay.
 for now, we have enough items such as batteries and ‘drinking water purifiers are enough, so we should expect to have more magic drones in the future.
”no matter how much money sungwoo had, the only way to get more items was to draw them randomly at the store.

“oh, in the ‘other items’ category of the level-up cards, you can find parts that can make weapons such as flying weapons,” inho said.
kyongsu added, nodding at his words, “right.
 not long ago, a monster crackdown team leader chose an item called ‘ballista blueprint’.
 if we can get the materials we need to make, i think we can run something like an armory.
”the “ballista” they obtained from the red orcs and the “iron mace of lightning” they acquired from the evolution society were certainly dreadful weapons.
 if they could get more items like that, they would be a tremendous addition to their power when the war among factions broke out in the future.
if they regarded dozens of bone wyverns as an air force, they could call lots of flying weapons artillery.
 needless to say, they would serve as mighty firepower for sungwoo and his allies in future conflicts.
“very good.
 don’t spare money to get more materials for the weapons.
”at that time, hanho, who was watching the community bulletin, suddenly stood and shouted, “sungwoo! we’ve got another message from kanghwa island.
”the players of kanghwa island, including muyon and heyon, expressed their support for sungwoo and his third camp from the beginning, for they didn’t feel a sense of belonging to junghoon’s new alliance.
 they were following the necromancer who saved them.
“according to the message, the pirate bastards are holding the parade at the square of taipei chiang kai-shek memorial hall at 3 pm tomorrow.
”the players on kanghwa island reported directly to sungwoo, not junghoon in youngdungpo, whenever they had the latest news from the chinese side.
“a lot of the prisoners who were expelled from china and those who were treated poorly in taiwan will allegedly participate in the parade and strengthen their unity.
”after they had been expelled from the china-2 server, the red revolutionary army was tossed out into the cold.
 however, after they succeeded in conquering taiwan and advocated hunting the necromancer, they recovered their former images surprisingly quickly.
 their leader, gen.
 chongong, was not content with conquering taiwan and was looking toward the korean peninsula.
“in the end, he’s trying to show off to mainland china.
”to return to the mainland chinese someday, the red revolution army was trying to win the favor of chinese players.
 that’s why they showed off their power by all means.
“by the way, it seems like they don’t get along well with the prisoners here.
 if that’s the case, don’t you think the size of the parade will be much larger than now?” in particular, not only the pirates but also the pro-chinese forces and the prisoners will be all gathered, it’s going to be a super huge parade.
”“really? didn’t they invite us?”so, sungwoo was thinking of decorating the stage they ambitiously prepared a little more gorgeously.

***meanwhile, a big change was taking place in youngdungpo because of the new angel statue unearthed in kimpo.
 when they touched the statue, they were given a new quest.
[faction quest]-title: killing “demon ” camp in the metropolitan area-type: target destruction-goal: destroy the demon statue in the north (uijeongbu area)-reward: faction skill, rank scorethere was a demon camp in the nearby area.
 the angel executors were looking forward to removing the stumbling blocks early on for the safety and endless development of their allies.
* when the battle begins, you will receive ‘blessings’ from the angel camp.
 (defense increase 20%)* when the battle begins, the ‘same quest’ is given to the opposing faction.
* you will fail the quest when the statue of the friendly team is destroyed.
“after all, this means we have to fight them.
 commander, i don’t think we can avoid war this time.
”“by the way, what the heck is this statue in the north?”“i think they are the reconstruction alliance in the north.
”“that’s what i expected…”as a giant force that could be compared to the liberation guild, the reconstruction alliance gathered in the uijeongbu area approached youngdungpo, showing a willingness to join the new alliance that junghoon was creating.
however, they seemed to monitor the strength of the nascent alliance, while constantly disturbing its development.
 so, sungwoo was planning to get rid of them someday, but unfortunately, they tried to get rid of the necromancer to receive the huge bounty and were annihilated by him.
“if the reconstruction alliance is on the side of the demon camp, it is very likely that they will try to fight us.
 i have not sized them up yet, but they also have over a thousand combat troops.
”after the players in the reconstruction alliance were annihilated by the necromancer, they seemed to blame the liberation guild for it.
 their attitude showed that there was a greater possibility of them trying to keep the youngdungpo group in check rather than cooperating with them in the future.
 moreover, if they were in the demon camp, it was highly likely that the youngdungpo players would not be able to avoid fighting them.
“in that case, we have to prepare to advance to uijeongbu.
”if the opponent wasn’t the necromancer, the liberation guild players were confident of beating anybody because the strongest force of the korean server was still the liberation guild.
however, the situation began to turn around very quickly and urgently.
“commander!”a member of the crusader team burst open the door of the conference room and shouted.
“a guard post in the dasan area was attacked!”the liberation guild set up observation posts all over the metropolitan area to check the trends of the monsters.
 according to the member, the guard post in the dasan new town area was attacked.
“a surveillance team member witnessed it while patrolling near the area.
 he said it was not destroyed by monsters, but by a player.
”a player? who dared to target the liberation guild?“oh, no way!”at that moment, a common message for the angelic camp and the demon camp on the korean server appeared.
[war quest]

-title: battle for the metropolitan area (1)-main forces: angel’s camp (youngdungpo district, seoul), demon’s camp (uijeongbu-dong, uijeongbu city)-reward: attack and defense increase 30% ( 7 days)-conditions: occupy the following areas.
* in addition to the main forces, the players who belong to the absolute race faction can ‘join voluntarily’.
the message encouraged them to wage a war.
 they could not avoid it anymore.
“…”“damn it…”the fact that the main forces of the demon’s camp were in uijeongbu-dong meant the statue was located there.
 in other words, the reconstruction alliance was responsible for the destruction of the guard post in dasan.
“deputy commander, call the leaders of each group right now! have the crusaders on standby, and dispatch the surveillance team to that area,” junghoon said.
“okay!”the first war event of the korean server has begun.
as long as junghoon and his forces belonged to the absolute race faction, they had to wage the war out of obligation, regardless of their will to fight.
war was both scary and interesting.
 everyone doesn’t want a war, but everyone is interested in it.
 who is fighting for what? how to fight? how terrible will it be? which hero will emerge at the end of the war? and who will win?the war was a comprehensive set of emotions and sorrows containing all kinds of stories that stimulate humans’ primitive senses.
therefore, the ‘battle for the possession of the metropolitan area’ quickly became the top concern of the korean server, overshadowing the situation of the necromancer’s third camp.


 