\section{chapter 312}

chapter 312: world season (6)22 hours before the start of the war, a splendid breakfast buffet was served in the penthouse of the massive building shanghai tower.
 all sorts of chinese dishes gave off a greasy smell.
 even though they were powerful rulers, it was a fantastic meal that they never imagined they would enjoy in a ruined world.





“…”rather than making the participants’ mouths water, the dishes smelled somewhat foreign to them.
 more precisely, they were feeling something like the high pride and vanity of the “power” who served this meal.
three guests from different regions did not eat any of the dishes because they were very uncomfortable about the situation they were in.
 they didn’t even talk to each other, and they just looked down at the city center outside the window.
it was the guide standing at the door who broke the silence.
“general xing is coming.
”soon, the door with gold embroidery was opened, and a short chinese man walked out.
he wore a blue traditional costume with a gold sword on his waist.
 he was quite young for a man with the position of a general.
“welcome, everybody! my name is xing liang, the great general of the empire.
 thank you for accepting my invitation like this.
”general xing was known as the second strongest man of the unified chinese server.
he approached with a brisk gait and asked to shake hands with his guests.
“siberian hunter, mr.
 boris, haha! you are so tall, as i heard!”“…”in russia, he was called tsar, or emperor, but general xing just called him “mr.
,” a very common title for a stranger.
but the way he called the russian tsar was very deliberate, which meant that he would not treat any man other than the chinese emperor respectfully.

“ah! who is this! welcome!”after passing by boris, general xing held the next guest’s hands.
 the middle-aged white man was wearing a baseball cap and laying his golf bag at his feet with three gun muzzles sticking out of the bag.
“i’ve heard a lot about you, admiral baker in america, but i never expected i would see you like this.
 it is an honor for me to see you.
”“…”the last was an asian old man.
“sir miyamoto, the big master of kyushu! one day, you will surely be able to rebuild kyushu.
 i’ll gladly help you.
”“…”when general xing approached the head table, the servants pulled out the chair for him, and he sat, lifting his sleeves.
he said, “now, i know that all of you here have one hope in your hearts.
”then, he laughed happily, interlocking his fingers.
“you want to kill the necromancer of the korean server, right? so, that’s why you responded to my offer to make an alliance.
”there was one thing in common that the three men invited to shanghai and gen.
 xing had about their organizations.
 all of them suffered a devastating defeat after challenging the korean server led by the necromancer.
as a result, there was no opportunity for them to challenge the “server master” because they were on shallow ground after their humiliating defeat.
and they were not here as the representative of their servers.
 rather, they left their servers and joined hands with the chinese server.

“but i didn’t lose to him,” said boris, the russian tsar, gnashing his teeth.
 “the moment i was about to tear him to pieces and kill him, some crazy guy broke in and complicated things.
”japan’s miyamoto nodded and expressed sympathy.
“the same is true of us.
 it is because of that man that kyushu collapsed.
 i could have stopped the necromancer without any difficulty…”“if i meet him again, i’m going to decompose the necromancer so that nobody can recognize him.
 so, i hope no one touches him until i kill him.
 this is my request and declaration.
”boris and miyamoto expressed their violent hatred and desire for revenge against the necromancer, and general xing smiled at them.
“i like your attitude like that, which is very desirable.
 by the way, have you ever checked out what the “declaration of war” among the world season’s rules was?”“you mean taking the initiative of the war?’at that moment, the servants came in and put down a cup of hot tea.
general xing nodded, raising the glass with both hands.
“that’s right, miyamoto.
 that’s right.
 having the initiative means you can decide the battlefield and the way you fight.
 in other words, since you fight according to the absolute race’s rules, you won’t be disturbed by the outside world.
 ·now, this is a high-quality tea made in yunnan province.
 its scent is very good.
 try it.
”but no one sipped the tea.
“so, what you mean is that disgusting bastard who deals with the lightning won’t appear in this war?” boris asked.
general xing said with a nod, “yeah, i’m going to make it happen like that.
 the guy, ranked no.
 1 in the korean server rankings, doesn’t seem to be interested in such a huge event like this.
 according to the espionage unit directly responsible to the royal presidential guard of the emperor, that guy is moving only to search for ‘the power of hell’.
 how about it? isn’t the scent really good?”“right.
 even when he attacked me, that guy talked about something like hell dimension.
 son of a bitch! i was ambushed last time, but if i meet again, i will kill him!”“boris, please come down by sipping tea.
 first, hear me out.
”“…”general xing started talking about the one who could be the biggest variable in this war, namely the no.
 1 in the korean server rankings, and that the ‘emperor’ of the chinese server was watching him closely.
 he said the man was veiled in mystery because nobody knew which server he belonged to or who he made friends with.
 besides, he had never taken the initiative in any major fighting until now.
“the espionage team of the royal presidential guard tracked him down, but they couldn’t figure out anything other than the fact that he wielded lightning because the espionage team members were annihilated after they shadowed him for hours.
”he drank the tea and slowly continued, “of course, there are a few cases where the man was seen fighting, but the guy unilaterally won, so there was no way of analyzing his strength in detail.
”miyamoto and boris frowned at that.
“that’s why the empire also regards him as the greatest threat.
 there is nothing as dangerous as someone that we don’t know.
”general xing pulled his head forward and lifted his index finger.
“but we only know one thing, which is very important.
”“hell dimension?”miyamoto replied, and general xing nodded lightly.
“when we analyzed his movement, we found out that he was chasing the hell dimension.
 so the royal presidential guard secured an incentive for that guy.
”general xing looked at boris with a smile.
“three hours ago we opened the gate to a three-story hell on the banks of the tunguska in siberia.
 boris, isn’t there a place as remote as siberia?”

“so, did he go to siberia?”“of course, he did.
 the three-story hell’s gate scroll is not an item you can obtain easily.
 you can get it only with special luck.
 can someone like him who only devotes himself to pursuing the power of hell ignore such a thing? even if he knows this item is a lure, he will try to swallow it.
”when he beckoned, the servant took out the teacup then came back with fruit.
“okay, i have created a situation where there is no obstacle like the guy in this war.
 so, how would you like to kill the necromancer?”“let me kill him,” said boris as if he wanted to take the initiative.
“dispatch me to the battlefield where he will fight.
 i can assure you that i can kill him right away unlike you guys trying to drag on the war.
”since boris was rather reckless in his words and action, his overconfidence looked childish.
but general xing knew well that he was really a powerful man.
“boris, i know you are overwhelmingly strong in a one-on-one showdown.
 the royal presidential guard gave me 26 pages of detailed reports about you.
”boris’s eyebrows wriggled at his words.
“what? somebody shadowed me?’“yep, they did for 13 days.
 we are investigating all the strong men.
 anyway, it doesn’t matter now.
 boris, tell me what you need.
 if you can win, i’ll support you, so you can definitely win.
”boris laughed and said, “then, give me sincere priests as many as possible.
 there were no such guys in siberia.
”“priest?”

 