\section{chapter 282}






 something started to happen.
 however, there wasn’t much that sungwoo could guess from the message alone.
 given the meaning of the word, it looked like a demonic beast came out.
“but, it’s demon beast!”this time the hunter became nervous.
“tsar has used the power of a hell pilgrim!”“damn it.
 hide wherever you can!”the hunters who were confronting the undead army widened their distance from the tsar.
 sungwoo also stepped back, feeling something ominous.
at that moment, a black crack broke out over the tsar’s shoulder.
 then, two small portals opened on the spot, and black lumps flowed out and fell.
 there were about 20 in total.
krrrrrrrrkur―they wriggled and started to take on form, something with four legs.
they were animals, but they could never be seen on earth.
kaaaaaaak!the monsters with two heads and six eyes raised themselves.
‘that’s why he was called the devil’s druid.
’they called him ‘devil’s druid’ in the memory fragments of chinese server players.
sungwoo could not understand it back then, but he now did.
‘this guy chose a high-ranking druid, ancient druid, as his primary job, and one that could control the hellish monster as his minor job.
’the two were linked together to deal with the beast of hell, the “demon beast.
”besides, that wasn’t the end.
-body functions are weakened due to unknown energy.
 (they are affected by a stronger wave because of the clash of two energies.
)* all stats decrease.
 (-5)
the above message appeared before everyone except sungwoo and the tsar.
in fact, the tsar also turned into an unknown “deity’ status.
“it’s now more fun, isn’t it?”soon, the “demon beast” completed his shape and moved.
shhhhhhhhhhhhhhhh–it was as fast as an arrow.
 he transformed his body freely and pierced the undead between sujngwoo and the tsar like a drill.
the skeletons guarding sungwoo collapsed all of a sudden.
“what do you think? is he a little better than your undead?”the demon beasts spread in all directions and formed a siege around sungwoo then charged at him all at once.
sungwoo immediately hung on the claws of one of bone wyverns.
 in order to avoid the demon beasts closing in on him, he had no choice but to soar into the sky.
kaaaaaaaaaaak!however, he couldn’t escape them.
 two of the demon beasts stepped on the rooftop of yongsan station then collided with bone wyvern, broke his ribs, and penetrated his body.
then, the two bounced back and forth inside, thoroughly disassembling bone wyvern.
 sungwoo hurriedly fled from bone wyvern and hung on the back of the zombie bird.
‘i can’t let this fight drag on like this.
 i need to kill them with one fatal strike.
’while he was on alert, sungwoo pondered over how to attack the tsar.
 he remembered one thing he had forgotten.
 it was the bone weapon manufacturing (ultimate) skill he obtained through synergy effects.
 he was so absent-minded with the fight that he could not check it out in such a hectic situation, but he thought it would give him a way out.
 now, was the time he needed a game maker.
sungwoo checked the skill information while giving the demon beasts the slip.
[skill information]-name: bone weapon manufacturing-grade: ultimate-category: active-consumption: 5~100 mana
*you can make a weapon using the bones of the corpse.
 currently, the types of weapons that you can make are as follows.
(1) common weapon(2) advanced technical equipment(3) flying weapon(4) free molding.
*the final products vary depending on the type and quality of the material, and the higher your skill level, the more sophisticated you can make the weapons.
based on the information, the bone weapon manufacturing (skilled) skill sungwoo originally possessed was only capable of making general weapons.
 but as he improved his skills in the future, he would be able to manufacture more sophisticated weapons endlessly.
‘no.
 3 flying weapons are amazing.
 but what is this no.
 4 free molding? does it mean i can mold them freely?’to be honest, sungwoo didn’t know how far that limit would be.
 however, as it was the “ultimate” stage, it would not be a mediocre weapon.
“how long are you going to run away? huh? since you guys are so weak like this, your people suffered so much in the past!”ignoring the tsar’s sarcastic remarks, sungwoo pulled the repeating crossbow.
tung! tung! tung! tung!“it’s useless!”as expected, the tsar turned into a turtle shape after folding his arms then charged at him from the front.
‘it’s only 10 seconds.
’sungwoo stepped back and the tsar kicked the ground.
sungwoo counted the numbers deep down.
‘5 seconds 4 seconds, 3 seconds…’a tiger shape emerged behind the tsar’s back at the last second.
‘right, this guy can’t change into a turtle shape for another 10 seconds.
’sungwoo found out that the tsar could not change into another shape for ten seconds once it became a certain shape.
 so, this moment was a good opportunity for sungwo to strike him.
sungwoo stretched out his hand into the air then cast the magic with a small voice.
“manufacture bone weapons!”at the same time, a group of bone wyverns flying all over the sky stopped flapping their wings.
 mana came out of their bodies.
then, their huge white bodies shattered and poured down.
 they were rain made of bones.
the whole world was covered with pure white bones and black shadows.
ooh ooh ooh-before long, they began to swirl in the air and merge into a single stem.
 soon, some form was completed.
it was a giant’s legs.
“what the heck?”the giant’s huge feet fell over the tsar’s head.
kwa-ang!the moment he stepped, a tremendous shock shook the whole area.
 it was as if a ancient giant was resurrected to end the civilization of mankind.
the ground where the tsar was standing collapsed, the pipes broke, and water soared.
 buildings in the area were staggering and windows broke.
 abandoned cars on the roads sank under the ground.
but it wasn’t over yet.
“manufacture bone weapons!”then all kinds of bone fragments, including the giant corpses of brown bears scattered on the ground, began to unite into a single place.
kugugugugugugu―this time it was the hand of a giant.
 as soon as the giant lifted his feet, a huge palm fell over it.
as expected, a tremendous shock swept through downtown.
 the giant clenched his fist slowly.
 more precisely, he grabbed something under his palm.
it was the tsar.
 covered with blood from only two strokes, the tsar raised his head painfully.


“kheeeeeeek! shit!”but it wasn’t the end.
 the tsar found something and raised his eyes.
there were a dozen “bone ballista” made of bones behind sungwoo’s back.
“before you die, show off all your power, you tough guy!”the way sungwoo dealt with a racist like the tsar was to make him feel keenly that no humans were superior to each other.
the ultimate bone weapon manufacturing was materialized beyond common sense.
 hundreds of undead were merged into one to form the arms and legs of the giant.
“argh…”the tsar groaned, twisting his body.
 even the “demon druid” who exerted superhuman power could not escape the grasp of the giant.
he realized that he could not escape with his own power, so he belatedly moved the ‘demon beast’.
“come here! bite off this one!”the demon beasts could have broken the giant’s arms and escaped, but sungwoo was faster.
“fire!”as soon as sungwoo ordered, the skeletons standing behind the ‘bone ballista’ activated the huge flying weapons.
tung! tung! tung! tung! tung!as expected, spears made of bones were shot like bullets.
 it was 14 in total.
 they were fired off from the giant’s hands and hit the one target, which was the tsar’s body.
but the tsar was intact, for at that moment a bear shape behind his back swung its paws and struck the flying spear.
 he was quite an adroit fighter.
only one spear passed through his side, but that alone couldn’t defeat him.
‘i have to give him another blow before he recovers.
’sungwoo raised his head.
 however, the giant’s feet were already tattered by the attacks of the horde of demon beasts.
sungwoo succeeded in striking the tsar by a surprise attack, but if sunwoo could try to manufacture bone weapons again, the tsar would block him after noticing it.
‘i need extra undead!’

 