\section{chapter 160}

                             




now, the troll skeletons fired huge slingshots at the hellhounds at random.
 fist-sized stones were fired like bullets, knocking down the hellhounds at the forefront.
after that, the ghouls started running and got into dogfights with the monster dogs.
the flames spewed by the hellhounds were powerful, but they were not fatal anymore.
the charcoaled bodies of the ghouls recovered in an instant, stood up again, and cut off the hellhounds’ heads.
“as things stand now, we can block them to some extent.
”as long as the effect of the killing scythe, grim reaper, was there, sungwoo was in a more favorable situation because he could make this a war of attrition.
thump- thump-however, sungwoo had to find a way to deal with the fire giant coming closer to him.
  ‘we can’t beat him with a simple attack .
’since the monster’s body was made of flame, ordinary physical attacks would not work.
 moreover, even a large skeleton would melt just by touching his flame body.
however, the fire giant had only one soft spot, namely his head.
 he had a skull that seemed to be made of stone.
‘okay, that’s the area we have to focus our attack on.
’every boss monster had its soft spot, and the fire giant was no exception.
sungwoo walked towards the fire giant without any hesitation.
“poisonous cloud!”sungwoo showed off his new skill.
kuuuuuuuuuuuuh ―then, dark clouds began to form at a rather low altitude in the sky over where sungwoo was standing.
 it was a mixture of purple and green, a skill he had obtained after winning the mini-game, called ‘poisonous cloud production’ skill.

but it was questionable whether something like poison would inflict any damage to such a huge fireball.
 but if it was rainwater coming down with poison, it might be able to annoy this monster composed of flames.
pitter-patter, pitter-patter.
raindrops started to fall.
 sungwoo reached out his hand and adjusted the position of the clouds.
the raindrops gradually began to fall heavily.
 they were not heavy enough to put out the flames, but they could still lower the temperature of his body because his temperature was like his heartbeat.
kuaaaaaaaaaaah!the fire giant screamed and reached out his hand to the building next to him.
 then, he ripped a handful of the outer wall of the building and threw it at sungwoo.
‘that’s dangerous.
’“watch out!”while manufacturing a bone shield, sungwoo lowered his posture.
 minsok hugged hanho and hid behind the car while jisu was ready to avoid the monster’s attack, concentrating all her senses.
bang!a firestorm swept through the area.
 cars on the road were crushed and skeletons shattered.
 furthermore, even the trees were smashed to pieces.
weeeeeeing! weeeeeeing!car alarms sounded here and there, and the water from fire hydrants on the sidewalk burst into the air.
“what the heck is this?”hanho finally woke up after he was showered with cold water.
“hey, if you have come to your senses, get up and throw your daggers!” sungwoo shouted.
sungwoo threw the tattered bone shield, made a new bone shield, and rushed toward the fire giant.
as the poisonous clouds poured out heavy rain, smoke blew out of his head.
sungwoo felt the flames of his body were much weaker now.
‘yes, his soft spot is his head.
 i can only hit his head.
’
in order to hit the fire giant’s head, sungwoo had to make the monster lower his head.
so, sungwoo boldly approached the monster until he was within ten meters of him.
thump- thump-at that moment, the monster bent his back and stretched out his hand toward him.
a pillar of fire erupted from the palm of the monster’s hand and struck sungwoo.
bang!“uh? sungwoo!”sungwoo lifted the shield, but the huge flames swallowed his whole body in an instant.
“…kuuuuuuuuek!”although sungwoo was in lich mode, he felt enormous pain, like a needle was pricking his whole body.
 the monster let out a tremendous roar as if tearing his eardrums.
kugugugugugugu ―as a child, sungwoo was scared of fire.
 so, he hated fire.
 fire took everything away from him, but he was not scared anymore.
the flames that crushed sungwoo’s body were gone.
 sungwoo wriggled behind the charcoaled bone shield.
 by now, he should have been burnt to ash, but he was intact.
 after gnashing his teeth tight, he let out a breath, at last.
“i am not dying in this fire.
”he earned the title of “amateur dragon hunter ” and 30% immunity to fire after hunting the drake.
 in addition, he earned an additional 30% fire immunity by combining ‘drake’s leather’ and the ‘shadow king’s robe.
’ he had a total fire immunity of 60%.
in other words, no matter how strong the flames were, they could not inflict more than 40% damage to him.
krrrrrrrrrrrrrrrrr-even the fire giant was questioning what was happening.
‘yeah, now is the time!’while sungwoo was drawing his attention, somebody approached the monster from behind.
it leaped from the roof of an eight-story building, fell on the head of the monster, grabbed his skull, and struck him down to the ground.
it was ogre skeleton.
 sungwoo had summoned that large skeleton on the roof of the building.
 although the fire giant was huge, ogre skeleton was also pretty large.
 the head of the fire giant struck the asphalt.
 however, due to the enormous heat, ogre skeleton began to melt.
‘now is the time.
 i don’t have much time.
’sungwoo jumped off the ground and took the hand cannon from the waist.
 then, he pulled the trigger, aiming at the giant’s forehead.
bang!there was a crack in his skull and an explosion, but one shot was not enough to break it.
“orun!”as soon as he shouted, orun bounced to sungwoo’s right.
 orun threw away his knife and took out his hand cannon.
as orun got closer, his bones began to melt, but he finally squeezed into it.
 then, he pushed the muzzle into the crack in the giant’s skull and pulled the trigger.
bang!at that moment, the giant’s forehead shattered like ceramic.
 at the same time, both arms of ogre skeleton shattered because of the heat.
goowoooooooooo ―the monster staggered before raising his body, but sungwoo was faster.
 he stabbed grim reaper’s long blade into the cracks.
when sungwoo pulled it, the giant’s skull was split in half.
ahhhhhhhhh!the monster fell, roaring.
 there was something in his cracked skull.
 it was a red bead.
‘that’s it.
’sungwoo recalled that when the monster appeared that marble appeared before the flames formed around it.
“kuuuuuuuuuuuuuk!”sungwoo jumped into the flames and stretched out his left hand.
 the enormous heat crushed his whole body, but thanks to his flame immunity, he overcame it.
 he managed to grab the marble and pull it out

poohhhhhhhhh!the monster’s massive body collapsed and a vast amount of fire and heat scattered in all directions.
-you have earned 2,800,000 gold by hunting the ‘fire giant’.
the towering flames disappeared completely.
“uh, did you kill the monster? i’m not dreaming, right?”hanho was still blinking without coming to his senses yet.
jisu also stared at the stunning scene unfolding before her eyes, and minsok gave a burst of hollow laughter.
 and the players who escaped from the burning building also looked dumbfounded as if they could not believe what they had witnessed.
– oh! i forgot this, too!at that moment, nabi’s voice was transmitted through the fairy communication network.
-by the way, you have to destroy the core inside the fire giant’s head to hunt him! kangsok had a hard time trying that, so be careful!  “i know.
” – what? how do you know?“i just cracked open his skull.
”– what? did you do it already? no way! are you kidding me?sometimes there were people who didn’t want to believe what the necromancer had done, but they came to believe him when they witnessed his brilliant activities.
-kangsok! looks like these guys are faster than us.
however, the flames were not extinguished yet.
 there was the real boss monster left.
sungwoo was thinking of going into the flames.


 