\section{chapter 400}

sungwoo had no choice but to step back for now.
 not only did he not know the emperor's whereabouts, but also he could not stay in the middle of the enemy camp any longer because his operation failed.
 it would be an act of suicide if he stayed there anymore.





'well, this takes me back to square one!'he missed the best chance to kill the emperor.
after all, the necromancer and the emperor exchanged secret cards that they had never unexpected.
zi xuan, the woman who controlled the clouds and wind, lowered her hand while looking at the necromancer disappearing from her.
"is that the guy we're looking for?"at that moment, a male voice was heard from somewhere.
 but the owner of that voice was not seen anywhere.
she also didn't try to find the location of that voice.
 instead, she simply nodded as she looked into the air.
"i knew it, but he's more annoying than i thought.
 we're going to change our plan.
"it was an emotionless voice, but she could feel the anger in it.
 she put her hands together and bowed her head.
"it's better to quickly capture the rampart rather than giving him more time to fight us using another tactic.
"judging that the necromancer might inflict far more destructive damage in another bizarre way, the owner of the voice decided to pursue a perfect victory over keeping his pride.
"you deal with him until then!"she slowly raised her head and said, "i can kill him by myself.
 if you give me the order…"then, something started to form in the air, and she stopped.
"no, let me kill him after we destroy the rampart.
 zi xuan, you should only move according to my intentions.
"the objects created in the air fell to the floor.

clink-it was two items, namely, two spears.
at first glance, they were very unusual.
 but they looked very familiar to her.
it was none other than the legendary weapon of gen.
 guan yu, the 'blue dragon sword,' and lu bu's 'bangchon spear', the famous fighters appearing in china's three kingdoms chronology.
"i'm currently checking the broad picture of the war.
 so, if i make a wrong move even once, my whole plan will go amiss.
"she now lowered her head more deeply.
tramp- tramp-at that moment, two terracottas walked out.
 they were different from other terracotta.
judging by their excellent appearance and some extraordinary energy, they seemed to be fairly high level among terracotta.
rattle-they picked up blue dragon sword and bangchon spear.
then, the appearance of the two terracotta began to change rapidly.
- legendary-grade 'terracotta' draws the special energy of the item.
- the incarnation of a hero was born through 'connection with artifacts'.
 (guan yu)- the incarnation of a hero was born through 'connection with artifacts'.
 (lu bu)they became very similar to the appearance of the two heroes guan yu, lu bu of the three kingdoms chronology.
drawing the power from the item owner and giving it to the doll was one of the puppeteer's magic tricks, which reached the climax of his power.

rattle- rattle-the two heroes began to advance towards the rampart.
 countless rank-and-file terracotta soldiers followed them.
"i am now advancing towards the rampart.
 stop the guy from stepping on my shadow.
"the tide of the battlefield began to change.
***sungwoo escaped from the enemy camp and returned to the undead army.
even though he gained the upper hand of the war using huge explosions, he couldn't stop this huge battle.
 shortly afterward, the battle resumed.
"damn, there is no big change even if we destroyed them a lot!"li wei shouted, complaining about the lack of a decisive win.
as she said, most of the terracotta that landed on the ground were burned, but more than them came pouring out of the sky barracks to replace them.
"uh! they're moving!"all of them started moving toward sungwoo's allies at once.
 they were now launching a frontal attack.
 sungwoo felt something strange in their movement.
"but they are not coming to us.
""you're right.
 where are they moving then?""they are advancing to the rampart.
 they changed their plan!"obviously, the emperor changed his mind for some reason.
"well, it means he has chosen an easier way to attack us.
""should we stop them?"after nodding, sungwoo immediately moved the troops.
 he moved the undead army waiting in the rear towards the wall, except for those fighting on the front line.
right at that moment, there was a roaring sound.
 then, a gust of wind blew.
sungwoo grabbed his fluttering clothes and turned his head.
 it was a tornado.
"ugh! look over there!"seven tornadoes the size of a house blocked and swept away sungwoo's undead army heading towards the rampart.
 sungwoo knew what the tornado was.
"it's that woman!""the woman?""you know there is a woman controlling the water and the wind, right?""ah, that bitch?"li wei seemed to know the woman's true identity.
"that bitch has bound my water spirits and locked them in the ark of spirits.
 i don't know how she is doing it, but she has complete control over the water and wind.
 she's really annoying…"sungwoo nodded.
 when he watched li wei masterfully controlling the water spirits a little while ago, he wondered how she could have her spirits taken away by somebody else.
however, if that woman had the deity status that empowered her to control the water and the wind, it was possible that she could take away li wei's spirits.
at that moment, sungwoo felt something like divine power and looked somewhere.
"she's coming…"a woman was walking out leisurely from the wind and rain that blew away everything, including buildings, terracotta, and even skeletons.
 she didn't get a drop of water on her amid the storm.


she stopped about 30 meters away from sungwoo, then said coldly, "i'm sorry, but you can't escape here.
"sungwoo said sarcastically, "don't you think you are too arrogant when you are only an extra to buy your boss more time?"she didn't show any slightest change of expression at sungwoo's provocations.
 but her face turned pale like a corpse.
she then moved her blue lips to open her mouth again.
"i see you have two deities, anubis and god of underworld…"sungwoo frowned at that, wondering how she found it out.
'can she read the player's capabilities?'sungwo could also feel that she had deity status, but could not figure out how many deities she had.
"ummm.
.
.
you've got two useless deities.
 they don't work out against me.
"she turned her head and gently lifted the index finger of her left hand.
 then, the tornado changed its direction and blocked the undead army that was about to return.
as if it had a magical power, the tornado even swept away the ghosts.
as she said, her abilities were clearly the worst match for sungwoo who commanded the undead army.
"don't try to do anything.
 you can't pass by me," she said, twirling her index finger.
"i have divine dragon power.
 it's not the deity of the evil spirits that you have.
"anubis and the king of underworld are evil spirits? he didn't know how she could judge the deity, but it was clear that she regarded any other deity than her own as evil spirits as if she was deeply influenced by traditional chinese ideology.
by the way, sungwo found something important in her last words.
"did you mention a dragon?" he asked sarcastically.
 "that's a mistake.
"she tilted her head and asked, "uh? what do you mean?"

 