\section{chapter 224}

                            shortly after sungwoo arrived in the suwon village, he agonized over how to inform the villagers about the japanese server’s plan to invade busan.
 he could not post a thread about it because it would leak the information to the enemy.





but hanho solved his headache simply.
“oh, that’s easy.
 let me leave a secret comment on an old thread posted by the hwarang guild.
”if it was an old thread, nobody would confirm it anyway.
 so, if hanho posted a secret comment and had the hwarang guild confirm it, he could relay a warning message to them.
“oh, you are very smart in this field, hanho.
”“of course, this is basic.
”hanho succeeded in delivering a message to the hwarang guild according to his idea.
- the strongest one, hanho lee (secret): hello! do you know my id? i’m necromancer’s colleague.
 i’ve got some information that may be helpful to the hwarang guild, so i leave a secret comment to you…recently, there is a suspicious movement on the japanese server, so i think the hwarang guild needs to be careful.
after only a few minutes, the hwarang guild confirmed and left a reply.
└ hwarang press bureau (secret): thank you for the warning.
 we also continue to monitor the movement of the japanese server facing the korean sea, and we also maintain several coastal batteries.
 we don’t think what you are worried about won’t happen.
 we hwarang guild members love peace and we are strong enough not to bow to any outside forces.
confirming the message, hanho said, “it looks like their response is rather cold.
 in particular, the last line of their message is especially meaningful.
 of course, it’s stupid to figure out their intentions from their message…”the hwarang guild said they would not be hostile to the world tree camp but it was only their political stance.
 it was inevitable that they had bad feelings toward the necromancer because they belonged to the demon camp.
“well, i did my best.
”since they said they were doing their job well, hanho had nothing to add to his comment.

“whew! i hope the hwarang guild guys can come to their senses this time.
 coastal batteries? they don’t know this is a game.
 so, they don’t know where the enemies will attack.
 who knows if they will invade through the underground tunnel?”as hanho said, it would be naive if they thought that the japanese players would invade through the land, the standard attack route.
in games there are always variables, so something unexpected always happens.
didn’t the red revolutionary forces capture the taiwanese servers in an unexpected way using the “mini-game”?“we don’t care about anything else.
 we just have to prepare ourselves for their attack.
”sungwoo and his allies would have to fight a war someday, so other camps won’t be of any big help to them.
 so, they had to come up with their plan to win.
***where does the war begin?at that time, dozens of super-sized kites flew from a barge on the korean strait between busan and daemado island in the darkness.
“group no.
 3, start invading busan.
 good luck!”it was an item called ‘ride-on kite’, a means of penetrating high altitudes for ninjas, which was an item that could fly them on a super-sized kite in the wind.
the yamato guild was carrying out the operation of invading the korean server much more secretly and faster than expected.
their bold action like that far exceeded sungwoo’s expectation, not to mention the intelligence of the hunter company.
whuuung-
the ninjas soared in the dark, seeing nothing ahead at all.
 with the night sky and sea being indistinguishable, there was only one person that they could rely on, namely the leading “guide” that could see through the darkness using a special item.
the rest of the ninjas followed the tail of the kite hanging on a faint light and crisscrossed into the darkness.
“i can finally see the coastline of busan.
 they have dispatched a lot of batteries out there.
”they could hear each other’s voices from a distance through the skill called ‘spiritual unity,’ one of their exclusive skills.
“well, it looks like they spent lots of gold constructing the batteries, fortunately, it doesn’t seem they found us yet.
”the hwarang guild’s coastline batteries were a threat to them.
they installed surveillance posts at key points and numerous ‘mechanical fixed catapults’ along the coastlines of busan.
if the yamato guild’s warship fleet had approached them nearby, they would have been sunk before even attempting to land on the coast with overwhelming power.
however, there was no way for the hwarang guild to detect their covert infiltration on a small scale.
“good, good.
 we’ll pass by them and land on the northern hill.
 lower the altitude from now on.
”the ninjas silently landed in the middle of mt.
 kugok in busan in the darkness.
then, they buried the “ride-on kit” items under the ground to hide the traces of their infiltration, and all of them finally gathered in one place after teleporting from their first landing place.
“now, let’s install the ‘hyper gate’ item here.
 how long will it take?”“it is difficult to infuse large amounts of mana immediately, so it takes at least 12 hours.
”it was a legendary item called ‘hyper gate’ that they selected as the first means of infiltration to conquer the korean server.
it was an item that could open a two-way portal lasting for 10 minutes.
 considering that two people can pass through it at the same time, a significant number of troops would be able to penetrate easily through the portal.
“soon we’ll carry out the operation to support the evolution society of the korean server.
 they will spray poison gas in busan.
”he lifted his finger and pointed to the light of the hwarang guild camp at the foot of the mountain.
“we’ll trigger the hyper gate during the chaotic moment and carry out our operation successfully while watching out for the surroundings.
”“after 12 hours, our main unit will set foot on this land with the korean server players kept in the dark about our ambush.
 this is going to be great fun!”although they didn’t know the whereabouts of group no.
 1 and group no.
 2 members who first infiltrated the korean server because they lost contact with the two groups, they didn’t give up because they ended up carrying out their mission successfully despite making numerous sacrifices until now.
and at this moment, they were more confident than before.
“yeah, we’re going to start from here and move up to suwon to get rid of the world tree camp.
”as always, a war begins earlier than expected.
***on the other hand, the world tree camp was preparing for the upcoming war comprehensively because they got wind of it to some extent.
after learning about the japanese server’s plan to invade busan, they revised the defense-oriented strategy and started preparing for a long-distance expedition.


“well, if we have to fight them in busan, we should also consider how to move the flying weapons to busan, which is very far from here.
 even if we use the inventory, we can use only ten.
 but the problem is we’re going to have more and more flying weapons in the future.
”kyongsu, who was planning the deployment of the flying weapons in consideration of the defense-oriented strategy, raised a question.
but the blacksmiths came up with an idea.
“we have the large undead as well as bone wyverns, right? we can have them carry ballistas on their backs.
 it’s okay to install the fixed fire rocket arrows.
’the bone wyvern was large enough to carry the huge turret ballista on him.
the blacksmith continued, “i watched the scenes of the bone wyverns wiping out the pirates in taiwan, but it was a little disappointing that they had no choice but to engage in melee fighting despite their aerial advantage.
 how about us making flying weapons that can show arrows or fire a fatal shot at the enemy while hovering in the sky?”the blacksmith was talking about something like an air turret.
“oh, that would be very useful!”“that’s a good idea.
”sungwoo also agreed with his idea, and the blacksmiths started making such weapons right away.
first of all, they manufactured a structure that could securely fix the flying weapon to the bone wyvern’s backbone.
 they also made a cover just in case of the bone wyvern’s high-speed flight, which could minimize wind resistance.
soon, they completed the prototype of the new flying weapon.
 the blacksmiths could produce such weapons so quickly thanks to their excellent skills as well as all kinds of buff effects.
but they needed to test the weapons for real deployment.
“let’s start the test flight”

 