\section{chapter 409}

a drone was floating in the air behind sungwoo.
 it was the drone of the official channel to capture the fighting scenes.





"hey, lots of people are watching this channel, so don't try to put on airs like this, and reveal yourself right now!" sungwoo shouted.
but there was no reply.
 kuguk - kookuk-instead, the giant statues lined up from side to side began to move.
thump- thump-the giant statues holding the swords and axes got out of their fixed spots and began to move forward.
 there were a total of 12 statues.
 they blocked him by standing on the left and right.
 incense smoke spewed from their bodies, making them look much bigger than before.
"what can you do here? you can't even summon your main forces.
 but i can…"rattle- rattle-something like a big noise could be heard from inside, which sounded like numerous footsteps.
 thousands of footsteps, which meant a large army was marching forward.
 but sungwoo didn't care.
 he glanced at the statues standing in front of him.
"stone.
.
.
well, it's easier to break you guys than the gold guard.
"he once fought against the enemy empty-handed even at the forge of hephaestus.
although they were more numerically, the 'gold guard' was much more intimidating.
'and it wasn't just the fighting experience that i gained back then.
'sungwoo took a breath and recalled a message before his eyes.
[skill information]- name: dragon lord-red- grade: special
- category: active- condition: 3 or more 'red dragon' itemsupdated from lightnov‌elworld.
c‌om* available skills vary depending on the set items.
1) breath field: activated through 'red dragon spear'.
 change the area (100m) where the spear is stuck into a lava field.
2) boiling armor: activates through 'red dragon armor'.
 surrounds the user with a powerful fire vortex.
3) summon dragon soldier: activated through 'red dragon bracelet'.
 you can summon and control 10 dragon soldiers.
it was the 'set effect' he obtained through the red dragon's item, the legacy of the world eater he had acquired while fighting against the gold guard.
'finally, the time has come for me to use it.
'sungwoo did not use the newly acquired weapon recklessly because the 'hidden card', which he saved for launching a surprise attack on the enemy, was always important.
'now is the time for me to use this hidden card.
'at last, he got close to the emperor.
 in other words, the time has come for him to mount a surprise attack against him.
sungwoo used one of the three skills available.
"summon dragon soldier!"at that moment, the red dragon bracelet on his wrist began to glow red.
woo woo woo-the teeth, which were threaded with tendons, spontaneously loosened and fell to the ground.
 a total of ten dragon teeth began to swell after wriggling on the floor.
soon they turned into reptilian skulls.
 and the moment when they formed a perfect shape, flames erupted from their skulls and turned into huge bodies.
 they were bipedal, with long arms and long tails.
"hey, sorry to disappoint you, but i can still summon my subordinate spirits.
"
sungwoo could summon dragon soldier even if he didn't open the 'space.
' all he needed was for the teeth sewn into the bracelet to change their appearance, so he could summon them even within the emperor's territory.
krurrrrrrrrrrrrr.
.
.
they slowly raised their heads.
 sparks dripped from their charred jawbones.
 the next moment they charged forward with a wild roar.
 flames erupted wherever they stepped on it.
 they jumped and threw themselves towards the statues.
they made a gigantic jump, but it was literally an explosion.
 their bodies made of flames soared in the air as if sparks were flying everywhere.
this content is taken from lightnov‌elworld.
c‌omthen the dragon soldiers pierced through the statues in front.
 the huge statues collapsed helplessly.
kahhhhhhhhhhh!after that, the dragon soldiers that got stuck on the statues began to attack ruthlessly.
 they swung their arms, legs, and tail made of flames, grabbing and tearing the statues.
kwajik! kwajik! kwajik!then, the statues made of the rock fell apart like a sponge.
 it was an unbelievable scene.
 'as expected, it's also the best of the dragon's power!'although they were only dragon teeth, they were much stronger than skeletons because they were made with special magic.
 soon the 12 statues fell one after another.
thump- thump- thump-when the statues that stood in sungwoo's way collapsed, the podium on which the emperor was sitting finally revealed itself.
 black stairs, gray smoke, a red tent, and the shadow of a man behind them.
whooooo-wind was created by the impact of the statues toppling over.
 a thin red cloth obscuring the emperor's looks was turned upside down.
 finally, the emperor's face was revealed.
".
.
.
"an old man with a gray beard was looking down at sungwoo fiercely.
 then he slowly opened his mouth.
"oh, i see.
 you had a hidden card!"it was the first time sungwoo heard the emperor's voice.
 his voice was full of confidence, but it was trembling.
 was it because he was old?sungwoo looked at him and smiled cynically.
"from now on let me show you something interesting since you said you had a discerning power of everything when you have got stuck in your room like this…"sungwoo had several 'hidden cards'.
 in addition to summoning dragon soldiers, he had two 'set effect' skills, and even one item he received from heyon.
"just hold your head tightly because you might fall anytime…"sungwoo was thinking of taking them out one by one.
the source of this content is lightnovelworld.
c‌omsince there was not a single player here, the official channel didn't capture it, but there was a place where a fierce battle was taking place.
clang! clang! it was the lobby of a secluded building outside the tomb of emperor qin shi.
the necromancer's three elite subordinate spirits were engaged in fierce fighting with the emperor's elite terracottas.
however, the necromancer's soldiers were inevitably pushed out by them because they were inferior numerically.
tung!minsok was kicked out and stuck against the wall by hsiang yu.
 he stood up right away and shook his head.
 then he looked at the small chest through which he could approach the 'tomb of emperor qin shi, which was guarded by the terracottas.
 "damn it, i can't afford to be late.
.
.
"

even though sungwoo went inside the tomb to kill the emperor, he gave minsok a secret mission in advance.
 in other words, he had to go inside and deliver something to sungwoo by all means.
 it was the same item that heyon handed to sungwoo a little while ago, but it was so bulky that he could not carry it in person.
 but minsok found it very hard to break through the terracottas.
 "man, what if something bad happens to sungwoo if i get stuck here…"while he was muttering like that, he suddenly raised his head and looked at the ceiling.
"alright, let me use it!"rattle- rattle-the heroic terracottas, including hsiang yu, closed in on him, but minsok recited something in a low voice.
 "explosion!"bang! bang!a loud explosion was heard over his head, shaking the whole building.
it was a corpse explosion favored by sungwoo.
 using the power of the lich, minsok revived the corpses in the building, then piled up the monster corpses on the upper floor to cause the 'corpse explosion'.
thump- thump-with the ceiling collapsing, its fragments fell on the heads of the terracottas, which gave minsok a chance to break through them.
this content is taken from lightnovelworld.
com"now is the time!" you can also read this novel on the more advanced platform lightnovelspot.
com

 