\section{chapter 453}

"gosh, they've made very annoying stuff!" grace said in an annoyed voice.
 




gangsok didn't respond, but he was also surprised.
'i've never seen such a technology before.
'while playing the game several times, he has never seen 'magic engineering' make as much progress as this one.
'did i leave him alone for too long? he's made all sorts of weird stuff.
'obviously, the magic engineer needed lots of factors to be able to make such stuff.
for example, they needed the power to create a huge infrastructure by combining their skills, manpower, capital, buffs, etc.
, and all other factors.
'i knew that he had been investing a lot, but i didn't know that he made such a huge investment like this.
 was i too complacent?'at that moment, he turned his head and looked at the castle.
 ".
.
.
"his eyebrows twitched.
 he felt something strange.
"demon king, what's wrong with you?""he's faster than i thought.
""pardon? then he…""he has already reached the bottom floor of the labyrinth," he said, turning then.
now was not the time for him to worry about the world tree fleet ahead of him.
since the castle was under his control, a system message appeared whenever they broke through the gate.
 finally, they succeeded in passing the seventh gate.
 in other words, the labyrinth was opened.
"demon king, don't you have very valuable stuff there?"
gangsok felt that his plan began to go wrong for the first time.
"we're going to get rid of the rats in the house first.
"new novel chapters are published on lightnovelworld.
comthen he raised his left hand, and black-red smoke flowed from it, then flowed into the bodies of his three confidants.
 a message appeared before their eyes.
- your stats increase temporarily due to the effect of 'demon king's confidant'.
 (+15)* this effect only lasts within the 5km vicinity of 'demon king's territory (demon king's castle)'.
"let me share my power with you.
 from now on, get rid of the key players of the enemy who are scattered inside the castle.
"since there were a lot of troops on the defensive route outside the castle, they looked like the main forces of the enemy, but those assigned to the attack route inside the labyrinth of the demon king's castle were their main forces.
so, the demon king thought if his minions could attack them individually, he could dismantle the world tree camp easily.
 "alright.
 let me kill that woman wielding the sword.
"having said that, vivona flew somewhere toward the castle alone.
in fact, he was determined to take revenge on jisu after he was dealt a humiliating blow by her some time ago.
so the demon king's minions dispersed to attack their targets.
gangsok also stepped forward to the center of the giant castle.
 "open!"when he reached out his hand, the bricks of the wall were folded like paper, and the ceiling opened.
 inside the castle the space of dozens of floors was opened and closed at once, opening the vertical passage leading to the lowest floor.
pop! pop! pop!
at that moment, an explosion sounded over their heads.
 and black smoke started coming down from the explosion.
 it was the breath of the abyss.
when they confirmed gangsok turned and headed back to the castle, they were trying to create an environment favorable to the necromancer before the fight.
"yeah, after all, they're just incompetent guys who depend on the necromancer alone.
"in fact, gangsok was immune to such 'status abnormality' to some extent.
 so he turned his head again, sneering at the explosion.
 but something white appeared under his feet in the open space.
 it looked like a ghost covered in cloth.
'is it specter?'the source of this content is lightnovelworld.
comspecter meant the necromancer's eyes.
at that moment dozens of black spheres soared from the bottom of the hole.
"kheeeeeeeeeeee!"gangsok twisted his body immediately to the black sphere that narrowly brushed past his shoulder.
 a roar rang out when there was an explosion over his head.
"necromancer.
.
.
.
"was he preparing for a surprise attack after he was briefed about the situation outside the castle in real-time? that was just the beginning.
the wind blew out of the hole violently, followed by something huge.
it was a black arm with chains.
'what the heck is that?'even though gangsok played this game several times, he could not figure it out this time.
 at this moment he felt as if he was looking down at the hole through which the train was passing.
 then the hand crawled out of the hole gangsok opened forcibly, punching his forehead hard like a thirty-ton truck at his head.
 gangsok kicked off the ground, avoiding that punch.
but when the giant fist unfolded, a red ball of fire erupted from the palm of his hand like a shotgun.
 they were none other than dragon soldiers with skulls, whose bodies were made from flames.
they crouched in the giant's hands, then fired rockets towards gangsok.
khaaaaah!they were as intimidating as if ten guided missiles followed them.
 gangsok raised his staff and fired lightning bolts.
 four dragon soldiers fell and were crushed.
 however, the other six dragon soldiers escaped the lightning, landed on the wall, and jumped up once more.
 it was a series of attacks.
 'what a queer thing!' gangsok thought to himself, looking at them.
he has confronted the necromancer in the previous game, but he didn't have things like this.
 he stepped back, then carefully intercepted the dragon soldiers again.
clang! clang! clang!since he had no fairy butterfly that could assist in his fight, he had to pay attention to lots of stuff in person.
 in the meantime, with the rampart collapsing, gigas, the owner of the giant hand, appeared finally.
updated from lightnovelworld.
comgooooooooh-it wasn't just one.
 two strange creatures revealed their marvelous bodies on top of the demon king's castle.
gray smoke billowed out whenever they breathed out.
 and gigas' body cast a shadow below the wall, and something waved at the edge of the shadow, where sungwoo appeared.
gangsok could not see him because he was behind his back, but sungwoo didn't move recklessly.
'he was embarrassed,' sungwoo mumbled.
 sungwoo felt that gangsok seemed to be impatient.
 even though gangsok was blocking the enemy's attack, he was not as relaxed as before.


in the meantime, hundreds of ghosts rose from the inside of the hole and charged at gangsok, while skeletons climbing up the rampart fired aoe weapons at him.
no matter how experienced gangsok was at fighting, it was so difficult for him to respond calmly to their coordinated attacks as if they had been trained for this for a long time.
'it seems his condition is not good, either.
'obviously, sungwoo's attack against him in the underworld paid off nicely.
 this was a golden opportunity for sungwoo.
'alright.
 i can kill him now.
'sungwoo fired 'winter predator' against his back.
 clang! clang! clang!but gangsok noticed sungwoo's attack, then quickly turned around and swung his staff.
electric currents stretched like a spider's web, blocking the frozen bullets.
at that moment one dragon soldier charged at his ribs right away.
since gangsok wielded his right hand and staff at sungwoo, he pulled something from his waist with his left hand and fired at the dragon soldier.
bang! bang! bang! bang!it was a revolver.
gangsok quickly took out a sub-weapon that he had never used before, which suggested that he was driven into a corner.
the most up-to-date novels are published on lightnov­elworld.
com'alright.
 let me keep pushing him like this.
 he has yet to reveal his true identity.
 he can't even afford to do so right now.
' you can also read this novel on the more advanced platform lightnovelspot.
com

 