\section{chapter 247}

                            dr.
 yu controlled the battlefield by looking down on the cavity from his safety capsule on the ceiling, and everything was unfolding as he intended.





“okay, it’s not as difficult as i thought.
”the necromancer came up with several options to overcome the difficult situation facing him, but dr.
 yu grasped his intentions before he could act.
it was thanks to his ability to respond quickly that he quickly froze the bone imoogi and smashed it by focusing his lightning magic on the giant snake.
“necromancer, don’t you have any other option? so, this is going to be your last moment?”at that moment, however, he noticed some suspicious movement.
 a huge black horse among the undead crowd started spurring the ground.
 it was one of his experimental subjects, ‘durahan’.
“oh, good.
 so, you seem to hit on a new idea, necromancer!”dr.
 yu watched durahan’s movements to grasp the necromancer’s intentions while scrutinizing other places at the same time.
“no, no.
 necromancer, your real plan isn’t to use durahan, right? i already know everything.
”in dr.
 yu’s eyes, durahan was most likely a trick, for what he could do for now was nothing except gallop alone on the empty floor.
but dr.
 yu finally discovered something strange about durahan.
“did he have a head?”durahan, a knight without a head, had a pure white skull sitting on his shoulders, which didn’t fit him at all.
“ah! damn it!”at that moment, dr.
 yu grasped the necromancer’s next movement, but it was both unexpected and so extraordinary that he didn’t have time to respond.
durahan wasn’t bait.
du du du du du du!durahan, who drove through the cavern towards the wall, picked up the “goblin skeleton” resting on his shoulders.
hung!then, he flung the goblin skeleton toward the exhaust vent on the wall.
thud!the goblin skeleton was thrown into the exhaust vent, and he got in.
the sound of him clashing deep inside the vent continued.

“no way!”dr.
 yu checked the dashboard anxiously.
– warning! abnormal condition in ‘engine-3’.
soon, the third engine out of the six was turned off.
“oh, no! you can’t!”he even separated the engines into six rooms just in case the engine was attacked, but engine-3, the most important engine among them, was attacked.
it was a coincidence for the necromancer, but it was tremendously bad luck for dr.
 yu.
ooh ooh ooh-soon, the two cranes connected to engine-3 stopped.
 that was the crane on which dr.
 yu’s main force, the priests, hung.
at the same time, all the shields over the cranes disappeared.
 it was the moment when dr.
 yu’s forces were faced with a fatal weakness.
however, he had already been prepared for such a problem in advance.
“alright.
 all i have to do is just hold out for only one minute until emergency power comes back on.
 just one minute.
 if i can hold out only one minute…”he made sure that if the main engine was turned off, he could draw electricity from the main facility.
 to save time, he pulled the unshielded crane to the rear.
-facility power is switching to emergency power.
 (34%)the resurrected “bone imoogi” began to erect his huge body.
“you can’t use the same trick again!”dr.
 yu immediately moved the wizard crane and cast freezing magic towards the bone imoogi.
 his head got frozen in an instant.
 he would most likely be smashed again this time.
at that moment, bone imoogi stood upright in a diagonal line like a runway.
something got on his back.
it was the black horseman, durahan.
“no! lightning strike! smash him!”the lightning magic flew toward the frozen bone imoogi.
 again, it completely froze the body of bone imoogi.

doo doo doo!but durahan was faster.
 like a fighter jet taking off from an aircraft carrier, durahan sprang fiercely on the jumping board.
 the moment durahan ran across bone imoogi’s nose, a ghost knight squad arose on his left and right.
“oh, no!”the eight-member violet knight squad soared tens of meters and climbed onto the crane behind its broken shieldsquaguaguagua!during that moment when dr.
 yu was breathing out briefly, a crane was already tilting to one side, and 20 dolls fell helplessly.
the ghost knight squad flew towards another crane.
 like a knight squad attacking the rear of the enemy line, they showed surprising destructive power at a tremendous speed.
thump- thump-it was a disaster.
 the cranes, which used to be an impregnable fortress, began to collapse one by one like rotten branches.
kiyiyeeeeeeee-as the seams were broken and the rails smashed, roaring noises and sparks sprang up everywhere.
 the weapons soon turned into an ugly mass of scrap metal.
“oh, no.
 nonsense! this can’t happen!”it was the biggest weakness of an army directed by one man that they would collapse at once as soon as they showed their fatal weakness.
sungwoo was always conscious of that because he always dealt with the snipers aiming for his neck, but dr.
 you had never experienced this kind of fight before.
“…”one minute was too long for dr.
 yu who had never experienced such a fight.
***durahan leaped forward according to sungwoo’s will.
bang! quaguaguagua!the ghost knight squad jumped and moved around the crane behind the broken shields.
 then, running through the tilted cranes, they took away all of the 20 players from the crane.
when the wires and hoses connected to their brains and spines were cut off, their half bodies fell to the ground like fruit hit by a typhoon.
puck! puck! puck!their bodies hit the ground and smashed to pieces.
-you have provided those who could not die with ‘a resting place.
’ (112/240)that was liberation.
-you have provided those who could not die with a ‘resting place.
’ (121/240)-you have provided those who could not die with a ‘resting place.
’ (144/240)a series of quest messages appeared.
“tear out the rooftop capsule!”the divine shield was turned off, so dr.
 yu was now defenseless.
sungwoo moved the group of bone wyverns right away.
quaddddddd!they raised their tough claws and ripped the whole capsule out of the ceiling.
 they threw it down violently before sungwoo.
thud!dr.
 yu climbed out of the tattered safety capsule.
 he was already covered with blood.
“how can i collapse so helplessly like this…?”sungwoo came to his side then looked down at him cynically.
“if you were thinking of controlling the whole world by yourself, you should have thought about it a little more.
 you are finished!”dr.
 yu looked up at him with bloodshot eyes and shouted, “what the hell are you talking about? you don’t know anything!”with his bloody mouth open wide, he screamed, “do you know how i prepared all this? when you guys didn’t know anything, i foretold the coming of this hellish situation!”sungwoo laughed it off and said, “so what? even if you knew it, you didn’t do anything.
 what did you do?”upset by sungwoo’s words, he sprang to his feet and started pointing at him.
“damn it! i had a great plan ready.
 yeah, i had a big plan!”there was no more trace of an intellectual gentleman in dr.
 yu.
 instead, a stubborn old man was staggering before sungwoo.
 he charged at sungwoo and thrust his fingers out as if he wanted to poke sungwoo’s eyes.


“i’ve failed because of you! if an ignorant guy like you had not disturbed me, i would have–”at that moment, sungwoo cut off one of his arms.
“ahhhhhh!”dr.
 yu grabbed his cut area and bent down in pain.
sungwoo sighed, putting the grim reaper on his shoulder, “you seduced the survivors by pretending to play the government role and held numerous human beasts here to experiment with them freely.
 was that all you could do as a man who predicted the coming of this hellish situation?”“argh…”“because an insane guy like you is pretending to be the world’s best elite, humans have been suffering without doing anything.
”sungwoo pushed the sickle into his neck.
“if you had known this could happen, you should have acted a little more responsibly, you useless junk!”“sense of responsibility? you need responsibility when you can be responsible for something.
 i didn’t feel any need to take responsibility for this damn human world.
 this world is finished anyway.
 what can i gain from it? why is it important, you ignorant bastard?”dr.
 yu would not give in.
 it seemed that he would not give up his wrong conviction until the moment he died.
“so, what did you find?”“world eater.
”‘world eater?’ sungwoo frowned at it.
 it was a strange word, but he had an ominous feeling.
“it is an absolute being that will lead us to transcend.
 they are watching us even at this moment…”having said that, he turned his head and started to stare at the ground in the middle of the cavity.
‘something is looking at this place now?’sungwoo put his hand in his pocket.
-off air (-)‘is it at least different from the creator imoogi mentioned?’if that’s the case, “world eater,” the unknown entity dr.
 yu has been serving, could also be just one element of the system.
“world eater? what is that?”“i swore to them that instead of being reborn as a transcendental being, i would give this earth to them.
 but i couldn’t keep that promise…”

 