\section{chapter 242}

                            according to the white wolf’s advice, sungwoo went towards the 12 o’clock direction.
 when he destroyed the wall, a huge vertical passage appeared.





“yeah, this is the elevator he mentioned,” jisu said.
it looked like a passage through which only a secret elevator moved.
so, sungwoo stuck his head out and checked inside it carefully.
 an unpleasant wind blew from inside, but there was nothing but darkness in the bottomless pit.
the 8th basement floor was only 5 stories below them, but it looked quite deep because the stairs were rather high.
sungwoo summoned some zombie monsters and slowly went down with jisu.
 fortunately, there was nothing that stood in their way until they reached the 8th basement floor.
jisu, who always mobilized all her senses to monitor her surroundings, felt more relaxed.
“there is no resistance.
 it’s quiet,” she said.
“i think he gave us the correct direction,” sungwoo responded.
if sungwoo and jisu had tried to crush the stairs and elevators, not to mention the floor, to go down to the 8th floor, they would have encountered considerable resistance along the way.
“we’re almost there,” sungwoo said.
finally, they arrived on the last floor of the core building of the evolution society headquarters, the 8th basement floor.
“there is only one road,” jisu said.
a huge horizontal passage like a tunnel unfolded before them.
 unlike the research facility on the upper floor, it was a space that had not been maintained at all.
as if it was left behind after a huge creature dug through the ground, there was no trace of human touch at all.
sungwoo and jisu stepped inside.
 they walked through the passage for quite a long time.
whooooooooo-at that moment, an unpleasant wind began to blow.
 the wind was flowing from deep in the horizontal passage.
“it’s hot.
”
as jisu said, the wind blowing from the basement was quite humid and hot.
so much so that they would be burned if the hot wind touched their skin.
she wiped off her sweat, revealing her anxiety.
“sungwoo, it keeps getting hot quickly.
 if it’s this hot…”even though they didn’t go deep inside, the wind’s temperature was rising rapidly.
 they could hardly breathe in now.
 it was ominous.
 jisu keenly felt the unknown threat right around the corner better than anyone else.
the next moment, she was astonished to find something.
“this is a dangerous place! we have to get out of here right now!”goo goo goo goo!soon, a tremendous vibration shook the entire passage where they were standing.
something huge was pouring out through the hot passage.
“step back!” sungwoo shouted at her.
sungwoo then pulled jisu back right away and summoned “bone drake” and “bone wyvern alpha male” right in front of him to use them as protective shields.
 as expected, the two monsters completely blocked the huge passage.
 at the same time, sungwoo formed a bone shield and stuck it into the floor.
soon, the front of the passage began to glow orange.
 something hot was very close to them.
‘it is fire.
 an incredible fire pouring out.
’sungwoo and jisu had no time to escape.
 they would have no choice but to collide with it.
“get out quickly! i’ll be blocking it! i have fire immunity!” sungwoo shouted at jisu.
fortunately, sungwoo had 40% fire immunity thanks to the title of “professional dragon hunter”, and he got 30% fire immunity and 70% fire immunity by combining “drake’s leather” with the shadow king’s robe.
but jisu had no way to bear the intense heat.
 so, sungwoo had the ogre skeleton grab her and get her out through the entrance they came through.
 then, he summoned more undead to block the cave completely.
 he had to hold out there until jisu safely escaped from this place.

– warning! ‘underground rage’ is flaring up!the intense fire was everywhere, dyeing the area red.
“what the heck is this…?”it was as hot as, or even more than, the fire of hell he had experienced before.
‘i can’t stand this either!’sungwoo stepped back because he realized that even with 70% of flame immunity, he couldn’t withstand it.
at that moment, sungwoo thought of one item, so he pulled out a small bead-shaped item from his pocket.
[item information]-name: hellfire armor-grade: special-category: reversion item-effect: you can use ‘hellfire armor’ when you are equipped with it.
 (defense +50% magic immunity +30% fire immunity +100%, fire damage increase +20%)-description: when you are equipped with it, the size of the item is automatically adjusted to your body.
 you can’t take it off once you wear it.
it was an item sungwoo obtained by killing the hell moving armor, the flame from hell.
when sungwoo wore it, his fire immunity increased by 100%.
 as a result, if he added the 70% immunity he currently possessed, his immunity would reach 170%.
-would you like to wear ‘hellfire armor’? (y/n)* this is a reversion item.
 you can’t take it off once you wear it.
 (however, when you don’t want to use it, you can store it in the form of mana in the ‘pattern of the wrist’.
)it was a reversion item, but it didn’t mean that he should always wear it.
 he could store it in an invisible shape, but he could not afford to ponder over it for a long time because a huge column of fire would devour him at any time.
“wear it!”-‘hellfire armor’ has been applied to you.
at that moment, sungwoo’s body began to be equipped with the armor.
the black iron armor stretched out across his body then assembled to fit his body.
at the same time, flames rose from all over his body.
 of course, it took effect right away.
‘i don’t feel any heat anymore.
’-‘salamander’s aura’ is given to you because ‘fire immunity’ exceeds the given value (150%).
* a ‘burn’ effect is applied to all your direct attacks.
* if you are hit by a ‘flame attack’, your health will be restored.
 (+1%)with that message, the red flames covering his body began to change into blue flames.
‘it feels cool rather than hot.
’surprisingly enough, sungwoo didn’t feel the intense heat of the cave anymore.
the higher the temperature of the fire, the closer it was to blue.
 sungwoo’s body was hotter than the overwhelming flames emanating from the passage.
the next moment, a swirling wave of the flames rushed in.
 the column of fire had finally arrived.
quaguaguaguagua!all the undead quickly turned into ash in the intense heat of the fire.
 it wasn’t the kind of heat that they could endure.
the column of fire swallowed up sungwoo.
 a tremendous roar, so powerful it almost tore through his eardrums, shook his auricle.
 the outer walls of the cave were shattered by the heat, and a pile of dirt flew behind him.
 like the blade of a mixer, the column of fire swept over everything inside the passage.
“…”

however, sungwoo could easily withstand the heat and stand firmly in his place.
 it looked like he was facing a strong wind.
ooh ooh ooh-soon, as if a gust of wind passed by, the powerful column of fire disappeared behind him.
sungwoo took off the hood he was wearing.
“if this was all the attack you prepared, it’s my turn…”soon, green eyes lit up one by one amidst the burnt ashes, and hundreds of undead began to resurrect immediately.
“you are finished!” sungwoo shouted at the boss monster.
the necromancer’s undead army began to advance along the path the huge flames swept across moments.
jisu was safe because sungwoo quickly pulled her back and evacuated her to the point where the flames could not reach her.
before he advanced to chase the boss monster, he said to her, “we never know how far this road will go, and if you face the flames in the middle of the road, you won’t be able to avoid it.
 so, please defend in the rear.
”“…”sungwoo wanted her not to go further down the road, but to stay behind and wait for his return.
she couldn’t hide her displeased expression, but he was right.
 if she went further recklessly, she would most likely be killed for no good reason.
“understood.
 but if i don’t see any flames coming out after you enter it, let me go in then.
”“you must be careful, though.
”jisu was a stubborn woman.
 she hated being a burden on him.
“then, see you later.
”sungwoo went into the passage.
 his undead troops were already waiting to go with him.


 