\section{chapter 365}

chapter 365: devil’s world tree and world eater (7)one by one the skeletons crawled out of the pile of bones.
 then, they picked up their weapons and lined up in a line.
 they began to snowball to hundreds in an instant.
 they slowly raised their heads.
 a blue eye light was emitting from their hollow eyes.





- you are given the command over the apocalypse army (prisoners).
* assault warriors of the ancient conquest empire (150 players)* shield warriors of the ancient conquest empire (150 players)* elite archers of the ancient conquest empire (150 players)* iron armored knights of the ancient conquest empire (50 players)* dark priests of the ancient conquest empire (50 players)sungwoo didn’t know the details about this skeleton army, but all of them were fully armed.
they were not simply wearing shallow armor, but they were armed with items containing magical power.
 they seemed to be at least hero level.
‘each of them is a well-armed player.
’sungwoo noticed that purple chains were wrapped around their necks.
 he didn’t know much about it, but it seemed that he could control them with the chains.
rattle! rattle!they numbered a total of 550.
 while they were raising their bodies on the ground and sorting their weapons, 550 extra shadow soldiers were created.
 it was a moment when 1,100 soldiers were recruited at once.
so now, under the root of the world tree, it seemed that the huge underground space was reminiscent of the terracotta army of emperor qin’s mausoleum in china.
“rattle! master, you are truly the lord of death!”victor, the natural undead, grated his teeth, with both hands trembling violently as if he admired sungwoo.
“wow! they befit the title of the undead corps!” said minseok, who couldn’t help but admire sungwoo, either.
honestly, sungwoo was surprised because the power of his army increased tenfold in one day.

but that wasn’t the end.
 immediately after sungwoo summoned the apocalypse army, a black wave spread across the ground.
 it was as if the water was filling up.
whoooooooo-and gray smoke slowly rose.
- a certain area (10km) has been declared as a ‘death place’.
this was the effect of the famine power among the ‘power of the 4 knights of apocalypse’ skills.
- the area (10km) will temporarily enter the ‘abyss’ and ‘space overlap’ state.
* the ‘people of the abyss’ takes effect.
 the attack power and defense power of the undead army increase.
 (+10%)* random grade ‘ownerless zombies’ are generated in random numbers (maximum 5) at a certain period of time (1 minute).
‘zombies can be replenished in real-time?’‘death place’ overlapped with the space called ‘the abyss’, which was like the hometown of the undead.
 in other words, sungwoo’s army was going to grow more and more as time went on.
with such an overwhelming force under his control, sungwoo looked up at the world eater, whose face turned even more gloomy.
“what do you think? do you still think i’ve not changed at all?” sungwoo asked.
“…”“yeah, if you still don’t know, let me make you feel it.
”at that moment, sungwoo’s undead army began to move and turned into a huge wave to charge at the world eater.
 hundreds of bows and magic were fired, followed by the arrival of more undead troops.
rattle! rattle! rattle!along with the footsteps of the undead army, the sound of their bones clashing resonated through the unknown space.

‘they are heavy.
’obviously, sungwoo felt something pretty different from when he mobilized a couple of undead armies in the past.
 the difference was so huge that he felt like he was running a large truck instead of a small car in the past.
‘yeah, it means they are very destructive.
’the attack by such a large number of the undead army was unprecedented.
the new ‘apocalypse army’ was definitely different from the general skeletons.
 even though sungwoo didn’t give them an order, they knew how to use systematic tactics on their own.
they divided their forces and surrounded the enemy.
 the skeletons with the shields advanced first.
 by the time the ‘dark priests’ were giving buffs to them, those in the rear fired shots at the world eater all of a sudden.
shhhhhhhhhh!they also threw things like bomb sacks, which released abyssal breath while they were exploding.
rattle! rattle!seizing the moment, the ‘iron armored knights’ rushed toward the world eater.
they were so swift and overwhelming that they would have smashed the typical enemy in an instant.
 but their opponent was the mighty world eater.
“are you going to kill me with such shabby tactics?” the world eater shouted.
as expected, the world eater was not an easy opponent.
bang!the moment he set foot on the ground, a shock wave was generated, blowing away the armored knights who were closing in on him.
then his sword burned red, which was about to explode at any moment.
feeling uneasy, sungwoo backed away as far as possible.
at that moment, the world eater swung the sword at sungwoo.
kwagagaga!a pillar of fire erupted, but the skeletons threw themselves first to form a shield to protect sungwoo.
‘fire breath?’it was an overwhelming flame that could be called the dragon’s flame breath.
dozens of large skeletons melted in an instant.
 if they melted like that, it would be difficult to resurrect them, sungwoo thought.
“necromancer!”when faced with the undead army charging at him with vehemence, the world eater smashed them one after another, targeting sungwoo’s heart.
‘you can’t come close to me.
’stepping back, sungwoo analyzed the situation.
 he might have had his heart taken away by the world eater if he had not obtained the power of the 4 knights of apocalypse.
no matter how many skeletons he had dispatched to block the world eater, the latter would have broken through them and dealt a fatal blow to sungwoo.
‘but you can’t do it now.
’sungwoo became much stronger than before.
 so all the world eater could do was to get out of sungwoo’s fierce attack.
“finally, that monster is getting exhausted.
’sungwoo could see the world eater’s mouth slowly opening.
‘how can the level 43 knight-type player get exhausted so easily?’sungwoo thought it was strange.
 even the tsar, who was much lower level than the world eater, confronted sungwoo’s undead army but never showed he became exhausted.


‘obviously, the world eater’s condition is not good.
’since he had been asleep in the capsule for a very long time, it looked like the world eater had a mental and physical problem.
 besides, he wasn’t armed with any items, so it was obvious that he couldn’t show his skills fully.
‘yeah, i can beat him!’dodging his attack adroitly, sungwoo took out another item.
[item information]- name: bi hyong’s fan- rank: mythical- category: wand- effect: increases magic immunity (+15%).
 it can summon the souls of the dead (ghosts).
 (maximum 10) the performance of the ghost varies depending on the user’s affinity for the ‘death trait.
’- description: it contains the spirit of ‘the one who controls ghosts’.
woooooooo-ten spirits appeared around sungwoo.
- you can control the ‘ghosts’.
 (your affinity for death traits is the highest level.
)* not affected by ‘physical attack’.
* you can ‘control’ the weapons of ‘all grades’.
* you can issue the curse of ‘confusion’ to the attack target.
* you can ‘infuse into’ a target below a certain level.
sungwoo scattered all his items in the air.
 at that moment, ten ghosts ran toward them and snatched them away.


 