\section{chapter 471}

cronos swung the scythe at the demon king.





whooooooooooo-a gust of wind blew even with a simple movement.
the scythe was not fixed in its length and shape.
 its length and shape changed, depending on the enemy's location and direction.
 anyway, the sickle made of smoke stretched out through several kilometers of space at once and struck the demon king's left shoulder.
two arms were severed in a single blow and bounced off.
the demon king's left head screamed.
 but the smoke scythe struck back straight away, grinding his middle head and right head.
 eight red beams were emitted simultaneously and pierced through cronos' body.
whoo-woo-woong-but the red beams flowed through the body made of smoke and scattered into the air.
 cronos suffered no damage.
'invincible?'they were summoned for only 100 seconds, but they basically could not resist the opponent's attack.
in the meantime, cronos swung squitte once again, cutting the demon king's one more arm.
 then he stretched out his left hand and grabbed the demon king's right head forcefully.
flop.
 the demon king's right head, which was just healed after being melted by dragon breath, was smashed at once, and his four eyeballs popped out and fell to the ground.
 but cronos could no longer attack him because the given time of 100 seconds was up.
- the sealed, cronos' unsealing time has expired.
 so he has been resealed.
 (cooldown: 72 hours)you are lucky.
the squitte that cronos was wielding stopped in the air.
 then a white chain came up from somewhere, then shackled cronos' neck and arms.

shortly afterward, cronos' body, namely, black smoke, began to be sucked into the magic circle drawn on the floor.
 in sungwoo's eyes, this was a moment he regretted because cronos could have killed the demon king with a little more time.
 'he could take the demon king's life.
'the source of this content is lightnov­elworld.
c­omif only he had one more minute, he could do it.
 'but i can't wish for sheer luck like that.
'this was a game.
 the rules of the game were by no means fair, but it was natural to put a tight limit on somebody with tremendous power.
the demon king was covered with wounds all over his body after he was attacked for only 100 seconds.
 "sungwoo! he is starting to recover!" junghoon screamed behind his back.
sungwoo also confirmed that the hell creatures were quickly crawling and melting into the demon king's wounds for his quick recovery.
 but sungwoo would not want to let him recover this time.
 'well, let me open his wounds and break his heart.
'sungwoo riding on bone dragon soared into the air.
"let me kill you completely.
"sungwoo mounted a frontal attack against him again.
gigantes took the lead.
 the four giants advanced, pounding the ground.
 thousands of undead were following them chaotically like a pack of undisciplined dogs.
'let me kill him before he recovers his arms and hair.
'his arms and head were the demon king's main weapons, but some of them were lost while he was confronting sungwoo.
 in other words, he exposed his weak spot.
 
kuruk- kuruk- kuruk-the bundles of tentacles that made up the demon king's lower body were spreading sneakily along the floor.
 they were trying to wrap and kill gigantes easily.
"you won't make it this time.
"but unlike before, the battlefield was full of all kinds of corpses.
 sungwoo felt it uneasy to touch the corpses of hell creatures and players, not to mention allied players, but sungwoo could not afford to think about it.
"explode!"bang! bang! bang!visit to lightnovelworld.
c­om discover new novels.
when a chain explosion occurred, tentacles that had been crawling along the ground were engulfed in flames.
 the explosion was not destructive enough to cut off those thick and tough tentacles at once, but its impact made them stop it for a while.
in the meantime, sungwoo took another action.
 he threw himself off the bone dragon and muttered, "manufacture bone weapons!"the bone dragon and the bone wyvern alpha male who followed him began to split themselves and fell to the ground, then began to merge into a new form.
it was an oversized weapon.
 axes, spears, and hooks of enormous size fell and got stuck on the ground, but four gigantes rushed toward them and pulled out their weapons.
thump- thump- thump- thump-giants with hundreds of meters of "dragon weapons" rushed fiercely towards the giant who was bigger than them.
'come on, use the beam.
'the demon king used two heads to emit eight beams to confront cronos a little while ago, so he could use only his left head and four beams.
if the demon king used up the remaining four beams, they could approach him more easily.
 'the cooldown of the beam is about 5 minutes.
 and that's enough time.
'if the demon king could no longer use the brutal beams, the world tree camp could successfully mount a frontal attack against him.
but instead of the beams, the demon king stretched out his hands and fired waves.
 obviously, he saved the beams for his more decisive attack.
 even the waves pushed gigantes to block him from approaching.
but while the demon king was focusing on gigantes, someone was moving in a place invisible to him.
 since he could not move freely because his right hand was smashed, the demon king could not notice it.
 soon someone got close to his left head, or the back of his left head.
"hi.
" it was none other than jisu.
 "i'm back.
"she bothered to open her mouth and draw his attention.
 he turned his left head to her right away.
 'now is the time!'the demon king's eyes monitoring the battlefield disappeared drastically.
 this was a golden opportunity for sungwoo to attack him.
 so sungwoo controlled gigantes to do something.
'throw it.
'the most up-to-date novels are published on lightnovelworld.
comgigantes stopped charging at the demon king, then stepped back.
 then he pulled his right leg back and held a spear made of dragon bone upside down.
 then he pulled his shoulder behind his back.
'it's a javelin.
'sungwoo used javelins very well in the early days when the world turned into a game.
 shortly afterward, gigantes moved resiliently and threw hundred-meter-long spears at the demon king.
tung- tung- tung- tung-with a force stronger than any other aerial weapon, the spears were thrown toward the target strongly like a missile thrust.


puck! puck! puck! puck! four spears penetrated all over the demon king's thick body.
 his two arms drooped.
 and his one head and five arms were maimed.
'alright! now is the time!'even though the demon king had some beams, sungwoo could not wait any longer.
 the thing was the king lost most of his defense.
 so sungwoo turned his head to find junghoon, who was leading the few remaining special commando unit members and the hippogriff squadron.
"cover me!"shouting at him, sungwoo climbed on top of the zombie hippogriff.
 junghoon and the special commando unit immediately followed him.
 "cover the necromancer!"when junghoo shouted, one griffin and 21 hippogriffs speeded up while dispersing in all directions.
 sungwoo took out the bow tied around his waist, 'superheavy bow.
''let me blow him with a single shot.
'then, he took out the 'superheavy arrow' hanging behind his back.
'let me kill him once and for all.
'he strung the superheavy arrow on the superheavy bow to aim at the demon king.
follow new episodes on the lightnov‌elworld.
com platform.
but the demon king was also watching him sharply.
 his head was in the center and three of his four eyes were keeping an eye on sungwoo.
 his three arms were intact and functioning fully.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 