\section{chapter 358}

chapter 358: jeju island and attack on demon’s cave (22)dozens of monsters that had already escaped the portal were scattered here and there, harassing the players.





“don’t worry about the portal.
 just focus on killing them first!” inho shouted.
when they repositioned those near the portal, they could deal with the monsters more efficiently.
 thanks to valkyrie’s warriors blocking the gate of the demon’s cave, the players could play their role faithfully while remaining composed.
it was as if the machine, which stopped because of a malfunction, came back online.
“good! let’s help valkyrie then!”if so, it was time to thoroughly seal the gates of the magul from now on.
“move calmly and efficiently!”it was time for them to shut the gate of demon’s cave completely.
“move slowly and efficiently!”suddenly, their panic caused by fear was gone.
 with the priests putting up a shield, the snipers assisted the players’ attack, and ice-type wizards froze the monsters coming out of the portal.
then, einherjar’s attack became even more lethal.
 they ran wild without hesitation, killing the monsters with a single strike.
- you have obtained 846,000 gold by killing ‘an alien’ (intermediate monster)’.
- you have obtained 821,000 gold by killing ‘an alien’ (intermediate monster)’.
jisu kept killing the monsters.
- you have leveled up.
 (lv.
 22)her level went up again.
 the second floor of the gate of demon’s cave was a dungeon suitable for those whose level was 43.
 it was natural that she acquired lots of exp points.
that wasn’t all.

[exclusive quest]- title: guardian’s qualifications- type: remove target- goal: eliminate the boss monster ‘commander of demon’s cave’- compensation: choose between the ‘regular deity’ and ‘the right to change your occupation.
’*you are fighting against the alien beasts that invaded this land.
 as a result, you are given the opportunity to obtain the title ‘guardian’s qualifications.
’if jisu eliminates the core entity (boss monster) of the invasion force, she will be able to send a strong warning message to the invaders.
* the boss monster ‘commander of demon’s cave’ will appear after the ‘second wave’ is over.
* if you can’t kill the target within 24 hours, you will not be able to earn the title of ‘guardian’.
‘guardian?’she knew that sungwoo already had the title of guardian, so she thought that this was a title that only a giant like the necromancer could get.
‘well, finally i can…’in fact, this title was very hard to obtain, but she already reached a level high enough to challenge that title.
in the meantime, the expedition team led by sungwoo walked down inside the demon’s world tree for quite a long time.
since the tree was extraordinarily large, enough to cover the whole area of yeouido, it was not easy for them to traverse it quickly.
“gosh, it seems that we have now reached the lower end of the trunk of the tree.
”
they seemed to have walked down deep inside.
“by the way, there is a huge facility here.
”they knew that the inside of the devil’s world tree had been artificially built up by someone, but the further they went down, the more traces they could find.
 stairs continued along the wall from a certain point, and some spaces of unknown purpose came out, which were made by digging into the wall.
they went down the stairs for several minutes when suddenly darkness fell.
 the expedition stopped moving.
“what the hell is this…”the ray of light from the lanterns the expedition members were holding did not work.
 the light wasn’t gone.
 when they reached the end of the wall and the ceiling continuing on the right, there was an open space, so their lanterns were useless.
 an incredibly wide space engulfed the light of the lanterns.
“cliff!”a dark abyss spread out to the right of the revolving stairway.
“what a huge space!”there was a huge cave in the lower part of the devil’s world tree.
 the wall on the other side could not be seen as it was buried in darkness, but it seemed wider and taller than a domed stadium.
‘it’s impossible for a tree to grow as big as this.
’obviously, somebody created this space by damaging the world tree.
if that was the case, there was a high possibility that they could find the facilities of the fallen down there.
 and probably there could be the ‘heart of the gate of demon’s cave.
’one wizard cast fire magic down the cliff to measure its height.
 but before it hit the floor, the fire scattered.
“it’s too deep.
 i can’t measure it.
 i think it’s at least four hundred meters deep.
”four hundred meters? sungwoo doubted it.
 so he summoned two bone wyverns.
“no matter how deep it is, we can now go down quickly.
”the expedition team led by sungwoo could quickly finish the tedious journey that made them feel as if they were exploring a narrow tunnel.
the two bone wyverns were barely hanging on the revolving stairway.
sungwoo jumped on the wyvern’s back and shouted, “come on, everyone get on board!”when they got on the two bone wyverns, they spread their wings and thrust their heavy bodies into the darkness.
“it’s like we’re going down in a submarine,” kyungsoo said.
like he said, they felt as if they were riding a submarine made of bones and sinking into the dark sea.
they descended as slowly as possible because they didn’t know if there was a trap.
the crew members held the bones of the bone wyvern tightly and lay flat to protect their heads while staying on alert.
sungwoo checked out the wall closely and found out that some unusual traces began to appear on the wall.
‘what the heck is this?’the surface of the wall was mangled by something sharp.
 three lines of scratches scattered at regular intervals were the marks of the claws of a giant beast.
‘it is a very large beast.
’each claw was probably 25 centimeters wide.
 considering that the claws of the wyvern were 8 to 9 centimeters tall, it was possible that this beast was several times larger than the wyvern.
‘there was a big battle here too.
 did the guardians who didn’t fall into the trap come all the way down here to confront something?’judging from the fact that there were a lot of traces of attack magic, such as the traces of claws and the cracks and blackened marks on the wall, it seemed that there was a battle between the owner of the claws and a number of players.


“…”all the crew members witnessed the terrifying traces, but none of them mentioned it recklessly.
 but it was clear they had goosebumps at the moment.
was it possible that the beast that made such marks was sleeping down there?“if you look at a fantasy novel, this is usually a bad sign…’ hanho said, expressing unease.
sungwoo was imagining who could be the owner of that claw at that moment.
“i can see the bottom!”two bone wyverns landed on the bottom of the cave.
 at the same time, the crew members jumped out in all directions, raising the lanterns and weapons.
“it’s safe here!”“it’s safe here too!”after checking all directions, they waited for sungwoo’s order.
sungwoo lifted the lantern and scanned the bottom.
“it looks like they had a fight here as well.
”a number of bones and items were seen scattered when sungwoo turned the lantern light toward them.
 and there were even several flying weapons.
 it seemed that there was a much larger battle than thought.
“sungwoo, is this a golem?” hanho asked from behind.
sungwoo and kyungsoo turned their heads.
“oh, my god! so huge!”several huge objects were leaning against the wall.
 they looked like giants in armor.
judging from the rust on the surface, they were made of metal, and they felt like statues of heroes found in the ruins of a ruined civilization.


 