\section{chapter 44}

                            “what the fuck are you talking about? are you kidding me? okay, let’s say you’ve intruded this place.
 what are you going to do alone here? huh?”




the branch manager felt keenly that in this world that changed like a game, he could do nothing alone.
 that’s why he blindly trusted the man called the representative.
 the representative was a leader who led the group with an absolute hand forged with the oath of blood.
but the young man was still smiling.
 why?the young man opened his mouth, “i liked being alone.
”“what, what the heck is this?”“uh?”and a red warning message appeared before the branch manager’s eyes.
caution! “fellblade” is now in your area!soon, black smoke exploded and filled the inside of the factory.
“ahhhh!”“argh!”screams of death broke out from everywhere.
-you have been possessed by the curse of death.
 your stats are greatly reduced.
at that moment there was something behind the black smoke.
“what a cool skill!”they were none other than the white demons that appeared all of a sudden.
fellblade, the sub-effect of ‘vacant sanctuary,’ was a skill that spread curses to the affected area when a large number of subordinates were summoned all at once.

as it turned out, the “triggering condition” of the skill was to summon at least ten subordinates.
 as a result, the black smoke was enough to fill the small factory, and skeletons began to take shape everywhere.
“cough! cough! argh!”“block them!”as the skill grade of fellblade was low, the black smoke quickly dissipated.
 however, the branch manager’s momentary embarrassment was enough for sungwoo to use his fatal weakness.
“ahhhhh!”screams were heard everywhere.
 and along with the screams, the sound of creepy bones clanking against each other rang.
rattle, rattle…“wake up! they’re all scarecrows anyway! all you have to do is kill the bastard controlling them.
”the branch manager shouted at his men hanging from the railing on the second floor.
the moment the smoke spread, he jumped and grabbed the railing.
 he had something to trust.
 he thought that the three vampires, including himself, were powerful enough to overpower ordinary monsters and players incomparably.
 therefore, they could kill a ‘rat’ like sungwoo.
“that bastard!”then he found a man in the scattering smoke massaging his wrists after releasing the rope, namely sungwoo.
crackle!next to him was right, the goblin skeleton.
 right broke the rope around his hands.
“kill that bastard first!”the branch manager yelled, but nobody followed his direction.
 in fact, they couldn’t.
bang! clang!they were already struggling to beat their opponents that were everywhere.
“they’re coming from there, too!”“damn, tell the security guards outside to come in!”
ordinary players barely could confront the orc skeletons.
 however, if they had the misfortune of confronting the werebear skeleton…the vampires tore apart the orc skeletons without any difficulty, but the situation didn’t get better.
“what the heck! they are being resurrected!”-the dead has become your subordinate under your authority.
they now faced the strange phenomenon of the monsters’ bodies piled up in the factory, reviving.
 the corpses they collected to get meat, bones, and leather after dissecting them revived and walked toward them with glittering red eyes.
 they were now shuddering with fear.
the branch manager stared at sungwoo, gnashing his teeth because he realized that there were no subordinates to help him.
“hey, branch manager? when the branch here disappears, what title are you going to use?”his face turned red at sungwoo’s provocative question.
eventually, he couldn’t stand it anymore and charged at sungwoo, kicking the railing.
 but sungwoo stepped back and disappeared into the thin smoke.
 the branch manager, checking his movements, quickly landed on the ground and chased him.
at that moment, however, something flew toward his face.
puk!the object was broken to pieces with a dull sound.
 and the liquid in it was splashed over his face.
“ahhhhhh!”the branch manager held his face and stepped back.
 it was also ‘slime liquid.
’ the tremendous amount of acid melted his hair and skin.
puk!then, while he was groaning with pain, a spear made of bones flew and struck his left shoulder.
rattle, rattle.
after that, right charged at him.
 although he hurriedly pulled out a kukri knife, he slipped while his knife clashed against the other party’s sword.
 this time again, the synergy of the “one-armed warrior” right was triggered.
its saber cut deeply through his right thigh.
the branch manager, covered with wounds, gasped for breath and stared at sungwoo and right.
 in addition to the apparent damage he took, his whole body was contaminated with all kinds of curses.
-‘curse of death’ reduced stats.
-contaminated by ‘devil’s blood,’ his health will continue to decrease.
not only the curse of fellblade, but also the ‘devil’s bloodstone’ that sungwoo obtained by killing the chief orc was taking effect.
 it was a terrible weapon that burned the mana of the opponent and consumed his health until there was no mana left.
and vampires had no mana in the first place due to the characteristics of the vampire clan.
so this item was the natural enemy of the vampires, which sungwoo didn’t realize at all.
but that was not the end.
“maybe i should use this skill too.
 it’s been a while.
”sungwoo activated the red bracelet on his right wrist.
wild madness has been triggered!increases attack power (+10%) and attack speed (+20%) against ‘goblin-type’ mercenaries for 10 minutes.
it was a useful item that sungwoo used when carrying a large number of goblin skeletons, but now the target of its application was only right.
 however, right always did its share faithfully.
bang!the results of the fighting between those with huge buffs and their opponents with huge debuffs were obvious.
 sungwoo and right gradually closed in after surrounding him.
in the meantime, the factory door opened and six security guards entered.
 hearing that their members inside were knocked down, they came in a hurry.
however, the first thing they saw was a 2 meter 50 cm black skeleton holding their colleague’s cut arms and legs.
“uh…”they had no other choice but to stop at the entrance.
 however, that was their mistake.
 they had to turn back and run away because the werebear skeleton and beasts made of bones rushed at them.


puk!their lower bodies were crushed by their kicks, and their smashed shoulders bounced off the concrete floor.
meanwhile, a bus was rushing toward the factory that turned into a mess.
bang! screech!the bus trampled down the gate and entered the factory.
 then, the bus braked shortly afterwards, and jisu, hanho, and kyongsu came out of the bus.
“over there!”they ran straight and freed the detained hostages.
 meanwhile, hanho’s parents threw the bone weapons that sungwoo had made out of the bus windows.
“move! if you get hurt, get on the bus right away!”“kyongsu, i can fight!”“okay, take the weapon.
”all this was taking place according to sungwoo’s planned operation.
 namely, he would enter the factory alone to confuse the vampire and his gang members inside through fellblade, then save the survivors by attacking them.
 the instant the survivors grabbed the weapons, sungwoo’s allies would be now superior to them numerically.
 now, it was certain that sungwoo’s party would prevail.
the branch manager looked around and could not hide his embarrassment.
 all the people he had kidnapped were released, and his subordinates fell to the ground without any exception.
looking at him, sungwoo laughed and ridiculed him by saying, “oh my god! your branch has really disappeared!”how did he, faced with defeat and death, feel humiliated by the opponent? the branch manager felt an indescribable anger.
 and something wiggling deep inside beyond his control began to dominate his whole body.
 at that moment, a familiar voice was heard in his ears.
‘what the heck? that guy is a bit strong.
 let me give you my power.
 kill him by all means.
”it was a sweet voice.
“argh!”he vomited out blood.
 then he couldn’t even scream at the pain of his whole body twisting hard.
 his shoulder bones broke through the flesh, while his skull tore his melted face and came out.
“what the heck is that?”“man, he was not a human!”

 