\section{chapter 330}






 after checking out the situation, the liberation guild decided to take over the post-war reconstruction of seoul and manage the prisoners there.
sungwoo and the rest of his party opened the ‘hyper gate’ to return to suwon.
“man, i’m so tired.
 whew! we can take a break now, right?”“yeah, me, too.
 i want to take a break.
”even jisu complained she was too tired.
 in fact, the fiercest ever fight was over.
 it was natural that they were exhausted while feeling finally relaxed after the war.
mir already fell asleep in sungwoo’s arms.
 everyone was desperate for a break.
“uh? why don’t you guys take a break? i thought all of you were having a sound sleep by now,” hanho said.
 like he said, everybody was still at work in the suwon village even after the war was over.
 there were trucks with lots of loads driving here and there.
 they had already begun to restore the broken walls.
soon, muyon, who was checking at the collapsed wall, discovered sungwoo’s party and approached them.
“oh, you are here! thank you all.
 you guys really had a great fight.
”there was relief and relaxation in muyon’s expression.
“by the way, why are you not taking a break?”“oh, non-combat personnel can still work.
 so, we’re trying to temporarily repair a large broken hole.
 it won’t take long, so we’re going to take a break after we’re done.
”if muyon could use the “automatic construction” function, the restoration work would not be hard.
 actually, he could repair three holes without any big difficulty.
“even though we have won, we never know what will happen all of a sudden, right? our castle wall exists just in case.
”sungwoo nodded at his words.
 somebody like muyon who had a sense of responsibility was essential for the wellbeing of the organization.

“okay.
 by the way, thanks to the wall, you could hold out for a long time.
 it’s really fortunate for you to have built the castle wall in advance,” said sungwoo.
muyon smiled at him for his praise.
“but i need to reinforce the wall a bit more.
 in fact, it collapsed earlier than i thought.
 the moment the wall collapsed, it was really a close call for all of us here.
”the chinese bombing, led by admiral baker, was stronger than expected.
 so much so that not only the invisible barriers but also the wall collapsed like a sandcastle.
it was evident that if they had not built a wall, they would not have held out long and their village would have been devastated.
“now, don’t worry about us.
 just go and take a rest.
”“yeah, i guess so.
”sungwoo was also so tired that he couldn’t stand anymore.
sungwoo’s party headed to the main building of the world tree camp, namely the old museum building.
 then, they dispersed to their own quarters.
at the entrance of sungwoo’s personal office was hung a nameplate called “server master’s room”.
 it seemed that the general affairs department put it up even though they were busy.
“man, i’ve never been so tired like this before…”he felt his whole body tingle, but he still had work to do before taking a rest as the “server master”.
 in fact, it wasn’t a big deal.
 he needed to confirm all sorts of reward messages that he had slept on for a while.
 the first he confirmed was the message about the ‘acquisition of the title’ that always increased his capabilities substantially.
-the title ‘war hero (level 2)’ has been replaced with the title ‘war hero (level 3)’.
* all stats increase (+5)since he obtained the title after winning the 1st and 2nd korean-japanese wars, he obtained one for the third time, which increased his stats enormously.
he said, “open player profile.
”
[player profile]-name: sungwoo yu-level: 23-job: necromancer, black wizard-ability: muscle strength (44+13), agility (31+11), stamina (37+15)-gold reserves: 338,500,412he slowly looked at his profile with stiff eyes.
‘i usually have 57 muscle strength.
 in addition to this, all my stats increase by 25, including 10 from the lich effect and 15 from the anubis effect…then my muscle strength is 82…’sungwoo pulled out the myth-grade item “heavy bow”, which he had previously obtained from a secret shop.
[item information]-name: heavy bow-grade: myth-category: bow-effect: an ordinary person can never pull it.
 (condition for using: 100 or more muscle strength)*when you pull a bow, an arrow is automatically generated, and the “sun fall” skill is activated at the striking point.
+ fall of the sun: causes a wide range of explosions and flame magic near the striking point.
 care must be taken because it can destroy the whole area.
 (cooldown: 10 days)+ unconfirmed set effect: triggered when possessing heavy arrowsungwoo tried pulling it with force, but he could hardly pull the heavy bow.
as a matter of fact, sungwoo’s grip was strong enough to break even a steel bar, but he needed 18 more muscle strength points in order to pull this properly.
 it was literally so heavy that he didn’t know how to use it.
 anyway, it was useless for now.
“as expected, this was a necessary evil…”sungwoo confirmed another message.
-‘victory reward’ is given to the ‘server master’.
* war prize: 300,000,000 gold“300 million gold…”strictly speaking, he got much more gains than losses from this war.
 the gold he gained by beating the enemy, the items he obtained from the defeated enemy, and the airships laid the foundation for the growth of the korean server.
but he was not satisfied with the 300 million gold as a reward when tens of thousands’ lives were at stake in this war.
but that wasn’t the end of the message.
-the korean server will be given an ‘opportunity of counterattack (leadership)’ against ‘the other party (chinese server)’* when you decide to counterattack, you can take the initiative and decide on the ‘battlefield’ and ‘the type of war’.
* you can decide to end the war with the server master’s authority.
 (the war ends without any additional reward in that case.
)-if you decide to counterattack within 48 hours, the ‘counterattack’ effect is given to all your allies.


* all stats increase (+3)* moving speed increases (+10%)‘a counterattack effect? alright.
 the system wants me to go after the chinese server and completely destroy them.
’if the system wanted him to attack china, he was going to follow it at least for now because he didn’t have any intention of saving this bastard called the emperor of the chinese server.
“but this is not the right time.
”sungwoo decided to put off that decision for a while.
 if he chose to counterattack, the message that he would resume war would obviously appear before their eyes.
the war just ended.
 so, he needed to let his troops relax without worrying about another war.
sungwoo put the message aside for now.
“by the way, how long should i fight like this?”for the first time, he felt he was sick and tired of fighting.
‘why?’sungwoo took a nap, but he woke up three hours later when kyungsoo visited him.
“sungwoo, i checked everything as you said, but i didn’t see anything like that little statue.
 but if i discover something, i’ll let you know right away.
”“okay.
”kyungsoo searched general xing’s personal belongings, but he could not find the second statue, “sign of blessing.
”‘if so, there is a high possibility that it’s kept in beijing, china.
 they know it’s important, but they must have kept it in a safe place because it’s helpful in battle.
’

 