\section{chapter 383}

chapter 383: hephaestus’ forge (7)a huge number of airships filled the hangar, and not a small number of them were flying in the sky all the time to monitor the surroundings.





the whole area of the world tree camp was covered with the shadow of the world tree that soared up high into the sky.
 so it was natural that the outside players were amazed in admiration, feeling this space seemed like a completely different world.
“oh my god! what the hell…”even minhum, the deputy commander of the crusaders team, couldn’t hide his surprise.
 while he was approaching sungwoo, he raised his head and looked around.
“sungwoo, what happened to you?”although he admitted that the world tree camp was the largest team of the korean server, the gap between the crusader team and the world tree camp continued to widen beyond comparison.
secret? was there anything like a secret to the spectacular growth of the world tree camp?“well, i don’t know.
 there were so many guys who picked a fight with me, so i think i have obtained a lot while fighting them,” said sungwoo.
minheum shook his head at his reply.
“well, if you think that’s the secret, i don’t want to follow you.
”in fact, minhum watched him fighting those who picked a fight with him, so he knew how strong those who challenged sungwoo were.
aside from the liberation guild, other large organizations of the korean server also dispatched excellent troops to the world tree camp.
 for example, the hwarang guild that completely recovered from the damage they suffered from the korean-japanese war, the paju-uijeongbu allied forces that were once hostile, but now pledged allegiance to the world tree camp, the hunter company made up of a small number of elite players, etc…
but all of them showed the same reaction when they reached the world tree camp.
“wow, this is crazy! what the heck is this?”“i wonder if we can be of any help to them!”even though they maintained the hegemony of a certain region, they felt overwhelmed whenever they faced the world tree camp.
however, the allied forces of these groups were so powerful that sungwoo could not give them up.
 the fact that many different powers gathered under sungwoo’s world tree camp was quite meaningful in itself because they served as a central base to respond to the catastrophe that was driving the world to destruction.
***the commander’s meeting began with inho serving as the chair.
“first of all, on behalf of the world tree camp, i would like to express my gratitude to all of you who are here to help us fight the war.
 this is probably the most valuable moment since the game started.
”not only those players from all the servers of korea but also those from the american server, the taiwanese server, the canadian server, and the 2nd server in china were also attending the meeting.
 they would become the central members of the basic framework of the ‘control mechanism’ that sungwoo had announced on the air.
“okay, we’ve got only six hours left to choose the type of war with the chinese server.
 so, we’re going to have a strategy meeting to decide which environment and which rules are the most effective.
 by the way, we are going to share the information about the estimated strength of the chinese server first.
”the first to brief them about the chinese server was li wei, the only one who had experience fighting the ‘emperor’ of the chinese server.

but she confessed diffidently, “to be honest, i’m ashamed to say that i didn’t confront that bastard head-on…”li wei had been competing with the emperor over the hegemony of the chinese server for quite some time, but she said that she was just bent on stopping the emperor’s offensive rather than fighting him.
“the generals under the emperor are so strong.
 and there are so many ‘terracotta’ under their control…”just like those with 5-star jobs, the emperor had a job that allowed him to form a large army.
nobody knew exactly what kind of job the emperor had, but considering that he was controlling the earthenware doll ‘terracotta’ that had infiltrated the crusader team before, he seemed to be a 5-star ‘puppeteer’.
“to be honest, his army is similar to the undead army under the necromancer.
 as far as i know, they can’t be resurrected like the undead army, but it seems that the emperor can produce such disgusting toys endlessly.
 even now they are being produced and accumulated underground in beijing, i think.
”it was quite unpleasant to know that a huge number of earthenware dolls were being piled up even at this moment, just like the terracotta warriors of emperor chin’s tomb.
“if that’s the case, there would be no good in delaying the attack because it only gives him time to build up more troops.
”after li wei explained the situation, each group shared the information they had obtained in their own way.
 as always, the wide area surveillance team of the liberation guild and the intelligence team of the hunter company provided them with the most information.
based on their shared information, the participants kept exchanging views about the best strategy.
“we’re now in a position to attack the chinese server first after we have won big, but i don’t think it’s a good idea to choose beijing as the battlefield because they have been working very hard to confront us there.
”“well, wouldn’t it be right to confront them frontally instead of thinking too hard about the details? with the mighty firepower based on multiple airships and the defense power of the undead army, i think we can easily defeat them.
”“well, it’s not that simple.
 just like we did, they must have built a defense line that we might not be able to break through quickly.
 time is on their side if we delay further.
”sungwoo quietly listened to them exchanging their views and thought to himself, ‘other variables may not be that important.
 the most important thing we have to care about is the player called the emperor.
’the emperor’s power was thoroughly veiled.
 the one thing sungwoo knew was that what the emperor was controlling was dolls, not living creatures.
‘he’s a puppeteer.
 the puppeteer may be the worst match for me.
’to sungwoo, who could raise the dead and use corpses as bombs as his main weapon, the doll army that he could not resurrect for his own and a bomb was far from favorable to him.
‘while i was attacking the demons’ cave, i destroyed the enemy’s major forces.
 at the same time, i have grown stronger several times than before.
’singwoo was so confident in himself now.
‘of course, i have to find the best strategy before fighting the emperor, but what if i face the worst situation when i am way off base?’at that moment sungwoo was fiddling with an item he had prepared for such an occasion.
then, the item information appeared before his eyes.


[item information]- name: resurrection scroll (location designation)- grade: special- category: consumption- effect: when you die, you are revived at the designated location.
‘yes, i’ve another chance.
’it was an item he had bought a long time ago at the secret shop of gimpo international airport.
 he didn’t have to use it because he had never been defeated.
however, if he faced the moment to use it, he couldn’t guarantee that he could save the lives of those who came here with a total belief in him.
 that’s why he had to win by all means.
“well, you shouldn’t think of it as a simple matter.
”“but don’t you think you can find the answer easily?”they couldn’t find a common solution at the strategy meeting.
 basically, there were so many variables in the fight against the emperor.
however, an incident occurred that poured cold water onto their heated debate.


 