\section{chapter 158}

                             




“that’s true.
 when i dispatched the wide area surveillance team to confirm it, they confirmed a group of monsters driving flames in the pyongtaek and ansung areas.
”minhum reported to junghoon and sungwoo.
after sungwoo relayed the news to them, they confirmed it in four hours thanks to the wide area surveillance team composed of bandits and wizards.
 the group was formed urgently when sungwoo emphasized the necessity of an intelligence agency.
 the agency was growing into an organization capable of gathering intelligence in all the areas including the metropolitan region.
“the boss monster is a 4-meter armor type monster called ‘hell moving armor.
’ and there are dozens of ‘hell hounds’ around it.
 in addition, they are notorious for burning all the roads they pass into ashes.
 i’m afraid they will do us great harm.
”behind minhum appeared a screenshot from a magic drone on the screen.
 it seemed to be the city center of the southern part of kyonggi province, but huge flames engulfed the whole area as if a big fire had broken out there.
junghoon looked at sungwoo, covering his chin with both hands.
“so, does it mean they are coming to youngdungpo right now?”“i can’t single out youngdungpo, but as long as they are advancing north, it is inevitable for us to collide with them.
”it wasn’t clear how the twin ‘hell moving armors’ were moving together, but the problem was they were burning everything on the ground while passing by.
 if that’s the case, not only youngdungpo but also suwon would be in a dangerous situation.
“man, we were done stopping the chinese pirates; now, we’re faced with the monster in armor from hell.
 did you accept kangsok han’s offer, sungwoo?”kangsok suggested a game to sungwoo.
 namely, who was going to hunt the two ‘hell moving armor’ fastest? the winner would get the reward.
of course, kangsok didn’t tell junghoon about this, only saying he asked for sungwoo’s cooperation.
sungwoo said, “well, that guy suggested we leave today.
 i guess we shouldn’t be late.
 according to him, they are becoming stronger as time goes by.
”“then, by the time they arrive at youngdungpo, they will be much stronger than now, right?”“i guess so.
 so, we have to get rid of them as quickly as possible.
 oh, just in case, can you take some measures to evacuate the players in suwon?”“of course.
 let me help you with that matter.
”in fact, junghoon felt frustrated with the fact that he had to rely on the necromancer and take care of the people left behind, but he felt he had to put up with this for the sake of a great cause.
‘the most important thing is the establishment of a coalition.
 i should put this ahead of all else.
 when i establish the coalition, i’ll be in a better position.
”in a difficult situation like this, the necromancer was like a breakwater for the establishment of the coalition.
 without him, it would have taken junghoon much longer to achieve his goal.
‘that’s why i have to support sungwoo right now.
’at that moment, the door opened, and one of his crew members came in.

he relayed new information from the wide area surveillance team.
minhum checked it and said, “we have confirmed their route.
 as expected, they are destroying the places where player groups are staying.
”literally, they were hunting humans everywhere while coming north.
 it was now clear that the survivors’ village in suwon was in a dangerous situation.
“junghoon, you need to be prepared for their attack,” said sungwoo.
“if we fail to stop them, we have to make a plan to escape to kanghwa island.
”sungwoo nodded at him.
if the no.
 1 and no.
 2 players in the korean server failed to stop the twin monsters, it was logically impossible for anybody to stop them.
so, they had to set up a contingency plan.
 kanghwa island looked like a good choice.
 junghoon already thought about it.
“i think it’s about time we got rid of these parasites.
 i’ve been looking for a chance to get rid of those who were trying to do harm to us while pretending to be interested in joining our coalition, and i think this is the right time.
”in sungwoo’s eyes, junghoon referred to the reconstruction alliance.
“when this is over, we will form a new coalition.
”it wouldn’t be long before the birth of a huge organization that would fight against the hellish game.
***sungwoo went into the vip lounge with jisu and hanho.
 kangsok was also ready to leave.
he was wearing black ‘hard leather armor’ with a huge wooden cane.
 the head of the cane was shaped like a hawk.
 with a huge beak protruding, it seemed to act as a blunt instrument.
he looked at sungwoo’s party and raised his eyebrows.
“uh? i thought you were going alone.
 let me tell you seriously.
 your colleagues could be killed.
”hanho looked at him, embarrassed by what he said, then asked, “are they so dreadful?”on the other hand, jisu said confidently, “well, there was always a high chance we would be killed, but we have survived on such occasions, and the odds of our survival have gone up.
”kangsok said with a smile, “okay, i’m going to move to osan via teleport magic.
 nabi has already secured a teleport point.
 nabi, say hello.
”“this is nabi!”a blue-haired fairy, nabi, appeared on his right shoulder.
 hanho and jisu looked at the fairy in admiration.
 in particular, hanho opened his eyes and waved his hand.

“oh, hi, nabi!”but nabi turned her head with a sullen expression.
“huh! go away!”“uh? what the heck? why …”“it stinks!”“what the hell, what do you mean?”but nabi didn’t explain what she meant by that.
“now, let’s move right away.
”“good!”when kangsok said that, nabi flew into the air.
 then, she sprinkled her golden powder all over and held out her tiny hands over her head.
“we’re flying!”-you have ‘teleported’ to the designated location.
 (designated spot number 3)wuuuuuuuuuuung―“uh?”the next moment, they were standing on the osan station railway.
 they moved from youngdungpo to osan station in the blink of an eye.
hanho looked around with his mouth open.
 sungwoo also admired it.
“great item!”“right.
 well, she is most happy after eating, and this is her second-best skill,” said kangsok.
“what? i heard you!” nabi complained.
“now, you guys, move to pyongtaek.
 let me take care of ansung.
 i have one more teleport point nearby, so i’m going to move there.
”having said that, he held out something, which looked like pink petals.
“this is also one of nabi’s skills.
 if you put this on your ear, you can communicate with each other in real-time.
”“you can’t take it off! if you take it off, it disappears!” said nabi.
sungwoo received one of the petals.
 when he brought it near his ear, it automatically stuck to it.
-you are connected to the fairy’s communication network’.
“connected!”“well, good luck!”saying so, kangsok struck his cane on the railroad.
 at that moment, bright light covered his body.
“…”sungwoo and his party stood on the railway and looked in the direction where kangsok disappeared.
“wow, the no.
 1 on the korean server is really different! how cool! but nabi sucks!” hanho said.
“as far as i see it, orun is better than nabi, hanho.
 orun is the best!”sungwoo silently summoned bone wyvern.
 now, it was time for him to fly to move.
at that moment, hanho looked gloomy.
“man, i already begin to miss teleporting.
”after getting aboard bone wyvern, they flew straight in the direction of pyongtaek.
soon, they saw huge flames soaring downtown in the distance.
-it’s me, nabi! can you hear me?nabi’s voice came through the fairy communication network.
“i can hear you well.
”-of course, you should! it’s my magic!when they entered the outskirts of the city center, jisu shouted, “sungwoo! look right under the big building!”looking down, sungwoo saw a group of people near the five-story building.
 there were a total of seven.
 they were running to a bus about to start.
 children and women were inside the bus.
 it seemed that they were evacuating north, to avoid the flames.


-oh, i forgot to say something!“they are being chased by hellhounds!”three-meter long black dogs were running after the players.
they were the hell hounds, hellish watchman born out of the ashes.
 these monsters jumped a few meters and narrowed the distance in just one leap.
 the players were already exhausted, so it seemed the monsters would catch up with them and devour them.
-that armor summons the ‘fire giant,’ then throws it randomly.
 so, be careful when you fly in the sky!“uh? sungwoo, look over there!” hanho shouted.
huge flames soared vertically between burning buildings, then they started to swirl and form something.
 then, the vortex vanished.
“well, what the heck is that?”black smoke rose from the spot, and a huge hand soared and touched the roof of the 7th floor.
 it raised its huge body.
 it was a ‘fire giant’ that was 20 meters tall.
krrrrrrrrrrrrrr ―his burning eyes were fixed on bone wyvern flying low at the moment.
 the monster was too close to bone wyvern.
 sungwoo quickly turned around.
at that moment, the monster grabbed the roof of the building, ripped it off, and threw it at bone wyvern.
 a lump of concrete engulfed in flames flew at great speed.
they could not avoid it.
“hold tight!”puck! kugugugguu!the fireball hit the stomach of bone wyvern.
 a crack appeared in the body of bone wyvern, dividing him into two parts.
 the fragments were scattered in all directions.
sungwoo and his party fell to the ground, hanging on to the huge bones.
 they were in the middle of a hellish landscape surrounded by flames, including trees, buildings, and vehicles.
“sungwoo, look down!”dozens of hellhounds began to pop out of the alley like a herd of rats and ran toward them.
“we’re falling!”they fell into the inferno.


 