\section{chapter 291}

chapter 291: american sailboat that crashed in suwon (1)




while heading to suwon, sungwoo chose the ‘level up card' that he had put off.
-choose a level-up card.
1) stats (random)2) skill (random)3) items (random)4) other (random)5) corpse explosion (confirmed)‘let me have the corpse explosion.
'no.
 5, the ‘corpse explosion', in particular, caught his eyes.
 actually, this item has been more useful to him than any other skill until now.
its current grade was ‘skilled', so sungwoo had an option to release a small amount of ‘abyssal breath' every time the corpse explosion occurred.
 what kind of option would he have if it's upgraded to a professional grade?sungwoo chose no.
 5 right away.
-skill grade has been upgraded.
 (skilled → professional)[skill information]-name: corpse explosion
-grade: professional-category: active-consumption: 5 mana*it triggers an explosion by detonating a corpse.
 it releases a lot of additional damage (+50%) and ‘abyssal breath' containing the power of death after the explosion.
+ high-pressure explosion: the corpse expands for 30 seconds before causing a powerful explosion.
 additional damage (+300%), extra release of abyssal breath (+100%)*however, if you are attacked while the corpse is expanding, the explosion will fail and you won't be able to use the corpse.
sungwoo received an additional option with the additional skill called ‘high-pressure explosion.
' he could use a ‘high-pressure explosion' selectively while using a general corpse explosion normally.
‘well, the time limit of 30 seconds is a problem, but it's going to be a big help.
'as a matter of fact, 30 seconds was long enough to determine one's life and death as well as the tide of war.
 therefore, he would not use this additional skill indiscriminately like the general corpse explosions, so it seemed that he had to consider the situation carefully before using it.
after a while, the helicopter carrying sungwoo and his party pa.
s.
sed through the invisible barrier of the world tree, kyongsu was waiting for them there.
“welcome back.
 fortunately, you've come back quickly.
 if you are away from here for long, we still feel uneasy.
 i just have no idea why something bad keeps happening…”“i heard american players landed here and contacted you.
”as soon as he landed, sungwoo asked the most important thing first.
as if he waited for such a question, kyongsu began to explain the situation in detail.
“yes, that's right.
 but while we were waiting for you, an accident happened, as you already heard.
”
it was not known what happened, but a delegation from the united states was allegedly annihilated by someone.
“the american delegations didn't have any official contact with us, but since they were killed during their visit here, it's going to escalate into a sensitive diplomatic issue, isn't it?”in short, this was a situation in which the world tree camp could be misunderstood for the accident and take full responsibility.
“anyway, we have dispatched an investigation team to look into the accident.
 come with me a little later for safety reasons.
”“okay.
 when they are done controlling the situation, tell them to report to me right away.
”but this wasn't the only bad news that sungwoo heard from kyongsu.
“ah, i've some news about china.
 i hear that the chinese server no.
 1 has unified mainland china after beating the chinese server no.
2.
”“after all, that's how they ended up.
”the loser of the 1st server, the self-proclaimed “emperor,” was waging a war of conquest to unify the chinese server which had been divided into three groups.
sungwoo knew that the “emperor” had subjugated the no.
 3 server in the early days with overwhelming power then he had been driving the leader of the no.
 2 server, the “spirit man,” into a corner.
‘it looks like he has finally beaten the chinese server no.
 2 server.
 then, his next target will be ours.
'as a matter of fact, the chinese server no.
 1 dispatched the siberian hunters to keep the world tree camp at bay while they were busy fighting the chinese server no.
 2 because they felt the world tree camp led by sungwoo would stand in the way of carrying out their ambitions.
 besides, they already expressed their ambition to devour the korean peninsula openly.
‘if unified china is stabilized to some extent, they will launch a war on us.
 even if they don't mount a direct attack, they will turn to various ways to hold us in check.
'as sungwoo expected, it was now inevitable to see a large-scale war with the chinese server no.
 1.
 and the war was around the corner now.
 so, sungwoo had to prepare for it, just like he had been doing so steadily until now.
“we're almost done with the construction of the walls.
 i think we're going to finish it tomorrow.
”actually, the production of the new wall and flying weapons was part of sungwoo's strategy to prepare for the upcoming war.
“since we have enough material and funds, we can do this work easily and smoothly.
 yeah, money is the king.
”even though the wall was a pretty big construction project, they reached the final stage of the construction without any big problems.
 if they could move the building materials to the correct location, muyon would be able to lay bricks with his “automatic construction” skill.
sungwoo and his party felt relieved when they thought about the completed wall surrounding the suwon village with the world tree in the center.
“great, the new wall is so cool! i can see it here too.
 but when you think about when we first came here, wow, this is a huge change!” hanho muttered as if he was greatly moved.
“it was originally a place where vampires gathered to kill everyone, right? but it has become the safest place…”having heard that, sugnwoo also felt somewhat touched by the new wall and the surroundings of the suwon village.
‘this place certainly has changed a lot as much as we have invested.
'sungwoo looked around the village once.
a huge tree with mysterious power, the world tree, grew tall from the center of the village and established itself as a solid pillar of the village, with branches and leaves extending out magnificently to form a high ceiling.
under that cozy environment over three hundred players were busy working such as building warehouses and moving materials to develop the village.
there were cheerful noises from everywhere.
“it looks like i've made the leather very well this time.
 i soaked it in herbal water, then it came with health recovery buffs.
”“good job! your skills are improving day by day!”

various workshops were producing numerous items.
 not long ago, they were working in a makes.
h.
i.
+ft workplace.
 but they overhauled one whole block of the village and turned it into something like a ‘workshop center.
'“we are going to transport bricks to the construction site in the west! transportation no.
 2 team, please come over here!”freight trucks and forklifts were busily moving on the road that had been cleaned up.
in addition, they renovated abandoned buildings and used them for new purposes, and demolished some old buildings to make fields to grow crops.
mysterious herbs grew in mt.
 paldal in the north.
 “mountain rangers” who specialized in managing the mountains were dispatched to stop villagers from collecting too many medicinal herbs.
 they improved the medicinal herbs to develop new varieties.
in short, the villagers, who were faithful to their respective roles, had a perfect self-sufficiency system.
“security guard reserve no.
 1 team, fall in! from now on, you're going to have emergency response training!”and the invisible barrier surrounding the whole village as well as the solid wall, the turrets, and even the security guards were perfect to make the village a huge city and a fortress.
however, if they were complacent enough to idle away, they would lose everything.
“sungwoo, they have allegedly done the preliminary search in the accident area.
 i think it's safe to go there,” said kyongsu.
sungwoo nodded while looking around the village.
“then, let's go there right now.
”“sure.
 let's go there and check what happened first, and root out the problem.
”if you have something, there must be someone who wants to take it away from you.
so, sungwoo had to nip the intruder's wicked intentions in the bud because that was the basis for peace.


 