\section{chapter 193}

                             




the hunter company’s negotiator had no choice but to accept sungwoo’s offer.
“sure, i’ll deliver you good news.
 i know i’m asking for too much, but would you please take care of our prisoners’ safety?”ky asked sungwoo a favor, kowtowing to him, but sungwoo did not give a positive answer.
“you seem to be mistaken, but my bargaining chip is not the lives of your prisoners here, but the whole life of your organization.
”“oh, i see.
 thank you.
”sungwoo knew that this guy couldn’t say anything right now, but once he returned to the headquarters of his company, he might try to come up with a dirty trick.
 sungwoo could not rule out the possibility that he would join hands with the evolution society to get their help.
‘they are not stupid.
’however, the hunter company was a group with a working system of their own, so they would carefully decide which faction would be more beneficial for them to take sides with.
taking note of that, sungwoo returned the negotiator, ready to take some risk.
 in other words, sungwoo was placing bait to catch a large fish.
the next day, sungwoo paid attention to the administrative affairs of the village.
“um.
 when i look at it at a glance, the world tree seems to grow 50 cm a day,” kyongsu said.
 sungwoo looked up at the world tree, which had transcendent power.
it was much bigger than before he went to taiwan.
 and its power was already having a tremendous effect on the whole area.
“on mt.
 paldalsan, the glowing grasses started to grow, so i dug some of them.
 strangely enough, they are called items.
 namely, it’s a medicinal herb.
”kyongsu opened a small box.
 inside, there was some blue-colored grass with its roots lightly covered with dirt.
[item information]-name: healing herb-grade: rare-category: medicinal herb-effect: after you eat it, it has the effect of quickly healing your wounds.
 you can get much better effects by processing the herbs.
 in addition, regular consumption can lead to an increase in your stamina level.
these special herbs began to grow around the world tree.
 this was certainly the influence of the world tree.
on the one hand, since the world tree was influenced by sungwoo, something unusual was sometimes discovered.
[item information]
-name: abyss root-grade: rare-category: herb-effect: attention! it is a herb that has been affected by something wrong.
 when you eat it, your health is greatly reduced.
 you can get a much stronger effect by processing it.
“it looks like you have to deal with this type of herb carefully.
”“does anybody have a job specializing in processing this?”when sungwoo asked, kyongsu opened his mouth, scratching his chin.
“uh, it can be used as an ingredient for cooking… oh, one of the players with the cooking job has chosen alchemist as his minor job.
 he even made a potion once.
 i think it’s okay to leave this task to him.
”since kyongsu categorized production workers separately, provided work facilities and encouraged production activities, they were organized according to their jobs.
players who leveled up in such an environment have become experts, so they were ready to use new materials immediately.
“how about setting up a separate potion manufacturing room? there is virtually no basis for potions.
 i think it will be necessary for us to learn the manufacturing method by experimenting.
”“that’s a good idea.
”a potion was an essential item during a battle as well as after a battle.
 when they used special materials, they could get powerful buffs, too.
however, this was not all about the influence of the world tree.
“sungwoo! listen to this.
”hanho brought his father, jeongho, and began to explain something.
“dad, so what you mean is at some point you didn’t need mana and gold anymore when you opened the safety zone, right?”“yeah, that’s right.
 i think that phenomenon happened probably after the world tree had been planted.
 suddenly, i saw a message saying something like synergy.
”the “pioneer camp” skill, which jeongho used to build the safety zone, was given a new ability after it had been affected by the “shadow of the godly tree.
”“so i got a secondary skill called eyes of the air.
 when i sit still and close my eyes, i can see the area near the invisible barrier surrounding the village.
”“really? then, it’s like cctv, right? sungwoo, isn’t this a great skill?”“hey, son, don’t make a fuss over it yet.
 that’s not the end.
 if you sit near me and close your eyes together with me, you can also connect to my skills and see what i see.
”
then, jeongho opened three of his fingers happily.
“i can connect up to 3 people.
 do you want to try?”“oh, awesome! you got a windfall without doing anything!”“windfall? son, how can you say that to your father? how ugly of you to select such vulgar words?”hanho shrugged and said.
 “well, it’s better than you playing cards like before.
 back then, you spent all the money, ruining our family’s fortune.
 now, you can keep sentry.
”“hanho, don’t you think that the experience i had gained while playing cards paid off?”anyway, jeongho’s additional skill was a great contribution to tightening the security around the village.
 of course, it was only when jeongho was awake could he use his new skill.
there was one more beneficial effect of the world tree.
-‘abundance of the godly tree’ is given to the whole area.
* item creation success rate increases.
 (+50%)* increases the probability of additional options when making items.
 (+10%)* item production cost is reduced.
 (+10%)buffs were given to all production operations.
the influence of a world tree was tremendous.
 even considering that the world tree was still only at the low level of ‘growth stage 2’, it would give great buffs beyond imagination if it grew in the future.
‘if this trend continues, we can widen the gap between us and the other groups.
’although the village had only 226 people, they were growing into a truly elite group.
when they accepted more players, these people would play a central role.
‘it was regrettable that we broke up with the youngdungpo group, but someday we could be bigger than the youngdungpo group.
’of course, even after sungwoo formed the third camp, he had no intention of accepting new players because an incompetent majority would be a big headache rather than help.
so, he was thinking of forming a sound and strong group with excellent quality, even though it was small.
 to keep such qualitative excellence, he needed to have a lot of good items.
“leader! i found a new store!”the best way to obtain good items was a shop.
 in that respect, taesung was making a great contribution.
 taesung and his friends went around the area several times a day, checking the newly formed dungeons, facilities, and objects, and informing the village about them.
“but this time something is weird.
 i was trying to check what level it was, but it says no access.
”sungwoo’s eyes narrowed when he heard that.
“where is it?”taesung seemed to have hit the jackpot this time.
‘if this is an inaccessible store, it must be a secret store.
’sungwoo had a “secret store coupon,” which he obtained after hunting the wyvern alpha male.
‘it’s high time to spend the money.
’he had a huge amount of money to spend on items.
it was a movie theater near paldalmunit was quite old and small for a multiplex, but a red question mark icon was flashing at the entrance of the theater.
‘as expected, this is a secret store.
’sungwoo stepped into the theater with big strides.
“you wait here.
”“uh, it’s inaccessible.
 can you go in, captain?”sungwoo nodded without a word.
“wow, our captain is special!”-would you like to use a ‘secret store coupon’? (y/n)no one could enter the ‘secret shop’ freely.
 when they found a duty-free shop at kimpo airport, only sungwoo, who had a coupon, could enter.
in addition, the secret shop system was not completely random, so a few high-end items were presented to the visitor, who then had to decide which one to buy within 10 seconds.
[player profile]-name: sungwoo yu-level: 22

-job: necromancer, black wizard-ability: strength (24+13), agility (19+11) stamina (16+9)-reserve gold: 148,155,405-trait: chaos‘now i don’t need to give it a pass like last time when i had to because of insufficient gold.
’in addition to the gold he accumulated, he also gained an enormous amount of gold by wiping out the pirates and blocking the waves of the devil’s gate.
 of course, the 67 million gold he obtained from the pirates’ vault was the largest portion of his gold reserve.
when he entered the theater, a screen lit up.
-sit down.
sungwoo sat in the middle of row f.
-a total of 5 carefully selected items will be released in turn.
 if you are willing to buy, please say “buy”.
* you have 10 seconds to make the decision.
* items that you once miss cannot be purchased.
the screen advanced to the next message.
-since you have a lot of gold, the item grade will be upgraded.
‘i came in with 10 times more gold than last time.
’-the first item has been revealed.
[item information]-name: set of 5 panacea-grade: special-category: consumption-effect: when you use it, all ‘abnormal status’ can be canceled.
* price: 3,000,000 gold‘this is an item i gave a pass last time.
’

 