\section{chapter 287}






 the expected place of the angel’s advent was ‘above youngdungpo station’.
 in fact, it was never specifically stated, but the liberation guild speculated like that.
“if the angel comes down to judge us, she will come down where we are because we can’t escape seoul anyway.
”like minhum said, it was unlikely that the absolute race would secretly descend in a corner of seoul then sneak up to them to attempt an assassination.
the core fighters of the liberation guild began responding based on such speculation, and soon, youngdungpo station became noisy with them preparing for the defense.
“large vehicles are coming in! please move away!”“place the water tanks right here!”junghoon and minhum, who were standing on the rooftop of the station, were looking down at all the preparations.
 they were preparing in unison, and the leaders of each team came up and briefed them about the progress of their preparations.
the first one to report was the supply team leader.
“we have mobilized all the sprinklers.
 and we also moved all the rainwater tanks we had collected nearby.
”“good job.
 if you can mobilize more from nearby places, please get them all.
”“sure, let me check once more.
”fire trucks they mobilized from all over seoul arrived at several places.
 they were all filled with water.
the next to report to them was the security team leader.
“we have placed players on each rooftop capable of dealing with freeze and fire-type wizards and water spirits.
 when they use their magic, we will be able to use the water sprayed from the sprinklers and the water tanks on the rooftop.
”“good.
 deploy multiple tanks to protect them.
 that’s the heart of this battle.
”
“okay.
”the team leaders kept reporting about the status of their preparations.
this time the transport team leader said, “the fire helicopters are filled with water.
 if you give orders, we can pour tons of water at once.
”“please have the pilots on standby all the time.
”firefighting helicopters used for transportation were restored to their original function after a long time.
as a result, all the water that they could draw from youngdungpo was stored in various forms.
“got it.
 i will report to you right away if i have any additional things.
”upon receiving all the reports, minhum suddenly looked around.
 the man who asked for this kind of preparation was not seen.
“commander, where did sungwoo go?”junghoon shook his head.
 he also has not seen sungwoo since they started to prepare for the defense.
 so, he just believed sungwoo was taking some important measures right now.
“by the way, can you figure out why he has asked to collect so much water like this? even the swimming pool wouldn’t use this much water, as you know.
”sungwoo asked them to collect all the water as much as possible, but he didn’t explain why the water was needed.
normally, junghoon would have objected, but since everything depended on sungwoo, they had no choice but to trust and follow him.
 furthermore, he understood why sungwoo didn’t tell him the reason.
“i think sungwoo is right.
 since we belong to the angel camp as of now, it’s possible that this kind of information can be leaked to the angel camp, so it seems safe that we just don’t know.
”“that makes sense!”the absolute race would be watching over this land.
 junghoon couldn’t figure out what method they used, but the most promising method was to use the players under his command.
 of course, junghoon and his players were still registered as the ‘target of judgment’ because he broke the angel statue and escaped from them.

“because they can still use our eyes and mouths, we should be careful.
”if the weaker side dared to confront the stronger side, they had to be very prudent.
time passed.
 the remaining time until the angel would come down began to pass, which deepened their worries and anxiety.
-the time remaining until ‘the angel’s advent’ (00:01:42)now, it’s only a little over one minute left.
 the players of the liberation guild on standby could not hide their anxiety.
“are we all dying when this time passes? what if we die even without confronting them?”“hey, why are you making such an ominous comment? we’re all here to fight back, right?”“but they are the absolute race.
 shall we be able to fight them?”ironically, the very being they served and followed would be judging them.
 they just felt uncomfortable.
 they felt as if they were uprising against god.
therefore, they needed a new spiritual leader, some hero who could be a strong supporter enough to fight against the absolute being.
“even if we didn’t know, the necromancer was constantly fighting the absolute race.
 he is right here with us right now.
”naturally, they came to repeat the name of the necromancer.
“oh, if you think about it, didn’t the absolute race keep losing to him?”“that’s right.
 they even issued a world quest, but they were defeated.
 well, they might not be the absolue race in that respect.
”the absolute being had been defeated several times already, so they began to gradually realize that they could stand up on their own and survive.
 such awakening made them pluck up courage.
“good.
 let’s fight to the end!”“by the way, where is that man? i haven’t seen him for a while.
 he must be working on some strategy…”the man could not finish his words because time was up now.
-time remaining until the ‘judgment.
’ (00:00:00)“it is the beginning.
”as soon as it started, there was silence among them.
“…”the air around them became heavier.
more precisely, the flow of air stopped.
 then, as if the wind disappeared from the world and the sound evaporated, perfect silence came.
without saying anything, everybody raised their heads and looked up at the sky.
“…”a blue sky and a mass of heavy clouds were slowly passing over youngdungpo station, but there seemed to be nothing strange about it yet.
“uh, look over there…”but the abnormal sign started from something very trivial.
 there was a hole in the middle of the cloud.
 and soon the whole clouds began to disappear.
 specifically, the clouds were being sucked somewhere.
“it’s a hole!”someone muttered quietly.
 there was a hole in the sky.
 it was a portal of enormous size.


a portal is a door.
 yes, someone opened the door.
 if so, what will come out of that door?ooh-ooh-ooh-ooh-ooh-ooh-the wind and sound that had disappeared came back.
ooh-ooh-ooh-ooh-ooh-ooh-the wind and the sound were insane.
 they became a roaring sound like the cry of a beast, as if they were awakened from the primitive nature that had been asleep, and blew above their heads wildly“…”soon, something began to come down very slowly from the door that was opened from the other world.
 it had pure white toes.
“is that an angel?”the angel put her feet into this world.
-the ‘angel judge’ has begun to come down.
* because of the ‘angel judge’s power’, all your stats are drastically reduced.
 (-90%)it was the moment when the absolue race revealed themselves for the first time in the history of the korean server and other servers around the world.
“ugh! i feel like i’m emaciated…”“i feel like my legs have become wobbly.
”the players of the liberation guild began to feel restless, faced with the expected curse.
“keep your place! we’re going to confront them according to our operation!”

 