\section{chapter 361}

chapter 361: devil’s world tree and world eater (3)this place really looked bizarre.
 roots and vines came down like hair from the ceiling.





they were tangled, lumpy, and scattered like blackout curtains here and there.
besides, dead roots and vines piled up one after another on the floor, forming a bumpy road, so they found it hard to walk smoothly.
“i think we have to watch out while walking.
”after all, the roots here were those of the devil’s world tree.
 so it would not be strange at all even if they harmed sungwoo’s allies.
 for example, the monsters could pop out and attack them suddenly.
sungwoo’s party felt as if they were walking into the jaws of a giant monster and advanced further inside very slowly.
“there is a capsule on the front.
”they found one huge capsule in the center.
“it’s unusual…”like an ancient altar, a green glowing capsule was placed on a stone pedestal, and the roots descending from the ceiling carefully wrapped it.
woooooooooo-and inside the capsule was a long-haired man with pure white skin.
 bubbles of air flowed out of his mouth, rising slowly.
“who the hell is he?”the expedition members stared blankly at the man.
 they faced a man in an unknown world amid a myriad of questions.
 who was this man? no one could guess anything about him.
‘is this guy the winner?’thinking like that vaguely, sungwoo approached the capsule.
 the closer he got there, he could feel more intense strength from it.
 actually, he experienced it before somewhere, something like a sense of intimidation.
 this was the same feeling when he confronted the overwhelming being from an alien world.
at that moment, the man opened his eyes all of a sudden.

- the winner of the 31st world, world eater, has appeared.
clang!suddenly, the capsule broke like an explosion.
 liquid splashed in all directions, along with the pieces of torn roots.
the players lowered their postures and hugged themselves, while sungwoo hugged mir and created a bone shield.
gray smoke began to fill the room.
 and with the smoke in the background, a long-haired man began to walk down the altar.
“necromancer, i didn’t expect you to come this far…” the man muttered feebly.
sungwoo looked at him and asked, “world eater, who are you?”the guy with a pale face and piercing eyes looked down at sungwoo.
the world eater, who once appeared in the form of one huge eyeball, was nowhere to be found.
 in this server that met its ending, world eater was just a normal human figure, namely, a player in the destroyed world.
as if he was tired, he closed his eyes slowly and said, “i am a player, the guardian, the demon king, and the world eater.
”familiar words appeared one after another.
 player, guardian, demon king, the world eater.
did he use those titles in that order?but there was one title that bothered sungwoo the most.
“did you say you’re the guardian? aren’t you the fallen? the devil’s world tree must belong to the fallen, right?”he looked at sungwoo sarcastically.
“yes, like you said, i am definitely an evil spirit.
 but in our world, i am the only savior.
”
“saver?”he came one step closer to sungwoo.
“after defeating the fallen and taking over the devil’s world tree, i prepared an ‘ark’ here.
 and i’m the last player in the world to supply energy to maintain this ark.
”the ark he referred to seemed to mean the capsules that they just passed by.
this time sungwoo got closer to him.
 this was an opportunity for him to get essential information about this game from the world eater.
“is that the reason you want to destroy our world? energy? what do you want to use it for?”“…”“are you giving life to the players in the capsule? huh? if you’re also involved in a game like this, can we talk?”sungwoo tried to glean information from him.
 however, the world eater seemed unwilling to continue the conversation.
 he raised his right hand without responding.
 then, a bunch of roots came down from behind.
the roots were peeling off little by little then a sword came out.
 the sword looked very familiar to sungwoo.
‘that’s the ruler’s sword.
 it’s an item that can get me the right to possess the dragon…’it looked like the ‘ruler’s sword’ that minseok had, namely, the sword of the dragon knight.
sungwoo finally knew the answer: the world eater was the dragon knight.
the dragon of this cave died fighting against the fallen in order to protect the guardians who were killed here.
 sungwoo was displeased with the truth.
“okay, so you don’t want to answer, do you?”“…”the world eater remained silent.
 given that he took out the sword, he suggested he would resort to force rather than dialogue.
 sungwoo stretched out his right hand and summoned the grim reaper.
“i wonder who you are, but i don’t really care who you are or what you want.
”the world eater seemed to know that it was meaningless to talk with sungwoo frankly.
they must kill each other to achieve their own goals, it was the rule of the game.
“then you can get your sword and others, then get to the end of this game and find the truth for yourself.
”the truth could only be seen by those who survived to the end.
the identity of the world eater was a player in the destroyed world.
for some reason, he claimed that he was an evil god and that he was planning to devour another world.
‘why should he attack our world then?’given the situation here, sungwoo felt that the world eater had some inevitable reasons, which seemed to have something to do with the players sleeping inside the capsules that they witnessed while coming to this place.
‘it doesn’t really matter.
’sungwoo tried to converse with the world eater, but the latter didn’t respond.
 it seemed that he needed to ruin the world where sungwoo lived in order to achieve his goal from the beginning.
in other words, this was not a problem that could be resolved through dialogue.
“…”the guy looked down at sungwoo silently.
 sungwoo could feel a strong determination and a murderous intent on his expressionless face.
 he would never give up his goal.
‘then, i have no choice but to kill him first.
’

sungwoo grabbed the grim reaper and summoned the undead army behind his back.
- caution! the fellblade begins in this area.
- caution! ‘death response’ begins in this area.
an overwhelming force of an undead army appeared behind sungwoo.
 their number greatly increased due to the effect of the ‘devil spirit magic manual’ that he had obtained in the trap pit.
there were 85 subordinate spirits, 60 zombies summoned through death response, and 2 flesh golems.
rattle! rattle!while the sound of clashing bones filling the place, death knight minsok, lich victor, and durahan were summoned one after another and stood on sungwoo’s left and right.
“crackle! this time that is the only guy we have to kill?”“but he looks unusual.
”along with mir, they were classified as sungwoo’s ‘special subordinate spirits,’ so he could summon them even if their addition exceeded the quota of his subordinate spirits.
“let me summon my own subordinate spirits, too!” said victor, summoning his family.
- caution! ‘death response’ has begun in the area.
since victor had not yet mastered the ‘fellblade’ skill, he could not control high-quality skeletons without the necessary materials, but he could use the ‘death response’ that summoned the ownerless zombies from the abyss.
at that moment, 15 zombies appeared suddenly and slightly exercised their power.
- caution! the fellblade begins in that area.
then, mir summoned the ‘chicken skeletons’.


 