\section{chapter 230}






 players around the world watching the scene through the official channel witnessed something like a “war movie” changing to a “slasher movie,” which featured the battle zone shrinking gradually, monsters that never died, and demonic beings with no mercy.
“ahhhhhh!”“help me!”with the victims screaming in pain, the fight between them was so terrible and bizarre.
the japanese soldiers had nothing like a fighting strategy.
 with everything collapsing, all they could do was struggle desperately to survive until the all-out war was over.
-the battle zone will be reduced in 60 seconds.
 (-500m²)what was left behind was the sound of bone bumping inside the shrinking dome, and the invaders dying with regret while retreating.
it didn’t take too long for sungwoo to get rid of the japanese remnants.
 the fight was over before sungwoo summoned the ‘grim reaper’ and ‘the power of anubis’.
“we have chased and killed them.
 they are running to the north.
”“we have also killed them all in the west.
”the whole world could not help but be astonished because the advance party of about 2,000 japanese troops who set foot on the korean soil was annihilated.
 they were killed by one korean player in less than 40 minutes.
but the only one, the commander of the japanese army, swordmaster akira okata was different from others.
‘yeah, he is a monster.
 i have no choice but to admit it.
’he survived the necromancer’s ‘evil spirit bombing’.
 his survival was abnormal, but after surviving the bomb, he was holding out for the remaining time while blocking the undead’s endless attack.
only a little while ago, he struck back dozens of arrows, stepping on the thighs of the troll skeleton, and grabbed his ribs.
 then, he bounced up and cut the cervical vertebrae of the troll skeleton at oncethen, he cut the heads of two ghouls charging down from the air.
all this happened in just a few seconds, but this was repeated for dozens of minutes.
-grim reaper remaining time (00:14:29)
-anubis remaining time (00:14:30)‘i am afraid i can’t finish this fight so quickly.
’sungwoo couldn’t step forward recklessly.
 he dispatched a lot of undead to kill akira, but the latter broke through the siege and escaped by widening the distance with them.
even if sungwoo stepped forward now, he would not defeat akira.
 sungwoo would have to be ready to have his head cut by such a strong swordsman like akira.
sungwoo could know it while watching the highly skillful jisu using her sword.
 those using the sword freely knew how to deal a fatal blow to their opponents.
‘as expected, this guy is dangerous.
’sungwoo canceled anubis to save the remaining time of awakening and his deity status and withdrew the undead, and as a result, the tedious confrontation between them continued for a while.
“sungwoo? is it okay to leave him alone like that? he seems a little tired, so why don’t you kill him right away?”“just leave him alone because we have won.
”the japanese soldiers were annihilated except for akira.
the korean server virtually won the fight.
-korean server wins the all-out war with the japanese server!-‘victory buff’ is given to the korean server!* increase defense power for one hour (+30%)finally, the all-out war was over.
-from now on, ‘free battle’ begins for 1 hour.
“it’s all over because our enemies were wiped out, right?”“probably.
 phew…”the survivors of the hwarang guild on the korean server side were relieved.
 when they gave up everything, they were saved by the unexpected reinforcement.

“well, we have won because the japanese soldiers were killed except for that one crazy swordsman…”“what a relief! i never expected that the necromancer would come here so soon!”“you bet! come to think of it, he is a good man.
 don’t you think we have to switch to the world tree camp?”but contrary to their expectations, the war was not over.
“not yet! watch the broadcast!”“the official channel’s broadcasting drone was still flying over busan.
 that meant the war was not over yet.
”and now the screen of the broadcast showed the coast of busan.
“what the heck is that?”more precisely, the drone was showing dozens of ships off the coast of busan.
“how many warships are there?”“are they all japanese warships?”the japanese reinforcement troops arrived via sea.
 since the coastline batteries had been disabled, there was no way to prevent them from landing on korean soil.
everyone’s eyes turned to sungwoo.
 everything depended on him, but even sungwoo was in agony at the moment.
‘i’ve got only 14 minutes to use the anubis status.
 it’s not reasonable to fight them now.
’until now, he always destroyed his enemies within an hour.
 however, if the japanese troops attacked massively back to back, he could not handle them alone.
‘if i can’t function properly, we are overwhelmingly inferior.
’the number of world tree camp players that sungwoo took with him were only 30.
 even if he combined the hwarang guild members, they were numerically inferior to the japanese fighters.
in this situation, sungwoo and his party would not be able to escape after his awakening and deity status ended in14 minutes.
“does it mean we have to give up busan?”sungwoo could not think straight at the moment.
 what he got was one hour of free battle.
 after that, the japanese server would try to fight again by selecting the ‘fighting mode,’ regardless of whether it is a one-on-one duel or other forms of fight.
“necromancer?”at that moment, the executive members of the hwarang guild came to sungwoo.
“currently, the representative of the korean server side is you, necromancer.
 we will follow your order.
”“give us an order, please!”they were full of determination, but what sungwoo said to them was quite surprising.
“i think i have to abandon busan.
 prepare to retreat north, so guide us.
”sungwoo came to such a conclusion after a long thought.
“pardon? retreat?”“yes.
 hurry up, please.
”there were more than 1,000 survivors of the hwarang guild, but most of them inhaled the abyss of breath, so they could not fight.
moreover, more than 2,000 japanese troops were annihilated by sungwoo.
 this meant the japanese reinforcement troops would be several times as many as them.
‘i need a reinforcement force.
’however, this was not sungwoo’s area.
‘i have to widen the distance with them by all means, so we can fight them again after 24 hours.
’the players of the world tree hurried to prepare for a retreat.
 they collected the flying weapons and stored them in the inventory.
 they monitored the surroundings carefully while preparing to retreat.
even after the great victory, there was nervousness and anxiety in sungwoo and his allies on the korean server.
“hurry up! they have already landed!”“there are so many injured people here.
 i don’t know how to take them…”

at that moment, somebody shouted.
“necromancer! something is flying from the southern sky!”sungwoo looked to the south.
 there was a bunch of something hanging in the orange sky.
“that’s…”hundreds of large kites were flying, riding in the sea breeze carrying ninjas.
“airstrike!”“even the human beast monsters are moving in the north!”the troops of the “evolution society”, who sungwoo forgot for a long time, began to move again.
 they were only a few people, but they could spray “breath of abyss” to block the streets.
“what should we do, sungwoo?”“i’m afraid we can’t retreat in this situation.
”“i guess so.
”wasn’t there any way to fight them at all? sungwoo realized that he was in big trouble.
‘can i open the demon’s door?’if he approached the main unit of the enemies and opened the demon’s door, they would be busy fighting the demon’s door without paying attention to sungwoo and his allies.
but that option was sungwoo’s final card.
 at the same time, it was something like a mutual destruction card.
sungwoo and players of the world tree camp may somehow survive, but the survivors of the hwarang guild, where there were many wounded, would be annihilated.
“prepare for battle once more!”“ready for battle!”sungwoo decided he would have to resist by all means.


 