\section{chapter 476}

- select the winner's right, 'ending'.





1) next assignment* this is an extension of the main game, and you will carry out the mission of the 'world eater' in your world that has faced the 'apocalypse'.
* when the world eater invades another world and meets 'special conditions', he will get a chance to 'rebuild the world'.
* survivors except you are sealed in a 'capsule' and their 'spirits' are used as a 'boss monster' in the target world.
2) new game* this will receive the 'supporter' of the 'gambler' and can become the second player.
 in addition, you can receive a 'special reward' when you sign a contract with the gambler and meet 'certain conditions'.
* however, all survivors except for you are consumed as the souls of 'lower monsters'.
3) game ending.
 *gm respects your rest.
 you can choose death to do nothing.
* however, all players in your world will be 'discarded' together, and the world will be recycled as a 'map'.
"do i have to choose one of the three options?"in the first place, this game didn't have a happy ending, so there was no way out.
that was not the only shocking truth.
 it was terrible even to deal with the follow-up of the world that had reached the ending.
'how can a survivor's mind be used as a monster?'the king of the great mountains, victor, isabella, or more precisely, all the monsters including them were players from other worlds.
'is the map based on the ruined earth, after all?'even the special spaces used in the game, such as dungeons, subspaces, and hidden stages, were created using the destroyed world.
'then why?'when sungwoo was fuming with anger, he suddenly recalled what gangsok had once said.
 at the last moment, he was dying by the primordial death, he made excuses with a gloomy expression.
'necromancer, did you call me a villain? yeah, that might be right.
 but there was no other option for me, and i had to do this.
 i had to choose just one of the things they wanted.
'sungwoo asked, 'who the hell are they?'
gangsok hesitated to answer his question because he knew they were watching this scene right now.
 but now there was nothing he could lose.
gangsok nodded and opened his mouth.
try the lightnovelworld.
com platform for the most advanced reading experience.
'they are at least not gods.
 they are not different from us.
 perhaps they are the worst beings that we could be.
"he died after saying that.
it was not known whether he died by leaking information, or whether he died due to the primordial death, but he died before sungwoo.
".
.
.
"sungwoo pondered about the choice for a long time.
 but he couldn't decide.
he came to understand gangsok's statement that he was no villain.
'nonetheless, it was a mistake for him to have made such a choice.
'even if he was forced, he acted to implement it faithfully.
 that couldn't be an excuse for his actions.
however, sungwoo also had to make a choice.
 after much deliberation, he finally made a choice.
 he looked at kyungsoo and said, "kyungsoo?""yes, go ahead.
"horsesungwoo kept thinking, then slowly opened his mouth.
 "please prepare to return to suwon.
 i hope we can all have a party tonight.
"kyungsoo couldn't hide his puzzled expression.
"party?"throwing a party? normally sungwoo would not think of it.
sungwoo continued, "come to think of it, we haven't had a proper rest until now, have we?"that's correct, this was sungwoo's choice.
 instead of choosing the option, he chose to throw a party.
 
but right now, i don't want to think about anything and just want to sleep.
"he chose not to choose anything.
"oh, that's right.
 everyone, including you, should rest.
 we all have suffered so much.
"sungwoo nodded and walked forward.
hundreds of thousands of players, who belonged to the world tree camp, fought this war together and gathered around him, stepping to the left and right to pave the way for him.
he chose not to choose anything.
 if this game and this world had an ending right now with sungwoo's choice, he was not going to have the ending of this world forever by not choosing it forever.
 that was sungwoo's choice.
new chapters are published on lightnovelworld.
combut the system would not allow for it, of course.
- warning! if you don't make a choice, the winner's right can be transferred to another player.
 sungwoo stopped walking.
 everyone was looking at him.
'transfer?'it was meant to force this crazy choice on someone else.
sungwoo agonized for a moment about who he would pass on, and what kind of choice he would make.
 nonetheless, he still didn't choose.
he didn't want to be stupid enough to play into the other's hand by succumbing to the other's threats.
then a problem arose.
"huh! what's this?""a world quest all of a sudden?"the players who had gathered around sungwoo began to whisper.
 "no way! this doesn't make any sense!"and they were clearly perplexed.
"sungwoo?"a message that was invisible to sungwoo appeared to all of them.
the message that they saw was like this.
 [world quest]- title: a chance to win- type: kill- objective: kill kor-157- reward: grant the winner's rights*the winner of this game, 'kor-157', is driving the world into a worthless path through a mistaken judgment.
 if you get rid of him, you obtain the 'winner's right' and can control the direction of the world.
 work together and kill him right now!at the same time, everyone's cell phone lit up, and a video played by itself.
it was the broadcast screen of the official channel.
 sungwoo appeared on the screen.
the source of this chapter is lightnovelworld.
comsungwoo raised his head.
wooooooooooong-drones floating all over the place were filming sungwoo.
 they were showing the target of the world quest, namely sungwoo's location, in real-time.
sungwoo glanced around.
".
.
.
"nobody moved.
 ".
.
.
"silence, tension, anxiety, and all kinds of incongruity complicated sungwoo's thoughts.
sungwoo finally said, "did you just see the message that ordered you to kill me?"he looked around and made eye contact with some players.
 some avoided his eyes.


"if you want to kill me, that's alright.
 but don't try to do it now.
 that's inefficient.
"he quickly lifted his head and looked at the camera on the drone.
"i'll show you a much easier way.
"to be precise, he made eye contact with the entire world who was looking at him through the camera.
"tonight, we are having a party.
 you guys have suffered so much so far.
 so you deserve a good night's rest.
"sungwoo opened his arms and continued, "i will be defenseless tonight.
 if you're going to kill me, kill me at that moment.
 it will be much easier.
 so! everyone, come to the world tree camp and enjoy the party.
 i invite you all.
"sungwoo then turned his head to kyungsoo.
 his face turned pale blue.
"kyungsoo, it doesn't matter no matter how many people come to the party, right?"but kyungsoo felt more relaxed to hear him talking in a leisurely manner.
"well, not a problem…" he quickly smiled and nodded.
"sure.
 no matter how many people come, i've prepared enough food and snacks for them to eat and drink for a few days.
 isn't that why we have won? ah! i will open the hypergate to the whole world.
"sungwoo looked at the drone camera again and said, "did you hear me? don't be afraid to come and kill me.
 of course, i can resurrect myself as many times as you do now, so come with a careful plan if you want to do it.
"then someone laughed.
 and there was somebody's call from somewhere.
"wow, it would take a hundred years just to make a plan, right?"updated at lightnov‌elworld.
comsuddenly, laughter was heard from everywhere.
"doesn't he mean we should not come?""shh, that's a secret.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 