\section{chapter 206}

                             




however, since their troops were dispersed widely, the demon camp could not respond to the angel camp properly, so they were unilaterally defeated.
“that’s alright.
 we’re going to accept our defeat for now because it’s more important than anything else to catch up with the necromancer.
”the demon camp didn’t give up.
 since they bet everything on this battle, they could not give up.
“we’ve found them! two wasps at 11 o’clock position!”the necromancer burned down almost all of the wasps’ nests, but there were some wasps still alive.
 some wasps had been away from the nests when the fire burned them down.
 besides, there were also hives on the outskirts the necromancer could not remove.
 also, as time passed, new wasp nests were respawning.
-toxic giant wasp hunting (99/100)“just one wasp! we only need to find one!”“good! everyone, open their eyes wide! let’s grab it quickly and run right away to break the back of the necromancer’s head!”they boosted their morale once again with only one more wasp to catch.
 although they were behind now, they began to have the hope that they could catch up with the necromancer.
the next stage had to be the boss stage, so it would be hard for the necromancer to clear the quest quickly, no matter how strong the necromancer was.
‘well, it might be more favorable to us if we attacked him while he is fighting the boss monster,’ bumyeol thought, cautiously hoping he could kill the necromancer.
however, at the very moment when they had to catch only one more wasp, a message appeared before their eyes and made the entire demon camp silent.
-the ‘python cave’ dungeon has been conquered.
*soon the dungeon will disappear.
along with a short message, huge trees were withdrawn and the ceiling began to open.
brilliant sunlight poured over their heads.
“ah, ah….
”“oh damn it!”“necromancer! that son of a bitch!”
the demon camp couldn’t control their raging anger.
they brought in a whopping 741 men to conquer the cave.
 they were the total forces of the demon camp, but 211 out of them were killed.
nevertheless, they obtained nothing.
 they just lost a lot.
 it was a one-sided and humiliating defeat.
“captain, is our fighting over like this?”“this is ridiculous! how come we have been defeated like this? didn’t we keep rising even after we were defeated and conquered the mountain area?”the warriors of mt.
 taebaek asked bumyol in dejection.
 he looked up at the sky silently.
then, he shook his head as if he was determined about something.
“no, this is the beginning.
 as you said, we rose after we were defeated.
 now is the moment for us to rise again! we’re going to make mt.
 pukhan the necromancer’s tomb.
 everybody, clear for action!”“yep! to arms!”“get ready again! even if we keep losing, we will triumph eventually!”they didn’t want to give up the fight for control of the metropolitan area like this.
since the quest was over, the “pk prohibited zone” would be released, and if so, those who were numerically superior like the demon camp could be in a favorable position.
“yes, in a situation like this, that senior man said he would have 320 additional soldiers ready on the outskirts.
”in the meantime, younghwan lee, the chairman of the reconstruction alliance, who did not directly participate in the dungeon attack, had prepared “plan b” for contingencies.
his strategy was named ‘expel demon’ and was intended to catch the necromancer.
the demon camp bet everything on this, and they were determined to fight it out with the necromancer.
“let’s catch and kill the necromancer!”“go!”the self-styled warriors of the mountains began to prepare for the real battle.

***“it’s finally over! the huge dungeon that covered mt.
 pukhan is disappearing by itself!”reporter ahn’s camera was focusing on the mountain ridge.
 the trees that had been tangled randomly and covered the mountains like a dome were rapidly shrinking.
“ah! the moment i brought you this news, the winner! the eternal winner! necromancer is coming out!”the camera angle turned quickly and focused on one side of the forest road.
the necromancer team was walking down the road.
 sungwoo, jisu, hanho, and minsok were seen emerging from the woods.
“who the hell doubted him? surprisingly, this is the moment when the third camp has defeated the other two absolute races and confidently rose to the top of the korean server!”after his request for the interview was ignored when the necromancer appeared, reporter ahn hated him, but at this moment, he had no choice but to cheer for him because it would draw in more viewers to his channel.
at that moment, jisu, the woman in red standing next to the necromancer, drew her sword.
then, she stepped forward all of a sudden.
since she moved so quickly, no one could respond.
“uh?”“what the heck did she do?”reporter ahn and his assistants stiffened their expressions, stunned at the unexpected scene.
 she blocked the necromancer with her whole body.
 she then glared into the air and swung her sword.
clang! clang!at that moment, a bright light erupted when the blade hit something a couple of times.
shortly afterward, what fell on the ground was a silver arrow cut in half.
as if to prove that it wasn’t an ordinary arrow, it released tremendous energy even though it was cut in half.
“uh? surprise attack? suddenly, someone attacked the necromancer! the fighting has begun again…”even before reporter ahn began to broadcast that unexpected fighting, the situation unfolded urgently.
sh-sh-sh-sh-sh-sh!the next moment, hundreds of arrows were fired from the forest.
at the same time, the attackers revealed themselves.
 they were the members of the skoll unit that the reconstruction alliance was proud of.
 they started firing numerous arrows.
“sungwoo, they are preparing to shoot again.
 let me go and disturb their attack, so get ready,” jisu said.
 she couldn’t guarantee she could stop the snipers’ attack.
 in this situation, it was the best option for her to distract the enemy camp and block the snipers.
sungwoo nodded.
 after making two bone shields, sungwoo threw one at hanho.
minsok raised the shield he was originally holding.
jisu put on the “goblin face armor” stretching to her neck and jumped into the arrows pouring down like rain.
clang! clang! clang! clang!she charged at the enemy camp at great speed, knocking down everything that flew over her head.
 as she passed, the broken arrows scattered in all directions.
it looked like she was a demon rushing toward them.
“can you see her? can you describe her as human? it looks like each member of the third camp has extraordinary skills.
”that wasn’t all.
 using the ‘shadow chase’ skill, she quickly reached the place where the snipers were located.
in the blink of an eye, she cut the four players holding axes.
 two of them collapsed, cut in half, while the other two fell at the invisible energy of the sword.
“argh!”“stop her!”that was the starting point of the domino phenomenon.
 behind her, the snipers began to fall one by one.
some of the snipers saw their arms cut while trying to fit the arrows, and even their wrists were severed and floated in the air.
“ahhhhhh!”

“argh!”the warriors whose limbs were amputated leaned against the trees and rolled on the ground, crying out in pain.
 their heads, torn from their torsos, rolled downhill.
a devil covered with red blood ran wildly, shaking the enemy camp.
“stop her!”“skoll troops, retreat!”“wizards, pull back!”like this, they were forced to focus on the woman in red, so they could not dare to aim for the necromancer because if they got distracted for a second, they were not sure when they would be beheaded by her.
 the warriors who allegedly had survived the hellish mt.
 taebaek were stricken with deep fear.
bumyeol clicked his tongue, watching the unbelievable situation.
“damn it! what the hell is that crazy bitch! how could she block the arrows?”he fired the item “sacred blood arrow” at the heart of the necromancer twice.
 the two arrows were destined to deal a fatal blow to the necromancer, which he had planned very carefully.
but no one, including bumyeol, imagined that the ghostly female samurai lady would destroy the two arrows.
bumyeol gnashed his teeth and shouted, “i now see why that old man told me to kill that woman first.
 but i really can’t believe she can fight so well like that!”but bumyeol’s assassination plan wasn’t a failure yet.
‘it’s too early for me to give up.
 i’ve got two more fatal arrows.
 let me kill that woman first and wait for the right time to attack the necromancer.
”bumyeol revised his plan and lifted his ax at the same time.
 then, he began to loosen his thick neck.
 of course, he had no intention of confronting that monstrous woman directly.
“euijin!”“yes, captain!”“use that picture! blow that woman away!”“got it!”

 