\section{chapter 363}

chapter 363: devil’s world tree and world eater (5)woo woo woo!




as expected, a gust of wind blew, turning back the freezing bullet.
 a blizzard swept towards sungwoo like a tsunami.
 a hundred or so undead around the world eater got frozen at once.
“kheeeeeeeeh!”in an instant, sungwoo teleported behind the world eater by using the ‘shadow movement’ technique.
 at the same time, he swung the grim reaper and sent out ‘evil spirit bombing.
’‘good!’dozens of spheres smashed towards the world eater.
 did he think that he could avoid them by moving his body? he drew his brows slightly.
‘what the heck? he only drew his brows?’obviously, sungwoo didn’t unleash this kind of attack to tease him.
in no time black spheres exploded, and black waves emitted from the sword.
 they acted like gravity, powerfully pressing down on the space in the area.
 the altar he was stepping on suddenly collapsed.
kugugugugugugu…the ground was made hollow in a hemispherical shape, shaking the entire space.
 and a huge amount of smoke was coming out from there.
“no matter how hard you attack me, it’s useless!”the world eater’s body slowly soared from within the hollow ground.
 he was still in very good condition.
‘what the heck is that?’something was running over his pale naked body.
 it was like dark red blood.
 but it wasn’t his blood.
 it flowed out of the jewels embedded in the sword’s hilt and covered his body, then formed red armor.
 it looked like the scales of a dragon.
‘is he invincible?’when sungwoo checked him with naked eyes, the world eater suffered no damage at all.
 it was highly probable that he was a perfect ‘invincible defender’ that needed no shield like the turtle image of the tsar sungwoo had confronted some time ago.
however, given that it peeled off immediately, he didn’t seem to maintain his current form forever.
“just give up.
 even if you do not die here, you are destined to die in the next war anyway.
”
he seemed to refer to the dozens of gates of devil’s cave that were opened in beijing.
like he said, sungwoo couldn’t survive the war in the future if he didn’t beat the world eater here.
 so, sungwoo had to kill him by all means.
but how?‘no matter how much i think about it, i can’t beat him alone.
’sungwoo judged his situation coldly.
 without others’ help or new methods, he could not defeat the world eater with his own weapon alone.
‘i need more power.
 i need to get out of here first…’at that moment, an item flashed through sungwoo’s mind.
‘ah, the second grim reaper?’but the world eater charged at him at that moment.
 he swung his sword at sungwoo swiftly.
he was so fast.
“no way!”but minseok popped out suddenly to block his sword.
the two ‘ruler’s swords’ clashed for the first time.
clang!with a clunking sound, minseok’s knee was bent, with his arms bouncing back.
“khuuuuuuk…”even the death knight could not withstand the world eater’s power and collapsed helplessly.
“ugh?”
however, for some reason, the world eater did not launch an additional attack on minseok.
he was distracted by the ‘ruler’s sword’ held by minseok.
 then, he reached out and grabbed minseok’s wrist.
“you can’t wield this sword!”when he confirmed that minseok was holding the same sword as his, he began to react sensitively.
“argh! how dare you say that?”“do you know what this is?”minseok nodded at his question.
the world eater clenched his wrist so hard that his bones were almost smashed, but minseok didn’t care at all and said, “argh! isn’t a perverted weapon swung by a naked idiot or a guy who wore clothes but had only bones with no flesh? i don’t look as good as you, but it still works the same.
”when minseok shouted back, there was anger in the world eater’s face.
“don’t make fun of me if you don’t know anything about the sword! i have lost many companions in order to own this sword.
”“…”“i was more powerless than anyone else, but i knew that one day it would change, so i had no choice but to sacrifice them for the future of this world.
”the world eater’s statement reminded sungwoo of the dragon knight boy he had seen in the past.
 the job of a dragon knight was obviously to be powerless in the beginning.
 was the world eater the same?“this sword is the strength i have gained in exchange for all that blood that i shed and all the patience that i had.
 and it is also the power with which i can rebuild this world someday.
 you guys will never know.
 so put your sword down right now.
”sungwoo could feel the world eater’s pent-up anger in his voice.
 minseok also looked up at him calmly as if he noticed it because he already knew the feelings of somebody who tried to protect someone else.
“hahaha…”at that moment, somebody sneered at the world eater.
“well, just give it to him!”it was sungwoo.
 the two turned their heads to him.
“pardon?”“what did you say?”sungwoo looked at the world eater with lots of ridicule and said, “you said from the beginning you were the last player or savior, but you were actually a failed guardian who couldn’t protect your world.
 you are an example of incompetence.
 i can understand why this world was ruined.
 your colleagues who died for you were an investment failure.
”as soon as sungwoo said that, the world eater released his grip on minseok’s wrist then approached sungwoo.
 red energy was spreading over his pale face.
 it was anger.
“necromancer, come a little closer to me and say it again.
”“i hate that.
 and …”sungwoo slowly stepped back, then looked over his shoulder.
“now is the time!”as soon as sungwoo shouted, a werewolf skeleton that was far away moved right away.
holding the second grim reaper, he threw it somewhere.
“uncle!”that huge weapon fell near his most reliable partner, minseok.
 minseok stretched out his arm to grab it.
 as soon as he grabbed it in his hand, a message appeared.
- your ‘death knight’ has met the special conditions to reach the state of ‘lich’.
a purple glow spread from minseok’s body.
 it was deeply concentrated energy of death.
“ugh! what is this power?”it was minseok who already had the trait of ‘skeleton mage’ when he was appointed ‘death wizard’.
 moreover, since he once experienced death, he even satisfied the special condition of ‘death witness’.
by obtaining the grim reaper, he could be reborn as the strongest death wizard, lich.


the whole area shook.
- you receive ‘synergy effect’ due to team play.
the synergy effect was the best even with three lich, but it was now upgraded to four lich.
[synergy list][ol start=”7-]revelation of apocalypse (hidden)- category: job synergy- condition: 4 or more users of ‘lich’ level death magic- effect: you can upgrade to the exclusive skill ‘ultimate’ (1 random type), and get the special skill, ‘power of the 4 knights of apocalypse’.
“what the heck is all this?”when something beyond his understanding happened before his eyes, the world eater’s face was distorted.
“what the hell did you do?”although he frowned when he confronted the ‘evil spirit bombing’ a little while ago, this time he was greatly agitated, or more precisely, embarrassed.
“why are you embarrassed?”he was obviously embarrassed.
“…”with a smile, sungwoo looked at the message that appeared in front of him.
 it was information about the special skill ‘the power of the 4 knights of apocalypse’ that he obtained through the synergy effect.
his eyes were slowly opening wide.
“a super-grade skill? wasn’t the ultimate rating the highest of all grades?”he finally got something huge enough to close the gap between him and the world eater.


 