\section{chapter 357}

chapter 357: jeju island and attack on demon’s cave (21)in the end, their shields that had been so strong broke and collapsed one by one.
 the monsters’ power was beyond imagination.
 the players’ skills were useless before their overwhelming power.





“no way!”their shields bounced off and their armor was torn apart.
 some of them were dragged into the air, caught by their claws.
“argh!”even though the crusaders boasted the best defense capabilities, they numbered a little over 100.
 so there was a marked decrease in their power when they collapsed one by one.
when their defensive line was in disarray like that, three monsters passed by at the same time and swung their claws, which pierced the shield and ripped off the crusaders’ heads as easily as they picked fruit.
“lower your head!”at that moment, their blood splattered through the air.
 it was as if someone sprinkled a bucket full of blood.
 in the blink of an eye, 11 members fell.
“commander! as things stand now, we’re going to be annihilated!”“…”frustration was growing in junghoon’s eyes.
 obviously, he made the right judgment, but he didn’t have enough strength to block the demons.
seizing the moment when they slacked off, about a dozen monsters escaped the siege.
 it was certain that the monsters would cause further damage to the people in the rear.
at that moment, a light flashed in the air, smashing the 11 monsters instantly.
 they soon scattered and fell to the ground.
right after that, jisu jumped down next to junghoon.
 then, two spirits appeared behind her.
“ah, jisu!”jisu, who had been dealing with the monsters that attacked the wizard troops, arrived here.
“it’s going to be a tough fight.
”she was clearly an overwhelming fighter, but even if she joined the crusader team, she could not block the entire portal.
 there was clearly a limit to each player’s room for maneuvering, but the battlefield was too wide for them to deal with the demons properly.
she looked into junghoon’s eyes and said, “brave guys have fallen.
”
“yeah, it’s because i was incompetent.
”jisu looked down at the dead.
“can i take their bodies?”“pardon?”junghoon could not figure out what she meant, but he soon understood and nodded.
there was no other choice at the moment.
 she lifted the sword and closed her eyes.
woooooooooo-then, a white beam of light came out from behind her.
 it was like she was spreading pure white wings.
- valkyrie takes the souls of the ‘qualified warriors’.
a white beam of light embraced the dead crew.
 then, their bodies began to shake.
“kheeeeeeeeee…”“ugh!”it was not their bodies alone that were moving.
- 18 warriors will be reborn as your ‘einherier’.
* you have reached the maximum number of your subordinate spirits.
blue souls were separated from their red hot corpses.
“you should not give up.
”jisu then turned her head and looked at the door of the demon’s cave.

behind her back, 20 rays of light, or more precisely, 20 einherjars, stood there, emitting a bright ray of light.
 it wasn’t just the necromancer alone who took death as assets.
***contrary to romantic sagas, human courage burns out as easily as a candle when they are faced with an unmanageable threat.
 no matter how much training a warrior may have had, the moment he smells the scent of death, he gets cold feet and eventually fails to show his capabilities properly.
that’s why the necromancer was strong because the army he led carried out their mission without hesitation under any circumstances.
“don’t step back!”then, what about those who have already experienced death once?“stop them from going outside!”“sweep them away!”those fighters who did not feel pain and had nothing to lose but who were full of anger were clearly different from other fighters.
unlike the coldness of the undead army, there was something like desperation and cruelty in their eyes.
 so, they fought more fiercely.
“man, are you sure they are our members?”minhum couldn’t hide his surprise.
 all of them were members of the crusader team who grew under junghoon.
but after they were resurrected, they were now totally different beings as if they realized their own fates.
“sure, they were once your members.
 they are clearly the guys we used to know, but they are moving without any fear or hesitation.
”they charged without hesitation toward the gate of the demon’s cave, led by the angel of the battlefield, namely valkyrie.
even ‘einherjar’ will disappear if they suffered a lot of damage, but since they experienced death already, didn’t they care at all?“don’t let any monster escape!”rather than block the portal while maintaining their formation like the crusader team did, they pushed hard toward the gate.
 they were now fighting against the terrible monsters.
since they were translucent ghosts, they soared into the sky, disregarding the laws of physics, then smashed the demons coming out of the portal in droves.
“wow! they fought well last time, but they are really doing great now!”one valkyrie and twenty einherjars moved vertically and horizontally in the three-dimensional space, tearing apart the monsters that came out of the portal.
the players felt a sense of awe while watching the scene.
“look at that.
 it feels like they are moving in unison!”“wow, it looks like an angel is swinging dozens of wings?”einherjar’s translucent bodies were connected to jisu, who could use them as if she was wielding a giant mace.
 according to her will, the mace dealt flexible and irregular blows to the monsters then it was summoned behind her back at a dangerous moment.
 when seen from a distance, it looked as if 20 beams of light were flashing and knocking down the portal.
as their attack continued, the corpses of the monsters piled up under the portal.
“we have made it! the monsters can’t come out now!”suddenly, the tide of the battlefield was turning in jisu’s favor.
- you have obtained 850,000 gold by hunting an ‘alien being’ (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien being’ (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien being’ (intermediate monster)’.
- you have obtained 850,000 gold by hunting an ‘alien being’ (intermediate monster)’.
(intermediate monsters)’.
a large number of messages kept popping up before her eyes.
 she achieved something remarkable, which was different from when she fought alone.
her ability to summon her subordinate spirits brought about a very effective ‘synergy effect’.
[synergy list]

god’s soldier (level 2)- category: attribute synergy- condition: 20 or more ‘intellectual families’ with deity status.
- effect: increases health (+70%), increases immunity against all abnormal status (+50%) and forms a shield equivalent to 150% of health.
existence without substance (stage 4)- category: attribute synergy- condition: 20 or more in the form of ‘soul’- effect: moving speed increases (+35%),with such a synergy effect, jisu moved faster and slaughtered the monsters that came out of the portal.
jimin couldn’t keep her mouth shut.
 she was, of course, surprised by her sister’s unbelievable performance, who changed so much since she had seen her last time.
 but she just felt dizzy when she found jisu fought better every time she confronted her opponents.
“gosh, what have you gone through until now?”in the meantime, even inho couldn’t take his eyes off the scene for a while, even though he had to check out the allies’ status on the battlefield.
“valkyrie has won the battle with one single attack.
 yeah, i know why sungwoo has left her behind here.
”but the battle wasn’t over yet.
inho came to his senses and issued a new order.
“we need to quickly get rid of those monsters who slipped out of the portal and help valkyrie!”

 