\section{chapter 317}

finally, the broadcast screen showing the battle situation in busan was restored.
 it seemed that they dispatched another drone, which was looking down at busan from much higher in the sky.





"ah…"the moment the two commentators saw the scenes they had been waiting for, they couldn't help but open their mouths wide, stricken with shock.
"oh, my god! busan.
.
.
""in fact, busan has disappeared!"the heat of the explosion was somewhat gone.
 however, a scene reminiscent of an inferno was still unfolding in the ruins of busan.
 not only the two commentators but also all the viewers could not believe it because everything they used to know of the city was swallowed by 'black smoke'.
"man, i thought it was the sea.
""me, too.
"visit lightnovelpub[.
]com for the best novel reading experience several skyscrapers that survived the fire were barely sticking their heads out of the black smoke.
 they looked like a square island floating on a black sea.
 in addition, dark purple clouds in the sky were pouring black rain everywhere, so they looked like a secluded island in the vast sea hit by a storm.
"we are definitely being ruined right now, but everything in busan was ruined way beyond our imagination.
 i've never imagined busan was devastated like this.
"and they saw the necromancer flying in the sky on the fringes of the hellish island.
one of the drone cameras directed toward him showed him keeping up with fierce bombings on busan.
although they expected someone was responsible for such a devastating attack, this was the moment when the person who launched such a massive attack was none other than the necromancer.
"alright.
 let me correct my analysis and tell you all over again," said reporter ahn, unable to hide his excitement.
 "at first, i thought that since most of our korean server troops were deployed in suwon, they might want to move to another battlefield after winning in suwon.
"
"you mean while they were holding out in seoul and busan?""yes.
 i thought while seoul and busan were like shields, suwon was like a spear.
 but…"reporter ahn reached out and pointed to the screen behind his back, namely the scenes of busan.
 the necromancer was fighting fiercely there.
 visit lightnovelpub[.
]com for the best novel reading experience"after all, the necromancer was the spear, as expected, which could break through everything at that.
 if so, where would he throw the spear?""seoul? or the most important city of suwon? he would obviously throw it at one of the two, but i wonder which one he would prioritize.
"reporter ahn nodded at his assistant's words.
 "no matter where he throws it, i can believe that he will pierce the hearts of the chinese players with the spear.
"looking straight at the camera, reporter ahn continued, "now, i am convinced that we are going to win this war.
"reporter ahn decided to trust the necromancer again.
***in the meantime, the troops of the korean server deployed in seoul rightly used the strategy of "holding out.
""brother! they are coming in droves from the north!"the source of this content is lightnovelpub[.
]comone tiger reported to the king of the great mountain.
 "really? they dared to come down now?"
the king dusted off his long pipe right before lighting it then put it inside his pocket.
"we're going to retreat to the designated exit!"they hurried to the alley.
 since they were monsters that lived in the mountains, they could quickly notice and respond to enemies' approaches.
they stopped running away for some time.
 "whew! i think we are out of the enemy's range.
 let me watch out for the surroundings carefully!"jisu, the king of the great mountain, and their dependents dispersed all over seoul as part of their 'evacuation strategy.
'while they were trying to save as many as possible without confronting the 4,000 enemy soldiers, they sought to avoid being defeated by the enemies.
 for more, visit lightnovelpub[.
]comhowever, the enemies' chase was persistent.
 the enemies were also stronger than the king thought.
 the king felt in real-time that his subordinate spirits in seoul were being killed everywhere.
"they are closing in on us gradually.
""you bet! more and more are dying.
""then, how about confronting and killing them?" jisu asked.
 but the king of the great mountain shook his head at her suggestion.
"lady jisu, our operation this time is different.
""you're right…"several times jisu suppressed the urge to behead those who were chasing them.
'the king is right.
 they are so numerous that i can't stop them by simply using my sword.
 rather, i would give away our location.
 so, it's right to run away from them according to our original operation.
'this content is taken from lightnovelpub[.
]comwhile holding back her instincts, she withdrew her hand from the sword on her waist.
"by the way, jisu, it looks like they are very good swordsmen.
 do you happen to know them?""yeah, maybe.
"the group who persistently chased jisu and the king of the great mountain were obviously those in the 'ninja' occupation group who she had met before.
 in other words, they were the subordinates of the sword master of the japanese server.
after the sword master was defeated by jisu, had they been waiting for an opportunity to take revenge on jisu and her party? jisu felt they were fully prepared to kill her this time.
"in my view, they have been trained to kill a swordsman like you.
 so, you have to keep that in mind all the time!""yeah.
 i also felt it.
"they knew very well that it was very unlikely that they would beat jisu in sword fights.
'because i cut down the sword master, they must have felt i was the terrific blade woman.
'visit lightnovelpub[.
]com for a better experienceso, they moved around to hunt, not as swordsmen.
 even if they discovered jisu, they never got close to her.
 instead, they closed in on her little by little from a distance, then poured all kinds of ranged attacks on her.
especially something like a bomb a moment ago is dangerous to me, too.
'no matter how many arrows they fired, she was confident of blocking them, so they prepared more draconian weapons.
 in other words, they threw something like a "bomb bag" filled with beads or iron pieces.
 if jisu moved even a little late, she could be ripped apart in an instant.
 'at first, it was a close call! i was lucky.
'

about 10 minutes ago, an object she saw for the first time fell right beside her.
 she was wary of its strange appearance, so she made the mistake of instinctively raising her sword.
 that was not something she could strike down with the sword.
 if the king of the great mountain had not covered her body with tree roots, she could have really died.
"they are approaching us again!""this time they have even blocked our retreat!"it was stupid to hope for continued success while repeating the same operation.
 but the problem was that there was no other way.
 jisu put her hand on the hilt of her sword.
follow current novels on lightnovelpub[.
]com"let me break through them.
""yeah, we have to confront them this time.
" the king lifted the blue dragon ax.
so jisu and her party rushed toward one side of their siege.
 dozens of them blocked them, but when jisu charged at them desperately at the risk of her life, they could get through in just a few seconds.
 whenever they threw bomb bags, the king covered them with tree roots.
 "jisu, keep moving! don't pay attention to your surroundings! i'll provide cover for you," the king shouted.
after all, jisu and her party succeeded in breaking out of the siege, but this time, some of the people under the king's command fell behind.
 and there was the sound of explosions and shouting in other places.
"brother, more and more of our people are dying.
""already more than half…"the friendly forces were being defeated unilaterally.


 