\section{chapter 430}

"it's all over.
"




nguyen gave up and sat down on the chair, and at that moment, the ceiling was torn off and light penetrated it.
"here you were! it smells.
"a huge demon was standing in front of nguyen and his men.
 he had only one long, reddish-brown eye torn vertically, a muscular black body, and blood-stained wings.
"the smell of the weak, the smell of prey.
"but there was a player standing near the giant's feet.
 nguyen knew him.
 it was tran, the leader of the demon worshipers.
"nguyen, is this the first time i have seen you so miserable.
"despite tran's sarcasm, nguyen didn't say anything.
 he didn't want to speak with this human scum unnecessarily until the last moment.
"it looks like you don't even have the courage to open your mouth.
 yeah, you should have made a good choice! man, do you think the world tree camp can accept us when they are busy saving themselves?"advertisements    while laughing sarcastically, he spat at nguyen.
"well then just die while regretting your decision!"light emanated from the devil's eyes.
 it was a light attack.
"ah…"nguyen and his men did not dare to resist his attack.
even if they took down this monster somehow, they would not be able to block the thousands of demons behind him, who were ready to storm into the building.
 at that moment a strange thing happened.
bang!a huge green object fell from the sky and crushed the demon.

it was the huge feet of a huge beast.
 "argh! hey, what the heck is this?"tran, who was standing next to him, ran somewhere, panicked.
"what is it?"then, there was an explosion that seemed to tear the whole world apart, and it seemed as if the demons flying in the sky were falling in droves.
 but ngyun could not find out what's going on inside the chaotic hole.
 nguyen eventually crawled out of the hole.
 and he looks around.
 "oh, nice to see you here!"a giant green turtle-shaped monster was standing tall above the hole, and a six-armed man with six shields stood next to him.
even though that monster greeted nguyen, he had no time to mind others at the moment.
 nguyen even wondered if that monster was a devil because of his bizarre appearance.
"everyone, don't worry now.
 i'm here! you saw that man already on the broadcast, right? i mean the hero who protected the world tree by confronting the emperor alone.
 it's me!"after he rambled on like that, he turned his head somewhere.
"we've found some survivors here! sungwoo, look over here! i've saved them!"nguyen turned his head to follow that man's gaze and looked around.
 obviously, something astounding happened a moment ago.
"oh my god…"a huge number of players appeared suddenly, who were now slaughtering the demon army that had taken over hanoi.
"commander, they're coming from over there!"as he turned his head at his deputy's shouting, a fleet of airships appeared from the northern sky.
"over there, too!"
in the east, a huge wave rose from the ground and devoured the demons.
it was a counterattack by the world tree camp players who increased dramatically with the continuing arrival of their reinforcements.
 nuyen and the players on the vietnamese server stared blankly at their brilliant fighting, who overwhelmed the demon army.
 "i can't believe my eyes! they are the world tree players!"when they were blown away by the world tree players' mighty power, a black shadow fell from somewhere.
"dragon… bone dragon!"the most powerful subordinate spirit under the necromancer, bone dragon, approached them.
he then landed on the ground, and someone jumped down from his head.
it was the necromancer who wore dark green robes and bone armor with an indescribable aura.
 "are you the commander of the vietnamese server?"at the necromancer's question, nguyen was momentarily spaced out.
 but he came to his senses shortly afterward and nodded.
"yes, that's right," nguyen replied politely.
"let me ask you one thing.
"having said that, the necromancer looked back.
 behind him was a huge number of troops that they had never seen since the destruction of the world.
 they were a mix of airship fleet, undead, ghosts, players, hippogriffs, and even dragon.
nguyen lost his sense of reality for a moment.
 their formation was a magnificent and fantastic scene as if an artist portrayed the army of a great empire on a huge battlefield.
"do you want to join us?"nguyen was both embarrassed and thrilled to be invited to join sungwoo's forces.
 as a matter of fact, he wanted to join the world tree camp for a long time.
 they appeared directly here, saved them, and now invited them to join.
"absolutely!"the necromancer stretched out his hand, and nguyen hurriedly held it.
"alright.
 we're going to start an expedition to destroy the two absolute races from now on.
 get ready!after he said that, sungwoo turned.
'i've already won over seven servers.
'players from a total of 6 servers, including korea, taiwan, china 1, china 2, china 3, and vietnam, have united together.
 "okay, our next target is the laos server! when our moving option comes up, we're going to choose the laos server!"six servers were just the beginning.
 in the future, dozens or hundreds of servers would join forces.
'they are wrong.
'the absolute races might have thought this event was in favor of them.
they might have seen it as an opportunity to regain the initiative lost to the world tree camp and recover the shaken ecosystem by uprooting the world tree camp.
'on the contrary, it is an opportunity for us to burn down the remnants of the absolute races.
'if they toured the world by attacking each server like this, it was an opportunity for them to unite all the forces scattered throughout the world at once and easily eliminate the remaining followers of the absolute races.
nguyen was still staring blankly at the back of the necromancer as if he was still confused.
 then, one of his subordinates approached and said, "commander, we have gathered the surviving comrades.
 what should we do now? please give us an order.
"at this question, nguyen nodded and raised his voice.
"vietnamese warriors! follow the necromancer from now on! we, humans, are going to counterattack!"if one faces the savior in the midst of a crisis of death, one will naturally follow him.
 and one naturally relies on him and takes for granted everything he says and does.
 that's one's instinct.
 sungwoo was convinced of this time-honored rule.
 'after this war is over, the governing body i'm devising will be complete.
'

the crisis for him was a huge leap forward, as always.
 ***immediately after the invasion began, the 'fight ranking' was released, which was also being updated in real-time.
"now, we have found out the fight ranking as of now.
 let's check it together!"reporter ahn made a chart of the 'fight ranking' visible only to some players and put it on the screen.
"well, should i call it as expected? nonetheless, this is really surprising.
 one whole page is full of the players from the korean server!"[fight ranking]1) kor-157: 14,880 points2) gangsok han: 13,560 points3) kor-339 : 10,900 points4) yeongdeungpo prosecutor's office: 8,500 pointsadvertisements    5) most strong: 7,440 points"wow! all the top five players are from the korean server! it wouldn't be strange if i mistake it for the korean server rankings.
""another thing we have to pay attention to is that four of them are affiliated with the world tree camp.
 don't you think so?"reporter ahn nodded repeatedly at his assistant's words.
"yes, that's right.
 that was inevitable from the beginning!"

 