\section{chapter 422}

sungwoo already planted his image as something holding the hegemony of the world by defeating the emperor.
 what if he would be pushed aside by somebody else in this 'ranking competition'?




'if i lose, everything will go wrong.
'it's hard to build one's solid reputation, but it's easy to ruin it.
in that respect, he would engage in this upcoming war as a defending champion.
sungwoo raised his head and looked at the commanders.
"we're starting again," he shouted.
 all of them nodded.
 actually, they were quite familiar with this kind of atmosphere.
"from now on, please go to your place and be prepared…"they had only 48 hours to go before the invasion.
 so, sungwoo needed to arm all his troops to the maximum within that time.
 "mobilize all your resources for this fight.
 don't spare anything, and invest all of it.
"what the world tree camp could be proud of numerically was that they had a lot of money.
sungwoo envisioned a special operation for this war.
, and he called somebody to take care of this operation.
 they were jisu, junghoon, and heyon.
so he headed to the 'a-grade item warehouse' with them.
 it was the most secure warehouse where the items of the minimum hero level were stored.
"welcome.
"the chief of the 'logistics management team' welcomed them.
 
"this warehouse is the place where we store the most valuable items in the world tree camp.
 since they have several security measures in place, there is no risk of theft.
"as he said, the highest-grade weapons were stored there.
 among them were a lot of loot from this war, such as the blue dragon sword and banchon spear.
visit lightnov­elworld.
com for a better experience"now, everything inside this red line here is legendary or higher grade items.
 they are a total of 24 items, and we got 17 out of them during the recent war.
 ah! please let us know when you take them out.
 even if you are our allies, we have to keep the records thoroughly.
"after having said that, the logistics management team leader disappeared out of the warehouse, and sungwoo opened his mouth.
".
well, no matter how high your level, it's not easy to get legendary items unless you're lucky.
"he looked at them and said, "so, someone will have to deal with this top-grade equipment… i would like to ask you a favor.
then he lifted the 'blue dragon sword' among the legendary items.
 its heavy shadow fell over his feet widely.
 "please select elite players of the highest level and establish a special commando unit.
"special command unit? the three of them could not hide their bewildered expressions.
 in particular, heyon seemed not only embarrassed but also scared.
 "special commando? you didn't call me for this operation, right? i think i heard it wrong," she said, expressing surprise.
 the other two standing next to her were strong enough to fit such high-grade items, but she thought she had nothing to do with such weapons.
"it's true i called you for this team," sungwoo replied briefly.

he continued, "now, we need warriors who can properly use these quality items.
 i'm going to maximize their power by making them into a team.
"among the many players, there were definitely those with overwhelming abilities.
even though they were not as strong as sungwoo, jisu, and hanho, they could be something like a strong and important weapon for the world tree camp if they were fully supported physically and materially.
"what i want is not just a high-level and well-armed unit, but a 'special unit' who can carry out special missions.
"special unit? in fact, if sungwoo were to train such players, nobody was as good as jisu and junghoon as their trainers.
for example, based on her transcendental sense, jisu knew how to use the most skilled movement than anyone else, and junghoon was already commanding the most elite unit called the 'crusader team'.
 on the other hand, heyon still didn't know why she was here.
follow new episodes on the lightnov­elworld.
com platform.
"um, when you say special command unit, you mean we are training the players to achieve a specific purpose.
 then what is your purpose?" junghoon asked.
 sungwoo pointed to the blue dragon sword and said, "it's an air maneuver operation.
""you mean training them to fight in the air?""yes.
"as if he was bothered by something, junghoon asked again, "then what are the means of flying in the air?"at that moment the warehouse where they stood shook because airships flew over it a moment ago.
"they are coming.
 let's get out.
"the fact that the airships were flying overhead meant that the "hypergate" was most likely opened.
 they left the warehouse.
 then, the shadows of the airships were thickly cast over their heads widely.
"is this a security operation?"the 'jump space', where the hypergate was installed, soared tens of meters above the ground, so it was exposed to terrorism completely.
 in other words, in preparation for an emergency, a large number of airships went into a sharp alert operation whenever the hypergate opened.
 "come on, look over there.
"sungwoo pointed to the towering 'jump space'.
 soon, the space was distorted, opening the hyperspace.
 then something started pouring out of it.
 these were winged creatures, who spread out in all directions and scattered, then started spinning on the runway.
heeeeeeeeeey!it was hippogriff, a flying creature that looked like a mixture of a horse and an eagle.
hundreds of hippogryphs appeared in the world tree camp.
"a little while ago jisu contacted me.
 according to her, the players on jeju island captured and tamed a number of hippogriffs.
"jeju island's 'monster worshipers' tamed a number of hippogriffs and used them as an air force.
visit to lightnovelworld.
c­om discover new novels.
however, after the monster worshipers were wiped out by the world tree camp, the jeju island players led by jimin captured all of the hippogriffs and learned how to train them to fly.
 "from this war on, the players of jeju island also decided to fight together as part of the world tree camp.
"just like the group of players in ganghwa, taiwan, and paju, the players on jeju island grew strong enough to do their part and joined them as they promised.


"the special commando unit i mentioned will ride hippogriffs and serve as the 'deck plane' of the world tree fleet.
"the 'united fleet' of the world tree camp was obviously a tremendous force.
 however, during the last battle, it was not easy for them to fight against close-flying attacks.
 they were also exposed to the attacks by the mongolian server's keshik cavalry.
so, if they had a small and agile flying force that could act as a deck plane, they could not only defend against such an attack but also increase the attack power of the fleet.
sungwoo looked at heyon and said, "now you understand why you're here, right?""oh, i see.
.
.
""you have to be the flight instructor for the special commando unit.
"heyon's face blushed.
 "i'm afraid i can do it well…"she was not confident.
 even though her job was a 'griffin rider', she served only as a liaison officer until now.
 sungwoo said firmly, "i don't know that either, but nobody can do it except you.
"the proper working of an organization depended on whether it had the right people with the right capabilities.
 she took a deep breath and said with a nod, "alright.
 let me try.
"she was nervous for a moment, but she was by no means a fragile girl.
 since she was in ganghwa island, she admired the necromancer, and at the same time she tried hard to be strong/"sorry, i disappointed you by replying like that.
 let me try to do it well.
"visit to lightnovelworld.
com discover new novels.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 