\section{chapter 262}

                            “i hear the liberation guild and the hunter company will arrive within an hour to come to our rescue, so if we can hold out until then…”




they pinned hope on the fact that they would get help from giant groups that declared their participation in the war.
 however, their hopes quickly fell apart.
“captain!”“what’s the matter?”“thousands of zombies are coming down from the north in droves!”“oh, my god…”the hordes of zombies that he expected would come down first finally began to move.
“damn it! if they come down now…”right now, just stopping the monster army was overwhelming for them.
 if thousands of zombies joined them, it would be a disaster for the players in paju.
“we really can’t defend against them.
”they would collapse helplessly like a small embankment swept away by a tsunami.
meanwhile, reporter ahn was filming all of these scenes from the roof of a building a few hundred meters from the fortress.
“ah! gosh! hordes of zombies are coming down in droves! they are huge!”even reporter ahn spoke in an embarrassed voice, faced with such an unexpected situation.
“they can’t stop the zombies! it’s impossible to stop them! they are on the verge of annihilation! if any of you coming to help the paju players right now are watching our broadcast, we hope you hurry up! their fortress is going to collapse quite soon!”however, an unexpected situation occurred once more.
“what the heck?”
the hordes of zombies that approached the rear of the monster army started attacking the monsters.
“what the heck is happening now?as if they didn’t expect such a situation at all, the monster army was wiped away helplessly.
 they started resisting belatedly, but the hordes of zombies that already arrived weren’t easy to stop.
as if the dam broke, the horde of zombies penetrated the monster army, who began to collapse after their formation was broken.
reporter ahn opened his mouth wide at that shocking scene.
“i can’t believe how the zombies could attack the monsters…no, i can’t believe this… i wonder if this was possible because of…”he didn’t know what was going on, but he realized who was responsible for the zombies’ indiscriminate attack.
“is it the necromancer?”the necromancer moved.
the monster army attacking the paju fortress thought mistakenly that the hordes of zombies coming down were their friendly forces.
 they were dispatched by the necromancer to help the paju players.
so, the moment the orcs, who were on standby in the rear, had their necks bitten by the zombies, all they did was watch them helplessly.
kheeeeeeeeek!it was natural.
 didn’t the zombies originally attack the korean server while serving the ‘monster emperor’ like them? how could they attack monsters like them from behind?unless they were players, monsters wouldn’t attack other monsters because they shared common interests.
 therefore, they had no choice but to be attacked by the zombies.
“the army of monsters from the north has begun to collapse because of the hordes of zombies from the north!”reporter ahn, witnessing the actual scenes of their fighting, was conveying what was going on in real-time in an excited voice.

“well, as if they didn’t expect it at all, they were completely caught off guard! by the way, i am not sure if the hordes of zombies are the necromancer’s subordinate spirits.
 they had been affiliated with the north korean server for a long time, but how could they come down to the south like that…”reporter ahn could not grasp the exact situation.
 but he knew one thing for sure.
 the only one who could send out zombies like this was the necromancer.
it was becoming clearer who would emerge as the winner of the battle.
oooooooh!although these low-level zombies dispatched by the necromancer were weaker than orcs, they attacked from all directions, so the monster army could not withstand their attack.
 even if they killed one zombie, two zombies immediately counterattacked them.
since the zombies attacked without fearing death, the monsters could not afford to recalibrate their attack.
 it was as if they were facing an unstoppable landslide.
grrrrrrr-as a result, the monster army was gradually losing their fighting spirit since they were exposed to the zombies’ attack.
“alright! now is the time!”above all, the fact that their retreat was blocked was a fatal blow to the enemy forces.
“they’re offensive has weakened! it’s time for us to demonstrate our firepower!”“cast the ranged magic!”finally, the paju players, who survived the enemies’ offensive, began to demonstrate a wide range of firepower while focusing on their attack.
since the enemies’ retreat was blocked, there was nowhere they could escape.
 so, the paju players’ ranged attacks dealt intense and lethal damage to the enemies.
“they are collapsing!”“let’s finish this fight! everybody, get ready to charge them!”the paju players who gained the momentum to turn the tide aggressively charged at the monsters to end the fighting as soon as possible.
goo goo-finally, the iron gate of the fortress opened.
 at that moment, two 20-ton trucks pushed ahead to open the way for the players.
 tankers ran out in a row and lifted their shields.
“ready to push them with the shields!”“let’s sweep them away!”with the addition of the hordes of zombies dispatched by the necromancer, they were no longer inferior to the enemies numerically, which made them fearless.
 relying on their unique strong formation, the players began to push back the monster army.
“great! we are starting to break through the enemy line!”“they can’t focus their attack against us because of the zombies! we have to crush them right now! charge!”the players who were beheading the orcs and goblins came to encounter the zombies at some point.
 thousands of zombies were in front of them now, which meant that they annihilated the monster army.
 but the players were faced with an indescribable dilemma when they looked at their bizarre looks.
“these zombies are on our side, right?”they felt like they were compelled to use their weapons to attack the zombies.
“yeah, they are probably controlled by the necromancer.
”“by the way, is the necromancer on our side?”the players recalled the time when they swore at the necromancer, though briefly.
wasn’t it the one heart association that shifted the responsibility of the mainstream to the necromancer and posted a message to the community, urging them to cut down the world tree?“i’m afraid the necromancer might kill us because of that.
”“no way! i was cheering for the necromancer from the beginning.
 i didn’t swear!”

“i know! it’s afterward.
 the damn dotards of the one heart association who posted such comments criticizing the necromancer, not us! they didn’t even ask for our opinion.
”when they began to feel the overwhelming status of the necromancer, they began to deny their long-standing association with the one heart association.
at that moment, the zombies began to step back one by one.
 thousands of them were split like the red sea, which moses divided by stretching out his hand over it.
someone walked along the long road between them.
“is he the necromancer?”as expected, he was the necromancer wearing a dark green robe.
 he looked at the players who came out of the fortress and opened his mouth.
“our battle is not over yet.
 so, go back and repair the fortress.
”“ah, yes! understood!”the players of the one heart association followed his instruction obediently as if he was their supervisor.
“we have no time to take a break! immediately return to the fortress and repair all damages!”“everybody, go back to the fortress!”but the necromancer turned right after saying that.
“wait a minute! is he going back again?”“what? i hope not…”the commander of the one heart association could not hide his anxiety, so he chased the necromancer.
“wait a minute, necromancer!”

 