\section{chapter 264}

                            “wow! oh, my god! you have shown the mighty power befitting the god of death! crackle! crackle!”




watching sungwoo’s subordinate spirits smashing 100 trolls in an instant, victor expressed excessive admiration.
“shut up!”“ah, yes! crackle!”sungwoo and victor’s undead army pushed deep into the north korean server and repeated combat and bypass while moving.
 when they encountered opponents they could fight, they smashed but avoided them if the fighting would be likely to take long.
“master, don’t you think our guys in the rear are going to be in danger?”victor was right.
 that was why the expeditionary forces did not attack the capital immediately but smashed the castles on the outskirts first.
sungwoo also knew that his forces would be exposed to the enemies’ attack if they pushed ahead recklessly.
“yeah, i know.
 but i have a plan for that.
”“got it.
 i trust you.
 crackle!”while they were advancing deeper and further towards pyongyang, a message rang.
-‘lich (victor)’s ability slightly increases.
* you can control a ‘small skeleton’.
as an undead with excellent intelligence, victor could see his ability increase by being next to sungwoo.
“oh, master! i just wanted to let you know…”“i know that already.
”“crackle!…”of course, a small skeleton was not a powerful undead.
 at best, he could resurrect goblins or kobolds.
 however, in terms of the wide range of materials that could be used, sungwoo could diversify the types of combat troops and make use of the lightness and agility of the skeletons.
‘if they can be upgraded to medium-sized skeletons, they are going to be a much more powerful force.
 an orc skeleton unit with 3,000 soldiers?’
monster lich had his strength like the player lich mainly in terms of quantity rather than quality.
they kept advancing into the north for several hours.
“master! a huge army is approaching us from a place about 14km away.
”finally, their long boring march was at an end.
sungwoo stopped his troops on the ridge.
“huge army? how many are they?“they’re a whopping 10,000 or more than that.
 crackle! it looks like the emperor ordered them!”if this was an army of more than 10,000, they were different from the defending troops along the borders.
‘these troops have been dispatched from pyongyang.
’finally, the time he had been looking forward to came.
“good.
”sungwoo immediately summoned a bone wyvern.
 when he got on it, victor tried to follow him, but sungwoo stopped him.
“what are you going to do, master?”“now we’re dividing our troops into two before moving on.
”“pardon?” victor was confused.
“from now on you are fighting them.
”“you mean i am alone fighting them?” victor asked as if he was embarrassed.
“more precisely, just keep dragging it out while confronting them.
”
“what about you, master?”“i’m going to move to pyongyang.
”this was the reason why sungwoo brought the thousands of zombies controlled by victor deep into the north korean server.
“make that guy called the emperor believe that i’m still staying here.
”“…”having said that, sungwoo got on the bone wyvern and flew away with victor looking at him blankly.
crackle! crackle!only the sound of him nervously bumping his teeth resonated over the desolate north korean soil.
***pyongyang was very different from the regions that sungwoo’s troops went through.
 they could see some high-rise buildings in pyongyang on the north korean server, compared with lots of desolate regions.
 the tallest building among them “ryugyong hotel,” was a modern pyramid built by the north korean dictator.
but now there was some mysterious noise coming out of that building.
 it was the sound of the rebar bending due to the unidentified heat rising from the basement under the center of the building.
nonetheless, the building did not collapse because of some magical power.
three players arrived at a place hundreds of meters away from ryugyong hotel.
 they were sweating even in the middle of winter.
“damn, it’s hot even if i’m standing so far away from the hotel.
 damn fire lizard…”“watch your mouth.
 he’s notorious for having a nasty temper.
 don’t forget that we are the emperor’s emissaries.
”they stared at ryugyong hotel with an unhappy glance.
“how can the guy claim to be the emperor when he is nothing but a monster? by the way, i wonder what kind of business our real emperor is going to do with him.
”“using the enemies to fight against our enemies!”1“…”as their conversation suggested, they were the envoys from the “china-1” server.
after finding out that a large number of intelligent monsters were born on the destroyed north korean server, they reached.
and what they expected was that the monsters on the north korean server would destroy the potential enemy of the south korean server, the necromancer.
“that butler is coming.
”at that moment, a lizardman walked out from ryugyong hotel.
 he was dressed in a black suit and looked quite different from typical monsters.
the lizardman bowed to them first, then said, “our emperor has not yet woken up.
 so, i’m afraid you have to wait for a few more hours.
”the three players were not familiar with this kind of monster who used such precise language.
“we are envoys from the chinese emperor.
 haven’t we waited two days already? how can you treat us so poorly?”“moreover, the necromancer is marching north, according to the korean server.
 is it okay for you guys to stand as onlookers like this?”1they wondered if it would make sense for them to complain to the monster, but the lizardman politely responded after listening to their complaint, “please wait a little more.
 the necromancer from the south can’t move up here.
 no matter how strong he is, he can’t deal with the 20,000 troops our emperor has dispatched.
”“what? 20,000 troops?”given the size of the troops, they were clearly in a different league.
 although the necromancer fought many times, he typically confronted an army of several thousand.
“that’s right.
 since his majesty stayed in bed longer than expected, he had his generals in charge of the troops when he dispatched them.
 as a result, we hear that the necromancer has begun to go back to the south, driven out by our troops.
”the lizardman in black suit fluttered his tongue after saying that.
 there was confidence in his eyes.
 they got rid of all the players on the north korean server and gained enormous power.
so, they didn’t feel the korean server players were a big threat to them, no matter how strong they were.
“oh, that’s good to know.
 we just felt you were too complacent when the enemies were around the corner.
”“chinese envoys, let me tell you something briefly.
”

the lizardman explained to them arrogantly as if he wanted to teach them.
“only one ‘monster king’ appeared on the korean server.
 but i hear they were nervous because they could not kill him.
 we have eight monster kings, and the one with the most overwhelming power is his excellency, the emperor.
”then, he finished talking, slowly bowing to them.
“you don’t have to worry at all.
 even if he is the strongest on the south korean server, our emperor is in a different league.
”“…”the faces of the chinese players were still full of irritation because they couldn’t wait indefinitely, but they could not complain anymore.
“sure, we’ll wait a little longer.
”“thanks, i’ll convey your message to the emperor.
”after all, they turned around to wait a little longer.
thud!at that moment, a small explosion was heard somewhere.
 all of them turned their heads to the explosion.
 the epicenter of the explosion was the skyscraper of ryugyong hotel.
“who the hell is that guy…”someone was standing on the skyscraper.
“he’s that bastard!”the players on the chinese server recognized him, holding a huge black sickle with his green robe fluttering.
“necromancer.
”at that moment, the black scythe he was holding was seen swinging with a black wave.
it turned into opaque spheres and began to form on the blade of the sickle.
 they numbered about 50.


 