\section{chapter 271}






 the king nodded.
 after eating the potatoes, he took a long pipe out of his pocket.
then, the tiger standing behind him put tobacco leaves inside the pipe.
when the king snapped his fingers, a blue flame floated in the air and landed on the tobacco leaves.
 the pipe was lit.
“whew… our world also has a power comparable to the world eater’s power.
 the so-called world spirit can stop him from using his power.
”“then, they must be desperate to get rid of the world spirit, right? and that’s why they want to make everything in this world their subordinate like the evolution society.
”“jisu, that’s correct.
”as jisu said, dr.
 yu, the head of the evolution society, had been serving the world eater.
“because they cannot directly exert power, they first corrupt someone through minimal intervention, then control him like their minion.
 i think it’s their strategy, but i think there are several minions right now.
 perhaps they might have intervened in the collapse of the north korean server.
”the king’s gaze again turned to sungwoo.
 then, he pulled something out of his pocket and presented it to sungwoo.
“you know what it is?” the king asked.
it was a dimly lit black stone with all sorts of symbols engraved on its surface.
“isn’t it a prophecy stone?”“yeah, it’s going to tell you about a guy of very high social status.
 you will be surprised a lot to hear it.
”sungwoo accepted the prophecy stone.
 compared to the prophecy stones he confirmed until now, he felt it was somewhat heavy.
-you have touched the prophecy stone (world bad ending-2).

as expected, a video began to play.
‘earth?’the first scene that unfolded was the earth itself.
 as if looking down from the space station, he could see the whole earth at a glance.
despite the destruction of the earth, its appearance from space did not look much different.
 the part where the light did not reach was immersed in the colorless darkness.
something was floating on the border of that darkness.
‘what is that? a face?’it was a face.
 like a mask, a face with only facial skin, but without a skull, floated in the orbit.
 it was impossible to identify its age or gender.
 it looked like a mannequin’s face, but it was ridiculously large.
 it was too big to be realistic.
 he was looking down at the earth with a face that was only as large as the north american continent floating in the air.
 the pacific ocean was completely obscured by the shadow of the face.
kuuuuuuuuuuuuuuuuhhhhh-its glaring eyes were full of greed.
 it started to open its mouth.
 because it was so huge, it looked as if a super-sized hangar was opening.
-the ‘world’ loses its initiative.
-the ‘world eater’ is coming down.
with that message, the earth’s rotation stopped.
 and behind the giant face, the moon that lost its balance was seen bouncing out of orbit.
ooooooooooh-changes also began to take place on earth.
earthquakes broke out, clouds scattered, and the continents split.
 red lines sprouted from all over.
 it was lava.
 very small dots arose from the soil.
 at first, they looked just like dust, but when they gathered together, they began to be sucked into a huge mouth.
 soon the screen was adjusted to show the expanded dust.
they were humans.

all life on earth was being sucked into the mouth of the huge face like a whale swallowing krills.
there was no way to resist it.
 when left neglected like that, the earth gradually lost its light.
 and soon, it was split in all directions and met its final moment.
as a result, the earth and everything related to it disappeared into the dust of the universe.
it was an eternal end.
-this is the future of the earth that will happen if all the ‘world spirits’ that exist all over the world are destroyed.
the video ended there.
it was the most terrible ending that sungwoo had seen so far.
sungwoo slowly raised his head and looked at the king of the great mountain.
“how can we stop it?”the king of the great mountain sighed and looked up at the sky.
“let’s think upside down.
 if i were the world eater, what would be the best way for me to destroy the world spirit?”the king pointed to sungwoo with the pipe, then continued, “isn’t the best way just spreading an infectious disease, namely death? however, because you have grasped the reins of death in your hand, he could not achieve his goal contrary to his expectations.
 good job.
”when the king said that, sungwoo couldn’t help thinking of the evolution society.
 they studied death for a long time, arguing that it was the path of evolution.
‘and the world eater said that it should be one body, regarding it as transcendence….
’the evolution society completely turned into the world eater’s hand.
“and the second best way? i told you that the world spirits were hidden all over the earth, right? then, what is the most powerful being that has taken root in this land and influences the world itself?”when he asked that question, sungwoo remembered the prophecy stone that junghoon had shown him.
 according to the prophecy stone, the world tree that grew in yeouido ended up sucking up the souls of the entire korean server.
“the world tree?”“that’s right.
 even that is growing well under your protection, right? now, do you know roughly why the world eater is trying to catch and kill you?”the king of the great mountain stood up, shaking off the cigarette ash from the pipe.
“as for the world spirits, there are a total of three on the korean server, and you have one of them.
”“what about the other two?”“i don’t know.
 however, the world tree that you are growing now may play the role of the world spirit someday.
”sungwoo wondered if this was good news.
 it was good for him to keep it to the end, but the problem was monsters like the world eater would continue to attack him endlessly to get rid of it.
“so you have to keep it well.
 if the world tree grows well, it will serve as the strong defender of the world, but if it grows wrong, it will be like putting a stake in the heart of the world…”sungwoo knew what it meant.
 the trait of the world tree depends on the character of its owner.
 therefore, if a wicked man kept it, he would bring about a huge disaster beyond imagination.
at that moment, minsok interrupted the conversation between sungwoo and the king.
“i’m sorry for interrupting you, but…”as if he had something urgent, he was holding the “ownerless sword” in both hands.
“i’ve come to cut in because what i’m going to tell you is also very important.
”sungwoo looked at him as if he was expecting something.
 he nodded, so minsok could talk.


“it’s all over.
 i have filled in all the remaining numbers.
”-your ‘credentials certification’ has been completed.
finally, the time has come.
sungwoo accepted the “ownerless sword” minsok handed to him.
then, came out the item information, which had changed considerably.
[item information]-name: ruler’s sword-grade: myth-category: two-handed sword-effect: ignores strength (+10) and some of the defense effects of the attack target.
 (20%),-description: this sword is a key to awakening the black dragon and a symbol of a collar that can handle the dragon.
you are the owner of this sword, and your actions will give it a ‘new name’.
finally, the sword has a new owner, namely sungwoo.
more precisely, sungwoo had been recognized as the sword’s owner in exactly 5,000 days.
“then, is the egg about to hatch soon?” minsok asked.
nodding at him, sungwoo pulled out an “unknown egg” from the bag.


 