\section{chapter 366}

chapter 366: devil’s world tree and world eater (8)this chapter is updated by wuxiahere.
com




‘i must confuse him by repeating the anomalous attack.
 then, he will definitely let down his guard,’ sungwoo thought.
he resorted to using all of his skills and weapons including leviathan, ruler’s sword, ascalon, fighter’s shackles, repeating crossbow, hand cannon, and even the winter predator.
 these highly efficient items began to swirl in the air in the hands of the ghosts.
clang! clang! clang!when his weapons collided with the world eater’s weapon, they bounced off because of his overwhelming force and even flew backward to hit sungwoo’s allies, resulting in great damage.
 so much so that even minsok collapsed at his single strike.
however, if the ghosts were formless, there was no possibility that they would inflict damage to the allies even if they were struck back by the world eater.
clang! clang! clang!the world eater had to devote a considerable amount of time to strike back the magical weapons flying toward him in an irregular pattern.
 moreover, they were not common items, but legendary and mythical grade items with huge impacts.
leviathan spewed magma, winter predator fired ice bullets, and repeating crossbow fired arrows incessantly.
and above all, the fighter’s shackles were working.
– the weapon is sealed by the ‘fighter’s shackles’.
 (5 minutes)“it’s all over!”“what the heck is this?”purple chains spewed out from the fighter’s shackles, wrapped all of sungwoo’s weapons and even the world eater’s sword, then threw them down to the ground.
now, sungwoo and the world eater could not use their weapons for 5 minutes.
“you can’t beat me even if your level is high and your items are good.
”sungwoo made sure the fighter’s shackles took effect as much as possible without letting the world eater notice it.
 even if the world eater was a top-level player who had seen the ending of the game, he was supposed to be finished the moment he let down his guard.

“kheeeeeee…”for the first time, the world eater groaned in pain.
 obviously, he felt threatened, not just embarrassed.
“alright.
 let me have it out with you!” shouted the world eater.
then, he stretched out his left hand behind his back.
 a beam of light shot from his palm at that moment.
bang!a huge explosion occurred, making a huge hole in the wall.
 light poured in.
kugugugu-the roots of the world tree were pierced through to make an opening.
“i didn’t mobilize the devils to prevent contamination of the ark, but i have nothing to lose now,” the world eater shouted.
as soon as he finished saying that, a terrible scream began to be heard from outside the hole.
kheehe! kheeeehe!they were devils.
 those devils that had been lurking outside the world tree began to flock towards them after hearing the noise and smelling their scent.
“only now you are revealing your true nature, peeper monster!”as a last resort, the world eater brought in the devils outside the world tree.
 as if there was a hole in the bank, a huge number of monsters poured into the world tree.
 but that was just his desperate effort to survive.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.

– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.
then, sungwoo’s undead army started moving systematically, closing the hole, and catching and killing the monsters coming out over their heads one after another.
– all skill effects increase by absorbing ‘death’.
 (1 %)– all skill effects increase by absorbing ‘death’.
 (1 %)– all skill effects increase by absorbing ‘death’.
 (1 %)– all skill effects increase by absorbing ‘death’.
 (1 %)the death of the monsters turned into sungwoo’s power according to the ‘power of the 4 knights of the apocalypse’.
as always, the world eater’s thinking that he could beat the necromancer with an overwhelming number of troops turned out to be a mistake.
“oh my god! how could you bring out such a powerful synergy…”the world eater’s face was greatly distorted.
 it was clear that he was full of fear.
“it looks like you have lost a sense of fighting after sleeping too long.
”sungwoo stood in front of the ruler’s sword that world eater missed.
 five minutes later, the seal of the sword would be unlocked.
sungwoo turned his head and looked at the place he passed by, namely the cave where huge bones were asleep.
“i’ll put you to bed in five minutes.
”at that moment, a huge number of devils poured in through the hole.
but it didn’t change the situation much.
 it would be a different story if they poured out from all directions, but killing them coming out through the hole the size of a small tunnel was as easy as providing food to the wild beasts in a cage.
the corpses of the devils piled up one after another in front of the undead army.
– all skill effects increase by absorbing ‘death’.
 (1%)– all skill effects increase by absorbing ‘death’.
 (1%)– all skill effects increase by absorbing ‘death’.
 (1%)sungwoo’s undead army, which had eaten such high-quality food, was already strengthened by 143%.
 as the battle went on, they were growing exponentially stronger.
– 3 ‘masterless zombies (advanced)’ have been summoned from the abyss.
zombies were being summoned every minute due to the effect of ‘descent of death’.
there were already 24 zombies who were summoned like that, ranging from low to high grade.
 they were supposed to keep growing.
watching them in the rear, sungwoo recited a magic spell whenever the corpses of the devils were piled up high.
“explode!”bang! bang! bang!his exploding corpses were always right.
 the corpses of the monsters piled up near the hole exploded at once, pushing out the devils who were pushing in.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.
– you have obtained 500,000 gold by hunting ‘alien creatures (lesser monsters)’.


the world eaters didn’t sit idle while watching the devils being killed helplessly.
 he stood near the hole and used ranged magic to help the devils pour out from the hole.
dozens of the undead army members were smashed every time the light flashed from his hand, slowing down their blocking of the devils.
‘well, you can’t block them like that.
’sungwoo’s undead army was never pushed out.
‘no matter how high his level is, his magic is not that strong.
’the world eater was a knight-type wizard.
 so he was like a toothless tiger now because he could not exert any monstrous power without the help of his partner dragon here.
what’s more, he showed signs of exhaustion.
 it was also clear that there was a fatal flaw in his body.
“okay, let me kill him right away.
”sungwoo was going to launch an all-out attack when the devils’ attack stopped all of a sudden.
‘what the heck?’sungwoo felt strange and stopped the operation.
‘something else is coming in!’sungwoo could feel some strange energy emanating from the hole.
 it was not comparable to the ‘dragon fear’ used by the world eater, but that unknown creature was approaching with intimidating and heavy steps.
thump- thump-soon, a giant stood tall in the middle of the hole.
 with his back to the light, his huge shadow was cast in the hole.
– the boss monster ‘commander of the 2nd corps of demon’s cave’ has appeared.
‘commander?’

 