\section{chapter 324}






 general xing was also a spirit controller by profession.
 but he preferred to use his “control” to have spirits serve as his slaves rather than borrowing the power of spirits by cultivating “affinity” with them.
 the general used the method of hunting and detaining spirits for this purpose, but he needed a special solvent and courage for this, so he created dozens of “dedicated teams” made up of spirits and alchemists.
‘i feel good.
 they are the guys who used to be under leeway’s control.
’the “high-grade water spirit” was a strong weapon as well as a difficult material that could not be obtained again.
 so, the general saved it to deal with the necromancer, but he boldly used some of it.
kheeeeeeeeeeeeh!the water spirits began to swell like a bubble while it was being dragged by the chain.
“uh? run away, everybody!”“get away from the wall!”the chinese army hurriedly retreated, remembering the indiscriminate bombing carried out by admiral baker.
 soon, the high-grade water spirits turned into huge waves, soaring like dragons before thundering toward the wall.
 then, they swept away everything like a roaring river.
bang!cracks broke out in the wall, and those standing in front of the hole were swept away by the “spirit waves”.
it wasn’t just a stream of water.
 long arms protruded between the streams, grabbing, scraping, and pulling those that stood in the way before drawing them.
 all this happened in an instant.
as a result, those blocking the third hole were swept away once again.
 it was more effective than admiral baker’s bombing.
general xing said to his deputy, with his hands behind his back, “now, i’ve opened the gate to the wall.
 just go and take over the castle!”however, his expression was distorted as if he felt ominous.
“oh my…general, look over there!”“uh?”there were some who were standing tall in the place devastated by the overwhelming waves.
 “i can’t believe it! they withstood it and survived?”as expected, it was minsok and hanho who survived the devastating attack.

minsok held out by hooking a chain on the wall, while hanho endured, holding on to the six daggers he struck into the ground.
 in other words, they withstood the natural disaster with their bodies.
“cough! cough! man, this is nothing, compared with the ocean world’s wave pool! cough!”with his hands trembling violently, hanho was shouting in anger like a stray cat revealing her teeth to protect her territory after she was hit by a splash of water.
but the presence of the two was enough to slow down the enemies who were about to charge at the castle.
 it was natural that they were scared of the two players’ strong resilience before such a devastating attack.
“who the hell is that guy?”“why didn’t he fall?”and finally, the man that hanho had been waiting for arrived.
-the ‘winner (korea server)’ of the busan battlefield has joined the battlefield in suwon.
* ‘battlefield victory buffs’ are issued to the korean server.
 (temporarily increase all stats +10)1the time has come.
the same message appeared before everyone’s eyes on the battlefield.
hanho grinned, spitting out water mixed with blood from his mouth.
“wow, we’ve survived!” he shouted with joy.
on the other hand, there was a deep confusion on the chinese side.
the chinese troops got louder and busier to prepare for the necromancer’s attack.
“by the way, where is that guy?”the general looked around, but he couldn’t see his undead army anywhere.
general singh shouted, “no matter where he appeared with his forces, our forces are overwhelming! watch out for the explosion! stop him from advancing and break through the castle gate!”
general xing thought that although the necromancer blew away busan entirely with an unknown skill, such a trick would not work in suwon.
1‘no way! he would never turn the tide of the battle with such a cheap trick.
’general xing thought he could win the battle in suwon easily.
‘and it’s not difficult to stop his undead army.
 let me have the water spirits and the rear army delay his advance, then break through the castle gate and pull out the world tree!’the necromancer’s troops were certainly strong, but they were not enough to overwhelm the huge chinese army.
 as a result, the battle would inevitably drag on, and given the limits to the necromancer’s power, the chinese army would inevitably win, the general thought.
‘soon, my troops will join us from seoul, so we will prevail anyway.
’like he said, if the chinese forces joined them in suwon, the battle would be over in favor of general xing.
at that moment, a blue light spread over his head with a roaring sound.
 everyone raised their heads.
over the sky of the battlefield, something began to come out from the grey clouds.
“watch out!”“he is coming down from the sky! prepare for anti-aircraft fire!”the chinese army quickly moved in unison.
 since they already predicted his attack from the air, they were well prepared for that.
soon, a portal opened in the sky.
 everyone looked at it in silence.
then, someone shouted, “uh? what the hell is that?”what popped out of it was something that no one predicted.
 the chinese soldiers were swallowed up by the enormous shadow of that ridiculous object.
“no way…”“is it a building?”what protruded from the portal was the skyscraper of an overturned building.
kugugugugugu–a huge arm made of bones appeared, holding the whole building broken in half.
the building used to stand in haeundae, busan.
“nonsense! how come a building popped out from the sky?”perhaps because the building was swept by a big explosion, flames were soaring all over the building.
 with hundreds of undead spirits attached to the wall, they were hugging many more corpses.
kugugugugugu―that enormous object fell toward the middle of the enemy camp, exhaling long streams of gray smoke.
“…”it was something like an asteroid colliding with another one.
1hanho giggled at the scenes because he now knew why sungwoo could not join him late.
“well, i didn’t expect he would arrive with a meteor.
 this is a bit too strong…”the necromancer didn’t want a long fight.
 that’s why he appeared with a fatal weapon to destroy the enemy with one attack.
***jisu was gasping for breath, leaning against the wall.
the moment the tanks fired cannons, she fell on the floor and hid between the corpses.
she could save her life, but she could not avoid being severely wounded.
“haaaa…”her palms on the floor were soaked in blood.
 lots of blood flowed from the wounds all over her body.
 an ordinary man would have already died from shock.


“the necromancer has arrived in suwon.
 please rest assured.
”the king of the great mountain approached her.
 he had stopped maintaining the enormous number of roots because his roots attack paid off.
“well, we have made it!” she smiled at him.
their operation was a success.
 by tying up to 6,000 chinese troops in seoul, they helped protect the korean server.
however, their fight was not over yet.
there was an explosion in the hallway.
 soon, two tigers covered in blood were thrown into the room.
 they were hit by the large cannons.
“kheeeeeek!”after jisoo collapsed, the two tigers were trying to stop them by all means, but they could not resist any longer.
“argh! brother, my younger tiger was…”one tiger raised another one’s head, but that’s it.
 he didn’t move at all.
“he is dead.
”as a matter of fact, the tiger was covered with more wounds than jisu.
 his fur was already soaked with blood, with iron fragments all over his body.
“and i don’t think i’m going to survive.
 sorry…”even the surviving tiger’s eyes began to be blurry.
 he struggled to survive, but couldn’t.
“thanks for your good job!”when the king approved, the tiger lowered his head.
“poor guys! they lived on potatoes all their lives…but you guys will have a different fate.
”the king lifted the blue dragon ax that he stuck on the floor.


 