\section{chapter 204}

                             




a blue pattern was shining on the forehead of the serpent, stopping all the projectiles from flying toward its head in the air.
“is this the only thing you can do?” the serpent scoffed at sungwoo.
then, all the projectiles flew back toward sungwoo and his forces.
bang! bang!sungwoo discovered a shadow created by the goblin flame in a moment and teleported into that shadow.
however, sungwoo’s undead troops were shattered by the returning storms.
of course, they could resurrect, but they would be useless if their attack was futile.
at that moment, two bone wyverns descended from the ceiling and lifted their claws.
sungwoo wanted to have the bone wyverns appear from the place where the serpent didn’t expect at all, then attack its vital point.
but even that attack was useless.
dozens of patterns bloomed above the serpent’s head, rotated at high speed, then soared vertically.
 then, they began to grind two bone wyverns like a mixer.
‘i can’t beat the serpent like this.
’the serpent’s attack was overwhelming.
 he recalled drake he had faced before awakening during his raid in youido.
 sungwoo felt a power gap that he could hardly narrow back then, and he was killed miserably by drake.
‘it’s dangerous.
 i may have to use the resurrection spell.
’sungwoo could not help but fear his death because he felt a bigger difference in power than he did back then.
however, he had one insurance policy.
 it was a “resurrection spell” he had obtained from the secret store at kimpo international airport.
‘but hanho and jisu…”jisu and hanho also concentrated on avoiding the flying goblin flames, not knowing what to do.
 if sungwoo was killed here, the two would die forever.
so sungwoo couldn’t give up fighting easily.
but no matter how hard he thought about it, this situation was embarrassing to sungwoo.
didn’t he clear all the quests with an overwhelming power until now?then, how come this quest boss, given to everybody fairly, was so strong when the serpent was not even the field boss monster?”
‘is there any other strategy this serpent is using now?’at that moment, a scene suddenly flashed through his mind.
‘mural?’the hieroglyphs he saw at the entrance to the cave came to his mind suddenly.
the giant snake drawn in a circle.
 it was this place where the snake was located.
if so, what’s the next picture? and were there any hints to look for in it?sungwoo brought out the memory as best as he could.
‘there was a triangle on the back of the snake.
’as soon as he got to that point, he finally realized it.
‘i should not aim for the snake from the beginning.
 there is an answer elsewhere.
’-souls under control by the “soul container” (80)thanks to one of the new skills of the world tree, , sungwoo could save the souls of those who died.
 and he took them out in preparation for this dungeon attack.
-‘evil spirit bomb’ has been embedded in your weapon.
sungwoo immediately consumed five souls to use the evil spirit bomb.
 his target was not the giant serpent.
 he intended to stare at the wall that the serpent had been blocking.
at that moment, an unintelligible message appeared.
-code“ what the heck is this?”“uh?”“sungwoo, tell me what the heck this is.
”suddenly, some strange messages that he could not understand at all began to come out.
-email protected 
-the connection to the client server has been terminated due to a fatal error.
 (error code:0014231532)something absurd began to happen.
“oh no! has this game been forcibly terminated?”as soon as sungwoo asked the question, all the undead stopped moving in their place.
‘move, move!’but even sungwoo’s order didn’t get through to them as if it was not connected to the server from the beginning.
 sungwoo even forgot how to move them.
and that was the same with the giant serpent.
chiji-chijiji!the serpent wriggled as if it was electrocuted.
 then, it lowered its head and didn’t move anymore.
“…”since all this happened suddenly, sungwoo and his party were aghast.
but they could not feel relaxed because they didn’t know what was going to happen all of a sudden.
at that moment, there was a voice heard somewhere.
“have you ever thought somebody has been watching you?”it was none other than the giant serpent.
 it slowly raised its head again.
with its two dark eyes staring at sungwoo, it said, “but not now.
 sungwoo yu, come to me.
”“…”what the hell is going on?after pondering over it for a moment, sungwoo slowly took a step.
then, he walked forward, saying, “you seem to have something to say to me.
 i don’t know what the hell is going on, but….
”he was certain of one thing.
 right now, the system, the culprit behind all of this, exposed a loophole.
 and he could find out the whole truth through the loophole, namely the identity of this game.
“sungwoo, i think that monster called your name.
”following the system error, a phenomenon that sungwoo could hardly understand happened.
 like hanho just said, a monster named “1st python”, obviously part of the system, called sungwoo’s name.
‘how does it know my name?’no matter how great the boss monster is, it was too strange that the monster recognized the real name of a player.
that’s why sungwoo could instinctively realize something was wrong.
‘there is a problem with the system.
’he didn’t know what the system was yet, but at this moment, it was not something that the system intended at all.
as if to prove it, the giant serpent said something unintelligible.
“there is no time.
 only this area is hidden from the creator, but they will soon notice it.
”sungwoo frowned unwittingly when he heard that very foreign and eerie word.
“creator?”“of course, he is not your creator.
 he is the being that has created my power, this place, and your power.
”it was right that the being was the serpent’s creator.
 but my creator?to put it simply, it was the being that pushed this hellish system into the world where sungwoo was living.
 in other words, the being was the “invader” playing with this world.
“then, who are they?”“i don’t know yet.
 i wasn’t allowed to know their existence.
”sungwoo tilted his head and asked, “very strange.
 i think you already know them to some extent.
”if the serpent was just a dungeon boss monster and a subordinate to the system, wasn’t it natural that it didn’t even know the existence of the creator?“just a moment ago, a certain ‘unknown force’ came inside me.
 at that moment, i could realize something very small.
 but that’s not what matters now.
 take my words seriously from now on.
”the serpent moved its head and approached sungwoo.
its giant head was intimidating just by moving.
“sungwoo!”jisu was about to attack the serpent, but sungwoo stopped her by stretching her palms.
 the giant serpent moved its huge mouth right in front of him and whispered.


“sungwoo yu, there is someone who wants to contact you.
 they are also like my creator.
 they can’t reveal themselves in person, so they want to use my mind to convey a message to you.
”“the same being…”the fact that they were trying to secretly contact sungwoo even though they were on the same type of being as the creator might mean that the creators of this system were divided into two groups and competing with each other.
“what do they want from me?”“the collapse of the system.
”in other words, it meant they wanted to end this game.
“but why me? why do they want to see me?”but why did they come to seek sungwoo? even though sungwoo had been performing well until now, he has been doing so within the system.
“they have watched everyone and chosen you because you have continuously deviated from the direction set by the system.
 sungwoo, survive and overturn the system.
 they will find an opportunity to contact you and call your name again.
”-the system is under emergency recovery.
 (13%)the serpent also slowly raised its head as if it saw the message.
and there was nothing like determination in its eyes.
 so much so that sungwoo could feel something like a sense of loss in its eyes, something completely different from what it was when it first appeared in the dark.
the giant serpent continued, “i’ve just realized that my existence is meaningless.
”then, it turned around and started scratching the wall behind it all of a sudden.
the surface of the wall was a little scratched, and stone debris fell off.
it was the spot where the triangular pattern sungwoo was trying to aim for was.
‘as expected, is it the serpent’s soft spot?’it seemed that they gave sungwoo a hint about how to win this game, thinking sungwoo didn’t yet notice it.
 did those who said they had chosen sungwoo underestimate him?-the system is under emergency recovery.
 (56%)“they will come back.
 one of my scales is growing upside down.
 kill me and get it secretly.
”“scales?”“it is a gift from someone who wants to help you.
 the power hidden in it will tell you if somebody is monitoring you or not.
”

 