\section{chapter 429}

"stop attacking! the angels are not coming out! stand on alert, everybody!"




someone shouted from the ranks of the allies.
 since there was a sea of fire inside the hole, along with the explosions right at the entrance of the hole, it was no wonder the angels could not come out.
after that, what came out of the hole and fell to the ground was not angels, but the fragments of the angel bodies.
 the broken hole in the sky began to throw out huge shards of marble stones.
"it's all over! all we have to do is clean them up! wipe them away!"when sungwoo issued an order like that, the hippogriff squadron sitting on the airships flew all at once.
 the special commando squadron began to approach the hole, forming a formation as they were trained.
"sweep them away so that no one can escape! charge!"even though a few angels escaped from the portal, they were immediately killed by the special commando squadron members.
like a flock of birds preying on a swarm of dragonflies, they charged at the angels and crushed their heads in an instant.
attacking the angels after unleashing massive firepower was their standard way of war tactics, dealing a decisive blow to the pride of the absolute races.
advertisements    ***all the servers around the world were being invaded.
 the korean server deterred the invasion, but other servers did not.
 "retreat! retreat to the air-raid shelter!"this was taipei on the taiwanese server.
"a massive barrier has been broken down!"even though the tawainese server was once occupied by pirates, they regained relative stability after liberation, then developed rapidly to emerge as a strong server befitting the new era.
 but they were being thoroughly trampled upon once again.
bang!
a whole building collapsed in the explosion.
 at the same time, hundreds of angels squirmed out of the concrete, like swarms of wasps whose hives were broken.
"damn it! they are coming!"the taiwanese players fired shots to check them while running away.
"chen! we can't stop them!"chen shook his head at his colleague's shouting.
"no! we can still hold out! we should!"when the taiwanese players made their way home to defend taipei, the necromancer said that he would come as quickly as possible as long as they could hold out.
chen trusted the necromancer.
 just as he drove away the pirates by appearing suddenly, chen believed he would appear again this time.
 while facing death, he was waiting for such a dramatic moment.
"they're coming from above!""no, stop them!"angels came down from all directions.
 they popped out of alleys, jumped over buildings, and knocked down buildings, then grabbed the players and soared into the air.
"hey, save me! argh! aaaaaaaaah!"then the angels dragged them into the air and ripped them apart.
 the sticky blood and flesh of human beings got stuck all over their white bodies.
 as the number of survivors decreased, the bodies of the angels became more and more reddish, covered with human blood.
 "chen! we need to get out of this city right now!"when his colleague insisted on retreating repeatedly, chen shook his head again.
he still believed the necromancer would come here, though he was worried that his savior would arrive a bit late.

"chen! please.
.
.
 argh!"at that moment an angel held out her white hands suddenly, grabbed his colleague's neck, and flew away.
"oh, no!"chen hurriedly raised his crossbow, but the angel was too fast for him to aim properly.
at that moment a flash of light emitted from somewhere, and the angel holding his companion was cut in half.
 the colleague fell to the ground and landed on the ground safely.
"what happened a moment ago?""no idea…"immediately after that, the entire sky suddenly turned red with a huge explosion.
bang! bang! bang!chen instinctively lowered his body.
 it was an explosion that seemed to rip the sky, burn everybody's ears, and tear their eardrums.
"lower your heads!"an unfamiliar voice shouted.
shhhhhhhhhhhhh! steel rain fell from the sky.
 the angels who snatched the players while flying low collapsed to the ground.
 their bodies turned to marbles and scattered across the ground.
chen was puzzled by what was happening before his eyes.
 'what the heck is that?'he had never seen a weapon that wiped out these countless angels flying so fast.
 actually, it was something that no extensive large-scale magic could do.
at that moment, he recalled the necromancer's voice.
'oh, yes, that's the new weapon he mentioned.
'sungwoo once told chen that he developed a new weapon, but since he didn't have many of them in stock, he had to use it on only one battlefield.
 at that time, chen told him that he would hold out by all means because he totally trusted his judgment.
his judgment was right.
 the best option for him was to finish the battle on one battlefield as quickly as possible, then move to the next battlefield.
"have i come too late?"someone sat down in front of chen.
 it was valkyrie, a female warrior in dark red armor.
chen looked up at her and nodded.
"then get up! there are still many places where people are waiting for us to come.
"chen got up and asked, "ah, are you now going to mainland china to support the chinese server?"but jisoo shook her head and looked up at the sky.
 chen also followed her gaze.
whooooo-hundreds of hippogriffs were moving in groups, hunting down angels soaked in steel rain.
"no.
 we have already defeated them because the necromancer went there.
 they are now joining hands to go further.
"sungwoo's counterattack started from a small server in the east, and now he was moving toward the west at full speed.
***

the demon race invaded the vietnam server.
"commander, our last line of defense has collapsed.
 the survivors there are retreating toward our area.
"the master of the vietnamese server, nguyen, actually received the last report from his deputy in the underground air-raid shelter.
"there is no more place for us to retreat because the demon worshipers have blocked the way out.
"currently, the vietnamese server was a total mess.
 it was not just because of the demon army.
 "according to the latest information, the leader of the retreating army met the commander of the demon army.
 it seems our allied commander wants to swear an oath of allegiance to him.
"the demon army commander was a boss monster.
 when the invasion was successful, he came down to the ground.
nguyen threw down the mana potion he was holding.
clink!"traitors, let me go after you by all means!"originally, the entire vietnam server was under the influence of the 'demon camp'.
 however, after all the representatives gathered and had a meeting, they agreed to leave the demon camp and join the world tree camp.
"son of a bitch! they agreed to join the world tree camp with us, but how could they betray us and join hands with the demon camp?"just before this invasion began, the frightened guys turned their coats and chose to obey the demon camp.
advertisements    nguyen and other key players on the vietnamese server didn't know it, they felt as if they were stabbed in the back.
thud! thud!the ceiling shook as if it was about to collapse.
 the demon camp soldiers seemed to know where the vietnamese players were hiding.
bang! bang!they were like a rat in a trap at the moment.


 