\section{chapter 475}

at the last moment, the necromancer went into the demon king's body.





bang! shortly afterward, a huge explosion occurred inside his body.
 at the same time, his back began to swell, and blood gushed out of it.
 but that's just the beginning of the necromancer's attack.
 soon a ray of light arose and reached the sky, and the red clouds were split in half and pushed outside.
 although the explosion occurred inside the demon king's body, its impact shook the whole world.
"what the heck is happening now?"the shock wave that split the red clouds descended, and the demon king's castle collapsed.
 the air was twisted and the ground trembled violently.
 "everyone, bow down!"a big storm and an earthquake shook the amazon rainforest.
"ugh!"even all the mana in the area burned, so the wizards also suffered considerable damage because of the 'mana burn' phenomenon.
but nobody was sure what the hell happened.
"what the heck is this…"instead of showing the inside, the drone camera of the official channel only displayed the body of the giant demon king nearby.
"what's going on?"as the explosion that shook the world stopped, silence fell very slowly and calmly.
".
.
.
"suddenly everything stopped.
the struggles of the demon king and the attacks by hell creatures stopped, so the players had no choice but to stop, too.
 they didn't know what to do.
 they just stood there, looking at the hole in his chest blankly.
the battlefield also showed a momentary lull.
 "ah…"reporter ahn sighed.
 he didn't know what to say.
it was too serious a moment for him to ramble on thoughtlessly.

".
.
.
"so he had no choice but to hold his breath and wait for what would happen next.
".
.
.
"updated at lightnov­elworld.
c­omit's been some time since he started to watch that terrible scene, not knowing what the hell was going on in there.
"oh, look at that!"the demon king's body began to shrink.
 like crumpled paper, his bones folded, his flesh dented, then his body began to condense into a size that could not get smaller physically anymore.
"the demon king is going to die!"reporter ahn noticed that the demon king was dead.
 that was positive news.
then, what about the necromancer?reporter ahn said, "the necromancer is inside right there.
 can he escape?"even though he asked the question, he was convinced that he would be able to get out of that hell by all means.
"given the circumstances, i think i can conclude with the hope that the necromancer has defeated the demon king.
 all he has to do is just walk out of it.
"watching the scene, everyone was earnestly waiting for the necromancer to escape from the demon king's crushed body.
 "what the heck?"the necromancer did not come out until the demon king's huge body kept being crushed before being reduced to the tiniest dot and disappeared.
".
.
.
"everyone was astonished to see that.
".
.
.
"no matter how closely they looked around, there was nothing in the place where the demon king was standing.
 many people looked around just in case they could find his traces, but none of them witnessed him escaping.
 "oh my…"after a few minutes of silence, reporter ahn opened his mouth.

"is it possible that the necromancer could have been .
.
.
?"he was hesitant to say he was dead.
 he found it difficult to spit out that word.
 'how come did the necromancers disappear?'everybody has been restoring order finally since the game started, and that was possible entirely because of the necromancer's determination and power.
 'but when he disappears, what will happen in the future?'they just felt embarrassed when they thought of the new world without the necromancer.
'we can't sit idle foolishly.
"reporter ahn soon came to his senses, and did what he could do, and said what he had to say.
visit to lightnov‌elworld.
com discover new novels.
"all players who are watching this broadcast, let me tell you this.
 if the necromancer wins this battle, and at the same time he disappears.
.
.
"he swallowed, then continued, "ladies and gentlemen, we will have to prepare for the post-necromancer world from now on.
"his assistant looked at him with a blank expression.
 he couldn't even chime in like before.
reporter ahn continued, "we've been relying on the necromancer's power and vision for quite some time.
 i think all of you agree with me.
 and we have also left our future with him.
 that's why we have always hoped he would win and restore order.
"in other words, the absence of the necromancer meant that the central pillar of their support would disappear.
he added, "there will be a lot of chaos.
 without him, we're going to face great chaos.
"at that moment the official channel broadcast screen rotated and showed somewhere.
it was someone's face.
"huh? is it the necromancer?"the face of the necromancer, namely sungwoo's face, who was regarded as almost dead, was reflected on the widescreen.
he was walking forward, with the blue aura around him.
 "by the way, where is he right now?"***there was a single portal open at the end of the amazon battlefield.
 it was a portal leading to the world tree camp, namely suwon in the outskirts of seoul.
 since the demon king's army was advancing towards it, many players surrounded it and maintained a tight defense.
but something bizarre was happening.
"ugh?"someone walked out of there.
"gosh, are you necromancer?"it was sungwoo, indeed.
 "what? is he real?"security personnel guarding the portal stepped back with a surprised expression.
 how could he who went into the demon king's body come out of the portal connected to suwon? soon one of them turned, and shouted, "he's alive! the necromancer is alive!"rumors about his survival spread quickly everywhere.
"the necromancer has won!""he hasn't suffered any wounds!"content is taken from lightnovelworld.
com"what happened?"in their eyes, this was something they could not understand because the resurrection charm was the rarest item in the item game.
"sungwoo!"his closest aide, kyungsoo, rushed over to him.
"are you okay? what happened? you were inside his body, right?"kyungsoo was also shocked, thinking that sungwoo was killed with the demon king.
but sungwoo responded calmly, "i'll tell you later.
"sungwoo felt he didn't have to go into details about his resurrection charm.


instead, he said something more important.
"the demon king is dead.
"this war was finally over.
"what a relief! i'm so glad to hear that!" said kyungsoo.
"no, not yet.
""pardon?"but another problem arose, which was much bigger than anything else.
'it's the ending.
'sungwoo was looking into the air at that moment because he was reading a message.
[ending quest]- title: winner's right- type: choice- goal: choice of an ending- reward: differential reward based on the choice.
*congratulations! you have been selected as the 'interim winner'.
 this means that you can exercise the same right as the 'winner'.
 you can choose the last moment of the world.
 your choice determines the fate of the world and even yours.
*be careful.
 the interim winner means that he can take away the winner's right at any time.
ending quest? sungwoo wondered if he was required to choose the ending of this world.
the latest episodes are on the lightnovelworld.
com website.
and the choice that he had to make drove him nuts.
 he really could understand why he had to make such a choice, which made him upset.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 