\section{chapter 408}

reporter ahn's studio was in chaos.
 whenever the scenes changed on the official channel, the status of the war also changed.
 as a result, ahn and wong were getting exhausted gradually.





of course, the birth of a new deity status was a big surprise, so it brought new vitality into his broadcasting.
reporter ahn shouted, "oh my god! that guy is necromancer's colleague! he is that very thief who wielded six arms and used his body to block a guided bomb! priest? warrior? well, anyway, he is such a fighter! great! this is totally unexpected!"however, the appearance of hyunmu restored the balance of power that had suddenly collapsed after the enemy broke through the rampart.
then the fighting between both sides intensified again.
 it was fierce but protracted.
"um…"without any surprising turn of situation, the fighting was going on like before.
 at that moment the official channel showed another scene.
 "uh!""finally necromancer is back!"since the appearance of the necromancer changed the tide of the war drastically, they could not help but get excited.
 "where has he appeared this time?"he was inside a dark building.
 given that the battle cry was barely audible, it seemed that the building was outside the invisible barrier, namely, some distance away from the battlefield.
rattle- rattle-the necromancer was walking slowly down the long hallway.
 and a thunderous noise was heard while he was walking.
it was the sound of something breaking.
 soon, the camera angle slowly turned to capture the back of the building, and at that moment, a black blade pierced the two terracottas at the same time.
 their fragments collapsed, allowing for a clear view of the hallway.
"whew!"it was death knight minsok.
 durahan and goblin skeletons were following him.

under their feet were piles of crushed terracotta, which suggested that the enemy troops were infiltrating through the place that these terracotta secretly guarded.
"where are these guys going? they look like the most elite troops.
 and why are the emperor's terracottas defending this place?" ahn asked.
visit lightnovelworld.
com for a better experiencebut wong could not give him a plausible answer.
 he finally shook his head and replied, "well, i have no idea.
"in fact, he didn't know much about the emperor either.
 come to think of it, no one has ever seen the emperor in person.
perhaps, at this moment, the person who knew the most about the emperor might be none other than the necromancer.
the camera was capturing the scenes of the necromancer and his party walking.
 soon a large lobby appeared as if it was a fairly large building.
rattle- rattle-this time again, a number of terracottas blocked them.
 they totaled around 30.
"this time, they are unusual!" minsok said, looking at the terracottas warily.
at first glance, they were armed with very high-grade items.
in other words, these were not rank-and-file soldiers.
 'these are hero terracottas like li bu and guan yu who headed to the rampart.
'sungwoo already heard about the status of fighting at the rampart, so he knew these terracottas who looked like the two heroes stood at the forefront in the battle.
"man, that guy looks like hsiang yu!"minsok pointed to the largest terracotta standing some distance away.
 he was wearing thick armor and a red cloak, holding a large sword in his right hand and a long spear in his left.

squeaking!the sound of his large hands gripping the spear resounded fiercely.
 his overwhelming presence itself was really terrifying.
"do you mean that strongest guy hsiang yu who appears in the legend of chu and han?" sungwoo asked.
 sungwoo did not know the details of hisang yu because he had never read the legend of chu and han, even though he read the three kingdoms chronology.
 but minsok seemed to have some knowledge about the legend of chu and han.
 "that's right.
 if i have to pick the strongest among the heroes of chinese legend, he would be supreme ruler hsiang yu.
"this content is taken from lightnovelworld.
comhsiang yu was a hero who was called everybody's enemy or supreme ruler.
 he was generally regarded as much stronger than li bu.
'as expected, this guy is tough enough to defend the emperor.
'using the memory bead that traced zian's memory, sungwoo found out the location of this place, where the emperor was hiding.
 so without revealing it to anybody, he stormed this place, only accompanied by three subordinate spirits including minsok.
however, this place was under tight security, as expected.
"well, i expected this place would be protected by a strong army like this.
 then, hold them as much as you can! you can kill them, of course.
 let me go after the emperor!" said sungwoo.
"sure, will do!" minsok replied.
when sungwoo took one step forward, hsiang yu also stepped forward.
 "hey, i'm your target, not him!" minsok shouted at him.
having shouted at him, minsok raised the sword, but hsiang yu took turns wielding a sword and a spear.
kwaaaaaaaaaang!the floor and the ceiling were torn apart, falling over sungwoo's party.
 all of them bounced back at the impact.
"oops! don't worry! just go!" minsok said.
fortunately, sungwoo was not affected by the attack because he used the skill 'shadow movement.
'"alright, hope you can defeat them!"sungwoo then stood up behind the terracottas.
 then he fired the winter predator in his left hand everywhere, swinging the grim reaper in his right hand over his head.
he smashed the three terracottas nearby, then turned to face the terracottas in the back.
'that box!'one of the terracotta was carrying a small box.
 zeng! zeng!sungwoo shot the winter predator to freeze his feet, then cut off his hands at once.
 this content is taken from lightnovelworld.
comthe small box dropped on the floor.
 sungwoo jumped the floor, with the winter predator around his shoulders, holding out his left hand to grab the lid of the box.
 at that moment he disappeared.
as was already known, the emperor was not on the battlefield.
 he was controlling his army in a special safety zone.
 finally, the necromancer got there.
- you have entered the tomb of emperor quin shi.
* you are classified as an 'intruder', so you are not forcibly expelled.
 whoo-

the air inside the tomb was bad.
 'as expected, i'm running out of gas.
'a long corridor of darkness and smoke appeared.
 huge statues lined up on the left and right of the corridor, creating a strange sense of intimidation.
then the heads of the statues turned wildly and began to stare at sungwoo sharply.
"you have made a mistake!"a voice rang out from somewhere.
 sungwoo didn't know where it was coming from.
it was as if this space itself said something.
 "how could you jump into my territory? are you so stupid? so you might want to do some trick on me.
 but this is clearly your mistake!"sungwoo grabbed the grim reaper with his right hand and gently lifted the winter predator with his left hand.
- this space is the 'god's territory' governed by someone with a 'specific deity'.
 you can use no other deity status here.
as he already experienced it in the forge of hephaestus,' sungwoo could not turn to his deity status here.
 nor could he summon the skills that affected space.
"how could a man who controls death as a weapon risk your death? you have made a crucial mistake of causing your death!"but sungwoo sneered at that voice, then turned his head and looked behind him.
woo woo-the source of this content is lightnovelworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 