\section{chapter 326}






 as things stood now, thousands of chinese soldiers, who were lined up along the four-lane road, would be killed instantly, crushed under the building.
“get out of here right now!”“everyone, run away!”at that moment, a huge stream of water soared from the wall.
 it was the “high-grade water spirits” that had swept through the castle wall.
kugugugugu!they swirled and flew toward the collapsing building.
 then, with tremendous force, they supported it.
quaguaguguagua!numerous concrete debris and bone fragments were scattered in all directions.
“what the hell are you doing? we are still at war!” general xing shouted, stretching out his hand toward the building.
 “come on, move again! advance! take over the enemy’s castle! let me stop him!”however, general xing’s wishful thinking went nowhere.
 he was still mistaken.
 he could never stop the necromancer’s power.
rattle! rattle!hundreds of undead troops were hung on the building that stopped collapsing thanks to a stream of water.
 they started jumping down all at once.
 it looked like airborne rangers were descending from a huge transport plane.
“uh? what the heck is that?”furthermore, the giant ‘bone hands’ holding the building began to turn into thousands of ‘bone spears’ after being separated and scattering in the air.
 they rained down on the heads of the chinese army like rain.
 it was an attack that the necromancer launched by applying the skill .
“oh, my god…”“unfurl the shield right now!”the chinese soldiers could not keep up their morale in the face of all sorts of bizarre phenomena unfolding right before their eyes.
 so, they desperately ran about to survive without remembering the general’s order.
gugugugugugu-
and there was a creature running down the outer wall of the sagging building.
it was ‘durahan’.
 that headless knight charged fiercely at the chinese army, as if riding on a runaway, just like he did on a giant snake before.
“he’s coming our way!”the moment durahan landed on the road, the ghost knight guard popped out from both sides as if his wings spread.
 then they trampled on the embarrassed chinese soldiers and moved on.
 it was a terrible slaughter.
such a heinous scene was a shock to the korean server as well.
 while letting out a sigh of relief on the castle wall, they were amazed by what’s going on right before their eyes.
“man, what’s going on all of a sudden?”“wow, i can’t believe it!”but the real spectacle just began.
the center of the building collapsed, creating a huge hole.
 and something bizarre popped out from the hole.
 it was so bizarre that even those chinese soldiers running away stopped and looked at it.
“damn it, what the heck is that?”“we are finished!”it was bone imoogi.
 that giant snake monster was coiled up inside the building for a long time.
 and the moment when the tide of the battle turned in favor of the necromancer, the giant snake appeared.
 its sudden appearance dealt a devastating blow to the morale of the enemies who already lost the will to fight.
bone imoogi pushed its heavy body towards the chinese military stationed on the four-lane road.
 it was as if a ktx train was running over a sidewalk crowded with people.
“rattle! rattle! explosion!”sitting on top of bone imoogi’s head, victor triggered a corpse explosion in the middle of the chinese army.
bang! bang! bang!concrete fragments, bone spears, and an army of undead rained down on their heads, while durahan and bone imoogi were pushing them hard like a tsunami from behind.
and a huge wall was standing before them.
in other words, a massacre was underway and none of them had a means of escape.

they should move faster.
’riding on wyvern alpha male high in the sky, sungwoo was controlling the situation, but he didn’t feel at ease.
‘seoul is dangerous.
 i could save time because i pulled out a building and carried it here, but as things stand now, jisu could be killed.
’however, like he said, there were always variables in a war, and the tide of the battle in seoul was turning due to unexpected variables.
***reporter ahn looked at the screen with his mouth wide open.
 his assistant covered his mouth with his hand.
 they were shocked by a series of events that they could not believe.
the chinese troops in busan were annihilated by a huge explosion that wiped out the city entirely, an overturned skyscraper of a building crashed over the suwon battlefield, and bone imoogi popped out of it.
“ah….
”however, at this moment, the screen of the official channel was showing not the fierce battlefield in suwon, but one corner of seoul because something important was taking place there.
it was a road covered with blood on the battlefield in seoul that the drone camera was showing now.
“that woman…”the assistant barely opened his mouth, but he couldn’t say any more.
 then, reporter ahn stepped forward and wrapped it up with an important announcement.
“she finally stood up again…”it was a variable in the fight that would turn its tide.
meanwhile, bird of washington, the only surviving airship and admiral baker’s flagship, was also involved in the battle.
“somebody is infiltrating the ship!”“take them out right now!”although they barely avoided the building falling from the sky, several undead that got stuck to the building jumped over the airship.
“well, our deck soldiers are fighting them, but they seem to be on the defensive right now!”although the airship boasted of strong firepower enough to break through the invisible barriers and walls, there were only 47 people aboard the ship.
 among them were only thirty crew members who could actually fight, so it was impossible for them to respond properly.
“our forces are being pushed by the enemy right now!”“you are the guards of the flagship! don’t allow them into the ship!”they could barely hold out because some of them with fine capabilities were selected as crew members.
“they are coming over here!”however, they could not stop the undead from leaving the deck and heading to the flagship by stepping on the outer wall of the airship.
“uh? they are already here!”soon, dozens of ghouls appeared on the window of the flagship, then swung their weapon-like hands.
clang! clang! clang!when there were spiderweb-like cracks in the flagship’s glass window, everyone stood up in fear.
“oh, no!”“we can’t stop them from coming inside!”but admiral baker was still sitting in the chair, never unmoved by their fuss.
soon three rifles slowly floated behind his back.
“admiral?”“admiral! please give us an order!”admiral baker’s eyebrows wriggled when somebody demanded.
“keep fighting! if you can’t, step aside.
”his order was pretty irresponsible.


crack!eventually, the window was smashed.
 dozens of ghouls infiltrated the control room where the admiral was sitting.
the crew began to flee, screaming.
 but they couldn’t be faster than the ghouls.
they swept over the crew members, and the flagship with the control room not functioning properly began to tilt sharply.
admiral baker stood up to keep balance.
 at the same time, he aimed the three muzzles at the ghouls’ heads.
bang! bang!as the muzzles fired in succession, the skulls of the three ghouls shattered to pieces.
however, the fragmented skulls started to regenerate quickly.
admiral baker frowned and shouted, “disgusting…”then he reloaded the three rifles.
 of course, it was not real bullets that filled the powder chamber.
 a circular figure appeared around the cylinder part and rotated to supply mana.
“ahhhh! go away!”“help me, admiral!”with almost all of the crew members slaughtered, admiral baker alone was standing tall.
“tut, tut, just useless guys…”mumbling like that, the admiral snapped his fingers.
 then, an ammunition band he made with magic from behind came up.
 they were connected to the rifles that floated in the air.
soon, a support made of magic near the shoulder soared to fix the rifles.
“even though you occupied america, you can take over my flagship.
”soon the three muzzles began to fire at the ghouls.
bang! bang! bang!

 