\section{chapter 411}

the incarnation of hyunmu and the oppressor's hand got entangled before falling to the ground simultaneously.
 




the two gigantic figures crushed the terracottas gathered under the wall and rolled over them.
chuchuchuchuchu-in terms of resilience, the oppressor's hand prevailed over the incarnation of hyunmu.
 the five fingers of the oppressor's hand moved around and pressed down the incarnation of hyunmu.
 it was as if a human hand was clutching a softshell turtle.
 it spewed out a large number of golden threads and wrapped around the incarnation of hyunmu.
"uh? what's going on? this should not happen!"the tide of the fight changed now.
 huge shadows appeared one after another over the two entangled figures fighting against each other.
 woo woo woo-it was a combined fleet of over twenty airships.
"get ready to fire, entire fleet!"commander inho, who was watching the situation from the deck of the main airship, understood how the situation changed and how to respond.
"we have to stop that hand from going back.
"inho sent radios to the entire fleet.
"prepare the hooks of the world tree, not the shells!"the world tree hooks, an item that sungwoo once used in the devil's cave, were made by connecting bone hooks to the world tree's stems.
at that time, they were used as a tactical weapon to block the swarms of "intermediate monsters", but it has been modified to be used as a tow rope or anchor, equipped on an airship, since then.
"fire the hooks of the world tree at that hand!"
tung! tung! tung! tung! tung!a total of five world tree hooks were shot and wrapped around the oppressor's fingers.
this content is taken from lightnovelworld.
com"we have made it! we've bound the target!"the end of the long vine of the world tree was hooked to the pulley device inside the ship so that the hooked object could be pulled by mechanical force.
 the effect of the vine of the world tree itself was maximizing the pulling force of the hook.
"pull it hard, so you can't allow the hand to move at all!"the oppressor's hand, which showed an overwhelming majesty, began to be towed like a powerless giant beast.
when the necromancer defeated the oppressor's hand by a surprise attack, the emperor's forces that heavily gathered near the rampart to break into it were significantly reduced, and the tide of the war also changed.
***the tomb of emperor quin shi was a very large temple, but it was too narrow for these two men to fight.
 the necromancer and the emperor were staring at each other.
kwajeeeeeeeek!at that moment the head of the statue was cut in half.
 two dragon soldiers grabbed its huge head from both sides and split it in half.
 that was the last statue.
like a demolished site, all kinds of stone fragments and iron weapons were strewn around.
the ten dragon soldiers who finished demolishing the statues stood tall among the debris and roared wildly.
kaaaaaah!sungwoo walked towards the emperor.
 the emperor was still at ease and relaxed.
 he stroked my beard and nodded at sungwoo.
 
"yeah, necromancer.
 your tactics were great.
 so is that all your trick?"a huge golden hand arose behind the emperor's back.
 it was the oppressor's hand, its left hand.
 it placed its palm near the emperor's head, prepared to protect him in case of emergency.
"i know you hastily summoned that hand from the rampart," sungwoo shouted.
 in his mind, it was clear that that hand was the emperor's skill in the category of his deity status.
'i don't know exactly what his deity status is, but it's obviously his deity skill that controls everything by force.
'sungwoo witnessed the emperor not only controlling the terracotta dolls he made but also controlling the airships as well as the guardian's statue.
 this content is taken from lightnovelworld.
com'that means he can even control my subordinate spirits!'not surprisingly, the moment the oppressor's hand reached out toward sungwoo, golden threads spewed out of it all of a sudden.
 chuchuchuchuchu —the oppressor's hand was so fast that sungwoo couldn't even respond.
 the golden threads were shot at the dragon soldiers.
 obviously the emperor was trying to control them.
cheeeeeeeee!the moment the golden threads wrapped around the dragon soldiers, they began to be burned black.
 the emperor's left eyebrow twitched twice.
 it seemed he didn't expect this kind of situation at all.
sungwoo said, sneering at him, "well, it looks like your threads don't work.
 don't you want to use another skill?"but the golden threads could even control a huge airship like a toy, so there was no way they could be burned by ordinary flames.
 however, the flames that formed the dragon's bodies were the power of the 'red dragon', which was stronger than any other flame magic.
'after all, there are loopholes and weaknesses in any power.
'if the red dragon item had had no set effect, the necromancer's army could have been virtually neutralized by the emperor's bodyguard team.
 in other words, the necromancer's hidden card paid off greatly.
tramp- tramp-but the emperor did not blink an eye.
 still sitting on the throne, he was looking down at sungwoo solemnly.
 'obviously, he must have another card.
'like a gambler who had a knack at spinning cards, the emperor was hiding his expression.
it was exactly what they described as a poker face.
'if i make a mistake, the tide of this war will be in his favor.
'sungwoo tried to remain prudent.
 the battle taking place here was the "final big fight".
in other words, the winner of this battle would take everything.
'something is coming.
'visit lightnov‌elworld.
com for the best novel reading experiencesoon the emperor began to use his second hidden card.
kugugugugu-a stone wall soared and opened behind the emperor's back.
 there was a wide hallway that continued endlessly.
 a large number of terracotta troops were gathered there.
 the forces attacking the rampart were summoned here.
but sungwoo didn't think they were a major threat.
 he also revealed his second hidden card.
it was a spear made of bones, namely the red dragon spear.
 sungwoo grabbed the spear upside down, then pulled it behind his shoulder.
 then he threw it hard towards the emperor with all his might.


tung-at that moment the oppressor's hand fired golden threads to block it, which was an easy target.
but the moment the spear got stuck in the ground, something the emperor never expected was happening.
 - caution! a 'breath field' has been formed in the affected area.
this was sungwoo's hidden skill.
 armed with the set effect of the red dragon item, it was a 'sustained range' skill that changed the area 100 meters within the spear into a 'lava field'.
whoops-the air over the space with a radius of 100 meters with the spear stuck in the ground began to boil in an instant.
 cobweb-like cracks appeared on the ground and walls, coloring everything there dark red.
 and magma flowed out of gaps everywhere.
 cheeeeeeeee-with stone material boiling, toxic gas kept coming out.
 bang! bang! flames and magma erupted even from the area where the terracotta army was positioned.
 - you have obtained 3,000 gold by removing the player's 'intermediate terracotta'.
- you have obtained 3,000 gold by removing the player's 'intermediate terracotta'.
- you have obtained 10,000 gold by removing the player's 'advanced terracotta'.
new novel chapters are published on lightnovelworld.
com- you have obtained 3,000 gold by removing the player's 'intermediate terracotta'.
as a result, it brought about an extreme environmental change as if they entered the crater of an active volcano.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 