\section{chapter 38}






 “whew…”the skill she obtained with the linked card was fully activated.
besides, sungwoo’s skill was also in play at the moment.
-aura of death is awarding the effect of ‘forced slowdown’ to the subordinate.
-the enemy that came into contact with the subordinate has fallen into a state of ‘weakness.
’normally the orc skeleton would have collapsed without overcoming the vampire’s power, but now it had its shoulder only dislocated.
besides, a series of warning messages appeared before the vampire’s eyes.
2-you have fallen into a state of weakness.
the man felt every part of his body slowly crushing as if his muscles had desiccated and his bones were being dried.
 he could still stand up though thanks to his extraordinary physical strength.
“ugh…who the hell are you?”“you blindly charged at us, stupid.
 now you want to talk to us?”sungwoo was holding two spears in one hand.
“yes, i want to know who you are.
 tell me first.
”the vampire stretched his waist as if he was not vigilant anymore.
obviously he needed to try to buy time to recover.
 then, when the wounds were healed to some extent, he apparently planned to cut sungwoo’s neck and get out of the building to escape.
‘he only controls the skeletons, but he is weak.
 so, i can kill him right away.
’of course, he could not realize this kind of escape plan.
a spear was thrown and stabbed into his belly.
puk!another spear pierced through his chest.

“but you can open your mouth even if i cut your arms and legs, right? since we don’t even have to shake hands, you don’t need arms.
 now, tell me.
”“ahhhhh….
you son of a bitch…”puk!this time his right thigh was stabbed.
“watch your language, man.
 i’ve got lots of spears.
”1in no time the floor was soaked with his blood.
“…don’t be mistaken.
 you’re not superior to us just because you killed a lower vampire…”“us?”“our representative won’t spare his investments, so you son of a bitch will be… ahhhhhh!”at that moment, the man’s eyes turned red, and blue veins began to bulge out of his neck.
this was also a familiar scene for sungwoo.
 after he changed into that bizarre shape, he would be running wild with his stats greatly increased.
 that’s what happened to president park whom he had met at the apartments.
“jisu, kill him.
”at sungwoo’s uging, she immediately grabbed the sword with both hands and struck down his head.
 his head fell over a puddle of blood.
-you have earned 332 gold by killing a player.
3and a bonus was given based on the individual’s contribution to the battle.
sungwoo turned his head calmly and looked at taesung standing behind.
“hey.
”taesung’s face turned white.
 he stepped back awkwardly.
“oh, i don’t have anything to do with that man,” taesung said.
“i didn’t ask that.
”“then…”
“i told you earlier.
 give me all the gold you have.
 you guys used to bluff me like that.
 don’t you understand?”***-you have received 984 gold.
-you have received 431 gold.
-you have received 891 gold.
gold was received only through physical contact such as shaking hands.
1sungwoo confiscated all the gold the young gangsters had robbed from the street survivors.
“hey, not that many.
 i guessed we would get at least 10,000 gold…”hanho grumbled while receiving his share of gold.
“well, you’ve got to take into account the fact they are low-class gangsters…”like sungwoo expected, they were merely a third-class gang with no power.
but he didn’t know that they had been forced to panhandle under the vampire’s tight control.
taesung testified that the vampire called ‘uncle,’ whom sungwoo just killed, visited this place every day to take away gold.
 the vampire even tried to subdue them under his organization by making them vampires.
“i wonder if the ‘boss’ or ‘representative’ was the same man,” said jisu, looking at the vampire’s cut head on the floor.
“i don’t know, but this guy is deliberately and systematically expanding his power.
 only a few days after this kind of thing happened, he sent out collectors to rob people of gold.
”“you bet.
 i was just amazed by your swift adaptation, so i never thought there would be a man who did terrible things like this.
”sungwoo tilted his head at her reaction.
“well, these guys are not content with adapting to the situation….
actually they fit well in this world.
”vampires are not just adapting themselves to new things for survival.
 it seemed that they were enjoying the situation, just like a person who lived in this world in the past.
“and this vampire was stronger than the one in the h apartments.
 given that he could infect directly and freely move around without any restraint, he seemed to be directly related to the main vampire.
”it was evident that the main vampire controlled this area, with many subordinates under his authority.
 actually this ‘uncle’ mentioned ‘us.
’‘but can i ignore them?’ sungwoo murmured.
it was obvious that the main vampire was tough.
 even when dealing with only one vampire, sungwoo had to use all his resources.
 but what if these guys attack him in a group or in a gang of dozens?‘they are clearly a potential threat.
’besides, the main vampire was aware of sungwoo’s movement who killed the vampire at the h apartments.
 then, he would be informed of what just happened here.
thinking that someday he would confront the main vampire, sungwoo looked at taesung squatting in one corner.
 sungwoo had to be armed with more powerful items in preparation for confronting them.
sungwoo said, “i heard there was a shop here.
”when asked, taesung hurriedly stood up and escorted him, “oh, this way!”taesung walked ahead with big strides because he recognized that sungwoo’s party was much stronger than the vampire who had controlled him and his friends.
however, everyone, including sungwoo and taesung, had to stop at the entrance of the office, noticing the red letters before their eyes.
-here’s the problem.
 what if you were arrogant enough not to pick up your cards even during the second round?“what the heck is this? can you see this?”“…”in sungwoo’s mind, this was not intended to cause any problems.
 but it was written in red font provocatively.
‘it is a sign of something impending.
’sungwoo looked around the people in the office.
 all the members of sungwoo’s party had already chosen their jobs.
“uh, minsik?”the children’s eyes turned to one boy.
 the child called minsik was sitting on the sofa, restless.
“minsik, didn’t you choose a job?” taesung asked.
 minsik nodded with an uneasy expression.
“no, i didn’t…”“why?”

“because it’s weird! i have a bad feeling about this!”1his action was understandable.
 nobody wanted to plunge into this strange phenomenon when they didn’t know its cause.
 if they could stand outside safely and watch, there would be lots of people who would choose to do so.
1“…”taesung did not criticize minsik because he had no idea of what was going to happen.
-the correct answer?“w-what the fuck! what is it!” minsik shouted anxiously.
-if you haven’t yet woken up to reality after you were given two chances, you will be given the chance to become a monster if you don’t want to be a player!2“…what?”“minsik?”everyone stepped away from minsik.
“i wasn’t the only one who didn’t choose a card.
 jaehee didn’t either!”minsik pointed his finger to the boy named jaehee.
 his face was flushed.
“ah…”a dark vein began to grow out on his face.
 he touched his face and soon knelt in uncontrollable pain.
“oh, ahhhhhhhh!”their flesh swelled, their bones thickened, and black hair began to come out.
he sprouted.
 the height of the two boys, about 170 cm, quickly began to grow to 180, 190, and 200 cm.
 at first glance, they were not ordinary monsters.
“oh my god!”“uh, run away!”at a loss about what to do, the children started running out of the office, and the two boys who were in the process of becoming monsters screamed in pain and knocked on the walls and the floor.
bang!

 