\section{chapter 374}

chapter 374: exit from demon’s cavil and preparing to conquer china (6)she took off the armor of valkyrie.
 she put the sword back in the sheath and let out a sigh of relief.
 she said again, “i mean that man who always wins.
”




jisoo was ready to beat the chinese server with sungwoo, hunt the dragon, and finish this game.
just before escaping from the demon’s cave, the black lion felt a certain energy from beyond the portal.
 he said he felt like it was the commander of the 2nd army of demon’s cave that they encountered inside the devil’s world tree.
even though the world eater disappeared, there were still some monsters that hadn’t yet perished with him.
 it seemed that those monsters associated with a specific quest were preserved for the smooth progress of the quest in the system.
“well, this game is over anyway.
 let’s put an end to it quickly.
”so, sungwoo summoned ‘bone dragon’ and had him pass through the portal.
 of course, the bone dragon got rid of the remaining monsters at once.
‘the attack on the demon’s cave is now over completely.
 but i have to start another war.
’while the players were cheering enthusiastically, sungwoo was thinking about something else.
 he stood above the bone dragon’s head, summoning an old message.
- the korean server has been given an ‘opportunity to counterattack (initiative)’ against the ‘war opponent (chinese server)’.
* when you choose to counterattack, you can take the initiative and decide the ‘battlefield’ and ‘type of war’.
* you can select ‘termination of the war’ with the authority of the server master.
 (the war ends without any additional rewards.
)sungwoo immediately decided to ‘counter-attack’ against the chinese server.
at that moment the following message was displayed in front of all players around the world.

- the ‘korean server’ declared war on the ‘chinese 1 server’ (counterattack).
* this war will be broadcast live through ‘official channel-9’.
the players of the world tree camp, who cheered him enthusiastically, became silent at once.
 then, they checked the message that popped up.
- ‘counterattack’ effect is applied to all allies.
* all stats increase (+3)* moving speed increases (+10%)- since you have the war initiative, you can choose the ‘war method (battlefield, war type)’.
 (remaining time: 23:59:59)“whew! we’re at war again.
”“i know you have been fully prepared for it.
”in an era when everything was on the verge of destruction, they already knew that the end of one war meant the beginning of another war.
at that time, a drone was created in the air.
 it was the so-called ‘official channel’ drone for broadcasting.
weeeeeeng-
the drone started taking pictures of sungwoo riding on top of the bone dragon.
 as the war began, the official broadcasting also began again.
normally sungwoo would not have been interested in it, but he looked at the drone.
after a moment’s silence, he opened his mouth.
“on behalf of the korean server, let me say something to all the players in the world who will be watching this broadcast.
”although he said nothing inside the demon’s cave, he had something to say to those who still survived in this world.
 it was natural that they would focus on the voice of none other than necromancer.
he said, “it’s been a long time since this mysterious phenomenon in the form of a game began to ruin our world.
 we now need to prepare for the end of the game.
”so far, many players have questioned the truth of this game, but it was the first time we talked about the ‘end’ of the game.
“how long do you think this game will last? and does anyone know what the end of the game will look like?”most of the players in the world have stopped asking this question in order to survive.
 those who governed each server reflected on that old question, but they did not have as much information as sungwoo.
 in other words, they were ignorant.
 and their ignorance meant they were helpless.
“but i know what the end of the game is like.
”sungwoo briefly indicated to them how he was different from other rulers.
 in short, he wasn’t simply strong-willed, but he was the one closest to the essence of the game.
“all i know is that our world is now heading towards the worst of the worst.
 and what i’m trying to do is try to avoid the worst by all means.
”sungwoo witnessed the truth of the demon’s cave and realized something.
 in other words, he had to do everything to stop the worst.
kugugugu-at that moment, the bone dragon raised his head.
 the drone of the official channel raised its altitude accordingly.
 then, the fleet and troops of the world tree camp deployed in oreum were captured in one frame.
the reputation of ‘necromancer,’ who was at the center, stood out more greatly with the overwhelming majesty of ‘bone dragon’ next to him.
“to achieve my goal, i’m going to strike the chinese server invaders first, then i plan to launch a global organization, a kind of world control organization, with the world tree camp as the main base.
”in order to stop the worst situation, he needed a strong organization.
 no matter what they might be faced with the worst ending, they needed only one united power that could persist to the end.
“i warn you in advance.
 this upcoming organization will not be merciful to everyone.
 in order to protect the world, we will begin to aggressively weed out those who are deemed unnecessary, so all the players of all servers watching this broadcast, please…”sungwoo deliberately stopped at that point for a moment.
 his brief silence made the atmosphere of his dramatic speech even heavier.
in addition, it raised the concentration of those watching him, reminding them of the importance of what he had to say next.
sungwoo slowly opened his mouth.
“i hope you can make a wise choice.
”having said that, he turned.


the last part of his words mattered, after all.
 after all, the gist of his messages was to force them to choose between joining hands with the world tree and becoming their enemy.
to gain power, sungwoo boldly demonstrated his newly acquired subordinate, ‘bone dragon,’ to them.
‘it will be more beneficial to me to show my new power openly rather than hiding it for the sake of war with the chinese server.
’the necromancer riding on top of the bone dragon had a majestic aura that could not be compared to anything else.
‘it takes a kind of maturation stage for me to establish a solid image among them.
’now, the message he conveyed to them through this speech would linger in their minds for quite some time.
 and the moment sungwoo defeated the emperor of the chinese server, the world players will naturally trust sungwoo’s claim.
 that was the process of his message becoming his image.
“what the heck? sungwoo!”when sungwoo got off the dragon’s back, hanho ran to him.
“you know what? all of a sudden about 180,000 players watched your speech!”since the war between the korean server and the chinese server was the most attention-grabbing event in the world, a huge number of viewers watched the official broadcast when he was delivering the war message.
 the 180,000 viewers would certainly make a big fuss on their respective servers and convey sungwoo’s message to everyone.


 