\section{chapter 190}

                             




but their fight wasn’t over yet.
 they only stopped the wave of the devil monsters from coming out of the devil’s gate, but the basic obstacle to their further advance was the gatekeeper.
so, it was time sungwoo and his party stormed inside the gate after killing the gatekeeper.
‘but just because we’re going in now, we can’t attack the monsters.
 besides, my demigod status will be deactivated soon.
’so, sungwoo gave up and walked toward the portal.
 he was wondering if there was any information he could get from there.
at that moment an unexpected message appeared.
-you can ‘save’ the stages of dungeon attack on the ‘devil’s gate’ scroll that you possess now.
*caution! when you decide to save, the dungeon difficulty level will be increased by one level when you use the devil’s gate later.
‘save?’it seemed that some sort of function was given when he interacted with the devil’s gate item he had obtained from the container ship before.
and if the level of difficulty was higher, he would receive a better reward.
‘of course, that’s fine with me.
’so, sungwoo chose ‘save.
’-item information (devil’s gate) has been changed.
[item information]-name: 2nd floor of the devil’s gate-grade: special-category: magic scroll-effect: opens the door of the devil’s gate for 36 hours when used.
-description: create a passage that connects with the devil’s gate.
 you can get very valuable items by exploring the inside of the devil’s gate, but we recommend that you don’t try it hastily.
 don’t forget that someone might come out of the door that you can enter.
 (recommended level 43)
“let me go in by all means next time.
”when the save was over, the portal of the devil’s gate gradually began to shrink.
that meant the door was closed, and the quest was over.
“wow! wow! it’s over!”“incredible! we won.
”“hooray, necromancer!”“hurray!”cheers and shouts of joy came from all over.
 the taiwanese players were not only liberated from the pirates but also survived the terrible hell called the devil’s gate.
and everyone couldn’t help but admit that it was the necromancer of the korean server who saved them.
-all stats decrease for 24 hours as a strong power gets drained out of your body.
 (-10)even before he knew it, sungwoo’s demigod status was also at an end.
 come to think of it, it was indeed a close call.
 if sungwoo had come a little later, he would have not been able to kill the gatekeeper.
meanwhile, the most important thing was the ‘exclusive quest’ that sungwoo received when the door of the devil’s gate opened.
-you have successfully cleared the exclusive quest .
* you can choose a reward.
‘right to change a job’ i don’t need to change my job.
 hanho may want to.
’so, sungwoo chose no.
 1 without any hesitation, namely regular deity status.
 changing to another job was unthinkable for him.
-you can choose the regular deity status.
there seemed to be several gods related to death.
 however, the only one that sungwoo could use for now was anubis, the egyptian god of death.
sungwoo was curious about the abilities of the other deity statuses, but it was impossible to find out the conditions they required.

so, he chose no.
 1.
-the regular deity status has been granted to you.
* god of death: anubis[skill information]-name: anubis’ power (1st stage)-grade: demigod-classification: passive and active-consumption: 0for only one hour per day, you gain the power of ‘anubis’ by gaining the deity status.
 all stats increase by (+10).
 you can use exclusive skills.
now, he could maintain anubis status without resorting to the ‘human beast transformation ampoule’.
he felt it regrettable he could maintain anubis status only one hour, but given that ‘1st stage’ was written next to the skill, it seemed that there was room for increasing it in the future.
at that moment, the taiwanese players approached him.
one of them said, “thank you very much.
 it would have taken much longer if we had tried to get rid of the devil monsters by ourselves.
”this man’s name was chen.
 he had been rescued from a dungeon by sungwoo’s party.
 after that, he returned to his organization and successfully carried out the guerrilla operations.
of course, as chen said, this mission would have been impossible without sungwoo’s help.
even if the taiwanese players had succeeded in expelling the pirates, general chongong would have opened the devil’s gate as the last resort.
so, the taiwanese players expressed their gratitude to sungwoo and his party several times.
“you’re our savior.
 if there is anything we can do to help you, please feel free to contact us.
 we will be the first to help you.
”“i will contact you someday.
”sungwoo did not refuse such a request because it was certainly useful for him to have supporters like the players on kanghwa island.
chen hesitated for a moment, then opened his mouth again.
“by the way, i heard you were preparing a third camp.
 if you don’t mind, can our players join and support you?”it was never an easy choice for chen to choose the third camp rather than the absolute race camp.
he might have hesitated to choose a nascent organization instead of the strongly established force despite its merits, but he made the decision.
 this meant he recognized that the necromancer’s performance was great, and he accepted the necromancer as a trustworthy ally.
sungwoo replied, “i’m sorry, but i have not yet established the third camp.
 i want to ask you one question.
”“sure, please go ahead.
”“why do you want to choose the third camp?”“that’s because…” chen hesitated.
then, the woman standing behind him opened her mouth.
“because of our safety.
 there is nothing more important than our safety.
 we’ve already been beaten by the pirates.
”chen nodded as if he agreed with her.
sungwoo shook his head and said, “if you want to survive by relying on us, you’d rather choose the absolute race.
 i can’t provide a security cover for you.
”“really? then, what is the goal of the third camp?”sungwoo couldn’t help but think hard about his question.
‘goal?’he chose the third camp by chance.
 however, the reason that sungwoo boldly broke the angel statue was that he had the conviction that there was something possible only when he got out of the absolute race’s grip.
“well, my goal is to resolve this ridiculous phenomenon.
”sungwoo’s goal was not just to survive but to resolve this strange and absurd situation they were faced with at the moment.
 ironically, that was also the way for them to survive.


“i’m not going to recklessly accept anybody who wants to join us.
 i’m going to gather only qualified people and resolve this situation.
”there was a momentary silence.
“then, we are not qualified to join you,” said chen calmly, but there was self-mockery in his voice because they had been detained by the pirates until this morning.
“if you want to solve this hellish situation, you have to be able to protect yourself and your family first.
 let me turn off the broadcast now.
”after he said that, the broadcast ended.
the activities and goals of the third camp were broadcast to the entire korean server.
 and now those on the korean server were contemplating whether to choose the third camp or the absolute race.
-you have successfully cleared the camp quest .
*a reward is given to you.
 (camp skills, camp items)in other words, sungwoo’s propaganda broadcast was successful.
however, the fight was not over yet.
hanho rushed to sungwoo, holding a cell phone in hand.
 he must have received some message.
“sungwoo! an emergency call from the village!”“what happened?”sungwoo had asked the villagers to contact him whenever they encountered emergencies because he could go back to the village immediately using his ‘return’ skill.
“it seems some outsiders attacked them while we were away from them.
”“what did you say?”sungwoo hastily prepared his return skill.
 the fact that the village was attacked meant the world tree was in danger.
but hanho said, waving his hand hastily, “no, you don’t have to go back.
 the village players have captured all the attackers.
”was sungwoo too worried?the village players already became strong enough to protect themselves.


 