\section{chapter 451}

'what? second?'




apparently, the other team led by jisu and others already passed the gate.
'what a relief!'to be honest, sungwoo was worried about the other team.
 jisu and hanho were both strong fighters, but in case of emergency, sungwoo couldn't go to help them.
"the gate here has been opened!"when sungwoo killed petros, the stone gate behind the amphitheater opened, leading to the passage to the next gate.
thud! thud!at that moment, there were vibrations heard from somewhere, and stone dust poured from the ceiling.
"it looks like something happened upstairs.
 can't you feel the strong heat?"as li wei said, some very hot heat was spreading to the labyrinth.
did a fire break out?in the meantime, hanho and junghoon were marching along a long corridor with 121 players.
clang! clang!while they were moving along, they were showered with all kinds of attacks from all corners of the hallway.
"watch out! it's over our heads!"the ceiling opened and fire magic poured over their heads.
 then, poison stings came out of the floor.
 besides, acidic liquid erupted from both walls.
"don't worry! just move on! i'll stop them all! just keep going!"despite such attacks, they kept moving.
 standing at the forefront of the players, hanho and junghoon blocked all attacks, holding their shields.
"alright.
 i see the end of the gate over there!"the gate they faced was a sort of death room laid out with a large-scale trap.
originally, those in the thief and explorer occupation were supposed to move on slowly and cautiously and dismantle the traps.
"keep moving forward!""move! move! just keep moving and watching ahead!"
they moved on, taking all the risks along the way.
 more precisely, they could keep moving thanks to the 'power of hyunmoo' that shielded the entire party.
"haha! i feel as if i'm seeing a water gun parade.
 they are firing something from all sides, and i'm just thrilled when i fully expose them!"he was talking nonsense, but he was obviously thrilled.
for more, visit lightnovelworld.
c‌omat that moment, jisu said, "hanho, don't let down your guard! you never know what might put you in danger!""bahahahaha! let them bring it on! they won't be able to overcome the power of hyunmu!"holding the extreme shield of hyunmu, they kept moving and incapacitated all the traps by removing the core device at the end of the corridor.
- you have passed the labyrinth no.
 '2' gate (4/7)so, they succeeded in passing one gate.
"well, we can do it without sungwoo's help anyway.
 bahahahaha!"junghoon let out a sigh, looking at him.
 of course, he did a great job, but junghoon was still concerned because he could be reckless.
"whew! alright.
 this is just a warm-up exercise.
 by the way, what about the other team?" hanho asked.
when he asked, the signal operator who was holding a radio item raised his head.
"oh, i hear that the necromancer has just passed through gate 4.
""hey, no wonder he passed it.
 what about sister jisu? it's about time we went ahead of her team," hanho asked with some expectations.
but the operator said, shaking his head, "no, i hear that they have already passed through two gates and entered the third.
""really? how come they moved faster than sungwoo?"the operator replied, "um, i don't know either, but it looks like the red dragon there is going on the rampage.
 i don't know what they are talking about.
"at that time, sungwoo's party already arrived at gate no.
 7, which was actually the second gate of the labyrinth.
it was an old underground facility, and it felt like a damp swamp because of moss here and there.
"what the heck is this place? it's so humid.
 my spirits are whispering that it's so disgusting.
 it looks like water nearby has been polluted.
"not surprisingly, a deep puddle was on one side.
 and above the puddle, marble columns and statues were standing here and there as if old remains had been submerged.

the players raised their weapons and began to search the area.
"necromancer!"one of the members called sungwoo and said, "something over there is moving inside!"sungwoo looked at it.
 clearly, a huge shadow was wriggling inside the puddle.
then suddenly two red lights appeared above the shadow.
soon, the head of a giant snake soared out of the pool with a splash of water.
"oh, my god…"- the hidden stage boss monster 'basilisk' has appeared.
you can find the rest of this content on the lightnovelworld.
com platform.
basilisk, a monster appearing in various myths, was best known for its shape as a huge snake.
it was shorter than imoogi, but its head was about 1.
5 times as big as imoogi's.
his red eyes looked down at sungwoo.
"little creatures, unfortunately, welcome to gate 7 of the labyrinth of the demon king.
 the rules here are very simple.
"bubble- bubble-after he said that, the water in the puddle spewed out bubbles like boiling water, and the water level began to rise rapidly.
"you just need to escape before the room is full of water and drowns you.
 of course, you have to beat me first to get out of here.
"the water from the puddle already rose to sungwoo's feet.
"the water level is rising!""check out the escape route!"the players responded while acting cautiously.
however, sungwoo stood still and examined basilisk.
 his eyes were suspicious.
 they looked like the eyes of a luxury brand's chief designer who was choosing new products to be released in the upcoming season.
 basilisk asked if he felt sungwoo's gaze strange.
sungwoo finally opened his mouth.
"alright.
 it looks useful.
""i have something similar to you, but i thought it would be nice for me to have one more.
"bang!at that moment, the wall on the side of the passage sungwoo's party had passed by collapsed, and something elongated came out of the gap.
"everyone, lower your head!"it was a hand.
 a gigantic hand with broken chains broke through the wall and stretched out into the puddle.
"pick him up.
"the hand grabbed basilisk's head according to sungwoo's command, but it was so big that it pulled basilisk out of the puddle as if it picked up an eel.
grabbed by gigas's hand, he twisted his body, scattering something in all directions.
the source of this content is lightnov­elworld.
comcheeeeeeeeeee-it was black liquid and smoke, or more precisely, deadly acid venom spewed from his two fangs.
"damn it! it's poison! retreat!"the players spread their shields and hurriedly stepped back.
since sungwoo was resistant to poison, he stood still and examined him again.
gigas grabbed basilisk's neck with one hand, and his lower jaw with the other, then forced it apart.
he wriggled his body to resist, but to no avail.
 although he was a monster in myths, he could not be compared to the giant race in myths.


after that, a second giga broke the wall and grabbed his body.
"okay, let me see…"with him unable to move, sungwoo looked inside basilisk's mouth like a dentist.
"yeah, that's it.
"when sungwoo nodded, giga grabbed one of his fangs with his index finger and thumb.
 he then turned it clockwise and pulled it out.
his sharp teeth fell to the floor while he was screaming in pain.
sungwoo examined his teeth.
"venom-spewing teeth? well, bones and skins are not all that's useful! this is also good!"sungwoo looked down at his wrist, the bracelet of the red dragon.
 it was an accessory made by weaving the teeth of the red dragon, with which he could summon 10 'dragon soldiers'.
"if i ask hearst to weave it here, he's going to produce something useful.
"after all, the magic workshop was useful in various ways.
"this is not a labyrinth, but a great treasure trove!"sungwoo was going to obtain as many as possible before its owner returned.
at that moment, someone called him from behind.
"necromancer!"he was the wireless operator.
"this news is just in from the messenger on the defensive route! the demon king has appeared in the sky outside the rampart!"the latest episodes are on the lightnov­elworld.
c‌om website.
finally, the owner of the castle returned.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 