\section{chapter 216}






 a well-organized party was marching into the narrow crypt.
 there were a total of 25 players from the world tree camp.
 at a glance, they seemed exhausted.
“haa…”“everyone, hold out a little more.
 you will arrive at a turning point.
”they were undergoing hard training to become an elite group, and it was not easy.
it was true that they raised their levels through active hunting even while sungwoo was away, but none of them had experience in attacking the dungeon of the highest difficulty level.
“something is charging at us!”ooooooh!“they’re trolls! four trolls are attacking us!”“don’t panic! with our current level, we can hunt them!”thump- thump- thump-of course, these players were not an undisciplined group.
 even if large monsters attacked them, the players quickly recovered their composure and began to focus on their assigned roles.
“tanker, advance!”“cast protection magic on the shield!”the tankers were ready to hold out after blocking the narrow street corner.
 then, the wizards in the rear swung their wands and prepared magic.
“muscle paralysis!”“heavy legs!”“shield breaker!”after weakening a group of trolls by casting the magic of an abnormal state, ranged dealers spammed tremendous firepower.

shunnnnnnng! shunnnnnnnng!when dozens of arrows hit the trolls’ legs, they began to collapse one by one.
“good job! charge!”“kill them all!”the players made a frontal attack on the trolls.
 since the troll race’s resilience was very high, they should not give the trolls any chance to recover.
 so, the players had to run straight and stab their vital spots.
 the players started to kill the trolls without any hesitation.
puck! puck!a terrifying noise resonated through the crypt.
-you have earned 3,100 gold by hunting ‘underground trolls’.
-you have earned 4,550 gold by hunting ‘underground trolls’.
-you have earned 3,650 gold by hunting ‘underground trolls’.
-you have earned 13,500 gold by hunting ‘underground troll watcher’.
the monsters were strong enough to give any player who hunted them 60,000 gold, so as a well-trained party, the 25 players could hunt them without any difficulty.
of course, if the players were caught off guard, their shield wall could collapse in the blink of an eye, and the wizards and archers with weak defense could be slaughtered.
 fortunately, no such accident had occurred yet.
“whew! we have finished! the entrance to the second floor is over there! that’s the turnaround point.
”“everybody, good job.
 looks like you guys finished much faster than before.
”the players were accumulating combat experience by attacking only the first basement level of the large-scale dungeon in the “troll’s crypt” in the nearby “west lake park.
”it was a dungeon consisting of three floors, and the first floor was a relatively safe area, so there were no casualties yet.
however, they have been attacking in the predetermined order for eleven hours now, so they were almost exhausted.
“i want to take a rest.
”
“i feel like i want to vomit because i have not been able to rest for two hours while attacking the troll monsters.
”since they attacked the monsters faster and faster, their break time was drastically reduced because they had to prepare for the next attack as soon as they were done.
‘it’s hell.
’‘too tough.
 i regret saying i would work hard.
’therefore, as time passed by, they were facing their limits of exhaustion.
some even had nosebleeds.
exhausted by the endless hard training, all of the players wanted to give up right away, but they refreshed their determination.
‘well, i really can’t say i will give up.
”after they cleared the trolls’ corpses and their equipment, they checked the necromancer’s expression, who was standing behind them.
“…”after looking at the traces of their fighting, the necromancer turned around without saying anything.
then, the skeletons waiting in the rear came running and carried the bodies of underground trolls, and started to get out of the dungeon.
it meant the end of their offensive against the trolls.
“well, the necromancer’s action means we did a good job, right?”“don’t you think we still have a long way to go?”“man, i have no idea…”the players could hardly figure out the necromancer’s reaction, but they could fight more actively because he was standing behind them.
 they knew he would come to their rescue in an emergency.
in other words, they knew that hard training was the fastest and safest way for them to grow.
meanwhile, the next group was on standby at the entrance of the ‘troll’s crypt’ dungeon.
they were still exhausted because of a short break, but they had no choice but to get ready to attack the dungeon.
“hah, i’m so tired…”“if i repeat this attack exercise two more times, i might die.
 i think i am fighting while dozing off.
 hey guys, please come out a little later!”however, the entrance to the dungeon lit up against their wishes.
 it meant their previous group’s dungeon attack was finished, so the next group should be ready to go in.
“what the heck? did they already finish and come out? they went in a short time ago, right?”“man, they are so fast!”group 3, who entered the dungeon earlier, began to come out.
 all of the players were already exhausted.
“group 3, you guys finished in 15 minutes and 34 seconds.
”“wow! we shortened our attack by four minutes, compared with our last attack.
 awesome!”although group 3 completed the attack when they were at the end of their tether, they were soon elated at the better results than expected.
“15 minutes? well, it seems that i’m fighting more confidently with more fighting experiences.
 before i knew it, i used skills automatically.
”“right.
 this time, it seems that none of my arrows or magic missed the target.
 yeah, i think my fighting has improved through this hard training several times.
”all the players felt they were growing every moment.
 they even felt they were stronger than they were only two hours ago.
 so, it’s no wonder they felt a great sense of achievement.
they extracted skin and blood from the bodies of the “underground trolls.
” as a result, they were piling up a lot of materials for future wars.
“uh? they’re coming in again!”a huge shadow cast over the sky in the suwon village.
 it was sungwoo’s bone wyvern.
when a total of three wyverns landed in the vacant lot, the players in the field of living and production started to get busy.
“what the heck? they came here so fast! we haven’t even processed all the materials we received last time.
”“aren’t the players attacking the dungeon more and more crazy? they are supposed to get more and more tired as time passes, but how can they speed up their attack?”

the players here specialized in their field through a division of labor, so they dismantled the materials and produced items in an organized way.
they could just stack up the materials and produce them slowly, but it seemed like they were also training for a total war that might break out someday.
“all the boxes are full.
 bring extra boxes!”“there are already over 60 boxes of recovery potions.
”“crazy! it’s like we’re working in a drink company?”‘troll’s blood’ had excellent self-regeneration properties and was good material for recovery potions.
even if the players take it raw, they could expect the healing of their wounds.
 so, they were reborn as a much more effective item through processing.
“damn trolls! their skin is too tough, my wrist hurts so much.
 i heard that mr.
 kim, the tanner, used to work at the pyeonghwa market.
 he says it’s tougher to work here.
”“hey, try to trim even more leather instead of chatting like that.
”the leather of the monster was perfect as an armor material.
 the tanners and blacksmiths joined hands to produce better than average defense items.
also, those in a cooking position were cooking many foods that had a buff effect and distributing them to those in need.
it’s been 13 hours since they started attacking the dungeon when they had a brief break.
at that moment, kyongsu came and reported to sungwoo.
“our players’ average level is over 11.
 more precisely, it’s 11.
6, so rounding it up will be 12.
”the average level of 226 players was a whopping 11.
6.
 excluding children who couldn’t fight yet and players in the field of living and production, their average level would be higher.
moreover, even the elderly, who were often treated as a nuisance in most survivor groups, also played their role well.
“are you sure your level is 13, sir? oh my god! weren’t you level 7 until recently?”“hahaha.
 i think i can fight well when i reminisce about my fighting days during the vietnamese war.
”some seniors recovered their health when they leveled up, so they were now strong enough to fight with young players.


 