\section{chapter 281}






 at that moment, a dark wave spread in all directions.
 it was mana.
 mir used some sort of magic.
and a message about the identity of the magic appeared before sungwoo’s eyes.
however, it was sungwoo who was most surprised.
– caution! ‘fellbalde’ begins in the affected area.
“what? fellblade?”did mir already learn the empty haven and fellblade magic? and what the hell was he summoning?although sungwoo was the owner of this little dragon, he realized at the same time that mir was unpredictable.
and something beyond explanation happened.
rattle! rattle!a relatively small black smoke arose, and a group of skeletons walked out of it.
“chicken?”all of them were ‘chicken skeletons’, 14 in total.
 sungwoo wondered where all the bones of the 14 barbecued chickens had gone, and mir put and kept all of them in the empty haven.
“what the heck are you doing?” the guy named tsar shouted at sungwoo.
 did he think sungwoo tricked him?but sungwoo shrugged and said casually, “no idea.
” he was serious.
and things he could not understand kept going on.
-‘black dragon (hatchling)’ has created a ‘new skill’ by applying the skill he inherited from you.
“what else?”[skill information]-name: death flames-grade: skilled-category: active (on/off)
-consumption: 5 mana per flame*you can give ‘death flames’ to the undead under your command.
 this flame does not turn off easily and inflicts “flame” damage to the target it contacts.
the next moment, a red light lit up inside the ribs of the chicken skeletons.
it was flame.
 it rose from the part where the heart was located and covered the whole body.
“oh my god! sungwoo, what the heck is that?”sungwoo’s answer was the same again.
 “i don’t know.
”he really didn’t know.
 all he could guess was that mir created something ridiculous by combining sungwoo’s “salamander’s aura” with the necromancer’s skills.
that wasn’t all.
-‘synergy effect’ is given due to team play.
[synergy list]4) harmony of death (hidden)-category: job synergy-condition: 3 or more ‘lich’-level death magic users-effect: upgrade to the ‘ultimate’ level of the exclusive skill (1 random type)it seemed that mir’s use of the undead reached the level of ‘lich’, and as a result, sungwoo was given a hidden synergy thanks to the presence of a total of three liches in sungwoo’s camp.
‘ultimate level?’-the skill of “bone weapon manufacturing (skilled)” is temporarily upgraded to “bone weapon manufacturing (ultimate)”.
as expected, there was a higher level than the ‘craftsman’ level.
 sungwoo felt that the so-called “ultimate” level was the final stage, as the name suggested.
‘i’ve added only one dragon, but the possibilities for my skill utilization are endless.
’grrrrrrrrrrrrrr!when sungwoo was amazed by such possibilities, mir pushed his snout forward.
then, the burning chicken skeletons began to run in a waddle.
 mir ordered them to advance.

“man, they are fire chicken skeletons!”hanho shouted excitedly at their bizarre and ridiculous appearance.
rattle! rattle!the ‘fire chicken skeleton’ squad named by hanho stepped forward bravely and clashed with the ancient giant bears.
 it was a really ridiculous scene.
thud! thud!but the bears, whose bodies turned stiff, couldn’t catch the fire chicken skeletons running around under their feet.
meanwhile, the fire chicken skeletons spread flames on their bodies while rubbing against fur.
cheeeeeeee-the flames began to spread from their legs to their waists and backs, plunging them into a panic.
“lol! let me show you how painful our attack is! do you know fire chicken? yeah, this is the essence of our cruel attack!”it was an unbelievable scene.
it seemed that the tsar did not want to watch such an absurd scene.
 a shape like a giant bear appeared behind his back.
 it was attack magic.
‘that’s dangerous.
’sungwoo hastily made a bone shield to cover mir’s body.
 right after that, the tsar swung his fist.
 then, the creature looking like a bear behind his back swung his front paws.
kuwoooong!as if sonic boom occurred, the air exploded and the bear’s paws flew in.
but the tsar’s target was none other than his subordinate spirits, ancient giant bears.
all the brown bears collapsed with one stroke with their heads smashed.
and the fire chicken skeletons lingering around them were also shattered.
 only one of them bounced off and fell before mir.
grrrrrrrrrrrrrrrr-watching the chicken skeletons smashed to pieces, mir became so excited that he was ready to counterattack the tsar at any moment, but sungwoo stopped him right away.
the tsar shook his wrist then stared at sungwoo.
“it looks like you are mistaken.
 they are only my pets.
 they are different from skeletons.
”then, he laughed scornfully at sungwoo.
“i am different from you.
 you’ll come out and fight me, won’t you?”the tsar jumped off the ground to attack sungwoo.
 at the same time, the siberian hunters and the undead army moved again and clashed for the second time.
sungwoo stepped back, firing his repeating crossbow.
tung! tung! tung! tung!but the tsar did not avoid his attack.
 he wrapped his body with both arms.
 then, the bear shape behind his back changed.
 this time it was a turtle.
tong! tong! tong! tong!a green shield floated over its body, repelling all attacks.
 perhaps because of the turtle’s traits, his moving speed was markedly slow.
“jisu!”sungwoo threw mir at her.
 she jumped quickly and received him.
mir might flee from her arms using shadow movement skill, but sungwoo could not afford to pay attention to it.
after exactly 10 seconds, the tsar changed into another shape.
 this time it was a wolf shape.
“you are at best prey! a little tough game!”the tsar charged at sungwoo at a tremendous speed then e changed into another shape.
this time it was a tiger.
 he was thinking of running to sungwoo like a wolf and stopping his windpipe like a tiger at once.
 when he swung his fist, the tiger shape struck the ground with his paws.
 his sharp claws tore the air.
sungwoo blocked the attack with a bone shield, but it hurt as if his arm was broken.
 sungwoo’s body bounced off, crushing a bench as he hit the wall of yongsan station.
it had been a while since sungwoo was hit directly like that, but he was not groggy yet.
sungwoo raised himself and controlled the undead.
‘surround him!’the tsar changed into a wolf shape and charged at sungwoo.
 however, sungwoo’s undead were also fast.
 those who could move fast gathered around the tsar immediately.


“get out of here!”the tsar swung his hands violently.
 huge claws scratched the area around him, and the ghouls aiming at the tsar’s neck were smashed to pieces.
 however, that little moment was more than enough for sungwoo to prepare for the next attack.
whooooooooong-when sungwoo swung the grim reaper, ten black spheres were fired.
 it was “evil spirit bombing”.
however, the tsar did not avoid his attack again this time.
 when he wrapped his body with both arms again, and a turtle shape appeared.
gu-gu-gu-gung-a black sway flew through the shield, scattering behind the tsar’s back.
 he made a scornful smile.
watching it, sungwoo thought, ‘man, this guy’s defense power is tremendous.
 if the ‘evil spirit bombing’ didn’t work, i can’t beat him by mobilizing simple firepower alone.
’ten seconds later, the tsar became a wolf shape and ran at sungwoo fiercely.
 but sungwoo kept stepping back, throwing the undead at him.
 he also placed some undead on the retreat route to prevent the tsar from chasing him.
“hey! how long are you going to play with me?”the tsar stopped chasing then opened his arms toward sungwoo provocatively.
“aren’t you a strong player who fought against and beat the angel and demon camps? was it all a fake?”“…”“hey, let’s fight a one-on-one match!”the tsar smashed a skull, showing a desperate wish to fight him.
“if you are a real man, you have to show your own strength.
 asian men aren’t even as strong as women…”he kept talking to sungwoo with provocative words, but the latter lifted the repeating crossbow without replying to him.
 then, he fired an arrow.
tung!the tsar turned his head to avoid the arrow, but its tip got caught on the fur hat, sending it far away.
 a vein was seen on his forehead.
“damn it! yeah, i’m interested in your response anyway!”he raised his right hand in violent excitement.
 the tattoo on the back of his hand began to glow black.
– caution! a ‘demon beast’ has been summoned in the area.


 