\section{chapter 191}






 the world has become like a game.
why?at first, everyone questioned whether the world could change like a game.
 they questioned who the hell was responsible.
 was it the conspiracy of the corporates? or was it god’s play? if they were not responsible, was it a dream?but nobody cared about it soon.
what was important to them was not who gave the quest.
 how to clear the quest right now was the most important thing in the world.
they couldn’t even afford to question it for their immediate survival.
but the necromancer said, “i’m trying to resolve this strange phenomenon.
”people took his remarks very seriously because he said that after his overwhelming performance.
 they felt like a powerful revolutionary man appeared and argued for justice when everybody closed their eyes without resisting in a society where corruption was rampant.
and nobody could ignore the impact of his remarks.
[501] i support the necromancer.
-author: kangbuk 1994 │ hit: 11,443i’ve discovered lots of things while watching for fun the broadcast on the necromancer’s crackdown on the pirates.
 i’ve agonized once again why the world has ended up in a miserable situation like this.
 and i became very much upset.
 why should we suffer like this? and what are the intentions of the angel camp and the devil camp? i have to think carefully about them.
 i don’t dare say that i want to join the third camp because of my lack of ability, but i support the necromancer.
 and i will try my way.
[comments: 14]- seungcheol123: i support him, too.
- kor-2222: i support him, too.
- sergeant park: i will follow you.
- mister 55: i want to resist like a human being instead of surviving like an animal.
- goo hee-mang: i want to join the third camp.
- yasuo 1: hmm…meanwhile, after the necromancer’s broadcast ended, the war between the angel camp and the demon camp resumed in northern seoul.
there was quite an important development.
 the crusader team led by junghoon pushed out the reconstruction alliance and secured a “cheongnyangni base.
”and the crusaders also broadcast the scenes of defeating them for propaganda purposes.
[real time chat]
- survive to the end: yeah, the crusader team is amazing but not that impressive.
- jinsang js: i’m not impressed after having watched the necromancer’s performance.
- living in incheon: nothing particular.
- yeongdeungpo monk: good job!the viewers who watched it did not hide their empty feelings and their reaction in the chat room was lukewarm.
everyone knew the reason.
 it was because all the players of the korean server were pretty much influenced by the necromancer’s performance.
“hey, we also have to hunt from now on.
 haven’t you heard what the necromancer said? otherwise, we’ll be eliminated at the end of the day!”“got it, heyon, please calm down first.
”after she watched the necromancer’s broadcast, she made a fuss like a child.
her father, muyon, calmed her down and said, “no matter what, you shouldn’t be hasty.
 you have to prepare slowly and carefully.
 after all, we have to protect ourselves, so we have to make sure none of us die or get hurt.
”“okay, dad…”of course, muyon also hoped that the players on kanghwa island would become strong.
 he was thinking of leveling up and securing the items to steadily increase their survival skill.
since they had been already defeated by the pirates, they knew they could not afford to be complacent until they were fully competent enough to confront the pirates.
until now they had been focusing on restoring the basic facilities for their daily lives and monitoring the chinese servers.
 that’s what they promised the necromancer, which required considerable manpower and time.
however, the situation changed because the necromancer defeated the pirates.
“now the time has come for us to protect ourselves.
 we can’t stay as a weak group forever.
 in other words, we can’t seek the necromancer every time we run into difficulties.
 as he said, we need to be more useful to him.
”“you’re right.
 we’ve been helped twice by him.
 someday we should be able to help him, too.
”they have already supported the third camp for a long time and have followed the necromancer’s intentions.
 therefore, they had no choice but to take seriously what sungwoo emphasized, namely, they needed to strengthen themselves.
“sure, we have to be useful to him someday…”they were determined to give strong support to the necromancer by emerging as one of the proud pillars of the third camp.
***“oh, awesome! great!”just like the name of the pirates suggested, their warehouses were full of all kinds of items.

hanho took out two green-bladed daggers.
[item information]-name: ghostly dagger-class: hero-category: dagger-effect: when you swing a knife, you can fire a ‘ghost blade’ that mimics the shape of the blade.
 (reuse standby: 10 seconds)until now, hanho has relied on crude weapons such as the bone daggers made by sungwoo.
 however, he finally obtained a great item, leaving his nasty past behind.
“finally, i’ve obtained it, too!”it was a really lucky day for him because he got an item specialized for throwing daggers.
he was moved to tears before he knew it.
“man, many memories of my hardships are going through my mind like a flash!”in the meantime, sungwoo was also picking up useful items and putting them in his backpack, accompanied by the undead army.
if he could have his way, sungwoo would collect all the items available here, but since most of the items had been stolen by the pirates, sungwoo wanted to leave behind enough items to help the taiwanese players recover their ruined areas and establish a solid foundation for living.
 “but i can’t give up this one.
”of course, there were things that he couldn’t give up.
[item information]-name: vault of oath-grade: special-category: finance-effect: some of the gold earned by the ‘contracted player’ is automatically deposited.
-description: you can ‘register a contract’ by placing your palm on the safe.
 the vault owner can set a ‘collection rate’, and the amount of gold earned by the contractor is automatically deposited into the vault.
* collection rate: 50%* registered contractors: 119 people* current gold: 67,858,248it was almost 68 million gold.
 this time, the pirates left behind a huge legacy of wealth.
“we’ve got too much gold.
”meanwhile, jisu has reached the exp with which she could use “c-class exp’ by clearing the “survival quest”.
even though she did not hunt many devil monsters, she obtained lots of exp because of the huge level difference.
 she leveled up using her coupons.
as a result, there was a change in the rankings of the korean server.
[kor server ranking (page 1)]1) kangsok han (lv.
 22)2) kor-157 (lv.
 22)3) doctor-000 (lv.
 20)4) youngdungpo inspector (lv.
 19)5) kor-339 (lv.
 18)finally, jisu was ranked 5th on the korean server.
 and this incident, too, was enough to make the third camp stand out, for the fact that two of the necromancer’s team were among the top 5 rankers was surely an attractive symbol.
“let’s go back.
”when sungwoo said that, jisu and hanho approached him.
“we’re all set.
”“me, too! great! i’ve got a weapon, too! hahaha, you don’t need to make me a bone dagger anymore, sungwoo!”hanho and jisu looked somewhat proud and satisfied with their results.
when sungwoo and his party finished preparing to return to the korean server, the taiwanese players approached them and said goodbye.
“thank you very much.
 thanks to your help, we have regained freedom.
”“we won’t forget your help!”they once again expressed their gratitude,finally, chen stepped forward and said, “although i’m not yet competent enough, i’ll contact you soon.
”on behalf of the taiwanese players, he expressed his strong ambition.


“i promise you that i will not disappoint you then.
”sungwoo’s conditions for them to join the third camp was that they needed to develop the power to protect themselves.
 it was a desire for them to realize as well as their big challenge.
 so, they felt a lot more attracted to the third camp that revealed their weakness.
“sure, let me wait.
”sungwoo nodded, then opened the portal.
-the ‘return portal’ to the world tree has been opened.
the necromancer’s team quickly changed the situation of the world, then went back to the korean server.
***after sungwoo returned to the village, he released all the items he had brought from the pirates’ warehouse.
 the collected items were so many as to fill almost one truck.
 each of them was quite a luxury item.
kyongsu and inho could not help but be in awe.
“wow! what the heck is all this? it looks like you’ve returned from overseas trading on a large cargo ship.
”“you have plundered the pirates!”having heard that, hanho stepped forward, with a proud expression.
“hahahaha! it is too early for you to express admiration for them.
 look at this!”he pulled out two daggers from his waist.
 kyungsu and inho stared at the green objects blankly.
“pardon?”“what is that? razor?”hanho was upset about their ridiculous reaction.
“what did you say? a razor!”“or is it a cake cutter? are you going to celebrate the victory by yourself?”“oh, that’s right.
”“no kidding! oh my god!” hanho fumed.
hanho swung two daggers and explained to them how effective his item was.
but kyongsu and inho didn’t pay much attention to what he explained.
 instead, they were busy classifying the items according to their uses.


 