\section{chapter 465}

"yes, this is what we want to see! this is the united power!"




watching the players fighting, all united as one, reporter ahn could not hide his admiration.
 "i'm just overwhelmed…"he wiped his face.
 he had never thought he had love for humanity.
 but he began to cultivate something like love for humanity while watching a series of battles.
 "i've been broadcasting player-to-player battles among the victims of this game.
 but when i look back and think about it, it's just funny.
""pardon? what's so funny?"reporter ahn looked directly at the camera at his assistant's question.
"why do we have to fight among ourselves?" he asked sternly.
 "we are all being victimized by this game.
 as the necromancer once said, we have to find out the reason for this game.
"his assistant said, "do you think we can find it out? i hope so, but …"reporter ahn replied, shaking his head, "well, i don't know.
 it would be hard to find it out.
 there must be somebody who has enough power to play with one world from the beginning.
"it was safe to say that he must be an almost absolute being since he could put those players who broke the rules to "automatic death.
" "can we dare to challenge such a being? but…"he took a deep breath as if he was trying to say something boldly.
 "i want to know what the heck they are trying to do before i face my final moment.
"***the elite forces of the world tree camp, including sungwoo, his 'colleagues', and the special commando unit were gathered at the frontline.
 as their forces in the rear firmly took their positions, they were now in a better position to fight the demon king and his forces because their strong firepower swept away the hell creatures summoned by the demon king, who had been a big hindrance to their advance.
of course, it would be hard for them to provide firepower if they approached the demon king closer.

"now, we must be ready to attack the demon king," sungwoo said.
 the demon king was still standing firmly behind the black castle under the red clouds.
his lower body got stuck between the cracks, so it seemed that it was connected to the red 'clump of tentacles' rising from underground.
 "we have to approach him by all means," sungwoo emphasized.
 the demon king showed no sign of moving from the spot where he was, but they couldn't wait forever before attacking him.
 "you mean we have to break through his striking distance even when he can sweep away everybody with a beam of light when they approach him closely, right?" li wei asked.
 sungwoo nodded at him and said, "that's the only way.
"but it wasn't easy.
 sungwoo has already tried to do so but failed.
of course, the situation was different this time because he had the full backing of his colleagues and allies.
 but the problem was that even if they succeeded in breaking through his resistance, they had to confront his eight arms.
"the eight arms around his body are faster than you think.
"the moment they were caught by the arms, they would be killed.
 sungwoo recalled the mighty power of the demon king pressing down gigantes with one arm like a child.
"what's more, you have to watch out for the ground where you are standing because his tentacles come up from underground and bind you tightly.
 but even if you get through all of that…"sungwoo turned his head and looked at the demon king.
"if we don't target his head, we are not going to inflict any real damage to him.
"like a swarm of bees clinging to a beehive, tentacles tightly surrounded the demon king's whole body.

hanho said with a sigh, "man, he's a real monster!"the demon king himself was none other than an impregnable fortress.
 but they had to get rid of him by all means.
 "we don't have a second chance to kill him if we don't do it this time.
"sungwoo turned, and the elite forces also followed him.
thump- thump- thump- thump-gigantes advanced, followed by large skeletons, including bone dragon, and hanho's hyunmoo.
 the players also advanced, hiding behind them.
"we're within the demon king's striking range of the beam!"they could not block the demon king's beam attack, so they were on full alert, ready to escape just in case.
whoooooooooo-a huge shadow followed them from the sky.
 it was the red dragon, isabella.
"if we narrow the distance with the demon king, isabella will nosedive and let out dragon breath toward him!"the only attack that could be effective was her 'dragon breath', except for sungwoo's superheavy arrow.
 when they approached the demon king to some extent, he tilted his head, then his 12 eyeballs moved toward them all at once.
 and his voice resounded to everybody loudly.
 "necromancer, you can't stop the bad ending of this world, no matter what you do!"as somebody who experienced this game three times, the demon king advised him.
"you want to know why? it's because there is no such thing as a happy ending in this game!"'bad ending.
.
.
'sungwoo recalled the demons' cave, another earth.
'yeah, no matter how much i resist, i might end up losing again.
'but he hated succumbing to this game and fooling around like gangsok, or the demon king.
 'i would rather die resisting, even if my attack is meaningless.
'sungwoo made up his mind a long time ago.
at that moment, the demon king raised his head.
 twelve horns rose from his three heads.
 it was a beam attack.
 red beams emitted from the horns and began to split the entire space around the players.
"advance!" sungwoo shouted.
 his allies dispersed in all directions as if they promised.
 only hanho stayed behind.
"socrates! let's stop him!"hyunmoo by the name of socrates crouched down when a tremendous heat struck hyunmoo.
- caution! the damage you can endure has exceeded its limit.
 'incarnation' may disappear.
even hyunmoo's power, 'absolute defense,' seemed to be unable to withstand it for long.
 it was several times more powerful than dragon breath.
"kheeeeeeeek! i wonder if i can endure it.
 can i? but i want to strike back!"

the energy of the rays that hit hyunmoo was being absorbed into hanho's body, which was tangled and shot forth.
clang!hyunmoo disappeared as soon as it reflected a single beam.
 the reflected beam flew straight towards the demon king's right head.
"alright! it hit the target!"but the demon king instinctively lowered his head, then raised three arms at the same time to shoot defensive waves.
 this attack had once destroyed isabella's dragon breath.
the reflected red light was much tougher than dragon breath.
 as if three hands were not enough, he raised the fourth hand and fired a wave.
"now is the time!"while the four beams and four arms were incapacitated, sungwoo's allies who had dispersed in all directions charged at the demon king.
 sungwoo approached him as close as possible, using shadow movement.
'hasn't he noticed me yet?'his tentacles did not respond because sungwoo narrowed the distance with him in an instant.
 it seemed that they didn't move automatically.
 so sungwoo fired 'winter predator' at one of the demon ding's joints near his arms in the 'expansion mode'.
about 50 frozen bullets hit his elbow, making him unable to bend the joints.
'great!"of course, he couldn't grasp the demon king's huge forearms forever.
 soon cracks began to come out on the ice, which occurred in an instant.
 as a result, his four beams and five arms were disabled immediately.
kheeeeeeeeh!

 