\section{chapter 384}

chapter 384: war for war (1)“uh?”




“what the heck…”everyone was silent, staring at the message that appeared before their eyes.
checking the message, sungwoo also couldn’t control his frustrated expression.
[world message]- congratulations! among the players in the world, the ruler of the ‘hell’, the ‘demon king’ has been born!* ‘demon king’s fortress’ has been designated in the ‘world’.
 (location: amazon river basin of the brazilian server)“what the heck is this? demon king?”“didn’t we say that the brazilian server was ruined?”no one could hide their embarrassment.
 few among them knew about the demon king.
and no one other than sungwoo knew that the only player who became the demon king was kangsok han, the number 1 player in the korean server rankings.
 sungwoo couldn’t think straight at the sudden appearance of an unexpected variable.
‘as far as i know, this guy has been steadily moving on to achieve his goal.
 then why did he…’at that moment, jonathan jumped to his feet.
 he had the most serious expression among them.
“if i may say one thing, i don’t know what the demon king is, but the problem is that he has appeared in amazon, not any other place.
 that place is…”having said that, he looked at sungwoo.
sungwoo nodded, then said, “that’s where the dragon is…”
the unidentified guy who always rubbed sungwoo the wrong way began to plot something dangerous.
sungwoo had jonathan get in touch with the wpu in america.
since the wpu had been monitoring the amazon dragon for a long time, it was highly likely that they had more detailed information.
‘in the worst case, the wpu fleet here may try to return to defend their us continent.
”currently, the amazon dragon is in a “dormant” state, so the wpu could boldly dispatch a huge number of airships.
 however, given the current situation, there might be unexpected developments, so they might try to focus on defending the us mainland by summoning back the dispatched troops.
‘if they make a decision to withdraw their troops, i can’t stop them.
’sungwoo looked at inho.
reading an uneasy expression on his face, inho grabbed the microphone.
“ah, let’s take a 10-minute break then resume the meeting.
”their strategy meeting ended due to an unexpected situation.
sungwoo sat quietly in his seat, lost in thoughts.
‘demon king, hell, angels, and demons…’there were so many unsolved puzzles.
‘if the demon’s cave is a destroyed parallel world, what is the rest of the world? what about kangsok? what the heck is he doing now?’when sungwoo asked him about the demon king a long time ago, kangsok replied that the reason he wanted to be the demon king was that he wanted to build up an independent power so as not to be ruled by the world eater or angels and demons.
 then he disappeared after saying it vaguely.
 in other words, it was highly likely that kangsok knew something that ‘the really important question is whether he can help us protect our world or whether he will drive us into destruction.
 come to think of it, i still don’t know anything about him.
’
although he fought the enemy with kangsok several times, he could not trust kangsok blindly.
 but he was too strong to be ignored, but he was veiled so much.
while sungwoo was thinking about it, jonathan finally came back.
 everyone looked at him in silence, but his expression darkened even more.
“…”he sat down without a word and looked at sungwoo.
“our agent dispatched to south america has sent us some pieces of intelligence.
”when sungwoo nodded, jonathan continued, “a new quest has been issued in the area.
 again, this is a disaster quest.
”disaster quest.
according to chairman love, a disaster quest called [worst creature] was also issued before.
the gist of it was that the dragon that destroyed south america would wake up after 48 days of ‘dormancy’ and destroy north america.
“does it mean we have to anticipate another attack after the dragon’s attack?”“that’s right.
”then, jonathan explained the contents of the message that appeared before the south american informant’s eyes.
[disaster quest]- name: the two kings of the demon king castle- type: ‘war’ or ‘submission’- goal: unknown- reward: unknown*the ‘dragon’, which brought about disaster in south america, returned to his nest again and fell into a ‘dormant’ state.
 then, he met an unexpected guest, who was the ‘demon king’.
the demon king and the dragon formed an alliance and built the ‘demon king’s castle’ on the ‘dragon rare’.
 it became a passageway to ‘hell’ and began producing numerous ‘hell creatures.
’ after that, the two kings came up with an evil plan called ‘conquest of the world’.
 and they chose ‘north america’ as their first goal.
* a 14-day ‘war preparation period’ will be given.
 if you do not escape north america by then, you will be designated as a ‘target’ and you will have to choose between ‘war’ and ‘submission’.
after hearing that, sungwoo thought, ‘now it’s very clear that this guy is our enemy.
’sungwoo was convinced that the demon king was an enemy, and the commanders were embarrassed.
“demon king this time?”they were the ‘dragon’ and the ‘demon king.
’although they had never witnessed the two, they were often portrayed as the supreme rulers that could never be treated lightly in any fantasy.
“…”with a heavy silence going on, sungwoo recalled what kangsok had told him during their meetings until now.
‘i have to know what he wants first to be able to find out what he is going to do.
’of course, kangsok persistently hid his inner feelings and motivations, but sungwoo tried to trace anything that could help him find out kang’s motivations.
‘yeah, come to think of it, he never talked about his own survival.
 he acted as if he didn’t care about his life…’

since sungwoo moved for the purpose of survival, he joined hands with so many people and even now he was fighting to prevent the destruction of the world.
but it seemed that kangsok was acting solely for his own benefit as if he wasn’t interested in the survival or the destruction of the world.
 he only focused on getting stronger, as if he was playing a real rpg game.
that’s what made him different from sungwoo.
sungwoo thought to himself, ‘even though kangsok said he would fight to stop the invasion of the hell creatures and confront the world eater, angels and demons, it seemed he was doing it only to make himself stronger.
 why does he have to be strong at the risk of his life?’maybe the answer to his question was simple.
‘power and domination…’was he wary of the world eater or the absolute race because he, not them, was determined to rule this world?‘if i look at the emperor of the chinese server right now, his goal is to dominate the world.
 so, it’s no wonder that there are other people who share the emperor’s view.
 of course, kangsok doesn’t seem to be greedy about power only…’the emergence of those greedy for power in turbulent times was repeated throughout history.
‘anyway, the thing is this guy intends to act for his own interests, i think.
’when he solved the complex puzzles about kangsok’s motivations, sungwoo felt rather relieved.
‘if he is only concerned with dominating this world, i can solve the problem easily.
 all i have to do is think about defeating him from now on.
’while silence continued in the hall, sungwoo slowly raised his head.
 everyone was looking at him.
so he slowly opened his mouth.
“we’ve got nothing to change.
”

 