\section{chapter 166}

                            those monsters scattered to surround the building, the zombie monsters waiting in the rear and the cloth monsters in the trucks began to flock toward sungwoo and his party.
 they numbered over one hundred.





“everyone, withdraw from the necromancer!”obviously, these monsters would not rush en masse like that to kill sungwoo.
 sungwoo thought there must be the so-called “hitman’ among them, who aimed at cutting his windpipe.
finally, that monster appeared in front of sungwoo.
the werebull, a gray bull, came to the forefront.
“you guys, stop the undead.
 let me hunt the necromancer!”following his order, the monster troops began to close in on the undead.
 obviously, they tried to separate the undead from sungwoo, then attacked separately.
thump-thump-the werebull approached sungwoo.
“oh, necromancer…your style has changed a little.
”the monster spoke, blowing out through his nostrils.
 all kinds of tattoos were engraved on his body, which was particularly muscular.
 he was holding a wooden shield engraved with a goblin in one hand and a flail in the other hand.
“oh, werewolf? are you of the same race as us?” asked the werebull.
“how are wolves and cows like you of the same race?” sungwoo responded.
“we don’t divide our race, based on such a primitive concept.
 we have been born as human monsters and threw away the empty shells of humanity,” said the werebull.
sungwoo laughed it off and said, “since you are talking nonsense like that, you must be one of the four fake cult leaders.
”right after sungwoo ambushed the sindorim research center of the evolution society, there were human monsters called “four beasts” that he confirmed through the research director’s memory fragments.
the white wolf who used psychometry was one of them, and the pomade-haired man said that they were more powerful than player rankers.
“oh, you know us.
”“well, we have known each other for a long time, right?”the werebull blew out through his nostrils.

“as of today, our quest for each other will end.
 as you know, i am a ‘red flagman’, one of the so-called four beasts.
 i’ve come here to cut your windpipe.
”“flagman? is that your name?”“i threw away my old name, which was an empty shell of my life during human days.
”-‘evil spirit bomb’ is embedded in your weapon.
sungwoo confirmed that the cooldown was over, so he immediately loaded the evil spirit bomb.
 when a black spirit shrouded the grim reaper, the werebull was on alert.
boo-woooooong!sungwoo swung the grim reaper.
 the evil spirit bomb dropped, but the monster raised the shield engraved with a goblin.
 at the same time, he displayed the magical power of the shield and covered his body with a red shield.
goong― gugung―unfortunately, the evil spirit bomb was blocked.
“this is useless now.
”since the werebull was dispatched to kill the necromancer, he was armed with unusual items.
‘what a headache!’in fact, sungwoo had another big problem now.
-grim reaper retention time (00:12:33)-werewolf retention time (00:13:49)in other words, sungwoo could not afford to drag out this fight.
‘i’ve got to end this fight within ten minutes.
’at that moment, the werebull shouted, “hey, you can’t work things out as you expect, right? i can see it in your face.
”the werebull was ready to attack sungwoo.
 he closed in on sungwoo, wielding the huge flail in his right hand, which was twice as big as his head.

in fact, a long time ago the orc chief sungwoo had to deal with used a weapon like that.
it was dangerous because it constantly rotated, so it was hard to tell when and where it would fly toward him.
boo-wooooong-when he was dealing with the orc chief, sungwoo could easily defeat the monster because he had the resurrected skeletons charge at him recklessly.
‘i can’t use the undead now.
’as if the human monsters thought the best way to deal with the necromancer was a one-on-one fight, they were tenaciously attacking the undead group.
 so, he could not pull out a large number of them to help him out.
“why are you looking elsewhere now?”at that moment, werebull narrowed the distance and swung the flail.
sungwoo hurriedly lifted the grim reaper.
clang!the two giants collided in the air, shaking the playground.
now, the monster began to swing the flail at a faster speed.
booooooooong-boooooooog-booooog-“are you not confident? why are you trying to hide behind the undead all the time?”it seemed the werebull had the confidence to defeat the necromancer in a one-on-one battle.
“hey, because fighting in a cunning way is my fighting style.
”at that moment, the monster’s weapon turned into a purple chain then wrapped around the grim reaper.
 an unknown force pulled the grim reaper, and sungwoo slipped.
sungwoo’s repeating crossbow and hand cannon were drawn to the chain as if attracted by a magnet.
-your weapon has been locked by the ‘fighter’s shackles’.
 (5 minutes)sungwoo’s weapon was stuck on the ground, entangled with the werebull’s weapon.
and a purple chain icon emerged above it.
 it was literally “locked”.
“locked?”“huhhhhh! actually, i’m not the type who is fighting with a weapon.
”then, the monster threw the shield and approached, turning his neck and wrists.
 something like a red wave appeared in his hands.
 in the beginning, this monster’s job was fighting.
now, the monster stretched out his forefoot and threw his left fist.
it was a jab.
 sungwoo quickly stepped back, but the monster stepped forward, throwing a right-hand straight jab and right-foot middle kick.
puck!sungwoo allowed his middle kick.
 he felt a shock that seemed to break his ribs.
 he was thrown into the air before falling and rolling across the playground.
then, the monster rushed at him, shaking the ground, but sungwoo stood up straight and avoided his punch.
 however, the monster grabbed sungwoo’s neck with his left hand and threw him down on the ground.
 a tremendous shock came up the spine.
“hey, great necromancer, the hero of the korean server! but now you don’t have your subordinate spirits or weapons.
 what’s left?”sungwoo barely raised himself with his hand on the ground.
 as if he seized the moment to win, the monster threw a punch with a smile.
 if hit accurately, sungwoo’s head would have been ripped apart.
sungwoo wrapped his fist with his palm.
“uh?”the monster could not move his fist.
 besides, sungwoo’s grip began to crush his fist like a hydraulic press, twisting his fingers.
“argh! how come your power is…”confusion spread across his face.
 he couldn’t believe it.
 there was a ridiculous situation unfolding at the moment.
 as a werebull with a high muscle strength level, he was being held by sungwoo of the wizard type and could not move at all.
“without your subordinate spirits and weapons, how can you fight me like this?”“why are you thinking one-dimensional? don’t you think that my subordinate spirits and weapons gave me overwhelming stats?”

“what the heck?”sungwoo’s muscle strength value was 52.
 in addition to that, he could exert a much stronger grip when he added the correction effect he gained while turning into a human beast.
 besides, he obtained the “godly stature,” which reduced the stats of those nearby.
even though sungwoo didn’t have fighting skills, he could overpower werebull.
at that moment, sungwoo’s right fist struck the monster’s ribs.
“kuuuuuuuuh!”hit by sungwoo’s body blow, the monster staggered.
 his punch was so devastating the monster’s intestines ruptured.
sungwoo continued to throw punches, crushing his ribs.
 a groan burst out of his mouth.
 eventually, the monster kneeled, unable to withstand sungwoo’s mighty punch.
at that moment, the monster thrust the huge horns on his head, aiming at sungwoo’s stomach, so sungwoo had no choice but to move back, letting go of his hand.
“it’s not over yet.
 i’ve prepared a hidden card for this fight,” shouted the monster.
the monster stepped back and pulled something from his waist.
as expected, it was an ampoule, his main specialty.
 then, he took out a syringe and injected it into his thigh.
“ugh!”his body began to swell.
 his bones and his muscles grew.
 his nails turned long and hard.
 and the horns on his head began to grow rapidly.
“kaaaaaaaaaaaah!”his screaming resonated.
 the ground he was standing on shook, making a crater in the shape of his hoof.
he opened his red eyes slowly under his huge horns, letting out a hot breath.
“necromancer… you are done now.
”but sungwoo smiled slightly, looking at him.
“i think i can obtain nice bones.
”

 