\section{chapter 245}

                            pushee―




gas was ejected from six exhaust vents of the innermost wall.
 as if the engine seemed to be getting hotter, the gas jet cycle started to shorten.
as a result, the machines on the ceiling and walls moved faster and faster.
ooh ooh ooh-the whole cavity was a huge machine.
dr.
 yu’s body was pulled by the cables and soared gradually.
 soon, he reached the ceiling.
weeeeeeeeeeng-a square capsule protruded from the ceiling.
 dr.
 yu went into it.
 then, white patterns began to emerge around the capsule.
sungwoo immediately noticed what it was.
‘it’s divine magic.
’the number of patterns was a whopping 22.
 he hid inside a device with divine magic, so sunngwoo couldn’t attack him directly.
tung!also, the entrance to the corridor, where sungwoo and minsok walked in, closed by itself.
 and dozens of divine magic were cast there.
“you guys can’t get out of here anymore.
”dr.
 yu’s voice rang above their heads.
 speakers on the wall resonated with his voice throughout the cavity.
“necromancer, if you have the undead, i have dolls.
 now, let’s play soldiers.
”what he meant by the dolls seemed to refer to the players hanging on the crane.
how could he hang them in such a state that they couldn’t even die, then call them dolls?this was something only this man, nicknamed ‘mad scientist’, could do.
a quest message appeared before sungwoo’s eyes as if the players who were treated as dolls appealed to him.
[exclusive quest]-title: for rest in peace-type: rescue
-goal: deliver death to those who cannot die-reward: exclusive skill*you witnessed a terrible scene.
 you have seen those who, deceived by the evil spirits, can’t die, suffering eternal pain.
 they can feel everything, even though they can’t scream.
death is not anyone’s right.
 however, some death may be the only escape from tragedy.
 you can give them a way out and a resting place.
* we must provide rest to all those who cannot die (total 240 people)* your choice affects your ‘destiny’.
sungwoo now understood why such a quest was issued.
in the meantime, dr.
 yu was moving them here and there after hanging the players with only their upper bodies on a line.
twelve cranes moved up, down, left, and right to select different positions.
warriors with spears and shields were in the front, shooters with bows and crossbows were in the middle, and priests and wizards in the rear.
the sight was bizarre, but it was no different from a normal battle formation.
“damn it.
 i really can’t bear seeing this cruel scene.
 if they use magic at the same time, it will deal a fatal blow.
 in particular, the priests in the rear seem to be very dangerous,” said minsok.
“yes.
 be careful, minsok!” said sungwoo.
no matter how powerful they were, sungwoo and minsok had to be wary so as not to be directly hit by a series of divine magic with the opposite trait of ‘death.
’‘there are a total of 240 people hanging on the crane.
’considering the players sungwoo had dealt with until now, he had no problem with smashing the 240 players here.
‘but they are not ordinary 240 players.
’the “dolls” dr.
 yu controlled were different.
 since he regarded his battle with sungwoo as the last one, he probably mobilized all his resources to make them strong.
‘i can see many of the shooters in the middle with silver arrowheads.
’sungwoo has already experienced fighting against them several times.
 the silver arrowheads were weapons that made the undead impossible to resurrect.
of course, as it was quite difficult to produce them, not all the players were armed with them, but they were the forces sungwoo had to be most concerned with.
“watch out for snipers, especially the silver arrows.
”“oh, i know what they are.
 understood.
”
moreover, the army controlled by one man was more efficient than anything else.
because they had no emotion, they could be operated as a program without any delay.
sungwoo knew it better than anybody else.
“let’s get ready.
”sungwoo also prepared an all-out war.
– caution! the ‘fellblade’ begins in that area.
– caution! ‘death response’ begins in that area.
– caution! ‘shadow legion’ will gather up in that area.
as always, everything started with black smoke erupting from behind him.
rattle! rattle!the undead legion walked out of it and lined up behind sungwoo.
 he could increase the undead army by double.
tsutsutsutsutsu―the shadows cast on the floor wriggled immediately and raised themselves.
 then, they filled the gaps between the undead, completing the necromancer’s total power.
“here’s one more thing.
”sungwoo then prepared a new skill that he acquired a while ago.
[skill information]-name: appointed death wizard-grade: basic-category: active-consumption: 50 mana*when you raise a skeleton, this skill gives you ‘magical talent’ to make it a ‘skeleton mage’.
 (maximum 5 skeleton mages)skeleton mage can use several attack magic spells and curse type magic spells, and it will use more powerful magic when the skill is upgraded.
* skeleton mage can become a ‘death priest’ if it meets ‘specific conditions’.
* skeleton mage can become ‘lich’ if it satisfies ‘specific conditions’.
it was a skill that would supplement the subordinate spirits of the ‘wizard’ series,” which sungwoon didn’t have until now.
 based on this, sungwoo was going to diversify his tactics.
sungwoo immediately used the skill on one werewolf skeleton.
-you have appointed him as the ‘death wizard’.
* because the target’s intellect is weak, the skill of ‘basic grade’ is given.
 (the possibility of upgrading is slim.
)there was a green light coming from the werewolf skeleton’s grasp.
 he could use magic in an instant.
 however, one of the system messages was somewhat annoying to sungwoo.
‘·intellect? the possibility of upgrading it is dim?’the fact that the skeleton could use magic alone was encouraging, but sungwoo could not make light of the skeleton’s low intellect.
‘the power of magic is particularly different, depending on the level of the user’s intellect.
 if intellect affects the level of magic…’so, sungwoo appointed minsok, who was standing next to him, as a “death wizard” this time.
-you have appointed him as the ‘death wizard’.
* due to the superior intellect of the target, a ‘professional level’ skill is given.
 (there is a very high possibility of upgrading.
)as expected, a much higher grade skill was given to minsok, unlike the werewolf skeleton.
“uh? suddenly, i have multiple magic skills, right?”minsok looked down at his hand and looked embarrassed.
 he was a knight-type profession, but he suddenly obtained several magic powers.
but that wasn’t all.
-new skills are given in connection with the target’s existing profession card (death knight).
[skill information]-name: black magic sword-grade: professional-category: passive-consumption: none

-inject mana into a weapon to ‘enhance’ it.
 (+110%) also inflicts a ‘confusion’ curse on the attacked enemy.
 each time the skill is upgraded, the ‘enhancement effect’ increases dramatically.
the addition of the wizard job group to his knight job group enabled minsok to be a ‘magic swordsman.
’“oh, i just got another good one!”“i know this is the first time you are using magic, so use it by learning it well.
”minsok lifted his shield and sword, showing his confidence.
“okay.
 i know how to because i studied hard when i attended school.
”sungwoo and minsok were ready for the battle.
the two grabbed their weapons and looked up at the ceiling.
 dr.
 yu was also looking down at them from inside the capsule.
“…”but neither of them moved first.
 it was like a big battle.
 with both sides facing each other on a huge battlefield, they were waiting for the right time to attack because they knew the other was not easy prey.
 the moment one of them showed any weakness, the other party would seize the chance to attack and defeat them right away.
with both sides keeping silent, some wind that came from somewhere was blowing through the cavity.
 the wind was blowing among the bones of the skeletons, making an eerie sound.
“shall we hit them first?”“well, for a moment….
”however, something unexpected took place out of nowhere.
a roaring sound was heard from the doorway sealed with divine magic behind sungwoo.
“what the heck is that?”dr.
 yu also seemed embarrassed by the unexpected situation.
clang! clang!something was hitting the iron gate hard.
 the wall around the door shook in a small shock.
had it not been sealed with divine magic, it would have been broken apart much earlier.
bang!soon, the door was torn out.
 with the led lights in the hallway behind, a shadow walked out.
“ah, jisu!”

 