\section{chapter 227}

                             




-a camp quest (special) has been issued.
[camp quest (special)]-title: take glory in the chaos-type: assassination-goal: assassinate kor-157-reward: rank score*after the war between the korean-japanese servers broke out, the korean server fell into great chaos.
 chaos provides an opportunity for you to boldly cut out the rotten parts.
 take order and draw your sword.
* in case of non-compliance, your ‘rank score’ will be reduced.
 (if your non-compliance is repeated, you may be excluded from various camp benefits.
)“damn it…”frowning at the message, junghoon stared at the angel statue hidden in the deepest part of yeongdeungpo station.
the angel statue with four wings was one cut above other angel statues.
 therefore, junghoon expected to receive a higher level quest than this, but the quest didn’t take its eyes off kor-157, namely sungwoo.
this quest wasn’t helpful to junghoon’s purpose at all.
“maybe what sungwoo said back then was…”he recalled what sungwoo had told him on the day he destroyed the first angel statue, expressing what he felt frankly.
junghoon began to feel at some point that the names of the absolute races were a shackle.
***the last bastion of the hwarang guild was inside a university campus in downtown busan.

of course, unlike the general campus, it was filled with iron gates made of magic metal and barbed wires.
 the hwarang guild built it as a temporary shelter in case of an emergency.
that’s why they could hold out there until now.
bang! bang!an ear-splitting roar was ringing across the campus.
 it was the noise of invaders tearing through the front door that served as a protective shield, made of magic metal.
“we can’t hold out here anymore.
 they’re closing in on us from all directions.
”somebody brought tragic news to the commanding post set up at the university headquarters.
since they already suffered so much damage, they could no longer resist the enemy’s attack.
 almost half of the guild members could not play their role properly after taking in the ‘breath of abyss.
’“if our leader hyunmin had not collapsed helplessly, we could have broken through the enemy line…’their leader hyunmin jang was killed by the japanese sword master akira in the one-on-one fight, so their morale was completely broken after that duel.
they couldn’t open their mouths, their expressions were somber for a while.
 there was no hero nor hope for those who were left behind.
one of the ranking members of the hwarang guild came up with an idea.
“if we can hold out a little longer, we will have the chance to choose the ‘next option.
’ it’s our turn to choose it, so let’s try to flee during the breathing time right after choosing the type of fight.
”what he suggested was to seek the chance to retreat by making use of the loophole in the rules of the korean-japanese war, for another fight was prohibited while the ‘duel’ was going on.
“can we escape during that time? isn’t it too short…”“well, don’t you think that’s the only way for now?”they eventually devised an escape plan which was close to suicide.
somebody came in with an urgent message.
“man, we’re in big trouble!”
“what happened this time?”to try that plan, they had to hold out until they would choose the next option, but it seemed almost impossible to carry out such a plan.
“they already tore down the front door shield!”massive pieces of metal debris fell over the campus, breaking down the walls before being dumped in a parking lot.
“they are now intruding onto the campus!”they could not stop the enemies.
 when hundreds of heavily armed assault troops stormed like a herd of water buffalo, the security guards at the front door were destroyed in an instant.
“we’re going to be killed!”“yeah, you’re right… we have done our best.
”the remaining hwarang guild members had no choice but to give up, staring blankly at the hundreds of intruders outside the window.
“damn it.
 i feel so ashamed to be killed like this…” one of them muttered.
however, his lament did not fit the situation.
 how could he say he felt ashamed, not scared, in this precarious moment?“what do you mean?”the man responded, his face filled with anger, “what i mean is the whole world must have watched the japs destroying us when we could not counter-attack them.
 that makes me ashamed.
”“i agree.
”“besides, our leader was killed.
 maybe foreign players were thrilled to see this.
 god damn ninjas and samurai!”he was very unhappy the hwarang guild lost to japan in the korean-japanese server wars.
 as he said, the official channel, which was currently being watched by 10 million people, was overflowing with comments posted by those deeply immersed in ‘japanese fantasy’ figures such as ninjas and samurai.
he could not do anything other than lament about the miserable situation the hwarang guild was in.
“what’s the point of complaining about our weakness?”that was the right answer to their current problem.
“damned bastards! my grandfather also died under japanese colonial rule, but i have never thought i would also be killed by japs.
 i wish lightning would fall over their heads.
”at that moment, a stroke of lightning fell.
kwagwagwagwagwa-dozens of arrows rained down on the hundreds of japanese intruders walking up to them through the road leading to the main gate they broke through.
 they were not ordinary arrows.
 instead, they were like iron thunderbolts, full of magical power.
“damn it! what the heck is all this?”the japanese troops were embarrassed by the unexpected arrow attacks, but they suffered little damage thanks to their heavy armor.
 however, they had to stop and tightened their security.
“is this a trap?”“lift your shield! it’s just an arrow!”in the next moment, there was a spate of arrows flying at them again.
puck! puck! puck!dozens of arrows exploded like dynamite and swept over them.
 this time the arrows caused much more damage to them because they were stuck in their shields and armor.
 some of them exploded under their feet.
“argh!”“help! ahhhhhhhh!”the japanese troops, who had entered the gate triumphantly, stopped.
“what happened?”“what’s up? it’s not our attack, right?”it was somebody’s counterattack that even the hwarang guild did not know about because they had already given up fighting.


the hwarang guild members turned their heads and started looking for the place the arrows came from.
 soon, they discovered something was moving on the rooftop of a university building.
“that’s…”it was the fire rocket arrow.
a pair of giant wings spread across the sky, with a bone-made monster raising its long neck.
 a monster arose on the battlefield.
 black smoke rose from its back, and soon, dozens of bone wyverns poured out and scattered in a fan shape toward the sky.
 the sun disappeared in seconds.
it was natural the eyes of the players around the world became fixated on the scene.
at the same time, there was a moment of silence.
“wow, he’s here!”“that man has come to save us!”what’s more, there were some other powerful weapons such as two iron maces of lightning and five ballistas.
the bone wyverns darkened the ground with their wings, while the fixed turrets were pulled tightly behind their backs.
“everybody, get ready to shoot!”suddenly, dozens of players, who appeared from all over the rooftops, began to aim repeating crossbows toward the incoming japanese intruders.
-your body functions are weakened due to unknown energy.
* all stats decrease.
 (-3)with every turret being pulled tight, someone raised himself above the head of the massive monster, bone wyvern alpha male, that blocked the sunlight from reaching the ground.
he was wearing a dark green robe, holding a giant scythe, and looked like a black wolf.
his figure was familiar to the korean server players, but it was unknown and bizarre to the world.
the next moment, korean players who had been quiet for a while on the official channel’s chat window began to get thrilled and upload posts one after the other.
they said that the main unit of the korean server finally arrived in busan and the japanese intruders were finished.


 