\section{chapter 33}






 “three orcs.
”“i saw them too.
”jisu pulled out her sword.
when sungwoo raised his head and checked them, the three orcs were resting at the entrance to the b compound.
one of them was wearing a bunch of colorful clothespins as a necklace, which seemed to look cool to them.
“there might be more around.
 as this place is rather complex, you never know where they will pop out.
 let me ambush them with five skeletons, so both of you take care of the rear with the other four skeletons!” sungwoo said.
then he took out a one-handed spear that he had tied to the orc skeleton’s bag.
 it was an item he obtained from the h apartments gang members.
“let’s go.
”at his order, the skeletons moved in an organized way.
the three orcs, sensing human movement, raised their heads and looked over.
puk!at that moment, sungwoo stabbed the spear into one of their necks.
when one fell, the other two threw their bodies to escape the flying daggers and picked up the axes placed at the wall.
but they also fell onto the cold floor because right circled the building and ambushed from behind.
 it was a perfect raid close to an assassination.
“it’s their habit not to look back.
”sungwoo always pursued the most effective battle method like this.
“wow, they were killed instantly… there’s no more human movement nearby,” said jisu.

hanho hurried into the b compound.
 he was impatient.
“ah?”the narrow corridor was unexpectedly neat and clear.
 as if the front doors of apartment 101 and 102 were forcibly opened, traces of the axes were clearly visible, while the thick iron gates were completely crushed.
while passing by the door for a moment, the house reeked of blood.
hanho impatiently jumped up the stairs, but sungwoo followed and stopped him by grabbing his shoulders.
“hey, hey! calm down.
 how can you walk up like that when you don’t know if the monsters will pop out over your head?”“…whew! we’re almost there.
”hanho’s house was upstairs, room 202.
 it was already a mess with the traces of axes.
fortunately, the door was not opened, unlike the first floor.
with a ray of hope, hanho entered the door lock password with his trembling finger.
t-t-t-t-t-t-t-trring!when he opened the front door, it was still locked, a very good sign.
hanho looked into the house through the gap.
 and then he found someone.
“ugh? mom! open the door!”soon, a middle-aged woman opened the door.
 she was hanho’s mother.
“hanho!”“what? what did you say now? hanho is here?”
shortly afterwards, hanho’s father rushed to him.
 finding them safe, hanho breathed a sigh of relief.
***“hey, mom.
 i can understand you, but i wonder why dad didn’t draw a card when he liked playing the go-stop game so much.
 it looks like he lost his senses after playing go-stop a lot,” hanho said while chewing on egg rolls.
sungwoo and jisu were eating lunch served by hanho’s mother.
 as the food hadn’t yet run out at hanho’s house, they enjoyed the taste of home-cooked meals.
“hmm, i don’t like the pictures on the card, so i didn’t choose it.
”“with his pocket full of coins, dad went out somewhere and came back every day.
 by the way, the orcs smashed the front door.
 how did you stop them?”“well, i sprayed f killer.
”“…what? pesticide?”“yeah, when your father kept spraying it through the gap, the orcs ran away.
”3it was an absurd but effective method to repel the orcs.
even after the meal, hanho’s mother expressed her gratitude to sungwoo and jisu and provided all kinds of snacks.
“sungwoo and jisu, thank you so much for bringing him here.
 oh, i don’t have drinks like cocoa, but i’ve green tea.
”“no.
 thank you.
”but hanho quickly intervened, a bit upset.
“oh, mom! i also helped them.
 i forced my way here, knocking down all the monsters.
 i’m serious!”“can you shut your mouth, son?”5hanho’s parents said they thought that hanho helplessly died somewhere on the street.
 so, they never expected that he would come back home alone after a long journey like this.
“the boiler is off, so it’s cold water, but it’s still coming out.
 so, wash and relax.
”they relaxed as much as possible in hanho’s house.
 they had home-cooked meals after not having them for a long time and took a shower.
 jisu could finally wash her blood-stained red sweatpants.
 as if she felt attached to the clothes, she declined hanho’s offer to give her another set.
“oh, no thanks.
 but i’m just going to wash this one and wear it.
 i like these sweatpants because they were not visible even with the blood stains.
 whew! i feel much better because above all, i can wash my clothes.
”however, they couldn’t afford to stay any longer.
 so, the three of them sat in hanho’s room and pondered over what to do in the future.
“sungwoo, what do you think? it’s unreasonable to stick it out here, right?”“let’s set the destination before moving.
 the orcs we killed at the entrance were the scouts.
 if there are a bunch of orcs nearby, they could launch a large scale attack on us.
”the problem was that they didn’t know where to go from now on.
their first goal was to escape from campus, and their next goal was to get to hanho’s house.
as they had no long-term goal, they often found themselves feeling vague about it.
at that moment, hanho, who was monitoring the bulletin comments in the community, brought up a piece of news.
“sungwoo, look at this.
”“hey, you’re hooked on sns, even now!”sungwoo noticed him focusing on his cell phone even in classes, and rebuked him several times, but hanho never cared.
“dang it, it doesn’t matter now.
 you know that youngdungpo prosecutor, the guy who posted a second thread yesterday so others could post their comments freely, right?”“yea.
 why?”“the man commented again.
 just read it.
”[3] survivors in youngdungpo must read! i’ve secured a safe zone!

-author: youngdungpo prosecutor │ views: 45,499i’ve prepared a safety zone in youngdungpo.
 there is a lot of controversy over the first thread, but i mean it.
 among my colleagues, i know a guy with a three-star job card called ‘pioneer’, and he can use his exclusive skills to turn the interior of youngdungpo station into a zone where monsters cannot enter.
 he can’t accommodate everyone, but right now he is recruiting the first members to go with him.
 because it costs a lot to maintain the skill, you will receive gold or food once you enter the zone.
 please understand that this is an inevitable choice for the survival of all the members.
comments: 45 again, an issue about the safety zone.
“can i believe it this time? this guy really looks like a good person.
”2“well, that’s why he posted a thread yesterday.
”“pardon?”“it wasn’t unconditional.
 this was his purpose?”it might be true that ‘youngdungpo prosecutor’ said that he prepared a real safety zone.
sungwoo also thought it was highly likely that he did so because it was definitely a game with all kinds of jobs and skills.
 but he thought that the man’s decision to donate 1,000 gold and create an environment where others could freely comment was not necessarily made in good faith.
“look at the comments.
 this guy yesterday has already gained credibility because of his thread yesterday.
”comments: 46― dash tanker: after all, kudos to ‘youngdungpo prosecutor! thank you for the really good information again! our party has been with puchon, but we decided to switch to youngdungpo!see you in person then.
^^― two-star monk mr.
 kim: i trust you! i will follow you!― heejin yang: youngdungpo prosecutor! what is your real occupation? will you save us from this crazy world? i really didn’t want to use 100 gold, but let me leave a comment like this.
those were the comments that hanho showed to sungwoo.
“all the comments are praising the guy.
 in fact, there were a lot of thank-you comments on his thread yesterday.
 anyway, he’s going to be popular among them.
”

 