\section{chapter 207}

                             




the man called euijin took something out of his backpack.
it was rolled paper, and it looked like korean paper.
“alright.
 come on! i have prepared an item to deal with an annoying intruder like you.
”euijin approached her and unwrapped the rolled picture, revealing the scenery of the mountains painted with ink.
-‘the divine real landscape painting’ has been activated!at that moment, ink spewed out of the painting.
 then, it moved as if it was alive and stretched out toward jisu.
“what the heck is this?”when jisu responded, she could not get out of it.
“ugh!”in no time its ink sprayed all over her body.
 although she swung her sword, it was useless like cutting through water.
 eventually, she was dragged by the ink and sucked into the painting.
 the painting fluttered where she disappeared.
“done!”“good!”it wasn’t an item that could kill somebody.
 its effect was to send a specific target to a distant space, more precisely, somewhere in mt.
 taebaek.
however, that attack alone could significantly weaken the necromancer’s power.
since jisu, who was almost like his personal bodyguard, was separated from him on the battlefield, the chances of sniping the necromancer increased twice as much.
“we’ll prevail even after repeated defeats.
 get ready for the attack!”when bumyol shouted, the warriors who were positioned among the trees came to their senses.
 they held their weapons and stared at their enemy in front, the necromancer.
“attack the necromancer!”“let’s go!”“kill him!”with thundering shouts, the warriors of mt.
 taebaek rushed toward the necromancer.
“…”
watching them charging at him, sungwoo threw down the bone shield with dozens of arrows stuck on it.
 there was faint anger on his face.
“i have warned you many times…”a green flame from the corners of his eyes spread over his body.
 then, a huge black sickle appeared.
 the moment he grabbed it, black hair began to grow on his body.
-an unknown energy is spreading to the whole area.
with the appearance of a black wolf, anubis, appeared.
-bodily functions are weakened due to unknown energy.
* all stats decrease.
 (-1)when sungwoo became a deity, this message appeared before the eyes of all the players standing nearby.
“damn it!”“what the heck is this…”the warriors of mt.
 taebaek flinched at the black wolf, suddenly slowing down.
“don’t be scared!”“wait for him to summon the undead!”they have seen the necromancer’s combat style several times.
 they knew he could summon undead troops with black smoke anytime, anywhere.
“it’s dangerous if you get close to him carelessly!”“close in on him slowly!”therefore, they tried to surround the necromancer by spreading around him instead of colliding with him recklessly.
they seemed to think the snipers would deal a fatal blow to him while they were distracting him.
at that moment, the necromancer opened his mouth.
“this is my last warning!”gu gu gu gu―as soon as he said that, there was an unknown vibration in the forest.
 in the distance, trees were broken and a flock of birds soared.
 it was an unusual phenomenon.

“…”everyone turned their eyes in that direction, and even the cameraman started filming there.
there was something huge coming toward them.
soon, the trees were split and some monster revealed itself.
“ahhhhhhhh!!”“well, what the heck is that monster?”it was the giant serpent called imoogi, the owner of mt.
 pukhan dungeon.
 a huge creature made of bones came out of the forest.
its long body, dozens of meters long, struck the demon camp.
“as of today, there is no demon camp on the korean server.
”a tree was broken entirely, and a huge creature appeared.
 it was as if the bank burst and the river was pouring out.
as such, this ‘bone imoogi’ was different in size from other huge undead that sungwoo had acquired.
“what the hell is that?”“so big!”the size of the serpent’s skull was no different from that of bone drake, but it was overwhelmingly long.
it was about 30 meters long excluding its head, which was thicker and longer than the sea serpent sungwoo had used to attack the pirates’ container ship.
because of its huge body, the serpent could easily devastate the whole area by wriggling only once.
“avoid the monster!”“ahhhh!”the demon camp troops who were besieging the necromancer while preparing for the emergence of the undead troops never expected such a huge monster would pop out of the forest.
the self-proclaimed “mountain warriors” collapsed miserably after they were swept back and forth by the dynamic movements of bone imoogi.
“ahhhhh!”“beat it!”“too late!”no matter how well-organized they were, they couldn’t avoid the oncoming train.
 bone imoogi’s attack had much more destructive power than they thought.
lots of the demon camp soldiers were ripped apart by the imoogi’s attack.
 some of them were laid under the heavy weight of the giant serpent and crushed to death.
-you have earned 9,000 gold by killing a player-you have earned 12,000 gold by killing a player-you have earned 14,000 gold by killing a playerbone imoogi passed through the demon camp and disappeared into the other forest.
since its body was so huge, even turning in the other direction was quite a difficult task for the serpent.
a long ditch was dug along the road the serpent passed.
 there were numerous bodies buried underneath it.
rattle! rattle!in the meantime, other undead appeared, including bone drake and ogre skeleton, and surrounded the necromancer.
“damn it! the serpent disappeared!”“everybody, line up! secure the space to target the necromancer while keeping the undead in check!”“don’t be scared! you only need to kill the necromancer!”as they were determined to target the necromancer, they tried to find the right moment to attack him.
 while watching the numerous battles involving the necromancer, they realized that it was meaningless to destroy the undead troops.
 they wanted to get rid of the necromancer controlling the undead.
sungwoo looked around the demon camp while hiding himself among the troll skeletons.
‘the arrow they used a little while ago is similar to the item used by the evolution society in pyeongtaek.
’the undead hit by the arrows containing divine power could not resurrect, which meant they could inflict fatal damage on sungwoo.
‘only jisu could detect the arrows.
 it is difficult to avoid the arrows unless i find out the location of the guy firing such arrows.
’sungwoo gained a supernatural sense after turning into the status of anubis, but it was difficult for him to accurately detect the divine arrows in question.
besides, it was almost impossible to distinguish a few specific shots with divine power from the hundreds of arrows they were firing.
of course, if the necromancer let down his guard, he could be fatally hit by the arrows.


‘i don’t know how many they have of such arrows, but they probably do not have many.
’at first, they only fired two arrows, but no more after that.
in other words, it was clear they had only a few chances to use such arrows.
 that’s why they were looking for the perfect moment to attack the necromancer.
“sungwoo, should we keep hiding like this? by the way, what happened to jisu?”jisu disappeared somewhere when they used an unknown item.
 sungwoo felt once again how helpful she was in fighting off the enemies.
“by the way, that arrow was weird.
 i felt like i would be killed if i was hit.
”“well, we should find out who is firing such arrows.
”“how?”it wasn’t sungwoo, but the demon camp troops who got impatient.
 the more impatient they were, the more likely they would fire the divine arrows at the wrong moment.
so, sungwoo planned to make them misjudge.
“keep the defense line behind the tree!”“scouts, check out imoogi’s approach and report back to me!”although the cooldown of his major skills such as “fellblade” and “death response” was not over yet, each of the necromancer’s undead had formidable power.
besides, they were not sure when imoogi, which disappeared into the forest on the other side, could come back and disturb the ranks of the demon camp.
therefore, the demon camp got more and more impatient, preparing for the necromancer and imoogi’s attack.
“come on, it’s time you guys came out…”kate kim, the sniper belonging to the struggle guild, was watching the battlefield, while he was curled up on a tree.
as a member of the high school archery department, she immigrated to canada to compete on the professional archery team, so she knew everything depended on the tip of her arrows.
“let me kill you right away, so come on!”her first couple of shots were perfect, but a woman with tremendous senses ruined everything.
but now, that woman was not here.
‘when another opportunity comes along again, let me hit him on the spot.
”

 