\section{chapter 337}

chapter 337: jeju island and attack on demon’s cave (1)“necromancer, have you, too, entered the gate of the demon’s cave?”




when sungwoo gathered important figures around him and mentioned his operation about attacking the demon’s cave, that’s the question li wei asked him.
sungwoo looked at her curiously, thinking to himself, ‘she is asking me now?’so, he asked back, “then, have you been there?”“yep.
 i was almost killed there.
”he inquired about her experience.
 it was clear that her experience could be helpful to carry out his operation.
she said, “um.
 a few days ago, i infiltrated beijing to rescue the spirits captured by the emperor but ended up being isolated.
 i was completely surrounded, and i was on the verge of being killed helplessly, but i ran into the gate of the demon’s cave opened by the enemy.
 gosh…it was really crazy.
”actually, sungwoo witnessed lots of gates of the demon’s cave open in downtown beijing.
“so, you’re going to attack them from now on? well, i don’t have to tell you that killing the bees that come out of a hive is different from putting your hand into a hive, right?”“so, what does it look like?”li wei pretended to cut her throat and said, “it’s the right place for you to be killed.
 except for the ruins, there is nothing like ecology except for monsters there, and you really can’t figure out where you are once you are inside.
 what’s important is this.
”she then lifted her hand with which she cut her throat, then covered one of her eyes with her palm.
“it’s dark and sandy.
 there is no way of checking your direction… it’s almost like a labyrinth.
 it might be easy to get inside, but it’s hard to get out.
”“how did you escape?”
she shook her head at his question, then said, “well, it wasn’t because i was good enough that i could escape.
 it was then that i summoned the ‘spirit king’.
 and by using the skill he possessed called ‘eye of the world’, i could barely escape.
”“eye of the world?”“well, how should i describe it? oh, it’s kind of a ‘mini-map,’ so it can help you figure out the direction even if you can’t see anything.
”the mini-map was a kind of navigation-like concept within the game.
 it was natural that she could find a way out of the cave if she had that skill.
li wei complained that after she escaped, she was infused with the ‘damned god,’ and went back into general xing’s residence.
“can you summon that spirit king again?”she said, shaking her head, “i’m sorry, but i can’t.
 it requires very tough conditions.
 besides, i’m waiting for its 30-day cooldown right now.
 until then, i can’t summon him.
”after that, there was a brief silence between them.
 both were frustrated.
‘mini-map? did anyone have such a navigation skill among players?’there was none with that skill among the players that sungwoo knew.
such a skill itself was very rare, and even if it was, it would be very disadvantageous for survival because it was not very useful in a modern city center where regional divisions were clear.
‘it’s unreasonable for me to go into the cave recklessly.
’as li wei said, killing the bees crawling out of a hive was different from putting one’s hand into the hive.
 in particular, if he could not figure out the direction at all inside the cave, he would not be able to clear the quest.
 besides, this quest had to be cleared within a certain time.

‘if you do not destroy the heart of the demon’s cave within 48 hours of entering it, you will face resistance from the demon’s cave itself.
’at that moment, someone shouted, “i know one person with such ability.
”it was the white wolf who said that.
 everyone turned their eyes to him.
he looked at sungwoo and said, “but he is not a player.
”“then, is it a human monster?”the white wolf nodded and said, “the shameful old nickname, the first of the four human beasts, can use the ability of ‘predator’s realm’.
”come to think of it, sungwoo once met the last one of those four human beast leaders.
“he might not be as good as the spirit king, but he can detect anything within a certain radius.
 perhaps if he serves as a navigator, you can find the heart of the demon’s cave more quickly.
”“where is he now?”when he asked, the white wolf said, letting out a long sigh, “he is on jeju island.
 that’s all i know…”sungwoo didn’t have enough time to carry out his operation, but he had more and more work to do.
“i think i have to go to jeju island.
”that’s the only way he could solve the problem for now.
***the alliance between the evolution society and the human beasts allegedly started on equal footing, but their relationship was lopsided for a long time.
 in other words, the evolution society used not only the human beasts but also used them as experiment subjects.
at that time, the leaders of the human beasts called ‘four human beasts,’ resisted in order to be freed from dr.
 yu’s grip but failed, which sungwoo had already witnessed.
“dr.
 yu was trying to make us his slaves.
 the first victim was our leader, called the ‘black lion’.
 although he was seriously injured, i helped him escape to jeju island.
”“did you lost contact with him after that?”the white wolf nodded.
sungwoo asked again, just in case, “didn’t he die after that?”“no, he didn’t.
 i think he’s just disappointed in himself.
 he thought he was responsible for the killing of his people by joining hands with the evolution society.
 that’s why he did not want to appear before us.
”“if there is a way you can contact him, let him know that it is time to wash his sins away.
”“yeah, i’ll do so if i can contact him.
 if i go to the mountain hut in the middle of mt.
 halla where i last met him, i’ll be able to trace my memory of the various things left out there and chase him in one way or another.
”fortunately, the white wolf had a clue about the human beast’s whereabouts.
using his psychometric abilities, it would not be difficult for him to follow in the footsteps of a specific person.
meanwhile, the world tree’s fleet finished preparing for the upcoming war.


sungwoo stood up and said, “we’ve got only three days left until the war.
”from now on, there would be 36 hours of waiting time up to the ‘selection of counterattack’, 12 hours up to the ‘selection of event and place’, and finally 24 hours of waiting time up to the start of the war.
 if sungwoo couldn’t take the action until that time, the chinese server would take back the ‘initiative’ to control the war.
“i have to finish everything until then.
”he had to destroy the heart of the demon’s cave and achieve level 25 within three days.
otherwise, he had no chance of winning the war.
“we’re all done preparing for the war.
”after he was briefed by kyugnsoo, sungwoo got on the messenger, the flagship of the world water fleet, along with hanho and jisu.
“wow! we’re aboard a magic airship now, right? we’ve been aboard bone wyvern and a helicopter before, but this is the real thing! how hilarious!” hanho shouted with joy.
when they arrived at the control room, the players of the world tree camp were busy preparing for the war.
inho greeted sungwoo’s party.
“well, as a former army sergeant i feel rather awkward flying in the sky riding on a ship like this.
 anyway, we can fly anywhere right now, captain!”

 