\section{chapter 234}






 when the black smoke that filled downtown busan, the breath of abyss, approached sungwoo, he could feel how strong it was.
 its powerful vitality dominated his body, making the cooldown of all his skills back to the default.
‘it’s so strong and so different from in the past.
’it seemed that the evolution society developed a much more toxic breath of abyss through continuous research.
sungwoo turned his head and looked at jisu.
 her item, ‘ghost facial mask’, seemed to have some anti-toxic gas function, but its effects were limited.
 other players were exposed to the gas without any preparation for such an attack.
“jisu, take people and get out of this place right now!”“how about you, sungwoo?”“i’m fine, so i’ll catch up with you after checking out the surroundings!”“okay!”human monsters wearing gas masks began to appear from all sides.
with gas cylinders on their back, they sprayed the breath of abyss through some sort of pipes.
not content with using the shells, they were turning the entire area dark by spraying toxic gas.
‘are they trying to fill the whole city with the breath of abyss? why? ain’t i their target?”-the ‘breath of abyss’ is accumulating in your body.
-the cooldown of ‘all skills’ has been reduced.
but they didn’t know the breath of abyss gave the necromancer a huge buff.
“ahhhhhh!”“kuuuuh!”“help me!”if the evolution society kept up with the gas attack like this, it would most likely annihilate even the japanese troops they joined hands with.
 they numbered 5000.
 such a large force, who had not suffered any damages until now, was dying rapidly, fully exposed to the breath of abyss.
‘then, the evolution society even planned this?’
sungwoo started to have reasonable doubts about what those crazy guys of the evolution society had been doing.
 did they bring in the japanese troops because they needed such a huge number for “test targets”?thud! kugugugugugu!a roar broke out above their heads.
 shortly afterward, a transport plane appeared in the dark sky.
 the transport plane was crashing toward downtown busan with smoke on its tail wings.
 in no time, it fell between the two buildings and crashed ruthlessly on the road where japanese troops were crowded.
“argh!”“damn it!kwaguaguaguagua!that big chunk of metal crushed the japanese soldiers like a tsunami made of steel.
 then, pushing the asphalt road like dough, it slid towards the place where tengu, the reincarnation of the killed akira, and sungwoo were standing.
“khhhhhhhh…”tengu, who was struggling in pain while breathing in the breath of abyss, turned after finding the transport plane falling toward him.
 he stretched out both hands.
thick black wings spread, sputtering sparks all over his body.
then, like the item called “blessing of thunder god,” used by ogre skeleton, tremendous electric shocks erupted from both hands and began to block the transport aircraft running toward him.
cheeejik- cheeejik-the transport plane began to slow down at the electric shock, and soon stopped half-buried in an asphalt road.
chijik! cheeeejik!electricity could be seen flowing over the surface of the scrap metal.
 melted gray paint spilled onto the road and sparks splattered from the control board in the cockpit.
 the two pilots were already dead, turning into charcoal in fireballs.
thud! thud!but there was still something inside the plane.
thud! thud! thud!it was trying to get out of the wreckage.
soon, something came out after opening the “lamp door,” which was tattered on impact.

gu- gu-it was a monster with an unclear shape.
 as smooth as a lugworm, it had a sticky body.
when it spotted tengu nearby, it lifted its huge body into the air then revealed hundreds of teeth hidden in its body while opening its four-part head.
 the inside of its hollow throat looked like a deep sewer pipe.
“what the heck is this?”looking at that monster, tengu raised his fist as if he was annoyed.
 something unrealistic took place.
“kuhhhhhhhh!”the head of the lugworm charged at him like a bullet and swallowed his head at once.
 tengu couldn’t react because it happened in the blink of an eye.
“uh! ahhhhhhhhhh!”tengu desperately struggled with all his might.
 he tried to push it away by all means, but he was gradually being sucked into its mouth.
 its hundreds of teeth moved gradually and began to crush tengu’s head.
wooduk! wooduk! wuuuuuuuuuu!tengu could resist only briefly.
 the lugworm quickly swallowed his neck, chest, and stomach then his whole body.
his body disappeared into the monster’s mouth, and his arms and legs were still left.
 then, the moment tengu’s soles disappeared, only black feathers were fluttering on the ground.
“…”while watching that terrific scene, sungwoo unwittingly stepped back.
that monster showed something grotesque that could be found in a powerful monster, but something that only humans could feel.
‘what the hell is that?’sungwoo couldn’t figure out what that monster was.
kouuu- kouuu-after eating tengu, the monster made a short cry as if it was in a good mood.
 then, it opened its four-pronged mouth towards the sky.
 it seemed as if it was trying to make photosynthesis.
whoo-the breath of abyss in the air began to suck into his body, but it wasn’t just the breath of abyss being sucked into it.
 the breath of abyss got mixed with the souls that came out of the bodies of the japanese soldiers on the road that the transport plane traversed then got sucked into the body of the monster.
‘swallowing their souls?’sungwoo noticed he and the monster had some similarities.
 for example, the monster gained strength from the breath of abyss, and when sungwoo turned into the condition of ‘anubis,’ sungwoo could make use of the souls of the dead.
the next moment, something popped through the skin on its back.
it was black wings, which were similar to the black-feathered wings of tengu.
‘it can absorb the power of its prey.
’then, someone walked out to the monster.
“long time, no see!” he said to sungwoo.
he was a man in a black suit, wearing a full-face gas mask.
 his face glimmered inside the translucent reinforced plastic armor.
“oh, of course, you must have met another me.
”sungwoo said, “you must be the leader of the evolution society.
”sungwoo once had met him.
 he was the head of the evolution society, “doctor,” who he encountered in the underground facility of beomgye station.
“so, what number are you?”this guy could create clones, and such clones were also listed in the korean server rankings.
at one time, five clones, each with a different number, were all ranked within the top 20 of the korean server.
“my number doesn’t matter,” he said.
suddenly, the breath of the abyss downtown faded away and sunlight came back.
when the guy’s gas mask reflected light, sungwoo could not see his expression.
the masked man said, “after all, it’s all one.
 both you and the bodies scattered here must be one.
 it should be like that in the future.
 that’s the ending of this game.
”the drone of the official channel was still operating in the sky.
 the players all over the world were witnessing all the strange phenomena happening on the korean server at the moment.
they couldn’t understand what was going on now.
 they were curious about what the korean server was doing, and why this kind of thing happened one after another.


it was originally a war between the korean server and the japanese server, but at some point, two korean players stood facing each other.
“so, you guys brought in the japanese server for this purpose from the beginning,” sungwoo said.
he nodded at that and replied, “you are sharp-minded.
 i think you remember another me telling you that i was working on death, so i needed a war to secure the material of a large number of deaths.
 i needed an object that could rather easily die.
”doctor reached out and pointed at the monster behind his back.
“now, this is the result.
”the monster was evolving rapidly as if he met some “conditions” after breathing in the breath of abyss and souls.
suddenly, ugly forelimbs protruded out of its body, which looked like giant hooks.
 moreover, the tail became the form of a mace, protruding from the end.
“i would like to introduce myself to you formally.
 my name is chimera.
”chimera, a monster from greek mythology, was known as a mixture of all kinds of beasts.
the unidentified monster created by the evolution society was also a random mix of parts that would not fit at all when put together.
 each of those parts looked like a deadly weapon.
“it is the ultimate creature we have created by studying death.
”at that moment, a message rang.
[exclusive quest]-title: existence of wrong death-type: hunt-goal: eliminate the player-manufactured creature ‘chimera’-reward: exclusive skill*those who deceive death are performing strange rituals with wrong beliefs, which produced a result.
 if you don’t get rid of him quickly, he will not only deceive death, but also make it meaningless, and that means that there are no more beings left in this world who can face death.
* if the target is left neglected for a long time, he will turn into a being that you will never be able to confront.
* your choice affects your ‘destiny’.


 