\section{chapter 396}

chapter 396: full control over death (5)the cavalry quickly surrounded the airships.
 as li wei said, they temporarily turned into ‘the state of souls’ in which their bodies turned translucent, then penetrated the invisible barrier inside.





bang! bang! bang!after pouring various bombs and skills to seriously damage the battleships, they were quickly infiltrating inside.
“no.
 11 is sinking!”in particular, no.
 11 battleship, which was at the rear of the combined fleet, was destroyed in an instant after being exposed to their multiple attacks.
“next, the left engine of battleship no.
 9 seems to have suffered serious damage! it’s going off course after losing its balance!”“damn it…”although the combined fleet had a huge fleet, they had no task forces to defend against this kind of swift attack from the outsiders.
 so they were just helpless like a battleship exposed to the enemy attack.
however, they had a plan to deal with this kind of situation.
“they have arrived!”as soon as somebody shouted, the deckmen and crew on the ship raised their heads toward the sky, where someone was standing tall in the high sky.
“valkyrie has arrived!”the ‘arrow unit’ of the allies to attack their enemy counterpart arrived using ‘teleportation.
’several horsemen with keshik around her were already falling, bleeding.
“kill that woman!”a loud shout was heard from somewhere.
 at the same time, some of the keshik cavalry, who had been scattered in all directions, began to increase their attitude toward jisu.
at that moment, 20 einherjars began to rise like flames behind valkyrie.
“sweep them out!.
”when she shouted, 20 einherjars bounced forward.
the moment they collided with the keshik horsemen, 30 of them collapsed in an instant.
 two seconds later, they returned to her back.
then they slaughtered dozens of enemies once more at a time after bouncing in the opposition direction.

“hey, what the heck is that!”“it’s so fast!”although the keshik troops were the fastest of the chinese army in terms of mobility, they quickly realized that their counterpart right in front of them was more than a match for them.
they quickly slipped away from her and scattered.
thanks to that, the world tree fleet escaped from the melee and retreated toward the castle wall at full speed.
“get out of here, everybody!”at that moment, someone shouted from the keshik cavalry.
 soon somebody stepped forward with the troops dispersing to the left and right.
he was tall enough to make the horse look small, with a kite sitting on his shoulder.
“hmm…”he frowned and looked up at jisu.
 apparently, he was no.
 1 on the mongolian server.
he slowly moved his horse left and right, then suddenly took out a spear hanging from the saddle and threw it towards jisoo forcefully.
even when he threw it with his bare hands, the air was ripped apart, causing a gust of wind.
the horses around him scattered to the left and right with a roaring sound.
‘how fast he is!’the tip of the spear, which seemed as small as a toothpick, became huge in the blink of an eye.
‘but he’s not faster than me.
’jisu quickly moved as if walking in the air, avoiding his attack very naturally.
“oh, how could you…?”the enemy made an unbelievable expression.
jisu looked down at her feet.

“i’m fine…”she could avoid his attack so easily thanks to the ‘talaria (hermes’ shoes)’ that sungwoo offered as a gift.
[item information]- name: talaria (shoes of hermes)- rank: myth- category: shoes- effect: agility increases (+10), stamina increases (+2), moving speed increases (+200%), flying speed increases (+300%).
 you can temporarily enter the ‘gasification state’.
 (cooldown: 10 minutes)even though jisu was very fast, this new item enhanced her mobility further.
then the enemy leader slowly approached her, then took out one sword from his waist.
electricity flowed along the blade and sparks went off.
“alright, i think i know who you are.
 you must be the famous swordsman in this land, right? hahaha! i like you! when this fight is over, i’m going to have you as my woman!”“…”the enemy commander bluffed recklessly, but he couldn’t approach her easily.
wheeeeee-there was a brief confrontation between them, making the atmosphere bleak.
it looked as if they charged at each other to have it out right away.
however, the official channel’s camera captured some other place all of a sudden.
such a sudden change of camera angle meant they were going to broadcast something more important soon.
“stop! stop entering the invisible barrier!”then the chinese forces entering the area stopped near the widening hole in the invisible barrier, then began to watch out in all directions.
then, general lee ran into the hole in a hurry and knelt on the dirt ground with his head down, a bit far from the hole.
“…”moments later, all his troops near the hole knelt and bowed their heads towards the hole.
a solemn atmosphere that belied this wild battlefield dominated the place.
suddenly, a person stood tall in front of the hole.
 she made a cold expression, holding a small box in both hands.
she walked slowly into the invisible barrier and put down the boxes on the ground draped by a red cloth.
at that moment, the boxes opened, causing a gust of wind.
 those who were lying on the ground had to tighten their grip on the ground so as not to be flown away.
tramp- tramp-someone walked out from the gust.
whoops-he was a very tall man.
 that’s all they could see.
since an opaque shield surrounded his body, they could only have a vague glimpse of that man.
however, those viewers around the world watching this scene could figure out what’s going on now.
“your majesty!”the no.
 1 in the chinese server rankings, the emperor himself, appeared finally.
***“no way!…”reporter ahn’s nervous voice echoed in the quiet studio.
 he could not continue, swallowing at the shocking scene.
then wong opened his mouth after a very long time.
“you’re right.
 he is the emperor.
 he appeared in person!”

with a serious expression, wong continued in a very serious tone, “the emperor also commands a huge army.
 perhaps he will summon the very army that unified the chinese server.
 they are stronger than the necromancer’s army…”as he said, something started to happen.
the emperor’s body wrapped in a shield slowly floated into the air.
 at the same time, something started to form in the sky.
 it wasn’t one, but numerous.
- caution! a “sky barracks” will be opened in the area.
they were chinese-style gates that seemed to have been made of old wood.
 they opened at once.
boowooooooooo-a trumpet sounded softly from somewhere.
then a huge number of things started pouring out of the gates.
they were a huge army composed of not hundreds or thousands but tens of thousands, packing the whole sky over the battlefield.
 they easily outnumbered all the players combined here.
“oh my god! i can’t believe it!” reporter ahn shook his head.
as if he was also a bit perplexed, wong also nodded, then said, looking into the camera, “hi, korean server guys, i hope you won’t forget that what i have told you is still valid.
 i really called a spade a spade.
” wong was still stubborn.
reporter ahn nodded and said, “yes, that’s right.
 now the war started.
 wong, look at the screen again.
 it has changed again!”the screen was suddenly showing somewhere else.
 the screen change meant something more important was happening.
the screen was showing the necromancer, who wore a dark green robe with some majestic aura over his head.
“the allies’ army has arrived, too.
”the necromancer and his army arrived near the castle wall.
reporter ahn sensed immediately that the most important moment came, and raised his voice.
“alright, the fight to determine the fate of asia as well as who is the strongest of the world is about to begin!”two huge waves started crashing against each other.


 