\section{chapter 223}

                             




the ninjas, who were overwhelmed by the appearance of the necromancer, could not move recklessly.
 even while the necromancer and the president of hunter company were talking, they shut their mouths as if they were the extras.
“…”if they charged at the necromancer quickly and stabbed him, they could kill him right away, no matter how strong he was.
but strangely enough, they got cold feet.
 they felt weakened not only physically but also mentally.
‘i really can’t pluck up the courage to move.
 what’s wrong with me?’they didn’t know it, but it was because of sungwoo’s “deity status.
” repressed by his demigod status, they were terrified, and their muscles were stiffened.
 when the necromancer in the shape of a black wolf glared at them with green eyes, they flinched before they knew it.
“oh, information about the japanese server? sure, i’ll try to get it,” said the president.
when the necromancer said that he chose the japan server as his next hunting ground, he kept nodding.
 even at the insulting moment, the ninjas could not do anything.
“by the way, let me open these guys’ heads first.
”“their heads?”the ninjas could not understand what the necromancer was talking about, but they came to their senses at that terrible expression.
 they realized that even if they did nothing, they would be killed by him anyway.
“damn it! kill him!”“move!”at their leader’s order, they reluctantly moved, but it was too late.
 skeletons in a bizarre shape came out of the collapsed ceilings and exterior walls of the building.
they charged at the ninjas instantly, snatching them with their long arms, breaking their heads.
“what the heck are these monsters?”they were none other than the giant jannabi skeletons.
 they fought very well in the forest, but here in the collapsed building, they were good fighters.

“argh!”“kuuuuuuuhuh!”since the ninjas had their senses dulled by sungwoo’s deity status, they were easily caught by the long, thick hands of the monster monkeys from all directions.
their fight was quickly over.
however, sungwoo could not find any “memory fragments” from their heads.
it seemed that the ninjas here had no important information because they were lower in rank than the ones sungwoo killed in suwon.
there was only one other source of information.
 after eavesdropping using the ‘specter,’ he realized that the hunter company had some intelligence contacts in japan.
sungwoo sat on the sofa in the middle of the penthouse where the ceiling was blown off.
the president and executives of the hunter company stared at him blankly.
“okay, as i told you, can you take a look at my request and check your source in japan?”“sure, of course.
”sungwoo wasn’t joking when he said his next hunting ground would be the japanese server.
 he just needed a guide.
***the hunter company had been faithfully conducting a background investigation of the evolutionary society after its president and top executives were taken hostage and threatened by sungwoo.
however, they didn’t collect any useful information since the core leaders of the evolution society were kept secret.
 to make matters worse, they were caught shadowing the evolution society, so one whole investigation team was annihilated.
after they lost favor with the evolution society, the ninjas of the yamato guild, another mercenary, stormed into their building to kill them.
“although we couldn’t identify the core leaders of the evolution society, we were trying to find out what they were up to.
 i think our information will be of great help to you, necromancer.
”
junho paek, the president of the hunter company, checked sungwoo’s expression while explaining his findings to him proudly.
junho found himself admiring him at some point.
 when junho was saved by the necromancer, he almost became a fan of his lifesaver.
“we have maintained contacts on the chinese and japanese servers for a long time.
 based on their information, we can collect information in real-time.
”he grew his company in a systematic and organized way, so he could collect information through official contacts in japan and china.
 so, they could help sungwoo to some extent.
“so, if you can ask me for any information, i will collect and tell you everything about it in as much detail as i can.
”“it seems like the japanese server is devising a plan to attack me or our server?”junho immediately started briefing him.
“that’s right.
 shortly after world quest was issued, there was something unusual on the japanese server.
”“what is that?”“it is also known as japan bashing korea.
”according to junho, the so-called “kyushu unified army”, with the yamato guild as the central forces, was preparing for an attack on the korean peninsula with the motto of “japan bashing korea.
’although the groups in that plot were trying to block any intelligence leaking out, they could not stop the relevant rumors and gossip from circulating on the server community.
in other words, their plan to infiltrate the korean server was not made official, but it was virtually a fait accompli.
“do you have any details?”“i’m not 100 percent sure because we collected the rumors and tips from some petty members of the japanese server, but it seems their massive forces are preparing to land in busan.
”busan? it looked like they made a very detailed plan on landing in busan, the biggest port city of korea in the south.
“large troops? how many?”“well, i think the yamato guild is the central force of the kyushu united army, so when they seized power, they mobilized many ninjas to assassinate the heads of the neighboring organizations.
 so, the organizations in kyushu didn’t suffer any big damage.
”junho scratched his head and continued.
“as for the size of their troops, i guess they can mobilize over 4000 as a combined army.
 considering their reserve forces, i think they can mobilize up to 6,000.
”considering that the population of the kyushu region was much smaller than that of other japanese islands, up to 6000 was huge.
 certainly, the damage caused by the war seemed to be small in the kyushu area.
“so, in my opinion, they don’t seem to have much experience combating their opponents.
 as you know, during the japanese army’s massive invasion of korea during the 17th century, their troops were very dreadful to koreans because they had great combat experience from the civil war of their home country.
”junho provided him with even the backgrounder about the japanese forces.
‘in fact, 4,000 or even 6,000 troops are not that big.
’sungwoo had already experienced fighting against thousands of players including the chinese pirates and the red revolutionary forces.
‘what matters is the quality of the troops.
’it could be a fatal mistake to judge, as junho reasoned, that the japanese forces would not be strong simply because they had little combat experience.
‘since this world has turned into a game, the number of troops is more important than skill in a large-scale battle, and what’s more important than the number is the level of the players, and what’s more important than the level are the items.
’there was a possibility that they already secured a higher level and better items by attacking a large dungeon rather than fighting against their opponents.
in the case of the red revolutionary forces, they had some fighting experience while waging a campaign to occupy taiwan, but they could not launch any massive attacks.
 as a result, they were low-level players who were wiped out by the undead helplessly.
on the other hand, the ‘struggle guild’ had little experience fighting against other opponents, but after they increased their levels gradually while fighting in mt.
 taebaek, they could confront sungwoo with a much smaller number of troops than the red revolutionary forces.
of course, both troops were devastated by sungwoo and his allies.
anyway, it was still too early for sungwoo to judge the level of japanese servers.
he needed more information to make the correct judgment.


“alright.
 keep collecting information about them.
”“sure.
”sungwoo stood up to leave the place.
 junho and his executives also stood up at the same time.
“oh, i forgot to ask you one more thing,” sungwoo said, raising his index finger.
“please go ahead.
”“think of the way to move to busan as fast as possible.
”the kyushu united army chose busan as the first stronghold to occupy the korean server.
but even in this small land of korea, busan was far too far from the place where they were now.
“busan?”“right.
 i should be ready to respond immediately when something happens.
”at that moment, junho was at a loss how to respond because it was really hard to accept his request no matter how much he thought about it.
“i think my saving your life is enough to cover the expenses for my request, right?”“of course!” he could not reject sungwoo’s request in that situation.
having said that, the necromancer disappeared, riding the bone wyvern.
junho stared at him blankly.
“well, he is cool…”he was serious.


 