\section{chapter 237}






 sungwoo led the undead army to busan port.
 the japanese troops left behind at the port were preparing to retreat, but more than half of the battleships were already sailing offshore.
“i can’t just let you guys leave like that.
”sungwoo immediately dispatched a group of bone wyverns.
since fixed turrets were installed on the back of bone wyverns, they launched indiscriminate air bombardment at their battleships.
eventually, sungwoo succeeded in wiping out all the remnants of the japanese server’s invading forces.
their battleships were sunk deep in the sea, and that was the end of the korean and japanese war.
-the korean server has won the final victory in the ‘1st korean-japanese war!* reward is given in proportion to the contribution of the korean server.
-‘rewards for the 1st korean-japanese war are given.
* contribution: 1st place* reward: 30,000,000 gold* additional reward: ‘war hero’ title.
-you have acquired the title of ‘war hero’.
* all stats increase (+2)“well, necromancer? is our fight over now?” asked the new leader of the hwarang guild.
 sungwoo shook his head and said, “i don’t know what else they did somewhere on this land.
 mobilize your troops to search for suspicious stuff, especially look for the traces of the evolution society.
”sungwoo could not let the evolution society guys escape this time.
 so, he asked not only the hwarang guild but also the hunter company and the “wide area surveillance team” of the liberation guild to chase those affiliated with the evolutionary society.
 junghoon also accepted sungwoo’s request.
“they will go into hiding for some time.
 so, we have to track them down when they have revealed themselves next.
”
the liberation guild knew very well that neglecting them was like raising terrorists.
“thank you.
”“they are our public enemy.
”as a result, sungwoo’s allies began the largest search operation of all time.
 they originally intended to find the hidden main stronghold of the evolution society by tracking the movement path of the evolutionary society everywhere, starting in busan.
but strangely enough, their traces were found in a place that they had never expected.
it was none other than the 2nd korean-japanese war quest.
[server quest]-title: the 2nd korean-japanese war: bloody return match-type: war-purpose: winning the war-compensation: to be announced laterthe first korean-japanese war broke out due to the japanese server’s attack.
 and it was the korean server, the defender, that raised the flag of victory.
and this time the korean server is given a chance to counterattack.
 it is up to the korean server whether to resolve the deep-rooted animosity between the two servers through a bloody war or forget it calmly.
* if the leader of the korean server (kor-157) chooses to give up the counterattack, the quest will end.
[information on the 1st korean-japanese war]special rules will be given for their exciting fight.
 here are the details:1) the counter attacker (korean server) is given a ‘big counterattack bonus’.
 the leader of the counterattack side can use the ‘location check’ of the hostile forces and the ‘quick move’ to their location.

2) depending on each individual’s will, they can support the opposite server and they are allowed to transfer to the opposite server.
3) all the processes of the quest will be broadcast live through the official channel.
the system didn’t ask the korean server for a vague counterattack.
 instead, the system gave them a lot of merits to urge them to take revenge against the japanese server.
“location check?”so-called “location check” and “quick movement” were special benefits intended for a surprise attack.
-the location of the ‘hostile forces’ is displayed on the map.
* you can open ‘hyper gate (fast movement)’ by selecting one of the marked locations.
 (remaining number of times: 1)soon, a map appeared before sungwoo’s eyes.
 it was a map of the korean peninsula and the japanese archipelago.
 on the map, only two spots were marked with red dots.
 the first one was japan’s “tsushima” island.
‘if it were tsushima island, it would be the place where the japanese army is located.
 but didn’t they say kyushu was their main base?’sungwoo didn’t know their specific situation, but it seemed clear that the outpost of the “kyushu unified army” that attacked the korean server was based in tsushima.
‘so, i can move there, according to the reward?’it wasn’t a bad idea for sungwoo to raid it right now and wipe it out.
 since their main unit was destroyed by the korean server, they were probably defenseless.
 so, this was the perfect time to mount a large-scale counterattack against them.
however, the problem was the second red dot.
‘daejeon?’the red dot was stamped on the korean peninsula at daejeon.
 at first, sungwoo could not understand why the “hostile forces” of the korean server were in daejeon.
however, he soon came to know the reason when he thought about who could be the hostile players of the korean server inside korea.
‘they must be the evolution society.
’they were ruled as “hostile forces” by the system and marked on the map.
 daejon was their main base.
 after all, they left a trace they could never hide after making such bold terrorist attacks.
“sungwoo, what should we do now? should we invade japan like when we attacked taiwan?”sungwoo shook his head.
 he felt he could get rid of the japanese server at any time.
however, if he could not smash the evolution society this time, he would never know where these cockroach-like guys would lay eggs, grow, and crawl out.
 so, he needed to track them down by all means.
“let me crack down on these bastards in daejon first.
”after all, it was time for him to annihilate these wicked players once and for all.
***the main base of the evolution society has been kept under wraps until now.
 even though sungwoo and the “wide area surveillance team” of the liberation guild searched for them everywhere, they could not gather any information.
but, for some reason, the system put red dots on the map, so their location was revealed.
‘the important thing is that the evolution society guys don’t know i know their location.
.
’in other words, sungwoo could mount a perfect surprise attack.
 however, he needed to be very careful because they had very good intelligence.
 if they noticed something strange, there was a strong possibility that it would quickly escape like a loach.
so, sungwoo mobilized all his forces to pretend they were searching for the evolution society.
it was a deception tactic.
‘if i want to launch a surprise attack, i can use the “quick movement” bonus, but i have to save it just in case in the future.
’he was supposed to attack tsushima island for the 2nd korean-japanese war right after getting rid of the evolution society guys, so he decided to save the one-time-only ‘quick movement’ for that purpose because there was no good way for him to cross the sea.
besides, daejeon was located close enough to suwon, so he could attack it anytime he wanted.
“now, let’s all go home, everybody.
 we need to figure out how many are here, so, get aboard the helicopter!”“i want to tell them how well we fought here.
 i can’t wait!”

the players of the world tree camp were preparing to return to their main base in suwon.
when they came to busan, they used an item called “space movement stone”, but unfortunately, there were none left.
 so, they borrowed four helicopters from the hwarang guild.
the players of the world tree camp were eagerly preparing to return home in excitement.
“jisu!sungwoo called her secretly.
 she knew why he called her, so she followed him cautiously.
‘there may be somebody keeping an eye on us.
’the enemies could collect information with a skill specialized in espionage instead of simply monitoring them.
 therefore, the two conversed secretly behind the helicopters.
“we will sneak into the main base of the evolution society after moving along the road leading to suwon.
”even though he didn’t explain much, she nodded as if she knew what he was talking about.
“well, it reminds me of bumgye station where i fought them.
 i hope i won’t see them again.
”“yeah, that’s why we have to get rid of them tonight.
”sungwoo had no detailed operational plan.
 he just thought he and jisu could move down to daejon to get rid of them.
 that was enough.
in the afternoon when darkness began to fall, sungwoo began returning to suwon with the players of the world tree camp.
doo doo doo!with bone wyvern escorting them, four helicopters took off.
then, when they were moving from boeun-gun area to cheongju area, sungwoo and jisu slipped away from them using zombie birds and turned to daejeon.
their secret operation to infiltrate into the evolutionary society began.


 