\section{chapter 236}






 as the collapsing outer walls and concrete lumps poured down like rain, the drone of the official channel that had been filming all these scenes avoided the debris and raised its altitude.
wooooooong!all these fierce fighting scenes were being captured by the camera, and the whole world was witnessing the necromancer’s incredible performance.
“this must be crazy!”“what the heck is this neighborhood? so scary…”the surviving soldiers of the japanese server were stunned to watch the dreadful scenes from a distance.
 they set foot on a foreign land under the name of the “main force,” but they found themselves messed up even without fighting the necromancer and his allies.
 fortunately, they could save their lives because they brought some emergency gas masks.
“uh! they are charging at us!”“run away!”now, they were in a precarious situation just like a lamp before the wind.
 chimera and the necromancer’s army popped out through the building into the alley where the japanese remnants were hiding at the moment.
“uh? argh!”“ahhhhhhhhhh!”this was a situation where, as the saying goes, an innocent bystander often gets beaten up.
the japanese soldiers were smashed after they were embroiled in the fierce fight between the two sides.
 their final moments were so tragic.
thud! thud! thud!chimera and the undead army didn’t care about them.
 they broke through a few more buildings before coming out to the broad street.
 their bloody fighting continued there.
 it was like hundreds of hounds biting one brown bear.
bang! bang! bang!the vehicles left neglected on the road were pushed back and forth as if they were swept away by a flood.
 the asphalt roads were broken down like dirt playgrounds, and the street trees were bent like reeds.
kueeeeeeeeh!chimera’s body was already tattered by now.
 in particular, its black wings that grew after it ate tengu were completely crushed.
‘well, it’s time i wrapped up this fight.
’
sungwoo felt the time finally came for him to kill chimera and sent a hand signal behind his back.
 then, a huge object began to move on the roof of a building.
 a long muzzle turned its direction.
at the same time, two blue flashes flew in and hit the camera hard with sungwoo’s subordinate spirits.
 it was the iron mace of lighting.
 those soldiers covering chimera were smashed in an instant, and chimera’s left hook was cut off by the iron mace’s terrible power.
kuheeeeeeh! kuheeeeeeeeeeh!-‘evil spirit bomb’ has been embedded in your weapon.
it wasn’t the end.
 sungwoo fired the 20 ‘evil spirit bombs’ that he had loaded in advance.
gu-gu-gu-gu-gung!a black marble exploded above chimera’s head.
 its impact was so powerful that the asphalt floor he was stepping on gave way suddenly.
however, chimera was different from the monsters sungwoo had dealt with.
kueeeeeeh! kueeeeeeeeeh!how could that monster scream like that even when he was attacked so brutally?did it mean that chimera could still strike back?‘i need a more powerful attack.
’sungwoo used up all the remaining souls to fight it out.
-the ‘twilight raid’ has begun.
this time he turned to the twilight raid.
 sungwoo’s body mingled with the evil spirits, then charged at chimera.
goooo!when chimera became groggy with repeated shocks from the attack, sungwoo bound its body with the ‘ghost’s hand.
’‘now is the time!’shortly afterward, the sky was covered with black shadows.
 it was the shadow of the “bone wyvern alpha male.
” he grabbed chimera’s body and suddenly started soaring into the air.
“alright.
 let me test how hard you are.
”falling from the sky.
 that was sungwoo’s last strategy.

bone wyvern alpha male flapped its huge wings and soared hundreds of meters in the air at once.
kueeeeeeeeeh!however, when the retention time of the ghost’s hand expired, chimera began to move again.
it struggled in the claws of bone wyvern alpha male, then attempted to escape by extreme means.
chimera swung its right hook and tore apart the wings of bone wyvern alpha male at once.
now freed from bone wyvern alpha male, it began free fall.
‘not done yet!’in preparation for this kind of situation, sungwoo dispatched another bone wyvern in advance.
another bone wyvern flying nearby immediately rushed, grabbed chimera’s head in the middle, then began to soar in the air vertically.
this time again the bone wyvern was crushed by chimera while soaring, but another wyvern snatched chimera again.
when a series of bone wyverns took turns raising their altitude with chimera in their claws, they succeeded in flying up thousands of meters in the air.
 chimera looked like a tiny dot in sungwoo’s eyes.
it was high enough in the air.
“drop it!”bone wyvern let go of chimera by loosening its claws.
 chimera’s body began to fall helplessly, spinning round and round.
chimera spread its black wings to keep its balance desperately, but it couldn’t because his body was cut during the melee.
kieeeeeeeeeeeh!free-falling from the sky had a much stronger impact than expected.
the moment an aircraft or spacecraft made of the best alloys hit the ground, it shattered to pieces in an instant.
 it’s not because it is less sturdy but because the impact of the free fall is much more destructive than expected.
 the same goes for well-made biological weapons.
 chimera’s body fell.
thud-a slight vibration from its impact spread over the roads in the city.
 its body was shattered to pieces, so much so that its shape could not be recognized.
that was it.
-you have earned 1,000,000 gold by hunting ‘experiment no.
-455’.
-you have acquired the title of ‘experiment disposal manager’.
* all stats increase (+1)even though sungwoo killed the worst monster of all time, he got only a million gold as a reward.
 aside from its pettiness, this game was not worth a candle for sungwoo.
nonetheless, he earned one title, but it was not satisfactory because it was not a monster made by the system.
but there was one important thing left.
-you have successfully cleared the exclusive quest ‘the wrong death’.
*you are given a reward.
 (exclusive skill)sungwoo confirmed the newly acquired skill after successfully clearing the exclusive quest.
[skill information]-name: appointed death wizard-grade: basic-category: active-consumption: 50 mana*when you resurrect a skeleton, you can give it ‘magical talent’ to make it a ‘skeleton mage’.
 (maximum 5).
 skeleton mage can use attack magic and curse-type magic, and it will use more powerful magic when the skill grade improves.
* skeleton mage can become a ‘death priest’ if it meets ‘specific conditions’.
* skeleton mage can become ‘lich’ if it satisfies ‘specific conditions’.
“wow, i have obtained the right reward finally,” sungwoo said.
the enemy’s challenge also left behind several gifts this time, too.
***

on the other hand, doctor realized that he couldn’t win even with chimera, so he chose to run away early on.
 but he didn’t run away that far because jisu, who had evacuated other players, sensed his movement and started tracking him.
a little later, doctor was dragged back in a miserable condition before sungwoo with his limbs cut off.
“he had a helicopter waiting nearby to run away just in case.
 i caught him just before its takeoff.
”doctor looked up at sungwoo, with his face covered with blood.
“it’s useless if you kill me.
”what he meant was that since he was only one of the clones, the evolution society would continue to survive even if sungwoo killed him.
“but it doesn’t make any sense for me not to kill you, right?”“…”sungwoo knew it was just pointless to talk with him anymore, so he killed that guy without any hesitation.
then, the nickname “doctor-001” disappeared from the player rankings.
except for the core creature, ranked 7th in the korean server rankings, he was listed as the highest rank.
however, sungwoo felt somewhat uneasy.
‘this fight will never end here.
’as long as the core creature that generated the clone “doctor-000” survived, the evolution society would attack sungwoo again by using another grotesque means.
“jisu, there may still be some human monsters made by the evolution society around here.
”“i have to catch them.
”“yeah.
 we need some clue to pursue them.
”sungwoo still did not know where the evolution society was located.
 unless he rooted them out completely, this kind of annoying thing would keep happening.
‘by the way, the korean-japanese servers’ war has not yet finished…’sungwoo had some other work to finish before chasing the remnants of the evolution society.
 the whole world was watching the fierce fight between the korean and japanese servers, but it was clear that the victory of the korean server was around the corner.
‘alright.
 let me finish this war first.
’

 