\section{chapter 252}

                            ‘it means a human who has inherited the blood of a dragon.
’




in other words, if the human beasts such as werewolf and werebear could acquire the appearance and physical abilities of the wolf and bear, respectively, then the dragon race could exert the power of dragons.
‘wyverns were the dominant ruler of the korean server.
 dragon? i’ve never seen this race before.
’however, the name of the dragon was enough to explain everything.
 it was often said that the status of the dragon in fantasy was the most powerful like the final boss level.
sungwoo checked the credential qualification time for the “ownerless sword” carried by minsok.
-time remaining until credentials: 1,001 daysnow, after the remaining days are over, the ‘unidentified egg’ will hatch.
 it started 5,000 days ago, so sungwoo shortened the required time much faster than he thought.
‘at this rate, it will hatch soon.
’based on the recent boss monsters he confronted, he thought he could complete the time requirements by hunting two more boss monsters.
“i don’t have to rush.
 i’ll fulfill the time while i’m doing what i have to do.
’he knew that he could lose everything if he rushed.
so, sungwoo decided to take care of what he was faced with right now.
***that night, the players of kanghwa island arrived with the cry of a griffin.
“necromancer! it’s been a while!”heyon on the griffin landed finally.
 she couldn’t take her eyes off the world tree from the sky.
“wow! this tree is so big!”then, three helicopters landed in a makeshift field.
 some of the 256 players of kanghwa island arrived first.
when they heard their arrival, all the villagers came out and greeted them.
“wow! welcome!”
“welcome, everybody! we’re being reunited like this!”both sides exchanged greetings in a friendly manner.
 they had been looking forward to meeting for a long time, and the time finally came.
“let’s work together well!”“of course!”then, kyongsu stepped forward and escorted them to their lodging.
“okay, everyone.
 please unpack your baggage first.
 the building you see over there is your lodging.
 it is very spacious and clean.
 please feel free to talk to me if you have any inconveniences.
”the villagers renovated several stores in front of the museum into lodging for the kanghwa players.
they were divided into family groups before choosing one per family.
 since they were assigned to each room according to the number of people, all the rooms were distributed fairly.
“wow! each room has a bed! i also see tableware and towels ready.
”“there is also a barbecue grill on the roof.
”they could not help but be deeply moved by the villagers’ considerate attention to their welfare during their stay here.
“man, they have even connected the battery items! i can feel how much they care about us.
”“you bet.
 they said they were busy because they were short-handed, but i can feel how much they care about us by providing us with this kind of good accommodation.
”after unpacking, they looked around the facilities in the village, checking the village terrain, and exchanged greetings with the village players.
“uh, hanho? it’s been a while!”“hello! isn’t our village so cool?”“it’s the best!”“now this has become our village!”since hanho already met some of the village players several times, he greeted them gladly like friends.

“you are my brother, the strongest thief, right?”at that moment, somebody called him from behind.
 a little boy who looked like an elementary school student came running to him.
 he was heyon’s stepbrother, youngin.
“oh, it’s you!“yeah! i’m now a level 6 player!”he boasted of his level first.
 he was far below average level, but considering his age as an elementary school student, he was growing steadily.
“really? you must be the highest level among your friends.
”“yeah! i’m the strongest among my peers.
 brother, you have reached level 20, right? you are cool!”although some of the top rankers were killed during the korean-japanese war, hanho was ranked quite high.
“uh? did you check out my ranking, too? hahaha!”“someday i’m going to reach as high a level as you, brother.
 by all means!”“as things stand now, you can!”anyway, they were getting along well like this from the beginning.
however, they could not afford to stay complacent forever.
around 10 pm, kyongsu’s voice came out through the speakers in the square.
“today is the first day we have met, so i would like to have a small party for you, but starting at dawn tomorrow, you have to transport a large number of people.
 so, please go to bed early tonight.
”tomorrow, 40 people were scheduled to head to busan to transport the war booty from tsushima island, while 50 people would head to the main site of the evolution society in daejon to take care of the prisoners there.
in other words, they could not relax without any worries yet.
 the world quest aimed at the world tree camp was still valid, so they didn’t know when they would be attacked again.
“let’s go to bed early for tomorrow.
”“sure! we have to save our stamina!”the biggest reason they gathered here was to prepare for the upcoming war.
***sungwoo delivered a message about the prisoners of the evolution society to the liberation guild.
 the next morning they sent a reply to him.
hanho read it.
“uh, um… they say the terrain of a mine has appeared on mt.
 bukhan.
 various ore items are found here, but because of their huge reserves, they are thinking of using the prisoners.
”“sounds good.
”“they said they were still discussing the details, so they will contact you again next time.
 when i escaped from yeongdungpo, i thought we would fight these guys, but i’m glad we can get along with them.
”fortunately, there was a way to deal with a large number of prisoners.
 just as herbal items grew in mt.
 paldal, special items could be gathered and mined in certain areas.
if they dispatched the prisoners to such areas, they could monitor and control the prisoners while utilizing them at the same time.
 it was like killing two birds with one stone.
‘if this happens, economic power will become important in the future.
’as each server entered a stable phase, giant forces with more capital than individuals could even dream of began to establish themselves.
‘if i stay complacent, relying on individual power, they could catch up with me anytime soon.
a little later several helicopters arrived.
“supplies are coming in from daejon! please prepare to transport them!”a huge number of supplies were brought in at once by a cargo plane stationed at the headquarters of the evolutionary society.
as soon as they arrived, they drove the forklifts on standby to the temporary landing field.
 then, they began to transport the loot packed in wooden crates to the warehouse.
“what’s all this?”“they are three boxes of 200 mid-sized battery chargers.
’“okay, move them to warehouse no.
 1!”

a huge number of items began to pile up in the warehouse set up in advance.
other items in the form of finished products, such as battery chargers and radios, as well as all kinds of material items were still overflowing after they filled ten warehouses.
the continuous processions of transporting goods was reminiscent of a distribution warehouse on a port.
“what the heck is this? why is its packaging so complicated?”“look out! that’s the breath of the abyss!”“what! damn it! it was a close call!”several items needed special care because they were taken from the laboratory where all kinds of experiments were conducted.
 if anything went wrong, a major accident could occur.
“no matter what, you should make sure they don’t open this box.
 got it?”“don’t open the box! don’t check the contents of the box! hey, there! don’t open the box!”kyungsu and the staff of the general affairs department were busy going back and forth to relay sungwoo’s order.
“i’m looking for another place to store things temporarily because the warehouses are full now.
 so, make sure they pile up the items well in front of the warehouse.
”“okay!”when kyonhsu said that, the staff of the general affairs department communicated with each other through radio and spread his message.
“okay, from now on, we’re going to temporarily stack things in front of warehouse no.
 10! please follow my instruction!”“where? warehouse no.
 7 ?”“no! warehouse no.
 10!”they were in a hectic situation, but players in the life and manufacturing sector were watching their moving activities with satisfaction.
“hey, did you see that? looks like an ogre skull.
 given the stigma on its forehead, so it’s ogre magi.
”“where is it? it’s a jackpot! awesome! let’s make the bone helmets we made last time! this time, let’s properly enchant them properly and apply the magic damage amplification effect! i’m looking forward to it.
”the two blacksmiths chatted, checking the items in every warehouse.
 they were very much immersed in their job as blacksmiths.


 