\section{chapter 450}

it was a woman named jisu who said that.
 she was one of the strongest among the fragile humans.





'but she is nothing, compared with me,' isabella thought to herself.
 jisu looked at her from three or four steps away.
 her eyes were filled with sympathy rather than fear or vigilancebut every time isabella looked at her, she was filled with the desire to kill her 'if i can swing my arms just once, i can kill her right away.
'however, jisu was holding the remote control in her right hand.
 she noticed isabella's pupils dilating, so she tightened her grip, stepping back her right foot.
she put her thumb on the button of the remote control.
at that moment isabella let out a sigh and approached her.
"i know.
 let me go there.
 you are going to kill me if i don't, right?" she asked.
 behind isabella's neck were three swords attached to the 'dragon keeper' hanging upside down like a cloak.
if jisu pressed her button, the swords would stab her neck right away.
 "no, i don't have to kill you.
 i don't even want to," jisu replied.
 her reply was surprising to isabella, but she didn't care.
"really? but it's me who will decide it," isabella said.
 "you decide?" jisu asked isabella snorted at her as if she took it for granted.
 "as for that button, you can't decide to press it, depending on your feelings, right? i can decide by controlling my feelings.
 for example, if i suddenly get really annoyed and want to go on a rampage, then i'm going to die.
"it was a matter of pride to her, after all.
 in terms of pride, it was her basic instinct to take the initiative in this fight by all means.
"what did you say? your feelings?""yeah, i always do what i want according to my moods.
"isabella passed by her and walked towards the hallway.

however, jisu did not move like her, and asked, "are you sure?"isabella stopped at that.
 follow current novels on lightnovelworld.
c‌om"isabella, do you really want to do what you want to do?"isabella turned and looked at her, then asked, "what is the problem?"jisu replied, "then, what do you want to do?"isabella did not answer.
 she was embarrassed because she didn't know the answer.
 and she suddenly realized that she was hesitating like an idiot.
'what the heck?'she blushed.
 how could she feel shy as a dragon, the most powerful creature?"…isabella.
"at that moment jisu came closer to her.
 even though she knew it was dangerous, she approached isabella and looked up at her.
"i know someone like you.
 he told me about her old memories.
 some memories that she can't remember, or emotions like her memories.
.
.
""memory?"isabella frowned at her.
 she got annoyed and felt ashamed.
oddly enough, she didn't think she wanted to kill this woman this time.
 this was a different kind of anger for her.
 "everything has gone wrong.
"".
.
.
""the monster we need to fight isn't you, but the system.
"isabella felt dizzy, and at the same time, she felt upset.
 she didn't know why she was upset, but obviously, her anger was triggered by her memories that she could not remember.

"shit…" she murmured.
 of course, her emotions were still there.
 was it a trace of something else before she became a dragon?***the king of the great mountains has arrived in the middle of the amazon.
 he tried to habitually put the smoking pipe on his mouth as he used to, but he didn't have the guts to light it under the sweltering heat.
"damn! this is a different hell from mt.
 baekdu! shit!"behind him were the two young tigers gasping for breath, carrying baskets of potatoes on their backs.
follow current novels on lightnovelworld.
com"oh, your majesty, we are struggling now because we are covered with furs.
""why should we have to come all the way here to help those players?"was it because the two young tigers were not born a long time ago? they didn't yet know how to read their boss's mind.
" i don't know about it.
"however, even the king of the great mountains himself did not know the reason clearly.
"pardon? don't you know it?""how irresponsible!"the king sighed deeply at their frustrated and resentful voice.
he smacked his lips, looking at the smoking pipe, but put it back into his pocket, shaking his head.
"well, some voices in my mind keep telling me to kill you and others in the mountains, but i'm doing the opposite.
"they seemed embarrassed by his unexpectedly strange reply.
 "well, this looks like the only way if i want to do it my way…"the two tigers made a puzzled expression as if they could not figure out what he was talking about.
 then the king took out some boiled potatoes from the baskets that they were carrying on their backs.
"well, i'm sick and tired of these tasteless potatoes, but when i devour delicious things, i am eventually drawn to that voice.
 that's why i'm holding back my urge.
"the king bit a half-done potato.
bang!there were explosions in the sky far away.
 there were airships here and there in the sky.
"the battle seems to have begun, and we must go and help.
"he moved against his forced instinct.
***sungwoo looked up at the two giants, who cast an infinitely huge shadow over the collapsed amphitheater.
goooooooooooh-their black bodies didn't feel like a living thing.
 they were rough and hard like a rock, and geometric patterns were engraved on them, giving off a purple light.
visit to lightnovelworld.
com discover new novels.
the chains that wrapped around their arms and legs also shone brilliantly, and the heat came out when they let out their breath filled the area around their faces and the ceiling.
 and even their purple eyes shining in the heat were far from ordinary.
'gigantes.
.
.
'in greek mythology, it was the name of the race that was locked in a place called 'tartaros' deeper than the underworld after losing the war with the gods.
two of them were summoned and controlled by sungwoo.
 "kuuuuuuuuuuuh…"at that moment, petros rose from the wreckage.
after goliath's head was smashed, he summoned another warrior twice, but they could not confront gigantes.
"let me take the bones of your warriors," sungwoo shouted.
 and the bones of those warriors were taken by sungwoo.


rattle! rattle!".
.
.
"petros's fighting spirit was obviously broken by now.
 he could not deny he was defeated.
 it was the necromancer who was once engaged in a fierce fight with the demon king and dealt a fatal blow to him.
 so, as the demon king's minion who managed his castle, petros could not be the necromancer's rival from the beginning.
'this guy is just buying time for the demon king anyway.
'this labyrinth was nothing more than a kind of security system in which they could keep the intruders like the necromancer at bay until its owner gangsok returned.
``he will come here soon.
'even though gangsok lost the fairy butterfly, he was with the magicians with sophisticated magic skills.
 he also had other attack means available.
he would definitely arrive more slowly if he was denied the portal created by the fairy butterfly, but it would not take him long to come back to his castle.
'let me destroy the world seed before he returns.
 if i can't, i should deal a bigger blow to him than before.
'sungwoo brought the grim reaper to petros's neck.
"if i kill you, the next gate will open for me, right?""come on, wait a minute…"but sungwoo didn't stop.
 he didn't want to waste time conversing with him.
follow new episodes on the lightnovelworld.
c‌om platform.
petros' head was cut off and rolled down the ground- you have passed labyrinth no.
 '4' gate (2/7) you can also read this novel on the more advanced platform lightnovelspot.
com

 