\section{chapter 380}

chapter 380: hephaestus’ forge (4)“as expected, you did a great job,” said kyungsoo, nodding at sungwoo, then turned.





“ah, can you tell hanho and jisu to come over here when you see them?”“sure.
”a little later, hanho and jisu came to see him.
“wow, what is this? every time you go somewhere, you bring such a wealth of treasure! you look like a daddy who comes back home after work,” hanho said excitedly.
looking at the items piled up in his office, hanho looked excited like a child during christmas.
“don’t touch yet.
 wait.
”he calmed hanho down like he was a puppy and organized the items he had obtained by robbing two safes.
 no matter how effective the items were, he needed the players who could use them properly.
 in that sense, jisu and hanho were inevitably the first beneficiaries.
sungwoo gave jisu myth-grade shoes, ‘thalaria (hermes’ shoes)’.
[item information]- name: talaria (hermes’ shoes)- grade: myth- category: shoes- effect: agility increases (+10), stamina increases (+2), moving speed increases (+200%), flight speed increases (+300%) you can temporarily enter the ‘gasification state’.
 (cooldown: 10 minutes)this kind of option would greatly increase her fatal blow to her opponent.
“ah, thank you, sungwoo, for taking care of me every time,” she said.
“well, all you can do for me next time is just bring me something like the shadow king’s legacy,” he replied.

it was jisu who made it possible for sungwoo to complete the shadow king’s legacy set, which accounted for about half of the forces under his control.
 so, no matter how much he gave her, he could not repay her enough yet.
she took the shoes with a smile, and replied, “sure, will do.
 i will always look for such an item.
”then, it was hanho’s turn to receive the item from him.
 sungwoo picked up a round shield among the items.
 all kinds of drawings were engraved along the circular line on the surface of the shield as if it was a heroic epic.
“come on, this is for you, hanho.
”hanho was waiting hesitantly, then jumped forward.
“oh, sungwoo! i believed you would give me one, too!”what he gave to hanho was an item called ‘achilles’ shield’.
 hanho did not match the image of that strong hero at all, but there was one option that matched his image.
[item information]- name: achilles’ shield- rank: myth- category: shield- effect: increases physical strength (+10), increases physical defense (+100%), increases magic resistance (+100%), immunity to all curses increases (+50%), increases abnormal status (+50%).
 when you inject mana, it will open a ‘sacred shield.
’ also, all the targets within the shield are immune to abnormal status effects.
it was a shield option.
 it would be a bonus for hanho who relied on a one-sided battle based on the overwhelming defense unique to him.
after wearing the shield, hanho waved his arms around in a weird posture, then admired it.
“wow! i look like a real warrior with this item, right?”in the meantime, hanho had six hands, so even if he was equipped with a heavy shield, he could freely use other weapons.
 surprisingly, the shield was uniquely advantageous to him.

when sungwoo was giving the items to jisu and hanho, he heard footsteps echoing in the hallway.
“it’s kyungsoo.
”jisu recognized whose footsteps they were only by hearing them.
soon, the door opened and kyungsoo entered.
“it looks like a hypergate will open soon.
”it was time for them to welcome the arrival of the wpu dispatched by the american server.
“okay.
 it’s opening sooner than we expected.
”as the level of wizard players went up, the operating time of the ‘hypergate’, which required a large amount of mana supply, was significantly reduced.
 now, it was easy to open and close as if they easily opened a large tent.
sungwoo’s party moved to ‘first airfield’.
 it used to be called a “temporary airfield,” but now it was fully refurbished.
woowoowow-there was even a runway about 50 meters long, which they built after demolishing the surrounding buildings.
 the airship was taking off there.
since all of the helicopters and airships operated by the world tree camp could take off and land vertically, they didn’t need a long runway, so it was just a vast space for the landing of a number of airships.
two “hypergates” were installed on one side of the runway.
 when sungwoo appeared with kyungsoo, the on-site manager rushed to them to report something.
“airship no.
 5 and airship no.
 6 are moving to their duty position, and airship n.
 7 is located behind the hypergate, so they can get ready to destroy the gate with cannon fire in case of emergency.
”just in case of an emergency.
 three airships of the world tree fleet were waiting in the air to warm up their weapons.
they were now preparing to welcome their allies, but they had to be always careful when they let their guests inside the castle wall.
not long ago they were almost bombed by an enemy disguised as the crusader team, so they had no choice but to be more prudent.
“10 seconds to go before the hypergate opens!”a loud voice was blaring from the speaker on the control tower.
 then, somebody started counting down.
the players of the world tree camp stopped what they were doing and looked at the hypergate.
“the hypergate is opening now!”woowoowoo-the space began to be distorted when light between the two pillars flashed.
finally, an opening to the us server has been opened.
a black shadow appeared in the center of the passage, then a huge airship came out.
it was the wpu fleet.
“man, it’s a fleet!” kyungsoo said.
the appearance of the airship was unexpected.
 although the airships were the mainstay of their forces, the us server gave most of their airships to sungwoo in the past.
‘didn’t they say that they would keep the remaining airship at their home base?’but that wasn’t all.
 a couple of more airships came out, followed by a lot more.
wooooo-“what the heck is this?”

“can you count how many?”it seemed that the airships numbered well over twenty.
 they were literally a large fleet.
naturally, there was a big confusion in the control tower.
“secure the space in the sky right now!”three airships of the world tree fleet floating above the airfield hurriedly rose to a higher altitude because there was a high possibility of them clashing with the many airships in the sky.
“i think we need to make a separate space for those airships to land.
”sungwoo didn’t expect such a large number of airships would be dispatched by the wpu.
 sungwoo was really surprised.
 how did they prepare such a large number of airships?“i don’t know if we can make enough space for them…”the propulsion engines of dozens of airships sucked in air, causing a strong wind around the world tree camp.
woowoowoo-all sorts of mechanical sounds mixed and resonated above their heads, so they felt as if they were inside a huge machine.
the airships moved in unison and spread out into the sky, forming in line one after another from high altitudes.
 when a giant airship came out, the hypergate finally closed.
 then, some familiar guys began to appear on the deck.
“how are you?”they were jonathan cage and arnold hearst.
 it was nothing surprising that jonathan came here, but it was quite unusual that herst, the master of the hearst workshop, visited here in person.
 in other words, the blacksmith appeared at the forefront.
at that moment, hearst grabbed the railing and shouted at sungwoo, “hey! are you better off now after taking away all our items?”

 