\section{chapter 233}






 when akira finally succeeded in cutting her shoulder, the japanese troops shouted for joy.
responding to their thunderous cheering, he lifted his hand with a swagger.
 he even turned to the camera, showing his broad smile as if he seized the chance to beat her.
“now, it’s your turn.
 show me anything if you can,” he shouted at her.
“well, you will die if i show you my next move.
”he burst into a hearty laugh at her bluffing.
“hahahaha!”he laughed loudly, then grabbed his sword again.
 then, he moved his head from left to right, making a provocative move at her.
“come on, you korean guys are full of bluffing! i have sized you up already.
 that’s how far you can show me! i can kill you!”at that moment, a one-line message appeared before her eyes.
-‘hunting start’ has opened.
this was the message she confirmed earlier, which would enable her to use the additional skill ‘hunting start’ when she continued to fight for 120 seconds after using ‘hunting instinct’.
“start!”as soon as she said that, a blue flame floating behind her back seeped into her body.
then, her eyes began to glow blue and blue breath soared from the gap in her mask.
-‘start hunt’ has been activated for 1 minute.
* all your stats have been greatly increased.
 (+20)* attack power against ‘the hunting prey’ has been greatly increased.
 (+50%)this skill gave her the best stats to slaughter her chosen prey, but she had to kill the prey within a minute.
’59, 58, 57…’
just like a beast that concentrated on killing its prey, jisu rushed at akira fiercely who she decided to kill by all means.
“sure, make my day!”then, she began to wield her sword at him violently, who she was determined to kill.
clang! clang! clang!she seemed to have swung the sword more violently than before, but her swinging was dominated by her instincts based on her overwhelming senses.
’52, 51….
’after clashing with her three times, he had to see his arm pushed back.
 startled, he tightened his body.
 only then did he realize there was some change in the way she wielded the sword.
clang! clang!“kuuuk! khhhhhhhhh!”“hey! big!”hit by her attacks marked by accurate timing, and power, akira tried to find the chance to strike back, but he could not even think of it“oh, my god… who the hell are you? this doesn’t make any sense!”he now realized he could not hold out for long.
 when she kept attacking him from all directions, he began to feel a sharp pain in his joints.
and every time he felt the shock of her attack, he began to lower his knees, elbows, and waist little by little.
“argh!”now, akira lost his balance, and finally, his knees bent in a humiliating blow to him.
“oh, no!”amid her endless attack, he barely managed to defend himself somehow, but he couldn’t defend properly because he kneeled.
 he could not grab the sword tightly, and the hilt rattled in his hand.
in the end, he let go of the hilt helplessly.
 his sword soared into the air and stuck in the middle of a streetlight.
“…”
he knelt empty-handed, lowered his trembling hands, and slowly raised his head.
“uh, how can this happen to me? i can’t believe this!”“i told you already!”a beastly woman with blue eyes was looking down at him.
 every time she opened her mouth, something blue came out of her mouth.
 the black blade of the sword in her right hand was lifted upright.
“i told you if you saw my next move, you would die.
”then she swiped her sword through his neck.
akira’s head was cut off before soaring into the air, and his body fell to the ground.
“…”the city was still quiet.
 the main unit of the japanese army, who was watching their fight, had no choice but to remain silent.
even the players of the korean server forgot to cheer for joy, overwhelmed by jisu’s incredible fighting.
-korean server ‘kor-339’ has won!-‘victory buff’ is given to the korean server!* attack power increases for 2 hours (+30%)“wow! we have won!”“it’s awesome! jackpot!”only after a message about their victory popped up before their eyes did the korean server shout for joy.
since the majority of the troops were left behind on campus, there were only 30 who came here, but their shouting was louder than before.
however, jisu didn’t yet let her guard down, grabbing the sword tightly.
she glared at akira’s body, feeling some ominous energy.
‘no, it’s not over yet.
’her hunch was right.
 some unexpected weird phenomena began to take place.
akira’s head, which was cut off, began to move alone and floated in the air.
what came next was disgusting.
tsutsutsutsu―blood veins protruded in bundles at the cut section of his neck.
 they clumped into one place and began to shape a huge body, like clay.
in no time a body in the shape of a big giant was completed.
it had a red body about 4 meters long, black wings protruding from the back, looking like a goblin called a “tengu” in japanese mythology.
“you have made me turn to the last resort…i won’t forgive you,” said the eerie being in a clumsy voice.
 it seemed like a mutation caused by some item.
 did he become a monster instead of prolonging his life?“what the heck is that?”“is it a human being?”while the korean server was whispering in shock, sungwoo, who had been watching the whole thing, stepped forward.
“jisu, let me take care of him from now on.
 as you know, it’s my specialty to kill a big guy like him.
”this was not a one-to-one confrontation.
 sungwoo thought of using the undead to get rid of him.
 he felt they could do it for the remaining 14 minutes.
the japanese troops were in chaos, at a loss about what to do because their leader was killed to their astonishment.
electric current was flowing from his hands.
 it seemed that this monster would not simply launch only physical attacks.
 so sungwoo summoned bone drake and ogre skeleton behind him right away.
“come on! let me tear them off!”at that moment, jisu shouted, “sungwoo, watch out for that in the air!”jisu was feeling some other danger.
sungwoo trusted her warning and made bone drake protect their heads.
peeeeeeee!

when sungwoo raised his head, he saw an object that appeared to be a bomb flying toward him while making a whistling noise.
 it wasn’t one or two.
 dozens of them were falling all over downtown busan.
“what the heck is that?”“ooops! they are flying toward us, too!”the target of that unknown object was specific.
regardless of the korean server or the japanese server, all of them were in the striking range of the unknown object.
 it was an indiscriminate bombing.
bang! bang! bang! bang!shells exploded everywhere before they could escape, and at that point, black smoke began to spread all over the city along the alleys.
the black smoke swallowed up everything.
 painful screams began to come everywhere.
“ahhhhhh!”in particular, the main unit of the japanese army was hit by a huge number of shells.
as a result, those japanese players who breathed in the black smoke began to fall helplessly.
‘this is the breath of abyss.
’sungwoo found out the identity of the shells at once and naturally guessed who masterminded this surprise attack.
‘the evolution society.
 why the heck did they join hands with the japanese server?”-mana has been greatly increased by ‘abyss of al breath’.
-‘abyss of breath’ is accumulating in the body.
the breath of abyss brought a tremendous buff to the necromancer.
 the evolution society would probably know this.
 then, why did they launch an attack with this breath of abyss?-‘grim reaper’ retention time has been increased.
-‘anubis’ retention time has been increased.
‘alright, let me get rid of you guys, no matter what!’

 