\section{chapter 156}

                             




“hey, let us meet the no.
 1 guy!”“do you think this is a big deal? nope, it’s not.
 why are you stopping us from meeting him? is the no.
 1 guy the president of korea? do you think your commander is like the premier? step aside, so i can directly ask to see him!”five men were screaming into the conference room from the hallway.
 the crusader team members were blocking them, but they seemed to be very embarrassed.
“deputy commander!”the crew members found minhum approaching from behind.
 then, they felt relieved because they knew he would take care of this troublesome headache.
“hey, guys, what’s going on?”the five guys turned to him immediately.
“you got here at the right time.
 deputy commander, you shouldn’t block player-to-player communication in this way!”“that is why we are asking for an equal decision council and opposing the policy on the coalition operating cost.
 are you really trying to pursue dictatorship?”when he heard that provocative word ‘dictatorship,’ minhum responded in an angry tone, “watch your language! who is a dictator? who is controlling you? kangsok han himself has made it clear that he would not meet anybody.
 why are you trying to pick a fight with us? we also can’t talk with him because he is refusing it.
”but the man who ground his nerves retorted, “don’t make excuses like that.
 do you think we don’t know you guys are monopolizing the position of no.
 1 even after winning over the necromancer? we know you sweet-talked the necromancer into fighting the chinese players, then reaped the sweet outcomes comfortably.
”when he said that, sungwoo stepped forward and said, “who is fighting whom?”the man remained silent when sungwoo appeared before him.
“necromancer?”“what the heck? when did you come?”some of them looked quite embarrassed because they did not expect him to appear here at all.
 one of them even stepped back as if he was shocked.
the images of the necromancer as they saw through the media were so impressive that he was considered as a hero and an overwhelming power.
“necromancer, i never expected you would be here.
”however, the three tall and heavy guys who stood before him were not moved at all.
as if they were from the same organization, they were wearing a green eagle-shaped badge on their left chest.
 and they were looking at sungwoo’s eyes keenly as if they were waging a war of nerves with him.

“i’ve joined this group on my own.
 i’m not controlled by anybody,” said sungwoo firmly.
then one of the three men, who was wearing rimless glasses, sneered at him and said, “don’t you think you’re mistaken?”“mistaken?”now, they were openly challenging sungwoo.
“well, what i mean is you might be mistaken that you are acting on your own? you might be playing into their hands.
 so, please give serious thought to it.
”sungwoo laughed it off, then said, “thank you for the advice.
 let me tell you this.
 just think carefully before you say something.
 you might be mistaken if you think you can get away with murder even if you shoot your mouth off these days,”“…”sungwoo gave them a clear warning.
the one who stepped back at his words moved back further.
 the guy wearing rimless glasses shut up.
 then, he passed by sungwoo, frowning at him.
 the other guys followed him hurriedly.
one of them shouted, “we’re not pushovers! don’t underestimate us.
”sungwoo ignored them, and they disappeared down the stairs.
minhum said, “they are the nasty guys i mentioned to you.
”“you mean they’re the members of the reconstruction alliance?”“yes.
 i hear they have their own leader, but we don’t know his identity.
”sungwoo calmly nodded and said, “when you form a coalition, you should check them carefully.
 you don’t know who is approaching for what purpose.
”“that’s right.
 we are extremely careful at the moment because people with the evolution society might infiltrate our alliance.
 the wide area surveillance team, which we founded recently, is doing their job well.
”it was the intelligence unit they founded at sungwoo’s recommendation.
minhum opened the door of the conference room.
 all kinds of documents were piled up like a mountain on the spacious desk in the conference room.
junghoon raised his head.
 he was taking off his full body armor at the moment, but he looked pretty haggard.
“oh, you are here.
”
“you look tired.
”“well, i was reading some stuff before you got here.
 by the way, as you guaranteed, you defeated the pirates.
 thank you.
”“because i promised.
”sungwoo sat across from him.
 jungwoo looked nervous.
“i would like to ask you a lot of questions about the chinese server, but there is someone who you need to talk to first.
”“you mean kangsok han?”“yes.
 ranking no.
1, kangsok han.
”junghoon looked more gloomy while mentioning his name.
“i can’t find out his real identity.
 besides, he said he came here to discuss something that could influence the fate of the korean peninsula.
 so, i just don’t know what will happen.
”“i heard he was looking for me.
”“yes.
 by the way, sungwoo, that guy is really different.
 yes, completely different from us.
 so, i’m not sure what will happen.
”junghoon stood up from his seat and said, “as this is an important issue, i hope that you can meet and talk to him.
 if this is something that can influence the korean peninsula, it’s very urgent.
”junghoon was clearly frustrated.
 even though he was the leader of this group, kangsok han refused to talk with him.
nevertheless, junghoon tried to find a rational answer.
 so, he thought that it was the best answer to arrange for a meeting between the two.
“okay.
”junghoon immediately escorted sungwoo to the place where kangsok was staying.
their destination was the vip lounge, the most antique place in the department store building at youngdungpo station.
 when sungwoo got closer, an ominous message appeared.
-an unknown energy is encroaching on the whole area.
“what the heck…”junghoon, walking ahead, nodded at sungwoo and said, “can you see it? i don’t know what this is.
”-your body function is deteriorating due to unknown energy.
* all stats decrease.
 (-1)the closer they got to that place, the worse their symptoms got.
-your body function is deteriorating due to unknown energy.
* all stats decrease.
 (-2)“right here!” junghoon said in a small voice and opened the door of the vip lounge.
then, the first thing that caught his eye was a roll cake on the wooden table.
 and next to the cake, something very small was eating the cake.
“sweet! sweet!”it was a very small woman.
 her back had four silver wings, and her long blue hair was impressive.
‘tinkerbell? or a fairy?’no matter how closely he looked at her, she was clearly a fairy.
 she poked the teaspoon into the roll cake, turned her head to sungwoo, then flew away.
“what the heck! is the guest already here?”“where is mr.
 kangsok han?”when junghoon asked, the fairy swallowed the piece of cake in her mouth, then flew somewhere.
“wait a minute!”there was another door inside the lounge.
 the fairy started tapping the door with her tiny fist.
“kangsok! kangsok! you have a guest here!”then, there was the sound of somebody stepping forward inside the door.
-your body function is deteriorating due to unknown energy.
* all stats decrease.
 (-3)

it meant they were getting closer to kangsok.
soon, the door opened.
-your body function is deteriorating due to unknown energy.
* all stats decrease.
 (-4)a man in a black shirt appeared.
 at a glance, he was somewhat different from a typical man.
regardless of whether he was handsome or not, there was some kind of halo around his body.
was it because of his mood? or was it because of the system?the message that came out next was even more shocking.
-you are facing a man with godly stature.
* since you are fully qualified, you can face the man with godly stature.
‘godly stature?’-the power of ‘demigod’ suppresses your strength.
* all stats decrease.
 (-5)sungwoo could not help but be embarrassed.
 demigod meant a semi-god or half-god.
in other words, it meant that he was similar to a god.
“necromancer, you have just found my identity, right?” kangsok smiled faintly, but sungwoo didn’t say anything.
‘no.
 1 guy is a god?”of course, sungwoo didn’t take it at face value.
‘is he 6 stars then?’if he wasn’t a real god, it meant that he exceeded certain conditions within the system.
 something more than 5 stars.
whatever it was, an unexpected situation was unfolding at the moment.


 