\section{chapter 272}






 [item information]-name: unknown egg-class: unknown-category: ‘exclusive item for the ‘dragon knight (★★★★★)’-effect: unknown-description: don’t be disappointed by looking at the shell.
 if you protect this egg, the moment something breaks out of the shell, your destiny will change.
woooong- woooong-as expected, the egg was already responding.
 just like a heartbeat, light vibrations were ringing at regular intervals.
 what felt like a cold stone disappeared and was now replaced with something that felt like a strong vitality.
-the ‘unknown egg’ will hatch soon.
 (47:59:59)a dragon was supposed to hatch exactly in two days.
 sungwoo had been expecting it for a long time, but he felt a bit embarrassed when he witnessed it right before his eyes.
‘when a dragon is born, what should i feed it?’dragons were far from ordinary pets such as dogs and cats.
 he could not ask around.
‘well, my occupation is not a dragon knight, so i don’t have any information about it because i got it by accident.
’he didn’t get this dragon formally, so there was nothing like a manual.
while he was pondering over it, he suddenly recalled somebody.
‘ah, heyon’s advice might be helpful because she has experience raising a griffin.
’as a griffin rider, heyon has been raising the griffin, gust, the creature of an alien world, for a long time.
 so, he thought that she would be able to give him some good advice, although it might not be the exact solution.

“now, let’s go back to suwon.
 by the way, how did you deal with the spectator?”before he fought against the world eater, sungwoo ordered minsok to chase the unknown players.
“well, two of them ran away, but i captured another guy, but he passed out.
 i think i hit the back of his head too hard…”“good job.
 let’s deal with urgent matters first before we interrogate them.
”“got it.
”after saying goodbye to the king of the great mountain, sungwoo and his party immediately headed to suwon.
there was still time for the egg to hatch, so they needed to go back to their headquarters and take some rest.
***large-scale construction was underway in the suwon village.
 they were constructing the external walls and magic turrets, which they had planned a while ago.
“if you put them in the spaces marked on the floor, the captain will build the walls with his skills.
 please stack them well so that they don’t get out of the compartment.
”“hey, move the brick material mixed with troll blood here! over here, not there!”it was a massive civil engineering project with a large force led by muyon, the “high architect.
”muyon had “automatic construction” among his skills, but they had to move materials to a certain place manually.
so, sungwoo visited muyon first, who was in charge of the construction work.
“it seems everything is going well,” sungwoo said.
“ah, are you here? thanks to large-scale supplies from daejeon and japan, our construction is well underway without any problem.
”“how long do you think it will take?”
“well, i think we’re going to finish the basic framework in one week.
 of course, we need some more time to check the details after that.
”that wasn’t the only issue that occurred while sungwoo was away.
when sungwoo approached the world tree, kyongsu approached him.
“yesterday, a small group of survivors came to the village.
 there are about thirty people, but they are currently detained outside the invisible border.
 they said they knew you.
”“they know me?”“yeah.
 they are from pyeongtaek.
”in pyeongtaek, there was one group that sungwoo met before.
 they fought with him when the gate of hell opened.
“i think i know them.
”sungwoo visited a group of survivors waiting outside the invisible border.
 they were escorted by the world tree camp, but they were not yet allowed to enter the invisible border.
“ah! necromancer! do you remember us?”“sure, i do.
”“thank you.
 i’m sorry to have come like this.
 i’m afraid we’re causing inconveniences to you…”“not at all.
 welcome.
”currently, the large construction required more manpower, and they had a clear background.
 sungwoo decided to accept them.
“kyongsu, please take care of these people.
 i have something urgent.
”“okay.
”sungwoo had no time to exchange formal greetings with them because he had to pay attention to the dragon’s egg right now.
***sungwoo took out the unknown egg in front of the world tree.
woong-woong-woong-a faint heartbeat was heard from the egg.
 the egg would hatch in the next 43 hours.
‘if this is hatched, one of the conditions of the origin of the race, aka myth quest, will be met.
’of course, more time was still needed to meet the remaining conditions, namely the “complete” stage of the world tree.
-the world tree (stage 1 of maturity) is growing.
 (41%)the world tree was only in the first stage of maturity.
 it was not known how many stages of maturity it had, but it still seemed to need a lot of time to reach the completion of its maturity.
‘until then, let me focus on the dragon.
’right now, sungwoo couldn’t know if the baby dragon to be hatched would be helpful or would be an unexpected headache for him.
‘because i didn’t obtain it formally, i don’t know what kind of penalty there will be waiting for me.
 for example, the dragon might try to disobey or beat the owner…’as a result, sungwoo was ready to fully prepare for the worst scenario.
sungwoo called heyon and asked her how to raise the dragon.
he asked her about how to feed it first.
“feeding?’ she asked, then scratched her cheek in embarrassment.
“well, in the case of gust, it’s predatory, so i used to grind meat to feed it when it was a baby.
 since the dragon won’t need breastfeeding, i think you should do the same thing as i did.
”then, she continued after thinking about it a little more.
“oh, you might see a message that the dragon is full.
 that’s what happened to me.
 and…”

she tried to think of other ideas as much as possible to be helpful to sungwoo.
“ah! one more thing! although it’s a baby, it’s still the premier monster, so it might smash everything before its eyes.
”“smashing?”that’s something sungwoo had to worry about the most.
“griffin used smash floor paper, furniture, and other stuff in the house.
 man, when i think about it, i still feel terrible.
 i’m afraid the dragon might be more violent.
 you had better not expect it to be docile.
”“i’m sure you’re right.
 i think i have to be ready for that.
”“am i right? right?”she was happy that her advice was helpful.
 like she said, even if it was a baby, it was a dragon anyway.
 it could not only break household belongings but also harm the world tree.
 so, he needed a separate facility to isolate the baby dragon from others.
 it would be sort of a cradle and fence.
sungwoo asked muyon to take some time to discuss this matter.
 although he was busy constructing the castle wall, he had to make a nest for the baby dragon first.
muyon seemed pretty embarrassed at his request.
“well, what kind of cradle should i make? i watched heyon raising gust right next to her.
 man, gust broke everything before his eyes…”muyon seemed just sick and tired of recalling it.
 since gust was a beast, it was obvious he had a very violent temper when he was a baby.
sungwoo said, “as you said, it’s a baby now, but it’s a dragon.
 so, i’m afraid it has a more violent temper.
 it can also grow quickly, so the space needs to be quite wide and very tight, so it can’t break out of it.
”muyon replied, “besides, it should be built without presenting any risk to the baby dragon.
 i think i have to make it with materials that are not sharp if possible.
”“that’s right.
”“okay, let me think a little more about it before making it.
”muyon hastily started drawing up the blueprint for the baby dragon den.


 