\section{chapter 269}

                             




[item information]-name: fire spirit stone (advanced)-grade: legend-category: manufacturing material-description: a magic stone that has a strong energy of fire.
“it seems to be better than the spirit of fire.
”he once obtained a similar item after killing the fire giant in pyeongtaek.
he loaded it on the repeating crossbow to add the ‘ignition’ function.
right at that moment, there was a violent vibration in the ground.
googoogoooo-“vibration?”sungwoo looked around.
 however, no phenomenon could cause vibration anywhere.
googoogoogoo-at that moment, he suddenly looked down at his feet.
 concrete debris trembled and rolled back and forth.
 the vibration was coming up from deep underground.
sungwoo was familiar with this kind of vibration, something coming up steadily and very slowly from a very deep place underground.
the middle of the rubble piled up like a mountain began to sink because of a large hole under it.
‘sinkhole?’and black smoke was arising from that hole.
 the smoke spread widely and formed a huge veil.
 this was also familiar to sungwoo.
“no way…”soon, a huge eyeball popped out of the veil.

“world eater!”this unidentified being, who sungwoo had once met in daejeon, appeared once again.
-you are overwhelmed by the presence of the ‘external world.
’* all stats decrease.
 (-60%)his pupils now moved toward sungwoo.
-the ‘unknown being’ is staring at you.
for some reason, the world eater didn’t attack sungwoo.
 back then, he disappeared with the warning that he would kill sungwoo someday.
‘today is the very day he wants to attack me?’ sujngwoo thought to himself.
sungwoo immediately prepared for the monster’s attack, but he was not sure if he could effectively defend against the monster.
as a matter of fact, he lost 60% of his stats.
 besides, this monster brutally killed dr.
 yu, the head of the evolution society in daejeon, in an instant.
 given his terrifying force, sungwoo felt he might be fighting this monster as he intended.
the next moment a series of messages appeared before his eyes.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
– caution! ‘devil’s gate’ has opened in the affected area.
“what the hell…”at first, sungwoo thought it was a system error.
 but when he turned his head and looked around carefully, he could see that it was happening.

dozens of purple portals, dozens of “devil’s gate” were opening around sungwoo.
whoooooooooo-since they sucked in the wind and swelled, gusts blew from all sides irregularly.
‘even if only one gate is opened, the whole area will be devastated.
 but ten gates are going to open all at once?’sungwoo could not block them at all.
‘i have to get out of here by all means.
’he gave up defeating the terrifying monster.
did the world eater also notice it?-the affected area has been closed due to ‘unknown power’.
 (pyongyang city)to make matters worse, sungwoo’s retreat was completely blocked.
 there was no way for him to run away.
‘how on earth can he shut down the area at will?’after all, sungwoo had no choice but to fight.
 he called back the undead army chasing the remaining monsters.
kook- kook- kook-it seemed as if the monster was sneering at him.
 the devil’s gates were expanding more and more.
 based on sungwoo’s experiences, it looked like hundreds of monsters would soon pour out of the gates.
goooooooooooooooo-the portal began to vibrate.
 intense power flowed from the inside.
kaaaak! kaaaak! kaaaaak!a huge number of demons poured out like a burst of water.
 they fell from the air and hit the ground before raising themselves and charging at sungwoo.
“damn it! they are attacking me already?”the undead army hadn’t arrived yet.
 sungwoo raised his bone shield and repeating crossbow.
no matter how strong he was, he could not confront such a huge number of monsters alone.
 as things stood now, he was destined to perish.
however, at that moment, something huge, mixed with green and brown, fell right in front of the hordes of demons before sungwoo.
 at first, sungwoo thought a building collapsed.
kueeeeeeeeeeeeeeeh-the monsters buried under the massive object groaned in pain.
 the object rose slowly again, and the shadow over his head felt like the feet of a giant dinosaur.
upon closer inspection, it was the stem and root of a plant.
 more precisely, it was a bundle of roots.
 all kinds of thick roots were randomly entangled in the shape of a giant tentacle.
quadddddddddddd-soon, roots soared from everywhere.
 they broke through from concrete floors, crumbled debris and building windows, then got entangled with each other and began to turn into something like heavy blunt weapons.
it looked as if an enormous octopus underground sent out its long tentacles out of the ground and wriggled.
“good!”somewhere a clear voice was heard.
“you’ve done everything cool on your own, but it’s me who played a crucial role like this! i think you can understand my intervention, right?”a black-haired man wearing a white scroll with a huge blue dragon ax in hand was sitting with his legs crossed on a bundle of roots.
 he was holding a long pipe in his left hand.
“well, i’m going to play the king as well as the house owner today…”he was none other than the king of the great mountain.
“then, don’t you think i’m qualified enough to be your neighbor? watch me beat them!”the king slowly woke up.
 when he removed the pipe from his mouth and put it behind his back, a root wriggled and accepted it.
“i wish they could leave us alone, but…”the king grabbed the blue dragon ax with both hands.
“if you guys really won’t leave me alone, what should i do? let me try more!”the next moment, the king lifted his ax while jumping off the ground.
he soared before falling down with the axe, striking down the target like lightning.


his target was the giant eyeball, world eater.
the king of the great mountain swung his ax and hit the giant eyeball right on the mark.
 more precisely, the ax was stuck in the shield around his eyeball.
 cracks began to spread over the gray shield.
“how could you dare sneakily intrude into my territory with that nasty eyeball? you bastard voyeur!”having shouted at him, the king swung his ax again.
clang–as if thin plastic crumpled, his protective shield was torn apart by the king’s ax.
“go back!”clang-at last, the protective shield around his eyeball was ripped apart.
kook! kook! kook!the world eater panicked and hid halfway in the veil.
 for some reason, it seemed he could not exert the power with which he brutally killed dr.
 yu.
at that moment, the king of the great mountain reached out his left hand.
 at the same time, a blue light erupted from his palm.
oohoohooh!that light pushed away the world eater and forced it into the black veil.
-‘the power of the world’ has pushed out the ‘being of the external world.
’then, the black waves that made up the veil disappeared as if it evaporated.
in other words, the king expelled the world eater with an unknown force.
but it wasn’t the end.
kaak! kaak! kaak!apart from the world eater’s forced retreat, dozens of demon’s gates were still open.
just like soldier ants pouring out of an ant den, a huge number of monsters were still crawling out.
rattle! rattle!

 