\section{chapter 346}

chapter 346: jeju island and attack on demon’s cave (10)this chapter is updated by wuxiahere.
com




immediately after the gate of demon’s cave opened, a zombie monster bird grabbed sungwoo’s shoulder and jumped up to where the messenger was on standby.
after getting on the deck, sungwoo hurriedly entered the control room.
“we’re ready to depart!”watching sungwoo come into the control room, kyungsoo shouted.
 he took over control of the control room in this operation.
 a total of 25 people were mobilized for this operation, including the crew in charge of steering, hanho, li wei, black lion, and white wolf.
“the portal has grown large enough! we can pass through it!”seated at the captain’s seat, sungwoo was watching at the front.
 outside the window, the purple portal that opened in the air was growing bigger and bigger with lots of vibration.
 the hole sucked in all the air around the area and created a vortex.
‘the second floor of demon’s cave is definitely different.
’it was the first time he saw a two-story demon’s cave.
 he didn’t know what the concept of ‘second floor’ meant, but it was clear that it was a more dangerous place than a normal demon’s cave.
at that moment, something popped out of the portal.
 it was just a head with no eyes and no nose, only a terrible mouth.
 dozens of them started coming out one after another.
“they’re coming out!”“now, get ready to fight!”finally, monster creatures began to appear in droves from the gate of demon’s cave.
“break through them right now!”gugugugugu-as soon as sungwoo gave an order, the entire airship vibrated from exerting its maximum output of the engine that they had turned on in advance, they began to push the giant airship forward.
 then, like a cart full of stuff, the airship moved slowly at first, then accelerated quickly.
woowoowooo!
the flag hanging on the bow fluttered violently.
 the airship got close to the portal suddenly.
“we’re crashing against the portal!”just before the demons popped out of the portal, the messenger slammed into them heavily.
thud! thud!no matter how strong and fierce the monsters were, they could not withstand a head-on collision with such a giant airship.
 after all, they bounced back into the portal.
“we’re getting into the portal!”the messenger also tried to enter the portal.
geeeeeeeeeeee-the moment the airship pushed forward into that sticky portal, a bright light burst out as if it was trying to push it back.
 they felt a strong resistance.
 but the portal couldn’t stop this massive airship run by magical power.
 after all, starting with the bow of the ship, its stern was quickly sucked into the portal.
– you have entered the demon’s cave of the alien world.
finally, sungwoo and his party arrived there.
***exploring the unknown always leads to unexpected things.
 if they did not overcome it, they arrive at the only predictable phenomenon: death.
“damn it!”about 20 minutes after entering the demon’s cave, the messenger could not do anything.
“man, we can’t do anything here because we can’t see…”
visibility was nil.
 they could not see anything, literally.
 the black lion was trying to detect something, but it didn’t seem he could do so yet.
kugugugugugugu-the violent sandstorm shook the messenger.
 it was almost like they were diving into rough muddy water, so it was hard for them to come to their senses because they had no sense of direction.
“do you see anything?”“nope!”“i don’t see anything.
 the altimeter doesn’t work, so i can’t figure out where we’re flying.
”the crew didn’t know what to do either.
 all they had to do was slow down the cruising speed as much as possible and wait until they could see something.
kugugugugugugugu-however, they could not see anything other than something hazy like a screen with noise.
 they had headaches and nausea while watching it.
 they might go crazy if they were forced to keep watching it.
“well, as things stand now, we won’t be able to move forward even if we knew the direction…”even if the black lion could find out the direction, they couldn’t move without being able to see clearly because they were not sure if anything formidable was blocking their ship.
the wizards flew ‘magic drones’ and sungwoo also summoned ‘specter’, but they didn’t help much.
“gosh, i already told you so!” li wei groaned, covering her forehead with hands.
 “you know what? they are swirling like this for half a day! this is a crazy place!”since she had an experience of escaping from the devil’s cave, she was aboard the messenger, but it seemed she regretted coming with them.
at that moment, one crew member shouted.
“uh? steer the ship!”everyone turned their heads to the right.
 something popped out of the sandstorm.
“damn it! prepare for the clash!”it was a building.
 they avoided a head-on collision with it because the helmsman quickly steered the ship away.
the right hull of the airship scraped past the building.
 even the slightest friction caused the control room to shake violently.
 if they had turned the ship a little late, they would have fallen into the sea like a ship that hit a reef.
the players in the control room stared blankly at the huge building disappearing to the rear right.
 but no matter how much they thought about it, they couldn’t understand what was going on.
“hey, a building in demon’s cave? it’s true we saw a building a moment ago, right?”“what the hell is this place?”stunned by what they just witnessed, they began to whisper here and there.
‘yeah, it was definitely a building,’ sungwoo muttered to himself.
what he could confirm at the passing moment was a building in a ruined state with all the windows smashed.
 based on that, he could imagine the scenes of a general office building where desks, chairs, computers, and file folders were all scattered everywhere.
at that moment, an unsolvable question came to his mind.
‘where am i?’at that moment, somebody shouted, “we’re starting to see something!”after they passed by the building, they could see something to some extent because something huge was blocking the sandstorm.
 and the identity of the veil was now clear.
 in other words, they were blocked by the shadow of the building.
the messenger was now flying through a forest of buildings.
“hey, where are we now?”

“raise the altitude!”buildings were as menacing as the reefs that appeared in the storm.
 the messenger hurriedly increased its altitude to get out of the huge obstacles then succeeded in escaping from the place by navigating through the skyscrapers adroitly.
“whew! we’re out of there!”without slacking off, however, they watched the buildings disappearing away under their feet.
but they were shocked to find out where they were now.
“sungwoo, this is seoul, isn’t it?”as hanho said, it resembled the scenery of seoul.
 and kyungsoo found conclusive evidence.
“sungwoo, look over there.
 as far as i know, it is a financial center in seoul.
 this place must be kangnam or south of han river!”like he said, it was downtown kangnam.
 all the buildings ranging from those in gangnam station to those in seolleung station were seen vaguely in the sandstorm.
sungwoo turned to li wei and said, “li wei, how was it when you entered the demon’s cave?”as if she didn’t expect to see such a scene, she looked embarrassed.
“well, i stayed only on the ground, and i was so absent-minded that i couldn’t see clearly, but i think i was in shanghai.
”sungwoo stood up.
 then, he approached the window and checked out the outside once more.
“then, is this place part of the earth?’li wei approached sungwoo and said, “well, i guess so, but this is not the earth we used to know.
 the real shanghai i know was not like this, but seoul is still intact, right? it’s definitely a different space.
”

 