\section{chapter 320}

                             




huge roots and vines filled everything inside a 35-story building made of concrete and reinforced steel.
 they sprung up from the basement, blocking the windows, and tightly wrapping the walls and columns.
 thump! thump! the bombardment against the building continued.
 the enemies intended to use flying weapons to destroy the building.
 the building shook as if it would collapse at any moment, but it would hold out for 11 minutes because the roots were firmly supporting the entire building.
 “their bombing has stopped…” when jisu said that, the king of the great mountain gently opened his eyes.
 sitting cross-legged in the middle of the building, he was energizing the roots at the moment.
 “they realized that attacking so recklessly like that would take more time.
 they know how precious time is now…” although jisu and her party preferred to hold out even one more minute, the enemies wanted to finish the battle one minute faster.
 apart from victory or defeat, the battle in seoul was a ‘race against time.
’ “but the fact that they became so quiet…” jisu gently closed her eyes.
 she expanded her senses and examined the situation outside the building.
 “well, it means that they have hidden intentions.
” the enemies were still hovering around the building.
 unlike when they were determined to blast the building with flying weapons, they were now moving very secretly.
 ‘they are moving while muting their footsteps as much as possible.
 they are ninjas!’ the king of the great mountain also noticed their movement.
 “exactly.
 they have decided to penetrate our area.
 so, please understand my arrogant posture like this because i have to pay attention to supporting the building all the time.
” the king was using all his power to control the roots.
 nodding at him, she drew his sword and said, “don’t worry.
” and she stood in the middle of the dark corridor.
 beyond the darkness was the main gate of the building.
 she stared at the gate.
 she could not check it out with her naked eyes because there was no light, but her sharp senses vividly reproduced the entire space.
 ‘they have come in.
’ jisu turned her wrist holding her sword to loosen its muscles.
 “jisu, they just took off the roots and came inside the building.
 let me continue to regenerate the broken holes, but i can’t keep stopping them like this, so you have to fight them.
” then, the king’s eyes turned to the two tigers behind his back.
 “just assume you’re dead when you go out and fight.
” “yes! of course!” “i will sacrifice my life!” instead of the king who could not move, the two tigers stepped forward.
 they stood side by side on both sides of jisu, with a huge sledgehammer on their shoulders.
 then, he stared into the darkness of the hallway.
 at that moment, a breath of wind blew in and wandered the hallway.
 it meant that the entrance of the main gate was opened slightly.
 the two tigers pricked their ears attentively.
 jisu opened her eyes wide.
 she slowly raised her left hand and put on the ghost face mask then held her breath briefly.
 suuuuuuuuuuuuuuuuu- this time it was not the sound of the wind.
 this was the sound of their footsteps disguised as that of the wind.
 grrrrrrrrrrrrrrrr- when the two tigers exposed their teeth, their heavy roaring resonated throughout the hallway.
 obviously, they sent a warning to those who came inside the building.
 it was also a warning to the friendly forces that if they dared to approach, it would be inevitable for them to collide.
 ‘they are coming.
’ what came next was obviously their collision.
 something flew in the dark in the hallway.
 it was a heavy leather pouch.
 “it’s a bomb!” the tigers shouted.
 it was a bomb bag.
 they struck the hammer to the floor.
 then, a green shield bounced off the floor and encircled them.
 however, jisu made a different choice.
 ‘if we let them take the initiative, we are going to be driven into a corner.
 we can’t hold out long here in that case.
’ in an instant, a blue flame rose above her shoulder.
 at the same time, she jumped off the ground.
 she got out of the shield and ran toward the darkness in the hallway.
 bang! bang! bang! an explosion was heard behind her, scattering pieces of iron in all directions.
 she was still within the striking range of the enemies.
 dozens of pieces of iron were being thrown to rip her apart.
 she could feel that her neck, back, and pelvis would be smashed into pieces when hit directly.
 so, she had to lie flat on the floor.
 but she couldn’t stop here.
 hwaaaaaaaah! she swung the sword to emit the flashes of the blue blade.
 dozens of flashes were shot toward the narrow corridors, ripping the roots tangled in walls and ceilings.
 when they made roaring noises from the walls, those faces hidden in the darkness were clearly revealed, stricken with fear.
 she wielded the blue blade of the sword against them.
 “ahhhhhhhhhh!” “argh!” the flashes of the blue blade killed the ninjas in black clothes hiding between the roots mercilessly and disappeared at the end of the corridor.
 it was a perfect stroke.
 “ugh!” but jisu was also hit, with blood coming from her shoulder and waist stuck by pieces of metal.
 no matter how fast she ran, she couldn’t avoid the flying fragments of the bomb.
 but she adjusted her position without caring at all.
 when she was done slaughtering a group of ninjas, their blood gushed into the air, then came down into her sword.
 -‘wolfberg’ absorbs the enemy’s blood.
 (total 5)

temporarily increases muscle strength and agility (+5) her viking sword “wolfberg” began to take a peculiar effect with blood.
 in addition, jisu also prepared for a full-scale hunt.
 -you have activated ‘hunting instinct’.
when the battle lasts for 120 seconds, ‘hunting start’ opens.
 her eyes were torn vertically, scanning the darkness.
 “whew…” there were corpses scattered in the corridor where the blue blade of her sword swept through.
 but not all of them were killed.
 “kill that bitch!” “tear her right away!” those who escaped her attack crawled out of their fellows’ corpses.
 they were a total of 11.
 they threw shurikens at jisu at the same time.
 two of them even lifted ‘hand cannons,’ which were very lethal in a narrow place like this.
 bang! bang! jisoo struck back their shurikens then turned her body round to get out of their attack range.
 however, the corridor was too narrow for her to avoid all the iron beads scattering widely.
 “argh!” several iron beads brushed past her neck and shoulders.
 one of them crushed her left collarbone.
 she felt pain and hotness all over her body.
 “what are you doing? stop her!” but when she swung her sword, two guys’ necks were cut at once.
 -‘wolfberg’ absorbs the enemy’s blood.
 (total 7 people)

temporarily increases muscle strength and agility (+7) right after that, she pushed the falling enemies to the side then penetrated the enemy line and nullified their rifles.
 spitting out curses, they fired hand cannons and drew swords.
 but it was too late.
 when she swung her sword twice; their four arms were cut off at the same time.
 they instinctively stepped back but got entangled back and forth in the narrow corridor, creating a huge mess.
 “kheeeek!” and she beheaded two more in the blink of an eye.
 puck! puck! she brutally killed them one after another, as if she were a wild cat attacking a chicken coop at dawn.
 “damn it! ignore that bitch and infiltrate into the building! kill the guy making the roots!”

 