\section{chapter 267}

                            in the meantime, the king of the great mountain approached jisu.





“ah, i’m sorry i couldn’t tell you this in advance…”having said it, the king took out a boiled potato from the bag the tiger was carrying.
“actually, it’s not the monster emperor alone that we have to pay attention to.
”“what do you mean?”chewing the potato, he said, “world eater.
”he mentioned that unexpected monster all of a sudden.
he continued, “i expect that monster will appear on the battlefield this time.
”the salamander stretched his right hand to the side.
 at that moment, a flame arose from his wrist and burst out like a breath.
quaguaguagua!the concrete was engulfed in the flames, leaving a long trace of it as if it were overturning a sandy beach.
 and on top of it was a sword.
cheejeeeeeeee-as if it was made of magma, a reddish sword was stuck in the ground, releasing gray smoke.
soon, the sword flew to his hand.
 it was a huge sword, at least two meters.
“let me rip you apart before roasting every part of your body,” shouted the monster.
this time sungwoo took out an unfamiliar weapon.
 it was the “flail” he had obtained by killing the red rider during the battle in pyongtaek.
booooooong!the salamander charged at him.
 he aimed his sword at sungwoo’s head, but sungwoo avoided his attack by stepping back.
 his sword struck the concrete debris.
thud! puck!the moment the sword hit the ground, flames soared from the front and melted everything nearby.
 sungwoo threw himself to the side, leaving a large trajectory to escape the flames.

sungwoo did so deliberately.
booooooong!the monster jumped off the ground.
 because the iron mace was attached to the tip of the chain, sungwoo could not block him, so he had no choice but to swing it in the same direction.
clang! clang!they clashed only twice, but sungwoo had to step back first.
 although sungwoo’s muscle strength was good enough, the salamander was stronger than him.
each time sungwoo clashed with him, his flail flew back and returned, as if hitting a ball tied to a string.
‘man, this monster’s so strong!’sungwoo found his hand torn and bleeding because of the enormous impact of the clash.
 but he had no intention of avoiding the monster’s attack.
now, all he had to do was clash with the monster three more times.
clang!‘two more!’then, the monster struck the ground, firing a series of flames.
 sungwoo pretended to barely avoid the flames by deliberately stepping back.
at that moment, the monster thrust at him with the sword, but before it touched his stomach, sungwoo’s flail struck the top of the sword, blocking it.
clang!it was sungwoo’s turn to counterattack.
he turned the flail once quickly then lifted and struck his head hard.
 the monster defended by lifting the sword with tremendous resilience.
but, at that moment, sungwoo’s flail turned into a purple chain and wrapped around the sword.
 the flail and the sword got entangled and fell on the ground.
 then sungwoo’s other weapons were dragged onto it like a magnet.
the salamander looked down at his “sealed” weapon with a frustrated expression.
“what the heck is this?”[item information]
-name: fighter’s shackles-class: hero-category: blunt object-effect: when you clash with the enemy 5 times, the ‘shackles of the fighter’ skill is activated.
 it ‘seals’ your own and the enemy’s weapons for 5 minutes.
“do you like to fight bare-handed?”clang!when the monster was hesitant, embarrassed by sungwoo’s unexpected question, sungwoo kicked his knees.
“kueeeeeeeeeeeh!”while he was staggering, the monster swung his fists violently at sungwoo.
however, sungwoo was not there.
 he appeared behind the monster in his shadow.
 besides, his hands were already covered with a knuckle made of bones.
“damn it! when did you do that?” the monster muttered, startled.
sungwoo punched his side.
puck! puck!sungwoo punched him twice.
“kheeeeeeeeeeeeeeeek!”because he was a monster that got the title of emperor, the durability of his body was enormous.
 however, since sungwoo was also a player who gained the status of deity, his strike was devastating.
 while the monster was staggering, sungwoo prepared another powerful strike.
-the ‘twilight raid’ has begun.
sungwoo’s body was covered in black smoke in front of the monster.
goooooooooo-then, sungwoo charged at him right away, swallowing up his body, and throwing him down to the ground.
at the next moment, his body was shackled by 20 ghosts’ hands.
 sungwoo stood tall right before him and threw his punches ruthlessly.
punch! punch! punch! punch!sungwoo punched him for only ten seconds, but his face was covered with wounds.
 he seemed to have suffered more damage than when he was trapped under the collapsed hotel.
eventually, he helplessly collapsed.
“kuuuuuk…you bastard! ptui!”plunging to the ground, the salamander spat blood.
“who the hell are you?” asked the monster.
sungwoo retorted scornfully, “hey, you said you were not curious a little while ago, right? did you change your mind?”incensed by sungwoo’s insulting words, the monster raised his head.
 he glared at sungwoo with a murderous look.
 he was not yet ready to give up fighting.
“so, what brought you here, bastard? what the hell do you want?”“what i want is just one thing,” sungwoo replied scornfully.
 “it’s your bones.
”the monster was startled while he was burning with a desire to kill sungwoo.
the salamander’s body began to expand.
 then, as if a volcano erupted, an enormous amount of magma began to erupt from within his body.
pusheeeeeeee!sungwoo pretended to step back as if he couldn’t overcome the intense heat.
the magma, which flowed like a liquid, soon formed a shape like a giant lizard made of clay.
-the field boss monster “salamander” has appeared.
at that moment, a 30-meter magma lizard raised his head.
“grrrrrrrrrrrrrr- do you think you can strike me down with your punches?”

the salamander, who had been maintaining human form until a moment ago, revealed its original appearance.
 what they commonly called “page 2” began.
 the monster now got on his high horse as he wanted to use his full force to smash sungwoo immediately.
however, sungwoo was not swayed by his terrifying movement.
rather, he nodded, watching his terrible looks.
“yeah, you’ve got the bones that i want!” sungwoo shouted.
“what?”what sungwoo wanted was not human bones.
 it was the huge bones inside that monster-like body.
“good.
 you should have appeared like this from the beginning!”“grrrrrrrrrrrrr- it looks like you haven’t figured out who i am.
 this is what i look like.
 i’m different from when i wielded the sword in the form of a human body!”each time he opened his mouth, the magma dripped from his body.
 he kept huffing and puffing before opening his chin toward sungwoo.
 a fireball was seen boiling in his throat.
it was breath.
fuhuahuahua!sungwoo threw himself to the side and avoided the column of fire he was emitting.
at the same time, he took a fan out of his pocket.
[item information]-name: bi hyung’s fan-grade: myth-category: wand-effect: increases magic immunity (+15%).
 you can control the soul of the dead (ghost).
 (maximum 10) the ghost’s performance varies depending on the user’s ‘affinity for the tribute of death.
’-description: it contains the spirit of ‘a man who controls the ghost.
’finally, the time had come for sungwoo to experiment with this newly acquired item.
 sungwoo summoned some of his souls as ghosts.


 