\section{chapter 226}

                             




the chat window of the official channel was getting hotter and hotter with the watchers reacting to the news that one of the “top ten strongmen” of the korean server stepped forward.
“um…’however, even though hyunmin approached, akira, who already came to bexco square in advance, looked sullen.
 he sat cross-legged on the bench, with his chin resting on his hand but didn’t even move.
eventually, hyunmin drew the big sword and opened his mouth first.
“i am hyunmin jang, the leader of the hwarang guild against which you mounted a terrorist attack.
”hearing that, akira yawned, totally ignoring him.
“uh? welcome, small fish of the korean server!” akira shouted.
“what the heck did you say?”when hyunmin reacted with a stiffened expression, akira scorned him as if it was fun.
“well, since you have decided to confront me to save your dying organization, let me commend you for that, so let me kill you without pain.
”having said that, akira stretched then picked up one of the four swords leaning against the bench.
“oh, i forgot to tell you this, but i can’t guarantee i’ll kill you without any pain because i like to cut from the outside.
”akira stretched again and stood up.
-the duel begins! (10 seconds to go)the first one-on-one confrontation between the two began with the whole world watching them.

hyunmin used enhancement skills unique to the paladin.
 all kinds of magic circles were laid under his feet, causing multiple effects.
“are you done?” akira scorned him again, but he became calmer.
“no, i’m not done yet.
 my attack only ends when i kill you.
”“hey, i’m sick and tired of such a cliche.
”the four-star paladin occupation possessed solid defense and attack power, so anybody with that job had more advantages than his opponent in a one-on-one confrontation.
because of that, hyunmin never thought he would lose to him in this situation.
“you die!”the two began to collide violently.
clang! thud!but the roaring sound didn’t last long.
hyunmin, ranked 8th in the korean server, lost his left hand when akira swung his sword for the fifth time.
 without screaming at all, hyunwmin quickly lunged at him with his sword, but akira got around him and cut his ribs and knees successively by pointing at the small gap between his armor.
 the cut was very deep.
 however, he didn’t collapse because of paladin’s defense power and spirit.
 he thought he could kill akira with one stroke, no matter how he was attacked.
 puck!at that moment, his right ankle as well as its armor covering it was severed entirely.
“argh!”did akira possess skills that nullified hyunmin’s defense power? hyunmin, the paladin’s body, decorated with all kinds of magic, was cut by akira’s sword.
hyunmin couldn’t stand on the ground any longer.
 he lost his balance suddenly.
 even before he collapsed, however, akira lifted his sword and cut his neck right away.
all this happened so quickly that nobody watching this one-on-on match could figure out what happened.

hyunmin’s fall also meant the impending fall of the hwarang guild.
“uh? is it true that he was already beheaded? i thought he was still fighting…”even though akira won, akira’s face was full of irritation.
-japanese server “yamato’s sword” wins!-the ‘victory buff’ is given to the japanese server!* increase attack power for 2 hours (+30%)the players on the other servers cheered for the strength of the japanese samurai, but the korean server was thrown into chaos as well as shock.
 it was even more shocking to them because the 8th strongest man on the korean server lost to his japanese counterpart.
akira put the sword on his shoulder while looking at the drone camera, the official channel’s camera, capturing all these scenes from the sky.
“hey, kor-157, if you are watching this fight, listen to me carefully.
 i will be waiting for you while cutting open your colleague’s stomach.
”-from now on, ‘free battle’ begins for 2 hours.
“what the heck is this? sungwoo, i can’t believe this.
 what happened a moment ago is real, right?”“…”even the players of the world tree camp could not believe their eyes.
 they could feel keenly that the japanese master samurai, akira, perfected his sword skills in action.
shortly after the shocking showdown was over, sungwoo received two messages.
 the first came from junghoon.
 junghoon said he also took this korea-japan event seriously, so he would prepare for the contingency situation after the japanese server occupied busan.
 he seemed to want sungwoo to join his operation.
“sungwoo, how should i reply to him?”“i’m sorry, but please tell him that we’re going to go to busan soon.
 if he wants to join us, ask him to let us know.
”the other message came from the hunter company’s president baek.
 he even came directly to the suwon village.
“whew! necromancer, i have successfully carried out the mission you gave me.
”finally, sungwoo headed out to bush to confront the japanese server.
***the quest of the korean-japan war drove the entire korean server, not to mention the hwarang guild and the world tree camp, into an emergency because they would never know how far the repercussions would reach if they lost to the japanese server.
however, as the history of the countries’ fights shows, the japanese server wouldn’t be able to predict an easy victory.
therefore, jungwoo thought that he was not going to ignore what was happening in busan.
 he summoned the ranking officers of his allied forces and ordered a total mobilization.
“we must be wary of foreign servers influencing us within our servers.
 call your troops right away and mobilize all the allied forces to prepare for the japanese server’s attack.
”“okay!”“we must be ready to go to busan in an emergency.
 if the hwarang guild holds out longer than we think, we may have to build a line of defense with them.
”at this point, some ranking members questioned junghoon’s direction.
 among them was kangyun lee, the leader of the daehakro group.
“uh? are you now saying that we should join hands with the hwarang guild? as you know, they belong to the demon camp.
 of course, the situation is so urgent, so…”as kangyun said, the hwarang guild in busan was a member of the demon camp, so they were the hostile forces in the eyes of junghoon’s forces who belonged to the angel camp.
in some respects, even if kangyun thought their defeat would not be a loss to the angel camp, nobody could blame him for his selfish thinking.
junghoon shook his head firmly.


“this is not a matter of simply joining hands with them.
 don’t you think the system is driving the whole korean server into destruction?”“ah…”after the world quest was issued, the system seemed to force other servers to take hostile action against the korean server.
“as you know, we need to save the korean server for us to win and survive.
”“to save the korean server? oh, i understand.
”junghoon turned his head to his deputy commander minhum, “minhum, tell the players of the demon camp in uijeongbu who surrendered a while ago that if they participate in this battle, we will waive their detention period and pay the legitimate compensation for their efforts.
”“sure!”to save the korean server, junghoon intended to mobilize as many players as possible within the korean server because even if he didn’t need them right now, he would need contingency troops if he confronted the worst situation someday.
after junghoon wrapped up the meeting, he still couldn’t stop thinking about one thing.
‘why is the system trying to make the korean server the prey of foreign players around the world? just because of the emergence of the third camp?”he could not know the reason, but in his mind, he thought there might come a situation where the angel, demon, and the world tree camp would have to join forces to confront the foreign intruders.
‘if that happens, we three camps have to be united, which is not impossible.
”their combination could produce a positive influence, which was also junghoon’s goal from the beginning.
his goal was not to pit each camp against another but to integrate them as a strong joint force to confront this mysterious phenomenon.
‘but even in a moment like this, the real problem is…’the biggest problem was the angel statue.


 