\section{chapter 417}

"now, finally, the hero of the korean server, necromancer, defeated the emperor who unified the chinese servers.
 that means he has grabbed the steering wheel of the world.
 how and where will this world be headed in the future?"




then reporter ahn paused for a moment, creating a moment of tension, then continued, "as he said, can he create the governing body and unite the world under his leadership? can he find out the cause of this game, its truth, and dark secret? can he really find what caused this whole event, whatever it is?"reporter ahn shook his head and said, "i don't think he can't do it yet.
 there is one thing we forgot because of the fierce battle that unfolded before our eyes.
"soon two photos appeared on the big screen behind ahn's back.
one was a map of south america and the other was a black giant soaring above its rainforest.
"this photo, which was secretly airlifted by our 'reporter ahn's apocalypse news intelligence team, shows amazon, the brazilian server in south america.
 i think all of you have noticed what it is.
 some time ago there appeared a world message that announced the advent of the demon king.
.
.
"when reporter ahn clicked the remote control, the map of south america disappeared from the screen, and another picture was uploaded.
it was the huge world tree, and the fortress walls surrounding it, which was a distant picture of the world tree camp.
with the world tree camp on the left and the demon king's castle on the right, it was reminiscent of a confrontation between two camps.
 "well, i, reporter ahn, would like to guess cautiously if it's the harbinger of the next war or if the just ended fight was only the start of a long war.
"at that moment the two photos disappeared with a burning effect.
"now i would like to end my apocalyptic news and live war report here.
 i'll see you soon in our war analysis program in a moment.
"***after they already went through several large-scale wars, their post-war recovery work was carried out perfectly.
 having lost the emperor and several commanders, the chinese forces surrendered immediately.
 it was natural that they did so.
 after that, sungwoo's control over the chinese server was carried out without any trouble.
 
above all, it was decided that the players of the 'chinese 2 server' who remained loyal to li wei would raid beijing and open a large-scale portal to suwon.
the source of this content is lightnov‌elworld.
c­om"necromancer! i'm going to occupy beijing and take control of it, so don't worry.
 just get rid of your opponent here!"having said that, li wei disappeared through the portal.
about an hour later, kyungsoo came to sungwoo and reported about the situation.
 "we have taken a total of 5,441 people as prisoners of war.
 we have retrieved all the gold they had.
 they had a total of 604,511,200 gold.
.
.
"turning over a page of the document, kyungsoo continued, "the emperor's main camp in beijing has also announced their surrender.
 it looks like they had two or three thousand guards, so it was inevitable that they surrendered.
 so we also collected lots of gold from them.
"since the war was over, it was time for sungwoo to take the booty like gold.
 this time it was huge, compared with what he obtained in the past.
"well, according to li wei, they had about 450 million gold.
 by the way, they were not just rank-and-file soldiers, but players, so we're still collecting their gold.
"as a result, it was more than 1 billion gold that they collected from the chinese players.
 but this was only the beginning.
 "kyungsoo, please remind li wei that they must be items for collecting taxes, like the 'treasury of oath' in our possession.
 if she can find it, she will be able to collect more gold.
""oh, i guess so.
 let me deliver your message to the communication center right away.
 and we have a report from the 'expeditionary fleet' that had been dispatched to collect the supplies…"kyungsoo turned over the document again and said, "they say they occupied key facilities in beijing and secured all items, gold, and supplies that they had stored in the warehouse.
 they are going to open the hypergate and collect them today.
 man, i think we have to make the entire northern area a warehouse.
"not only gold, but all kinds of items and supplies were flowing in.
sungwoo nodded, stroking mir.

"as expected, a war costs lots of money, but we can make much more if we win…"but this was not the end.
[colony list]1) china's 1st server.
updated from lightnovelworld.
c‌om- collection rate: 50%- total income (gold): 150,501,2002) china's 2nd server.
- collection rate: 10%- total income (gold): 34,500,0003) china's 3rd server.
 - collection rate: 10%- total income (gold): 31,000,200as the chinese server, which lost the war, became the "colony" of the korean server, sungwoo had the right to collect gold.
 this was going to be a source of huge money, which meant that a certain portion of all the gold earned by all players on the korean server would be automatically deposited into sungwoo's account.
'wow! i've already collected so much gold in just an hour after the chinese server has been colonized.
 i think i can expect much more in the days ahead.
'but it wasn't over yet.
[item information]- name: safe of oath- grade: special- category: finance- effect: a portion of the gold earned by the 'contractor player' is automatically deposited.
- description: you can sign a contract by placing your palm on the safe.
 the safe deposit box owner can set the 'collection rate', and a certain portion of the gold earned by the contractor is automatically deposited into the safe deposit box.
follow current novels on lightnovelworld.
c­om* collection rate: 5%* registered contractors: 14,526* current gold: 1,453,455,048before the war, sungwoo forced all players of the allied army to sign up for the ' 'safe of oath''.
since they became full members of the world tree camp, they had an obligation to pay taxes from now on.
as a result, in addition to the 'world tree camp operation fund' accumulated before the war, the gold sungwoo obtained during the war was piled up in the 'treasury of oath,' which snowballed in an unprecedented way.
'and the gold i currently have is 2 billion.
'

as a result, the funds available to the world tree camp right now reached a whopping 4.
6 billion gold.
"kyungsoo, we need to send trustworthy people to all the shops in the area to exchange a total of about 1 billion gold for items.
"there were many ways to obtain the materials, but purchasing them at the store was the easiest way.
 of course, it was a random acquisition, but about 1 billion gold would be enough to get all the necessary things.
"pardon? one billion gold? ah, we have no problem lavishing such a huge amount of gold now…"sungwoo said with a nod, "if we win the next war, we'll have more money.
 but there is no guarantee that we will win the next war, so we have to invest as aggressively as possible.
"as kyungsoo was about to leave after the briefing, sungwoo stood up and said, "oh, please call master hearst when you see him on the way.
"sungwoo was thinking of giving the blacksmiths a chance to flex properly with the huge amount of gold and materials.
 after the game started, modern science became obsolete, but there was 'magic engineering' that could replace it.
'magic engineering will become more important in the future.
'after the world regained some stability, the role of magic engineering was getting bigger as the infrastructure was built for them to focus on research and production.
sungwoo was planning to invest generously in them.
visit lightnov‌elworld.
c‌om for the best novel reading experience"yeah, no matter how great a dragon is, they can't catch up with the technicians that we will invest…" you can also read this novel on the more advanced platform lightnovelspot.
com

 