\section{chapter 318}

"if we are attacked like this, we're going to be the only ones left here.
 if all of the enemy troops surround us, we can't run away anymore.
"




only 30 minutes had passed since the start of the war, but jisu and her party were now in a dangerous situation.
 the enemies already occupied the entire battlefield of seoul and closed in on jisu and her party.
 if time passed a little more, it would be almost impossible for them to escape at all.
'they are driving us into a corner slowly.
 and they know they will win in the end.
'it was as if a horse ran away but would be caught at a dead end by a tiger.
"we still have to hold out here as much as we can.
 isn't that the only way?"jisoo nodded and said, "then, we should die as late as possible.
"it wasn't their death that they feared.
 however, they were afraid that if they were killed here helplessly, it would have negative repercussions on their allies on other battlefields.
in other words, their death here would be directly relevant to that of their allies, so they wanted to stop such a disaster.
so, their mission was not survival, but holding out as long as possible.
"hum.
.
.
how to die late.
"new novel chapters are published on lightnovelpub[.
]com at that moment, one idea came to jisu's mind.
"we need a place where we can resist as long as possible at the last moment.
""place?""it should be a place with all directions blocked so that we can nullify the enemy's siege.
 can you make things like that with tree roots?"the king of the great mountain tilted his head as he touched his chin.

"well, i'm afraid i can't do it with my skill alone, but if i find a solid building and use it, i may make it, but whatever i make, it won't last long.
"everything was the worst.
 but they had to choose the best of the worst.
"whatever you do, it's probably the best way for us to hold out as long as possible.
 let's find a proper place right now.
""haha! then, it could be our graves, so we should decorate it as colorfully as possible.
"the most up-to-date novels are published on lightnovelpub[.
]comjisoo nodded calmly.
 then, the king said with a bright smile, "who knew we would end up like this?"".
.
.
"jisu didn't take his words seriously.
 she just felt that they might not be able to hold out long.
'my prediction won't miss.
'as a matter of fact, her predictions were always correct.
***the situation was not good in suwon.
 although almost all the troops on the korean server were gathered there, they were still inferior to the chinese server troops in size and number.
bang! bang! bang! bang!the most up-to-date novels are published on lightnovelpub[.
]com
they could hold out until now because of the invisible barriers and the castle walls.
besieging the east side of the wall, the chinese troops were unleashing huge firepower on a single target.
 "the eastern side of the invisible barrier has thinned out! as things stand now, we're not going to hold out even for a few minutes!"in particular, the cannons mounted on admiral baker's fleet were displaying overwhelming firepower.
the baker fleet had only three warships, but they took turns firing at the invisible barriers outside the striking range of the korean server, and as a result, dozens or hundreds of cannons were hitting one target accurately, which was a weird phenomenon.
"damn it! how come they are firing from a distance while using the same airship as ours?""did they modify the airship? i can't understand their attack if they didn't modify it.
"the world tree camp's airship was also built in the "hearst workshop".
 in other words, their airship was obviously the same model as that of the baker fleet, but the baker fleet's airship was better than that of the world tree camp in terms of accuracy, striking range, and destructive power.
"it must be their skill! just focus on holding on!"follow current novels on lightnovelpub[.
]comthe reason the airship of the baker fleet was one cut above that of the world tree camp was that admiral baker's job was "canon operator.
" as a result, he could not only control his cannon remotely but also give all sorts of buff effects.
 the most effective among them was the increase in its striking range.
"i feel really bad as we are bombarded like this…"since the south korean server allies were inferior to their chinese counterparts in every way, they had no choice but to break through their siege and get out, but they were now helplessly bombarded, driven into a corner.
"oh, my god! the invisible barrier has collapsed!"after all, the part of the invisible barrier that was intensively bombed collapsed.
 as part of the invisible barrier melted down, it lost its function, too.
 bang! bang! bang!after several bombings, the elaborately built castle walls also collapsed.
that was, in fact, the moment when their last hope was lost.
"defend the collapsed place!"for more, visit lightnovelpub[.
]combut the enemies began to charge through the gap of the collapsed invisible barrier.
***"ah, it is hopeless! we are certainly fighting well in busan, but it seems we have no hope in seoul and suwon!" reporter ahn announced in a subdued tone.
".
.
.
"although he predicted the victory of the necromancer and his allies until now, his face turned gloomy again.
 the chinese server's forces were unexpectedly powerful.
"in particular, it seems seoul has been ruined completely, as expected.
"reporter ahn felt skeptical about his job out of anger because he had to broadcast the defeat of the friendly forces led by the necromancer, but he opened his mouth again.
"well, they might be able to hold out in suwon, but if the chinese troops who won in seoul moved to suwon, the battle will be finished even before the necromancer arrived there.
"having said that last, he looked at the official channel's broadcast screen blankly.
 his pupils were trembling at that moment.
for more, visit lightnovelpub[.
]com

a bloody fight was going on near the collapsed wall.
 the korean server players concentrated their firepower at the human wave of the chinese troops flocking like a swarm of ants, but it seemed that they were more and more on the defensive.
fortunately, junghoon and his crusader team were defending against them by using his unique golden shield.
 without their defense, the korean server would have been defeated by now.
"ha.
.
.
"just watching the scene made him sweat and let out a long sigh.
"oh my…'subsequently, the walls of other places collapsed, and the scenes of dozens of people being killed at once were broadcast live.
 the chinese warriors now began to charge at them.
 there was no solid barrier like the crusaders team had there.
"man, our friendly forces are collapsing more easily than we thought…"reporter ahn's legs trembled.
 he felt frustrated as if he could not overcome his anger.
 he wanted to hit the chest with his fist.
the most up-to-date novels are published on lightnovelpub[.
]com then, the other walls began to shake.
 the walls that were built up solidly were covered with shields here and there, but they could not withstand the enemies' fierce bombardment for long.
"oh, no! if the three places are attacked at the same time, there is really nothing we can do…"at that moment, the broadcast screen changed.
 "uh?'"what the heck?"

 