\section{chapter 372}

chapter 372: exit from demon’s cave and preparing to conquer china (4)currently, the ‘power of underworld’ that he earned temporarily required the conditions such as ‘bi hyongrang’s fan’ or ‘judge’s mark’, but he might lose it for some unknown reason.





taking all this into account, he decided to upgrade the deity of the ‘king of underworld’ to the regular deity rather than strengthening the power of anubis.
- you are granted a regular deity.
* god of death: king of underworld.
[skill information]- name: the power of the king of the underworld.
- grade: demi-god- classification: passive and active- consumption: 0*for just one hour a day, you gain the deity (divine power) and acquire the power of ‘king of underworld’.
 all stats are increased by (+10).
 you can use exclusive skills.
he finally got two regular deity statuses.
‘if i add it to lich status, my stats go up by a whopping 35.
 it will not be long before i can pull the ultra-heavy bow.
’then, he confirmed the last message about selection.
- choose your level-up card.
.
 stats (random).
 skill (random).
 item (random).
 other (random)
.
 toxic cloud manufacturing (confirmed)he chose item number 5, namely, toxic cloud manufacturing.
 with a big war around the corner, strengthening the ranged magic could be a good choice for him.
- your skill level has improved.
 (basic → skilled)[skill information]- name: toxic cloud manufacturing- grade: skilled- category: active- cost: 50 manawith this skill, you can create a cloud containing poison and pour ‘toxic rain’ over the area for 20 minutes.
 (1-hour cooldown)*it causes an additional ‘abnormal status’ on the target exposed to rain.
 asymptomatic symptoms (20%), respiratory distress symptoms (10%).
according to the description, it was going to be strengthened by skill level, with more use time and additional effects.
“good.
 this is it.
”sungwoo succeeded in increasing his power once more.
while he was heading to the exit of the demon’s cave, sungwoo began to get familiar with the skills of ‘the power of king of underworld’ in his mind.
‘the chinese server doesn’t know that i have this kind of ability.
’he felt he could give them a surprise shock.
***
an airship began to crash with a roar on oreum in jeju island.
 it was the 4th airship of the world tree fleet.
“hey, it’s falling this way! avoid it, everyone!”the no.
 4 airship was partially destroyed after being hit by something.
 something pierced its lower deck and ripped apart some important devices inside the ship.
 it was one monster that tore that huge weapon manufactured by magic engineering to pieces.
“there it is! it’s on the deck of the no.
 4 airship!”a monster was wielding a whip made of vertebrae with hundreds of mouths all over its body.
the final boss monster on the 2nd floor of the demon’s cave, namely its 1st army commander, appeared from the deck of the no.
 4 airship that was falling.
“uh? it’s coming this way!”the monster leaped from the crashing no.
 4 airship while simultaneously swinging a vertebrae whip at the nearby no.
 3 airship.
no.
 3 airship made a hasty turn, but it seemed impossible for the airship to dodge the whip that was approaching as fast as a snake’s jaws.
“damn it!”the moment it was hit, thorns would protrude from within the vertebrae and devastate the inside of the airship.
clang!at that moment, the tip of the vertebrae hit something and bounced back before being distorted.
 thanks to that, the airship barely escaped the monster’s attack.
“valkyrie has appeared!”it was jisu who blocked the attack.
 she floated in the air and watched the commander of the 1st army of the demon’s cave fall to the ground.
“wow! she is alive!”in fact, when the monster appeared, it was jisu who blocked him.
 she fought the monster with 20 einherjars, her subordinate spirits.
however, the commander was different from the gatekeeper of the demon’s cave.
 in just 10 minutes, most of the 20 einherjar disappeared at the monster’s attack, and she also bounced far away from his single strike.
fortunately, valkyrie’s armor had a better defense than expected, so she survived.
 but there was no guarantee that she could withstand the monster’s next attack.
‘i can’t beat him alone.
’the surviving einherjars, including two tigers, floated behind her.
 there were 7 in total.
“lady, be careful.
 that monster is so tough!”the other 13 einherjar already perished.
 even though they were souls, they became partially embodied, so they could not avoid physical damage completely in the actual battle.
“everybody, step back! let me summon you at the crucial time when i notice his soft spot.
 there is no other way.
 we have to wait for the right timing to attack him!”even though einherjars could move faster than when they were alive, it didn’t mean that they could move as quickly as jisu.
“right now, i am the only one who can avoid his attack.
”the commander of the 1st army of the demon’s cave swung the two long whips on his arms quickly.
 also, several long spikes shot out from his whip, breaking everything around it.
‘even if i avoid his attack, i can’t approach him.
’that wasn’t the end.
 hundreds of mouths all over his body spat out acidic liquid.
 if she approached him recklessly, it was certain that she would die from her bones melting.
“then, we trust you.
”the remaining einherjars retreated without saying a word.
 the moment jisu broke through his attack and penetrated deep, they would be summoned near her to deal a decisive blow to him.
“whew…”she grabbed her sword and took a deep breath.
 in fact, she was already hit once.
the monster was really hard to deal with, but she wasn’t scared.


kugugugugugugu-there was a big roar when no.
 4 airship crashed on oreum, but the commander landed it roughly.
 every mouth that hung on his body was open with their tongues darting in and out and drooling.
‘it’s not that there is no way for me to win.
 i can definitely find a way.
’she recalled sungwoo.
 even though the invincible necromancer’s power was overwhelming, he was also put on the defensive while fighting,‘the reason sungwoo was so strong was that he always found a way to win.
’at that moment, one thing came to her mind.
 she turned her head and looked at the king of the great mountain.
“can you restore the shield by supplying mana with the energy of the mountain for the airship that crashed over there?”“uh? you mean the shield?the king of the great mountain could receive mana from the mountains, but he could release mana through the roots, too.
 that meant he could activate the mana-powered device.
“well, it’s not difficult to restore the shield for a short time.
 why?”jisu turned her head again and looked at the commander of the 1st army of the demon’s cave.
“i don’t have time to explain to you.
 as soon as i touch that airship, please restore the shield.
”as soon as she finished talking, the monster sprinted off the ground and stretched out his hands towards her.
two whips rushed towards her.
 she twisted her body, shooting like a beam of light, and narrowly avoiding his attack.
but at that moment a huge number of thorns spurted out from the whips like a stream of water.
 it was the technique with which he crashed the no.
 4 airship with just one single strike.
‘i should reach the no.
 4 airship!’

 