\section{chapter 393}

chapter 393: full control over death (2)sad news was delivered to the ‘spear unit’ of the chinese army, who were preparing for a massive offensive right in front of the invisible barrier of the world tree camp.





“what? i can’t believe that!”what they heard was that the shield unit gathered on gwanggyo lake park collapsed in an instant.
 general lee, the commander of the spear unit, made an incredulous expression.
“what the hell are you talking about? didn’t you just report a minute ago that the enemy troops turned into ashes and scattered around?”“well, what really happened was…”could they believe that the necromancer smashed the white sacred sphere with a single arrow and smashed the shield unit without seeing it for themselves?after all, his deputy held out his cell phone and showed the broadcast screen of the official channel.
“what the heck…”what was being shown on the screen was obviously gwanggyo lake park.
“they collapsed in just a few minutes?”the situation was completely different from when gen.
 lee led the spear unit to the war first.
the place was burning, and a huge number of undead were slaughtering the disintegrated shield unit of the chinese army.
“no way! this can’t happen…”gen.
 lee was dumbstruck by the shocking news.
 he was stricken with panic.
as long as the shield unit was in good shape in this war, the spear unit led by him could launch an effective offensive against the enemy.
 but he could not guarantee the success of his unit’s attack if a huge undead army attacked them from the rear.
“general, don’t you think you should report it to the emperor?”gen.
 lee nodded, with his face turning white.
 then he hurriedly headed somewhere.
“get out of my way!”
the emperor was in the most heavily guarded of the place where the ‘spear unit’ was stationed.
 lots of wizards were always deploying a large-scale shield around his place.
“get out of my way! i’ve got to see his majesty the emperor!”he pushed aside the royal secret service members blocking the way and stood in front of a huge palanquin with ornate decorations.
 at a glance, it was no ordinary kiln.
the kiln moved on its own even without a horse pulling it, and it was larger than a large truck.
 this was also a product of ‘magic engineering’ that reached a very high level.
“hmm, hmmm…”general lee adjusted his outfit correctly and bowed his head toward the door of the kiln.
“your majesty, this is general lee.
 i have an urgent report for your majesty…”even before the general finished rumble!as soon as the words were finished talking, somebody flung the door of the kiln open hysterically.
 then a beautiful royal beauty came out of it.
she began to scrutinize him up and down.
 at that moment, her pupils turned amber and were torn vertically like the eyes of a snake.
- your body functions are weakened by unknown energy.
* all stats will drop.
 (-4)general lee’s body hardened at that moment.
 he felt as if needles pierced every nook and cranny of his body, with him fully naked.
 this was a process he had to go through all the time to meet the emperor, but he was hardly accustomed to it.
after scrutinizing him, the woman stepped aside silently.
“…”checking her expression, general lee entered the kiln.
there was not a man, but a small box inside the kiln.

he bowed before it, with his hands clasped on his navel, trotted along and stretched out his right hand very carefully.
and the moment his hand touched it, he was standing in a different space.
- you have entered the tomb of emperor qin shi huangwhooooo-it was a very dark and cool place.
 and there was a strong smell of incense everywhere.
it was like a temple of black and gray stones, with a very high ceiling.
 and on the left and right, huge statues were standing in a row, holding weapons such as a sword and an ax.
and they were alive.
 when general lee stepped forward, they turned their heads, following him.
kuguk - kookuk-every time they turned their heads, the sound of stones scraping against each other resounded.
“general lee!”a solemn voice rang out from the front, from the high stairs, and general lee answered, startled.
 “yes! your majesty!”someone was sitting on a podium covered with a red cloth in the dark.
 incense was arising around it, forming a thick smoke, adding to his mystery.
even though the emperor was covered with a cloth, general lee did not dare to look straight ahead, so he sat down on his knees a long distance away from the emperor.
“your majesty! i’ve come here because…”“i already know.
”“oh, i see!”how did he know? general lee thought he had been serving him up close in person; he still didn’t know exactly who it was.
“taegam is still alive.
 so go and tell him he has to hold out by all means even by using the ‘secret card.
’ only when you occupy the enemy’s castle will our operation be successful!”general lee bowed his head once more.
“ah, secret card! sure, i’ll convey your words to him!”the emperor beckoned from the veil.
- you are forced to leave by the authority of the ‘tomb’ of qin shi huangthen general li found himself sitting in a huge kiln, not in the secret tomb.
at that moment the woman standing outside opened the door of the kiln.
 then she cast a sharp glance at him.
 general lee hurriedly ran out of the kiln.
“deputy!”then his top deputy who was standing in front of the kiln came running to him.
“yes, general!”“contact the shield unit immediately! the emperor has ordered you to stop the necromancer using your secret weapon! and we are going to begin the general offensive right now!”“understood!”they still had several secret cards to turn the tide.
***the emperor’s orders were delivered to taegam, the commander of the shield unit, through the radio.
“…”as soon as he heard the order, taegam closed his eyes as if he was frustrated.


then he took a deep breath and opened his eyes again.
rattle! rattle!strange noises were heard from all directions.
 it was certain that he would lose in this fight.
 thousands of undead soldiers easily slaughtered the shield unit troops that had already collapsed.
 every time they were killed, more undead were born.
 sungwoo’s lich exerted his power fully, and zombies crawled out of the purple puddle generated in the middle of the battlefield at regular intervals.
moreover, the shield unit could not block the truly overwhelming creature, ‘bone dragon.
’“yeah, that’s the only way i can stop them!”taegam silently nodded, as if he made up his mind, then turned his head to look at his soldiers.
“bring me the second secret weapon!”soon, one of his subordinates came with something like an old box with lots of charms attached to it.
“come together, everybody!”taegam glared at his subordinates fiercely while shouting at them.
startled, they hesitantly came to him.
 they were trembling with fear because they knew what that old box was.
“it takes the blood and souls of 100 men for me to use this secret weapon! you have pledged allegiance to the emperor, so your blood and soul are no longer yours! give it to me without any complaint!”shouting like that, taegam opened the box.
 and he pulled out something the size of a palm from it.
 it was the shell and bone characters carved on a turtle’s shell.
- would you like to use ‘ancient charm (unknown)’? (y/n)an unclear message came out, but taegam didn’t think hard about it.
he chose y right away.
woo woo woo-

 