\section{chapter 153}

                             




“is it difficult for us to capture the ship?”“yes, if you storm it recklessly.
”if the enemies deployed a large-scale shield, it would be difficult to have the undead infiltrate the ship, and the corpse explosion strategy would not work.
 it was a very tricky situation.
of course, sungwoo could try to deplete their mana first, but it was a very inefficient method.
after agonizing over it for a moment, sungwoo suddenly looked toward the sea.
“are there any monsters on the coast around here?”“under the sea?”“yes, i hear that monsters are crowded under the sea.
”“ah yes.
 there are a lot of scary guys out there.
 they gather quickly as soon as they smell blood, but the pirates seem to be sailing away with electric magic.
 why are you asking that?”sungwoo turned to the shore.
“well, if that’s the case, let me go fishing.
”in fact, he was thinking of attacking the pirates from the land, sea, and air altogether.
the container ship, which served as the flagship of the pirates, was moving off the coast of kanghwa island.
most of the troops landed on the island by fishing boats during the mini-game, but there were still a number of on-call soldiers guarding the flagship.
“they are moving out!” heyon shouted.
as if they found sungwoo’s bone wyvern, they picked up speed and started heading north of the island.
 they didn’t want to be noticed by sungwoo, but there was no way for the huge ship to avoid sungwoo’s gaze when bone wyvern carrying him was flying high in the sky.
 and there were still five hours left until the mini-game was over.
they were like a rat in a trap.
when the bone wyvern approached the ship, they immediately deployed a shield.
 a large shield appeared over the container ship like an umbrella.
 with that shield in place, sungwoo could not infiltrate it from the air.
but if he hit the ship under the hemispherical shield, it’s a different story.
 with the waves soaring in the air, a giant sea snake stuck its head over the deck.
“ahhhhhhhhh!!”“it’s a serpent!”it was a “sea serpent”, a twenty meter-long monster, but the shape of its body was somewhat strange.
 hard scales covered its whole body, but its bones were exposed here and there.
 crucially, its green eyes sparkled from within its giant head.

“uh, undead?”it was a monster that belonged to an owner.
when the serpent climbed up the ship and shook its body, the wizards, standing on the deck to supply mana to the shield, were crushed and fell off the deck.
“argh!”“block the serpent! push the monster out!”but it wasn’t easy.
 sungwoo had to put in a lot of effort to catch that monster.
‘it took an hour to hunt it.
”while sungwoo hunted the sea monster, he threw the bait all around the coast in kanghwa island.
 as a result, he could find a “little serpent,” which took him an hour to catch.
 it was so difficult for sungwoo to pull it out of the sea and load it with damage, but the hard-won serpent paid off nicely.
 its huge body completely took over the deck of the container ship.
“the shield is flickering!”and he could destroy the ‘large shield spell’ just by cutting off the mana supply.
like heyon said, the giant shield started to flicker and soon lost its shape.
“let’s land!”sungwoo landed on the deck instantly.
 the game was actually over.
after getting rid of the remnants on the container ship, hanho and jisu joined and began to search it.
“wow! look at this.
”soon hanho came out with something.
 it was a black box the size of a laptop.
[item information]-name: charger (extra-large)-grade: rare-category: other-effect: it supplies current or charges the battery.
 (remaining capacity: 69%)“it was attached to the engine room.
 it seems that they used this to power this big ship.
 isn’t this an energy revolution? there are a few more like this.
”
like he said, if the charger was powerful enough to move this huge container ship, it had tremendous energy.
“got it.
 put it back.
 all the lights in the ship are out.
”“aha? i wondered why it suddenly got dark.
”given that thousands of people were on this ship, sungwoo could obtain a huge amount of necessities, but he found a real treasure.
sungwoo went to the captain’s office.
a gray safe lay on an old iron desk.
 sungwoo pulled out the safe with his bare hands.
because he received all kinds of buffs, he could exercise superhuman power.
and inside it was an item he saw in jahon’s memory fragments.
[item information]-name: devil’s gate-grade: special-category: magic scroll-effect: opens the devil’s gate for 24 hours when used.
-description: it creates a passage that connects with the devil’s gate.
 you can get very valuable items by exploring the devil’s gate, but we recommend that you don’t try it recklessly.
 don’t forget that someone might come out of the door through which you can enter.
 (recommended level 35)it was the same as described in the fragments of memory.
 its original use was a ticket with which to enter the hidden dungeon.
however, because the level for its use was so high, the monsters that appeared were overwhelmingly strong, so it could also be used as a strategic weapon to destroy a certain area.
‘of course, it would be a bigger benefit to use it for its original purpose.
’a hidden dungeon of this level would surely bring about huge rewards.
 however, it seemed too difficult for sungwoo to try it right away.
“what is this?”there was one more thing in the safe.
 it looked like a metal item about the size of a tissue.
[item information]-name: vault of oath-grade: special-category: finance-effect: some of the gold earned by the ‘contracted player’ is automatically deposited.
-description: you can register a contract by placing your palm on the safe.
 the vault owner can set a ‘money collection rate’, and the amount of gold earned by the contractor is automatically deposited into the vault.
* collection rate: 80%* registered contractors: 26* current gold: 13,455,048“wow! this is a windfall.
”it looked like a vault operated by the pirates.
 it contained over 13 million gold.
it seemed that the pirates used these items to collect all the gold earned by their subordinates.
the fact that there were only 26 contractors meant that there were only 24 survivors of the pirates.
 now, sungwoo got to know the number of the pirate remnants hiding all over the island.
‘i think we can collect effectively in the future.
’sungwoo was raising several groups, for example, the seoul metropolitan area alliance with the liberation guild in the suwon village as the main, and even this area in kyodong island.
one of the reasons he patronized them was because they would bring about a lot of gold in the future, and he got a very efficient item for the tax system.
***the players of kyodong island searched all over kanghwa island and succeeded in eradicating the few remaining pirates.
in addition, they secured a huge container ship and dozens of fishing boats and set up a mechanism to monitor the chinese community from time to time by detaining the chinese player xiaojun.
“necromancer, if you leave it to us, we will monitor the chinese side.
”the players of kyodong island, including muyon, took on the role of watchers of the yellow sea.
“we will search the yellow sea by using the ships we have captured, and monitor the chinese side of the community to check their movement much as possible.
”it was something someone had to do anyway.
“if you do, i am really grateful to you.
”

“don’t mention it.
 we owe a lot to you, so we will do our best, it’s our repayment for saving our lives.
”they were rather passive until they were attacked by pirates, but on the occasion of attacking the pirates successfully, they decided to join the metropolitan players’ alliance.
 of course, the reason they did so was that they had total trust in sungwoo.
-the mini-game (korean hopscotch) has ended with the allies’ victory.
-reward is paid.
finally, the final 12 hours passed and the mini-game was over.
 the shutdown of the region was lifted and huge compensation was paid.
-you have gained 1,500,000 gold as the mini-game reward.
-you have leveled up.
 (lv.
 19)during the war, they killed a huge number of players, but the exp of the mini-game was also quite good.
-choose a level up card.
sungwoo chose no.
 2, skill item.
< you have acquired the skill .
[skill information]-name: manufacturing toxic cloud.
-grade: basic-category: active-cost: 30 mana*you manufacture a cloud containing poison and spray ‘poisonous rain’ on the entire area for 10 minutes.
 (1-hour waiting time for reuse)‘it’s a black wizard skill.
’it was a new skill and the black wizard-type skill at that.
 it was a very powerful skill that could inflict poison damage in a wide area.
 it seemed that the new skill would exert tremendous power in large-scale battles if it was mixed with the ‘crystal of chaos’ effect, which continuously consumed mana and stamina.
with corpse bombing, stamina-eating curses, and poisonous rain, the necromancer’s war equipment grew more and more abundant.
‘it’s great.
’he felt like the pirates gave him treasure.


 