\section{chapter 249}

besides, there was a lot of work to be done.
 first of all, the most pressing issue was how to deal with the prisoners.





"there are 491 human beasts affiliated with the evolution society who were not slaves and 1,914 players.
 we're not done counting all of them, so there are more.
 there seem to be some prisoners still staging a sit-in at the underground facility…"sungwoo was willing to set free the human beasts under the white wolf, but he could not free them without any safety measures because they might raise a new rebel force influenced by their long association with dr.
 yu.
"sungwoo, there are too many of them for us to control effectively.
 we have to think about them a little more.
""how about contacting the liberation guild?""yeah? liberation guild? oh, you said that they are also managing the players in uijeongbu, right?"after sungwoo destroyed the demon camp in uijeongbu, the liberation guild took control of the remaining prisoners there.
 it seemed that they managed the prisoners well.
however, it was unknown whether the liberation guild would cooperate this time.
 since the uijeongbu area was within the metropolitan area, they took the prisoners.
 but the prisoners here were in daejon, which was outside the metropolitan area.
'anyway, there is no other force that can manage the overcrowded prisoners here.
 they might want to take revenge on the evolution society's terrorism attacks against yeongdeungpo station, their main base.
.
.
.
'sungwoo wanted to hand the prisoners over to them if they were willing to accept them because he had to leave soon to take care of some important mission.
 "inho, our work here is important, but some of our troops have to be ready to go to japan.
""ah, i've forgotten that we have to finish the korean-japanese war!"the 2nd korea-japan war was still in progress.
 sungwoo felt he had to get rid of them before it's too late.
 so, he planned to go straight to tsushima using his skill 'teleport.
'at that moment, hanho brought some embarrassing news.
"sungwoo, some forces already struck japan.
""uh? who did?""tsushima island.
 some attacked there first.
 isn't it absurd?"what the hell was this? was there any other force than sungwoo who could attack the japanese server?"who?"hanho held out his cell phone and said, "look at this!"it was the broadcast screen of the official channel showing the whole scene of tsushima island from a distance.
 the entire island was covered with black smoke.
 there was a battle there.

ku-gung! kuggugugugu!lightning began to strike the entire island.
"what the heck is that?"dozens of lightning bolts thundered like machine guns and struck all over the island.
 whole buildings collapsed, the trees burned, the roads cracked, and the players were smashed.
 it was like a heavy bombing.
the processions of people trying to escape the island continued from the dock, but the blue lightning did not miss the ships.
two cargo ships were smashed to pieces with a loud roaring.
 dozens of ships were sinking along the coast of tsushima at the moment.
it was the attacker's victory, but it was a tragedy.
"this is a broadcast screen, and it's been like this for 2 hours already.
 the japanese side couldn't do anything because they were being bombed like that…"hanho swallowed once and looked at sungwoo.
"i think that guy must have initiated this attack, right?" hanho asked.
sungwoo nodded.
"kangsok han…"he was the guy who was still ranked 1st in the korean server rankings.
 nobody knew the reason, but his forces headed to tsushima first, smashing the japanese army.
'why did he choose to fight them?'then, kangsok appeared on the next screen.
 he was standing at the top of "mt.
 shirataki" on tsushima.
 he lifted his head and looked at the drone camera.
then, he laughed and said, "hey, are you looking at me, necromancer?""hi! it's me! remember me, right?"a fairy butterfly flew from his shoulder.
"butterfly, be quiet.
 if you are babbling like that, you make me look shallow.
""what? when did you start caring about your image?"
kangsok continued while pressing the butterfly's head with his index finger.
"anyway, i envy you because you seem to be doing well.
 i think i've been visiting disgusting places like this.
"sungwoo could not know what and where he had been doing, but when he encountered kangsok at a school in pyeongtaek, he heard that kangsok was pursuing a quest related to the "gate of hell".
"anyway, i will contact you for business soon.
 oh, let me give you the spoils of war in our battle here in tsushima as a gift.
"then, a portal opened behind him.
 just before entering the portal, he looked at the drone camera again, as if he thought of something.
"oh, i think you have a hobby of growing potted plants these days.
 someday, i want to take a look.
 is it okay?"sungwoo felt a bit uncomfortable about his last words.
 what he referred to as a 'potted plant' was the world tree.
'if he wants to watch, it means that he may be interested in or greedy about the world tree.
'sungwoo's concern might be groundless, but he was worried that he might have to confront kangsok someday.
if he knew the value of the world tree, he would certainly want to take it into his possession beyond just showing interest and envy.
'i don't know what his real purpose is, but i can't afford to feel complacent just because i have allied with him.
'whatever the purpose, kangsok might have felt it necessary to be strong by all means.
 sungwoo could not rule out the possibility that he would take away the world tree.
'even if i continue to grow like this, kangsok is still no.
 1 in the rankings.
 maybe he is taking a bigger advantage than me.
 he knows more than i do.
 but, the only advantage i have over him is that i have this world tree.
'when sungwoo was pondering over the world tree, a message about it appeared.
that was good news to him.
-the world tree has reached 'mature (1st stage)'.
-'link' with the world tree increases stats by a certain amount.
* increases stamina (+1)the world tree has gone beyond the stage of growth and reached maturity.
 as a result, a new function was added.
-the mature power of the world tree has a profound effect on the whole area.
 inhabitants near the world tree are allowed to receive special 'tribe traits'.
"tribe?"'what the heck is this tribe out of nowhere?'sungwoo could not understand it at once.
aren't all of the player's traits "human"?subsequently, a specific message appeared.
-'owner of the world tree' can select one of the following tribe traits.
 depending on the propensity of the owner, the 'detailed traits ' of each race may vary.
1) fairy (specialization: sense, dexterity, wisdom, etc.
)2) tree spirit (specialization: life, regeneration, affinity, etc.
)3) giant (specialization: stamina, defense, resistance, etc.
)4) not found (specialization: unknown)*you are too far from the world tree.
 please enter the 'shadow of the godly tree' and proceed with the 'selection'.
sungwoo looked at the message for quite some time.
 this was an important turning point for him.
'is it a tribe after the camp?'it was not known whether acquiring the tribe traits would mean going beyond humanity, but it was clear that he would obtain one more advantage over ordinary humans.
so, sungwoo slowly examined the contents of the message.
'fairy? an elf-like tribe is usually described as living in the world tree.
'the "elves" in fantasy are often described as being higher than humans.
 although it is different, depending on each fantasy work, they have a long lifespan and show a prophetic trait by dealing with mysterious power.
'a tree spirit or a giant looks great because of its name, but it seems that they are not relevant to humans.
"elves weren't even humans, but they certainly had a human appearance and face.
 however, the other two seemed out of touch with humans.
sungwoo frankly felt repulsed if his selection meant he would lose any humanity.


'the problem is no.
 4.
 not found? what should i find? if it's a hidden option, it must be some kind of hidden element.
'while the game offered easy options, it also hid puzzles that aroused a desire for extraordinary challenges.
 and those things bring a little more reward.
'i have to find no.
 4.
 it won't be too late if i select the option after that.
 how can i find it?'when sungwoo tried to find the way, inho approached him and said, " i got a call from kyongsu in suwon.
 he said the world tree has just grown very rapidly for no reason.
""yeah.
 i just learned about it through a status message.
"sungwoo knew faster than anybody else because he had the title of "owner of the world tree".
 however, inho described the status of the world tree at the scene that sungwoo had not witnessed.
"well, i heard that the world tree grew as tall as an apartment building…"apartment? isn't it as tall as 60 meters? if so, it would be taller than the largest building in the village.
"after we were done with the quest to protect the tree, it began to grow and bore fruits for the first time, right?""yeah, that's right," said sungwoo.
he was linked to the world tree after eating the fruit.
"i hear that the world tree bore three more fruit.
 they said they would not touch the fruit until you arrive.
"sungwoo could not help but be surprised, too.
 'three fruit?'he didn't know what special abilities he would be given this time, but he was convinced that this "growth" would transform the world camp dramatically.
"let me go there right now.
""sure, let me have the helicopter ready right away.
"the harvest season was back.


 