\section{chapter 176}

                             




in junghoon’s opinion, the two absolute races, angels and demons, could only present the direction of the game but could not become its key players.
 on the other hand, the necromancer was the strongest key player.
so, striking a subtle balance between the two sides was what junghoo had to do for now.
‘to make it happen, i must not be pushed around by either side.
 yeah, i have to be stronger first.
’soon, he found hope.
 a member of the crusader team, currently belonging to the wide area surveillance team, brought some good news to him.
“we have intelligence that our members have found an angel’s statue in the kimpo area.
”junghoon sighed in relief at the news because if he didn’t have a statue, he was most likely to be eliminated from the current mainstream.
 if that really happened, he could not found a coalition of the survivors’ groups.
“what a relief! please carry out the plan to transport it safely under tight security.
”“yes, we will.
 by the way, commander, the statue we have found this time is a bit different from the one we found before.
 i hear that this statue has four wings.
”“four wings?”“the statue we found last time had only two wings.
”junghoon didn’t know what the difference between these two statues was, but it seemed that the angels’ statues had grades.
 as a result, junghoon became more anxious.
‘if i can gain more power with this statue, they will give me more responsibility.
’currently, there was only one thing the angelic race wanted.
‘they want me to kill the necromancer, but they could pressure me more if i have more responsibility.
’junghoon now felt he was at a crossroads of great choice.
***-the sprout of the world tree is growing.
 (77%)
as time passed by, a group of powerful monsters began to come from a little further distance.
 a group of red orcs and trolls that survived after the appearance of the warlord monsters began to pop up.
ooooooooooh!“three trolls are coming from the right!”“have a shield on the tank and block them with faint skills!”the more terrifying monsters approached, the more the players’ ability to cope with the monsters enhanced.
 the players of the same occupation grouped to fight together to receive the optimal synergy effect.
thud-“well done!”“fire a burst at the fallen monster!”they were now gaining enormous exp while blocking the monsters behind the solid wall instead of moving around in dangerous areas to search for the monsters.
in the meantime, sungwoo stood next to the world tree, which was now as high as his waist, and watched the fighting between the village players and the monsters in the area.
 sungwoo’s subordinate spirits supported the players, but it was the players who were doing most of the battle now.
‘this is an opportunity for me to build a strong army while protecting the world tree.
 and based on that, i can form the third camp.
’just like the village itself became a haven for sungwoo, it could be a greater help to him in the future, and when the day came when he could not hide the world tree, he would need the troops to protect the world tree.
kyongsu and inho approached him after their battle entered a lull.
“as things stand now, i think the players will reach level 9 on average in a couple of days.
 among them, those with the highest level will be 15.
”“as expected, suwon is much safer and more comfortable than i thought.
”the village players reached level 8 on average only recently, but they are now on the verge of reaching level 9.
considering that the 50 members of junghoon’s crusader team were level 11 on average, the village players’ current level was quite high.
“thanks for your hard work! given that the players suffered no casualties, i think you guys really worked very hard to train them.
’
-the sprout of the world tree is growing.
 (99%)the first stage of growth of the world tree was already at an end.
‘it’s around the corner!’a little later, the stems and branches of the world tree began to grow rapidly, emitting a golden color.
-the world tree has reached the ‘first stage of growth’.
* permanent stat increases are given to all players in the quest.
 (muscle strength +1)* blessings are given to all players in the quest for 24 hours.
 (all acquisition rate increase +20%)the young world tree grew as high as two meters, about the height of a typical adult male.
it didn’t look much different from a typical tree, but sungwoo realized that some mysterious phenomenon was taking place inside the thin bark.
‘i can feel some energy.
’he could feel the white rays of light extending from the roots rising up the stem, passing through its branches and flowing through all the leaves, and this unidentified ray of light was getting stronger as the world tree grew.
that wasn’t the end.
woooooooong- woooooooow-light began to focus on the thickest branches of the world tree.
 the light was condensed in one place and formed a circular object.
‘it’s a fruit.
’soon, a golden fruit was born.
 it was smaller than he thought.
 at best, it was about the size of a finger joint.
-the world tree bore its first fruit.
* only the one who is qualified can take the fruit.
of course, the one who was now qualified to take the fruit was sungwoo.
 so, he took the fruit boldly.
[item information]-name: the first fruit of the world tree-grade: myth-category: consumption-effect: unknown-description: this is a fruit containing the mysterious power of the world tree.
 you can gain special power if you eat it.
the item he obtained from the world tree could give him special power.
 so, he immediately put it in his mouth without any hesitation.
there was no time for him to feel what it tasted like because it instantly disappeared in his mouth like melting snow.
now, he felt something spreading all over his body, starting from his mouth.
-by eating the first fruit, you are now ‘linked’ with the world tree.
[skill information]-name: world tree (link)-grade: max-category: passive-consumption: 0*you have been connected to the world tree by eating its first fruit.
 whenever the world tree grows, you can get a certain number of stats.


+ return: no matter where you are, you will return to the world tree.
 (cooldown: 24 hours)‘man, i can’t wait to see it growing bigger and bigger!’whenever the world tree grows, would sungwoo enjoy an increase in his stats?he didn’t know how much that would be, but he was sure it would be a huge advantage because it meant he could increase his stats twice as many as others.
moreover, the “return” skill also seemed to have an infinite range of applications because he could use it not only as a simple movement technique but also for escape purposes in case of an emergency.
‘if it really happens, i can mount an attack on the pirates in taiwan and escape.
’he obtained an angel’s wing fragment when he destroyed the angel’s statue.
 it was an item he could use to move at once to an angel statue in another area.
in other words, he had a way to ambush the pirates in taiwan before they noticed it.
however, currently, taiwan was like a pirate’s lair.
 it would be easy for him to get in, but if something went wrong, there was no way for him to escape, so he couldn’t do it hastily in the past.
 now, things have changed.
‘when the world tree stops growing and stabilizes, let me go and attack them in taiwan.
”since such a tremendous reward was given, it was far from easy to protect the world tree.
-the quest ‘for the spiritual tree-2’ begins.
* the energy of the world tree spreads farther and attracts more powerful monsters.
the quest was not over yet, and it was getting more and more difficult.
at that moment, the guard on the rooftop announced that sign.
“magic drone #2 has found something in the northern sky! please check!”sungwoo and kyongsu hurried up to the rooftop.


 