\section{chapter 266}

                            “wow! now, it’s bright around us.
 sis, i’ve been curious about it.
 what the hell is that?”




jisu put the flame flying over her shoulder on her palm.
“well, when i ianded here alone in the mountain last time, i got this as a hidden quest.
 it’s called ‘goblin fire’, which is an item that belongs to its new user.
”like the ‘hellfire armor’ used by sungwoo, this item belonged to the new user once it’s used instead of being returned to its original owner.
“really? how about the item’s effect?”“it greatly enhances skills that radiate energy.
”“aha? that’s why you emitted numerous energy blasts from your sword.
 i know how thrilling it is because i can throw multiple daggers at a time.
”“yeah, it’s similar to that.
”as soon as they finished chatting like that, they faced a steep downhill road.
 they couldn’t tell how long it was because the flickering lights could not reach far.
“everyone, watch your step.
 it’s a steep downhill slope.
 by the way, you guys make sure you don’t drop the bags containing boiled potatoes,” said the king.
“yes, sir!”the cave was very deep.
 and it was rough.
 there were few spaces for them to step on, and it was very slippery inside because of the moisture.
 because of that, they had no choice but to be very alert while moving, which made them tire easily.
“well, that’s why i brought the boiled potatoes because we need snacks on a long and hard journey like this.
 don’t you appreciate my great vision?”the king walked downhill, chewing potatoes.
 no one answered because what he said was nonsense.
at some point, however, the cave began to fill with light.
 a blue light was coming up from below.
“we’re almost there.
”suddenly, they saw the bottom of the cave and heard the gentle sound of water.

“what the heck? is it a lake?”water was flowing at the bottom of the cave.
 it looked like a puddle created by accumulated groundwater and was the epicenter of the blue light.
 the water was emitting light.
“wow…”the bottom of the cave was very mysterious.
 not only was the lake shining in cobalt blue, but also the tree roots that came down from somewhere were scattered around the lake like a curtain.
 and between the roots, all kinds of items were entangled like fruit, which was quite eerie as if they fell in a strange country.
“gosh, what are all these items?”like a child who came to a museum, hanho stopped by here and there, asking the king a lot.
“this is also my treasure trove.
 i collected them while protecting the great mountain range.
 you will find lots of useful things.
 if you need anything, just pick one.
”“really? are you giving us a gift? are you sure?”“yes, because we need weapons, not treasure now.
”after he said that, the king broke through the thick roots and pulled out something among them.
“good.
 it’s been a while since i grabbed it.
”it was an incredibly huge ax with a blue blade.
 it seemed to be the king’s weapon, but it was so big that humans could not handle it.
 the king lifted it easily and put it on his shoulder.
the ax looked very unusual.
 two blue dragons were engraved on its long handle.
 they bent up on the handle, carved in relief at the point they touched the blade while sticking out each of their heads on a single blade.
“let me see if there is anything flying…” said the king.
meanwhile, hanho wandered here and there then found something special.
there was a tree base between the thicket roots on which a pot was placed.
“uh? what is this?”
at that moment, the king of the great mountain stopped him.
“oh no, you can’t have it.
”the king was suddenly alert.
“what the heck is it?”“it’s alcohol.
”“alcohol? oh, man!”hanho suddenly lost interest in it and turned, but only then did jisu don an interesting expression.
“liquor? i wonder if it was…”“that’s right.
 i made alcohol with the small crystals you brought me, jisu.
”sungwoo gave her the small crystals with the spirit of mt.
 taebaek.
“this terrible alcohol is getting more and more fermented with the spirit of the mountain every day.
 jisu, just pick one item you think will be useful to you.
”at the king’s urging, she also began to look at the items.
 then, a sword caught her eyes.
“jisu, you know how to find a good item.
”then, the king of the great mountains immediately pulled out the sword.
“this is the one you might want.
”“but i haven’t chosen yet.
”“now, don’t hesitate to take it.
”he held out the sword to her.
[item information]-name: ulfberht-grade: legend-category: one-handed sword-effect: whenever you cut an enemy, your strength and agility temporarily increase by (+1).
 (maximum +10) when you reach the maximum, you obtain the effect of the ‘song of the battle’ for 5 minutes.
 (you become immune to abnormal conditions, so you don’t feel any pain.
)“i’m sure this must be a good choice.
”did he advise her to choose it because he knew something about the item?an unexpected message appeared before her eyes.
-you have met certain conditions.
* world tree resident (special identity) + legendary grade viking sword (warrior’s mark) + unknown (additional acquisition required)“this one is…” jisu showed surprise at that moment.
the king of the great mountain smiled as he faced her wearing an embarrassed expression.
“i don’t know what it is, but think about it slowly, not now.
”“i got it.
”she knew that the king of the great mountain was looking farther than she thought, and he used it beneficially.
hanho picked up an iron helmet after hard thinking.
 it was an item called “spirit of the guard”, which had the effect of putting a shield on himself and one of his colleagues for a certain period of time.


“how can you match that plate helmet with your occupation as a thief?” jisu asked.
she couldn’t hide her puzzled expression, but hanho seemed pretty satisfied with the item.
“isn’t it cool? hahaha! since i already played the priest, rogue, and asura ghost, let me play the tank this time!”“…”when everybody was all set, the king of the great mountain walked into the lake.
“okay, let’s go now.
”watching him, hanho hesitated then stepped back.
“uh, oh, my god, i wonder if you are not going under the water? i don’t know how to swim…”“this is not water.
 you can think of it as a kind of condensed energy created by the combined spirits of the mountains.
 i will open the door by casting a spell for space movement here.
”the two tigers followed the king into the water.
 then, jisu went into the water, which forced hanho to do so.
when everyone was soaked in the water, the king lifted his left hand and put it into his mouth, breathing out.
 surprisingly, his breath materialized as a blue mist.
 and the moment he dropped it on the lake, it flashed blue before their eyes.
-the ‘mountain trail’ opens.
-you have arrived at the ‘connected area (mt.
 duryu)’.
and that was it.
 they were standing in an unfamiliar valley, which was the north korean territory.
“uh? what the heck? is it over already?”“what did you expect?”“oh, nothing.
 it’s good.
 i was afraid i might vomit, but i didn’t.
 not bad! let’s go and beat the monster boss.
 wouldn’t it be better for us to go quickly before sungwoo is done hunting all the monsters alone?” hanho began to shout in excitement.


 