\section{chapter 314}

the world season was the cornerstone of a world war.
 all the countries of the world declared wars against each other.





however, the place that drew people's attention more than anywhere else was the korean peninsula.
"finally, it has begun! time for cross selection!""oh, it's a tense moment!"reporter ahn and his assistant made a big fuss by shouting.
 a huge screen spread behind their back to broadcast the start of the war through the official channel.
the place where they were broadcasting was a kind of studio.
 since reporter ahn could not film the three battlefields at the same time, he was broadcasting it to the best he could by relaying the official channel.
 in other words, he was doing a 'piratical broadcast.
'-[live] reporter ahn's commentary on the war between the korean server and the chinese server (35,444 people watching)despite the official channel, reporter ahn's pirate broadcast attracted a whopping 30,000 viewers because of his mention of the necromancer.
"necromancer! and all the warriors of the korean server! you can win! our team of reporters has always remained neutral in our reporting, but this time we want to bet on your victory out of our patriotism!"watchers got more interested in reporter ahn's noisy and lively commentary than the lonely and static official channel.
 "okay, as you can see here, there are three battlefields according to the rule: suwon, busan, and seoul! they have to deploy troops by cross-selection, but the important thing is that once they deploy troops in a specific battlefield, they have to provide such information to their opponent!""uh, wait a minute? the korea server has to show them their troops and the battlefield first, right? in that case, the enemy can check out the strength of the korean server troops and come up with a customized strategy, right?""yes.
 that's right.
 it's the worst.
"
-first choice (korean server)"what is the korean server's first choice?"-battlefield: seoul"first of all, they chose seoul.
 it's pretty frustrating for them to have to make the first choice.
 but they can't help it because the other party already declared war and took the initiative.
""you bet.
 then, let's see how many troops come out, and who will lead them.
"at that moment, the screen of the official channel was showing somewhere in seoul.
 soon, a portal was opened there and the troops of the world tree camp were summoned.
-the list of their deployed troops was sent to their opponent, the chinese server.
 "oh my.
.
.
the number of their troops is too small," reporter ahn lamented.
 those who came out of the portal were about 100, including jisu, the king of the great mountain, and tigers, all of whom reporter ahn didn't know well.
 "what the heck? aren't they monsters?""yeah, i guess so.
 oh, there is something that even reporter ahn doesn't know.
"reporter ahn scratched his cheek and said, "haha, well, the important thing right now is that they haven't yet shown the necromancer card.
 it looks like they have decided to dispatch a force strong enough to hold out in seoul.
 since the woman swordsman, no.
 4 in the korean server rankings, has been included in the force, i don't think they can be easily defeated.
 i trust them!"
"oh, i see.
 then, we have to watch how strong the chinese server troops are.
"-second choice (chinese server)-place: seoul"man, they have picked seoul like the korean server! they are coming out now!""oh, my god…" reporter ahn laughed in embarrassment because an enormous number of chinese server troops came out, incomparable to the korean server troops.
 "gosh, at first glance, they are estimated to be 4,000.
 i see lots of flying weapons and even the japanese server troops because of the japanese national flags here and there.
""japanese server? who are they?""maybe they are the remnants from the kyushu region, who were defeated by the korean server during the recent korean-japanese war.
 i heard that they became pirates, but now they seem to have sharpened the blade of revenge on the korean server.
"since reporter ahn also had some intelligence about the japanese server, he could keep making a plausible commentary.
 "by the way, damn bastards! how many times did they invade the korean server?" when his assistant asked angrily, gnashing his teeth, ahn nodded, then said, "good.
 we are going to add our commentary in our broadcast today!"-third choice (korean server)"now, it's the korean server's turn again.
"-battlefield: suwon"this place is the most important suwon! that's the place where the world tree has been growing! and it's the headquarters of the world tree camp!""you are right!"all the rest of the korean server troops were concentrated there.
"wow!"nine naval fleets, various flying weapons, and all the forces from all over the country were concentrated in the suwon village, the home of the world tree camp.
they settled inside the invisible barriers and castle walls, which would be a tremendous advantage for them.
 of course, the chinese server must have chosen this place knowingly.
"it's amazing.
 as a matter of fact, the korean server's fate is at stake in this place.
 the entire army of the korean server has gathered in suwon, i think.
"reporter ahn nodded at his assistant's commentary, but there was more anxiety than admiration on his face.
 "well, given this troop deployment, one man is missing in the remaining korean server forces.
 only one who has the biggest power…"when reporter ahn mentioned it, his assistant turned his head, startled.
 

"if so, the necromancer alone is going to go to busan to deal with the chinese server troops there?"reporter ahn slowly nodded and opened his mouth.
"what kind of strategy is he going to use? is he going to hold out even in busan? i am not sure if he wants to win the battle in suwon first, then move to busan.
 no matter how strong the necromancer is, i don't think he can destroy the whole enemy troops in one battlefield alone.
""wait a minute, reporter ahn! as you know, the necromancer defeated lots of enemies on many battlefields alone, right? we also confirmed it several times, right?"the assistant cameraman still trusted the necromancer's victory.
 but reporter ahn was skeptical.
"when you look at the necromancer's battles so far, he has done a lot of damage to the enemies in a sudden surprise attack.
 but this time it's an all-out war, and the chinese server must have analyzed the necromancer's strength and strategy for a long time.
""oh, i see…""if so, the chinese server will come up with the right strategy to defeat him.
 now, what happens if the necromancer is emerging as the sole fighter? well, he could be the chinese server's easiest prey.
 i'm really worried.
"deep anxiety was seen on reporter ahn's face.
 he didn't show any more vitality in his broadcasting because he also feared that the korean server could become the chinese server's colony.
 "well, reporter ahn, he is none other than the necromancer! he must have some strategy that we might not know.
""yeah, that's right.
 he is the invincible necromancer!" reporter ahn took a cigarette out of his pocket and bit it.
 he was not in a mood to keep the broadcasting decorum now.
"the obvious thing is the chinese server will deal a fatal blow to him.
 let's wait and see if their attack will prove to be a game-changer or the worst move.
"

 