\section{chapter 406}

with his face covered by his left hand, li bu's left arm got stiffened after it was hit by the petrification beam.
 but he kept swinging the bangchon spear with his right hand.





"hey! how come you are so arrogant before me who has six arms when you have only one?"but li bu approached hanho, wielding his spear dazzlingly.
watching him, junghoon couldn't hold back his soaring anger.
contain his worries as he looked at him.
'no way! you can't beat him…'junghoon knew that this man named hanho was engaged in doing something weird, but he didn't seem to be good at using weapons.
compared with him, li bu wielded the sword well as if he actually lived as li bu in the three kingdoms chronology.
when they fought in terms of strength and skills, li bu's chance of winning was definitely higher than him.
clang! clang! clang!'by the way, what the heck is this?'junghoon was embarrassed.
clang! clang! clang! it was really demanding and challenging for hanho to use five shields in six different arms.
 naturally, junghoon didn't know hanho had as many as six arms.
 what he was witnessing right now could not happen to humans using only two arms.
clang! clang! clang!"hey, hit me harder!"at that moment a golden light shone all over hanho's body.
 then li bu's bangchon spear, with which li bu was charging at him, got stuck in the air unexpectedly.
 it was a shield.
 a thick shield suddenly popped out on the spear's trajectory.

'did he intentionally turn off the shield for that effect?'when the spear was caught in the air like that, li bu had no choice but to stop moving for a moment.
for more, visit lightnovelworld.
comhanho seized the moment to attack him.
puck! tung! one of the four shields struck down the back of his feet while another stabbed his neck.
 the third one pushed into his stock.
 when li bu lost his balance because of the impact, his top hand, which he didn't use until now, began to move.
at that moment hanho pierced his head with the spear called yonwoldo.
 the earthenware doll that posed such a terrifying threat to junghoon collapsed all of a sudden.
"whew!"throwing away one of the spears, hanho lifted li bu's bangchon spear.
 junghoo got up and approached hanho.
when he got close to hanho, he was shocked to find that hanho was holding the blue dragon sword, with which he pierced through li bu's head.
'what the heck? did he kill the two monster terracotas?'junghoo was shocked to discover hanho's terrific skills and admired his performance at the same time.
'not only the necromancer but also his party has reached a tremendous level.
'at that moment, hanho raised his head toward the air.
"uh! watch out!"then he pushed junghoon with a shield.
 the moment junghoon's body floated in the air, there was an explosion over hanho's head.

bang!hanho was thrown away instantly and crashed into brick materials stacked nearby, which sungwoo had stored to fix the broken rampart.
it was the cannon fired by the airship that fell over his head.
 after the emperor felt that li bu and guan yu fell, he fired two cannons from the airship in a row.
"hanho!"junghoon ran towards him, who was trapped inside a pile of bricks.
"are you okay?"this content is taken from lightnovelworld.
com"ugh, i'm alright!"fortunately, hanho wasn't killed by that attack.
 as a matter of fact, he emerged intact even after he was hit by a guided bomb fired by admiral william baker.
"oh my.
.
.
i'm so glad to see you here!"even though hanho was not wounded, he was murmuring something crazy as if there was something wrong with his brain.
 "alright, dear, come to me right away!"murmuring like that, hanho got up from the piles of bricks.
but he was a bit different from before.
 he threw away one shield and grabbed li bu's bangchon spear after killing him, but he was holding five shields like before.
"i've finally found it!"it was the 'achilles' shield' that he had received from sungwoo.
 there was some other change in him.
 a white light began to flow from his body.
"oh my god! something is happening now!"like he said, something eye-opening happened.
***inho was disappointed.
 he couldn't find the answer.
"the enemy has finished loading their guns! they are aiming at us!"the 'oppressor's hands' handled by the emperor were driving the combined fleet into a corner by controlling the airships.
 four airships were already shot down.
if the combined fleet retreated right now, the world tree would be exposed to the emperor.
inho wrapped his head with both hands.
 as the commander of the combined fleet, he was responsible for overcoming this crisis.
"if sungwoo were in my position, i wonder how he could…"but they began to find a ray of hope unexpectedly.
"uh? the enemy directed the muzzles of the cannons somewhere else! they are aiming at the ground!"when somebody reported to him, inho approached the window.
 indeed, all the cannons on the three airships were aimed at different places.
"is he hanho over there?"new novel chapters are published on lightnovelworld.
comhanho was standing there.
 but there was something strange about him.
 a dazzling light was emanating from his body.
inho didn't know what it was, but obviously, the emperor also felt the intense power emanating from hanho and directed the cannons toward him.
then a thick green shield covered his body, which looked stronger than any other shield he had ever seen.
bang! bang! bang!soon the cannons were fired at hanho.
 not content with the cannons, the oppressor's hands swung dozens of golden threads.
bang! bang! bang!the area where hanho stood was devastated, and the place where he was standing completely collapsed.
all the crew on the decks began to whisper at the terrible scenes.
 it was impossible for him to survive such a devastating attack.


"was he killed?""i guess so…"but when the smoke went away and the bombing point came to light, hanho emerged intact!"nonsense!"there would be no player who could survive such an attack, no matter how specialized he was in defense.
"give me telescopes!"inho scrutinized hanho the telescope item.
 hanho was smiling, with his gum fully shown.
 he was shouting at the emperor in the sky at the top of his voice.
 obviously, he was rambling.
and there was another strange thing.
 traces of the bombardment around hanho, for example, heat, flames, and mana, were flowing into hanho's body.
'what? is he absorbing damage?'the next moment hanho shot out a ray of light.
 it was the energy he just absorbed.
 the light penetrated the rampart and struck the oppressor's left hand hard.
 all the golden threads on his left hand were cut off, shaking the airships violently.
"no.
 18 airship, no.
 21 airship, and no.
 22 airship reportedly have restored their control completely!"shouts of joy among the crew were echoing all over the decks.
 "oh my god! is that…"the source of this content is lightnovelworld.
c‌ominho also knew to some extent what that great power meant.
 it was the formidable power that only sungwoo or jisu had shown until now.
"by the way, how come hanho…"oddly enough, inho was more perplexed than surprised by hanho's unprecedented performance.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 