\section{chapter 419}

[item information]




- name: gleipnir- rank: myth- grade: noose- effect: when you bind a specific target with this rope, you can bind it with magical power.
 if your muscle strength level is less than 250, you can't break it by yourself.
 you need 3 or more wizards to be unlocked.
+ tyr's arm: if you give out your right arm to the opponent, this item will automatically activate and bind the opponent.
this was the item that the fake emperor bound jisu.
"i want you to make a weapon with which i can tie the dragon's wings and drop him?"hearst chuckled at sungwoo's words and replied, "so, it's time to hunt him down?"sungwoo nodded.
 as hearst said, sungwoo was going to hunt the dragon and the demon king.
 s in the meantime, the main base of the world tree camp was divided into a total of four areas with the world tree at the center.
warehouses and various workshops were located in the northern area.
 due to the huge amount of goods coming in, vehicles and forklifts were constantly coming and going, making lots of noise.
 the western area contained hangars, a runway, and jump stations.
 it was kind of an airport.
 the eastern region was densely populated with players.
 their population increased dramatically recently, so it was expanding day by day to accommodate them.
 finally, the southern part was scheduled to have an administrative body.

"oh my god, can you believe they built this huge building in just 53 hours? i am always amazed," kyungsoo said.
 for more, visit lightnovelworld.
comsungwoo raised his head and looked up at the huge building in front of him.
 that gigantic structure stood tall under the huge ceiling covered with the world tree.
 - you have witnessed the aura of the masterpiece building.
 'fantastic blessings' are granted to you for 30 minutes.
* health and mana recovery speed increase (+20%)* all stats increase (+1)'i can't believe this architecture itself is a masterpiece.
.
.
'as the center of the world tree camp, this building was to serve as a general administrative center, the so-called 'order tower'.
 its structure was obviously a modern building, but it felt a bit strange because it was made of pure white marble and a magnificent mural was engraved on the exterior wall of the building.
'well, it's all about me.
'most of the contents of the mural showed sungwoo as its main character of the wars that he had been engaged in until then, such as the drake in yeouido, imugi from mt.
 bukhan, demon's cave in taiwan, etc.
 the adventure stories about him were depicted in the mural like epic poems engraved on the ruins.
of course, in one corner of the mural was drawn jisu's transformation into valkyrie and hanho wielding five shields.
'man, i feel embarrassed to see that…'
it wasn't just the looks of the building that caught his eye.
 'shield generators' and 'mana batteries' were installed throughout the building to surround the entire building with a shield, and flying weapons were installed on the roof, making it serve as a huge fortress in case of emergency.
sungwoo nodded, admiring the magnificence of the whole building.
"it seems that our architects are improving their skills day by day.
 i think we can start building the second rampart soon.
"as the world tree camp was growing explosively, the current rampart where they were located was clearly not spacious enough to house them because it was built a long time ago.
you can find the rest of this content on the lightnov‌elworld.
com platform.
muyon expressed his ambition to build a second rampart soon, and sungwoo was fully ready to actively support the construction.
"well, if we had enough supplies for them, they said they could build even a city within a month!"the two entered the building.
the 'general affairs department', led by kyungsoo, was now expanded and reorganized under the name of 'general control office', so they were establishing various administrative departments.
"of course, we can build these buildings with the skills, but the administration is basically something done by humans, so i think it will take some time to have it fully ready.
"they had no skills that could be helpful to their administration.
 of course, they could get things done quickly by applying other skills, but running administrative departments required human skills.
then the two got on the elevator.
 it was a device run by the power of mana, not electricity.
kyungsoo pressed the button on the 25th floor.
 the "international communication center" was located on the highest floor of the order tower.
when the elevator door opened, a middle-aged man with glasses ran out to greet them.
 he was the head of this center, who was in charge of this place.
"ah! necromancer! control center chief! i've been waiting for you.
 let me escort you inside!"the international communication center dates back to the days when the world season began.
when sungwoo issued the order to mobilize the whole 'korean server' to confront the chinese server, they were flooded with numerous responses from everywhere, so they hastily established a 'temporary communication center' under the 'general affairs department' to take care of a heavy load of work.
 whew! how fortunate it is that we have been laying the groundwork for this center since then.
 we can respond to any contingencies at this critical time!"as the head of the center said, the temporary institution was now playing a significant role.
 while escorting sungwoo and kyungsoo into the facility, he continued, "ah, we are trying to have multiple communication items for smoother and faster communication.
 all thanks to you two!"updated from lightnovelworld.
comthe center was very spacious since it used the entire 25th floor.
 in particular, the 'control room' was reminiscent of a cctv integrated control center, with dozens of screens filling one wall.
"right here we can monitor the community of 24 servers at the same time.
 our monitors are on standby all the time and to collect news from each server.
"then, the center director stood in the right corner of the control room, which was a small space separated by a glass wall.
 given the yellow tape on the floor, it showed that this was a controlled area.
"this is the most important space on this floor.
"there was an item inside it.
 

"this typewriter-like device connects to the rooftop 'community access permission generator' so that we can post any message and announce it to the world immediately, or more specifically we can write and post a message on the 'community' of other servers.
"the community divided by each server could not be accessed except by the players of that server.
 but this unusual item called the 'community access permissions generator' made it possible.
"since the message we are sending here is the voice of the world tree camp, we shouldn't make any mistake.
 so nobody can't access this place.
 it has been secured with a small invisible barrier so that only a few authorized people can access it.
"sungwoo nodded, then asked him, "great.
 i have to send a message right now.
"then the center director pulled out a notebook.
s "please speak.
 let me write it down to spread it to the world accurately.
"so, he had the world tree camp's 'control center' spread his message throughout the world.
 it was about convening the so-called 'temporary committee' to discuss the formation of the control center, which he mentioned several times.
the center director, who wrote down his instructions, entered the small invisible barrier and began to type it on the typewriter.
'it will be an opportunity that everyone can't refuse.
'follow new episodes on the lightnovelworld.
com platform.
the head of each server around the world was well aware that if they didn't join the "control center" this time, they would eventually be eliminated from the central axis of the world in the near future.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 