\section{chapter 439}

since the poison gas was generated behind her back and over her head, it was not easy for her to blow it away with the wind.
 if something went wrong, she and paulo would be exposed to the poison.





she totally focused on the poison area while trying to generate the wind, then pushed it toward sungwoo by moving it delicately, so the poison gas would not come down to the floor.
whoop!"hold your breath!" minsok shouted.
when green smoke swept over grace and paulo, minsok charged at them.
when he blocked their vision in an instant, he threw a black chain, which immediately bound grace's left arm and wand.
"argh! what the heck is this?"stunned, she tried to pull her arms from the chains, but it was not easy.
"sungwoo, now is the time!"as soon as minsok shouted, sungwoo ran through the poison gas, then jumped into the air.
advertisements    - 'evil spirit bombing' has been embedded in your weapon.
 (max)the grim reaper swallowed the black sphere.
 sungwoo dropped right away to grace, wielding the grim reaper at her neck.
but something stood in front of her to block his attack.
 it was paulo's arms.
 his thick arms made of stone stopped the grim reaper.
"hey! wasn't the necromancer from a wizard series? he's strong enough for a wizard series, given that he broke my four arms like this at once.
""i won't allow you to add one more word…" said sungwoo, letting out a breath.
then he blew mana somewhere.
 "think of your next move, you idiot!"- the 'law of the underworld' has been issued in the area.
* you now control all vengeful spirits.
 
one of the underworld king's powers, the 'law of the underworld', could resurrect the souls of the dead as demons.
 in other words, it meant that the 'souls' used in 'evil spirit bombardment' could also be these vengeful spirits.
shortly afterward, 40 ghosts burst out from the grim reaper stuck in paulo's arms, scraping his whole body like a rotating blade.
 stones fell all over the place.
"argh! argh!"paulo stepped back, screaming in pain.
 he could not shake off the demons stuck all over his body that his physical attacks such as fists did not work at all.
 his body was like a rock, but no matter how hard it was, it was inevitable to get scratched when punched endlessly.
 after all, his damage piled up.
"ahhhhhh! take them off me!"sungwoo's party began to counterattack right away.
 orun bounced off from the still remnant poison gas.
 it was from the direction where jisu was, who had been confronting vivona.
bang!the hand cannon exploded.
 but vivona's hand rose from the shadow under his feet, blocking the hand cannon.
 of course, this was not all.
 throwing the hand cannon, orun drew the sword and charged at vivona's side.
 "you dumb bastard…"while vivona was distracted by orun, jisu seized the chance to attack him.
'alright, now is the time!'she immediately rushed toward him, getting close under his neck.
vivona hurriedly moved his shadow, but even a brief lapse in attention on his part provided her with a golden chance to counterattack at the perfect timing.
jisu cut through his thigh and side right away.
his shadow soared momentarily, wielding six hooks around the area, but she was not there.
 "argh, you bitch!"
vivona grabbed the wounds with his hands, swearing at her, then made two giant hands in the shadow and wrapped his body.
jisu was a warrior while vivona was an assassin.
 in a one-on-one confrontation, she could defeat him, but in a simultaneous battle like this, she was inevitably vulnerable to his attack.
"damn it! grace! take this off!" paulo shouted.
but even grace could not shake off minsok's 'chains of abyss' that bound her arms.
"what? imperial ranger?"sungwoo strode closer to paulo.
 and he aimed the 'winter predator' at his feet.
tung! tung! tung! tung!several freezing bullets hit his lower body.
his thick thighs and calves got frozen and stuck to the ground.
 "ugh! ouch! go away!""imperial ranger, you are disbanded as of today," sungwoo shouted.
then he slammed the grim reaper towards his neck with all his might.
his thick neck was cut off at once.
 even though he had a super strong build like a rock, he could not withstand sungwoo's forceful strike, who had overwhelming stats.
 sungwoo kicked his severed head, then turned to grace.
 she was now full of embarrassment in a break with her composure a little while ago.
"all you can do is just stall for time! just open that door.
"at that moment there was some vibration.
 then the stone door, which had been firmly closed, began to open with a roaring sound.
 and something was flickering red inside the grey darkness.
it was flames.
 the flames were now coming out.
"i think i said i didn't want this kind of commotion.
"to be precise, it was a person covered in flames.
 it was a woman in red, with red scales sprouting from her smooth body, red hair, red horns, and vertically torn orange eyes.
"uh? why is paulo's head here?"she found paulo's cut head rolling near the stone gate, then turned her head slightly, looking at somebody behind her.
"oh my.
.
.
gangsok, what should i do? i don't want to cross words with these guys.
"as expected, she was the dragon.
more precisely, she was the "disaster" dragon that was born in the amazon and destroyed all of south america.
she finally revealed herself before sungwoo.
"you guys have been running around recklessly without knowing what's going on.
"her eyes sparkled while she gave out such a warning.
 - caution! 'dragon fear' has been activated.
* it stiffens low-ranking creatures.
"argh!"at that moment li wei, who was standing next to sungwoo, stepped back hesitantly.
 even junghoon frowned, grabbing his heart in pain.
 dragon fear itself suppressed creatures weaker than itself.
 and this one was the strongest of all kinds of dragon fears.
 the dragon said, giggling at them, "i don't want to deal with weaker creatures.
"fortunately, neither li wei nor junghoon fell into critical condition.
since they were the strongest players even without the divine power, they could hold out in one way or another.


"isabella.
"at that moment gangsok appeared from the inside of the stone gate.
"stop it.
 they are my guests.
"isabella seemed to be the name of that red dragon.
 did she have that name in spanish style because she was from brazil?gangsok was holding something white in his right hand.
 he looked at sungwoo and put it in his pocket.
'world seed.
.
.
'it was an item that gave a quest to become the world eater.
 he obtained it first, after all.
 "guest? if i kick them out of here, they are not your guests, right?"but gangsok firmly shook his head.
 but isabella still didn't withdraw her 'fear.
' rather, she stared at sungwoo's party and pressed them even harder.
"they cut off paulo's head.
 i think i need to take revenge on them because i'm going to be stressed out if i have to put it back to him"gangsok shook his head once more.
 then, she deactivated her 'fear'.
"oh, really! lizards are so ferocious!"it was the fairy, the butterfly that always accompanied gangsok.
 advertisements    when the fairy jerked out, isabella growled at her.
 she quickly hid behind gangsok's shoulders.
gangsok walked towards sungwoo and said, "it's been a while, necromancer.
"".
.
.
"without responding, sungwoo looked over his shoulders at the inside of the stone gate.
at first glance, the inside was a mess.
 because of the dragon's breath and gangsok's surprise attack, everything inside was crushed, but there was something huge in the middle.
 it was probably the head of the angel race.


 