\section{chapter 436}

after defeating both angel champions, sungwoo stood in front of the pyramid that was partially broken.
 after he revealed that the demon king and the dragon were inside the pyramid, the situation took a different turn.





instead of fighting later, he might have to confront them right now.
"we must enter the pyramid with a small force.
"although this pyramid was indeed enormous, they could not take the airships inside it.
"inho, please have the airships keep a certain distance while encircling the pyramid.
 also, stay vigilant!"the bone dragon could break through the wall of the pyramid in case of emergency, but the airships would be helplessly useless without enough space inside it.
"have only a few of the special commando unit wait at the entrance of the pyramid, while the rest of them besiege the pyramid.
"after all, five of them decided to go into the pyramid: sungwoo, jisu, hanho, junghoon, and li wei.
 'it won't change anything even if i take more people with me.
'sungwoo knew who he would end up confronting at the end of the day.
 if he had to confront that guy, they would die in vain, no matter how many players did so.
advertisements    'moreover, that guy is helped by the dragon.
'the moment they were exposed to dragon fear, those without the divine power would be able to move at all by falling into a rigid state.
"by the way, kyungsoo, please go to the forge of hephaestus and convey my message to master hearst.
"nodding, kyungsoo approached sungwoo.
 "as for the weapon that i asked him to make, just tell him i need it right now even if he has not tested it fully.
""let me keep it on the messenger when he hands it to me.
"after that, he went into the pyramid with an extremely small elite force.
 
the inside of the pyramid was like a honeycomb.
"wow, that's really big.
 if something happens, i think i can use my lethal weapon hyunmu.
"it was so wide that the pyramid-shaped structure on the ground looked like its cover.
watching it, sungwoo was reminded of a limestone mining site, which was centered around a vast pit, and spiraled down to the edge.
"it looks like the bottom of the devil's world tree," li wei said.
 sungwoo agreed with her.
 although it was brighter than it was back then, the overall terrain was similar to it.
 this did not mean that there was any connection between the two spaces.
"alright.
 let's get aboard the bone wyvern to go down like before! please watch out!"sungwoo summoned the bone wyvern because the bone dragon was not useful in such a narrow space.
the dragon seen in such a narrow space was not useful.
whooooooo-"ugh, what the heck is this smell? something is burning down there?"hanho said, grabbing his nose.
 as they went down further, the more pungent the burnt smell was.
"hey, i think it was caused by the pillar of fire that broke through the pyramid's ceiling," junghoon said.
 "it looks like this place was hit by an incredibly powerful attack.
"the flames from the two pillars that penetrated the pyramid were gradually sprayed into the pyramid inside, and when they went down to some point, the traces of something that melted in the fire began to appear black ashes piled up thickly on the edges of the hill.
"the angels were all dead.
 i now see why they were trying to escape through that hole.
.
.
 they look like a swarm of insects hit by pesticide.
"given that there were some large fragments of angel corpses here and there, which kept their original forms, it seemed that not only ordinary angels, but also executive level angels melted away at once.

even the walls and floors where the pillars of fire directly scratched were still boiling in flames after they melted black.
"don't breathe in that smoke.
 you will feel dizzy because of its toxic gas," jisu said, covering her nose with her sleeve.
``judging the damages that the angels suffered, they were devastated with only two attacks by the demon king and the dragon.
"when sungwoo thought about the impact of their attack, he recalled just one thing.
'dragon breath.
.
.
'as expected, the living adult dragon seemed to have devastating power.
 sungwoo even wondered if his fire immunity power might be neutralized by the intense heat like this.
thud-while he was thinking about it, they finally reached the bottom of the pit.
they saw a huge passage out there.
 and there was an unusual vibration emanating from it.
jisu listened for the sound, with all her senses focused, then looked at sungwoo.
"this sounds like somebody is fighting…"sungwoo nodded and said, "that guy wants to take this place ahead of us.
"it seemed that gangsok also received a quest to become the world eater.
 ``perhaps he received the quest earlier than me.
"there wouldn't be only one way to receive the quest related to the world eater.
as the strongest player in the world, and as the ruler of another world, sungwoo was also qualified to challenge the 'world eater', which would mean winning a world.
'if i become the world eater, followed by the demon king and the dragon, nobody will challenge me.
'gangsok's 'purpose' was still veiled.
 but no matter what it was, sungwoo decided not to agonize over it.
 'he is the guy who picked up the fight first.
 i can't stand idle.
'actually, gangsok started a war on me from the beginning.
 that's why the 'disaster quest' was issued.
 whatever his intention was, or even if he had a great cause, i had no choice but to confront him directly since i could not figure out what it was.
"let's go inside.
"sungwoo then summoned two 'specters' and sent them in first.
"go into it while ensuring your safety!"after that, he summoned minsok and victor.
"you guys, follow us at some distance just in case they ambush us from the rear.
"gangsok knew that sungwoo would follow him into the pyramid.
if gangsok and the dragon had any intention of obstructing sungwoo's chase, he could not ignore the possibility that they set a trap along the way.
"alright, let's get inside now.
"sungwoo's party slowly entered the passage, leaving minsok and victor behind.
tramp- tramp-

relying on specter's eyes, sungwoo went inside about 50 meters, looking around carefully.
 fortunately, there was nothing unusual, except for some angel corpses here and there.
'uh?"but when he went deep inside, something brushed past him instantly.
 it looked like a shadow.
 sungwoo hastily moved the specter to chase the shadow.
 at that moment a light flashed all of a sudden.
 - your 'subordinate spirit (specter)' has disappeared.
his eyes went black at the same time.
 after all, he had to rely back on his eyesight.
obviously, specter was attacked by something.
"as expected, someone is in front of us with hostile intent.
 get ready.
"sungwoo's party started walking again, fully prepared for fighting.
 whooo-a gentle breeze blew past the floor, and suddenly the ceiling rose and a lobby-like space appeared.
 and at the end of it, a white gate stood tall.
 it was large enough to be seen as the gate of the fortress.
"i hear the noise coming from there.
 and there is someone standing out there.
"advertisements    jisu stared intently into the darkness.
a number of cipher torches lit up on either side of the door, with a shadow standing between them.
 it was a human.
 "oh, there you are!"he waved his hands, welcoming sungwoo's party gladly.
 actually, he was familiar with them.


 