\section{chapter 261}

                            the last to express support for the necromancer were the players in uijeongbu.
 they once had a head-on conflict with the necromancer, whose defeat led to the disintegration of the “reconstruction alliance.
” but they decided to support the necromancer now.





[1,047] uijeongbu emergency committee declares their participation in this war.
-author: uijeongbu emergency committee chairman │ hit: 40,003*although we once fought against the necromancer, we are going to wash away the sins from back then and move on with a fresh start.
 the first occasion for our new start is this mainstream.
[comments: 11]they expressed their desire to join the world tree camp early on, but they were rejected by sungwoo.
 after that, they were in the process of creating a new organization under the supervision of the liberation guild.
 fortunately, they could join hands with the necromancer, though belatedly.
as a result, all those who had some direct or indirect ties with the necromancer expressed their intention to participate in the all-out war, regardless of whether they were affiliated with the angel or demon camp.
although they have not yet issued an official statement, it was a fait accompli that the liberation guild would also fight with the necromancer.
hanho and jisu, who were preparing to carry out other operations while staying at the king’s hut, were watching the whole situation through the community.
“really? this actually means a great integration of all the korean server members, right? apart from these big groups, even small groups have also started declaring their participation, too.
”as hanho said, numerous forces of the south korean server declared their participation in the war and began to rally around the necromancer.
“if this is the case, i think we can mobilize more troops than we did during the warlord monster event.
”“you bet.
 after all, the warring states period is over, isn’t it?”when the large groups declared their alliance with the necromancer one by one, those who harshly criticized the necromancer began to disappear overnight.
 instead, there was a growing voice for the unity of various groups to protect the korean server.
of course, none of those who criticized the necromancer came out to join hands with the necromancer.
there was a gathering cloud of war over the south korean server.
***
meanwhile, apart from the formation of his alliance groups, sungwoo was driving out the monsters of the north korean server.
the 20 death priests were driven out of the room where the altar was and gathered in the corridor.
 inside the room, sungwoo and the north korean lich were talking face to face.
“chief priest, what will happen to us?”since they could not know what the two leaders were talking about inside the room, they were frustrated.
“well, if you’re lucky, you’ll probably be working for that man.
”“pardon? who the hell is that man? how can our prophet of death become so miserable before that stranger…”at that moment, some terrible sound was heard by his bedside.
 it was the sound of the zombie dogs.
 the 20 death priests were entangled with them and stuck in the corner of the hallway.
“chief priest? they aren’t biting people, right?”“no, but they are eating people.
”“oops! hiccup!”“so, don’t move and stay put in your place if you don’t want to be eaten.
”the fear of death was approaching the death priests.
meanwhile, the situation inside the altar room was serious.
 the north korean lich was sitting in a small chair straight up with his hands placed on his knees to maintain an upright posture.
although he was seated in such a proper position, he kept moving his chin.
crackle! crackle! crackle!“close your mouth!” sungwoo shouted.

“…”he immediately stopped moving his jaw at sungwoo’s shout.
 sungwoo was sitting in front of him, holding his black scythe in his hand and staring at him.
 behind him, minsok and orun stood on his right and left.
purrrrrrrrr―the headless knight on a giant monster horse, durahan, was holding a big sword as if he would rush to the lich right away.
 since the severed head in his left hand was staring at him, lich had no choice but to feel scared despite his status as lich.
at that moment, sungwoo opened his mouth, “what’s your name?”lich victor was really happy sungwoo asked him.
“my name is lich victor!”“what can you do?”“i can control up to 2,000 low-level zombies! however, if i raise 20 death priests, i can control an additional 50 per priest.
”victor tried to put his best foot forward as if he was having a job interview, but sungwoo’s expression was coldness itself.
victor’s hollow and glowing eyes trembled anxiously, looking at sungwoo and minsok alternately.
at that moment, minsok, who was standing next to him, opened his mouth, “this monster can think.
 wouldn’t it be better to kill him to get rid of the cause of possible troubles? if you don’t mind, let me behead him right away.
 then, you might be able to meet the conditions for certification of your qualifications completely.
”“ah! wait a minute!”victor tried to defend himself, but sungwoo cut him off and opened his mouth.
“who else is there above the monsters who have received the title of king?”“oh, the kings only serve the emperor, just one rank higher than them.
”“emperor?”“yes, the monster called the emperor is the strongest among the monsters that have earned the title of king.
 crackle! it’s safe to say he is the highest-grade monster on a server!”the more they were left alone, the more the boss monsters grew, but they were usually in the order of raid boss, warlord, and king in terms of hierarchy.
 however, it seemed that the emperor was on top of them.
“aren’t you serving him too?”“of course, i am,” said victor, nodding awkwardly.
“so, you want to follow me from now on?”“of course! my job is to serve death above all else!”as if to prove he was serious about it, a message appeared before sungwoo’s eyes.
-you can use the same type (undead) monster ‘lich (victor)’ as your subordinate spirit.
* because he has an ‘independent will’, he can “act” outside your influence.
* the target will obey your order.
given the contents of the message, sungwoo judged that he could trust this lich.
‘although this guy is a low-level zombie who can’t be resurrected, it’s going to be a tremendous increase in my power if he can control thousands of zombies,’ sungwoo thought.
without any hesitation, sungwoo immediately took victor as his subordinate spirit.
then, his eyes became even deeper and clearer.
 obviously, he was feeling relieved, knowing he would not be killed.
“crackle! crackle! thank you for choosing me!”

he suddenly sprang to his feet and bowed to sungwoo.
sungwoo stood up and said, “show me you are helpful to me.
”it was time for sungwoo to test his new weapon.
***there was an outpost of the one heart association in munsan town in paju.
it was a fortress they prepared for the possible disaster from the north, which was a pentagonal structure they built by mobilizing three architects.
right now, it was under attack by the enemy.
“the northern fence has collapsed! send us reinforcement troops!”an army of monsters mixed with trolls, orcs, and goblins filled the north side of the fortress.
they came across the dmz to the south earlier than expected.
“damn it, i thought the hordes of zombies would come first.
 how come those monsters came so early?”“reinforcement troops are coming soon! let’s hold out a little longer! if we are pushed back by them, we will suffer huge damage!”the one heart association could not give up paju because if they lost it, they lost everything they had achieved through hard work.
of course, they also had hope they could protect all of that.
“i hear the liberation guild and the hunter company will arrive within an hour to come to our rescue, so if we can hold out until then…”they pinned hope on the fact that they would get help from giant groups that declared their participation in the war.
 however, their hopes quickly fell apart.


 