\section{chapter 316}

a huge flame soared from downtown busan.





".
.
.
"it was bigger than any other explosion he had seen so far.
 it looked as if a volcanic eruption occurred or even an atomic bomb was dropped.
 when the red flames devoured the city center, super-sized buildings collapsed like dominoes.
 the flames that filled the roads and alleys climbed up the walls of the buildings, stretching toward the sky.
the red demon hit the official channel's drone.
as a result, the broadcast screen was turned off.
 ".
.
.
"reporter ahn and his assistant sprang to their feet and just looked at the terrible scenes blankly, but couldn't say anything.
 however, reporter ahn was confident that the necromancer took an extreme step.
busan, the place chosen as the battlefield, was devastated entirely.
all parts of the earth in busan were immersed in red flames.
 just like the early earth billions of years ago when it was nothing more than a fireball, only primitive and destructive scenes were unfolding repeatedly in the ruins.
follow current novels on lightnovelpub[.
]com "how terrible!"sungwoo was looking down at the terrible scenes while riding the wyvern alpha male in the sky.
 riding behind sungwoo, victor kept crackling his teeth while looking at the ground.
"crackle! crackle! wow, it's an absolutely destructive power! this is the true power of death! ultimate skill! crackle!"just like victor admired, sungwoo reinforced one skill to the 'ultimate' level through the synergy of , but this time it was not the skill of .
"as expected, explosions are valuable.
"that was true.
 the skill sungwoo used was the ultimate .
if there was an annoying enemy that sungwoo found hard to beat in person, he didn't have to fight the enemy directly.
 all he had to do was to blow up the ground the enemy and his allies were standing on.

***among the wizards who deal with death, lich boasts the highest level and shows a powerful "death power" that cannot be compared with those with lower levels.
 they could be an "arc mage" in terms of a wizard.
for more, visit lightnovelpub[.
]comso it was virtually impossible for one team to have three liches.
'yeah, that's impossible unless a dragon born from an egg that i picked up a long time ago learned my magic and became lich after having a boss monster born on another server as my subordinate spirit…'the numerous coincidences overlapped and created a ridiculous phenomenon.
it was , which enhanced one random skill to the 'ultimate' level, which was more effective and destructive than any synergy sungwoo experienced so far.
and the skill he got was as follows.
-the  skill has been temporarily upgraded to the  level.
[skill information]-name: corpse explosion-grade: ultimatenew novel chapters are published on lightnovelpub[.
]com-category: active-consumption: mana 1*it triggers an explosion by detonating a corpse.
 it releases a lot of additional damage (+200%) and 'abyssal breath' that contains the power of death after the explosion.
+ high-pressure explosion: the corpse expands for 20 seconds, then causes a powerful explosion.
 releases additional damage (+600%) and abyssal breath (+200%)
however, if you are attacked while the corpse is expanding, the explosion fails and you won't be able to use the corpse.
'up to this point, it's not much different from the previous one…'the important thing was that there was one more option below it.
 sungwoo once again confirmed the contents.
+ twilight flooding: gives the power of death to all corpses within a certain range (10km), then causes a 'super explosion' after undergoing a 30-minute 'soft' process.
 releases additional damage (+1,200%) and abyssal breath (+500%)visit lightnovelpub[.
]com for the best novel reading experience*in addition, after the explosion disappears, the phenomenon of 'twilight exposure' is triggered, which will make all the corpses revive as 'zombies.
' however, if you are attacked during the softening process, the explosion will fail and you won't be able to use the corpses.
'twilight flooding? this is really ridiculous.
'sungwoo tried to maximize the effect of this tremendous skill.
 he thoroughly prepared it during the 12-hour cooldown period.
'this battlefield is limited to parts of the city center within busan.
 that means that i can have all the enemies within the striking range of the corpse explosion.
'sungwoo mobilized all the demons and undead to scatter the corpses very secretly.
 in other words, he had them deploy corpses in various places in busan, such as underground facilities and buildings.
and 30 minutes before the start of the war, he imposed the "twilight flooding," causing a historical fanfare.
- caution! there is a "twilight flood" going on in the area.
such a warning message appeared in the eyes of the enemies, but 30 minutes was insufficient for them to grasp the situation accurately.
 even if they quickly noticed what "twilight flooding" was, they would not be able to find all the bodies that had been deployed laboriously by sungwoo's undead for 12 hours.
eventually, huge explosions swept the enemies away.
new novel chapters are published on lightnovelpub[.
]combut that was only a precursor to a bigger attack.
 a tremendous amount of abyssal breath was overflowing under the soaring flames, even if the enemies survived the explosions, they would slowly die in the breath of abyss.
"pour more corpses!"sungwoo wasn't satisfied with it.
 a group of bone wyverns flew over busan, dropping corpses like bombers.
then, they even dropped a gas cylinder.
 it was a bottle containing 'abyssal breath'.
 sungwoo obtained it from the main office of the evolution society, then stored it in a warehouse in the suwon village, waiting for the day when he could use it properly.
 and today was the very day he could use it.
 what if the enemies survived this attack?"poison cloud!"- caution! a 'poison cloud' has been formed in the affected area.
sungwoo was determined to kill them all.
follow current novels on lightnovelpub[.
]com"crackle! crackle! i'm going to use it, too!"- caution! a 'poison cloud' has been formed in the area.
victor also had the skill of 'poison cloud'.
 two huge clouds spread out right away, pouring poison over the ground that turned into hell.
even mir used it.
 - caution! a 'poison cloud' has been formed in the area.
when the three liches gathered, their destructive power was beyond imagination.
 sungwoo thought even the creator of this game might not have expected this kind of situation.
"good job!.
 both of you did a great job!"

-you have earned 17,000 gold by killing a playerthe source of this content is lightnovelpub[.
]com-you have earned 16,000 gold by killing a player-you have earned 19,000 gold by killing a player-you have earned 17,000 gold by killing a player-you have earned 18,000 gold by killing a player"alright.
 our operation is nicely paying off!"the messages that appeared before his eyes endlessly proved that his operation was successful.
the chinese army in busan was destroyed 10 minutes after the start of the war.
***"oh, my god.
.
.
what happened?"this content is taken from lightnovelpub[.
]comreporter ahn's studio was still paralyzed, unable to broadcast.
 all they did was show the huge explosions in busan, but when the drone filming the terrible scenes was ruined in an explosion, they could not do anything for about 5 minutes.
 of course, there wasn't just one drone filming the fighting in busan.
 dozens of drones were scattered all over busan, but all of them were smashed.
"okay, regardless of the identity of the explosions, isn't the "official channel" operated by the system itself? this means it's a huge variable that even disrupted the system's intentions.
""oh, i see.
 since the official channel was stopped, only the broadcast screens of the battlefields in suwon and seoul were shown.
 please those living near busan, please report to us what's going on in busan right now! we hope you have not been swept away by the explosions.
"of course, the players in busan finished evacuating before the war began.
"wait! the moment we just started announcing it, we have restored our broadcast screens for busan!"

 