\section{chapter 152}

                             




hanho was embarrassed by youngin’s question.
 is it really good for this little kid to become as strong as a one-star thief like hanho himself?“brother hanho, can i fight confidently without being intimidated in front of enemies like you?”hanho hesitated but nodded reluctantly.
“well, of course! it’s a bit difficult, but when i tried it, i could do it without any problem!”even after he drew the occupation cards, one-star thief and one-star priest, hanho thought he was so unlucky because he got only mediocre items, so he was deeply touched by youngin’s extolling of him and his fighting.
“brother hanho, you’re so cool!”“hahaha! do you really think so?”was he in the process of becoming a hero while struggling to survive?hanho felt very much satisfied after a long time.
***the terrible battlefield was captured by the camera.
“it’s all over…”the camera operator muttered, his voice trembling.
 there were no trees left after the bombing.
 the bodies of pirates were piled up.
“except for the few who ran away, our troops have been annihilated.
 this is a total defeat!”the camera operator was broadcasting all the scenes of the fighting at the order of the necromancer.
 as jahon was killed and the pirates were on the defensive, most of the viewers left, but 20,000 were still watching.
[real time chat]- chi-111004: that korean general is similar to china server 1’s emperor.
- xian5523: i also recalled that emperor.
 i saw only his photo and heard rumors about him, but i think he looks like the emperor when i actually see him.

- 壮烈: i think he is a level lower than the emperor.
 i heard that the emperor used more than 200 subordinate spirits in the latest battle.
- 李 大阿哥: since it is a small country, he must be a level lower than the emperor.
 i can’t recognize his competence, based on his victory today.
“emperor? who is the emperor?”when sungwoo asked, the camera operator opened his mouth in a subservient manner.
“oh, yes.
 china is divided into three servers, and the hegemon of server 1 based in xianxi province and beijing, is calling himself emperor.
 he conquered server 3, so he is considered the strongest on the mainland.
”“but why are they saying he is similar to me?”“as far as i know, that player named emperor also has multiple subordinate spirits like the necromancer.
”most of those with the five-star occupations were specialized in forming groups.
for example, the vampire lord infected the players to get them as his followers, and the crusader commander made crusaders.
 the so-called gen.
 chongong, whose identity was not yet revealed, seemed to be able to brainwash players below level 5.
however, it seemed that this guy named emperor was different from sungwoo by nature because sungwoo controlled monsters, not players.
 nonetheless, why are they saying he is similar to sungwoo?“what’s his job?”“i’m not sure…”it was natural that the strongest in mainland china would not easily leak information about himself.
after telling the operator to stop broadcasting, sungwoo bound him.
 he planned to detain this man in order to monitor the movement of the chinese servers because although he was in korea now, his mobile phone stayed connected to the chinese community.
then, sungwoo stood in front of jahon’s body.
 two hand cannons dropped near him.
[item information]-name: hand cannon (level 3)-grade: hero
-category: hand cannon-effect: inject mana to load bullets.
 (10 mana spent)it was a weapon that could inflict damage powerful enough to push back an opponent with a shield.
 although sungwoo couldn’t fire it randomly like a repeating crossbow, he could use it for a fatal attack.
 if the timing of the attack was good, it would be a pretty useful weapon.
sungwoo took one of them and tied the other one around orun’s waist.
“although you have only one arm, try to use it well.
”crackle! crackle!“as a one-armed warrior, orun, you can’t give up the warrior synergy.
 by the way…”sungwoo suddenly examined orun.
“if you have only one leg, what synergy will come out of it? i am suddenly curious.
”pondering over it, sungwoo looked at him, but he avoided sungwoo’s gaze slowly.
“oh, you can’t give up your excellent agility, of course.
”crackle! crackle!sungwoo continued to check jahon’s items.
 they were trifling accessories compared to the ones around his body.
“let me give this to hanho.
”as always, sungwoo took care of his juniors very well.
now he had one last thing to do.
-the dead will be your subordinate spirit.
-you can read the “memory fragments” of the dead.
jahon’s memory was regenerated.
the place was inside the ship.
 it appeared to be inside the container ship, the flagship of the pirate fleet.
“it is said that an angel statue was found in taiwan.
”saying so, jahon sat down.
 at the long green table were the executives including kuan and huei.
“an angel statue? this is the first time since the demon statue was found on server 1?”“oh, my god! oh, my god! finally, the hint about the absolute race is coming to the surface? what kind of features does the statue have?” kuan asked as if excited.
‘i forgot about it.
 i remember there was going to be updates on the angel and the devil.
’sungwoo also paid attention to it.
 he had no information about the ‘absolute race’.
“only gen.
 chongong touched the statue.
 according to the general, we should receive a quest, but he didn’t tell me the details yet.
”“really? he didn’t tell you about it, gen.
 jigong?”jahon, namely gen.
 jigong, nodded, then said, “it seemed difficult for him to tell me right away.
 he said he would tell me after conquering seoul.
”“i’m very curious.
”“i’m curious too, but we have to focus on our mission,” jahon said and put something on the table.
 it was a brown parchment scroll.
“now, let’s get to the point.
 shortly after occupying kanghwa island through a mini-game, huei’s team will sneak into seoul and use this scroll.
”it seemed that they had already set up the plan for what to do after conquering kanghwa island.
 taking off his sunglasses, kuan began to make a fuss.
“wait a moment! isn’t it “devil’s gate”?”“right.
 immediately after using this, the devil’s gate opens for 24 hours, and all kinds of monsters will pop out.
 the monsters will disappear after 24 hours, but it’s enough time for them to destroy the whole area.
 maybe we can occupy seoul without letting out blood.
”kuan nodded in admiration.


“this is an item that originally opens the hidden dungeon, but the level of difficulty is so high that it has established itself as a legendary scroll used as a strategic weapon! do we have to use this after the mini-game? i can’t help but think it’s too precious to use.
”“well, this kind of investment is nothing.
 the korean server will be much more valuable to us than the taiwan server.
 gen.
 chongong said we should not spare investment for this.
”unfortunately, the investment he made fell flat.
“we’re going to start the operation now.
 huei, take your assassins and set out to kanghwa island.
 go and stick the flag there!”“yes, gen.
 jigong!”the video ended there.
‘what is the purpose of this memory?’as always, the fragments of memory showed sungwoo something helpful.
 so, generally speaking, he could find some clues or information from the scenes from the fragments of memory.
‘i think i need to obtain the magic scroll called devil’s gate.
’since he already won the battle, he might not be about to recover key information from it, or it could provide some information about the location of good items.
anyway, he had to go to their container ship.
in fact, he had asked heyon to monitor the fleet near the landing site of the pirates in order to get rid of the enemy’s remnants.
a little later gust flew from the southern sky.
 then, heyon jumped down hurriedly and came running to sungwoo.
“i’ve seen everything! i think they are preparing to turn the course to taiwan right now.
”a considerable number of on-call soldiers remained on the container ship.
 however, since the mini-game was not over yet, they couldn’t leave the coast of kanghwa island, but they could escape after nine hours.
“by the way, wizards on the deck are on standby all the time.
 i think they are holding out there, thinking they have to stop the allies forces from getting aboard the ship.
”obviously, they seemed to have prepared a means to defend the fleet in case of contingencies.
if there were a number of wizards on the deck, like she said, it was highly likely that it would be impossible for sungwoo to attack them or infiltrate the ship.


 