\section{chapter 463}

they let out an eerie sound and spewed sticky liquid around gigantes' bodies.





while they were tied like that, the demon king punched his arms at their heads.
since he had eight arms, he could attack four gigantes at the same time.
koo-woong-gigantes also raised their arms to defend, but they lost their balance and knelt when the demon king struck them with his arms that were larger than their heads.
at that moment isabella let out dragon breath, nosediving toward him.
kwagwagwagwa!but the demon king raised both hands and fired a certain wave, which mixed with ice breath and canceled out its devastating power.
right after that, something passed over gigantes' head and hit the demon king's arm.
it was the cannon fired by the fleet.
 the airships fired cannons all at once to keep the demon king at bay.
"get ready to fire again!"but the demon king's counterattack was faster this time.
 he turned one of his heads and looked towards the fleet, then sparks began to emit between the two horns on his head.
"those at the forefront, avoid it!"but it was too late.
a single-shot red lightning bolt, which was a bit weaker than a beam attack, was fired.
at first, the shield of the airship seemed to block the beam, but it bent inward like plastic before it was punctured sharply.
 and the exposed hull of the airship was torn apart in the blink of an eye.
"emergency! get out of here!"everyone died on the deck of the airship, and the hippogriffs hanging from the stern soared into the sky all at once.
 but most were swept away by the beam.

they were literally annihilated.
disaster was also happening on the ground.
 a tremor erupted under the ground where the retreating ground forces were stepping on, then something soared from underground.
"what the heck is that?"it was a bunch of red tentacles.
when they fell on the heads of the retreating soldiers, dozens of them were killed at once.
 even hellish beings even began to spring out from the bundles of tentacles.
kheeeeeeeeeeeeeeeeee!they charged at the soldiers and burrowed into these soldiers retreating in big confusion.
"ahhhhhhhhhhhhhh!"a massacre was taking place.
"hey, wake up! block them!""watch your back! ouch!"the players suffered huge casualties without even inflicting any damage on the demon king.
 and this horrific scene was being broadcast live to 91.
2% of those who refused to pledge an oath of allegiance to the demon king.
a heavy tension dominated reporter ahn's studio.
reporter ahn paused for about 30 seconds before opening his mouth.
"well, i just don't know how to explain this situation now…"sungwoo's allies were overpowered by the demon king.
 and there was a high possibility that they would be annihilated soon.
"have they ever been attacked by an enemy like this in the past?" reporter ahn asked his assistant, who shook his head in bewilderment.

"i can't remember very well, but i can recall one thing for sure.
""can you name it?"the assistant lifted the bottle of water, but his hands were trembling.
"well, i know they were pushed back by the enemy when they were not with the necromancer, but they had never been pushed back when they were with him!"reporter ahn said with a nod, "you bet.
 the necromancer has always been prepared for the worst to come and came up with a new strategy.
 it looks like he is currently trying to come up with something, but it's just useless.
"while he was briefing the situation in low spirits, the scenes on the battlefield displayed on the screen behind his back showed them sliding into a more and more desperate situation.
a terrible cry rang out, and the creatures of hell rushed at the players on the ground.
"hold out!""too late! let's run away!"come on, take a seat!"the players were already exhausted, so their ranks collapsed.
 and they didn't receive any gunfire support from the world tree fleet.
 that's why they struggled to defend.
"as things stand now, we're going to be slaughtered.
 how can the players from all over the world collapse like this?""well, this is a moment that requires the turn of events like a miracle!""you're right.
 i also look forward to that.
 i wish something could happen.
.
.
"at that moment something really began to happen.
bang!the ground shook with a roaring sound right before the creatures of hell, then something came out from the underground.
 it was a huge green lump.
"·whew! something has appeared!"it was a giant mythical creature in the shape of a turtle, namely, hyunmu.
"hope we're not too late.
 everyone, come out quickly!"hanho, jisu, junghoon, li wei, and chen were riding on the back of hyunmu.
besides, lots of players also came out from the ground that hyunmu lifted, who were the elite forces affiliated with the special commando unit that attacked the labyrinth.
"now, let's go!"shouting like that, hanho spread his six hands in all directions.
 then his eyes turned green.
- caution! a 'shadow zone' has spread in the area.
hanho used one of hyunmoo's powers, the 'shadow zone'.
 the energy of the shade filled with cold and poison spread and formed a wide buffer zone.
 as a result, the creatures of hell couldn't easily attack them, while the players got their act together.
"now! wake up and come together!" the voices of the commanders rang out.
"tanks, move forward! raise your shield!""wizards, prepare your defense magic!"their formation was a bit different this time.
 the necromancer did not appear in front of them, but they stood ahead of him.
"alright! finally, they're back!" reporter ahn shouted.
 their appearance was dramatic enough to give them a ray of hope.
"even though they seemed to number around 200, they have high morals.
 wait a moment.
 what is that?"at that moment cannons of fire fell over the heads of the hell creatures clustered outside the shadow zone.
 they were obviously the start of bombardment by sungwoo's allies.
 "hell creatures suffered near-annihilation after they were exposed to the allies' bombardment!""but don't you think it's a bit strange? the fleet is clearly far ahead of them, right?'

"they are not the world tree fleet! they started bombing from behind! look at the scenes of bombing on the screen.
"as the assistant said, the bombing started from the rear.
 soon, the screen illuminated it.
woo woo woo-a whopping 24 airships filled the western sky.
"are they the wpu fleet?"when the hypergates opened at the rear, the wpu fleet, which had returned to the us server, finally joined them.
"wow! jonathan! long time no see!" hanho shouted.
jonathan was standing on the deck of the lead airship.
 and next to him was chairman love.
 that wasn't all.
"look at the dot over there!"a huge number of portals were open beneath the numerous airships.
 all of them were hypergates.
"dozens of hypergates are open! that means they are not connected to just one place.
 how come they are connected like this?" shortly afterward a huge number of players began to come out through the hypergates.
"let's go!""move! come on, take your position!"they dispersed in all directions, lifted their weapons, and showed up with a significant number of flying weapons, and began to install them here and there.
they kept coming out, who seemed to number over 100,000.


 