\section{chapter 461}

when she replied repulsively, his eyebrows twitched.





"what did you say? sounds good?"but she turned to the right and shouted, "bring it on! don't try to put on airs because you wounded me a bit!"soon vivona's shadows began to rotate rapidly.
 she could not figure out which one was the real one.
"you have not yet come to your senses, bitch!"but she just raised her middle finger without responding.
".
.
.
"wishing earnestly that this psychopath could get furious and attack her stomach, she focused on her body, not his shadows.
 she was willing to let him attack it.
at that moment, her body flashed and shot like a light beam.
 most ordinary players could not avoid her skill because she rushed and wielded the sword in the blink of an eye.
 but vivona was different.
clang!his shadows soared and clanged her sword.
 she immediately stepped back.
"are you going to use that shallow skill again?" vivona laughed.
she scratched her head, then lifted her middle finger once more.
".
.
.
"vivona's lips twitched when he saw it.
'from now on let me block his attack once, but wield my sword twice.
'hoping earnestly that he could expose his weak point, she was on alert.
tramp- tramp-she clenched the sword with her right hand, then slowly walked to the left.
vivona stuck where he was.
at that moment she jumped off the ground.
 then she did three run-offs before jumping, then she approached him in an instant.
 so much so that both of them were so close to him as to kill each other with just one strike at any moment.
'his shadows are coming…'she could feel his shadows coming close to her, but she could not see them.
but the air his shadows pushed out touched her body, which made her feel something was getting close to her.

jisoo's body, letting him know that something is very close.
of course, their closeness meant that both of them could not avoid their attack against each other.
'he's aiming at my stomach!'furious about her provocations, vivona aimed at her stomach like crazy.
but she turned her waist to the side as far as possible, put down her left shoulder, and covered her stomach with her left hand.
at that moment vivona attacked her.
 her left arm was completely cut, fully exposing her flesh and bones.
it was a close call for her.
 but a clear message appeared before her blurred eyes.
- 'synergy effect' is given due to team play.
[synergy list]1) one-armed warrior- category: individual synergy- condition: sword on one arm- effect: increases the success of the first attack by 88%.
jisu did not stop.
 she felt a tingling sensation in her left arm.
 an unbearably intense pain dominated her nerves and central nervous system.
'i've managed to defend!'even though she lost her left arm, she was not killed.
her eyeballs and eardrums throbbed in excruciating pain.
 she now focused only on her right hand holding the sword.
'alright.
 let me attack him this time.
'she aimed at his side.
at that moment he smiled and raised his hand, which he had never moved before.
he was holding two daggers.
 he didn't move from his spot.
 he smiled in satisfaction because he was now confident that he could block her attack.
'he doesn't know it yet,' she thought to herself.
she was right.
 vivona didn't know the synergy of 'one-armed warrior' because he had never had his arms cut by somebody else before.
 and there were few who survived after his arms were cut.

but she experienced it indirectly as soon as the game started because she saw somebody who survived with one of his arms cut.
huuuuuuuung!she swung the sword at the daggers he lifted high.
 then she looked straight into his smiling eyes.
"ugh?"he stopped smiling in embarrassment.
"crazy!"the moment he blocked her sword, his sword, his arm, and his balance slid all the way down.
"alright, now is the time!"finally, vivona exposed a critical weak spot that could make her deal a fatal blow.
'this is my second attack!'she focused on it as best as she could.
 stepping on the ground with her right foot, she pulled her severed left arm back as far as possible, then tightened the tip of the blade after swinging her waist.
it was a perfect single attack.
with beeping in her ear, she heard the sound of something falling.
- you've obtained 24,000 gold by killing a player.
"argh…"vivona felt dizzy and nauseated.
 when he turned his head slightly to the left, his left arm was cut off to the shoulder line.
 blood gushed out like a fountain, staining his entire left body.
 and something round was half-submerged in the pool of blood.
 it was his head'i've killed him!'***"hahaha! i've won!"hanho's voice echoed in the hallway.
 a large man was lying at his feet.
 of course, he was paulo.
"ugh.
.
.
"he was gasping for breath, with his whole body shattered.
 metal beads were stuck all over his body.
"my god.
.
.
how stupid i'm to allow you to attack me like this…"obviously, he still didn't seem to be able to accept his defeat.
"hey, junkie, think about it carefully.
""what the heck are you talking about?"hanho squatted down and looked down at him, sneering at him.
then he said, "maybe you might be a hamster.
"paulo barely tilted his head since he was too weak to move.
"hamster? what the hell are you talking about?"hanho stroked paulo's head, saying, "you know what? i've come to realize that hamsters don't know they are hamsters.
""oh my…""and your name sounds like a hamster.
 pudding hamster, in particular.
 paulo, well, let me give you a new name.
""what the heck…"hanho stood up and raised a hand cannon.
"anyway, it was fun fighting you.
 hamster, just keep rolling the wheel in the sunflower garden in the future!"how would he feel if this was what he heard last while he was alive?bang!paulo felt his last moment came.
while hanho killed him, junghoon and the players under his control also got rid of all the remaining monsters.
"come on, get ready to move! got to the exit!"at that moment a woman's shout was heard from behind.
"help! help me!"it was li wei's voice.
"ugh?"li wei appeared with the water spirit in the darkness deep inside the hallway.


jisu was placed on top of the water spirit.
but strangely enough, the water spirit was all dyed red.
"priest! come on, priest! is there a priest with a rank of 4 or higher?"only then did hanho check jisu's condition.
"ugh? jisu! what happened to your arm?"one of her arms was entirely severed, and it appeared that she already shed too much blood.
as liwei said, she needed a high-grade priest, but it was hard to find such priests right now.
"are you okay, jisu? right?"jisu opened her eyes, but she couldn't reply.
 was she too weak to say?"well, you've overcome all the difficulties until now.
 so you can…"at that moment something fell in front of hanho's feet.
"what the heck? blood? blood!"it looked like she bled at least several liters of blood.
"oh, no······.
"only then did he feel she was in serious condition.
 besides, there was no player here who could heal her wounds.
"come on, let's get out of here! if we go back to the airship.
.
.
" then they turned to the exit.
"wait, wait.
"at that moment somebody blocked them.
 there was one big shadow and two small shadows.
"um, this is the first time i've seen her severely wounded.
 i am heartbroken.
""uncle tiger?"

 