\section{chapter 319}






 they were embarrassed to see the official broadcast changing to a different battlefield in an instant.
 all the viewers were confused.
but the reason was simply that there was a much more interesting situation unfolding somewhere else.
 the camera was illuminating the center of the ruined city covered with black fog.
 nobody would have survived in such a situation.
 but the necromancer was standing in the middle of that hell.
 he was grabbing someone’s neck.
“kheeeeeeeeeek!”sungwoo shouted, “why did you come back?”it was boris, the assassin sent to kill the necromancer, who was no.
 1 in the russian server rankings, called the tsar, who was struggling to get out of the necromancer’s tight grip.
with both eyes bloodshot, he could not use any force.
 he somehow survived the hell the necromancer created, but that was it.
“so, the land here is much colder and harsher than siberia?”the last survivor of the busan battlefield was captured by the necromancer.
since he once fought against the necromancer, he was confident that he could kill the necromancer easily.
“yes, boris is the strongest guy who can beat anybody, and i’m sure he can beat the necromancer.
 sure, i trust him.
”general xing concluded that boris could beat the necromance after carefully analyzing his power based on a lot of information.
 that’s why he dispatched boris to the battlefield in busan.
“but i can’t rely on boris alone.
”general xing was not the type of man who relied on his own conviction too much.
 so, he recognized boris’s power but did not trust him.
‘of course, he can fail…’that’s why he took extensive “additional measures” in case of boris’s failure.
 in addition to the priests requested by boris, he decided to select and send a number of “elite soldiers” to busan.

right before he deployed them, general xing gave them a sharp reminder.
“just remember that nothing is as foolish as your conviction.
 your conviction leaves you off guard and makes you miss the chance to prepare thoroughly.
 so, you should try to stand on your own rather than relying on boris.
”“yes, we’ll kill him without fail.
”“general, don’t worry.
 you trust us, right?”the “elite troops” selected by the general were full of confidence, as always.
 in fact, they comprised one thousand ace fighters, including the sniper squad who assassinated thousands so far, the kwanggum unit, often called china’s holy knights, and the sorcerer corps led by the four-star “arc mage”.
because of that, they would certainly get on their high horses even when they were sent out to confront the dragon, not the necromancer.
“alright.
 no matter what they say, you are the best elites of the empire.
 but you have to make yourself perfect warriors for your honor and reputation all the time.
 and you can become perfect when you think you are not perfect.
”as soon as general xing spoke with a heavy voice, they, who were overflowing with confidence, became sober and sincere.
“we’re going to keep in mind what you have said, and join you in suwon, your battlefield right after doing a great service in busan.
”“sure, i will trust you.
”with such a large number of overwhelming elites deployed in busan, general xing thought it was a fait accompli that busan would be the necromancer’s grave.
however, their operation completely failed.
twelve hours after they were deployed in busan, the battle began.
while general xing was commanding his troops in suwon, he was briefed on a shocking report.
“general!”
“what’s up?”“busan was bombed!”“…”“and it’s estimated that our forces were annihilated!”at first, the general could not figure out what his deputy was talking about.
 he even doubted the war report.
 but by checking the official channel broadcast, he could confirm the devastated busan, which gave him the creeps.
‘man, this was a much more difficult battle than i thought.
’despite the tremendous tragic news, general xing was not embarrassed.
 he rather began to be happy.
‘a difficult war is supposed to bring more pleasure.
’feeling his heart beating fast, he quickened the pace of occupying suwon because he was not sure when the unpredictable monster necromance would appear.
‘this is a race against time.
 i have to end this fight before he appears here.
’then, the general lifted his head and looked at the world tree rising in the center of the village inside the city.
‘let me quickly break through the wall and pull out the world tree.
 so, even if the necromancer wins this battle, i have to make sure he does not challenge us again.
’he smiled softly.
 even if he lost one battle, he had no problem as long as he won the war.
***boris struggled with his neck grabbed by the necromancer.
 he could not admit it.
wasn’t he the ruler of the harsh siberia and no.
 1 in the russian server rankings?although he was humiliated in a surprise attack last time, he was different this time.
 he came out, burning with desire to take revenge on the necromancer.
 he didn’t even drink to guard himself against any stupid lapse or mistake.
but he collapsed without even attacking the necromancer.
“damn bastard…”boris survived thanks to his strong build but that was it.
he couldn’t even walk on his own because he was trapped by all kinds of curses, such as explosions, poison, and abyssal breath.
“how could you attack me in such a mean way…?”he couldn’t give up his pride until the last minute.
puck!at that moment, sungwoo punched his abdomen heavily, its impact made him droop helplessly.
“kheeeeek…”then, sungwoo tightened his grip on his neck hard.
“this time i don’t smell any alcohol from you.
”“…”“yeah, i didn’t drink because i came here sober after deciding i would not be defeated again.
 i was determined i would not let you deceive me…”sungwoo sneered at him and quipped, “man, that’s why you’re stupid.
 you just believed you found out how to attack me and became arrogant as if you found a new world.
 that’s why you are repeating the same mistake.
”

sungwoo smashed boris down to the concrete.
 a tremendous impact climbed up his spine and made his backbone tingle.
“ugh…”next, a troll skeleton appeared right next to sungwoo.
 the skeleton was holding a lava-flowing sword, ‘levatain,’ in his hand.
sungwoo was handed over the sword.
“wait a minute…”boris held out his palm, but sungwoo stabbed the sword in his chest without hesitation.
puck!no matter how strong his body was, he could not withstand sungwoo’s lethal stroke.
“i’m sorry, but i don’t have time to hear your bullshit.
”when lebatain turned red with flames, boris’s upper body crumbled and turned into ashes.
the moment the last survivor collapsed, a message appeared before sungwoo’s eyes.
-the korean server has won the ‘busan’ battlefield!* you can ‘join’ another battlefield in 5 minutes.
sungwoo’s eyebrows wriggled when he saw the message.
 it was an unexpected situation.
“man, this is dangerous…”he could not move to suwon in five minutes, no matter what.
 these five minutes would make heaven and earth difference in this all-out war.
 if he couldn’t arrive at the next battle in five minutes, his allies could be killed.


 