\section{chapter 263}

                            the moment the necromancer arrived at the battlefield, the tide of the war was turned.
 so, the leader of the one heart association felt that the necromancer’s presence itself could increase the morale of his players.
 he and his players wished this savior could stay.





“i thought you would stay here with us.
 no?”the necromancer shook his head and said, “i’m going to the north.
”“really? oh, you have to stop the monsters from coming from north korea, right? can i ask you which area you are going to defend?’but his answer was rather unexpected.
“this is a war.
 you cannot win just by defending.
”“pardon?”the message about the mainstream was that they should defend this land by confronting the large-scale monsters from north korea.
but he chose to attack the monsters rather than defending this land, which was clearly against the intention of the system.
1***sungwoo got information about the north korean server through victor.
since victor was one of the king monsters on the north korean server, he provided sungwoo with more reliable information than anybody else, such as the distribution of monsters within the north korean server and the emperor-grade monster who controlled them.
“the emperor-grade monster is in pyongyang.
 i have never seen that bastard’s face.
”“have you never seen him before? then, why did you serve him?”“well, there were lots of wild rumors about the guy.
 according to the rumors, he was originally a field boss monster, but he increased his worth by eating the raid boss monsters that were created afterward.
 if they didn’t obey him, he chased and ate them…”if he were a field boss monster, he was probably like the korean server’s bone wyvern alpha male.
 in other words, he was a monster at the leadership level of the korean server.
‘if he had been left alone, he would certainly have grown endlessly…’monster growth was not an event that took place in real-time.
 like the king of the great mountain, who was created in mt.
 taebaek, such a phenomenon occurred only when there was no crackdown on the local monsters.

“so, what kind of race does this emperor belong to?”it was the most important information.
“in the past, he was affiliated with ‘elder drake’.
 it was a smelly reptile.
”sungwoo had once confronted drake during the yeouido raid.
 however, he was a young drake in sungwoo’s memory.
“how about now?”“he is associated with a feverish reptile now.
”“are you making fun of me now? you want to give me a quiz?”when sungwoo frowned, victor’s glaring eyes trembled out of fear.
“crackle! no, sir! he is salamander!”‘salamander?’that name was also familiar to sungwoo.
 the moment he put on the hellfire armor, he got the privilege of the ‘salamander’s aura’ that was triggered when his immunity exceeded 150%.
and in fantasy, a salamander is often described as a ‘fire spirit’, a lizard covered in flames.
“does he have the trait of flames?”“yes! i hear that he emits a fire hot enough to melt rock.
 he has a very nasty temper, so other king-grade monsters are reluctant to approach him.
”“really?”“yeah, he’s a horrible guy.
 so you had better watch out for him…”“well, it looks like i can enjoy talking to him.
”
“pardon?”sungwoo led thousands of zombies and began to advance to the north.
***“well, isn’t this too unexpected a situation? he clearly said he would hold out at the imjin river.
 why did he suddenly move to the north?”the king of the great mountain was watching all the scenes through a crane.
 he even grasped the situation where sungwoo’s undead army turned their direction and marched toward the north.
“if that’s the case, what about his promise to appear at the critical moment for us?”“well, he takes care of anything cool by nature,” said hanho when the king let out a sigh.
“are his actions always this unpredictable?”jisu, hanho, and the king were supposed to join sungwoo a little later after taking care of other pending issues first.
but sungwoo suddenly decided to advance to the north, which made them change their original plan.
“oh my… it looks like he is going to have a hard time fighting the monsters in the north…”“aren’t you supposed to move north and join him as soon as possible?”at that moment, jisu felt a bit annoyed because they could not do anything when sungwoo was now advancing to the north.
“anyway he moved faster than we thought… hey, have you boiled potatoes yet? didn’t i tell you i needed some snacks before going deep into the mountain?”when the king shouted in an angry tone, one of the tigers walked out of the kitchen hesitantly.
“oh, brother, i have run into a problem.
”“uh? what happened?”the tiger looked back at jisu.
“well, jisu, you said i needed to boil potatoes long enough, so i could poke them deep with a chopstick, right?”“yes, that’s correct.
”the tiger looked embarrassed.
 then, he gave him something.
 it was a potato.
“even though i didn’t boil them, i can poke them deep like this.
 so, can i eat it now? i’ve already taken a bite of it, but it doesn’t taste crispy at all.
 is it because they are rotten or bad?”the raw potatoes he showed had five traces of chopsticks stuck deep into them.
“…”even if they weren’t ripe, these giants were so strong that they got poked deep enough when they slightly touched the potatoes with the chopsticks.
“gosh! get out of the way.
 let me boil them,” said jisu.
she felt it would be faster if she boiled them in person, so she rolled up her sleeves.
but the king sprang to his feet and flew into a rage.
“you punk! how dare you have your guest roll up her sleeves? how rude and stupid of you! when can i expect you guys to be useful to me?”the tigers froze at the king’s angry scolding, but she stared at him instead.
“be quiet.
 we have to get things done here and move quickly!”“what? did you just say it to me?”she had to leave right now, but the king put priority on eating potatoes, which made her so frustrated.
“come on! don’t play the game of a king! act like a king!”“ah, i see.
 hope i’m in your good hands, jisu.
”

at that moment, the king immediately bowed to her, nodding.
“act like a king…”when she entered the kitchen, the two tigers quickly followed.
 they glanced out of the kitchen and started flattering her.
“jisu! what you said just now was the most fantastic statement that i heard!”“act like a king instead of playing the game of a king! yeah, you’re right!”but jisu stared at them angrily and said, “excuse me? you’re blocking the sunlight.
 so, just go outside the kitchen.
”“yep.
”“i will do as instructed!”***thousands of zombie corpses advanced to the territory of north korea.
 hundreds of crows were following them like a dark cloud, which spread from time to time in all directions and monitored everything around the area.
“master! when you cross the hill, you’ll find a troop of trolls! they look like almost 100!”victor has reported to sungwoo about the tips he obtained through the crows’ eyes.
sungwoo felt it was so convenient as if he had an aide-de-camp because of victor who could control his undead.
“let the zombies bypass the trolls!”“yes, master!”the maximum number of zombies that victor and the death priests controlled reached 3,000, but they could not be resurrected, and they were no more than low-level zombies.
 in other words, they would suffer huge damages if they confronted the trolls.
because of that, sungwoo changed the direction of his troops while advancing toward pyongyang.
 he was thinking of preserving the troops as much as possible.
sungwoo sent several large undead to clash with the trolls because they were an easy target.


 