\section{chapter 278}






 “are you asking for gold?” sungwoo asked.
“so, how much gold do you want?” minhum asked.
 since the liberation guild was already driven to a dead end, he asked it with the worst situation in mind.
“so, you want to know our demands first? great.
 but don’t be too surprised.
”“…”“300 million gold in return for our withdrawal, but if you want to get rid of our secret client, your potential adversary, you can add another 300 million gold to it.
 in other words, a total of 600 million gold.
 do you have it?”the liberation guild didn’t have that much gold, and even if they had, they didn’t have any intention of agreeing to her offer, but minhum was attracted to her offer in a different sense.
‘then, it means they have at least 200 million gold right now?’however, minhum quietly stepped back.
 whether it was 300 million or 600 million, the liberation guild could not afford to secure that money.
“uh? looking at your expressions, it looks like it’s difficult for us to strike a deal.
 do any of you want to bargain with me?’no one answered.
 then, she got on her high horse, nodded with her arms folded.
“if you don’t have money, just run away quickly.
 you still have time to run away until our tsar wakes up.
 but, you should go as far as you can.
 just cross the pacific ocean to go to america in search of your american dream.
”‘the moment she finished talking, the cigarette she held with her index finger began to freeze.
“then, you could survive for a few more months.
”blah blah-at that moment, the ice floor began to spread from under her feet.
 the marble material froze in an instant, and sharp ice sprouted above it.
“aren’t you running away? then, i think i have no choice but to put up a few ice statues at this station.
”her eyes turned blue.
 at the same time, the temperature in the area quickly fell.
sungwoo, hanho, and minhum felt their skin hurt because of the freezing cold, and the russian men sitting behind her also began to fasten their collars.

it was at that moment they realized who froze the entire crusader team members.
minhum trembled in the biting cold, then instinctively stepped back.
“sungwoo?”but sungwoo was different.
 he walked forward.
 his body began to be covered with black armor.
 it was “hellfire armor”.
rattle- rattle-blue flames emanated from the black armor around his body.
 then, the ice floor that approached his feet melted and slowly began to retreat.
cheeeeeeeeeeeeeeee-water vapor exploded from everywhere.
“oh, what the heck! who are you? aren’t you the necromancer? yeah, you’re right.
 but why are you giving off something hot like this?”having fire immunity, and as a result, not feeling something hot meant that sungwoo had so much heat.
furthermore, one more buff was added to him.
-‘fire spirit stone (higher)’ causes a ‘special effect’ in response to your power.
* temporarily increases fire immunity (+10%)* temporarily increases fire damage (+10%)whenever sungwoo moved, all the surroundings around him began to be filled with water vapor.
 the russian guys who tightened their collars behind the woman unzipped halfway again.
 then, they put down the alcohol bottles and took out their weapons.
watching them, sungwoo smiled at them.
“well, let me offer you a little cheaper price.
”“what?”
“give me 200 million in return for your going back alive.
”“crazy bastard!”“aren’t you running away? then, let me do something else instead of setting up a statue…”a huge black sickle appeared in sungwoo’s right hand.
“i’m going to erect your bones.
”in no time, heat and cold collided, causing a vortex.
ooooooooh-the frost that had stuck to the surface of the floor and walls rose as water vapor, then became snow in the air and scattered everywhere.
 that phenomenon was repeating over and over again.
tatana tried hard to cover sungwoo and his party with the intense cold she exhaled but that didn’t happen.
“uh? this guy is a lot more annoying than i thought.
”“don’t start to throw a tantrum already!”at that moment, an army of the undead came out from behind sungwoo.
 hundreds of undead walked out of the black smoke.
 what really annoyed her was hundreds of undying troops.
but even faced with such an overwhelming force, the siberian hunters weren’t scared.
“look at that shit! lots of cute guys appeared.
”“hey, andrei, there’s one guy that resembles your wife.
”“my wife will kill you!”they started to warm up as if they encountered something interesting.
 they totaled 21, only one-tenth of the undead army, but they stepped forward confidently.
“let’s wipe them out before our tsar wakes up!”“sure.
 if he wakes up, he’ll still be drunk and talking nonsense!”rattle! rattle!the undead army passed by sungwoo and pushed into the square of yongsan station like waves to clash with them.
when tatana waved her hand, an ice pick soared from the ground.
 the vanguard of the undead army shattered at once, and an ice barrier blocked their advance.
however, the undead army did not stop.
 they climbed on a pile of broken bones and jumped over the ice barrier.
bang!an explosion occurred in the air, scattering bone fragments in all directions.
 it was a canon.
 one of the hunters was holding a barrel the size of his body.
“oh! nice explosion!”just like their title ‘hunter’ suggested, they moved in tandem to find the best way to attack.
tatana stepped back then used freezing magic around sungwoo.
 even that magic made lots of undead skeletons unable to function properly.
bang!wizards and shooters in charge of firepower attacked the undead in the rear, and freezing magic exploded over their broken bones.
since the bone fragments that should be recombined were coated with ice, it took a considerable time for them to be resurrected.
the strategy of the hunters was quite unusual.
‘if they keep attacking us like this, we’ll have no choice but to be on the defensive.
”lots of enemies chose the so-called ‘main target assassination” as the surest way to attack the necromancer.
 since they found it hard to endure the unilateral damage inflicted on them, they came up with such a strategy.
but it wasn’t easy to translate it into action.
 the moment the assassination failed, their strategy was supposed to fail, too.
“alexey! charge at him and hit back the bone fragments with a shield! make it hard for him to come back!”

the hunters’ strategy was quite different.
 because each of their skills was outstanding, they chose a war of attrition.
 they decided to close in on the necromancer.
at first, a large number of the undead army were defending the necromancer, but when they kept up with the freezing and fire attacks, those undead skeletons who became incapacitated increased.
 and they didn’t give the incapacitated undead any time to restore themselves.
khaaaaaaaaaaa!a giant brown bear rushed with the giant warrior named alexey and blew away the undead.
each time the brown bear swung its paws, five or six undead were thrown dozens of meters away.
‘man, i mobilized the entire undead army to confront them, but they didn’t kill even one hunter! each of them is pretty strong.
’sungwoo moved back and forth between the undead and fired the repeating crossbow.
tung! tung! tung! tung!however, they blocked the arrows by rolling on the floor or lifting their shields.
 they had extraordinary senses.
 it seemed difficult to hit them with a weapon flying in a straight line.
“if that’s the case…”sungwoo took out ‘bi hyung’s fan’ and summoned ghosts.
 ten ghosts appeared around him.
 -you can control ‘ghosts’.
 (your affinity for death traits is the highest.
)* you are not affected by the opponent’s ‘physical attack’.
* you can ‘control’ all grades of weapons.
*you can inflict a ‘confusion’ curse on the target of attack.
* you can ‘infuse’ into the targets below a certain level.
next, he summoned two more specters to give them a ‘synergy effect’.
their moving speed increased by 30% due to the effect of the .
 after sending them to confront the hunters, he also fired the repeating crossbow once again.
tung! tung! tung! tung!

 