\section{chapter 458}

paulo's provocative words seemed to reflect the culture of his country, but hanho firmly shook his head and said, "well, i don't beat you like that.
 i know something spectacular.
 you will never find it out unless i can format your brain first! hehehe!"




hanho's ridicule helped to rub him the wrong way.
 his eyebrows twitched.
"hey, kid, if you don't take out your weapon now…" at that moment, he jumped off the ground and charged at him.
 "i'm going to take the brain out of your head first!"then he skydived to hanho to throw his arm made of rocks at hanho, but hanho pulled something from his back.
 it was a hand cannon.
"this is my answer, you bastard!"he fired from the first hand cannon on the left.
bang! dozens of iron balls were fired at paulo, who was pushed back and crashed into the ceiling before falling on the ground.
 "ugh, what the heck is this?"no wonder this item was made by arnold hearst, which was a miniaturized version of the 'bug hunter' that annihilated the absolute races.
hanho loaded the hand cannon with which he had just fired at paulo.
due to its structure, only one person could handle only one item, but hanho could use a whopping 4 hand cannons at the same time.
"i'm not good at shooting because i've never dealt with a gun.
 but i just thought this shotgun would somehow hit anybody if i just fired it.
 man, i was right!"hanho grinned and turned the guns of the four hand cannons at once, aiming at paulo who fell on the ground.
 but paulo stood up casually as if nothing happened to him and said, "did you think you could kill me with that shotgun?"obviously, he didn't seem wounded much.
 he was only pushed back by the unique firing power of bug hunt.
"hey, i'm not done yet.
 can you open your mouth wider? let me slam a bigger marble into your mouth!"
fuming at hanho's provocative words, paulo threw himself toward hanho.
 hanho's muzzle followed his movement, then fired.
bang!but paulo turned in the air, using his sharp eyes and reflexes.
 the iron balls fired from hanho's shotgun didn't hit him accurately.
 but as if he expected it, hanho turned his second hand cannon toward him and fired.
bang!paulo didn't back off easily, as expected.
 in that brief moment, he quickly rotated his body, allowing only a fraction of the buckshot before landing on the ground.
but hanho's third gun was aimed at him.
bang!this time he was hit accurately.
 no matter how fast he moved, he could not dodge the firing from the four muzzles that hanho could easily turn to aim at him.
"what a pity! i could have seen you punching at me if you had avoided my bullet only twice!"hanho kept loading the hand cannons while provoking him.
his six hands moved like an automated machine, loading and firing the hand cannons very quickly without any failure, and in the blink of an eye, the four hand cannons were set on standby.
"while i was coming here, i practiced loading it all along.
 as you know, i'm very good with my hands! hahaha!"when he was hit by two shots in a row, there seemed to be a crack on the rock covering paulo's skin.
 but he didn't give up.
"don't be ridiculous! don't act flippantly just because you hit me a couple of times!"instead of jumping, he moved to the left and right, widening the distance with hanho.
 
obviously, he realized that he found it hard to change direction while floating in the air.
bang! bang! hanho fired two shots at paulo, but paulo avoided the bullets by dodging them immediately.
 he even avoided the other two shots adroitly.
"alright!" paulo shouted for joy.
 hanho was now defenseless.
paulo raised his six clenched arms, exposing his gums.
"i've caught you!"at that moment, however, a light burst from hanho's empty hands and splashed on paulo's face.
"ugh! what the heck is this!"the light completely blurred his vision.
 while he was hesitating, he missed hanho.
".
.
.
it's slow.
"bang! bang! two cannons were fired at paulo's left head.
 he bounced off again and crashed into the wall.
 this time he heard something like tinnitus.
 obviously, he was wounded.
 no matter how strong he was, he was suffering a lot of damage over time.
"uh, hey, is this the divine light? isn't that a priest-type skill? what is it? it's strange.
"paulo stood up, rubbing his eyes.
 "oh, you know that? that's right," hanho replied.
 this was one of the basic skills that the priest-type paladin could use.
"did you say it's right? how could you use it?""uh? it's because i'm a priest?"but paulo sneered at him.
"are you kidding? it's ridiculous you are claiming you're a priest, much less paladin when you are using a shield.
 how stupid! i know you are lying to me now.
 do you think you can pull wool over me by lying to me?""what? i'm serious!" hanho said in a frustrated voice.
but paulo got angry and shouted, "don't be ridiculous! are you making fun of me? bastard, let me blow your head off!"even though he was cheerful as a rule, he seemed to get pissed off easily when his pride was hurt.
 then he charged at hanho again.
"light? it's useless if i don't look at it from the front!"hanho pulled the trigger, but as if he was used to it, paulo avoided all four cannons.
when paulo approached him, a 'divine light' exploded from hanho's hand.
since he was hit by it, paulo maintained his eyesight, minimizing his exposure to the light by tilting his head to the side.
"i've caught you now!"at that moment, however, hanho's body disappeared all of a sudden.
"ugh?"it wasn't because of the glaring light.
 hanho himself became transparent.
 this was a kind of hiding skill.
paulo punched in the air, not at his target.
 "what the heck? where have you gone?"

while he was at a loss, not knowing what to do, he heard the sound of somebody next to him pulling a trigger.
bang!this time it hit his temple right.
 his body turned upside down and fell to the ground.
 but hanho kept firing at him.
bang! bang! bang!a whopping three cannons hit his body in a row.
 the sound of metal marbles getting stuck in his body and crushing it was heard.
 "wow! three of four shots were successful! perfect! great!"while hanho's voice was receding, the sound of him reloading the hand cannons resonated.
 but paulo rolled to the side and stood up.
with his hiding skill deactivated, hanho was seen pointing his gun at paulo.
"man, what are you doing again? hiding again? you said you're a priest.
 how could you use hiding skills?""wel, actually, my first job was a thief, right? well, i'm not very good at stealing, but i guess i've mastered this skill so easily.
 hahaha!"paulo frowned hard.
 stone debris fell from his body.
 he found it hard to move his body easily because of the considerable damage that had accumulated after he was hit.
 "you bastard, don't lie! how could you choose between a thief and a priest unless you're stupid?"paulo argued with him seriously, and hanho's expression hardened at that.
"hey, have you never thought that you could hurt someone's feelings by talking like that?"this time hanho charged at him and raised the muzzles of the four hand cannons.
bang! bang! bang!

 