\section{chapter 469}

rumbling-




a single red lightning bolt struck from the red clouds.
 even though it was just one lightning, dozens of players who were rescuing survivors fell at once.
 they were killed in an instant.
 shortly afterward, a surgical lightning bolt struck down everywhere.
 it looked like an ant hunting.
the victims would snowball soon.
 if the lightning struck down hundreds of thousands of players waiting outside the demon king's striking range, the damage would be catastrophic.
'they are going to be annihilated.
'there were very few people who could stop it.
 the only person who could somehow buy time by drawing the demon king's attention was sungwoo himself.
sungwoo got up and summoned a zombie hippogriff nearby.
"sungwoo, what are you going to do?" junghoon asked worriedly.
if sungwoo went out and caught the demon king's attention, there was no guarantee that he would survive, no matter how strong he was.
 "we have to buy some time by all means.
 when we are within his striking range, all of us will be killed.
"sungwoo would not have cared at all in the past.
 'i would rather have used their sacrifices.
'there were times when he put his top priority on his survival.
'at that time, that was my only goal.
.
.
'but he's been through a lot, and now he has other goals beyond his survival.
'i'm going to see the happy ending and break down the system.
'that wasn't just his goal.
 currently, he is in a dangerous situation.
 so he had to ponder over the situation after he won the fight.
'rebuilding the world.
.
.
'sungwoo realized that he could never do it alone.
 so he walked towards the demon king.
"ugh?"but a message that suddenly rang stopped sungwoo who was about to get on the zombie hippogriff.
- 'guide of the dead' begins in the area and 'gate of the underworld' opens.
"gate of the underworld?"
sungwoo immediately raised his head and began to look into the sky.
'gate of the underworld?'you can find the rest of this content on the lightnovelworld.
com platform.
couldn't it be opened by the underworld king's power, which was sungwoo's divine power?"it's real.
"the red clouds that filled the sky were scattered and a black hole was opened on one side of the sky.
at that moment he realized it was the gate of the underworld that he knew for sure.
but it was rather smaller than one that he could open with the power of the underworld king.
 then something strange began to happen.
woooooooooo-souls arose from the corpses of players all over the place, then they gathered in twos and threes before flying away somewhere.
 someone was standing where the souls gathered.
 it was jisu.
 she was standing high in the sky with a circular green aura over her head.
she wasn't valkyrie now.
 sungwoo felt something familiar about her.
'the power of death?'it was something similar to his, yet completely different from his.
 ***kyungsoo brought a total of 5 exp cards.
 using four of them, jisu could reach level 25 finally.
right after that, she obtained a second divine power.
- you will gain the power of the shaman goddess 'baridegi'.
* every time you exercise your divine power, you become a demigod.
 * all your stats are greatly increased.
 (+10)
* you can use the  skill.
baridegi was a well-known korean shaman, a being called the goddess of all shamans, also known as 'princess bari'.
 baridegi was known as a goddess in charge of the underworld and a being who guided the dead.
 it looked almost like valkyrie.
but strangely baridegi had only one skill.
[skill information]- name: guide of the dead - grade: demigodthe source of this content is lightnov‌elworld.
com- category: active- consumption: -*when you use this skill, you temporarily open the 'gate of the underworld' and guide the 'spirits' of the deceased nearby.
 * the 'gate of the underworld' is subject to 'priority activation' regardless of surrounding restrictions, so you can enter directly.
whenever baridegi guides the spirit to the 'gate of the underworld', she temporarily gains a certain stat increase, and she can use the following skills, depending on the accumulated stats.
 1) soul strike (guide 10 people): sends a wave that ignores all defenses of the opponent, inflicting 'constant damage'.
2) destruction of evil spirits (guide 100 people): annihilates the subordinate spirits of the enemy within a certain radius.
 (except for intelligent beings)3) resurrection of the dead (guide 1,000 people): only one player can be 'resurrected'.
 (within 24 hours of death)when jisu used the 'guide of the dead' skill, the gate of the underworld opened in the sky and the dead spirits began to rise from the ground.
- guide a total of 475 dead spirits to the 'gate of the underworld' safely.
baridegi seemed to have to meet the conditions for using the skill through this kind of mini-quest.
 apart from jisu's wishes, something started to happen near the gate of the underworld.
those demons that were out of jisu's control began to ascend towards the underworld.
"sungwoo?"he looked at the gate of the underworld that opened in the sky.
 he really could not figure out what's going on.
 since this was the demon king's territory, he could not use the skill to open or close the space.
'maybe this is happening because…'of course, there was an exception.
 'even the demon king has destroyed my territory.
'when he confronted the demon king in the hall of angels, the underworld collapsed when he made a hole in the space with a skill called 'demon king's invasion'.
'is this a repetition of the same skill?'the demon king lifted the left part of his head, then looked at the gate of the underworld.
 his expression was rather strange but unpleasant.
'but i haven't destroyed his territory yet.
'sungwoo examined the hole carefully.
 i felt something strange.
even though it was opened by jisu's power, that space was the same place as the underworld that sungwoo controlled.
 updated from lightnovelworld.
c‌om'its size and purpose are different, but that space is the place where my power as the underworld king is effective.
'watching the hole, he used his power as the underworld king, 'open the gate of the underworld'.
woooooooooo-then, the 'ghosts' scattered everywhere, who were under his control, began to climb right there.
 in other words, his power began to be effective between the cracks of the hole, not within the demon king's territory.
when they merged into one and assimilated into the hole, something striking happened.
 - caution! the 'gate of the underworld' has opened in that area.
"great!"a huge hole was opened by force in the demon king's territory.
 it is difficult to tear down a solid wall.
 however, when there is a single crack or even a hole, it is relatively easy to pry through that spot and open it.
 "necromancer, what did you do?" the demon king shouted angrily.
 "how come you dare do this?"

his voice that once strongly resounded in his territory was split and hoarse.
'his territory is beginning to collapse.
'the gate of the underworld slowly expanded, then began to push out the red clouds.
 whenever the two spaces collided, colorful sparks bounced off, creating a bizarre and surreal scene.
- two territories have collided.
* if you don't close one, both will collapse.
the two territories clashed in one space and interfered with each other.
 - caution! the two territories (the demon king's castle and the underworld) are collapsing.
 in the end, the demon king's territory has collapsed.
the red clouds that covered the sky began to slowly fade away.
 "is it starting all over again?"sungwoo checked the skills enhanced with new synergies, especially the 'apocalypse army's summon list.
- select the target (army) to summon.
 (simultaneous selection available)1) prisoners unit (summonable)2) gigantes (currently summoned)follow current novels on lightnovelworld.
com3) sealed one (summonable)"but things have changed a lot now.
"sungwoo summoned 1, 2, and 3 at the same time.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 