\section{chapter 438}

right before sungwoo decided to counterattack, something happened in an instant.





clang! squeak! it was the sound of something sharp scratching against each other.
jisu touched sungwoo's neck with the blade of her sword.
 more precisely she blocked the claws of the shadow that aimed at his neck.
"argh! avoid him!"sungwoo hurriedly pulled back, and she stood in his place and blocked him.
"damn it!"vivona got furious when his surprise attack failed, then took his shoulder off the wall where he was leaning against.
 he still didn't move a bit from his spot, but his long shadow stretched out and reached sungwoo's feet.
advertisements    koooooooooooh-and he was still moving independently, crawling on the floor like a predator.
 he was like a great white shark hovering around a boat.
 suddenly, something rose from his shadow.
 they were three hook-shaped weapons.
clang! clang! clang!jisu struck back the hooks flying in from all directions.
 but they were much faster than she expected.
with the sound of her cutting him and bloodletting, she stepped back staggeringly.
 she was bleeding from her side.
"khuuuuuuk"she caught her breath and adjusted her posture again.
 fortunately, she didn't appear to have been fatally wounded, but it was a bit of a shock that she was pushed back in a head-on fight.
'this is their first clash, but this is the first time of her being on the defensive in a fight between swordsmen.
'of course, sungwoo could not sit idle when she was put in danger like that.
 he summoned his subordinate spirits right away.
- caution! the 'fellblade' has begun in the area!black smoke filled this space, and white soldiers stood up from inside.

"wake up, storm!"sorceress grace shouted.
 at the same time, a gust of wind blew from the front.
woooooooooooooo.
"argh!"a strong wind shook the entire space as if a jet engine blasted from the front.
 sungwoo couldn't even stand properly.
 that wind pushed the black smoke that the fellblade had exhaled out of the aisle.
rattle! rattle! rattle!more than one hundred undead corps summoned by the fellblade were not only deprived of their majestic appearance but also suffered the shame of having to lie flat on the floor to avoid being blown away by the wind.
"necromancer, lower your head!" li wei shouted.
 when she reached out her hand, water spirits were summoned from her ceiling.
in an instant, they covered the ceiling and fell like a waterfall.
"well, it won't do you good if you want to confront me.
"when grace gently swung her wand, the airflow began to change.
splash! splash!even the water spirits were pushed away by the gust of wind, then crushed by the wall and scattered everywhere.
 "hey, asian woman, don't you know that even the waves in the ocean are caused by the wind?" gracie said, looking at li wei with a smile.
 li wei bit her lips and approached sungwoo.
 she said, "she is a very high-level wizard.
 she specializes in the wind.
 she will control various kinds of winds, so watch out.
"come to think of it, it seemed that he had never encountered a high-level wizard like her before.
 the wizard, who reached the apex in fantasy, belonged to a more powerful profession than anything else.
 so they were dangerous.
in particular, such a narrow space like this was disadvantageous for sungwoo because he could not control his undead army.

'if i could somehow inflict only dot damage like breath of abyss, i could eat away her health with the chaos crystal effect, but i can't approach her easily.
'the chaos crystal was an item that he had forgotten for a long time.
[item information]- name: chaos crystal (sea spirit's tears + demon's bloodstone)- rank: legend- category: orb- effect: grants 'chaos' trait to its owner.
 mana increases (+500), mana restores (+250%).
 steals the opponent's mana and health at the same time when attacking (3%)although it was an item that was no less than a natural enemy to the wizards, it was useless unless it didn't inflict any damage, so sungwoo had no means to break through the wind created by grace.
 'alright.
 let me summon ghosts.
'sungwoo summoned 10 ghosts using bihyongryang's fan.
 woooooooooooo-since the ghosts were formless, they could ignore physical phenomena such as wind and move on.
 they flew towards grace.
"oh, is this your weapon?"when grace held out her hands and gave off a white light, they evaporated as if they were burnt away.
 it seemed that she cast a spell that neutralized ghosts.
"alright, let me confront that guy!"it was paulo who shouted like that.
 he ripped off the t-shirt he was wearing and threw it down to the ground.
tung!then he charged at sungwoo like a giant cannonball.
"don't move!"sungwoo felt that he could not avoid him, so he had a few undead stand before him.
clang!however, someone other than the undead rushed in and blocked paulo's punch.
"ugh! you muscular pig! my head aches!"it was hanho.
 he held out four shields and stopped paulo.
"what did you say? muscular pig?"hanho grinned at him, then he checked his forearm and tilted his head.
"oh my.
.
.
you really have super muscles.
 i think i know who you are.
 you must be a drug addict, right?""what the heck…"as soon as he heard the word addict, paulo got furious right away, but hanho chuckled loudly and shouted, "hahaha! roider! roider! roider!"as if hanho's shouting was a spell that awakened paulo's instincts, he ran towards him like a gorilla with his gums exposed.
"aaaaaaaaaaah! what the hell are you talking about? let me kill you!""gosh, you are really a drug addict since you are so excited.
 are you a eunuch?"the two exchanged useless chats, then immediately started fighting.
tung! tung! tung! tung! tung!although hanho was pushed back by paulo, he fought hard, backed by his overwhelming defense power and his six hands.
at that moment paulo's body seemed to harden, then his upper body was covered with black stones.
 and something arose behind my back.
"arms?"six arms made of black stone protrude out of it.
then he wielded a total of eight arms and struck back hanho's shield.
bang! their impact echoed through the entire underground.
"ugh!"

hanho's shield was not broken.
 but he was bounced back because of the devastating impact.
 after being thrown against the wall, hanho struggled to get up.
"man, he's got six arms…"then junghoon charged at paulo.
 but even hanho couldn't stand his attack.
 junghoon was also punched hard by him and fell right away.
after defeating the two easily, paulo let out a wild shout like a beast.
"hahaha! you can't defeat us! we're so-called 'imperial rangers' chosen by the demon king!""hey, paulo, please stop giving yourself such a childish nickname like that!"grace rubbed her forehead, shaking her head.
 "grace! you don't really have a sense of art, unlike your looks.
 why don't you love my sensual buttocks?""gosh, how can a gorilla-looking guy like you talk about art? don't insult me sexually like that, will you? how vulgar you are!"they even exchanged jokes like that in a relaxed manner.
at that moment someone's voice was heard from the aisle behind them.
"poison field!"at the same time, something began to spread around the ceiling near the stone gate.
it was dark green smoke, namely, poison gas.
 minsok and victor walked out from the aisle.
advertisements    "necromancer!""right! master!"minsok and victor came to their rescue, who sungwoo had dispatched just in case.
"damn it!" grace was obviously embarrassed.


 