\section{chapter 457}

dragon breath.
 exhaling one single dragon breath distorts the entire terrain and its heat reduces all living things to a handful of ashes.





"just exhaling dragon breath once was powerful enough to shake the foundation of the pyramid in the hall of angels and destroy the huge structure.
"what kind of creature can survive after being attacked by dragon breath?at that moment that destructive pillar of fire fell over the demon king.
kugugugugu-the ground he was standing on melted like cheese, then turned into a deep pit.
his body was crushed by the pillar of fire and pushed deep into it.
'he was hit directly.
 he could not withstand the heat in that situation.
'sungwoo swallowed, watching it.
when isabella appeared, he thought things were going to get the worst, so this was completely an unexpected twist.
'wasn't she detained forcibly?'he examined the huge red dragon's neck.
 but there was no 'dragon keeper' with three dragon slayers around it.
'i don't know what the hell is going on, but i don't have to care about it.
"holding back the question, sungwoo pushed gigantes forward.
 all of a sudden, the dragon breath stopped and the liquefied ground was boiling.
it was an opportunity for sungwoo.
"trample on it and crush it!"at sungwoo's order, gigas at the forefront raised his foot.

he was as slow as a tower crane, but his massive step was so heavy as to crush anything at once.
bang!gigas's gigantic feet trampled on the liquefied land.
 the spot where his feet fell was hollowed out, and the surrounding ground shook and soared like a wave.
bang!it was as if he put something in a mortar and pounded it repeatedly.
bang!then his eyes met isabella's.
sungwoo asked cautiously, "i wonder if you don't know the collar around your neck has come off, right?"isabella grinned and said, "collar? it's still around my neck.
 it's older and tougher than the one you shackled around my neck.
"sungwoo could not figure out what the heck she was talking about.
she continued, "i've reassured myself that i won't be used as his tool.
"hearing it, sungwoo nodded.
 he didn't know why she changed her mind all of a sudden, but it was a good turn of events for him.
'if an adult dragon becomes my ally, he is a stronger ally than anybody else.
 i wonder if he has become another king of the great mountains.
'but sungwoo was even doubtful about that possibility.
'if the monster doesn't move as designed by the system, is it a system error? or is it also designed so by the system from the beginning?'sungwoo believed that he could probably find it out when the game was over.

actually, the game would be over in the near future, but he had to overcome the current difficult situation.
"necromancer, don't let down your guard.
 don't underestimate the demon king.
 you can't kill him as easily as you think.
 as you know, his territory is still intact!"as isabella said, something was moving under the burning red pit.
***the battle was taking place in every space, and the remaining players inside the labyrinth were also suffering from a new threat.
"damn it! they're coming from there too!"the group to which hanho and junghoon belonged was running through a spacious hallway inside a maze-like labyrinth.
 they didn't know the way to escape the labyrinth yet, so they were wandering for quite some time.
"uh? i see a light in this hallway!"when they arrived at a place diverging in four directions, one hallway was shining unusually bright.
 obviously, it was the light coming from outside.
"whew! we're almost there! it's the end of the tunnel!"but they could not approach it easily because about fifty shadows were blocking the way leading to it.
they were monsters.
"to arms, everybody!" junghoon shouted.
then he stepped forward and looked around to check the enemies.
the soldiers of the hell in red armor were holding spears and shields.
junghoon felt something strange.
'instead of moving, they are waiting for us.
'even if they discovered the outside players, they did not move from the spot where they were standing.
 it seemed that they were trying to stick to their position by tightening their formations.
'originally they charged at us as soon as they discovered us, but they changed all of a sudden.
'there was some change in their attitude.
"enemy forces are chasing us in the rear!""damn it! they're coming from the left hallway!"now only one place, namely, the right hallway was empty.
 it seemed that they were trying to induce us to go in that direction.
 but they couldn't, of course.
"we're going to hold out here.
 so try to secure the exit!"the enemy seemed to use the narrow corridors to lock them in, so they could delay sungwoo's forces from joining their allies in other areas.
this was not something a normal monster could do on its own.
 it seemed that some monsters that had intellect were controlling this situation.
junghoon's reasoning was correct because a player, not a monster, walked out of the hallway in the back.
"it was you, eight arms, bastard!"hanho recognized him and shouted in anger.
 soon a large man appeared from the darkness.
 it was paulo.
"what the heck did you say?"at that moment his body turned into a rock, and rock-made arms protruded from behind his back one by one.
"well, you have eight arms, so i gave it a nickname because i was a little envious!"

paulo grinned, then twisted his neck from side to side to loosen his muscles.
"hey, little asian kid, you must have been pretty pissed off because i beat you back then, right? i guess you didn't feel hurt at that time because of your torn eyes and high cheekbones.
""really? your crooked posture is not bad because i can add one more chapter about you in my autobiography? i can write down what a junkie racist like you lectured me about.
""hey, bastard, i told you not to say that…"paulo approached hanho, fuming, but hanho also stepped forward without avoiding him.
"youngdungpo prosecutor, let me get rid of this naughty junkie! please get rid of the golems coming from behind!" hanho shouted at junghoon.
in the past junghoon felt uneasy to ask hanho to take care of something, but after hanho confronted the oppressor's hand after being awakened, junghoon changed his perception of him.
"alright, focus on securing the exit, everybody!"the other players followed junghoon's order with hanho and paulo pitting against each other face to face.
"are you kidding me? are you going to stop me by yourself? hey, kid, i think you watched too many hero movies.
 just because you are holding several shields, you don't become captain america!""well, stop talking bullshit!" since hanho already fought him, he knew paulo was not his rival as far as grip power was concerned.
 but he could not summon the lethal skill of hyunmoo in a narrow place like this.
 he needed a different weapon.
tung- tong-hanho stepped back and put down all the weapons he was holding in his six hands.
"i've been thinking for quite some time on how to catch a heavy guy like you.
 i think i have drawn 21 sketchbooks to come up with ideas by myself.
""what is that? hammer or something like that? or do you want to talk to your grandmother? hahaha!"

 