\section{chapter 425}

as for the two items mentioned above, it was clear what additional effect they would bring about.
 namely, they were fire damage or fire immunity.
 this would be similar to the 'element' series such as water, wind, and ice.





time, on the other hand, was slightly different.
 what kind of effect did the time-related orbs really give him?as if he noticed sungwoo was curious, hearst explained this further.
"well, i think this item will probably reduce the 'cooldown' or increase the 'sustained use' of the additional skill attached to it.
 depending on how you use it, it can be the best enhancement.
"sungwoo recalled something at that moment.
"then can you enhance this one, too?"sungwoo held out his empty right hand.
 hearst wiggled his eyebrows, wondering if he made fun of him, but a black scythe appeared over his hand.
rattle-it was sungwoo's grim reaper.
"um, is it a summoning item? well, i can't even put it on the anvil for enhancement from the beginning…"tap-hearst tapped hephaestus' anvil with his palm.
"but this thing is unique, so let me try enhancing it.
 can you put it over here?"sungwoo placed the grim reaper neatly on the anvil of hephaestus.
woowooooooooongfortunately, the anvil didn't reject the black scythe.
 as if the two synchronized, purple light began to emit from it.
"let me see…"hearst placed his hand on the anvil and began to manipulate something that appeared before his eyes.
 at this moment he looked more like an engineer operating a mechanical device than a blacksmith using a hammer.

"alright.
 i can do it.
"having said that, he pulled an emerald-colored hammer from his waist.
 then he extended his left hand to sungwoo.
follow current novels on lightnovelworld.
com"give me that orb.
"sungwoo handed him the orb, 'help of time', then hearst placed it next to the grim reaper.
"gosh, it costs 120 million gold to combine them!" hearst shouted.
"no worries! just go ahead.
""crazy······.
"hearst stuck out his tongue and put on goggles.
 then he lifted the hammer and slammed the orb with all his might.
clang!at that moment, the orb was shattered into pieces, and an incredibly bright light burst out.
sungwoo instinctively turned his head.
sparkling!that light turned into an electric current and soon began to get tangled up like a knotted skein.
hearst took a deep breath, as if he made up his mind, and grabbed the hammer.
"come on, watch out! if this explodes, we all die!"was it such dangerous work? indeed, those blacksmiths who were standing around him began to step back.

"ahhhhh!"hearst clenched his teeth, with the hammer in both hands, and pulled the skein-like current.
 then he slammed the hammer at the grim reaper with all his might.
then the current flew into the grim reaper, to everybody's surprise.
"come on! get into it, please!"given that the grim reaper's black blade was turning dark blue, it was clear that some big change was taking place inside it.
- the masterpiece 'grim reaper' has been enhanced into a special power.
 (a new effect is given.
)visit to lightnovelworld.
com discover new novels.
it was a great success.
"ha…"the light stopped.
 but their visions were blurry because they were exposed to too much light momentarily.
"fortunately we got everything right at the perfect time.
 i could do it because of good materials, good facilities, and good technicians.
"sungwoo picked up the enhanced grim reaper.
 since this item was directly connected to the 1st awakening skill, skill information appeared before his eyes.
[skill information]- name: summon grim reaper (time domination)- grade: 1st awakening- category: active- consumption: 0*you can summon the grim reaper, the black scythe, for only 3 hours a day, and you will temporarily become 'lich'.
+ realm of the dead: while you are gaining the lich's power, you can maximize the number of subordinate spirits by (+50) and all stats increase by (+10).
 the skill effect increases by (+20%) every 1 hour due to the effect of 'skillful suffering'.
 in addition, you can resurrect nearby destroyed undead 'indefinitely as many as the maximum number of your subordinate spirits.
+ primordial death: when the summoning duration of the item ends, you can bring out 'primordial death' for 1 minute.
 no one knows what will happen.
sungwoo could not hide his spontaneous admiration.
'i can't believe this!'the retention time of the grim reaper increased as long as three times.
 that wasn't all.
'skillful suffering? it gets stronger over time.
'originally the necromancer gets stronger as the battle continues.
 that formula was amply verified by his fighting until now.
 now, that formula was further improved.
'by the way, primordial death? what the heck is this? why is its function hidden?"sungwoo could not figure it out for now, but he felt it was dangerous.
visit lightnovelworld.
com for a better experience'can i use it only when the summoning of the grim reaper is over? man, i should not use it if i can.
'at that moment hearst suddenly asked, "how do you like it? well, i can notice it on your face even if you don't express it.
"at hearst's question, sungwoo could not take his eyes off the black scythe and nodded slowly.
"yeah, this is the best you've ever made for me until now.
"after all, he was reaping the returns on his investment in the technicians by double.
***

with 12 hours until the enemy's invasion, the world tree camp began to move.
"one minute before the activation of the hypergate!"thousands of players gathered and moved busily on the vast runway.
woo woo woo-soon, with the roaring of heavy engines, 15 airships, and the world tree fleet were appearing over the players' heads.
"all the fleet ships, keep a safe distance and prepare to enter the hypergate in a hovering mode!"according to the order of the flagship 'messenger', 15 airships moved slowly and went out to find their places.
 that wasn't all.
 eleven helicopters followed them to the left and right of the fleet, and one griffin and 213 hippogriffs were lined up at a high altitude in the sky.
"special commando unit, you guys enter it after the entire army gets out of the hypergate!" junghoon shouted.
the special commando unit was fully vigilant even at this moment because even the process of their entering the war was part of their operation, and at the same time, it was the moment when they could be most vulnerable to the enemy's attack.
meanwhile, sungwoo and kyungsoo, who were standing on the deck of the messenger, were watching the whole process carefully.
"wow, we now have a perfect formation of the entire army! i'm sure they are the strongest troops in history.
 i am overwhelmed by their fantastic power!"kyungsoo couldn't help but admire the majestic formation of the entire army.
 looking back, he only drove one school bus out of the campus when this game started.
none of the people on the bus at the time would have imagined that they would see such a spectacular scene like this.
sungwoo also nodded and said, "yes, that's right.
 in fact, we had the strongest army at every moment.
 but we were on the defensive all the time.
"this content is taken from lightnovelworld.
c­omthe world tree camp became stronger at every moment.
 nonetheless, they struggled in the face of a giant war.
 since they started with a small number of elites, it was inevitable they were pushed out numerically by the enemy.
"but this time it's a different story.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 