\section{chapter 472}

a huge hand reached out towards sungwoo.
 it made a quick and rough gesture, as if it tried to kill a wasp flying toward it.
 in other words, it was pretty hard to avoid it.





"it's dangerous!" heyon shouted.
she instinctively felt that if sungwoo didn't change the flying direction, he would be caught by the hand.
"avoid it right now!"but the gigantic grip stopped all of a sudden.
"ugh! i've caught it!" hanho shouted.
 "sungwoo! i'm holding it.
 so move on!"the demon king was holding the stem of the world tree,' whose tip was tied to his arms.
 "argh!"hanho was pulling the demon king after binding his arms with a rope.
 even though the demon king was much stronger than him, his six arms were tightly bound by the stems of the world tree, which cancelled out the difference in their strength.
 as a result, the demon king's six arms were incapacitated.
kheeeeeeeh- but thousands of hell creatures began to rush towards hanho, who was holding out on his own.
 he was completely defenseless.
"oh my god! this is too…"at that moment, a wave arose behind hanho's back.
"alright! i trusted you!"waves the size of a house came from three directions and surrounded hanho.
hell creatures were swept away by the disaster while not even a drop of water touched hanho's body.
"necromancer! just move ahead!" li wei shouted.
 "spirit king, please tie him up!" sungwoo responded.
 
when li wei shouted, some blue-tinged stream of water rose like a dragon and wrapped around the demon king's other arm.
 it wasn't an ordinary spirit's power.
the water flowed up his arm like a snake and turned into a barbed wire.
 the most up-to-date novels are published on lightnovelworld.
comthen it dragged his thick forearms down to the floor.
 his seventh arm was disabled.
 'now he's got only one arm left.
.
.
'but sungwoo was wary of his remaining arm.
 but even that arm was tied to something.
"roots?"a huge amount of tree roots that rose from the floor were coiling the demon king's fingers.
 it was the king of the great mountains that did it.
 'he didn't go into hiding.
'sungwoo didn't even think of such unexpected support from the king.
 was the king waiting for the right opportunity like this while hiding somewhere?if so, he came at the perfect time.
"alright.
 i can kill him shortly.
"when his allies joined hands to make such a golden opportunity for attack, sungwoo seized that moment and pulled the trigger.
 sungwoo possessed one single fatal skill that could end this fight once and for all.
 and he had been waiting for the right moment to deal a fatal single blow until now.
'now is the right time!'riding on the hippogriff, he approached the demon king, then strung the superheavy arrow on the superheavy bow.
'this is a weapon that can even kill a god…'he slowly pulled the bow, which alone caused a huge wave, shaking the air around it.
 
he felt as if he was twisting the space with bare hands.
feeling the acute pain as if his shoulder was broken, he pulled the bow harder while grabbing it which was about to dart forward because of its great tension.
but another problem occurred at that moment.
 'hold it tight!'zombie hippogriff', who sungwoo was aboard right now, could not withstand the formidable force, so he began to move up and down precariously like a bird that met a typhoon.
 because of that, sungwoo could not aim at the demon king accurately.
 'if i can't aim accurately, this is going to be a fiasco!'updated from lightnov‌elworld.
c­omhe could not shoot the arrow at the moment.
 but he could not get off the hippogriff, either, because the ground was covered with a bunch of tentacles generated by the demon king.
"cover me from behind!"sungwoo hastily moved a group of 'born wyverns' following him from behind to support the zombie hippogriff by balancing his weight from both sides.
when five or six bone wyverns joined their hands, sungwoo could keep his balance even if he pulled the bow a little harder.
 - the power of the 'holy sword' is applied to the weapon.
* additional damage is given when you attack the 'demon king'.
 (+2,000%)finally he made his single fatal strike perfect by applying the 'holy sword' effect of his brave warrior privilege.
wooooooooooo-a strange air blew through the back of sungwoo's hand.
'i have to be very careful.
' sungwoo did not let go of the bow recklessly.
 'he's totally focused on stopping my attack right now.
'the demon king was watching him closely.
 even though his eight arms were tied tightly, it didn't mean they were completely disabled.
sparks erupted from his left head and four horns.
 he was ready to fire the beam at any moment.
'but this guy also has the last chance to kill me.
'already he used up the beams of his two heads.
'the winner is the one who hits the target!'facing each other, sungwoo and the demon king began to fight like gunslingers in the west.
 at that moment the demon king took out another hidden card.
 "ugh?"hell creatures that had been attached all over his body screamed all at once, emitting black smoke, then started to harden like stones.
'what the heck?'visit lightnovelworld.
c­om for the best novel reading experienceentangled with each other, they were now turning into stones.
 so much so that the bizarre scenes reminded sungwoo of the worst of hell.
as if his body was hardened with concrete, the demon king created a solid 'armor.
'then black symbols began to be engraved on its surface.
 it seemed like he had some other physical power.
 shortly afterward, his armor shone and vibrated, and another layer of a red shield was placed over his body.
it was an aoe defense skill, which seemed pretty simple.
at that moment sungwoo agonized over how to attack him.
'can i break through it?'of course, he could.
 he knew it for sure.
 he once nullified even the world tree.
but there was another problem.
 sungwoo wondered if he could kill the demon king after breaking through his armor.
 if he could not, he would have to face another grueling moment.
 

'regardless of the results, i have to shoot the arrow!'he already pulled the bow, to which he applied the effect of 'sacred sword.
' he could not take it back now.
 at that moment, a black shadow fell over his head.
"get out of my way!"it was the red dragon, isabella.
she appeared above sungwoo's head using 'teleportation' magic.
"isabella? what are you trying to do?""let me break the obstacle! so look for his loophole!"shouting like that, she ran past him.
 so sungwoo slowly lowered the bow, watching her closely.
 she was in bad shape after she had been a big blow by the demon king, with her scales peeled off.
 so much so that her whole body was covered with wounds.
 nonetheless, she was still a dragon.
'let me trust her and wait for now.
'spears made of light arose behind her back, which was five in total.
 they were shot in a straight line and crashed into the demon king, or more precisely, his thickly inflated 'armor'.
puck! puck! puck! puck!follow current novels on lightnov­elworld.
comafter that, round marbles floated above her head.
 they flew away and exploded near the demon king's chest.
bang! bang! bang! you can also read this novel on the more advanced platform lightnovelspot.
com

 