\section{chapter 332}

                            kill junghoon and the crusader team?




‘aren’t you supposed to tell me why?’sungwoo was embarrassed.
 how could the king advise him to kill the person who visited him without telling him the exact reason?he was angry.
 the king said he was helping sungwoo to collapse the system, but sungwoo wondered if the king was making fun of him.
‘no, i should not be emotional.
’so, he tried to suppress his emotions and think as rationally as possible.
‘let me stop thinking he is playing with me.
 right now, i’m in an important situation.
 there is clearly some reason for me to kill him.
’since the system inside the cave of the giant snake monster imoogi encountered an error, this was the third time sungwoo contacted junghoon.
 and this ‘unidentified helper’ has never given him any wrong advice until now.
perhaps the king gave him only a fragment of the information, hard-pressed for time.
 the king had to avoid the eyes of the system to do this, which was not simple at all.
  ‘i have no choice but to trust him right now.
 okay, let’s assume it’s absolutely necessary for me to kill junghoon and the crusader team, and it will not be difficult for me to kill them.
 this is my main base anyway.
’however, the question was why he should kill them all.
‘his advice that i should kill them unconditionally means they are very dangerous.
 why are they?”sungwoo agonized over it briefly, but he couldn’t figure out why junghoon was dangerous.
 as a matter of fact, he had been the most reliable ally and the most important helper to sungwoo.
if so, there was only one thing sungwoo could handle the best way, which was he should take extreme caution, assuming junghoon and the crusade team were dangerous.
sungwoo looked at kyungsoo and asked, “kyungsoo, where is the crusader team right now?”
kyungsoo turned his head out of the window.
“they have just arrived, so they’re coming this way.
 they have probably passed the castle wall by now.
 i hear they landed outside the village because of the invisible barrier.
 i wonder why he hasn’t asked you to open it…”fortunately, they hadn’t yet arrived at the center of the town.
“from now on, i won’t allow anybody except for the world camp members to enter the center of the village.
 don’t let them approach the world tree and watch out.
 i’m going out a little later.
”kyungsoo said, tilting his head, “watch out?”“they are not yet part of our camp.
 and they were once our enemy.
 we should put our village, and the world tree under the best possible security all the time.
”at first, kyungsoo looked puzzled at his words but soon nodded as if he understood.
“got it.
 you’re right.
 no matter how much you ensure safety, it’s not enough.
”then, he hastily disappeared out of the door.
sungwoo stood up from his seat and began to grab weapons, while the king yawned while rubbing his eyes as he was having the aftereffect of having been possessed by a spirit.
“well, i still don’t know anything about what’s going on in this world.
 how about you?”the king asked with a sullen expression, sticking a pipe in his mouth.
 “hmm, you contacted him because you insisted.
 didn’t you get anything?”he said, looking at the king, “well, i came to know i was not a fake anyway.
”“am i a fake then?”“…”grrrrrrrr-at that moment, mir woke up whining.
 it seemed that mir was awakened by the sound of him picking up weapons.
 mir yawned and raised his body, stretched his legs, then tried to snug back into sungwoo’s arms.

“why are you waking up at this moment?”sungwoo had no choice but to take mir and climb to the rooftop of the museum.
‘they are already here.
’a group of men in full plate armor was approaching from a distance.
 they were a team of about 30 men including junghoon and his crusader team members.
‘it’s strange that they came here without informing me in advance, but why is he bringing the fully armed crusader team here?’sungwoo examined them slowly.
 of course, junghoon was standing in front of them.
‘he is different.
’sungwoo frowned because he felt strange about junghoon this time.
 he couldn’t know exactly why, but he could feel no more “aura” in junghoon like before.
kyungsoo and the village security guards stepped forward and stopped them.
 just like sungwoo ordered, they stopped junghoon and his team from getting access to the center of the village where the world tree and art museum were located.
then, something unexpected happened.
grrrrrrrrrrr-“uh? what’s wrong?”– caution! the fellblade has begun in the area.
all of a sudden mir opened the fellblade.
pusheeeeeeee―black smoke erupted behind sungwoo’s back.
 there were 6 chicken skeletons inside the smoke, whom mir summoned.
rattle! rattle!the bizarre skeletons jumped down the railing.
puck! puck! puck!it seemed that a few pieces of their bones were smashed and bounced off with a loud crash when they jumped, but they started to run somewhere without caring at all.
“uh?”in fact, their target was none other than the crusader team.
rattle!the chicken skeletons jumped to the ground and threw themselves at junghoon’s head.
junghoon immediately avoided them by turning his head, so one of the skeletons hit the face of the crusader team member standing behind him.
“argh!”the attacked crew member grabbed his nose and hesitated.
 it was an absurd situation that they could not understand, so all of them opened their mouths in embarrassment.
“catch them!”at that moment, kyungsoo and the guards hurriedly moved to capture the chicken skeletons.
 even hanho, who was passing by, rolled up his sleeves, stunned at the unexpected scenes.
“what’s going on? why are chicken skeletons attacking humans? where are you, sungwoo? stop them!”sungwoo looked at mir with a sigh.
 but mir hissed toward the crusaders’ team as if he was on alert, sticking out his head from sungwoo’s arms.
“what the heck is this…oh, you must have a reason to do something bad like this, right?”grrrrrr-

sungwoo left the building.
 and he looked at the face of the team member who was hit by the chicken skeleton.
the scratches were clearly seen on his face as if he was scratched by the chicken skeleton’s claws.
 he made eye contact with sungwoo then bowed his head.
‘his face had scratches, but he didn’t have any protective shield.
 besides, there is no blood on his face.
’the crusader team was supposed to be protected by a golden shield of their own.
 it was because of the characteristics of their job called “crusaders.
”the shield was powerful enough to defend against any outsider’s attack, but why didn’t the shield take effect this time?‘that shield is the crusaders’ job trait.
 it makes no sense they could not trigger it in this situation.
 then, these guys are not protected by the shield.
 why?’while narrowing the distance with junghoon, sungwoo began to check out everything he had taken for granted until now.
  there was nothing more foolish than believing something as it appeared at a time when people took the unrealistic situation for granted.
if so, sungwoo had to break the existing assumption about junghoon and his team members.
‘are these guys the same men that i used to know? yeah, i can understand this situation if these guys are not genuine crusaders.
 that’s why they can’t spread the protective shield…’grrrrrr-sungwoo stroked mir, who was growling at the crusaders.
‘as a matter of fact, mir didn’t act without any reason.
 he felt instinctively, or with some supernatural sense, that the other party was hostile before summoning the chicken skeletons to attack them.
’come to think of it, what the unidentified helper told him was to kill a ‘certain visitor’, not junghoon and the crusaders.
who were these visitors then?‘this is a trap!’

 