\section{chapter 322}






 while all those who stepped out to block the hole were warrior-type players, only hanho was an assassin-type player.
“do not worry.
 you may worry if i have only one dagger, but i’ve got six! you will see me using an unprecedented skill.
”soon, four arms protruded from behind his back, lifting a total of six daggers.
“of course, there are few players who can withstand their attack as well as you, but i can’t believe a thief-type like you is standing at the forefront like this…”at that moment, a blue light flashed from hanho’s iron helmet.
 then, a protective shield was created around hanho and minsok.
 it was the effect of the “spirit of the personal guard”, an iron helmet hanho received from the king of the great mountain, which gave a shield to him and one of his allies.
“minsok, i am not an ordinary thief,” said hanho with a smile.
“oh, you must be a miscellaneous, oh no, talented thief…”they stopped talking right away because the advance party of the chinese troops approached them very closely.
“they are coming!”the overwhelming number of chinese troops stormed like a swarm of grasshoppers, which dwarfed the korean server troops.
“everybody, get ready for collision with the enemies!”“put your shields forward!”everyone lifted their shields.
 in the name of the korean server, they were now ready to engage in an all-out fight with the chinese troops.
sheeeek! sheeeeek! sheeeek!right before the two sides started fighting, hanho threw three daggers at the same time.
the advance party of the chinese troops also lifted their shields, but hanho’s daggers fell through the shields, stabbing into their chests accurately by flying in a parabola as if they calculated the enemies’ movement.
“argh!”the two at the forefront fell.
 then, a holy shield was overlaid on hanho’s body.
 it was the moment that his skill, ‘killer of conviction,’ was triggered.

when minsok reached out with his left hand, green energy shrouded hanho’s six arms.
-‘paralysis poison’ has been applied to your weapon.
* when you attack the enemy, it causes a “paralysis” effect.
hanho looked at minsok with a surprised expression.
“wow! what is this?”“if you received something, don’t you think you should give me something in return? as a matter of fact, i’m not an ordinary knight.
”“great! bring it on!”after all, the knight who used magic and the thief who used all kinds of skills joined hands to block the enemies at the forefront.
“let’s fight!”“hold out!”as soon as the warriors shouted and collided with the enemies, five or six weapons were thrown at hanho’s head.
 noticing he had no helmet, they wanted to kill him first.
tung! tung! tung! tung! tung!but it was their mistake.
 hanho was covered with a heavy shield just like the crusader team.
 besides, it was refilled with a new one when broken, so he was more sturdy than any tank.
puck! puck! puck! puck!without any hesitation, hanho got entangled with the enemies and stabbed them with the six daggers randomly.
“get away from me, bastard!”“ugh, who the heck are you, son of a bitch!”no matter how wide their shields were, they could not block the six blades he was stabbing randomly from their left, right, above, and below.

“argh!”“ahhhhhhhh!”kheeeeeeek!”their screams burst out endlessly.
in addition, the paralysis skill that minsok used on his behalf also played a part in stopping the enemies from charging at him.
 as a result, those enemies who collided with hanho collapsed without any exception.
“bring it on! hey, you!”hanho defeated more enemies than minsok, the “death knight” who stood next to him.
seen from a distance, it looked like a mixer with six blades seemed to rotate when hanho attacked them.
even minsok, fearing the enemy’s offensive, was standing firmly while holding up his shield tightly, but hanho could unilaterally attack them without any hesitation.
“man, you are much stronger than i thought, hanho…”minsok was truly surprised.
 he fought with hanho on the same battlefield several times, but it was the first time he witnessed hanho fighting right before his eyes.
“hahaha! oh, i’m disappointed that you have realized my abilities only now! yeah, there are a lot who don’t know i’m the hidden strong guy among the necromancer’s team members.
”anyway, they could defend the no.
 3 hole thanks to hanho’s brilliant performance.
“great! we can hold out!”“everyone, hold out with the strongest thief as the leader!”highly motivated by hanho, those fighting with him shouted hanho’s name here and here.
 and their morale was at an all-time high.
in fact, hanho was always forgotten among his allies, but it was true that he was one of the top fighters.
but the chinese troops didn’t ignore the defeat of their advance party.
 they immediately began to carry out another operation.
“uh, look at that over there!”the security guys at the watchtower at the highest place of the castle wall in the village found something suspicious.
“we’ve noticed some suspicious movement in the enemy’s flagship!”admiral baker appeared directly on the deck of his ship.
 he was aiming at the third hole with a rifle.
“is he going to snipe?”“from such a distance?”the guards couldn’t figure out what he was trying to do, but they noticed a line of red lasers coming out of the muzzle.
“no way! is that a guided bomb?”it was similar to the technique of inducing an air bombardment by the ground troops.
 as expected, something strange rose from the stern of the flagship.
it climbed vertically, followed by gray smoke, then quickly flew toward the wall in a parabolic curve.
 obviously, it was something like a guided bomb.
it was one of the exclusive skills that admiral baker could use, which he could not use in succession, but it was a special item that boasted of a tremendous striking range.
frightened by that scene, the guards shouted at the third hole.
“run away! it’s a long-range bombing!”but they had little time to avoid the bombing.
 with the troops from both sides engaged in fighting with bare hands, the guided bombs fell over them.
 baker even killed his own troops to break through the blocked third hole.
bang! bang!red heat filled the third hole fully.
 about a hundred people, both from the korean server and the chinese server, were killed at once.
“argh…”fortunately, hanho survived the bombing.
“ooops! i feel like throwing up…”

swept by the tremendous explosion, he bounced off into the castle and hit against the street light, but he could come to his senses because of the hard banging.
-all your shields have been ruined by the big impact.
the shield covering his body flickered, then went out.
“hanho!”hanho’s mother, eunhee, jumped out from among the non-combat players who were supporting the battle in the rear.
 but she called her son’s name desperately when she was stopped by people around her.
 actually, she secretly discouraged him not to when he told her he would go to the frontline for fighting.
“hanho! oh, no! come over here!”hanho shook his head violently.
 he felt so dizzy but came to his senses a bit when he heard his mother’s voice.
“you were wounded a lot.
 you need treatment quickly!”but hanho barely stood, feeling the pain all over his body.
shaking his head, he murmured because he was too weak to shout to his mother.
“ah, i’m sorry, mom.
”he again turned to the third hole.
“gosh, i don’t really want to play this cool role again, but if i come to your side, mom, the guys here are in big trouble.
”then, he adjusted his helmet and summoned asura’s arm again.
“i can’t run away from here.
 sungwoo has assigned me here…”but the moment he took his first step, he became frustrated.
“uh?”he stumbled.
 at the same time, he felt tremendous pain all over his body including the back of his head.
 he felt like all his nervous system was screaming, so he almost fell over and screamed.
“damn it…it hurts so much.
”

 