\section{chapter 303}

[item information]




-name: world tree vine-grade: myth-category: special equipment-effect: if you tie one side of the vine somewhere, and the other side to a target object, you can pull it with a powerful force.
because of that, even the airship was forced to be pulled away the moment it was bound by the vines, no matter how large and heavy it was.
 -hyper gate will be closed soon.
 (00:07:49)however, since the item called hyper gate could not be opened indefinitely, he could not steal all the airships as he pleased.
tung-"the airship came out!" "charge!"finally, the airship popped out of the first hyper gate.
 the players of the world tree camp jumped on the airship in an organized manner, then overpowered the confused crew and succeeded in capturing the ship.
after that, a total of three airships, with two of them destroyed by half, were taken to the korean server one by one.
 ***sungwoo could easily win the victory by bombing the washington fleet that had been anchored for some time.
 however, even if the washington fleet, which was the wpu's greatest power, was devastated, it didn't mean that the entire wpu was neutralized.
"the ground troops 'capital guard' will move to salvage the wpu.
 so, we have to rescue chairman love before they move in.
"after getting a cell phone connected to the american server community in the fleet battle in changwon, jonathan was secretly communicating with his close associates there.

as a result, he could find out where chairman love and his aides were detained.
"wow, it's washington, dc, america!"hanho looked around the strange land with admiration.
 it was certainly an exotic city, which was unfamiliar to him.
 "washington, dc? but there is nothing special here.
"washington, dc once boasted of extraordinary splendor as the capital of the world's most powerful country, but now it was just a city full of scars.
but there was something strange around it.
 in the center of washington dc near the capitol, unidentified buildings were protruding here and there.
"what is that?" hanho asked, pointing at a building.
it was a large, straight square stone building, marked by all kinds of carvings on the wall.
it didn't exist there from the beginning, so it must have been built after the game started.
'that's the dwarf's skill?'the wpu had all sorts of unusual items, starting with the airship, and all the information about it contained the word "dwarf.
" sungwoo was bothered by that.
 dwarf was a race that appeared regularly in fantasy.
 it originated from nordic mythology, and they are described as being short, but they have exceptional technological prowess because of their great dexterity.
"oh, that's the dwarf's workshop.
 they make various weapons with magic.
 they also build airships there.
"when jonathan explained about it, he also used the word 'dwarf'.
"if you are talking about a dwarf, do you mean a small man?"sungwoo remembered the "myth quest" he was proceeding with now.
 according to the quest message, when the world tree reaches the 'completion stage', the camp could be reborn as the 'dragon race.
'
then, did the dwarf get a new racial trait after completing such a myth quest?"oh, that's just a nickname.
 it's called the hearst workshop where 100 blacksmiths gathered, and the synergy effect must have contained the word 'dwarf.
"in other words, there was no dwarf race in washington, dc.
sungwoo's party soon landed near garfield park prison.
 even the jail itself had pretty strong security, so their covert attack would be more effective than their frontal attack.
 but when they arrived at the prison building, they encountered an unexpected situation.
"what the heck? it doesn't look like the security here is that tight.
"like hanho said, many of the prisons were broken apart here and there.
 it seemed that there was just a battle a little while ago.
 jonathan, looking through the scenes carefully, clenched his fist.
"oh, my god, it's our allies.
 they have arrived here first!"after receiving a call from jonathan, his associates said that they were mobilizing the supporters of chairman love, but when they heard about the battle on the potomac river, they mounted an attack here early on.
"uh? johnny!"they recognized jonathan first.
 they seemed to be his colleagues.
jonathan hugged a white man.
"i'm glad to know you're alive!""i was lucky.
 there are people who have helped me out.
"then, an elderly white-haired white woman walked out of the crowd.
 she seemed to be chairman love.
"captain cage, thanks for your hard work!"the power befitting her fame was felt in her wrinkled eyes.
 there was a steely determination in her soft posture.
 her skin was also full of vitality.
 since she was detained in a prison for only a few hours, she didn't look shabby at all.
"don't mention it, chairman.
 this has happened because i did not cope well with the situation.
 many people turned to admiral baker because of misinformation, but they will come back when they come to find out the truth.
"chairman love nodded at that.
 "the situation has already changed.
"then she turned her gaze at sungwoo's party beyond his shoulders.
 jonathan introduced them to chairman love, then chairman love walked over and stood in front of them.
"i don't know how to express thanks to you properly.
 of course, a material reward rather than paying lip service is more gentlemanly, right?"sungwoo felt he could communicate with her better than he expected.
chairman love continued, "please come with me to our congress.
 just tell the truth to those who are mistaken and misinformed.
 tell them we have to be united together to survive in this world…" she insisted on the integration of players from all over the world, which sungwoo repeatedly heard.
 but it wasn't something that sungwoo, who survived on his own, could say.
"okay.
"but he agreed to go to congress because this was a golden opportunity for him to destroy the wpu.
***the players on the wpu, or more precisely, "us 1 server", were weaker than expected.
"it looks like their average level is low, given that they are elite soldiers guarding the congress.
"just like jisu pointed out, the capital guard was pretty weak.
 

when sungwoo's undead army stormed into it, all of them helplessly collapsed like duckweed swept by the waves.
"as a matter of fact, the washington fleet was the only one owned by the us 1st server.
"sungwoo could figure out why easily.
 thanks to chairman love's excellent leadership, they formed an integrated force from the beginning.
as a result, the players hardly engaged in fighting for their vested interests, but they had little fighting experience.
'because they have embraced peace too early, there are hardly any strong fighters among them.
'in addition, thanks to the technology of the "hearst workshop," called dwarf, they have won the fight unilaterally, using high-tech weapons rather than fighting themselves.
 as a result, they led affluent lives with a strong army, but each of them was too weak.
and their weakness was fully revealed today.
 the moment their fleet collapsed, they helplessly collapsed at the attack of even a small number of strongmen.
"kheeeeeeeeek!"the last capital soldier guarding the entrance to the capital collapsed.
rattle! rattle!sungwoo's party and chairman love's forces went into the white dome with the skeleton army.
 "probably, their emergency meeting is still going on inside.
" "it's been more than 20 minutes since the washington fleet collapsed, but why they are holding out here?"sungwoo could not understand.
 "inside the capital, there has been installed a hyper gate just in case of an emergency, so i think that the remaining forces of the washington fleet and the capital guard will try to hold out until the gate is back in operation.
 by the way, i didn't expect there was such a big loophole in the capital security guard," said chairman love, clicking her tongue.
 because she found a huge loophole in the wpu that she built by herself, she felt bitter.
 clang!soon, the huge door to the congress opened, revealing the senate, which they only saw in the movie.
 american players sitting all over the top turned their heads.
 there was confusion and contempt on their faces.


 