\section{chapter 414}

sungwoo punched his side, belly, and jaws randomly.
 the impact of his punch was so strong that the emperor could not stand any longer.
 at last, he collapsed helplessly like a flat balloon.





"kheeeeeeh…"the emperor grabbed his belly, rolled up his body, and put his forehead down to the ground.
 he completely lost his will to fight.
 'well, i think i've shown him enough.
'in fact, if he had used a weapon, he could have killed him at once.
 however, the reason he went to the trouble of fighting him without any weapon was that he wanted to "show off" his physical strength.
 it was not the emperor alone who wanted to maximize the propaganda effect through the war.
 sungwo was also trying to use it to promote the world tree camp, conscious of the broadcast of the official channel.
'a lot of people around the world are watching this fight.
 they are already feeling it.
'sungwoo fought this war for the future.
 in other words, it was just kind of a strategic inflection point in some respects.
 sungwoo felt it necessary to send a strong message to the players around the world and raise the value of the world tree camp for the establishment of the 'control body' later.
but this war ended up with sungwoo's one-sided victory to everybody's surprise.
 as a result, all the players watching this war had no choice but to change their perceptions of the necromancer a lot.
 the strong image of the necromancer has been enhanced further.
 'this is especially effective in that i have dampened the fighting will of the chinese server.
'if he had defeated the emperor barely, he would have faced a strong resistance even if he succeeded in dominating the world.
 'i have come to stoke more terror in the minds of people by defeating the emperor overwhelmingly who has ruled the world with terror.
"in other words, sungwoo absorbed all the majestic aura of the emperor overnight.
"if you had wanted to act like the emperor any longer, you should have just stayed put.
"while murmuring like that, sungwoo pulled the grim reaper from the ground.
the emperor didn't make any resistance.
 sungwoo wielded the black scythe to cut his head.
 - you have earned 29,000 gold by killing a player.
'it's over…'but the war was not over as he wished.
 woo woo woo-
a golden soul arose from the emperor's drooped body.
"what the heck is this?"visit to lightnov‌elworld.
c­om discover new novels.
the soul radiated an eerie light, then vanished somewhere as if evaporating.
it was an ominous sign.
"well, it's not over yet.
"did the emperor have another hidden card?"then, let me fight it out!"sungwoo also had a hidden card.
it was the last card that he saved to leave a strong impression on the players around the world.
***the battle at the rampart was still going on.
"hole no.
 3 fixed!"the situation has gotten much better.
 sungwoo's party killed all of the terracottas that penetrated the rampart, and the blacksmiths led by muyon worked hard to restore the collapsed parts of the rampart here and there.
 "move forward under artillery cover, the entire fleet!"woo woo woo-the combined fleet, which had to be hidden behind the rampart, also advanced outside the rampart, firing enormous cannons.
 "stop that crazy golden hand!"the reason why the tide of the war was in favor of the allies was that the "oppressor's hand" disappeared and its right hand was tied.
 
of course, just because sungwoo's allies gained the upper hand in the fight at the rampart, it didn't mean that the emperor's army lost.
 the number of chinese troops was still overwhelming, and the thing was this was not the place that determined the victory of the war.
 "push them hard! we're going to win when the emperor is arriving here!"as long as the terracotta army was still functioning, it meant that the emperor was still alive.
 so the chinese army persistently continued the offensive, thinking that all they had to do was to hold out until the emperor arrived.
at that moment somebody shouted, "uh? what the heck is that?"the forward soldier on top of the rampart found something.
 a bright light began to flicker beyond the invisible barrier.
woo woo woo-you can find the rest of this content on the lightnov­elworld.
com platform.
soon, the upper part of the barrier was pierced as if melting, then a golden sphere flew in and began to fall somewhere behind the terracotta army like a shooting star.
then the elite terracottas standing there dispersed to the left and right.
 in their place was an unidentified black box.
 the golden sphere crept into it.
bang!a few seconds later, the black box exploded and something walked out of it.
tramp- tramp-it was none other than the emperor.
 the emperor, who was beheaded by sungwoo, was standing tall there, intact.
".
.
.
"- your soul has permeated the 'replica terracotta'.
this was the emperor's divine skill.
 if there was a terracotta resembling him within a certain distance, the emperor could infuse into it and continue his life.
the emperor prepared for the worst from the beginning.
"alright.
.
.
what a relief it was that i prepared three replica dolls!"the emperor patted his neck, staring at the rampart.
 "even though i lost to the necromancer, i can win this war.
"having said that, he raised his hands.
 then a brilliant beam of light behind his back flickered in the air, forming a certain shape.
 - caution! 'oppressor's gaze' has been activated in the area.
the 'oppressor's gaze' and 'the oppressor's right hand,' which were the emperor's divine power that controlled everything, reappeared.
woooooooo-the giant hand and huge eyes that appeared in the middle of the battlefield were enough to draw the attention of everyone on the battlefield and those players watching the broadcast.
"what the heck is that?""he's come back!"the players on the korean server watching it from the rampart couldn't help but be terrified at the scene.
 they could not help but be mistaken, too.
 "oh, my… no way! did the necromancer lose?"new novel chapters are published on lightnovelworld.
com"what? nonsense!"since they could not hear the broadcast in real-time, it was natural for them to think that the reappearance of the emperor meant the necromancer's defeat.
"if that's true.
.
.
""we are finished.
"that terrific scene itself frustrated them so much, and the emperor's offensive was a devastating shock.
 - you have been exposed to 'the oppressor's gaze'.
 all your bodily functions are weakened.
 * caution! prolonged exposure to it will make you vulnerable to his 'mind control'.
when the golden gaze of the oppressor passed through the rampart, the players standing on top of the rampart collapsed.


"ahhhhhhhhh!""i can't move my body…"the fallen players felt disgusting as if someone was pressing down their heads.
"ouch! my head! my head feels strange!"strangely enough, as time went by, they felt somewhat relaxed and even comfortable.
 "your majesty.
.
.
 ugh, what am i doing…"they were bound by the emperor's 'mind control.
'as such, the 'oppressor's gaze' was powerful enough to end a large-scale war at once.
the reason the emperor didn't use it from the beginning was that he wanted to show it at the decisive moment, fully conscious of the necromancer.
 but the emperor regretted his decision.
 "yeah, this is great.
 if i had used it from the beginning, i could have won with less damage.
.
.
.
"actually, he was tricked by the necromancer because he saved this hidden card until the last moment.
 "alright.
 let me repair the damage from now on.
"players' moaning in pain and frustration resounded from above the walls, inside the walls.
on the other hand, the chinese army outside the rampart shouted for joy as if they won the war.
 it seemed that the tide of the war was about to be in their favor again.
for more, visit lightnovelworld.
c­omat that moment another shooting star appeared.
whoooooo! you can also read this novel on the more advanced platform lightnovelspot.
com

 