\section{chapter 169}

                            the evolution society was thorough.
 they aimed precisely at the time when sungwoo would be the weakest, and they never put in a small number of troops.





moreover, they even mobilized a flying weapon of tremendous destructive power, called the iron mace of lightning god, to stop sungwoo from maneuvering in the air.
however, something that not only they but also sungwoo didn’t expect at all happened consecutively.
 sungwoo gained the power of anubis and kangsok appeared all of a sudden.
“they left behind a lot of treasure.
”therefore, most of the weapons they prepared became the loot of the allied forces.
[item information]-name: iron mace of god of lightning-class: unknown-category: player’s manufacturing-effect: when mana is injected, a powerful ‘lightning bullet’ is formed from the barrel made of the spirit’s core.
 (once per minute)“oh, we have obtained a flying weapon in addition to the ballista we got last time.
 i think we can transport them by helicopter,” said minhum after checking the items.
in shooting mode, it was about the size of an suv, but it could be disassembled and folded into a smaller size.
 there were three iron maces, so they decided to dispatch one in the suwon village.
“this is not the end of the story.
 there are all kinds of weapons on those trucks.
 it seems like they left an entire unit behind.
”meanwhile, sungwoo also gained a lot.
[item information]-name: fighter’s shackles-class: hero-category: blunt weapon
-effect: when colliding with an opponent’s weapon 5 times, the ‘warrior’s shackles’ skill is activated.
 it ‘seals’ your own and your opponent’s weapons for 5 minutes.
[item information]-name: mountain ghost’s wooden shield-class: hero-category: shield-effect: a shield that ‘disables’ 3 magic attacks is formed.
 (one hour’s cooldown)in addition to this, he also acquired two ‘human beast ampoule (werewolf)’.
 since he still had one ampoule, he could use anubis’ power three more times.
and he even got a new skeleton.
 it was a 4th stage werebull with a unique build.
 given that the monster pushed sungwoo when he was in demigod mode with tremendous force, he would be a powerful addition to sungwoo’s force in the future.
sungwoo’s party took a helicopter and moved to youngdungpo.
 originally, they were going to stop by the suwon village, but after hearing that the “angel’s stone statue” had been excavated, they changed their destination.
shortly after they arrived in youngdungpo, minhum brought news about the statue.
“the stone statue was found near mt.
 namsan, but since this is an installation object, i hear that it is possible to move it only one day after it was first discovered.
”“then, how many hours are left?”“we’ve got 17 hours left.
 currently, we’re tightening security around it and preparing to move it.
 sorry, but you have to wait a little longer.
”thanks to this time gap, sungwoo could take a break.
 since he was very tired after being released from the demigod condition, he took a nap.
***shortly after sungwoo woke up, hanho brought news.
“they achieved level 8 on average, so they are now celebrating.
 since we went there on a mission, we could not take part in their party…”it was good news that the villagers were level 8 on average.
 the skills of production players were also improving significantly.

according to the news, the quality of items made by the blacksmiths and tanners has improved day by day, and the menus prepared by the cooks were diversifying.
 jungho’s skill in establishing a safety zone also improved a lot.
“it looks like the village is functioning properly now.
”like hanho said, the functions like those of the villages in rpg games were being completed one by one.
 in other words, they were now in the process of securing a space where they could take a rest safely after the dangerous field.
“i also got a call from kanghwa island.
 it seems that the movement on the chinese side is unusual again.
 the number of their appearances on the coast is increasing, and even within the chinese 2-server community, lots of people are talking bullshit, arguing they have not yet finished conquering the korean peninsula.
”on kanghwa island, a chinese server player was held captive, so they could check their movement through the chinese community.
“really? it seems taiwan is stabilizing to some extent.
 so, they began to entertain the idea of occupying the korean peninsula.
”although the chinese players failed to occupy kyodong island and the korean peninsula, they successfully took over taiwan.
even so, they could not even imagine going back to mainland china, so it was possible that they still regarded the korean servers as a relatively easy target.
“will they come back?”“not for the time being.
”since they were defeated so thoroughly twice, they would not come back right away.
so, making such a fuss within the chinese community seemed just to be a common diplomatic provocation.
 namely, they kept reminding their players of the external enemies while solidifying the internal unity, so they could show to the outside that they were still active and strong.
“even if they have completely occupied taiwan, they will have to stay there for some time.
 in the meantime, we have to hurry up the formation of the alliance to find stability before preparing for a bigger fight.
”however, stability was not something they could get just by wishing for it.
the game once again began to change drastically.
-as of now, the mainstream ‘chapter 2-1: the balance patch is urgent!’ has ended urgently.
* the rankings of the warlord boss monster removalkor-157: 3kangsok han: 2doctor-000: 2yoon choi: 2hyonmin jang: 1doctor-001: 1remote villager: 1chairman of the reconstruction alliance: 1masan sword king: 1(a total of 15 warlord boss monsters)“uh?”“the game started again?”another new mainstream has begun.
[mainstream start guide]-chapter 3: select campdear all survivors of the korean server! i am happy to be able to share this news although you have gone through a long ordeal.
the mainstream so far has been a tough event where you have to fight against increasingly stronger monsters and survive, but now, the moment has come to determine your fate.
the two absolute races who are leading the game are waiting for you to join their faction.


from now on, please choose one of the two races, angel and devil, and continue the fight for the survival of earth![caution (important)]you can sign a contract with the faction through the ‘stone statue’ of the absolute race.
you can receive a ‘promotion quest’ through the stone statue, and when you clear the quest, you will receive a certain grade of ‘epaulet’.
a ‘faction quest’ is given to each faction, and a great reward is given to all of them upon clearing it.
a number of new large dungeons will be added.
the event will last for 7 days and the schedule may change, depending on the game situation.
finally, the absolute race came to the surface, and the selection of the factions began.
“angels and demons? then, shouldn’t we join the angels unconditionally? it seems that few people choose to be the devil’s faction.
”hanho tilted his head.
 as he said, the images of the two words were completely different.
“are the angels and devils the same as we know?”“oh, that’s a good question.
”“well, they are making fun of us now.
 it seems meaningless to judge good or bad about this.
”are they really the angels and demons from humanity’s view of religion?sungwoo thought they were not.
 in his mind, they were close to the concept that people were divided into a blue team and a white team in a simple competition.
“then, are they aliens? i’ve been thinking about this, but it’s clear that aliens are making fun of us.
 maybe they’re voting for us like superstar 101.
 sungwoo, they might have formed a fan club for you.
 if that’s the case, you owe a lot to orun! sungwoo, summon orun more often, will you?”“…”of course, sungwoo could not agree with him.
a little later the object in question, the angel’s stone statue, arrived at youngdungpo.


 