\section{chapter 444}

just before gangsok and his party were about to enter the portal, somebody shouted, "stop there! i'm charging at you right now!"




it was none other than hanho.
hanho was hiding among the rubbles nearby, waiting for the right time to attack gangsok.
 when the right moment came, he charged at him like an american football player.
thud!he slammed into vivona's body with two shields.
 and he wildly swung a whopping four spears at gangsok behind him.
clang!however, gangsok easily dodged the spears, then kicked his shield hard.
hanho was thrown into the air by his hard kick, then bounced off helplessly.
 thud!hanho was thrown into the wreckage of the pyramid at some distance.
 gangsok immediately turned and walked into the portal.
"oh, no! gangsok!"the fairy butterfly shouted.
 gangsok instinctively turned his head and found the butterfly grabbed by hanho.
woooooong-but at that moment, the portal was closed.
"hehehe! i've caught a butterfly!"it turned out that the four spears hanho was holding were not just spears, but the "dragonfly nets' attached to the tips.
 in other words, hanho made a surprise attack to catch the butterfly from the beginning.
gangsok's fairy, the butterfly, played a huge role.
 its primary role was to provide a powerful utility for him such as creating a portal or a shield.
 in that respect, hanho's catching the butterfly was a big achievement.
 "can i spray some insecticide on this moth?" said hanho.

he smiled wryly, raising the cage made of magic engineering.
 then the butterfly trapped inside was terrified and backed away.
"no! are you crazy! it's dirty!"in fact, hanho had a deep-rooted grudge against the butterfly for quite some time.
visit to lightnovelworld.
com discover new novels.
even though sungwoo and jisu couldn't remember it, hanho said the butterfly had shouted at him to go away, complaining that he was stinking.
"hehehe! i've been waiting for this day when i catch you! revenge! torture! ecstasy! delight!""ouch! go away! get lost! you smell dirty! terrible! you stink!"meanwhile, hearst and the blacksmiths came up with a way to bind isabella more tightly.
hearst presented a new item, and said, "well, you can think of it as a collar for a dragon.
"it was a mechanical necklace with three great swords embedded in it, like a dog collar with a pointed gong.
 the special thing about it was that all the three swords attached like a gong were 'dragon slayers'.
"now, if you press the button on the remote control like this.
.
.
"clang!the blade that protruded outside with a roaring sound penetrated inward.
"this is how the three swords are stabbed into the dragon's neck.
 the dragon might be killed or at least pass out.
"if sungwoo binds isabella with it, he might be able to control her by force.
".
.
.
"isabella was huffing and puffing in anger as if she had a deep grudge against not only sungwoo and the world tree, but also her boss gangsok.
"don't touch her right now.
 talk her into it later, so she can understand well.
"it was okay to make it with bones, but it would look pale when compared with the real dragon.

***"we have to find a way to stop the demon king before he obtains the last world seed.
"when sungwoo said that, the white wolf nodded.
 he was covered with blood after he was attacked by gangsok.
 fortunately, the white wolf knew how to use quite a bit of magic, so he cast a spell to strengthen his body the moment gangsok attacked him.
 after that, the priests rushed to him and cast a recovery spell for him, so he could survive and stand up again.
"i think we need some clues to track him down, right?""yeah.
 if we can't, it's impossible to stop him.
"gangsok escaped, but they wondered if they could beat him when he obtained the power of the world eater.
 the battle was not in favor of sungwoo's party.
the latest episodes are on the lightnovelworld.
com website.
"okay, this is an item.
 can you read the memories inside it?"sugnwoo lifted the cage where a butterfly with inflated cheeks was trapped.
when he first met gangsok, he said even the fairy butterfly was the type of item that belonged to its original owner.
 if that's the case, it would be possible to read the memories inside the item through 'psychometry',clang-the white wolf reached into the cage and grabbed the butterfly.
"ugh! dirty wolf, go away! ugh.
.
.
"the butterfly resisted by whining, but when the white wolf closed his eyes, it went limp.
 his psychometry just began.
".
.
.
"some time has passed since the white wolf tried to read the memories by having the butterfly go through a psychometric test.
 after all, he succeeded in reading the memories, so he whispered something into sungwoo's ears.
it seemed that he was still weak after he was hit by gangsok.
after hearing it, sungwoo nodded, then turned his head and spoke to the players of the world tree camp gathered around him.
"we are right now heading …"fortunately it seemed that the demon king was somewhere.
everyone held their breath, wondering what their next destination would be.
"everybody, we're heading to the demon king's castle right now.
"their crackdown on the demon king's castle began.
 while the war was going on across the world, something was happening somewhere in the valley of mt.
 sorak.
 "gasp! gasp!"two men were climbing the mountain road.
"we're almost there!"they were young men in the shape of a tiger.
 they were climbing the hill with a basket the size of their bodies.
 "man, this is so heavy! why is the king always eating only potatoes?""i don't know.
 i hope we have boiled them well this time.
 i wish he would not complain this time.
"visit to lightnov‌elworld.
com discover new novels.
they climbed the mountain road again, carrying baskets of steamed potatoes.
 and finally, they arrived at their destination.
"see that cave over there? that's our destination!"they lit a torch prepared in advance.
 however, they saw something strange ahead.
 "ugh! what the heck is that?"

something was crawling out of the cave.
"the purple smoke.
.
.
this must be…"it was the smell of death.
 it looked like something was going on under the cave.
 the king of the great mountains was down there.
 obviously, something bad happened to him.
"come on, hurry up!"they put down baskets of potatoes and ran downhill into the cave.
if anything really happened to the king, there was nothing they could do.
 as the king's subordinate spirits, they instinctively moved only out of loyalty to him.
"gasp! gasp!"by the time they reached the cave, something shone after reflecting on the light of the torch.
 it was an underground lake.
 but a very dark purple smoke was waving over it.
"your majesty king!"they hurriedly ran around and called their king at the top of their voice.
 just then, someone walked out of the purple smoke.
"ugh? what happened?" the king of the great mountains asked.
 "why are you screaming like that? you guys have such a loud voice that my ears can be deaf!"he was healthy and intact.
 "your majesty!" the two tigers were bewildered.
 in their view, the king of the great mountains was wearing a very odd mask, which was a k-1 gas mask.
"cough! cough!""oops! what is this?"they felt relaxed to confirm their king was safe, but they had no choice but to cough after breathing in a lot of purple smoke.
new novel chapters are published on lightnov­elworld.
com"ah! i forgot to tell you guys that you should wear a gas mask before coming here.
 this is a poison gas called 'breath of the abyss' that i got from the necromancer.
 if you breathe in this gas carelessly, you will be paralyzed, so stop breathing from now on.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 