\section{chapter 254}

                            in season 2 , sungwoo vividly remembered the terrible scenes he saw through the prophetic stone which showed lich on bone wyvern resurrecting the corpses piled up on gwanghwamun boulevard as an undead army.





however, sungwoo thought that would not happen after he took over the grim reaper and became lich because he changed the future.
‘did lich appear on the north korean server?’moreover, it’s still more than a month left until the first day of the new year when the season 2 update was scheduled.
‘as expected, things haven’t worked out as i intended.
’it has always been these kinds of variables that made this game great.
 nobody was sure whether or not another lich might be growing his strength somewhere.
‘if there is another lich, i had better get rid of him, whether it is a player or a monster.
 for me, he is like a competitor who consumes the same resources.
’he could confirm it by recalling the ‘awakening quest’ in the past.
recalling the description at the time, the message was about taking over the ‘reaper’s scythe’ first.
 in other words, there was only one item called grim reaper, and now, it was in sungwoo’s possession.
even if there was a player with a similar profession to sungwoo somewhere, he couldn’t possess the grim reaper without killing sungwoo.
‘what if there is another exclusive item…”conversely, it also meant that another competitor could preemptively obtain the item and adversely affect sungwoo’s growth.
therefore, sungwoo concluded that it would be beneficial to eliminate his competitor.
“sungwoo, are you going to move right now?”he shook his head at jisu’s question.
“wait.
 i always need an upgrade before the big battle.
”“pardon? upgrade?”sungwoo summoned a werewolf skeleton.
 the backpack on his back was bloated, which served as something like an inventory.
sungwoo continued, “well, i haven’t opened the legendary item box that i earned after winning the metropolitan occupation war.
”at that time, he won five legendary-grade item boxes after winning the metropolitan occupation war.
however, he kept delaying opening the box because he was so busy dealing with various urgent matters, so he was still holding them without opening them.
 now, he could not put it off any longer.

sungwoo pulled out all the item boxes.
“wow, it’s a jackpot!”with hanho exclaiming in admiration, he lifted one of them.
[item information]-name: legendary item box-grade: special-category: event item-effect: when you open it, one ‘legendary level’ item is given at random.
“wow, five legendary items? it’s a really exciting moment.
 i know you will be kind enough to give me one, sungwoo.
 right?”but as soon as he tried to open the box, a message that popped out suddenly blocked his eyes.
-you can exchange 5 ‘legendary grade item boxes’ for one ‘myth grade item box’.
“what?”this was a privilege he didn’t expect at all.
 it looked like he could exchange five item boxes for a higher grade box.
‘myth grade?’the myth grade items sungwoo obtained so far were only three.
the first was the ‘seeds of the world tree’, the second one was the ‘herculean bow’, which he could not use yet, and the third one was the ‘shadow king’s crown’ he had obtained as a set item.
‘based on the items i obtained until now, there are tremendous restrictions on using the myth grade items.
’for example, it required 100 stamina to pull the herculean bow, and the seeds of the world tree were not easy to plant.
 the shadow king’s crown could also be used only when sungwoo collected a legacy set.
in other words, the myth-grade items could be a necessary evil.
 it could have been more effective for sungwoo to hang the five legendary-grade items on his body.
“nope, it’s a higher grade than the legendary item.
”
“pardon?”“hanho, i’m sorry, but i think i might not give you one.
”“man, you are so mean!”he had never used the herculean bow, but considering the influence of the world tree or the effect of the shadow king’s crown, a myth grade had much more power than the five legendary items.
-would you like to exchange the item? (y/n)sungwoo clicked y.
 then, the five legendary grade item boxes turned into a golden powder then started to unite into one.
 soon, a small case was created.
 it had an emerald color, which gave him the impression that it was a higher grade than the legendary item.
‘let me open it without any reservation.
’sungwoo boldly opened the box.
 then, a small stick fell from the air.
-you have exchanged it for a ‘myth grade’ item.
when he checked it, it was a fan.
[item information]-name: fan-grade: myth-category: wand-effect: increases magic immunity (+15%) and can control the soul of the dead (ghost).
 (maximum 10) the ghost’s performance varies depending on the user’s ‘affinity for death trait.
’-description: it contains the spirit of ‘the man who controls the ghost.
’luckily, the item was perfectly suitable for sungwoo.
 besides, there seemed to be no specific conditions for its use.
 however, when looking at the item description only, it looked rather shabby compared with the previous myth grade item.
‘i can control ghosts with this item?’sungwoo felt he needed to use it first to figure out how effective it was, but it looked like he could not expect this item to be as powerful as ‘the shadow king’s crown’, which had doubled in power at once.
at that moment, a message rang.
-you have met certain conditions.
* lich (the one who deals with death) + fan (the one who controls the ghost) + unknown (requires additional acquisition)‘conditions?’it was a message similar to the one that he saw when he obtained anubis first.
 at that time, he could temporarily use the power of anubis when his lich condition was mixed with the human beast condition.
‘what kind of puzzle is this?’is it more powerful than anubis, given that it requires three conditions? since there was no hint at all, sungwoo could not figure it out at all.
he turned to look at jisu and hanho.
“alright.
 let’s go now.
 hanho, you are all set, right?”as expected, they had to take care of the pending task first.
“well, i only have a few items.
 so, i hardly have anything to prepare.
”“really? good.
”“what are you talking about?”sungwoo passed hanho and stood in front of jisu.
“the mountain terrains might look complicated when you look down from the sky, jisu.
 can you find out where the king of the great mountains is?”“oh, i know how to do it without flying.
”having said that, she pulled something out of her pocket.
 sungwoo thought it was something like a medal, but when he looked closely, it was something like a medal with a horse drawing on the surface.
“the king of the great mountains gave this to me, promising to meet me next time.
 i can go right to him with this.
”“it looks like that monster liked you very much, jisu.
”come to think of it, thanks to the king of the great mountain, jisu could teleport to suwon and busan in an instant, not to mention her awakening.
“ah, this one…”

when she used the item, a turquoise portal opened.
sungwoo, jisu, and hanho entered the portal.
***as soon as they exited the portal, a misty valley unfolded before them.
“oh, my…”sungwoo and hanho were distracted by the mysterious scenery at the foot of the mountain.
“when i came here on a school trip, i didn’t feel that mt.
 solak was so mysterious back then.
 i just can’t remember.
”as hanho said, there was something different about the mountain that he had been so familiar with.
while walking uphill, escorted by jisu, they were fascinated by the mountain scenery.
with white frost piling up, a light fog peeled away little by little as they moved forward.
mountain peaks stretched to the left and right of the winding valley, and scattered clouds were hanging like curtains right under them.
ooh ooh oohas the mountain breeze pulled the edge of the clouds vigorously and pulled the curtain off, a dark stone mountain gradually emerged.
 it was as if the head of a giant was looking down at sungwoo’s party.
“well, don’t you think a mountain god is living somewhere here?”as the mountain terrains changed steeply, they began to look downward.
then, the tough roots of centuries-old pine trees continued to spread like a river stream, and white rocks stuck through the greenery were connected like stairs.
red flowers of unknown names were also blooming in clusters between the rocks.
“it certainly didn’t seem like this from the beginning.
 it’s rather alien.
”“you bet.
 this is the kind of place my father likes very much,” said hanho.
all the mountains also had some sort of mysterious appearance, but now this particular appearance of mt.
 solak seemed to have been modified by the system in one way or another as if its intrinsic characteristics were intended to stand out.
“if we go a little further, we will reach the king’s dwelling,” jisu said.


 