\section{chapter 342}

chapter 342: jeju island and attack on demon’s cave (6)dozens of undead were rushing towards kumiho, who could not escape from bone imoogi’s jaws.
 then, they started pounding kumiho, who had been worshipped as god for such a long time.





‘hum…i obtained exp as well as good bones here.
 it wasn’t a bad place for me to stop by.
”finally, sungwoo jumped off bone wyvern alpha male and landed on the ground.
then, he looked at the worshipers who could not hide their bewilderment.
“your god is now in my hands as a collector’s item.
”suddenly, the fanatics’ eyes seemed to have cleared up a bit.
kumiho, the nine-tailed fox, was helpless.
of course, it was clear that the cunning fox was a powerful presence that had no rival on jeju island, but that was her limit.
due to the nature of the game, those creatures that do not interact with other worlds cannot gain exp.
 in other words, their growth is supposed to stop at some point.
so, kumiho could not help but be helpless before the world’s foremost power, the necromancer.
“ah, our god…”while watching the nine-tailed fox unilaterally being attacked, they could not take any action.
 it was a moment when the world they believed in was shattered at once.
and finally, kumiho, covered in blood, fell.
- you have obtained 8,750,000 gold by hunting the field boss monster ‘kumiho’.
sungwoo frowned, looking at the message.
“only 8,750,000 gold?”
he wasn’t satisfied with the reward at all.
‘but her bones are good-sized and good for moving fast.
”given that he obtained decent bones, the fight was worthwhile.
 and a marble rolled out of the nine-tailed fox’s mouth.
 it was an item.
[item information]- name: fox bead- grade: legendary- category: orb- effect: increases maximum mana (+300).
 when mana is injected, you can scan the area within 20km thoroughly for 1 minute, and open a portal that can move within 10km after 1 minute.
 (24 hours standby for reuse)- description: a marble imbued with magical power.
it was a ‘fox bead’ that appeared frequently in fox tales.
 like the legend that it made those who swallowed it master geography, it was equipped with the effects of terrain observation and teleportation.
‘this can be helpful to me just in case.
’because it could take effect only one minute, the fox bead would not be able to even play the role of a navigator, but it would be useful when sungwoo attacked the demon’s cave.
 he put it into his inner pocket.
at that moment, the worshipers came in droves and knelt in front of sungwoo.
 an old man with white hair, who seemed to be the head of the group, looked up at him and rubbed his palms together.
“please save our lives! we were stupid! we would serve you as our god or even king!”“…”
sungwoo was dumbfounded to hear that.
 king? was it the universal characteristic of a weak human being to wander in search of something to worship?“oh, is the fighting over?”at that moment, inho and hanho reached the top of oreum with somebody that sungwoo had never seen.
when sungwoo looked at them with a puzzled expression, inho introduced them.
“ah, these are the survivors in jeju island.
 unlike those fanatics, they were fortunately sane all along.
”but the woman standing at the front of the group of survivors shook her head.
there was murderous intent on her expression for some reason.
“oh, i’m sorry, but i’m not particularly sane, you son of a bitch!”she suddenly spat out curses then jumped to the ground and charged at sungwoo.
more precisely, she was charging at the ‘monster worshiper’ who was kneeling before sungwoo.
 then, she kicked the face of the white-haired old man, the leader of the group.
her kick hit the old man’s lowered crown.
 he fell flat on his face, with his broken mouth bleeding.
“ahhhhhhh!”while everyone could not hide their embarrassment, the woman grabbed the old man by the collar and lifted him.
“well, i have to go crazy to deal with this crazy bastard! sorry.
”she stared at the old man with an angry expression.
 she seemed satisfied she could catch him finally.
“damn it! how can you grab an old man like me cruelly…”the old man began to struggle and moan unnaturally as if he was trying to provoke her sympathy.
“crazy.
 how can you pretend to be an old man when you have the highest level and you are the most healthy among us? you fed those herbs to little children, right?”then, she raised her left hand and pointed it somewhere.
 behind the survivors were some children.
 all of them had sunken eyes.
it seemed that they had been brainwashed while they were held captive, and the unknown medicinal herbs must have driven them crazy.
“i used them to deepen your faith…”the old man muttered instinctively but stopped soon because the subject of their faith disappeared.
 his eyes were full of confusion.
sungwoo allowed the two to talk for some time because it seemed that the bad blood between them ran deep.
 and a few minutes later, she thanked sungwoo’s party with her fists covered in blood.
“we have been freed from this crazy world thanks to your help.
 we don’t know how we should repay your help.
 by the way, is everything okay on the mainland?”since they were isolated on jeju island for quite some time, they didn’t know what was going on in the outside world.
that’s why they couldn’t recognize the necromancer and the world tree camp.
“well, it’s the same in the mainland, too.
 as a matter of fact, more unfortunate things are happening all the time.
”like inho said, they were not dominated by somebody, but they went through more heinous things.
 they managed to withstand it all until now, though.
“by the way, how many survivors are there other than the fanatics?”she shook her head with a bitter expression.


“as far as i know, there are not many.
 one thousand at most, i think.
 there are some people hiding all over the island, but as you can see, there are more monsters.
”an isolated island like jeju could be stabilized like the us server if things worked out well, but if something went wrong, those remaining on the island had no choice but to become endlessly miserable.
 unlike the mainland where almost all monsters were cracked down on, this place was still dangerous.
“look at this! we’ve found something!”at that moment, the crew who launched the search pulled down something from an iron tower, the highest point of oreum.
“i think this is an item that blocks radio waves.
”[item information]- name: secret pole- grade: hero- category: totem- effect: all ‘remote connections in the area (5km) where the pole has been installed will be cut off.
 when more than 10 poles are ‘connected’, they will affect more broadly.
“yes.
 there are things like this all over jeju island.
 we tried to break them by all means, but we failed because we lacked power.
”jeju island had been isolated by blocking one bulletin board like this, which reconfirmed the power of the function of the community.
“by the way, haven’t you heard anything from jisu?”“not yet.
”there was still no message from jisu’s party, which searched for traces of the black lion.
 as time passed by without any update, sungwoo had no choice but to be impatient.
“okay, let’s get ready, so we can move anywhere.
”

 