\section{chapter 299}






 when the gunnery officer shouted, those on the deck were quiet.
but soon somebody asked mischievously, “hey, manager! so, what is the client’s request?”the gunnery officer opened his mouth with a stern expression.
“well, he has ordered us to begin the attack as soon as inspiration comes to our mind!”a peal of laughter burst out.
meanwhile, those on the ‘superstructure deck’ were also busy.
 a number of combat troops were preparing for an unexpected situation.
 their mission was to block the enemy by spamming attack magic when they approached, and going one step further, they should also prepare for a hand-to-hand fight just in case by getting on the deck.
“uh?”“what the heck is that? shadow?”what made them so embarrassed was the shadow cast on the deck.
but this time the shadow didn’t pass by quickly.
 it got bigger and bigger and covered the deck.
this was the outright approach of the shadow.
“it’s over our heads!”above their heads came down a pair of huge wings.
 they were an exceptionally large bone wyvern and bone wyvern alpha male.
 the enemy was about to attack them over their heads.
“prepare the freezing magic!”“do not panic! they can’t penetrate our shield anyway!”all ships were covered with powerful shields.
 so, they couldn’t jump off the deck.
 if somebody threw himself without knowing anything, he would slide and fall into the sea.
the troops on the deck were on standby just in case.

“everyone, save mana! if they are stupid enough to touch the shields, we’re going to smash them to pieces!”but their expectations were wrong.
clang!a large cannon mounted on the back of bone wyvern alpha male fired.
 a beam of flames struck the ship’s shield.
clang!the shield was crushed with one stroke, shaking the deck.
 the deck soldiers lost their balance and fell.
 then, the enormous heat that melted the shield came down, burning their faces and necks.
“argh!”“damn it! what the hell did they fire?”it was a ‘supernatural storm’ equipped with a ‘fire spirit stone (advanced)’.
 contrary to the blacksmith’s expectations, the cannon could not crash the airship with a single stroke.
however, it did its job nicely by breaking through the shield.
– caution! the ‘fellblade’ has started in the affected area.
“what the heck is this message?”along with a messenger that the players on the us server had never seen before, black smoke rose from the wings of the enormous shields above their heads.
at first, they thought it was just a dark cloud.
“oh, my god!”“oh, god…”soon, the undead army began to pour down onto the deck like a waterfall.
tung! tung! tung! tung!
since the shield was gone, they could not attack the enemy.
“argh!”the panicked players were crushed to death by huge skeletons falling from the air.
rattle! rattle!they covered the superstructure deck in an instant.
 then, they squeezed themselves into the cabin, went down the stairs, and began to occupy the airship.
their ambush was an unexpected development, and it happened in an instant.
since they had little time to grasp the situation, the order from their superior was delivered belatedly.
 so, the players onboard were kept in the dark about what’s going on.
“you heard something like an impact, right? what was it?”even the gunnery players on the deck were sitting blankly, aiming at the approaching bone wyvern.
“we have received no orders yet.
”if there was anything different now, they didn’t smile anymore.
 tight-lipped, they listened for the strange noises coming from above their heads.
rattle! rattle!as the horrible rocking noise got closer and closer, someone left the place and quietly stood.
 his action was a violation of the rules, but no one stopped him.
“…”he slowly approached the door.
at that moment, the door broke, and white demons poured in.
in contrast to the gray ruins that they left behind in jinhae port, another work of intense red was born.
***the flagship “bird of washington” led by admiral william baker of the wpu was shrouded in silence.
 there was only the screaming of the signal officer.
“blue wing! respond! respond!”however, all he heard from the radio item was a miscellaneous signal.
 he could not make any contact with the players on the airship that they had dealt with the enemy’s intrusion and reported back.
“there is no answer from them.
”the ‘blue wing,’ the 3rd airship, as seen from the flagship, broke away from the line of battle and gradually sailed backward.
 but it looked as if the airship was sinking into the sea.
the massive bone wyvern that hit the blue wing was expelled by its shielding, but only after a significant number of undead troops invaded the ship.
nobody could figure out what kind of terrible things were going on inside the ship.
“…”with everybody silent amid restlessness, admiral william baker, in his late 60s, was resting his chin on his hand with a calm expression.
“uh? the blue wing is moving again!”the altitude of the blue wing, which was slowly sinking as if drifting, was up a bit.
 that meant that somebody was doing it manually.
“i’ll try to contact them again!”when the signals officer said, the admiral’s eyes wriggled a little, but still, he looked like a relaxed old man keeping an eye on a rye field.
then, he slowly fixed his posture and spit out a command in a slow tone.
“shoot it down.
”“pardon? shoot down the blue wing?”when the admiral ordered, all the crew members of the flagship turned around.
at first, they could not believe their ears.


even if they allowed the enemy to intrude into the ship, how could he sacrifice the precious airship and the lives of dozens of crew members on the blue wing?“…”when all the crew hesitated, admiral baker’s eyebrows wriggled twice.
he typically showed that body gesture when he was displeased with something.
“shoot it down before i shoot you in the head right now!”his tone was still slow, but there was a murderous intent in it.
now, all the crew looked at the blue wing and began to carry out the order.
“this is an order to all the battleships! fire and shoot down the blue wing…”but it was too late.
 suddenly, the blue wing’s muzzles tilted and began to fire.
bang! bang! bang! bang!four shells hit the no.
 2 ship, floating right next to the flagship.
 the lower deck was crushed, with the pieces of wood fluttering everywhere like autumn leaves.
“uh, what the heck?”no.
 2 ship lost its track, tilting before colliding with no.
 6 right beside it.
the two ships broke away from the line of battle and started drifting back a few dozen meters.
“…”everyone on the flagship was so shocked that they could not think straight.
 what the heck happened? how come the blue wing was attacking their friendly forces?at that moment, admiral baker raised his hand for the first time.
 then, he loaded one of the four rifles behind his back.
 at the same time, the signal officer, who stopped while conveying the admiral’s order to fire, was shot through his head.
 when he fell, with his head slamming against the dashboard, the crew member next to him immediately picked up the radio.
“all the battleships! bombard the blue wing!”

 