\section{chapter 300}






 as soon as the order was conveyed, the remaining five battleships poured shells at the blue wing.
 as a result of the ruthless bombing, the blue wing lost its balance and began to sink into the sea.
“blue wing is sinking!”with such heavy damage, it was obvious that its engine was damaged.
 so there was no chance of its rising above the sea again.
admiral baker stood up and shouted, “you idiots! did you think all the undead were stupid like you? they are human-controlled undead, and somebody who is much smarter than you controls them!”he loaded all four rifles behind his back and shouted, “okay, from now on, i’m going to keep only useful guys on the ship.
”the crew members corrected their postures.
in the meantime, sungwoo soared to a high altitude, riding bone wyvern alpha male.
 shortly after he raided the blue wing from the air, he was intensively bombarded by the ships, but he managed to get out of the striking range at the last minute.
he took turns hiding behind the clouds and coming out, repeating such a strange action for a while.
“summon!”when he said that, a skeleton was summoned over the wide spine of the wyvern alpha male.
 it was victor.
“rattle… rattle…”victor felt tired a lot.
 so much so that he squatted as soon as he was summoned.
“master? rattle…”leaving that word behind, he was summoned back into the “void haven.
”“summon!”and he was summoned again.
 it was already his 11th resummon.

however, sungwoo was just staring in the air without looking at victor at all.
“rattle….
”“done.
”sungwoo smiled at the message that appeared before his eyes.
-‘synergy effect’ is given due to team play.
[synergy list]5) death harmony (hidden)-category: job synergy-condition: 3 or more ‘lich’-level death magic users-effect: upgraded to the exclusive skill, ‘ultimate’ level (1 random type)* players only-the skill  is temporarily upgraded to .
sungwoo aimed at a loophole in the condition of synergy activation to obtain  among random skill enhancements.
 synergy was triggered when three lich worked as one team.
however, when victor’s summoning and returning were repeated, synergy’ activation’ and ‘cancellation’ would be also repeated, which meant that the target skill to which the synergy was applied should be continuously ‘reset’.
“rattle… rattle!”and sungwoo could get the skill he wanted after summoning victor and canceling it eleven times.

“no way! should i continue to do so in the future? it feels like motion sickness…”when victor said that, sungwoo looked at him, which made him flinch.
“do you get motion sickness?”“that’s right!”“even if you have motion sickness, you have nothing to throw up, right? are you lying to me? biologically, you can’t get motion sickness.
”“if you think like that, it is impossible for me to be biologically alive.
 rattle.
.
”“…”sungwoo turned his head, thinking victor was smarter than he looked.
however, victor was nervous because he thought his tongue slipped before his master.
“now, let’s go out of the clouds.
”it was time to launch a full-fledged fight with the enemy fleet.
whoooooooooooo-bone wyvern alpha male pushed the wind hard and rose above the clouds in an instant.
sungwoo looked down on the terrifying battlefield from the high sky.
 the baker fleet looked like a tiny dot on the sea down there.
‘two battleships broke away from the flagship.
 there are only five left.
’even before the full-scale battle began, the lineup of the baker fleet was quite disorganized because sungwoo took over one of them then bombarded another using it.
nonetheless, they didn’t retreat.
 watching the approaching bone wyvern, they were still prepared to fight back.
 it showed they were confident of defeating sungwoo’s army.
“yeah, then destroy them as much as you can!”sungwoo controlled the undead army in the northern sky.
 dozens of bone wyverns spread to the left and right widely.
 it was a battle formation intended to suffer as little damage as possible from the enemy’s firepower.
as a result, the battleships of the baker’s fleet also began to widen the space from each other little by little.
 it was a change of location to fire shells over the widest possible area.
 it was this kind of comprehensive attack that made people so scared of the attack by the fleet.
‘but they are moving slowly, compared with the bone wyvern.
’sungwoo confirmed the weakness of the baker fleet.
 although the weight of the battleships was reduced due to the power of the ‘flying stone’, the weight of the cargo and crew in it could not be ignored.
‘when starting from the hovering position, they can’t help but move slowly.
’if the battleships accelerated, they would be able to achieve a speed of more than 30 knots (55.
5km/s), but when they stopped moving before operating again, it was inevitable for them to move very slowly.
‘let me break them one by one.
’sungwoo gave orders again.
 all bone wyverns turned to the right.
 they aimed at the leftmost airship of the baker fleet as their main target.
of course, the baker fleet wasn’t stupid either.
 the leftmost airship, which was sungwoo’s target, slowly sailed back, while the airships on the right gradually advanced.
 it looked as if the compass needle was spinning slowly.
just by tilting their ranks with the flagship as the center, they could confine the battle group of bone wyverns within the striking range of their bombardment.
and finally, when they got close enough, dozens of muzzles began to fire from the baker battleships.
bang! bang! bang! bang! bang!there were sporadic explosions along with tremendous vibrations shaking the sky.
even though the battleships fired only once altogether, the battle line of the baker fleet was forcibly sailed back as far as ten meters by the impact of the firing.
colorful shells containing the power of various spirits were fired in a straight line.


in just 3 seconds, the group of bone wyverns was destroyed.
kugugugugugugugugu-the bombardment not only affected the entire group of bone wyverns but also filled about one-third of the northern sky with smoke.
“crazy…”although sungwoo was prepared for their fierce counterattack, their firepower was much more forceful than he thought.
explosions of all colors intertwined, forming a huge layer of fog.
 and he saw numerous pieces of bone being smashed and bouncing everywhere.
bone wyverns were devastated.
 sungwoo’s undead army as a whole evaporated in just one moment.
“they’re so thrilled….
”sungwoo watched the soldiers on the deck of the baker fleet cheering for joy.
 it seemed that they were confident of the victory.
however, sungwoo was making a mockery of their hasty joy.
“but it’s too early for you to rejoice…”the next moment, something popped up from the left side of the colorful layers of fog.
googoogoo-it rotated fast, like a tornado moving horizontally, and fired toward the airship on the far left.
the soldiers on the deck then stopped cheering and began to see the strange phenomenon taking place in the devastated enemy camp far away.
 they still didn’t know what it was.
it was as if a huge monster in the fog layer stretched out its tentacles.
looking down at them, sungwoo murmured, “manufacture bone weapons!”

 