\section{chapter 144}

                            in addition, the building was located inland, so sungwoo and his party could buy some time to respond to the enemy’s surprise attack.
 the building was also adjacent to a big boulevard, so they could escape to the city of inchon through the nearby kanghwa bridge if needed.





“okay, everyone, move! stack the daily necessities on one side, and put the weapons on the entrance wall.
 make as much space as possible around the door because we need to be able to get out in case of an emergency.
”“do we have to jump right out of bed and kill those chinese bastards?”“that’s right.
 if you want to kill them first, put your sleeping bag near the entrance.
 i have already secured a space there.
”like muyon said, the survivors of the kodong island group were full of anger, not fear.
“come on in, guys! i’ll kill you all this time!”“even if it doesn’t come now, i will somehow take revenge.
”meanwhile, heyon was having a hard time persuading a little child.
 for some reason, the child, who seemed to be an elementary school boy, holding a shield as large as sungwoo’s upper body in hand, was throwing a tantrum at her.
“i can fight, too.
 so, i’ll fight!”“you can’t! you’ll be in big trouble!”“i’m level 3, too! i have killed a goblin before.
”“you can’t do anything with level 3.
 don’t you know that?”“that’s why i want to fight because i want to level up!”“how come you are so stubborn, boy?”sungwoo got involved in the quarrel between the two while approaching them to ask her about the location of the forge in kanghwa island.
“hey, mr.
 necromancer!”“uh?”the child ran to sungwoo suddenly, then said, “please let me fight, too.
 tell that sister i can fight, too! i have to fight to get stronger, right? if i don’t fight, i have no choice but to keep being weak!”heyon was on the spot at the moment in embarrassment.
 she shook her head secretly while looking at sungwoo.
 the child had a point, but this was not a fight for an elementary school boy with level 3.

after all, sungwoo said, shaking his head, “no, that’s not true, boy.
”“pardon? then, what should i …”“because a dead person cannot be strong.
”“well,… but…”“if you go out to fight recklessly, you will only raise the level of others.
”the child dropped the shield as if he was shocked.
“you should know when to fight, and you have to fight in a smart manner.
 so, you want to be strong? think if this is the right time to fight.
”“yeah.
”the boy soon became depressed and walked away with his head down.
watching the boy, she said with a sigh, “he’s my relative’s younger brother.
”“if that’s the case, your father…”“that’s right.
 the elder brother of my father served as our leader…”she continued to speak in a small voice, “but he was killed by the pirates.
”she said he was eaten by the monster bird.
“youngin witnessed that terrible scene.
 despite the great shock, he is so courageous, and i’m proud of him, but i’m worried about him because he is so stubborn in taking revenge against the chinese pirates.
 i hope you won’t involve our kids in the fight.
”it wasn’t right to keep protecting the senior men just because they were elderly because it’s like stopping them from becoming strong.
 but it was important to differentiate between the battle they could participate in and the battle they could not.
“our kids can’t be allowed to participate for now.
 we’ve lost if the moment comes when we have to mobilize our kids in the fight.
”heyon nodded at sungwoo’s remarks.
 she was clearly worried, though, because she had experienced it once.
“i don’t think it will happen because we are with the necromancer, right?”
in fact, the people in kyodong island could get out of the hellish world thanks to the timely intervention by the best reinforcement: the necromancer.
“by the way, do you know where the forge is? i asked your father, but i couldn’t get his answer because he was on patrol.
 ”“ah, yes! i know.
”has the time finally come for him to combine items?***black human shadows were climbing through the cracks of the rocks on the southern shore of kanghwa island.
 there were a total of eight men.
the players on the island were watching the shore, but they couldn’t notice their underwater infiltration.
“now, we will use our stealth skill to enter the forest.
”furthermore, when they used some skills, they disappeared into the forest.
a few minutes later, they reappeared from a distance, climbing a slope past the trees.
and finally, they stood on an unknown mountain peak.
 the cold breeze made their wet bodies cold, but they were busy carrying out the operation, not caring about it at all.
“captain, what happens if i use this item?”a masked man holding a flag with a game machine icon on it asked hui, the leader of the team.
“i used an item with two higher levels than this one in taiwan, too.
 as a result, we crushed the taiwanese guys with a much smaller force after winning the mini-game.
”[item information]-name: mini-game generator (intermediate)-grade: special-category: event flag-effect: if you stick a flag, a mini-game (korean hopscotch) will be launched within a certain radius.
-description: when the game is launched, an area with a certain radius is designated as a ‘mini-game area,’ and ‘occupied areas’ are formed in a total of 3 areas.
*each time you occupy an occupied area, different buffs are given.
 when you occupy all areas, they are designated as ‘occupying forces,’ and a huge buff is given.
“actually, i wonder if i have to use something like this.
 this item can be used in our favor when a small number of people face a large number of people.
 well, i think the general is trying to make sure that we do not make a mistake again.
”the flag was stuck on the mountain peak.
 then, a pink game console icon appeared on the flag.
“start the game!”***while he was trying to move to the forge, escorted by heyon, sungwoo suddenly received a message.
-a ‘mini-game (korean hopscotch)’ will start in the affected area!-occupied area has been designated in random sites (a/b/c)-enormous buffs are given when you secure the occupied area.
-the area will be ‘closed’ in 15 minutes.
“uh? what the heck is this game?”“mini-game?”even sungwoo was embarrassed by this unexpected situation.
 at that moment, some noise was coming out of the radio item that muyon gave him.
-necromancer! they have appeared on the southern coast!it was muyon’s voice.
 he kept saying something urgently.
-it’s a fleet! the container ship fleet is back! they are approaching the south coast quickly!‘they are coming back at the same time the mini-game starts?’

-and we’ve got a report from the west coast! several fishing boats are preparing to land on the coast!it was clear that the mini-game was launched by the enemy.
 according to the rule, they clearly intended to enter the island simultaneously within 15 minutes, namely, before the access to the local area was closed.
“they haven’t given us a chance to reinforce our troops….
”-there is an occupied area nearby.
 (zone c)“uh, what should we do now?” heyon asked.
immediately after confirming the message, jisu and hanho approached sungwoo.
“sungwoo? what the hell is going on now? is this a game in a game? what the heck is this game?”now, they had only one choice.
 as always, all they had to do was win according to the rules of the game.
 what kind of strategy should they take to win?“i don’t know for sure, but i think the key is to occupy three occupied areas.
 they’re going to attack us by mobilizing a large army.
”the enemy was numerically superior to sungwoo’s troops.
 so, it’s highly likely that they would most likely obtain the occupation buff by a massive attack, then thoroughly defend the occupied territory because that was the most simple and powerful method.
“then how do we deal with them?”sungwoo walked out of the gym.
 at that moment, all kinds of red, blue, and green lights were shooting into the sky from all over kanghwa island.
 it seemed that they were the three occupied areas a, b, and c.
‘it is difficult to recover the occupied area after losing it.
 in that case, we’re going to fight them in a very unfavorable situation.
’sungwoo summoned bone wyvern.
“first, let’s take over the area and hold out because we can move faster than them.
”what if it was a battle of not occupying, but defending the area?“let me make them pay the price for starting the game without checking their balance.
”this was a battle of about 3,000 vs.
 262.
 the inevitable death match began on the small island.


 