\section{chapter 273}






 meanwhile, hanho’s mother, eunhee, began preparing food for the baby dragon as the chief chef.
“when it’s born, its intestines are still weak, so i have to make soft food, so it can swallow easily.
”eunhee was studying the menu with her fellow cooks.
but hanho, who was overhearing her, tilted his head and asked, “mom, it’s a dragon.
 do you think its intestines are weak?”“what? what did you say? dragon?”“um… if this guy enters puberty and throws a tantrum, our whole village may be shaken.
 yeah, it might be more terrible than dad’s shaking the village with playing cards.
”other cooks grinned at his joke.
eunhee slapped him on the back.
“ouch! what’s wrong?”“ugh! what are you talking about? just get out of here, son! you’re disturbing our cooking.
”“ah, it’s true! it’s a dragon! ouch! ouch!”she didn’t know it was a dragon, but she was thinking of preparing all kinds of food if she was not clear about the right menu.
the kitchen staff was suddenly busy.
***the next day, a ‘nest’ was made for the baby dragon.
 muyon had an “automatic construction” function, so he could build it in one day as long as he had enough gold.
“the auto construction cost a total of 2 million gold,” he said.
“you didn’t spend much.
”“yeah, i think so.
”the nest was located in the west of the world tree, namely in the middle of mt.
 paldal.
muyon thought it would be safer in the mountains than in a place with many buildings.
“moreover, when it grows bigger, it will feel more comfortable to have a nest in the mountains.
”“good idea.
”so, muyon flattened the middle of the hillside and built a circular den on it.

he used concrete mixed with ‘troll’s blood,’ which had the function of recovering some damage by itself.
then, kyongsu came up with several men carrying something on their backs.
“well, i thought you might need something to lay on the floor.
”they were a mattress, a blanket, and a cotton comforter.
“let’s take out the comforter.
 it’s going to break it anyway.
”“got it.
 oh, i brought something like this, too.
”[item information]-name: branch of the world tree-grade: myth-category: manufacturing material-effect: just having it on your body gives you blessings.
 if used as a material, different effects are given depending on the degree of completion.
-description: this is a branch of the world tree that has fallen naturally.
 strong power is still embedded in it.
[item information]-name: blessing flower-grade: legend– category: medicinal herb-effect: when you eat it, your stamina and mana recover rapidly.
 in addition, all regeneration capabilities are improved for ten minutes.
 (50%)kyongsu added, “i’ve brought it because it can have a positive effect on it while it’s growing.
”“that’s a good idea.
 let’s put them together in the den.
”another day passed while they were busy preparing for the baby dragon’s hatching.
it was d-day finally.
 the egg was about to hatch anytime, but sungwoo and other villagers were at the baby dragon’s nest in mt.
 paldal.
“now, it could be dangerous, so except for the essential workers, please get out of the den!”since the birth of the dragon was already the hot topic of the whole town, many villagers wanted to see it for themselves.
 however, it was never a sightseeing event, so kyongsu controlled them.
“can’t we look at it from a distance?”
“do you think this is an attraction? just get out here quietly.
 it’s going to hatch right now.
”the onlookers were kicked out of the den.
meanwhile, sungwoo took out the egg and checked it again.
-the ‘unknown egg’ will hatch soon.
 (00:01:48)less than two minutes were left now.
 in the center of the nest-building, there was a cradle with the branches of the world tree under it, so everyone except sungwoo stepped back.
“it looks like we’re watching somebody taking care of an unexploded bomb…”it was a moment of tension for everybody.
“whew… we’re not making any mistakes now, right? hope an ancient cursed demon is not born.
”“hanho, please don’t talk about anything ominous!”sungwoo took the unknown egg out of his pocket and placed it on the cradle.
wooooooooong-vibration grew so much that sungwoo could see it.
not only the heartbeat but also an unknown force was working.
 there was a big change going on inside the egg.
 it was the force that was pushing the shell away.
‘it’s coming out.
’sungwoo could feel it coming out of the shell.
at that moment, the egg cracked then burst in an instant.
“ouch!”“what the heck is that?”the villagers stepped back further when the egg fragments splattered in all directions.
however, a very small black creature crouched on the branch of the world tree where the egg was placed.
krrrrrrrrrrrrrrrrr-“is that a dragon?”it was the size of a human’s palm.
 aa a baby dragon, it was about the size of a puppy.
upon a close look, it had unique features, namely black scales shimmering like wet pebbles, golden eyes, and a smooth streamlined body.
 it looked like a very well-formed miniature.
then, it slowly spread its toy-like wings and stretched.
“oh oh!”“it’s cute!”the baby dragon’s hatching was different from the general hatching, for it came out after bouncing off the shell surrounding its body like a grenade.
‘what a nasty temper!’sungwoo felt a bit worried, watching its hatching.
the baby dragon looked at sungwoo who was closest to it, blinking its bright yellow eyes.
at that very moment, a message rang.
-a ‘noble creature’ has been born on the korean server.
the same message was displayed throughout the world.
 the birth of the dragon was a shocking event.
but more messages were appearing before sungwoo’s eyes.
-‘black dragon (hatchling)’ learns magic through its owner.
* since it is a race with overwhelming magical talent, it’s most likely to obtain a high grade.
* in addition, it can create more powerful magic through instinctive application.
‘what the heck? can it learn my magic?’can he take it to mean that the baby dragon can become lich someday?sungwoo could not think straight right now, so he just decided to approach the baby dragon first.
the baby dragon showed interest in him.
 it raised its head and stretched its paws as if it wanted him to embrace it, but he did not approach it hastily.
“please bring me something to eat,” sungwoo shouted to the cooks behind him.
eunhee and the cooks brought pre-prepared baby food and laid it behind sungwoo.
it seemed as if they were serving a buffet.
“first, give it a special formula first.
”eunhee recommended the menu confidently.
 so, he served a plate of white soup to the dragon.
 but it flipped his head and struck the plate with his tail.
 eunhee’s special milk powder fell upside down on the floor.


“oh, my god! look!”as expected, it had a pretty nasty temper.
“then how about this?”sungwoo gave the next menu.
 it was a barbecued chicken.
 its lean meat was very soft.
 he would never have recommended it to a human, but this was a baby reptile.
sniffing- sniffing-not surprisingly, the baby dragon pushed his snout as if it liked it.
“uh, is it eating?”hanho’s guess was wrong.
 the baby wasn’t interested in food.
-the dead will be the subordinate spirit of the black dragon (hatchling).
“what?”sungwoo could not believe his eyes.
 he even thought he saw the wrong message.
but at that moment, the barbecued chicken raised itself.
 more precisely, the chicken bones raised themselves after removing its skin.
rattle-“oh my god! what the heck? is this bone resurrection magic?”hanho’s absurd speculation was wrong again.
 it was just a skeleton.
then, the baby dragon flew over the chicken skeleton (?) it just resurrected.
then, it started rubbing its body as if playing.
 it swung its forefoot and chewed the chicken’s wing bones.
rattle-the chicken skeleton escaped from the dragon’s arms as if it was burdened, but the baby dragon chased after it.
perhaps this guy wanted a toy before food.
“…”when everyone couldn’t say anything, stunned, hanho opened his mouth.
“man, this guy acts like his dad.
 how terrible!”a dragon resembling the necromancer was born.


 