\section{chapter 443}

hundreds of ghosts slammed against him, along with 'punishment of evil.
'




tung! tung! tung! tung! tung!the shield seemed to withstand their attack to some extent but eventually flickered and disappeared.
even though gangsok wrapped himself with an electric current, he could not block the 'punishment of evil.
'swash!the demon spirits brushed through him.
 after bouncing back and forth at the impact, he crashed into the hard ground at a distance.
".
.
.
"he didn't scream, but his whole body was in tatters.
 however, thanks to the butterfly's shield, he avoided immediate death.
"whew…"he staggered to adjust his posture.
 colorless blood ran down his face.
 with his eyes trembling, he looked at sungwoo and said calmly, "yeah, i thought you're going to put me in trouble.
 i was wondering if i should have killed you early on.
 in fact, i thought it would be beneficial for you to grow more and handle more troubles, and as expected, you did a very good job because you got rid of the evolution society, the chinese server, the american server, and even the world eater.
" said sungwoo, approaching him.
 but gangsok responded with a smile, "yup, all the things are working as planned.
"".
.
.
"colorless blood ran down his chin, then dropped to the ground.
"necromancer, i'm sorry, but while i'm talking with you like this, my subordinate spirits are attacking the demon race.
 since you followed me faster than i thought, i changed my plan, but it was really successful.
"his blood that dropped on the ground began to wiggle and form a certain shape.
cheeeeeeeeee-then, like an acidic solution, it began to melt the ground, around which a red color began to appear.
 in the colorless world, only his blood regained its original color.
"i will take the last remaining world seed and rule this world.
 you should have taken my side.
 sorry, you didn't.
 they might have liked you a lot…"sungwoo frowned at his words.
'world seed.
.
.
'
this was a quest for gangsok to be the world eater, so it seemed that he was collecting a certain number of 'world seed.
''does he already have the world seed of another world, namely, the world seed of the hall of angels? then the last one.
.
.
.
'updated from lightnovelworld.
comif that's true, the world seed would obviously be somewhere in the main base of the demons.
"necromancer, you did really well.
 you just lacked experience.
"at that moment his red blood drew a huge magic circle.
"unfortunately, this is your last moment.
"sungwoo was not sure what gangsok's first divine power was, but his second one was clear.
 it was the so-called 'demon king.
'it was not a god that existed in the real world, so it was obviously a different creature.
 and that power of his was trying to do something about sungwoo.
the magic circle soared into the air and expanded to a much larger size, then covered the sky.
- 'the demon king's invasion' has begun.
* all 'defense' effects in the area will be weakened.
* the effect of the 'territory' in your area will be nullified.
the demon king in fantasy was expected to wage a war of aggression to dominate the world.
'the power of the demon king' was also designed for aggression to disrupt the world order.
gangsok shouted, "your world no longer exists.
"a crack began from the area where gangsok stood, and sungwoo's territory, namely, the underworld, was broken.
- your 'territory (underworld)' will collapse.
the colorless space gradually peeled off and began to be restored to the real world.
"ugh.
.
.
"
gangsok groaned, grabbing his head.
 red horns were growing on his head.
- the boss monster 'demon king' has appeared.
gangsok was obviously a player, but he was recognized as a monster like the world eater.
"sungwoo!" jisu shouted.
now the underworld has completely disappeared.
but it wasn't over yet.
 although sungwoo couldn't kill gangsok, obviously he inflicted lots of damage on the demon king.
new novel chapters are published on lightnovelworld.
com"catch him!"watching them from the air, the bone dragon nosedived toward gangsok, swinging his front paws towards him.
red lightning bolts shot like a spider's web, striking the dragon's front paws.
 there seemed to be fierce fighting between them for a while, but bone dragon flew back when its front paws were crushed.
in the meantime, sungwoo applied 'evil spirit bombing' to the grim reaper, then charged at his side.
"no!"the fairy butterfly noticed it and reached out her wings towards sungwoo.
a round beam of light shot out.
"uh? where did he go?"sungwoo moved behind gangsok using 'shadow movement,' then fired 'evil spirit bombing' towards him.
but gangsok quickly turned around and raised his left hand to fire a red wave.
 it pushed away the black sphere and changed its trajectory.
thud!the black sphere scattered in all directions and exploded around gangsok.
sungwoo fired the 'winter predator' and moved a large skeleton.
cheeeeeeeee-a beam of light was created between his head and two horns, then radiated out in all directions, melting everything around it.
sungwoo blocked his attack using bone salamander, but he was thrown away by the huge impact.
jisu and the einherjar troops under her control also attacked him but bounced back at the impact of the red wave.
"demon king!"grace shouted somewhere.
 they were captured and surrounded by the special commander unit.
"stop him!""do not come! i will kill the dragon!"even the special commando unit could not block gangsok who was in the condition of the demon king at the moment.
when the red lightning flashed at his gesture, they had no choice but to retreat helplessly.
for more, visit lightnov‌elworld.
com"let me fly to you!"the butterfly flew away quickly, untying grace and vivona.
"grace, untie isabella.
"grace hurried to isabella and checked gleipnir that was binding her body tightly.
but it was not easy to free her from the sturdy rope.
"demon king? i'm sorry! i can't untie this right now.
 i need the ultimate magic to free her from that bondage, so i need some time to prepare.
""then just take her without untying her.
"grace nodded her head and blew the wind with her bare hands, blowing isabella into the air.
wooooong-

meanwhile, the butterfly, scattering golden powder, opened a portal.
"i've opened it, gangsok!"obviously, they were trying to escape.
 just as they were about to disappear beyond the portal, isabella's body, floating in the air by the wind, was dragged away.
"hey! leave that noisy dragon behind!"it was hurst who shouted at her.
 he was holding a remote control, with a mechanical device right next to his feet.
weeeeeeeeeeeeew!that mechanical device swung wildly around the rope, which was attached to the gleipnir that bound isabella's body.
"do you think our best blacksmiths didn't even have a safety hook to prevent your escape?"actually, hearst took additional steps like that while sungwoo went into the underworld with gangsok.
"ugh! how dare you…!"isabella ground her teeth while she was being dragged along by the rope in humiliation.
gangsok turned around frowningly, but sungwoo and jisu stood before him.
gangsok let out a sigh, saying, "i can't help it.
 we have to leave you behind.
"gangsok knew well that the longer he fought, the more dangerous it would be to him.
follow new episodes on the lightnov­elworld.
c­om platform.
isabella was startled by his words.
"no! don't leave me behind!"however, gangsok looked at her blankly for a moment, then turned coldly.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 