\section{chapter 250}

                            after hearing about the current status of the world tree, sungwoo decided to go back to suwon.





“inho, please take care of the situation here.
 i know you have to care about lots of stuff, but you guys are going to be of great help to us.
”“sure, don’t worry.
 let me scrutinize this place and get rid of any remaining monsters.
”sungwoo decided to let inho take control over the evolution society headquarters and left jisu behind as a contingency.
even now there was a possibility that some dangerous test specimens peculiar to the evolution society could pop out.
 so, at least one strong man needed to stay here to prepare for it.
“well, i think i have to leave here as soon as i have arrived here.
 why did i come?”sungwoo decided to take hanho with him this time.
 he needed to be with either hanho or jisu because he didn’t know what the growth of the world tree would bring about.
no matter how reliable the villagers were, they were not as trustworthy as the two in sungwoo’s mind.
“why did you come here? hey, you feel comfortable riding on a helicopter, right? since i gave it to you instead of the bone wyvern you felt uncomfortable about, you have to use it often,” said sungwoo.
“man, you are so mean.
 i wonder how long you can be so mean to me like that…”sungwoo got on the helicopter with hanho.
on the way back to suwon, sungwoo received a message that the ‘2nd korean-japanese war’ was over.
-the korean server has won the final victory in ‘the 2nd korean-japanese battle: bloody war of revenge’!* rewards are given to each player, depending on their contribution to the korean server’s victory.
this victory was possible because kangsok han suddenly appeared and beat the kyushu united army in tsushima while sungwoo and his allies headed to daejon to annihilate the evolution society.
‘is it okay for me to share his credit?’sungwoo thought about it for a moment because he was given the rewards for free this time.
 it was natural that he felt a bit uncomfortable.

-the rewards for the ‘2nd korean-japanese war: bloody war of revenge’ are given.
* contribution: 2nd place* reward: 45,000,000 gold* additional reward: ‘war hero’ title.
-the title of ‘war hero’ is replaced with the title of ‘war hero (level 2)’.
* all stats increase (+3)since the evolution society was also ruled as a “hostile force,” sungwoo received the reward for his considerable contribution, but he was only 2nd place this time.
however, he wasn’t disappointed at the rewards because he could see the positive side, too.
‘well, i can now pay attention to other places instead of going on an expedition to japan.
 japan isn’t the last force that i will have to defeat in the days ahead.
’sungwoo thought of devoting the time he saved to developing the world camp further.
“sungwoo, the chat window is very frantic with people gossiping about the victory in japan.
 do you want to check it?”the chat window on the official channel was still boisterous because the final results of the koran-japanese war were so shocking.
[real time chat]― dinossauro22 (por): there is something we forget.
 thousands of japanese players were killed in just one day.
 and they were killed by only two men!― gold5551 (gha): i’ve been watching the fight all along.
 but only two men played a decisive role.
 i still can’t believe it.
 what happened?― omgplz (usa-1): 7,000 vs 2 wow, so cool!
― ngưỡng mộ (vie): the korean server had a worldview of the dragon ball.
 why does such a strong player, strong enough to destroy the planet, keep appearing?― this is the country of necromancer (kor): lol.
 why is the japanese server keeping silent? where are they?― bigchicken (aus): i don’t think japan will target korea in the future.
 they were defeated so big this time.
―ezezez (usa-1): i forgot.
 these guys are geniuses, the koren players! the world is collapsing, but it’s a game in the end! oh, my god.
 they will conquer the world, i believe.
― amigo41 (bra): what does korea have to do with the game? can they excel beyond others just because of the game system? how can japan, the country of martial arts, japan, collapse so easily?― gungunbang (usa-2): i can’t even understand, but i think i can obey.
 i just hope he isn’t like hitler.
although the battle ended several hours ago, the chat window on the official channel was still flooded with their outbursts of admiration.
 since the performance of the korean server players was so overwhelming, it was natural that those watching their fighting were still reveling in the afterglows of the victory.
– the ‘event broadcasting’ of the official channel is expected to end soon.
 (00:04:59)since the korean-japanese war event ended, there was no reason to air the broadcast anymore.
 accordingly, the first exchanges among countries through the broadcast were cut off.
however, as the viewers scattered to the community of their server and spread the shocking news, the korean-japanese war event was becoming a hot issue everywhere.
in the meantime, those giant forces of each foreign server, who were planning to clear the world quest were forced to reconsider their expedition on the korean peninsula.
to put it simply, they got cold feet because of the korean server’s spectacular performance.
after watching 6,000 japanese troops get killed, they realized that they should not even try to touch the korean server with ordinary forces for now.
 that meant they would organize a large expedition later.
‘we’ll face a bigger war.
’sungwoo thought that he should prepare for such a war.
 so, he had to make the suwon village a key strategic base in the upcoming war.
“we will be arriving in town soon!”the pilot’s voice was heard through the headset.
then, he gave them a briefing.
“the world tree grew so high that we had to move the helicopter landing area in the square.
 so, let me land on a nearby landing place!”sungwoo looked out the window.
 hwaseong palace began to come into his view.
 he saw a huge tree standing tall in the middle of it.
 as he already heard, it was as high as a 20-story apartment building.
‘man, it looks much taller than an apartment building!’although it was as tall as a building, its branches that stretched out to the sky were overwhelmingly long and heavy.
its huge greenery covered all the buildings in the area just like a huge umbrella.
“it’s crazy! it wasn’t that tall a little while ago.
 it looks like a mountain when i look down on it from here!”like hanho exclaimed, the world tree looked like a mountain thick with trees and bushes.
***after getting off the helicopter at the simple landing site, sungwoo went to the world tree with kyongsu who greeted him.
suddenly, not only the plaza but also the entire shopping district was under the shadow of the world tree.
sunlight penetrated through the branches of the tree, creating a mysterious atmosphere.
‘how come it has changed like this overnight?’he felt like he was inside a huge dome stadium.
 the lighting seeping through the branches reminded him of the lights hanging from the ceiling of the stadium.
a group of mountain birds flew up from the center of the branches.
 they flew for a while and finally reached the end of the branches.
 the world tree was the whole world for them.


“i don’t know how big it will grow in the future, but i think we have to make a city plan with the world tree in mind.
”“what’s the problem?”“well, the roots of that monster tree have already filled the square, so we never know when they will affect the surrounding buildings.
 the roots are so strong that they will push away everything around, be they concrete or reinforced steel.
”kyongsu seemed to be worried about the rapid growth of the world tree.
 as he said, it grew so fast and tall.
 so much so that someday it could push out all the nearby facilities.
to make matters worse, all the main facilities of the world tree camp were concentrated near the square.
“didn’t the area of the invisible barrier expand thanks to the growth of the world tree?”when sungwoo asked, kyongsu said, “well, i measured it.
 it extended to about three kilometers from the world tree.
 i could not confirm it with my eyes, but it seemed the barrier was thicker than before.
”“well, if that’s the case, we have to think about developing the area inside the invisible barrier as well as the plaza as much as possible.
”“yes.
”this time, busan was attacked by the japanese server, but suwon, the main base of the world tree camp, would be a target one day.
 so, they had to hasten to fortify it as soon as possible.
“by the way, after kangsok han swept tsushima, he left behind the japanese military items.
 so, i contacted the hwarang guild to collect the items.
”kangsok said on the air he would leave behind the war booty, so sungwoo would gladly accept them.
however, when the quest was over, sungwoo could not use the teleport skill, so he could not go there in person.
 so, he decided to use the “hwarang guild” that he had helped before.
“since we have decided to share the loot with the hwarang guild, i think we have to dispatch some of our members to busan to transport the items.
”if the loot from busan, the loot from the evolution society, and the loot from tsushima island were added, they would provide a tremendous source of growth for the suwon village.
however, kyongsu made a gloomy expression for some reason.


 