\section{chapter 225}

                             




while soaring in the sky aboard bone wyvern, sungwoo had one werewolf skeleton control the ‘fixed turret’.
 there was a target in one corner of mt.
 paldal.
 it was about 900m from the werewolf who was, but as he was looking down from the sky, he had a wider view and more control.
 compared to flying weapons on the ground, this kind of remote control had a huge advantage.
“fire!”the werewolf, acting on sungwoo’s order, pulled the lever of the turret.
tuuung!the thick iron bow moved wildly, shaking th0e turret once.
 even though it fired an iron spear with an overwhelming force, the bone wyvern’s path remained steady despite the reaction force of the turret.
shhhhhhhhhh!the iron spear fired from the sky and landed on the target.
 the dirt around it soared as if it had been struck by a bomb.
 the iron spear, 180cm long, was stuck halfway into the ground.
“jackpot!”“we have succeeded in hitting the target on our first attempt!even if there had been a player or a large monster in place of the dummy target, the iron spear would have killed them on the spot.
“what a great success!”when the bone wyvern landed, the blacksmith team leader approached him with pride.
“i’ll fix the minor problems soon.
 besides, our team is working on ways to enhance the firepower of the large undead.
 if we come up with something good, i’ll let you know right away.
”“good.
 thanks for your hard work.
”as seen in their hard training, the world tree camp was continuously growing in various fields, but they realized that they couldn’t afford to prepare slowly.
-“korea server” in an emergency!
“uh?”“what happened?”while they were kept in the dark about the invasion by the japanese server players, the inevitable war between them and the korean server was around the corner.
[server quest]-title: the 1st korean-japanese war-type: war-purpose: victory-compensation: to be announced laterthe korean and japanese servers have maintained a history of sharp conflict since the days of the “old world.
” and, as expected, their mutual hatred is continuing in the new world.
 can the players on both servers finally fight against each other for the final victory?[information on the 1st korean-japanese war]special rules will be given for their exciting war.
 here are the details:as soon as sungwoo saw the message, he looked at hanho.
“hanho, check the community right now.
”when hanho checked the community, he saw a tremendous number of messages about the terrible news about the japanese server’s attack in busan.
“uh, a few hours ago, somebody launched a terrorist attack against the hwarang guild camp.
 terrorist attack!?”“terror?”“it’s a similar situation to the terrorist attack against yeongdeungpo station in the past.
 man, this was a large-scale attack! it’s the japanese server who was responsible for the attack.
 crazy! i knew the hwarang guild would be attacked!”
earlier than expected, the ‘evolution society’ and the ‘yamato guild’ jointly launched the attack.
the hwarang guild members, who were not only hit but also ambushed by the japanese server, abandoned their main base and retreated, resisting against them in the fortress in the rear.
they were even blocked from retreating by the evolution society, so they were appealing for support from allies through broadcasts and community posts.
“man, this kind of korea-japan quest is so cruel! honestly, this is bad.
”the system issued a quest using the two countries’ deep-rooted hatred toward each other.
 it was evident the creator enjoyed this situation, urging them to wage a greater war.
what’s more, the system was going to broadcast their fight live to the world through the so-called “official channel”, which was very unfamiliar to everybody.
it seemed safe to say that this was related to the world quest issued some time ago.
 in other words, by exposing the current situation of the world tree camp to the world, the system wanted to instigate more active challenges from the players around the world.
[official channel: live] ‘worldwide’ live broadcast of the korean server vs.
 the japanese server.
(7,915,144 watching)naturally, not long after the official channel started broadcasting, a huge number of viewers flocked to the channel.
 it was a worldwide broadcast.
 in other words.
 every server in the world, every player, would flock to watch the korean server that saw the birth of the kor-157 and the world tree camp.
hanho accessed the broadcast.
 then, a message appeared on the tv screen.
-please select the first ‘game item’!*’offensive side-japanese server’ selects first.
it wasn’t just a simple battle.
 the victory of the game was decided under the rules given by the system.
-the japanese server has selected no.
 3 (duel)’ event!* the representatives of both sides must dispatch one ‘great warrior.
’* if you fail to respond, a ‘penalty’ will be given to the server.
* upon victory, a ‘buff’ will be given to the winning server.
first of all, the japanese side, who had the priority on the selection, chose confrontation, namely one-on-one duel.
 the japanese ‘great warrior’ was selected first.
[duel]-japanese server great warrior: yamato’s sword-korea server great warrior: (undecided)the japanese server id “yamato’s sword” was okata akira, aka “sword saint”.
he appeared on the screen of the official channel that hundreds of thousands of people were watching now.
“i am okata akira, honbucho of the yamato guild! open your ears and listen to me, korean server!”in front of the main base of the hwarang guild, akira, a tall man with four swords, shouted at the camera, staring into the camera.
“i’m not interested in small fries.
 i want to confront the leader of the world tree camp! come out here if you want to save the korean server! let me use my sword to prove how incompetent you are.
”with all the players from all over the world watching the live broadcast, he threw down the gauntlet to the necromancer.
[official channel: live] ‘worldwide’ live broadcast of the korean server vs.
 japanese server (13,335,134 watching)the war between korea and japan was taking place while the whole world was watching.
the ‘hwarang guild’ in busan was devastated by the large-scale ambush by the yamato guild following the terrorist attacks of the abyssal breath.
as a result, the remaining players of the hwarang guild were in a very difficult situation, but they had to select one ‘great warrior’ to avoid the penalty.
-10 minutes left until the selection of the ‘duel’ fighter.


* if you fail to respond, a ‘penalty’ will be given to the server.
and finally, someone’s name was on the list.
[duel]-japanese server great warrior: yamato’s sword-korea server great warrior: hyunmin jang* both ‘great warriors’ must move to the designated place (bexco) in one hour.
* once the duel begins, other battles are prohibited.
 (when you violate this rule, you will be declared ‘automatic death’.
)“what the heck? sungwoo, isn’t he the leader of the hwarang guild?”like hanho, who was watching the broadcast, hyunmin, the leader of the hwarang guild, volunteered to confront his japanese counterpart.
currently, he was ranked 9th on the korean server.
 he was ranked 5th in the ‘raid boss monster hunt rankings’ and was responsible for raising the hwarang guild as the strongest force in the southern part of the korean peninsula.
“it seems he wants to beat akira and save his guild,” sungwoo said.
the hwarang guild was now driven into a dead end.
 with their retreat blocked, they could not hold out anymore if their buffs were taken away by their opponents.
so, it seemed that hyunmin, the highest level holder of the hwarang guild, decided to throw down the gauntlet to akira.
he must be stupid enough not to send one of his guild members to confront akira.
an hour later, the two men faced each other in front of bexco, designated as a duel site.
rattle- rattle-hyunmin was a “paladin” armed with dark green plate armor.
 his bodyguards were also fully armed, showing that the hwarang guild was not a force they should make light of on the korean server.


 