\section{chapter 321}

                            they were now on the defensive.
 so, they focused on tackling the source of the problem rather than confronting her.
 in other words, they thought that if they could get rid of the roots surrounding the building by obstructing the king of the great mountain, their troops estimated several thousands could mount an all-out attack.
 “who the hell are you aiming at now?” “you can’t pass here!” the two tigers firmly blocked the exit of the corridor.
 the ninjas charged at them recklessly, but they right away turned into chunks of meat when hit by their sledgehammers.
 “man, they’re easier to handle than boiling potatoes!” “jisu, don’t worry about this place!” instead of caring about the ninjas who were running away behind her back, she kept moving forward, killing a total of ten ninjas.
 at that moment, a message appeared before her eyes.
 -‘wolfberg’ has absorbed enough blood from the enemy.
 you get the ‘song of battlefield’ effect for 5 minutes.






you become immune to all ‘abnormal status,’ so you don’t feel ‘pain’.
 ‘alright.
 i can fight more boldly now,’ jisu murmured.
 she looked down at her sword and checked out the effect again.
 [item information] -name: wolfberg -grade: legend -category: one-handed sword -effect: whenever you cut the enemy, your strength and agility are temporarily increased by (+1).
 (maximum 10) when you reach the maximum, you get the ‘song of battlefield’ effect for five minutes.
 (you become immune to abnormal conditions, so you don’t feel any pain.
) but that wasn’t all.
 -you have been invited to an ‘unknown place’.

in order to accept the invitation, you must meet the ‘special conditions’ first, then open the ‘door of the recognized.
’ ‘unknown place? what the heck is this?’ this was a strange message to her, but it seemed that she received a ‘hidden quest’ when the effect of “song of battlefield” was issued.
 ‘this is not important now.
” she had no time to pay attention to the message.
 “break it!” shouted the enemies.
 suddenly, more enemies came inside the building.
 this time there was a whopping 22.
 jisu charged at them once again.
 “uh?” the enemies momentarily stopped at jisoo’s bold attack.
 and their hesitation led to their death.
 “kheeeeeeeel!” the moment the tip of jisoo’s sword touched the enemy’s neck, the lights of blade energy came out, cutting his neck before hitting the eyes of another enemy right behind him.
 jisu killed the two enemies who were collapsing then got right into the middle of the 20 enemies.
 “what the heck is this?’ “oh my…” the enemies were embarrassed by jisu’s fanatic attack, as it was beyond their understanding.
 their embarrassment clouded their judgment and slowed down their action.
 jisu was again much faster.
 she swung her sword in all directions as if dancing with it in an instant, 14 out of 22 enemies fell after they were beheaded.
 the remaining eight aimed for the king’s life, but they were stopped by the two tigers.
 in no time, the long corridor was filled with the enemy corpses so much that there was no place to put their feet.
 there was a pool of blood under the corpses.
 while adjusting her posture, she felt like she was now standing in a muddy field near a ditch.
 without the disgusting smell of blood, she might have believed that.
 “dispatch team 4!” “just advance without stopping! there are only four enemies!” the enemies kept intruding inside the building.
 with thousands of enemy troops on standby around this building, it was natural that they would stay on the offensive.
 gasp! gasp! jisu was out of breath now.
 she didn’t feel any pain thanks to the effect of the song of the battlefield, but the blood kept coming out from the open wounds all over her body.
 she even felt the fragments stuck into her skin were getting into it more deeply.
 but what she could do right now was to ignore such strange feelings and cut the enemies.
 “that bitch has appeared again!” there were more enemies this time, 26 all told.
 she chose to charge at them again.
 she didn’t want to give them any time to respond calmly.
 “she is coming! get ready!” the enemies shouted.
 however, the moment she took one step forward, she realized that she made the wrong choice.
 ‘there must be something different here.
’ the moment the enemies dispersed to the left and the right, an unknown object lifted its head.
 “ah…” it was a huge cannon.
 it was already ignited, making the powder chamber and barrel glow red, just like the snout of an excited sea crocodile.
 ‘let me shadow step as soon as possible…’ she murmured.
 no enemies were moving at that moment.
 while she paused very briefly, the muzzle opened fire.
 bang! no matter how fast she was, she couldn’t escape the attack of the massive flying weapon that fired hundreds of shots in this narrow corridor.
 sh-sh-sh-sh-sh! hundreds of pieces of iron flew in, slashing the air into pieces.
 no matter where she moved, she couldn’t escape.
 she crouched, but her little body was swept away by the pieces of iron.
 she soared into the air like a kicked doll, thrown into the wall at the end of the corridor.
 “argh…” her vision turned blurry.
 -you got closer to the ‘door of the recognized.
’ 

standing in the ruined busan, sungwoo was staring at the message before his eyes.
 -you can join another battlefield soon.
 (00:00:04) “finally, i can move….
” it was a timer.
 five minutes was very long for him, but finally, the countdown was over.
 -choose the battlefield you want to join.


 