\section{chapter 183}

                            -third option: destroy the statues of the absolute race (2/3)




“necromancer!”while watching, gen.
 chongong shouted, gnashing teeth.
he shouted at the top of his voice, forgetting his honor and dignity.
“why did you come here? what the heck?”and that’s why all the players had no choice but to tune into necromancer’s broadcast.
the shadows the necromancer brought covered the strange land.
the expression, a “dramatic moment,” was reserved for this moment.
“necromancer!”the necromancer, the enemy of the china-2 server, appeared in taiwan.
he appeared while gen.
 chongong was delivering the keynote speech in which he announced he would kill the necromancer and occupy the korean server.
“man, what the hell are those monsters…?”gen.
 chongong could not figure out the identity of the troops sungwoo brought.
 there were monsters made of bones with huge wings everywhere.
 they weren’t one or two.
 dozens of wyverns filled the sky of taiwan.
wherever gen.
 chongong looked in the northern sky, their huge wings covered the sky, and their flapping wings caused a gust of wind.
whoowoong―so, gen.
 chongong got confused as if a typhoon landed in taiwan with huge dark clouds.
“are you sure that’s the necromancer?”“yeah, that’s a devil.
 devil!”the players of the red revolutionary army were taught about their persistent bad ties with the korean server.
 they were brainwashed that they must destroy the korean server someday as part of their efforts to regain the chinese server.
however, they realized the necromancer they encountered now was never the object of conquest.
 they felt like the necromancer was something they had to avoid by all means.
“everybody, get ready for the fight!”
“everyone, prepare for his attack!”meanwhile, the korean server, the taiwanese server, and the chinese server,were watching the scene, as well as the broadcasting agencies and communities in the three regions began to make a big fuss over the fighting.
a situation nobody expected unfolded, and nobody could predict what would happen in the future.
riding on the back of bone wyvern alpha male, sungwoo looked down at the square.
tens of thousands of players were crowded in front of the square.
 on the red podium at the very end, he could see the main figures including gen.
chongong seated.
‘that guy must be gen.
 chongong.
’the man dressed in red, gen.
 chongong, caught his eye.
 he was looking up at sungwoo with an embarrassed and angry expression.
“sungwoo, there are a lot of snipers on the roof of the building.
 i can feel a lot of troops moving around the square.
”jisun, who was riding on a different wyvern right behind sungwoo, briefed him about the situation.
 as she said, there was tight security in and around the square.
although gen.
 chongong and his subordinates didn’t expect sungwoo would make a surprise attack by using the ‘angel’s wing fragment’, they were thoroughly prepared for the contingent situation because they were holding a very important event.
furthermore, almost all of the troops under gen.
 chongong were gathered in one place for the parade.
 they were so large in number that it was difficult to count them accurately.
as a result, it would never be an easy fight.
‘by the way, not everyone who participated in the parade is my enemy.
’this was taiwan.
 so, many of them might have been forced to attend the parade after taiwan had been conquered by the pirates.
however, there was no way for sungwoo to distinguish them.
 besides, if he paid attention to that, he would not be able to wage the battle efficiently.
‘i can’t hesitate to attack gen.
 chongong and his forces because of that.
’he needed to be more aggressive in his approach.
“let us get rid of the snipers first,” sungwoo said.
there was snipers’ busy movement on the rooftop of the surrounding building.
so, sungwoo had to kill the snipers first.
 if they were allowed to move around freely, it was inevitable that sungwoo and his party’s actions would be limited.

“jisu, please proceed with the second operation.
”“okay.
”nodding at him, she flew away in the opposite direction from sungwoo.
she had work to do there.
“wipe them out,” sungwoo shouted.
he dispatched 33 bone wyverns and 9 zombie monster birds.
they folded their wings and started to descend ferociously.
 they moved as fast as a bullet.
“uh? they are flying toward us!”“damn it! everybody, run away!”the snipers on the rooftop could not help but be embarrassed.
 they weren’t preparing for aircraft fire, but they were monitoring the security around the square.
therefore, they were helplessly exposed to the wyverns’ attack.
“ahhhhhh!”a bone wyvern lifted his claws and made a dent on the rooftop.
 although the wyvern passed over it only once, there was a long cut on the rooftop, and all the snipers fell over the railings.
in the meantime, zombie monster birds flew here and there in groups, leaving deadly scars on the heads, faces, and necks of the snipers with their beaks and claws.
“argh! take them off me!”“kuuuuuuuuuuh…”only their tattered corpses were left behind in the place where the zombie monster birds passed and wiped them out like a swarm of locusts.
[synergy list]3) aerial advantage (2nd stage)-category: trait synergy-condition: 40 or more flying traits-effect: flying speed increases (30%), descending speed increases (20%), probability of woe attack avoidance increases (20%)because of this synergy effect of “aerial advantage (2nd stage),” they could even focus accurately on their targets.
“i can’t aim at them because they are flying so fast!”even if they managed to aim at the wyverns and monster birds, they could not get them with just one attack.
 even if they succeeded in destroying the wyverns and monster birds, that was not the end because they would be revived.
“we have to get off of the rooftop right now!”“get out of here!”in the end, they couldn’t stop the wyverns’ relentless attack.
“ahhhhhh! we’re too late! lie down!”“argh!”the snipers resisted by counterattacking as best as they could, but they could not avoid the fate of being killed and absorbed by sungwoo as souls.
-you have exploited a soul.
 (37 items)sungwoo used the human beast (werewolf) ampoule early to gain the power of anubis.
he spent the acquired souls and invested them in strengthening the undead.
-you have strengthened the undead using exploited souls.
 (3 stacks)1) attack power increases by 10%2) defense increases by 10%3) immunity to magic increases by 10%the more the battle continued, the stronger sungwoo’s subordinate spirits would be.
the given time was only one hour, but it was certain that quite a few of gen.
 chongong’s men would be killed in one hour.
in an instant, all the rooftops around the area were destroyed, and the snipers there were annihilated.


“now, we are storming into the center,” sungwoo said.
sungwoo was watching what’s going on from bone wyvern alpha male in the sky.
those who gathered in the square were running away from the square in a disorganized manner.
 after the players who had nothing to do with the pirates left the place hurriedly, those who were left behind were the real target of sungwoo’s attack.
“okay, wipe them out!”bone wyverns grabbed the debris of the rooftop.
 they grabbed a mass of concrete, rebar, and even the bodies of the pirates with both feet, then glided towards the parade to throw them over their heads.
“ahhhhhhhhhh!”“everybody, lie down!”the square was vast, but there were too many people crowded there.
 since the square was crammed full of people, there was no space for them to move around, so they could not avoid the stones raining down on their heads.
-you have earned 8,000 gold by killing a player.
-you have earned 11,000 gold by killing a player.
-you have earned 12,000 gold by killing a player.
with the concrete fragments pouring on their heads like hail, they were not armed with any weapons because they attended the parade, so they could not avoid the monsters’ attack.
“argh!”“lift your shields! protect your head!”moreover, the bodies strewn everywhere heralded the beginning of their secondary damages.
“explode!”the security guards came running and lifted their shields to protect themselves from the falling stones, but they could not pay attention to the corpses of their colleagues scattered under their feet.
 while they were raising their heads, their corpses swelled.
bang! bang!with the explosions everywhere, the bodies of the pirates were ripped and bounced off in all directions.
 since they were gathered in one place, the explosions caused more damage to them.
“damn it! get ready for the counterattack according to our operation!”“respond to the aerial attack!”

 