\section{chapter 196}

                             




gu gu gu gu―“uh, uh! suddenly, there is an earthquake…”the ground shook with vibrations, and the birds soared, while sand exploded from the center of the black forest.
 and a huge rock mountain suddenly arose from within.
gugung―after the vibrations stopped, gray fog rose around it.
“oh my god, that’s the python’s cave! it seems that’s where the boss is located!” said reporter ahn.
huge caves were seen all over the surface of the rock mountain.
there were entrances into the rock mountain.
“34 hours from now, three camps will participate in this quest and compete with us! which side will win?”since he was the most famous camera operator, he proceeded skillfully despite the bizarre phenomenon.
“don’t you think the winner is the angel camp with the largest force crusader team? or the necromancer’s camp that has always been showing overwhelming power? if they are the winner, then…”the camera operator swallowed once then opened his mouth again.
“is it possible for the demon camp to reassert themselves after they suffered a crushing defeat? please stay tuned.
 i’ll continue to deliver news from here on mt.
 pukhan.
”as the scenes of mt.
 pukhan being transformed into a dungeon were revealed, people were getting more and more interested in the three-way competition among the three camps.
the community posted a series of posts and comments predicting the outcome of the fight.
 in addition, the noisy and confusing situation continued as posts calling for the participation of each camp were mixed up with other posts.
meanwhile, the liberation guild gathered all the allies to strengthen their power.

however, junghoon thought that it was not enough, so he reinforced items by collecting almost all the funds available.
 nonetheless, he couldn’t get rid of his anxiety.
there was only one reason for his anxiety.
“damn it! after all, do i have no choice but to fight sungwoo?”“well, you would not have avoided it anyway,” said his deputy.
there was a high possibility that the crusaders would have to fight the necromancer’s third camp.
“our team members are also anxious.
”“of course they are.
 i’m nervous, too.
”the crusader team, including junghoon, felt a different pressure from fighting against the reconstruction alliance.
the third camp was included in the participation list.
 as far as they knew, the necromancer would grab the opportunity to participate in the quest by all means.
“but i never think of losing at all.
 the demon camp has virtually lost its power, so let’s focus our firepower on the necromancer and sungwoo.
 we can make it.
”“got it.
 i’ll think about the best way to confront sungwoo’s undead army.
”they prepared their best strategy, so much so that their fighting moral knew no limits.
[601] liberation guild, it looks like they were determined to fight it out this time.
-author: lkk │ hit: 15,562i’m a player living in youngdungpo.
 i saw the liberation guild participating in the war.
 they were really powerful, mobilizing five helicopters.
i wonder if they can defeat the necromancer.
 i saw the crusaders fighting in the battle of kwangwoon university.
 they were terrific!
[comments: 13]- ko go-hyuk: i’ve just imagined them beating the necromancer! no way! that’s impossible!- yasuo 1: lol.
 i agree.
- jinyong 2: honestly, i don’t think it’s possible realistically.
- strong willpower: i think they can win.
 i support the liberation guild and the angel camp!pc room survivor: the crusader team and the necromancer have never fought, so nobody knows the outcomes if they engage in a fight.
 the crusaders’ defense and breakthrough power is much stronger than the necromancer.
most of those debating in the community focused on the confrontation between the angel camp and the necromancer, so the demon camp was not the subject of their interest.
it’s because the demon camp lost lots of troops after they were severely defeated.
but the situation got more complicated.
-[live] the ‘struggle guild’ in kangwon province declares their support for the demon camp (12,454 watching)a powerful reinforcement army began to join hands with the demon camp.
a muscular, middle-aged man with a battle-ax stood in front of the camera.
“we, the 245 members including master bumyol of our “struggle guild,” declare that we will participate in this competition.
”it was an organization called the ‘struggle guild’ that was newly emerging in the kangwon province.
they recently unearthed a devil’s stone statue, so they belonged to the demon camp.
 after they declared their participation in the “fight for the control of the metropolitan area (2),” they represented one of the strong forces of the korean server.
“we will cooperate with the reconstruction alliance in uijongbu area to lead the demo camp to victory.
 as players in kangwon province know, we are the warriors who survived the hell of mt.
 taebaek.
”they didn’t exaggerate their confidence.
 the reason they did not appear until now was that the level of the difficulty of the local quest was considerably high.
by hook or by crook, the assassins killed the boss monsters, but the monsters who lost their leader hid in the mountains and formed a new force.
“we have been fighting without a break until now.
”as a result, the ‘hidden quest’ unique to mt.
 taebaek was triggered, reinforcing the monsters there.
like the bandits, the herd of monsters plundered the player’s village, then repeatedly ran away to the mountain.
 however, the struggle guild members couldn’t attempt to crack down on the monsters recklessly because countless players were annihilated after they went into the deep mountain to go after the monsters.
“but finally we have won!”the group that ended up defeating those hellish monsters was none other than bumyeol’s “struggle guild.
” although their members were not ranked high in the korean server rankings, each of them boasted an excellent level and combat power.
“but we won’t take a break.
 we’ll move to the new battlefield and win again.
”with the addition of the struggle guild, the demon camp, widely regarded as the weakest force, was not to be taken lightly, which made the situation more unpredictable.
and there was an event that made this situation even more violent.
[fight for the control of the metropolitan area (2)-predicting winner (betting)]* when betting, you will receive a “bet token” item.
* the winning camp receives 1% of the ‘total bet amount’ as the prize money.
* dividends based on the dividend rate are paid when you accurately predict the winner (excluding 1% of the winning camp’s prize money)the event where they could predict the winning team among the three camps and bet gold formally began.
 simply put, a gambling place was opened for them.
and it started to be called “dungeon toto,” causing a tremendous repercussion because they could make lots of money instead of standing as bystanders.


it was good enough to draw even those independent players who had remained passive bystanders until now into the indirect competition.
meanwhile, among the parties to the betting, there was someone who was attracted to it.
“give 1% of the bet amount?” sungwoo asked.
take 1% off the total bet? in sungwoo’s eyes, it only seemed that the system allowed the participants to make money.
 and that wasn’t the only way to make money.
“well, if that’s the case, i think i should pretend to be weak.
”if anybody bets on one of the three teams that are predicted to be less likely to win, they can get a windfall if their prediction is correct.
 if the third camp wins with the fewest bets, the person who bets on the third camp will hit the jackpot.
however, hanho was not persuaded after hearing sungwoo’s explanation.
“pardon? do people think we’re losing? as you know, we have fought everywhere and won.
”as hanho said, people watched the necromancer fighting brilliantly beyond their imagination.
so, few could predict openly that the necromancer will lose.
so much so that few would believe he would lose, no matter how often they heard about it.
“let me make them anxious.
”but as long as they bet money, it was supposed to change their mindset.
 people hesitate to bet when rumors spread that even the horse with the best odds of winning in horse racing is in bad condition.
 why? because they fear they might lose money.
that was the power of tabloid papers.
“let me feign illness, so i can look weak.
”sungwoo decided to be an underdog.


 