\section{chapter 335}

chapter 335: post-war recovery and second system error (7)li wei pushed the little statue onto the table.
 the object finally came into sungwoo’s hand.
 -you have acquired the item ‘the devil’s statue (token of blessing)’ of the hostile camp.





this is a special reward given only to the ‘high officer’ of the demon camp.
 if you take it to the ‘symbol (world tree)’ of your camp, you can exchange it for a ‘camp item.
’ ‘alright.
 all you have to do is just take it to the world tree.
’ sungwoo looked at li wei while picking up the token of blessing.
 “by the way, how did you come into contact with that unknown being you called a damned god?” the only way for sungwoo to get in contact with a helper was for the helper to come to see him voluntarily, so he asked her if there was any other way.
 “well, i think you know that.
 you have experienced a system error, right? when series of error messages come out.
 you know it, right?” sungwoo nodded.
 “after losing the battle with the emperor, i summoned the “spirit king” to escape, but at that moment the system error occurred.
” “spirit king?” “ah, the spirit king is the strongest spirit that a sorcerer like me can summon in a very special way.
 anyway, when i fused with him, he told me to seek you if i wanted to beat the emperor.
” in the end, the helper came to see me directly.
 “but the spirit king told me i should bring the gift with me by all means.
 so, while i was running, i turned around and snuck into general xing’s residence” she leaned against her chair and let out a sigh.
 “gosh, i almost died at that time.
 i was on the run after being almost killed by him, but i found myself going back into the enemy camp and barely escaped them.
 looking back, my try was worth it.
” sungwoo stood up without responding because he didn’t know anything yet.
 for now, all he could do was just do whatever the unidentified help wished of the big picture.
sungwoo brought two stone statues to the world tree.
 then, a message appeared before his eyes.
 -you can select ‘reward (camp items)’ by consuming the ‘loot’ you have obtained from the hostile camp.

.
 mark of the priest.
 mark of the high warlord
.
 mark of the judge it looked like they could get the items necessary to run their camps.
 no.
 3 option among them caught his eye.
 “is this what you can get?” some time ago, the item he obtained by capturing the angel judge, namely the judge’s mark, was one of some unknown ‘conditions’ that were strange to him.
 anyway, he chose no.
 3 without any hesitation.
 oooh- at that moment, the two statues lost their shape and merged into a single ray of light.
 then, it was molded into a different shape and landed on his palm.
 [item information] -name: judge’s mark -grade: special -category: camp item -effect: a person who has this mark can designate a member of his own camp as a ‘subject of judgment.
’ (you can track down his location, and all stats are temporarily reduced by 90%.
) -description: you can achieve this power with the special achievement of your camp.
 with this power, you can play an excellent role in maintaining the discipline and security of your camp.
 ‘i’ve met all the conditions with this.
’ soon, a message rang.
 -special conditions have been satisfied.
lich (the one dealing with death) + bi hyung’s fan (the one who controls ghosts) + judge’s mark (the one who enforces the law) -you can get a new deity status, ‘king of death.
’ ‘king of death’? it’s a deity that deals with death.
 can i have two?’ the power of anubis raised sungwoo’s power tremendously.
 if a new deity was added on top of it, he would be able to exert synergies beyond imagination beyond simply doubling his power.
 but there was a problem.
caution! since your level is not high enough, you can’t have two deity status right now.
 you have to give up one of them.
to have multiple deity status, you must be at least level 25.
 “man, this is really frustrating…” currently, sungwoo is level 23.
 in order to possess two diety statuses, he had to raise two more levels, but he was not sure how long it would take him.
 ‘i can’t raise my level unless i fight another war.
’ he could not go on a hunt because he had to prepare for war.
 while he was agonizing over the best course of action, somebody shouted behind him.
 “sungwoo, the white wolf has arrived!” after all, this was not the time to go out hunting.
 his priority was to break the emperor’s psychometry and peek into general xing’s memory.


the white wolf was building a village for human beasts in the chungnam region, but he came running to sungwoo when the latter asked for his cooperation.
 it was already the second time he came to sungwoo’s response.
 since he owed a great deal to the necromancer, he had no choice but to maintain a cooperative relationship with the latter.
 “well, what you mean is that there’s a psychometric spell in the general’s body, right?” the white wolf frowned at sungwoo’s explanation.
 he put his hand on the general’s skeleton and nodded.
 “you’re right.
 i can feel it.
 it is certainly controlled by the emperor’s psychometric power.
” “can you break that?” “well…” he couldn’t answer right away.
 “the confrontation between people with psychometry is based on the mind, not the body.
 if something goes wrong, my mind could be destroyed, and i could die.
 well, it’s very likely.
” “if you have a high chance of dying, does it mean that there is an opposite possibility?’ sungwoo intended to peek into the general’s memories.
 the white wolf nodded with a sigh.
 “this is a very extreme way.
 you need to get into his memory first and draw his attention.
” he lifted his index finger and touched the skeleton’s head.
 “his brain is like his mental world right now.
 so if you disturb him so much as to distract his mind, i can find a chance to penetrate his mind.
” “then, how can i draw his attention?” the white wolf grabbed and shook the skeleton’s skull.
 “just disturb him.
 all you have to do is make him focus on something else, so he doesn’t know somebody is penetrating his mind.
 to put it simply, make him pissed off!” sungwoo nodded and said, “i know what you mean.
 let me try it.
” the white wolf gazed at sungwoo.
 his expression was full of concern.
 “keep in mind.
 if the general notices it, this fight won’t happen.
 the mind is different from the body, so it will be expunged with just a little shock.
 i really hope you won’t kill me.
” sungwoo nodded and put his hand on the skeleton’s shoulder.
 although the white wolf’s life was at stake, sungwoo had no time to think about it carefully.
 -you can read the ‘memory fragments’ of the deceased.
 and once again he went into the general’s memory.
 this time, again, the same place appeared.
 he saw a room with a hearth, a table, and a man with a mustache.
 “what else?” the mustached man frowned on sungwoo, looking at him.
 obviously, he didn’t like sungwoo’s unexpected visit.
 “oh, you decided to come back with some sort of wishful thinking? don’t waste your breath! the general’s memory is connected with me.
 that means i can control it anytime, anywhere.
” “i know,” sungwoo said, nodding.
 then, he looked around.
 “ah, did you come back to accept my offer? uh?” he stuck his head toward sungwoo with a smile.
 it seemed like he was going to give sungwoo a lecture again.
 “when you went back and thought about it, you couldn’t sleep with fear, right? so, you broke my stubbornness and wanted to pledge loyalty to our emperor…” “shut up!”

 