\section{chapter 229}

                             




“now is the time!”sungwoo sent bone imoogi to disrupt the formation of the japanese troops and break them into two groups.
 as he intended, the japanese troops were split into two groups, with the bone imoogi straddling them in the middle.
however, the japanese troops had no time to notice such an attack and prepare for it because there was a huge shadow cast over them.
“watch your head above!”“aerial alert!”bone wyverns flew in at once and began to throw huge rocks toward the japanese soldiers who were on the upper side of the bone imoogi.
“shield!”puck! puck!the flying rocks were threatening, but they blocked it by spreading a large-scale shield.
 that was not sungwoo’s intention.
‘manufacture golem!’the rocks thrown by bone wyverns crushed the asphalt roads, causing the soil hidden underneath it to come out.
sungwoo used the skill of golem manufacture (skilled).
-you have summoned a golem (mud).
-you have summoned a golem (mud).
two squishy mud creatures rose among the japanese soldiers.
 they were massive monsters, as high as ten meters and weighing several tons.
“golem!”golems weren’t easy to deal with.
 swords or spears could not damage their sticky mud body and their composition canceled 80% of magic damage.
as a result, they could inflict huge damages on the japanese soldiers.
“what the heck are they doing now?”but the golems didn’t seem to be interested in them.
 they just went downhill and got stuck on the bone imoogi that broke the formation of the japanese soldiers.
they just squashed their arms, legs, and body between the bones of the giant snake then stayed still.
“shit, what the hell these monsters are doing…?”
the japanese soldiers didn’t know anything about this kind of strange action by the necromancer’s undead, but they felt an ominous feeling.
in the meantime, it continued to rain.
 as time passed, more and more rain poured out from the purple dark clouds in the sky.
“uh!”only then did they begin to notice the poison water flowing was rising around their feet.
“rainwater is collecting!”“toxic rainwater is rising on the ground.
 watch your feet!”when they lowered their heads, they found the poison water was flowing like a stream.
ramps in busan were notorious for being steep.
 the pouring rainwater was supposed to flow along the asphalt into the lowlands.
but now, the middle of the ramps was blocked by the bone imoogi and mud golems like an embankment.
 to make matters worse, the unmaintained sewerage system had long lost its function, so the rainwater on the roads didn’t drain quickly.
eventually, the rainwater began to rise slowly under the japanese soldiers’ feet.
“ahhhhhh! my feet hurt!”“poison is seeping into my feet! give me an antidote….
”poisoned by the rising water, japanese soldiers screamed in pain.
 they were wearing heavy and thick plastic raincoats to avoid the poison, but they could not do anything about the poison coming up from below.
“our advance party has been isolated! we have to break through.
 everyone, prepare explosion magic!”“oh no! watch out the wall!those in the rear tried to break through the bodies of the bone imoogi and mud golems, but they were stopped from doing anything by the ghouls and giant jannabi skeletons hanging on the walls.
sungwoo was now ready to deal a fatal blow.
“now is the right time.
 block the alley!”sungwoo gave the direction to someone through the radio item.
 then, some of the bone wyverns in the rear began to move.
 there were six wizard players behind them.
“freeze them!”“ice wall!”they were freeze series wizards.
 the moment bone wyverns flew low, they used magic to freeze the edges of the two-lane road and the entrance to the alley.

in other words, they completely sealed off the gap through which the rainwater could drain.
have you ever seen how fast water rises in a steep valley? rising water always sweeps, swallows, and collapses everything beyond people’s imagination.
kwaguaguagua!while the rainwater filled with strong poison streamed down the hill, it began to rise at a tremendous rate.
 when the poisoned rainwater rose above their ankles, all the japanese troops isolated in front were poisoned.
“oh, my god… i can’t move…”exposed to the poison like that, they could hardly fight, and their strategy of being united to cope with the monsters also collapsed.
– caution! ‘death response’ begins in that area.
wuuuuuuuuuuh!to make matters worse, a horde of zombies popped out among them.
“ahhhhhh!”“what? what? damn it!”twenty-five zombies jumped out of the water, grabbed the legs and arms of the japanese soldiers like water ghosts, and dragged them into the water.
they fought against each other in the rising poisonous water, but a large number of japanese soldiers drank the poison through their noses.
“kuheeeeeeeee!”“argh!”on the rooftop where flying weapons were installed, the players of the world tree camp were watching the scene closely, waiting for sungwoo’s order.
“yes, it’s good that these japs, intruders of korea dating back to ancient times, get to taste the water here.
”sungwoo ordered, “now is the time! fire!”“understood! break down the embankment with the iron maces of lightning!”the iron maces of lightning, fully loaded, aiming at the japanese soldiers, emitted a blue flash.
the huge magic bullet hit the dam and the imoogi’s waist and the mud golems, which had been blocking the rainwater coming down to the downhill, were blown away, opening the waterway for the raging current.
kwaguaguagua!a tremendous roar began to sweep downhill with the water.
many japanese troops, who had already noticed the operation, were hiding in the alley, but those isolated at the forefront were dragged down the waterway and met their last moments.
“wow, look at the strong current of the water!”but unfortunately, their fighting was over at that point.
-stop free battle!the two-hour free battle’ has ended, and the time for event selection has finally come.
-select the second ‘battle event’!* ‘defender-it’s the korea server’s turn to select.
* time remaining until selection (00:04:59)now, it was time for the korean server to select.
-the ‘captain’ of the defender (korean server) has been changed.
* new captain: kor-157the hwarang guild, whose leader was the captain of the first event, handed over their authority to sungwoo.
 since they could not continue to fight any longer, it was natural they let sungwoo take over the leadership.
the japanese server’s swordmaster, akira, appeared again.
“hey! necromancer!”the drone of the official channel began to move at his thunderous shouting that resonated across the battlefield.
 the drone lit his face because his provocation would certainly draw the interest of the viewers as much as it could.
“i believe you have come out at my request, so let me…”akira drew a sword and shouted, “let’s have a duel! so, choose duel!”he urged the necromancer to have a duel with him by choosing the event option duel.
“prove your abilities and your identity to the world!”as soon as he finished talking, a shadow was cast over his head.
 bone wyvern alpha male approached him.
 looking down on him, sungwoo scorned him.
“duel?”

“yes.
”sungwoo stretched out his index finger and chose one item.
-the korean server has selected ‘no.
 1 event, all-out war!* the battle zone is limited after one minute!* every 10 minutes, the battle zone will be reduced!* the all-out war ends in 60 minutes.
sungwoo didn’t accept akira’s request.
akira’s face looked gloomy at that message.
“what the heck! damn it! necromancer! come down right away and fight me! are you scared of me?”no matter how desperately akira shouted at him, sungwoo raised one of his fingers with a relaxed expression.
“there is only one thing i can prove.
”the black scythe he was holding had a black wave at that moment.
 it was the evil spirit bombing.
“my point is if you enter this land recklessly, you can’t survive.
”having said that, sungwoo swung the grim reaper towards akira’s head.
 black souls shot out in a straight line, covering his body.
gu-gu-gu-gu-gung-the soul swelled, spreading its black wave then crushed everything around him.
akira disappeared from the screen of the official channel, with only sungwoo left behind.
“now, let’s continue with what i have just started.
”-the battle zone has been set.
 (total of 3,000m²)soon, a red dome was placed over the heads of the two camps.
a stadium where they could not escape was prepared.
-the battle zone will be reduced in 10 minutes.
 (-500m²)the battle was destined to be a little stickier.


 