\section{chapter 395}

chapter 395: full control over death (4)[live chat]




― k.
j.
y: as expected, he is the best! i’ve trusted him from the beginning!― dongsook ahn: wow! jackpot!― gwanghwamoon bear: wow, he is terrific! what a relief he is our ally, not the enemy!― bing: by the way, reporter ahn, it seems that your famous guest was speechless as if he was shocked???― mr.
 bongdam jeon: after all, china tried to defeat the necromancer’s army with massive troops in vain.
the chat window was heated with the viewers’ admiration and sarcasm.
“well, at this point, i would like to evaluate the situation.
 since we don’t know how the necromancer would shock us, we need to calm down a bit for the sake of our mental health.
”reporter ahn smiled and turned his head to the seat next to him.
“now, mr.
 wong?”wong’s face was already blushing with embarrassment.
“mr.
 wong? can you give us your feedback on the just-ended war?”“well…”“i think, as you said, the emperor of the chinese server did a lot of research to fight the necromancer and prepared a lot of hidden cards, but it turned out that he didn’t fully understand the necromancer yet.
 do you agree?”“oh, i think…”with a bit of hesitation, wong looked at the chat window.
 of course, the chat window was overflowing with viewers’ feedback ridiculing him.
then, reporter ahn stepped in and began to serve as a moderator between them.

“come on, everyone, please calm down! it’s possible that you don’t know everything.
 you know what? we, humans, tend to exaggerate to avoid being treated like an idiot for our defeat.
 for example, even if we fall in a local stream and struggle to get out of there, we feel as if we’ve survived the rapids of the valley!”“…”“i think mr.
 wong is in a similar situation.
 well, it can happen to you! now, mr.
 wong, don’t worry and just say your opinion.
”reporter ahn put his hand on his shoulder to comfort him, but he was already out of sorts and depressed.
“well, let me give you my commentary again… uh?”at that moment, the screen of the official channel showed some other things.
“…”this time, it was the main base of the world tree camp.
“what the hell is going on now?”the invisible barrier broke down during that short moment.
***there are countless items in this game, and even new ones are made by the players.
as a result, the players often used extraordinary items to catch the opponent off guard.
in that respect, the technology of producing items with useful functions based on special materials, so-called ‘magical engineering’, was establishing itself as a more important industry than anything else.
on the other hand, the large-scale battle near the castle wall was nothing more than a head-to-head battle between the magical engineering skills of the opposing sides.
“there is not enough mana supply! connect a new mana tank to the ‘veil shredder’!”
the flying weapon item called the ‘veil shredder’ was one of the hidden cards of the chinese army.
 the gigantic tank, rolling on a caterpillar orbit, fired orange rays from its long cylindrical muzzle, breaking through the invisible barrier like an oxygen cutter.
jeeeeeeeeeeeee!the equipment was equipped with a ‘mana backflow’ function, which was effective in breaking down the invisible barrier.
 in other words, it was much more effective than just attacking the barrier with hundreds of flying weapons.
in the meantime, the world tree camp deployed 7 airships near the invisible barrier to prevent the enemy’s surprise attack.
 they carried out air bombardment using ‘airships’ and ‘iron cannons’, the products of magical engineering, but they didn’t bring about intended results.
“deploy the shield!”as a matter of fact, the chinese army was already prepared for it because they had predicted such an attack for a long time.
a whopping four layers of the shield were spread over the veil shredder for a thorough defense.
however, it was not an ordinary large-scale shield.
 in the first place, a large-scale shield deployed by a dozen wizards could not withstand the fleet’s ruthless shelling.
“consumed mana completely! replace the shield battery!”then, the warrior-type guys jumped in with huge green barrels and connected them to a circular device that looked like a radar.
 the green barrel, which was veiled until now, squeezed mana from the captured wizards and condensed them in a physical barrel as if they were raising the wizards.
 in other words, it was a kind of mana battery.
“charging complete!”in this case, they could avoid the cumbersome procedure that had to be supplied by many wizards on the spot.
 besides, the mana that was forcibly extracted and refined was of much better quality.
“as expected, the ‘kuyaja’ item is reliable! keep going!”while the korean server boasted of the world tree and the ‘hearst workshop’ sent by the us server, the chinese server had its own counterpart ‘kuyaja facility.
’the kuyaja facility was an institution under the direct control of the emperor that produced various magical engineering weapons for the chinese server, such as making ‘white sacred sphere’ by grinding 3,333 priests into it.
clang! clang!with two explosive sounds, some parts of the invisible barrier of the world tree camp were broken like a window.
“we made it! we broke the barrier!”with a large crack in the invisible barrier, a passageway through which a large number of troops could enter was created.
 soon, the chinese army’s “spear unit’ began to advance.
“everybody, advance!”the steel golems marched forward first.
 they, too, had shield generators attached to their bodies and lifted the gigantic flying weapons as if they were personal firearms while withstanding the bombardment.
tuuuuuung! tunnnnnng!an iron spear with lightning magic flew toward the lower deck of the airship.
tung! tung! tung!of course, the airship was also protected by a solid shield, so it was not shot down at once.
“sh*t!”nonetheless, the hit airship was in a big chaos.
 they were now in the worst situation because the invisible barrier was broken through so quickly.
“all fleets, get ready for fire!”the 7 airships that had been forward deployed heated their barrels by supplying mana to all cannons, then fired all at once.
bang! bang! bang!dozens of cannons devastated the area near the invisible barrier.
the bombardment was so powerful that all the buildings in the area collapsed and the roads were destroyed, but the chinese army’s advance team, armed with magic engineering, advanced without caring at all.


thump- thump- thump- thump-27 steel golems, who already penetrated the invisible barrier, were installing large flying weapons to shoot down the airships.
“captain! we can’t stay in this place for long!”inho, who took command of the fleet, nodded.
“retreat while monitoring the enemy’s movement!”eventually, the world tree fleet began to retreat slowly.
 it was best for them to have the final battle with the chinese army at the castle wall.
at that moment, somebody shouted, “a huge enemy army is now infiltrating into the invisible barrier! they are so fast!”when the observation crew shouted, inho turned his head to the barrier.
 numerous horses raced through the hole in the invisible barrier.
 they were cavalry made up of about a thousand horses.
“we’re flying!”after passing through the hole, they began to soar into the air.
no matter how closely they watched, they could find no wings.
 as if there was an invisible path in the air, they charged at the airships by rolling their feet.
“they are mongolians!”they were the top guy of the mongolian server and his cavalry ‘keshig.
’ as expected, they were coming in droves to attack the combined allies’ fleet.
“they can ignore our shields.
 in that case, the whole ship will be defenseless! retreat at full speed!”with the engine pulling out its maximum power, the whole ship shook.
“the enemy is approaching us too fast!

 