\section{chapter 389}

chapter 389: war for war (6)at that time sungwoo was checking all the weapons and tested each of them to see if they were functioning properly.





“all good.
”he found no malfunctioning weapon.
after 12 hours passed, the troops of each side began to be deployed.
 the world tree camp players were located inside the castle wall of their main base.
the chinese army arrived near gwanggyo lake park, about 10 km away from sungwoo’s army, and regrouped themselves to prepare for the war.
the commanders of the world tree camp were watching the four monitors while sitting at the ‘control tower’ of the western wall.
 one of them was broadcasting an official channel.
- [official channel: live] world season 9 (9,896,404 people)“wow, the number of viewers is so huge, isn’t it? man, there are still huge survivors on earth.
”given the whole world was watching this fight, the estimated viewers numbered as many as 10 million.
 when the viewers of the pirate broadcast were added here, a lot more people would be watching this scene.
because of that broadcast, the world tree camp was on an emergency alert.
“they’re now broadcasting our place!”since anybody could watch the fight without any restrictions, regardless of allies or the enemy, they were afraid that such indiscriminate broadcasts could show the weak spots of the other party.
“just remind our troops that they should never open the hangar door.
 we should never have our fleet power exposed to the enemy.
 the enemy doesn’t know it yet.
”
of course, the forces of both sides were captured by the cameras of the ‘official channel,’ so the overall strength of their power was revealed to the public, but it was hard to tell they represented their total power.
for example, even sungwoo could hide all his troops in the ‘sanctuary of the void’, and in addition to that, he’s trying to hide his core forces such as the ‘allied fleet’ of 32 vessels as much as possible.
“well, they would hide their resources as well.
 that means what we see is not their total power,” inho said with a frown.
the overwhelming number of their troops was really beyond imagination.
“oh my god.
 even if you try to hide their troops as much as possible, they can’t because they are so many.
 yeah, they can’t hide their national identity wherever they go.
”what they saw on the screen was countless players crowding the entire gwanggyo lake park just like swarms of worms on the ground.
“gosh, even the ‘red orc corps’ that appeared in gimpo weren’t as numerous as them, right?”the world tree camp players watching the scene were shocked to watch the endless stream of chinese soldiers moving toward the lake.
 they looked five or six times more than they were during the first war.
and the flying weapons were lined up on one side, and some unknown giants were standing behind them.
“who are those giants? who is controlling them?” kyungsoo said, who noticed it quickly.
but sungwoo thought they were ‘steel golems,’ judging by the passing scenes of them.
when he entered the devil’s world tree, he saw something similar to them inside the cave where the dragon’s bones were hidden.
 back then li wei informed him that they were steel golems.

“they are golems.
 the guy must have a fairly high-level job because he can control the golems.
”“golem…if we didn’t get rid of them early on, they might cause fatal damage to the castle wall.
”the steel golem was among the strongest among golems.
then li wei stood up and said, “ah! they must also be the mongolian reinforcements.
”she once told sungwoo that they had a ‘golem master’ in mongolia who could handle all kinds of golems.
“if they are the mongolian reinforcements, i think there are some really annoying guys.
 in my opinion, maybe they are in charge of fighting our ‘arrow unit’ among others.
”then li wei explained that there was a task force called keshig under the control of the strongest player on the mongolian server.
“they can summon giant horses, and they can fly in the sky.
 and when they use a certain skill, they turn into a soul state and charge at a tremendous speed.
 the problem is they seemed to have the effect of nullifying the opponent’s defense the moment they collided with their target.
”it was presumed that it was one of the chinese military’s hidden cards.
as li wei said, such a unit with excellent mobility would be organized to fight against the arrow unit and try to rush into the battlefield.
“by the way, nullifying our defense power? a skill like that could be fatal to our fleet.
 isn’t this a card that they prepared to aim at the airship?” said jonathan in a worried voice.
sungwoo already proved that no matter how powerful the fleet was, he could destroy them easily, depending on the situation.
“then we will have to beef up our forces on the deck side.
”just like sungwoo’s allies had a lot of cards under their sleeves, the enemy must be hiding a hidden card.
 and responding appropriately to such a moment would change the fate of this war.
***when they were done deploying their troops, they were given a long waiting time of 12 hours.
during that time, the world tree camp reaffirmed their tactics and action guidelines for action according to the unit.
“we’re going to start briefing about the operation of the no.
 2 team of the shield unit.
 fall in, everybody!”the ‘shield unit’ led by junghoon was undergoing thorough training repeatedly.
junghoon went up to the podium and raised his voice.
“let me stress again! as for the shield unit, you guys will not be able to move around freely ten minutes after the war starts.
 i don’t know yet how far you guys will be able to move.
 that’s why it’s so important how you are deployed at first.
 alright, let me once again…”he emphasized the precautions again and again.
 he even ordered each squad of the unit to memorize the precautions just in case.
when a battle broke out, many people would fall into panic, so junghoon believed that repeated training could prevent it to some extent.
‘this time we will never let them run over us,’ junghoon muttered, refreshing his determination once again.
 ‘we’re sick and tired of defeat and failure.
 no more!’

in the past, he was called the best hero on the korean server, but he yielded his top position to the necromancer.
 today the necromancer has established himself as an idol that cannot be compared with anybody else.
‘yeah, i have to admit that i can’t perform as brilliantly as the necromancer.
 but i’m going to succeed by all means within my limits.
’so he was determined to put everything on the upcoming war.
 even if he couldn’t be a hero, he didn’t want to be a burden on the necromancer.
woo woo woo~in the meantime, one airship was carrying something, with 6 wires stretched tight.
“uh? watch out! that’s the key weapon of our war with the chinese server!”it was the masterpiece ‘guardian’s statue’ made by the blacksmiths and architects.
a blue waterproof tent was put on it, so that nobody could see it yet.
“pull it up! a little more!”the statue was carried to the highest point of the castle wall before being placed on a pre-made stand.
thump-the blacksmiths who were waiting there ran to it and fixed the statue’s shoes on the stand.
“now, we’re going to take out the guardian statue immediately after the battle begins! be careful not to reveal it as much as possible!”

 