\section{chapter 431}

almost all the other servers were gaining scores by struggling against the invasion of the absolute races.
 in fact, it was more important for them to survive than to score points.
 on the other hand, the korean server was going all over asia, hunting, or slaughtering the absolute races.





reporter ahn continued, "as expected, their korean nicknames are familiar to us.
 it seems the heroes stand out in any difficult situation.
"of course, what killed the most enemies was magic engineering weapons such as 'bug hunter'.
 since the enemies were dealt a harsh blow with such weapons, it provided the perfect environment in which the heroes could fight brilliantly, so it was no wonder they gained huge scores.
 they weren't the only ones who obtained high scores.
"and other than that, the top and bottom pages on the next page are all full of the names of the world tree camp players.
 it's amazing.
"the majority of those ranked from the top to the bottom was filled with korean nicknames, namely, the players of the world tree camp.
"reporter ahn, when this is over, the world tree camp will grow once more, right?""you bet! perhaps we might see the emergence of an empire that encompasses the world beyond the governing body!""wow, empire…"
nobody could come up with the word 'empire' easily, but it's about time they could mention it freely.
advertisements    at that moment the screen showed another scene, this time the battlefield.
"ah, the fighting on the bangkok battlefield is already at an end.
 as a result, the world tree camp led by the necromancer conquered 11 battlefields, and they are now heading to the 12th battlefield, the nepido battlefield in myanmar.
"the world tree camp's victory after victory on the battlefield continued quickly.
"world tree forces are endlessly increasing.
 every time they conquer the battlefield, the forces of the server in the area they have saved are joining them, so it's inevitable that their firepower is getting more and more powerful! it's just terrific!"various player units of different servers were following the necromancer.
 because of this, it seemed that the players of the world tree camp outnumbered the angels and demons of the absolute races.
 "it looks like the advance of the world tree camp will never stop! i think they can save the whole world!"his assistant added, "yeah, like a bulldozer.
"
ahn giggled at him, then nodded.
"bulldozer? they are definitely pushing everything away like a bulldozer.
"the korean bulldozer accelerated.
***the battlefield for the indian server 2 was mumbai.
"the gates of heaven have been opened!"mumbai was the largest city in india, but it has undergone a drastic geographical change since the game began.
"everyone, worship toward the sky!"they demolished the slums that occupied one side of the city completely and built a giant 'altar' by paving its vast land with marbles.
 tens of thousands of players gathered there, lying on the floor, and bowing their heads towards the altar that rose in the center.
"the messengers of god are coming down for us! welcome them!"with shouts like that, they began to play various instruments, starting with the trumpet somewhere.
a man in golden armor stood up among them.
 then he went up to the highest point in the center of the altar and stretched out his hand toward the sky.
"ah, the messenger of the gods! your servants have been waiting for you for a long time!"those they were welcoming were the angel race.
 

however, unlike in other places, the angels that appeared here did not come out aggressively but were descending very slowly and gracefully.
gooooooooooooo-it really looked like a divine being descended from the herd of angels, but his appearance was terrifying.
"we have been waiting for you patiently, not yielding to any temptation, in order to stop the terrible calamities that have occurred on this land and receive the salvation of the gods!"as could be seen from their actions in mumbai, they chose to obey the angel race.
before the game started, mumbai was the world's most densely populated city.
but that was the worst disaster because in a lawless world there were more victims due to the conflicts between players than by monster attacks.
but a knight wearing this golden armor, so-called 'sunika', in the hell borrowed the power of 'angel camp' to unite mumbai.


 