\section{chapter 441}

the white wolf was thrown away with a roaring sound and crashed into the wall.





"you know what? cunning abilities like psychometry make this game uninteresting.
"after all, it was war.
sugnwoo kicked off the ground, then wielded the grim reaper.
 at the same time, the butterfly flew from gangsok's shoulder and spread her wings.
"no!"a shield has been created around gangsok.
clang!sungwoo's grim reaper was blocked by the shield.
 sungwoo could not help but be embarrassed by the fairy butterfly's intervention.
he lifted the 'winter predator', switched it to 'spread mode', and aimed it at isabella and the dragon.
 they were the targets that he had to keep at bay first.
'even if i have the support of the dragon slayer and the dragon expedition, i can't let down my guard.
 this is a dangerous situation.
"when as many as 50 freezing bullets were shot at her, isabella spread her hands and crouched her body in flames, but that could not stop the bullets.
 powerful cold bullets got stuck all over her body and covered it completely.
 in an instant, a spherical ice prison was formed around her.
"vivona! kill them all!" grace shouted.
then a huge shadow rose from beneath vivona's feet.
"stop him!" junghoon shouted.
bang!sungwoo's sickle and gangsok's wand collided strongly.
"did you make a deal with the administrator of the system?"sungwoo asked, staring at him.
 gangsok nodded, with a relaxed expression on his face.
"that's right.
 this game is also a gambling board.
 the gamblers promised me a certain reward for destroying the three worlds.
 this is the third world.
"if that's the case, was he supposed to infiltrate the world by disguising himself as a player?"necromancer, you and i are no more than beings who are controlled in this game anyway, but if you're controlled, isn't it better to be one that they like you?"
".
.
.
""think about it well.
 you have a chance, too.
 the reason i am telling you this is to give you that opportunity.
"as he said, he could not get out of this system forever.
 or he could be forced into captivity like the world eater and his comrades.
if that is his destiny, would it be better for him to adapt to the system and become a part of it like gangsok? is it really the right thing for him to curry favor with the operators of this game and the crazy perpetrators to destroy another world?the most up-to-date novels are published on lightnovelworld.
comwhen he thought about it sungwoo shook his head.
"no, you are going to be dropped from this game right now!"as soon as sungwoo shouted, the space shook and an explosion was heard from the ceiling.
bang! bang! bang!"bombing?""aaaaah! so cold!"the world tree fleet that had been floating over the pyramid began to bomb the pyramid.
"are you going to destroy this whole place?"the ceiling of the pyramid shook, with its debris falling.
 even if this was the structure built by the angels, it could not withstand such indiscriminate bombardment.
"argh! i'll kill you!"at that moment the ice prison that had bound isabella's body melted in an instant, and a red beam burst out from the center of her body.
"avoid it!"sungwoo's party threw themselves to avoid the huge pillar of flames.
 'it's breath!'it was the dragon's breath, which was more lethal than dragon fear.
the glowing breath melted the back wall and penetrated inside, and as a result, the space instantly turned into a fire pit.
besides, the structure was collapsing quickly as if the glowing breath destroyed the entire foundation of the pyramid.

kugugugugu-cracks spread through the wall and the floor.
 no one could stand without shaking.
 even isabella stepped back staggeringly.
"hanho!""yes! i'm ready!"at that moment, hanho summoned 'hyunmu'.
 a huge green figure appeared, taking up half of this space and crouching down, and sungwoo's party threw themselves down under it.
thud! thud! thud!heavy fragments poured down on hyunmu's shell, and the world went dark.
kugugugugugugugu-after all, the pyramid collapsed completely, separating the two sides from each other.
the latest episodes are on the lightnov­elworld.
com website.
but their separation lasted only briefly.
 "socrates! wake up!" hanho cried out in the dark.
then, hyunmoo, who grew tremendously taller, got up and pushed away the debris that covered his back.
 little by little the sunlight was seeping in, and then there was an escape route.
 sungwoo ran out through the route right away.
'i have no time to waste a second.
 i have to overwhelm him right now!"there was a huge pit with no ceiling now, and with a pile of white debris standing here and there, a tornado wind rising from the front pushed the debris away.
 it was grace's skill.
 and her allies were standing there.
"fire shells at them!" sungwoo shouted.
the airships floating in the sky confirmed the target.
 and the moment they tilted the muzzles toward them, the whole world turned white.
 it was an intense light.
at the same time, dozens of lightning bolts fell from the sky.
lightning struck one of the airships, melted the shield around the airship in an instant, and shattered it to pieces right away.
 it collapsed like crumbling crackers.
"crazy…"it was unbelievable firepower.
 but sungwoo's party could not sit idle, overwhelmed by such a mighty attack.
the battlefield was extended, but it was not necessarily bad for sungwoo's party.
rattle! rattle! the undead army under sungwoo's control came from all directions, surrounded and tightened them.
'let me fight it out with these guys.
'sungwoo had been prepared for a war with the dragon for a long time.
 in that sense, the current situation was rather an opportunity for him because they were not prepared for this kind of war very well.
thud! at that moment something fell in front of sungwoo.
 it was a long iron box sent by the messenger.
"i can't afford to test it.
 let me trust them.
"sungwoo picked it up.
khwaaaaaaaaaaaa!this time breath rained down.
 one red pillar of fire hit one airship.
as expected, the shield around the airship was useless.
 the whole airship melted like cheese, then fell helplessly.
 kugugugugugugugugugu-the latest episodes are on the lightnovelworld.
com website.
even though sungwoo didn't lose even one airship while undergoing dozens of wars until now, two airships crashed in just a few seconds this time.
 'i'm fighting against the demon king and the dragon.
 no wonder they were so powerful.
'sungwoo just focused on their attack.
 thousands of undead rushed toward them.
 but they could not break through the pillars of flames.
 they just could not approach the enemies.
 soon a gust of wind, lightning, and flames swept away the undead army.


'now is the time!'but sungwoo mobilized the undead army to distract the enemies.
- 'twilight assault' begins.
sungwoo assimilated with the black smoke and penetrated the enemies.
 at that moment, jisu alsojumped in.
 they literally intruded right into the middle of the enemies.
using the 'twilight assault,' he aimed at the wind wizard, grace.
thud!the black smoke engulfed her, then slammed her down to the floor.
"ugh! how unpleasant…"the dead man's hand rose from the floor and tied her.
 in the meantime, jisu clashed against vivona.
then their firepower was significantly reduced, and the undead army quickly closed in on the enemies.
sungwoo quickly turned his head and swung the grim reaper towards isabella, while jisu summoned einjrahher to attack vivona.
'kill the dragon first, the most dangerous creature!"but the dragon was not easily defeated.
puck!"khuuuuuuuuk!"isabella punched sungwoo in the stomach.
 her punch was so fast that he couldn't avoid it.
'my ribs are broken.
'he was thrown dozens of meters, falling down on the ground.
sungwoo could hardly breathe now.
 "ugh!"it was the worst pain he felt after a long time.
the latest episodes are on the lightnovelworld.
com website.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 