\section{chapter 405}

she jumped off the ground once more.
 she then summoned all of einherjars behind her, then launched a frontal attack against the emperor from various directions.





but she was faced with the counterattack again.
 shhhhhhhh-when the golden threads spun from the right of the golden hands and stirred in the air, all einherjars were thrown out right away.
jisu could barely escape and landed on the rampart.
gasp! gasp! she was gasping for breath.
 there were too many golden threads.
 when she approached very close, it seemed that more than hundreds of threads seemed to have come out, but maybe there were more.
"what the heck! how come they are encircling them like that?"the golden threads from the left hand, which she didn't notice, coiled the three airships tightlywoo woo woo-then the three airships started turning the bow into the rampart.
 they began to move according to the emperor's intentions.
 the crew on the decks could not do anything.
"i can't control the ship at all!""all the buttons don't work at all!"chuchuchuchu-thinner threads began to come out from the golden threads that wrapped around the airships, then began to penetrate the airships.
 they were now taking control of everything on the airships.
 bang! bang! bang!then they started firing cannons at another airship inside the rampart.
this time the combined fleet also began to counterattack.
 even though the allied crew were aboard the ships, it was certain that they would incur great damage because they were preoccupied with the golden hands' attack.
 they had to crush the airships floating in the air by all means.
 
"fire cannons! we have no other way!"however, the shield of the airship was not torn apart even when bombed by dozens of cannons.
 follow current novels on lightnovelworld.
com"looks like mana is being supplied to the airship controlled by the enemy!"that was correct.
 the golden threads that came out of the thumb of the oppressor's hand were connected to the "mana battery" at the rear.
in other words, the emperor was now controlling the airship that constantly received mana, as if he was dealing with a pistol.
watching that scene, jisu closed her eyes.
'i need to come up with another method.
'she thought that if she could break through the right of the golden hands and cut the emperor in half, she could at least buy some time, even though she could not turn the tide of the fight.
 she was thinking of buying some time for the necromancer to deal a fatal blow to the emperor.
she believed that the necromancer must have been preparing for that fatal blow somewhere.
 she knew him very well.
 he wasn't the kind of person who would continue to engage in an unworkable and inefficient fight.
 'that's why i have to inflict damage on the emperor.
 that's my job.
'catching her breath, she grabbed the sword and jumped again.
***in the meantime, junghoon's situation was not good either.
clang! clang! he lifted the sword and the shield to defend against the two spears flying toward him at the same time.
 the terracottas in the form of two heroes, li bu, and guan yu, were fast, rough, and strong.

clang! the moment he blocked li bu's bangchon spear with the shield, which was falling towards his head, he lost his balance and staggered a bit.
'damn it! that guy is so strong…'even though he had 81 muscle strength, his right arm was shaking very hard.
 he backtracked inside the rampart while blocking their attack.
even though his crusader team members tried to cover for him while attacking them from behind, they failed.
tung! tung! tung!updated from lightnovelworld.
c‌omthe moment they were faced with arrows or magic, one of them moved back to strike back all of them quickly.
 even if they were stormed by the enemy from behind, they smashed the attackers in an instant.
 obviously, they fought so fiercely like the two heroes of the three kingdoms chronology.
clang! junghoo soon found that his stamina was gradually exhausted.
thud-after all, he allowed li bu's hard kick in his stomach.
 because of that, he was thrown over the railing dozens of meters away, falling deep inside the rampart.
"argh.
.
.
shit…"when he fell on the dirt ground, he felt a huge shock on the spine.
his limbs felt numb and his head was in the clouds.
 he could not move at all because he could hardly breathe.
when jisu and junghoon were neutralized like that, the emperor easily penetrated the rampart.
gasp! gasp!falling under the shadow of the rampart, junghoon watched the three airships flying over the high rampart toward the world tree.
bang! bang! one of the friendly airships was shot down by the enemy's bombing.
 they already lost the 3rd ship, not knowing how many more they would lose.
 "we've got to stop them…"when junghoon touched the ground, trying to overcome the pain, somebody landed right next to his head.
 he lifted and turned his head.
 rattle- rattle-it was li bu.
 that expressionless earthenware doll walked toward him, making the sound of stones rubbing against each other.
 he was intent on killing junghoon.
"damn it…"at that moment, somebody else appeared next to him.
 was he guan yu?fortunately for him, it was not guan yu.
"oh my.
.
.
it looks like that chinese guy is strong!"visit to lightnovelworld.
c‌om discover new novels.
it was the voice of hanho, who seemed to be a social misfit because he was not good at grasping the situation well.
with a smile hanho lifted something.
 it was a shield.
 more precisely, it was 'aegis'.
 he seemed to have picked it up when it fell off the guardian's stone.
jeeeeng-he fired a petrified beam at li bu.
 but at that moment, li bu raised his left hand to block the light and minimized the range of his exposure to the light.
even though his left shoulder and arm turned to stones, he just moved around nonchalantly because he was made of clay from the beginning.
"what the heck? how could he block my attack?" hanho was shocked.
 then he raised six arms in which he was holding six items.


the composition of the items was terrific.
 they were even bizarre.
what hanho was holding now was four shields and two spears.
'four shields?'junghoon could not understand how hanho possessed so many spears like that.
 when he lifted the four shields side by side, they looked as if four spartan warriors were gathered together.
"give me that shield over there.
"he even threw away one of his spears and held out his hand toward junghoon.
"pardon?"was he going to pick up another shield now? he already had four shields.
 then did he want to use five shields?"hurry up! let me give it back to you later! i'm not going to make it my own like somebody else!"junghoon didn't understand what he was talking about, but he gave the shield to hanho with a nod.
"oh, this is a good one.
 well, since you are the captain of the crusaders team, you deserve this kind of shield.
 well, this is not that good, compared with the achilles shield that sungwoo gave me.
 by the way, where did it fall?"muttering like that, he walked towards li bu.
 rattle- rattle- rattle-follow current novels on lightnovelworld.
com you can also read this novel on the more advanced platform lightnovelspot.
com

 