\section{chapter 376}

chapter 376: exit from demon’s cave and preparing to conquer china (8)at that moment, an airship came out of the portal.
 it was the messenger.
 as the ship soared over the dragon’s head, cheers erupted from everywhere.





and the man in a dark green robe stood from the head of the ‘bone dragon’ that landed on oreum.
 only then did those gathered together began to chant his name ‘necromancer’.
“they’ve come here! the necromancer has come out!”“we’ve won! the necromancer has won!”although jimin and the players on jeju island reluctantly accepted this impressive situation, they were puzzled about what was going on.
“what the hell is that person?”jimin also encountered sungwoo before, but she was puzzled by him now.
who the hell was this person who was so trusted and admired by everybody while leading such a large army?jisoo opened her mouth.
“that’s him!”“uh? what do you mean?”sungwoo was also well aware of the fact that a group of thugs originating from a cartel in latin america took control of the mexican server and often looted the american server.
but this time, the situation was quite different.
“um, according to jonathan’s report, they seem to have become the servants of the dragons in amazon.
”“oh, you mean the cartel worships the dragons of the amazon?”kyungsoo nodded at his question.
 then, he picked up the paper on which he wrote down something.
“um, what i mean is that according to the agent i have planted in south america, the dragon devastated south america then went dormant.
 after that, a regional quest was issued in that area where they could become the worshippers of the dragon.
”kyungsoo’s expression darkened, but sungwoo nodded calmly.

“that’s quite possible.
”it was not uncommon to see monsters with intelligence taking players as their subordinates.
 actually, sungwoo witnessed that on jeju island.
“we need a ‘control center’ to prevent the emergence of groups with such extreme ends.
”earlier on the broadcast, sungwoo stressed the need to create a control center to counter powerful monsters such as the ‘dragon’, but he was more concerned with controlling the players moving in disarray without a central leader.
‘it’s not the monsters that the system created to ruin our world.
 it’s ourselves.
”although some servers were devastated helplessly by the monsters, most of the other servers overcame the crisis and found stability soon.
 then, strong men with the wrong purposes were created.
 the so-called ‘fallen’ of the world eater’s original server was also destroyed by such a player.
‘we had several such bad actors on our server, such as the vampire lord, doctor, emperor, etc.
 they will continue to appear in the future.
’in other words, the biggest enemy was the players themselves.
 so, uprooting them and nipping them in the bud was the only way to protect this world.
“ah, kyungsoo, please ban anybody’s access to the world tree right now.
”“for what?”sungwoo got up from his seat, taking out the ‘spirit of the world tree’ from his pocket.
 in order to gain greater power, he had to use all his resources to the fullest.
the largest resource among them was the world tree, of course.
“maybe the world tree will grow rapidly.
”he didn’t know what would happen if he took it to the world tree, but it was dangerous to anybody who was near the world tree.
at that moment, mir, who had been sleeping, curled up under sungwoo’s feet, was whimpering then suddenly trembled.
grrrrrrrrrr- grrrrrrrrrrr-“uuh? what’s the matter? are you sick?”
sungwoo lifted mir.
 the guy wiggled his body and opened his mouth wide.
and then he burped.
“how can you burp?”he burped violently.
- ‘black dragon (hatchling)’ has completely absorbed a magical object.
he seemed to have completely absorbed the ‘fox marble’ that he had swallowed a while ago.
 he then rolled his eyes with a happy expression.
but mir’s eyes changed.
 a little while ago his eyes were red, but as soon as he absorbed the fox marble, the color of his eyes changed to gold.
- ‘black dragon (hatchling)’ creates a ‘new skill’ by applying the skill inherited from you.
[skill information]- name: world eye- grade: special- classification: passive/active- consumption: none*you have gained eyes to penetrate something.
 based on that information, you can easily remove all the obstacles of your exploration.
+ master’s map: it creates a mini-map that displays all the topographic features in a certain area (20km) and displays your location in real-time.
 this map will expire after 20 minutes.
 (cooldown: 1 hour)+ neutralization of the maze: it detects the ‘hidden space’ within a certain radius (300m) and easily unlocks the ‘traps’ and ‘seals’ of super grade.
 (cooldown: 30 minutes)“oh, my god! this one is…”this was the skill that li wei once described as the world eye.
‘didn’t she say that i could use it when i reached the level of the king of the spirits?’how could this little hatchling get it for me? sungwoo could not believe what happened before his eyes.
 even if mir swallowed the fox marble, it was beyond his understanding that he could bring such a skill to him.
come to think of it, mir could do it just because he was a baby dragon.
‘by the way, it has a lot more diverse functions than i thought.
’the world eye didn’t exist simply to show a ‘mini-map.
 it was a tremendous skill that could literally remove all obstacles that stood in the way of sungwoo’s progress.
grrr- grrr-while sungwoo was reading the message, mir, who was in his arms, began to struggle.
“why are you moving again this time?”mir tried to get out of his arms, so sungwoo let go of him.
 then, he spread his wings and flew to the end of the room.
 then, he landed in front of the sealed box that hanho had found next to the spirit of the world tree.
sniff! sniff!he began to sniff, showing interest in the box.
“isn’t that the box you brought from the demon’s cave?”“yes.
”sungwoo was not sure why mir got suddenly interested in it.
snap!-the seal has been released.
 (the forge of hephaestus)

“uh? what the heck is this?”“did he open that box now?”“yeah, that’s right…”both could not hide their surprise.
‘he unsealed the first-class seal of the box with the maze neutralization skill of the world eye.
 by the way, what the heck is the forge of hephaestus?’sungwoo slowly approached the box.
 then, he placed his hand on the open box very slowly.
a huge space opened up before his eyes.
- you are entering ‘the forge of hephaestus’.
it was translucent, and it overlapped with sungwoo’s office.
“do you see anything?”sungwoo nodded at kyungsoo’s questionit was a space filled with orange color everywhere.
 there was a huge brazier and anvil on one side, and numerous items on display on the left and right.
while looking around that place, sungwoo recalled what the world eater once told him.
“the reason the world eater asked me to check the ceiling of the halls of guardians was not because of the spirit of the world tree.
”the legacy of the destroyed server was contained in this box.


 