\section{chapter 462}

he was the king of the great mountains.
 he entered the hallway with two young tigers.





"hey, you look very sick.
 would you like a drink of strong alcohol to get better?"hanho thought the king cracked a joke, as usual, but he really held out a bottle of wine.
"uh, that one is…"hanho remembered what it was because he had seen it in an underground lake in the cave of mt.
 sorak.
"that's right.
 i've fermented it enough to drink, so drink it, jisu.
 your fatigue will go away.
"hanho received it in a hurry and opened the lid for her.
there was something unusual about the purple smoke coming out of it.
he saw a message about it clearly.
[item information]- name: regret- grade: myth- class: consumption- effect: 'spirit of the mountain' and 'soul of the dead' have been mixed to create a sweet drink with a strange power.
 if you sip it just a little bit, your 'spirit affinity/dominance' and 'death-attribute affinity' will increase significantly.
in addition, it gives you insight into life and death and awakens the qualifications of a 'shaman' that connects this world and the afterlife.
 (acquire shaman properties)- description: the spirits of the dead harmonized with the spirits of mt.
 taebaek.
 what can this be called? since life and death are contained in one cup, can you understand everything in the world if you sip it? (it tastes sweet and bitter.
)'what the heck is this? why this one?'hanho could not understand it, but he just tilted the cup into jisu's mouth.
***jisu was dead.
 nobody knew why she died.
 excessive bleeding? death from shock? whatever it was, her entire left shoulder area was severed, so it's no wonder she died.
'well, this is not the first time i feel this.
'
come to think of it, it was her second death.
she died in seoul while she was fighting the chinese server.
at that time she obtained the divine power of valkyrie after clearing the event called 'the gate of the recognized.
''i felt the same thing back then.
'for her, it was another death.
 this time she could not see anything, but she smelled some incense.
 then the cool wind tickled her whole body as if she entered a cave.
then somebody's voice echoed.
"hey, you are not dead yet.
"she couldn't tell if it was a woman or a man, but it sounded like an old man's voice.
was this the start of another event?"i can't believe you went through the strange experience of crossing life and death twice.
 what an arduous adventure!"letters appeared in the darkness.
 now you are qualified to connect those two worlds.
 go back and fulfill your role.
"- 'shaman' trait has been added.
'shaman? what is this?'that wasn't the end.
-you have met the given conditions.
* shaman trait (vengeance of death) * valkyrie (female warrior) * unknown (additional acquisition required)in the end, it was another chance for her survival.
'why?'she felt everything was strange now.
 why did she go through such strange experiences twice?
a light appeared from somewhere.
"sis? sis jisu! have you come to your senses?"it was hanho's voice.
"oh my…" her vision slowly returned.
hanho and li wei were looking down at her under the ceiling of the hallway shimmering in the light.
"wow! great! she has woken up!""ha, what a relief!"she instinctively raised his right hand and placed it on his left shoulder.
her severed arm was restored.
"ah! you know what? when i just sipped that weird purple drink, it just started regenerating! it was a little creepy, but it was amazing!"jisu finally raised her upper body and turned her head to look for somebody.
the king of the great mountains was sitting in the place where she rested her eyes.
"jisu, have you woken up?"he smiled brightly, but she didn't.
"what's going on?" she asked.
she didn't feel good about her two deaths at all.
 so she was in strong doubt at the moment.
 why did this strange thing keep happening to her?but the king pretended not to know anything.
"ugh? do you have any problems?"he not only helped jisu's awakening but also induced her to attain the divine power of valkyrie.
 this time, too, he had her obtain something.
"how come you have necessary things ready every time like this?""ummm…sorry, but that's a secret.
"she frowned at his reply.
 but the king of the great mountains scratched his cheek and looked into the air.
"well, if i can say anything…" he looked at her.
 "all i can tell you is that the voice ringing in my head isn't just the command of this system.
"was it a different voice?"then…"at that moment, the king stood up from his seat.
"well, stop being curious.
 won't you go out and help the necromancer? it seems there is a lot of chaos outside right now.
"he was right.
 this was not the time for her to be curious about it.
***the amazon rainforest was on fire.
hundreds of trees were cut and the ground melted every time the demon king dealt a blow.
"avoid it!"someone on the ground shouted.
 but soon his body was touched by the red light and evaporated.
 and the ground he was treading on broke apart and soared into the air.
12 beams of light emitting from the 12 horns on his three heads devastated the whole area ruthlessly.
"we can't get to him!"it was impossible for them to dodge the beam attack unless they had had an extraordinary sense and agility.
everything within the 5km radius of the demon king was devastated.
 nonetheless, it was only five minutes for the king to stand by for his next attack.
 that's why they could not approach him.
"retreat again, everybody!"sungwoo's ground troops that advanced toward the demon king eventually had no choice but to retreat after suffering great damage.
"man, how can we break through the demon king's ferocious attack?"

"maybe necromancer could…""well, his undead army was already annihilated twice!"as a matter of fact, sungwoo's undead army was burnt into ashes by the demon king's fiery attack.
in the meantime, sungwoo got on the bone dragon and looked down at the battlefield.
he had to climb up to a high altitude to avoid the demon king's beam attack.
'alright.
 during the next five minutes, i have to deal a crushing blow to him by all means!'sungwoo moved two gigantes to the left, then their two shadows to the right.
thump- thump- thump- thump-they surrounded the demon king in all directions.
 however, the demon king's body was so large that it looked as if children surrounded an adult.
'even if there are four children, they can harass an adult even briefly.
'sungwoo turned his head.
"isabella!"when he shouted, isabella, who soared high in the sky to avoid the beam attack, looked down at him.
"let me keep him at bay.
 just burn his head!"at that moment the 4 gigantes began to advance.
 ku-wu! ku-wu! ku-wu! ku-wu!as the giants of enormous weight moved toward the demon king, the ground around them swayed as if they turned into liquid.
'yeah, as long as i can hold him somehow, isabella can hit him with dragon breath.
'but his grand plan fell apart.
 suddenly, a bunch of red tentacles spewed up from the cracks in the ground, then tied gigantes' feet tightly.
kuruk- kuruk- kuruk-

 