\section{chapter 473}

the demon king's body shook back and forth, and the red film around it disappeared like sugar melted.
 that wasn't all.





a stopwatch icon appeared on his armor, then corroded in an instant just like time passed quickly.
'alright.
 isabella did a great job! she almost broke his armor!'she cast three types of magic in a row, then approached closer and opened her mouth wide.
 she let out red pillars of fire, namely, 'dragon breath', toward his armor that was broken by half.
 at the same time, a red beam was shot from the demon king's four horns.
'he fired the last beam!'the demon king eventually used his last beam to push isabella away.
at that moment dragon breath and the demon king's beams collided and hit both.
"argh…"isabella was thrown away behind sungwoo's back and crashed again.
could she survive this time even if she was the formidable dragon?sungwoo looked at the front instead of paying attention to her.
'alright.
 he's exposed his loophole.
'sungwoo quickly stepped forward and aimed the superheavy arrow at him.
'alright, he is fully vulnerable now!'the demon king's chest completely melted.
 even his ribs were crushed, so there was a big hole in his chest, revealing its inside clearly.
kuuuuuuuuuung-the sound of his heart beating, his gigantic heart churning out blood, and someone's face embedded in that heart.
 it was gangsok's face that got pressed down to the heart.
'that's his real identity.
'at that moment, the guy violently twisted his body.
with the 'cluster of tentacles' from his lower body stuck into the ground like a lever, he was moving his upper body from side to side violently.

"what the hell is he doing now?"after all, was this his last resort when all his hidden cards failed?'damn it, i can't aim at him properly.
'the latest episodes are on the lightnov‌elworld.
com website.
his violent shaking alone was enough to disturb sungwoo's fatal attack because he could not aim accurately because his heart moved up and down frequently.
"argh! sungwoo!" hanho shouted.
as his violent shaking intensified, those who were restraining his arms were struggling to hold out desperately.
"take some action! i can't hold out any longer!" the king of the great mountains shouted.
tuk- tuk-even the 'roots' of the king of the great mountains, which were tying up the demon king's other arm, began to break loose.
'obviously, he wants to avoid an instant death.
'his last resistance was reckless but pretty much annoying.
if sungwoo's superheavy arrow hit his ribs or stomach instead of his heart, he might not be able to kill the demon king completely, which would make the fight in the latter's favor again.
at that moment sungwoo had a lot of thoughts in his mind, but he could not delay any longer.
- grim reaper retention time (00:03:51)the retention time of sungwoo's most powerful skill, 'summon grim reaper,' which symbolized his power itself, was to expire pretty soon.
 if he could not kill the demon king right away, there was no guarantee that he could beat the king later.
"if that's the case.
.
.
"sungwoo quickly threw himself towards his chest.
'let me use some extreme method!'''
sungwoo did not try to aim the arrow accurately.
'let me shoot the arrow and hit him, no matter what.
'he intended to get directly into his chest, so he could rule out the chance of missing the target.
at that moment, a bolt of blue lightning flashed from his heart.
 that was gangsok's power, the true identity of the demon king.
sensing that sungwoo was approaching, gangsok was trying to block his entry into his body.
 even long thorns sprouted from his melted ribs.
'it doesn't matter.
' sungwoo didn't care.
- 'twilight assault' has begun.
sungwoo jumped off the zombie hippogriff's back, and threw himself after turning into a ray of black smoke, then got into his open chest in an instant.
for more, visit lightnovelworld.
comthe moment he landed near gangsok's heart and got out of the black smoke, a long thorn protruding from his bones got stuck on his back.
 gangsok was faster.
sungwoo felt dizzy at that moment.
puck! puck!then, two thorns that came up from the ground pierced his left thigh and abdomen.
"argh!"he almost lost his mind for a moment, but he barely held out.
then he fired the superheavy bow first, which he had been pulling until a little while ago.
- the 'dreadful killer weapon' has been activated.
the moment the superheavy arrow left the bow, a thorn protruding from the ceiling pierced his right eyeball.
 and the strong current from his heart pierced through his body.
- you have obtained 700,000,000 gold by killing the world boss monster 'demon king'.
that was the last message.
sungwoo was dead.
 it was already his second death.
his life was about to flash before his eyes, but he suppressed it.
'the next moment matters.
'he knew he would open his eyes again.
 so he shook off idle thoughts and waited for his sensations to come back.
 he had to react quickly.
'i have to confirm his death with my own eyes.
'he confirmed the message that he killed the 'demon king'.
 but after that, there was no message that he killed the 'player'.
'when i killed the world eater, both the monster and the player appeared at the same time.
'both the world eater and the demon king were originally players, who later turned into transcendent monsters.
 so his original self, namely, the player had to be killed with the demon king.
 only then could sungwoo confirm he killed the demon king once and for all.
'do i need to do something else?'soon, something began to brighten in front of his eyes.
- you have 'resurrected' as someone with the job trait of necromancer.
 (cooldown: 31 days)this was the 'hidden ability of the necromancer that he learned when he was killed by 'bone drake' in yeouido.
 since he was not killed until now, it's been quite a long time since he activated it.
 shortly afterward, the holes in his body were filled, and his skin burned by the lightning attack was restored.
for more, visit lightnov­elworld.
c‌om"haaaa…"then he could breathe slowly when the air was filling his lungs.
his sensations returned.
- the retention time of 'grim reaper' has expired, so you cannot use the power of 'lich'.
* you can use the special skill 'primordial death' because you have satisfied the special conditions.


as a result, sungwoo exhausted his power.
by pouring out all his energies and power, he could succeed in dealing a fatal blow to the demon king at the last moment.
'it was really a close call.
'sungwoo looked inside the demon king's body.
 there was no more vitality in his gigantic body.
 it just felt hard like a damp cave.
'he was definitely dead.
'sugnwoo raised his head and looked straight ahead.
his huge heart was torn apart and scattered all over the place, and the superheavy arrow burst through his heart and shimmered inside after getting stuck somewhere deep inside.
 and gangsok's body, which had been embedded in the demon king's heart, was also drooping.
'this is a corpse.
'sungwoo could feel it.
 gangsok was dead.
but something eerie happened.
with a bizarre sound, his body turned to dust and began to fly.
stunned by that bizarre phenomenon, sungwoo stepped back and lifted 'winter predator'.
tsutsutsutsutsutsu-the powders gathered in one place as if flying in a flock, then started to recombine.
his bones, intestines, blood vessels, and skin were attached to his body.
 his eyeballs were soon formed.
 he was rolling his eyes here and there, then looked at sungwoo.
that way gangsok was regenerated in his original form.
in other words, he has been resurrected.
".
.
.
"visit to lightnovelworld.
com discover new novels.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 