\section{chapter 288}






 however, none of them moved from their assigned positions.
 they were patiently waiting for junghoon’s order and the necromancer even though their legs were quaking violently.
ooh-ooh-ooh-ooh-ooh-ooh-as if the angel’s body was tied to a string, she slowly descended.
 she had nothing like wings.
 she was just huge, white, flat, and soft.
 like a newborn child, her white skin was rather pink.
when she approached the station with the sun against her back, a huge shadow engulfed the entire youngdungpo station.
 in the darkness brought about by the white body, the players lifted their heads and looked at the angel at an extremely high altitude.
“ah…”the angel also slowly lowered her head toward the players.
 her fluffy blonde hair was brilliant, but her face was far from beautiful.
“damn it! is that the angel we have relied on?”“this is nonsense.
”her white and soft face had only a mouth.
 her pink mouth stretched from her forehead to the tip of her chin and slowly opened with translucent saliva falling from it.
that was the reality of the angel.
“gee, now is the time! sprinkle it!”they couldn’t wait any longer.
 if they delayed it, they would find out what punishment that terrible being would mete out to them.
“spray water!”as directed by the necromancer, high-pressure hoses placed in all directions began to spray water profusely.
then, the water spirits controlled by someone made a wave-like waterway from the open water tank and marched toward the angel.
 tons of water soared with just one single magic.
“spell fire magic in the air!”“our target is not the angel, but the air! evaporate the water!”
then, the flame magic was cast.
 it got entangled with the water, causing something like water vapor in a wet sauna.
but all their attacks were in vain.
 there was no way that such water bombs could inflict any damage.
 no matter how powerful they sprayed water, it just scattered into the air when it approached the angel.
 all of the air and mana nearby belonged to the angel.
in other words, the angel was in control of this area.
a rainbow spread over the shoulders of the angel hovering in the air.
junghoon clenched his fists while watching the angel.
“sungwoo, i still don’t know what the angel is trying to do, but take some action quickly, no matter what.
”at that moment, the angel said, “you guys will see your final moment today.
”then, the players standing near the angel collapsed after losing their strength.
nobody knew what happened to them, but the angel seemed to have exercised something like absolute power.
“what the heck! how could they…”“damn it! we are going to be killed!”the angel lifted her left hand forward, slowly.
 then, the water drops that surrounded her stopped moving in the air immediately.
 it seemed that god was doing miracles.
“you guys are just meaningless and worthless.
”more players in a wider area fell at the angel’s words.
“what the heck? are they dead just like that? everyone, step back!”the angel’s attack range was gradually expanding.
 death began to slowly swallow youngdungpo.
 and their despair spread faster than that.
“just run away!”
“no! keep spraying water on the angel!”“are you crazy, captain?”the players’ will to survive knew no limits now.
the will to live began to explode.
“shut up! fire water cannons!”“how long should we keep doing this? all of us are going to die!”“do you think you can survive by running away? the necromancer is the only answer now!”“then, when is that person coming?”right, at that moment he appeared.
thud! kuggugugugugu!the ground under the angel’s feet suddenly sank.
 there was an explosion underground.
 and a handful of blue flames soared from it.
 it was a very trifling movement compared to the gigantic angel, but everyone’s eyes now turned toward it.
“he has arrived!”he was none other than the necromancer, the angel’s opponent as well as the man who got rid of the absolute race’s footprints on the korean server.
 standing tall on the ground, he looked up at the angel.
“welcome to our land.
”in his left hand, he was holding a jewel that gave off red energy, and in his right hand, he was holding a jewel that gave off blue energy.
as soon as the necromancer appeared, the water in the area began to boil and evaporate because his body was blowing out tremendous heat.
the angel’s long mouth wriggled.
“you sinful existence; you can’t reach me.
”“really? but it’s not me you have to fight.
”while saying so, sungwoo dropped the blue jewel “frozen seed” in his right hand right under the angel’s feet.
 at the same time, he jumped off the ground and moved back.
clang!as soon as the jewel was stuck on the ground, a pillar of ice soared from the ground, holding the “frozen seed”.
 at that moment, the temperature in the area began to drop rapidly.
-‘frozen seed’ is in operation.
* the temperature of the whole area is dropping sharply.
* a powerful blizzard will blow.
everything happened in an instant.
 the water drops that had been sprayed expanded rapidly after being frozen.
 a huge amount of water or huge chunks of ice filled the air.
“keep spraying the water!”“spray the water!”“then evaporate it!”the water drops that the angel used her power to stop moving in the air now backfired, threatening her.
dozens and hundreds of tons of water and water vapor floating around her body froze all at once, binding the angel’s body tightly like a straitjacket.
this was why he ordered the players to sprinkle and evaporate tons of water.
goo goo goo-a blizzard created a huge glacier above youngdungpo station.
 the body of the angel was buried entirely in the glacier.
 she had no time to move at all because it all happened in an instant.
-‘frozen seed’ is in operation.


* creates an ice age in the area (seoul).
 (49:59:59)* if you want to stop the operation, you have to separate it from the ‘tower’.
the angel murmured, “how dare you play a trick on me…”her long mouth stiffened quickly.
“that’s why you should have checked the local weather.
 you will feel frozen to the bone here, regret the winter of korea.
”the giant angel froze entirely.
***the angel judge was certainly an overwhelming being.
“man, that angel is tremendous.
”she was bigger than any tall building in youngdungpo station.
 she was the largest of all the monsters that had appeared on the korean server so far.
the players couldn’t do anything, buried under her magnificent shadow.
 just raising their heads and looking up blankly was all they could do.
“kheeeeee!! i still can’t breathe well.
”“those with lower levels, step back!”even though the angel did not launch any serious attack, many players lost their minds or died just by being in the same space as the angel.
just like the title ‘judge’ suggested, it was obvious that the system designed the liberation guild as an entity that was virtually impossible to resist because they were stigmatized as the ‘target’ of judgment by the angel.
therefore, this was an event that should have been conducted unilaterally as the system designed, so this event was a clear lesson for all participants.
 in other words, the event was a clear warning to all that they would receive a heavy punishment if they betrayed the absolute camp.
however, such a warning was ignored by the necromancer.
“wow! he’s the necromancer we have been looking forward to!”

 