\section{chapter 449}

the owner of that eerie laughter appeared from the stadium across from them.
 he was a giant in colorful clothes.





"hehehehe! come on! welcome to no.
 4 gate! labyrinth explorers, you guys have come to a very terrible path.
 how unlucky you are!"he was a clown.
 the giant, who was about 3 meters tall and dressed as a clown, bowed his head toward us and greeted us.
 "hello! i am petros, one of the butlers who serve the demon king and manage this labyrinth.
"- the hidden stage boss monster 'petros' has appeared.
sungwoo looked around the stadium while holding onto the railings of the stadium.
 "gate? is it like a game?" sungwoo shouted.
 having heard it, petros raised the corner of his mouth and nodded softly.
"game? oh, yes.
 it's going to be a fantastic game.
 hehehe!""since you mentioned the gate, do we move to the next gate if we win here?""oh, yes! hehehe.
 you are a man of great discernment! let me explain to you fully.
"gugugugugu-at that moment a small podium appeared in front of sungwoo and petros.
 small statues like chess pieces were on top of it.
 'it looks like an annoying rule.
"the labyrinth seemed to be a place where they had to go through complicated and unfavorable trials.
"now, you're going to face a one-on-one duel tournament! let me count you.
 one, two, three.
.
.
man, lots of you are here, but only one person can have a duel.
 so you will have a total of three games.
"then petros giggled at them and stood in front of his podium.
"but it would be no fun if it were a simple one-on-one duel, right? necromancer, you're going to use the most powerful clan 'bone dragon', right? if not, i think you will use 'bone imoogi' or other beasts! hehehe.
 your tactics are so obvious!"".
.
.
""but if such terrible beasts appear on the stage, they're going to make our beautiful stage dirty, so i won't allow them to come here.
"then he picked up a stone statue on the podium.
"so you can choose one of the 'no participation' options here on this table! it's a rule that will make the game so interesting!"
sungwoo looked down at the table.
- no participation option (select one.
)1) human typenew novel chapters are published on lightnovelworld.
com2) animal type 3) plant type4) machine type5) formless"alright.
 if i choose one of those five statues, the one i select will definitely win!"- your opponent has selected the target of 'no participation.
' (animal type)the animal type except for the human type seemed to mean life forms, so dragons and giant snake imoogi were also included in that category.
"hehehe! as for your proud undead army, i have been watching and researching them for a long time.
 well, they are a pushover for me.
 now, what can you do?"sungwoo looked down calmly and chose the same 'animal type' as him.
 since he didn't know the other party's card, it was useless for him to ponder over it deeply.
- you have selected the target of 'no participation'.
 (animal type)"hehehe.
 good.
 it's not a bad choice! hehehe! but it wasn't the best choice.
"thump- thump- thump-at that moment, the sound of huge footsteps began to resound from somewhere.
"come on, focus! let me introduce my champion first!"an iron fence on the wall of the amphitheater opened and something heavy stepped out.
"giant warrior, goliath!"
- your opponent, 'giant fighter goliath' has appeared.
the giant clad in iron armor and wielding a giant mace shouted.
he was well over 30 meters tall, so his voice resounded throughout the stadium.
 there were tattoos all over his body exposed outside the armor.
 given that they were glowing, they seemed to be protected by special magic.
'goliath?'goliath was a well-known giant warrior who fought against david the great in the old testament.
 although he was knocked down by david the great's stoning, he was portrayed as a monster strong enough to beat anybody in the world.
"hehehe.
 this guy is very good at one-on-one combat.
 is there any subordinate spirit under your control who can fight this guy? or would you like to see your miserable fellows driven into a dangerous situation?"when sungwoo didn't answer, he laughed his head off.
follow current novels on lightnov‌elworld.
c‌om"no way! i wonder if you want to make the foolish decision to be the biblical david the great to fight him.
 hehehe! i look forward to this upcoming fight!"but sungwoo was still calm.
 then he opened his mouth finally.
"hey, clown, when you gamble.
.
.
"suddenly sungwoo grabbed the grim reaper, and continued, "you don't know that you have to keep your mouth shut until you see your opponent's card.
""uh? i beg your pardon?"sungwoo immediately summoned victor and minsok.
 of course, he didn't summon them to have them confront the giant.
 he wanted to use the synergy that he could obtain through four liches, namely, the manifestation of the apocalypse.
after all kinds of messages flashed before his eyes, an important option appeared.
- select the target (army) to summon.
1) prisoners unit (summonable)2) gigantes (summonable)3) sealed person (unsummonable: below overall level)sungwoo chose one of them.
"this one is mine.
"- the 'apocalypse army (gigantes)' has been summoned from the abyss.
among the things sungwoo controlled was something very huge other than the animal types.
 even sungwoo hadn't confirmed its reality.
gugugugugugu-with the whole amphitheater shaking violently, a purple magic circle was drawn over it.
it began to rotate slowly, and then huge shadows rose from its center along with black smoke.
".
.
.
"all of them raised their heads and looked at that terrible scene, with their mouths wide open.
 so did petros.
 something of enormous size engulfed in darkness began to walk amid black smoke.
rattle- rattle-the shackles swaying from those thick ankles and wrists slammed against the walls of the arena, pulling down the wall here and there.
"no way! this is like a scam!"petros was so frustrated.
 a huge creature that could destroy everything on the stage appeared.
new novel chapters are published on lightnovelworld.
c­om"man, when i did the research, there was nothing like this in your possession, necromancer! then did you hide it even when you fought our demon king?"while petros's bewildered voice was resounding, sungwoo's voice echoed softly under the huge shadow.
"hey, clown, just sit back and watch if your great warrior can be the david the great!"the situation reversed in sungwoo's favor.
- round 1 has begun!as soon as the message announcing the start of the game rang, something heavy and huge moved.
 and the whole stadium collapsed.
***

something mumbled in her head.
 isabella stopped on the spot.
'what the heck is this?'she felt dizzy.
 when she showed her abnormal behavior, jisu and other players also stopped.
".
.
.
"no one opened their mouths.
with her hands tied, isabella has been dragged for their attack on the demon king's castle.
because of that, she was raging with anger and shame, but at the same time, she recalled some childhood memories because she had similar experiences like this.
'what was it? was there anything like that?'but she could not recall it.
 she was obviously trying to remember something, but her memory disappeared as if it had gone dark.
'what is it? is my memory correct?'she didn't have any childhood days from the beginning.
 when she somehow recalled her earliest memories, she, who had a red and huge body, woke up in the middle of a damp rainforest in the amazon.
 and the first emotions that she felt were anger, which was instinct anger.
 something hot rose from the inside of her throat.
on the first day she opened her eyes, she used her powerful body and magic to kill all the monsters and players in her area.
and now she got furious like she did at that time.
but she was unable to translate her anger into action right away, so her body began to react abnormally as if something had gone wrong.
this time she reacted by questioning herself first.
'why am i always angry? what is the reason? why?'something came to her mind.
 it was a voice that ordered her to destroy and conquer somebody.
 it wasn't her voice, but something like that was churning in her head and moving her.
 her pupils dilated and her mouth opened.
 it felt as if her breath was about to come out at any moment.
visit lightnovelworld.
c‌om for the best novel reading experienceat that moment someone approached her and said "isabella, you have to go now.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 