\section{chapter 197}

                             




since the betting game started, each camp’s propaganda war had grown even more intense.
the low dividend of a camp was a numerical indication of the players’ low expectations and support for that camp, which would have a great influence on their choice of the camp in the future.
in other words, this betting game was not just gambling.
 closely linked to politics, it was like an “exit survey” ahead of the decision of the next leader.
therefore, the representatives of each camp appeared on the air and made a passionate appeal like an election speech.
junghoon, the leader of the liberation guild, said, “after winning the latest battle, the liberation guild will bring about a perfect victory by attacking the dungeon in mt.
 pukhan.
 we have become stronger because we have obtained buffs as a reward for the latest victory.
 and…”he then paused for a moment to create a sense of tension.
the hidden card he prepared was quite surprising.
“in addition to the legendary items, we will share various rewards with the founding groups of the “metropolitan players coalition”, which i am currently preparing to establish, so we can seek an equal distribution of power.
”he even decided to share the ‘legendary grade items’, the reward for the successful attack of the dungeon.
 in other words, the liberation guild chose to respect the sentiment of the allied players as much as possible.
on the other hand, people paid intense attention to what kind of card the demon camp, whose support base was weak, would play.
the demon camp also expressed their strong determination to win.
 the ‘chairman’ of the reconstruction alliance, who had been hiding his identity far, appeared in person on the air.
-[live] demon camp’s official broadcast: direct announcement by the chairman of the reconstruction alliance (45,655 viewers watching)“dear viewers, thank you for watching our broadcast.
 let me introduce him to you for the first time.
 now, this is the chairman of the reconstruction alliance.
”as soon as the emcee announced, a gray-haired old man with a stern expression appeared.
however, the chat window quickly started to become noisy, for someone who any korean would know for sure appeared.

[real time chat]- ahn jung-hyuk 2: ????- gwangmyeong brown bear: ?????- shin mango: isn’t he younghwan lee, the chairman of chonsang group?- y jinho: that “bulldozer” younghwan lee?- jj song: right! wow, he is still in great shape even when the whole world is collapsing.
 i hear rumors that he has been in critical condition, but he seems to be healthier.
 all the rumors about him are fake!- baedal park: wow, but i didn’t even think he was the head of the reconstruction alliance.
 i thought he would act differently.
 his nickname is “bulldozer”, isn’t it?the identity of the chairman of the reconstruction alliance was none other than younghwan lee, once the chairman of korea’s largest company, the chonsang group.
he was nicknamed “bulldozer” because of his aggressive investment and bold business strategy.
 and he was surprisingly popular because of his guts.
in other words, he was influential enough to appear suddenly at such an important moment.
he opened his wrinkled mouth.
“we will take the initiative to revive the demon camp based on our victory.
 and we are not the only force of the demo camp.
 i know there are many players of the demon camp in busan.
”as if he intended it, he continued to speak somewhat arrogantly.
“we want to interact with them, and we are willing to give them two of the legendary items given as a reward for our successful attack.
 and…”he lifted his index finger, which meant numeric number 1.

“i will give one legendary item to an independent player who chooses the demon camp in the future.
 it’s simple.
 you just need to keep your ‘betting certificate’ and visit the demon camp with it.
 i’m going to announce the details to the community.
”to put it simply, he presented the legendary grade item as something like a “lottery prize”.
although it was a dilemma for those players who hadn’t yet decided which camp to choose, lee’s offer was certainly appealing to them.
[real time chat]- insok park: wow, this is great! isn’t it a golden chance to win the legendary item?- youngrok: yeah, the bulldozer chairman is different.
 he’s generous!- seong-sung lee: chairman! we trust you!- gwangmyeong brown bear: man, he won my trust all of a sudden.
 so, the ceo of the demon camp is younghwan lee…like this, both camps offered a big reward item as an invitation to the players to join their camp.
 it meant that this event was a matter of life and death to both camps.
if that’s the case, what would the third camp, the most promising candidate for the championship, present as an enticement?people waited for the necromancer’s announcement with considerable anticipation.
they believed he would be able to come up with something surprising even if he didn’t offer any reward.
however, twelve hours before they entered the dungeon, there was some unexpected news in the community.
[622] i’m in suwon right now, but there is some smoke rising from the main base of the necromancer.
 what is this?-author: strongest sergeant │ hits: 41,443i have a hideout near suwon.
 while i was passing by, i saw a lot of smoke rising from haenggung-dong.
 did somebody attack again? i’m hearing the fighting noise.
 did somebody attack when they let down their guard with the competition around the corner?[comments: 13]at first, it was only a small thread.
 somebody made up a conspiracy story about the “necromancer’s crisis.
” but the initial reaction of those who saw that thread was very lukewarm.
[comments: 13]- kim min-cheol0456: what? terror kim went there to attack the necromancer, he was badly beaten, right?└ mokpo man: even the wyvern group ate them all.
 you are free to go there, but never get out as you wish.
└ baedal park: come to think of it, are they already doing a campfire to celebrate their victory?└ strongest sergeant: yeah, that’s an ambush.
 i saw them ambushing the necromancer and getting out.
 it looks like they suffered big damage.
 i think the necromancer was ambushed.
 come to think of it, terror kim went there for a surprise attack.
└ lee yoo-yeon: what the heck? are you serious?└ bus driver: i don’t think so.
 if you look at the fights we have won until now, it’s the necromancer who made a surprise attack first.
 what if he was ambushed?this time, another player appeared, saying that he was near the main base of the necromancer.
 he uploaded pictures of black smoke rising, and there ensued heated controversy.
[comments: 27]- lee yoo-yeon: that’s right.
 that’s where terror kim appeared on the air.
- yasuo 1: man, he got killed, then?- masan wizard: but who dares to attack the necromancer? was there anyone who dared to attack him though he destroyed the pirates?

└ lks: yeah, i don’t think so.
 if this is true, he might be the strongest man on earth.
└ gong jinsu: does it mean there has emerged a guy who can confront the necromancer?└ exchange dragon: oh, isn’t he from the fourth camp? the appearance of a hermit master?└ strong stone: i’m really curious who he is.
now, they began to post a series of comments praising the unknown group who attacked the necromancer.
 these comments made it a fait accompli that the necromancer was ambushed while emphasizing the prominent role of the attackers, which naturally led everybody to get curious about the identity of the attackers.
“alright!”there was someone who had been monitoring the whole situation.
 it was hanho.
“now, our troll farm threw the bait! it’s time for our actor to appear.
 dispatch him!”when he said that, kyongsu brought someone out.
 he was the leader of the “hunter company” who had been held captive.
kyongsu untied him and presented a cellphone to him.
“just do it.
”when kyongsu demanded, the team leader frowned and expressed his strong displeasure.
“our company won’t like the way i’m doing this.
 our company values its good image.
 so, they don’t want me to get involved in manipulating…”“what are you going to do if you don’t like it? do you think they can start an all-out war with us by posting a rebuttal?”“this is not something i can decide.
”“gosh, do you want to talk to the necromancer if you don’t want it? but he tends to use a scythe instead of talking with someone like you.
”

 