\section{chapter 398}

the water spirits smashed hundreds of terracotta at once and devoured more terracotta than that.





"whew! good job!"if it was an ordinary wave, they would have lost their kinetic energy, but li wei's high-grade spirits were not yet satisfied.
 when the waves were weakened after they collided with the terracotta, they began to move wildly, changing their positions this time.
kugugugugu-then, a vortex occurred.
 the spirits crushed the terracotta they swallowed like a mixer, increasing their rotation speed more and more.
soon they rose like a volcanic eruption, and using their rotational speed, they began to throw out the crushed terracotta fragments in their bodies towards the enemy.
puck! puck! puck! as if to explode claymores one after another, the fragments hit the terracotta standing nearby, destroying hundreds of them at once.
"hey, i don't know when i enjoyed this pleasure last…"li wei, who had stayed helpless for quite some time, finally returned to the top of the chinna serve 2 rankings.
 sungwoo was looking somewhere amid such a chaotic moment.
".
.
.
"and he injected mana cautiously, looking at some place.
***meanwhile, while the emperor and the necromancer were fighting fiercely.
 the other chinese troops, namely spear unit and arrow unit, continued to attack the castle wall.
"while his majesty is confronting the necromancer, we're going to capture the wall! charge!"those who led the attack were the 'kesik cavalry' of the mongolian server.
 they rushed towards the castle wall after barely avoiding the bombing by the airships.
the moment they passed by, they quickly escaped after pouring all kinds of attacks using bombs and skills.
bang! bang! bang! bang!a large number of troops defending the wall were caught up in the explosions.
the explosions were like an attack by a dive bomber, so it was not easy to shoot them down because they hit and ran in an instant.
 
"shit! they are so fast!"with the bombing raining down on the allied forces defending the wall, kyungsoo ran through the gray smoke to the wall.
"get out of the way, everybody!"he looked at the highest point of the wall, something covered with a blue cloth.
four blacksmiths were lying on the floor, avoiding the bombardment.
"open the statue!"when he shouted, the blacksmiths raised themselves then took out the tent right away.
the masterpiece revealed its splendor.
- 'statue of the guardian' gives the effect 'presence of wonder' to the area.
1) all stats will increase.
 (+10)2) physical defense and magic resistance increase.
 (+100%)3) the 'holy shield' is granted and strengthened.
 (+200%)when the shimmering light spread out, a huge buff was wrapped around all the defensive forces on the wall.
 the buff effect was also applied to the wall itself.
 this was not the end.
- 'guardian's statue' shoots 'petrification beam' every minute.
in an instant, a white beam of light flashed out from the stone statue's chest, one of the scales of the armor, 'aegis'.
zeeeeeeeeeng-the keshik cavalry hurriedly moved to avoid the light, but no matter how fast they were, they couldn't beat the light.
 a beam of light swept through the entire squadron of the cavalry.
11 soldiers and 11 horses turned to stone with just one strike then collapsed helplessly.
"what the heck is that?"the keshik cavalry, startled by the power of the petrification beam, began to scatter in all directions.
 then, they switched to a formation that kept a distance from each other in order to minimize damage from the enemy's further attacks.

"they can't keep shooting the beam!"after they found out the mechanism of the petrification beam, they made a bold decision.
"squadron 17, destroy that statue now!"one squadron descended sharply towards the statue.
 they were holding something like leather-pouch bombs in their hands.
 "they're coming! defend the statue!"the world tree camp also moved to counterattack.
 archers with automatic crossbows lined up in front of the statue.
then, they fired hundreds of arrows toward the sky all at once, forming a curtain of bullets.
tung! tung! tung! tung! tung!however, when the two horsemen at the front lifted the shields, a huge shield appeared to bounce back all the flying arrows.
"uh? they're still attacking?"even though they prepared several countermeasures, they could not deal with the enemies properly because the latter moved so fast.
dozens of bomb bags were already raining down on their heads and the statues.
 they had no time to attack the enemy's attack.
 "spread the shield…"it was late, too.
 even the wizards did not have enough time to cast magic.
 at that moment, something passed by the pouch-bombs.
 the next moment, all the pouch bombs exploded in the air and scattered in the wrong direction.
even though fierce flames passed through the castle wall, the defending troops could avoid their direct attack.
"we have survived!"it was really a close call.
 "spread the shield right now!" it was a valkyrie who shouted at them.
 she ripped the pouch bombs then rushed straight towards the keshik cavalry.
"uh? it's that bitch! stop her!"the horseman shouting at the front was beheaded right away.
 then, she cut another four enemies then leaped to a higher place using their corpses as a stepping stone.
shheeeeeeeeek! shheeeeeeeeek!although the enemies fired arrows, she circled to avoid them and penetrated deep into the main base of the keshik cavalry.
"who the hell is that bitch?""kill her!"she was surrounded by enemies.
 she rolled her eyes.
 there were 86 people within her striking range.
 it looked like they entered the cave of a hungry tiger.
 she began to pierce them with the spear.
 all of a sudden a blue flame was swirling around the sword.
 it was like a wick on fire.
the next moment dozens of blue blades exploded in the middle of the cavalry as if they had penetrated the enemy's bellies and detonated bombs.
 dozens of players and dozens of horses were torn to pieces.
 red blood splattered along the length of the blades, creating a crazy scene as if a brush soaked in red paint was stirred around.
"let me summon them…"as soon as she said that, 20 einherjars jumped out from behind her.
"sweep them away!"at her simple and clear command, einherjars jumped out in all directions and began to hunt the keshik cavalry in a one-sided attack.
"argh!""ahhhhhhhhhh!"whenever einherjars moved, thousands of cavalry floating in the sky fell.
"no way!"general lee shouted in shock.
 

according to his original operation, he would send the kesik cavalry as an advance party to break the fighting spirit of the allied forces before launching a frontal attack.
he had never imagined that the entire keshik cavalry would be swept away even before they reached the call.
"was valkyrie so powerful like that? aside from the necromancer, they were far superior to us!"the royal secret service, the bodyguard service under the direct control of the emperor, carefully analyzed the opponent's power and sent a report to gen.
 lee, but their analysis was wrong.
 "damn it, we might be ruined…"he nervously turned his head.
 the battle between the emperor and the necromancer was in full swing behind him.
 "whew! our emperor is great!"fortunately, the emperor's army was holding out strongly.
even though the necromancer and the water spirits attacked them in various ways, they were overwhelming numerically.
 and even now additional troops were pouring out from the 'sky barracks.
'"yeah, i don't have to worry at all.
"general lee was amazed again about the emperor's power.
 obviously, he was strong enough to occupy the entire world.
 he nodded again in relief.
"yeah, he's going to end the fight anyway, so we have to hold out here until then…"but he soon realized that it was too early for him to let out a sigh of relief.
kwagaguaguga!suddenly, the world shook and the earth twisted.
 at the same time, his face turned red.
it was light.
 a very dark light came out from somewhere.
 "what is it?"the earth was turned upside down and flames soared.
 the emperor's army was swallowed up by that instantly.
 not only that but everything on the battlefield was engulfed in red flames.
it was a huge explosion.
 because of that shock, everybody on the battlefield stopped fighting.
 they lowered their posture and protected their heads then looked at the dark light with worried eyes.
 at the moment when everything paused, something more important than the explosion was happening.
'what the hell is that?'

 