\section{chapter 418}

not long after the war ended, the world tree camp was busy on the runway.





the combined fleet did a brief maintenance of their warships, then they were put on various missions immediately.
"the 2nd hypergate mana injection is successful, and the jump space is ready to start!"they prepared a separate space called 'jump space' on one side of the runway in case they would use the hypergate more frequently.
 it was a huge steel structure like an airship dock in east potomac park in washington, dc, and served as a kind of support to install a hypergate away from the ground.
"there is no risk of collision when i double check around the exit!"the reason the hyperspace had to be installed at a high place was because there was a risk of colliding with the ground or surrounding buildings immediately after the airship passed the hypergate.
"operate hyperspace!"as soon as inho ordered, the space between the two iron pillars was distorted, and the passage to beijing was opened.
woooooo-some of the "first expeditionary fleet" that was dispatched to beijing began to return.
meanwhile, the '2nd expeditionary fleet' was waiting behind the hypergate to head for beijing.
"a total of 7 units of the 1st expeditionary fleet have returned! the 2nd expeditionary fleet begins to move in!"it was a kind of shift of duty, which was part of the "supplied transportation operation" to collect as much as possible of the strategic supplies piled up in beijing.
"wow, look at what's piled up on the deck! it would be a huge job to organize them in the warehouse.
"the 1st expeditionary fleet, returning from the chinese server, was loaded with lots of stuff on the stern.
 the inside of the airship was probably full.

in order to cope with these huge supplies, the world tree camp was concentrating all its efforts on building a logistics warehouse and renovating half of the undeveloped land to turn it into a warehouse.
follow current novels on lightnov­elworld.
com"it's not just the problem of the warehouse.
 we also have to build the lodgings for those coming in!""oh, you're right.
 it's not just supplies that come in this time, right?"it wasn't just gold or supplies that they collected from the chinese server.
the so-called 'hiring operation' to recruit talented players in the manufacturing and life fields for the world tree camp was also in full swing.
"i heard that a whole group of blacksmiths is joining us this time.
 i feel like all the engineers around the world are gathering here.
""you bet.
 team leader kim of the world tree workshop has been absorbed into researching something day and night.
 there is no guarantee that he is not going to be pushed aside by these foreign engineers, right? man, kim is a real tough cookie!"given the nature of this game, one talented person who has grown up properly could outperform even ten, 100, and more than 1,000 people.
'things are changing so much every day.
'sungwoo was looking down at the scene on the ground from the new administration center 'order tower' in the southern part of the world tree camp.
this was a building built in just a few days by muyon who had extraordinary architectural skills after the museum building became unusable due to the growth of the world tree.
 in addition, muyon and his helpers built many other buildings as best as they could.
rattle-at that moment arnold hirst came to sungwoo's office.
 sungwoo called him a few hours ago because the 2nd expeditionary fleet needed urgent maintenance, so he arrived only now.
 
"oh, you have arrived.
""well,.
.
.
"as always, he had a sullen expression on his face.
"um, why did you call me this time?"the most up-to-date novels are published on lightnov­elworld.
comsungwoo sat opposite him on the sofa and said, "is your construction of suwon center going well? is that space enough?"tomorrow, a large number of employees from the hearst workshop in washington were due to move in.
 so he was in the process of building the 'hearst workshop - suwon center.
'hearst nodded and said, "i think we can even build something like empire state building in three days with that master mr.
 lee"of course, what he meant by 'master lee' was muyon.
"the reason i have invited you here is that i want to leave a project to you.
""huh, that's fine.
 so what is it?"sungwoo turned his head and looked at the airships floating in the air outside the window.
 it was the expeditionary fleet that just returned.
"the blacksmith team from the chinese server will join us soon.
"hearst's eyebrows twitched.
he said, "what? are you saying you want me to team up with them this time?""yes.
 they are capable and talented.
 they will be helpful to you.
"if the us server has hearst workshop and the korean server has the world tree workshop, the chinese server has this 'kuyaja facility.
'the highly sophisticated magic engineering items, such as white sacred sphere, veil shredders, and mana batteries, all used by the chinese military during this war were all made at the kuyaja facility.
"hmm, okay, i've been wanting to meet these guys who made such terrible weapons during this war.
 sure, let me meet them.
"hearst was a stubborn old man, but he had no prejudices against people.
 basically, he recognized anybody as long as they were competent.
the most up-to-date novels are published on lightnovelworld.
c­om"master hearst, let me ask you about this bluntly.
"crossing his arms, sungwoo said, "can you obtain the divine power of hephaestus or that of other blacksmiths at an early day?"when asked, hearst stroked his chin and gently nodded.
"well, i think i've found it out to some extent.
"there were two conditions for the activation of the divine power or deity.
 he could obtain temporary divine power by collecting "conditions" such as puzzles, or he could obtain the regular divine power immediately by exercising his power at the highest level.
 "every time i completed a legendary or masterpiece item, i saw a message that i was getting closer to the 'unknown condition'.
 at first, i wondered about this, but come to think of it, i think i'm reaching that divine power as a blacksmith.
"

since sungwoo already witnessed the same phenomenon in hanho, he felt what hearst said made sense.
 "great.
 then, please don't care about the grade of items.
 just make the item and obtain the divine power as soon as power.
"hearst shrugged and said, "it's fine with me, but do you know how much i have to spend every time i have to use hephaestus' anvil and fireplace? you will be surprised to know it!""how much?"as if he had a headache when sungwoo asked about the cost, hearst pulled a cigar out of his pocket and said, "well, it costs at least 100,000 gold or at most 1 million gold to operate a furnace, and it costs 1,000 gold when you hammer it on the anvil every single time.
""really? then let me assign 2 billion gold to assist in your research.
 so i really hope you can obtain the divine power and make the item that i want.
 will you?""how much did you say?"arnold hirst dropped the cigar in his mouth.
 2 billion gold?"um…"he quickly asked again, as if he thought sungwoo mentioned the wrong number, but he was obviously embarrassed, given his eyebrows wriggling.
 the source of this content is lightnovelworld.
com"alright.
 let me try.
 so what do you want? if you let me know in advance, i think i can make a blueprint on it.
"sungwoo took out an item and showed it to him.
 it was something like a rope.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 