\section{chapter 186}

                             




the monster’s body came out of the portal.
 his slim and sleek black body was similar to a human body, but his face with unclear features and horns protruding from the whole body showed that he was not from this world.
he looked around, darting his long tongue in and out as if he was looking for his first meal.
krrrrrrrrr-however, he could not help but fix his eyes on one man, namely the necromancer, who had a stronger presence than anybody else in this place.
kaaaaak! kaaaaaaaaaaah!as if he was embarrassed by the necromancer, he stepped back.
-your deity status drastically lowers the stats of the ‘lower demon’.
 (-30%)“uh?”just like the players had been overwhelmed by the alien beings earlier, the necromancer overwhelmed this alien being thanks to his demigod trait.
“i think something better than i thought would happen.
”the next moment, sungwoo jumped off the ground, grabbed the monster’s chin, and struck him down to the ground.
thud-then, sungwoo swung the grim reaper, trampling on his head with his right foot.
 the broad blade of his sword tore his tough skin and smashed his bones.
sungwoo beheaded the monster in an instant.
-you have earned 500,000 gold by hunting an ‘alien being (lower monster)’.
despite his threatening appearance, he helplessly collapsed, hit by the necromancer’s fatal attack.
 gen.
 chongong could not hide the embarrassment on his face.
“who the hell are you?”gen.
 chongong’s devil’s gate was his last resort.
 it was a self-destruction attack he launched thinking he would start all over after killing the necromancer.
but the necromancer killed his opponent so easily.
of course, there were more low-level monsters, but the necromancer could destroy the monsters that he thought of as a strategic weapon.
gen.
 chongong could not believe what happened.
“who the hell are you? what is your identity?” gen.
 chongong asked, aghast at sungwoo’s incredible fighting, but sungwoo focused on something else.

-you can make an alien being a subordinate spirit.
‘what the heck is this alien being?”sungwoo watched the swirling portal.
 to know what this alien being was, he had to go into the portal.
the portal will stay open for the next 24 hours.
 however, his demigod status would be canceled in the next 39 minutes.
 in other words, the remaining time for him was only 39 minutes.
‘it’s like a gamble to go into it.
”if he couldn’t get out of the swirling portal in 39 minutes, he might have to fight a hard battle while enduring the enormous aftereffects of his canceled demigod status.
‘i am not sure if i can endure even outside if these monsters keep coming out for 24 hours.
 can i block them?’that wasn’t just a problem for sungwoo.
[hidden quest]-title: in front of the devil’s gate-type: survival-goal: survive for 24 hours.
-reward: c-class exp card, additional differential reward.
*a curse has arrived on this earth that you cannot bear.
 the ‘devil’s gate’ has opened.
 soon, beings from the alien world will come out and trample everything on this earth.
there is not much you can do.
 just do everything you can to survive.
* the devil monster can detect living things within a certain distance.
*when you hunt the devil monster, you will be issued an ‘additional reward’ after the quest ends.
this “survival quest” was given to all players in taipei.
 given that it was not a quest like ‘attack the dungeon,’ it seemed that the average level of the players was far below the proper level of the ‘devil’s gate.
’however, only sungwoo was given a different quest.
[exclusive quest]-title: guardian’s duty-type: remove target
-goal: remove the boss monster ‘devil’s gate gatekeeper’-reward: choose ‘regular deity status’ or ‘job change right’*the alien beings have begun to invade this earth.
 you have a duty to defend this land as the ‘guardian’ who once defeated the head of the alien beings.
 if you remove the key figure (boss monster) of the invading force, you will be able to send a strong warning message to the invaders.
* the boss monster ‘devil’s gate gatekeeper’ will appear after the ‘second wave’ is over.
* if you fail to kill the target within 24 hours, you may be deprived of the title of ‘guardian.
’sungwoo obtained the title ‘guardian,’ along with the title of ‘hell repeller,’ and that’s why he was given a different quest.
‘by the way, what the heck is ‘regular deity status’?of course, what the deity status here meant was his demigod status.
 until now, sungwoo has been able to temporarily gain anubis’ power through his change to lich and the human beast ampoule.
‘however, kangsok han has always been in demigod status.
 in other words, he has a regular deity status.
’kangsok once told him that his demigod status was temporary, so he needed to learn it by himself to get its full power.
‘i think such an opportunity has finally come along.
’-while you are proceeding with the guardian’s quest, the cooldown of all your skills will be reduced.
 (-60%)at that moment, a tremendous vibration came out from the devil’s gate.
gugugugugugugu―-the ‘1st invasion wave’ has begun at the devil’s gate.
“alright, i think i can hunt these expensive monsters to my heart’s content.
”it seemed that sungwoo’s enemies always gave him quality exp.
so, he gathered all the undead in front of the portal.
 he intended to show the invaders what hell was.
now, everyone’s eyes turned to the portal where a tremendous vibration was coming out.
‘now is the time!’gen.
 chongong turned around.
 when he confirmed that his last resort failed, he had no choice but to flee the scene.
 he hurriedly moved while the necromancer was distracted by the devil monsters.
 since he was protected by a special spell, gen.
 chongong would not be attacked by devil monsters.
 so, his life would be spared if he could hide it in a place invisible to the necromancer.
however, just before going down the stairs after he went around the building, a skeleton blocked him.
rattle- rattle-it was a goblin skeleton.
“uh?”the skeleton charged at him, swinging his sword.
puck!gen.
 chongong grabbed his stomach and fell over.
“argh!”gen.
 chongong had little experience in combat, not to mention combat skills because he was protected by the numerous subordinates he had brainwashed.
as a result, he could not cope with the attack of a mere skeleton.
“i see.
 so, you want to escape alone when things don’t work out for you, right? is that all you can take responsibility for?”the necromancer arrived and stood in front of him.
“oh, my god… i heard that you had been serving the angel race for a long time.
 can i take this as the level of the players who are relying on the absolute race?”then, sungwoo turned his head to somebody behind him.
 he was the camera operator of the korean server who had been with hanho until a little while ago.
sungwoo slowly opened his mouth, looking at the camera.
“how do you believe in this kind of man and the absolute race who has this kind of man?”sungwoo asked the korean server.
“of course, i could never believe in them!”after he said that, sungwoo lifted the grim reaper.
“oh, no! wait a second!” gen.
 chongong shouted.
sungwoo shook his head and said, “i’m sorry, but i don’t have time because i have to take care of what you’ve messed up here…”he struck down the general with the grim reaper.
-you have acquired 340,000 gold by killing the “executive player” of the angel camp.


as always, those who confronted the necromancer faced a miserable last moment.
this time, sungwoo collected much more gold from him than a normal player as a reward.
in this way, the absolute race induced each faction to attack each other.
‘oh, i heard the necklace is protecting him.
’sungwoo took the necklace item in the shape of a rat skull from his neck.
[item information]-name: the devil’s gate key-class: unknown-category: necklace-effect: mana increases (+100)-description: when you wear it, you are excluded from the target of the devil monster.
 but you can get the effect by offering up a human sacrifice to the devil’s gate periodically.
 (remaining period: 13 days)*whenever you renew the validity period, you can get a ‘devil’s gate’ item.
“what the heck is this?”sungwoo was not sure exactly what gen.
 chongong’s job was, but it was clear that he continued to offer up human sacrifices to the devil’s gate, aside from brainwashing the low-level players.
in other words, gen.
 chongong was like a pseudo-religious leader who served the devil.
-angel camp’s bounty on your head has been increased.
* angel camp’s new reward: 75,000,000 goldit seemed that the angel camp’s anger toward the necromancer had intensified after he killed gen.
 chongong.
 however, simply raising the bounty didn’t mean they could stop sungwoo.
‘is this amount all they can increase under the grand name of absolute race?’the devil’s gate now began to vibrate more violently.
sungwoo turned around, thinking to himself, ‘someday i will confront the absolute race itself directly.
’the system certainly wanted such an exciting situation, but it was good for his leveling up for him to deal with them directly.


 