\section{chapter 55}

                            “what? what the heck are you talking about?”




“…explosion!”bang! bang!“ahhhhhhhhhh!”‘body explosion’ occurred in his both hands.
 the zombies that stopped moving were determined to be corpses, and thus he applied the body explosion.
 as a result, not only choi’s hands but also his shoulders were completely ripped apart and blown away.
“ahhhh!”new bones began to sprout between the wounds, but sungwoo immediately moved to stop his counterattack.
 actually, sungwoo knew how to respond in this situation, which he had learned while dealing with several vampires until now.
rattle! rattle!three werewolf skeletons jumped at him.
 thanks to synergy , they could enjoy a drastic increase in their muscle strength when attacking one opponent at the same time.
“argh!”choi twisted his body, screaming, but since he was heavily injured, he could not outmuscle the werewolf skeletons.
crunch! crunch!sungwoo ordered them to break his legs first.
 choi could no longer resist or move.
in the meantime, the other vampires were completely eradicated.
 the auditorium was suddenly quiet.
 only choi moaned occasionally.
sungwoo walked towards him and said, “well, i guess your representative appears before you to talk nonsense, or he may make you run wildly insanely.
 i don’t want it, of course.
”sungwoo then pulled the sword, which was the ‘masterless black sword’ that had belonged to the dragon knight.
“do you think a shit like you can stop the representative? he is great, great!” choi shouted.

“how can you guys exalt him so much in only six days? your brain needs to be opened for examination, i think.
”high-grade vampires acted as if they had fallen in love with the vampire lord.
“…so disgusting.
”although choi was the representative’s subordinate like skeletons under sungwoo’s authority, sungwoo liked the obedient skeletons.
crackle.
“how could you blame my representative?”puk!sungwoo stabbed his chest with the black sword right away.
 although it didn’t inflict fatal damage because it didn’t recognize the owner, its blade penetrated into his heart mercilessly.
‘nice blade.
’sungwoo knew his muscle strength had increased by six, but at the same time he could immediately feel that this ‘black sword’ item was of excellent quality.
“argh!”with his heart pierced, he vomited a pool of blood before dropping his head.
-you have earned 20,000 gold by killing a special player.
the event paid off after all.
 he received 20,000 gold.
 in other words, he earned two gold roulettes.
 besides, by beheading him, sungwoo shortened the hatching time of the “unknown egg.
”-time left until hatching: 4,949 dayssungwoo heard that the hatching time would decrease when he killed more powerful enemies.
 actually, when he beheaded the master grade vampire, the hatching time was advanced by 50 days.
 it seemed to be generous, but looking at the remaining time, the hatching time was still very far.

standing in the middle of the killing scene, sungwoo nullified the summoning of all the remaining orc skeletons.
 he felt attached to them for their great service until now, but it was time to part with them to further strengthen his forces.
 he resurrected four vampires and added them to his force.
-the dead have become your subordinate under your authority.
-‘synergy’ effect is given due to team play.
[synergy list]those who eat blood (stage 1) -category: synergy-condition: 5 vampires-effect: sucking blood when attacking (+2%), all stats increase in a ‘frenzied state’ right before being destroyed (+10%)as a result, sungwoo had the strongest possible deck.
woowoong!sungwoo’s cell phone vibrated.
 it was a secret comment posted on sungwoo’s thread.
- kor-339 (secret): it’s me, jisu.
 they started moving somewhere urgently.
 even the so-called managers around us, who were relaxed until now, suddenly started to collect weapons from us urgently, saying it’s the condition for allowing us to enter into the safety zone.
 it looks like something will happen soon.
 please reply.
anticipating that the vampires would soon search for him, sungwoo set a trap.
when a troublemaker was approaching to take the bait, it was impossible to not catch him.
 as expected, a swarm of mosquitoes were caught by the spiderwebs that sungwoo set.
“no wonder they are in a chaotic situation now.
”on one hand, sungwoo planted more reliable moles than taesung, namely hanho and jisu.
 they blended in with the survivors that the vampires had lured at the hwaseong haenggung square, and updated sungwoo about the situation there.
 and the reason why the crowds in the square became impatient was simple.
“it’s because the representative realized that his subordinates were all killed.
”the representative felt that lots of vampires who chased sungwoo until now were slaughtered at once.
 he knew he could not afford to stay relaxed anymore.
“the tables have turned.
”it was the moment when the chasers and fugitives reversed roles.
survivors in shabby clothes gathered at hwaseong haenggung square, where the citizens once spent their leisure, one of the first, magnificent cultural heritage sites in suwon.
 all the traffic noise on the wide roads disappeared completely, and only those who survived breathed nervously.
“look at that over there.
”“damn it, why did they hang it like that?”there was a large placard hanging on the wall of suwon ipark municipal art museum, located next to the square.
 the placard advertised an artist’s exhibition, but the letters were invisible because the placard was stained with blood.
 the victims were hung from the roof.
“i don’t know what happened, but it’s just unbelievable that the monster caught them.
”“you bet.
 i saw that monster killing a big wolf.
 how did he catch them?”four werewolves were stuck and hung on the spears.
 the grotesque bodies of the werewolves were clearly intended to show off the force of those who gathered the survivors.
“jisu, it’s our turn next.
 i’ve hidden a dagger on my thigh.
”jisu and hanho were mixed in with the crowds.
 about 200 gathered in the square, and as players, they were holding weapons that matched their jobs.
 but the people in the safety zone demanded they submit their weapons for control and safety reasons.
 their demands looked reasonable, but there was a wicked plot hidden behind such demands.
“hanho, look at the entrance to the museum on the right.
”“…i think i recognize who they are.
”

“yeah.
 the vampires hiding there seem to be crawling out now.
”fifteen people were coming out from the direction that she pointed to.
 she immediately felt they were vampires.
 they came out so naturally that they were far from the survivors who took pains to come to the safety zone.
 besides, it was very suspicious that all of them were wearing masks.
‘they are wearing masks to hide their canines.
’in no time a man who controlled the survivors was seen rushing toward them.
seeing him, jisu and hanho became convinced they were definitely vampires.
“does it make any sense? don’t you know how many i sent them? why are all of them defeated like that? stupid!”one of them in particular stood out conspicuously.
 he was wearing glasses in a beige suit, but only he was dressed up.
 he was shouting at his colleagues in a fit of anger.
 given that he didn’t care about the survivors in the square, he was obviously the crazy representative that sungwoo mentioned.
‘that bastard is the main culprit of this incident.
’jisu secretly hid the ‘ignition whetstone’ in a flower bed at the edge of the square.
then she submitted the other weapons as demanded.
 therefore, about 200 survivors, including jisu and han, became fully disarmed.
staying empty-handed in this hellish world made them feel nervous and uncomfortable.
 they waited only for time to enter the safety zone anxiously.
 but there were only a few who knew they would never have such an opportunity.
“they’re beginning to surround us.
”“damn it.
 i wish sungwoo could arrive quickly.
”about 30 members, including 15 vampires, began to stand at the edges of haenggung square in a move to broadly surround the survivors.
 at first glance, they seemed to protect the disarmed survivors, but they were watching the survivors with their greedy eyes.
“now, pay attention!”shortly afterwards, the man in a beige suit came forward.
 the survivors shut their mouths and turned their heads.
“uh, so… humans stopped evolving!”

 