\section{chapter 208}

                             




kate was armed with the skills and items that gave buff effects to archery, not to mention the senses she had cultivated through her lifelong training.
moreover, the combination of her first job, “sniper,” and her second job, “slayer,” optimized her abilities for long-range shooting.
 so, missing the target was unthinkable.
‘i succeeded in sniping in a harsher environment than this.
’while traversing deep in the mountains alone in the harsh environment of mt.
 taebaek, she once killed a troll unit of 33 trolls.
 she also had plenty of experience, so she was confident that if she had a chance, she would never miss the target.
“now is the time!”she had another chance to kill him because a werewolf with a huge scythe in a dark green robe appeared before them.
 he was the target that she had been eagerly looking for.
“whew…”she pulled her bow then stopped breathing.
 her fingertips stopped trembling.
the target was standing between a tiny gap about three steps behind two troll skeletons.
the target didn’t know she was aiming at him with a fatal arrow.
 as always, the prey was supposed to pour out blood under the illusion that they were safe.
tung!“you’re the same!”she muttered, watching the arrow leaving her bow.
 then, she smiled in satisfaction.
the moment the arrow left the bow, she usually sensed immediately whether it would hit the target or not.
“i got him this time.
”the silver arrow drew an arc then flew toward the target.
 the arrow passed through the narrow gap and hit the target.
 the next moment his body crumbled.
 the arrow hit the target directly.
but there was something strange.
“uh?”she could not see any blood gushing from the target.
it was a white body that was hit by an arrow and collapsed.
 why was it white?she soon made eye contact with a man, standing a few steps next to the target.
‘i am undone!’the man pulled the dark green robe from the collapsing werewolf skeleton and wrapped it around his body.

“damn it!”the man deliberately exposed a loophole.
 it was bait.
 he did it to find the sniper’s location.
 she calmed down her rough breathing as much as possible.
‘i’ve got only one shot now.
’she hastily loaded one last arrow on the bow, while keeping an eye on the real necromancer.
 even though she failed for the third time, she could kill him because she knew where he was now.
“uh? where did he go?”she didn’t take her eyes off him, but he was not there.
 her eyes began to tremble.
she had never missed the target she had once noticed, but the necromancer disappeared from his place as if he evaporated.
however, from the place where the necromancer was, she could see two waves soaring into the sky.
 with her vision that surpassed the human limit, it looked like a ghostly white tablecloth.
“what the heck is that?”but kate didn’t look away from him.
 since the target was far away from her and not threatening, she felt it was intended to draw her attention.
 she didn’t fall for such a trick.
“uh, where are you?”she quickly rolled her eyes and looked for the target among the undead.
she thought the target was somewhere among them.
at that moment, she threw herself down from the tree.
“damn it!”puck! puck!a barrage of arrows was stuck in the tree that kate left.
“ugh!”she rolled on the ground, pulled out an ordinary arrow, and loaded it on the bow.
she then fired it in the direction where the arrows were fired.
the arrow was blocked by a bone shield.
 the necromancer was standing right there.
“how dare you…”he was standing at the edge of the forest, about 300 meters from kate.
but he was a whopping 150 meters away from the troll skeletons.

the next moment, the necromancer’s body seeped into the shadows.
 she realized it was magic, but kate lost him once more.
now, she had a lot on her mind.
‘he jumped an enormous distance at once.
 did he use the skill of teleporting? but that’s a fairly advanced skill among the wizard-type skills.
 can the necromancer handle it? that doesn’t make any sense.
’soon, she got scared.
 it was the moment that she could not figure out how to understand the necromancer.
but she didn’t give up, even though she could not kill the necromancer…‘i don’t want to die!’there was something she couldn’t give up.
 pulling tight on her bow, she watched the surroundings.
 she believed that even if he was invisible, she could catch him by detecting his presence.
at that moment, something passed over her head.
 they were tablecloth ghosts.
 they made eerie cries and passed through the trees.
and the moment she witnessed them, she felt suffocated.
-you are trapped into the curse of ‘specter’.
* you are stricken with a sense of fear.
*’your moving speed’ decreases.
 (-30%)“grr… what the hell are you doing?!”she caught her breath while she was in great chaos.
 a cold sweat broke out and her heart was pounding, but she somehow tried to calm down.
she wanted to get out of this terrible situation.
 she became more and more patient.
rustling‘behind my back!’she quickly turned around and shot an arrow.
ping!however, her arrow missed the target because it was smaller than she expected.
it was a goblin skeleton, not sungwoo.
rattle- rattle-and the muzzle of the hand cannon in his hand was directed at her.
 in an instant, a sparkle came out of the muzzle.
although she lifted her arm to block it, scatter shots covered her whole body.
she was thrown up and bumped into a tree.
 because she had low defense, she couldn’t endure the damage of a powerful hand cannon.
“if you are impatient, you can’t see the target properly.
”soon, the necromancer appeared behind the tree.
 he approached her casually, then drew a silver arrow from her waistline.
“is this that arrow?”without giving a glance to her, he seemed to examine the arrow closely.
“i think i know who has made this kind of arrow.
”he turned to her, and she realized they would be defeated, no matter what.
she already began to feel something that confirmed her foreboding.
the demon camp troops began to shout with scared voices.
“it’s coming! imoogi has appeared!”scouts began to announce the appearance of the snake monster.
“where is it?”what the scout said next was enough to break the demon camp’s morale completely.
“it’s coming from behind our back!”“what? from our back? there is a dense forest behind us!”“yes, but it’s coming! damn it!”it was rather late that bone imoogi that had smashed the demon camp reappeared like this.
 but its reappearance at this time was intentional.
in other words, the snake made a big turn around the mountain to inflict a fatal blow in a place that they did not expect at all.
bone imoogi twisted its body and began to break down all the trees behind the demon camp.
 the thick trees collapsed like millet.
“what the hell is it doing?”“what is it going to do this time?”bone imoogi was blocking their retreat and removing any cover for them.
in other words, it was now in the process of removing the whole forest behind them.


“prepare the freezing skill! when the imoogi gets closer, it will freeze its joints!”“good.
 no problem!”since it was relatively thin, compared with its long body, its movement could be restricted if its joints were frozen.
however, the imoogi didn’t come any closer.
“what the heck? this time what’s it trying to do?”they began to get scared even before the snake’s attack.
as expected, with the cover of trees disappearing, a huge shadow was cast over the sky.
bone wyverns flee down from the sky.
the necromancer was tricking his enemies with his strategy, turning the tide.
“nonsense!”“shit! that’s why the snake removed the whole forest!”since they challenged the necromancer, they belatedly realized that it was almost impossible to get out of this place.
sungwoo was looking down on the battlefield from the sky through the ‘specter’.
he could see everything easily high in the sky as if he was controlling units in a real-time strategy game.
‘it’s much easier to get them all.
’from sungwoo’s point of view, he not only easily grasped the situation on the battlefield, but also he could control a large number of subordinate spirits in a more favorable position.
‘now i can respond several times faster, not to mention judging well in advance.
’the demon camp troops were moving to the position he had expected early on.
watching them heading out there, sungwoo muttered, “let me throw them over their heads.
”when a group of bone wyverns’ appeared above their heads, the players of the demon camp instantly dispersed, running wildly.
 they got scared even under their shadows.
“hide in the forest that was not yet destroyed! you will be wiped out if you stay on the ground!”the demon camp soldiers hurriedly escaped into the remaining forest, but the bonn wyverns dropped something over their heads.
kaaaaaaaaaaaaah!

 