\section{chapter 421}

kyungsoo clicked the remote control again.





"next, we have a message from mumbai, india server-2.
 but the portal here is a little different.
"unlike the previous two portals, the portal that appeared in the indian sky was red.
"there are only two portal colors that have appeared so far.
 my simple guess is that angel is blue while demon is red.
"the two absolute races started the invasion at once, but as they were clearly rivals, it seemed that they were going to appear in different regions.
kyungsoo then continued to display the slide show.
 photos from all over the world followed one another.
 looking at them as a whole, it seemed that one portal would be opened in one city per each server.
"according to the information circulating in the community on multiple servers, a 'faction quest' has been given to players who still belong to the absolute race faction.
 the gist of the quest was reportedly to make a contribution by taking part in the capture of each city.
"it was the beginning of the last struggle of the absolute race.
as the slide show was over, a heavy silence fell in the conference hall.
sungwoo stood up from his seat with a calm expression.
he said, "if this is the case, we have to delay the temporary committee…"for now, his top priority was to defend their own home turfs.
"let me contact the telecommunication center and convey your message about the indefinite delay of the temporary committee.
"sungwoo nodded at kyujngsoo's words.
as always, things changed rapidly, so they needed to adjust to the situation.
 they were once again ready for war.
"oh, by the way…"while frowning before he knew it, sungwoo uttered with a displeased expression.

"we have to keep in touch with the brazilian server, the demon lord.
 since they seem to know more than we do, we need to get as much information from them as we can.
"it was also the demon king who first informed sungwoo's party of this phenomenon.
 they may have other intentions, but for now, it was right for them to let down their guard and engage them.
you can find the rest of this content on the lightnovelworld.
com platform.
"by the way, can we trust that person?" jisu asked.
sungwoo shook his head without any hesitation.
"no.
 i didn't believe him from the beginning.
 i just had no reason to confront him.
 now that i have a reason to fight, i shouldn't trust him all the more.
"kang sok, who ranked no.
 1 on the korean server, decided to conquer the world after forming an alliance with the amazon dragon.
whatever his intentions, kang sok threw down the gauntlet at sungwoo.
this wasn't something sungwoo could take lightly.
"this guy is not going to be beneficial to us.
"even if he could prevent the destruction of the world, the world he dominated would never be beneficial to sungwoo and his allies.
***a portal was opened to all the servers around the world.
nobody knew what would come out of it, but they started to prepare for what would come next.
those who escaped from the absolute race camp prepared for resistance.
 they united to form an air defense and built a fortress.
"a number of servers have sent us a message, saying they are ready to defend us.
"
those wishing to participate in the control body wanted to stay connected with the world tree camp.
 however, some servers were terrified and even departed from the city where the portal was opened.
 that's only the beginning.
"by the way, the mongolian server has lost contact with us.
 when we contacted them, we heard that they were preparing a welcome ceremony to usher in the demon race instead of fighting against them.
 damn it, i knew they would act like this, damn bastards!"unlike the world tree camp players, the absolute race terrified most of the players belonging to other camps.
therefore, they just lost any fighting spirit as soon as they heard about the appearance of the absolute race.
"we never know what will happen if we block them from invading seoul, but can't stop them from occupying other cities…"since this situation was happening all over the world at the same time, it was not something sungwoo alone could solve.
for more, visit lightnov‌elworld.
com'after all, this is going to be a tough fight.
'sungwoo and the commanders were watching the broadcasting screen.
- a new event is about to start.
 (00:02:03)only 2 minutes were left until the event started.
"we have just received a call from the liberation guild.
 just in case, they said they placed a total of 30 flying weapons under the portal as well as large-scale attack magic.
"if they launch an attack when the remaining time is zero, they won't be able to defend with what they are armed with for now.
 since junghoon and the liberation guild knew it, they prepared the additional defense like that in advance.
- (!)a red exclamation mark.
it was a message that appeared whenever the rules of the game changed rapidly.
there was usually a lengthy explanation after that.
 that's the case this time, too.
[world season start notice]- world season 2: the age of decision (fight and obedience)survivors of the world.
.
.
 the two 'absolute races' have made an important decision.
as the solidarity of the world has loosened, they have decided to tighten it once more.
 and they will do it by way of violence, and they will start meting out a massive judgment soon.
prior to that, they have given you an 'opportunity for atonement'.
 within the next 48 hours, you can think about your mistakes and be 'obedient' to the absolute races.
folks, never forget! the most important thing is whether you can survive right now.
 that's all.
[information (important)]1) judgment by the absolute races will start simultaneously in the 'important city' of each server after 48 hours.
2) you have 'two choices (fight/obedience)' in this event, and different rules are given depending on your choice.
visit lightnovelworld.
c‌om for the best novel reading experience'man, is this what they want, after all?'the world season this time was a message apparently tried to persuade the world servers to obey, not to resist.
sungwoo then read down the two options.
1) choose to fight: you will fight against the invasion of the absolute race faction.
 if you start on one 'battlefield (city)' and 'succeed to defend' it, you can move to another 'battlefield (city)' that is still under invasion.
the 'fight ranking' is configured in real-time, and you win when you defend 80% of the entire 'battlefield (city)'.
 and the reward is granted according to your ranking.


* 1st place: 3 myth grade item boxes* 2nd place: 2 myth grade item boxes* 3rd place: 1 myth grade item box* 4th to 10th place: legendary grade item box* 11th to 100th place: hero grade item box (2 pcs)* 101st~1,000th place: hero grade item box* 1,001 ~ 3,000: other item box bundle* basic victory reward: 100,000 gold2) choose to obey: you will be subordinated to the absolute race camp you have chosen and will act according to their faction quest'.
 your reward is also given according to the standards of your faction.
'certainly, things got complicated.
'because of the nuances of this message, it was highly likely that more players would join the absolute race faction again.
'and it will be impossible for those who have chosen to fight to unite as one, given the huge number of myth-grade items and legendary-grade items as the rewards.
 they are going to feel greedy in such a situation.
'since the rewards would be differentially given according to the 'fight ranking', it was highly likely that the competition among them would be fiercer than cooperation.
'it will also be clearly known who is the most powerful of all the servers in the world.
 i can't lose under any circumstances.
'you can find the rest of this content on the lightnov­elworld.
com platform.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 