\section{chapter 423}

before the invasion of the absolute races began, two options appeared before everyone's eyes.
 they were required to choose between 'fight' and 'obey'.





of course, sungwoo chose 'fight.
'- you have chosen to 'fight' against the absolute races.
 the absolute races will descend upon this land to chase you.
then the detailed rules on how to fight were presented.
[rules of fight (important)]1) when the invasion starts, you are automatically moved to the 'battlefield (city)' closest to where you are located.
* current nearest battlefield: seoul2) if you successfully defend the battlefield (city), you will see 3 nearby battlefields (city) that are currently under invasion.
 you can 'teleport' to that battlefield by selecting one of these.
3) 'points' reflected in 'fight ranking' are as follows.
* general angel/demon kill: 1 point* ranking angel/demon kill: 10 points* boss angel/demon kill: 50 points* battlefield (city) defense success: 100 points* satisfying hidden conditions: 300 pointssungwoo examined the rules slowly because he needed to set up an operation according to them.
'there are three nearby battlefields.
.
.
'with seoul as the starting point, the nearest servers were the taiwan server, the china 2 server, and the japanese server.

'great.
 as soon as i defeat the enemy in seoul, i can go help the taiwanese and chinese allies.
'taipei on the taiwan server and shanghai on the chinese server-2 were selected as battlefields, where chen and li wei were supposed to lead the defensive operation, respectively.
 since both sides are key allies of the world tree camp, it was ideal for sungwoo to quickly defend the battlefield in seoul, then move to the two places for support.
new novel chapters are published on lightnov­elworld.
com'and i have to pay attention to the fact that the defense success point is a whopping 100.
 if i follow the successive defensive success route, even those players who did nothing can score high points.
'if sungwoo did it well, he would be able to include lots of players of the world tree camp into the 'fight ranking.
'if he could do that, he could obtain a huge amount of material once again.
 besides, it was also an opportunity for sungwoo to prove and show off the power of the world tree camp once again.
'alright.
 let me use these obstacles as an opportunity.
"he encountered many obstacles, but until now, he has taken all the obstacles as a springboard to leap further.
 this time he intended to do so.
***with the absolute races' invasion around the corner, the foreign server allies gathered in the world tree camp had no choice but to return.
the first to leave the world tree camp was wpu.
 22 airships, which comprised more than two-thirds of the combined fleet of the world tree camp, took off all at once, preparing to return to the american server.
sungwoo faced jonathan in front of the 'jump space'.
"i send my best regards to chairwoman love and stick it out there as much as you can.
 i will go over there while cleaning up the nearby servers.
"the us server was very far from the korean server, so sungwoo could not directly support them like the taiwanese server or the chinese server 2.
"don't worry.
 we don't know how they will attack us, but we have the best firepower ever.
 we'll make sure they can't even stick their bread out of the hole.
"sungwoo nodded and held out his hand.
 jonathan held his hand and smiled leisurely.

"hey, jonathan!"at that moment, someone called jonathan from behind sungwoo.
"ah, master hearst, you must be very busy right now.
 how come you came out in person?'"can't i get some fresh air? i've loaded cannons on airship no.
 18 and airship no.
 21.
 so try firing a couple of test shots and judge whether you want to keep using them.
"although the wpu fleet decided to return, the members of the hearst workshop decided to stay in suwon.
 no matter what, this place, the headquarters of the world tree camp, was the safest, so they could produce weapons without any damage.
 what's more, there were more than enough supplies everywhere.
"oh, please let nobody touch my workshop.
"new novel chapters are published on lightnov‌elworld.
c­om"of course.
 we will defend your workshop well like new.
"jonathan grabbed the ladder that came down from the airship.
"then, good luck!"the ladder went up automatically, and jonathan disappeared into the airship.
woowoowoo~soon the wpu fleet began to enter through the hypergate.
"since half of the airship departed, i already miss them, even though they are not ours.
"as kyungsoo said, sungwoo felt like the sky was empty.
 obviously, there was something like a power gap with the exit of the wpu airships.
but there was another way.
 sungwoo turned to hearst.
 he momentarily flinched at sungwoo's sharp glance.
 obviously, sungwoo was full of wariness.
"master hearst, how many airships can you build in the next 48 hours?"hearst nodded as if he expected such a question.
"well, two ships are already in the final checkup stage.
 i think i can build four more.
 if i really push the blacksmiths hard, i can build up to five ships.
"since hearst had enormous resources and skilled technicians, he could build them like factory items if they wanted.
"alright.
 i hope that you encourage them a little more and build up to seven ships.
"the reason why they were so powerful was that they could demonstrate 200% or 300% of their abilities with their health as a backup in case of emergency.
***the battlefield for the korean server was seoul.
 to be precise, the blue portal of the angel race was opened in jongro, downtown seoul.
with 43 hours remaining until the start of the invasion, an officer from the general control office reported on behalf of the busy kyungsoo.
"we've got a report from the liberation guild! they are creating a space by refurbishing the terrain under the portal in jongro, so they can provide a space for cover and flying weapons!"the source of this content is lightnovelworld.
comthe main base of the liberation guild was still in yeongdeungpo, so they were in the process of checking the place and doing the necessary work as an advance squadron.
the world tree camp decided to join them during the remaining 12 hours, so they were supposed to check their equipment and go through operational training until then.
"that's it.
 if we have any additional information, we will let you know right away!"many people still had a hard time facing the necromancer in person.
 was it because his image as the necromancer was so tough?"got it.
 keep up the good work!"

having said it, he looked up at the sky.
"oh, sungwoo, they're starting drilling again!"now, sungwoo and hanho, standing on the runway, were watching those riding hippogriffs staging a war drill in the sky.
woo woo woo-eleven airships cast dark shadows over the runway.
 right after that, hundreds of small shadows were separated from the huge shadow.
whooooo!they were one griffin and 213 hippogriffs.
'how fast they are!'their flight was truly spectacular.
the sound of engines shaking the air, the sound of hundreds of wings hitting the wind, and even the shouts of the riders aboard the hippogriffs got mixed and resounded throughout the sky.
when they blended with the shadows on the runway, it was as if they were watching a performance in the air.
"wow! the world tree fleet and special commando unit are so cool!"of course, heyon and griffin were at the forefront of their swinging movement in the air.
"let's go, griffin!"visit lightnovelworld.
com for the best novel reading experiencea slightly larger than hippogriff, griffin flew through the sky with more agility than anything else.
beep! you can also read this novel on the more advanced platform lightnovelspot.
com

 