\section{chapter 194}






 this item was also available in the secret store at kimpo airport.
at the time, after thinking hard about it, he gave it a pass to save money to buy more expensive items.
-7 seconds left.
“purchase!”now that he had a huge amount of gold, he could buy one without any hesitation.
-the second item has been revealed.
[item information]-name: asura’s robe-grade: legend-category: overcoat-effect: agility increases (+2), stamina increases (+3).
 if you put your hands together, the four arms engraved on the robe activate and last for 10 minutes.
 (wait for reuse: 1 hour)* price: 6,000,000 gold‘the price is twice as high as the first item.
’sungwoo was already wearing a ‘shadow king’s robes’ item in the ‘overcoat’ category.
the ‘asura’s robe’ item had better stats, but sungwoo needed to stick to the shadow king’s robe for the set item effect.
-5 seconds left.
‘by the way, it protrudes four arms? isn’t it too ugly?’but sungwoo could not give up this good item because of that.
“purchase! well, let me give it to hanho.
 he can throw more daggers if he wears this.
”sungwoo felt that it would be more beneficial to give it to hanho than not to buy it.
-the third item has been released.
[item information]-name: universal key-grade: special-category: consumption-effect: can open all locked locks.
 it is destroyed when you use it just once.
* price: 9,000,000 golda universal key? sungwoo had never seen an object called “lock” until now.
he wondered if it appeared in a treasure box.
‘can it unlock the area restrictions, too?”come to think of it, sungwoo had a “purple chain” that closed access to a certain area with a similar icon, but he didn’t know whether this universal key could solve it, too.
“purchase!”since he didn’t know when he would find this item useful, he thought he had better buy it.
-the fourth item has been revealed.
[item information]-name: goblin face armor-grade: legend-category: mask
-effect: when you wear it, the damage of the ‘sword’ increases in proportion to the ‘agility’.
 you can detect the presence of people around you more clearly.
 (+20%)* price: 12,000,000 gold“this one …”its appearance was a face armor that looked as if only the lower part was separated from the face of a goblin.
after checking closely the effect of the item, sungwoo decided to buy it too.
“looking at the effect, this item is perfect for jisu!”jisu’s agility was high, so when she wore it, she could maximize its effect in terms of her senses.
sungwoo wanted to buy one item for her because he already purchased one for hanho.
-7 seconds left.
apart from that, jisu was a player worth investing in.
 except for sungwoo, she was stronger than any other player with her overwhelming strength.
although she could not summon subordinate spirits or use aoe skills to kill a large number of enemies like sungwoo, she was superior to him in terms of individual power.
“purchase!”jisu has always been playing a bigger role than expected, so sungwoo believed that if she could get stronger, she could display her skills much better than now.
-the fifth item has been revealed.
and now it was time that the last item appeared.
“what the heck is this…”sungwoo once again checked the letters that appeared before his eyes.
“myth grade?”among the items available at the secret shop, the most expensive one was the fifth item.
in other words, it was clear that it was a terrific item.
‘what a terrific item!’[item information]-name: 600kg bow-grade: myth-category: bow-effect: an ordinary person can never pull this bow.
 (using condition: 100 or more muscle strength)when the user pulls the bowstring, an arrow is automatically generated, and the “fall of the sun” skill is activated at the hit point.
+ fall of the sun: causes a wide range of explosion and flame magic near the target area.
 you should exercise caution when using it because it can destroy the whole area.
 (waiting for reuse: 10 days)+ unconfirmed set effect: triggered when holding 600kg bow* price: 15,000,000 gold“myth level?”apart from everything, this was a “myth” grade item.
 sungwoo has never seen a myth grade item except “the seeds of the world tree” until now.
given the influence of the seeds of the world tree, sungwoo was well aware that the meaning of the myth grade was enormous.
‘that’s why the terms of use are so strict.
’-8 seconds left.
the value of muscle strength required to pull just one arrow was a whopping 100.
 even if sungwoo, wearing all the buffs, such as lich and anubis, brought out his maximum strength, the most he could get was only 57.
in other words, it would take a tremendous amount of time and effort for sungwoo to pull this.
‘of course, although i can’t use it right away, i have to buy it.
’
-3 seconds left.
“purchase!”of course, sungwoo never bought it on an impulse because he never knew when he could get another chance to buy these items.
-item disclosure has ended.
-you will exit after 10 seconds.
this was the end of his shopping.
he spent a total of 45 million gold.
 he used a lot of gold to get quality items.
 nonetheless, he still had 100 million gold left.
it meant that sungwoo could pick this kind of valuable item twice more.
 of course, the key was how to obtain a coupon for the secret shop.
‘after all, it was unreasonable for me to expect the shadow king’s item.
’what he felt regrettable was that there were no items related to ‘the shadow king’s legacy’.
 of course, it was chosen at random, so it was unlikely that he would get this item.
‘well, i still have one more item, so let me find a way to get it.
’if the shadow king’s legacy was completed, he expected a tremendous increase in power.
***“uh? are you sure you are giving it to me as a gift?”hanho, who was fidgeting with the two daggers he had obtained a while ago, felt suspicious rather than feeling gratitude for the gift sungwoo gave him.
“you aren’t taking it away from me after giving it to me, right? you remember that japanese sword you gave me, then took it back.
”“japanese sword?”when sungwoo tilted his head, hanho opened his eyes wide and said, “you gave it to me l then took it back from me on campus.
 you even threatened me, telling me you would give it back to me if i cut my arm.
”“man, how come you still remember that?”“well, i have a good memory.
 i’m writing down in my diary all the bad things that you have done to me.
 you remember you threw me into a helicopter, right? please do not forget.
 if you forget, i have to explain to you later when i get even with you.
”“hey, i didn’t throw you! i gave you a helicopter.
 if you don’t want it, let me give it to uncle minsok.
”snorting at him, sungwoo withdrew his hand, but hanho quickly took it back.
 his pride wasn’t strong enough for him to give up a legendary grade gift.
“oh, no! got it, sungwoo! i was kidding.
”hanho finally threw off the “thief hood” that he had acquired during his first level up then put on a new item.
 then, he showed off fully after taking out the two daggers.
“hahahaha.
 four arms behind my back! great!”sungwoo also gave a gift to jisu.
 it was a legendary-grade item, ‘goblin face armor’.
she looked at him blankly as if she never expected such a gift from him.
“really? are you giving me a gift, too?”“i think this item is perfect for you.
”“oh, i see…”jisu smiled softly after checking the item information.
 it was a huge option item that she could not easily obtain.
“thank you.
 i can sense the presence of others with this? it looks like i can serve better with this sensor.
”“i look forward to it, jisu.
”although she said that as a joke, she could serve as a much powerful surveillance sensor with that face armor, in addition to her transcendental senses.
 “oh, i got it!” hanho clapped his hands as if he remembered something.
 “because i kept watching the liberation guild broadcast.
”“why? what happened?”if jisu was like a senor, in reality, hanho was always gathering new information as a virtual sensor.
“there was fierce fighting in various places in the north of seoul, but now it seems that there has emerged a winner.
”the “fight for control of the metropolitan area (1)” event that took place a few days ago was still going on.
 several battles were fought, leaving hundreds of victims.
 now, the angel camp was emerging as the winner of the battle.
“a few hours ago, the deputy commander announced it in the broadcast briefly.
 the broadcast ended a moment ago, but given his words that the end of the fight was near, it seems the angel camp guys are now advancing to their opponent’s last stronghold in mt.
 pukhan, i think.
”when they occupied a total of three bases, they would receive tremendous buffs marked by an increase in attack and defense by 30% for seven days.
although the expected buffs did not have a big impact from an individual perspective, they would bring about an overwhelming gap in the strength of their forces in large-scale battles.
in other words, if they won this battle, they would have an opportunity to completely eradicate the opponent’s camp.
‘that’s why both camps have no choice but to make an all-out effort to defeat each other.
 i remember hearing at first that the reconstruction alliance was winning the battle at first…’the power of the reconstruction alliance was stronger than expected.
 with the so-called ‘skoll troops’ as their main force, they pushed the advance team of the angel camp to the brink of annihilation.
‘but that was their last push.
’according to hanho’s explanation, the tide was turned when the crusader team taking side with the angel camp appeared after that.
“man, i have to admit the crusader team’s defense was the best.
 i guess there were as many as 75 guys armed with full plate armor.
 they put on shields and all kinds of buffs before aggressively pushing forward.
 they didn’t budge at all even though arrows rained down on them endlessly.
”the reconstruction alliance fighters couldn’t defeat the crusader team wearing hard armor and shields despite their overwhelming firepower.
“the youngdungpo prosecutor stuck a flag on the ground to use an aoe buff, while the priests in the rear continued to heal each of the crusader team members fighting the reconstruction alliance guys.
 in my opinion, junghoon’s troops were well organized.
”fighting against the reconstruction alliance’s tremendous firepower from the front, the crusaders rushed through the railroads of kwangwoon university.
 then, they swept awaythe skoll troops immediately, the pride of the reconstruction alliance.
 the scenes of the crusaders crushing the skoll troops were broadcast live to 110,000 people.
“to be honest, their fight scenes were cool.
”the viewers who were not impressed with other fighting scenes could not help but feel thrilled at the crusaders’ fantastic performance.
“yeah, the crusaders have always been strong.
”sungwoo thought the world of them.
 they weren’t on the same battlefield where the necromancer fought, so their fighting was given more prominence.
 nonetheless, the crusaders, composed of a total of 75 players, had tremendous power.
on this occasion, they once again verified their power to the entire korean server.
but sungwoo felt something different after the two camps’ fierce fight.
‘as i expected, the two camps are not my rival.
’in other words, the angel camp and the demon camp on the korean server were not powerful enough to be a big threat to sungwoo.
‘as long as there are no other variables, i can destroy them.
 let me dominate the korean server while growing the world tree.
’suddenly, sungwoo was setting up a new goal, a clear and bold goal that was markedly different from the previous one.
‘if i keep trying like this, i’ll be able to find out the cause of this phenomenon and the solution to it faster.
”as always, it took power to find out the truth.
***exactly 14 hours later, the official statement of the liberation guild appeared in the community.
[544] liberation guild’s official statement about the fight for the control of the metropolitan area.
-author: youngdungpo prosecutor │ hit: 45,542if you are a member of a specific camp, you may have already heard the news through the system, but i would like to inform you that the angel camp, where our liberation guild is the key player, has won the ‘fight for the control of the metropolitan area (1)’.
however, we seek peace and harmony, and we do not want to conquer by force.
we want to announce to the demonic camp that if you are willing to give up a meaningless fight, please make a declaration of surrender through an official announcement, then follow the liberation guild’s demands.
 we will give you a grace period of 24 hours, starting now.
[comments: 101]“wow, they ended the fight in only one day.
 aren’t they going to use the momentum to form the coalition of survivor groups?”in the end, junghoon’s angel camp won.
 he proved that he could accomplish the mission without relying on the necromancer’s power.
 as a result, he would take control of the metropolitan area.
 in other words, he was one step closer to the creation of the coalition that he had been longing for.
but there were always variables in the system.
“well, i don’t think this is the end of the battle for the control of the metropolitan area.
”

“really? why?”“there was a number at the end of the quest’s name.
”like sungwoo said, ‘the fight for the control of the metropolitan area (1)” was the name of the quest.
 tin other words, the number suggested there could be a follow-up quest.
as soon as sungwoo said that, a variable appeared.
“uh, what the heck is this? man, are you a shaman, sungwoo?”a quest appeared.
“oh my god…if this is the case, it means we have to fight…”[war quest]-title: battle for the control of the metropolitan area (2)-key players: angel camp (korea server), devil camp (korea server), third camp (temporary)-reward: 5 legendary item boxes-condition: attack the large-scale dungeon “python’s cave” on mt.
 pukhan before other camps.
* you can enter it after a certain time.
 (35:59:59)* different entrances to the cave are provided for each camp.
– an opportunity to participate will also be given to the third camp currently under construction.
would you like to participate in the ‘war’? (y/n)and this time, the third camp affiliated with sungwoo was also included in the variable.
“war?”“are we finally participating in the war, too?”finally, the three-way war among the three camps began.
***chi-chi-chi!a great nature scene unfolded on the noisy screen.
“hello everyone? today, something shocking happened on mt.
 pukhan, so i turned it on live broadcast like this.
”a player with the nickname “reporter ahn” turned on a personal broadcast.
 he became famous because he continued to tenaciously cover and broadcast live the fighting scenes of the ‘fight for the control of the metropolitan area (1).
’in particular, after he gained a considerable exp thanks to the 80,000 people who watched the battle at kwangwoon university, he volunteered as a war correspondent for the angel camp.
“can you see it?”his camera was now capturing the hillsides of mt.
 pukhan where the day was breaking.
but there was something very strange about mt.
 pukhan.
“i think that’s the second place where the fight for the control of the metropolitan area was supposed to take place….
”wooooooh-black trees shot up from the center of the mountain.
“man, they are huge!”they quickly spread all over mt.
 pukhan like fungi.
 they formed a tremendous force by pushing out the trees that had been taking roots on the korean peninsula for a long time.
furthermore, the black branches of the trees stretched up like tentacles, intertwined with each other, and began to form a huge roof covering the entire mountain.
while constantly wriggling, the huge roof made those watching squeamish as if the whole mountain was alive.
“it seems as if the entire mt.
 pukhan has been covered with a huge dome.
 isn’t it impossible for sunlight to permeate into it even during the day? it’s a devil’s forest!”that wasn’t the end.


 