\section{chapter 341}

chapter 341: jeju island and attack on demon’s cave (5)sungwoo thought it was some kind of magic that brainwashed the players by keeping them insane but watching the scene, he thought they might use an item instead of magic.





some of them ate whole red herbs as if the potions alone were not enough.
“let’s kill the devil!”“for the sake of god!”they flocked towards the undead army, and soon there was a melee among them.
they didn’t seem to care at all that their fanatic resistance was tantamount to suicide.
as far as sungwoo knew, the only way to treat these kinds of symptoms was to kill them.
when sungwoo attacked the center of the enemy camp and engaged in a melee, hanho and inho came down to the ground with a small number of elite troops.
 then, they entered oreum through a hole in the lower floor that they broke through by bombing.
inho looked around and said, “from now on, we’re going to attack the rear of the enemy, then assist the necromancer to capture this place.
 avoid head-on clashes with the enemy as much as possible and move secretly.
”no matter how powerful the airship’s attack was, it was the job of the ground forces to finish the battle.
 of course, the undead army led by sungwoo would be strong enough to finish the job, but sometimes humans with intellect were needed to do this kind of job.
 so, they needed to stand by while preparing for that moment.
while they were climbing oreum, those at the forefront urgently gave a stop signal, and everyone fell flat on the floor.
“i’ve found a bunch of enemies.
 uh?”the scout in front looked at inho with a puzzled expression.
“even they are breaking through the invisible barrier!”breaking through the invisible barrier? inho climbed up the hill and lay down next to the scout.
 then, he looked at the place that the scout pointed to.
indeed, a group of players was tearing apart one side of the invisible barrier and infiltrating oreum.
 there were about 30, all told.
“come on, let’s go! this is a great opportunity!”“that’s where the prisoners are!”
they took advantage of the confusion caused by sungwoo’s attack and started attacking a certain building on the side of oreum.
‘it wasn’t true that the monster worshipers took over the whole island.
’inho understood the situation.
 they were the resistance army that survived on jeju island.
when they witnessed the monster worshipers’ main base attacked, they seemed to start moving for some purpose.
 however, there were lots of monster worshipers standing in their way, who poured out of the building.
“they are unbelievers!”“they’re also coming from below! kill them all!”they numbered dozens.
 and it seemed that the building the resistance army was aiming for was quite important.
“jimin! careful!”“don’t worry!”fortunately, a woman named jimin, who took the lead, fought very well.
 she, who was wearing iron knuckles, ran uphill in a flash, smashing three worshipers in the blink of an eye.
the resistance forces began to knock down the enemy guards in the building with her as the leader.
“wow! she is really cool! i might have mistaken her for jisu if she had held a sword.
”hanho was not exaggerating at all.
 inho also agreed, nodding at him.
“well, if we mount a joint attack with them, we can finish this job faster.
 i guess they might want us to join them.
”at that moment, there was suddenly an earthquake.
 with a great roar, blue light colored the sky.
 inho turned his head toward the epicenter.
“what the heck is that?”the light was bursting from the vicinity of lake baengnokdam in the center of mt.
 halla.

then, a sharp roar was heard.
“is that the god they worship?”something woke up.
***frowning, sungwoo looked at the place near the summit of mt.
 halla, where the light burst.
‘is it the monster the worshippers call god sleeping in lake baengnokdam?’monster worshipers said that the god they worshipped was sleeping near lake baengnokdam.
at that moment, some people in red cloaks stood on the altar installed in the center of oreum.
among them, an elderly-looking old man raised his arms.
“oh, oh, my god!”then, he started bowing towards the sky over lake baengnokdam.
 did they summon that god?kugugugu-the scenes of lake baengnokdam emitting blue light while shaking the whole island were certainly spectacular.
“oh, god who makes this dead land breathe! please break loose the demon’s grasp from the ruined world!”at that moment, a ray of lightning came in from the light that rose from lake baengnokdam.
clang!lightning struck the altar.
 then, the space there was distorted and a blue portal opened.
‘something is coming.
’sungwoo stepped back, very much nervous.
 at that moment, a flash of light erupted from the portal.
 the flash shattered the three bone wyverns nearby in an instant and landed on the altar again.
 soon, the light faded away and there appeared a certain creature.
“uh? is it a fox?”it was a huge, well-decorated fox the size of a brown bear.
- the field boss monster ‘kumiho’ or fox with nine tails has appeared.
but like the message that rang after that, nine tails arose behind it.
“ah, my god!”the worshipers bowed their heads at the appearance of a giant nine-tailed fox.
“lord, i’m so moved to see you before i die! ahhhh!”“god, please punish the demons!”they rolled on the ground fanatically as if they were shocked by their god’s appearance.
obviously, they believed such a monster was their god.
after examining the situation, sungwoo wondered if the nine-tailed fox had some kind of influence on this area to grow hallucinogenic herbs.
 and the players who ate the herbs turned into such fanatic believers.
“by the way, kumiho?”sungwoo smiled before he knew it.
no matter how intelligent a kumiho was, sungwoo had even bone imoogi under his control, who was superior to kumiho.
“well, i’m going to beat kumiho more easily than i think.
”

kugugugugu-at that moment, a roar began to be heard from the low floors of oreum.
as vibrations big enough to shake the whole mountain-covered oreum, kumiho raised its fur as if she felt something unusual.
grrrrrrr…then, she lowered her posture, with her blue eyes flashing.
 she was now ready to jump like a flash of light at any moment.
kwagwagagaga!at that moment, a very huge and white object soared up the steep hill.
it was bone imoogi, who opened his huge jaws towards kumiho.
it looked like an anaconda snatching a small animal that came to the lake.
kumiho jumped off the ground.
 she seemed to avoid the jaws of bone imoogi quickly, but two chains protruded from bone imoogi’s head and wrapped around kumiho’s front paws and neck.
“hey, i got him!”minsok shouted.
 riding on top of bone imoogi, he threw black chains toward kumiho.
kumiho, caught in the black chains, could not jump as far as she would like and was bitten by imoogi’s giant mouth.
the monster worshipers opened their mouths wide in shock when the monster they believed was god screamed in pain.
“oh, god!”“what’s wrong with you?”soon, there ensued a fierce fight between kumiho and bone imoogi.
 it was not god’s fight, but a monster animal’s fight.
 at some point, kumiho could no longer resist.


 