\section{chapter 455}

gangsok began to breathe in again.





then his back split in half, and his vertebrae squeezed out of his body.
that wasn't all.
 his arms and legs were twisted, and his horns grew, with his whole body twisting in a bizarre way.
"whew…"as soon as he breathed out again, the heat of the magma dissipated, and the boiling ground crumbled hard.
in other words, just by exhaling breath, gangsok got rid of sungwoo's ice breath.
then he finally raised his body.
two red horns arose from his head like a helmet, and a golden glare shone in his red eyes.
 sharp horns protruded along his spine, and his arms and legs grew long enough.
 in short, he had an eerie and majestic build.
- the boss monster 'demon king' has appeared.
"has he finally revealed himself?but sungwoo was also ready to fight again.
in the meantime, while a fierce battle was going on outside the castle, there were still "attack routes" players left in the labyrinth.
"valkyrie, over there! i see the end of this room!"the members of the no.
3 team including jisu, chen, and isabella were going down the stairs after breaking through three gates.
and finally the stairs ended and a dark hallway appeared.
"isabella, is this the lowest floor of the labyrinth?" jisu asked.
"yeah," isabella answered briefly.
since she stayed at the demon king's castle for a while, she was quite familiar with the internal structure of the labyrinth.
".
.
.
"however, jisu felt that isabella didn't speak much since she entered the labyrinth.

and she seemed to be lost in thoughts a lot.
'i don't know what she is thinking, but it's clear her mind is wandering now.
 just like i did when i saw the king of the great mountains first, she is clearly pondering over her identity.
'when jisu fell on mt.
 taebek and met the king of the great mountains, she was in a similar situation.
'at that time he told me he was embarrassed to say he had been hearing somebody's voice telling him to kill me…'so jisu asked the king if he would follow that man's voice, but the king said he would have done so only a few days ago, but he began to feel annoyed by that voice, so he would resist this time.
'then he said he often recalled some other voices.
'it's very funny and strange that the king brought up the word 'pc room.
'then he said he recalled a scene where he was talking and laughing with somebody in the pc room.
'if he were just a monster, it's impossible that he recalled such a thing.
 perhaps intellectual monsters like him …'while jisun was thinking about it, isabella, who was walking ahead, stopped, then turned around, looking at her.
"i have a question for you.
""uh?'jisu was embarrassed by that question because she wondered how this highbrow red dragon who looked down on humans asked such a question.
isabella said, "did you guys exist in this world from the beginning?""pardon?"jisu felt her question was so strange because she took it for granted all the time.
no wonder isabella didn't know anything about the outside world except for the game.
jisu said, nodding at her, "we lived a peaceful life.
 we didn't fight fiercely like this, and we didn't need to fight at all, but one day the game suddenly started.
"isabella's eyebrows twitched.

"then the purpose of this game is to drive you into a corner, and my purpose is to disturb you, right?"jisu nodded after pondering over her reply because it was true.
"then why am i so confused? i don't have any reason to be so confused like this, right?"her unnecessary thoughts and confusion were what the king of the great mountains felt.
so jisu asked, "can you hear anyone's voice trying to control you? even if it's not a real voice, but something like a voice.
"".
.
.
"isabella did not answer, which suggested she was hearing it.
"if that's the case, do it the other way around.
 if you want to find the purpose for your existence or your true identity, you should not be controlled by somebody else.
"you have to be controlled by someone.
""purpose of my existence?"but their conversation did not last long.
jisu felt something, so she drew the sword, which isabella also felt.
it was clear that something was going on beyond the darkness of the hallway.
a light, yet fierce wind blew from the other side of the hallway.
"it's coming!" isabella said.
jisu pulled her right foot back and tightened her thighs.
soon a gust of wind blew in.
"duck down, so you guys can't be blown away!" chen shouted as he was going down the stairs.
 the players crouched down on the stairs, vigilant about the darkness in the hallway.
 then, something flew from there.
"argh!"it was a human, or more precisely, a woman.
"li wei?"she was obviously li wei.
 but wasn't she with sungwoo?"li wei!"right before she was blown away by the gust and tossed on her floor, jisu ran and grabbed her.
 water spirits rushed around her, and water droplets scattered over her head.
"li wei, what happened?""it's you, jisu! what a relief! that bitch is coming!""who the hell is she?"suddenly, someone walked out of the darkness in the hallway.
 she was none other than grace.
"gosh, you guys gathered here, too?"grace smiled relaxedly, then slowly rolled her eyes.
 soon she found isabella standing behind jisu.
"uh, isabella?"the smile disappeared from grace's face.
"wait a moment, please!"she raised her wand, while jisu raised the tip of her sword.
at that moment, someone put her hand on jisu's shoulder.
 it was isabella.
"you are already tied up," isabella whispered to jisu.
"what?""look at your feet.
"

jisu looked down at her toes with her head turning to the front.
'shadow?'the shadow was weird.
 isabella was obviously basking in the lantern that sungwoo's allies were holding.
 in other words, normally the light should have come from the front while its shadow should have come from behind.
 however, her shadow was stretched very long.
'i'm trapped.
'the shadow of the staff was stretched long and already wrapped around jisu's ankle.
"vivona will take you away.
 if she can survive there, then…"jisu did not hear isabella well because her vision was blurred all of a sudden.
- caution! you are caught in the 'shackles of shadow'.
jisu began to sink into the darkness somewhere.
 she gripped the sword tightly.
 but she found it uncomfortable to move her body.
 as if she fell into the water, she felt an unknown pressure all over her body.
 she was sharply alert because she knew she would be beheaded if she let down her guard a bit.
'yeah, he is the best assassin.
 i didn't even notice him approaching me.
'but she was determined not to be defeated by this guy so easily.
'i cannot die in vain here.
 if i am missing in this important battle, more people will die.
 i've got to get out of here as soon as possible.
'jisu felt a sense of responsibility and let out a breath, and soon she reached the bottom.
it was a rough stone floor.
 she rubbed the floor with her shoes and turned his head to the right.
"i know you're there!"at that moment a pure white light poured down from the ceiling.
she frowned but didn't close her eyes.
'this time my shadow is strange.
'

 