\section{chapter 464}

reporter ahn and his assistant looked at each other with their mouths wide open.





"man, this is…""i think they are here to support the world camp.
"not only the us server but also the canadian server, the taiwan server, and the chinese server, namely, the reserve forces around the world, came out in support of the world tree camp.
"if we lose here, we are extinct anyway!""let's join hands to crack down on the demon king!"that was true.
 this was the complete entity of the world tree camp.
this was great news for sungwoo, as well.
'i can use my colleagues thanks to the warrior's privilege.
'as a matter of fact, they were a great addition to his forces.
thud! thud! thud!hyunmu, on which hanho mounted, trampled on the creatures of hell and approached sungwoo.
 behind him were jisu and li wei.
"sungwoo! have you been waiting for a long time?"sungwoo nodded silently, and hanho grinned at him.
"well, i can't let you claim the credit alone.
 i've got divine power, too!"- you have used the 'colleague selection' thanks to the warrior's privilege.
so sungwoo chose hanho, jisu, li wei, and junghoon.
the white light that spread from sungwoo's body was absorbed by their bodies.
"ugh? did you obtain this great stuff while we were away?"
they were surprised by the huge increase in their stats.
 all stats increase by a whopping 15.
 this was even more than the increase in the stats that went up when he obtained divine power.
"is that ruthless rascal the demon king?" junghoon asked.
since they were still in the labyrinth, they did not know what was going on here.
"yes, that's right.
 you have to target his face.
 it's hard to inflict any damage on his body.
"since his body was so large, it was difficult for them to inflict real damage.
what's more, hell creatures crawling out of the portals covered his entire body.
they were randomly intertwined and acted like scale armor.
"if we can break through the obstacles and seize the moment, we can deal a decisive blow to him!"sungwoo took out the superheavy bow and the superheavy arrow.
 it was the moment for him to use this lethal weapon set.
 he could inflict 2,000% additional damage to the demon king by using it with the 'sacred sword.
'"damage is 20 times the amount of technology that can kill the world tree, so even the demon king can survive this.
"but sungwoo could use these weapons only once, which meant he had to wait for the decisive and definitive moment to attack the demon king.
"okay, if you are ready…"but jisu was strange.
 she just looked at sungwoo blankly as if she was mesmerized by something.
"jisu, are you okay?"when he asked, she rolled her eyes and nodded.
"ah yeah, i'm fine.
"as if she was tired, she rubbed her face with her palm.
"she has gone through some bad things," hanho said.

"oh, i'm okay now.
"sungwoo nodded at her, and said, "okay, let's go.
 time is not on our side.
"she looked at his back, or more precisely, the grim reaper hanging on his shoulder.
'why is that shining?'it wasn't just shining.
'what the heck is that?'it was definitely seducing her.
one day a card suddenly appeared before sungwoo's eyes, then monsters appeared.
the survival game of hell began out of the blue like that.
since there was no warning, nobody could cope with it properly.
but some survived, adapted themselves, and established themselves in the new world.
ironically, however, their next opponents were themselves.
in other words, the survivors split up and waged war against each other.
there was no other choice.
 and everybody knew that the system divided them into factions, and induced them to invade and kill each other.
 even though they knew it, they could not resist the system, so they had to fight like dolls on a string.
but these players around the world who had been divided until recently became united and fought against their common enemy.
"unite behind the formations!""move as one!"the amazon rainforests were gradually torn apart while the battles were going on, and the players marched on the ruins.
"today we're going to end this hell!"players from different servers prepared to fight their common enemy by mobilizing all their skills.
 a whopping 320,000 players gathered to confront the demon king.
"as for those controlling the flying weapons, follow the direction of the 'general control room' of the world tree camp! stand by!"the general control room, led by kyungoo, worked hard to control the sudden increase in the number of troops of foreign servers.
"they are hippogriffs flying in the sky! they are our allies! don't be surprised if they get close!""you need to spread the formations a little bit more to reduce the damage by the demon king's aoe attacks!"but the enemy didn't wait until the players completely lined up.
 a battle began at the forefront of their formations.
kheeeeeeeeeh!hell creatures, which already grew in multitude, rushed in, trampling down the fallen trees.
"lead archers, ready to fire!"the players at the forefront pulled the bows at the hell creatures charging at them.
"fire!"sheeeeeeeesh!the enemies could not easily approach them"soldiers on the 2nd and 3rd rows, fire at the same time!"when so many players, armed with shields, shot arrows and cast all kinds of magic, they formed a net of firepower that could never be penetrated by anybody.
as the corpses of fel creatures piled up, players leveled up rapidly.
"come on! beef up the forces in the rear like this!"

in the meantime a large-scale shield spread over a vast area, protecting the players' heads safely.
"keep the shield from peeling off!"although they were outside the demon king's striking range, they didn't know what kind of surprise attack they would be under.
since there were so many players here, they could be out of control when they were in a big chaos.
 because of this, the defense was more important than attack.
"place mana batteries at a certain distance and supply mana potions!""captain! we've brought a lot of totems to help restore mana!"it wasn't just the players who came to support.
 they mobilized all kinds of items to maximize their combat readiness.
"great! let's keep this formation, and keep providing fire support for the necromancer!"players stopped after advancing to a certain point.
 there were very few players who had access to the demon king from the beginning.
 because of this, their general offensive would only result in pointless sacrifices and unnecessary confusion.
so they had to wait for the right time to attack while protecting themselves.
"get ready to fire air weapons!"they focused on providing stable firepower for their allies in the 'real battle' that would take place at the forefront.
 and their firepower was tremendous.
"fire!"bang! bang! bang!37 airships fired cannons at once, creating a huge wave of flames over the amazon.
 then, air weapons and large-scale magic exploded one after another, shaking the waves more ferociously.
 attacked by the firepower strong enough to destroy even a mountain, thousands of hell creatures were turned to ashes at once.
kheeeeeeeeeh! kheeeeeeeeeeeh!even if hell creatures broke through that inferno, countless arrows rained down on them, so they could not even approach the shield of the players in the first place.
"alright! keep firing!"it was as if hundreds of thousands of parts were neatly connected to make a mechanical device that rolled powerfully without any error.


 