\section{chapter 214}

                             




hanho felt the world quest this time was very unfair.
“sungwoo, when i think about the current world quest more and more, i think it’s unfair.
 don’t you think so?”“why?”“how come the system makes not only korea but the whole world our enemy? don’t you think the system is very mean to us?”sungwoo was touching the scales of the imoogi in his pocket.
-on air (!)was it because the world’s attention was focused on one place? those unidentified figures watching sungwoo closely didn’t disappear.
“they won’t dare attack us recklessly.
”“why?”although the bounty for kor-157 had been increased worldwide, it was the first time the same quest was issued on all servers.
in other words, after the world turned into a game, the biggest event was triggered with the start of the world quest.
 so, what would those foreign players who don’t know the situation of the korean server think about the “world tree camp”?“foreign server players who have only heard about us through the system messages will have no choice but to regard us as supernatural forces at least for the time being…”weren’t sungwoo, or the necromancer’s forces confronting the absolute race bravely? so, even the foreign players could not think the necromancer’s team was an easy target.
“aha? they must be scared of us, right?”“of course, they should be.
 their perception of us will make them hesitate.
 so, while they are undecided, we have to thoroughly prepare for their attack.
 this could escalate into a world war…”“world war? are you serious?”foreign players would not be able to attack the third camp led by sungwoo recklessly, but they would start investigating sungwoo sooner or later.
 after that, quite a few of them would eventually take the risk of attacking the korean server.
since they misunderstood sungwoo’s forces as supernatural, they would ally a joint attack.

‘they will come to attack us on a large-scale expedition.
’it was not an exaggeration that sungwoo said they should prepare for a world war.
“by the way, if i check our server community, there aren’t any guys who are trying to pick a fight with us.
 as you know, there were so many trying to argue with each other about this kind of fight.
 where are all of them now?”“i think they are watching our movement in secret.
”on the other hand, there was no movement at all to overthrow the necromancer on the korean server, which was very strange.
”“they are watching us in hiding? oh, they are keeping quiet because they have watched us beat our opponents so severely several times? maybe…”since they have already witnessed the results of the necromancer’s fight with his opponents several times, they must have realized that they could gain much more by maintaining a good relationship with him rather than being hostile to him.
in particular, this was a very sensitive issue for the groups belonging to the “demon camp” who had once been eliminated by the necromancer.
-[live] the official position of the ‘hwarang guild’ of the demon camp about the world quest (19,555 viewers currently watching)“the demon camp in busan, led by our “hwarang guild,” avoids extreme confrontation.
 we want peaceful and diplomatic exchanges.
 for this…”the “hwarang guild,” regarded as the strongest force in the southern part of the korean peninsula, began to appease the necromancer team.
they were conscious of the possible confrontation with the necromancer when they were mentioned as the next opponent of the necromancer in the community.
other forces followed suit.
[694] an independent group in cheongju supports the world tree camp.
-author: cheongju signboard │ hit: 21,456[697] chuncheon 188 people group would like to join the world tree camp.
-author: lee sangtae │ inquiry: 19,541[702] it’s a demon camp, but it’s a necromancer.

-author: paju’s daughter │ hits: 11,986not only those forces that have not yet belonged to any camp, as well as those who already belonged to the existing camps support and hope to join the “world tree camp” in a dramatic show of the world tree camp’s strong presence on the korean server.
[715] haven’t you guys seen this situation before?-author: kimchi master │ hit: 41,443as for the world quest, don’t you think we’re in the same situation back in 19th century-old korea when the royal government attracted foreign forces because the government troops failed to block the native farmers’ militia’s uprising? come to think of it, i feel upset when i imagine foreign players fighting like crazy to kill the necromancer.
 how about you, guys?[comments: 44]- kim min-cheol0456: you’re right.
 i belong to the angel camp, but i really can’t stand foreign server players coming here to make a big fuss.
- ko hyeongwoo: 2222 if foreign players come, i will fight with you.
 just call me.
- baekkyung: the moment i saw this quest, i found myself supporting the necromancer naturally.
- lee sh: lol.
 even if the country fails, the necromancer survives?└ 1yasuo: i should open a rice and soup restaurant near youngdungpo…└ mokpo man: isn’t it a matter of survival? what would you do if the necromancer lost to the foreign forces? do you think they will leave after defeating him? nope, you guys will be their slaves.
└ gwanggwan: stupid guys, are you going to destroy the necromancer even when the chinese pirates are attacking us? we have to join forces to stop them, regardless of whether we are on the side of the demon camp or the angel camp.
now it has become an undeniable fact that the world tree camp has emerged as the representative of the korean server in terms of their power and public opinion.
***at that time, a large “bulk carrier” was floating off the coast near tsushima of the japanese server.
doo doo doo!soon, a helicopter flew from the sea of the korean server and landed in an empty place in the cargo department of the bulk carrier at the signal of its crew.
the man who got off the helicopter was pomade-haired.
 he shook hands with the man in a white suit who was waiting for him.
“hello, mr.
 arahata!”“dr.
 yu, welcome.
 this is my first time seeing you like this.
”the two had different nationalities and spoke different languages, but the system broke such barriers and made their business possible.
“did your leader come directly to the sea?”when dr.
 yu asked, arahata shook his head.
“dr.
 yu, kumicho does not move directly to such remote areas like this.
 thank you for your generous understanding.
”“i see.
 if you don’t mind, can you tell me who i’m supposed to see instead of kumicho?”“the one who arranged this meeting is okata akira “honbucho”, who is educating the guild’s daggers.
”having said that, arahata opened the door of the compartment to the inside of the ship.
the narrow corridor leading to the cabin was lined with ugly gang members.
dr.
 yu knew that they were lined up there to break the spirits of an uncomfortable guest, but dr.
 yu continued without paying any attention to them.
“oh, i have heard of his name.
 he is the swordmaster, right?”“yes, he has been called like that for a long time.
”they walked through the corridor and carefully opened the captain’s door.
surprisingly, it was renovated into a guest room with japanese floor mats.
 given that it was more spacious than he thought, it seemed like the walls of a few rooms were broken open to make space for the guest room.
a sharp-looking man at the head table stood up when they entered.
he was the swordmaster boasting of perfect sword skills.


-his keen sensation sees through your identity.
* part of your information is exposed.
* your movement is being read.
his eyes were not human.
 they were close to the eyes of a bird of prey with the pupil torn vertically.
 his eyes moved fast and scanned dr.
 yu’s hands, neck, and eyes in turn.
only then did he open his mouth.
“dr.
 yu, thank you for coming to this place in person.
”“you’re welcome.
 it is an honor to meet you, swordmaster.
 and i’m glad i can stand behind that hilt.
”akira smiled with satisfaction at dr.
 yu’s response.
“hahaha! i’m surprised you know my nickname that they on the japanese server call me jokingly.
 i think your intelligence capabilities are great.
”the two shook hands and sat.
soon, as if it were a really important business, a dining table was prepared for them formally.
it wasn’t until after they exchanged a few more pleasantries they formally started to talk about their secret business.
“so, what you mean is that the target that you and the evolution society requested us to kill is that guy picked by the world quest yesterday, right?”“yes, he is the necromancer.
”raising the teacup, akira fell into a long agony.
“…”he fixed his eyes on the ukiyoe-style painting on the wall behind dr.
 yu.
‘isn’t this guy kor-157 of the world tree camp? players here are already clamoring to get rid of him.
 if we get tipped by our informant on the korean server and get rid of him first, this is a jackpot! wow, we’ve trapped a big shot.
’after some time, he put the teacup down and said, “i’ve been thinking about it for a long time.
 since kumicho has let me decide on that, let me dispatch my favorite commodore.
 so, you don’t have to worry, dr.
 yu.
”

 