\section{chapter 413}

no matter what the outcome, they were engaged in a fierce battle at the moment.





because of that, the winner of this fight could claim his victory proudly, and the loser could raise his honor highly in history thanks to his majestic fighting.
reporter ahn added, "everyone knows that this war will determine the winner's 'tentative supremacy' of the world.
 both sides showed overwhelming force, so no matter who would emerge as the winner, the whole world would recognize him, but this fight seems…"after all, the ending of any story was important, and the last impression of any fight would determine the first phrase that would go down in history.
at that moment a thunderous and threatening sound came out from the large speaker.
reporter ahn and commentator wong flinched.
"well, the ending of this fight makes me feel sorry for …"feel sorry? was it the right description that the commanders who were defeated in the war should hear? didn't they usually use descriptions such as 'heroic' 'gruesome' or 'courageous'?however, reporter ahn could not think of any other expressions than 'sorry' for the current fight between the necromancer and the emperor.
reporter ahn and wong kept frowning while watching the scenes on the official channel.
"the two commanders fought against each other after they were separated from their main troops, but this is a lopsided fight.
"after they entered the forge of hephaestus, the necromancer was literally punching the emperor endlessly.
"kheeeek!"the necromancer's right hand struck the back of the emperor's nose, and his left fist punched his ribs.
 the emperor wriggled in pain as if he had a seizure.
 he was wearing an item made of cloth, which had obviously a good option, but its defense against the opponent's physical damage was relatively low.
"khuuuuuuuh…"the emperor staggered backward, reaching out his hand towards sungwoo.
then five strands of threads came out.
chuchuchuchuchuchu!,
it seemed that even if he did not use the oppressor's hand, he could attack or control his opponent by spewing threads from his hand.
but the five strands of threads became oxidized and disappeared before they even touched sungwoo's body because of the flames of the 'boiling armor' covering his body.
you can find the rest of this content on the lightnov­elworld.
com platform.
"how come you throw threads at me when you keep failing? didn't you understand it yet? or can't you admit your failure?" sungwoo shouted.
actually, that's what the emperor shouted at sungwoo a little while ago.
 then sungwoo slowly approached him with a smile.
"gasp, gasp, gasp…"the emperor stepped back, gasping for his breath.
 his pupils trembled.
it seemed that he could not find the right way to break through this difficult situation.
 he fell into a panic when he realized that he could not summon the 'terracottas', his main force.
 "yeah, you're nothing because you are not helped by your undead army!" he shouted.
 this was an insult that sunngwoo had heard too often.
 those who criticized the necromancer always said the same thing.
 they criticized that he was a coward hiding behind the undead army, so he was really weak without them.
but that wasn't true.
compared to those with the combat-related professions, he lacked the skills specialized for combat, but his stats and item levels were higher than anyone else's.
the reason was simply that he continued to grow overwhelmingly by utilizing a huge number of his subordinate spirits.
 he was sort of snowballing.
but that was the same case with the emperor.
'even though i punched him strongly endlessly, he is still intact.
 obviously, he has considerable stats.
'
the emperor was also boasting of extraordinary stats and items.
 but that alone was not enough.
'he is very slow, though.
'no matter how good his equipment was, it was of no use if he didn't use it in training.
 no matter how much he trained himself, he could not be adroit in fighting unless he had actual fighting experience.
the biggest reason why sungwoo surpassed others in fighting was that he was so adroit and experienced while engaging in numerous fighting and confronting various opponents until now.
"you're exactly like a senior stuck in a room!"while confronting the emperor, sungwoo realized that the emperor had little experience fighting in the war.
 in other words, he had no idea how to move quickly.
 the latest episodes are on the lightnovelworld.
com website.
"shut your mouth!" he angrily shouted back at sungwoo.
 at that moment, two threads came out of the index and middle fingers of his right hand then crawled into his chest.
 then two strands of threads popped out, and something on the end of them flashed and flew towards sungwoo.
 whoosh! whoosh! it was a deadly attack.
 but sungwoo easily avoided it by turning his head.
 two daggers cut through the air in vain.
"how dare you avoid my daggers?"given the green color of the blades, the daggers had poison on top.
 the emperor began to wield two daggers violently, waving his hands.
 boo-woong! boo-woong!but sungwoo avoided his attack by moving around him calmly.
"yeah, i feel you have never moved properly in actual fighting.
 you have led a complacent life while acting like a king from the beginning.
"as sungwoo said, the emperor's attack was just clumsy.
 at that moment sungwoo snatched a dagger flying in a predictable trajectory, then threw it back at him.
puck! the dagger flew in a straight line and hit the emperor's left thigh.
"argh!"the emperor lowered himself in extreme pain.
 then he stretched out his hand to the right.
he spewed threads again this time.
but it was far from an attack.
 a single strand of thread passed sungwoo and got stuck in the right wall far away.
in an instant, the emperor's body turned into light, then flowed through the thread like an electric current, flashing near the wall on the right where the thread was stuck.
'he's trying to escape now!'this content is taken from lightnovelworld.
comobviously, the emperor was using a moving skill.
 he stretched out his hand once more there.
 it was a thread again.
 this time it was stuck in front of the anvil at the end of the hallway.
the next moment, he was standing in front of the anvil.
"great.
"the emperor then turned his head to look at sungwoo and smiled at him.
"you won't be able to get on your high horse anymore.
 get ready to come back into my space again!"he touched the anvil.
 as sungwoo said when he entered this space, the emperor put his hand on the anvil to flee from this space.


"exit!"but things didn't work out as he wished.
 - if you use 'hephaestus anvil', your 'success chance' and 'additional effect chance' are greatly increased.
 also, your basic durability is increased by 300%.
".
.
.
"what appeared before him was an ordinary message about enhancement.
 examining the message carefully, the emperor swallowed nervously.
 at that moment sungwoo shouted at him, "what are you doing here?"".
.
.
""hey, you think you are a member of a dream team who can pass through obstacles to get to the finish line easily?"the emperor must have been a cold-hearted person.
 but he had never been hit or faced a crisis in his life.
 as a result, it was difficult for him to keep a clear head in a war situation like this.
 above all, he lacked any sophistication and actual fighting experience.
sungwoo used 'shadow movement' skill to move over the long shadow of the emperor caused by the flames of the hearth.
at the same time, he kicked the emperor's leg with all his might.
 the emperor bent his legs, screaming in pain.
"khuuuuuuuuuk!"the moment he lost his balance, sungwoo kept throwing his punches at him endlessly.
follow new episodes on the lightnovelworld.
com platform.
puck! puck! puck! you can also read this novel on the more advanced platform lightnovelspot.
com

 