\section{chapter 362}

chapter 362: devil’s world tree and world eater (4)this chapter is updated by wuxiahere.
com




in fact, it was only a handful of the troops that lich summoned, but sungwoo could double that number.
– caution! ‘shadow army’ will rise in the area.
at that moment, a ‘shadow king’s crown’ was created above sungwoo’s head, creating the shadow army.
it was a moment when the army was exactly doubling.
“to arms, everybody!”“prepare for combat support from the rear!”the players let the undead corps confront the enemy then retreated to the rear to prepare sniping and magic.
sungwoo glanced back at his troops.
 victor’s cradle here was not very wide, but it was large enough to house all the undead army here.
‘there are far more than 300 like this.
’since it was moderately wide, it was perfect for the undead army to encircle and crush the single enemy with a large number of troops.
however, the world eater was calm, showing no particular reaction.
 he just watched the whole process silently without interfering.
“…”he scrutinized the undead army that filled the room, then turned his head to sungwoo.
“it’s useless.
 you cannot defeat me.
”his conclusion was very simple.
 but his cold expression made sungwoo feel like everything he said was true.
“most of the guys i’ve met until now have said so,” sungwoo replied sternly.
but he felt that the world eater was quite different from the opponents he had confronted.

“necromancer, you are definitely one of the strongest players in your world and on your server.
 but i am different.
 you’ve come to the wrong place.
”he slowly raised his sword and pointed its tip at sungwoo, but he moved stiffly.
was it because he hadn’t used his body for too long? he looked sick with a pale complexion and naked.
 however, unlike his appearance, his strength was enormous.
“do you know why the recommended level for attacking this demon’s cave is 43?”“…”“it’s because the final boss here is me, and i’m level 43.
 simply put, this is not the place you should visit.
”sungwoo’s level was only 24.
 the level gap between the two was simply incomparable.
’19 levels of a gap between him and me?’sungwoo thought that the level gap was just a number because the additional power that he could obtain by leveling up was not as big as he thought.
rather, the rewards that he obtained through special methods such as ‘acquisition of title’, ‘item effect’ or ‘synergy effect’ gave him much stronger power.
 but such a comparison was made on the assumption that the involved players’ levels were similar.
 if the level gap was 19, this was a different story.
‘he must have more than two divinities.
’actually, sungwoo was on the verge of gaining two divinities.
 then, the world eater already had more than two divinities.
sungwoo took a step back.
 the undead corps began to move.
the world eater came one step closer to sungwoo.
“just serve as a nutrient for us without resisting, necromancer.
”at that moment, something exploded from his body.
kugugugugu-
it was a transparent wave.
 it shook everything in the room like a sonic boom.
bundles of the roots were cut, plucked, and flew through the air.
 the undead army was pushed back.
 players crouched down and complained of pain.
“ugh!”it wasn’t just the simple wind.
 it was something like a mana storm.
 a huge amount of energy was exploding from his body.
– you are now facing the divinity of the opponent.
* you are qualified enough to face his divinity.
the world eater finally revealed his divinity.
“necromancer!”at that moment, the black lion called sungwoo.
 he turned his head slightly and looked at the black lion.
“that guy is different! i can feel the power of the dragon and the world tree in his body!”“what?”did he have the power of the world tree and the dragon? what kind of divinity did he have?at that moment, he soared into the air and shouted, “yes, i am the owner of the dragon, and the one who killed another dragon and took his blood then grew after gnawing at the world tree.
 that’s why i have become the dragon himself!”as soon as he finished talking, the world eater charged sungwoo.
 he ran toward him so fast just like a javelin.
sungwoo fell back and lifted ‘winter predator’.
 then, he fired three shots at the world eater.
bang! bang! bang!they were powerful freezing bullets that had frozen anything until now, but this time it didn’t work at all.
 by simply sticking out the tip of his sword, the world eater evaporated the freezing bullets that approached him.
“damn it!”then, the world eater tried to stab sungwoo with the sword.
 but sungwoo fell sideways and had the skeletons block it.
his single strike killed and shattered dozens of skeletons into pieces.
 it pierced through them more than 10 meters.
 then, when he swung the sword to the right, a fierce gust arose and swept away everything in the area.
 the undead army rushing towards him collapsed like a toy.
‘what the heck is this…”how could he cut dozens of undead soldiers by simply swinging his sword, which was not armed with the energy of the sword blade or skills?this time the players in the rear cast magic on him.
 but when he swung his sword over his head, a gust of wind blew and the magic reversed, soaring and hitting the ceiling.
kwagagaga-root fragments rained down on them.
“this is ridiculous!”“how could he wipe them away so easily?”faced with the world eater’s overwhelming power, the players were speechless and embarrassed.
“everyone, prepare a large-scale magic again!”at that moment, the world eater turned to the players behind him.
 and something started happening, with his eyes glowing red.
– caution! ‘dragon fear’ has been activated.
* stiffens low-intelligent creatures.
“dragon fear?”at that moment, all of those with intelligence hardened.


“kheeeeeeeeeeh!”“oh my!”“damn it!”they felt something completely different from what they had felt when confronting the aliens or those with divinity.
 the players were literally frozen like statues, unable to move at all in their places.
 some even flopped.
 even sungwoo with divinity felt his thighs got heavier.
‘this is different from the dragon fear that mir used before.
’sungwoo was now convinced that the world eater possessed divinity related to a dragon.
‘i have to make him let down his guard by all means.
’sungwoo caught his attention by pushing the undead corps toward him.
 it was true that the world eater had overwhelming destructive power, but he could not completely neutralize the undead army’s power.
snap!sungwoo turned behind him and changed the winter predator to ‘extension mode’.
 he could not block the world eater with a single-mode shot.
 at the same time, he grabbed the grim reaper with his right hand.
– ‘evil spirit bombing is embedded in your weapon.
 (max)sungwoo used winter predator to distract him because he had some other attack in mind.
‘now is the time.
’the world eater was already distracted elsewhere.
 he smashed durahan, who rushed toward him from the front.
 while he was trying to block minsok’s black chains, sungwoo raised the muzzle toward his side.
he fired dozens of freezing bullets, which immediately began to freeze the area around the world eater.
 the undead army was also within that range.
 sungwoo could not afford to fire shots outside the undead army.
but the world eater slowly turned around and swung his sword, as if nothing happened.


 