\section{chapter 420}

in particular, if they became the so-called 'founding member' of the control center, they could feel that this would be a very important opportunity to get ahead of other servers.
 they could even feel as if they became permanent members of the united nations.





'it's not a matter of rivalry or superiority among us.
 it is also important that this upcoming meeting will serve as the first international meeting of all the servers of the world since the game started.
'in other words, this "temporary committee" would be the starting point of the new international order.
 therefore, even if they did not like the "control organization," they had no other choice but to participate in this important gathering.
 they would attend it to check out how the new organization would work.
 'i'm sure all the servers around the world will voluntarily come to the korean server even if they are not forced to.
'sungwoo's prediction turned out to be correct.
just a few dozen minutes after he announced the message, each server started sending messages about their intention to join the new organization.
"we have a message from the australian server.
 they have expressed their intention to participate.
"the 24 screens filling the front wall displayed different foreign server communities.
"this time we have a message from the vietnamese server! they say they can depart right now!"the center director, holding the, was controlling the situation.
s "okay! so far, we've received responses from two foreign servers.
 as soon as you get the messages from other servers, compile a list of them right away!"having said that, he glanced at kyungsoo.
"i also got a message from the mongolian server!"kyungsoo tilted his head at that"mongolian server? they joined hands with the emperor to attack us, right? of course, their situation might have changed because the emperor was killed, but we need to keep an eye on them just in case they can stand in our way.
"
not all server representatives who would come to the temporary committee were friendly.
the most up-to-date novels are published on lightnov­elworld.
comin this regard, it was necessary for sungwoo to operate a spy unit to discover their true intentions in advance.
"russian server and laos server also replied in the positive!"anyway, all the servers around the world were responding to the necromancer's summon order.
"man, it looks like it's going to be much bigger than we planned!"kyungsoo could not hide his worries, watching the list of prospective visitors who were on the rise in real-time, for he was responsible for managing and controlling the incoming visitors.
"as many as 23 servers have already responded.
 i think all the server representatives are participating without any exception.
""hope so.
"it was the moment when sungwoo's propaganda was paying off nicely.
 'but i wonder if the system can welcome this phenomenon'the system held an event called 'world season' to cause conflict among the servers around the world.
 as a result, numerous wars broke out.
however, they were integrated contrary to the plan of the system.
 did the system guys anticipate this?'if they didn't welcome this, they would definitely try to disturb me.
 i can't predict what will happen.
.
.
'this was a huge gamble for sungwoo.
 there was nothing more tedious and boring than integration and peace, so the system guys would certainly foster division among the participating servers.
 
but then an unexpected message came in.
"uh? what the heck is this?"one of the center staff shouted.
 everyone looked at him.
 he got up from his seat and approached sungwoo and kyungsoo, not the center director.
"necromancer, this is a message from the brazilian server.
"visit lightnovelworld.
com for a better experiencesungwoo frowned before he knew it.
"brazilian server?"the brazilian server was destroyed.
 to be precise, it was taken over by the dragon in amazon.
according to w·p·u's intelligence, the players there were loyal to the dragon.
"yes, that's right.
 it is from the demon king.
 the demon king said that he would also participate in the upcoming temporary committee.
"it was an unexpected message.
 'why? what does he want to come?'how could the demon king, who declared war on the world, come here? the center staffer continued, "and the dragon said he would also come, and asked to relay his message to you, necromancer.
"then he looked at sungwoo and continued, "necromancer, don't forget that our enemy is the angel and 'absolute race'.
 it was them, not the players, that i declared war and wanted to attack.
 two hours ago, they opened the gates of heaven.
 prepare for the final war.
"someone was obviously watching, or even enjoying this game.
 if so, which scene did they want to watch?angels and demons, the world divided into two factions following them, and fierce competition and war between them.
 this was one of the main scenarios of this game.
however, all those scenarios came to nothing, and all of a sudden peace and harmony began.
to emerge among the servers around the world.
 'for those who are enjoying the suffering of others, this kind of new world order will certainly dampen their interest.
"that's why another extreme event began.
"as a result of the investigation, almost all large organizations of the korean server have left the absolute race camp.
"with all the commanders present at the conference room, kyungsoo reported the results of the investigation.
the most up-to-date novels are published on lightnov‌elworld.
com"that's the same case for the taiwanese server.
 the chinese server is also rapidly withdrawing from the absolute race.
 the us server-1 had no affiliation from the beginning.
 but the us server-2, the u server-3, and the canadian server have withdrawn from the absolute rae camp one after another.
"in other words, lots of servers were already freed from the two absolute races of angels and demons.
 and it wasn't just the alliance servers affiliated with the world tree camp.
"when we again contacted those servers who would participate in the temporary committees, most of them said they either left the absolute camps or were planning to withdraw soon.
"in some respects, it was inevitable for them to leave.
"it seems that the performance of our camp until now has been a great stimulus for them.
"the necromancer and the world tree camp have triumphed over and over again, and numerous forces under the absolute camps collapsed after confronting sungwoo's forces.
 because of that, lots of players around the world had no choice but to be skeptical about their association with the absolute camps.
 

while they were agonizing over it, sungwoo's message about the 'control organization' began to spread rapidly to them, which prompted their withdrawal from the absolute camps.
in other words, the more sungwoo succeeded and prospered, the more rapidly the absolute camps were disintegrating.
'they must have judged that once the world control body was established, they could no longer function properly.
 that's why i held an event like this.
"at first, it seemed that it was difficult for the absolute races to directly intervene, but that restriction seemed to have been lifted.
"i heard that the gates of heaven were opened.
 do you have any specific evidence?" sungwoo asked.
 kyungsoo nodded and operated the remote control.
 a picture appeared on the big screen behind him"this is rome on the italian server.
"s a blue portal was open in the roman sky.
 and some letters floated along its edge.
- a new event is about to start.
 (00:28:03)for more, visit lightnovelworld.
com"this time let me show a picture sent by wpu.
 it shows washington, dc.
"the same thing was happening there.
 a blue portal and a warning message appeared.
"by the way, according to our server, a blue portal was created in jongno, seoul.
 i haven't received the photos yet, but the liberation guild said they would send us a video soon.
" you can also read this novel on the more advanced platform lightnovelspot.
com

 