\section{chapter 231}






 arrows and magic were shot one after another from the roof of a university building.
 in the dark sky, fireworks and colorful magic exploded, immersing the whole campus in a dark color.
pop! pop! thud!the japanese ninja units landed near the campus and were approaching across the ground.
 they were shooting arrows with explosives and flying pigeons with bombs to create an opportunity to approach the allies.
“five ninjas are coming from the right!”five ninjas attacked after climbing over the railing.
 they were strong enough to easily wipe out shooters.
“no way, no way!”however, minsok, the skeleton knight with green eyes, was protecting the shooters of the world tree camp behind them.
“you guys can’t climb over it!”he jumped off the floor so violently there was a dent in the urethane floor of the roof and blocked the ninja at the forefront with a shield.
no matter how competent the ninja was, he could not avoid minsok’s adroit attack.
 as if the ninja was run over by a truck, he bounced off the railing.
at the same time, minsok swung his big sword and cut the second ninja’s chest.
the ninjas who followed dispersed in all directions, trying to pass by minsok, but minsok’s black chains stretched out like tentacles and entangled their limbs.
 when they could not get out of his chains, they were killed miserably like crucian carp caught on a fishing line.
“you guys can never climb over this wall!”before becoming the death knight, he always led a passive life, protecting somebody behind his back, but he was different now.
 he never allowed anybody to escape by getting past him.
“more ninjas are charging at us from the right!”hearing that, he dropped the black chain.
 then, he turned his head and called someone.
“hey, little boy!”rattle-orun appeared out of nowhere.
 minsok wrapped orun’s body with a chain, then threw him to the right as forcefully as possible like a top tied to a string.
bung-boo-woong!
three ninjas were cut in half on the spot.
 it all happened in an instant.
 the moment orun stopped rotating, he threw the dagger at the ninja who was aiming at another player.
“kuhhhhhhhhhuk!”orun was also holding a hand cannon.
 he landed on the floor then aimed at the two ninjas soaring in the air.
kwa-ang!two ninjas fell helplessly as orun fired shots at them.
“good job, little boy!”when not only minsok and orun but also hanho threw six daggers at a time and made a combined attack, the ninjas collapsed without attacking properly.
although the players from the world tree camp were fighting back well, other players were not in a good situation.
“our defense team in the brown building at one o’clock position seems to have been annihilated.
 ninjas are coming from that building!”“it looks like our team on the first floor of this building has been defeated!”sungwoo was saving ‘awakening’ and ‘deity status’ in preparation for the worst situation, he could not afford to defend the hwarang guild.
‘the situation is not good.
 if this kind of situation continues, they won’t be able to hold out for long.
’besides, sungwoo and his allies had yet to confront the main forces of the japanese troops.
 that’s why he was saving his skills for the upcoming fight, but he could not guarantee.
“their main unit has appeared!”“they must be crazy.
”finally, sungwoo saw a large number of japanese troops gathering on the road not far from him.
 they were huge, compared with their advance party sungwoo had annihilated.
 they also had several flying weapons.
watching them approach, the defense team of the hwarang guild suddenly became dejected, overwhelmed by their troops and weapons.
“damn it! we killed lots of them, but they are still coming like this…”“damn bastards!”when their main unit arrived finally, the ninjas’ offensive began to intensify.
“they are coming in droves!”
“more japs are coming! fire!”the japanese troops were laying the groundwork for the final offensive.
pop! pop! pop!several small iron barrels fell on the rooftop, rolled, and emitted white smoke.
pushee―“what the heck is that? is it a smoke bomb?”” be careful! it’s only a smokescreen!”and dozens of black shadows arose in the white smoke.
 after they blocked minsok and his allies’ vision with the smoke bomb, they began to attack all at once.
“oh, damn it…”with minsok groaning in an embarrassed voice, the japanese troops charged at them in all directions.
“argh!”“ahhhhhhhhh!”various screams came out in the smoke.
“oh, no!”in the end, minsok failed to protect the shooters and wizards.
 and it meant his allies had been annihilated.
“damn it! come on! don’t attack them.
 just come and fight me!” hanho shouted in anger.
with his six arms outstretching, he aimed everywhere in the fog.
 but he didn’t see anything.
“uh? where are you! come out!”even right now they could come out and cut him, but at that moment something fell under his feet.
“uh?”it was a severed arm.
 the black camouflage and the dagger on his index finger showed the victim was not from sungwoo’s allies.
in no time another thing fell behind his feet.
 as expected, it was also a body in a black outfit.
 somehow, the ninjas’ severed bodies began to pile up one by one around them.
“who the hell…”the next moment, a powerful gust of blue flames blew in.
 a powerful blow swept over the rooftop, making the smell of blood in the air stronger.
hanho lowered his posture, protecting his head with his four arms.
when the gust pushed the smokescreen away, the cruel reality of the rooftop was revealed at once.
“oh my god! jisu?”“you must be jisu, right?”jisu was standing on the railing.
 the bodies of ninjas were scattered everywhere on the railings and edges of the rooftop around her.
 that wasn’t all.
“crusader team! get ready for the battle!”on the campus playground, there were about 80 knights armed with full plate armor.
 they were the crusader team led by junghoon and his deputy minhum.
hanho and his allies didn’t hear them flying in with a helicopter, but they appeared so quickly without letting anybody know.
“protect our land!”“defend it!”as soon as junghoon shouted, he fixed a golden flag down on the floor.
a golden wave spread, covering the crusaders with shields.
-‘the sacred war’ is declared in the affected area.
 (lasts 2 hours)* all allies gain an auto-healing effect.
 (2% per second)* all stats of the ‘crusaders’ increase.
 (+7)“attack!”“wipe them out!”

the crusaders rushed fiercely and pushed out the ninjas that had occupied the ground.
 the ninjas launched all kinds of attacks, but they couldn’t break through the crusaders’ thick golden shields.
“jisu, what happened?” sungwoo asked.
she replied, “i have cleared the hidden quest.
 and i learned that you participated in the battle of busan.
 this time again, i asked the king of the great mountain and obtained a space movement stone.
”the space movement stone was an item that enabled its holder to teleport to a distant place instantly.
 sungwoo and the players from the world tree camp arrived in busan by using the “space movement stone” that the hunter company obtained for him.
“then, did you bring the crusaders team here, jisu?”“yeah, because you needed a reinforcement force.
 they are the strongest among those who can help us, right?”sungwoo nodded.
 ironically, he badly needed their help at this moment.
-‘free battle’ is over!with the arrival of the reinforcement unit led by junghoon, the free battle ended.
-please select the third ‘battle event’!* ‘attacker-japanese server’ selects this time.
1) all-out war2) occupation war3) duel* time remaining until selection (00:04:59)with the war in a stalemate, it was now the japanese server’s turn again.
“it’s going to be noisy again.
”the official channel’s drone camera again turned to akira.
 since he went through a hellish war for almost an hour because sungwoo selected an all-out war, he distorted his expressions immediately.
it was so clear that he was not as complacent as before.
 instead, he was full of anger.
he stared at his camera and shouted.
“you can’t escape this time! let me smash you to pieces.
 so, come out, necromancer!”

 