\section{chapter 336}

chapter 336: post-war recovery and second system error (8)at that moment, sungwoo stood up and turned over the round table.





bang!the table was thrown away, hitting the wall.
 the teacup on it bounced off and hit his forehead.
“what the hell are you doing?”sungwoo kicked the heater hard.
 the huge metal ball flew through the wall.
 the firewood was scattered like a shotgun, and the ashes made the room hazy with dust.
“are you crazy! what the hell are you doing now?”however, sungwoo began to smash the entire room, not caring about him at all.
he smashed the cabinet, pulled down the grandfather clock, lifted the pot, and threw it into his face.
bang! bang!the easiest way to upset him and disturb his mind was to go on the rampage like that.
the primal emotion of anger was easily triggered by simple and ignorant provocation.
not surprisingly, the man who watched sungwoo going berserk was seeing red.
“crazy bastard! you are not in reality but an illusion! no matter how violent you are, it’s useless, you stupid bastard! why are you doing this to me?”like he said, sungwoo was in illusion but he could not help but be upset since the necromancer was causing disturbances like this.
 finally, he lifted his index finger, fuming.
“damn it! get out of here! never come back!” he shouted firmly and turned.
he was going to forcibly kick sungwoo out of the memory.
“…”but nothing happened.
 sungwoo was still standing in the fragments of memory.
as if he felt something strange, the guy turned his head slowly.
“what the heck is this? why are you…?”his eyebrows wriggled.
 when things didn’t work out as he wished, the guy was full of embarrassment.

at that moment, someone’s voice rang.
“this is not your world anymore.
”soon, the atmosphere began to change.
the white curtains fluttered as the wind came in from outside the window.
 the clouds gave way to the full moon, which shed a brilliant ray onto his face.
“now let me take control of him.
”someone was standing on the terrace.
 his blue eyes were slowly shining.
 he was the white wolf.
 while sungwoo was making a big disturbance, the white wolf succeeded in taking over the guy’s spiritual world.
“what the hell is it? what did you do?”when the white wolf walked into the room, the mustached man stepped back.
“get out of me! oh no, just let me go!”having lost control of this world, he couldn’t drive anyone out or even get out on his own.
all he could do was shudder with fear, leaning against the wall.
“please…”the white wolf slowly approached him and opened his mouth wide.
then, he bit the guy’s neck at once.
“kheeeeeeek!”the white wolf killed his spirit.
-the memory of the deceased has been intertwined, so it shows a ‘hidden scene’“hidden scene?”the white wolf nodded, wiping his mouth.
“maybe you can see more details.
 this is also the effect of psychometry.
”
at that moment, the scene began to change.
 the messed-up room moved and disappeared behind his back, and sungwoo found himself suddenly standing inside a skyscraper in beijing.
finally, the real memories of the general began to play.
“there is nothing to lose in this war.
”the man who said that was general xing.
 he was confident of victory, looking down at the troops lined up on the eight-lane road.
“absolutely, general!”“haha! who can dare stop our large army?”his staff standing on both sides of him chimed in.
smiling at them in satisfaction, he turned his head.
“yeah, the presence of our large army itself is overwhelming enough, so you don’t have to use that terrible weapon.
”he turned his head and held onto the railing inside the building.
 there was a large lobby under the railing, where a purple portal was open.
‘a terrible weapon?’ sungwoo murmured.
the general seemed to refer to that portal.
“it’s really creepy whenever i see it.
”oohoohooh-dozens of such portals filling the lobby were sucking in air at that moment.
the sound of them sucking air resonated through the building, ringing like the cries of a giant beast.
 sungwoo knew what that weird portal was.
‘it’s the demon’s cave.
’there were as many as 21 open holes that endlessly poured out terrible monsters.
sungwoo could not believe it.
“can the emperor truly control those monsters?”“are you suspicious of his majesty?”“oh, no, i didn’t mean it.
”smiling at him, general xing pointed at the portal with his finger.
“our emperor made an agreement with the head of the devil’s cave.
 the monsters in those holes will always fight for us.
”the head of the demon’s cave was obviously the “world eater,” the ruler of the demon’s cave.
‘i think i know what the situation is.
’the emperor’s identity was finally revealed.
 like the “evolution society,” he was obviously a player who grew up under the protection of the world eater, namely, “the fallen”.
watching the scene with sungwoo, the white wolf looked at him with a terrified expression.
“can you beat that guy?” he asked.
but sungwoo could not answer.
‘i cannot win unless i close the door.
’when sungwoo killed salamander in pyongyang, the world eater appeared and opened dozens of gates of the demon’s cave.
at that time, he forcibly closed the portal using the tree branches containing the spirit of the mountain that the king of the great mountain brought.
‘but if they defend the gates thoroughly like that, it would be difficult even to close them…’the reason he could close the demon’s gates in pyongyang was that it was an open place, and he quickly killed the monsters even before more monsters crawled out.
‘no matter how hard i agonize over it, i can’t think of how to close the gates and kill them…’when he gradually became more and more frustrated, fortunately, he saw a ray of hope.
[exclusive quest]-name: defender’s duty-3-type: target destruction

-goal: destroy the ‘heart of the demon’s cave.
”-reward: choose between ‘upgrading of deitus’ and ‘the right to change jobs’*you have foreseen a massive raid by the external forces.
 as the defender, you have a duty to stop the disaster.
 all of the demon’s gates are connected to one world.
 and at the center of that world is the ‘heart of the demon’s cave’.
 if you destroy it, you will be able to cut off the evil relationship between the two worlds forever by destroying the entire demon’s cave.
* if you fail to destroy it within 48 hours of entering the demon’s cave, you will face a ‘strong resistance’.
* when you destroy the ‘heart of the demon’s cave’, all the demon’s gates open to this world will be closed.
in other words, as the defender, sungwoo was given a hint on how to cope with that ridiculous ordeal.
“yeah, it’s the demon’s cave.
”so, sungwoo remembered the scroll of the demon’s cave that he had carried for a long time.
[item information]-name: 2nd floor of the demon’s cave-grade: special-category: magic scroll-effect: you can open the door of demon’s cavel for 36 hours when you use it.
-description: create a passage that connects the demon’s cave.
 you may get very valuable items by exploring the inside of the demon’s cave, but we recommend that you don’t try it out recklessly.
 don’t forget that someone might come out of the door that you can enter.
 (recommended level 43)actually, sungwoo was thinking of destroying the demon’s cave someday, and this was the right moment.
but the problem was he needed level 43 to be able to attack the dungeon.
“i can make up to 25 levels.
”before the war resumed, he found a way to use the two deity status.


 