\section{chapter 268}

                            soon, a hazy shape began to arise nearby with a creepy cry.





-you can control ‘ghosts’.
 (your affinity for death traits is the highest.
)* you are not affected by ‘physical attack’.
* you can ‘control’ all kinds of weapons.
* inflicts the curse of ‘confusion’ on the target of your attack.
* you can possess targets below a certain level.
in the case of the undead, they could not approach salamander because they would melt in the strong heat.
 however, it would be different if they were in the form of souls.
no matter how strong the flames, salamanders would inflict little damage because the undead that transformed into souls had no physical shape.
in addition to this, sungwoo summoned up to two “specters” to maximize the synergy effect.
-you have received a ‘synergy effect’ due to team play.
[synergy list]being without substance (3rd stage)-category: trait synergy-condition: 12 or more in the form of ‘soul’-effect: moving speed increases (+30%),as expected, sungwoo could obtain only the 3rd stage effect by adding two specters.
he then cast long spears and blunt weapons he made using bone weapon manufacturing skills all over the place.
 at that moment, the ghosts used their telekinetic power to lift the bone weapons.
 and some were interested in the items that were tied up in the ‘warrior’s shackles’.
 after 5 minutes, their seal was released.
 among them was the magma sword used by the salamander.
[item information]-name: lebatain (disabled)-grade: legend-category: sword
-effect: increases muscle strength (+5), increases flame immunity (+10%), increases flame damage (+10%), and ‘flame waves’ when you hit the ground.
 (cooldown: 1 minute)-description: it hasn’t burned completely yet.
 additional conditions are required to demonstrate its full power.
“man, you had some other good materials other than bones,” sungwoo said scornfully.
since it is a weapon with a fire trait, it would not have a great effect on the salamander, but at least, it would be able to inflict physical damage.
“what the hell are you trying to trick me with? whatever you do will be useless.
 i’m going to melt everything!”the salamander blew his nostrils and swung his tail, which alone caused a gust of wind and blew the surrounding debris like styrofoam.
kugugugugugugugu!his target was the group of ghosts floating in the air, but his thick tail only stirred the air.
even after he swung his thick tail, the ghosts were still floating there.
 at best, his tail crushed the bone weapons that the ghosts lifted in the air.
“what the heck is this?”this time the ghosts moved around the salamander.
 they flew around the salamander like a swarm of bees, wielding the weapons lifted by their telekinesis.
puck! puck! puck! puck!long spears were stuck into the salamander’s back and tail, followed by blunt weapons on his head.
 even though such attacks didn’t inflict strong damage, they were still annoying to him.
“kaaaaaaaaaaaah!”although he let out breath in the air, shouting, it did nothing to repel the ghosts.
the ghosts hovered over the salamander’s head to look for his soft spot then stabbed the spears one by one.
puck! puck!“argh! you dirty bugs!”the salamander kept wriggling, not knowing what to do about the ghosts’ random attack.
 but he found the solution to all his problems.
“alright.
 it’s all over if i kill you!”the salamander cast his gaze on sungwoo who was controlling the ghosts.
“oh, you aren’t that stupid,” sungwoo scorned.

now, the salamander ignored the horde of ghosts and began to rush at sungwoo.
stepping back, sungwoo fired the repeating crossbow.
tung! tung! tung! tung! tung!however, the salamander suffered little damage because the arrows couldn’t penetrate his thick hide.
he twisted his body and swung his tail at sungwoo violently.
thud! kuggugu!“kuuuuuck!”although sungwoo was not hit directly, concrete fragments flew like buckshot.
 hit by the fragments, sungwoo was pushed back.
 the salamander then pushed his head toward him and opened his mouth as wide as possible.
 a fireball burst out of his throat.
sungwoo could not escape it.
noticing sungwoo was on the defensive, the salamander gathered all the magma boiling deep inside and threw it out all at once.
puhuahwahwahwa-the breath of fire swallowed sungwoo.
 although sungwoo was hit by fire several times, the salamander’s breath was in a different league.
the steel frames nearby bent like malt, and concrete fragments melted like cheese.
at the same time, gray smoke soared, making the whole area dense with smoke like a haze.
hwaahah-all objects the flames touched lost their original shape.
nonetheless, the salamander did not stop.
 he pulled out all the flames that had been stored deep in his body.
 like heil declared the other day, he was determined to burn sungwoo into a handful of ashes and lay it on his bedside.
‘you are finished.
 you’re dead.
’at that moment, the flames salamander emitted split into four.
the salamander doubted his eyes.
‘what happened?’something was coming up from the bottom of the flames.
it was too late when the monster noticed something strange.
breaking through the red flames, the blue flames climbed right up his neck.
it was the necromancer.
 he was floating in the middle of the flames before the salamander’s mouth, taking his breath without any burns.
“just don’t move your open mouth!”then, sungwoo swung his huge black sickle.
 the black spheres formed there were fired all at once, flowing into his mouth.
goooooooooogung!a series of explosions occurred inside the salamander’s body.
“kheeeeeeeeeek!”it wasn’t an ordinary explosion.
 it was sungwoo’s skill that crushed everything in the area with enormous pressure.
then, sungwoo withdrew the grim reaper.
“did you think i avoided your attack because your breath was so hot?” sungwoo snapped.
the salamander struggled, with his stomach facing upwards.
 but he could do nothing, let alone scream.
“don’t think that no one else can do what you can do!”as if his body became a blender barrel, everything in his stomach was completely shredded.
“kueeeeeeeh…”soon, his eyes rolled back.
-you have obtained 28,000,000 gold by hunting the field boss monster “salamander”.
it was a perfect victory for sungwoo.
‘fortunately, this monster was completely smashed.
’however, sungwoo would not have been sure of the victory if he had collided with the monster one on one.
 fortunately, he could end the fight quickly by using deception.
-you have acquired the title of ‘spirit predator’.


* fire immunity increases (+20%)* spirit dominance increases (+20%)* stamina increases (+2)-you have acquired the title of ‘emperor killer’.
* all stats increase (+3)* damage to the boss monster increases (+10%)finally, another fight was over.
 and this meant the end of the mainstream itself, which terrified the entire korean server.
-as of the current time, the mainstream ‘chapter 4-1: flooding of the ruined world’ has ended.
* there will be an announcement of the next update in the future.
the necromancer alone ended the mainstream.
when the boss monster collapsed like that, the rest of the remnants lost their will to fight.
the monsters who were trying to rescue the salamander by breaking through the undead army began to run away, but the undead army persistently chased and slaughtered them.
however, that wasn’t all they had to take care of.
“look for the spectators!”sungwoo noticed that a small number of players nearby had been watching the whole situation.
he couldn’t figure out who they were, so he needed to catch them and interrogate them about their intentions.
meanwhile, sungwoo looked at the salamander’s body.
 perhaps because of the trait of the spirit, his entire body was being vaporized and disappeared as soon as he was killed.
fortunately, his bones remained intact.
‘there is something more here in his body.
’a round object rolled down his body.
sungwoo picked it up.


 