\section{chapter 379}

chapter 379: hephaestus’ forge (3)the red dragon spear smashed his forehead and pierced his neck and back before being stuck in the opposite wall.





- you have obtained 1 gold by killing the guardian of the forge, ‘gold guard’.
kugugugugu-the huge golden body collapsed like a rock.
 sungwoo admired the power of the red dragon spear once again and turned his head to look inside the safe.
it was full of various items besides the spear.
 and many of them were items made from the bones and skins of ‘red dragon’.
“man, this was worth risking one’s to steal it.
”- the no.
 13 secret safe has been forcibly opened.
the description of the item said that forced opening was possible only once a day.
 so, it seemed sungwoo had one more important task to take care of, starting today.
“by the way, a set of dragons…”when he held the ‘red dragon spear’, he confirmed that it had an unconfirmed set effect.
in the center of the safe were the red scales of red dragon, along with the dragon’s blade and black metal overlaid with armor that exuded an overwhelming aura around it.
“is it time for me to change your armor?”now that he destroyed the gold guard, it was time for him to check the loot he obtained leisurely.
‘it’s impossible to set a price on this valuable room!’various items were placed on the display shelf.
 since they were used by the world eater, or the victor of the ruined world, each of them had very special functions.
‘especially, that armor is …’
the first thing he checked among them was the dark red armor that was placed in the center.
it stood out as a very special item.
 just by looking at it, sungwoo immediately discovered that it was made with the scales of red dragon.
[item information]- name: red dragon armor (+2)- grade: unknown- category: player manufacturing- effect: agility value increases (+3), stamina value increases (+6), physical defense increases (+300%), magic resistance increases (+200%), fire immunity increases (+30%), penetration resistance increases ( +70%), fear resistance increases (+10%).
 when you wear it, you give the low-level opponent a sense of ‘intimidation.
’- description: this is armor made of ‘dragon’s scales’ and various ‘magical metals’.
 it contains the power of hephaestus, so it’s very durable.
 in addition, the archmage’s ‘special spell’ is engraved on the surface.
+ unidentified set effect: it’s activated when you put on 3 or more ‘red dragon’ items.
‘wow, this is also great.
 it has more various effects than any other item that i have obtained so far.
’of course, the ‘hellfire armor’ that i am currently using is also a great item, but this is nothing, compared with the ‘red dragon armor’.
it was a pity that the hellfire armor could not be passed on to someone else because it belonged to its original owner, but he could carry it for emergencies because he could automatically remove and wear it at any time.
‘i wonder what the set effect attached here is …’to complete the set effect, sungwoo started looking for other dragon items among the items on the shelf.
then, he found a certain black bracelet.
 when he examined it closely, it appeared that the dragon’s huge teeth were cut, ground, and woven together to make it.

[item information]- name: red dragon bracelet- grade: unknown- category: player manufacturing- effect: all stats increase (+3), maximum mana increases (+500), magic resistance increases (+50%), fire immunity increases (+30%), fear resistance increases (+10%).
 when you wear it, you will give the low-level opponent a sense of “intimidation.
’- description: it’s a magical accessory made by grinding dragon teeth.
 it contains the power of hephaestus, so it’s very durable.
+ unidentified set effect: it’s activated when you put on 3 or more ‘red dragon’ items.
when sungwoo possessed three red dragon items at once, the ‘unconfirmed set effect’ took effect.
- ‘set item (dragon road-red)’ has been completed.
[skill information]- name: dragon lord-red- grade: special- category: active- condition: 3 or more ‘red dragon’ items required.
* available skills vary, depending on the set item.
.
 breath field: activated through ‘red dragon spear’.
 change the area (100m) where the spear is stuck into a lava field.
.
 boiling armor: activates through ‘red dragon armor’.
 surrounds the user with a powerful fire vortex.
.
 summoning dragon soldier: activated through ‘red dragon bracelet’.
 you can summon and control 10 dragon soldiers.
each of the three items was given a special skill, but sungwoo took note of the third item, namely, ‘summoning of dragon soldiers.
’‘dragon soldier?’dragon soldiers literally meant soldiers made of dragon’s teeth.
 he didn’t know anything about them, but they were probably very powerful.
‘can i summon ten?’as a matter of fact, he was already armed with a large number of undead army, so the addition of the dragon soldiers would be another powerful addition to his troops.
‘well, with this huge power, i can even beat the chinese server easily.
’he thought he had enough troops to confront and beat the chinese server.
 but that’s not all.
he also had items of “myth grade” appearing in myths such as red dragon’s boots, aegis shield, achilles shield, and talaria (hermes’ shoes).
‘i can’t check them one by one right now.
 i think i have to collect all of them before getting out of this place.
’since he could not anticipate the unexpected attack of the dead giant statue ‘gold guard,’ he didn’t know what would happen again to him.
in particular, most of his abilities were limited in this space, so he was never safe here.
 in short, it was never good for him to stay here any longer.
when sungwoo came out to the real world, kyungsoo was sitting on the sofa, waiting for him.


“oh, you are back! i’d like to ask you where you’ve been, but…”looking at the ‘red dragon armor’ sungwoo was wearing, he made a surprised expression again.
 it was obviously something very unusual.
“wow! you have returned with something great, as usual.
”kyungsoo nodded, as if he was familiar with his enormous loot, then began to report to him.
“as you instructed, i have ordered them not to approach the world tree.
 in the meantime, i got a call from the us server.
”“you mean the wpu?”“yes.
 they offered to send reinforcements to help us in the upcoming war.
 so, i’ve asked them to operate the hypergate we shared before.
”the us server was allied with the korean server, but during the last war, they could not afford to send troops.
 but while the whole world was shaken by the war, the us server allied with neighboring countries.
 therefore, they strengthened their forces during that peaceful period through alliance.
 since they were waiting for the fight with the dragon, it’s highly likely that they beefed up their forces a lot.
“well, not only the troops of the us server but also our allies will arrive here pretty soon.
 we have to prepare the accommodations for them,” said sungwoo.
when he said that, kyungsoo smiled as if he was already prepared for it.
“absolutely.
 we are preparing thoroughly this time because we once had big difficulties preparing it during the last war.
 for example, we converted empty buildings into lodgings for outsiders.
 so, you don’t have to worry.
”right before the war with the previous chinese army, a large number of allied forces came in droves, causing lots of chaos among sungwoo’s troops.
at that time, they could not accept the outside reinforcements into their camps blindly, so they had to have them encamped outside the castle wall and sort them out one by one.
at that time, it was kyungsoo who worked harder than any others to make accommodations for them.
 so, he was thoroughly prepared this time.


 