\section{chapter 394}

chapter 394: full control over death (3)this chapter is updated by wuxiahere.
com




then, the shell and bone characters emitted a blue light, then the turtle’s shell became powder and scattered in the air.
– you sacrifice the players written on the list to activate the ancient charm.
“kheeeeeeeek!”“khuuuuuk!”his subordinates fell one by one, vomiting blood.
 it was the same for taegam himself.
taegam rolled his eyes, looking for something while blood was dripping from his mouth.
“designate the attack target!”– the attack target has been specified.
* target: kor-157* goal: kill– ‘the wild hunt’ has begun.
according to a european legend of the ‘wild hunt,’ numerous ghosts roamed in groups to hunt people.
 this unidentified item, which they called a ‘secret weapon,’ was a curse that could force an attack by controlling the ghosts in the area at the sacrifice of as many as 100 people.
woo woo woo-as soon as the item was activated, the souls of the dead began to arise from all over the battlefield.
woo woo woo-since certain conditions had to be met, not all the souls were summoned.
however, a huge number of ghosts arose from the fallen white sacred sphere.
 they were so countless that it seemed as if the water vapor was soaring from there.

“alright.
 work off your grudge against us on him!”the unknown reality of the white sacred sphere was that it killed a whopping 3333 priests and bound their souls with a powerful curse.
ironically, through the death of the priests, they created a powerful ‘holy field’ that could suppress even ‘death magic’.
khaaaaaaaaah! khaaaaaaaaaaaah!they harbored a deep grudge because they were not only killed against their will but also overworked.
 as a result, they differed in the color of their souls.
 while the souls of the dead who died on the battlefield were white or gray, they were dark black.
kwaaaaaaaajik! kwaaaaaaaaaajik!the vindictive spirits flew wildly towards the target designated by ancient magic, the necromancer, then began to smash all his subordinate spirits.
kwaaaaaaaajik! kwaaaaaaaaaajik!hundreds of ghosts and hundreds of skeletons were dragged up into the air and roughly disassembled.
 like a herd of piranhas rushing towards a drowned wild beast, they were quick, rough, and ruthless.
“yeah, no matter how strong you are, you won’t be able to escape from the chase of the cursed ghosts.
”taegam laughed, showing his teeth, even though he was bleeding all over his body.
his legs were weak, so he fell to his knees, but he raised his head stiffly because he wanted to see the necromancer’s last moment.
“this is my last wish, so just go to hell!”even though his eyes were full of blood, blocking his vision, he wiped the blood with his fingers.
 he wanted to see the necromancer’s last moment with his eyes.
however, something very strange happened.
“what the heck?”he became sober again even though he was hazy a moment ago.
 he couldn’t believe it.
 he felt as if he had hallucinations right before he died.

“what the heck is happening…?”purple chains began to spurt out of the air.
 they moved as if they were alive and captured all the vindictive ghosts in the area.
 the ghosts who had been running wild could not do anything because they were bound by the chains.
khaaaaaaaaah!besides, shackles were fastened to their necks.
 then, the ghosts that had run wildly became as meek as the tamed wolves.
“ah…”taegam saw him while breathing his last breath, standing between the undead army and hundreds of ghosts.
 that man, stretching out his hands, was controlling the chains, the ghosts, and everything else.
– the ‘law of the underworld’ has been applied to the area.
*you have control over all ghosts.
of course, that man was the necromancer.
“well, i wanted to hide it a little longer…”a green aura appeared behind sungwoo’s head.
 it wasn’t just light.
 it was more dazzling than any light and far deeper than any darkness.
 it was an inexplicable, noble light that proved that it was a different existence that did not exist in this world, namely the underworld.
“well, since i have come to this point…”sungwoo reached out and scanned the battlefield once.
 then, with his palm facing the floor, he slowly lifted it.
– the souls of the dead are summoned according to the decrees of the underworld.
then, a huge number of ghosts stood up, bound by purple chains.
“alright.
 let me summon all of them before attacking…”he now began to exercise complete control over the bodies and souls of the dead.
who is the most famous person in this world that has been turned into a game?the moment when they were asked such a question, they would think of only one player without hesitation.
“necromancer!”he has achieved so many achievements as to be mentioned several times through the ‘world message’.
 in addition, he showed himself throughout the world through the broadcast of the official channel, where he proved he was not famous by any chance by repeatedly demonstrating his overwhelming power.
“everyone, can you believe this? i just can’t help but be surprised every time!” reporter ahn shouted.
“today his army is…”reporter ahn wiped his face with a trembling hand.
“he is obviously different from the man that we used to know until now.
 he is evolving all the time!”hundreds of immortal undead were the symbol of fear that no one could stop until now.
but the necromancer that reporter ahn saw on the screen was totally different from the man that he used to know.
kugugugu-the battlefield of gwanggyo lake park seen from the air was crowded with the undead army.
 they numbered at least several thousand.
 they were ruthlessly pushing the chinese army’s “shield unit” like combine machines plowing wheat fields.
“look at that! it’s bone dragon! he was seen on the channel when i broadcasted the necromancer’s counter-attack recently.
”bone dragon’s appearance was not that surprising because sungwoo was on top of his head when he announced the creation of the ‘control center’ on the official channel.
but bone dragon’s performance gave the viewers another sense of intimidation.
thump- thump- thump-whenever the monster moved, dozens of flying weapons were crushed under his feet.


so much so that even the highest-grade golem, ‘steel golem’, was crushed like dough.
 it was impossible for taegam’s troops to stop him.
but the real surprise was that what the necromancer showed until now was only half of his total power.
“right now he is controlling a huge number of ghosts! can you believe it?”while the undead army was beating the chinese army on the ground, the ghost army was joining them from the air.
woo woo woo-after they flew with an ominous scream, they snatched up the enemies and ripped them in the air.
 then they swung the weapons that had fallen on the floor with telekinetic power to attack from an unexpected direction.
“when i look at them from a distance, it looks like a mist flowing at great speed.
 a mist mixed with a large amount of blood…”as a result, those stranded in the violent storms had no choice but to collapse in vain.
the battle didn’t take long.
“the war is over…”finally, the ‘shield unit’ of the chinese army was annihilated.
reporter ahn picked up a bottle of water, wiping sweat from his forehead.
“whew! as expected…”although he expected the necromancer would win, the latter won faster than expected.
“to sum this up in one word, the necromancer did his job the best!”reporter ahn’s voice cracked with admiration and even trembled, but he did not hide his feelings.
 those watching his fantastic performance on the chat window showed the same reaction.


 