\section{chapter 446}

that was the demon king's territory, but it was not the kind of castle where the princess in the epic story of a hero could be stuck.
 it was much like the remains of an ancient ruined empire.
 a fortress full of vines and moss stretched across the king's vast domain.
 




and there were a lot of unknown monster statues on the wall.
the strangest thing was the dark red clouds that gathered over the demon king's castle.
 from a distance, it looked like a pool of blood.
'it's his territory, so going into that area puts me at a disadvantage.
 but i still have to go there.
'since he killed paulo and captured the dragon and the fairy butterfly, inflicting heavy damage on the demon king, sungwoo had some chances of defeating him.
'he has been seriously injured.
 he must have been treated after he escaped, but he won't be able to recover fully.
'although his territory, the underworld, was attacked by gangsok, the demon king, it was true that sungwoo dealt a devastating blow to him.
"we've finished installing hypergates! let me have it ready for operation by supplying mana batteries!"they carried out the operation without any failure, and finally, two hypergates opened, and ground troops and the airship fleet came out of them.
 woooooooooong-when dozens of airships flew low over the trees, countless birds and insects soared into the sky.
"ugh, it's so hot here…""man, it's more suffocating than india!"desperate shouts were heard from everywhere.
 a wide variety of players from all over the world couldn't easily adapt to the suffocating air of the amazon rainforest.
"everyone, watch out for vipers and poisonous insects!"the amazon rainforest has never been a gentle place for outsiders.
 poisons, fungi, and animals were all life-threatening factors to them.
 even the veteran players needed to be on extreme alert.
however, the real reason why this green hell was dangerous was that this was the origin of the 'disaster quest'.
"look at that castle.
 it's so huge!" 
"that makes me feel really bad.
"everyone looked at the black giant towering in the distance.
visit to lightnovelworld.
com discover new novels.
"don't gape at that! start moving!"the players were dismantled according to their servers, removed some of the rainforest with their skills and a vacant lot.
 in other words, they made the campsites before starting the war.
one hour later they were joined by the forces that just arrived from the hypergates.
"all troops have arrived! everything is ready!"just then, huge wings cast a black shadow over all the campsites.
 it was bone dragon.
"from now on we will.
.
.
"and the one who got on it, the leader of this army, the necromancer opened his mouth.
"let me start…"the commander of the troops, who was aboard bone dragon, opened his mouth.
 "we're now demolishing the demon king's castle.
"finally, sungwoo's crackdown on the demon king began.
***paulo died after he had his head cut off by the necromancer.
 but he could be resurrected by some special magical power.
"argh!"
however, he felt dizzy and nausea perhaps because of the aftereffects of beheading.
"ugh, it looks like my neck is falling apart again! whew! grace, can you check if the back of my neck is about to fall?"grace looked at him pathetically for a while and clicked her tongue.
"you bastard, why did you let him behead you like that? the more i see you, the more frustrated i am.
""what? why are you so mean? don't you know i blocked him to defend you? i'm going to smash them next time!"at that moment, vivona suddenly appeared before them and offered something to grace.
 it was a cell phone.
follow new episodes on the lightnov‌elworld.
com platform.
"uh? vivona, what's going on?""they went to the amazon rainforest!"she was stunned to hear it, then grabbed vivona's cell phone.
they were broadcasting it on the official channel.
 according to the broadcast, the necromancer and his army were there, with the black giant castle of the demon king in the background.
"oh my god! he's in big trouble now.
 grace? what should we do? yuk!"while paulo felt nauseous again, grace hurriedly went to see gangsok in hiding about the situation.
but there was no change in his facial expression even when the situation was so grave right now.
 "my lord, what should i do? shall i open the portal to go back to the castle? if you give me an order.
.
.
"but gangsok silently shook his head and said, "first, we just focus on what we're doing.
 the demon king's castle is protected by a heavy shield and lots of security forces.
 so they won't break through it easily.
"even if the world tree camp launched an all-out offensive, they would not easily occupy the castle like gangsok said.
 then he turned, thinking that if he obtained the world seed and became the world eater, he could easily hit back their attack.
at that moment grace called him again in a trembling voice.
 "demon king?"he didn't even turn around, but only slightly turned his head.
"well, it seems like the castle is in danger.
.
.
how can they…"grace held out her cell phone and showed the screen, namely the broadcast of the official channel.
 it was showing something shocking.
hundreds of hippogriffs, hundreds of ghosts, and dozens of bone wyverns were flying toward the castle in a big formation.
 and a huge shadow fell over them.
 the wings of the bone dragon filled the screen, but there were two pairs of wings.
actually two, not one, dragons were there.
'two? why?'gangsok snatched isabella's cell phone from her hand and looked closely at it.
you can find the rest of this content on the lightnovelworld.
com platform.
one was the 'bone dragon' sungwoo was aboard, while the other was a slightly smaller but living real dragon.
 all of them were racing towards the castle.
 "demon king…" grace asked without hiding her embarrassment, "has isabella betrayed us?"gangsok frowned at that.
 he thought they could have killed, not control her, because nobody could clumsily control a dragon.
 if the other party let down his guard a bit, the dragon would be able to escape by exercising his overwhelming power.
 so gangsok thought isabella would do so.
 even though she was taken by the necromancer, she was basically like a bomb that nobody could control properly.
as it turned out, sungwoo was controlling her as he wished.
 'how can he control her like that?'***

red flames blazed on the hemispherical shield that covered the black giant castle.
 bang! bang!it was the bombardment by the world tree fleet.
 they focused their bombing on one spot to break through the barrier.
kheeeeeeeeeh~ kheeeeeeeeeeh~when they began to bomb, numerous creatures of hell in the castle under the demon king's control came out in droves and resisted by spewing flames and poison.
but their resistance was pointless because the airships were firing shouts outside their striking range.
"that castle's shield is stronger than any shield i've ever seen! that must be the demon king's power!"sungwoo nodded at jungwoo's assessment, who was in charge of the special commando team's attack.
'it is a stronger shield than the white light sphere.
'perhaps sungwoo could easily break through the shield like he had dropped that bizarre object of the chinese server by shooting the 'fall of the sun' using the super heavy arrow.
 but the super heavy arrow was currently on standby until its cooldown period was over.
 'i'm relieved to have that weapon!'sungwoo turned his head to the right, following the flashing red color in his eyes.
the red dragon, isabella, exhaled breath towards the demon king's shield.
kwawagaceae!updated from lightnovelworld.
comthe spot of the shield where the bombardment was directed intensively began to melt.
the dragon breath carried a destructive force equivalent to the 'fall of the sun'.
because of that, the shield seemed to break open soon no matter how strong it was.
 you can also read this novel on the more advanced platform lightnovelspot.
com

 