\section{chapter 378}

chapter 378: hephaestus’s forge (2)this chapter is updated by wuxiahere.
com




since this palace was literally a space created by the power of hephaestus, nobody could use any other divinity here.
bang!sungwoo checked the skills he could use while avoiding the statue’s huge feet stomping over his head.
 however, due to the nature of the necromancer with few attack skills, he could not fight without summoning the undead.
“do i have to fight that statue alone?”besides, he left behind the major equipment, such as the winter predator, in the real world.
fortunately, there was only one thing that he could summon, namely the grim reaper.
– you have summoned the grim reaper, the scythe of the death god.
* grim reaper’s retention time (00:59:58)* you have gained the power of lich.
sungwoo became lich then grabbed the grim reaper.
 the moment he thought it was fortunate he wasn’t empty-handed, the giant statue punched him with his right fist.
thud-but sungwoo avoided it barely then swung the grim reaper towards the back of his hand.
quagga!the grim reaper’s huge sickle ripped through the statue, cutting his thumb off, which was thrown away.
 but it was not strong enough to shake the statue.
not caring a bit, the statue swung his hand with his thumb cut off.

sungwoo could not avoid his wide horizontal attack.
“kheeeeeeeeh”sungwo was thrown into the air, hit hard by the statue’s attack.
 fortunately, he stabilized himself in the air and landed safely on the ground.
although sungwoo’s muscle strength was considerable, he could not exercise his power because he could not use his double divinity.
thump- thump-the giant statue slowly walked towards him.
 the hallway was quite wide, but with the giant statue, as tall as 20 meters, occupying it, sungwoo was practically blocked off from all directions.
 because of that, sungwoo could not find his weak spot by getting around him.
 he had no other choice but to face him directly.
‘i can’t beat this guy by fighting like this.
 i need to fight in a different way.
’so, he looked around to find any items nearby.
 if there was even a chandelier hanging from the ceiling, he intended to damage the statue by cutting it off.
then, he was distracted by something else.
“what the heck is that?”he saw an unknown energy emanating from a single safe on the left behind the approaching ‘gold guard.
’ it was literally a shimmering light from the crack in the door.
‘i feel something strange there.
’and he felt he was familiar with it.
 he felt as if it was pulling him.
‘i have to go over there.
’thump- thump-however, in order to get there, he had to pass through this massive statue completely blocking his passage.
 but he jumped across the hallway and ran ahead to that statue.
 at that moment, the statue leaned to one side, stretching out his hands to kill sungwoo by pressing down on him.

sungwoo teleported towards the shadow on the floor behind him.
 then, he turned and swung the grim reaper with all his might.
he smashed the statue’s left achilles tendon.
 the cracks in his ankle caused the statue to lose its balance and collapse.
using that moment, sungwoo ran towards the door of the safe in the gap and stretched out his hand towards the handle.
‘it’s opening now.
’when he pulled the handle, he heard the sound of metal hitting each other, but that of a sophisticated device interlocking.
– the seal of the door has been unlocked by the one with an ’embedded footprint.
’“done.
”when the door opened, he couldn’t help but wonder at the same time.
how come the door with the ’embedded footprint’ was here?thump- thump-he had a lot of doubts, but the golden guard was approaching him from behind.
he rushed into the safe.
 as expected, there were many items on the shelf such as shields, spears, etc.
‘i need a more powerful weapon than the grim reaper.
’sungwoo picked up a long spear 2 meters taller than him among the items displayed in the safe.
 he judged that a weapon like a spear would be more effective than a sword when dealing with such a huge statue.
‘by the way, is this spear made of bone?’when he touched it, its material was familiar to him.
[item information]– name: red dragon spear (+3)– grade: unknown– category: player manufacturing– effect: strength increase (+1), agility increase (+5), stamina increases (+2), max mana increases (+300), magic resistance increases (+20%), fire immunity increases (+20) %), fear resistance (+10%), penetration (+1,000%).
 the ‘dragon hunt’ effect is applied when you throw a javelin, so it reduces your target’s moving speed.
 (-30%).
 when you hold it, it gives a low-level target a sense of ‘intimidation.
’– description: the strongest weapon made by grinding dragon bones.
 it contains the power of hephaestus, so it is very durable.
 in addition, the archmage’s ‘special spell’ is engraved on the surface.
+ unidentified set effect: it’s activated when you are armed with 3 or more pieces of equipment made of red dragon bones.
‘what? dragon bones?’sungwoo could not believe his eyes.
 how could he find a weapon made of dragon bones here? to put it bluntly, the weapon he possessed now was literally made of the strongest material known in the game.
“oh, i see.
”the moment he read the description of this item, he could finally dispel his doubts why the safe with his name imprinted on it was here.
‘this is the equipment of the world eater, the dragon slayer of the ruined world.
’he was right.
 this safe was the world eater’s safe.
 he kept the items here when he was an ordinary player.
 but sungwoo obtained ‘balmung (the ruler’s sword)’ from the world eater, so he took away all the power of the dragon knight and obtained the right to enter this place.
‘because this is a safe for the dragon slayer, there are lots of equipment made from dragon materials here.
’the world eater once told sungwoo that he obtained the divinity called ‘siegfried’ by slaughtering the dragon.


if that’s the case, the world eater must have taken special care of the best loot he had obtained by slaying the dragon, namely the dragon’s bones and skins.
 besides, he had the best skills for forging: hephaestus’ forge.
“yeah, the world eater has empowered me in many ways.
”sungwoo put down the grim reaper and grabbed the ‘red dragon spear’.
 then, he turned the spear upside down and grabbed it.
‘it’s been a long time since i used a javelin.
’when the game just started, he often used javelins.
 besides, he had additional effects related to javelins, so he was ready to deal a devastating blow to the giant statue this time.
thump- thump- thump-while the ground was vibrating severely, sungwoo turned towards the door.
 in no time, the ‘gold guard’ was standing in front of the door.
that monster bent his legs and slowly crouched down.
 then he bent his flat head down as if he wanted to look inside the safe.
“you have made a big mistake!”at that moment, sungwoo threw the red dragon spear towards his head with all his might.
there was a wind strong enough to shake the inside of the safe when he threw the huge spear.
the spear hit the statue exactly on the forehead, and the body of the gold guard who was lying flat on the floor bounced back as if it had been kicked by someone bigger than him.
 he was thrown away to the other side of the wall.
at the same time, sungwoo ran out of the safe to follow up with another attack.
but he didn’t have to launch another attack.
‘well, i killed him with just a single strike.
’

 