\section{chapter 331}






 sungwoo called kyungsoo who was about to leave the room.
“kyungsoo, keep general xing’s body separately.
 make sure no one has access to it.
”“sure, will do.
”sungwoo needed to confirm what happened through the ‘memory fragments’ of the general’s body.
 he could not go back to sleep once he woke up, so he put down mir, who was sound asleep, then came out.
 it was already dark, but the inside of the world tree camp was filled with blue light, the brilliant ray emanating from the world tree.
“uh? has he woke up already?”the king of the great mountain was sitting on the great roots of the square.
 as expected, he was puffing up the smoke of his big pipe, as usual.
“i can tell you confidently that if you work so hard like that, you will die even if you don’t fight in the battle.
”“…”the king presented something to him.
“alright.
 just eat this one and give one to jisu.
 she could survive miraculously, but she was engaged in such a fierce battle that she must be suffering from serious aftereffects beyond just being tired.
”it was a dumpling-shaped item, which was effective for stamina and rejuvenation.
however, sungwoo wanted to discuss something with the king.
“i need to talk with you.
”“uh?”the king was very much embarrassed at his unexpected request for a meeting.
in fact, sungwoo had something he wanted to ask the king for a long time, but he kept putting it off because he was so absent-minded until now, so he thought this was the right moment.
“what is it? you make me scared!”sungwoo put his hand in the pocket, then held the scales of imoogi with his hand.
-off air (-)
“can’t you see me?” sungwoo asked.
“oh, i am afraid of your eyes.
”the king came down from the roots with an awkward expression.
then, he followed sungwoo with an embarrassed expression as if he was dragged like a prisoner then entered the server master’s room.
“well, why do you want to talk to me at this late hour in the night?”“i want to ask you about valkyrie, namely jisu’s deity.
”the king’s expression became bright at that.
“oh yeah! she was really cool.
 you should have watched her at that moment.
 it was a once-in-a-lifetime spectacle…”“did you help her play that role?”his bright expression hardened at once.
“uh? what are you talking about?”he scratched the back of his neck and avoided sungwoo’s gaze.
“that sword, the viking sword used by jisu, was one of the conditions for her getting deity status.
 she told me you gave it to her, so stop pretending not to know about it.
”sungwoo has been suspicious of the king for a long time.
 as a former monster, he helped her achieve awakening, and he even gave sungwoo some warning just like imoogi had done before.
 obviously, the king did all this because he knew something.
what’s his real identity?the king laughed heartily at sungwoo’s words, which was also enough to make him look more suspicious.
“well, the world has more coincidences than you think.
 if you try to connect all of them, you just get confused all the more,” the king said.
“coincidence?” sungwoo asked with a smile.
 “do you think this crazy world was made by coincidences? you know you are not here by mere accident, right?”“well, is it fate, then?”“no, this is manipulation.
”
it was a problem that he didn’t have to worry about.
 after this world turned into a game, or maybe even long before that, there was probably no coincidence or fate in this world.
in other words, everything was thoroughly being manipulated by someone, for some purpose.
“where do you come from and for what purpose are you here? tell me, king of monsters!”as if sungwoo touched his soft spot, the king frowned.
monster… obviously, his identity was a monster.
the king nodded with a very serious expression, then said, “yes, i want to know that too.
 didn’t i tell you at our first meeting? why am i here? and the voice that is ringing in my head is not a voice…should i call it revelation? i don’t know what it is.
”this time sungwoo frowned and said, “what is that voice? as you said last time, is it really something like god?”sungwoo didn’t believe in god throughout his life.
 since the game began, however, there was no other reasonable inference than the one that god punished the world.
“well, god? i just wonder what’s the concept of god.
 it’s the most incomprehensible…”“i don’t feel like punning now.
 you really don’t know?”sungwoo asked aggressively.
 he was impatient because he wanted to ask the king as much as possible while they were off-air.
finally, the king nodded with a long sigh.
“i just don’t know, but….
”suddenly, the king twisted his body.
feeling uneasy, sungwoo turned his head.
and a familiar message rang.
-뀕궭$%%%[email protected]긝!(%67#)-shhh!$!$%$$##%!!&*-the connection to the client-server has been terminated due to a fatal error.
 (error code:0014231532)“this one is…”as the message slowly faded away, the king raised his head.
 more precisely, his eyes were different.
“well, i know…”right now, someone on the other side of the system was staring at sungwoo.
“yeah, sungwoo, i understand that you have lots of questions.
 but what you are doing now ignores a big risk facing you.
”sungwoo looked straight into his eyes.
 eventually, he encountered an unidentified helper.
sungwoo slowly said, “who are you?”“i can’t tell you,” he replied firmly.
at that moment, sungwoo felt that he could never get his answer.
so, he changed the question.
“then, who am i?”it was a difficult question.
 in a ridiculous situation where the world turned into a game, it was natural for him to doubt his own existence.
as a matter of fact, even sungwoo agonized over whether this was reality or he was like a ‘brain in a barrel’.
as if he understood sungwoo’s question, the king just smiled, which was an artificial lifeless smile.
“you are just you.
 don’t worry about it.
”should he feel relaxed about this kind of reply?“this world, including you, is a natural being.
 you can just think that you have been invaded by the outside world.
 and you just have to believe that i’ll help you achieve liberation.
”although he got confused, sungwoo didn’t reply.
“but, as i said earlier, i’ve no time to satisfy your curiosity.
 as you know, i won’t be here long, but let me give you one more important piece of advice.
”“advice?”“don’t forget that my advice has always been valid, so listen to me well.
 a little later, someone will come to you.
”

he held out his head and approached sungwoo.
then he whispered, “kill that man.
”that was the last word the king left behind.
-the system has been urgently restored.
the king dropped his head right away as if he fainted.
 then, he put his head down on the desk.
“oh, it aches!”at that moment, sungwoo heard somebody’s footsteps in the hallway.
 like the king said, someone came.
 sungwoo moved his hand and grabbed the hand cannon in the waist.
rattle-somebody quickly opened the door without knocking.
“well, sungwoo!”it was kyungsoo.
sugnwoo was embarrassed because he was advised by the king to kill the one who came to him.
 was it kyungsoo? no way!“uh, that’s….
”kyungsoo took turns looking at the king, who grabbed his head with his head down, and sungwoo with a terrible expression.
 it looked like sungwoo punched the king hard.
“ah, was i rude?”“what is going on, kyungsoo?” sungwoo asked, suppressing a sense of alertness.
“junghoon has come here with his crusader team members.
 he says he needs to talk to you urgently, so he wants you to come down right now…”someone that sungwoo had to kill like the king said was junghoon, not kyungsoo.
why?“man, if this is what you mean, you are now making fun of me…”

 