\section{chapter 377}

chapter 377: hephaestus’s forge (1)hephaestus was a blacksmith god in greek mythology, and many gods and heroes used his weapons.





‘is it possible to craft or enhance items in a space named after the blacksmith god?’of course, there was no way hephaestus would strike the hammer himself.
 however, the fact that the place was named after him meant that the blacksmith there had such power.
sungwoo looked around.
 it overlapped with reality because the forge was in a translucent shape, so it was blocked by the walls of reality, even though it was quite a large space.
‘should i open it in a wide place like this?’questioning it, sungwoo slowly took a step forward.
then, a message rang.
- do you want to completely enter the subspace? (y/n)* y: you are being moved to the ‘hephaestus’ forge’.
* n: you continue the state of ‘space overlap’ with reality.
‘yeah, this is what i expected.
’after all, it’s impossible to apply the system clumsily to a place named after hephaestus.
the so-called ‘space overlap’ function seemed to have been made easy to use even without anybody entering the forge completely.
sungwoo turned to kyungsoo and said, “kyungsoo, i need to visit a place briefly.
 like i said, you should not allow anyone to approach the world tree.
”“pardon? where are you going…?”sungwoo clicked y even before hearing him out.
 then, the office and kyungsoo disappeared before his eyes, and the blacksmith that seemed translucent stood out clearly before him.

sungwoo was standing in a different space all of a sudden.
 the brightness of the room as well as its temperature changed.
 a huge brazier in the distance was burning hot, heating the room.
‘is this a space for crafting and storing items?’a long corridor continued to the hearth, and numerous rooms were adjacent along the hallway to the left and right.
 it was not an ordinary room.
 roman numerals were engraved on each iron door with all kinds of patterns, which looked like a kind of safe.
sungwoo approached the nearest door.
 then, he looked inside it through a small window at the top of the door.
 there was a decoration cabinet, and all kinds of items were displayed in it.
‘alright, this is the place where they keep the items of the guardians of the world eater’s world.
’it made sense logically.
 the items of those who were sealed in the capsules of the hall of the guardians seemed to be stored in this space.
in other words, their items were stored in a sort of mega-inventory like this, so that they could use the items again when they woke up one day.
 but it was impossible for them to wake up again, so the world eater handed over all of their items to sungwoo in his last moments.
‘in that sense, the world eater must have wanted to resist the system…’sungwoo turned his head again and looked at the end of the hallway.
 he approached the giant brazier and anvil there.
 that was the core facility of this space.
‘this looks similar to the forge created in the field, but it is much more luxurious.
’he then put his hand on the anvil.
- if you use ‘hephaestus anvil’, the ‘success chance’ and ‘additional effect chance’ are greatly increased.
 also, its base durability increases by 300%.
he smacked his lips at the moment.
 in his eyes, this item was not very attractive.
‘well, i guess the blacksmiths will still like it.
’the blacksmiths of the world tree camp were growing at a considerable level.
 however, they hadn’t yet reached the skill level of the wpu hearst workshop.

‘i’ve seen them working there, but they are definitely ahead of the guys here.
’hundreds of blacksmiths worked with arnold hearst, the “elder blacksmith,” as their leader, who was a five-star blacksmith.
therefore, they could make a large airship as easily as a car when they received the synergy effect of ‘dwarf’.
‘if they are excellent in skill and synergy, we can narrow the gap with them using our myth-grade equipment.
’but sungwoo was more interested in something else.
 he took off his hand from the anvil and turned his head again.
sungwoo and the world tree camp players could now possess the enormous items in the numerous safes on the left and right of the hallway.
so he placed his hand on the doorknob of the nearest door, vault number 23, and pulled it open slowly.
snap-it was locked- the door is protected by powerful magic.
* only the one with an “embedded footprint” in the box can access it.
* you can’t unlock it in any other way.
“as expected, it’s been sealed.
”but it was a little different from before.
 sungwoo could not use the ‘unseal’ spell or the ‘unlock’ skill.
 it seemed like a very special seal.
“if the seal is so special, does it mean that even mir can’t unlock it?”although mir opened the world eye and the hephaestus forge, he could do it with the ‘unseal’ spell.
 in other words, he could not use it this time.
“then, how can i open this?”sungwoo was embarrassed at the moment.
 all of those who had “embedded footprints” in the box were dead, so how could he open it?but he stubbornly pulled the door again.
 then, an additional message rang.
- guidance: if you need to ‘force release’ due to the long absence of those with “embedded footprints,” use the two methods below.
.
 use hephaestus’ master key (hephaestus’ power required.
).
 grave robber’s trial (unknown) *you can try this only once in 24 hoursfortunately, there seemed to be an alternative option, but the no.
 1 option that seemed to be legitimate was beyond sungwoo’s reach.
hephaestus’s power meant sungwoo should have the blacksmith’s divinity, but he had nothing to do with a blacksmith, so there was no possibility of his obtaining it.
‘well, if i can rely on hearst, the elder blacksmith, i might get it someday, but i can’t afford to wait indefinitely.
’since it was inevitable for him to forcibly unlock the safe, sungwoo had to clear the quest shamelessly called ‘ grave robber’s trial’so he chose the no.
 2 option without hesitation.
at that moment, he heard something open from the ceiling.
 he instinctively stepped back.
then, a large shadow fell over him and spread quickly.
 something huge was falling.
koo-woong-

when that huge object hit the ground, it shook violently.
 it was a huge golden statue about 20 meters in size.
 to be precise, it was a giant statue made of gold.
gugugugu-the giant statue slowly raised his head.
 a red light shone in his blurry eye sockets, then he looked at sungwoo.
- the guardian of the forge, ‘gold guard’ has appeared.
“what the heck? has the fight already started?”sungwoo was really embarrassed because he expected he would receive something like a quest.
 but he found himself engaged in a fight all of a sudden.
“well, it’s good that this is not complicated stuff.
”actually, the fight wasn’t that difficult for him.
 he bravely entered the demon’s cave and killed the world eater, so it was a piece of cake for him to destroy the giant statue.
so he stepped back and opened the fellblade.
 but he encountered some unexpected difficulties.
- a ‘special power’ dominates this space.
 the use of ‘the skill’ has been restricted.
he could not even use his divinity.
- this space is ‘god’s realm’ that is governed by a ‘specific divinity’.
 you can’t use any other divinity here.
“damn it!”

 