\section{chapter 150}

                             




“hey, my little boy! you’re doing great, too! good boy! let’s move!”minsok was now different from the days when he fought to protect his family.
 now that he had nothing that forced him to look at something compulsively, he raised his shield and rushed fiercely into the enemy camp.
then, he swung his long sword up and down violently.
 whenever he swung it, cut bodies piled up under his feet.
“ahhhhhhhh! go away, you devil!”the chinese wizard screamed in horror.
“devil? yes, i can be a devil to protect my family, you scum!”based on his strong conviction, minsok slaughtered those he defined as enemies.
 since he didn’t have to look back to protect his family, he has been reborn as a “death knight,” who killed his enemies without hesitation.
a black chain stretched out of his shield, tying and dragging the enemies’ bodies.
then, orun quickly ran toward these defenseless enemies and swung his sword.
orun made the most of the increased mobility inherent in his small body.
 orun jumped out of unexpected places while wandering around on the complex battlefield, then dealt a fatal blow.
even if the enemies defended against his attack, the moment they aimed their weapons against him, they would slip and lose their balance as if they were oiled.
 therefore, orun’s follow-up attack after they fell was right on the mark.
puck!“watch out for your left!!”“hey, a corpse is falling on your right! avoid it!”bang! bang! kugugugugugu…as the fight went on, the pirates that numbered a total of 3,321 decreased rapidly.
 as things stood now, it was highly likely that they would be annihilated in this mini-game.
“hold out!”“if you hold out a little longer, you’ll get a buff!”nevertheless, the reason they were holding out to the end was that they had some conviction.
 in other words, not only jahon but also the pirates were convinced that since huei joined the occupation operation, he would certainly succeed.
“if huei wins, we will win, too!”
“trust huei!”who is huei? he defeated many swordmasters in a one-on-one confrontation and reigned as the strongest among swordsmen in mainland china.
 so much so that even if chinese players spat out curses against the red revolutionary army, huei was exempt from such criticism.
“soon they’ll get buff at point b.
”“so, hold out until then! next is point c!”shortly afterward there arrived news about huei.
 since his performance was being broadcast live, they could know it in real-time.
“what the heck! what happened to huei?”someone raised his voice.
 even in the fierce battle, they heard his voice clearly.
“he was killed!”it was a shock.
 the only person they relied on the unfavorable battlefield was killed.
“what did you say? who the hell killed him?”“he was killed by a korean woman! huei couldn’t swing his sword at her more than ten times before she beheaded him!”“no way! how could that happen?”“are you sure it’s huei?”it was the moment when their last hope disappeared.
“how ridiculous! how can i believe he was killed?”even jahon, who heard the shocking news, felt dizzy for a moment.
kuan came to him and said, “general, they turned the camera angle to this place because camera 2 was hit by the enemy.
 shouldn’t we stop broadcasting right now? we can’t broadcast the scenes of us being defeated…”“no! if we end up like this, not only we and our organization but also our general are history!”jahon couldn’t give up here.
 now he had only one option left.
 it was to defeat the necromancer in this place.
 he looked around the battlefield desperately, as if he was grasping at straws.
“necromancer….
”he then loaded the hand cannon.

“necromancer, where are you?”bang! bang!he fired the cannons randomly and walked into the middle of the battlefield.
“necromancer!”and he found the necromancer in the shadow of the trees.
 he was disguised as lich in a dark green robe and a hero of the korean server.
“come on! let me deal with you! i’m gen.
 jigong of the red revolutionary army!”“…”“if you don’t come out, let me rush at you!”bang! bang!he fired the hand cannons in both hands in succession.
 the necromancer created a bone shield to block the cannons, but the bone shield was shattered and his body bounced back.
the power of a hand cannon was different from that of arrows.
when jahon loaded his hand cannon and went valiantly, the camera filmed him.
in fact, this scene was their last hope because jahon made the necromancer step back.
“let me jerk you off one more time!”shouting like that, jahon moved on toward him.
 the moment he stepped on the shadow of the tree, the necromancer disappeared in an instant.
“uh?”he felt somebody’s presence behind him.
 right there, somebody’s green eyes glowed.
 sungwoo teleported from shadow to shadow by using the ‘shadow king’s bracelet.
“general!”kuan, who was standing next to him, called him first.
 he spotted the necromancer appearing behind him, opened his mouth, and prepared to shout at the top of his voice.
 he felt he would be able to drive out the necromancer when he shouted like that, but the necromancer was faster.
 his huge scythe passed through kuan three or four steps away.
kuan’s head was blown away, and his sunglasses fell into the mud.
 then, sungwoo’s left hand grabbed jahon’s neck.
“argh!”jahon felt a sharp pain as if his spine was broken.
 since sungwoo was receiving a tremendous increase in stats due to lich buff and occupation buff, his current muscle strength was 45.
 nobody could endure such strength.
sungwoo stuck jahon’s head into the dirt.
puck-“argh!!”in the middle of the battlefield, jahon was completely overpowered, losing his hand cannon.
minsok and orun approached sungwoo and watched out for the surroundings.
 no pirates dared to approach them because they knew they would face the same fate if they did.
“general…”“now, what should we do?”even the camera operator, completely stiffened, was filming this scene.
 his hands were trembling.
 he knew it was right to end his broadcasting, but he could not judge at all because he had been following jahon’s orders until now.
“hey, smile! the cameraman is filming you.
”sungwoo shouted at jahon, looking at the camera.
 underneath his smile was seen the scene of jahon frowning, incapacitated.
following the female swordsman running wild, stained with blood, this time a demon with the bones of half of his face exposed and his green eyes flashing was being broadcast on the chinese server.
“kuuuuuuuuuuuuh…”sungwoo pressed his neck with his feet and lifted the grim reaper.
at that moment, jahon shouted.
“general! gen.
 chongong! please don’t come to korea! never! never!”that was jahon’s impression of the korean server.
 he realized that regardless of the reputation of the red revolutionary army, his whole organization could be destroyed if they set foot in korea recklessly, and that was his last desperate will based on his costly experience.
“no, you can come over and play!” sungwoo said, looking at the camera operator.
“hey, come here.
 don’t end the broadcast yet.
”as a result, this hellish broadcast was going to continue.


although they had little chance of winning, the pirates did not stop resisting.
“we have to fight to the end!”“we can’t run away anyway!”as long as the mini-game was open, there was no way for them to escape the island.
 therefore, even though their leader was killed, they had no other choice but to resist strongly.
sungwoo started work to get rid of the pirate remnants.
 he planned to occupy all three places a, b, and c, then destroy them with the help of overwhelming buff.
-grim reaper retention time (00:14:53)since there was not much time left to maintain the effects of grim reaper and lich, he had to get things done quickly.
however, there was one problem.
 the moment he held the flag, he could not move, so it was impossible for him to occupy the places alone.
so, he called heyon, who was on gust to fly over kanghwa island, as an alternative option.
soon, heyon appeared.
 gust made a turn around the foot of the mountain at tremendous speed, then landed at point a at the peak of mt.
 mani.
“necromancer! let me occupy it now!”when he nodded, she grabbed the flag.
-allies are occupying it! (100 seconds remaining.
)“they are trying to take it over!”“if we lose point a, we’re doomed!”the pirates moved to stop the occupation.
 however, sungwoo’s undead blocked them.
when the three bone wyverns sat down on the peak, spread their huge wings, and raised their heads threateningly, the pirates couldn’t even dare to approach.
“damn it!”“how can we break through such monsters?”now, unlike when they occupied point b, 100 seconds was too short for them to take any action.
 so, the pirates climbing the peak could not help but be devastated when they watched the number appearing above the flag.


 