\section{chapter 437}

"oh, you are that famous necromancer and valkyrie! and their minions! hi, guys!"




from a close look, he was a big guy who was more than two meters tall.
 a black tattoo stood out over his ragged muscles because he was only wearing a tight t-shirt.
it looked like a mestizo, a mix of latin and native americans, but was he from the extinct brazilian server?"what did you say? minions? i'm no longer his minions.
"hanho murmured if he was dissatisfied, and jisu placed her hand on the back of the sword.
"there are three of them!" jisu shouted.
as soon as she said that, two more walked out from the shadow of the wall.
 they werea tall hispanic woman and also a slender hispanic man.
 judging by their outfits, they looked like a wizard and an assassin, respectively.
they reminded sungwoo of the mexican "cartel" that chairman love once told him about.
 she said they were also loyal to the amazon dragon.
"i can feel they have murderous intent against us.
 especially that guy on the right who had something under his shadow.
 i just feel ominous," jisu whispered into sungwoo's ears.
advertisements    so sungwoo looked at him sneakily.
 at first glance, he was a wicked guy.
".
.
.
"he was wearing a black robe pressed down on his disheveled head.
 he was looking down on the floor even though he was facing sungwoo.
 his face, which was slightly revealed, was filled with all kinds of piercings.
'by the way, what about his shadow?'when he scanned that man's shadow, sungwoo could discover that his shadow was somewhat darker and longer.
 it was no ordinary shadow.
"is that his skill? i mean that shadow.
"
"i think so.
 please watch out.
"actually, her warning was true.
 'i think i have to stay alert,' sungwoo thought to himself.
 he took a deep breath, raising his alertness at the highest level.
 his opponent was the demon king gangsok and his colleague dragon.
given that gangsok, who usually enjoyed playing solo, hired the dragon, the latter must be very strong.
"where is gangsok han, by the way?"having said that, sungwoo looked at the huge stone gate blocking him.
then that muscular man began to shout, blocking his vision.
"ah, our demon king has something to take care of, so if you want to see him, you should wait a little longer.
 can i ask for your understanding?"giggling at sungwoo, he put his hand on his chest and lowered his head.
his exaggerated gestures were funny.
 "really? well, i also have something to take care of.
 can you step aside?" sungwoo responded.
 "uh? what are you talking about? are you here to see our queen that you have never met?"queen? did he mean the dragon? sungwoo specifically pointed to the stone gate by raising his index finger.
 "absolutely! why am i here if i don't want to see them? if you don't want to fight us, can we just pass by?"
right inside that door was the answer to this quest.
 even though gangsok came here first, sungwoo had no intention of giving way to him.
 as expected, that muscular man scratched his chin as if he could not accept sungwoo's demands.
"um, our demon king didn't tell us to fight you if you didn't listen to us, but she didn't clearly tell us not to fight you.
 man, this is a dilemma.
 grace! what do you think?"that tall guy turned to grace, showing his back to sungwoo.
 obviously, he tried to show he was confident of defeating sungwoo.
 the female wizard called grace raised her head and looked at him.
 but she shook her head as if she didn't feel up to fighting.
"well, hey! vivona! what do you think?"vivona was a wicked man leaning against the wall on the right.
 but he, too, only rolled his eyes at sungwoo briefly, then looked down on the ground.
"man, my friends are so reticent that they don't want to express their opinion easily.
 well, it looks like it will take us some time to fight or not.
 can you wait?"after all, he played on words to provoke sungwoo.
 sungwoo sighed at that because he had no choice but to fight.
at that moment, jisu moved her feet a bit.
 sungwoo stopped after sensing her reaction.
 'what is it?'she was staring at the ground, more precisely, that muscular man's toes, who was standing in front of her, but she felt something weird elsewhere.
sungwoo knew that she was paying all attention to the man in the shadow leaning against the wall on the right, the guy called vivona.
".
.
.
"obviously, she was sending a clear signal that she would behead him if he showed the slightest sign of moving.
 …"vivona seemed to be staring into the air, but he must have been scanning the entire space.
for some reason, sungwoo felt the air filling this space was scary.
 obviously, the two seemed to have already clashed their swords several times.
'the moment he clashed with her, he would try to behead me.
'the reason the assassin was so scary was that he could kill his target in an instant by totally ignoring the opponent's power.
 and if he had the job of an assassin, he would usually aim at the most important player first.
 and he was the necromancer.
however, sungwoo had a solid supporter, namely, jisu.
'i can't tell how strong this guy is, but let me trust jisu.
"but it seemed that even she began to have some trouble.
 "hah…"sunwoo felt her breathing roughly.
 a drop of sweat ran down her cheek.
 'what's the matter with her?'he could not believe that she felt some sort of uncontrollable tension when she was equipped with the supernatural senses that no ordinary player could ever achieve.
sungwoo's heart was beating fast at the same time.
".
.
.
"a brief silence passed, and the muscular man scratched his chin and took two steps forward.
"ah, i hate this kind of atmosphere, but i'm sorry i don't know how to serve guests.
""paulo, you're talking too much.
"

it was the wizard called grace.
 she stepped out of the shadow, striking the ground with a long old wooden stick.
 she was an alluring and cold-hearted beauty.
 looking at sungwoo carefully, she said in a sweet voice, "by the way, that handsome man, necromancer can be upset and cut your jaw in an instant.
 it looks like they are quite upset right now.
"that muscular man called paulo, pretending to have been surprised, stepped back.
"no way! how can he do something so ungentlemanly when he has seen me first? even the warriors of vale tudo i fought were not that rude!"vale tudo was a brazilian martial art without any standard rules.
paulo seemed to be a martial arts-type player, considering that he had a big build and held no weapon in his hand at all.
 thump- thump-while they were dragging their feet like this, there was a big vibration inside of the stone gate.
sungwoo glanced at jisu quickly.
 when the fighting started, the man in the shadow would try to behead sungwoo, but she would try to protect him, of course.
 advertisements    'i have no choice but to trust jisu.
'sungwoo raised the grim reaper.
'since there are only three here, let me push them with multiple weapons.
'at that very moment, something unusual happened.
clang!

 