\section{chapter 433}

"by the way, what the heck is this special awakening or dimensional predator?"




sungwoo had heard that word.
 when he encountered the world eater, it was the title attached to his name.
"then, i can be the world eater?"when sungwoo sought and found the world eater, he wasn't necessarily a ruthless aggressor.
 he was also a player of another world, so he was eating another world to save his world.
"i don't want to go through the same tragic fate of that world eater…" said sungwoo, getting aboard bone dragon.
 "but i need his power.
"bone dragon soared towards the split sky.
***the sky was split in half.
- you can enter the hidden stage 'hall of angels'.
entering an unfamiliar place was always difficult for sungwoo to decide.
 especially when he didn't know what's on the other side, like a portal, it was even more difficult.
 advertisements    but he had to go there in order not to get stuck at this place.
 'i'm going to put an end to the old troubles.
'this was like disinfecting the 'source' infested with pests to eradicate them.
'after this, we're going to approach the end of the game.
'there were not many opponents left behind, who could be regarded as "monsters" that had appeared when the game began, except for the players.
except for the two absolute races, angels and demons, their only opponent was the amazon dragon.
they got almost close to the entrance of the hall of angels.
 
"okay, let's enter the hall of angels!"all the troops floating in the sky turned their direction at sungwoo's order.
"i don't know what's inside! so, get ready to go inside while staying on alert!"since the entrance to the hall of angels was open high in the sky, only the world tree fleet and the special commando unit could follow sungwoo.
 "don't worry about us.
 just keep going!" said minhum.
 inevitably, tens of thousands of troops had to stay behind on the ground, so minhum decided to control them.
sungwoo and bone dragon shoved themselves through the cracks in the sky.
- you have entered the hidden stage 'hall of angels'.
as soon as he entered it, sungwoo summoned 20 ghosts and spread them everywhere.
since this was the main base of the enemy, he had to get them ready for their surprise attack.
 'i don't see anything.
'however, nothing stood in the way of sungwoo's forces.
 instead, something like a vast field appeared before them.
'white desert?'as if he looked at a salt desert, a white desert filled with pure white sand appeared before his eyes.
 it was so vast that wherever he looked, half of it was the blue sky while the other half was the white sand desert.
 the special commando unit then followed him into the hall.
 they dispersed in all directions while staying vigilant.
"stay vigilant!"
after they confirmed the area was safe, the airships came inside slowly.
 wooooooooooo-the messenger approached bone dragon.
 inho was on the deck of the messenger.
 he shook his head while looking around the new world.
"man, this is driving me nuts.
 i really can't figure out which way we should go.
"wherever he looked, he saw the same landscape, so he could not find out the right direction at all.
"i know how.
"fortunately, sungwoo had one with the special ability to overcome the difficult situation when he was faced with an unknown place like this.
 it was none other than mir.
"let me rely on your power, mir.
"after swallowing and absorbing the fox's marble, mir acquired the skill 'world eye.
"[skill information]- name: world eye- grade: special- class: passive/active- consumption: none*you obtain the eyes with which you can see through everywhere.
 based on that information, you can also easily overcome all the obstacles to your exploration.
+ master's map: you can make a small map that displays all the topographic features in a certain area (20km) and displays your location in real-time.
 this map will expire after 20 minutes.
 (cooldown: 1 hour)+ neutralization of the maze: locates the 'hidden space' within a certain radius (300m) and easily unlocks the 'traps' and 'seals' over the absolute grade.
 (cooldown: 30 minutes)"let me see…"one of the lesser effects of world eye, 'master's map,' creates a detailed map of the surrounding 20km.
 but there was a problem.
sungwoo lifted his head and looked around.
 it seemed that nothing existed within 20 km of the surrounding area, but the white desert continued into the horizon in the distance.
"man, i need something like a starting point in order to use this map.
.
.
it is just useless even if i make a map and see nothing.
"in the worst case, even if i made the map using my skill, there could be nothing on the map.
 the one who came up with the answer to my question was the black lion, the head of the human beasts aboard the messenger.
"necromancer! it's northeast! i can feel a certain intense energy moving this world over there.
"the black lion once found the heart of the demon's cave through the skill 'realm of the predator'.
 at the time, he did quite well even in a sandstorm with near-zero visibility, so it seemed that he could sense it more easily and further than before in open and unobstructed terrain like this.
"then we will fly in combat recon formation while thoroughly searching the surroundings.
"the world tree fleet has practiced numerous formations in preparation for various situations.
 one of them was a "combat reconnaissance formation" to guard and search a wide area.
"spread widely in the sky, and scan the entire area on the ground! you must not miss even a single ant!"the 15 airships widened the gap between them, and the special commando unit members filled the space among them while advancing.
 a total of 15 members of the special commando unit flew at the forefront on the search and recon mission.
ten minutes into flying, they noticed something on the ground.
 "hey, i've found something unusual on the ground!"the search team found something.
 piles of white stones were piled up on the white sand.
 junghoon descended with a few members of the special commando unit, retrieved the fragments, and brought them to sungwoo.
 

"sungwoo, these are the corpses of angels.
"they were pieces of marble that angels turned into after dying.
 "then, did they fight somewhere here?"fight?sungwoo tilted his head at his question.
 what did the angels fight inside their den?there was a fat chance that they fought against each other…at that moment one of them came to junghoon and sungwoo and shouted, "look over there! it's like a building!" when they looked at the horizon he pointed at, there was a black shadow between the blue sky and the white desert.
 they could not identify it accurately because it was so far away, which was just shaking like a haze.
'hum, let me make a map over here.
'there was a strong possibility that there were angels over there, but because of the evidence of their fighting, it was not prudent to go there recklessly.
- 'black dragon (hetzling)' creates a 'map of mastery' around this area.
mir read sungwoo's intentions and made a 'map of mastery' using his world eye.
woowooong-advertisements    then some lights were combined in the air to create a translucent white paper.
it was like a paper-type display made with futuristic technology.
sungwoo looked at the map, which showed all areas within 20 km.
he really felt as if he was looking at the mini-map of the game.
"what is this place?"

 