\section{chapter 368}

chapter 368: devil’s world tree and world eater (10)hundreds of mouths opened all of a sudden, vomiting acidic liquids, but they were useless before this gigantic being.





then, the monster swung his arms and attempted to attack him with the whip.
 it was the same tactics that he used to destroy the large skeletons at once.
 but even such an attack failed.
the dragon’s bones were as thick as old trees and hard as tungsten.
the whip only made some scratches on the surface of the bones.
 even though bone dragon lost his life a long time ago, and went through the hard times since then, he withstood all the attacks by the monster.
‘he is so cool for an undead!’even sungwoo admired bone dragon.
 he didn’t know much about aesthetics, but this gigantic creature was not just huge, but antique and grand.
 he was beautiful in terms of the balance, texture, color, and curves of his figure.
‘above all, he’s overwhelmingly strong.
’dragon bones were often treated as the most powerful weapon material in numerous fantasy stories.
 this game was no different.
“…”even the world eater got carried away with his beautiful figure.
 however, he seemed shocked in a different way.
“you, you…”was it because he recalled some old forgotten name? he couldn’t speak easily.
bang!bone dragon lifted his claws once more and slammed it down over the commander.
 when the commander was devastated by bone dragon, the undead army charged at him all of a sudden like a swarm of ants.
puck! puck! puck! puck!with the monster commander unable to move at all, it didn’t take long for them to disintegrate that disgusting body.
- you obtained 45,000,000 gold by hunting the boss monster ‘commander of the 2nd army of demon’s cave.
”meanwhile, sungwoo did not stand still while bone dragon was attacking the commander.
he controlled 10 ghosts and aimed at the world eater who let down his guard at the moment.

“kheeeeeeeeeeeeeeh!”when the world eater was attacked by ten ghosts at the same time, he quickly moved his body, startled, which didn’t befit his reputation at all.
 now, that he was empty-handed, he couldn’t defend himself properly, but he was still strong enough, as his level 43 showed.
when the light exploded from his palm, one of the ghosts disappeared after he was hit directly by the light.
 but the next moment, sungwoo appeared behind him using the ‘shadow movement’ skill.
 then, sungwoo swung his grim reaper in his and balmung in his left hand.
the blade of the giant sickle slammed into his neck without a single error.
puck!but they couldn’t inflict any damage at all because he spewed dark red blood over his body, forming a thin film.
‘that’s an invincible skill.
’he was wearing a blood-red armor that covered his body, so the blood was flowing from his hand, not the sword.
 it was probably a ‘proprietary item’.
when sungwoo’s attack failed, this time the world eater started a counterattack.
 he spread his palms toward sungwoo’s face.
 it was magic.
at that moment, a sword fell from the air.
 it was the telekinesis of a ghost.
 it hit the world eater’s back.
blood splattered from his body.
 he staggered.
“argh!”for some reason, the sword broke through his invincible skill and harmed him.
‘my attack worked a moment ago.
 why?’but he didn’t think about it for long.
 the weapon that hit the world eater was the sword ‘ascalon’ he had obtained from under the dragon’s bones.
 he realized that the sword had the ‘dragon slayer’ effect.
“that armor and dragon’s blood?”as balmung proved, siegfried, immortalized after being bathed in dragon blood, was the world eater’s divinity.
 that dark red bloody armor was also his ‘divine skill’.
even if he was immortalized, he had a dragon’s blood, after all.
 as a result, it was destined to be easy prey of the dragon’s natural enemy, the ‘dragon slayer’ effect.

“alright!”sungwoo handed the grim reaper to one of the ghosts, then grabbed ‘balmung’ which he had taken from the world eater.
 then, he charged at the world eater.
the world eater was overwhelmingly faster than sungwoo a little while ago but not anymore.
‘he is definitely slow.
”the world eater was dying in real-time.
 sungwoo jumped and chased him, who soared into the air and disappeared from sungwoo.
but sungwoo had other options to chase him.
puck!“argh!”ascalon was stuck in his left wing bone.
 actually, sungwoo sent a ghost to intercept his escape route and attack the fleeing world eater.
 when his movement slowed significantly, sungwoo charged at him and stabbed him in the stomach with balmung.
“ahhhhhhh!”finally, his invincible skill made of blood was broken and his body became defenseless.
sungwoo received a third sword to deal a fatal blow to the world eater.
 it was the “ruler’s sword” connected to mir.
puck!it pierced the heart of the world eater.
 it was a perfect fatal wound.
 sungwoo grabbed the handle of the ruler’s sword and looked directly at the world eater’s face.
“world eater, no matter what your background is, it doesn’t matter to me at all.
 you failed.
”“…”“by the way, you’ve sacrificed so many of your colleagues to defend this world, but you failed.
 how can you dare to devour another world?”when sungwoo accused him harshly, the light gradually went out from his eyes.
 helplessness replaced his cold-heartedness.
 he gasped for breath.
“yeah, i failed.
”he admitted his failure without any objection.
 he had no choice but to do so because there was nothing more he could do.
the world eater barely grabbed his neck and said, “you must protect everything in this world.
 and take revenge on those who have caused so much havoc on this world!”he released sungwoo’s collar and raised his finger to point somewhere.
“check the ceiling of the guardian’s hall…”after he spoke for the last time, the world eater’s eyes began to close.
he turned his eyes to bone dragon at the last minute, then seemed to call his name quietly.
- you earned 43,000 gold by killing a player.
then, a black flame rose from his body and disappeared into the air.
- you have obtained 1,000,000,000 gold by eliminating the alien predator ‘world eater’.
starting with that, all kinds of messages popped up before sungwoo’s eyes.
- you have successfully cleared the exclusive quest [guardian’s duty-3].
* you can choose a reward.
.
 upgrading of your regular deity.
 right to change your job- you have leveled up.
 (lv.
 25)- you can have multiple deities by satisfying the conditions.
* you can use the deity of the king of underworld.


‘finally, i got this title, king of underworld.
’the best reward for him was the king of underworld title.
then, some unexpected things happened one after another.
- the ‘ruler’s sword’ has obtained a new name because you met the special conditions (dragon slayer)’.
the ‘ruler’s sword’ connected to mir killed the world eater, who had the dragon deitus, which, in turn, gave him the ‘dragon slayer’ effect.
‘if this is the case, i have three ‘dragon slayer’ items?’usually, a special synergy would start when the three of them came together.
that’s what happened next.
- the ‘synergy effect’ has been triggered by team play.
[synergy list][ol start=”43-]dragon expedition (hidden)- category: weapon synergy- condition: equipped with 3 or more ‘dragon slayer’ weapons- effect: additional damage when attacking dragons (+200%), all types of ‘breath immunity’ increase (+200%), ‘dragon peer’ immunity increases only for its owner (+200%)as sungwoo told chairman love in america, he began to gather the strength to fight the dragon.


 