\section{chapter 260}

                            ‘one heart association’, an association of survivor groups in paju, had no choice but to react to the mainstream this time.
 geographically, they faced the north korean server, so they should brace for the possible disaster.





because of that, seven groups living in paju gathered together.
 they held an emergency meeting.
“hasn’t all this happened because of that bastard, the necromancer? why do we have to suffer damage when we are living peacefully here?”“yes, you’re right.
 let’s post a condemning statement on the community right away.
 how long can we stay silent?”“you bet! i’ve never had this kind of bolt out of the blue in my life!”they had never come to the fore until now, but they built a considerable force on their own.
they were comprised of five groups with a total of 3,000 survivors.
“if the necromancer hadn’t moved around frivolously from the beginning, this wouldn’t have happened!”“tut! tut! i knew that bastard would bring about big trouble someday!”they concluded that this main quest was a human disaster caused by the necromancer and agreed to hold the world tree camp accountable.
one heart association was not the only organization that showed such a hostile reaction.
[1,015] necromancer, take responsibility and cut down the world tree.
-author: dave choi │ hits: 51,453no matter how good you are, this is not something you can tackle.
 they are going to carry out simultaneous massacres on the entire korean server.
 can you take responsibility for that? don’t be stubborn, necromancer! just accept the conditions of the mainstream and cut down the world tree right away and end this dangerous situation.
 i strongly recommend you cut the tree down as soon as possible and turn on the broadcast.
[comments: 13]- respect 02: i agree.
 if you want to fight them, you guys go and fight.
 we’re going to live quietly.
 so, don’t mess up with our lives!
- sokcho captain: i support you.
 make a wise decision, necromancer! all of us might die.
- hyeyoni: i agree!- cholgap hwang: it’s a catastrophe.
 this is not kid’s stuff.
 don’t go around as if you are a hero and do harm to us innocent citizens.
 this is a serious warning from our survivors!- kim min-cheol0456: lol.
 i think you guys complaining about him have never engaged in any fighting.
 how can you hold any individual player accountable?└ hhh44: yeah, that’s right.
 it’s the system that makes the situation more and more complicated.
 you guys should give it a thought before posting your articles!except for a few, lots of people on the korean server outpoured their complaints about the necromancer.
they watched the numerous incidents that had happened on the korean server as bystanders, but when they were faced with a real threat this time, they didn’t sit idle.
the people in suwon village were also checking their reaction.
 while checking every comment on the community bulletin, heyon felt irresistible anger.
“look at this, dad.
 how rude they are! this is the way they are reacting.
”she ran to her father muyon and showed him her cell phone.
“look what these people are babbling about! these guys were stuck in their rooms and didn’t do anything even when the whole village was flooding.
 how dare they try to complain like this?”however, muyon, who read all the bad comments, remained calm instead of sympathizing with her.
“heyon, don’t bother about that.
”“how can’t i, dad? what do they know about the necromancer? they are spitting out disrespectful words when they don’t know anything about him.
 what if other people agree with them?”although heyon was seething with anger, muyon was still working on the “castle wall blueprint” without any change in his facial expressions.

“honey, there are people like that everywhere.
 those who are smart and know which way the wind is blowing find the right way for themselves.
”“but what if these people behave nasty?”“their complaints are nothing in this world.
 think of their complaints as a child’s whining.
”“do you think so?”“sure.
 just wait and see.
”as he said, their negative opinions briefly appeared on the server but didn’t last long.
 above all, they were far from the mainstream opinion on the korean server.
many on the korean servers supported the necromancer.
 besides, the huge forces that held the real power of each region supported the necromancer.
“wow, they have begun to support necromancer!”“i told you so! if you go on the right path, they will follow you.
”the first group to participate in the upcoming war was “hunter company” in chonan.
[1,024] the hunter company supports the world tree camp and joins their fight.
-author: president baek │ hit: 111,463*we plan to temporarily suspend all our business and start an all-out battle to protect the south korean server.
 we are recruiting “field staff” for this purpose, so we ask for your attention.
 (loot from the war will be distributed fairly.
)[comments: 41]junho, the president of the hunter company, was looking up at the building under renovation with a serious expression.
 it was damage left by the necromancer who appeared at the dramatic moment when the japanese ninjas stormed in a few days ago.
“it’s all thanks to the necromancer that this building, our company, and all of us have survived.
”when he turned around, muttering like that, there were about a hundred employees lined up behind him.
 all of them were ready for the upcoming battle.
junho looked around them and shouted, “we must repay his help! so we will protect the world tree from the invasion of the north korean server by joining hands with the necromancer!”he spoke like a general.
 all of the staff responded loudly to his words.
“understood!”“okay!”although they were smaller than other groups, they were elites who had been trained as mercenaries throughout the country.
“good…”junho felt overwhelmed by their spontaneous support.
 he had a considerable reputation for his mercenary business, but he felt like he began something extraordinary.
‘if i can draw the necromancer’s attention by doing this…”he already became an ardent follower of the necromancer.
he decided to join the necromancer in the upcoming battle partly because he was the latter’s avid fan.
“all hunter company employees, prepare for a march to the north immediately!”“yes, sir!”the ‘hwarang guild’ in busan also declared their support of the necromancer.


although they suffered tremendous damage following the japanese server’s invasion, they had no intention of sitting idle when the mainstream started again, for they also knew that they survived thanks to the necromancer.
“the world tree camp had warned us of the japanese aggression even before the korean-japanese war broke out.
”“we ignored the warning and responded foolishly…”the leaders of the hwarang guild discussed the issue of participation in the mainstream war at an emergency meeting.
 however, there were few dissenting voices among them.
“nonetheless, he came running to save us.
 we have to pay back his help by all means!”“that’s right! everyone must work together regardless of which camp they belong to, just like the necromancer of the world tree camp did.
”“i agree! this is also for the sake of the entire south korean server.
”moreover, as one of the central forces of the south korean server, the hwarang guild had a sense of responsibility to solve the problem.
 this was also the will of their former leader, hyunmin jang, who was killed during the korean-japanese war.
“if our leader had survived, he would not have hesitated to dispatch our troops.
 according to his will, let’s dispatch half of the troops.
 i think we can send at least 600 players.
”“i will send the advance team first by helicopter.
”they announced their decision on the community and decided to participate in the war like the hunter company.
[1,044] the ‘hwarang guild’ is going to fight the enemies with the world tree camp.
-author: hwarang press │ hit: 145,551*since we are recovering from the damages of the korean-japanese war, we cannot send many troops, but we are dispatching 600 in recognition of the seriousness of the problems we face.
 our gallery guild will fight with a sense of responsibility.
[comments: 24]

 