\section{chapter 184}






 soon, the wizards gathered together and began to prepare a large-scale shield.
 as they promised, they knew the way to kill the necromancer.
 they had prepared some countermeasures against the aerial attack.
 the first step was creating a shield.
however, sungwoo also expected they would use a large-scale shield, so he had prepared a secret weapon to destroy it.
something approached the wizards who were preparing magic from behind.
at that moment, they stormed and killed the wizards in an instant.
“keeeeeeeeh!rattle- rattle-they were none other than orun and a group of ghouls.
it wasn’t just concrete and corpses that bone wyverns threw.
 numerous small undead were also thrown, mixed with them.
 it was a way only available for the undead that could keep reviving indefinitely.
“protect the wizards!”“we’re done without the shield!”however, they couldn’t stop the ghouls from attacking them in the rampage, and eventually, they could not use any magic.
soon, a monster’s huge wings began to descend over the square without any hindrance.
it was the biggest monster, the bone wyvern alpha male, and his arrival meant that the necromancer also landed on the ground.
– caution! the ‘fellblade’ begins in the area.
– caution! ‘death response’ begins in the area.
– caution! a ‘poisonous cloud’ is formed in the area.
the necromancer began to transform the place into a battlefield for him.
pusheeeeeee―a cloud of black smoke spread and squeezed everyone’s breath.
 and a huge number of undead poured out in the smoke that couldn’t be seen before.
rattle! rattle!“block them!”“hey, move back and make the space for a retreat!”
“damn it.
 there are too many people for me to get out of this place.
”but sungwoo’s attack didn’t end there.
tuk- tuk- tuk-tuk-raindrops started to fall on their heads.
 at first, they couldn’t even notice it was raining.
-you have been exposed to poisonous clouds.
“uh? what the heck is this?”“ugh! this, what is this?”but soon they developed fatal symptoms.
 after they were exposed to raindrops containing poison, they began to have seizures in groups.
since they were already pushed aside by the monsters, they immediately collapsed one by one as soon as they were exposed to the poisonous raindrops.
-body functions have been weakened due to unknown energy.
* all stats decrease.
 (-2)furthermore, when sungwoo entered into the status of a demigod, he even lowered the stats of the players around him.
thud! thud! thud!this time, large undead such as bone drake and ogre skeleton rushed to the huge crowds of weakened humans and trampled on them like a bulldozer.
sungwoo also swung the grim reaper and moved forward, spamming the repeating crossbows.
 finally, he stood in front of the stairs on the platform.
on top of the 89 stairs, on the platform, stood gen.
 chongong.
 he was looking down at sungwoo without moving a step.
those who appeared to be his bodyguards lined up on both sides of him.
four cameras were still operating beyond a small shield formed by two wizards.
“necromancer…”why was gen.
 chongong still and turning on the broadcast in a situation where he and his men were devastated by the monsters controlled by the necromancer? it seemed he decided to have the cameras film the scenes of him killing the necromancer by all means.
otherwise, there was nothing he could rely on now because everything he intended, the forces that he built up until now, and the public opinion that he manipulated in his favor were collapsing all at once.
“…”
the camera lens captured two men at the same time.
gen.
 chongong glared at the necromancer then raised his right hand toward the sky.
at that moment, a ray of light shot from his palm.
clang!the beam of light burst like a firecracker then began to scatter in all directions.
its final destination was the head of the pirates.
– caution! the ‘fanatic’s runaway’ begins in the affected area.
along with the message, the pirates trembled as if they were electrified by something.
“ahhhhh! let’s sacrifice ourselves!”“for the safety of our general!”“everyone, defend the general!”they screamed weirdly as if they were insane then began to rush sungwoo like crazy.
until a little while ago they moved back to fight in a safe zone, but as soon as gen.
 chongong acted, they immediately ran wildly to chase sungwoo.
‘it’s part of his skill of brainwashing the players,’ sungwoo thought.
it seemed that gen.
 chongong seemed to have a job specializing in brainwashing low-level players.
 and he formed an unshakable army blindly following him.
 his ability to control the pirates was based on this.
“sacrifice your lives to protect our general!”“don’t be afraid of death!”their eyes already turned red and the heat was surging all over their bodies as if they were given strong buffs.
 although they were weakened by poisonous clouds, they didn’t seem to suffer any pain.
“charge at him!”hundreds of pirates rushed to sungwoo like crazy.
 all of them spammed their skill, pushing out the undead to some extent.
the four cameras busily captured the scenes that seemed to be a turnaround on the part of the pirates.
“wow! our revolutionary army has risen again! they are back on the offensive, pushing out the necromancer! maybe, maybe…”the camera operator commented excitedly with some vague hope, but unfortunately, sungwoo was calm and composed.
“it looks like they don’t know which way the wind is blowing.
”the players would stop moving anyway when they died.
 moreover, when they died, they were transformed into souls and corpses that would be helpful to sungwoo.
 nonetheless, they were recklessly sacrificing themselves.
 even though they were devastated by the necromancer several times in the past, they still didn’t know how to deal with him.
-you have strengthened the undead with exploited souls.
 (12 stacks)1) attack power increases by 30% (+3)2) defense increases by 30% (+3)3) immunity to magic increases by 30% (+3)4) moving speed increases by 30% (+3)“if you get hit twice by me and still don’t know me, you have to die.
”sungwoo strengthened the undead using accumulated souls.
after that, the pirates’ offensive was markedly weakened, and soon, the undead began to push them aggressively.
“ahhhhhhhh!”“don’t stop attacking them to the end! kuuuueeeeh…”the ranking officers of the red revolutionary army, who were watching the fight, were astonished.
only then did they realize that they had been serving the wrong leader.
“what the heck?”“general, we can’t beat him.
”watching them, sungwoo slowly climbed the stairs.
“general! come on! issue an order!”“we must retreat now!”their voices were broadcast in real-time on three chinese servers and the taiwanese servers.
an anubis-shaped necromancer approaching them was displayed on the screen.
“stop him! even if we suffer big damages, we have to kill him here and start over! if we can kill him, our people will support us…”

when he said that, a werehog standing on his right raised an iron hammer.
then, he began to stride toward sungwoo.
whooooooooooh!the werehog struck the hammer toward sungwoo’s head.
 however, after avoiding it quickly, sungwoo stretched out his left hand and grabbed his wrist.
“kueeeeeeeeeeeh!”sungwoo broke his thick wrist with his tremendous grip.
 since sungwoo had mighty power similar to a stage four werebull, he could easily deal with this kind of monster.
sungwoo threw him down the stairs then lifted the grim reaper.
-‘evil spirit bomb’ dwells in your weapon.
“he’s using his skill! protect the general!”even though they felt they were defeated, the brainwashed officers tried to protect gen.
 chongong.
 they surrounded the general.
but at that moment, sungwoo swung the grim reaper.
goo-gung goo-goo-gung!when the black wave overwhelmed them, the only person who was standing was gen.
 chongong.
 the officers had already been torn apart to the extent they could not be recognized.
it seemed he could survive alone because his bracelet formed a shield around him.
 however, as if it was a disposable item, the bracelet broke and fell on the ground.
“huh huh huh, how could you break into my area and destroy my men? i thought you were a negligible being…” said gen.
 chongong with a hollow smile.
sungwoo stood tall in front of him and said, “why do you think you are stronger than us?”“what did you say?”“do you think if the territory of your country is large, you are good in every way? you still seem to be mistaken, but you have never been stronger than me for a single moment.
”the only thing the pirates surpassed sungwoo and his party in was their numerical superiority.
 they used brainwashing to control a huge number of mediocre troops, and they achieved victories by resorting to extreme strategies such as mini-games.
however, after they had been severely defeated twice, they realized they could not confront the necromancer with a human-wave strategy alone.
 nevertheless, it seemed that they could not still admit it.
“the reason you have been defeated every time is because you haven’t given up that terrible delusion.
”the scene of the necromancer lifting the grim reaper was broadcast live on the servers in korea, china, and taiwan at the same time.


 