\section{chapter 201}

                             




the third camp passed the first test, although other camps were at a loss, not knowing how to attack the monkeys.
 how did the necromancer hunt the monkeys?bumyeol, the vanguard of the demon camp, gnashed his teeth after looking at the message.
“necromancer…”he prepared a special item to kill him, but if he wasn’t on the same battlefield as the necromancer, he wouldn’t have a chance to use the item.
in the worst situation, he might have to chase them without firing the arrows while attacking the dungeon.
“what kind of method did the necromancer use?”they had no way of knowing it.
about 20 minutes prior, it was jisu who offered the clue about the attack.
she put on the item “goblin face armor” she had received from sungwoo.
 when she wore the mask with the goblin’s teeth exposed, only her insensitive eyes were exposed, creating a terrible atmosphere.
“…”she closed her eyes and developed her extended senses.
-in proportion to your agility level, the damage of the ‘sword’ increases.
 (+44%)-through the ‘goblin’s senses’, you can detect objects around you more clearly.
even without such a mask, she had supernatural senses, so she could feel all the movements in her area.
when she was given the buffs by wearing the goblin’s face armor, she could detect what was going on nearby without light.
“i can hear them…” she said.
“pardon?”“the sound of something bumping.
 it’s a key.
 giant furry beasts on a tree… one of them has the key.
”that showed how sharply she could sense and detect what was around her.
sungwoo and his party trusted her and pondered over the best way to hunt the monkeys based on the information she provided.
“sungwoo, how can we lure them down the trees? they are swinging back and forth above our heads, but they aren’t coming down.
”
they also seemed to be aiming for sungwoo’s party, but they only followed at a certain distance as if to check their opponent’s capabilities.
“should we climb the trees?” hanho asked.
of course, they could not.
 among the subordinate spirits under sungwoo’s control, ‘ghoul’ or the ‘zombie birds’ could attack them on the tall trees, but they could not get the monkeys to come down.
‘giant jannabi’ were large monsters, and dozens of them were flocking around in a group.
so, if they recklessly tried to climb the trees, they would be annihilated before they could attack them.
“we have to make them come down.
”“how?”“they think the treetops are the safest place for them, so we have to change their thinking.
”“i know, but how?”sungwoo used the skill without replying to him.
– caution! a ‘poisonous cloud’ will be created in the target area.
but he could not confirm the effect of his skill even though mana was consumed.
that was understandable, given that the raindrops could not be seen because the enormous trees intertwined with each other formed a dense roof, blocking the light.
“sungwoo, what did you do a moment ago?”sungwoo waited patiently.
tuk- tuk-standing in a dense forest, they could avoid the splattering raindrops because raindrops fell on numerous leaves rather than falling on the ground.
 then, what about the top of the trees?the answer was they could get wet enough from the raindrops.
as expected, shortly afterward, the monkeys’ disgusted shouts came out.
the giant jannabi near the top of the trees were exposed to the poisonous clouds little by little.
“uh, they’re coming down!”kuuuuuuuuuuuuuuuh! kuuuuuuuuh!
they began to descend to a slightly lower position, screaming in embarrassment.
the ghouls sungwoo had summoned in advance began to move.
while hiding behind the wooden pillars, the ghouls climbed up the trees in no time and struck down the giant jannabi.
thud-they got tangled with each other before falling.
 they were large and strong, but when three ghouls charged at them at the same time, they had no choice but to fall from the trees.
wooduuuuuuuuuuk!however, as they were 3 meters tall and heavy, their grip was very powerful.
they easily threw off the two ghouls stuck on their arms then plucked the heads of the ghouls from their bodies.
it seemed that the ghouls alone could not confront them, but sungwoo already prepared another option to deal with such a situation.
green eyes emerged from the dark.
then, two black chains came out suddenly and wrapped around their necks and shoulders.
he was minsok, the death knight.
 he used the “abyss chain” skill to bind the giant jannabi.
kaaaaaah!minsok was dragged a couple of steps when one of them strained his body, but minsok started pulling it backward with a chain on his wrist.
 the ghouls’ grip was nothing compared to minsok’s pull.
“hey! you can’t beat me!”at the next moment, jisu appeared in front of the giant jannabi and cut its neck before stepping back.
 then, sungwoo lifted his repeating crossbow at the monkey who couldn’t escape at all.
tung! tung! tung! tung! tung!the monkey suffered severe damages before collapsing.
-you have earned 135,440 gold by hunting ‘giant jannabi’.
“wow, one down!”kaaaaaaaaaaah!there was a series of loud screaming over their heads as if to shake the whole forest.
other monkeys who witnessed the death of their fellows began to scream and threaten them.
since they belonged to the primate species, it seemed they had a strong kindred for each other.
ooh! ooh! oooh! ooooh!“ugh, it’s so noisy.
”they got excited and started to jump around the trees, but they didn’t dare to come down.
“i don’t think they want to come down yet.
”“well, when they get exposed to the poisonous clouds once again, they will have to.
 so, everybody, take a deep breath.
”“pardon? deep breath?”something flew through the trees.
 they were “zombie birds.
” they grabbed the corpses of ghouls and giant jannabi and climbed up.
the zombie birds flew near the tops of the six trees where about ten giant jannabi were hanging.
 the monkeys were gazing at their fellows’ corpses the zombie birds were carrying toward them.
something that they couldn’t imagine happened.
“explode!”bang! bang! bang!flames rose amid the explosions of the corpses, but they could not make the monkeys come down.
what sungwoo aimed at was the next attack.
poooooooooh-he let out the ‘abyssal breath’, which was an additional effect of the ‘corpse explosion’ skill after he had upgraded it.
compared to the original abyss breath, it was rather weak but alone it was powerful enough to disrupt the monsters’ bodily functions.
keeeeeeeeeeeh! keeeeeeeeh!the monkeys who breathed in the abyssal breath got frightened and began to come down to the lower trunks of the trees.
 some of them lost their balance, rolling down the trees.
khhhhhhhheck!

the undead hiding around them charged at them instantly.
in other words, they entered the realm of the necromancer’s team.
-you have earned 170,000 gold by hunting ‘giant jannabi’.
-they have become your subordinate spirits.
sungwoo could obtain a large number of giant jannabi skeletons.
by using them, sungwoo took down the monkeys on the tall trees and started hunting, and soon, he caught the giant jannabi who was holding the key.
this was the necromancer’s unique, all-weather strategy.
“phew! we’ve finally found it.
”-the ‘third camp (temporary)’ has obtained the key.
then, the bronze key on the neck of the monkey glowed green.
 it floated by itself into the air and flew away!“it seems the key is leading us to the next area, right?”the third camp was ahead of the other two camps now.
in the meantime, about a hundred people were waiting near the entrance of the dungeon.
most of them were affiliated with the angel or demon camp, so they were guarding the entrance in case of an unexpected situation.
with a strange and tense atmosphere, some people had been talking since the others entered the dungeon.
“hi folks, although it’s quiet here right now, i guess they are now fighting severely inside the dark forest.
 pardon? well, the reason i keep broadcasting despite nothing special happening is that we want to bring you the news as soon as possible.
 i would appreciate it if you keep watching this broadcast!”they were camera operators doing their broadcasts, including reporter ahn.
since all the camps decided not to have the cameramen film their attack for fear of exposure to the other party, they had no choice but to wait outside the dungeon.
the only information they could get was from the status messages written above the entrance of each camp.
 however, since it took time for them to attack successfully, the broadcast was getting boring, and the viewers began to complain one by one.
one of the cameramen shouted.
“look at that! reporter! look!”

 