\section{chapter 210}






 -you have earned 9,000 gold by killing a player.
-you have gained a ‘holy shield’ for 15 seconds thanks to the ‘slayer of faith’ skill.
 (400/400)“damn it! who are you bastard?” one of the players shouted.
“oh, you still don’t know me? i’m the strongest and holy asura thief!”the man who was following the necromance around was known as a dumb guy, but hanho ranked 23 on the server at level 15.
given his stats, he was as strong as any decent player.
 besides, all sorts of odd skills and items created strange synergies, so he could get rid of enemies without getting injured at all.
puck! puck!‘great! wonderful! perfect!’he swung six arms back and forth like a spider wrapping its prey in the web and defeated the players of the demo camp one by one.
“ahhhhhh!”“you crazy filthy monster, go away!”-you have earned 10,000 gold by killing a player.
-you have earned 9,000 gold by killing a player.
‘man, ain’t i cool? i am no longer a weak player who used to confront the goblins or the pirates in kanghwa island! i’ve evolved!’at the same time, hanho even became conscious of the people around him.
‘oh, my god! is the cameraman filming my fight?’reporter ahn and his assistants were broadcasting the fierce fight between the necromancer team and the demon camp soldiers, and hanho stood out among his team members at the moment.
‘well, they have no choice but to film my activities.
 are they going to make a fan club for me? gosh, i wish i had practiced writing down my signature!’convinced that the cameraman was taking shots of his activities, hanho stretched out his six hands in all directions as if a peacock was spreading its tail wings.
“phew… you guys are…”
muttering like that, he slowly turned his head in the direction of the camera.
then, he shouted cheerfully, “you guys are too slow…”however, the camera angle was pointing in the opposite direction to capture the best star on the korean server, the necromancer.
“to become a superhero, i think i’ve got to be independent of him.
 i can’t shake off my image as an assistant of the necromancer as long as i stay with him,” said hanho, laughing bitterly.
“i wonder if robin next to batman feels like me.
 a star-crossed dark horse… well, it’s okay with me for now….
”in the meantime, what the cameramen were following intensively was something important enough to draw everybody’s attention.
almost when the fierce battle between the two camps was at an end, their leaders were going to have a one-on-one confrontation.
 it was a breathtaking event, so it was natural that all the cameras were fixed on that fight.
“ah…”reporter ahn was so impressed by the necromancer’s fighting he was speechless for a while.
 his assistant camera operators felt the same.
ahn soon came to his senses after realizing he forgot to explain to his audience the fighting scenes for so long.
 then, he mentioned something that his audience could agree with.
“oh, my god! what happened a moment ago?”inside the still camera angle, the necromancer was looking down at someone.
then, he slowly opened his mouth.
“as i told you, there is someone who said the same thing as you.
 now, you are the second.
”a red-skinned giant was lying down helplessly under his feet.
their duel was over so quickly.
the necromancer was standing in the place where reporter ahn and his assistants turned all the cameras.
 numerous trees around him were broken down, and the whole ground was overturned, strewn with blood everywhere.
with the traces of such a rough fight revealed graphically, the necromancer in the form of a black wolf was standing tall alone.
 it was strong evidence that he was the winner.
the necromancer defeated the challenger without using his subordinate spirits.
 the loser was lying under his feet.
“kuhuuuuuuuuuh, kuh…”it was none other than the red-skinned giant, bumyol, the head of the struggle guild.

he vomited blood, and his whole body was covered with blood.
then, he barely said, shaking his head, “how did i get defeated like this? my stats were ahead of you, though my level was not…”he muttered as if he couldn’t understand the situation.
sungwoo responded, “it looks like you received a lot of extra stats at the hidden quest?”“…”bumyol just looked up at sungwoo without refuting him.
 as he said, bumyol’s level was 18, ranked 10th on the korean server, which lagged far behind sungwoo’s level 22.
however, he survived the hellish mt.
 taebaek and received several bonus stats after clearing all kinds of hidden quests.
 so, he thought that his strength would be comparable to those ranked in the top five of the korean server.
‘although i was a bit short of the required level, i could overcome it by eating fresh ginseng and receiving the mountain spirit.
’he ate the “ginseng with the mountain god’s spirit” at the risk of his health, and as a result, he gained a tremendous increase in his abilities.
so he thought he could defeat the necromancer.
“why do you think that only you walked a special path? did you say you were a warrior of mt.
 taebaek? i think you are trapped in a very autistic narcissism.
”the necromancer’s criticism frustrated bumyol.
 his point was bumyol was like a frog in a well.
“no! no!”then, he denied reality and exerted all his strength to pick up his ax.
“no!”he swung his ax at the necromancer’s neck, but the latter acted faster.
it was bumyol who had his head cut off by the necromancer.
-you have earned 145,000 gold by killing a player who gained ‘special strength’.
the necromancer’s final blow meant that their fight was over.
with the blunt noise of something falling, the players of the demon camp began to lay down their weapons.
 it was a declaration of surrender.
when they realized they were driven into a corner with no way out and their leader was killed, it was natural they lost the fighting will.
“we lost.
 please, just spare our lives!”uijin, the player who appeared to be the deputy commander of the struggle guild, approached and begged for his life cowardly.
 however, sungwoo ignored him and checked the items on the ground first.
it looked like beads with strong energy, but its texture was close to clay.
[item information]-name: tolerance of mt.
 taebaek-grade: legend-category: consumption-effect: by accepting the ‘mountain spirit’, you can get a tremendous increase in stats.
 also, your ‘affinity and dominance’ over nature and spirits increases drastically, and in some cases, you can obtain the ‘power of the mountain god (deity)’.
*caution! to fully absorb it, you need a ‘physical strength value ‘ of at least 80.
 (recommended value: 100)* caution! if you have a different ‘deity’, they can conflict with each other and have adverse effects.
-description: a ‘tolerance’ has been formed because an unqualified person absorbed ‘the ginseng with the mountain god’s spirit’ and had his strength sucked by the ginseng.
 this tolerance has absorbed the stats of the arrogant person, becoming stronger.
this item had the effect of giving its owner the ‘deity’ status.
 however, given that there was no clash between the necromancer and bumyol, it seemed that the latter didn’t meet the conditions for eating the ginseng with the mountain god’s spirit.
“by the way…”sungwoo looked at uijin who was awkwardly hesitating to speak to him.
he was stunned as if he was electrocuted when sungwoo turned to him.
“where did she go?”“pardon? who do you mean…”“the woman in the red sweatshirt!”sungwoo asked him about jisu’s whereabouts because he saw uijin sucking her up with some paper.
 then, he put down his backpack and hastily pulled out something.
“here you are!”

uijin took out something with trembling hands.
 it was a rolled paper.
sungwoo carefully received it and checked the item information.
[item information]-name: real landscape painting of the god’s spirit-grade: legend-category: consumption-effect: instantly moves the ‘designated object’ to the position in the picture.
 (cooldown: 96 hours)“where is it in this picture?”“it is the deepest place on mt.
 taebaek.
”“mt.
 taebaek? is it a safe place?”although sungwoo was not worried about her safety, he still wanted to know exactly where she was now.
uijin said, shaking his head, “no, it’s not safe.
”“why? didn’t you say that you guys killed all the monsters in mt.
 taebaek?”when the struggle guild joined the demon camp, they said emphatically on the air that they fought several monsters on the hellish mountains and killed them all.
“well, it’s partly true, but it was a lie.
”then, he confessed that they had not yet killed all the monsters.
“we tried our best to get rid of them all, but couldn’t.
 since the mountains were so deep, the monsters got stronger and increased all the more.
 they even fought among themselves for hegemony, and after all, one monster unified all of them in one area…”he swallowed, then continued, “the king of the great mountain was born.
”king of the great mountain?“what is that?”

 