\section{chapter 442}

jisu was also thrown away by the surprise attack.
 it seemed that gangsok hit her with lightning at that moment.





"gosh, how could you vermin touch my body?" shouted isabella, looking at sungwoo scornfully.
 but sungwoo was laughing at her.
"you are trapped!""what the heck?"she felt some eerie, then slowly lowered her head.
 only then did she realize that she was tied to something.
 a green rope was wrapped around her body, tightening her harder and harder.
the unusual light emitting from it showed it was something very unusual.
"how about it? do you like it?"isabella tightened her grip on the rope.
 although she was "polymorph" born into a human form, she was a dragon.
 in other words, even if she was tied with a ship chain, she could break it off easily as if it was a straw.
but she could not cut or untie the rope binding her tightly.
 no wonder she began to be embarrassed.
"what did you do to me?" she shouted.
sungwoo stood up, dusting his pants.
 even though his ribs were crushed, he could achieve his goal.
 "this is a necklace that was custom-made for you at the hearst workshop.
 it's a masterpiece of magic engineering, and i'm glad it seems to fit you well.
 i am happy to see it.
"it was 'gleipnir'.
 more precisely, it was gleipnir that was improved by magic engineering.
inspired by the corpse of the dragon killed by the world tree, sungwoo specially asked the hearst workshop for an item that could bind the dragon.
"ahhhh! take this off from me!"she shouted, looking at gangsok, but sungwoo blocked them.
 it was the moment when the most menacing creature to sungwoo was neutralized.
 
now it's time for him to confront gangsok face to face.
"gangsok, let's have a talk in a quiet place…""sure.
 i know a good place.
"at that moment, the demons soared into the sky, then started to merge into a single point.
 and a very deep pit opened in the sky- caution! the 'gate of the underworld' has opened in that area.
suddenly, all the colors of the world disappeared, leaving only white and black lines.
follow current novels on lightnovelworld.
com- your name has been written in the life and death book.
frowning hard, gangsok looked up at the sky.
 for the first time, his expression hardened.
- you have entered the underworld.
in an instant, he was in a different space.
sungwoo, the owner of this space, walked up to him and asked, "did you say the gamblers bet on you?"gangsok didn't respond to his question.
 "then go and tell them.
>an indescribably wondrous aura appeared over his head, and its light and its darkness engulfed gangsok's face.
"tell them they can cancel their bet on you if they can.
 tell them to bet on me.
>
the moment sungwoo dragged gangsok into the underworld, it was inevitable that gangsok and the dragon would collapse.
 "drop your weapon," jisu said.
 with the dragon and isabella unable to move with gleipnir wrapped around them, there was nothing grace and vivo could do by themselves.
 "i don't want to repeat.
"jisoo stared at vivona.
 grace already put down her wand.
"shit!" after all, vivona removed a huge shadow, swearing at jisu.
 it was certain that he would die in vain if he resisted now.
 shortly afterward, master hearst descended to the ground and checked the condition of gleipnir.
"um, there's nothing wrong with it.
"since he had never tested it before, he wanted to double-check it just in case it could be broken.
 "we never know what this dragon bitch would do, so bind her more tightly with the world tree vines.
 if possible, tie her mouth too.
 i didn't know a dragon was noisier than a parrot.
""what the heck! what are you going to do about me this time! ugh, i'm going to kill you all!"isabella shouted at the top of her voice, struggling to get freed from the sturdy rope by trying to fire breath, but she could not do anything.
gleipnir limited the abilities of those bound by it and nullified their skill effect, so she could not do anything.
follow current novels on lightnov‌elworld.
com"it's just useless.
 so don't waste your breath.
 do you think the rope is made out of ordinary material? this rope is the masterpiece among masterpieces made by grinding all kinds of top-level magical items into the gleipnir base.
""shut up! you dotard! how can you ramble in front of me?""um, yes, next time i'm going to make a prison of thorns to put you in, or a cast iron pot to boil you inside.
"while watching hearst speaking to isabella, hanho clapped his hands as if something came to his mind suddenly.
 "oh, that's what i figured!"then he ran to hearst.
"master hearst!""huh? what's up?"hanho said with a fishy smile, "hehe, can you make something like a butterfly net? a very long one.
"hearst made a big frown at his absurd request.
***gangsok han, ranked no.
 1 on the korean server.
this mystery man was always ahead of sungwoo, or anybody else.
of course, he was ahead of sungwoo not only in rankings but also in other fields.
 sungwoo has defeated numerous players who were higher level than him.
but this guy was somewhat different from them.
 'he was always at the top without any exception.
'only now did sungwoo realize why gangsok was always at the top.
 it's because this was not the first time he survived in the game.


'nonetheless, the situation is different now.
'sungwoo dragged him into the 'underworld'.
 of course, gangsok would know that he would see his power weakened because this was sungwoo's exclusive area.
the moment even the conceited 'emperor' of the chinese server knew it, he became frustrated and even begged for sungwoo's mercy.
'but this guy is unusually calm.
'gangsok just looked around the underworld slowly.
 and then he spat out a word, "man, you have a pretty bad hobby, don't you?"updated from lightnovelworld.
c­omsungwoo responded, "yup.
 this is a very bizarre place.
""ugh! i don't like it.
 i want to get out!"gangsok and the fairy butterfly complained like that, but sungwoo didn't respond.
he didn't feel it necessary to talk with gangsok anymore.
 he immediately summoned the undead corps.
rattle! rattle!thousands of undead and hundreds of ghosts charged fiercely at their single enemy.
but gangsok didn't avoid them.
a white electric current gushed out of his staff, wrapping his body and smashing the area around him.
 because of that, the undead, let alone the ghosts, could not approach him.
 'it's a sacred power.
'sungwoo instantly noticed it.
 more precisely, it was some sort of discomfort.
 the electric current he exhaled clearly contained "sacredness".
'is it an item?'he was not sure if it was an item or a skill, but it was clear that gangsok prepared the weapon with which he could confront the necromancer.
 but he could not overwhelm the necromancer with that weapon alone.


 