\section{chapter 241}

                            it wasn’t easy to recognize the shape of the trampled corpses strewn here and there because they were run over by the mounted ghost knights.





purrrrrrr―sungwoo nodded, watching the tragic massacre that took place in just a few seconds.
he was confident that durahan would be an important force in the future.
sungwoo was satisfied with his performance.
 so, sungwoo put him in the “void haven.
”“now, let’s stop going down further.
 let’s go inside instead.
”since he found out that the security guards were chasing them, he needed to change the route of their movement.
 even if sungwoo and jisu were not discovered by the chasing guards, any further delay would give doctor more time to prepare a counter attack.
sungwoo and jisu came out through the corridor on the second basement floor.
after destroying all cctvs around them, they checked the “facility map” attached to the wall.
after examining it, sungwoo realized they were in the ‘abyss research sample center’.
“abyss research sample? does it mean the undead?” jisu asked.
“i think so.
”as jisu guessed, there were a series of containment facilities installed along the corridor, containing undead monsters such as zombies, ghouls, and skeletons.
the room where durahan was located was the most secure facility at the end of the corridor.
‘if i had been caught, i would have been contained in a room next to durahan’s.
’
these guys would clearly have considered sungwoo as the most important specimen.
he felt terrible when he thought about it.
“well, looking at the map, the 5th basement floor is the lowest.
 do you think he is there?” she asked, pointing at the very end of the facility map.
“i think so.
”sungwoo and jisu moved along the corridor.
 on both sides of the corridor, all kinds of undead were trapped in iron bars where the “purification energy” flowed.
however, perhaps because they felt the power of death possessed by sungwoo, the undead stepped back whenever sungwoo passed by as if they were paying homage to him.
sungwoo found a familiar face inside the iron bars at the end.
 it wasn’t undead.
“necromancer.
”it was none other than the white werewolf with the capabilities of psychometry.
“it’s already our third meeting,” the werewolf said casually, leaning against the wall.
“i know you’re not supposed to be trapped in a place like this.
 aren’t you, great wizard of the four human beasts?”he was the “the bearer of white” among the four human beasts leading the human beasts of the korean servers, but he was so miserable and shabby now.
 trapped inside the iron bars, he was wearing a thick chain around his neck: a prisoner.
“well, i had no other choice but to collapse when i became weak.
 i was nothing but a hound, after all.
”he laughed bitterly.
“was there a power struggle here?” sungwoo asked.

sungwoo remembered the enslaved human beasts when he infiltrated into this building.
 so, he judged there was a power struggle within the evolutionary society.
 the white wolf’s camp was defeated, given his current situation.
“power struggle? from the beginning, everything was a race for survival.
 we fell prey to their game because we didn’t choose the cards.
”there was resentment in his voice.
sungwoo asked cynically, “is terrorism part of the race for survival?”the terror of the breath of abyss they committed at yeongdeungpo station was unforgivable.
 the white wolf hung his head and slowly opened his mouth.
“if all of those were quests issued by the system, could you believe it? what if the system forced us to attack you?”the first quest given to the human beasts was to eat ten players.
 as a reward, the system restored their reason.
 based on that, the system wasn’t hoping for harmony between the players and the human beasts.
the white wolf continued.
“so, the system punished us for not choosing cards by forcing us to become beasts.
 then, the system used us for its extreme purposes, namely as hostile forces against you guys, the main players of the game.
”sungwoo didn’t know that was the main purpose of the system’s creation of human beasts.
“but it was up to you to proceed with the quest, right?” sungwoo asked.
“that’s right.
 we chose to do it so easily because we just wanted to survive even if we became beasts.
 we knew it was bad, but we decided to adapt to the system.
 we’re not asking for your forgiveness.
 we’re villains without any excuses and nothing can change that.
”as he said, no matter what the circumstances involving the human beasts, nothing changed.
 they are sungwoo’s enemies.
 so, sungwoo intended to kill all of them.
but if the human beasts had not conformed to the system, would sungwoo have made a different choice? sungwoo did not think about it longer.
‘no, they must have conformed to the system and attacked the players.
’sungwoo also acted freely to survive.
 after all, the greatest evil was the ‘system.
’“necromancer, i don’t want you to understand us.
 however, i will help you to get rid of the leader of the evolution society…”“dr.
 yu?”the white wolf nodded and said, “it’s embarrassing, but we were used by him from the beginning.
 he pretended to help us after we were turned into human beasts, but he used us as his slaves and materials for experiments.
 in the end, we couldn’t stand it and rebelled but ended up being slaves like this.
”sungwoo once again wondered if he could believe what the white wolf just said.
 however, it was clear that this could not be dr.
 yu’s trap.
it meant that at least he could get useful information from the white wolf.
“where is this bastard, dr.
 yu?”the white wolf stood up from its seat and pointed to the floor.
“he is probably in a hidden room on the eighth basement level of this building.
 maybe dr.
 yu is also ready to meet you.
”“ready?”“yes, he is serving another race, not the absolute race.
 probably, he is trying to use the power of that weird halo.
 i recommend you go down there quickly before he does it.
 the 6th to 8th basement floors are restricted areas, so it will be very difficult for you to penetrate them.
”as expected, the 5th basement floor marked on the map was not the final floor.
 there was a larger facility beneath it.
‘as expected, he seems to be preparing something just in case i came to this place.
 i don’t know what will happen if i give this guy more time.
’sungwoo looked into the white wolf’s eyes and said, “i think you know there is a way for me to go down there easily.
”

since the white wolf was once an executive of the evolution society, he probably had more detailed information.
 sungwoo needed it.
the white wolf smiled for the first time, then said, “if you promise not to kill our human beasts living as slaves after killing dr.
 yu, i’ll tell you.
 they were skeptical about killing players in the first place.
”the white wolf offered the human beasts’ lives and freedom as the condition.
“then, let me also tell you my premise.
 regardless of the system, promise that you guys will live quietly in a remote place when you are saved.
”“sure, i promise.
 i know we will be killed by you if i break that promise.
”“then, tell me how to get to dr.
 yu, quickly.
”“this facility is circular.
 if you break through the wall over there in the 12 o’clock direction, you’ll see a secret elevator.
 it’s the only direct passage down to the 8th basement level.
”“is it safe?”“i do not know.
 i don’t know what he might have done there, but there is no other passage that will take you there as fast as it does.
 otherwise, you’ll have to break through some tough security guards.
”sungwoo turned right away.
 he could not afford to stay there any longer.
“hey, necromancer!”the white wolf grabbed the iron bars and shouted a warning.
“as for the one that dr.
 yu is serving, i don’t know what it is! but it’s a wicked creature with tremendous force! you have to be careful about that creature.
 remember!”it didn’t matter what the creature was.
sungwoo was determined to confront an unknown “creator”, not to mention the absolute race that he declared as his enemy from the beginning.


 