\section{chapter 434}

sungwoo found an icon on the northwest side of the map.
 judging from the scale written at the bottom, it was about 14 km away from where he was standing.





sungwoo clicked the icon.
[region details]- location: sacred cradle- ownership: angel's camp- purpose: reproduction of angels* it is 18.
45 km away from your current location.
'wow, it's more detailed than i think.
'with this map alone, sungwoo could understand to some extent what kind of place it was that he saw for the first time.
"over here! i've discovered something else!"advertisements    the search team found something again.
 something huge was hidden in the shadow beneath the sandhill.
 "airship?""yes, it looks like an airship.
"it certainly looked like an airship made with magic engineering technology, but it wasn't the type of an airship like the one built by the wpu's hearst workshop.
it was close to a light airship fitted with a huge airbag containing hydrogen.
"i just have an idea why the airship flew over here.
 somebody came here ahead of us?"this place was open only to the one who blocked 20 attacks by the outsider.
 was there any possibility that anybody came here? sungwoo felt an ominous feeling when an explosion was heard over the sandhill.
bang! "this one?"".
.
.
"
sungwoo immediately got on bone dragon and soared into the sky to check over the sandhill.
 "i've confirmed two explosions in the form of fire pillars in the northwest, about 18 km away from here!" the aerographer reported to him.
in fact, he didn't have to report because the flames of the explosion were still rising so clearly far away.
kugugugugugugu.
red flames flashed between the blue sky and the white sand desert.
 "that place is…"sungwoo opened the map again.
"isn't this the angel's cradle?"the angels' corpses that they found on the way here, the airship, and the explosions that occurred in the angel's cradle.
obviously, someone came here first.
sungwoo approached the messenger and looked for kyungsoo who was standing on the deck of the messenger.
 "kyungsoo, please check out the inside of the airship with the human beasts.
 using their psychometric skill, you can find out who came here first.
"having said that, he looked at the white wolf, who, in turn, looked at him with a nod.
sungwoo turned, relying on them to hold out here.
 'if someone came here first and advanced ahead of us, this is definitely not good news.
'if that's true, it would mean that someone was trying to achieve sungwoo's goal first.
***a huge shadow of the bone dragon ran over the pure white sand, reaching the point where the explosions occurred.
'this is the sacred cradle.
'the sacred cradle, which was kind of a factory where angels were made, was a huge pyramid-shaped structure.

"somebody seems to have attacked that building!" junghoon shouted.
as he said, there were two holes drilled in the northern slope of the great pyramid.
it seemed to have been hit by a powerful fire attack.
kaaaaaaaaaaah!at that moment a swarm of angels was pouring out from the hole as if they touched the hive.
"enemy! respond immediately!"since they confronted these kinds of enemies, they responded quickly.
"ready to fire bug hunter!"they cross-fired the 'bug hunter' they had already loaded and killed all the angels coming out of the hole.
after that, the special commando unit stormed into the hole and got rid of the remaining angels who survived the bombardment.
 when the enemies increased again, they retreated and started bombardment.
"since they were once devastated, they can't seem to respond properly! someone must have attacked them!"apparently, an unidentified attack, whose evidence was found on the north side of the pyramid, devastated the inside of the pyramid.
so the angels crawling out of the hole seemed to be the remnants who survived the attack.
"then we need to get rid of them quickly and find the traces of those who came before us!" sungwoo said, moving his undead army.
sungwoo said so and moved the undead corps.
"understood!" so they began hunting the angels.
four liches under sungwoo's control were also in the process of being in sync with each other for the synergy effect.
"crackle! master, i will besiege the ground!"victor moved the skeleton troops he could handle and started setting up flying weapons on the ground of the pyramid.
"hey, victor! let me spread a poison mist over there! you'll be able to block the vision of your enemies!"minsok also controlled the troops on the ground while communicating with victor.
 since he was lich of 'skeleton mage', he had various buff magic.
grrrrrrrrrrrr! grrrrrrrrrrrr!but it wasn't easy for mir to communicate with others, but he was supporting them with his innate sense.
'yeah, they're helping me a lot.
'since he commanded numerous armies for a long time, sungwoo was the master of leading his troops on the battlefield.
 nonetheless, he also had limits as a human being.
 but the addition of four liches to his force took off lots of load from him, so he could make himself available at other places.
when they were exposed to the battles repeatedly, liches also gradually leveled up.
- lich (victor) has slightly leveled up.
 * you can use 'void haven'.
"wow, master! i, too, have gained the right to use void heaven!"each time victor leveled up, his skill grade went up or he received new skills.
 this time what he obtained was void heaven.
 of course, unlikesungwoo who obtained a master craftsman grade right away, victor started with an elementary level.
 that's why he could not use the fellblade, and the number of subordinate spirits he could keep was limited to 50.
but that wasn't the end.
- some of the powers of the 4 knights of the apocalypse (war authority) have been changed to the condition of 'available'.
this was the war authority', the first of the 'powers of the 4 knights of the apocalypse' he obtained through the synergy of the 'appearance of the apocalypse'.
 sungwoo checked the details.
- select the target (army) to summon.
1) prisoners' unit (currently summoned)2) gigantes (can be summoned)3) sealed person (cannot be summoned: below a comprehensive grade)

until now, sungwoo could summon only prisoners' unit, but when the liches that enjoyed synergy effects satisfied a comprehensive grade by leveling up, the no.
 2 option was given.
"gigantes?"gigantes literally means the giant race.
 as the word is plural, more than one giant would come out, but it didn't look like many of them would pop up in droves.
it may not be the only one that comes out, but that doesn't mean it's going to pour out.
'i guess i know what it is.
'in other words, sungwoo could summon the prisoners' unit if he preferred quantity over quality, or gigantes if he preferred quality over quantity.
 of course, it didn't mean one of them was better than the other, so he had to make a strategic choice, depending on the situation.
kuuuuuuuung-at that moment the ceiling of the pyramid collapsed with the sound of roaring, throwing out huge dust.
 "the building is collapsing!"at first, the building didn't seem to withstand the big shock, but that was not true.
kooooooooooooooooh-"something is coming from within!"when junghoon shouted at sungwoo, something pure white was arising from the gray smoke.
advertisements    "it's a giant!"it was the huge head of a giant, who was as tall as a building.
the terrific mouth torn vertically, which was unique to the angel race, was opened wide as if it would swallow the world tree fleet.


 